### 2023-10-03 No Diamond for 3 layers.tex
No Diamond theorem
The first draft of No Diamond theorem

\documentclass[]{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\ReLU}{\mathrm{ReLU}}

\title{Proof part 1: 3 layers}
\date{}

\begin{document}

\maketitle

First we consider the case when there are only three layers: input layer, one hidden layer, and output layer. For convenience, we assume that the output only has one node. Of course, we assume all active functions are ReLU function.

We use $c_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the hidden layer and use $x$ to denote the output node. We use $W$ to denote the weights and $W_{bc}$ and $W_{xb}$ to denote the components. We use capital letter $B$ to denote bias, although it is not important here.

\begin{definition}
	1. We use $b$ to denote the node before ReLU and $\hat{b}$ to denote the node after ReLU: $\hat{b} = \ReLU(b)$.

	2. $\bar{f}$ is the upper bound approximation function of DeepPoly, and $\underline{f}$ is the lower bound approximation function.
\end{definition}

\begin{theorem}
	If there following conditions holds, then the bounds of $x$ obtained by DeepPoly are equal to the actual bounds:

	1. All DeepPoly triangle are right-angled triangle: for any ReLU node $b$ that upper bound $u(b)>0$ and lower bound $l(b)<0$, the approximation of lower bound is the zero function $\underline{f}(b)=0$.

	2. No Diamond: for any input node $c$, any output node $x$, any two paths $p_1,p_2$ from $c$ to $x$ along the direction of forward propagation. If $p_1$ is $c,b_i,x$, $p_2$ is $c,b_j,x$, then for $W_{b_jc}W_{xb_j}$ and $W_{b_ic}W_{xb_i}$, either one of them is $0$, or they have the same sign: both positive or negative.
\end{theorem}

\subsection*{One} First, we compute the bounds obtained by DeepPoly. Without loss of generality, we only consider the upper bound of $x$.   By the algorithm, the DeepPoly upper bound of $x$ is computed by following steps: \begin{align}
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(b_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(b_i)+B_x\\
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+B_x\\
 =& C+\sum_{W_{xb_i}<0}W_{xb_i}\cdot\underline{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\cdot\bar{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)\\
 =& C+\sum_{c_j}c_j\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\\
 \rightarrow& C+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i<0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot l(c_j)\\
 &+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i>0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot u(c_j)
\end{align} Here, $\bar{k_i}$ is the coefficient of $\bar{f_i}$, which is a linear function, and $\underline{k_i}$ is the coefficient of $\underline{f_i}$, which is also a linear function. $C$ is the sum of all constants that occurs in above computations. $K_i$ is the coefficient $\bar{k_i}$ or $\underline{k_i}$ depending on $i$. Notice that by the definition of DeepPoly, all $K_i$ are non negative.

Among these formulas, (1) to (4) are abstract formula with formal variables $b_i,c_j$. The result of (5)(6) is the upper bound of DeepPoly for node $x$.

For for each fixed $c_j$, because we assumed no Diamond, so all (for different $b_i$) $W_{xb_i}W_{b_ic_j}$ must have the same sign, or be $0$, and so is $\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i$. So we assign each node $c_j$ a sign of $+,-,0$,  if at least one of $W_{xb_i}W_{b_ic_j}$ is positive, at least one of $W_{xb_i}W_{b_ic_j}$ is negative, or all $W_{xb_i}W_{b_ic_j}$ are 0. Then we use $s(c_j)$ be $u(c_j)$ or $l(c_j)$ or $0$ if $c_j$ has sign of $+$ or $-$ or $0$.

Then (5)(6) can be simplified as \begin{align}
	=C+\sum_{c_j}s(c_j)\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i
\end{align} This is the DeepPoly upper bound of $x$.

\subsection*{Two} Second, we show that when each $c_j$ of $+,-$ sign gets $s(c_j)$ value, the actual value of $x$ is the same as its DeepPoly upper bound, hence the DeepPoly upper bound is the actual upper bound.

Using the chain from (4) to (2), (7) is equal to: \begin{align*}
&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(\sum_{c_j}W_{b_ic_j}s(c_j)+B_i)\\
+&\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(\sum_{c_j}W_{b_ic_j}s(c_j)+B_i)+B_x
\end{align*}

We only need to show when all $c_j$ of $+,-$ sign get $s(c_j)$ value, each $\bar{f_i}(\cdots)$ in above formula (or $\underline{f_i}$) is equal to the actual value of $\hat{b}_i$.

\subsubsection*{positive} We fix a node $b_i$ that $W_{xb_i}>0$. If so, every $W_{b_ic_j}$ has the same sign as $W_{x_bi}W_{b_ic_j}$, and hence has the same sign as $c_j$ or is $0$ (and if $c_j$ has sign $0$, then $W_{b_ic_j}=0$, too). Consider all nonzero $W_{b_ic_j}$: because \begin{align}
	b_i = \sum_{c_j} W_{b_ic_j}c_j+B_i,
\end{align}  when all $c_j$ of $+,-$ sign get $s(c_j)$ value, $b_i$ also gets its upper bound. Because $b_i$ is in the second layer, this upper bound is equal to the DeepPoly upper bound of $b_i$.

Moreover, by the algorithm of DeepPoly, for any case of $\bar{f_i}$, if $b_i$ get its DeepPoly upper bound, then $\bar{f_i}(b_i)=\ReLU(b_i)$.

Put all together, when all $c_j$ of sign $+,-$ gets values $s(c_j)$, $b_i=\sum_{c_j}W_{b_ic_j}s(c_j)+B_i$ gets its actual upper bounds and DeepPoly upper bounds, and then  $\bar{f_i}(b_i)=\ReLU(b_i)$, the actual value of $\hat{b}_i$. This is what we want to show.

\subsubsection*{negative}Now we consider a node $b_i$ that $W_{xb_i}<0$. All are similar. Now, each $W_{b_ic_j}$ has the opposite sign of $c_j$. So when all $c_j$ of $+,-$ sign get $s(c_j)$ value, $b_i$ also gets its lower bound and DeepPoly lower bound. By the assumption, when $b_i$ gets its DeepPoly lower bound, $\underline{f_i}(b_i)=\ReLU(b_i)$.

151+124+103+48+3(estimate)=428

0 : 1, 6.942969230753979, 933.6970219612122

open 30 : 59 : -1, 1.3304800987255705, 213.07373809814453, DiamondMin of Min: -2.4831832946871297

open 0:   59 : -1, 2.2208665044849285, 110.11069464683533, DiamondMin of Min: -3.2142924202998118

open 20:  59 : -1, 1.5128416712774397, 169.37895846366882, DiamondMin of Min: -2.5436423082465973

open 40: 59 : -1, 1.1588057492305743, 167.29228901863098, DiamondMin of Min: -2.322909620171307

open 50: 59 : -1, 1.1332793237397172, 216.03394603729248, DiamondMin of Min: -2.3194345600969135

open 50: 59 : -1, 1.136410977665245, 250.3934416770935, DiamondMin of Min: -2.3194345600969135

open 50 (more data): 59 : -1, 1.1033637386628505, 321.2751393318176, DiamondMin of Min: -2.279701100000497

open 10: 59 : -1, 1.7965610184250298, 144.45073246955872, DiamondMin of Min: -2.8121700263290466

%random open 10: 59 : -1, 2.0868988971016167, 133.93379545211792, DiamondMin of Min: -3.070953068366777

%random open 20: 59 : -1, 1.9800122543451073, 130.6924500465393, DiamondMin of Min: -3.0701026929909143
%
%random open 20: 59 : -1, 1.97995359889014, 135.06353521347046, DiamondMin of Min: -2.9642806539605853

random open 21: 59 : -1, 1.8202823109335369, 158.56950044631958, DiamondMin of Min: -2.926562550850029

random open 21: 59 : -1, 1.8113843758166142, 128.9297330379486, DiamondMin of Min: -2.986175395636058

random open 31: 59 : -1, 1.617607152194705, 142.7976849079132, DiamondMin of Min: -2.7544434938921665

random open 31: 59 : -1, 1.6338272022581422, 147.04282569885254, DiamondMin of Min: -2.734869999570412

random open 41: 59 : -1, 1.4376834177337172, 141.38413166999817, DiamondMin of Min: -2.591134103101991

random open 51: 59 : -1, 1.2285876079490041, 218.22643494606018, DiamondMin of Min: -2.461825229746404

random open 61: 59 : -1, 1.0442270697364395, 315.7167875766754, DiamondMin of Min: -2.219210859797969

random open 61: 59 : -1, 1.0458496294859592, 375.4530429840088, DiamondMin of Min: -2.219210859797969

\end{document}

### 2023-10-03 No Diamond for 3 layers.tex
Update No Diamond for 3 layers.tex
Delete some error lines
test
lili
proof

@@
 
+\begin{definition}
+	A pair of paths $(\pi,\pi')$
+	is called {\em compensating} if they start in the same neuron $a$ and ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative.
+\end{definition}
+
+Intuitively, compensating paths will partially cancel out each other as they conribute the same weight $w(a)$ to the weight of the same neuron $w(z)$, but with opposite sign. 
+It is not simple to take this compensation into account because of ReLUs: the particular compensation will depend upon the weight of intermediate nodes seen along $\pi$ and $\pi'$, 
+as when one of this node gets negative input, it will clip it to 0.
+
+\begin{theorem}
+	If for all $(a,d)$ there is no compensation paths $(\pi,\pi')$ 
+	in the network from $a$ to $d$, then the LP approximation is 
+	$100\%$ accurate (or deepoly with the $f(x) \geq 0$ abstraction only, never using the 
+	$f(x) \geq x$ abstraction). 
+\end{theorem}
+
+\begin{proof}
 First we consider the case when there are only three layers: input layer, one hidden layer, and output layer.
@@
 This is what we want to show.
+\end{proof}
 
@@
 By the assumption, when $b_i$ gets its DeepPoly lower bound, $\underline{f_i}(b_i)=\ReLU(b_i)$.
-
-151+124+103+48+3(estimate)=428
-
-0 : 1, 6.942969230753979, 933.6970219612122
-
-open 30 : 59 : -1, 1.3304800987255705, 213.07373809814453, DiamondMin of Min: -2.4831832946871297
-
-open 0:   59 : -1, 2.2208665044849285, 110.11069464683533, DiamondMin of Min: -3.2142924202998118
-
-open 20:  59 : -1, 1.5128416712774397, 169.37895846366882, DiamondMin of Min: -2.5436423082465973
-
-open 40: 59 : -1, 1.1588057492305743, 167.29228901863098, DiamondMin of Min: -2.322909620171307
-
-open 50: 59 : -1, 1.1332793237397172, 216.03394603729248, DiamondMin of Min: -2.3194345600969135
-
-open 50: 59 : -1, 1.136410977665245, 250.3934416770935, DiamondMin of Min: -2.3194345600969135
-
-open 50 (more data): 59 : -1, 1.1033637386628505, 321.2751393318176, DiamondMin of Min: -2.279701100000497
-
-open 10: 59 : -1, 1.7965610184250298, 144.45073246955872, DiamondMin of Min: -2.8121700263290466
-
-%random open 10: 59 : -1, 2.0868988971016167, 133.93379545211792, DiamondMin of Min: -3.070953068366777
-
-%random open 20: 59 : -1, 1.9800122543451073, 130.6924500465393, DiamondMin of Min: -3.0701026929909143
-%
-%random open 20: 59 : -1, 1.97995359889014, 135.06353521347046, DiamondMin of Min: -2.9642806539605853
-
-random open 21: 59 : -1, 1.8202823109335369, 158.56950044631958, DiamondMin of Min: -2.926562550850029
-
-random open 21: 59 : -1, 1.8113843758166142, 128.9297330379486, DiamondMin of Min: -2.986175395636058
-
-random open 31: 59 : -1, 1.617607152194705, 142.7976849079132, DiamondMin of Min: -2.7544434938921665
-
-random open 31: 59 : -1, 1.6338272022581422, 147.04282569885254, DiamondMin of Min: -2.734869999570412
-
-random open 41: 59 : -1, 1.4376834177337172, 141.38413166999817, DiamondMin of Min: -2.591134103101991
-
-random open 51: 59 : -1, 1.2285876079490041, 218.22643494606018, DiamondMin of Min: -2.461825229746404
-
-random open 61: 59 : -1, 1.0442270697364395, 315.7167875766754, DiamondMin of Min: -2.219210859797969
-
-random open 61: 59 : -1, 1.0458496294859592, 375.4530429840088, DiamondMin of Min: -2.219210859797969
+This is what we want to show.
 

### 2023-10-04 No Diamond for 3 layers.tex
PROOF

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
 \theoremstyle{definition}
@@
 
+All DNNs $N$ considered only use ReLU activation function, and are fully connected (some wheight between neurons can be 0 though).
+A path $\pi$ in $N$ is a sequence of neurons $(a_i)_{i=0}^n$ such that for all $i < n$, layer($a_{i+1}$) = 1 + layer($a_{i}$).
+
 \begin{definition}
@@
 \begin{theorem}
-	If for all $(a,d)$ there is no compensation paths $(\pi,\pi')$ 
-	in the network from $a$ to $d$, then the LP approximation is 
-	$100\%$ accurate (or deepoly with the $f(x) \geq 0$ abstraction only, never using the 
+	If for all $(a,c)$ there is no compensation paths $(\pi,\pi')$ 
+	in the network from $a$ to $c$, then the LP approximation is 
+	$100\%$ accurate (or DeepPoly with the $f(x) \geq 0$ abstraction only, never using the 
 	$f(x) \geq x$ abstraction). 
@@
 \begin{proof}
+
 	First we consider the case when there are only three layers: input layer, one hidden layer, and output layer.
-For convenience, we assume that the output only has one node.
-Of course, we assume all active functions are ReLU function.
 
-We use $c_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the hidden layer and use $x$ to denote the output node.
-We use $W$ to denote the weights and $W_{bc}$ and $W_{xb}$ to denote the components.
-We use capital letter $B$ to denote bias, although it is not important here.
+%We use $c_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the hidden layer and use $x$ to denote the output node. 
+%We use $W$ to denote the weights and $W_{bc}$ and $W_{xb}$ to denote the components. We use capital letter $B$ to denote bias, although it is not important here.
 
-\begin{definition}
-	1. We use $b$ to denote the node before ReLU and $\hat{b}$ to denote the node after ReLU: $\hat{b} = \ReLU(b)$.
+\begin{itemize}
+    \item We will denote by $a_i$ nodes in the input layer, and by $b_i$ nodes in the hidden layer.
 
-	2. $\bar{f}$ is the upper bound approximation function of DeepPoly, and $\underline{f}$ is the lower bound approximation function.
-\end{definition}
+	\item We use $x^-$ to denote a node before applying the ReLU activation function (but after the linear weighted sum) and $x^+$ to denote the node after applying the ReLU: $x^+ = \ReLU(x^-)$.
 
-\begin{theorem}
-	If there following conditions holds, then the bounds of $x$ obtained by DeepPoly are equal to the actual bounds:
+	\item We denote by $\bar{f}(x)$ the upper bound approximation function of DeepPoly (using the $f(x) \geq 0$ abstraction only) for node $x$, 
+	and $\underline{f}(x)$ its lower bound approximation function.
+\end{itemize}
 
-	1.
-All DeepPoly triangle are right-angled triangle: for any ReLU node $b$ that upper bound $u(b)>0$ and lower bound $l(b)<0$, the approximation of lower bound is the zero function $\underline{f}(b)=0$.
+We want to show that for any $c$ in the output layer (3rd layer), there exist 
+input $\bar{Y}$ such that $W_{\bar{Y}}(x) = \bar{f}(c)(\bar{Y}) = \min_Y \bar{f}(c)(Y)$, and 
+ $\underline{Y}$ such that $W_{\underline{Y}}(x) = \underline{f}(c)(\underline{Y}) = \min_Y \underline{f}(c)(Y)$.
 
-	2.
-No Diamond: for any input node $c$, any output node $x$, any two paths $p_1,p_2$ from $c$ to $x$ along the direction of forward propagation.
-If $p_1$ is $c,b_i,x$, $p_2$ is $c,b_j,x$, then for $W_{b_jc}W_{xb_j}$ and $W_{b_ic}W_{xb_i}$, either one of them is $0$, or they have the same sign: both positive or negative.
-\end{theorem}
+Let $c$ be any output node.
 
-\subsection*{One} First, we compute the bounds obtained by DeepPoly.
-Without loss of generality, we only consider the upper bound of $x$.
-By the algorithm, the DeepPoly upper bound of $x$ is computed by following steps: \begin{align}
+\paragraph{DeepPoly bounds}
+
+First, we compute the bounds obtained by DeepPoly.
+The case of the lower bound is symetrical (because the abstraction $f(x)\geq 0$ is used, ensuring that the lower bound of $f(x)$ is reached at 0).
+
+The DeepPoly upper bound of $x$ can be expressed by the following steps:
+
+\begin{align}
  \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(b_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(b_i)+B_x\\
@@
  &+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i>0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot u(c_j)
-\end{align} Here, $\bar{k_i}$ is the coefficient of $\bar{f_i}$, which is a linear function, and $\underline{k_i}$ is the coefficient of $\underline{f_i}$, which is also a linear function.
+\end{align}
+
+Here, $\bar{k_i}$ is the coefficient of $\bar{f_i}$, which is a linear function, and $\underline{k_i}$ is the coefficient of $\underline{f_i}$, which is also a linear function.
 $C$ is the sum of all constants that occurs in above computations.

### 2023-10-09 Blaise.tex
blaise

--- 2023-10-04 No Diamond for 3 layers.tex
@@
 
-	\item We denote by $\bar{f}(x)$ the upper bound approximation function of DeepPoly (using the $f(x) \geq 0$ abstraction only) for node $x$, 
+	\item We denote by $\bar{f}(x)$ the upper bound approximation function of DeepPoly (using the ReLU$(x) \geq 0$ abstraction only) for node $x$, 
 	and $\underline{f}(x)$ its lower bound approximation function.
@@
 We want to show that for any $c$ in the output layer (3rd layer), there exist 
-input $\bar{Y}$ such that $W_{\bar{Y}}(x) = \bar{f}(c)(\bar{Y}) = \min_Y \bar{f}(c)(Y)$, and 
- $\underline{Y}$ such that $W_{\underline{Y}}(x) = \underline{f}(c)(\underline{Y}) = \min_Y \underline{f}(c)(Y)$.
+input $\bar{Y}$ such that $W_{\bar{Y}}(c) = \bar{f}(c)(\bar{Y}) = \min_Y \bar{f}(c)(Y)$, and 
+ $\underline{Y}$ such that $W_{\underline{Y}}(c) = \underline{f}(c)(\underline{Y}) = \min_Y \underline{f}(c)(Y)$.
 
@@
 First, we compute the bounds obtained by DeepPoly.
-The case of the lower bound is symetrical (because the abstraction $f(x)\geq 0$ is used, ensuring that the lower bound of $f(x)$ is reached at 0).
+The case of the lower bound is symetrical (because the abstraction ReLU$(x)\geq 0$ is used, ensuring that the lower bound of $\underline{f}(x)$ is reached at 0).
 
-The DeepPoly upper bound of $x$ can be expressed by the following steps:
+The DeepPoly function for $c$ can be expressed by the following steps:
+
+First, we particition the set of indices $i$ for $b_i$ as $I,I_0,I^+,I^-$ with:
+\begin{itemize}
+	\item $i \in I$ if the sign of $b_i^-=\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)(Y)=\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}$ and
+	$\underline{f}(b_i^+)=\underline{f}(b_i^-)$, and else:
+	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,
+	and else:
+	\item $i \in I^+$ if $\alpha_{b_i c}>0$, and:
+	\item $i \in I^-$ if $\alpha_{b_i c}<0$.
+	\end{itemize}
+
+Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.
+
+Then we have:
+\begin{align*}
+	&\bar{f}(c)(Y) = 
+	\sum_{i \in I} \sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}
+	+ \sum_{i \in I^+} \alpha_{b_i c} \cdot \bar{f_i}(ReLU(\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}))(Y)+ B_c 
+	\end{align*}
+
+Now,
 
  \begin{align}
- \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(b_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(b_i)+B_x\\
- \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+B_x\\
- =& C+\sum_{W_{xb_i}<0}W_{xb_i}\cdot\underline{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\cdot\bar{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)\\
- =& C+\sum_{c_j}c_j\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\\
+ &= C+\sum_{W_{xb_i}<0}W_{xb_i}\cdot\underline{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\cdot\bar{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)\\
+ &= C+\sum_{c_j}c_j\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\\
  \rightarrow& C+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i<0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot l(c_j)\\

### 2023-10-09 Yuke No Diamond for 3 layers.tex
new

\documentclass[]{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\ReLU}{\mathrm{ReLU}}

\title{Proof No Diamond (3 layers)}
\date{}

\begin{document}

\maketitle

\begin{definition}
	A pair of paths $(\pi,\pi')$
	is called {\em compensating} if they start in the same neuron $a$ and ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative.
\end{definition}

Intuitively, compensating paths will partially cancel out each other as they conribute the same weight $w(a)$ to the weight of the same neuron $w(z)$, but with opposite sign. 
It is not simple to take this compensation into account because of ReLUs: the particular compensation will depend upon the weight of intermediate nodes seen along $\pi$ and $\pi'$, 
as when one of this node gets negative input, it will clip it to 0.

\begin{theorem}
	If for all $(a,d)$ there is no compensation paths $(\pi,\pi')$ 
	in the network from $a$ to $d$, then the LP approximation is 
	$100\%$ accurate (or deepoly with the $f(x) \geq 0$ abstraction only, never using the 
	$f(x) \geq x$ abstraction). 
\end{theorem}

In this section, we only consider the case of 3 layers: that is, one input layer, one hidden layer and one output layer, which contains only one node. Of course, we assume all active functions are ReLU function. Before we introduce the proof, we list some definitions.

\begin{definition}
	1. We use $a_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the hidden layer and use $z$ to denote the output node. We use $W$ to denote the weights and $w({ba})$ and $w({zb})$ to denote the components: weight from one node to another. We use capital letter $B$ to denote bias, although it is not important here.

	2. We use $b$ to denote the node before ReLU and $\hat{b}$ to denote the node after ReLU: $\hat{b} = \ReLU(b)$.

%	3. $\bar{f}$ is the upper bound approximation function of DeepPoly, and $\underline{f}$ is the lower bound approximation function.
\end{definition}

\begin{proof}

The following definition is the most important concept in this proof.

\begin{definition}[Sign of Node]
	We define a sign function $S$ on every node $n$ such that: 	(1). $S(n)=0$ if all path from $n$ to $z$ has 0 weight; (2). $S(n)=1$ if all path from $n$ to $z$ has non-negative weight, and at least one path has a positive weight; (3). $S(n)=1$ if all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight.

	More specifically, for an input node $a_i$:

	(1) $S(a_i)=0$ if \begin{align}
		\forall b_j\ w(b_ja_i)\cdot w(zb_j) = 0.
	\end{align}

	(2) $S(a_i)=1$ if\begin{align}
		\forall b_j\ w(b_ja_i)\cdot w(zb_j) \geq 0 \wedge \exists b_j\ w(b_ja_i)\cdot w(zb_j) > 0. 
	\end{align}

	(3) $S(a_i)=1$ if \begin{align}
	\forall b_j\ w(b_ja_i)\cdot w(zb_j) \leq 0 \wedge \exists b_j\ w(b_ja_i)\cdot w(zb_j) < 0. 
\end{align}

And for a node $b_j$ in the hidden layer, $S(b_j)=1,-1,0$ if $w(zb_j)$ is positive, negative, or 0. Finally, for the output node $z$, we define $S(z)=1$.
\end{definition}

Notice that, if there is no Diamond, then $S$ is defined on all nodes, i.e., any input node must be one of above cases (1),(2),(3).

\begin{definition}
	For node $n$, we use $n^s$ to denote $S(n)\cdot n$. And we define that $n^s$ gets maximal value means that: if $S(n)=1$, then $n$ gets maximal value; if $S(n)=-1$, then $n$ gets minimal value (if $S(n)=0$, we say $n^s$ always gets maximal value).

	Similarly we define the meaning of $n^s$ gets minimal value.  
\end{definition}

\begin{lemma}[Sign and Weight]
	1. When one node $b$ (before $\ReLU$ function) gets its maximal or minimal value, $\hat{b}=\ReLU(b)$ also gets maximal or minimal.

	2. Suppose $L$ is a layer and $L'$ is the next layer. Then for any $n$ on $L$ and $m$ on $L'$, if both $S(m)$ and $w(mn)$ are nonzero, then we have that: \begin{align}
		S(n)=S(m)\mathrm{sign}(w(mn))
	\end{align}
\end{lemma}
\begin{proof}
	1. This is obvious.

	2. This can be proved by using definition. If $S(m)$ are nonzero, then there is a path $P$ from $m$ to the output node  $z$ with a nonzero weight of the same sign as $S(m)$.

	Then from $n$ to $m$ and along $P$ to $z$ is a path from $n$ to $z$, and the weight of this path is the product of weight of $P$ and $w(mn)$, which is nonzero and have the same sign as $S(m)\cdot w(mn)$. This is what we want to show.
\end{proof}

The following lemma shows the reason why this theorem is true.

\begin{lemma}
	Suppose $L$ is a layer (before $\ReLU$ function) other than output layer. Then when all $n^s$ gets their maximal value (where $n$ are node on $L$), for the next layer $L'$, and every node $m$ on $L'$, $m^s$ gets its maximal value. In formula: \begin{align}
		\max(m^s)=\sum_{n}w(mn)\ReLU(\max(n^s))+b
	\end{align}

	And for $m^s$ minimal value, we have the same result: \begin{align}
		\min(m^s)=\sum_{n}w(mn)\ReLU(\min(n^s))+b
	\end{align}
\end{lemma}

\begin{proof}
	Assume all $n^s$ on $L$ get their maximal, and $m$ is a node on $L'$, we try to show that $m^s$ gets its maximal value.

	If $S(m)=0$, then we have nothing to do. Without loss of generality,  we assume $S(m)=1$; for $S(m)=-1$, it is highly similar. Then by Lemma 1, for any $n$ in layer $L$ such that $w(mn)\neq 0$, $$S(n)=S(m)\mathrm{sign}(w(mn))=\mathrm{sign}(w(mn)).$$

	On the other hand, $$m=\sum_{n}w(mn)\hat{n}+b.$$ This means if all $\hat{n}$ with $w(mn)>0$ get maximal value and all $\hat{n}$ with $w(mn)<0$ get minimal value, $m$ also gets its maximal value. By Lemma 1, $\hat{n}$ gets maximal value or minimal value if $n$ does. So, when all $n^s$ get maximal value, $m$ will also get its maximal value.

	So, $m^s$ gets maximal if all $n^s$ in previous layer gets their maximal. The part for $m^s$ minimal value is almost the same, by replacing all maximal to minimal.
\end{proof}

From Lemma 2, we can easily see that: when all nodes $a_i^s$ in the input layer get their maximal/minimal value, all nodes $b_j^s$ in the hidden layer get their maximal/minimal value, and then the output node $z$.

The rest part is to show, interval arithmetic, and hence any approximation as accuracy as it, can get these exact bounds.

\begin{lemma}
	Suppose $L$ is a layer and $L'$ is the next layer, and  the lower and upper bounds for each node $n$ such that $S(n)\neq 0$ in $L$ stored by the approximation method Interval Arithmetic equal to the exact lower and upper bounds of it.

	 Then Interval Arithmetic can obtain the exact lower and upper bounds for every node $m$ such that $S(m)\neq 0$ in $L'$.
\end{lemma}

\begin{proof}
	Suppose $m$ is a node in $L'$ such that $S(m)\neq 0$. Without loss of generality, we assume $S(m)=1$, and $S(m)=-1$ will be similar. Interval Arithmetic will compute its upper bound using $m=\sum_{n}w(mn)\hat{n}+b,$ by taking all $n$ that $w(mn)>0$ to upper bound and taking all $n$ that $w(mn)<0$ to lower bound.

	On the other hand, by assumption, for all $n$ that $S(n)\neq 0$(which is equivalent to $w(mn)\neq 0$), the upper and lower bounds stored by Interval Arithmetic is equal to their exact upper and lower bounds, i.e., their maximal and minimal values. And for every $n$, its upper bound if $w(mn)>0$ or lower bound if $w(mn)<0$ is equal to the maximal value of $n^s$.

	Hence $$u(m)_{IA}=\sum_{n}w(mn)\ReLU(\max(n^s))+b=\max(m^s).$$ This is what we want to show.
\end{proof}

Use Lemma 3, we can see the Interval Arithmetic upper and lower bounds of the output node $z$ are equal to the actual upper and lower bounds of $z$

\end{proof}

\end{document}

### 2023-10-09 Yuke No Diamond for 3 layers.tex
proof part 1

@@
 	A pair of paths $(\pi,\pi')$
-	is called {\em compensating} if they start in the same neuron $a$ and ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative.
+	is called {\em compensating} if they start in the same neuron $a$ and 
+	ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative.
 \end{definition}
@@
 
-\begin{theorem}
-	If for all $(a,d)$ there is no compensation paths $(\pi,\pi')$ 
-	in the network from $a$ to $d$, then the LP approximation is 
-	$100\%$ accurate (or deepoly with the $f(x) \geq 0$ abstraction only, never using the 
-	$f(x) \geq x$ abstraction). 
-\end{theorem}
-
-In this section, we only consider the case of 3 layers: that is, one input layer, one hidden layer and one output layer, which contains only one node.
-Of course, we assume all active functions are ReLU function.
-Before we introduce the proof, we list some definitions.
+We assume all active functions are ReLU function.
 
 \begin{definition}
-	1.
-We use $a_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the hidden layer and use $z$ to denote the output node.
-We use $W$ to denote the weights and $w({ba})$ and $w({zb})$ to denote the components: weight from one node to another.
-We use capital letter $B$ to denote bias, although it is not important here.
 
-	2. We use $b$ to denote the node before ReLU and $\hat{b}$ to denote the node after ReLU: $\hat{b} = \ReLU(b)$.
+	\begin{itemize}
+	 \item  We use $a_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the first hidden layer, etc and finally use $z_i$ to denote the output nodes.
+	For $L,L'$ consecutive layers, for $x \in L$ and $y \in L'$, we denote 
+	$w({x y})$ to denote the fixed weight from $x$ to $y$, while we use
+	$weight_Y(x)$ to denote the weights of node $x$ from initial configuration $Y$. 
+	We use $bias$ to denote bias weightt.
+
+	\item We use $b^-$ to denote the node before ReLU and $b^+$ to denote the node after ReLU: $b^+ = \ReLU(b^-)$.
+	\end{itemize}
 
@@
 
-\begin{proof}
+\begin{theorem}
+	\label{th1}
+	If for all $(x,y)$ there is no compensation paths $(\pi,\pi')$ 
+	in the network from $x$ to $y$, then the LP approximation is 
+	$100\%$ accurate (or deepoly with the abstraction $\underline{f}(x) = 0$ for the lower bound, never using the $\underline{f}(x) = x$ abstraction). 
+\end{theorem}
 
+\subsection*{Proof of Theorem \ref{th1}}
+
+First, notice that if $weight_Y(b^-)$ is maximal (resp. minimal), 
+then $weight_Y(b^+=\ReLU(b^-))$ also gets maximal (resp. minimal).
 The following definition is the most important concept in this proof.
@@
 \begin{definition}[Sign of Node]
-	We define a sign function $S$ on every node $n$ such that: 	(1).
-$S(n)=0$ if all path from $n$ to $z$ has 0 weight; (2).
-$S(n)=1$ if all path from $n$ to $z$ has non-negative weight, and at least one path has a positive weight; (3).
-$S(n)=1$ if all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight.
+	We define a sign function $S$ on nodes $n$ such that: 	(1).
+$S(n)=0$ if all path from $n$ to $c$ has 0 weight; (2).
+$S(n)=1$ if all path from $n$ to $c$ has non-negative weight, and at least one path has a positive weight; (3).
+$S(n)=-1$ if all path from $n$ to $c$ has non-positive weight, and at least one path has a negative weight.
+	In general, $S$ may not be defined on every node (e.g.
+if there is a negative and a positive path from $a$ to $c$).
+However, if there is no Diamond, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
 
-	More specifically, for an input node $a_i$:
+	For instance, for an input node $a_i$ of any 3 layer DNN:
+	\begin{enumerate}
+      \item  $S(a_i)=0$ if 
+	  for all $b_j, w(a_i b_j)\cdot w(b_j c) = 0$
 
-	(1) $S(a_i)=0$ if \begin{align}
-		\forall b_j\ w(b_ja_i)\cdot w(zb_j) = 0.
-	\end{align}
+	 \item  $S(a_i)=1$ if for all $b_j, w(a_i b_j)\cdot w(b_j c) \geq 0$ and there exists 
+	 $j, w(a_i b_j)\cdot w(b_j c) > 0$
 
-	(2) $S(a_i)=1$ if\begin{align}
-		\forall b_j\ w(b_ja_i)\cdot w(zb_j) \geq 0 \wedge \exists b_j\ w(b_ja_i)\cdot w(zb_j) > 0. 
-	\end{align}
+	\item $S(a_i)=-1$ if for all $b_j\ w(a_i b_j)\cdot w(b_j c) \leq 0$ and there exists 
+	$j, w(a_i b_j)\cdot w(b_j c) < 0$ 
+\end{enumerate}
 
-	(3) $S(a_i)=1$ if \begin{align}
-	\forall b_j\ w(b_ja_i)\cdot w(zb_j) \leq 0 \wedge \exists b_j\ w(b_ja_i)\cdot w(zb_j) < 0. 
-\end{align}
-
-And for a node $b_j$ in the hidden layer, $S(b_j)=1,-1,0$ if $w(zb_j)$ is positive, negative, or 0. Finally, for the output node $z$, we define $S(z)=1$.
+For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $w(b_j c)$ is positive, negative, or 0 respectively. Finally, for the output node $c$, we define $S(c)=1$.
 \end{definition}
 
-Notice that, if there is no Diamond, then $S$ is defined on all nodes, i.e., any input node must be one of above cases (1),(2),(3).
-
-\begin{definition}
-	For node $n$, we use $n^s$ to denote $S(n)\cdot n$.
-And we define that $n^s$ gets maximal value means that: if $S(n)=1$, then $n$ gets maximal value; if $S(n)=-1$, then $n$ gets minimal value (if $S(n)=0$, we say $n^s$ always gets maximal value).
-
-	Similarly we define the meaning of $n^s$ gets minimal value.  
-\end{definition}
-
-\begin{lemma}[Sign and Weight]
-	1. When one node $b$ (before $\ReLU$ function) gets its maximal or minimal value, $\hat{b}=\ReLU(b)$ also gets maximal or minimal.
-
-	2. Suppose $L$ is a layer and $L'$ is the next layer. Then for any $n$ on $L$ and $m$ on $L'$, if both $S(m)$ and $w(mn)$ are nonzero, then we have that: \begin{align}
-		S(n)=S(m)\mathrm{sign}(w(mn))
-	\end{align}
-\end{lemma}
-\begin{proof}
-	1. This is obvious.
-
-	2. This can be proved by using definition. If $S(m)$ are nonzero, then there is a path $P$ from $m$ to the output node  $z$ with a nonzero weight of the same sign as $S(m)$.
-
-	Then from $n$ to $m$ and along $P$ to $z$ is a path from $n$ to $z$, and the weight of this path is the product of weight of $P$ and $w(mn)$, which is nonzero and have the same sign as $S(m)\cdot w(mn)$.
-This is what we want to show.
-\end{proof}
-
-The following lemma shows the reason why this theorem is true.
-
-\begin{lemma}
-	Suppose $L$ is a layer (before $\ReLU$ function) other than output layer.
-Then when all $n^s$ gets their maximal value (where $n$ are node on $L$), for the next layer $L'$, and every node $m$ on $L'$, $m^s$ gets its maximal value.
-In formula: \begin{align}
-		\max(m^s)=\sum_{n}w(mn)\ReLU(\max(n^s))+b
-	\end{align}
-
-	And for $m^s$ minimal value, we have the same result: \begin{align}
-		\min(m^s)=\sum_{n}w(mn)\ReLU(\min(n^s))+b
-	\end{align}
+\begin{lemma}[Sign]
+	\label{lemma1}
+Let $L,L'$  are consecutive layers be of a DNN without compensation. 
+Then if both 
+$w(m n) \neq 0$ and $S(n) \neq 0$, then 
+	$S(m)=S(n)\mathrm{Sign}(w(n m))$.
 \end{lemma}
@@
 \begin{proof}
-	Assume all $n^s$ on $L$ get their maximal, and $m$ is a node on $L'$, we try to show that $m^s$ gets its maximal value.
+	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $c$ with a nonzero weight of the same sign as $S(n)$.
 
-	If $S(m)=0$, then we have nothing to do.
-Without loss of generality,  we assume $S(m)=1$; for $S(m)=-1$, it is highly similar.
-Then by Lemma 1, for any $n$ in layer $L$ such that $w(mn)\neq 0$, $$S(n)=S(m)\mathrm{sign}(w(mn))=\mathrm{sign}(w(mn)).$$
-
-	On the other hand, $$m=\sum_{n}w(mn)\hat{n}+b.$$ This means if all $\hat{n}$ with $w(mn)>0$ get maximal value and all $\hat{n}$ with $w(mn)<0$ get minimal value, $m$ also gets its maximal value.
-By Lemma 1, $\hat{n}$ gets maximal value or minimal value if $n$ does.
-So, when all $n^s$ get maximal value, $m$ will also get its maximal value.
-
-	So, $m^s$ gets maximal if all $n^s$ in previous layer gets their maximal. The part for $m^s$ minimal value is almost the same, by replacing all maximal to minimal.
+	Hence there is a non zero path from $m$ to $c$: $(m n) \pi$, which is of sign 
+	$S(n)\mathrm{Sign}(w(mn))$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(w(mn))$.
 \end{proof}
 
-From Lemma 2, we can easily see that: when all nodes $a_i^s$ in the input layer get their maximal/minimal value, all nodes $b_j^s$ in the hidden layer get their maximal/minimal value, and then the output node $z$.
+For a node $n$, we use $n_s$ to denote $S(n)\cdot n$. 
+Notice that for $S(n)=1$, $n_s$ gets maximal value whenever $n$ gets maximal value; 
+while for $S(n)=-1$, $n_s$ gets maximal value whenever $n$ gets minimal value (and vice versa). For $S(n)=0$, $n_s=0$ and thus always reach his minimal and maximal.
 
-The rest part is to show, interval arithmetic, and hence any approximation as accuracy as it, can get these exact bounds.
+\begin{lemma}
+	\label{lemma2}
+	Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. Then:
+		$$ \max(n^-_s)=\sum_{m \in L}w(m n) \max(m^+_s)+bias_n \text{ and }$$
+		$$\max(n^+_s)=ReLU(\sum_{m \in L}w(m n) max(m^+_s)+bias_n)$$
+
+	Similarly  for minimal value,	
+	$ \min(n^-_s)=\sum_{m \in L}w(m n)\min(m^+_s)+bias_n $ and
+	$ \min(n^+_s)=ReLU(\sum_{m \in L}w(m n)\min(m^+_s)+bias_n)$
+\end{lemma}
+
+\begin{proof}
+We choose $\bar{Y}$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
+	that is setting $a$ as $max(a)$ for $S(a)=1$ and $min(a)$ for $S(a)=-1$.
+At configuration $\bar{Y}$, every $a_s(\bar{Y}))=\max_Y {a_s(Y))}=max(a_s)$ is maximized.
+
+Consider any $b$ in the next layer $L_1$.
+Assume first that $S(b)=+1$.
+We have $weight(b_s)= weight(b) = \sum_{a \in L_0} w(a b) weight(a) + bias_b$.
+If every $w(a b) weight(a)$ is maximized in the same time, 
+then $weight(b_s)= weight(b)$ is also maximized.
+
+We claim that this is the case at 
+configuration $\bar{Y}$.
+Indeed, if $w(a b)=0$, any $weight(a)$ can be chosen to maximize 
+$w(a b) weight(a)$. If $w(a b)>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
+$S(b)=+1$. We have $max(a_s) = max(a)$, maximizing $w(a b) weight(a)$.
+Finally, if $w(a b)<0$ then $S(a_s) = -1$, and we have 
+$max(a_s) = -min(a)$, maximizing $w(a b) weight(a)$.
+
+Hence $b$ reaches is maximum in configuration $\bar{Y}$, and the value satisfies: 
+$$\max(b)=\sum_{m \in L}w(a b) \max(a_s)+bias_b$$
+
+The case $S(b)=-1$ is symetric:
+$\max(b_s)= -\min(b)$ is reached when minimizing $b$, which is also 
+satisfied at $\bar{Y}$.
+In both case, $weight(b_s)$ is maximized at $\bar{Y}$. Notice that $\bar{Y}$ does not depend upon $b$, so choosing $\bar{Y}$ uniformly maximize all $weight(b_s)$.
+
+This implies that $ReLU(b^-_s)$ is maximized at $\bar{Y}$, and its value is 
+$ReLU(\sum_{m \in L}w(a b) \max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\bar{Y}$.
+
+We proceed by induction over every layer of the DNN till the output layer, proving that 
+$max(z_s)=max(z)$ is reached at configuration $\bar{Y}$.
+
+The case for $min(x_s)$ is similar, reached at configuration $\underline{Y}$.
+\end{proof}
+
+Notice that for all $x$, either $S(x)=+1$ and 
+$(\min(x),\max(x))=(\min(x_s),\max(x_s))$, 
+or $S(x)=-1$ and $(\min(x),\max(x))=(-\max(x_s),-\min(x_s))$.
+In both case, these two bounds are found in Lemma \ref{lemma2},
+from configuration $\bar{Y}$ and $\underline{Y}$.
+We now show that DeepPoly will generate the same bounds 
+$\underline{f}(x)=\min(x)$ and $\bar{f}(x)=\max(x)$.
+
+\paragraph{DeepPoly bounds}
 
@@
 
-\end{proof}
-
 \end{document}

### 2023-10-09 Yuke No Diamond for 3 layers.tex
proofs

@@
 
+The DeepPoly function for $b$ can be expressed by the following steps.
+First, we partition the set of indices $i$ as $I,I_0,I^+,I^-$ with:
+\begin{itemize}
+	\item $i \in I$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case 
+	$\bar{f}(b_i^+)(Y)=\underline{f}(b_i^+)=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$, and else:
+	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,	and else:
+	\item $i \in I^+$ if $w_{b_i c}>0$, and:
+	\item $i \in I^-$ if $w_{b_i c}<0$.
+	\end{itemize}
+
+Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.
+
+We have:
+\begin{align*}
+	\bar{f}(c)(Y) = &
+	bias_c + \sum_{b \in I} w_{bc}\sum_{a} w_{a b} weight(a) + bias_{b} \\
+	& + \sum_{b \in I^+} w_{b c} \cdot \bar{f}(ReLU(\sum_{a} w_{a b} weight(a) 
+	+ Bias_{b}))(Y) 
+	\end{align*}
+
+We proceed inductively, and prove the inductive step.
+The initialization is obvious as DeepPoly is always exact for the initialization layer.
+
 \begin{lemma}
-	Suppose $L$ is a layer and $L'$ is the next layer, and  the lower and upper bounds for each node $n$ such that $S(n)\neq 0$ in $L$ stored by the approximation method Interval Arithmetic equal to the exact lower and upper bounds of it.
+	Let $L,L'$ two consecutive layers.
+	Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by DeepPoly equals to the exact lower and upper bounds of $m$.
 
-	 Then Interval Arithmetic can obtain the exact lower and upper bounds for every node $m$ such that $S(m)\neq 0$ in $L'$.
+	Then DeepPoly computes the exact lower and upper bounds for every node $n$ of layer $L'$.
 \end{lemma}
@@
 \begin{proof}
-	Suppose $m$ is a node in $L'$ such that $S(m)\neq 0$.
-Without loss of generality, we assume $S(m)=1$, and $S(m)=-1$ will be similar.
-Interval Arithmetic will compute its upper bound using $m=\sum_{n}w(mn)\hat{n}+b,$ by taking all $n$ that $w(mn)>0$ to upper bound and taking all $n$ that $w(mn)<0$ to lower bound.
+	Suppose $n$ is a node in $L'$ such that $S(n)\neq 0$ (otherwise, it is trivial). 
+	First assume $S(n)=1$. The case $S(n)=-1$ is similar.
+
+	Deeppoly computes its upper bound using $m=\sum_{n}w(mn)\hat{n}+b,$ by taking all $n$ that $w(mn)>0$ to upper bound and taking all $n$ that $w(mn)<0$ to lower bound.
 

### 2023-10-10 Yuke No Diamond for 3 layers.tex
proof

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
 \theoremstyle{definition}
@@
 	\label{lemma2}
-	Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. Then:
+	Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
+	Then:
 		$$ \max(n^-_s)=\sum_{m \in L}w(m n) \max(m^+_s)+bias_n \text{ and }$$
@@
 
+As direct corrolary of Lemma \ref{lemma2}, we obtain:
+
+\begin{corollary}
+	\label{cor1}
+	$$\max(n^-)=\sum_{m \in L, w(m n)>0}w(m n) \max(m^+) + \sum_{m \in L, w(m n)<0}w(m n) \min(m^+) + bias_n$$
+	$$\min(n^-)=\sum_{m \in L, w(m n)>0}w(m n) \min(m^+) + \sum_{m \in L, w(m n)<0}w(m n) \max(m^+) + bias_n$$
+\end{corollary}
+
 Notice that for all $x$, either $S(x)=+1$ and 
@@
 \paragraph{DeepPoly bounds}
+
+To prove that DeepPoly bounds are the same as the exact bounds computed above, 
+we show that even the box abstraction (which is easier) would reach the exact bounds.
+We proceed inductively, and prove the inductive step.
+The initialization is obvious as Box Abstraction/DeepPoly is always exact for the initialization layer.
+
+\begin{lemma}
+	Let $L,L'$ be two consecutive layers.
+	Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by box abstraction equals to the exact lower and upper bounds of $m$ (as expressed above), i.e.
+	$\bar{f}(m)=max(m)$ and $\underline{f}(m)=min(m)$.
+
+	Then Box abstraction computes the exact lower and upper bounds for every node $n$ of layer $L'$, ie $\bar{f}(n)=max(n)$ and $\underline{f}(n)=min(n)$.
+\end{lemma}
+
+\begin{proof}
+	Suppose $n$ is a node in $L'$ such that $S(n)\neq 0$ (otherwise, it is trivial). 
+	First assume $S(n)=1$. The case $S(n)=-1$ is similar.
+
+	The Box absraction computes its upper bound using:
+	$$\bar{f}(n^-)= \sum_{w(mn)>0} w(mn) \bar{f}(m^+) + \sum_{w(mn)<0} w(mn) \underline{f}(m^+) + bias_n$$
+
+	By induction hypothesis, we have 
+	$\bar{f}(m^+)=max(m^+)$ and
+	$\underline{f}(m^+)=min(m^+)$, thus 
+	applying Corollary \ref{cor1}, we obtain
+	$\bar{f}(n^-)=max(n^-)$ and 
+	$\underline{f}(n^-)=min(n^-)$.
+
+	Now, if $\underline{f}(n^-)=min(n^-)<0$, 
+	then $\underline{f}(n^+)=min(n^+)=0$, 
+	and otherwise 
+	$\underline{f}(n^+)=min(n^+)=\underline{f}(n^-)=min(n^-)$.
+
+\end{proof}
+
+\end{document}
 
@@
 	\end{align*}
-
-We proceed inductively, and prove the inductive step.
-The initialization is obvious as DeepPoly is always exact for the initialization layer.
-
-\begin{lemma}
-	Let $L,L'$ two consecutive layers.
-	Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by DeepPoly equals to the exact lower and upper bounds of $m$.
-
-	Then DeepPoly computes the exact lower and upper bounds for every node $n$ of layer $L'$.
-\end{lemma}
-
-\begin{proof}
-	Suppose $n$ is a node in $L'$ such that $S(n)\neq 0$ (otherwise, it is trivial). 
-	First assume $S(n)=1$. The case $S(n)=-1$ is similar.
-
-	Deeppoly computes its upper bound using $m=\sum_{n}w(mn)\hat{n}+b,$ by taking all $n$ that $w(mn)>0$ to upper bound and taking all $n$ that $w(mn)<0$ to lower bound.
-
-	On the other hand, by assumption, for all $n$ that $S(n)\neq 0$(which is equivalent to $w(mn)\neq 0$), the upper and lower bounds stored by Interval Arithmetic is equal to their exact upper and lower bounds, i.e., their maximal and minimal values.
-And for every $n$, its upper bound if $w(mn)>0$ or lower bound if $w(mn)<0$ is equal to the maximal value of $n^s$.
-
-	Hence $$u(m)_{IA}=\sum_{n}w(mn)\ReLU(\max(n^s))+b=\max(m^s).$$ This is what we want to show.
-\end{proof}
-
-Use Lemma 3, we can see the Interval Arithmetic upper and lower bounds of the output node $z$ are equal to the actual upper and lower bounds of $z$
-
-\end{document}

### 2023-10-20 Paper/Paper.tex
test

--- 2023-10-10 Yuke No Diamond for 3 layers.tex
@@
 
-\begin{definition}[Sign of Node]
+\begin{definition}[Sign of Node]\label{sign_of_nodes}
 	We define a sign function $S$ on nodes $n$ such that: 	(1).
@@
 
+	Similarly, 
+	if $\bar{f}(n^-)=max(n^-)<0$, 
+	then $\bar{f}(n^+)=max(n^+)=0$, 
+	and otherwise 
+	$\bar{f}(n^+)=max(n^+)=\bar{f}(n^-)=bar(n^-)$.
+
+	Hence we have equality before and after ReLU in all cases.
 \end{proof}
+
+\section{No Diamond theorem part 2}
+
+Now we try to show the part 2 of No Diamond theorem. Again, we begin with 3 layers with only one output node $z$.
+
+\begin{theorem}[No Diamond theorem, part 2] \label{no_diamond_2}
+	Using MILP method, if all nodes $b_j$ such that there is a compensating path pair $\pi,\pi'$ with $\pi = a_k,b_j,z$ are opened, then the upper and lower bounds computed by MILP are the exact max and min value of $z$.
+\end{theorem}
+
+With out loss of generality, we only need to show the max side. The min side is almost the same.
+
+\begin{definition}
+	Let $K$ be the set of all input nodes $a_k$. We define a decomposition $K=I\sqcup J$ as follows:
+
+	An input node $a_k$ is in $I$ if for any two paths $\pi,\pi'$ that begin with $a_k$ (end with $z$), they are not compensating, i.e., the weights of them are both non negative or both non positive; hence all path $\pi$ that begin with $a_k$ (end with $z$) are non negative (or non positive).
+
+	An input node $a_k$ is in $J$ if it is not in $I$. We use $a_i$ to denote input nodes in $I$ and use $a_j$ to denote input nodes in $J$.
+\end{definition}
+
+\begin{lemma}
+	A node $b_i$ in the hidden layer will not be opened in Theorem \ref{no_diamond_2} iff one of the following two happen:
+
+	1. $w_{zb_i}=0$.
+
+	2. For any input nodes $a_j\in J$, $w_{b_ia_j}=0$.
+\end{lemma}
+
+\begin{proof}
+	First, we show if one of 1,2 happens, then $b_i$ will not be opened. If $w_{zb_i}=0$, it is obvious.
+
+	If 2 happens, suppose $\pi,\pi'$ is a pair of compensating path, then $\pi = a_k,b_i,z$.
+Because this is a compensating path, $w_{b_ia_k}\neq 0$.
+But because of 2, this means that $a_k$ is in $I$, and hence there is a compensating path begin with $a_k\in I$, a contradiction.
+Therefore, $b_i$ cannot be a node in a compensating pair.
+
+	Second, we show if both 1,2 not happen, then $b_i$ will be opened.
+Because of negation 2, there is a node $a_j$ in $J$ such that $w_{a_jb_i}\neq 0$, and since $w_{zb_i}\neq 0$, $\pi=a_j,b_i,z$ is a path with a  nonzero weight.
+By symmetry, we assume, $w_{zb_i}w_{b_ia_j}>0$.
+
+	Now, since $a_j$ is in $J$, there are two paths $\pi',\pi''$ that begin with $a_j$ but $\pi''$ has a positive weight and $\pi'$ has a negative weight.
+Consider $\pi'$.
+We claim that $\pi,\pi'$ is a compensating pair that make $b_i$ opened.
+$\pi'$ cannot be $a_j,b_i,z=\pi$ because $\pi$ has a positive weight.
+So $\pi,\pi'$ are two different paths with opposite signs of values.
+
+	So, $b_i$ will be opened. Now we prove this lemma. 
+\end{proof}
+
+Because for input nodes in $I$, they also do not have compensating path pair, we can define the sign as in Definition \ref{sign_of_nodes}:
+
+\begin{definition}[Sign of Nodes in $I$]\label{sign_of_nodes_in_I}
+	We define a sign function $S$ on $I$ such that: 	(1).
+$S(n)=0$ if all path from $n$ to $z$ has 0 weight; (2).
+$S(n)=1$ if all path from $n$ to $z$ has non-negative weight, and at least one path has a positive weight; (3).
+$S(n)=-1$ if all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight.
+
+	For an input node $a_i$ in $I$:
+	\begin{enumerate}
+		\item  $S(a_i)=0$ if 
+		for all $b_j, w(a_i b_j)\cdot w(b_j c) = 0$
+
+		\item  $S(a_i)=1$ if for all $b_j, w(a_i b_j)\cdot w(b_j c) \geq 0$ and there exists 
+		$j, w(a_i b_j)\cdot w(b_j c) > 0$
+
+		\item $S(a_i)=-1$ if for all $b_j\ w(a_i b_j)\cdot w(b_j c) \leq 0$ and there exists 
+		$j, w(a_i b_j)\cdot w(b_j c) < 0$ 
+	\end{enumerate}
+\end{definition}
+
+\begin{lemma}
+	node $z$ can get its maximal value if for all $a_i$ in $I$, $a_i$ gets its maximal if $S(a_i)=1$ or $a_i$ gets its minimal if $S(a_i)=-1$.
+\end{lemma}
+
+\begin{proof}
+
+	We use $a_S$ where $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$. Then $a_I\oplus a_J = a_K$ and $c=c(a_K)=c(a_I,a_J)$.
+
+	This is because \begin{align*}
+		\max_{a_K} c(a_K) = \max_{a_J}\max_{a_I} c(a_I,a_J)
+	\end{align*}
+
+	For any fixed input of $a_J$, $c(\cdot, a_J)$ can be regarded as a DNN $D'$ with input nodes $a_i\in I$ by regarding all $a_J$ and their propagation in hidden layers as bias.
+In the simplified $D'$, there is no compensating path because of the definition of $I$.
+Therefore we can apply the No Diamond theorem, part 1 to get that: (for fixed $a_J$) $c(\cdot,a_J)$ can get its maximal value if for all $a_i$ in $I$, $a_i$ gets its maximal if $S(a_i)=1$ or $a_i$ gets its minimal if $S(a_i)=-1$.
+
+	If we use $\max(\tilde{a}_I$ to denote above values, then we have $$\max_{a_I}c(a_I,a_J)=c(\max(\tilde{a}_I),a_J).$$ And therefore, $\max c=\max_{a_J} c(\max\tilde{a}_I,a_J)$
+\end{proof}
+
+Because for any method, like MILP, the upper bound computed will not be smaller that the actual maximal value, so we only need to show, $\mathrm{UB}_{\mathrm{MILP}}\leq \max c$ in any case.
+
+Suppose $O$ is the set of nodes opened.
+Then for any $b_h\notin O$, $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias).
+Then for any subdomain $d$ in one of  $2^{|O|}$ subdomains, suppose we compute an upper bound when $a_J=\bar{a}_J$ and $a_I=\bar{a}_I$, we show that this upper bound does not exceed the maximal value of $z$.
+
+By the algorithm, $$\mathrm{UB} = B_z+\sum_{b_h\in O}w_{ab_h}\ReLU(b_h(\bar{a}_I,\bar{a}_J))+$$
 
@@
 
-The DeepPoly function for $b$ can be expressed by the following steps.
-First, we partition the set of indices $i$ as $I,I_0,I^+,I^-$ with:
-\begin{itemize}
-	\item $i \in I$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case 
-	$\bar{f}(b_i^+)(Y)=\underline{f}(b_i^+)=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$, and else:
-	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,	and else:
-	\item $i \in I^+$ if $w_{b_i c}>0$, and:
-	\item $i \in I^-$ if $w_{b_i c}<0$.
-	\end{itemize}
-
-Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.
-
-We have:
-\begin{align*}
-	\bar{f}(c)(Y) = &
-	bias_c + \sum_{b \in I} w_{bc}\sum_{a} w_{a b} weight(a) + bias_{b} \\
-	& + \sum_{b \in I^+} w_{b c} \cdot \bar{f}(ReLU(\sum_{a} w_{a b} weight(a) 
-	+ Bias_{b}))(Y) 
-	\end{align*}
+%
+%The DeepPoly function for $b$ can be expressed by the following steps.
+%First, we partition the set of indices $i$ as $I,I_0,I^+,I^-$ with:
+%\begin{itemize}
+%	\item $i \in I$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case 
+%	$\bar{f}(b_i^+)(Y)=\underline{f}(b_i^+)=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$, and else:
+%	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,	and else:
+%	\item $i \in I^+$ if $w_{b_i c}>0$, and:
+%	\item $i \in I^-$ if $w_{b_i c}<0$.
+%	\end{itemize}
+%	
+%Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.
+%	
+%
+%We have:
+%\begin{align*}
+%	\bar{f}(c)(Y) = &
+%	bias_c + \sum_{b \in I} w_{bc}\sum_{a} w_{a b} weight(a) + bias_{b} \\
+%	& + \sum_{b \in I^+} w_{b c} \cdot \bar{f}(ReLU(\sum_{a} w_{a b} weight(a) 
+%	+ Bias_{b}))(Y) 
+%	\end{align*}

### 2023-10-23 Paper/Paper.tex
part2

@@
 
-Now we try to show the part 2 of No Diamond theorem. Again, we begin with 3 layers with only one output node $z$.
+Now we try to show the part 2 of No Diamond theorem. Again, we begin with 3 layers with one output node $z$.
 
@@
 
-\begin{lemma}
+\begin{lemma} \label{lem:open_node}
 	A node $b_i$ in the hidden layer will not be opened in Theorem \ref{no_diamond_2} iff one of the following two happen:
@@
 
-Because for input nodes in $I$, they also do not have compensating path pair, we can define the sign as in Definition \ref{sign_of_nodes}:
+Now we need the function in Definition \ref{sign_of_nodes}. The difference is that now it is a partial function.
 
-\begin{definition}[Sign of Nodes in $I$]\label{sign_of_nodes_in_I}
-	We define a sign function $S$ on $I$ such that: 	(1).
+\begin{definition}\label{sign_of_nodes_in_I}
+	We define a partial sign function all nodes such that: 	(1).
 $S(n)=0$ if all path from $n$ to $z$ has 0 weight; (2).
@@
 		\item  $S(a_i)=0$ if 
-		for all $b_j, w(a_i b_j)\cdot w(b_j c) = 0$
+		for all $b_j, w(a_i b_j)\cdot w(b_j z) = 0$
 
-		\item  $S(a_i)=1$ if for all $b_j, w(a_i b_j)\cdot w(b_j c) \geq 0$ and there exists 
-		$j, w(a_i b_j)\cdot w(b_j c) > 0$
+		\item  $S(a_i)=1$ if for all $b_j, w(a_i b_j)\cdot w(b_j z) \geq 0$ and there exists 
+		$j, w(a_i b_j)\cdot w(b_j z) > 0$
 
-		\item $S(a_i)=-1$ if for all $b_j\ w(a_i b_j)\cdot w(b_j c) \leq 0$ and there exists 
-		$j, w(a_i b_j)\cdot w(b_j c) < 0$ 
+		\item $S(a_i)=-1$ if for all $b_j\ w(a_i b_j)\cdot w(b_j z) \leq 0$ and there exists 
+		$j, w(a_i b_j)\cdot w(b_j z) < 0$ 
 	\end{enumerate}
@@
 
-\begin{lemma}
-	node $z$ can get its maximal value if for all $a_i$ in $I$, $a_i$ gets its maximal if $S(a_i)=1$ or $a_i$ gets its minimal if $S(a_i)=-1$.
+Because for input nodes in $I$, they do not have compensating path pair, so the sign function is defined on
+all nodes in $I$.
+
+We use $a_S$ where $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$.
+Then $a_I\oplus a_J = a_K$ and $z=z(a_K)=z(a_I,a_J)$.		Let $a_I^*$ be the input vector that for all $a_i$ in $I$, $a_i$ gets its maximal (if $S(a_i)=1$) or $a_i$ gets its minimal (if $S(a_i)=-1$).
+
+\begin{lemma} \label{lem:reach_max}
+
+	1. Node $z$ can get its maximal value if $a_I=a_I^*$
+
+	2.
+Similarly, for every node $b$ in the hidden layer (notice that $S(b)$ is always defined since there is only one path from $b$ to $z$), for any fixed input of $a_J$,  $b(\cdot,a_J)$ will get its max/min (if $S(b)=1$ or $-1$) if $a_I=a_I^*$.
 \end{lemma}
@@
 
-	We use $a_S$ where $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$. Then $a_I\oplus a_J = a_K$ and $c=c(a_K)=c(a_I,a_J)$.
-
-	This is because \begin{align*}
-		\max_{a_K} c(a_K) = \max_{a_J}\max_{a_I} c(a_I,a_J)
+	1. This is because \begin{align*}
+		\max_{a_K} z(a_K) = \max_{a_J}\max_{a_I} z(a_I,a_J)
 	\end{align*}
 
-	For any fixed input of $a_J$, $c(\cdot, a_J)$ can be regarded as a DNN $D'$ with input nodes $a_i\in I$ by regarding all $a_J$ and their propagation in hidden layers as bias.
+	For any fixed input of $a_J$, $z(\cdot, a_J)$ can be regarded as a DNN $D'$ with input nodes $a_i\in I$ by regarding all $a_J$ and their propagation in hidden layers as bias.
 In the simplified $D'$, there is no compensating path because of the definition of $I$.
-Therefore we can apply the No Diamond theorem, part 1 to get that: (for fixed $a_J$) $c(\cdot,a_J)$ can get its maximal value if for all $a_i$ in $I$, $a_i$ gets its maximal if $S(a_i)=1$ or $a_i$ gets its minimal if $S(a_i)=-1$.
+Therefore we can apply the No Diamond theorem, part 1 to get that: (for fixed $a_J$) $z(\cdot,a_J)$ can get its maximal value if for all $a_i$ in $I$, $a_i$ gets its maximal if $S(a_i)=1$ or $a_i$ gets its minimal if $S(a_i)=-1$.
 
-	If we use $\max(\tilde{a}_I$ to denote above values, then we have $$\max_{a_I}c(a_I,a_J)=c(\max(\tilde{a}_I),a_J).$$ And therefore, $\max c=\max_{a_J} c(\max\tilde{a}_I,a_J)$
+	If we use $\max(\tilde{a}_I$ to denote above values, then we have $$\max_{a_I}z(a_I,a_J)=z(\max(\tilde{a}_I),a_J).$$ And therefore, $\max z=\max_{a_J} z(\max\tilde{a}_I,a_J)$
+
+	2.
+This is simpler because for each fixed input of $a_J$, $$b= B'+\sum_{a_i\in I} w_{ba_i}a_i,$$ where $B'$ is a constant which is the sum of rest terms, including bias and $a_J$.
+By Lemma \ref{lemma1}, we can easily see the claim of this lemma is true.
 \end{proof}
 
-Because for any method, like MILP, the upper bound computed will not be smaller that the actual maximal value, so we only need to show, $\mathrm{UB}_{\mathrm{MILP}}\leq \max c$ in any case.
+Because for any  sound method, like MILP, the upper bound computed will not be smaller that the actual maximal value, so we only need to show, $\mathrm{UB}_{\mathrm{MILP}}\leq \max c$ in any case.
 
@@
 
-By the algorithm, $$\mathrm{UB} = B_z+\sum_{b_h\in O}w_{ab_h}\ReLU(b_h(\bar{a}_I,\bar{a}_J))+$$
+By the algorithm, \begin{align*}
+	\mathrm{UB} = B_z+\sum_{b_h\in O}w_{zb_h}\ReLU(b_h(\bar{a}_I,\bar{a}_J))+\sum_{b_k\notin O}w_{zb_k}\mathrm{Approx}(b_k(\bar{a}_I,\bar{a}_J)).
+\end{align*} Here, $\mathrm{Approx}$ is the approximation function of $\mathrm{ReLU}$.
+In our case (LP), it will equal to $\ReLU$ if $w_{zb_k}<0$, or a linear function if  if $w_{zb_k}>0$.
+$\mathrm{ReLU}$ and $\mathrm{Approx}$ are both non-decrease function.
+
+Then by Lemma \ref{lem:reach_max}, for any fixed $a_J$, for all nodes $b$ in the hidden layer, $b$ will get its max/min (if $S(b)=\mathrm{sign}(w_{zb})=1,-1$) if $a_I=a_I^*$.
+Hence we have \begin{align*}
+	\mathrm{UB} \leq  B_z+\sum_{b_h\in O}w_{zb_h}\ReLU(b_h(a_I^*,\bar{a}_J))+\sum_{b_k\notin O}w_{zb_k}\mathrm{Approx}(b_k(a_I^*,\bar{a}_J)).
+\end{align*} Meanwhile, when $b_k$ reaches its max or min, we have $\mathrm{Approx}(b_k)=\ReLU(b_k)$, hence we have: \begin{align*}
+	\mathrm{UB} \leq & B_z+\sum_{b}w_{zb}\ReLU(b(a_I^*,\bar{a}_J))\\
+	= & \max_{a_I} z(a_I,\bar{a}_J)\\
+	\leq & \max_{a_J}\max_{a_I} z(a_I,a_J)\\
+	= & \max_{a_K} z(a_K) = \max z
+\end{align*}
 

### 2023-11-16 Paper/Paper.tex
proof

--- 2023-10-10 Yuke No Diamond for 3 layers.tex
@@
 
+\section{Theorem 1}
+
 \begin{theorem}
@@
 
-As direct corrolary of Lemma \ref{lemma2}, we obtain:
+As direct corollary of Lemma \ref{lemma2}, we obtain:
 
@@
 
+	Similarly, 
+	if $\bar{f}(n^-)=max(n^-)<0$, 
+	then $\bar{f}(n^+)=max(n^+)=0$, 
+	and otherwise 
+	$\bar{f}(n^+)=max(n^+)=\bar{f}(n^-)=bar(n^-)$.
+
+	Hence we have equality before and after ReLU in all cases.
 \end{proof}
+
+\section{Theorem 2}
+
+We now show that if all intermediates nodes that are on compensating pairs are opened as MILP nodes, then MILP will be correct.
+First, we do the proof with 3 layers, assuming (without loss of generality) a unique output node $z$.
+
+\begin{theorem}
+	\label{no_diamond_2}
+	Using MILP method, if every nodes $b_j$ in any compensating path pair
+	 $(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
+	 bounds computed by MILP are the exact max and min value of $z$.
+\end{theorem}
+
+By symetry, we only show the max side.
+
+\begin{definition}
+	Let $K$ be the set of all input nodes $a_k$. 
+	We define a decomposition $K=I\sqcup J$ as follows:  
+	\begin{itemize}
+ \item $k \in I$  if
+ \begin{enumerate}
+	 \item every path from $a_k$ to $z$ has weight $\geq 0$, or
+	\item every path from $a_k$ to $z$ has weight $\leq 0$.
+ \end{enumerate}
+That is, $a_k$ is not a source of a compensating pair.
+	\item $k \in J$ if $k \notin I$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
+	one with positive and one with negative weight.
+\end{itemize}
+\end{definition}
+
+\begin{lemma} \label{lem:open_node}
+	A node $b$ in the hidden layer will not be on a compensating pair iff one of the following two happens:
+	\begin{enumerate}
+	 \item $w_{b,z}=0$, or
+	 \item For every input node $j\in J$, we have $w_{a_j,b}=0$.
+	\end{enumerate}
+	We denote $B_{pure}$ the set of such nodes $b$ such that at least one of the above holds.
+\end{lemma}
+
+\begin{proof}
+	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened.
+If 1), it is obvious.
+For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$.
+It means that $a \in J$.
+A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.
+
+	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
+	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
+	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
+	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
+	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
+	Then $((a_j,b,z), \pi')$ is also a compensating pair.
+\end{proof}
+
+Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
+
+\begin{definition}\label{sign_of_nodes_in_I}
+	We define a partial sign function $S$ over nodes $n$ such that : 	
+	\begin{enumerate} 
+		 \item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
+		 \item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
+		 \item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
+		 \item Otherwise $S(n)$ is undefined.
+	\end{enumerate}
+\end{definition}
+
+Notice that $S$ is defined on all nodes $a_i$ with $i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
+Hence it is undefined only for nodes $a_j$ with $j \in J$.
+
+We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$. We also denote $a_I\oplus a_J = a_K$ and $z=z(a_K)=z(a_I,a_J)$.
+Consider $a_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
+
+\begin{lemma} \label{lem:reach_max}
+	$max_a (weight_{a}(z)) = max_{\{a \mid a_I=a^*_I\}} (weight_{a}(z))$
+
+	Further, for every intermediate node $b$ in the hidden layer, for any valuation $a^0_J$, 
+	we have $max_{\{a \mid a_J=a^0_J\}} (weight_{a}(b)) = max_{\{a \mid a_J=a^0_J,a_I=a_I^*\}} (weight_{a}(b))$.	
+\end{lemma}
+
+\begin{proof}
+	For the first statement, we use 
+	$$max_{a_K} (weight_{a_K}(z)) = max_{a_J} max_{a_I} (weight_{a_I,a_J}(z))$$
+
+	Now, for any fixed input $a^0_J$, we can regard $weight_{a_I,a^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $a^0_J$ %and their propagation in hidden layers 
+	as bias.
+In the simplified $D'$, there is no compensating path because of the definition of $I$.
+Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,a^0_J)$ reaches its maximal value for $a_I=a_I^*$, and we are done.
+
+	The second statement is simpler because for each fixed partial input $a^0_J$, 
+	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $a^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
+\end{proof}
+
+\subsection{MILP abstraction}
+
+Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
+where each variable $\alpha_b$ for the ReLU from $b^-$ to $b^+$ is:
+\begin{itemize}
+	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \in B_{pure}$
+	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \notin B_{pure}$
+\end{itemize}
+
+Notice that there is only one layer of ReLUs, in the hidden layer.
+Denote by $\mathrm{UB}$ the maximal bound on $z$ considering the MILP constraints above, with ReLUs being either linear or binary depending on whether $b \in B_{pure}$ or not.
+
+We want to show that $\mathrm{UB} = \max z$. As the MILP abstraction is a sound overapproximation, 
+it suffices to show that $\mathrm{UB}\leq \max c$.
+
+For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
+Denote by $B_O$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
+$b \notin B_{pure}$. %For any subdomain $D \subseteq B_O$, 
+Let $a^0_J$ and $a^0_I$ be fixed inputs, and consider the associated upper bound 
+$\mathrm{UB}_{a^0_J,a^0_I}$. We have:
+%We show that this upper bound does not exceed the maximal value of $z$:
+
+\begin{align*}
+	\mathrm{UB}_{a^0_J,a^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{a^0_I,a^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{a^0_I,a^0_J}(b)).
+\end{align*}
+
+where $\mathrm{AppB}(weight_{a^0_I,a^0_J}(b))$ is the upper bound of 
+the (LP) approximation of $weight_{a^0_I,a^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
+of its (LP) approximation if $w_{b,z}<0$.
+
+By Lemma \ref{lem:reach_max}, for any fixed input $a^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
+$weight_{a_I,a^0_J}(b)$ will get its maximal value for $a_I=a_I^*$,
+and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{a^0_I,a^0_J}(b)$ will get its minimal value for $a_I=a_I^*$.
+Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
+
+\begin{align*}
+	\mathrm{UB}_{a^0_J,a^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{a^*_I,a^0_J}(b)) +
+	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b)).
+\end{align*}
+
+Added FIX:
+Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
+$w_{b,z} = 0$ and $b \in B^2$ iff $w_{b,z} \neq 0$.
+Hence:
+
+$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b)) = 
+\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b))$$
+
+For $b \in B^2$, we have $w_{a_j,b}=0$ for all $j \in J$
+by definition of $B_{pure}$ (Lemma 4.), hence
+
+$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b)) = 
+\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{a^*_I}(b))
+=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{a^*_I}(b))
+$$
+
+as $\mathrm{AppB}(weight_{a^*_I}(b))=\mathrm{ReLU}(weight_{a^*_I}(b))$ since 
+$weight_{a^*_I}(b)$ is an extremal value (minimum or maximal) and 
+$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values (make a lemma about that in the begining).
+
+Hence we have: \begin{align*}
+	\mathrm{UB}_{a^0_J,a^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(a_I^*,\bar{a}_J))
+	= \max_{a_I} z(a_I,\bar{a}_J) \\
+	\leq & \max_{a_J}\max_{a_I} z(a_I,a_J) 	= \max_{a_K} weight_{a_K}(z)
+\end{align*}
+
+Considering the maximal over all inputs $a_J,a_I$, we obtain
+
+$$\mathrm{UB} = max_{a_J,a_I} \mathrm{UB}_{a_J,a_I} \leq \max_{a_J,a_I} weight_{a_J,a_I}(z)$$
 

### 2024-01-02 Paper/Paper_noProof.tex
This is the paper (draft) without the proof of No Diamond theorem.

\documentclass[8pt]{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\ReLU}{\mathrm{ReLU}}

\title{Diamond and Vericompensate}
\date{}

\begin{document}

\maketitle

\section{Introduction}

\section{Background}

\subsection{The neural network and Verification problem}

In this paper, we focus on full-connected neural network. The network has weights and bias to send the input to output along hidden layers. In formula, the input layer of a neural network is a vector $x$ in $\mathbb{R}^{d_0}$, and the $i$-th hidden layer  is a vector in $\mathbb{R}^{d_i}$, and the output layer can be a vector in $\mathbb{R}^{d'}$ or a scale. The weights, bias and activation functions decide propagate the from previous to the next layer. In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight $W^i$ is matrix of $d_i\times d_{i-1}$, the bias is a vector $b^i$ in $\mathbb{R}^{d_i}$, and the activation function is $\sigma$, then  if the $i-1$-th layer is $\hat{z}^{(i-1)}$, then the value of $i$-th layer is computed by: \begin{align*}
	{z}^{i} &= W^i\cdot \hat{z}^{(i-1)}+ b^i\\
	\hat{z}^{i}(n) &= \sigma({z}^i(n)).
\end{align*} The vector $\hat{z}$ is called pre-activation values, while $z$ is called post-activation values, and $z^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer. In our style, we also call neurons \emph{nodes} and use $a,b,c,d$ to denote them. We use $W_{ab}$ to denote the weight from neuron $b$ to $a$. We use $x$ to denote the vector of input and  $f(x)$ to denote the output.

The verification problem is to determine whether the output of a neural network will be affected under small perturbations to the input. In formula, if we use a distance $d$, and if the $x_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(x,x_0)<\epsilon\}$ where $\epsilon$ is the parameter measuring the size of perturbation. And the problem will be \begin{align*}
	\forall x\in\mathcal{D} \   f(x) = f(x_0).
\end{align*} In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
\forall x \in\mathcal{D} \  \min f(x) = \min f(x_0)
\end{align*}

If so, the question of verification can turn to the following optimization question: \begin{align*}
	\min f(x) \ s.t. {z}^{i} &= W^i\cdot \hat{z}^{(i-1)}+ b^i\\
	\hat{z}^{i}(n) &= \sigma({z}^i(n)), x\in\mathcal{D}.
\end{align*}

In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$. We consider $L^{\infty}$ norm, that is $d(x,x_0)=\max |x(n)-x_0(n)|$, the max value of distance of each dimension.

\subsection{MILP formation of $\ReLU$ functions}

It is known in literature that if $x=\ReLU(y)$, and $y$ has its upper and lower bounds $u>0$ and $l<0$ (we call this unstable node; and if $u\geq 0$ or $l\leq 0$ then it is called stable node, and does not need MILP formulation), then this function can be formulated in MILP with one integer variable $a$ valued in ${0,1}$ (i.e., a binary variable) by:

\vspace*{-4ex}

\begin{align*}
	&x \geq 0, \ 
	x \geq y-l\cdot (1-a)\\
	&x \leq y,\ 
	x \leq u\cdot a
\end{align*}

It is a standard method to compute the lower bounds and upper bounds of neurons in a pure $\ReLU$ activation network by MILP optimization, because from previous subsection, the verification problem is equivalent to an optimization problem.

However, the cost of optimization of an MILP model is very expensive, especially when the number of binaries increases: solving MILPs are NP-hard, and often needs exponential time to solve it. A typical relaxation is to change the binary variable $a$ to a continue variable, then it will be equivalent to the standard triangle LP model for $\ReLU$ function.

Our strategy is to restrict the number of binary variables, and this will definitely lose accuracy of results.  The key problem is how to use fewer binary variables to get more accuracy. That is, to choose which node to be binary, and which not.

\begin{definition}
	1. For a full-connected DNN with $\ReLU$ activation, to compute the upper or lower bound of a node (in a hidden layer or output layer), its MILP model is formulated as follows:

	(1) For every node in the input layer $a$, set a $z_a$ variable with the same input interval: $l_a\leq z_a\leq u_a$

	(2) For each hidden layer $l^i$, set two variables , $z_c,\hat{z}_c$ for each node $c$ in this layer for pre-activation and post-activation.

	The constraints for pre-activation $z_a$ is the natural linear equation by the network. 	$$z_c=\sum_{d\in l^{i-1}} W^i_{cd} z_d+b^i_c.$$

	The constraints for $\hat{z}_a$ is defined by the standard MILP formulation mentioned above with known upper bound and lower bound as parameters.

	\vspace*{1ex}

	Since we only consider such MILP models, so when we say an MILP model, it is for a full-connected DNN with $\ReLU$ activation.

	2. In an MILP model, we say a $\ReLU$ node is open, if the binary variable corresponds to this function is still an binary variable; otherwise, it is relaxed as a continue variable. 
\end{definition}

We aim is to find an algorithm, to decide which nodes should be opened such that we can have more accuracy.

\section{Compensate, Diamond and Path chosen}

In this section, we will develop the process of open node chosen.

\subsection{Compensating pair}

In this subsection, we will explore the key factor for the loss of accuracy in our LP/MILP models. The answer is the \emph{compensating pair}.

In above figure, $a$ is the input neuron, $bc,b'c'$ are two nodes in the hidden layer, before and after the activation function, and $d$ is the unique output neuron. The numbers next to the arrows are the weights. So, $W_{ba}=1$ and $W_{b'a}=-1$, $W_{dc}=W_{dc'}=1$. The paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is the so called compensating pair, or a Diamond. The key point is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.

But if both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.

The definition of compensating pair is as follows:

\begin{definition} In a full-connected network with $\ReLU$ as activation function:

	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes from one layer by one layer. We call the first node source node and the last node target node.

	2. The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ba}\cdot W_{cb}\cdot W_{dc}\cdot W_{ed}\cdot \cdots$$

	3. A compensating pair is a pair of path with the same starting node and end node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).

	We also use \emph{Diamond} to call a compensating pair in the network.
\end{definition}

To explain the of meaning of compensating pair, we introduce the following theorems about Diamond:

\begin{theorem}[No Diamond Theorem, part 1]
	For a full-connected network with $\ReLU$ as the unique activation function, if there is no Diamond, then for any approximation that at least as accurate as Interval Arithmetic, it can get the exact upper and lower bounds of all output nodes and all hidden nodes.
\end{theorem}

Of course, in practice, it is very unlike to have a network without any Diamond. Therefore, the second theorem is more important in practice.

\begin{theorem}[No Diamond Theorem, part 2]
	For a full-connected network with $\ReLU$ as the unique activation function. If we open all nodes that occurs in a compensating pair path, then the we can get the exactly bounds.
\end{theorem}

The proofs of above theorems are in the Appendix.

\subsection{Choice of path and open nodes}

Based on No Diamond Theorem, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node. However, in practice, this is still too expensive because we will still need to open too many nodes. So we will set a parameter $O$ and choose up to $O$ many nodes to open.

In this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.

Basically, we do the process of open nodes chosen for one node each time, that is, receive one node as input each time. But in principle, we can develop a method receive more than one nodes as input. But in our experiences, this does not work well.

\subsubsection*{Value of a pair}

First we define the value of a compensating pair: for a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.

\subsection*{Case: Source node fixed}

The simplest case is we only consider compensating pairs with a fixed source node.

\subsubsection*{Sort all paths by values}

The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.

Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.

\subsubsection*{Sort pairs by values}

The second step is to sort all pairs by their values. Enumerate paths from the positive group and the negative group one by one and put the pairs obtained into a new list of pairs. Then sort all pair by their values from largest to the smallest: recall that the value of a pair $\langle P_1,P_2\rangle$ is $\min(|V_1|,|V_2|)$.

\subsubsection*{Choosing nodes}

The third step is to choose nodes from the list of pairs. According to the sorted list of pairs, enumerate pair one by one; for each pair, pick the nodes unstable in the two paths except the source and target node into the open node list. Repeat this process until $O$ nodes chosen or reach the end of the list.

\subsubsection*{Pseudocode}

The following needs a chart of pseudo-code

\vspace*{1ex}

1. Enumerate all path from the fixed source node to the target node.

2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.

3. Divide all paths into two group: positive paths and negative paths.

4. Pair positive paths and negative paths from those with larger absolute values to smaller.

5. For each pair, its value is the min of the weight positive paths and absolute negative values.

6. From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.

7. Repeat 6 until choosing sufficiently many nodes.

\subsection*{Case: Source nodes in a fixed layer}

The more general case is when the source node can be any node in a fixed layer. In this case, the process is very similar to previous case, except the value of a pair.

In this case, the value of a pair $P_1,P_2$ with the source node $a$, is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.

\subsubsection*{Pseudocode}

The following needs a chart of pseudo-code

\vspace*{1ex}

1. Enumerate all path from the fixed source node to the target node.

2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.

3. Divide all paths into two group: positive paths and negative paths.

4. Pair positive paths and negative paths from those with larger absolute values to smaller.

5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.

6. From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.

7. Repeat 6 until choosing sufficiently many nodes.

\subsection*{Source nodes in different layers}

The general case is that when the location of source nodes can be different layers. This case is much more complex, because the values of paths from different layers has very different size. This is because the every weight from one node to another is mostly much less than $1$ (absolute value). So longer path will usually has much less values than shorter path.

\section{Experimental Evaluation}

The neural network certification benchmarks for fully connected networks were run on a 32 core
GHz Intel with 256 GB of main memory. We use Gurobi 9.52 for solving MILP and LP problems

We used MNIST image datasets for our experiments. MNIST contains grayscale images of size 28 × 28 pixels. For our evaluation, we chose the first
1000 images from the test set of each dataset.

Each data example is associated with an $L^\infty$ norm $\varepsilon$ and a target label
for verification

\subsection{Comparison to Incomplete Verifiers}

We compare our method to two famous verifiers (their incomplete mode): PRIMA and $\beta$-Crown on 5 typical MNIST models. Basically, our method can exceed PRIMA on both accuracy and speed, and exceed $\beta$-Crown on accuracy.

We do tests on 5 typical MNIST models.

\section{Related Work}

\section{Conclusion}

\section*{Appendix: Proofs of No Diamond Theorem}

\end{document}

### 2024-01-02 Paper/Paper_noProof.tex
Test
test
This is the part of draft paper without the proof of No Diamond theorem.
Writing Experiment Section

@@
 \subsection{The neural network and Verification problem}
+
+% testtesttesttest
 
@@
 
-In this case, the value of a pair $P_1,P_2$ with the source node $a$, is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
+In this case, the value of a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
 
@@
 
-\subsection*{Source nodes in different layers}
+\subsection*{Case: Source nodes in different layers}
 
 The general case is that when the location of source nodes can be different layers.
-This case is much more complex, because the values of paths from different layers has very different size.
+This case is much more complex, because the values of paths from different layers are very different.
 This is because the every weight from one node to another is mostly much less than $1$ (absolute value).
 So longer path will usually has much less values than shorter path.
+
+In our experiments, we only consider the paths of length 3 and length 4: that means, the source node is 2 layers or 3 layers before the target node.
+In this case, we will dynamically adjust the values during the process of node chosen.
+
+\subsubsection*{Pseudocode}
+
+The following needs a chart of pseudo-code
+
+\vspace*{1ex}
+
+1. Generate the two lists of pairs sorted by their values for source nodes in 2 layers before the target node and 3 layers before separately as in the previous case.
+
+2.
+Enumerate pair from two lists one by one by their values and pick nodes as previous case.
+When comparing the values between pairs of length 4 and pairs of length 3, multiply the numbers of nodes in 1 layer before to the value of pair of length 4.
+
+In formula, when the target node is in layer $L$, for a pair $P_3$ of length 3 with value $V_3$ and a pair $P_4$ of length 4 with value $V_4$, if we have chosen $N$ nodes in layer $L-1$.
+Then the adjusted values for $P_3$ and $P_4$ are: $$V_3, N\cdot V_4.$$ Then we pick the next pair by the adjust value in two lists.
+
+3. Repeat 2 until choosing sufficiently many nodes.
 
@@
 Each data example is associated with an $L^\infty$ norm $\varepsilon$ and a target label
-for verification
+for verification.
+
+\subsection{Experiment setting}
+
+Our experiments are carried by different version codes, and the global process has been changed.
+
+The basic unit of running is image: all parameters will reset when one image is finished and turn to another image.
+
+\subsubsection*{Global Process}
+
+In the newest version, we do images by batches for 100 images each. For each batch, the running consists of three turns, very fast turn, fast turn and slow turn.
+
+In the very fast turn, it will run DeepPoly for all images to get a preliminary bounds for all nodes and verify the easiest images.
+Images verified and images with false predication will be deleted from the image list.
+
+Then sort all remain images by the size of uncertainty of DeepPoly from smaller to larger.
+The fast turn is to run the images from the smaller side to larger side until consecutive two images cannot be verified.
+All remain images and images tried but not verified will be put into the next list.
+And then run the list with parameters for slow turn.
+
+\subsubsection*{Run one image}
+
+In the very fast turn, we use DeepPoly. So, all discussion below only consider fast and slow turns.
+
+An image is the basic unit in the running. The running is carrying layer by layer. The bounds obtained in previous layer will be used to build the model for the next layer, till the output layer.
+
+Some parameters may be changed during layers.
+Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
+Here, \emph{local} is opposite to \emph{global}.
+We have global timeout parameters for images and the whole running.
+Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
+
+In one layer, in principle, running for nodes are in principle independent and can be done in parallel. In our experiments, some local parameters will be adjusted from nodes to nodes.
+
+\subsubsection*{Create Models}
+
+The most important parameter is the number $O$ mentioned in last section:  the number of open nodes.
+When the program creates a model for a node, we will read this parameter to decide how many nodes to open in this model.
+This parameter can change during the running of an image by the mechanic of the code.
+
+\subsubsection*{Optimization for a node}
+
+Another group of parameters is for the optimization of models.
+
+The optimization of a model is carrying by loops.
+For each loop, the model will do optimization by a timeout and observe the result.
+If it gets improvement, then continue the loop until the optimize bounds or the longer timeout.
+Otherwise it will give up optimization and store the best bounds obtained so far.
+
+During the loop of optimization, parameters might be changed and the model may be rebuild by the new parameter.
+
+\subsubsection*{Other Setting}
+
+In our experiments, we have not used PGD-attack to rule out images. In principle, there is no obstacle to use PGD-attack and it will save a lots of time.
+
+\subsection{Experiments Result}
+
+The following chart is the summary of 5 experiments.
 

### 2024-01-02 Paper/Paper_noProof.tex
abstract

--- 2024-01-02 Paper/Paper_noProof.tex
@@
 
-\title{Diamond and Vericompensate}
+\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
 \date{}
@@
 
+\begin{abstract}
+  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formaly  that they are correct, with an annual competition to compare them, etc.
+Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
+This allows e.g.
+to check local robustness around an input $I$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $I$.
+  In the most recent years, the focus has been on combining several of these efficient techniques to optimize the speed/accuracy trade-offs (branch and bound, multi neuron encoding, milp encoding).
+While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools,
+  some smaller DNNs (hundreds of neurons) are still paradoxally challenging to address with efficient algorithms.
+
+  In this paper, we analyze efficient DNNs algorithm based on abstraction (DeepPoly, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely compensation.
+Intuitively, a compensation happens when there are 2 paths
+   Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy.
+\end{abstract}
+
 \section{Introduction}

### 2024-01-02 Paper/Paper_noProof.tex

--- 2024-01-02 Paper/Paper_noProof.tex
@@
 \maketitle
+
+\begin{abstract}
+  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formaly  that they are correct, with an annual competition to compare them, etc.
+Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
+This allows e.g.
+to check local robustness around an input $I$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $I$.
+  In the most recent years, the focus has been on combining several of these efficient techniques to optimize the speed/accuracy trade-offs (branch and bound, multi neuron encoding, milp encoding).
+While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools,
+  some smaller DNNs (hundreds of neurons) are still paradoxally challenging to address with efficient algorithms.
+
+  In this paper, we analyze efficient DNNs algorithm based on abstraction (DeepPoly, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely compensation.
+Intuitively, a compensation happens when there are 2 paths
+   Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy.
+\end{abstract}
 

### 2024-01-03 Paper/Paper_noProof.tex
llncs
Writing
cav

@@
-\documentclass[8pt]{article}
-\usepackage{amsmath, amsthm, amssymb, amsfonts}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
+\documentclass{llncs}
+\pagestyle{plain}
+
+%\usepackage[latin9]{inputenc}
+%\usepackage[T1]{fontenc}
+\usepackage{float}
+\usepackage{wrapfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
+% \usepackage{esint}
+\usepackage{array}
+\usepackage{epstopdf}
+\usepackage{placeins}
+\usepackage{url}
+\usepackage{tikz}
+\usepackage{calc}
+\usetikzlibrary{positioning, arrows.meta,calc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\usepackage{amsmath, amsthm, amssymb, amsfonts}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{corollary}{Corollary}
+%\theoremstyle{definition}
+%\newtheorem{definition}{Definition}
+
 \newcommand{\ReLU}{\mathrm{ReLU}}
@@
 
-\subsection{The neural network and Verification problem}
+We follow some notions in PRIMA's and Beta-Crown's papers: we use lower case Latin for scalars, bold for vectors
+$\boldsymbol{z}$, capitalized bold for matrices $\boldsymbol{W}$. In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
+
+\subsection{Neural Network and Verification}
 
@@
 
-In this paper, we focus on full-connected neural network.
+We focus on full-connected neural network.
 The network has weights and bias to send the input to output along hidden layers.
-In formula, the input layer of a neural network is a vector $x$ in $\mathbb{R}^{d_0}$, and the $i$-th hidden layer  is a vector in $\mathbb{R}^{d_i}$, and the output layer can be a vector in $\mathbb{R}^{d'}$ or a scale.
+In formula, the input layer of a neural network is a vector $\boldsymbol{x}$ in $\mathbb{R}^{d_0}$, and the $i$-th hidden layer  is a vector in $\mathbb{R}^{d_i}$, and the output layer is a vector in $\mathbb{R}^{d'}$ or a scale.
 The weights, bias and activation functions decide propagate the from previous to the next layer.
-In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight $W^i$ is matrix of $d_i\times d_{i-1}$, the bias is a vector $b^i$ in $\mathbb{R}^{d_i}$, and the activation function is $\sigma$, then  if the $i-1$-th layer is $\hat{z}^{(i-1)}$, then the value of $i$-th layer is computed by: \begin{align*}
-	{z}^{i} &= W^i\cdot \hat{z}^{(i-1)}+ b^i\\
-	\hat{z}^{i}(n) &= \sigma({z}^i(n)).
-\end{align*} The vector $\hat{z}$ is called pre-activation values, while $z$ is called post-activation values, and $z^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer.
+In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight $\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, the bias is a vector $\boldsymbol{b}^i$ in $\mathbb{R}^{d_i}$, and the activation function is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, then the value of $i$-th layer is computed by: \begin{align*}
+	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \boldsymbol{b}^i\\
+	\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)).
+\end{align*} The vector $\hat{\boldsymbol{z}}$ is called post-activation values, and $\boldsymbol{z}$ is called pre-activation values, and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer.
 In our style, we also call neurons \emph{nodes} and use $a,b,c,d$ to denote them.
 We use $W_{ab}$ to denote the weight from neuron $b$ to $a$.
-We use $x$ to denote the vector of input and  $f(x)$ to denote the output.
+We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
 
 The verification problem is to determine whether the output of a neural network will be affected under small perturbations to the input.
-In formula, if we use a distance $d$, and if the $x_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(x,x_0)<\epsilon\}$ where $\epsilon$ is the parameter measuring the size of perturbation.
+In formula, if we use a distance $d$, and if the $\boldsymbol{x}_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(\boldsymbol{x},\boldsymbol{x}_0)<\varepsilon\}$ where $\varepsilon$ is the parameter measuring the size of perturbation.
 And the problem will be \begin{align*}
-	\forall x\in\mathcal{D} \   f(x) = f(x_0).
+	\forall \boldsymbol{x}\in\mathcal{D} \   f(\boldsymbol{x}) = f(\boldsymbol{x}_0).
 \end{align*} In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
-\forall x \in\mathcal{D} \  \min f(x) = \min f(x_0)
+\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
 \end{align*}
@@
 If so, the question of verification can turn to the following optimization question: \begin{align*}
-	\min f(x) \ s.t. {z}^{i} &= W^i\cdot \hat{z}^{(i-1)}+ b^i\\
-	\hat{z}^{i}(n) &= \sigma({z}^i(n)), x\in\mathcal{D}.
+	\min f(\boldsymbol{x}) \ s.t. {\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ b^i\\
+	\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)), \boldsymbol{x}\in\mathcal{D}.
 \end{align*}
@@
 In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$.
-We consider $L^{\infty}$ norm, that is $d(x,x_0)=\max |x(n)-x_0(n)|$, the max value of distance of each dimension.
+We will consider $L^{\infty}$ norm, that is $$d(\boldsymbol{x},\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|,$$ the max value of distance of each dimension.
 
@@
 
-It is known in literature that if $x=\ReLU(y)$, and $y$ has its upper and lower bounds $u>0$ and $l<0$ (we call this unstable node; and if $u\geq 0$ or $l\leq 0$ then it is called stable node, and does not need MILP formulation), then this function can be formulated in MILP with one integer variable $a$ valued in ${0,1}$ (i.e., a binary variable) by:
+In literature, many methods have been used to approximate $\ReLU$ functions. One of them is MILP (or MIP, Mixed Integer Linear Programming).
+
+For a activation $x=\ReLU(y)$, if we already know $y's$ rough upper and lower bounds $u,l$, then if $u>0$ and $l<0$, we call $y$ is unstable; otherwise, $y$ is stable.
+In practice, stable node is easier because $\ReLU$ function becomes a linear function on this node.
+The key problem is to deal with unstable nodes.
+
+In literature, if $x=\ReLU(y)$, and $y$ is unstable, then this function can be formulated in MILP with one integer variable $a$ valued in ${0,1}$ (i.e., a binary variable) by:
 
@@
 
-It is a standard method to compute the lower bounds and upper bounds of neurons in a pure $\ReLU$ activation network by MILP optimization, because from previous subsection, the verification problem is equivalent to an optimization problem.
+MILP becomes one of standard methods to compute the lower bounds and upper bounds of neurons in a pure $\ReLU$ activation network.
+Combining with the discussion from previous subsection, the verification problem is equivalent to an MILP optimization problem.
 
@@
 
-\section{Compensate, Diamond and Path chosen}
+\section{Compensate, Diamond and Node Chosen}
 
-In this section, we will develop the process of open node chosen.
+In this section, we will explore the key factor for the loss of accuracy in our LP/MILP models: \emph{compensating pair}.
+And we will develop a process of open node chosen by the principle of \emph{Compensating Pairs}.
 
@@
 
-In this subsection, we will explore the key factor for the loss of accuracy in our LP/MILP models. The answer is the \emph{compensating pair}.
+The basic mode of compensating pair is as follows:
 
-In above figure, $a$ is the input neuron, $bc,b'c'$ are two nodes in the hidden layer, before and after the activation function, and $d$ is the unique output neuron.
+\vspace*{2ex}
+
+\begin{tikzpicture}
+	\node[circle, draw= purple, thick, minimum width = 20,
+	minimum height = 20] (input1) {$a$};
+
+	% Hidden layers
+	\node[circle, draw= blue, thick, minimum width = 20,
+	minimum height = 20] (hidden1) at ($(input1) + (2,1)$) {$b$};
+	\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-1)$) {$b'$};
+
+	\node[circle, draw= blue, thick, minimum width = 20,
+	minimum height = 20] (hidden3) at ($(input1) + (4,1)$){$c$};
+	\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-1)$) {$c'$};
+
+	% Output layer
+	\node[circle, draw= blue, thick, minimum width = 20,
+	minimum height = 20] (output) at ($(input1) + (6,0)$){$d$};
+
+	% Connections
+	\draw[->,thick,draw= red] (input1) -- (hidden1) node[midway, below] {$1$};
+	\draw[->,thick,draw= green] (input1) -- (hidden2)node[midway, below] {$-1$};
+
+	\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
+	\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};
+
+	\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
+	\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
+\end{tikzpicture}
+
+\vspace*{2ex}
+
+In this figure, $a$ is the input neuron; $bc,b'c'$ are two nodes in the hidden layer, pre and post activation; and $d$ is the unique output neuron.
 The numbers next to the arrows are the weights.
 So, $W_{ba}=1$ and $W_{b'a}=-1$, $W_{dc}=W_{dc'}=1$.
-The paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is the so called compensating pair, or a Diamond.
+The paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is the so called \emph{Compensating Pair}.
+Because this figure looks like a diamond, it is also called a Diamond.
+
 The key point is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
@@
 
-\section{Experimental Evaluation}
-
-The neural network certification benchmarks for fully connected networks were run on a 32 core
-GHz Intel with 256 GB of main memory. We use Gurobi 9.52 for solving MILP and LP problems
-
-We used MNIST image datasets for our experiments. MNIST contains grayscale images of size 28 × 28 pixels. For our evaluation, we chose the first
-1000 images from the test set of each dataset.
-
-Each data example is associated with an $L^\infty$ norm $\varepsilon$ and a target label
-for verification.
-
-\subsection{Experiment setting}
+\section{Verification Framework}
 
@@
 
-\subsection{Experiments Result}
+\section{Experimental Evaluation}
 
-The following chart is the summary of 5 experiments.
+The neural network certification benchmarks for fully connected networks were run on a 32 core
+GHz Intel with 256 GB of main memory. We use Gurobi 9.52 for solving MILP and LP problems
+
+We used MNIST image datasets for our experiments. MNIST contains grayscale images of size 28 × 28 pixels. For our evaluation, we chose the first
+1000 images from the test set of each dataset.
+
+Each data example is associated with an $L^\infty$ norm $\varepsilon$ and a target label
+for verification.
+
+\subsection{Experiments about Node Chosen}
+
+The first group of experiments is to test the direct effect of node chosen by compensating pair, comparing to random chosen.
+We use the average of uncertainty of all nodes in a layer to measure the effect of node chosen: for a node $a$, its uncertainty $UN(a) = UB(a)-LB(a)$, and the average uncertainty of a layer $l$ is $$UN(l) = \dfrac{\sum_{a\in l}UN(a)}{|l|}.$$
+
+The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the standard MNIST image database. This image can have more unstable nodes in each layer.
+
+\subsubsection*{Node chosen in second hidden layer}
+
+The following table shows the average uncertainty of the second hidden layer when choosing different numbers of open nodes by random or by compensating pairs.
+
+\subsubsection*{Node chosen in the third hidden layer}
+
+The following table shows the average uncertainty of the third hidden layer when choosing different numbers of open nodes, by random or by compensating pairs.
+
+\subsection{Experiments Results}
+
+The following table is the summary of 5 experiments.
 

### 2024-01-03 Paper/Paper_noProof.tex
abstract

--- 2024-01-02 Paper/Paper_noProof.tex
@@
-\documentclass[8pt]{article}
-\usepackage{amsmath, amsthm, amssymb, amsfonts}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
+\documentclass{llncs}
+\pagestyle{plain}
+
+%\usepackage[latin9]{inputenc}
+%\usepackage[T1]{fontenc}
+\usepackage{float}
+\usepackage{wrapfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
+% \usepackage{esint}
+\usepackage{array}
+\usepackage{epstopdf}
+\usepackage{placeins}
+\usepackage{url}
+\usepackage{tikz}
+\usepackage{calc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\usepackage{amsmath, amsthm, amssymb, amsfonts}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{corollary}{Corollary}
+%\theoremstyle{definition}
+%\newtheorem{definition}{Definition}
+
 \newcommand{\ReLU}{\mathrm{ReLU}}
@@
 
-  In this paper, we analyze efficient DNNs algorithm based on abstraction (DeepPoly, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely compensation.
-Intuitively, a compensation happens when there are 2 paths
-   Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy.
+  In this paper, we analyze efficientalgorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programing, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely compensation.
+Intuitively, a compensation happens when there are 2 paths from the same neuron to the same neuron, one with positive and one with negative (product of) weights, which therefore (partly) compensate each other.
+It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions.
+Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which we consider both linear modes), rather than the usual few queries with potentially many 'open' ReLU nodes.
 \end{abstract}

### 2024-01-04 Paper/Paper_noProof.tex
Writing

--- 2024-01-03 Paper/Paper_noProof.tex
@@
 
-The key point is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
+The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
+This is key reason why fast approximation like LP cannot get the exact upper and lower bounds.
 
-But if both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
+If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
 
-The definition of compensating pair is as follows:
+The general formal definition of compensating pair is as follows:
 
@@
 
-	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes from one layer by one layer. We call the first node source node and the last node target node.
+	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes that goes consecutively through each layer. We call the first node source node and the last node target node.
 
@@
 	3.
-A compensating pair is a pair of path with the same starting node and end node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
+A \emph{compensating pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
 
@@
 
-To explain the of meaning of compensating pair, we introduce the following theorems about Diamond:
+The following theorem shows the meaning of compensating pairs:
 
@@
 \subsection{Choice of path and open nodes}
+
+In this subsection, we will introduce the method to choose open nodes for MILP model by compensating pairs.
 

### 2024-01-04 Paper/Paper_noProof.tex
Writing

@@
 	3.
-A \emph{compensating pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
+A \emph{Compensating Pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
 
@@
 
-The following theorem shows the meaning of compensating pairs:
+The following theorem shows the role of compensating pairs in the computation:
 
 \begin{theorem}[No Diamond Theorem, part 1]
-	For a full-connected network with $\ReLU$ as the unique activation function, if there is no Diamond, then for any approximation that at least as accurate as Interval Arithmetic, it can get the exact upper and lower bounds of all output nodes and all hidden nodes.
+	For a full-connected network with $\ReLU$ as the unique activation function, if there is no Diamond, then for any method/approximation that at least as accurate as Interval Arithmetic, it can get the exact upper and lower bounds of all output nodes and all hidden nodes.
 \end{theorem}
@@
 
-\subsection{Choice of path and open nodes}
+\subsection{Paths and Open Nodes Chosen}
 
-In this subsection, we will introduce the method to choose open nodes for MILP model by compensating pairs.
+In this subsection, we will introduce the method to choose open nodes for MILP model by considering compensating pairs.
 
-Based on No Diamond Theorem, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node.
+Based on No Diamond Theorem, for a target node, in its MILP model, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node.
 However, in practice, this is still too expensive because we will still need to open too many nodes.
-So we will set a parameter $O$ and choose up to $O$ many nodes to open.
+So we can only choose a limited number of compensating pairs and nodes.
+This is by setting a parameter $O$ such that the process only choose at most $O$ many nodes to open.
+Therefore, in this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.
 
-In this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.
-
-Basically, we do the process of open nodes chosen for one node each time, that is, receive one node as input each time.
+Basically, we do the process of open nodes chosen for one target node each time, that is, receive one target node (and other data) as input each time.
 But in principle, we can develop a method receive more than one nodes as input.
@@
 
+This process is not the unique method but the most natural way to choose open nodes. We introduce it in three steps from the simplest case to more complex case.
+
 \subsubsection*{Value of a pair}
 
-First we define the value of a compensating pair: for a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.
+For a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.
 
@@
 
-The simplest case is we only consider compensating pairs with a fixed source node.
+The simplest case is when we only consider compensating pairs with a fixed source node.
 
-\subsubsection*{Sort all paths by values}
+In this case, the process is very simple: enumerate all compensating pairs, and then sort them by their values.
+Finally, from the first to the last compensating pair, pick all unstable nodes in its two paths except the target and source nodes into the list of open nodes, until $O$ many open nodes.
 
-The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.
-
-Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.
-
-\subsubsection*{Sort pairs by values}
-
-The second step is to sort all pairs by their values.
+%\subsubsection*{Sort all paths by values}
+%
+%The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.
+%
+%Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.
+%
+%\subsubsection*{Sort pairs by values}
+%
+%The second step is to sort all pairs by their values.
 Enumerate paths from the positive group and the negative group one by one and put the pairs obtained into a new list of pairs.
 Then sort all pair by their values from largest to the smallest: recall that the value of a pair $\langle P_1,P_2\rangle$ is $\min(|V_1|,|V_2|)$.
-
-\subsubsection*{Choosing nodes}
-
-The third step is to choose nodes from the list of pairs.
+%
+%\subsubsection*{Choosing nodes}
+%
+%The third step is to choose nodes from the list of pairs.
 According to the sorted list of pairs, enumerate pair one by one; for each pair, pick the nodes unstable in the two paths except the source and target node into the open node list.
 Repeat this process until $O$ nodes chosen or reach the end of the list.
+%
+%\subsubsection*{Pseudocode}
+%
+%The following needs a chart of pseudo-code
+%
+%\vspace*{1ex}
+%
+%1. Enumerate all path from the fixed source node to the target node. 
+%
+%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
+%
+%3. Divide all paths into two group: positive paths and negative paths.
+%
+%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
+%
+%5. For each pair, its value is the min of the weight positive paths and absolute negative values.
+%
+%6.
+From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
+%
+%7. Repeat 6 until choosing sufficiently many nodes.
+%
 
-\subsubsection*{Pseudocode}
-
-The following needs a chart of pseudo-code
-
-\vspace*{1ex}
-
-1. Enumerate all path from the fixed source node to the target node.
-
-2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-
-3. Divide all paths into two group: positive paths and negative paths.
-
-4. Pair positive paths and negative paths from those with larger absolute values to smaller.
-
-5. For each pair, its value is the min of the weight positive paths and absolute negative values.
-
-6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-
-7. Repeat 6 until choosing sufficiently many nodes.
-
-\subsection*{Case: Source nodes in a fixed layer}
+\subsection*{Case: Source nodes in one layer}
 
@@
 
-In this case, the value of a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
+In this case, for a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, its value is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
 
-\subsubsection*{Pseudocode}
-
-The following needs a chart of pseudo-code
-
-\vspace*{1ex}
-
-1. Enumerate all path from the fixed source node to the target node.
-
-2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-
-3. Divide all paths into two group: positive paths and negative paths.
-
-4. Pair positive paths and negative paths from those with larger absolute values to smaller.
-
-5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.
-
-6.
+%\subsubsection*{Pseudocode}
+%
+%The following needs a chart of pseudo-code
+%
+%\vspace*{1ex}
+%
+%1. Enumerate all path from the fixed source node to the target node. 
+%
+%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
+%
+%3. Divide all paths into two group: positive paths and negative paths.
+%
+%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
+%
+%5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.
+%
+%6.
 From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-
-7. Repeat 6 until choosing sufficiently many nodes.
+%
+%7. Repeat 6 until choosing sufficiently many nodes.
 
@@
 
-The general case is that when the location of source nodes can be different layers.
-This case is much more complex, because the values of paths from different layers are very different.
-This is because the every weight from one node to another is mostly much less than $1$ (absolute value).
-So longer path will usually has much less values than shorter path.
+The general case is that when the location of source nodes can be in different layers.
+This case is much more complex, because the scale level of values of paths from different layers are very different: usually a weight will be very small since every layer has a large number of nodes, therefore values of longer paths are products of more small numbers, and is definitely much smaller.
+If we sort all compensating pairs from different layers directly, then a very long initial segment of this list will be occupied by compensating pairs with the shortest length.
+Therefore, we need use some scale factors when comparing values of compensating pairs of different length.
 
-In our experiments, we only consider the paths of length 3 and length 4: that means, the source node is 2 layers or 3 layers before the target node.
-In this case, we will dynamically adjust the values during the process of node chosen.
+In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before).
+We will dynamically adjust the values during the process of node chosen.
 
@@
 
-Our experiments are carried by different version codes, and the global process has been changed.
+%Our experiments are carried by different version codes, and the global process has been changed.
 
-The basic unit of running is image: all parameters will reset when one image is finished and turn to another image.
+We explain the framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
 
-\subsubsection*{Global Process}
+\subsection{Process for one image}
+
+The basic unit of running is image: all parameters will be reset when one image is finished.
+
+The process for one image is clear: compute the upper and lower bounds of nodes layer by layer to the output layer.
+
+Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers. Then we will compute bounds of every node in $l_i$ in parallel.
+
+\subsection{Precomputation}
+
+The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node.
+
+\subsection{Process for one node}
+
+\subsection{Global Process}
 

### 2024-01-04 Paper/Paper_noProof.tex
Writing

@@
 
-In this figure, $a$ is the input neuron; $bc,b'c'$ are two nodes in the hidden layer, pre and post activation; and $d$ is the unique output neuron.
+In this figure, $a$ is the input neuron; $bc,b'c'$ are nodes in the hidden layer, ($b,b'$ are pre-activation and $c,c'$ are post activation); and $d$ is the unique output neuron.
 The numbers next to the arrows are the weights.
 So, $W_{ba}=1$ and $W_{b'a}=-1$, $W_{dc}=W_{dc'}=1$.
-The paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is the so called \emph{Compensating Pair}.
-Because this figure looks like a diamond, it is also called a Diamond.
+The pair of these two paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is a so called \emph{Compensating Pair}.
+Because its shape looks like a diamond, it is also called a Diamond.
+The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
 
-The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
-This is key reason why fast approximation like LP cannot get the exact upper and lower bounds.
+The existence of compensating pairs is key reason why simple approximation like LP or Interval Arithmetic cannot get the exact upper and lower bounds.
+If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
 
-If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
+To explain why, suppose we have another input node $a'$, such that both $a$ and $a'$ has an input interval $[0,1]$, but the weight from $a'$ to $b$ or $b'$ are both $1$.
+Then both $b$ will have an interval $[0,2]$ and $b'$ will have an interval $[-1,1]$.
+More importantly, in LP formulation, $c$ will be $b$ but $c'$ will be $0.5(b')+0.5$.
+The upper bound of $d$ will be $c+c'$, and hence $b+0.5(b')+0.5$, and hence $a+a'+0.5a'-0.5a'+0.5=0.5a+1.5a'+0.5$.
+And this will leads to a upper bound $2.5$ but this is not exact.
+
+\vspace*{2ex}
+\begin{tikzpicture}
+	\node[circle, draw= purple, thick, minimum width = 20,
+	minimum height = 20] (input1) {$a$};
+
+	\node[circle, draw= purple, thick, minimum width = 20,
+	minimum height = 20] (input2) at ($(input1) + (0,-2)$) {$a'$};
+
+	% Hidden layers
+	\node[circle, draw= blue, thick, minimum width = 20,
+	minimum height = 20] (hidden1) at ($(input1) + (2,0)$) {$b$};
+	\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-2)$) {$b'$};
+
+	\node[circle, draw= blue, thick, minimum width = 20,
+	minimum height = 20] (hidden3) at ($(input1) + (4,0)$){$c$};
+	\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-2)$) {$c'$};
+
+	% Output layer
+	\node[circle, draw= blue, thick, minimum width = 20,
+	minimum height = 20] (output) at ($(input1) + (6,-1)$){$d$};
+
+	% Connections
+	\draw[->,thick,draw= red] (input1) -- (hidden1);
+	\draw[->,thick,draw= green] (input1) -- (hidden2);
+
+	\draw[->,thick,draw= red] (input2) -- (hidden1) node[midway, below] {$1$};
+	\draw[->,thick,draw= red] (input2) -- (hidden2)node[midway, below] {$1$};
+
+	\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
+	\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};
+
+	\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
+	\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
+\end{tikzpicture}
+\vspace*{2ex}
 
@@
 
-Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers. Then we will compute bounds of every node in $l_i$ in parallel.
+Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers.
+Then we will compute bounds of every node in $l_i$ in parallel using the data of bounds of previous nodes.
+The method is to build and optimize an MILP model.
+
+Some parameters may be changed during layers.
+Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
+Here, \emph{local} is opposite to \emph{global}.
+We have global timeout parameters for images and the whole running.
+Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
+
+In one layer, in principle, running for nodes are in principle independent and can be done in parallel. In our experiments, some local parameters will be adjusted from nodes to nodes.
 
@@
 
+The precomputation corresponds to the simplest case: source node fixed.
+We will compute and store a limited number of paths with highest (absolute) values before running any image.
+This does not rely on other parameters or results(bounds).
+
+Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
+This will use much less time.
+
 \subsection{Process for one node}
+
+For one node, we will build the MILP model for it.
+
+The most important parameter is the number $O$ mentioned in last section:  the number of open nodes.
+When the program creates a model for a node, we will read this parameter to decide how many nodes to open in this model.
+This parameter can change during the running of an image by the mechanic of the code.
+
+Another group of parameters is for the optimization of models.
+
+The optimization of a model is carrying by loops.
+For each loop, the model will do optimization by a timeout and observe the result.
+If it gets improvement, then continue the loop until the optimize bounds or the longer timeout.
+Otherwise it will give up optimization and store the best bounds obtained so far.
+
+During the loop of optimization, parameters might be changed and the model may be rebuild by the new parameter.
 
@@
 
-\subsubsection*{Run one image}
-
-In the very fast turn, we use DeepPoly. So, all discussion below only consider fast and slow turns.
-
-An image is the basic unit in the running. The running is carrying layer by layer. The bounds obtained in previous layer will be used to build the model for the next layer, till the output layer.
-
-Some parameters may be changed during layers.
+%\subsubsection*{Run one image}
+%
+%In the very fast turn, we use DeepPoly. So, all discussion below only consider fast and slow turns.
+%
+%An image is the basic unit in the running. The running is carrying layer by layer. The bounds obtained in previous layer will be used to build the model for the next layer, till the output layer.
+%
+%Some parameters may be changed during layers.
 Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
@@
 Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
+%
+%In one layer, in principle, running for nodes are in principle independent and can be done in parallel. In our experiments, some local parameters will be adjusted from nodes to nodes.
 
-In one layer, in principle, running for nodes are in principle independent and can be done in parallel. In our experiments, some local parameters will be adjusted from nodes to nodes.
-
-\subsubsection*{Create Models}
-
-The most important parameter is the number $O$ mentioned in last section:  the number of open nodes.
+%\subsubsection*{Create Models}
+%
+%The most important parameter is the number $O$ mentioned in last section:  the number of open nodes.
 When the program creates a model for a node, we will read this parameter to decide how many nodes to open in this model.
 This parameter can change during the running of an image by the mechanic of the code.
-
-\subsubsection*{Optimization for a node}
-
-Another group of parameters is for the optimization of models.
-
-The optimization of a model is carrying by loops.
+%
+%\subsubsection*{Optimization for a node}
+%
+%Another group of parameters is for the optimization of models. 
+%
+%The optimization of a model is carrying by loops.
 For each loop, the model will do optimization by a timeout and observe the result.
@@
 Otherwise it will give up optimization and store the best bounds obtained so far.
-
-During the loop of optimization, parameters might be changed and the model may be rebuild by the new parameter.
+%
+%During the loop of optimization, parameters might be changed and the model may be rebuild by the new parameter.
 
@@
 
-In our experiments, we have not used PGD-attack to rule out images. In principle, there is no obstacle to use PGD-attack and it will save a lots of time.
+In our experiments, we have not used PGD-attack to rule out images. In principle, there is no obstacle to use PGD-attack.
 

### 2024-01-05 Paper/Paper_noProof.tex
intro

--- 2024-01-04 Paper/Paper_noProof.tex
@@
 to check local robustness around an input $I$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $I$.
-  In the most recent years, the focus has been on combining several of these efficient techniques to optimize the speed/accuracy trade-offs (branch and bound, multi neuron encoding, milp encoding).
-While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools,
-  some smaller DNNs (hundreds of neurons) are still paradoxally challenging to address with efficient algorithms.
+  In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs.
+While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.
 
-  In this paper, we analyze efficient DNNs algorithm based on abstraction (DeepPoly, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely compensation.
-Intuitively, a compensation happens when there are 2 paths
-   Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy.
+  In this paper, we analyze efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programing, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
+Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other.
+It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions.
+Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes.
+These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.
 \end{abstract}
@@
 \section{Introduction}
+
+Complexity
+
+This paper does not focuss on producing the most efficient tool, and we did not spend engeenierial effort to optimize it.
+The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.
+For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in $\beta$-CROWN).
+Still, evaluation of the methodology versus even the most efficient tools reveal a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification.
 
@@
 
-The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
-This is key reason why fast approximation like LP cannot get the exact upper and lower bounds.
+The key point is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
 
-If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
+But if both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
 
-The general formal definition of compensating pair is as follows:
+The definition of compensating pair is as follows:
 
@@
 
-	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes that goes consecutively through each layer. We call the first node source node and the last node target node.
+	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes from one layer by one layer. We call the first node source node and the last node target node.
 
@@
 	3.
-A \emph{compensating pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
+A compensating pair is a pair of path with the same starting node and end node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
 
@@
 
-The following theorem shows the meaning of compensating pairs:
+To explain the of meaning of compensating pair, we introduce the following theorems about Diamond:
 
@@
 \subsection{Choice of path and open nodes}
-
-In this subsection, we will introduce the method to choose open nodes for MILP model by compensating pairs.
 

### 2024-01-08 Paper/Paper_noProof.tex
Writing

--- 2024-01-04 Paper/Paper_noProof.tex
@@
 
-In this subsection, we will introduce the method to choose open nodes for MILP model by considering compensating pairs.
+In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.
 
@@
 
-We explain the framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
+We explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
 
@@
 
-The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the standard MNIST image database. This image can have more unstable nodes in each layer.
+The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the MNIST image dataset.
 
@@
 
+\[
+\begin{array}{c|c|c}
+
+	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
+	0  &  2.22 & 2.22  \\ \hline
+	10  &  1.84 & 2.03  \\ \hline
+	20  &  1.50 & 1.82  \\ \hline
+	30  &  1.28 & 1.62  \\ \hline
+	40  &  1.14 & 1.44  \\ \hline
+	50  &  1.06 & 1.23  \\ \hline
+\end{array}
+\]
+
 \subsubsection*{Node chosen in the third hidden layer}
@@
 
+\[
+\begin{array}{c|c|c}
+
+	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
+	0  &  1.758 & 1.758  \\ \hline
+	10  &  1.677 & 1.695  \\ \hline
+	20  &  1.539 & 1.622  \\ \hline
+	30  &  1.431 & 1.542  \\ \hline
+	40  &  1.329 & 1.47  \\ \hline
+	50  &  1.243 & 1.39  \\ \hline
+\end{array}
+\]
+
 \subsection{Experiments Results}
@@
 The following table is the summary of 5 experiments.
+
+\[
+\begin{array}{c|c|c}
+
+	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
+	0  &  1.758 & 1.758  \\ \hline
+	10  &  1.677 & 1.695  \\ \hline
+	20  &  1.539 & 1.622  \\ \hline
+	30  &  1.431 & 1.542  \\ \hline
+	40  &  1.329 & 1.47  \\ \hline
+	50  &  1.243 & 1.39  \\ \hline
+\end{array}
+\]
 

### 2024-01-08 Paper/Paper_noProof.tex
Writing

@@
 \[
-\begin{array}{c|c|c}
+\begin{array}{c|c|cc|cc|cc|cc}
 
-	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
-	0  &  1.758 & 1.758  \\ \hline
-	10  &  1.677 & 1.695  \\ \hline
-	20  &  1.539 & 1.622  \\ \hline
-	30  &  1.431 & 1.542  \\ \hline
-	40  &  1.329 & 1.47  \\ \hline
-	50  &  1.243 & 1.39  \\ \hline
+	\text{Network}  & \varepsilon&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\
+
+  &  & \mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) &\mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) \\ \hline
+
+	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 \end{array}
@@
 
-We compare our method to two famous verifiers (their incomplete mode): PRIMA and $\beta$-Crown on 5 typical MNIST models.
-Basically, our method can exceed PRIMA on both accuracy and speed, and exceed $\beta$-Crown on accuracy.
+In Table 3, we compare against two representative incomplete
+verifiers on 4 MLP networks for MNIST under the same
+set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
 

### 2024-01-08 Paper/Paper_noProof.tex
Writing

@@
 \usepackage{calc}
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
 \usetikzlibrary{positioning, arrows.meta,calc}
@@
 
+\begin{algorithm}
+	\caption{Process for length 3 + length 4}
+	\KwData{Input data}
+	\KwResult{Open node list}
+	\While{condition}{
+		Perform operation 1\;
+		\If{condition}{
+			Perform operation 2\;
+		}
+		\Else{
+			Perform operation 3\;
+		}
+	}
+\end{algorithm}
+
 \section{Verification Framework}
@@
 
-\[
-\begin{array}{c|c|c}
+\begin{table}
+	\centering
+	\begin{tabular}{c|c|c}
 
@@
 	50  &  1.06 & 1.23  \\ \hline
-\end{array}
-\]
+\end{tabular}
+\caption{}
+\label{tab:example0}
+\end{table}
+
+\vspace*{-8ex}
 
@@
 	50  &  1.243 & 1.39  \\ \hline
-\end{array}
-\]
+\end{tabular}
+\caption{}
+\label{tab:example1}
+\end{table}
 
@@
 
-The following table is the summary of 5 experiments.
+\begin{table}
+	\centering
+	\begin{tabular}{c|c|cc|cc|cc|cc}
 
-\[
-\begin{array}{c|c|cc|cc|cc|cc}
+	\text{Network}  & $\varepsilon$&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\
 
-	\text{Network}  & \varepsilon&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\
+  &  & \textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) &\textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) \\ \hline
 
-  &  & \mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) &\mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) \\ \hline
+	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-\end{array}
-\]
+	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+\end{tabular}
+\caption{The data of verified accuracy (\%) and average time (s) of 1000 images evaluated on the PRIMA and on the beta-Crown are in CITE.}
+\label{tab:example}
+\end{table}
 
@@
 set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
-
-We do tests on 5 typical MNIST models.
 

### 2024-01-08 Paper/Paper_noProof.tex
Writing

@@
 We will dynamically adjust the values during the process of node chosen.
-
-\subsubsection*{Pseudocode}
-
-The following needs a chart of pseudo-code
+In text, the process of node chosen for length 3 plus length 4 is as follows:
 
@@
 
+\vspace*{1ex}
+
+And the pseudo-code is as follows:
+
 \begin{algorithm}
 	\caption{Process for length 3 + length 4}
-	\KwData{Input data}
+	\KwData{Sorted lists of length 3 + length 4}
 	\KwResult{Open node list}
-	\While{condition}{
-		Perform operation 1\;
-		\If{condition}{
-			Perform operation 2\;
+
+	Let $N = 0$ be the number of Chosen length 4 pair.
+
+	\While{len(Open node) $<O$}{
+		Pick the first element $P_3$ in the list of length 3\;
+
+		Let $V_3$ be the value of $P_3$\;
+
+		Pick the first element $P_4$ in the list of length 4\;
+
+		Let $V_4$ be the value of $P_4$\;
+
+		\If{$V_3 > V_4 \cdot N$}{
+			Add nodes in $P_3$ into Open list\;
+			Number of Chosen lentgh pair $N$ += 1\; 
 		}
 		\Else{
-			Perform operation 3\;
+			Add nodes in $P_4$ into Open list\;
 		}
@@
 
-We explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
+In this section, We will explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
 
@@
 
-\vspace*{-8ex}
-
 \subsubsection*{Node chosen in the third hidden layer}
@@
 
+\subsection{Comparison to Incomplete Verifiers}
+
+In Table 3, we compare against two representative incomplete
+verifiers on 4 MLP networks for MNIST under the same
+set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
+
 \begin{table}
@@
 
-	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 8$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 
-	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 
-	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 8$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 
-	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
 	\end{tabular}
@@
 
-\subsection{Comparison to Incomplete Verifiers}
-
-In Table 3, we compare against two representative incomplete
-verifiers on 4 MLP networks for MNIST under the same
-set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
+On all 4 networks, our fast version can exceed PRIMA both in accuracy and speed. On all 4 networks, our slow version can have a similar verified accuracy as beta-Crown.
 

### 2024-01-08 Paper/Paper.tex
Draft completed but need big revision.

@@
 
+\begin{lemma}\label{lem:AppB=ReLU}
+	Let $\mathrm{AppB}$ be the upper bound of lower bound approximation functions of LP for $\ReLU$ function with known upper and lower bound (numbers) $u,l$.
+Then when $x$ reaches the extremal values (maximum or minimum values, $u$ or $l$), then $\mathrm{AppB}(x)=\ReLU(x)$.
+
+\end{lemma}
+
+\begin{proof}
+	This is simply by definition of LP approximation functions.
+\end{proof}
+
 Notice that there is only one layer of ReLUs, in the hidden layer.
@@
 	\mathrm{UB}_{a^0_J,a^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{a^0_I,a^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{a^0_I,a^0_J}(b)).
-\end{align*}
-
-where $\mathrm{AppB}(weight_{a^0_I,a^0_J}(b))$ is the upper bound of 
+\end{align*} where $\mathrm{AppB}(weight_{a^0_I,a^0_J}(b))$ is the upper bound of 
 the (LP) approximation of $weight_{a^0_I,a^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
@@
 =\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{a^*_I}(b))
-$$
-
-as $\mathrm{AppB}(weight_{a^*_I}(b))=\mathrm{ReLU}(weight_{a^*_I}(b))$ since 
+$$ as $\mathrm{AppB}(weight_{a^*_I}(b))=\mathrm{ReLU}(weight_{a^*_I}(b))$ since 
 $weight_{a^*_I}(b)$ is an extremal value (minimum or maximal) and 
-$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values (make a lemma about that in the begining).
+$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values.
 
@@
 
-$$\mathrm{UB} = max_{a_J,a_I} \mathrm{UB}_{a_J,a_I} \leq \max_{a_J,a_I} weight_{a_J,a_I}(z)$$
+$$\mathrm{UB} = max_{a_J,a_I} \mathrm{UB}_{a_J,a_I} \leq \max_{a_J,a_I} weight_{a_J,a_I}(z)$$ And this us what we want to show.
+
+\section{Proof of Theorem 2, full version}
+
+In this section, we will try to prove the full version of theorem 2, that is
+
+\begin{theorem}
+	\label{no_diamond_3}
+
+	Suppose we have a DNN with $\ReLU$ as the unique activation functions. We consider compensating pairs in between any two nodes (i.d., the source node or target node can in hidden layers.)
+
+	Using MILP method, if every nodes $b$ in any compensating pair
+	$(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
+	bounds computed by MILP are the exact max and min value of $z$.
+\end{theorem}
+
+Before the proof of above theorem, we will try to weaker one, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes).
+We call such pair a weak compensating pair.
+
+We uses very similar definitions as in previous section.
+
+\begin{definition}
+	Let $K$ be the set of all input nodes $a_k$. 
+	We define a decomposition $K=I\sqcup J$ as follows:  
+	\begin{itemize}
+		\item $k \in I$  if
+		\begin{enumerate}
+			\item every path from $a_k$ to $z$ has weight $\geq 0$, or
+			\item every path from $a_k$ to $z$ has weight $\leq 0$.
+		\end{enumerate}
+		That is, $a_k$ is not a source of a weak compensating pair.
+		\item $k \in J$ if $k \notin I$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
+		one with positive and one with negative weight.
+	\end{itemize}
+\end{definition}
+
+\begin{lemma} \label{lem:open_node_2}
+	A node $b$ in the hidden layer will not be on a weak compensating pair iff one of the following two happens:
+	\begin{enumerate}
+		\item $w_{b,z}=0$, or
+		\item For every input node $j\in J$, we have $w_{a_j,b}=0$.
+	\end{enumerate}
+	We denote $B_{pure}$ the set of such nodes $b$ such that at least one of the above holds.
+\end{lemma}
+
+\begin{proof}
+	First, we show that if either one of 1,2 happens, then $b$ will not be opened.
+If 1), it is obvious.
+For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$.
+It means that $a \in J$.
+A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.
+
+	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
+	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
+	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
+	Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
+	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
+	Then $((a_j,b,z), \pi')$ is also a weak compensating pair.
+\end{proof}
+
+Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
+
+\begin{definition}\label{sign_of_nodes_in_I_2}
+	We define a partial sign function $S$ over nodes $n$ such that : 	
+	\begin{enumerate} 
+		\item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
+		\item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
+		\item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
+		\item Otherwise $S(n)$ is undefined.
+	\end{enumerate}
+\end{definition}
+
+Notice that $S$ is defined on all nodes $a_i$ with $i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
+Hence it is undefined only for nodes $a_j$ with $j \in J$.
+
+We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$. We also denote $a_I\oplus a_J = a_K$ and $z=z(a_K)=z(a_I,a_J)$.
+Consider $a_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
+
+\begin{lemma} \label{lem:reach_max_2}
+	$max_a (weight_{a}(z)) = max_{\{a \mid a_I=a^*_I\}} (weight_{a}(z))$
+
+	Further, for every intermediate node $b$ in the hidden layer, for any valuation $a^0_J$, 
+	we have $max_{\{a \mid a_J=a^0_J\}} (weight_{a}(b)) = max_{\{a \mid a_J=a^0_J,a_I=a_I^*\}} (weight_{a}(b))$.	
+\end{lemma}
+
+\begin{proof}
+	For the first statement, we use 
+	$$max_{a_K} (weight_{a_K}(z)) = max_{a_J} max_{a_I} (weight_{a_I,a_J}(z))$$
+
+	Now, for any fixed input $a^0_J$, we can regard $weight_{a_I,a^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $a^0_J$ %and their propagation in hidden layers 
+	as bias.
+In the simplified $D'$, there is no compensating path because of the definition of $I$.
+Therefore we can apply Theorem \ref{th1} to get that $z(\cdot,a^0_J)$ reaches its maximal value for $a_I=a_I^*$, and we are done.
+
+	For the second part, for any $b$ that is at least 2 layers after $a$, we can regard $b$ as the output node and apply the same argument above.
+
+	If $b$ is immediately after $a$, then the proof is the same as last part of Lemma \ref{lem:reach_max} last section.
+
+\end{proof}
+
+\subsection{MILP abstraction}
+
+Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
+where each variable $\alpha_b$ for the ReLU from $b^-$ to $b^+$ is:
+\begin{itemize}
+	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \in B_{pure}$
+	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \notin B_{pure}$
+\end{itemize}
+
+Denote by $\mathrm{UB}$ the maximal bound on $z$ and $\mathrm{LB}$ the minimal bound on $z$ considering the MILP constraints above, with ReLUs being either linear or binary depending on whether $b \in B_{pure}$ or not.
+
+For an input vector $a^0_I,a^0_J$, let $UB_{a^0_I,a^0_J}$ be the upper bound in the fixed formulation with input $a^0_I,a^0_J$, and similarly for $LB$ lower bound. We have the following lemma:
+
+\begin{lemma} In an MILP formulation, if $c$ is a node:
+
+	1. $UB(b)=\max_{a^0_I,a^0_J}UB_{a^0_I,a^0_J}(c)$.
+
+		1. $LB(b)=\min_{a^0_I,a^0_J}LB_{a^0_I,a^0_J}(c)$. 
+\end{lemma}
+
+\begin{proof}
+	This is by the definition of MILP formulation and $UB_{a^0_I,a^0_J}, LB_{a^0_I,a^0_J}$.
+\end{proof}
+
+\begin{lemma}\label{lem:pure_node}
+	For a node $c\in B_{pure}$ such that $w_{b,z}\neq 0$, $UB_{a^0_I,a^0_J}$ (and $LB$ the same) only depends on $a^0_I$.
+\end{lemma}
+
+\begin{proof}
+	We prove this lemma by induction. For the first hidden layer, this is trivial.
+
+	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
+		UB_{a^0_I,a^0_J}(c) = B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{a^0_I,a^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(B_{a^0_I,a^0_J}(b)).
+	\end{align*} But since $c\in B_{pure}$, for any $b\in B_O$, we must have $w_{b,c}=0$. Therefore, we will have:
+
+	\begin{align*}
+		UB_{a^0_I,a^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(B_{a^0_I,a^0_J}(b)).
+	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, either $w_{b,z}=0$ or it only depends on $a^0_I$. Since $w_{c,z}\neq 0$, if $w_{b,z}=0$, we must have $w_{b,c}=0$. Therefore, we will have:
+
+	\begin{align*}
+		UB_{a^0_I,a^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq0} w_{b,c} \mathrm{AppB}(B_{a^0_I}(b)).
+	\end{align*} So, $UB_{a^0_I,a^0_J}(c)$ only depends on $a_I^0$.
+\end{proof}
+
+We want to show that $\mathrm{UB}(z) = \max z$ and $\mathrm{LB}(z) = \min z$ for the unique output nodes and we will prove this for all $c$ such $w_{c,z}\neq 0$.
+As the MILP abstraction is a sound overapproximation,
+it suffices to show that $\mathrm{UB}\leq \max c$ and $\mathrm{LB} \geq \min c$.
+We will prove this by induction on layers from the first hidden layer to the output layer.
+More specifically, we will prove the following lemma:
+
+\begin{lemma}
+	For the $i$-th layer $l^i$ ($1$-th layer is the first hidden layer), for a node $c\in l^i$, if $w_{c,z}\neq 0$, then:
+
+	 For any fixed $a^0_J$, $\max_{a_I} UB_{a_I,a^0_J}(c)=UB_{a^*_I,a^0_J}(c)= weigth(a^*_I,a^0_J)(c) = \max_{a_I} weigth(a_I,a^0_J)(c)$, where $a^*_I$ is described in previous section.
+
+The similar is true for lower bound $LB$.
+\end{lemma}
+
+\begin{proof}
+
+	For $i\leq 2$, we have proved in previous section.
+
+	Suppose we have proved this lemma up to layer $i\geq 2$, and we are going to prove it for $i+1$-th layer. Let $c$ be a node on $i+1$-th layer such that $w_{c,z}\neq 0$.
+
+	By definition, we have that for any input vector $a^0_I,a^0_J$:
+
+	\begin{align*}
+		\mathrm{UB}_{a^0_J,a^0_I}(c) = B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{a^0_I,a^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(B_{a^0_I,a^0_J}(b)).
+	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $a^0_I,a^0_J$.
+$B$ is one of $UB,LB$  that, if $w_{b,c}>0$, then $B$ is $UB$ and otherwise $B$ is $LB$.
+
+	By Lemma \ref{lem:pure_node}, we can simplify above equation to \begin{align*}
+			\mathrm{UB}_{a^0_J,a^0_I}(c) = B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{a^0_I,a^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{a^0_I}(b)).
+	\end{align*}
+
+	By induction hypothesis, since both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have that \begin{align*}
+		\mathrm{UB}_{a^0_J,a^0_I}(c)\leq 
+		 &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{a^*_I,a^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{a^*_I}(b))\\
+		= & \mathrm{UB}_{a^0_J,a^*_I}(c) \\
+	\end{align*}
+
+Now, since when $x$ reaches the max or min of $\mathrm{AppB}$'s domain, $\mathrm{AppB}(x)=\ReLU(x)$, and by induction hypothesis part 2, for any $b\in B_{pure}\cap l_i\wedge w_{b,c}\neq 0$, $\mathrm{AppB}(B_{a^*_I}(b))=\ReLU(B_{a^*_I})$.
+Hence, by induction hypothesis, we will have \begin{align*}
+	\mathrm{UB}_{a^0_J,a^0_I}(c)\leq & \ \mathrm{UB}_{a^0_J,a^*_I}(c) \\
+	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{a^*_I,a^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{a^*_I}(b))\\
+	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(weight_{a^*_I,a^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{a^*_I}(b))\\
+	= & weight_{a^*_I,a^0_J}(c).
+\end{align*} This finishes the proof.
+	\end{proof}
+
+Now, we have that for any fixed $a^0_J$, $\max_{a_I} UB_{a_I,a^0_J}(c)= \max_{a_I} weigth(a_I,a^0_J)(c)$, therefore, $\max UB_{a_I,a_J}(c)= \max weigth(a_I,a_J)(c)$ and this is to say $UB(c)=\max(c)$.
 
 \end{document}
-
-%
-%The DeepPoly function for $b$ can be expressed by the following steps.
-%First, we partition the set of indices $i$ as $I,I_0,I^+,I^-$ with:
-%\begin{itemize}
-%	\item $i \in I$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case 
-%	$\bar{f}(b_i^+)(Y)=\underline{f}(b_i^+)=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$, and else:
-%	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,	and else:
-%	\item $i \in I^+$ if $w_{b_i c}>0$, and:
-%	\item $i \in I^-$ if $w_{b_i c}<0$.
-%	\end{itemize}
-%	
-%Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.
-%	
-%
-%We have:
-%\begin{align*}
-%	\bar{f}(c)(Y) = &
-%	bias_c + \sum_{b \in I} w_{bc}\sum_{a} w_{a b} weight(a) + bias_{b} \\
-%	& + \sum_{b \in I^+} w_{b c} \cdot \bar{f}(ReLU(\sum_{a} w_{a b} weight(a) 
-%	+ Bias_{b}))(Y) 
-%	\end{align*}

### 2024-01-08 Paper/Paper_noProof.tex
introduction

--- 2024-01-08 Paper/Paper_noProof.tex
@@
 \section{Introduction}
+
+In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers.
+This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy}\dots
+
+In this context, application of DNNs in safety critical applications is therefore cautiously envisioned.
+For that to happen at a large scale, hard guarantees should be provided, so that to avoid tremendous consequences.
+It is the reason for the developpement of (hard) verification tools since 2016, with now many tools with different trade offs from exact computation but slow (e.g.
+Marabou/Reluplex), up to very efficient but also incomplete (e.g.
+ERAN-DeepPoly).
+To benchmark these tools, a competition has been run since 2019, namely VNNcomp.
+The current overall better performing tool is $\alpha$-$\beta$-Crown, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs down to very efficient on larger DNNs.
+
+While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a Network, an Image and a small neighbourhood around this image, 
+is it the case that all the images in the neighbourhood are classified in the same way.
+While some quite large DNNs (e.g.
+ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input to check local robustness), with all inputs either certified robust or an attack on robustness is found in the neighbourhood,
+some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analyzed fully, with $\approx 20 \%$ of inputs where neither of the decisions can be reached.
+The main difference between these DNNs with very different behaviors lies in that the DNNs which are trained to be robust are much easier to verify, while the DNNs trained in a "natural" way are much harder to verify.
+
+In this paper, we focus on uncovering what makes the DNNs trained in a natural way so hard to verify.
+To do so, we analyze the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly, the Linear Programming approximation, PRIMA, and different versions of ($\alpha$)($\beta$)-CROWN.
+All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds.
+For instance, if for all image $I'$ in the neighborhood of image $I$, we have $weight_{I'}(n'-n) < 0$ for $n$ the output neuron corresponding to the expected class, then we know that the DNN is robust in the neighborhood of image $I$.
+We restrict the formal study to DNNs using only the standard ReLU activation function, although nothing specific prevents the results to be extended to more general architectures.
+We uncover that {\em compensations} (see next paragraph) is the phenomenon creating  inacurracy.
+We verified experimentally that indeed DNNs trained in a natural way have much more heavy compensating pairs than DNNs trained in a robust way.
+
+Formally, a compensating pair is a pair of path $(\pi,\pi')$ between a pair of neurons 
+$(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
+Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
+That is, it is loaded by $(w+w') weight(a)$.
+As $w,w'$ have oppositve sign, they will compensate (partly) each other.
+The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
+However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which all the efficient tools try to avoid because it is very expansive (could be exponential in the number of such ReLU nodes opened).
+
+Our first main contribution is to formally show, in Theorem \ref{th1}, that compensation is the sole reason for the inacuraccy as (most) efficient algorithms will compute exact bounds for all neurons if there is no compensating pair of paths at all.
+While this theorem is theoretically interesting, it is not usable in practice as (almost) all networks have some compensating pairs.
+However, this notion of compensating pairs opens a first interesting optimization concerning an exact abstraction of the network using a Mixed Integer Linear Program \cite{MILP}, where the weight of each neuron is a linear variable, and each ReLU node is associated with a binary variable, so that the values that can be reached by the neuron variable is exactly the value that can be reached by the weight of this neuron considering inputs of the DNN in the fixed neighbourhood.
+While LP tools can scale to thousands of variables, MILP encoding can only be solved for a limited number of binary variables.
+This suggests that a simpler encoding could be used for those ReLUs that are not on compensating pairs, as their precise outcome may not be necessary.
+
+Our second main contribution is to show formally in Theorem \ref{th2}, that 
+encoding all ReLU nodes on a pair of compensating paths with a binary variable,
+and using linear relaxation for the other ReLU nodes, will lead to exact bounds for (most) of the algorithms considered.
+This theorem allows to restrict the number of integer variables, and thus to obtain encodings that are faster to solve.
+Practically, however, (almost) all ReLU nodes are on some compensating path, and using this exact restricted MILP encoding will be too time consuming.
+
+Our third main contribution is more practical, proposing Algorithm \ref{algo1} based on this knowledge that compensating pair of paths are the reason for inacurracy.
+The idea is thus to use this information to rank the ReLU nodes in terms of importance, and only keep the most important ones as binary variables, and use linear relaxation for the least important ones.
+%More precisely, the algorithm will, as DeepPoly, consider layers one by one and neurons $b$ %on this layer one by one, selecting the most heavy pairs of compensating path ending in $b$
+%and associating these nodes with a binary variable. Then an MILP tool such as Gurobi is used %to compute the lower and upper bound for node $b$. 
+Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^k LP(N))$, where $N$ is the number of nodes of the DNN, $k$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
+This complexity is an upper bound, as e.g.
+Gurobi is fairly efficient and never need to consider all of the $2^k$ ReLU configurations to compute the bounds.
+Keeping $k$ reasonably low thus provides an efficient algorithm.
+By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
+An additional interesting point is that it is extremely easy to parallelize, as all the nodes in the same layer can be run in parallel.
+We verify experimentally that the algorithm offers interesting trade offs, by testing on local robustness for DNNs trained "naturally" 
+(and thus difficult to verify).
+
+This paper does not focuss on producing the most efficient tool, and we did not spend engeenierial effort to optimize it.
+The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.
+For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in $\beta$-CROWN).
+Still, evaluation of the methodology versus even the most efficient tools reveal a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification.
+
+\smallskip
+
+\noindent {\bf Comparison with related work:}
+Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on some ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inacurracy.
+If the ReLU nodes to abstract are chosen accurately, the result should be more accurate than early stopping the MILP algorithm using all the nodes.
+
+Compared with the linear relaxation of the MILP encoding, our algorithm is strictly more accurate by design, but it will also be slower.
+
+Compared with ERAN-Deeppoly \cite{deeppoly}, which compute bounds on the value in a very efficient way, we prove that the LP encoding is strictly more accurate, which as far as we know is a another novel result.
+To be more precise, DeepPoly
+abstract the weight of every node using two functions, one upper functions and one lower function. While the upper funciton is fixed, there are 2 choices for the lower bound.
+We prove in Proposition  \ref{LP} that the LP relaxation corresponds exactly to the intersection of both choices.
+It is thus more accurate than DeepPoly, but also not as efficient.
+Therefore, our algorithm will also be (much) more accurate than DeepPoly, but also not as efficient.
+
+For comparison, $\alpha$-$\beta$ CROWN (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
+On simple networks, such as those trained robust,
+this is particularly efficient because branch and bound can find very efficiently the bounds
+focusing on the actual question, considering the important branchs, while our algorithm will be less efficient as it has to consider each nodes one by one from the start.
+However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider and not enough can be discarded early.
+
+On such complex DNN, $\alpha$-$\beta$ CROWN resorts to a "refined" path, where the bounds on the first few layers are computed using the (exact) MILP encoding, with a time-out, reporting the best bounds that can be obtained.
+In our algorithm, this is pushed to all layers, which is possible in our case as we select only a limited number of important ReLU nodes to encode as binary variables, while this would be infeasible without the selection based on the compensating pairs.
+The refined version is particularly efficient on small networks, but as the network grows, the more work BaB needs to do and faces the same wall, and our algorithm becomes more accurate.
+
+Concerning PRIMA, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do).
+This allows to keep very efficiently dependencies from potentially many layers beforehand.
+We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between nodes.
+Our method is much more accurate locally, but we will tend to loose precision for  dependencies created many layers ago.
+Experimental tend to show that most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago).
+Also, the dependencies between nodes limit the paralelism, unlike in our method, which explains why we obtain both faster and more accurate results than Prima.
+
+Finally, alogirthms resorting to absraction on the network rather than abstraction of the values are much more different.
+For instance, Reluplex/Marabou is such an algorithm.
+Its original aim is to be a complete tool, so much slower but also more accurate than what we propose.
 
@@
 
-In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.
+In this subsection, we will introduce the method to choose open nodes for MILP model by considering compensating pairs.
 
@@
 
-We explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
+We explain the framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
 
@@
 
-The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the MNIST image dataset.
+The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the standard MNIST image database. This image can have more unstable nodes in each layer.
 
@@
 
-\[
-\begin{array}{c|c|c}
-
-	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
-	0  &  2.22 & 2.22  \\ \hline
-	10  &  1.84 & 2.03  \\ \hline
-	20  &  1.50 & 1.82  \\ \hline
-	30  &  1.28 & 1.62  \\ \hline
-	40  &  1.14 & 1.44  \\ \hline
-	50  &  1.06 & 1.23  \\ \hline
-\end{array}
-\]
-
 \subsubsection*{Node chosen in the third hidden layer}
@@
 The following table shows the average uncertainty of the third hidden layer when choosing different numbers of open nodes, by random or by compensating pairs.
-
-\[
-\begin{array}{c|c|c}
-
-	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
-	0  &  1.758 & 1.758  \\ \hline
-	10  &  1.677 & 1.695  \\ \hline
-	20  &  1.539 & 1.622  \\ \hline
-	30  &  1.431 & 1.542  \\ \hline
-	40  &  1.329 & 1.47  \\ \hline
-	50  &  1.243 & 1.39  \\ \hline
-\end{array}
-\]
 
@@
 
-\[
-\begin{array}{c|c|cc|cc|cc|cc}
-
-	\text{Network}  & \varepsilon&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\
-
-  &  & \mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) &\mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) \\ \hline
-
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-
-	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-\end{array}
-\]
-
 \subsection{Comparison to Incomplete Verifiers}
 
-In Table 3, we compare against two representative incomplete
-verifiers on 4 MLP networks for MNIST under the same
-set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
+We compare our method to two famous verifiers (their incomplete mode): PRIMA and $\beta$-Crown on 5 typical MNIST models.
+Basically, our method can exceed PRIMA on both accuracy and speed, and exceed $\beta$-Crown on accuracy.
 

### 2024-01-08 Paper/Paper_noProof.tex

@@
 
+\vspace*{1ex}
+
+And the pseudo-code is as follows:
+
+\begin{algorithm}
+	\caption{Process for length 3 + length 4}
+	\KwData{Sorted lists of length 3 + length 4}
+	\KwResult{Open node list}
+
+	Let $N = 0$ be the number of Chosen length 4 pair.
+
+	\While{len(Open node) $<O$}{
+		Pick the first element $P_3$ in the list of length 3\;
+
+		Let $V_3$ be the value of $P_3$\;
+
+		Pick the first element $P_4$ in the list of length 4\;
+
+		Let $V_4$ be the value of $P_4$\;
+
+		\If{$V_3 > V_4 \cdot N$}{
+			Add nodes in $P_3$ into Open list\;
+			Number of Chosen lentgh pair $N$ += 1\; 
+		}
+		\Else{
+			Add nodes in $P_4$ into Open list\;
+		}
+	}
+\end{algorithm}
+
 \section{Verification Framework}
@@
 
-We explain the framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
+In this section, We will explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
 
@@
 
+\begin{table}
+	\centering
+	\begin{tabular}{c|c|c}
+
+	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
+	0  &  2.22 & 2.22  \\ \hline
+	10  &  1.84 & 2.03  \\ \hline
+	20  &  1.50 & 1.82  \\ \hline
+	30  &  1.28 & 1.62  \\ \hline
+	40  &  1.14 & 1.44  \\ \hline
+	50  &  1.06 & 1.23  \\ \hline
+\end{tabular}
+\caption{}
+\label{tab:example0}
+\end{table}
+
 \subsubsection*{Node chosen in the third hidden layer}
@@
 
+\begin{table}
+	\centering
+	\begin{tabular}{c|c|c}
+
+	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
+	0  &  1.758 & 1.758  \\ \hline
+	10  &  1.677 & 1.695  \\ \hline
+	20  &  1.539 & 1.622  \\ \hline
+	30  &  1.431 & 1.542  \\ \hline
+	40  &  1.329 & 1.47  \\ \hline
+	50  &  1.243 & 1.39  \\ \hline
+\end{tabular}
+\caption{}
+\label{tab:example1}
+\end{table}
+
 \subsection{Experiments Results}
-
-The following table is the summary of 5 experiments.
 
@@
 
-We compare our method to two famous verifiers (their incomplete mode): PRIMA and $\beta$-Crown on 5 typical MNIST models.
-Basically, our method can exceed PRIMA on both accuracy and speed, and exceed $\beta$-Crown on accuracy.
+In Table 3, we compare against two representative incomplete
+verifiers on 4 MLP networks for MNIST under the same
+set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
 
-We do tests on 5 typical MNIST models.
+\begin{table}
+	\centering
+	\begin{tabular}{c|c|cc|cc|cc|cc}
+
+		\text{Network}  & $\varepsilon$&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\
+
+		&  & \textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) &\textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) \\ \hline
+
+		\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+		\textrm{MLP}\ 8$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+		\textrm{MLP}\ 8$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+
+		\textrm{MLP}\ 6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+	\end{tabular}
+	\caption{The data of verified accuracy (\%) and average time (s) of 1000 images evaluated on the PRIMA and on the beta-Crown are in CITE.}
+	\label{tab:example}
+\end{table}
+
+On all 4 networks, our fast version can exceed PRIMA both in accuracy and speed. On all 4 networks, our slow version can have a similar verified accuracy as beta-Crown.
 

### 2024-01-09 Paper/Paper_noProof.tex
test
introduction.tex

--- 2024-01-08 Paper/Paper_noProof.tex
@@
 \section{Introduction}
+
+\input{introduction}
 

### 2024-01-09 Paper/introduction.tex
introduction.tex

In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers. This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy}\dots

In this context, application of DNNs in safety critical applications is therefore cautiously envisioned. For that to happen at a large scale, hard guarantees should be provided, so that to avoid tremendous consequences. It is the reason for the developpement of (hard) verification tools since 2016, with now many tools with different trade offs from exact computation but slow (e.g. Marabou/Reluplex), up to very efficient but also incomplete (e.g. ERAN-DeepPoly). To benchmark these tools, a competition has been run since 2019, namely VNNcomp. The current overall better performing tool is $\alpha$-$\beta$-Crown, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs down to very efficient on larger DNNs.

While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a Network, an image and a small neighbourhood around this image, 
is it the case that all the images in the neighbourhood are classified in the same way.
While some quite large DNNs (e.g. ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input to check local robustness) \cite{crown}, with all inputs either certified robust or an attack on robustness is found in the neighbourhood;
some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analyzed fully, with $\approx 20 \%$ of inputs where neither of the decisions can be reached \cite{crown}. The main difference between these DNNs with very different behaviors lies in that the DNNs which are trained to be robust are much easier to verify, while the DNNs trained in a "natural" way are much harder to verify.

In this paper, we focus on uncovering what makes the DNNs trained in a natural way so hard to verify (because for "easier" DNNs, adequate methods already exist). To do so, we analyze the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly, the Linear Programming approximation, PRIMA, and different versions of ($\alpha$)($\beta$)-CROWN. All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds. For instance, if for all image $I'$ in the neighborhood of image $I$, we have $weight_{I'}(n'-n) < 0$ for $n$ the output neuron corresponding to the expected class, then we know that the DNN is robust in the neighborhood of image $I$. We restrict the formal study to DNNs using only the standard ReLU activation function, although nothing specific prevents the results to be extended to more general architectures. We uncover that {\em compensations} (see next paragraph) is the phenomenon creating  inacurracy. We verified experimentally that indeed DNNs trained in a natural way have much more heavy compensating pairs than DNNs trained in a robust way.

Formally, a compensating pair is a pair of paths $(\pi,\pi')$ between a pair of neurons 
$(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$. Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$. That is, it is loaded by $(w+w') weight(a)$. As $w,w'$ have oppositve sign, they will compensate (partly) each other. The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$. However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which all the efficient tools try to avoid because it is very expansive (could be exponential in the number of such ReLU nodes opened).

Our first main contribution is to formally show, in Theorem \ref{th1}, that compensation is the sole reason for the inacuraccy as (most) efficient algorithms will compute exact bounds for all neurons if there is no compensating pair of paths at all.
While this theorem is theoretically interesting, it is not usable in practice as (almost) all networks have some compensating pairs. However, this notion of compensating pairs opens a first interesting optimization concerning an exact abstraction of the network using a Mixed Integer Linear Program \cite{MILP}, where the weight of each neuron is a linear variable, and each ReLU node is associated with a binary variable, so that the values that can be reached by the neuron variable is exactly the value that can be reached by the weight of this neuron considering inputs of the DNN in the fixed neighbourhood. While LP tools can scale to thousands of variables, MILP encoding can only be solved for a limited number of binary variables. This suggests that a simpler encoding could be used for those ReLUs that are not on compensating pairs, as their precise outcome may not be necessary.

Our second main contribution is to show formally in Theorem \ref{th2}, that 
encoding all ReLU nodes on a pair of compensating paths with a binary variable,
and using linear relaxation for the other ReLU nodes, will lead to exact bounds for (most) of the algorithms considered. This theorem allows to restrict the number of integer variables, and thus to obtain encodings that are faster to solve. Practically, however, (almost) all ReLU nodes are on some compensating path, and using this exact restricted MILP encoding will be too time consuming.

Our third main contribution is more practical, proposing Algorithm \ref{algo1} based on this knowledge that compensating pair of paths are the reason for inacurracy. The idea is thus to use this information to rank the ReLU nodes in terms of importance, and only keep the most important ones as binary variables, and use linear relaxation for the least important ones.
%More precisely, the algorithm will, as DeepPoly, consider layers one by one and neurons $b$ %on this layer one by one, selecting the most heavy pairs of compensating path ending in $b$
%and associating these nodes with a binary variable. Then an MILP tool such as Gurobi is used %to compute the lower and upper bound for node $b$. 
Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^k LP(N))$, where $N$ is the number of nodes of the DNN, $k$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes. This complexity is an upper bound, as e.g. Gurobi is fairly efficient and never need to consider all of the $2^k$ ReLU configurations to compute the bounds. Keeping $k$ reasonably low thus provides an efficient algorithm. 
By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes. An additional interesting point is that it is extremely easy to parallelize, as all the nodes in the same layer can be run in parallel. 
We verify experimentally that the algorithm offers interesting trade offs, by testing on local robustness for DNNs trained "naturally" 
(and thus difficult to verify).

This paper does not focuss on producing the most efficient tool, and we did not spend engeenierial effort to optimize it. The focus is instead on the novel notion of compensation, the associated methodology and its evaluation. For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in $\beta$-CROWN). Still, evaluation of the methodology versus even the most efficient tools reveal a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification.

\smallskip

\noindent {\bf Comparison with related work:} Here, we will compare with some (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on some ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inacurracy. If the ReLU nodes to abstract are chosen accurately, the result should be more accurate than early stopping the MILP algorithm using all the nodes.

Compared with the linear relaxation of the MILP encoding, our algorithm is strictly more accurate by design, but it will also be slower.

Compared with ERAN-Deeppoly \cite{deeppoly}, which compute bounds on the value in a very efficient way, we prove that the LP encoding is strictly more accurate, which as far as we know is a another novel result. To be more precise, DeepPoly
abstract the weight of every node using two functions, one upper functions and one lower function. While the upper funciton is fixed, there are 2 choices for the lower bound.
We prove in Proposition  \ref{LP} that the LP relaxation corresponds exactly to the intersection of both choices. It is thus more accurate than DeepPoly, but also not as efficient. Therefore, our algorithm will also be (much) more accurate than DeepPoly, but also not as efficient.

For comparison, $\alpha$-$\beta$ CROWN \cite{} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities). On simple networks, such as those trained robust, 
this is particularly efficient because branch and bound can find very efficiently the bounds
focusing on the actual question, considering the important branchs, while our algorithm will be less efficient as it has to consider each nodes one by one from the start.
However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider and not enough can be discarded early.

On such complex DNN, $\alpha$-$\beta$ CROWN resorts to a "refined" path, where the bounds on the first few layers are computed using the (exact) MILP encoding, with a time-out, reporting the best bounds that can be obtained. In our algorithm, this is pushed to all layers, which is possible in our case as we select only a limited number of important ReLU nodes to encode as binary variables, while this would be infeasible without the selection based on the compensating pairs. The refined version is particularly efficient on small networks, but as the network grows, the more work BaB needs to do and faces the same wall, and our algorithm becomes more accurate.

Concerning PRIMA, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do). This allows to keep very efficiently dependencies from potentially many layers beforehand. We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurones. 
Our method is more accurate locally, but we will tend to loose precision for  dependencies created many layers ago. Experimental results tend to show that most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago). Also, the dependencies between nodes limit the paralelism, unlike in our method, which explains why we obtain both faster and more accurate results than PRIMA.

Finally, algoirthms resorting to absraction on the network (e.g. Reluplex/Marabou \cite{Reluplex,Marabou}) rather than abstraction on the values are much more different. These algorithms have been developped to be complete, so much slower but also more accurate than what we propose.

### 2024-01-09 Paper/Paper_noProof.tex
image

@@
 
-\section{Background}
+\section{Preliminaries}
 
-We follow some notions in PRIMA's and Beta-Crown's papers: we use lower case Latin for scalars, bold for vectors
-$\boldsymbol{z}$, capitalized bold for matrices $\boldsymbol{W}$. In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
+In this paper, we will use lower case Latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
+capitalized bold for matrices $\boldsymbol{W}$, similar to 
+notations in \cite{prima,crown}.
+
+%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
 
 \subsection{Neural Network and Verification}
+
+\begin{figure}[t!]
+\centering
+	\includegraphics[scale=0.4]{example.png}
+\caption{A DNN example from \cite{kneuron}}
+\label{fig1}
+\end{figure}
 
@@
 
+% test
+
 \section{Related Work}

### 2024-01-09 Paper/Paper_noProof.tex
backgrund

@@
 
-\section{Preliminaries}
+\section{Background}
 
-In this paper, we will use lower case Latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
-capitalized bold for matrices $\boldsymbol{W}$, similar to 
-notations in \cite{prima,crown}.
+In this paper, we will use lower case latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
+capitalized bold for matrices $\boldsymbol{W}$, similar to notations in \cite{prima,crown}.
+To simplify the notations, we restrict the presentation to feed-forward, 
+fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
+$ReLU(x)=x$ for $x \geq 0$ and $f(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
 
@@
 % testtesttesttest
+An $\ell$-layer DNN is provided by $\ell$ weight matrices 
+$\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
+and $\ell$ bias vectors $\boldsymbol{b}^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
+We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
+$d_0$ the input dimension, and $d_\ell$ the output dimension.
 
-We focus on full-connected neural network.
-The network has weights and bias to send the input to output along hidden layers.
-In formula, the input layer of a neural network is a vector $\boldsymbol{x}$ in $\mathbb{R}^{d_0}$, and the $i$-th hidden layer  is a vector in $\mathbb{R}^{d_i}$, and the output layer is a vector in $\mathbb{R}^{d'}$ or a scale.
-The weights, bias and activation functions decide propagate the from previous to the next layer.
-In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight $\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, the bias is a vector $\boldsymbol{b}^i$ in $\mathbb{R}^{d_i}$, and the activation function is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, then the value of $i$-th layer is computed by: \begin{align*}
+Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
+denoting $\hat{\boldsymbol{z}}^{i}(n)={\boldsymbol{z}}^0$, we define inductively the weight vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
+\begin{align*}
+	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \boldsymbol{b}^i\\
+	\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
+\end{align*}
+
+The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
+$\boldsymbol{z}$ is called pre-activation values, 
+and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
+Neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b}$ to denote the weight from neuron $a$ to $b$.
+We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
+
+\iffalse
+and the $i$-th hidden layer is a vector in $\mathbb{R}^{d_i}$, 
+and the output layer is a vector in $\mathbb{R}^{d'}$ or a scale. 
+The weights, bias and activation functions decide propagate the from previous to the next layer. In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight 
+$\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, 
+the bias is a vector $\boldsymbol{b}^i$ in $\mathbb{R}^{d_i}$, and the activation function 
+is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, 
+then the value of $i$-th layer is computed by: 
+\begin{align*}
 	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \boldsymbol{b}^i\\
@@
 We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
+\fi
 

### 2024-01-09 Paper/Paper_noProof.tex
background

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\vx}{\boldsymbol{x}}
+\newcommand{\vW}{\boldsymbol{W}}
+\newcommand{\vz}{\boldsymbol{z}}
+\newcommand{\vb}{\boldsymbol{b}}
 
@@
 Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-denoting $\hat{\boldsymbol{z}}^{i}(n)={\boldsymbol{z}}^0$, we define inductively the weight vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
+denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the weight vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
 \begin{align*}
@@
 $\boldsymbol{z}$ is called pre-activation values, 
-and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-Neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b}$ to denote the weight from neuron $a$ to $b$.
+and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
 We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
+Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b}$ to denote the weight from neuron $a$ to $b$.
+Similarly, for input $\boldsymbol{x}$, we denote by $weight_{\boldsymbol{x}}(a)$
+the weight of neuron $a$ when the the input is $\boldsymbol{x}$.
 
@@
 
-The verification problem is to determine whether the output of a neural network will be affected under small perturbations to the input.
+\medskip
+
+Similarly, for simplicity, we focus on local robustness for the verification problem, altough generalization to other problems pose no problem. 
+Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
 In formula, if we use a distance $d$, and if the $\boldsymbol{x}_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(\boldsymbol{x},\boldsymbol{x}_0)<\varepsilon\}$ where $\varepsilon$ is the parameter measuring the size of perturbation.

### 2024-01-09 Paper/Paper_noProof.tex
section 3

@@
 
-\subsection{Neural Network and Verification}
-
-\begin{figure}[t!]
-\centering
-	\includegraphics[scale=0.4]{example.png}
-\caption{A DNN example from \cite{kneuron}}
-\label{fig1}
-\end{figure}
+%\subsection{Neural Network and Verification}
 
@@
 and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
-Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $weight_{\boldsymbol{x}}(a)$
-the weight of neuron $a$ when the the input is $\boldsymbol{x}$.
+For $\boldsymbol{x}=\vz^0$ the vector of input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
+Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
+Similarly, for input $\boldsymbol{x}$, we denote by $weight_{\boldsymbol{x}}(a)$ the weight of neuron $a$ when the the input is $\boldsymbol{x}$.
+A path $\pi$ will be a sequence
+$\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight $w(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
 
@@
 
-Similarly, for simplicity, we focus on local robustness for the verification problem, altough generalization to other problems pose no problem. 
+Concerning the verification problem, we focus for simplicity on the usual local robustness question.
 Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
-In formula, if we use a distance $d$, and if the $\boldsymbol{x}_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(\boldsymbol{x},\boldsymbol{x}_0)<\varepsilon\}$ where $\varepsilon$ is the parameter measuring the size of perturbation.
-And the problem will be \begin{align*}
-	\forall \boldsymbol{x}\in\mathcal{D} \   f(\boldsymbol{x}) = f(\boldsymbol{x}_0).
-\end{align*} In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
+Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
+\begin{align*}
+	\forall \boldsymbol{x'} \text{ s.t. } d(x,x')\leq \varepsilon, \text{ we have }  
+	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
+\end{align*}
+
+\iffalse
+In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
 \forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
@@
 In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$.
-We will consider $L^{\infty}$ norm, that is $$d(\boldsymbol{x},\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|,$$ the max value of distance of each dimension.
+
+In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\boldsymbol{x},\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
+\fi
+
+\section{Value Abstraction for DNN verification}
+
+\begin{figure}[t!]
+	\centering
+		\includegraphics[scale=0.4]{example.png}
+	\caption{A DNN example from \cite{kneuron}}
+	\label{fig1}
+	\end{figure}
+
+An efficient and prolific line of work concerning DNN verification has been to develop value abstraction of the network.
+The idea is to compute upper and lower bounds on the values of (some) neurons in the DNN when the inputs are in a given neighbourhood, in order to conclude on the robustness without needing to compute the values exactly for all inputs.
+
+Consider the simpler abstraction, called the box abstraction \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
+For instance, on the DNN example of Fig \ref{fig1},
 

### 2024-01-10 Paper/Paper_noProof.tex
Table
Reference

@@
 	2.
-The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ba}\cdot W_{cb}\cdot W_{dc}\cdot W_{ed}\cdot \cdots$$
+The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ab}\cdot W_{bc}\cdot W_{cd}\cdot W_{ed}\cdot \cdots$$
 
@@
 
-		\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 51 & 159 &    68.4 & 142 & 69.9 & 102 \\ \hline
 
-		\textrm{MLP}\ 8$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 8$\times$100\  &   0.026& 52.7 & 92.3 & 42.8 & 301 &    65.8 & 364 & 62 & 103 \\ \hline
 
-		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 69 & 224 &    76.8 & 279 & 77.4 & 86 \\ \hline
 
-		\textrm{MLP}\ 8$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
+		\textrm{MLP}\ 8$\times$200\  &   0.015& 68.1 & 297 & 62.4 & 395 &    79.1 & 535 & 73.5 & 95 \\ \hline
 
@@
 
+\bibliographystyle{plain}
+\bibliography{references}
+
 \end{document}

### 2024-01-10 Paper/Paper_noProof.tex
section 3

--- 2024-01-09 Paper/Paper_noProof.tex
@@
 \newcommand{\vx}{\boldsymbol{x}}
+\newcommand{\vy}{\boldsymbol{y}}
 \newcommand{\vW}{\boldsymbol{W}}
@@
 
+In this section, we describe different value (over)-abstractions that are used by efficient algorithms to certify the networks.
+Although the analysis can be approximated, the over-abstraction ensures that all behavior in the original network are possible in the overabstraction, and thus if the over abstraction is safe, then so will be the original network.
+
+\subsection{Box and DeepPoly Abstraction}
+
 \begin{figure}[t!]
@@
 		\includegraphics[scale=0.4]{example.png}
-	\caption{A DNN example from \cite{kneuron}}
+	\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
 	\label{fig1}
@@
 
-Consider the simpler abstraction, called the box abstraction \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
-For instance, on the DNN example of Fig \ref{fig1},
+Consider the simpler abstraction, called the {\em box abstraction} \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
+For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $X_5,x_6 \in [0,2]$, and $x_7 \in [0,6]$ while $x_8 \in [1.5,3.5]$.
+While the bounds of $x_1, \ldots, x_6$ are correct (for all $\alpha$
+in the range, there is an input $\vy$ such that $weight_{\vy}(x_i))=\alpha$), 
+it is no more the case from the next layer (starting in $x_7,x_8$) because of potential 
+dependencies between earlier neurons: $x_3$ reaches weight $2$ only when $x_1=x_2=2$,
+in which case $x_4$ reaches weight $0$. Hence, it is impossible that $weight(x_7)$ reaches $6$, as it would require both $x_3$ and $x_4$ to have weight $2$.
+
+A still extremely fast algorithm that aleviates some of this issue is known as {\em DeepPoly} \cite{DeepPoly}, also rediscovered as the CROWN algorithm \cite{Crown}. Instead of 
+hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
+For instance, $f_i \leq weight(x_i) \leq g_i$ with $f_5(x_3)=f_6(x_4)=0$ and 
+$g_5(x_3) = \frac{x_3+2}{2}$,
+$g_6(x_4) = \frac{x_4+2}{2}$. 
+With that, we get 
+$x_7 \leq g_5(x_3) + 2 g_6(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{2x_1 - x_4 + 6}{2}\leq 4.5$.
+
+While there is an optimal linear function for the upper bound $g_i$ for ReLU nodes, there are two choices for the lower bound: $f_i(x_i) = 0$ or $x_i$.
+In the DeepPoly algorithm, the choice is made by considering the range of $x_i=[a,b]$ with $a < 0 < b$.
+If $|a|\geq |b|$ then $0$ is used, while if $|b|>|a|$ then $x_i$ (the identity function) is used.
+Let us call
+$\overline{\mbox{DeepPoly}}$ the Deeppoly algorithm such that 
+$f_i(x_i) = 0$ is always used, and $f_i(x_i) = x_i$ is never used. 
+It has a main advantage, as it subsmues the box abstraction.
+Indeed, taking an interval $x_i \in [-0.2,5]$, it gives $ReLU(x_i) \in [0,5]$, 
+while the normal DeepPoly algorithm would only allow to conclude that $ReLU(x_i) \in [-0.2,5]$.
+
+\subsection{PRIMA and $\beta$-CROWN}
 

### 2024-01-10 Paper/Paper_noProof.tex
Writing

--- 2024-01-10 Paper/Paper_noProof.tex
@@
 
-And the pseudo-code is as follows:
+The pseudo-code is as follows ():
 
@@
 
-In this section, We will explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.
+In this section, we will sketch the framework.
 
-\subsection{Process for one image}
+\subsection{Structure}
 
-The basic unit of running is image: all parameters will be reset when one image is finished.
+\subsubsection*{Precomputation}
 
-The process for one image is clear: compute the upper and lower bounds of nodes layer by layer to the output layer.
+The open node chosen is the key part of the whole framework but costs a lot of time. So some computation (those do not rely on certain image and bounds) is moved to the precomputation part.
 
-Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers.
+%The precomputation corresponds to the simplest case: source node fixed.
+We will compute and store a limited number of paths with highest (absolute) values before running any image.
+This does not rely on other parameters or results(bounds).
+%
+%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
+This will use much less time.
+
+\subsubsection*{Process for one image} An image is the basic unit in whole process.
+The process of one image is simple: compute the concrete bounds of nodes layer by layer, use the bounds of previous layer to build MILP models of current layer.
+In one layer, nodes runs in parallel.
+
+%Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers.
 Then we will compute bounds of every node in $l_i$ in parallel using the data of bounds of previous nodes.
@@
 
-Some parameters may be changed during layers.
+%Some parameters may be changed during layers.
 Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
@@
 
-In one layer, in principle, running for nodes are in principle independent and can be done in parallel. In our experiments, some local parameters will be adjusted from nodes to nodes.
-
-\subsection{Precomputation}
-
-The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node.
-
-The precomputation corresponds to the simplest case: source node fixed.
+%The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node. 
+%
+%The precomputation corresponds to the simplest case: source node fixed.
 We will compute and store a limited number of paths with highest (absolute) values before running any image.
 This does not rely on other parameters or results(bounds).
-
-Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
+%
+%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
 This will use much less time.
 
-\subsection{Process for one node}
+\subsubsection*{Process for one node}
 
-For one node, we will build the MILP model for it.
-
-The most important parameter is the number $O$ mentioned in last section:  the number of open nodes.
-When the program creates a model for a node, we will read this parameter to decide how many nodes to open in this model.
-This parameter can change during the running of an image by the mechanic of the code.
-
-Another group of parameters is for the optimization of models.
-
-The optimization of a model is carrying by loops.
+ The optimization of a model consists of loops.
 For each loop, the model will do optimization by a timeout and observe the result.
@@
 
-During the loop of optimization, parameters might be changed and the model may be rebuild by the new parameter.
-
-\subsection{Global Process}
+\subsubsection*{Global Process}
 
@@
 
-%\subsubsection*{Run one image}
-%
-%In the very fast turn, we use DeepPoly. So, all discussion below only consider fast and slow turns.
-%
-%An image is the basic unit in the running. The running is carrying layer by layer. The bounds obtained in previous layer will be used to build the model for the next layer, till the output layer.
-%
-%Some parameters may be changed during layers.
-Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
-Here, \emph{local} is opposite to \emph{global}.
-We have global timeout parameters for images and the whole running.
-Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
-%
-%In one layer, in principle, running for nodes are in principle independent and can be done in parallel. In our experiments, some local parameters will be adjusted from nodes to nodes.
+\subsection{Parameters}
 
-%\subsubsection*{Create Models}
-%
-%The most important parameter is the number $O$ mentioned in last section:  the number of open nodes.
-When the program creates a model for a node, we will read this parameter to decide how many nodes to open in this model.
-This parameter can change during the running of an image by the mechanic of the code.
-%
-%\subsubsection*{Optimization for a node}
-%
-%Another group of parameters is for the optimization of models. 
-%
-%The optimization of a model is carrying by loops.
-For each loop, the model will do optimization by a timeout and observe the result.
-If it gets improvement, then continue the loop until the optimize bounds or the longer timeout.
-Otherwise it will give up optimization and store the best bounds obtained so far.
-%
-%During the loop of optimization, parameters might be changed and the model may be rebuild by the new parameter.
+Parameters like open node parameter $O$ is important in the frame. Basically, all parameters will be reset after one image.
 
-\subsubsection*{Other Setting}
+\subsubsection*{Global parameters}
 
-In our experiments, we have not used PGD-attack to rule out images. In principle, there is no obstacle to use PGD-attack.
+\subsubsection*{Local parameters}
+
+$O$ and timeout parameters for loops will change frequently during the loops of one node. These change will not reset until the end of one layer or one image.
+
+\subsection{Other Setting}
+
+In our experiments, we have not used PGD-attack to exclude some images. In principle, there is no obstacle to use PGD-attack.
 

### 2024-01-10 Paper/Paper_noProof.tex
proofs.tex

@@
 
-\subsection{Experiments Results}
+\section{Proofs}
+
+\input{proofs}
+
+\section{Experiments Results}
 

### 2024-01-10 Paper/Paper_noProof.tex
fixed bug

@@
 
+First, remark that weighted sums is a linear function, so it is easy to represent it explicitly.
+The only problematic part to represent accurately is the ReLU function.
+While it is fairly simple piecewise linear function with 2 modes ($x<0$ and $x \geq 0$), it is not linear.
+Considering its iterated impact along the different layers of a ReLU DNN is much more complex that it seems.
+First, let us remark that it is easy to represent exactly $ReLU(x)$
+in case $x$ is known to be entirely positive and in the case where it is entirely negative
+(such a neuron $x$ is called stable), as in both case there is only one known linear mode involved. Hence, the sole problem remains how to treat unstable neurons.
+
 Consider the simpler abstraction, called the {\em box abstraction} \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
@@
 While the bounds of $x_1, \ldots, x_6$ are correct (for all $\alpha$
-in the range, there is an input $\vy$ such that $weight_{\vy}(x_i))=\alpha$), 
+in the range, there is an input $\vy$ such that $weight_{\vy}(x_i))=\alpha$, 
 it is no more the case from the next layer (starting in $x_7,x_8$) because of potential 
@@
 
-A still extremely fast algorithm that aleviates some of this issue is known as {\em DeepPoly} \cite{DeepPoly}, also rediscovered as the CROWN algorithm \cite{Crown}. Instead of 
+A still extremely fast algorithm that aleviates some of this issue is known as {\em deeppoly} \cite{deeppoly}, also rediscovered as the CROWN algorithm \cite{crown}. Instead of 
 hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
@@
 
-\subsection{MILP formation of $\ReLU$ functions}
+\subsection{MILP formulation of DNNs}
 
-In literature, many methods have been used to approximate $\ReLU$ functions. One of them is MILP (or MIP, Mixed Integer Linear Programming).
-
-For a activation $x=\ReLU(y)$, if we already know $y's$ rough upper and lower bounds $u,l$, then if $u>0$ and $l<0$, we call $y$ is unstable; otherwise, $y$ is stable.
-In practice, stable node is easier because $\ReLU$ function becomes a linear function on this node.
-The key problem is to deal with unstable nodes.
+At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method:
 

### 2024-01-10 Paper/introduction.tex
fixed bug

@@
 
-For comparison, $\alpha$-$\beta$ CROWN \cite{} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
+For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
 On simple networks, such as those trained robust,

### 2024-01-10 Paper/Paper_noProof.tex
some bug in MILP

@@
 
-A still extremely fast algorithm that aleviates some of this issue is known as {\em deeppoly} \cite{deeppoly}, also rediscovered as the CROWN algorithm \cite{crown}. Instead of 
+A still extremely fast algorithm that aleviates some of this issue is known as {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
 hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
@@
 While there is an optimal linear function for the upper bound $g_i$ for ReLU nodes, there are two choices for the lower bound: $f_i(x_i) = 0$ or $x_i$.
-In the DeepPoly algorithm, the choice is made by considering the range of $x_i=[a,b]$ with $a < 0 < b$.
-If $|a|\geq |b|$ then $0$ is used, while if $|b|>|a|$ then $x_i$ (the identity function) is used.
+In the DeepPoly algorithm, the choice is made by considering the range of an unstable neuron $x_i=[\alpha,\beta]$ with $\alpha < 0 < \beta$.
+If $|\alpha|\geq |\beta|$ then $0$ is used, while if $|\beta|>|\alpha|$ then $x_i$ (the identity function) is used.
 Let us call
@@
 $f_i(x_i) = 0$ is always used, and $f_i(x_i) = x_i$ is never used. 
-It has a main advantage, as it subsmues the box abstraction.
+It has a main advantage, as it subsmumes the box abstraction.
 Indeed, taking an interval $x_i \in [-0.2,5]$, it gives $ReLU(x_i) \in [0,5]$, 
@@
 
+\iffalse
 \subsection{PRIMA and $\beta$-CROWN}
+\fi
 
-\subsection{MILP formulation of DNNs}
+\subsection{MILP and LP encodings for DNNs}
 
-At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method:
-
-In literature, if $x=\ReLU(y)$, and $y$ is unstable, then this function can be formulated in MILP with one integer variable $a$ valued in ${0,1}$ (i.e., a binary variable) by:
-
-\vspace*{-4ex}
-
+At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction \cite{MILP}, which is a priori a complete method (but whose complete encoding is much slower). 
+Consider an unstable neuron $y \in[\alpha,\beta]$.
+The value of $\ReLU(y)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints:
+\vspace{-0.1cm}
 \begin{align*}
-	&x \geq 0, \ 
-	x \geq y-l\cdot (1-a)\\
-	&x \leq y,\ 
-	x \leq u\cdot a
+	\hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a)
 \end{align*}
 
-MILP becomes one of standard methods to compute the lower bounds and upper bounds of neurons in a pure $\ReLU$ activation network.
-Combining with the discussion from previous subsection, the verification problem is equivalent to an MILP optimization problem.
+This encoding is exact in the meaning that \cite{MILP} for all $y \in [\alpha,\beta] \setminus 0$, there is a unique solution $(a,\hat{y})$ satisfying the constraints, and we have $\hat{y}=\ReLU(y)$ (and $a$ is 0 if $y < 0$ and 1 if $y>0$, and can be either for $y=0$).
+Such an encoding can be used for all (unstable) ReLU nodes, and optimizing its value allows to certify a given image.
+However, for any networks hundreds of nodes or more, it means having hundreds of integer variables, and such network will usually not be solvable efficiently.
 
-However, the cost of optimization of an MILP model is very expensive, especially when the number of binaries increases: solving MILPs are NP-hard, and often needs exponential time to solve it.
-A typical relaxation is to change the binary variable $a$ to a continue variable, then it will be equivalent to the standard triangle LP model for $\ReLU$ function.
+MILP instances can be linearly relaxed into LP over-abstraction, where variables which were integers in 
+${0,1}$ are relaxed to be real in interval $[0,1]$, using otherwise the same encoding. 
+Solving LP instances being Polynomial time, much more efficient solution could be found, but at the price of a lack of accuracy (e.g.
+with not as thight bounds).
+This is called the {\em LP abstraction}.
 
+As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
+We state here and prove later that the LP abstraction is strictly more accurate than the DeepPoly abstraction.
+It actually corresponds to consider in DeepPoly both linear functions lower bounding the ReLU function, $ReLU{y} \geq 0$ and $ReLU{y} \geq y$, while DeepPoly consider exactly one.
+
+\begin{theorem}
+ Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints are equivalent:
+ \vspace{-0.1cm}
+ \begin{align*}
+	 \hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad & \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a), a \in [0,1] \\
+	 \text{and} \quad \hat{y} \geq 0 \quad & \wedge \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
+\end{align*}
+
+\end{theorem}
+
+\iffalse
 Our strategy is to restrict the number of binary variables, and this will definitely lose accuracy of results.
@@
 We aim is to find an algorithm, to decide which nodes should be opened such that we can have more accuracy.
+\fi
 

### 2024-01-10 Paper/Paper_noProof.tex
bug in milp

@@
 We state here and prove later that the LP abstraction is strictly more accurate than the DeepPoly abstraction.
-It actually corresponds to consider in DeepPoly both linear functions lower bounding the ReLU function, $ReLU{y} \geq 0$ and $ReLU{y} \geq y$, while DeepPoly consider exactly one.
+It actually corresponds to consider in DeepPoly both linear functions lower bounding the ReLU function, $ReLU{y} \geq 0$ and $ReLU{y} \geq y$, while DeepPoly considers exactly one.
 
-\begin{theorem}
- Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints are equivalent:
+\begin{proposition}
+	\label{LP}
+ Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems 1) and 2) of constraints are equivalent:
  \vspace{-0.1cm}
  \begin{align*}
-	 \hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad & \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a), a \in [0,1] \\
-	 \text{and} \quad \hat{y} \geq 0 \quad & \wedge \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
+	 1) \quad \hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad & \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a), \, a \in [0,1] \\
+	 \text{and} \quad  2) \quad \hat{y} \geq 0 \quad & \wedge \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
 \end{align*} 
-
-\end{theorem}
+\end{proposition}
 

### 2024-01-11 Paper/Paper_noProof.tex
Add files via upload
fix bug
milp fixed
section 3

--- 2024-01-10 Paper/Paper_noProof.tex
@@
 \begin{align*}
-	\hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a)
+	\hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \leq y-\alpha \cdot (1-a)
 \end{align*}
@@
 As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We state here and prove later that the LP abstraction is strictly more accurate than the DeepPoly abstraction.
-It actually corresponds to consider in DeepPoly both linear functions lower bounding the ReLU function, $ReLU{y} \geq 0$ and $ReLU{y} \geq y$, while DeepPoly consider exactly one.
+We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.
 
-\begin{theorem}
- Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints are equivalent:
- \vspace{-0.1cm}
+\begin{proposition}
+	\label{LP}
+ Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
+ 1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
+ \vspace{-0.3cm}
  \begin{align*}
-	 \hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad & \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a), a \in [0,1] \\
-	 \text{and} \quad \hat{y} \geq 0 \quad & \wedge \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
+	 & 1) \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \leq y-\alpha \cdot (1-a), \, a \in [0,1] \\
+	 \text{and} \quad  & 2)  \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0 \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
 \end{align*} 
+\end{proposition}
 
-\end{theorem}
+\begin{proof}
+Obviously, the 2 lower bound constraints are the same in 1) and 2).
+
+It remains to prove that the 2 upper bound contraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
+For that, we study the upper bound function in the variable $a \in  [0,1]$, with $y \in [\alpha,\beta]$ fixed.
+We have $\hat{y}$ in 1) upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, y - \alpha (1-a)))$, and this bound can be reached.
+The function $min(\beta \cdot a, y - \alpha (1-a))$ reaches its maximum for 
+$\beta \cdot a = y - \alpha (1-a)$, that is 
+$(\beta - \alpha) a = y - \alpha$, i.e. 
+$$ a = \frac{y - \alpha}{\beta-\alpha}$$
+
+It thus gives an upper bound at 
+$\beta \cdot a = \beta \frac{y - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
+\qed
+\end{proof}
 
@@
 
-\section{Compensate, Diamond and Node Chosen}
+\section{Compensating pair of paths}
 
-In this section, we will explore the key factor for the loss of accuracy in our LP/MILP models: \emph{compensating pair}.
-And we will develop a process of open node chosen by the principle of \emph{Compensating Pairs}.
-
-\subsection{Compensating pair}
+In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but too costly). 
+Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision.
 
@@
 
+\begin{figure}
+\centering
 \begin{tikzpicture}
+
 	\node[circle, draw= purple, thick, minimum width = 20,
@@
 \end{tikzpicture}
+\end{figure}
 

### 2024-01-11 Paper/Paper_noProof.tex
fig1

@@
 
-\begin{figure}[t!]
+%\begin{figure}[t!]
+%	\centering
+%		\includegraphics[scale=0.4]{example.png}
+%	\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
+%	\label{fig1}
+%	\end{figure}
+
+	\begin{figure}
 		\centering
-		\includegraphics[scale=0.4]{example.png}
+		\begin{tikzpicture}
+
+			\node[circle, draw= purple, thick, minimum width = 20,
+			minimum height = 20] (input1) {$x_1$};
+
+			\node[circle, draw= purple, thick, minimum width = 20,
+			minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$x_2$};
+
+			% Hidden layers
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$x_3$};
+			\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$x_4$};
+
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$x_5$};
+			\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$x_6$};
+
+			\node[circle, draw= blue, thick, minimum width = 20,
+			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$x_7$};
+			\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_8$};
+
+			% Output layer
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (output1) at ($(input1) + (10,0)$){$x_9$};
+
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$x_{10}$};
+
+			% Connections
+
+			\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
+
+			\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
+
+			\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
+			\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$1$};
+
+			\draw[->,thick] (input2) -- (hidden1) node[near start, above] {$1$};
+			\draw[->,thick] (input2) -- (hidden2)node[near start, below] {$-1$};
+
+			\draw[->,thick] (hidden1) -- (hidden3) node[midway, above] {$\max(x_1,0)$};
+			\draw[->,thick] (hidden2) -- (hidden4) node[midway, above] {$\max(x_2,0)$};
+
+			\draw[->,thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
+			\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
+
+			\draw[->,thick] (hidden4) -- (hidden5)node[near start, above] {$2$};
+			\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
+
+			\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(x_7,0)$};
+			\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(x_8,0)$};
+
+		\end{tikzpicture}
 		\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}

### 2024-01-11 Paper/Paper_noProof.tex
fig1
example

--- 2024-01-11 Paper/Paper_noProof.tex
@@
 With that, we get 
-$x_7 \leq g_5(x_3) + 2 g_6(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{2x_1 - x_4 + 6}{2}\leq 4.5$.
+$x_7 \leq g_5(x_3) + 2 g_6(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5.5$.
 
@@
 As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.
+We prove now that the LP abstraction is strictly more accurate tha3 the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.
 
@@
 Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision.
+
+Formally, a pair $(\pi,\pi')$ of paths is compensating if:
+\begin{itemize}
+ \item they have the same starting node $a$ (called {\em source} state) and ending node $b$ (called {\em target} state of $(\pi,\pi')$),
+ \item they are disjoints,
+ \item the weight $weight(\pi') < 0 < weight(\pi)$.
+\end{itemize}
+
+For instance, on Fig.~\ref{fig1}, the paths $\pi= x_2 x_3 x_7$ has weight $1$, while the
+path $\pi'= x_2 x_4 x_7$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
+We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or 
+$(\pi',\pi)$ is compensating.
+
+Compensating pair of paths will make precision of the target state reduce when using overabstraction of values.
+Here, $weight(x_7) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
+However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (a contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of the exact $-x_2 \leq 1.5$), and obtain a bound of $weight(x_7) \leq 5.5$ instead of $4$.
+
+Intuitively, the target state receives the weight from the source state from the different paths from the source to the target.
+As the weight of the path is opposite, some of this weight will cancel out,
+by an amount up to $2 min(|weight(\pi')|,|weight(\pi')|)$.
+This amount can however be reduced by the ReLU functions, because of clipping by the ReLU function.
+Assume that the inputs $x_1,x_2$ lies in $[-1,-0]$.
+Then the weight at $\hat{x_3}$ will be always 0, no matter the input, and there will be no compensation to
+$weight(\pi')$.
 

### 2024-01-11 Paper/Paper_noProof.tex

@@
 
-\begin{figure}[t!]
+%\begin{figure}[t!]
+%	\centering
+%		\includegraphics[scale=0.4]{example.png}
+%	\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
+%	\label{fig1}
+%	\end{figure}
+
+	\begin{figure}
 		\centering
-		\includegraphics[scale=0.4]{example.png}
+		\begin{tikzpicture}
+
+			\node[circle, draw= purple, thick, minimum width = 20,
+			minimum height = 20] (input1) {$x_1$};
+
+			\node[circle, draw= purple, thick, minimum width = 20,
+			minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$x_2$};
+
+			% Hidden layers
+
+			\node (hidden10) at ($(input1) + (2.5,0.6)$) {$0$};
+
+			\node (hidden20) at ($(input1) + (2.5,-1.5-0.6)$) {$0$};
+
+			\node (hidden50) at ($(input1) + (7.5,0.6)$) {$0$};
+
+			\node (hidden60) at ($(input1) + (7.5,-1.5-0.6)$) {$1.5$};
+
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$x_3$};
+			\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$x_4$};
+
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$x_5$};
+			\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$x_6$};
+
+			\node[circle, draw= blue, thick, minimum width = 20,
+			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$x_7$};
+			\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_8$};
+
+			% Output layer
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (output1) at ($(input1) + (10,0)$){$x_9$};
+
+			\node[circle, draw= black, thick, minimum width = 20,
+			minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$x_{10}$};
+
+			% Connections
+
+			\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
+
+			\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
+
+			\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
+			\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$1$};
+
+			\draw[->,thick] (input2) -- (hidden1) node[near start, above] {$1$};
+			\draw[->,thick] (input2) -- (hidden2)node[near start, below] {$-1$};
+
+			\draw[->,thick] (hidden1) -- (hidden3) node[midway, above] {$\max(x_1,0)$};
+			\draw[->,thick] (hidden2) -- (hidden4) node[midway, above] {$\max(x_2,0)$};
+
+			\draw[->,thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
+			\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
+
+			\draw[->,thick] (hidden4) -- (hidden5)node[near start, above] {$2$};
+			\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
+
+			\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(x_7,0)$};
+			\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(x_8,0)$};
+
+		\end{tikzpicture}
 		\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}

### 2024-01-11 Paper/Paper_noProof.tex
section 4

@@
 \newcommand{\vb}{\boldsymbol{b}}
+\newcommand{\val}{{\textrm{value}}}
 
@@
 Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $weight_{\boldsymbol{x}}(a)$ the weight of neuron $a$ when the the input is $\boldsymbol{x}$.
+Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the weight of neuron $a$ when the the input is $\boldsymbol{x}$.
 A path $\pi$ will be a sequence
@@
 
-	\begin{figure}
+	\begin{figure}[t!]
 		\centering
@@
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$x_5$};
-			\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$x_6$};
+			minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{x}_3$};
+			\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{x}_4$};
 
 			\node[circle, draw= blue, thick, minimum width = 20,
-			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$x_7$};
-			\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_8$};
+			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$x_5$};
+			\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_6$};
 
@@
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (output1) at ($(input1) + (10,0)$){$x_9$};
+			minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{x}_5$};
 
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$x_{10}$};
+			minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{x}_{6}$};
 
@@
 
-			\draw[->,thick] (input2) -- (hidden1) node[near start, above] {$1$};
+			\draw[->,thick] (input2) -- (hidden1) node[near start, below] {$1$};
 			\draw[->,thick] (input2) -- (hidden2)node[near start, below] {$-1$};
@@
 
-			\draw[->,thick] (hidden4) -- (hidden5)node[near start, above] {$2$};
+			\draw[->,thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
 			\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
 
-			\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(x_7,0)$};
-			\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(x_8,0)$};
+			\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(x_5,0)$};
+			\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(x_6,0)$};
 
 		\end{tikzpicture}
-		\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
+		\caption{A DNN example from \cite{kneuron}, where every node is separated into 2, $x$ after the weighted sum and $\hat{x}$ after the ReLU activation function.}
 		\label{fig1}
@@
 Consider the simpler abstraction, called the {\em box abstraction} \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
-For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $X_5,x_6 \in [0,2]$, and $x_7 \in [0,6]$ while $x_8 \in [1.5,3.5]$.
-While the bounds of $x_1, \ldots, x_6$ are correct (for all $\alpha$
-in the range, there is an input $\vy$ such that $weight_{\vy}(x_i))=\alpha$, 
-it is no more the case from the next layer (starting in $x_7,x_8$) because of potential 
+For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $\hat{x}_3,\hat{x}_4 \in [0,2]$, and $x_5 \in [0,6]$ while $x_6 \in [1.5,3.5]$.
+While the bounds of $x_1, \ldots, x_6$ are exact (for all $\alpha$ 
+in the range, there is an input $\vy$ such that $\val_{\vy}(x_i)=\alpha$), 
+it is no more the case from the next layer (starting in $x_5,x_6$) because of potential 
 dependencies between earlier neurons: $x_3$ reaches weight $2$ only when $x_1=x_2=2$,
-in which case $x_4$ reaches weight $0$. Hence, it is impossible that $weight(x_7)$ reaches $6$, as it would require both $x_3$ and $x_4$ to have weight $2$.
+in which case $x_4$ reaches weight $0$. Hence, it is impossible that $weight(x_5)$ reaches $6$, as it would require both $x_3$ and $x_4$ to have weight $2$.
 
-A still extremely fast algorithm that aleviates some of this issue is known as {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
+A still extremely fast algorithm that corrects some of this issue is known as {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
 hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
-For instance, $f_i \leq weight(x_i) \leq g_i$ with $f_5(x_3)=f_6(x_4)=0$ and 
-$g_5(x_3) = \frac{x_3+2}{2}$,
-$g_6(x_4) = \frac{x_4+2}{2}$. 
+For instance, $f_i \leq weight(\hat{x}_i) \leq g_i$ with 
+$f_{3}(x_3)=f_4(x_4)=0$ and 
+$g_3(x_3) = \frac{x_3+2}{2}$,
+$g_4(x_4) = \frac{x_4+2}{2}$. 
 With that, we get 
-$x_7 \leq g_5(x_3) + 2 g_6(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5.5$.
+$x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5.5$.
 
-While there is an optimal linear function for the upper bound $g_i$ for ReLU nodes, there are two choices for the lower bound: $f_i(x_i) = 0$ or $x_i$.
-In the DeepPoly algorithm, the choice is made by considering the range of an unstable neuron $x_i=[\alpha,\beta]$ with $\alpha < 0 < \beta$.
-If $|\alpha|\geq |\beta|$ then $0$ is used, while if $|\beta|>|\alpha|$ then $x_i$ (the identity function) is used.
-Let us call
-$\overline{\mbox{DeepPoly}}$ the Deeppoly algorithm such that 
+While there is an optimal linear function for the upper bound $g_i$ for ReLU nodes, there are two choices for the lower bound: $f_i(x_i) = 0$ or $f_i(x_i)=x_i$.
+In the DeepPoly algorithm, the choice is made by considering the range of an unstable neuron 
+$x_i=[\alpha,\beta]$ with $\alpha < 0 < \beta$. 
+If $|\alpha|\geq |\beta|$ then $0$ is used, while if $|\beta|>|\alpha|$ then $x_i$ (the identity function) is used. Let us call $\overline{\mbox{DeepPoly}}$ the Deeppoly algorithm such that 
 $f_i(x_i) = 0$ is always used, and $f_i(x_i) = x_i$ is never used. 
@@
 
-\section{Compensating pair of paths}
+\section{Compensating pairs of paths}
 
@@
 
-Formally, a pair $(\pi,\pi')$ of paths is compensating if:
+Formally, a pair $(\pi,\pi')$ of paths is {\em compensating} if:
 \begin{itemize}
  \item they have the same starting node $a$ (called {\em source} state) and ending node $b$ (called {\em target} state of $(\pi,\pi')$),
- \item they are disjoints,
- \item the weight $weight(\pi') < 0 < weight(\pi)$.
+ \item they are disjoints (the only common nodes are the source and the target),
+ \item the weights satisfy $weight(\pi') < 0 < weight(\pi)$.
 \end{itemize}
 
-For instance, on Fig.~\ref{fig1}, the paths $\pi= x_2 x_3 x_7$ has weight $1$, while the
-path $\pi'= x_2 x_4 x_7$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
+For instance, on Fig.~\ref{fig1}, the paths $\pi= x_2 x_3 x_5$ has weight $1$, while the
+path $\pi'= x_2 x_4 x_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
 We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or 
@@
 Compensating pair of paths will make precision of the target state reduce when using overabstraction of values.
-Here, $weight(x_7) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (a contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of the exact $-x_2 \leq 1.5$), and obtain a bound of $weight(x_7) \leq 5.5$ instead of $4$.
+Here, $weight(x_5) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
+However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (a contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of the exact $-x_2 \leq 1.5$), and obtain a bound $weight(x_5) \leq 5.5$ instead of $4$.
 
 Intuitively, the target state receives the weight from the source state from the different paths from the source to the target.
-As the weight of the path is opposite, some of this weight will cancel out,
-by an amount up to $2 min(|weight(\pi')|,|weight(\pi')|)$.
-This amount can however be reduced by the ReLU functions, because of clipping by the ReLU function.
-Assume that the inputs $x_1,x_2$ lies in $[-1,-0]$.
-Then the weight at $\hat{x_3}$ will be always 0, no matter the input, and there will be no compensation to
-$weight(\pi')$.
+As the weights of the paths is of opposite sign, some of these weights will cancel out,
+by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$. Further, no only do they cancel $min(|weight(\pi')|,|weight(\pi')|)$ out, but they also do not accumulate, in the same way as 
+$0= |1+(-1)| \leq |1|+|-1|=2$ from an inacurate analysis.
+The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function.
+For instance, consider that the inputs $x_1,x_2$ lies in $[-1,-0]$.
+Then the weight at $\hat{x}_3$ will be always 0, no matter the input, and there will be no compensation to $weight(\pi')$.
 
-The basic mode of compensating pair is as follows:
-
+\iffalse
 \vspace*{2ex}
@@
 
-\begin{theorem}[No Diamond Theorem, part 1]
-	For a full-connected network with $\ReLU$ as the unique activation function, if there is no Diamond, then for any method/approximation that at least as accurate as Interval Arithmetic, it can get the exact upper and lower bounds of all output nodes and all hidden nodes.
+\fi
+
+Hence, compensation is {\em one} factor of inacurracy. We prove now that it is actually the {\em only} reason for inacurracy, in the following meaning.
+If there is no compensating path in the DNN, then any method/approximation at least as accurate as the {\em Box} abstraction, e.g.
+$\overline{\text{DeepPoly}}$ or {\em LP}, computes the exact upper and lower bounds for every node, that is:
+
+\begin{theorem}
+	Let $n$ be any node of a DNN with {\em no} compensating path.
+For $[\alpha,\beta]$ the bounds computed by the {\em Box} abstraction for $n$, we have that for all $\gamma \in [\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n)=\gamma$.
 \end{theorem}
 
-Of course, in practice, it is very unlike to have a network without any Diamond. Therefore, the second theorem is more important in practice.
+Notice that standard {\em DeepPoly} does not satisfies the following theorem (it does not necessarily refine {\em Box}), and therefore we are not sure PRIMA or $\beta$-CROWN who refine DeepPoly do, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
+Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results
 

### 2024-01-11 Paper/Paper_noProof.tex
section 4

@@
 
-\iffalse
-Our strategy is to restrict the number of binary variables, and this will definitely lose accuracy of results.
-The key problem is how to use fewer binary variables to get more accuracy.
-That is, to choose which node to be binary, and which not.
-
-\begin{definition}
-	1. For a full-connected DNN with $\ReLU$ activation, to compute the upper or lower bound of a node (in a hidden layer or output layer), its MILP model is formulated as follows:
-
-	(1) For every node in the input layer $a$, set a $z_a$ variable with the same input interval: $l_a\leq z_a\leq u_a$
-
-	(2) For each hidden layer $l^i$, set two variables , $z_c,\hat{z}_c$ for each node $c$ in this layer for pre-activation and post-activation.
-
-	The constraints for pre-activation $z_a$ is the natural linear equation by the network. 	$$z_c=\sum_{d\in l^{i-1}} W^i_{cd} z_d+b^i_c.$$
-
-	The constraints for $\hat{z}_a$ is defined by the standard MILP formulation mentioned above with known upper bound and lower bound as parameters.
-
-	\vspace*{1ex}
-
-	Since we only consider such MILP models, so when we say an MILP model, it is for a full-connected DNN with $\ReLU$ activation.
-
-	2. In an MILP model, we say a $\ReLU$ node is open, if the binary variable corresponds to this function is still an binary variable; otherwise, it is relaxed as a continue variable. 
-\end{definition}
-
-We aim is to find an algorithm, to decide which nodes should be opened such that we can have more accuracy.
-\fi
-
 \section{Compensating pairs of paths}
@@
 
+\begin{table}[b!]
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+	\hline
+		\text{Source/Target Layers}  &  \text{Natural DNN} & \text{Robust DNN} & \text{Ratio Natural vs Robust} \\ \hline \hline
+	0 / 2 & 0.0304 & 0.00220  & 13.8x\\ \hline
+	1 / 3  & 0.0313 & 0.00875 & 3.58x \\ \hline
+	2 / 4  &  0.0267 & 0.00785 & 3.40x \\ \hline
+	3 / 5  &  0.0253 & 0.00804  & 3.18x \\ \hline
+\end{tabular}
+\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a Network Naturally trained and a Network Robustly trained with the same architecture and the same training set.}
+\label{tab:compensation}
+\end{table}
+
 \begin{theorem}
+	\label{th1}
 	Let $n$ be any node of a DNN with {\em no} compensating path.
@@
 
+The proof can be found in Section \ref{sec.proofs}.
 Notice that standard {\em DeepPoly} does not satisfies the following theorem (it does not necessarily refine {\em Box}), and therefore we are not sure PRIMA or $\beta$-CROWN who refine DeepPoly do, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
-Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results
+Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results showin that compensation is the reason for inacuracy.
 
-\begin{theorem}[No Diamond Theorem, part 2]
-	For a full-connected network with $\ReLU$ as the unique activation function. If we open all nodes that occurs in a compensating pair path, then the we can get the exactly bounds.
+This result has a first interesting application: explain why some DNNs are intrinsically easier to verify than others.
+This is the case for DNNs trained adversarially to be robust, vs same architecture, but trained in a "natural" way \cite{deeppoly,prima,crown}.
+Indeed, compensating pairs is a purely structural property on the DNN learnt, rather than more semantical notions, such as the number of unstable ReLUs, which depends heavily upon the image considered and the algorithm used.
+We compare compensations with source and target separated by 1 ReLU layer, e.g.
+source in layer 0 and target in layer 2, for two Networks with 5 hidden layers of 100 nodes each from the ERAN GitHub repository, one trained naturally ("$6\times100$"),
+and one trained using DiffAI ("$5\times100$"). 
+We report in Table \ref{tab:compensation} the average compensation strength, i.e. 
+the average of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$
+over all source/target states in given layers.
+The average compensations strenght are much lower in the Robust DNN than in the Natural DNN, and indeed the Robust DNN is much simpler to verify than the Natural DNN.
+
+\subsection{MILP$_{X_n}$}
+
+While Theorem \ref{th1} is interesting to understand that compensation is a key notion for accurate verification of DNNs, it is of little use to analyze DNNs with compensations, which are actually those that are most interesting to tackle, as current efficient algorithms are not accurate enough.
+Intuitively, when there are compensating paths, it seems necessary to consider exactly the (unstable) ReLU nodes that are seen along these paths. 
+Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds $[\alpha,\beta]$.
+Let $X_n$ be the set of neurons $x$ in layer up to $k-1$ such that there is a compensating path with target $n$ passing by $x$ (but not as its source or target).
+Let $Y_n$ be the complement of this set $X_n$ of neurons in the first $k-1$ layers.
+A quite efficient way to consider exactly this set $X$ of neurons is to use MILP$_{X_n}$, the relaxation of the MILP encoding where all the nodes in $Y_n$ are linearly relaxed (thus with $|X_n|$ binary variable, one per neuron in $X_n$), and including exact bounds for every neurons $n'$ in the first $k-1$ layers.
+We state now that the bounds $[\alpha,\beta]$ on neuron $n$ computed by such MILP$_{X_n}$ are accurate.
+
+\begin{theorem}
+	\label{th2} 
+	Let $n$ be any node of a DNN.
+Then for $[\alpha,\beta]$ the bounds computed by MILP$_{X_n}$ for neuron $n$, for all $\gamma \in [\alpha,\beta]$, there exists an input $\vy$ such that $\val_{\vy}(n)=\gamma$.
 \end{theorem}
 
-The proofs of above theorems are in the Appendix.
+Similarly, the proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs}.
 
-\subsection{Paths and Open Nodes Chosen}
+\subsection{Sketch of Proofs}
+\label{sec.proofs}
+
+Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes, and one can maximize/minimize independently the different input nodes in order to optimize any desired node.
+
+\subsection{An efficient algorithm}
+
+Using Theorem \ref{th2}, one could thus obtain accurate bounds by running MILP$_{X}$ inductively on every node layer by layer, obtaining accurate bounds $[\alpha,\beta]$ that can be used to compute the next layer accurate bound.
+In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$.
+Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strenght of compensation that are meaningful, and consider that paths below this treshold are not compensating strongly enough to deserve an integer variable (there are cases where the MILP algorithm is exponential in the number of integer variables), calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
+In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small.
+The pseudo-code of the algorithm is provided in Algorithm \ref{algo1}.
+
+This algorithm has a worst case complexity bounded by $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
+This complexity is an upper bound, as e.g.
+Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
+
+\section{Paths and Open Nodes Chosen}
 

### 2024-01-11 Paper/introduction.tex
section 4

@@
 %and associating these nodes with a binary variable. Then an MILP tool such as Gurobi is used %to compute the lower and upper bound for node $b$. 
-Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^k LP(N))$, where $N$ is the number of nodes of the DNN, $k$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
+Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
 This complexity is an upper bound, as e.g.
-Gurobi is fairly efficient and never need to consider all of the $2^k$ ReLU configurations to compute the bounds.
-Keeping $k$ reasonably low thus provides an efficient algorithm.
+Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
+Keeping $K$ reasonably low thus provides an efficient algorithm.
 By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.

### 2024-01-12 Paper/Paper_noProof.tex
Add code

@@
 
+\begin{algorithm}
+	\caption{The Frame work}
+	\KwData{Input Domain: $\mathcal{D}$}
+	\KwResult{Bounds of all nodes: $\mathcal{B}$}
+
+	Constant $\mathcal{R}$  \tcp*{Stored precomputation data}
+
+	Constant $\boldsymbol{W}, \boldsymbol{b}$ \tcp*{Weights and Bias of network}
+
+	Constant Layers = $[0,1,2\cdots,L]$ \tcp*{lists of all layer}
+
+	Constant NodesLayer = $[Nodes_0,Nodes_1,\cdots, Nodes_L]$ \tcp*{list of nodes in each layer}
+
+	Initialize $\mathcal{B}$ = \{\} \tcp*{To store upper and lower bounds of all nodes}
+
+	\For{$l$ in Layers}{
+		\If{$l$ = 0}{
+
+			$\mathcal{D}$, $\boldsymbol{W}, \boldsymbol{b}$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
+			\tcp*{Do linear transformation  from input to the first layer}
+
+			Add \{$x$: $(UB(x),LB(x))$,$\cdots$\} to $\mathcal{B}$}
+
+		\Else{
+
+			$l$, NodesLayer $\rightarrow$ $Nodes_l$ = $[x_0,x_1,\cdots]$
+
+			\For{$x$ in $Nodes_l$}{
+				$x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}
+
+				$\mathcal{B}$, $\boldsymbol{W}, \boldsymbol{b}$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
+
+				\While{}{$\mathcal{M}$ $\rightarrow UB(x),LB(x)$ \tcp*{Optimization}}
+
+				Add \{$x$: $(UB(x),LB(x))$\} to $\mathcal{B}$
+
+			}
+
+		}
+
+	}
+
+	\Return{$\mathcal{B}$}
+
+\end{algorithm}
+
 \subsubsection*{Process for one node}

### 2024-01-12 Paper/Paper_noProof.tex
ALGO

@@
 
+\SetKwInput{KwInput}{Input}
+\SetKwInput{KwOutput}{Output}
+
+\begin{algorithm}[t!]
+	\caption{}
+	\label{algo1}
+	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$}
+
+	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}
+
+	 Run DeepPoly to obtain preliminary lower and upper bounds for all nodes.
+
+	 Precompute $\mathcal{R}$ to know the compensation strenght
+
+	 \For{layer $k=1 \cdots \ell$}{
+
+	 \If{$k$ = 0}{
+
+	 $\mathcal{D}$, $\boldsymbol{W}, \boldsymbol{b}$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\}
+
+	 \tcp*{Do linear transformation  from input to the first layer}
+
+	 Add \{$x$: $(UB(x),LB(x))$,$\cdots$\} to $\mathcal{B}$}
+
+	 \Else{
+
+	  $l$, NodesLayer $\rightarrow$ $Nodes_l$ = $[x_0,x_1,\cdots]$
+
+	 \For{$x$ in $Nodes_l$}{
+
+	 $x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}
+
+	 $\mathcal{B}$, $\boldsymbol{W}, \boldsymbol{b}$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
+
+	\While{}{$\mathcal{M}$ $\rightarrow UB(x),LB(x)$ \tcp*{Optimization}}
+
+	Add \{$x$: $(UB(x),LB(x))$\} to $\mathcal{B}$
+
+}
+}	
+}	
+	\Return{$\mathcal{B}$}	
+	\end{algorithm}
+
 This algorithm has a worst case complexity bounded by $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.

### 2024-01-14 Paper/Paper_noProof.tex
first version

--- 2024-01-12 Paper/Paper_noProof.tex
@@
 \newcommand{\val}{{\textrm{value}}}
+\newcommand{\MILP}{{\textrm{MILP}}}
+\newcommand{\LP}{{\textrm{LP}}}
 
@@
   In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs.
-While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.
+While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern verifiers, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.
 
@@
 
-			\node[circle, draw= purple, thick, minimum width = 20,
+			\node[circle, draw= black, thick, minimum width = 20,
 			minimum height = 20] (input1) {$x_1$};
@@
 			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$x_5$};
-			\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_6$};
+			\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_6$};
 
@@
 
-			\draw[->,thick] (input2) -- (hidden1) node[near start, below] {$1$};
-			\draw[->,thick] (input2) -- (hidden2)node[near start, below] {$-1$};
+			\draw[->,color=green, thick] (input2) -- (hidden1) node[near start, below] {$1$};
+			\draw[->,color=red, thick] (input2) -- (hidden2)node[near start, below] {$-1$};
 
-			\draw[->,thick] (hidden1) -- (hidden3) node[midway, above] {$\max(x_1,0)$};
-			\draw[->,thick] (hidden2) -- (hidden4) node[midway, above] {$\max(x_2,0)$};
+			\draw[->,color=green, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(x_1,0)$};
+			\draw[->,color=red, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(x_2,0)$};
 
-			\draw[->,thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
+			\draw[->,color=green, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
 			\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
 
-			\draw[->,thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
+			\draw[->,color=red, thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
 			\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
@@
 
-While there is an optimal linear function for the upper bound $g_i$ for ReLU nodes, there are two choices for the lower bound: $f_i(x_i) = 0$ or $f_i(x_i)=x_i$.
+While there is one optimal linear function for the upper bound $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes, there are two choices for the lower bound: $f_i(x_i) = 0$ or $f_i(x_i)=x_i$.
 In the DeepPoly algorithm, the choice is made by considering the range of an unstable neuron 
@@
 \section{Compensating pairs of paths}
+\label{Sec.comp}
 
@@
 
+\input{proofs}
+
 \subsection{An efficient algorithm}
@@
 
-This algorithm has a worst case complexity bounded by $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
-This complexity is an upper bound, as e.g.
-Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
+\SetKwInput{KwInput}{Input}
+\SetKwInput{KwOutput}{Output}
 
-\section{Paths and Open Nodes Chosen}
+\begin{algorithm}[t!]
+	\caption{Compensate(K)}
+	\label{algo1}
+	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}
+
+	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}
+
+	 \For{layer $k=1 \cdots \ell$}{
+		\For{neuron $n$ in layer $k$}{
+
+	 		Compute $Z$ a set of $K$ nodes covering the compensating pairs of paths with target $n$
+			with heaviest compensation
+
+			Run MILP$_Z$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
+	 }
+	 }
+	 \end{algorithm}
+
+This algorithm has a worst case complexity bounded by $O(N \MILP(N,K))$, 
+where $N$ is the number of nodes of the DNN, 
+and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
+We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables.
+This complexity is an upper bound, as e.g. Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
+Notice that the for loop on neurons $n$ in layer $k$ at line 2 can be realized in parallel as we only need bounds from previous layers, not from the current layer $k$, 
+leading to a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, with $\ell$ the number of layers and $N_i$ the number of neurons in layers $0, \ldots, i$.
+Hence, for $K$ small enough, Algorithm \ref{algo1} calls many times MILP (e.g. Gurobi)
+with a limited number of integer variables, which should be efficient enough, and yet be quite accurate as it can compute exactly (Theorem \ref{th2}) the highest compensating path, which we will verify in the experimental section.
+
+\iffalse
+\section{Verification Framework}
+
+%Our experiments are carried by different version codes, and the global process has been changed.
+
+In this section, we will sketch the framework.
+
+\subsection{Structure}
+
+\subsubsection*{Precomputation}
+
+The open node chosen is the key part of the whole framework but costs a lot of time. So some computation (those do not rely on certain image and bounds) is moved to the precomputation part.
+
+%The precomputation corresponds to the simplest case: source node fixed.
+We will compute and store a limited number of paths with highest (absolute) values before running any image.
+This does not rely on other parameters or results(bounds).
+%
+%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
+This will use much less time.
+
+\subsubsection*{Process for one image} An image is the basic unit in whole process.
+The process of one image is simple: compute the concrete bounds of nodes layer by layer, use the bounds of previous layer to build MILP models of current layer.
+In one layer, nodes runs in parallel.
+
+%Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers.
+Then we will compute bounds of every node in $l_i$ in parallel using the data of bounds of previous nodes.
+The method is to build and optimize an MILP model.
+
+%Some parameters may be changed during layers.
+Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
+Here, \emph{local} is opposite to \emph{global}.
+We have global timeout parameters for images and the whole running.
+Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
+
+%The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node. 
+%
+%The precomputation corresponds to the simplest case: source node fixed.
+We will compute and store a limited number of paths with highest (absolute) values before running any image.
+This does not rely on other parameters or results(bounds).
+%
+%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
+This will use much less time.
+
+\begin{algorithm}
+	\caption{The Frame work}
+	\KwData{Input Domain: $\mathcal{D}$}
+	\KwResult{Bounds of all nodes: $\mathcal{B}$}
+
+	Constant $\mathcal{R}$  \tcp*{Stored precomputation data}
+
+	Constant $\boldsymbol{W}, \boldsymbol{b}$ \tcp*{Weights and Bias of network}
+
+	Constant Layers = $[0,1,2\cdots,L]$ \tcp*{lists of all layer}
+
+	Constant NodesLayer = $[Nodes_0,Nodes_1,\cdots, Nodes_L]$ \tcp*{list of nodes in each layer}
+
+	Initialize $\mathcal{B}$ = \{\} \tcp*{To store upper and lower bounds of all nodes}
+
+	\For{$l$ in Layers}{
+		\If{$l$ = 0}{
+
+			$\mathcal{D}$, $\boldsymbol{W}, \boldsymbol{b}$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
+			\tcp*{Do linear transformation  from input to the first layer}
+
+			Add \{$x$: $(UB(x),LB(x))$,$\cdots$\} to $\mathcal{B}$}
+
+		\Else{
+
+			$l$, NodesLayer $\rightarrow$ $Nodes_l$ = $[x_0,x_1,\cdots]$
+
+			\For{$x$ in $Nodes_l$}{
+				$x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}
+
+				$\mathcal{B}$, $\boldsymbol{W}, \boldsymbol{b}$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
+
+				\While{}{$\mathcal{M}$ $\rightarrow UB(x),LB(x)$ \tcp*{Optimization}}
+
+				Add \{$x$: $(UB(x),LB(x))$\} to $\mathcal{B}$
+
+			}
+
+		}
+
+	}
+
+	\Return{$\mathcal{B}$}
+
+\end{algorithm}
+
+\subsubsection*{Process for one node}
+
+ The optimization of a model consists of loops.
+For each loop, the model will do optimization by a timeout and observe the result.
+If it gets improvement, then continue the loop until the optimize bounds or the longer timeout.
+Otherwise it will give up optimization and store the best bounds obtained so far.
+
+\subsubsection*{Global Process}
+
+In the newest version, we do images by batches for 100 images each. For each batch, the running consists of three turns, very fast turn, fast turn and slow turn.
+
+In the very fast turn, it will run DeepPoly for all images to get a preliminary bounds for all nodes and verify the easiest images.
+Images verified and images with false predication will be deleted from the image list.
+
+Then sort all remain images by the size of uncertainty of DeepPoly from smaller to larger.
+The fast turn is to run the images from the smaller side to larger side until consecutive two images cannot be verified.
+All remain images and images tried but not verified will be put into the next list.
+And then run the list with parameters for slow turn.
+
+\subsection{Parameters}
+
+Parameters like open node parameter $O$ is important in the frame. Basically, all parameters will be reset after one image.
+
+\subsubsection*{Global parameters}
+
+\subsubsection*{Local parameters}
+
+$O$ and timeout parameters for loops will change frequently during the loops of one node. These change will not reset until the end of one layer or one image.
+
+\subsection{Other Setting}
+
+In our experiments, we have not used PGD-attack to exclude some images. In principle, there is no obstacle to use PGD-attack.
+\fi
+
+\section{Experimental Evaluation}
+
+Our experimental evaluations have 3 goals:
+\begin{enumerate}
+  \item Evaluate experimentally how accurate is $\MILP_Z$ when using compensating strenght 
+ to choose the set $Z$ of ReLU nodes encoded exactly using an integer variable, compared with randomly chosing the set $Z$, to make sure the choice is relevant.
+Also compare different choices for $K$ the size of $Z$ and how to rank nodes from different layers,
+  \item Evaluate on benchmarks the percentage of certification that can be obtained
+ using the compensation idea, and compare with competing efficient tools,
+  \item Evaluate the runtime of compensate($K$).
+\end{enumerate}
+
+\subsection{Setting}
+All the benchmarks were run on an AMD 5975WX ($32$ cores$@3.6$GHz, 7nm, year 2022) with 256 GB of main memory and 2 NVIDIA RTX 3090 (year 2022).
+Gurobi 9.52 was used for solving MILP and LP problems.
+Our implementations for Compensate($K$) is entirely realized in Python $X.Y$, and therefore not particularly optimal.
+
+The DNN certification for local robustness were run, using DNNs trained for the MNIST image dataset as its the only standard DNNs (MLP $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers).
+Indeed, today's efficient methods leave at least $14\%$ to $20\%$ of the images neither certified robust nor with an attack to robustness found, making them interesting DNNs to consider where to improve accuracy of efficient techniques.
+We also test on the larger MLP $6\times 500$, not previously tested in \cite{crown}.
+MNIST contains grayscale images of size $28 \times 28$ pixels ($752$ input neurons).
+For our evaluation, we evaluate on the standard first 1000 images of the dataset, to be directly comparable to experiments run in other papers, e.g.
+\cite{prima,crown}, except for MLP $5\times 500$ which is not reported in \cite{prima,crown} and takes a large amount of time, for which we only test on the first 200 images.
+Each data example is associated with a $\varepsilon>0$ for the $L^\infty$ norm, and a target label for verification.
+
+\subsection{Chosing nodes based on Compensation strenght}
+
+The first group of experiments we run, tests the accuracy of chosing a set $Z$ of $K$ nodes using compensation strenght, compared with randomly chosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+
+To mesure the accuracy, we measure the uncertainty of all nodes in a layer:
+the uncertainty of a node is the range between its computed lower and upper bound. 
+We then average the uncerainty among all the nodes of the layer.
+Formally, for a node $n$ with bounds $[\alpha,\beta]$, its uncertainty $unc(a) = \beta - \alpha$, and the average uncertainty of a layer $l$ is $\dfrac{\sum_{a\in l} unc(a)}{|l|}.$
+
+We experiment with the smallest network (MLP $6\times 100$), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
+We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first layer and $94(?)$ in the second layer), so we can experiment with a larger choice of values for $K$.
+
+\subsubsection*{ReLU Node in the first hidden layer}
+
+We first experiment with the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer.  Let $c$ be a node of the second layer.
+A compensating pair $(\pi,\pi')$ of paths with target $n$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
+The compensating strenght for $(b,b')$ is defined as
+$comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$. Indeed, 
+the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),weight(a,b',c))$, and $b,b'$ would help compensated set set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
+After selecting the heaviest $(b_0,b_0')$, we can then compute $comp(b)= \sum_{b' \text{already selected}} comp(b,b')+comp(b',b)$ and select iteratively the heaviest $b$'s one by one till reaching the threshold.
+We do this for all node $c$ of the second layer.
+
+We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
+The range of uncertainty created by inacurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
+Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
+We can deduce that selecting nodes based on compensating strenght helps to select important ReLU nodes for the accuracy.
+
+\begin{table}[t!]
+	\centering
+	\begin{tabular}{|c||c|c|}
+	\hline
+	\text{Number $K$ of nodes in $Z$}  &  \text{Compensate strength} & \text{Random Choice}  \\ \hline
+	\hline
+	0  &  2.22 & 2.22  \\ \hline
+	10  &  1.84 & 2.03  \\ \hline
+	20  &  1.50 & 1.82  \\ \hline
+	30  &  1.28 & 1.62  \\ \hline
+	40  &  1.14 & 1.44  \\ \hline
+	50  &  1.06 & 1.23  \\ \hline
+	61 (max) & 1.05 &  1.05 \\ \hline
+\end{tabular}
+\caption{Average uncertainty of $\MILP_Z$ for nodes of the second layer, for a set $Z$ of $K$ ReLU nodes of the first layer with the heaviest compensation, vs $K$ random nodes of the first layer.}
+\label{tab:example0}
+\end{table}
+
+\subsubsection*{ReLU Node in the first and second hidden layer}
+
+We now turn to evaluating chosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the second layers, wrt ReLU nodes in the first and second layer.
+The bounds for nodes of the second layers are computed exactly. 
+Let $d$ be a neuron of the third layer.
+We keep the previous evaluation for ranking nodes in the previous (second) layer. 
+Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$.
+We thus define
+$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min(weight(abcd),weight(ab'c'd))$ and the associated $comp(b)$, and select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
+
+We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly from layers $1$ and $2$.
+We compare choosing nodes in the second layer only with choosing nodes in both the first and second layer.
+Choosing ReLU nodes in the previous layer (layer 2) only is never a good choice. 
+When picking in both layer 1 and 2, choosing 50 out of 149(?) unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inacurate computations ($0.059$ vs $0.574$), while it only reduces the inacuracy by $65\%$ when choosing nodes randomly.
+Notice that this is direct inacuracy, applying this layer over layer will even further reduce inacuracy created by accumulation of inacuraccies.
+
+Notice that It is likely that selecting ReLU nodes up to 3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade off is unclear and we thus didnot experiment.
+
+\begin{table}[t!]	
+	\centering
+	\begin{tabular}{|c||c|c|c|}
+	\hline
+	\text{Number $K$}  &  \text{Compensate layer} 1+2 &  \text{Compensate layer} 2 & \text{Random layer } 1+2 \\ \hline
+	\hline
+	0  &  1.758 & 1.758 & 1.758  \\ \hline
+	10  &  1.677 & 1.677 & 1.695  \\ \hline
+	20  &  1.539 & 1.567 & 1.622  \\ \hline
+	30  &  1.431 & 1.489 & 1.542  \\ \hline
+	40  &  1.329 & 1.454 & 1.47  \\ \hline
+	50  &  1.243 & 1.432 & 1.39  \\ \hline
+	max  &  1.184 & 1.422 & 1.184  \\ \hline
+\end{tabular}
+\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for a set $Z$ of $K$ ReLU nodes of the (first and) second layer with the heaviest compensation, vs $K$ random nodes of the first and second layer.}
+\label{tab:example1}
+\end{table}
+
+\subsection{Comparison to efficient Verifiers}
+
+In terms of efficient verifiers we compare with, we report:
+\begin{itemize}
+	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}.
+We report the runtime from our own implementation used in Compensate($K$).
+It shows that our purely Python implementation is not optimal ($10$-$100$ times slower than the implementation in $\alpha$-$\beta$-CROWN, ERAN and PRIMA).
+Our aim is indeed not to have the most optimized tool, but to evaluate the idea around compensation.
+	\item PRIMA, the 2022 version, with results reported in \cite{prima} and \cite{crown}, as it is the closest in practice with our algorithm, computing accurate bounds for all neurons (as we do), although with a different technique: they focus on explicit correlations between neurons, while we consider the correlations indirectly through a better network abstraction.
+They use GPU while we do not.
+When computing the whole correlated space,
+	parallelization is difficult.
+	Notice that on these MLP networks, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
+This is doable on the first few layers as the number of integer variable is limited (but stil consequent).
+By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
+	\item $\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date.
+Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming \cite{BaB} on such DNNs, and heavily using GPU implementation (while we do not).
+Performance of pure BaB on these hard DNNs is however impaired by the large number of branchs to consider.
+Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also parallelized with 16 nodes in parallel, before running their BaB tool.
+We also test with the latest version of $\alpha$-$\beta$-CROWN ($X.Y$)
+	and of Prima ($X.Y$) on the MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
+
+	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
+	SDPFO \cite{SDPFI} which do not present favorable trade offs compared with $\beta$-CROWN. Results can be found in \cite{crown} and are performed in the same conditions so can be compared.
+	\item Finally, we run several version of Compensate($K$).
+First, we have a fixed choice for $K$ ($K=60$ for fast and $K=200$ for slow), with a fall back to a lower $K$ ($K=50$ for fast and $K=60$ for slow) if the bounds found is too far from the solution found (MIPGap $>0.5$ in Gurobi).
+We run (our implementation of) DeepPoly first, then the fast version (fast), before running slow on the remaining Images (fast+slow).
+	Further, we also experiment with an {\em adaptative} implementation, which lowers number $K$ adaptively between layers to adapt to the growing number $N$ of linear variables, which has an impact on the overall $\MILP(N,K)$ runtime.
+This is particularly useful for deeper network where $N$ is very different between the first and the last layer.
+Again, we run first an aggressive version of fast, before going to a more concervative slow version to treat the remaining images.
+All versions compute bounds for 20 neurons of the same layer in parallel, no GPU used.
+\end{itemize}
+
+In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
+DeepPoly/CROWN is by far the fastest, but also the most inacurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found.
+This is because these DNNs, altough of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strenght, see Section \ref{Sec.comp}).
+
+Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall method is quite similar, looking at all the nodes one by one from the begining of the network till the end.
+Our method compare favorably, both in terms of time and accuracy: our fastest setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except our fast adaptative method for $5 \times 200$ which is quite pointless on this shallow DNN - the fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
+Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
+This is very promising for this idea of compensation, which indirectly treats dependencies between the variables, which PRIMA represents explicitly.
+
+\begin{table}[t!]
+	\centering
+	\begin{tabular}{|c||c|c|c||cc|cc||c|}
+
+		\hline
+		\text{DNN}  & DeepPoly & PRIMA & $\beta$-CROWN &\multicolumn{2}{@{}c@{}|}{\text{ Comp (adapt.) }} & \multicolumn{2}{@{}c@{}|}{\text{ Comp (fixed) }} & Upper\\ 
+		 & / CROWN & (refined) & (refined BaB) & fast & slow & fast &slow & Bound\\
+		\hline \hline
+
+		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & no & point & $65.3\%$ & $68.4\%$ &  $84.2 \%$ \\ 
+		$\epsilon = 0.026$ & 5s & 159s & 102s& & & 117s & 142s &  \\
+		\hline
+
+		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & $64.3\%$ & $74.7\%$ & $72\%$ & $76.8\%$ & 
+		$90.1 \%$\\ 
+		$\epsilon = 0.015$ & 11s & 224s & 86s & 163s & 285s & 206s & 279s  &\\ \hline \hline
+
+		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & $52.7\%$ & $59.7\%$ & $61.4\%$ & $\mathbf{65.8\%}$  & $82.0 \%$ \\ 
+		$\epsilon = 0.026$ & 8s & 301s & 103s & 92.3s & 179s & 170s & 346s & \\
+		\hline
+
+		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & $68.1\%$ & $\mathbf{79.1\%}$ & $72.6\%$ & too & $91.1 \%$ \\ 
+		$\epsilon = 0.015$ & 17s & 395s & 95s  & 297s & 535s & $480s$ & slow & \\ \hline
+
+		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
+		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
+	\end{tabular}
+	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
+	Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.}
+	\label{tab:example}
+	\vspace{-1cm}
+\end{table}
+
+Compare with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), 
+the picture is more balanced, because the fundamentals of both algorithms are different. BaB 
+focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary. 
+Instead, we consider every node one by one from the input layer till the final layer, with the same accuracy.
+Hence our algorithm will spend a lot of time on nodes which are not necessary for the verification.
+Therefore, our naive implementation is not as efficient as the highly optimized
+$\beta$-CROWN: our implementation is 2 to 5 times slower than $\beta$-CROWN, while we are not using GPU, unlike $\beta$-CROWN.
+Things are more interesting on the accuracy front: on shallower DNNs ($5 \times 100$ and $5 \times 100$ with 5 hidden layers), the refinement with MILP treats all but the 2 last layers,
+leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accuate than using compensation: we are within $1.5\%$ of the accuracy.
+On deeper DNNs ($8 \times 100$ and $8 \times 100$ with 8 hidden layers), the refinement with MILP cannot treat the 4 last layers, and BaB has more ReLU to branch on.
+Therefore, Compensate($K$) is more accurate than $\beta$-CROWN,
+closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
+and from $17.6\%$ to $12\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than Compensate($K$) (see next Section).
+
+More importantly, $\beta$-Crown, while efficient, often faces a (complexity) wall, when there number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long time out (the reason why Refined BaB is more accurate on these networks).
+We verify that on a larger DNN learnt in a natural way, namely MLP $6 \times 500$, see Table \ref{tab:example3}.
+We tested PureBaB with two time out, from the standard 30s to an extreme 2000s, to match the average run time of our adaptative implementation (fast mode).
+Only $2\%$ more of images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
+Notice that the refined BaB mode of $\beta$-Crown (using MILP for the first few layers) failed to run on this DNN (NoImplementation error code), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as
+confirmed while running PRIMA.
+
+% test
+
+\begin{table}[t!]
+	\centering
+	\begin{tabular}{|c||c|c|cc||c||c|}
+
+		\hline
+		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\beta$-CROWN (pureBaB)}} & 
+		Comp(adapt.) & Upper\\ 
+		 & / CROWN & (refined) & TO=30s & TO=1200s & fast & Bound\\
+		\hline \hline
+
+		$6\times500$\  &   $26\%$ & &  &  $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
+
+		$\epsilon = 0.035$ & 34s & &  & 576s & 925s &\\ \hline
+	\end{tabular}
+	\caption{$\%$ of verified images and average runtime in seconds, over 200 images.}
+	\label{tab:example3}
+	\vspace{-0.8cm}
+\end{table}
+
+Last, we report the average runetime per number of nodes of both fast adaptive and of fast fixed compensation, for the different DNNs we considered.
+The time per node is not constant, but it is still controlled and does not show an exponential behavior (from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN).
+This indicates that Compensate($K$) can be run for larger DNN.
+While the time to verify images will be longer, it won't hit a wall as BaB does on DNNs hard to verify.
+
+\begin{figure}[b!]
+\centering
+\includegraphics[scale=0.8]{Graph.png}
+\end{figure}
+
+\section{Limitations and Discussion}
+
+For DNNs easy to verify, $\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images.
+Compensation strenght is not required in these contexts, and likely not useful, reason why we did not considered it.
+
+We only considered DNNs with ReLU activation functions in this paper.
+The reason is that MILP, which is the basic block of Compensate($K$), and BaB (the basic block of $\beta$-Crown) can handle the ReLU activation function efficiently, and more complex activation functions are abstracted in other ways, which PRIMA handles (unlike $\beta$-CROWN).
+Still, the compensation paradigm is totally orthogonal to ReLU activation function.
+It is very likely that studying the compensation strengh would be useful in this other context.
+We leave that for future work.
+
+While accuracy of compensate($K$) can be among the highest of the efficient verifiers, runtime, while never blowing-up, can be on the slow side, in particular for larger DNNs.
+There are many optimizations possible.
+The simplest is to run $\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\beta$-CROWN cannot conclude.
+Another simple way is to modify the refined BaB of
+$\beta$-CROWN to run compensate($K$) on more layers than what exact MILP can be run, and finish the study using BaB.
+More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strenght, which we experimentally proved to be an efficient trade-off.
+Last, an analysis of important nodes for the uncertain output nodes could be performed, allowing to compute much faster less accurate bounds for those nodes not important.
+
+On the correlation between neurons, which PRIMA encodes explicitely, our results tend to show that it is more efficient to use the compensation strenght.
+Still, considering ReLU nodes exactly tends to be very accurate locally, but less when the source of correlation is many layers away.
+Few important correlations a la PRIMA could be kept explicitly as linear constraints into the MILP encoding, helping to reduce the imprecision further.
+
+\section{Conclusion}
+
+In this paper, we presented the notion of compensating pairs of paths, with rationale why such a phenomenon creates inacuracies hard to handle when verifying DNNs.
+We proved that this phenomenon is actually explaining entierely the inacuracies, as in their absence, even very simple arithmetic algebra suffices to verify accurately DNNs.
+We verified that DNNs harder to verify indeed exhibits more paths with larger compensating strenght.
+
+Based on this idea of compensating path, we proposed a novel efficient algorithm considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if all the compensating paths are covered.
+We experimentally tested that chosing $Z$ covering the paths with the strongest compensation result to very good accuracy, and runtime which can be favorable in some (but not all) cases.
+This proves that compensating strength is a promising novel concept which should be further studied to 
+improve DNN verification. We finally proposed several ways to use the compensating strenght to optimize the tools even more than they are, and leave that as future work.
+
+\newpage
+
+\bibliographystyle{plain}
+\bibliography{references}
+
+\newpage
+
+\appendix
+
+\section{Ranking of Compensating Pairs}
 
@@
 
-\section{Verification Framework}
-
-%Our experiments are carried by different version codes, and the global process has been changed.
-
-In this section, we will sketch the framework.
-
-\subsection{Structure}
-
-\subsubsection*{Precomputation}
-
-The open node chosen is the key part of the whole framework but costs a lot of time. So some computation (those do not rely on certain image and bounds) is moved to the precomputation part.
-
-%The precomputation corresponds to the simplest case: source node fixed.
-We will compute and store a limited number of paths with highest (absolute) values before running any image.
-This does not rely on other parameters or results(bounds).
-%
-%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
-This will use much less time.
-
-\subsubsection*{Process for one image} An image is the basic unit in whole process.
-The process of one image is simple: compute the concrete bounds of nodes layer by layer, use the bounds of previous layer to build MILP models of current layer.
-In one layer, nodes runs in parallel.
-
-%Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers.
-Then we will compute bounds of every node in $l_i$ in parallel using the data of bounds of previous nodes.
-The method is to build and optimize an MILP model.
-
-%Some parameters may be changed during layers.
-Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
-Here, \emph{local} is opposite to \emph{global}.
-We have global timeout parameters for images and the whole running.
-Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
-
-%The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node. 
-%
-%The precomputation corresponds to the simplest case: source node fixed.
-We will compute and store a limited number of paths with highest (absolute) values before running any image.
-This does not rely on other parameters or results(bounds).
-%
-%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
-This will use much less time.
-
-\begin{algorithm}
-	\caption{The Frame work}
-	\KwData{Input Domain: $\mathcal{D}$}
-	\KwResult{Bounds of all nodes: $\mathcal{B}$}
-
-	Constant $\mathcal{R}$  \tcp*{Stored precomputation data}
-
-	Constant $\boldsymbol{W}, \boldsymbol{b}$ \tcp*{Weights and Bias of network}
-
-	Constant Layers = $[0,1,2\cdots,L]$ \tcp*{lists of all layer}
-
-	Constant NodesLayer = $[Nodes_0,Nodes_1,\cdots, Nodes_L]$ \tcp*{list of nodes in each layer}
-
-	Initialize $\mathcal{B}$ = \{\} \tcp*{To store upper and lower bounds of all nodes}
-
-	\For{$l$ in Layers}{
-		\If{$l$ = 0}{
-
-			$\mathcal{D}$, $\boldsymbol{W}, \boldsymbol{b}$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
-			\tcp*{Do linear transformation  from input to the first layer}
-
-			Add \{$x$: $(UB(x),LB(x))$,$\cdots$\} to $\mathcal{B}$}
-
-		\Else{
-
-			$l$, NodesLayer $\rightarrow$ $Nodes_l$ = $[x_0,x_1,\cdots]$
-
-			\For{$x$ in $Nodes_l$}{
-				$x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}
-
-				$\mathcal{B}$, $\boldsymbol{W}, \boldsymbol{b}$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
-
-				\While{}{$\mathcal{M}$ $\rightarrow UB(x),LB(x)$ \tcp*{Optimization}}
-
-				Add \{$x$: $(UB(x),LB(x))$\} to $\mathcal{B}$
-
-			}
-
-		}
-
-	}
-
-	\Return{$\mathcal{B}$}
-
-\end{algorithm}
-
-\subsubsection*{Process for one node}
-
- The optimization of a model consists of loops.
-For each loop, the model will do optimization by a timeout and observe the result.
-If it gets improvement, then continue the loop until the optimize bounds or the longer timeout.
-Otherwise it will give up optimization and store the best bounds obtained so far.
-
-\subsubsection*{Global Process}
-
-In the newest version, we do images by batches for 100 images each. For each batch, the running consists of three turns, very fast turn, fast turn and slow turn.
-
-In the very fast turn, it will run DeepPoly for all images to get a preliminary bounds for all nodes and verify the easiest images.
-Images verified and images with false predication will be deleted from the image list.
-
-Then sort all remain images by the size of uncertainty of DeepPoly from smaller to larger.
-The fast turn is to run the images from the smaller side to larger side until consecutive two images cannot be verified.
-All remain images and images tried but not verified will be put into the next list.
-And then run the list with parameters for slow turn.
-
-\subsection{Parameters}
-
-Parameters like open node parameter $O$ is important in the frame. Basically, all parameters will be reset after one image.
-
-\subsubsection*{Global parameters}
-
-\subsubsection*{Local parameters}
-
-$O$ and timeout parameters for loops will change frequently during the loops of one node. These change will not reset until the end of one layer or one image.
-
-\subsection{Other Setting}
-
-In our experiments, we have not used PGD-attack to exclude some images. In principle, there is no obstacle to use PGD-attack.
-
-\section{Experimental Evaluation}
-
-The neural network certification benchmarks for fully connected networks were run on a 32 core
-GHz Intel with 256 GB of main memory. We use Gurobi 9.52 for solving MILP and LP problems
-
-We used MNIST image datasets for our experiments. MNIST contains grayscale images of size 28 × 28 pixels. For our evaluation, we chose the first
-1000 images from the test set of each dataset.
-
-Each data example is associated with an $L^\infty$ norm $\varepsilon$ and a target label
-for verification.
-
-\subsection{Experiments about Node Chosen}
-
-The first group of experiments is to test the direct effect of node chosen by compensating pair, comparing to random chosen.
-We use the average of uncertainty of all nodes in a layer to measure the effect of node chosen: for a node $a$, its uncertainty $UN(a) = UB(a)-LB(a)$, and the average uncertainty of a layer $l$ is $$UN(l) = \dfrac{\sum_{a\in l}UN(a)}{|l|}.$$
-
-The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the MNIST image dataset.
-
-\subsubsection*{Node chosen in second hidden layer}
-
-The following table shows the average uncertainty of the second hidden layer when choosing different numbers of open nodes by random or by compensating pairs.
-
-\begin{table}
-	\centering
-	\begin{tabular}{c|c|c}
-
-	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
-	0  &  2.22 & 2.22  \\ \hline
-	10  &  1.84 & 2.03  \\ \hline
-	20  &  1.50 & 1.82  \\ \hline
-	30  &  1.28 & 1.62  \\ \hline
-	40  &  1.14 & 1.44  \\ \hline
-	50  &  1.06 & 1.23  \\ \hline
-\end{tabular}
-\caption{}
-\label{tab:example0}
-\end{table}
-
-\subsubsection*{Node chosen in the third hidden layer}
-
-The following table shows the average uncertainty of the third hidden layer when choosing different numbers of open nodes, by random or by compensating pairs.
-
-\begin{table}
-	\centering
-	\begin{tabular}{c|c|c}
-
-	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
-	0  &  1.758 & 1.758  \\ \hline
-	10  &  1.677 & 1.695  \\ \hline
-	20  &  1.539 & 1.622  \\ \hline
-	30  &  1.431 & 1.542  \\ \hline
-	40  &  1.329 & 1.47  \\ \hline
-	50  &  1.243 & 1.39  \\ \hline
-\end{tabular}
-\caption{}
-\label{tab:example1}
-\end{table}
-
-\section{Proofs}
-
-\input{proofs}
-
-\section{Experiments Results}
-
-\subsection{Comparison to Incomplete Verifiers}
-
-In Table 3, we compare against two representative incomplete
-verifiers on 4 MLP networks for MNIST under the same
-set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
-
-\begin{table}
-	\centering
-	\begin{tabular}{c|c|cc|cc|cc|cc}
-
-		\text{Network}  & $\varepsilon$&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\
-
-		&  & \textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) &\textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) \\ \hline
-
-		\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 51 & 159 &    68.4 & 142 & 69.9 & 102 \\ \hline
-
-		\textrm{MLP}\ 8$\times$100\  &   0.026& 52.7 & 92.3 & 42.8 & 301 &    65.8 & 364 & 62 & 103 \\ \hline
-
-		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 69 & 224 &    76.8 & 279 & 77.4 & 86 \\ \hline
-
-		\textrm{MLP}\ 8$\times$200\  &   0.015& 68.1 & 297 & 62.4 & 395 &    79.1 & 535 & 73.5 & 95 \\ \hline
-
-		\textrm{MLP}\ 6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
-	\end{tabular}
-	\caption{The data of verified accuracy (\%) and average time (s) of 1000 images evaluated on the PRIMA and on the beta-Crown are in CITE.}
-	\label{tab:example}
-\end{table}
-
-On all 4 networks, our fast version can exceed PRIMA both in accuracy and speed. On all 4 networks, our slow version can have a similar verified accuracy as beta-Crown.
-
-% test
-
-\section{Related Work}
-
-\section{Conclusion}
-
-\section*{Appendix: Proofs of No Diamond Theorem}
-
-\bibliographystyle{plain}
-\bibliography{references}
-
 \end{document}

### 2024-01-15 Paper/introduction.tex

@@
 In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers.
-This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy}\dots
+This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy2013}\dots
 

### 2024-01-15 Paper/Paper_noProof.tex
overall pass

@@
 		\end{tikzpicture}
-		\caption{A DNN example from \cite{kneuron}, where every node is separated into 2, $x$ after the weighted sum and $\hat{x}$ after the ReLU activation function.}
+		\caption{A DNN example from \cite{kpoly}, where every node is separated into 2, $x$ after the weighted sum and $\hat{x}$ after the ReLU activation function.
+The pair $(x_2 x_3 x_5,x_2 x_4 x_5)$ in green and red is compensating (weights of paths are $1,-2$).}
 		\label{fig1}
@@
 Here, $weight(x_5) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (a contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of the exact $-x_2 \leq 1.5$), and obtain a bound $weight(x_5) \leq 5.5$ instead of $4$.
+However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of exact $-x_2 \leq 1.5$), obtaining a bound $weight(x_5) \leq 5.5$ instead of $4$.
 
 Intuitively, the target state receives the weight from the source state from the different paths from the source to the target.
-As the weights of the paths is of opposite sign, some of these weights will cancel out,
-by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$. Further, no only do they cancel $min(|weight(\pi')|,|weight(\pi')|)$ out, but they also do not accumulate, in the same way as 
-$0= |1+(-1)| \leq |1|+|-1|=2$ from an inacurate analysis.
+As the weights of the paths is of opposite sign, some of these weights will cancel out, by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$.
+Further, no only do they cancel $min(|weight(\pi')|,|weight(\pi')|)$ out, but they also do not accumulate, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inacurate analysis.
 The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function.
@@
 over all source/target states in given layers.
-The average compensations strenght are much lower in the Robust DNN than in the Natural DNN, and indeed the Robust DNN is much simpler to verify than the Natural DNN.
+The average compensations strenght are much lower in the Robust DNN than in the Natural DNN, and indeed the Robust DNN is much simpler to verify than the Natural DNN (e.g.
+DeepPoly is more accurate and verifies more images).
 
@@
 
-Notice that It is likely that selecting ReLU nodes up to 3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade off is unclear and we thus didnot experiment.
+Notice that it is likely that selecting ReLU nodes up to 3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade off is unclear and we thus didnot experiment.
 
@@
 
-		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & no & point & $65.3\%$ & $68.4\%$ &  $84.2 \%$ \\ 
-		$\epsilon = 0.026$ & 5s & 159s & 102s& & & 117s & 142s &  \\
+		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & $57.5\%$ & $66.1\%$ & $65.3\%$ & $68.4\%$ &  $84.2 \%$ \\ 
+		$\epsilon = 0.026$ & 5s & 159s & 102s& 75s & 140s & 117s & 142s &  \\
 		\hline
@@
 Things are more interesting on the accuracy front: on shallower DNNs ($5 \times 100$ and $5 \times 100$ with 5 hidden layers), the refinement with MILP treats all but the 2 last layers,
-leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accuate than using compensation: we are within $1.5\%$ of the accuracy.
+leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accuate than using compensation: we are within $1.6\%$ of the accuracy.
 On deeper DNNs ($8 \times 100$ and $8 \times 100$ with 8 hidden layers), the refinement with MILP cannot treat the 4 last layers, and BaB has more ReLU to branch on.

### 2024-01-15 Paper/proof revison.tex

--- 2023-11-16 Paper/Paper.tex
@@
 \newcommand{\ReLU}{\mathrm{ReLU}}
+\newcommand{\Val}{\mathrm{Value}}
+\newcommand{\UB}{\mathrm{UB}}
+\newcommand{\LB}{\mathrm{LB}}
+\newcommand{\ub}{\mathrm{ub}}
+\newcommand{\lb}{\mathrm{lb}}
+\newcommand{\B}{\mathrm{B}}
 
@@
 \begin{document}
-
-\maketitle
 
@@
 
-We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$. We also denote $a_I\oplus a_J = a_K$ and $z=z(a_K)=z(a_I,a_J)$.
-Consider $a_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
+We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$.
+We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
+Consider $\boldsymbol{x}_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
 
 \begin{lemma} \label{lem:reach_max}
-	$max_a (weight_{a}(z)) = max_{\{a \mid a_I=a^*_I\}} (weight_{a}(z))$
+	$max_a (weight_{a}(z)) = max_{\{a \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (weight_{a}(z))$
 
-	Further, for every intermediate node $b$ in the hidden layer, for any valuation $a^0_J$, 
-	we have $max_{\{a \mid a_J=a^0_J\}} (weight_{a}(b)) = max_{\{a \mid a_J=a^0_J,a_I=a_I^*\}} (weight_{a}(b))$.	
+	Further, for every intermediate node $b$ in the hidden layer, for any valuation $\boldsymbol{x}^0_J$, 
+	we have $max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (weight_{a}(b)) = max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J,\boldsymbol{x}_I=\boldsymbol{x}_I^*\}} (weight_{a}(b))$.	
 \end{lemma}
@@
 	For the first statement, we use 
-	$$max_{a_K} (weight_{a_K}(z)) = max_{a_J} max_{a_I} (weight_{a_I,a_J}(z))$$
+	$$max_{\boldsymbol{x}_K} (weight_{\boldsymbol{x}_K}(z)) = max_{\boldsymbol{x}_J} max_{\boldsymbol{x}_I} (weight_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$
 
-	Now, for any fixed input $a^0_J$, we can regard $weight_{a_I,a^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $a^0_J$ %and their propagation in hidden layers 
+	Now, for any fixed input $\boldsymbol{x}^0_J$, we can regard $weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
 	as bias.
 In the simplified $D'$, there is no compensating path because of the definition of $I$.
-Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,a^0_J)$ reaches its maximal value for $a_I=a_I^*$, and we are done.
+Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
 
-	The second statement is simpler because for each fixed partial input $a^0_J$, 
-	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $a^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
+	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
+	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
 \end{proof}
@@
 $b \notin B_{pure}$. %For any subdomain $D \subseteq B_O$, 
-Let $a^0_J$ and $a^0_I$ be fixed inputs, and consider the associated upper bound 
-$\mathrm{UB}_{a^0_J,a^0_I}$. We have:
+Let $\boldsymbol{x}^0_J$ and $\boldsymbol{x}^0_I$ be fixed inputs, and consider the associated upper bound 
+$\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}$. We have:
 %We show that this upper bound does not exceed the maximal value of $z$:
@@
 \begin{align*}
-	\mathrm{UB}_{a^0_J,a^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{a^0_I,a^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{a^0_I,a^0_J}(b)).
-\end{align*}
-
-where $\mathrm{AppB}(weight_{a^0_I,a^0_J}(b))$ is the upper bound of 
-the (LP) approximation of $weight_{a^0_I,a^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
+	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
+the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
 of its (LP) approximation if $w_{b,z}<0$.
 
-By Lemma \ref{lem:reach_max}, for any fixed input $a^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
-$weight_{a_I,a^0_J}(b)$ will get its maximal value for $a_I=a_I^*$,
-and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{a^0_I,a^0_J}(b)$ will get its minimal value for $a_I=a_I^*$.
+By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
+$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
+and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
 Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
@@
 \begin{align*}
-	\mathrm{UB}_{a^0_J,a^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{a^*_I,a^0_J}(b)) +
-	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b)).
+	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
+	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
 \end{align*}
@@
 
-$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b)) = 
-\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b))$$
+$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
 
@@
 
-$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{a^*_I,a^0_J}(b)) = 
-\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{a^*_I}(b))
-=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{a^*_I}(b))
-$$
-
-as $\mathrm{AppB}(weight_{a^*_I}(b))=\mathrm{ReLU}(weight_{a^*_I}(b))$ since 
-$weight_{a^*_I}(b)$ is an extremal value (minimum or maximal) and 
-$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values (make a lemma about that in the begining).
+$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
+=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
+$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
+$weight_{\boldsymbol{x}^*_I}(b)$ is an extremal value (minimum or maximal) and 
+$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values.
 
 Hence we have: \begin{align*}
-	\mathrm{UB}_{a^0_J,a^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(a_I^*,\bar{a}_J))
-	= \max_{a_I} z(a_I,\bar{a}_J) \\
-	\leq & \max_{a_J}\max_{a_I} z(a_I,a_J) 	= \max_{a_K} weight_{a_K}(z)
+	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
+	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
+	\leq & \max_{\boldsymbol{x}_J}\max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\boldsymbol{x}_J) 	= \max_{\boldsymbol{x}_K} weight_{\boldsymbol{x}_K}(z)
 \end{align*}
 
-Considering the maximal over all inputs $a_J,a_I$, we obtain
+Considering the maximal over all inputs $\boldsymbol{x}_J,\boldsymbol{x}_I$, we obtain
 
-$$\mathrm{UB} = max_{a_J,a_I} \mathrm{UB}_{a_J,a_I} \leq \max_{a_J,a_I} weight_{a_J,a_I}(z)$$
+$$\mathrm{UB} = max_{\boldsymbol{x}_J,\boldsymbol{x}_I} \mathrm{UB}_{\boldsymbol{x}_J,\boldsymbol{x}_I} \leq \max_{\boldsymbol{x}_J,\boldsymbol{x}_I} weight_{\boldsymbol{x}_J,\boldsymbol{x}_I}(z)$$ And this us what we want to show.
+
+\section{Proof of Theorem 2, full version}
+
+In this section, we will try to prove the full version of theorem 2, that is
+
+\begin{theorem}
+	\label{no_diamond_3}
+
+	Suppose we have a DNN with $\ReLU$ as the unique activation functions. We consider compensating pairs in between any two nodes (i.d., the source node or target node can in hidden layers.)
+
+	Using MILP method, if every nodes $b$ in any compensating pair
+	$(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
+	bounds computed by MILP are the exact max and min value of $z$.
+\end{theorem}
+
+Before the proof of above theorem, we will try to weaker one, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes).
+We call such pair a weak compensating pair.
+
+We uses very similar definitions as in previous section.
+
+\begin{definition}
+	Let $K$ be the set of  all input nodes $a_k$. 
+	We define a decomposition $K=I\sqcup J$ as follows:  
+	\begin{itemize}
+		\item $a_k \in I$  if
+		\begin{enumerate}
+			\item every path from $a_k$ to $z$ has weight $\geq 0$, or
+			\item every path from $a_k$ to $z$ has weight $\leq 0$.
+		\end{enumerate}
+		That is, $a_k$ is not a source of a weak compensating pair.
+		\item $a_k \in J$ if $a_k \notin I$, that is there exists two paths $\pi,\pi'$ from $k$, 
+		one with positive and one with negative weight.
+	\end{itemize}
+\end{definition}
+
+\begin{lemma} \label{lem:open_node_2}
+	A node $b$ in the hidden layer will not be on a weak compensating pair iff one of the following two happens:
+	\begin{enumerate}
+		\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $w_{b,z}=0$ to denote this case, or
+		\item For every input node $a_j\in J$, for any path from $a_j$ to $b$ has a weight of $0$. We use $w_{a_j,b}=0$ to denote this case.
+	\end{enumerate}
+	We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.
+
+	We denote $B_O$ the set of all nodes $b$ that is in a compensating path.
+\end{lemma}
+
+\begin{proof}
+	First, we show that if either one of case 1,2 happens, then $b$ will not be on a weak compensating pair.
+If 1), it is obvious.
+For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$.
+It means that $a \in J$.
+A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.
+
+	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
+	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
+	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
+	Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
+	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
+	Then $((a_j,b,z), \pi')$ is also a weak compensating pair.
+\end{proof}
+
+Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
+
+\begin{lemma}\label{lem:subnetwrok}
+	$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only replies on nodes in $B_{pure}\cup I$ in previous layers.
+\end{lemma}
+
+\begin{proof}
+	This is simply because for a node $c\in B_{pure}$ in a hidden layer or the output layer, for a node $b$ in one layer before, if $b\notin B_{pure}\cup I$, then:
+
+	1. if $b\in J$, by definition, $w_{bc}=0$.
+
+	2. if $b\in B_{O}$, then $w_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.
+
+	3. if $b\in B_{zero}$, then $w_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
+
+\end{proof}
+
+\begin{definition}\label{sign_of_nodes_in_I_2}
+	We define a partial sign function $S$ over nodes $n$ such that : 	
+	\begin{enumerate} 
+		\item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
+		\item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
+		\item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
+		\item Otherwise $S(n)$ is undefined.
+	\end{enumerate}
+\end{definition}
+
+Notice that $S$ is defined on all nodes $a_i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
+And similarly, for nodes in  $B_{zero}$, $S$ is defined.
+We introduce the following lemma:
+
+\begin{lemma}\label{lem:sign}
+	For a node $b$, if there exists at least one path from a node $a_i\in I$ with nonzero weight, then  $S$ is defined on $b$.
+\end{lemma}
+
+\begin{proof}
+	Otherwise, suppose there exists two paths $P_1,P_2$ from $b$ to $z$ with (strictly) different signs.
+Then consider $\langle a_i,b\rangle+P_1$ and $\langle a_i,b\rangle+P_2$, they are two paths with weights with different signs.
+This is a contradiction since $a_i\in I$.
+\end{proof}
+Therefore, for any node $b$  that $S$ is undefined on $b$, it is only depending on the values on $J$.
+
+\begin{lemma}
+	If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$. Then $W_{bc}S(c)=S(b)$.
+\end{lemma}
+
+We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
+We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
+We can see that for a node $b$ that $S$ is not defined on it, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ becomes a constant.
+
+We define $\boldsymbol{x}_I^*$ to be the input vector such that for all $a_i \in I$, the value $x_{a_i}$ for $a_i$ gets its maximal value (if $S(a_i)=1$ or $0$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
+Similarly, we define $\boldsymbol{x}_I^\#$ to be the input vector such that for all $a_i \in I$, the value $x_{a_i}$ for $a_i$ gets its maximal value (if $S(a_i)=-1$ or $0$) or $a_i$ gets its minimal value (if $S(a_i)=1$).
+
+\begin{lemma} \label{lem:reach_max_2}
+
+	Assume $b$ is the output node or a node in a hidden layer that $S(b)=1$. Then
+	$\max_{\boldsymbol{x}} (\Val_{\boldsymbol{x}}(b)) =\max_{\{\boldsymbol{x} \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (\Val_{\boldsymbol{x}}(b))$.
+
+	Further,  for any valuation $\boldsymbol{x}^0_J$, 
+	we have $$\max_{\{\boldsymbol{x} \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (\Val_{\boldsymbol{x}}(b)) =  \Val_{\boldsymbol{x}^0_J,\boldsymbol{x}_I^*}(b).$$
+
+	If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\#_I$. 
+\end{lemma}
+
+\begin{proof}
+	For the first statement, we use 
+	$$\max_{\boldsymbol{x}_K} (\Val_{\boldsymbol{x}_K}(z)) =\max_{\boldsymbol{x}_J} \max_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$
+
+	Now, for any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
+	as bias.
+In the simplified $D'$, there is no compensating path because of the definition of $I$.
+Therefore we can apply Theorem \ref{th1} to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
+
+	For the second part, for any $b$ that is at least 2 layers after $a$, we can regard $b$ as the output node and apply the same argument above.
+
+	If $b$ is immediately after $a$, then the proof is the same as last part of Lemma \ref{lem:reach_max} last section.
+
+\end{proof}
+
+\subsection{MILP abstraction}
+
+Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
+where each variable $\alpha_b$ for the ReLU from $b$ to $\hat{b}$ is:
+\begin{itemize}
+	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \notin B_{O}$
+	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \in B_{O}$
+\end{itemize}
+
+Now consider the MILP framework for all hidden and output nodes layer by layer (to compute their bounds, and use the bounds of previous layers to build the MILP models of current layer), with ReLUs being either linear or binary depending on whether $b \in B_{O}$ or not.
+
+For a node $b$ in a hidden layer or the output layer, we denote by $\UB(b)$ the maximal bound on $b$ and $\LB(b)$ the minimal bound on $b$ considering the MILP constraints above.
+
+%\begin{definition} Assume $\boldsymbol{x}^0_I\oplus \boldsymbol{x}^0_J$ is a input vector, and $b$ is node in hidden layers or output layer.
+%
+%	1.
+For a given vector $\boldsymbol{x}$ , $\B_{\boldsymbol{x}^0_I, \boldsymbol{x}^0_J, \boldsymbol{x}}(b)$ is the value of $b$ in the MILP model for values $\boldsymbol{x}^0_I, \boldsymbol{x}^0_J, \boldsymbol{x}$.
+%\end{definition}
+
+For input vectors $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$, let $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ be the upper bound in the above fixed formulation and framework while the input $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$ is fixed: that is, besides the constraints in above MILP models, we add new constraints $\boldsymbol{x}_I,\boldsymbol{x}_J=\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
+We  define $\LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ similarly for $\LB$ lower bound.
+For them, we have the following lemma:
+
+\begin{lemma} In an MILP formulation, for a node $c$ in a hidden layer or output layer:
+
+	1. $\UB(b)=\max_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$.
+
+		2. $\LB(b)=\min_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$. 
+\end{lemma}
+
+\begin{proof}
+	This is by the definition of MILP formulation and $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}, \LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$.
+\end{proof}
+
+%\begin{lemma}\label{lem:pure_node}
+%	For a node $c\in B_{pure}$, $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$ (and $\LB$ the same) only depends on $\boldsymbol{x}^0_I$.
+%\end{lemma}
+%
+%\begin{proof}
+%	We prove this lemma by induction. For the first hidden layer, this is trivial.
+%	
+%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
+%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
+%		 + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
+%		 +\sum_{b\in B_{zero}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
+%	
+%	
+%	But since $c\in B_{pure}$, for any $b\in B_O$, we must have $w_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $w_{bc}=0$. Therefore, we will have:
+%	
+%	\begin{align*}
+%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
+%	
+%	\begin{align*}
+%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
+%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
+%\end{proof}
+
+We want to show that $\mathrm{UB}(z) = \max z$ and $\mathrm{LB}(z) = \min z$ for the unique output nodes and we will prove this for all $c$ such $w_{c,z}\neq 0$.
+As the MILP abstraction is a sound overapproximation,
+it suffices to show that $\mathrm{UB}\leq \max c$ and $\mathrm{LB} \geq \min c$.
+We will prove this by induction on layers from the first hidden layer to the output layer.
+More specifically, we will prove the following lemma:
+
+\begin{lemma}
+	For the $i$-th layer $l^i$ ($1$-th layer is the first hidden layer), for a node $c\in l^i$, if $c\notin B_{zero}$, then:
+
+	 For any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val(\boldsymbol{x}^*_I,\boldsymbol{x}^0_J)(c) = \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$, where $\boldsymbol{x}^*_I$ is described in previous section.
+More important, when $\boldsymbol{x}_I=\boldsymbol{x}^*_I$, for all node $c$ in the same layer, the approximation of $c$ is a constant number rather than an interval, and it is equal to $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$ or $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
+
+The similar is true for lower bound $\LB$.
+\end{lemma}
+
+\begin{proof}
+
+	For $i= 1$, we have proved in previous section.
+
+	Suppose we have proved this lemma up to layer $i$, and we are going to prove it for $i+1$-th layer. Let $c\notin B_{zero}$ be a node on $i+1$-th layer.
+
+	By definition, we have that for any input vector $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$:
+
+	\begin{align*}
+		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
+$\B$ is one of $\UB,\LB$  that, if $w_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
+
+	We can simplify above equation to \begin{align*}
+			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
+	\end{align*}
+
+	By induction hypothesis, since both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have that \begin{align*}
+		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
+		 &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
+	\end{align*} The equal is because by induction hypothesis, when $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, the approximation is a constant and is equal to $\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
+
+Now, since when $x$ reaches the max or min of $\mathrm{AppB}$'s domain, $\mathrm{AppB}(x)=\ReLU(x)$, and by induction hypothesis, for any $b\in B_{pure}\cap l_i$, $\mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))=\ReLU(B_{\boldsymbol{x}^*_I})$.
+Hence, by induction hypothesis, we will have \begin{align*}
+	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
+	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
+	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
+	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).
+\end{align*} This finishes the proof.
+	\end{proof}
+
+Now, we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$.
+Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$.
+This is what we want to show, and the same result holds for lower bound and minimal value.
 
 \end{document}
-
-%
-%The DeepPoly function for $b$ can be expressed by the following steps.
-%First, we partition the set of indices $i$ as $I,I_0,I^+,I^-$ with:
-%\begin{itemize}
-%	\item $i \in I$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case 
-%	$\bar{f}(b_i^+)(Y)=\underline{f}(b_i^+)=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$, and else:
-%	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,	and else:
-%	\item $i \in I^+$ if $w_{b_i c}>0$, and:
-%	\item $i \in I^-$ if $w_{b_i c}<0$.
-%	\end{itemize}
-%	
-%Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.
-%	
-%
-%We have:
-%\begin{align*}
-%	\bar{f}(c)(Y) = &
-%	bias_c + \sum_{b \in I} w_{bc}\sum_{a} w_{a b} weight(a) + bias_{b} \\
-%	& + \sum_{b \in I^+} w_{b c} \cdot \bar{f}(ReLU(\sum_{a} w_{a b} weight(a) 
-%	+ Bias_{b}))(Y) 
-%	\end{align*}

### 2024-01-15 Paper/Paper_noProof.tex
overall

@@
 Here, $weight(x_5) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of exact $-x_2 \leq 1.5$), obtaining a bound $weight(x_5) \leq 5.5$ instead of $4$.
+However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of exact $-x_2 \leq 1$), obtaining a bound $weight(x_5) \leq 5.5$ instead of $4$.
 
@@
 We experiment with the smallest network (MLP $6\times 100$), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
-We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first layer and $94(?)$ in the second layer), so we can experiment with a larger choice of values for $K$.
+We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first layer and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
 
@@
 \end{tabular}
-\caption{Average uncertainty of $\MILP_Z$ for nodes of the second layer, for a set $Z$ of $K$ ReLU nodes of the first layer with the heaviest compensation, vs $K$ random nodes of the first layer.}
+\caption{Average uncertainty of $\MILP_Z$ for nodes of the second layer, for $Z$ with $K$ ReLU nodes of the first layer (compensating strenght vs random choice).}
 \label{tab:example0}
+\vspace{-0.8cm}
 \end{table}
@@
 We compare choosing nodes in the second layer only with choosing nodes in both the first and second layer.
-Choosing ReLU nodes in the previous layer (layer 2) only is never a good choice. 
-When picking in both layer 1 and 2, choosing 50 out of 149(?) unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inacurate computations ($0.059$ vs $0.574$), while it only reduces the inacuracy by $65\%$ when choosing nodes randomly.
-Notice that this is direct inacuracy, applying this layer over layer will even further reduce inacuracy created by accumulation of inacuraccies.
+Choosing ReLU nodes in the previous layer (layer $2$) only is never a good choice. 
+When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inacurate computations ($0.059$ vs $0.574$), while it only reduces the inacuracy by $65\%$ when choosing nodes randomly.
+Notice that this is direct inacuracy, applying this layer after layer will even further reduce inacuracy created by accumulation of inacuraccies.
 
@@
 	50  &  1.243 & 1.432 & 1.39  \\ \hline
-	max  &  1.184 & 1.422 & 1.184  \\ \hline
+	116 &  1.184 & 1.422 & 1.184  \\ \hline
 \end{tabular}
-\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for a set $Z$ of $K$ ReLU nodes of the (first and) second layer with the heaviest compensation, vs $K$ random nodes of the first and second layer.}
+\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strenght vs random choice).}
 \label{tab:example1}
+\vspace{-0.8cm}
 \end{table}
@@
 First, we have a fixed choice for $K$ ($K=60$ for fast and $K=200$ for slow), with a fall back to a lower $K$ ($K=50$ for fast and $K=60$ for slow) if the bounds found is too far from the solution found (MIPGap $>0.5$ in Gurobi).
-We run (our implementation of) DeepPoly first, then the fast version (fast), before running slow on the remaining Images (fast+slow).
+We run (our implementation of) DeepPoly first, then the fast version, before running slow on the remaining Images.
 	Further, we also experiment with an {\em adaptative} implementation, which lowers number $K$ adaptively between layers to adapt to the growing number $N$ of linear variables, which has an impact on the overall $\MILP(N,K)$ runtime.
@@
 
-\begin{table}[t!]
+\begin{table}[b!]
 	\centering
@@
 		Comp(adapt.) & Upper\\ 
-		 & / CROWN & (refined) & TO=30s & TO=1200s & fast & Bound\\
+		 & / CROWN &  & TO=30s & TO=1200s & fast & Bound\\
 		\hline \hline
 
-		$6\times500$\  &   $26\%$ & &  &  $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
-
-		$\epsilon = 0.035$ & 34s & &  & 576s & 925s &\\ \hline
+		$6\times500$\  &   $26\%$ & $35\%$ &  &  $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
+
+		$\epsilon = 0.035$ & 34s & 121s &  & 576s & 925s &\\ \hline
 	\end{tabular}
@@
 
-\begin{figure}[b!]
+\begin{figure}[t!]
 \centering

### 2024-01-15 Paper/proof revison.tex
update proof

@@
 
-\begin{lemma}\label{lem:subnetwrok}
+\begin{lemma}\label{lem:subnetwork}
 	$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only replies on nodes in $B_{pure}\cup I$ in previous layers.
+We call this sub-network $N_I$.
+In $N_I$, there is no compensating pair.
 \end{lemma}
@@
 \end{lemma}
+
+\begin{lemma}\label{lem:subnetwork2}
+	The input set $J$ with nodes that only depending on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $N_J$.
+\end{lemma}
+
+\begin{proof}
+	This is because if there exists nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ but this means so does $c$, a contradiction.
+Therefore any $b$ such that $W_{bc}\neq 0$ is also in above set.
+\end{proof}
+
+By definition, we can easily see that, for any $b\in N_J$, either $b\in B_O$, or $b$ is a constant node.
 
@@
 Now consider the MILP framework for all hidden and output nodes layer by layer (to compute their bounds, and use the bounds of previous layers to build the MILP models of current layer), with ReLUs being either linear or binary depending on whether $b \in B_{O}$ or not.
+We call this standard framework.
 
 For a node $b$ in a hidden layer or the output layer, we denote by $\UB(b)$ the maximal bound on $b$ and $\LB(b)$ the minimal bound on $b$ considering the MILP constraints above.
+
+\begin{lemma}
+	In the standard framework, both $N_I$ and $N_J$ are accurate in the sense that for any $b$ in $N_I$ or $N_J$, $\UB(b)=\max\Val(b)$ and $\LB(b)=\min\Val(b)$.
+\end{lemma}
+
+\begin{proof}
+	For $N_I$, it is because of no compensating as proved in the first section. For $N_J$, it is because all nodes are either opened or constants.
+\end{proof}
 
@@
 
-We want to show that $\mathrm{UB}(z) = \max z$ and $\mathrm{LB}(z) = \min z$ for the unique output nodes and we will prove this for all $c$ such $w_{c,z}\neq 0$.
+We want to show that $\mathrm{UB}(z) = \max \Val (z)$ and $\mathrm{LB}(z) = \min \Val(z)$ for the unique output nodes and we will prove this for all $c\notin B_{zero}$ .
 As the MILP abstraction is a sound overapproximation,
-it suffices to show that $\mathrm{UB}\leq \max c$ and $\mathrm{LB} \geq \min c$.
+it suffices to show that $\mathrm{UB}\leq \max \Val(c)$ and $\mathrm{LB} \geq \min \Val(c)$.
 We will prove this by induction on layers from the first hidden layer to the output layer.
-More specifically, we will prove the following lemma:
+More specifically, we will prove the following lemmas:
 
@@
 
-	 For any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val(\boldsymbol{x}^*_I,\boldsymbol{x}^0_J)(c) = \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$, where $\boldsymbol{x}^*_I$ is described in previous section.
-More important, when $\boldsymbol{x}_I=\boldsymbol{x}^*_I$, for all node $c$ in the same layer, the approximation of $c$ is a constant number rather than an interval, and it is equal to $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$ or $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
+	\vspace*{1ex}
 
-The similar is true for lower bound $\LB$.
+	1.
+for any fixed $\boldsymbol{x}^0_J$ and for $\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
+The same is true for $\boldsymbol{x}^\#_I$.
+
+	\vspace*{1ex}
+
+	2.
+for any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$,  $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$.
+The similar for $S(c)=-1$, $\langle \LB,\min\rangle$, $x^\#_I$: we can change two of them at the same time.
+
+	\vspace*{1ex}
+
+	3. Therefore, $\UB(c)=\max\Val(c)$ and $\LB(c)=\min\Val(c)$.
+
 \end{lemma}
@@
 \begin{proof}
+	We prove this lemma by induction on layers. For $l_1$, it is obvious. Suppose we have proved part 1,2,3 up to layer $l_i$, then for layer $l_{i+1}$, suppose $c$ is a node in this layer.
 
-	For $i= 1$, we have proved in previous section.
+(1)	First, if $S$ is undefined on $c$, then by previous discussion, $c$ is in a sub-network from $J$ with all nodes opened and if $\boldsymbol{x}_J=\boldsymbol{x}_J^0$ is fixed, then in the MILP model, the value for $c$ is also fixed.
+If $S(c)$ is defined, then consider all $b$ such that $W_{bc}\neq 0$.
+First, $b$ cannot in $B_{zero}$; so by induction hypothesis, the value of $b$ is fixed under $\boldsymbol{x}^*_I,\boldsymbol{x}^0_J$ in MILP model.
 
-	Suppose we have proved this lemma up to layer $i$, and we are going to prove it for $i+1$-th layer. Let $c\notin B_{zero}$ be a node on $i+1$-th layer.
+	If $b\in B_O$, the term is $W_{bc}\ReLU(b)$. We know then by induction hypothesis, the value for $b$ in MILP is a fixed value. Then the term $W_{bc}\ReLU(b)$ is also a fixed number.
 
-	By definition, we have that for any input vector $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$:
+	If $b\in B_{pure}$, the term is $W_{bc}\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined.
 
-	\begin{align*}
-		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
-	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
-$\B$ is one of $\UB,\LB$  that, if $w_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
+	We know then by induction hypothesis part 1, 2 and 3,  we have the value of $b$ in the model is fixed (part 1), and it is equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ (by part 2, depending on $S(b)$).
+Since $b$ only depends on $I$, this value also equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$, and therefor equal to $\UB(b)$ or $\LB(b)$.
+For either of them, $\mathrm{AppB}$ will be fixed value.
+Hence, in this case, the term $W_{bc}\mathrm{AppB}(b)$ is also a fixed number.
 
-	We can simplify above equation to \begin{align*}
-			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
-	\end{align*}
+	Therefore, in the MILP model, $c$ is a sum of terms that are all fixed numbers. Hence $c$ is a fixed number.
 
-	By induction hypothesis, since both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have that \begin{align*}
+	(2) If $S(c)=1$, then we have the following:	\begin{align*}
+		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
+	\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$.
+Now by induction hypothesis part 2, combining with $S(b)$ and both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
 	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-		 &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
-		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
-	\end{align*} The equal is because by induction hypothesis, when $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, the approximation is a constant and is equal to $\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
+	&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+	= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
+	\end{align*}  This is the first equal.
 
-Now, since when $x$ reaches the max or min of $\mathrm{AppB}$'s domain, $\mathrm{AppB}(x)=\ReLU(x)$, and by induction hypothesis, for any $b\in B_{pure}\cap l_i$, $\mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))=\ReLU(B_{\boldsymbol{x}^*_I})$.
-Hence, by induction hypothesis, we will have \begin{align*}
-	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
-	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
-	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
-	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).
-\end{align*} This finishes the proof.
+	The second is simply because $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.	The third equal is proved in last subsection, Lemma \ref{lem:reach_max_2}.
+$S(c)=-1$ is similar.
+So we have proved part 2.
+
+	(3) Once we have part 2, then we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$.
+Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$.
+This is what we want to show, and the same result holds for lower bound and minimal value.
+This is for part 3.
+
 \end{proof}
 
-Now, we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$.
+%\begin{lemma}
+%	For the $i$-th layer $l^i$ ($1$-th layer is the first hidden layer), for a node $c\in l^i$, if $c\notin B_{zero}$ and $S(c)=1$, then:
+%	
+%	 1.
+if , then for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val(\boldsymbol{x}^*_I,\boldsymbol{x}^0_J)(c) = \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$, where $\boldsymbol{x}^*_I$ is described in previous section.
+More important, when $\boldsymbol{x}_I=\boldsymbol{x}^*_I$, for all node $c$ in the same layer, the approximation of $c$ is a constant number rather than an interval, and it is equal to $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$ or $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
+%	
+%The similar is true for lower bound $\LB$.
+%\end{lemma}
+
+%\vspace*{20ex}
+%\begin{proof}
+%	
+%	For $i= 1$, we have proved in previous section.
+%	
+%	Suppose we have proved this lemma up to layer $i$, and we are going to prove it for $i+1$-th layer. Let $c\notin B_{zero}$ be a node on $i+1$-th layer.
+%	
+%	By definition, we have that for any input vector $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$:
+%	
+%	\begin{align*}
+%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+%	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
+$\B$ is one of $\UB,\LB$  that, if $w_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
+%	
+%	We can simplify above equation to \begin{align*}
+%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
+%	\end{align*}
+%	
+%	By induction hypothesis, since both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have that \begin{align*}
+%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
+%		 &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+%		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
+%	\end{align*} The equal is because by induction hypothesis, when $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, the approximation is a constant and is equal to $\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
+%	
+%Now, since when $x$ reaches the max or min of $\mathrm{AppB}$'s domain, $\mathrm{AppB}(x)=\ReLU(x)$, and by induction hypothesis, for any $b\in B_{pure}\cap l_i$, $\mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))=\ReLU(B_{\boldsymbol{x}^*_I})$.
+Hence, by induction hypothesis, we will have \begin{align*}
+%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
+%	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
+%	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
+%	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).
+%\end{align*} This finishes the proof.
+%	\end{proof}
+%
+%
+%Now, we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$.
 Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$.

### 2024-01-15 Paper/Paper_noProof.tex
biblio

@@
 We tested PureBaB with two time out, from the standard 30s to an extreme 2000s, to match the average run time of our adaptative implementation (fast mode).
-Only $2\%$ more of images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
+Only $3.5\%$ more of images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
 Notice that the refined BaB mode of $\beta$-Crown (using MILP for the first few layers) failed to run on this DNN (NoImplementation error code), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as
@@
 
-		$6\times500$\  &   $26\%$ & $35\%$ &  &  $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
-
-		$\epsilon = 0.035$ & 34s & 121s &  & 576s & 925s &\\ \hline
+		$6\times500$\  &   $26\%$ & $35\%$ & $41\%$ & $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
+
+		$\epsilon = 0.035$ & 34s & 121s & 18.4s & 576s & 925s &\\ \hline
 	\end{tabular}
@@
 The simplest is to run $\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\beta$-CROWN cannot conclude.
-Another simple way is to modify the refined BaB of
-$\beta$-CROWN to run compensate($K$) on more layers than what exact MILP can be run, and finish the study using BaB.
+Another simple way is to modify the refined BaB of $\beta$-CROWN to run compensate($K$) on more layers than what exact MILP can be run, and finish the study using BaB.
 More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strenght, which we experimentally proved to be an efficient trade-off.
-Last, an analysis of important nodes for the uncertain output nodes could be performed, allowing to compute much faster less accurate bounds for those nodes not important.
+Also, an analysis of important nodes for the uncertain output nodes could be performed, allowing to compute much faster less accurate bounds for those nodes not important.
+Last, one could perform a Refinement Abstraction framework similar to \cite{atva}.
 

### 2024-01-15 Paper/proof revison.tex
update proof

@@
 
-\section{Theorem 2}
-
-We now show that if all intermediates nodes that are on compensating pairs are opened as MILP nodes, then MILP will be correct.
+%\section{Theorem 2}
+%
+%We now show that if all intermediates nodes that are on compensating pairs are opened as MILP nodes, then MILP will be correct.
 First, we do the proof with 3 layers, assuming (without loss of generality) a unique output node $z$.
-
-\begin{theorem}
-	\label{no_diamond_2}
-	Using MILP method, if every nodes $b_j$ in any compensating path pair
-	 $(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
-	 bounds computed by MILP are the exact max and min value of $z$.
-\end{theorem}
-
-By symetry, we only show the max side.
-
-\begin{definition}
-	Let $K$ be the set of all input nodes $a_k$. 
-	We define a decomposition $K=I\sqcup J$ as follows:  
-	\begin{itemize}
- \item $k \in I$  if
- \begin{enumerate}
-	 \item every path from $a_k$ to $z$ has weight $\geq 0$, or
-	\item every path from $a_k$ to $z$ has weight $\leq 0$.
- \end{enumerate}
-That is, $a_k$ is not a source of a compensating pair.
-	\item $k \in J$ if $k \notin I$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
-	one with positive and one with negative weight.
-\end{itemize}
-\end{definition}
-
-\begin{lemma} \label{lem:open_node}
-	A node $b$ in the hidden layer will not be on a compensating pair iff one of the following two happens:
-	\begin{enumerate}
-	 \item $w_{b,z}=0$, or
-	 \item For every input node $j\in J$, we have $w_{a_j,b}=0$.
-	\end{enumerate}
-	We denote $B_{pure}$ the set of such nodes $b$ such that at least one of the above holds.
-\end{lemma}
-
-\begin{proof}
-	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened.
+%
+%\begin{theorem}
+%	\label{no_diamond_2}
+%	Using MILP method, if every nodes $b_j$ in any compensating path pair
+%	 $(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
+%	 bounds computed by MILP are the exact max and min value of $z$.
+%\end{theorem}
+%
+%By symetry, we only show the max side. 
+%
+%
+%
+%\begin{definition}
+%	Let $K$ be the set of all input nodes $a_k$. 
+%	We define a decomposition $K=I\sqcup J$ as follows:  
+%	\begin{itemize}
+% \item $k \in I$  if
+% \begin{enumerate}
+%	 \item every path from $a_k$ to $z$ has weight $\geq 0$, or
+%	\item every path from $a_k$ to $z$ has weight $\leq 0$.
+% \end{enumerate}
+%That is, $a_k$ is not a source of a compensating pair.
+%	\item $k \in J$ if $k \notin I$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
+%	one with positive and one with negative weight.
+%\end{itemize}
+%\end{definition} 
+%
+%
+%\begin{lemma} \label{lem:open_node}
+%	A node $b$ in the hidden layer will not be on a compensating pair iff one of the following two happens:
+%	\begin{enumerate}
+%	 \item $w_{b,z}=0$, or
+%	 \item For every input node $j\in J$, we have $w_{a_j,b}=0$.
+%	\end{enumerate}
+%	We denote $B_{pure}$ the set of such nodes $b$ such that at least one of the above holds.
+%\end{lemma}
+%
+%\begin{proof}
+%	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened.
 If 1), it is obvious.
@@
 A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.
-
-	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
-	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
-	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
-	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
-	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
-	Then $((a_j,b,z), \pi')$ is also a compensating pair.
-\end{proof}
-
-Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
-
-\begin{definition}\label{sign_of_nodes_in_I}
-	We define a partial sign function $S$ over nodes $n$ such that : 	
-	\begin{enumerate} 
-		 \item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
-		 \item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
-		 \item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
-		 \item Otherwise $S(n)$ is undefined.
-	\end{enumerate}
-\end{definition}
-
-Notice that $S$ is defined on all nodes $a_i$ with $i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
+%	
+%	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
+%	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
+%	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
+%	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
+%	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
+%	Then $((a_j,b,z), \pi')$ is also a compensating pair.
+%\end{proof}
+%
+%Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
+%
+%
+%\begin{definition}\label{sign_of_nodes_in_I}
+%	We define a partial sign function $S$ over nodes $n$ such that : 	
+%	\begin{enumerate} 
+%		 \item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
+%		 \item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
+%		 \item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
+%		 \item Otherwise $S(n)$ is undefined.
+%	\end{enumerate}
+%\end{definition}	
+%	
+%Notice that $S$ is defined on all nodes $a_i$ with $i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
 Hence it is undefined only for nodes $a_j$ with $j \in J$.
-
-We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$.
+%
+%
+%We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$.
 We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
-Consider $\boldsymbol{x}_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
-
-\begin{lemma} \label{lem:reach_max}
-	$max_a (weight_{a}(z)) = max_{\{a \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (weight_{a}(z))$
-
-	Further, for every intermediate node $b$ in the hidden layer, for any valuation $\boldsymbol{x}^0_J$, 
-	we have $max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (weight_{a}(b)) = max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J,\boldsymbol{x}_I=\boldsymbol{x}_I^*\}} (weight_{a}(b))$.	
-\end{lemma}
-
-\begin{proof}
-	For the first statement, we use 
-	$$max_{\boldsymbol{x}_K} (weight_{\boldsymbol{x}_K}(z)) = max_{\boldsymbol{x}_J} max_{\boldsymbol{x}_I} (weight_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$
-
-	Now, for any fixed input $\boldsymbol{x}^0_J$, we can regard $weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
-	as bias.
+%Consider $\boldsymbol{x}_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
+%
+%\begin{lemma} \label{lem:reach_max}
+%	$max_a (weight_{a}(z)) = max_{\{a \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (weight_{a}(z))$
+%	
+%	Further, for every intermediate node $b$ in the hidden layer, for any valuation $\boldsymbol{x}^0_J$, 
+%	we have $max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (weight_{a}(b)) = max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J,\boldsymbol{x}_I=\boldsymbol{x}_I^*\}} (weight_{a}(b))$.	
+%\end{lemma}
+%
+%\begin{proof}
+%	For the first statement, we use 
+%	$$max_{\boldsymbol{x}_K} (weight_{\boldsymbol{x}_K}(z)) = max_{\boldsymbol{x}_J} max_{\boldsymbol{x}_I} (weight_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$
+%	
+%	Now, for any fixed input $\boldsymbol{x}^0_J$, we can regard $weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
+%	as bias.
 In the simplified $D'$, there is no compensating path because of the definition of $I$.
 Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
+%	
+%	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
+%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
+%\end{proof}
+%
+%\subsection{MILP abstraction}
+%
+%Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
+%where each variable $\alpha_b$ for the ReLU from $b^-$ to $b^+$ is:
+%\begin{itemize}
+%	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \in B_{pure}$
+%	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \notin B_{pure}$
+%\end{itemize}
+%
+%
+%\begin{lemma}\label{lem:AppB=ReLU}
+%	Let $\mathrm{AppB}$ be the upper bound of lower bound approximation functions of LP for $\ReLU$ function with known upper and lower bound (numbers) $u,l$.
+Then when $x$ reaches the extremal values (maximum or minimum values, $u$ or $l$), then $\mathrm{AppB}(x)=\ReLU(x)$.
+%	
+%\end{lemma}
+%
+%\begin{proof}
+%	This is simply by definition of LP approximation functions.
+%\end{proof}
+%
+%Notice that there is only one layer of ReLUs, in the hidden layer.
+%Denote by $\mathrm{UB}$ the maximal bound on $z$ considering the MILP constraints above, with ReLUs being either linear or binary depending on whether $b \in B_{pure}$ or not.
+%
+%We want to show that $\mathrm{UB} = \max z$. As the MILP abstraction is a sound overapproximation, 
+%it suffices to show that $\mathrm{UB}\leq \max c$.
+%
+%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
+%Denote by $B_O$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
+%$b \notin B_{pure}$. %For any subdomain $D \subseteq B_O$, 
+%Let $\boldsymbol{x}^0_J$ and $\boldsymbol{x}^0_I$ be fixed inputs, and consider the associated upper bound 
+%$\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}$. We have:
+%%We show that this upper bound does not exceed the maximal value of $z$: 
+%
+%\begin{align*}
+%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+%\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
+%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
+%of its (LP) approximation if $w_{b,z}<0$. 
+%
+%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
+%$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
+%and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
+%Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
+%
+%\begin{align*}
+%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
+%	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
+%\end{align*} 
+%
+%Added FIX:
+%Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
+%$w_{b,z} = 0$ and $b \in B^2$ iff $w_{b,z} \neq 0$.
+%Hence:
+%
+%$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
+%
+%For $b \in B^2$, we have $w_{a_j,b}=0$ for all $j \in J$
+%by definition of $B_{pure}$ (Lemma 4.), hence
+%
+%$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
+%=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
+%$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
+%$weight_{\boldsymbol{x}^*_I}(b)$ is an extremal value (minimum or maximal) and 
+%$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values.
+%
+%Hence we have: \begin{align*}
+%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
+%	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
+%	\leq & \max_{\boldsymbol{x}_J}\max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\boldsymbol{x}_J) 	= \max_{\boldsymbol{x}_K} weight_{\boldsymbol{x}_K}(z)
+%\end{align*}
+%
+%Considering the maximal over all inputs $\boldsymbol{x}_J,\boldsymbol{x}_I$, we obtain 
+%
+%$$\mathrm{UB} = max_{\boldsymbol{x}_J,\boldsymbol{x}_I} \mathrm{UB}_{\boldsymbol{x}_J,\boldsymbol{x}_I} \leq \max_{\boldsymbol{x}_J,\boldsymbol{x}_I} weight_{\boldsymbol{x}_J,\boldsymbol{x}_I}(z)$$ And this us what we want to show.
 
-	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
-	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
-\end{proof}
+\section{Proof of Theorem 2}
 
-\subsection{MILP abstraction}
-
-Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
-where each variable $\alpha_b$ for the ReLU from $b^-$ to $b^+$ is:
-\begin{itemize}
-	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \in B_{pure}$
-	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \notin B_{pure}$
-\end{itemize}
-
-\begin{lemma}\label{lem:AppB=ReLU}
-	Let $\mathrm{AppB}$ be the upper bound of lower bound approximation functions of LP for $\ReLU$ function with known upper and lower bound (numbers) $u,l$.
-Then when $x$ reaches the extremal values (maximum or minimum values, $u$ or $l$), then $\mathrm{AppB}(x)=\ReLU(x)$.
-
-\end{lemma}
-
-\begin{proof}
-	This is simply by definition of LP approximation functions.
-\end{proof}
-
-Notice that there is only one layer of ReLUs, in the hidden layer.
-Denote by $\mathrm{UB}$ the maximal bound on $z$ considering the MILP constraints above, with ReLUs being either linear or binary depending on whether $b \in B_{pure}$ or not.
-
-We want to show that $\mathrm{UB} = \max z$. As the MILP abstraction is a sound overapproximation, 
-it suffices to show that $\mathrm{UB}\leq \max c$.
-
-For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
-Denote by $B_O$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
-$b \notin B_{pure}$. %For any subdomain $D \subseteq B_O$, 
-Let $\boldsymbol{x}^0_J$ and $\boldsymbol{x}^0_I$ be fixed inputs, and consider the associated upper bound 
-$\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}$. We have:
-%We show that this upper bound does not exceed the maximal value of $z$:
-
-\begin{align*}
-	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
-\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
-the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
-of its (LP) approximation if $w_{b,z}<0$.
-
-By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
-$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
-and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
-Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
-
-\begin{align*}
-	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
-	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
-\end{align*}
-
-Added FIX:
-Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
-$w_{b,z} = 0$ and $b \in B^2$ iff $w_{b,z} \neq 0$.
-Hence:
-
-$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
-
-For $b \in B^2$, we have $w_{a_j,b}=0$ for all $j \in J$
-by definition of $B_{pure}$ (Lemma 4.), hence
-
-$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
-=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
-$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
-$weight_{\boldsymbol{x}^*_I}(b)$ is an extremal value (minimum or maximal) and 
-$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values.
-
-Hence we have: \begin{align*}
-	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
-	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
-	\leq & \max_{\boldsymbol{x}_J}\max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\boldsymbol{x}_J) 	= \max_{\boldsymbol{x}_K} weight_{\boldsymbol{x}_K}(z)
-\end{align*}
-
-Considering the maximal over all inputs $\boldsymbol{x}_J,\boldsymbol{x}_I$, we obtain
-
-$$\mathrm{UB} = max_{\boldsymbol{x}_J,\boldsymbol{x}_I} \mathrm{UB}_{\boldsymbol{x}_J,\boldsymbol{x}_I} \leq \max_{\boldsymbol{x}_J,\boldsymbol{x}_I} weight_{\boldsymbol{x}_J,\boldsymbol{x}_I}(z)$$ And this us what we want to show.
-
-\section{Proof of Theorem 2, full version}
-
-In this section, we will try to prove the full version of theorem 2, that is
+In this section, we will try to prove theorem 2, that is
 
@@
 We call such pair a weak compensating pair.
-
-We uses very similar definitions as in previous section.
 
@@
 
-	We denote $B_O$ the set of all nodes $b$ that is in a compensating path.
+	We denote $B_O$ the set of all nodes $b$ in a compensating path.
 \end{lemma}
@@
 
-Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
-
 \begin{lemma}\label{lem:subnetwork}
@@
 	3. if $b\in B_{zero}$, then $w_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
+\end{proof}
 
-\end{proof}
+Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
 
@@
 \end{proof}
-Therefore, for any node $b$  that $S$ is undefined on $b$, it is only depending on the values on $J$.
+Therefore, for any node $b$  that $S$ is undefined on $b$, it only depends on the values on $J$.
 
 \begin{lemma}
-	If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$. Then $W_{bc}S(c)=S(b)$.
+	If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$, then $W_{bc}S(c)=S(b)$.
 \end{lemma}
+
+\begin{proof}
+	This is proved in the first section.
+\end{proof}
 
@@
 
-We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
+We denote $\boldsymbol{x}_S$ for any subset $S\subseteq K$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
 We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
@@
 Therefore we can apply Theorem \ref{th1} to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
-
-	For the second part, for any $b$ that is at least 2 layers after $a$, we can regard $b$ as the output node and apply the same argument above.
-
-	If $b$ is immediately after $a$, then the proof is the same as last part of Lemma \ref{lem:reach_max} last section.
-
 \end{proof}
@@
 	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-	&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+	&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
 	= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 

### 2024-01-15 Paper/introduction.tex

--- 2024-01-11 Paper/introduction.tex
@@
 In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers.
-This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy}\dots
+This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations
+\cite{szegedy}\dots
 
-In this context, application of DNNs in safety critical applications is therefore cautiously envisioned.
-For that to happen at a large scale, hard guarantees should be provided, so that to avoid tremendous consequences.
-It is the reason for the developpement of (hard) verification tools since 2016, with now many tools with different trade offs from exact computation but slow (e.g.
-Marabou/Reluplex), up to very efficient but also incomplete (e.g.
-ERAN-DeepPoly).
+In this context, application of DNNs in safety critical applications is cautiously envisioned.
+For that to happen at a large scale, hard guarantees should be provided, so that to avoid dramatic consequences.
+It is the reason for the developpement of (hard) verification tools since 2016, with now many tools with different trade-offs from exact computation but slow (e.g.
+Marabou \cite{katz2019marabou}/Reluplex\cite{Reluplex}), up to very efficient but also incomplete (e.g.
+ERAN-DeepPoly \cite{deeppoly}).
 To benchmark these tools, a competition has been run since 2019, namely VNNcomp.
-The current overall better performing tool is $\alpha$-$\beta$-Crown, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs down to very efficient on larger DNNs.
+The current overall better performing verifier is $\alpha$-$\beta$-Crown, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs up to very efficient on larger DNNs.
 

### 2024-01-15 Paper/Paper_noProof.tex
biblio

@@
 over all source/target states in given layers.
-The average compensations strenght are much lower in the Robust DNN than in the Natural DNN, and indeed the Robust DNN is much simpler to verify than the Natural DNN (e.g.
+The average compensations strength are much lower in the Robust DNN than in the Natural DNN, and indeed the Robust DNN is much simpler to verify than the Natural DNN (e.g.
 DeepPoly is more accurate and verifies more images).
@@
 In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strenght of compensation that are meaningful, and consider that paths below this treshold are not compensating strongly enough to deserve an integer variable (there are cases where the MILP algorithm is exponential in the number of integer variables), calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
+Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this treshold are not compensating strongly enough to deserve an integer variable (there are cases where the MILP algorithm is exponential in the number of integer variables), calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
 In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small.
@@
 \begin{enumerate}
-  \item Evaluate experimentally how accurate is $\MILP_Z$ when using compensating strenght 
+  \item Evaluate experimentally how accurate is $\MILP_Z$ when using compensating strength 
  to choose the set $Z$ of ReLU nodes encoded exactly using an integer variable, compared with randomly chosing the set $Z$, to make sure the choice is relevant.
@@
 
-\subsection{Chosing nodes based on Compensation strenght}
-
-The first group of experiments we run, tests the accuracy of chosing a set $Z$ of $K$ nodes using compensation strenght, compared with randomly chosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+\subsection{Chosing nodes based on Compensation strength}
+
+The first group of experiments we run, tests the accuracy of chosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly chosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
 
@@
 A compensating pair $(\pi,\pi')$ of paths with target $n$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
-The compensating strenght for $(b,b')$ is defined as
+The compensating strength for $(b,b')$ is defined as
 $comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$. Indeed, 
@@
 Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
-We can deduce that selecting nodes based on compensating strenght helps to select important ReLU nodes for the accuracy.
+We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
 
@@
 \end{tabular}
-\caption{Average uncertainty of $\MILP_Z$ for nodes of the second layer, for $Z$ with $K$ ReLU nodes of the first layer (compensating strenght vs random choice).}
+\caption{Average uncertainty of $\MILP_Z$ for nodes of the second layer, for $Z$ with $K$ ReLU nodes of the first layer (compensating strength vs random choice).}
 \label{tab:example0}
@@
 \end{tabular}
-\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strenght vs random choice).}
+\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs random choice).}
 \label{tab:example1}
@@
 In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
-DeepPoly/CROWN is by far the fastest, but also the most inacurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found.
-This is because these DNNs, altough of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strenght, see Section \ref{Sec.comp}).
+DeepPoly/CROWN is by far the fastest, but also the most inacurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
+This is because these DNNs, altough of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
 
@@
 For DNNs easy to verify, $\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images.
-Compensation strenght is not required in these contexts, and likely not useful, reason why we did not considered it.
+Compensation strength is not required in these contexts, and likely not useful, reason why we did not considered it.
 
@@
 Another simple way is to modify the refined BaB of $\beta$-CROWN to run compensate($K$) on more layers than what exact MILP can be run, and finish the study using BaB.
-More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strenght, which we experimentally proved to be an efficient trade-off.
+More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strength, which we experimentally proved to be an efficient trade-off.
 Also, an analysis of important nodes for the uncertain output nodes could be performed, allowing to compute much faster less accurate bounds for those nodes not important.
-Last, one could perform a Refinement Abstraction framework similar to \cite{atva}.
-
-On the correlation between neurons, which PRIMA encodes explicitely, our results tend to show that it is more efficient to use the compensation strenght.
+Last, one could perform a Refinement Abstraction framework similar to \cite{atva}, \cite{elboher}, or \cite{SRGR}.
+
+On the correlation between neurons, which PRIMA encodes explicitely, our results tend to show that it is more efficient to use the compensation strength.
 Still, considering ReLU nodes exactly tends to be very accurate locally, but less when the source of correlation is many layers away.
@@
 We proved that this phenomenon is actually explaining entierely the inacuracies, as in their absence, even very simple arithmetic algebra suffices to verify accurately DNNs.
-We verified that DNNs harder to verify indeed exhibits more paths with larger compensating strenght.
+We verified that DNNs harder to verify indeed exhibits more paths with larger compensating strength.
 
@@
 This proves that compensating strength is a promising novel concept which should be further studied to 
-improve DNN verification. We finally proposed several ways to use the compensating strenght to optimize the tools even more than they are, and leave that as future work.
+improve DNN verification. We finally proposed several ways to use the compensating strength to optimize the tools even more than they are, and leave that as future work.
 

### 2024-01-15 Paper/introduction.tex
biblio

@@
 To benchmark these tools, a competition has been run since 2019, namely VNNcomp.
-The current overall better performing verifier is $\alpha$-$\beta$-Crown, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs up to very efficient on larger DNNs.
+The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
+\cite{cutting}.
 

### 2024-01-15 Paper/Paper_noProof.tex
biblio

@@
 Gurobi 9.52 was used for solving MILP and LP problems.
-Our implementations for Compensate($K$) is entirely realized in Python $X.Y$, and therefore not particularly optimal.
+Our implementations for Compensate($K$) is entirely realized in Python
+$3.8.10$, and therefore not particularly optimal.
 
@@
 Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also parallelized with 16 nodes in parallel, before running their BaB tool.
-We also test with the latest version of $\alpha$-$\beta$-CROWN ($X.Y$)
-	and of Prima ($X.Y$) on the MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
+We also test with the latest versions of $\alpha$-$\beta$-CROWN (October 2023)
+	and of PRIMA (2022) on the MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
 

### 2024-01-15 Paper/introduction.tex

@@
 
-For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
-On simple networks, such as those trained robust,
-this is particularly efficient because branch and bound can find very efficiently the bounds
-focusing on the actual question, considering the important branchs, while our algorithm will be less efficient as it has to consider each nodes one by one from the start.
-However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider and not enough can be discarded early.
-
-On such complex DNN, $\alpha$-$\beta$ CROWN resorts to a "refined" path, where the bounds on the first few layers are computed using the (exact) MILP encoding, with a time-out, reporting the best bounds that can be obtained.
-In our algorithm, this is pushed to all layers, which is possible in our case as we select only a limited number of important ReLU nodes to encode as binary variables, while this would be infeasible without the selection based on the compensating pairs.
-The refined version is particularly efficient on small networks, but as the network grows, the more work BaB needs to do and faces the same wall, and our algorithm becomes more accurate.
-
 Concerning PRIMA, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do).
@@
 
-Finally, algoirthms resorting to absraction on the network (e.g.
-Reluplex/Marabou \cite{Reluplex,Marabou}) rather than abstraction on the values are much more different.
+For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
+On simple networks, such as those trained robust, this is particularly efficient because branch and bound can find very efficiently the bounds focusing on the actual question, considering the important branchs, while our algorithm will be less efficient as it has to consider each nodes one by one from the start.
+However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider.
+
+On such complex DNN, PRIMA and $\alpha$-$\beta$ CROWN resorts to a "refined" path, where the bounds on the first few layers are refined using MILP on the exact encoding \cite{MILP2}.
+In our algorithm, we do not use an exact encoding but a partial one with the most important
+ReLU nodes obtained by considering the compensation strength. As it is much more efficient, 
+this can be pushed to all layers, while this would be infeasible without the selection based on the compensation.
+The refined version of $\alpha$-$\beta$ CROWN is particularly efficient on small  DNNs, but as the depth grows, the more work BaB needs to do and our algorithm
+is more accurate, lowering the gap of verified images to the upper bound down from $17.6\%$ to $12\%$.
+
+Finally, algorithms resorting to absraction on the network (e.g.
+Reluplex/ Marabou \cite{Reluplex,katz2019marabou}) rather than abstraction on the values are much more different.
 These algorithms have been developped to be complete, so much slower but also more accurate than what we propose.

### 2024-01-16 Paper/proof revison.tex
update proof

@@
 \newcommand{\ReLU}{\mathrm{ReLU}}
-\newcommand{\Val}{\mathrm{Value}}
+\newcommand{\Val}{\mathrm{value}}
 \newcommand{\UB}{\mathrm{UB}}
@@
 
+\section{Proof of Theorem 1}
+
+First of all, we recall some definitions.
+
 \begin{definition}
@@
 	is called {\em compensating} if they start in the same neuron $a$ and 
-	ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative.
+	ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative, and two paths do not have any common nodes rather than the start node and the end node.
+
+	We call the product of weights over a path the weight of that path.
 \end{definition}
 
-Intuitively, compensating paths will partially cancel out each other as they conribute the same weight $w(a)$ to the weight of the same neuron $w(z)$, but with opposite sign. 
-It is not simple to take this compensation into account because of ReLUs: the particular compensation will depend upon the weight of intermediate nodes seen along $\pi$ and $\pi'$, 
+Intuitively, compensating paths will partially cancel out each other as they contribute the same weight $w(a)$ to the weight of the same neuron $w(z)$, but with opposite sign. 
+It is not simple to take this compensation into account because of ReLU: the particular compensation will depend upon the weight of intermediate nodes seen along $\pi$ and $\pi'$, 
 as when one of this node gets negative input, it will clip it to 0.
@@
 	\begin{itemize}
-	 \item  We use $a_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the first hidden layer, etc and finally use $z_i$ to denote the output nodes.
-	For $L,L'$ consecutive layers, for $x \in L$ and $y \in L'$, we denote 
-	$w({x y})$ to denote the fixed weight from $x$ to $y$, while we use
-	$weight_Y(x)$ to denote the weights of node $x$ from initial configuration $Y$. 
-	We use $bias$ to denote bias weightt.
+		\item  We use $a_i,a_j\cdots$ to denote nodes in the input layer, use $b,c,b_i,b_j,\cdots$ to denote nodes in hidden layers, etc and finally use $z,z_i,\cdots$ and sometimes $c$ (if only 1 hidden layer) to denote the output nodes.
+We also use $n,m$ to denote general nodes (input, hidden, or output).
 
-	\item We use $b^-$ to denote the node before ReLU and $b^+$ to denote the node after ReLU: $b^+ = \ReLU(b^-)$.
+		\item For $L,L'$ consecutive layers, for $x \in L$ and $y \in L'$, we denote 
+		$W_{xy}$ to denote the fixed weight from $x$ to $y$.
+
+		\item  We use
+		$\Val_{\boldsymbol{x}}(z)$ to denote the weights of node $x$ from initial configuration vector $\boldsymbol{x}$.
+In the context, if we do not need to consider the input $\boldsymbol{x}$, we will omit it and write as $\Val(z)$.
+		We use $bias$ to denote bias.
+
+		\item We use $b$ to denote the node before ReLU and $\hat{b}$ to denote the node after ReLU: $\hat{b} = \ReLU(b)$.
 	\end{itemize}
@@
 
-\section{Theorem 1}
-
 \begin{theorem}
@@
 	in the network from $x$ to $y$, then the LP approximation is 
-	$100\%$ accurate (or deepoly with the abstraction $\underline{f}(x) = 0$ for the lower bound, never using the $\underline{f}(x) = x$ abstraction). 
+	$100\%$ accurate for approximation method as accurate as Interval Arithmetic (or DeepPoly with the abstraction $\underline{f}(x) = 0$ for the lower bound, never using the $\underline{f}(x) = x$ abstraction).
 \end{theorem}
 
-\subsection*{Proof of Theorem \ref{th1}}
-
-First, notice that if $weight_Y(b^-)$ is maximal (resp. minimal), 
-then $weight_Y(b^+=\ReLU(b^-))$ also gets maximal (resp. minimal).
+First, notice that if $\Val_{\boldsymbol{x}}(b)$ is maximal (resp. minimal), 
+then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).
 The following definition is the most important concept in this proof.
@@
 	We define a sign function $S$ on nodes $n$ such that: 	(1).
-$S(n)=0$ if all path from $n$ to $c$ has 0 weight; (2).
-$S(n)=1$ if all path from $n$ to $c$ has non-negative weight, and at least one path has a positive weight; (3).
-$S(n)=-1$ if all path from $n$ to $c$ has non-positive weight, and at least one path has a negative weight.
+$S(n)=0$ if all path from $n$ to $z$ has 0 weight; (2).
+$S(n)=1$ if all path from $n$ to $z$ has non-negative weight, and at least one path has a positive weight; (3).
+$S(n)=-1$ if all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight.
 	In general, $S$ may not be defined on every node (e.g.
 if there is a negative and a positive path from $a$ to $c$).
-However, if there is no Diamond, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
+However, if there is no compensating pair, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
 
@@
       \item  $S(a_i)=0$ if 
-	  for all $b_j, w(a_i b_j)\cdot w(b_j c) = 0$
+	  for all $b_j, W_{a_i b_j}\cdot W_{b_j c} = 0$
 
-	 \item  $S(a_i)=1$ if for all $b_j, w(a_i b_j)\cdot w(b_j c) \geq 0$ and there exists 
-	 $j, w(a_i b_j)\cdot w(b_j c) > 0$
+	 \item  $S(a_i)=1$ if for all $b_j, W_{a_i b_j}\cdot W_{b_j c} \geq 0$ and there exists 
+	 $j, W_{a_i b_j}\cdot W_{b_j c} > 0$
 
-	\item $S(a_i)=-1$ if for all $b_j\ w(a_i b_j)\cdot w(b_j c) \leq 0$ and there exists 
-	$j, w(a_i b_j)\cdot w(b_j c) < 0$ 
+	\item $S(a_i)=-1$ if for all $b_j\ W_{a_i b_j}\cdot W_{b_j c} \leq 0$ and there exists 
+	$j, W_{a_i b_j}\cdot W_{b_j c} < 0$ 
 \end{enumerate}
 
-For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $w(b_j c)$ is positive, negative, or 0 respectively. Finally, for the output node $c$, we define $S(c)=1$.
+For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $W_{b_j c}$ is positive, negative, or 0 respectively. Finally, for the output node $z$, we define $S(z)=1$.
 \end{definition}
@@
 	\label{lemma1}
-Let $L,L'$  are consecutive layers be of a DNN without compensation. 
+Let $L,L'$  are consecutive layers be of a DNN without compensation, and $m\in L$ $n\in L'$. 
 Then if both 
 $w(m n) \neq 0$ and $S(n) \neq 0$, then 
-	$S(m)=S(n)\mathrm{Sign}(w(n m))$.
+	$S(m)=S(n)\mathrm{Sign}(W_{n m}))$.
 \end{lemma}
@@
 \begin{proof}
-	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $c$ with a nonzero weight of the same sign as $S(n)$.
+	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $z$ with a nonzero weight of the same sign as $S(n)$.
 
-	Hence there is a non zero path from $m$ to $c$: $(m n) \pi$, which is of sign 
-	$S(n)\mathrm{Sign}(w(mn))$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(w(mn))$.
+	Hence there is a non zero path from $m$ to $z$: $(m n) \pi$, which is of sign 
+	$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
 \end{proof}
@@
 	Then:
-		$$ \max(n^-_s)=\sum_{m \in L}w(m n) \max(m^+_s)+bias_n \text{ and }$$
-		$$\max(n^+_s)=ReLU(\sum_{m \in L}w(m n) max(m^+_s)+bias_n)$$
+		$$ \max(n_s)=\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n \text{ and }$$
+		$$\max(\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n)$$
 
-	Similarly  for minimal value,	
-	$ \min(n^-_s)=\sum_{m \in L}w(m n)\min(m^+_s)+bias_n $ and
-	$ \min(n^+_s)=ReLU(\sum_{m \in L}w(m n)\min(m^+_s)+bias_n)$
+	Similarly for minimal value.
+
+%	for minimal value,	
+%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
+%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
 \end{lemma}
@@
 \begin{proof}
-We choose $\bar{Y}$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
-	that is setting $a$ as $max(a)$ for $S(a)=1$ and $min(a)$ for $S(a)=-1$.
-At configuration $\bar{Y}$, every $a_s(\bar{Y}))=\max_Y {a_s(Y))}=max(a_s)$ is maximized.
+We choose $\boldsymbol{x}^*$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
+	that is setting the value for node $a$ be $\max(a)$ for $S(a)=1$ and $\min(a)$ for $S(a)=-1$.
+At configuration $\boldsymbol{x}^*$, every $a_s(\boldsymbol{x}^*))=\max_{\boldsymbol{x}} {a_s(\boldsymbol{x}))}=\max(a_s)$ is maximized.
 
@@
 Assume first that $S(b)=+1$.
-We have $weight(b_s)= weight(b) = \sum_{a \in L_0} w(a b) weight(a) + bias_b$.
-If every $w(a b) weight(a)$ is maximized in the same time, 
-then $weight(b_s)= weight(b)$ is also maximized.
+We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
+If every $W_{ab} \Val(a)$ is maximized in the same time, 
+then $\Val(b_s)= \Val(b)$ is also maximized.
 
 We claim that this is the case at 
-configuration $\bar{Y}$.
-Indeed, if $w(a b)=0$, any $weight(a)$ can be chosen to maximize 
-$w(a b) weight(a)$. If $w(a b)>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
-$S(b)=+1$. We have $max(a_s) = max(a)$, maximizing $w(a b) weight(a)$.
-Finally, if $w(a b)<0$ then $S(a_s) = -1$, and we have 
-$max(a_s) = -min(a)$, maximizing $w(a b) weight(a)$.
+configuration $\boldsymbol{x}^*$.
+Indeed, if $W_{ab}=0$, any $\Val(a)$ can be chosen to maximize 
+$W_{ab}\Val(a)$. If $W_{ab}>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
+$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $W_{ab}\Val(a)$.
+Finally, if $W_{a b}<0$ then $S(a_s) = -1$, and we have 
+$\max(a_s) = min(a)$, maximizing $W_{ab}\Val(a)$.
 
-Hence $b$ reaches is maximum in configuration $\bar{Y}$, and the value satisfies: 
-$$\max(b)=\sum_{m \in L}w(a b) \max(a_s)+bias_b$$
+Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
+$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$
 
-The case $S(b)=-1$ is symetric:
+The case $S(b)=-1$ is symmetric:
 $\max(b_s)= -\min(b)$ is reached when minimizing $b$, which is also 
-satisfied at $\bar{Y}$.
-In both case, $weight(b_s)$ is maximized at $\bar{Y}$. Notice that $\bar{Y}$ does not depend upon $b$, so choosing $\bar{Y}$ uniformly maximize all $weight(b_s)$.
+satisfied at $\boldsymbol{x}^*$.
+In both case, $\Val(b_s)$ is maximized at $\boldsymbol{x}^*$. Notice that $\boldsymbol{x}^*$ does not depend upon $b$, so choosing $\boldsymbol{x}^*$ uniformly maximize all $\Val(b_s)$.
 
-This implies that $ReLU(b^-_s)$ is maximized at $\bar{Y}$, and its value is 
-$ReLU(\sum_{m \in L}w(a b) \max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\bar{Y}$.
+This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
+$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
 
 We proceed by induction over every layer of the DNN till the output layer, proving that 
-$max(z_s)=max(z)$ is reached at configuration $\bar{Y}$.
+$\max(z_s)=\max(z)$ is reached at configuration $\boldsymbol{x}^*$.
 
-The case for $min(x_s)$ is similar, reached at configuration $\underline{Y}$.
+The case for $\min$ is similar, with another input vector $\boldsymbol{x}^\#$ instead of $\boldsymbol{x}^*$.
 \end{proof}
@@
 	\label{cor1}
-	$$\max(n^-)=\sum_{m \in L, w(m n)>0}w(m n) \max(m^+) + \sum_{m \in L, w(m n)<0}w(m n) \min(m^+) + bias_n$$
-	$$\min(n^-)=\sum_{m \in L, w(m n)>0}w(m n) \min(m^+) + \sum_{m \in L, w(m n)<0}w(m n) \max(m^+) + bias_n$$
+	$$\max(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \max(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \min(\hat{m}) + bias_n$$
+	$$\min(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \min(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \max(\hat{m}) + bias_n$$
 \end{corollary}
@@
 In both case, these two bounds are found in Lemma \ref{lemma2},
-from configuration $\bar{Y}$ and $\underline{Y}$.
-We now show that DeepPoly will generate the same bounds 
+from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\#$.
+
+Once we have above corollary, things become very clear and simple. We now show that approximations like DeepPoly will generate the same bounds 
 $\underline{f}(x)=\min(x)$ and $\bar{f}(x)=\max(x)$.
@@
 	The Box absraction computes its upper bound using:
-	$$\bar{f}(n^-)= \sum_{w(mn)>0} w(mn) \bar{f}(m^+) + \sum_{w(mn)<0} w(mn) \underline{f}(m^+) + bias_n$$
+	$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + bias_n$$
 
 	By induction hypothesis, we have 
-	$\bar{f}(m^+)=max(m^+)$ and
-	$\underline{f}(m^+)=min(m^+)$, thus 
+	$\bar{f}(\hat{m})=\max(\hat{m})$ and
+	$\underline{f}(\hat{m})=\min(\hat{m})$, thus 
 	applying Corollary \ref{cor1}, we obtain
-	$\bar{f}(n^-)=max(n^-)$ and 
-	$\underline{f}(n^-)=min(n^-)$.
+	$\bar{f}(n)=\max(n)$ and 
+	$\underline{f}(n)=\min(n)$.
 
-	Now, if $\underline{f}(n^-)=min(n^-)<0$, 
-	then $\underline{f}(n^+)=min(n^+)=0$, 
+	Now, if $\underline{f}(n)=\min(n)<0$, 
+	then $\underline{f}(\hat{n})=\min(\hat{n})=0$, 
 	and otherwise 
-	$\underline{f}(n^+)=min(n^+)=\underline{f}(n^-)=min(n^-)$.
+	$\underline{f}(\hat{n})=\min(\hat{n})=\underline{f}(n)=\min(n)$.
 
 	Similarly, 
-	if $\bar{f}(n^-)=max(n^-)<0$, 
-	then $\bar{f}(n^+)=max(n^+)=0$, 
+	if $\bar{f}(n)=\max(n)<0$, 
+	then $\bar{f}(\hat{n})=\max(\hat{n})=0$, 
 	and otherwise 
-	$\bar{f}(n^+)=max(n^+)=\bar{f}(n^-)=bar(n^-)$.
+	$\bar{f}(\hat{n})=\max(\hat{n})=\bar{f}(n)=\max(n)$.
 

### 2024-01-16 Paper/proof revison.tex
update proof

@@
 
-	Suppose we have a DNN with $\ReLU$ as the unique activation functions. We consider compensating pairs in between any two nodes (i.d., the source node or target node can in hidden layers.)
+	Suppose we have a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$.
+We consider compensating pairs in between any two nodes (i.d., the source node or target node can in hidden layers.)
 
 	Using MILP method, if every nodes $b$ in any compensating pair
-	$(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
+	$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
 	bounds computed by MILP are the exact max and min value of $z$.
@@
 \begin{lemma} \label{lem:open_node_2}
-	A node $b$ in the hidden layer will not be on a weak compensating pair iff one of the following two happens:
+	A node $b$ in the hidden layer will not be on a weak compensating pair if and only if one of the following two happens:
 	\begin{enumerate}
@@
 \begin{proof}
-	First, we show that if either one of case 1,2 happens, then $b$ will not be on a weak compensating pair.
+	First, we show that if one of case 1, 2 happens, then $b$ will not be on a weak compensating pair.
 If 1), it is obvious.
@@
 \begin{lemma}
-	If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$, then $W_{bc}S(c)=S(b)$.
+	If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$ and $S(c)\neq 0$, then $W_{bc}S(c)=S(b)$.
 \end{lemma}
@@
 \begin{proof}
-	This is because if there exists nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ but this means so does $c$, a contradiction.
+	This is because if there exists nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ not in $J$ but this means so does $c$, a contradiction.
 Therefore any $b$ such that $W_{bc}\neq 0$ is also in above set.
@@
 
-By definition, we can easily see that, for any $b\in N_J$, either $b\in B_O$, or $b$ is a constant node.
+By definition, for any $b\in N_J$, either $b\in B_O$, or $b$ is a constant node.
 
 We denote $\boldsymbol{x}_S$ for any subset $S\subseteq K$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
-We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
+We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $\Val(z)=\Val_{\boldsymbol{x}_K}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
 We can see that for a node $b$ that $S$ is not defined on it, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ becomes a constant.

### 2024-01-16 Paper/proof revison.tex

@@
 In the context, if we do not need to consider the input $\boldsymbol{x}$, we will omit it and write as $\Val(z)$.
-		We use $bias$ to denote bias.
+		We use $\boldsymbol{x}_J$ to denote bias.
 
@@
 	Then:
-		$$ \max(n_s)=\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n \text{ and }$$
-		$$\max(\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n)$$
+	$$ \max(n_s)=\sum_{m \in L}W_{m n} \max(\hat{m}_s)+\boldsymbol{b}_n \text{ and }$$
+	$$\max(\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} \max(\hat{m}_s)+\boldsymbol{b}_n)$$
 
@@
 	%	for minimal value,	
-%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
-%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
+	%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+\boldsymbol{b}_n $ and
+		%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+\boldsymbol{b}_n)$
 	\end{lemma}
@@
 		Assume first that $S(b)=+1$.
-We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
+		We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + \boldsymbol{b}_b$.
 		If every $W_{ab} \Val(a)$ is maximized in the same time, 
@@
 		Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
-$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$
+		$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+\boldsymbol{b}_b$$
 
@@
 		This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
-$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
+		$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+\boldsymbol{b}_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
 
@@
 		\label{cor1}
-	$$\max(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \max(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \min(\hat{m}) + bias_n$$
-	$$\min(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \min(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \max(\hat{m}) + bias_n$$
+		$$\max(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \max(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \min(\hat{m}) + \boldsymbol{b}_n$$
+		$$\min(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \min(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \max(\hat{m}) + \boldsymbol{b}_n$$
 	\end{corollary}
@@
 		The Box absraction computes its upper bound using:
-	$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + bias_n$$
+		$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + \boldsymbol{b}_n$$
 
@@
 		%	Now, for any fixed input $\boldsymbol{x}^0_J$, we can regard $weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
-%	as bias.
+		%	as \boldsymbol{b}.
 In the simplified $D'$, there is no compensating path because of the definition of $I$.
@@
 		%	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
-%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
+		%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including \boldsymbol{b} and $\boldsymbol{x}^0_J$.
+Applying Lemma \ref{lemma1}, we obtain the statement.
 		%\end{proof}
@@
 		%
-%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
+		%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the \boldsymbol{b}). 
 		%Denote by $B_O$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
@@
 
-	1. $\UB(b)=\max_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$.
+				1. $\UB(c)=\max_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$.
 
-		2. $\LB(b)=\min_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$. 
+				2. $\LB(c)=\min_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$. 
 			\end{lemma}
@@
 			We want to show that $\mathrm{UB}(z) = \max \Val (z)$ and $\mathrm{LB}(z) = \min \Val(z)$ for the unique output nodes and we will prove this for all $c\notin B_{zero}$ .
-As the MILP abstraction is a sound overapproximation,
+As the MILP abstraction is a sound over-approximation,
 			it suffices to show that $\mathrm{UB}\leq \max \Val(c)$ and $\mathrm{LB} \geq \min \Val(c)$.
@@
 				1.
-for any fixed $\boldsymbol{x}^0_J$ and for $\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
+for any fixed $\boldsymbol{x}^0_J$ and for $\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number when $\boldsymbol{x}_I,\boldsymbol{x}_J=\boldsymbol{x}^*_I,\boldsymbol{x}^0_J$.
+Therefore naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
 The same is true for $\boldsymbol{x}^\#_I$.
@@
 				2.
-for any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$,  $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$.
-The similar for $S(c)=-1$, $\langle \LB,\min\rangle$, $x^\#_I$: we can change two of them at the same time.
+For any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$,  $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$.
+Similar results are true: the sign of $S(c)$, consider $\LB$ and $\min$, using $x_I^\#$, if we change two among them at the same time, then the conclusion still holds.
 
@@
 				If $b\in B_{pure}$, the term is $W_{bc}\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined.
+Consider the second case.
 
 				We know then by induction hypothesis part 1, 2 and 3,  we have the value of $b$ in the model is fixed (part 1), and it is equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ (by part 2, depending on $S(b)$).
-Since $b$ only depends on $I$, this value also equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$, and therefor equal to $\UB(b)$ or $\LB(b)$.
+Since $b$ only depends on $I$, this value also equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$, and therefore equal to $\UB(b)$ or $\LB(b)$.
 For either of them, $\mathrm{AppB}$ will be fixed value.
@@
 
-	Therefore, in the MILP model, $c$ is a sum of terms that are all fixed numbers. Hence $c$ is a fixed number.
+				Therefore, in the MILP model, $c$ is a sum of fixed numbers. Hence $c$ is a fixed number.
 
@@
 				\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$.
-Now by induction hypothesis part 2, combining with $S(b)$ and both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
+Now by induction hypothesis part 2, combining with $S(b)$ and the fact that both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
 					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
@@
 				The second is simply because $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.	The third equal is proved in last subsection, Lemma \ref{lem:reach_max_2}.
-$S(c)=-1$ is similar.
-So we have proved part 2.
+$S(c)=-1$ and/or $x^\#_I$ is similar.
+This is for part 2.
 

### 2024-01-16 Paper/Paper_noProof.tex
data
sketch of proof

@@
 \newcommand{\vz}{\boldsymbol{z}}
-\newcommand{\vb}{\boldsymbol{b}}
+\newcommand{\vb}{\boldsymbol{bias}}
 \newcommand{\val}{{\textrm{value}}}
+\newcommand{\Val}{{\textrm{value}}}
 \newcommand{\MILP}{{\textrm{MILP}}}
 \newcommand{\LP}{{\textrm{LP}}}
+
+\newcommand{\UB}{\mathrm{UB}}
+\newcommand{\LB}{\mathrm{LB}}
+\newcommand{\ub}{\mathrm{ub}}
+\newcommand{\lb}{\mathrm{lb}}
+\newcommand{\B}{\mathrm{B}}
 
@@
 $\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
-and $\ell$ bias vectors $\boldsymbol{b}^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
+and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
 We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
@@
 \begin{align*}
-	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \boldsymbol{b}^i\\
+	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \vb^i\\
 	\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
@@
 $\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, 
-the bias is a vector $\boldsymbol{b}^i$ in $\mathbb{R}^{d_i}$, and the activation function 
+the bias is a vector $\vb^i$ in $\mathbb{R}^{d_i}$, and the activation function 
 is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, 
@@
 \begin{align*}
-	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \boldsymbol{b}^i\\
+	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \vb^i\\
 	\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)).
@@
 $\beta \cdot a = \beta \frac{y - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
-\qed
+\hfill $\square$
 \end{proof}
@@
 
-The proof can be found in Section \ref{sec.proofs}.
+The sketch of proof can be found in Section \ref{sec.proofs}. 
 Notice that standard {\em DeepPoly} does not satisfies the following theorem (it does not necessarily refine {\em Box}), and therefore we are not sure PRIMA or $\beta$-CROWN who refine DeepPoly do, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
@@
 
-Similarly, the proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs}.
+The sketch of proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs}.
 
@@
 
-Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes, and one can maximize/minimize independently the different input nodes in order to optimize any desired node.
-
-\input{proofs}
+Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
+Consider a target neuron $z$.
+In case there is no compensating path, we can assign a sign to each neuron $n$: 0
+if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
+$-1$ if they have negative weights. Then we prove:
+
+\begin{proposition}
+	\label{prop.sign}
+There exists two inputs $\vx^\star,\vx^\sharp$ such that:
+\begin{enumerate} 
+	\item ${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons.
+	\item ${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
+\end{enumerate}
+\end{proposition}
+
+Hence $\val_{\vx^\star}(z)=\beta$ and Hence $\val_{\vx^\sharp}(z)=\alpha$,
+for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.
+
+\smallskip
+
+Concerning the Theorem \ref{th2}, consider an output node $z$.
+Let $[\alpha(z),\beta(z)]$ be the bound computed by $\MILP_{X_z}$.
+We will show the existence of $\vx^\sharp,\vx^\star$
+such that $\val_{\vx^\sharp}(z)=\alpha$ and $\val_{\vx^\star}(z)=\beta$,
+and we will get the proof of Theorem 2 by a continuity argument.
+For that, we partition the input neurons from layer $0$ into four groups:
+\begin{enumerate}
+	\item $A_{zero}$ is the set of input neurones from where all paths with target $z$ have weight $0$.
+	\item $A_{pos}$ is the set of input neurons from where all paths with target $z$ have weight $\geq 0$.
+	\item $A_{neg}$ is the set of input neurons from where all paths with target $z$ have weight $\leq 0$.
+	\item $A_{open}$ is the set of remaining input neurons.
+\end{enumerate}
+
+We define $A_{pure}=A_{pos} \cup A_{neg}$.
+We then partition the set of neurons in hidden layers: 
+\begin{enumerate}
+	\item $B_{zero}$ is the set of neurones from where all paths with target $z$ have weight $0$.
+	\item $B_{open}$ is the set of neurones reachable from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
+	\item $B_{pure}$ is the set of remaining neurons.
+\end{enumerate}
+
+Notice that the value of any node $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
+nodes in $A_{pure}$ or $B_{pure}$. 
+We can define the sign function for these neurons.
+Therefore, applying Prop. \ref{prop.sign}, we obtain 
+$\vx_{pure}^\star,\vx_{pure}^\sharp$ optimizing neurons in $A_{pure}$ or $B_{pure}$.
+Now, assume that $\MILP_{X_z}$ computes bounds $[\alpha,\beta]$ for $z$.
+We prove that there exists input 
+$\vx^\star$ extending $\vx_{pure}^\star$
+and input $\vx_{pure}^\sharp$ extending $\vx_{pure}^\sharp$
+from $A_{pure}$ to $A_{pure} \cup A_{open}$ such that 
+$\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$.
+
+The formal proofs are in appendix.
 
@@
 
-	Constant $\boldsymbol{W}, \boldsymbol{b}$ \tcp*{Weights and Bias of network}
+	Constant $\boldsymbol{W}, \vb$ \tcp*{Weights and Bias of network}
 
@@
 
-			$\mathcal{D}$, $\boldsymbol{W}, \boldsymbol{b}$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
+			$\mathcal{D}$, $\boldsymbol{W}, \vb$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
 			\tcp*{Do linear transformation  from input to the first layer}
@@
 
-				$\mathcal{B}$, $\boldsymbol{W}, \boldsymbol{b}$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
+				$\mathcal{B}$, $\boldsymbol{W}, \vb$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
 
@@
 
-		$6\times500$\  &   $26\%$ & $35\%$ & $41\%$ & $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
-
-		$\epsilon = 0.035$ & 34s & 121s & 18.4s & 576s & 925s &\\ \hline
+		$6\times500$\  &   $26\%$ & $32.5\%$ & $41\%$ & $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
+
+		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 576s & 925s &\\ \hline
 	\end{tabular}
@@
 \appendix
+
+\input{proofs}
+
+\end{document}
 

### 2024-01-16 Paper/proofs.tex
update proof
sketch of proof

--- 2024-01-16 Paper/proof revison.tex
@@
-\documentclass[]{article}
-\usepackage{amsmath, amsthm, amssymb, amsfonts}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newcommand{\ReLU}{\mathrm{ReLU}}
-\newcommand{\Val}{\mathrm{value}}
-\newcommand{\UB}{\mathrm{UB}}
-\newcommand{\LB}{\mathrm{LB}}
-\newcommand{\ub}{\mathrm{ub}}
-\newcommand{\lb}{\mathrm{lb}}
-\newcommand{\B}{\mathrm{B}}
+	\section{Proof of Theorem \ref{th1}}
 
-\title{Proof No Diamond (3 layers)}
-\date{}
-
-\begin{document}
-
-\section{Proof of Theorem 1}
-
-First of all, we recall some definitions.
-
-\begin{definition}
-	A pair of paths $(\pi,\pi')$
-	is called {\em compensating} if they start in the same neuron $a$ and 
-	ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative, and two paths do not have any common nodes rather than the start node and the end node.
-
-	We call the product of weights over a path the weight of that path.
-\end{definition}
-
-Intuitively, compensating paths will partially cancel out each other as they contribute the same weight $w(a)$ to the weight of the same neuron $w(z)$, but with opposite sign. 
-It is not simple to take this compensation into account because of ReLU: the particular compensation will depend upon the weight of intermediate nodes seen along $\pi$ and $\pi'$, 
-as when one of this node gets negative input, it will clip it to 0.
-
-We assume all active functions are ReLU function.
-
-\begin{definition}
-
-	\begin{itemize}
-		\item  We use $a_i,a_j\cdots$ to denote nodes in the input layer, use $b,c,b_i,b_j,\cdots$ to denote nodes in hidden layers, etc and finally use $z,z_i,\cdots$ and sometimes $c$ (if only 1 hidden layer) to denote the output nodes.
-We also use $n,m$ to denote general nodes (input, hidden, or output).
-
-		\item For $L,L'$ consecutive layers, for $x \in L$ and $y \in L'$, we denote 
-		$W_{xy}$ to denote the fixed weight from $x$ to $y$.
-
-		\item  We use
-		$\Val_{\boldsymbol{x}}(z)$ to denote the weights of node $x$ from initial configuration vector $\boldsymbol{x}$.
-In the context, if we do not need to consider the input $\boldsymbol{x}$, we will omit it and write as $\Val(z)$.
-		We use $bias$ to denote bias.
-
-		\item We use $b$ to denote the node before ReLU and $\hat{b}$ to denote the node after ReLU: $\hat{b} = \ReLU(b)$.
-	\end{itemize}
-
-	%	3. $\bar{f}$ is the upper bound approximation function of DeepPoly, and $\underline{f}$ is the lower bound approximation function.
-\end{definition}
-
-\begin{theorem}
-	\label{th1}
-	If for all $(x,y)$ there is no compensation paths $(\pi,\pi')$ 
-	in the network from $x$ to $y$, then the LP approximation is 
-	$100\%$ accurate for approximation method as accurate as Interval Arithmetic (or DeepPoly with the abstraction $\underline{f}(x) = 0$ for the lower bound, never using the $\underline{f}(x) = x$ abstraction).
-\end{theorem}
-
-First, notice that if $\Val_{\boldsymbol{x}}(b)$ is maximal (resp. minimal), 
+	First, notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
 	then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).
@@
 	\begin{definition}[Sign of Node]\label{sign_of_nodes}
-	We define a sign function $S$ on nodes $n$ such that: 	(1).
-$S(n)=0$ if all path from $n$ to $z$ has 0 weight; (2).
-$S(n)=1$ if all path from $n$ to $z$ has non-negative weight, and at least one path has a positive weight; (3).
-$S(n)=-1$ if all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight.
+		We define the partial sign function $S$ on neurons $n$: 	
+		\begin{enumerate}
+			 \item $S(n)=0$ if all path from $n$ to $z$ have 0 weight; 
+			 \item $S(n)=1$ if all path from $n$ to $z$ hafe non-negative weight, and at least one path has a positive weight; 
+			 \item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
+		\end{enumerate}
+	\end{definition}
+
 	In general, $S$ may not be defined on every node (e.g.
@@
 However, if there is no compensating pair, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
-
 		For instance, for an input node $a_i$ of any 3 layer DNN:
@@
 	For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $W_{b_j c}$ is positive, negative, or 0 respectively. Finally, for the output node $z$, we define $S(z)=1$.
-\end{definition}
 
@@
 		\label{lemma1}
-Let $L,L'$  are consecutive layers be of a DNN without compensation, and $m\in L$ $n\in L'$. 
-Then if both 
+		Let $L,L'$  consecutive layers of a DNN without compensation, 
+		and $m\in L$ $n\in L'$. Then if both 
 		$w(m n) \neq 0$ and $S(n) \neq 0$, then 
-	$S(m)=S(n)\mathrm{Sign}(W_{n m}))$.
+		$S(m)=S(n)\mathrm{Sign}(W_{n m})$.
 	\end{lemma}
@@
 		$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
+		\hfill $\square$
 	\end{proof}
@@
 		Then:
-		$$ \max(n_s)=\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n \text{ and }$$
-		$$\max(\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n)$$
+		$$ S(n) \max(S(n) n)=\sum_{m \in L}W_{m n} S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
+		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} S(n)\max(S(n)\hat{m}_s)+bias_n)$$
 
@@
 
-Consider any $b$ in the next layer $L_1$.
+			Consider any $b$ in the first hidden layer $L_1$.
 			Assume first that $S(b)=+1$.
@@
 			The case for $\min$ is similar, with another input vector $\boldsymbol{x}^\#$ instead of $\boldsymbol{x}^*$.
+			\hfill $\square$
 		\end{proof}
@@
 			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
-%Denote by $B_O$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
-%$b \notin B_{pure}$. %For any subdomain $D \subseteq B_O$, 
+			%Denote by $B_{open}$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
+			%$b \notin B_{pure}$. %For any subdomain $D \subseteq B_{open}$, 
 			%Let $\boldsymbol{x}^0_J$ and $\boldsymbol{x}^0_I$ be fixed inputs, and consider the associated upper bound 
@@
 			%\begin{align*}
-%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 			%\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
@@
 			%\begin{align*}
-%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
+			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
 			%	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
@@
 
-\section{Proof of Theorem 2}
+				\section{Proof of Theorem \ref{th2}}
 
@@
 
-	We denote $B_O$ the set of all nodes $b$ in a compensating path.
+					We denote $B_{open}$ the set of all nodes $b$ in a compensating path.
 				\end{lemma}
@@
 
-By definition, for any $b\in N_J$, either $b\in B_O$, or $b$ is a constant node.
+				By definition, for any $b\in N_J$, either $b\in B_{open}$, or $b$ is a constant node.
 
@@
 				%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
-%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
+					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
 					%		 + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
@@
 				%	
-%	But since $c\in B_{pure}$, for any $b\in B_O$, we must have $w_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $w_{bc}=0$. Therefore, we will have:
+				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $w_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $w_{bc}=0$. Therefore, we will have:
 				%	
@@
 
-	If $b\in B_O$, the term is $W_{bc}\ReLU(b)$. We know then by induction hypothesis, the value for $b$ in MILP is a fixed value. Then the term $W_{bc}\ReLU(b)$ is also a fixed number.
+					If $b\in B_{open}$, the term is $W_{bc}\ReLU(b)$. We know then by induction hypothesis, the value for $b$ in MILP is a fixed value. Then the term $W_{bc}\ReLU(b)$ is also a fixed number.
 
@@
 					(2) If $S(c)=1$, then we have the following:	\begin{align*}
-		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
+						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
 					\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$.
@@
 						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-	&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+						&constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
 						= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
@@
 				%	\begin{align*}
-%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 					%	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
@@
 				%	We can simplify above equation to \begin{align*}
-%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
+					%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
 					%	\end{align*}
@@
 					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-%		 &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+					%		 &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
 					%		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
@@
 					%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
-%	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
-%	= &B_c + \sum_{b\in B_O\cap l_i} w_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
+					%	= &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
+					%	= &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
 					%	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).
@@
 This is what we want to show, and the same result holds for lower bound and minimal value.
-
-\end{document}

### 2024-01-16 Paper/proofs.tex
update proof

@@
 	then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).
+
+	For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network, we write $\max(n),\min(n)$ directly, instead of $\max(\Val(n))$, $\min(\Val(n))$ or $\max_{\vx}(\Val_{\vx}(n)),\min_{\vx}(\Val_{\vx}(n))$.
+
 	The following definition is the most important concept in this proof.
@@
 	while for $S(n)=-1$, $n_s$ gets maximal value whenever $n$ gets minimal value (and vice versa). For $S(n)=0$, $n_s=0$ and thus always reach his minimal and maximal.
+
+	Using the concept of sign, now we introduce the key lemma for our theorem.
+
+	\begin{lemma}\label{lem:key1}
+
+		Let $\vx^{*}$ be the input vector that for every node $a_i$, if $S(a_i)=1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=-1$, then $x_{a_i}$ is the minimal value of $a_i$ ($S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
+
+		Then the input $\vx^*$ maximize all nodes $n$ that $S(n)=1$ and minimize all nodes $n$ that $S(n)=1$.
+	\end{lemma}
+
+	\begin{proof}
+		We prove this lemma by induction.
+For input layer, this is true by definition.
+Suppose this lemma is true up to layer $L_i$, we need to show this for layer $L_{i+1}$.
+Let $c$ be a node in layer $L_{i+1}$, then by definition, we have the following equation: \begin{align*}
+			c = \boldsymbol{bias}_c+\sum_{b\in L}W_{bc}\ReLU(b).
+		\end{align*}
+
+		Therefore we have the following inequalities:\begin{align*}
+				\max(\Val(c))\leq\sum_{b \in L_i, W_{bc n}>0}W_{bc} \max(\Val(\hat{b})) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\Val(\hat{b})) + \boldsymbol{bisa}_c\\
+			\min(\Val(c))\geq\sum_{b \in L_i, W_{bc n}>0}W_{bc} \min(\Val(\hat{b})) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\Val(\hat{b})) + \boldsymbol{bisa}_c
+		\end{align*}
+
+		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $W_{bc}>0$; if $S(b)=-1$, then $W{bc}<0$; if $S(b)=0$, then $W_{bc}=0$.
+
+		Combining with
+
+	\end{proof}
 
@@
 				\begin{definition}
-					Let $K$ be the set of  all input nodes $a_k$. 
-					We define a decomposition $K=I\sqcup J$ as follows:  
+					We define a decomposition of the input nodes set to be $A_{pure}\sqcup A_{open}$ as follows:  
 					\begin{itemize}
-						\item $a_k \in I$  if
+						\item $a_k \in A_{pure}$  if
 						\begin{enumerate}
@@
 							\item every path from $a_k$ to $z$ has weight $\leq 0$.
+
 						\end{enumerate}
-						That is, $a_k$ is not a source of a weak compensating pair.
-						\item $a_k \in J$ if $a_k \notin I$, that is there exists two paths $\pi,\pi'$ from $k$, 
-						one with positive and one with negative weight.
+						That is, $a_k$ is not a source of a weak compensating pair. 	We write $A_{pure}$ by $I$ for short.
+						\item $a_k \in A_{open}$ if $a_k \notin A_{pure}$, that is there exists two paths $\pi,\pi'$ from $k$, 
+						one with positive and one with negative weight. 	We write $A_{open}$ by $J$ for short.
 					\end{itemize}

### 2024-01-16 Paper/Paper_noProof.tex
spellchecking

@@
 \begin{abstract}
-  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formaly  that they are correct, with an annual competition to compare them, etc.
+	Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally that they are correct, with an annual competition to compare them, etc.
 Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
@@
 
-  In this paper, we analyze efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programing, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
+	In this paper, we analyse efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
 Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other.
@@
 
-Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
+%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
 Consider a target neuron $z$.
@@
 	\label{prop.sign}
-There exists two inputs $\vx^\star,\vx^\sharp$ such that:
+There exist two inputs $\vx^\star,\vx^\sharp$ such that ${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  ${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
+\end{proposition}
+
+Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
+for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.
+
+\smallskip
+
+Concerning Theorem \ref{th2}, consider an output node $z$.
+Let $[\alpha(z),\beta(z)]$ be the bound computed by $\MILP_{X_z}$.
+%We will show the existence of $\vx^\sharp,\vx^\star$
+%such that $\val_{\vx^\sharp}(z)=\alpha$ and $\val_{\vx^\star}(z)=\beta$,
+%and we will get the proof of Theorem 2 by a continuity argument.
+%For that, 
+We partition the input neurons from layer $0$ into:
 \begin{enumerate}
-	\item ${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons.
-	\item ${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
-\end{enumerate}
-\end{proposition}
-
-Hence $\val_{\vx^\star}(z)=\beta$ and Hence $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.
-
-\smallskip
-
-Concerning the Theorem \ref{th2}, consider an output node $z$.
-Let $[\alpha(z),\beta(z)]$ be the bound computed by $\MILP_{X_z}$.
-We will show the existence of $\vx^\sharp,\vx^\star$
-such that $\val_{\vx^\sharp}(z)=\alpha$ and $\val_{\vx^\star}(z)=\beta$,
-and we will get the proof of Theorem 2 by a continuity argument.
-For that, we partition the input neurons from layer $0$ into four groups:
-\begin{enumerate}
-	\item $A_{zero}$ is the set of input neurones from where all paths with target $z$ have weight $0$.
-	\item $A_{pos}$ is the set of input neurons from where all paths with target $z$ have weight $\geq 0$.
-	\item $A_{neg}$ is the set of input neurons from where all paths with target $z$ have weight $\leq 0$.
+	\item $A_{zero}= \{a \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)=0\}$.
+	\item $A_{pos}= \{a \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)\geq0\}$.
+	\item  $A_{neg}= \{a \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)\leq0\}$.
+	Let $A_{pure}=A_{pos} \cup A_{neg}$.
 	\item $A_{open}$ is the set of remaining input neurons.
@@
 
-We define $A_{pure}=A_{pos} \cup A_{neg}$.
 We then partition the set of neurons in hidden layers: 
 \begin{enumerate}
-	\item $B_{zero}$ is the set of neurones from where all paths with target $z$ have weight $0$.
+	\item $B_{zero}= \{n \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)=0\}$.
 	\item $B_{open}$ is the set of neurones reachable from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
@@
 
-Notice that the value of any node $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
-nodes in $A_{pure}$ or $B_{pure}$. 
-We can define the sign function for these neurons.
-Therefore, applying Prop. \ref{prop.sign}, we obtain 
+We can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
+Further, the value of any neuron $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
+nodes in $A_{pure}$ or $B_{pure}$. Therefore, applying Prop. \ref{prop.sign} on the DNN
+made of nodes from $A_{pure}$ and $B_{pure}$, we obtain 
 $\vx_{pure}^\star,\vx_{pure}^\sharp$ optimizing neurons in $A_{pure}$ or $B_{pure}$.
-Now, assume that $\MILP_{X_z}$ computes bounds $[\alpha,\beta]$ for $z$.
-We prove that there exists input 
+We can prove that there exists input 
 $\vx^\star$ extending $\vx_{pure}^\star$
@@
 from $A_{pure}$ to $A_{pure} \cup A_{open}$ such that 
-$\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$.
+$\val_{\vx^\star}(z)=\beta(z)$ and $\val_{\vx^\sharp}(z)=\alpha(z)$.
 
@@
 
-\begin{algorithm}[t!]
+\begin{algorithm}[b!]
 	\caption{Compensate(K)}
@@
 Hence, for $K$ small enough, Algorithm \ref{algo1} calls many times MILP (e.g. Gurobi)
-with a limited number of integer variables, which should be efficient enough, and yet be quite accurate as it can compute exactly (Theorem \ref{th2}) the highest compensating path, which we will verify in the experimental section.
+with a limited number of integer variables, which should be efficient enough, and yet be quite accurate as it can compute exactly (Theorem \ref{th2}) the highest compensating path, which we verify in the next section.
 
@@
 \begin{enumerate}
-  \item Evaluate experimentally how accurate is $\MILP_Z$ when using compensating strength 
- to choose the set $Z$ of ReLU nodes encoded exactly using an integer variable, compared with randomly chosing the set $Z$, to make sure the choice is relevant.
-Also compare different choices for $K$ the size of $Z$ and how to rank nodes from different layers,
+  \item Evaluate experimentally how the choice of the set $Z$ impacts the accuracy of $\MILP_Z$, and compare different choices for $K$ the size of $Z$,
   \item Evaluate on benchmarks the percentage of certification that can be obtained
@@
 \subsection{Setting}
-All the benchmarks were run on an AMD 5975WX ($32$ cores$@3.6$GHz, 7nm, year 2022) with 256 GB of main memory and 2 NVIDIA RTX 3090 (year 2022).
+The benchmarks were run on an AMD 5975WX ($32$ cores$@3.6$GHz, 7nm, year 2022) with 256 GB of main memory and 2 NVIDIA RTX 3090.
 Gurobi 9.52 was used for solving MILP and LP problems.
@@
 
-The DNN certification for local robustness were run, using DNNs trained for the MNIST image dataset as its the only standard DNNs (MLP $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers).
+The local robustness verification is performed on DNNs trained for the MNIST image dataset as its the only standard DNNs (MLP $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers).
 Indeed, today's efficient methods leave at least $14\%$ to $20\%$ of the images neither certified robust nor with an attack to robustness found, making them interesting DNNs to consider where to improve accuracy of efficient techniques.
@@
 We experiment with the smallest network (MLP $6\times 100$), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
-We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first layer and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
+We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
 
@@
 
-We first experiment with the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer.  Let $c$ be a node of the second layer.
-A compensating pair $(\pi,\pi')$ of paths with target $n$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
-The compensating strength for $(b,b')$ is defined as
-$comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$. Indeed, 
-the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),weight(a,b',c))$, and $b,b'$ would help compensated set set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
-After selecting the heaviest $(b_0,b_0')$, we can then compute $comp(b)= \sum_{b' \text{already selected}} comp(b,b')+comp(b',b)$ and select iteratively the heaviest $b$'s one by one till reaching the threshold.
-We do this for all node $c$ of the second layer.
-
-We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
-The range of uncertainty created by inacurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
-Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
-We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
-
-\begin{table}[t!]
+\begin{table}[b!]
 	\centering
@@
 \end{table}
+
+We first experiment with the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer.  Let $c$ be a node of the second layer.
+A compensating pair $(\pi,\pi')$ of paths with target $c$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
+The compensating strength for $(b,b')$ is defined as $comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$.
+Indeed, the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),weight(a,b',c))$, and $b,b'$ would help compensated set set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
+After selecting the heaviest $(b_0,b_0')$, we can then compute $comp(b)= \sum_{b' \text{already selected}} comp(b,b')+comp(b',b)$ and select iteratively the heaviest $b$'s one by one till reaching the threshold.
+%We do this for all node $c$ of the second layer.
+
+We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
+The range of uncertainty created by inacurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
+Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
+We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
 
@@
 	Notice that on these MLP networks, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
-This is doable on the first few layers as the number of integer variable is limited (but stil consequent).
+This is doable on the first few layers as the number of integer variable is not too large.
 By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
@@
 
-More importantly, $\beta$-Crown, while efficient, often faces a (complexity) wall, when there number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long time out (the reason why Refined BaB is more accurate on these networks).
+More importantly, $\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long time out (the reason why {\em refined} BaB is more accurate on these networks).
 We verify that on a larger DNN learnt in a natural way, namely MLP $6 \times 500$, see Table \ref{tab:example3}.
@@
 
-\begin{table}[b!]
+\begin{table}[t!]
 	\centering
@@
 		Comp(adapt.) & Upper\\ 
-		 & / CROWN &  & TO=30s & TO=1200s & fast & Bound\\
+		 & / CROWN & (refined) & TO=30s & TO=1200s & fast & Bound\\
 		\hline \hline
@@
 	\label{tab:example3}
-	\vspace{-0.8cm}
+	\vspace{-1cm}
 \end{table}
 
-Last, we report the average runetime per number of nodes of both fast adaptive and of fast fixed compensation, for the different DNNs we considered.
-The time per node is not constant, but it is still controlled and does not show an exponential behavior (from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN).
-This indicates that Compensate($K$) can be run for larger DNN.
-While the time to verify images will be longer, it won't hit a wall as BaB does on DNNs hard to verify.
-
-\begin{figure}[t!]
+\vspace{-0.4cm}
+\begin{figure}[h!]
 \centering
-\includegraphics[scale=0.8]{Graph.png}
+\includegraphics[scale=0.7]{Graph.png}
 \end{figure}
+\vspace{-0.4cm}
+
+Last, we report the average runetime per number of nodes of both fast adaptive and fast fixed compensation, for the different DNNs considered.
+The time per node is not constant, but it is still controlled and does not show an exponential blow-up, from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN.
+This indicates that Compensate($K$) can be run on larger DNN without hitting the same complexity wall as for BaB.
 
@@
 For DNNs easy to verify, $\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images.
-Compensation strength is not required in these contexts, and likely not useful, reason why we did not considered it.
+Compensation strength is not required in these contexts, and likely not useful, reason why we did not consider it.
 
@@
 Still, the compensation paradigm is totally orthogonal to ReLU activation function.
-It is very likely that studying the compensation strengh would be useful in this other context.
+It is very likely that studying the compensation strength would be useful in this  context as well.
 We leave that for future work.
@@
 There are many optimizations possible.
-The simplest is to run $\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\beta$-CROWN cannot conclude.
+The simplest is to run $\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\beta$-CROWN cannot conclude, possibly using more core to compute more nodes in parallel.
 Another simple way is to modify the refined BaB of $\beta$-CROWN to run compensate($K$) on more layers than what exact MILP can be run, and finish the study using BaB.
@@
 
-On the correlation between neurons, which PRIMA encodes explicitely, our results tend to show that it is more efficient to use the compensation strength.
+On the correlation between neurons, which PRIMA encodes explicitly, our results tend to show that it is more efficient to use the compensation strength to abstract the network.
 Still, considering ReLU nodes exactly tends to be very accurate locally, but less when the source of correlation is many layers away.
@@
 
-In this paper, we presented the notion of compensating pairs of paths, with rationale why such a phenomenon creates inacuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entierely the inacuracies, as in their absence, even very simple arithmetic algebra suffices to verify accurately DNNs.
+In this paper, we presented the notion of compensating pairs of paths, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
+We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even very simple arithmetic algebra suffices to verify accurately DNNs.
 We verified that DNNs harder to verify indeed exhibits more paths with larger compensating strength.
-
 Based on this idea of compensating path, we proposed a novel efficient algorithm considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if all the compensating paths are covered.
-We experimentally tested that chosing $Z$ covering the paths with the strongest compensation result to very good accuracy, and runtime which can be favorable in some (but not all) cases.
+We experimentally tested that choosing $Z$ covering the paths with the strongest compensation result to very good accuracy, and runtime which can be favourable in some (but not all) cases.
 This proves that compensating strength is a promising novel concept which should be further studied to 

### 2024-01-16 Paper/introduction.tex
spellchecking

@@
 In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers.
-This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations
-\cite{szegedy}\dots
+This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rationale: it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{szegedy}\dots
 
@@
 For that to happen at a large scale, hard guarantees should be provided, so that to avoid dramatic consequences.
-It is the reason for the developpement of (hard) verification tools since 2016, with now many tools with different trade-offs from exact computation but slow (e.g.
+It is the reason for the development of (hard) verification tools since 2016, with now many tools with different trade-offs from exact computation but slow (e.g.
 Marabou \cite{katz2019marabou}/Reluplex\cite{Reluplex}), up to very efficient but also incomplete (e.g.
@@
 To benchmark these tools, a competition has been run since 2019, namely VNNcomp.
-The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
+The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
 \cite{cutting}.
@@
 ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input to check local robustness) \cite{crown}, with all inputs either certified robust or an attack on robustness is found in the neighbourhood;
-some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analyzed fully, with $\approx 20 \%$ of inputs where neither of the decisions can be reached \cite{crown}.
-The main difference between these DNNs with very different behaviors lies in that the DNNs which are trained to be robust are much easier to verify, while the DNNs trained in a "natural" way are much harder to verify.
+some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $\approx 20 \%$ of inputs where neither of the decisions can be reached \cite{crown}.
+The main difference between these DNNs with very different behaviours lies in that the DNNs which are trained to be robust are much easier to verify, while the DNNs trained in a "natural" way are much harder to verify.
 
 In this paper, we focus on uncovering what makes the DNNs trained in a natural way so hard to verify (because for "easier" DNNs, adequate methods already exist).
-To do so, we analyze the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly, the Linear Programming approximation, PRIMA, and different versions of ($\alpha$)($\beta$)-CROWN.
+To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly, the Linear Programming approximation, PRIMA, and different versions of ($\alpha$)($\beta$)-CROWN.
 All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds.
-For instance, if for all image $I'$ in the neighborhood of image $I$, we have $weight_{I'}(n'-n) < 0$ for $n$ the output neuron corresponding to the expected class, then we know that the DNN is robust in the neighborhood of image $I$.
+For instance, if for all image $I'$ in the neighbourhood of image $I$, we have $weight_{I'}(n'-n) < 0$ for $n$ the output neuron corresponding to the expected class, then we know that the DNN is robust in the neighbourhood of image $I$.
 We restrict the formal study to DNNs using only the standard ReLU activation function, although nothing specific prevents the results to be extended to more general architectures.
-We uncover that {\em compensations} (see next paragraph) is the phenomenon creating  inacurracy.
+We uncover that {\em compensations} (see next paragraph) is the phenomenon creating inaccuracies.
 We verified experimentally that indeed DNNs trained in a natural way have much more heavy compensating pairs than DNNs trained in a robust way.
 
-Formally, a compensating pair is a pair of paths $(\pi,\pi')$ between a pair of neurons 
-$(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
+Formally, a compensating pair is a pair of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
 Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
 That is, it is loaded by $(w+w') weight(a)$.
-As $w,w'$ have oppositve sign, they will compensate (partly) each other.
+As $w,w'$ have opposite sign, they will compensate (partly) each other.
 The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
@@
 
-Our first main contribution is to formally show, in Theorem \ref{th1}, that compensation is the sole reason for the inacuraccy as (most) efficient algorithms will compute exact bounds for all neurons if there is no compensating pair of paths at all.
+Our first main contribution is to formally show, in Theorem \ref{th1}, that compensation is the sole reason for the inaccuracies as (most) efficient algorithms will compute exact bounds for all neurons if there is no compensating pair of paths at all.
 While this theorem is theoretically interesting, it is not usable in practice as (almost) all networks have some compensating pairs.
@@
 
-Our third main contribution is more practical, proposing Algorithm \ref{algo1} based on this knowledge that compensating pair of paths are the reason for inacurracy.
+Our third main contribution is more practical, proposing Algorithm \ref{algo1} based on this knowledge that compensating pair of paths are the reason for inaccuracy.
 The idea is thus to use this information to rank the ReLU nodes in terms of importance, and only keep the most important ones as binary variables, and use linear relaxation for the least important ones.
-%More precisely, the algorithm will, as DeepPoly, consider layers one by one and neurons $b$ %on this layer one by one, selecting the most heavy pairs of compensating path ending in $b$
+%More precisely, the algorithm will, as DeepPoly, consider layers one by one and neurons $b$ %on this layer one by one, selecting the heaviest pairs of compensating paths ending in $b$
 %and associating these nodes with a binary variable. Then an MILP tool such as Gurobi is used %to compute the lower and upper bound for node $b$. 
@@
 An additional interesting point is that it is extremely easy to parallelize, as all the nodes in the same layer can be run in parallel.
-We verify experimentally that the algorithm offers interesting trade offs, by testing on local robustness for DNNs trained "naturally" 
-(and thus difficult to verify).
+We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
 
-This paper does not focuss on producing the most efficient tool, and we did not spend engeenierial effort to optimize it.
+This paper does not focus on producing the most efficient tool, and we did not spend engineering efforts to optimize it.
 The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.
 For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in $\beta$-CROWN).
-Still, evaluation of the methodology versus even the most efficient tools reveal a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification.
+Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification.
 
@@
 \noindent {\bf Comparison with related work:} Here, we will compare with some (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
-Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on some ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inacurracy.
+Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on some ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inaccuracy.
 If the ReLU nodes to abstract are chosen accurately, the result should be more accurate than early stopping the MILP algorithm using all the nodes.
@@
 
-Compared with ERAN-Deeppoly \cite{deeppoly}, which compute bounds on the value in a very efficient way, we prove that the LP encoding is strictly more accurate, which as far as we know is a another novel result.
+Compared with ERAN-Deeppoly \cite{deeppoly}, which compute bounds on the value in a very efficient way, we prove that the LP encoding is strictly more accurate, which as far as we know is another novel result.
 To be more precise, DeepPoly
-abstract the weight of every node using two functions, one upper functions and one lower function. While the upper funciton is fixed, there are 2 choices for the lower bound.
+abstract the weight of every node using two functions, one upper function and one lower function. While the upper function is fixed, there are 2 choices for the lower bound.
 We prove in Proposition  \ref{LP} that the LP relaxation corresponds exactly to the intersection of both choices.
@@
 We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurones.
-Our method is more accurate locally, but we will tend to loose precision for  dependencies created many layers ago.
+Our method is more accurate locally, but we will tend to lose precision for dependencies created many layers ago.
 Experimental results tend to show that most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago).
-Also, the dependencies between nodes limit the paralelism, unlike in our method, which explains why we obtain both faster and more accurate results than PRIMA.
+Also, the dependencies between nodes limit the parallelism, unlike in our method, which explains why we obtain both faster and more accurate results than PRIMA.
 
-For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
-On simple networks, such as those trained robust, this is particularly efficient because branch and bound can find very efficiently the bounds focusing on the actual question, considering the important branchs, while our algorithm will be less efficient as it has to consider each nodes one by one from the start.
+For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaB \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
+On simple networks, such as those trained robust, this is particularly efficient because branch and bound can find very efficiently the bounds focusing on the actual question, considering the important branches, while our algorithm will be less efficient as it has to consider each node one by one from the start.
 However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider.
@@
 
-Finally, algorithms resorting to absraction on the network (e.g.
-Reluplex/ Marabou \cite{Reluplex,katz2019marabou}) rather than abstraction on the values are much more different.
-These algorithms have been developped to be complete, so much slower but also more accurate than what we propose.
+Finally, algorithms resorting to abstractions on the network (e.g.
+Reluplex / Marabou \cite{Reluplex,katz2019marabou}) rather than abstraction on the values are very different.
+These algorithms have been developed to be complete, so much slower but also more accurate than what we propose.

### 2024-01-17 Paper/proofs.tex
update

@@
 
-	\begin{lemma}\label{lem:key1}
+	\begin{definition}[Star and Sharp]
+	\begin{enumerate}
+		\item  $\vx^{*}$ is a input vector that for every node $a_i$, if $S(a_i)=1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=-1$, then $x_{a_i}$ is the minimal value of $a_i$ (if $S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
 
-		Let $\vx^{*}$ be the input vector that for every node $a_i$, if $S(a_i)=1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=-1$, then $x_{a_i}$ is the minimal value of $a_i$ ($S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
+		\item  $\vx^{\sharp}$ is a input vector that for every node $a_i$, if $S(a_i)=-1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=1$, then $x_{a_i}$ is the minimal value of $a_i$ (if $S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
+	\end{enumerate}
 
-		Then the input $\vx^*$ maximize all nodes $n$ that $S(n)=1$ and minimize all nodes $n$ that $S(n)=1$.
+	\end{definition}
+
+	\begin{lemma}\label{lem:key1}\label{lemma2}
+
+		The input $\vx^*$ maximize all nodes $n$ that $S(n)=1$ and minimize all nodes $n$ that $S(n)=-1$.
+
+		Similarly, the input $\vx^\sharp$ maximize all nodes $n$ that $S(n)=-1$ and minimize all nodes $n$ that $S(n)=1$.
 	\end{lemma}
@@
 	\begin{proof}
-		We prove this lemma by induction.
+		We prove this lemma by induction on layers.
 For input layer, this is true by definition.
@@
 		Therefore we have the following inequalities:\begin{align*}
-				\max(\Val(c))\leq\sum_{b \in L_i, W_{bc n}>0}W_{bc} \max(\Val(\hat{b})) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\Val(\hat{b})) + \boldsymbol{bisa}_c\\
-			\min(\Val(c))\geq\sum_{b \in L_i, W_{bc n}>0}W_{bc} \min(\Val(\hat{b})) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\Val(\hat{b})) + \boldsymbol{bisa}_c
+				\max(c)\leq\sum_{b \in L_i, W_{bc }>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
+			\min(c)\geq\sum_{b \in L_i, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bisa}_c
 		\end{align*}
 
-		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $W_{bc}>0$; if $S(b)=-1$, then $W{bc}<0$; if $S(b)=0$, then $W_{bc}=0$.
+		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $W_{bc}>0$; if $S(b)=-1$, then $W_{bc}<0$; if $S(b)=0$, then $W_{bc}=0$.
 
-		Combining with
+		By induction hypothesis, when input vector is $\vx^{*}$, for every $b$, if $S(b)=1$, then $\Val_{\vx}(b)=\max(b)$ and if $S(b)=-1$, then $\Val_{\vx}(b)=\min(b)$.
 
+		So combining formulas and above two facts, we will have that when the input vector is $\vx^*$, \begin{align*}
+			\max(c)&\geq\Val_{\vx^*}(c) \\
+			&= \sum_{b \in L_i, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
+			&\geq\max(c)
+		\end{align*}  Hence $\max(c)=\Val_{\vx^*}(c)$.
+
+		Similarly, we can prove if $S(c)=-1$, $\min(c)=\Val_{\vx^*}(c)$. And similarly, we can prove this for $x^\sharp$. This is the induction step. 
 	\end{proof}
 
-	\begin{lemma}
-		\label{lemma2}
-		Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
-		Then:
-		$$ S(n) \max(S(n) n)=\sum_{m \in L}W_{m n} S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
-		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} S(n)\max(S(n)\hat{m}_s)+bias_n)$$
+%	\begin{lemma}
+%		\label{lemma2}
+%		Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
+%		Then:
+%		$$ S(n) \max(S(n) n)=\sum_{m \in L}W_{m n} S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
+%		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} S(n)\max(S(n)\hat{m}_s)+bias_n)$$
+%		
+%		Similarly for minimal value.
+%		
+%		%	for minimal value,	
+%		%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
+%			%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
+%		\end{lemma}
+%		
+%		\begin{proof}
+%			We choose $\boldsymbol{x}^*$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
+%			that is setting the value for node $a$ be $\max(a)$ for $S(a)=1$ and $\min(a)$ for $S(a)=-1$.
+%			At configuration $\boldsymbol{x}^*$, every $a_s(\boldsymbol{x}^*))=\max_{\boldsymbol{x}} {a_s(\boldsymbol{x}))}=\max(a_s)$ is maximized.  
+%			
+%			Consider any $b$ in the first hidden layer $L_1$.
+%			Assume first that $S(b)=+1$.
+%			We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
+%			If every $W_{ab} \Val(a)$ is maximized in the same time, 
+%			then $\Val(b_s)= \Val(b)$ is also maximized. 
+%			
+%			We claim that this is the case at 
+%			configuration $\boldsymbol{x}^*$.
+%			Indeed, if $W_{ab}=0$, any $\Val(a)$ can be chosen to maximize 
+%			$W_{ab}\Val(a)$. If $W_{ab}>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
+%			$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $W_{ab}\Val(a)$.
+%			Finally, if $W_{a b}<0$ then $S(a_s) = -1$, and we have 
+%			$\max(a_s) = min(a)$, maximizing $W_{ab}\Val(a)$.
+%			
+%			Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
+%			$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$
+%			
+%			The case $S(b)=-1$ is symmetric:
+%			$\max(b_s)= -\min(b)$ is reached when minimizing $b$, which is also 
+%			satisfied at $\boldsymbol{x}^*$.
+%			In both case, $\Val(b_s)$ is maximized at $\boldsymbol{x}^*$. Notice that $\boldsymbol{x}^*$ does not depend upon $b$, so choosing $\boldsymbol{x}^*$ uniformly maximize all $\Val(b_s)$.
+%			
+%			This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
+%			$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
+%			
+%			We proceed by induction over every layer of the DNN till the output layer, proving that 
+%			$\max(z_s)=\max(z)$ is reached at configuration $\boldsymbol{x}^*$.
+%			
+%			The case for $\min$ is similar, with another input vector $\boldsymbol{x}^\sharp$ instead of $\boldsymbol{x}^*$.
+%			\hfill $\square$
+%		\end{proof}
 
-		Similarly for minimal value.
-
-		%	for minimal value,	
-		%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
-			%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
-		\end{lemma}
-
-		\begin{proof}
-			We choose $\boldsymbol{x}^*$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
-			that is setting the value for node $a$ be $\max(a)$ for $S(a)=1$ and $\min(a)$ for $S(a)=-1$.
-			At configuration $\boldsymbol{x}^*$, every $a_s(\boldsymbol{x}^*))=\max_{\boldsymbol{x}} {a_s(\boldsymbol{x}))}=\max(a_s)$ is maximized.
-
-			Consider any $b$ in the first hidden layer $L_1$.
-			Assume first that $S(b)=+1$.
-			We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
-			If every $W_{ab} \Val(a)$ is maximized in the same time, 
-			then $\Val(b_s)= \Val(b)$ is also maximized.
-
-			We claim that this is the case at 
-			configuration $\boldsymbol{x}^*$.
-			Indeed, if $W_{ab}=0$, any $\Val(a)$ can be chosen to maximize 
-			$W_{ab}\Val(a)$. If $W_{ab}>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
-			$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $W_{ab}\Val(a)$.
-			Finally, if $W_{a b}<0$ then $S(a_s) = -1$, and we have 
-			$\max(a_s) = min(a)$, maximizing $W_{ab}\Val(a)$.
-
-			Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
-			$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$
-
-			The case $S(b)=-1$ is symmetric:
-			$\max(b_s)= -\min(b)$ is reached when minimizing $b$, which is also 
-			satisfied at $\boldsymbol{x}^*$.
-			In both case, $\Val(b_s)$ is maximized at $\boldsymbol{x}^*$. Notice that $\boldsymbol{x}^*$ does not depend upon $b$, so choosing $\boldsymbol{x}^*$ uniformly maximize all $\Val(b_s)$.
-
-			This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
-			$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
-
-			We proceed by induction over every layer of the DNN till the output layer, proving that 
-			$\max(z_s)=\max(z)$ is reached at configuration $\boldsymbol{x}^*$.
-
-			The case for $\min$ is similar, with another input vector $\boldsymbol{x}^\#$ instead of $\boldsymbol{x}^*$.
-			\hfill $\square$
-		\end{proof}
-
-		As direct corollary of Lemma \ref{lemma2}, we obtain:
+		As direct corollary of Lemma \ref{lem:key1}, we obtain:
 
@@
 		In both case, these two bounds are found in Lemma \ref{lemma2},
-		from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\#$.
+		from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\sharp$.
 
@@
 				We define $\boldsymbol{x}_I^*$ to be the input vector such that for all $a_i \in I$, the value $x_{a_i}$ for $a_i$ gets its maximal value (if $S(a_i)=1$ or $0$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
-Similarly, we define $\boldsymbol{x}_I^\#$ to be the input vector such that for all $a_i \in I$, the value $x_{a_i}$ for $a_i$ gets its maximal value (if $S(a_i)=-1$ or $0$) or $a_i$ gets its minimal value (if $S(a_i)=1$).
+Similarly, we define $\boldsymbol{x}_I^\sharp$ to be the input vector such that for all $a_i \in I$, the value $x_{a_i}$ for $a_i$ gets its maximal value (if $S(a_i)=-1$ or $0$) or $a_i$ gets its minimal value (if $S(a_i)=1$).
 
@@
 
-					If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\#_I$. 
+					If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$. 
 				\end{lemma}
@@
 for any fixed $\boldsymbol{x}^0_J$ and for $\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
-The same is true for $\boldsymbol{x}^\#_I$.
+The same is true for $\boldsymbol{x}^\sharp_I$.
 
@@
 for any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$,  $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$.
-The similar for $S(c)=-1$, $\langle \LB,\min\rangle$, $x^\#_I$: we can change two of them at the same time.
+The similar for $S(c)=-1$, $\langle \LB,\min\rangle$, $x^\sharp_I$: we can change two of them at the same time.
 

### 2024-01-17 Paper/proofs.tex
update proof

@@
 	\begin{definition}[Star and Sharp]
-	\begin{enumerate}
+
+		\begin{itemize}
 			\item $\vx^{*}$ is a input vector that for every node $a_i$, if $S(a_i)=1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=-1$, then $x_{a_i}$ is the minimal value of $a_i$ (if $S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
@@
 			\item  $\vx^{\sharp}$ is a input vector that for every node $a_i$, if $S(a_i)=-1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=1$, then $x_{a_i}$ is the minimal value of $a_i$ (if $S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
-	\end{enumerate}
+		\end{itemize}
 
@@
 
-				In this section, we will try to prove theorem 2, that is
+				In this section, we will prove theorem \ref{th2}. We will prove that theorem by proving the following theorem:
 
 				\begin{theorem}
-					\label{no_diamond_3}
 
-					Suppose we have a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$.
-We consider compensating pairs in between any two nodes (i.d., the source node or target node can in hidden layers.)
+					Suppose $\mathcal{N}$ is a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$.
 
@@
 					$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
-					bounds computed by MILP are the exact max and min value of $z$.
+					bounds computed by MILP are the exact maximal and minimal value of $z$.
 				\end{theorem}
 
-				Before the proof of above theorem, we will try to weaker one, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes).
+				\subsection{Preparation}
+
+				Before the proof of above theorem, we will prove a weaker version, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes).
 We call such pair a weak compensating pair.
@@
 				\begin{definition}
-					We define a decomposition of the input nodes set to be $A_{pure}\sqcup A_{open}$ as follows:  
+					We define a decomposition of the input nodes set $A_{pure}\sqcup A_{open}$ as follows:  
 					\begin{itemize}
-						\item $a_k \in A_{pure}$  if
+						\item $a_k \in A_{pure}$  if either
 						\begin{enumerate}
@@
 						\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $w_{b,z}=0$ to denote this case, or
-						\item For every input node $a_j\in J$, for any path from $a_j$ to $b$ has a weight of $0$. We use $w_{a_j,b}=0$ to denote this case.
+						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $w_{a_j,b}=0$ to denote this case.
 					\end{enumerate}
-					We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.
 
-					We denote $B_{open}$ the set of all nodes $b$ in a compensating path.
 				\end{lemma}
+
+					We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.	We denote $B_{open}$ the set of all nodes $b$ in a compensating path.
 
@@
 				\begin{lemma}\label{lem:subnetwork}
-					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only replies on nodes in $B_{pure}\cup I$ in previous layers.
+					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
 We call this sub-network $N_I$.
@@
 
-				Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
+				Recall the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
 
@@
 					\begin{enumerate} 
-						\item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
-						\item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
-						\item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
+						\item if all paths from $n$ to $z$ have 0 weight, then $S(n)=0$; 
+						\item if all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, then $S(n)=1$; 
+						\item if all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, then $S(n)=-1$.
 						\item Otherwise $S(n)$ is undefined.
@@
 				Notice that $S$ is defined on all nodes $a_i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
-And similarly, for nodes in  $B_{zero}$, $S$ is defined.
-We introduce the following lemma:
+For the domain of $S$, we introduce the following lemma:
 
@@
 				\end{proof}
-				Therefore, for any node $b$  that $S$ is undefined on $b$, it only depends on the values on $J$.
+				Therefore, for any node $b$  that $S$ is undefined on $b$, it only depends on input nodes in $J$.
 
@@
 				\begin{lemma}\label{lem:subnetwork2}
-					The input set $J$ with nodes that only depending on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $N_J$.
+					The input set $J$ with nodes that only depends on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $N_J$.
 				\end{lemma}
@@
 
-				By definition, for any $b\in N_J$, either $b\in B_{open}$, or $b$ is a constant node.
+				By definition, for any $b\in N_J$, either $b\in B_{open}$, or $b$ is a constant node: to it, any path from any input node must have zero weight.
 
-				We denote $\boldsymbol{x}_S$ for any subset $S\subseteq K$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
-We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $\Val(z)=\Val_{\boldsymbol{x}_K}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
-We can see that for a node $b$ that $S$ is not defined on it, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ becomes a constant.
+				We denote $\boldsymbol{x}_S$ for any subset $S$ of input nodes to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
+We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and $\Val(z)=\Val_{\boldsymbol{x}}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
+For a node $b$ that $S$ is not defined on it, since $b$ only depends on $J$, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ will be fixed.
 
@@
 
-					Assume $b$ is the output node or a node in a hidden layer that $S(b)=1$. Then
+					Assume $b$ is the output node or a node in hidden layers that $S(b)=1$, then
 					$\max_{\boldsymbol{x}} (\Val_{\boldsymbol{x}}(b)) =\max_{\{\boldsymbol{x} \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (\Val_{\boldsymbol{x}}(b))$.

### 2024-01-17 Paper/proofs.tex
update proof

@@
 
-					2. if $b\in B_{O}$, then $w_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.
+					2. if $b\in B_{open}$, then $w_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.
 
@@
 
-					Assume $b$ is the output node or a node in hidden layers that $S(b)=1$, then
-					$\max_{\boldsymbol{x}} (\Val_{\boldsymbol{x}}(b)) =\max_{\{\boldsymbol{x} \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (\Val_{\boldsymbol{x}}(b))$.
-
-					Further,  for any valuation $\boldsymbol{x}^0_J$, 
-					we have $$\max_{\{\boldsymbol{x} \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (\Val_{\boldsymbol{x}}(b)) =  \Val_{\boldsymbol{x}^0_J,\boldsymbol{x}_I^*}(b).$$
+					Assume $b$ is the output node or a node in hidden layers that $S(b)=1$, then   for any valuation $\boldsymbol{x}^0_J$, 
+						we have: $$\max_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J=\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^*,\boldsymbol{x}^0_J}(b).$$
 
@@
 				\begin{proof}
-					For the first statement, we use 
-					$$\max_{\boldsymbol{x}_K} (\Val_{\boldsymbol{x}_K}(z)) =\max_{\boldsymbol{x}_J} \max_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$
 
-					Now, for any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
+					For any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
 					as bias.
 In the simplified $D'$, there is no compensating path because of the definition of $I$.
-Therefore we can apply Theorem \ref{th1} to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
+Therefore we can apply Theorem \ref{th1} to get that $\Val_{x_I,\boldsymbol{x}^0_J}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
 				\end{proof}
@@
 
-				Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
+				The standard MILP abstraction use the abstraction from \cite{MILP}, 
 				where each variable $\alpha_b$ for the ReLU from $b$ to $\hat{b}$ is:
 				\begin{itemize}
-					\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \notin B_{O}$
-					\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \in B_{O}$
+					\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \notin B_{open}$
+					\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \in B_{open}$
 				\end{itemize}
 
-				Now consider the MILP framework for all hidden and output nodes layer by layer (to compute their bounds, and use the bounds of previous layers to build the MILP models of current layer), with ReLUs being either linear or binary depending on whether $b \in B_{O}$ or not.
+				Now consider the MILP framework for all hidden and output nodes layer by layer (to compute their bounds, and use the bounds of previous layers to build the MILP models of current layer), with ReLUs being either linear or binary depending on whether $b \in B_{open}$ or not.
 We call this standard framework.
 
-				For a node $b$ in a hidden layer or the output layer, we denote by $\UB(b)$ the maximal bound on $b$ and $\LB(b)$ the minimal bound on $b$ considering the MILP constraints above.
+				For a node $b$ in a hidden layer or the output layer, we denote by $\UB(b)$ the upper bound on $b$ and $\LB(b)$ the lower bound on $b$ considering the MILP constraints above.
 
@@
 
-				We want to show that $\mathrm{UB}(z) = \max \Val (z)$ and $\mathrm{LB}(z) = \min \Val(z)$ for the unique output nodes and we will prove this for all $c\notin B_{zero}$ .
-As the MILP abstraction is a sound overapproximation,
-				it suffices to show that $\mathrm{UB}\leq \max \Val(c)$ and $\mathrm{LB} \geq \min \Val(c)$.
+				We want to show that $\mathrm{UB}(z) = \max (z)$ and $\mathrm{LB}(z) = \min (z)$ for the unique output nodes, and we will prove this for all $c\notin B_{zero}$ .
+As the MILP abstraction is a sound over-approximation,
+				it suffices to show that $\mathrm{UB}\leq \max (c)$ and $\mathrm{LB} \geq \min (c)$.
 We will prove this by induction on layers from the first hidden layer to the output layer.
@@
 				\begin{lemma}
-					For the $i$-th layer $l^i$ ($1$-th layer is the first hidden layer), for a node $c\in l^i$, if $c\notin B_{zero}$, then:
-
-					\vspace*{1ex}
-
-					1.
-for any fixed $\boldsymbol{x}^0_J$ and for $\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
+					For any node $c$ in a hidden layer or the output layer, if $c\notin B_{zero}$, then:		\begin{enumerate}
+						\item for any fixed $\boldsymbol{x}^0_J$, when  $\boldsymbol{x}_I=\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
 The same is true for $\boldsymbol{x}^\sharp_I$.
 
-					\vspace*{1ex}
+						\item for any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$, then $$\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c).$$ The similar for $S(c)=-1$, $\langle \LB,\min\rangle$, $x^\sharp_I$: we can change two of them at the same time.
 
-					2.
-for any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$,  $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$.
-The similar for $S(c)=-1$, $\langle \LB,\min\rangle$, $x^\sharp_I$: we can change two of them at the same time.
-
-					\vspace*{1ex}
-
-					3. Therefore, $\UB(c)=\max\Val(c)$ and $\LB(c)=\min\Val(c)$.
+						\item Therefore, $\UB(c)=\max(c)$ and $\LB(c)=\min(c)$.
+					\end{enumerate}
 
@@
 				\begin{proof}
-					We prove this lemma by induction on layers. For $l_1$, it is obvious. Suppose we have proved part 1,2,3 up to layer $l_i$, then for layer $l_{i+1}$, suppose $c$ is a node in this layer.
+					We prove this lemma by induction on layers.
+For first hidden layer $l_1$, it is obvious.
+Suppose we have proved part 1,2,3 up to layer $l_i$, then for layer $l_{i+1}$, suppose $c$ is a node in this layer.
 
-					(1)	First, if $S$ is undefined on $c$, then by previous discussion, $c$ is in a sub-network from $J$ with all nodes opened and if $\boldsymbol{x}_J=\boldsymbol{x}_J^0$ is fixed, then in the MILP model, the value for $c$ is also fixed.
+					(1)	If $S(c)$ is undefined, then by previous discussion, $c$ is in a sub-network from $J$ with all nodes opened; and if $\boldsymbol{x}_J=\boldsymbol{x}_J^0$ is fixed, then in the MILP model, the value for $c$ is also fixed.
+
 					If $S(c)$ is defined, then consider all $b$ such that $W_{bc}\neq 0$.
@@
 
-					If $b\in B_{pure}$, the term is $W_{bc}\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined.
+					If $b\in B_{pure}$, the term is $W_{bc}\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $S(b)$ is undefined and $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined.
 
-					We know then by induction hypothesis part 1, 2 and 3,  we have the value of $b$ in the model is fixed (part 1), and it is equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ (by part 2, depending on $S(b)$).
-Since $b$ only depends on $I$, this value also equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$, and therefor equal to $\UB(b)$ or $\LB(b)$.
-For either of them, $\mathrm{AppB}$ will be fixed value.
+					Then by induction hypothesis for all 1, 2 and 3 parts,  the value of $b$ in the model is fixed (part 1), and it is equal to $\max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$ or $\min_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$ (by part 2, depending on $S(b)$).
+Since $b$ only depends on $I$, this value also equal to $\max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I}(c)$ or $\min_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I}(c)$, and by induction hypothesis on part 3, equal to $\UB(b)$ or $\LB(b)$.
+For either of them, $\mathrm{AppB}(b)$ will be fixed value.
 Hence, in this case, the term $W_{bc}\mathrm{AppB}(b)$ is also a fixed number.

### 2024-01-17 Paper/proofs.tex
proof update

@@
 			%	\begin{enumerate}
-				%	 \item $w_{b,z}=0$, or
-				%	 \item For every input node $j\in J$, we have $w_{a_j,b}=0$.
+				%	 \item $W_{b,z}=0$, or
+				%	 \item For every input node $j\in J$, we have $W_{a_j,b}=0$.
 				%	\end{enumerate}
@@
 It means that $a \in J$.
-A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.
+A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.
 			%	
 			%	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
-			%	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
-			%	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
+			%	Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
+			%	Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
 			%	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
@@
 			%	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
-			%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
+			%	$$b= B^0 +\sum_{a_i\in I} W_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
 			%\end{proof}
@@
 			%
-			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
+			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}W_{b_ha_i}+B_h$ ($B_h$ is the bias). 
 			%Denote by $B_{open}$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
@@
 			%\begin{align*}
-			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 			%\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
-			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
-			%of its (LP) approximation if $w_{b,z}<0$. 
+			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $W_{b,z}>0$, and the lower bound
+			%of its (LP) approximation if $W_{b,z}<0$. 
 			%
-			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
+			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(W_{zb})=1$, then 
 			%$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
-			%and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
+			%and if $S(b)=\mathrm{sign}(W_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
 			%Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
@@
 			%\begin{align*}
-			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
-			%	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
+			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
+			%	\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
 			%\end{align*} 
@@
 			%Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
-			%$w_{b,z} = 0$ and $b \in B^2$ iff $w_{b,z} \neq 0$.
+			%$W_{b,z} = 0$ and $b \in B^2$ iff $W_{b,z} \neq 0$.
 			%Hence:
 			%
-			%$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-			%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
+			%$$\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
 			%
-			%For $b \in B^2$, we have $w_{a_j,b}=0$ for all $j \in J$
+			%For $b \in B^2$, we have $W_{a_j,b}=0$ for all $j \in J$
 			%by definition of $B_{pure}$ (Lemma 4.), hence
 			%
-			%$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-			%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
-			%=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
+			%$$\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
+			%=\sum_{b\in B^2} W_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
 			%$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
@@
 			%Hence we have: \begin{align*}
-				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
+				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}W_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
 				%	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
@@
 					\begin{enumerate}
-						\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $w_{b,z}=0$ to denote this case, or
-						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $w_{a_j,b}=0$ to denote this case.
+						\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
+						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
 					\end{enumerate}
@@
 It means that $a \in J$.
-A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.
+A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.
 
 					Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
-					Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
-					Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
+					Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
+					Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
 					Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
@@
 
-					1. if $b\in J$, by definition, $w_{bc}=0$.
+					1. if $b\in J$, by definition, $W_{bc}=0$.
 
-					2. if $b\in B_{open}$, then $w_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.
+					2. if $b\in B_{open}$, then $W_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.
 
-					3. if $b\in B_{zero}$, then $w_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
+					3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
 				\end{proof}
@@
 				%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
-					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
-					%		 + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
-					%		 +\sum_{b\in B_{zero}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
+					%		 + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
+					%		 +\sum_{b\in B_{zero}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 					%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
@@
 				%	
-				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $w_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $w_{bc}=0$. Therefore, we will have:
+				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $W_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $W_{bc}=0$. Therefore, we will have:
 				%	
 				%	\begin{align*}
-					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 					%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
@@
 				%	\begin{align*}
-					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
+					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
 					%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
@@
 
-				\begin{lemma}
+				\begin{lemma} \label{lem:main}
 					For any node $c$ in a hidden layer or the output layer, if $c\notin B_{zero}$, then:		\begin{enumerate}
@@
 						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
-					\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$.
-Now by induction hypothesis part 2, combining with $S(b)$ and both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
+					\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$.
+Notice that all $b$ displayed are that $S(b)$ defined, because if $S(b)$ undefined, then for fixed $\vx_J$, value of $b$ is fixed and will be put into the constant.
+
+					Now by induction hypothesis part 2, if $S(b)=1$, then $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\max_{\vx_I}\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$; and if $S(b)=-1$, $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\min_{\vx_I}\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
+Moreover, since $S(c)=1$, $S(b)$ and $W_{bc}$ have the same sign.
+And both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions.
+Combining all these facts, we have:\begin{align*}
 						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
@@
 					The second is simply because $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.	The third equal is proved in last subsection, Lemma \ref{lem:reach_max_2}.
-$S(c)=-1$ is similar.
-So we have proved part 2.
+The case $S(c)=-1$ is similar.
+This is for part 2.
 
-					(3) Once we have part 2, then we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$.
-Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$.
+					(3) Once we have part 2, we will have that for any fixed $\boldsymbol{x}^0_J$, $$\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c).$$ Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)$ and this is to say $\UB(c)=\max(c)$.
 This is what we want to show, and the same result holds for lower bound and minimal value.
 This is for part 3.
+\qed
 
 				\end{proof}
+
+				From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{th2}.
 
@@
 				%	\begin{align*}
-					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 					%	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
-$\B$ is one of $\UB,\LB$  that, if $w_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
+$\B$ is one of $\UB,\LB$  that, if $W_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
 				%	
 				%	We can simplify above equation to \begin{align*}
-					%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
+					%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
 					%	\end{align*}
@@
 					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-					%		 &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+					%		 &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
 					%		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
@@
 					%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
-					%	= &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} w_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
-					%	= &B_c + \sum_{b\in B_{open}\cap l_i} w_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} w_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
+					%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
+					%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
 					%	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).

### 2024-01-17 Paper/proofs.tex
update proof

@@
 			\label{cor1}
-			$$\max(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \max(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \min(\hat{m}) + bias_n$$
-			$$\min(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \min(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \max(\hat{m}) + bias_n$$
+			$$\max(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bias}_c$$
+			$$\min(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bias}_c$$
 		\end{corollary}
 
-		Notice that for all $x$, either $S(x)=+1$ and 
-		$(\min(x),\max(x))=(\min(x_s),\max(x_s))$, 
-		or $S(x)=-1$ and $(\min(x),\max(x))=(-\max(x_s),-\min(x_s))$.
-		In both case, these two bounds are found in Lemma \ref{lemma2},
+		Notice that for all $x$, for both $S(c)=1$ or $S(c)=-1$, these two bounds are found in Lemma \ref{lemma2},
 		from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\sharp$.
@@
 
-		\paragraph{DeepPoly bounds}
+		\paragraph{Approximation Bounds}
 
-		To prove that DeepPoly bounds are the same as the exact bounds computed above, 
+		To prove that Approximation Bounds are the same as the exact bounds computed above, 
 		we show that even the box abstraction (which is easier) would reach the exact bounds.
@@
 					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
-We call this sub-network $N_I$.
-In $N_I$, there is no compensating pair.
+We call this sub-network $D_I$.
+In $D_I$, there is no compensating pair.
 				\end{lemma}
@@
 				\begin{lemma}\label{lem:subnetwork2}
-					The input set $J$ with nodes that only depends on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $N_J$.
+					The input set $J$ with nodes that only depends on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $D_J$.
 				\end{lemma}
@@
 
-				By definition, for any $b\in N_J$, either $b\in B_{open}$, or $b$ is a constant node: to it, any path from any input node must have zero weight.
+				By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node: to it, any path from any input node must have zero weight.
 
@@
 In the simplified $D'$, there is no compensating path because of the definition of $I$.
-Therefore we can apply Theorem \ref{th1} to get that $\Val_{x_I,\boldsymbol{x}^0_J}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
+Therefore we can apply Lemma \ref{lem:key1} to get that $\Val_{x_I,\boldsymbol{x}^0_J}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
 				\end{proof}
@@
 				\begin{lemma}
-					In the standard framework, both $N_I$ and $N_J$ are accurate in the sense that for any $b$ in $N_I$ or $N_J$, $\UB(b)=\max\Val(b)$ and $\LB(b)=\min\Val(b)$.
+					In the standard framework, both $D_I$ and $D_J$ are accurate in the sense that for any $b$ in $D_I$ or $D_J$, $\UB(b)=\max\Val(b)$ and $\LB(b)=\min\Val(b)$.
 				\end{lemma}
@@
 				\begin{proof}
-					For $N_I$, it is because of no compensating as proved in the first section. For $N_J$, it is because all nodes are either opened or constants.
+					For $D_I$, it is because of no compensating as proved in the first section. For $D_J$, it is because all nodes are either opened or constants.
 				\end{proof}

### 2024-01-17 Paper/Paper_noProof.tex
update paper

--- 2024-01-16 Paper/Paper_noProof.tex
@@
 \begin{abstract}
-  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formaly  that they are correct, with an annual competition to compare them, etc.
+  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally  that they are correct, with an annual competition to compare them, etc.
 Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
@@
 
-  In this paper, we analyze efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programing, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
+  In this paper, we analyze efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
 Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other.
@@
 $x_i=[\alpha,\beta]$ with $\alpha < 0 < \beta$. 
-If $|\alpha|\geq |\beta|$ then $0$ is used, while if $|\beta|>|\alpha|$ then $x_i$ (the identity function) is used. Let us call $\overline{\mbox{DeepPoly}}$ the Deeppoly algorithm such that 
+If $|\alpha|\geq |\beta|$ then $0$ is used, while if $|\beta|>|\alpha|$ then $x_i$ (the identity function) is used. Let us call $\overline{\mbox{DeepPoly}}$ the DeepPoly algorithm such that 
 $f_i(x_i) = 0$ is always used, and $f_i(x_i) = x_i$ is never used. 
-It has a main advantage, as it subsmumes the box abstraction.
+It has a main advantage, as it subsumes the box abstraction.
 Indeed, taking an interval $x_i \in [-0.2,5]$, it gives $ReLU(x_i) \in [0,5]$, 
@@
 Solving LP instances being Polynomial time, much more efficient solution could be found, but at the price of a lack of accuracy (e.g.
-with not as thight bounds).
+with not as tight bounds).
 This is called the {\em LP abstraction}.
@@
 As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We prove now that the LP abstraction is strictly more accurate tha3 the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.
+We prove now that the LP abstraction is strictly more accurate that the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.
 
@@
 
-It remains to prove that the 2 upper bound contraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
+It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
 For that, we study the upper bound function in the variable $a \in  [0,1]$, with $y \in [\alpha,\beta]$ fixed.
@@
 As the weights of the paths is of opposite sign, some of these weights will cancel out, by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$.
-Further, no only do they cancel $min(|weight(\pi')|,|weight(\pi')|)$ out, but they also do not accumulate, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inacurate analysis.
+Further, no only do they cancel $min(|weight(\pi')|,|weight(\pi')|)$ out, but they also do not accumulate, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inaccurate analysis.
 The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function.
@@
 
-Hence, compensation is {\em one} factor of inacurracy. We prove now that it is actually the {\em only} reason for inacurracy, in the following meaning.
+Hence, compensation is {\em one} factor of inaccuracy. We prove now that it is actually the {\em only} reason for inaccuracy, in the following meaning.
 If there is no compensating path in the DNN, then any method/approximation at least as accurate as the {\em Box} abstraction, e.g.
@@
 Notice that standard {\em DeepPoly} does not satisfies the following theorem (it does not necessarily refine {\em Box}), and therefore we are not sure PRIMA or $\beta$-CROWN who refine DeepPoly do, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
-Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results showin that compensation is the reason for inacuracy.
+Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results show in that compensation is the reason for inaccuracy.
 
@@
 Hence $\val_{\vx^\star}(z)=\beta$ and Hence $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.
+for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invoking continuity.
 
@@
 \begin{enumerate}
-	\item $A_{zero}$ is the set of input neurones from where all paths with target $z$ have weight $0$.
+	\item $A_{zero}$ is the set of input neurons from where all paths with target $z$ have weight $0$.
 	\item $A_{pos}$ is the set of input neurons from where all paths with target $z$ have weight $\geq 0$.
@@
 In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this treshold are not compensating strongly enough to deserve an integer variable (there are cases where the MILP algorithm is exponential in the number of integer variables), calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
+Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this threshold are not compensating strongly enough to deserve an integer variable (there are cases where the MILP algorithm is exponential in the number of integer variables), calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
 In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small.
@@
   \item Evaluate experimentally how accurate is $\MILP_Z$ when using compensating strength 
- to choose the set $Z$ of ReLU nodes encoded exactly using an integer variable, compared with randomly chosing the set $Z$, to make sure the choice is relevant.
+ to choose the set $Z$ of ReLU nodes encoded exactly using an integer variable, compared with randomly choosing the set $Z$, to make sure the choice is relevant.
 Also compare different choices for $K$ the size of $Z$ and how to rank nodes from different layers,
@@
 
-\subsection{Chosing nodes based on Compensation strength}
-
-The first group of experiments we run, tests the accuracy of chosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly chosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-
-To mesure the accuracy, we measure the uncertainty of all nodes in a layer:
+\subsection{Choosing nodes based on Compensation strength}
+
+The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+
+To measure the accuracy, we measure the uncertainty of all nodes in a layer:
 the uncertainty of a node is the range between its computed lower and upper bound. 
-We then average the uncerainty among all the nodes of the layer.
+We then average the uncertainty among all the nodes of the layer.
 Formally, for a node $n$ with bounds $[\alpha,\beta]$, its uncertainty $unc(a) = \beta - \alpha$, and the average uncertainty of a layer $l$ is $\dfrac{\sum_{a\in l} unc(a)}{|l|}.$
@@
 We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
-The range of uncertainty created by inacurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
-Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
+The range of uncertainty created by inaccurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
+Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inaccuracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
 We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
@@
 
-We now turn to evaluating chosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the second layers, wrt ReLU nodes in the first and second layer.
+We now turn to evaluating choosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the second layers, wrt ReLU nodes in the first and second layer.
 The bounds for nodes of the second layers are computed exactly. 
@@
 Choosing ReLU nodes in the previous layer (layer $2$) only is never a good choice. 
-When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inacurate computations ($0.059$ vs $0.574$), while it only reduces the inacuracy by $65\%$ when choosing nodes randomly.
-Notice that this is direct inacuracy, applying this layer after layer will even further reduce inacuracy created by accumulation of inacuraccies.
-
-Notice that it is likely that selecting ReLU nodes up to 3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade off is unclear and we thus didnot experiment.
+When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inaccurate computations ($0.059$ vs $0.574$), while it only reduces the inaccuracy by $65\%$ when choosing nodes randomly.
+Notice that this is direct inaccuracy, applying this layer after layer will even further reduce inaccuracy created by accumulation of inaccuracies.
+
+Notice that it is likely that selecting ReLU nodes up to 3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade off is unclear and we thus did not experiment.
 
@@
 	Notice that on these MLP networks, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
-This is doable on the first few layers as the number of integer variable is limited (but stil consequent).
+This is doable on the first few layers as the number of integer variable is limited (but still consequent).
 By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
@@
 Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming \cite{BaB} on such DNNs, and heavily using GPU implementation (while we do not).
-Performance of pure BaB on these hard DNNs is however impaired by the large number of branchs to consider.
+Performance of pure BaB on these hard DNNs is however impaired by the large number of branches to consider.
 Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also parallelized with 16 nodes in parallel, before running their BaB tool.
@@
 This is particularly useful for deeper network where $N$ is very different between the first and the last layer.
-Again, we run first an aggressive version of fast, before going to a more concervative slow version to treat the remaining images.
+Again, we run first an aggressive version of fast, before going to a more conservative slow version to treat the remaining images.
 All versions compute bounds for 20 neurons of the same layer in parallel, no GPU used.
@@
 In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
-DeepPoly/CROWN is by far the fastest, but also the most inacurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
-This is because these DNNs, altough of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
-
-Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall method is quite similar, looking at all the nodes one by one from the begining of the network till the end.
+DeepPoly/CROWN is by far the fastest, but also the most inaccurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
+This is because these DNNs, although of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
+
+Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall method is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
 Our method compare favorably, both in terms of time and accuracy: our fastest setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except our fast adaptative method for $5 \times 200$ which is quite pointless on this shallow DNN - the fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
@@
 Things are more interesting on the accuracy front: on shallower DNNs ($5 \times 100$ and $5 \times 100$ with 5 hidden layers), the refinement with MILP treats all but the 2 last layers,
-leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accuate than using compensation: we are within $1.6\%$ of the accuracy.
+leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using compensation: we are within $1.6\%$ of the accuracy.
 On deeper DNNs ($8 \times 100$ and $8 \times 100$ with 8 hidden layers), the refinement with MILP cannot treat the 4 last layers, and BaB has more ReLU to branch on.
@@
 
-More importantly, $\beta$-Crown, while efficient, often faces a (complexity) wall, when there number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long time out (the reason why Refined BaB is more accurate on these networks).
+More importantly, $\beta$-Crown, while efficient, often faces a (complexity) wall, when there number of branches becomes too extreme for BaB to work: either BaB succeeds fast, or it will not succeed even with very long time out (the reason why Refined BaB is more accurate on these networks).
 We verify that on a larger DNN learnt in a natural way, namely MLP $6 \times 500$, see Table \ref{tab:example3}.
@@
 
-Last, we report the average runetime per number of nodes of both fast adaptive and of fast fixed compensation, for the different DNNs we considered.
+Last, we report the average runtime per number of nodes of both fast adaptive and of fast fixed compensation, for the different DNNs we considered.
 The time per node is not constant, but it is still controlled and does not show an exponential behavior (from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN).
@@
 Still, the compensation paradigm is totally orthogonal to ReLU activation function.
-It is very likely that studying the compensation strengh would be useful in this other context.
+It is very likely that studying the compensation strength would be useful in this other context.
 We leave that for future work.
@@
 
-On the correlation between neurons, which PRIMA encodes explicitely, our results tend to show that it is more efficient to use the compensation strength.
+On the correlation between neurons, which PRIMA encodes explicitly, our results tend to show that it is more efficient to use the compensation strength.
 Still, considering ReLU nodes exactly tends to be very accurate locally, but less when the source of correlation is many layers away.
@@
 
-In this paper, we presented the notion of compensating pairs of paths, with rationale why such a phenomenon creates inacuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entierely the inacuracies, as in their absence, even very simple arithmetic algebra suffices to verify accurately DNNs.
+In this paper, we presented the notion of compensating pairs of paths, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
+We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even very simple arithmetic algebra suffices to verify accurately DNNs.
 We verified that DNNs harder to verify indeed exhibits more paths with larger compensating strength.
@@
 Based on this idea of compensating path, we proposed a novel efficient algorithm considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if all the compensating paths are covered.
-We experimentally tested that chosing $Z$ covering the paths with the strongest compensation result to very good accuracy, and runtime which can be favorable in some (but not all) cases.
+We experimentally tested that choosing $Z$ covering the paths with the strongest compensation result to very good accuracy, and runtime which can be favorable in some (but not all) cases.
 This proves that compensating strength is a promising novel concept which should be further studied to 

### 2024-01-17 Paper/Paper_noProof.tex
update paper

@@
 Considering its iterated impact along the different layers of a ReLU DNN is much more complex that it seems.
-First, let us remark that it is easy to represent exactly $ReLU(x)$
+First, let us remark that it is easy to represent exactly $\ReLU(x)$
 in case $x$ is known to be entirely positive and in the case where it is entirely negative

### 2024-01-17 Paper/Paper_noProof.tex
typos

--- 2024-01-16 Paper/Paper_noProof.tex
@@
 \cite{prima,crown}, except for MLP $5\times 500$ which is not reported in \cite{prima,crown} and takes a large amount of time, for which we only test on the first 200 images.
-Each data example is associated with a $\varepsilon>0$ for the $L^\infty$ norm, and a target label for verification.
-
-\subsection{Chosing nodes based on Compensation strength}
-
-The first group of experiments we run, tests the accuracy of chosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly chosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
+%, and a target label for verification.
+
+\subsection{Choosing nodes based on Compensation strength}
+
+The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
 

### 2024-01-17 Paper/Paper_noProof.tex

@@
 
-To mesure the accuracy, we measure the uncertainty of all nodes in a layer:
+To measure the accuracy, we measure the uncertainty of all nodes in a layer:
 the uncertainty of a node is the range between its computed lower and upper bound. 
-We then average the uncerainty among all the nodes of the layer.
+We then average the uncertainty among all the nodes of the layer.
 Formally, for a node $n$ with bounds $[\alpha,\beta]$, its uncertainty $unc(a) = \beta - \alpha$, and the average uncertainty of a layer $l$ is $\dfrac{\sum_{a\in l} unc(a)}{|l|}.$

### 2024-01-17 Paper/proofs.tex

@@
 			Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by box abstraction equals to the exact lower and upper bounds of $m$ (as expressed above), i.e.
-			$\bar{f}(m)=max(m)$ and $\underline{f}(m)=min(m)$.
+			$\bar{f}(m)=\max(m)$ and $\underline{f}(m)=\min(m)$.
 
-			Then Box abstraction computes the exact lower and upper bounds for every node $n$ of layer $L'$, ie $\bar{f}(n)=max(n)$ and $\underline{f}(n)=min(n)$.
+			Then Box abstraction computes the exact lower and upper bounds for every node $n$ of layer $L'$, ie $\bar{f}(n)=\max(n)$ and $\underline{f}(n)=\min(n)$.
 		\end{lemma}
@@
 
-				\begin{theorem}
+				\begin{theorem} \label{thm:2}
 
@@
 
-				From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{th2}.
+				From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{thm:2} and hence Theorem \ref{th2}.
 

### 2024-01-17 Paper/Paper_noProof.tex
update

--- 2024-01-17 Paper/Paper_noProof.tex
@@
 Consider the simpler abstraction, called the {\em box abstraction} \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
-For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $\hat{x}_3,\hat{x}_4 \in [0,2]$, and $x_5 \in [0,6]$ while $x_6 \in [1.5,3.5]$.
-While the bounds of $x_1, \ldots, x_6$ are exact (for all $\alpha$ 
+For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $\hat{x}_3,\hat{x}_4 \in [0,2]$, and $x_5 \in [0,6]$ while $x_6 \in [0,2]$.
+While the bounds of $x_1, \ldots, x_4$ are exact (for all $\alpha$ 
 in the range, there is an input $\vy$ such that $\val_{\vy}(x_i)=\alpha$), 
@@
 dependencies between earlier neurons: $x_3$ reaches weight $2$ only when $x_1=x_2=2$,
-in which case $x_4$ reaches weight $0$. Hence, it is impossible that $weight(x_5)$ reaches $6$, as it would require both $x_3$ and $x_4$ to have weight $2$.
+in which case $x_4$ reaches weight $0$. Hence, it is impossible that $\Val(x_5)$ reaches $6$, as it would require both $x_3$ and $x_4$ to have weight $2$.
 
@@
 hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
-For instance, $f_i \leq weight(\hat{x}_i) \leq g_i$ with 
+For instance, $f_i \leq \Val(\hat{x}_i) \leq g_i$ with 
 $f_{3}(x_3)=f_4(x_4)=0$ and 
@@
 With that, we get 
-$x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5.5$.
+$x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
 
@@
 It has a main advantage, as it subsumes the box abstraction.
-Indeed, taking an interval $x_i \in [-0.2,5]$, it gives $ReLU(x_i) \in [0,5]$, 
-while the normal DeepPoly algorithm would only allow to conclude that $ReLU(x_i) \in [-0.2,5]$.
+Indeed, taking an interval $x_i \in [-0.2,5]$, it gives $\ReLU(x_i) \in [0,5]$, 
+while the normal DeepPoly algorithm would only allow to conclude that $\ReLU(x_i) \in [-0.2,5]$.
 
@@
 Compensating pair of paths will make precision of the target state reduce when using overabstraction of values.
-Here, $weight(x_5) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of exact $-x_2 \leq 1$), obtaining a bound $weight(x_5) \leq 5.5$ instead of $4$.
+Here, $\Val(x_5) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
+However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of exact $-x_2 \leq 1$), obtaining a bound $\Val(x_5) \leq 5$ instead of $4$.
 

### 2024-01-17 Paper/proofs.tex
update

@@
 	\section{Proof of Theorem \ref{th1}}
+
+	Before the proof of two theorems, we will prove a weaker version, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes).
+We may call such pair a weak compensating pair.
 
@@
 
-		Similarly, we can prove if $S(c)=-1$, $\min(c)=\Val_{\vx^*}(c)$. And similarly, we can prove this for $x^\sharp$. This is the induction step. 
+		Similarly, we can prove if $S(c)=-1$, $\min(c)=\Val_{\vx^*}(c)$. And similarly, we can prove this for $x^\sharp$. This is the induction step. \qed
 	\end{proof}
@@
 
-			Hence we have equality before and after ReLU in all cases.
+			Hence we have equality before and after ReLU in all cases. \qed
 		\end{proof}
+
+		\subsubsection*{From weak to normal}
+
+		\begin{lemma}
+			If a DNN has no compensating pair, then it also does not have weak compensating pair.
+		\end{lemma}
+
+		\begin{proof}
+			If it has a weak compensating pair of two path, $P_1,P_2$, then there exists a segment in two paths starting from the same node and end with the same node, but the weight along two segment have different signs.
+And this will also be a compensating pair.
+\qed
+		\end{proof}
+
+		This finishes the proof for compensating pair rather than weak version.
 
@@
 
-				Before the proof of above theorem, we will prove a weaker version, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes).
-We call such pair a weak compensating pair.
-
 				\begin{definition}
@@
 					from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
-					Then $((a_j,b,z), \pi')$ is also a weak compensating pair.
+					Then $((a_j,b,z), \pi')$ is also a weak compensating pair. \qed
 				\end{proof}
@@
 
-					3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
+					3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction. \qed
 				\end{proof}
@@
 This is a contradiction since $a_i\in I$.
+\qed
 				\end{proof}
@@
 				\begin{proof}
-					This is proved in the first section.
+					This is proved in the first section. \qed
 				\end{proof}
@@
 Therefore any $b$ such that $W_{bc}\neq 0$ is also in above set.
+\qed
 				\end{proof}
@@
 Therefore we can apply Lemma \ref{lem:key1} to get that $\Val_{x_I,\boldsymbol{x}^0_J}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
+\qed
 				\end{proof}
@@
 				\begin{proof}
-					For $D_I$, it is because of no compensating as proved in the first section. For $D_J$, it is because all nodes are either opened or constants.
+					For $D_I$, it is because of no compensating as proved in the first section. For $D_J$, it is because all nodes are either opened or constants. \qed
 				\end{proof}
@@
 				\begin{proof}
-					This is by the definition of MILP formulation and $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}, \LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$.
+					This is by the definition of MILP formulation and $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}, \LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$. \qed
 				\end{proof}
@@
 
+					\qed
 				\end{proof}

### 2024-01-18 Paper/Paper_noProof.tex
number for 6x500

@@
 		Comp(adapt.) & Upper\\ 
-		 & / CROWN & (refined) & TO=30s & TO=1200s & fast & Bound\\
+		 & / CROWN & (refined) & TO=30s & TO=2000s & fast & Bound\\
 		\hline \hline
@@
 
-		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 576s & 925s &\\ \hline
+		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 954s & 925s &\\ \hline
 	\end{tabular}

### 2024-01-18 Paper/Paper_noProof.tex
introduction

@@
 We tested PureBaB with two time out, from the standard 30s to an extreme 2000s, to match the average run time of our adaptative implementation (fast mode).
-Only $3.5\%$ more of images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
+Only $3.5\%$ more images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
 Notice that the refined BaB mode of $\beta$-Crown (using MILP for the first few layers) failed to run on this DNN (NoImplementation error code), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as
-confirmed while running PRIMA.
+confirmed while running refined PRIMA.
 

### 2024-01-18 Paper/introduction.tex
introduction

@@
 To benchmark these tools, a competition has been run since 2019, namely VNNcomp.
-The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
+The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound" (BaB), and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
 \cite{cutting}.
@@
 
-On such complex DNN, PRIMA and $\alpha$-$\beta$ CROWN resorts to a "refined" path, where the bounds on the first few layers are refined using MILP on the exact encoding \cite{MILP2}.
-In our algorithm, we do not use an exact encoding but a partial one with the most important
-ReLU nodes obtained by considering the compensation strength. As it is much more efficient, 
-this can be pushed to all layers, while this would be infeasible without the selection based on the compensation.
-The refined version of $\alpha$-$\beta$ CROWN is particularly efficient on small  DNNs, but as the depth grows, the more work BaB needs to do and our algorithm
-is more accurate, lowering the gap of verified images to the upper bound down from $17.6\%$ to $12\%$.
+On such complex DNN, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
+In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
+As it is more efficient, this can be pushed to all layers.
+This would be infeasible without the selection based on the compensation.
+The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs.
+As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound down from $17.6\%$ to $12\%$.
 
-Finally, algorithms resorting to abstractions on the network (e.g.
-Reluplex / Marabou \cite{Reluplex,katz2019marabou}) rather than abstraction on the values are very different.
-These algorithms have been developed to be complete, so much slower but also more accurate than what we propose.
+Finally, algorithms abstracting the network (e.g.
+Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown} $\cdots$ These algorithms have been developed to be complete, so they are much slower but also more accurate than what we propose.

### 2024-01-18 Paper/Paper_noProof.tex
colors

@@
 We report the runtime from our own implementation used in Compensate($K$).
-It shows that our purely Python implementation is not optimal ($10$-$100$ times slower than the implementation in $\alpha$-$\beta$-CROWN, ERAN and PRIMA).
-Our aim is indeed not to have the most optimized tool, but to evaluate the idea around compensation.
-	\item PRIMA, the 2022 version, with results reported in \cite{prima} and \cite{crown}, as it is the closest in practice with our algorithm, computing accurate bounds for all neurons (as we do), although with a different technique: they focus on explicit correlations between neurons, while we consider the correlations indirectly through a better network abstraction.
+It shows that our purely Python implementation is not optimal ($10$-$100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
+Our aim is indeed not to have the most optimized tool, but to evaluate the accuracy of Compensation.
+	\item PRIMA, with results reported in \cite{prima} and \cite{crown}, as it is the closest in practice with our algorithm, computing accurate bounds for all neurons (as we do), although with a different technique: they focus on explicit correlations between neurons, while we consider the correlations indirectly through a better network abstraction.
 They use GPU while we do not.
@@
 By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
-	\item $\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date.
-Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming \cite{BaB} on such DNNs, and heavily using GPU implementation (while we do not).
+	\item ($\alpha$)$\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date.
+Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming \cite{BaB}, and heavily using GPU implementation (while we do not).
 Performance of pure BaB on these hard DNNs is however impaired by the large number of branchs to consider.
-Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also parallelized with 16 nodes in parallel, before running their BaB tool.
-We also test with the latest versions of $\alpha$-$\beta$-CROWN (October 2023)
-	and of PRIMA (2022) on the MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
-
+Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running their BaB tool.
+	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
 	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
 	SDPFO \cite{SDPFI} which do not present favorable trade offs compared with $\beta$-CROWN. Results can be found in \cite{crown} and are performed in the same conditions so can be compared.
-	\item Finally, we run several version of Compensate($K$).
+	\item Finally, we run several version of Compensate($K$) ({\color{blue} Comp} in Table \ref{tab:example}).
 First, we have a fixed choice for $K$ ($K=60$ for fast and $K=200$ for slow), with a fall back to a lower $K$ ($K=50$ for fast and $K=60$ for slow) if the bounds found is too far from the solution found (MIPGap $>0.5$ in Gurobi).
-We run (our implementation of) DeepPoly first, then the fast version, before running slow on the remaining Images.
+We run (our implementation of) DeepPoly first, then the fast version, before running slow on the remaining images.
 	Further, we also experiment with an {\em adaptative} implementation, which lowers number $K$ adaptively between layers to adapt to the growing number $N$ of linear variables, which has an impact on the overall $\MILP(N,K)$ runtime.
@@
 		\hline
-		\text{DNN}  & DeepPoly & PRIMA & $\beta$-CROWN &\multicolumn{2}{@{}c@{}|}{\text{ Comp (adapt.) }} & \multicolumn{2}{@{}c@{}|}{\text{ Comp (fixed) }} & Upper\\ 
-		 & / CROWN & (refined) & (refined BaB) & fast & slow & fast &slow & Bound\\
+		\text{DNN}  & DeepPoly & PRIMA & $\beta$-CROWN &\multicolumn{2}{@{}c@{}|}{\color{blue}\text{ Comp (adapt.) }} & \multicolumn{2}{@{}c@{}|}{\color{blue} \text{ Comp (fixed) }} & Upper\\ 
+		 & / CROWN & (refined) & (refined BaB) & {\color{blue}fast} & {\color{blue}slow} & {\color{blue}fast} &{\color{blue}slow} & Bound\\
 		\hline \hline
 
-		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & $57.5\%$ & $66.1\%$ & $65.3\%$ & $68.4\%$ &  $84.2 \%$ \\ 
-		$\epsilon = 0.026$ & 5s & 159s & 102s& 75s & 140s & 117s & 142s &  \\
+		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {\color{blue}$57.5\%$} & {\color{blue}$66.1\%$} & {\color{blue}$65.3\%$} & {\color{blue}$68.4\%$} &  $84.2 \%$ \\ 
+		$\epsilon = 0.026$ & 5s & 159s & 102s& {\color{blue}75s} & {\color{blue}140s} & {\color{blue}117s} & {\color{blue}142s} &  \\
 		\hline
 
-		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & $64.3\%$ & $74.7\%$ & $72\%$ & $76.8\%$ & 
+		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {\color{blue}$64.3\%$} & {\color{blue}$74.7\%$} & {\color{blue}$72\%$} & {\color{blue}$76.8\%$} & 
 		$90.1 \%$\\ 
-		$\epsilon = 0.015$ & 11s & 224s & 86s & 163s & 285s & 206s & 279s  &\\ \hline \hline
-
-		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & $52.7\%$ & $59.7\%$ & $61.4\%$ & $\mathbf{65.8\%}$  & $82.0 \%$ \\ 
-		$\epsilon = 0.026$ & 8s & 301s & 103s & 92.3s & 179s & 170s & 346s & \\
+		$\epsilon = 0.015$ & 11s & 224s & 86s & {\color{blue}163s} & {\color{blue}285s} & {\color{blue}206s} & {\color{blue}279s}  &\\ \hline \hline
+
+		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {\color{blue}$52.7\%$} & {\color{blue}$59.7\%$} & {\color{blue}$61.4\%$} & {\color{blue}$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
+		$\epsilon = 0.026$ & 8s & 301s & 103s & {\color{blue}92.3s} & {\color{blue}179s} & {\color{blue}170s} & {\color{blue}346s} & \\
 		\hline
 
-		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & $68.1\%$ & $\mathbf{79.1\%}$ & $72.6\%$ & too & $91.1 \%$ \\ 
-		$\epsilon = 0.015$ & 17s & 395s & 95s  & 297s & 535s & $480s$ & slow & \\ \hline
+		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {\color{blue}$68.1\%$} & 
+		{\color{blue}$\mathbf{79.1\%}$} & {\color{blue}$72.6\%$} & {\color{blue}too} & $91.1 \%$ \\ 
+		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}slow} & \\ \hline
 
@@
 
-Compare with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), 
+Compared with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), 
 the picture is more balanced, because the fundamentals of both algorithms are different. BaB 
@@
 
-More importantly, $\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long time out (the reason why {\em refined} BaB is more accurate on these networks).
-We verify that on a larger DNN learnt in a natural way, namely MLP $6 \times 500$, see Table \ref{tab:example3}.
-We tested PureBaB with two time out, from the standard 30s to an extreme 2000s, to match the average run time of our adaptative implementation (fast mode).
+\newpage
+
+Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long time out (the reason why {\em refined} BaB is more accurate on these networks).
+We verify that in Table \ref{tab:example3}, on a larger DNN learnt in a natural way, namely MLP $6 \times 500$,.
+We tested PureBaB with two timeouts (TO), from standard 30s to an extreme 2000s, to match the average runtime of our adaptative implementation (fast mode).
 Only $3.5\%$ more images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
-Notice that the refined BaB mode of $\beta$-Crown (using MILP for the first few layers) failed to run on this DNN (NoImplementation error code), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as
-confirmed while running refined PRIMA.
+Notice that the refined BaB mode of $\alpha$-$\beta$-Crown (first few layers using MILP) failed to run on this DNN (error code: NoImplementation), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as confirmed while running PRIMA (refined).
 
@@
 		\hline
-		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\beta$-CROWN (pureBaB)}} & 
-		Comp(adapt.) & Upper\\ 
-		 & / CROWN & (refined) & TO=30s & TO=2000s & fast & Bound\\
+		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (pureBaB) \,}} & 
+		{\color{blue}Comp (adapt.)} & Upper\\ 
+		 & / CROWN & (refined) & TO=30s & TO=2000s & {\color{blue}fast} & Bound\\
 		\hline \hline
-
-		$6\times500$\  &   $26\%$ & $32.5\%$ & $41\%$ & $44.5\%$  & $\mathbf{65\%}$ & $92\%$ \\
-
-		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 954s & 925s &\\ \hline
+		$6\times500$\  &   $26\%$ & $32.5\%$ & $41\%$ & $44.5\%$  & {\color{blue}$\mathbf{65\%}$} & $92\%$ \\ 
+		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 954s & {\color{blue}925s} &\\ \hline
 	\end{tabular}
@@
 
-Last, we report the average runetime per number of nodes of both fast adaptive and fast fixed compensation, for the different DNNs considered.
+Last, we display the average runtime per number of nodes of both fast adaptive and fast fixed compensation, for the different DNNs considered.
 The time per node is not constant, but it is still controlled and does not show an exponential blow-up, from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN.
-This indicates that Compensate($K$) can be run on larger DNN without hitting the same complexity wall as for BaB.
+This indicates that Compensate($K$) can be run on larger DNNs without hitting the same complexity wall as BaB.
 
 \section{Limitations and Discussion}
-
-For DNNs easy to verify, $\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images.
+\label{Discussion}
+
+For DNNs easy to verify, $\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images \cite{crown}.
 Compensation strength is not required in these contexts, and likely not useful, reason why we did not consider it.

### 2024-01-18 Paper/introduction.tex
colors

@@
 For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in $\beta$-CROWN).
-Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification.
+Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).
 
@@
 
-On such complex DNN, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
+On such complex DNNs, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
 In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.

### 2024-01-18 Paper/proofs.tex
update proof

@@
 
-				In this section, we will prove theorem \ref{th2}. We will prove that theorem by proving the following theorem:
+				In this section, we will prove theorem \ref{th2}. We will prove it by proving the following theorem:
 
@@
 
-					Using MILP method, if every nodes $b$ in any compensating pair
+					Using MILP, if every nodes $b$ in any compensating pair
 					$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
@@
 				\begin{lemma} \label{lem:open_node_2}
-					A node $b$ in the hidden layer will not be on a weak compensating pair if and only if one of the following two happens:
+					A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
 					\begin{enumerate}

### 2024-01-18 Paper/proofs.tex
update proof

@@
 				\begin{lemma}\label{lem:subnetwork}
-					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
+					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
 We call this sub-network $D_I$.
@@
 
-				Recall the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
+				Recall the sign function of nodes from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, the sign function is no longer total (no longer defined on all nodes).
 
@@
 
-				Notice that $S$ is defined on all nodes $a_i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
-For the domain of $S$, we introduce the following lemma:
+				Notice that $S$ is defined on all nodes $a_i \in I$. For the domain of $S$, we introduce the following lemma:
 

### 2024-01-18 Paper/Paper_noProof.tex
TYPO

@@
 
-For DNNs easy to verify, $\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images \cite{crown}.
+For DNNs easy to verify, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images \cite{crown}.
 Compensation strength is not required in these contexts, and likely not useful, reason why we did not consider it.
@@
 We only considered DNNs with ReLU activation functions in this paper.
-The reason is that MILP, which is the basic block of Compensate($K$), and BaB (the basic block of $\beta$-Crown) can handle the ReLU activation function efficiently, and more complex activation functions are abstracted in other ways, which PRIMA handles (unlike $\beta$-CROWN).
-Still, the compensation paradigm is totally orthogonal to ReLU activation function.
-It is very likely that studying the compensation strength would be useful in this  context as well.
+The reason is that MILP, which is the basic block of Compensate($K$) (and BaB for $\beta$-Crown) can handle the ReLU activation function efficiently.
+Other activation functions are abstracted in more complex ways, e.g.
+by PRIMA (unlike $\beta$-CROWN).
+Still, the compensation paradigm is  orthogonal to the activation function.
+We believe that studying the compensation strength would be useful with other activation functions as well.
 We leave that for future work.
 
-While accuracy of compensate($K$) can be among the highest of the efficient verifiers, runtime, while never blowing-up, can be on the slow side, in particular for larger DNNs.
+Accuracy of Compensate($K$) can be among the highest of the efficient verifiers.
+Runtime, while never blowing-up, can be on the slow side though, in particular for larger DNNs.
 There are many optimizations possible.
-The simplest is to run $\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\beta$-CROWN cannot conclude, possibly using more core to compute more nodes in parallel.
-Another simple way is to modify the refined BaB of $\beta$-CROWN to run compensate($K$) on more layers than what exact MILP can be run, and finish the study using BaB.
+The simplest is to run $\alpha$-$\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\alpha$-$\beta$-CROWN cannot conclude, possibly using more CPU cores to compute more nodes in parallel.
+Another simple way is to modify the refined BaB of $\beta$-CROWN to run Compensate($K$) on more layers than what exact MILP can do, and finish the verification using BaB.
 More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strength, which we experimentally proved to be an efficient trade-off.
@@
 We verified that DNNs harder to verify indeed exhibits more paths with larger compensating strength.
+
 Based on this idea of compensating path, we proposed a novel efficient algorithm considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if all the compensating paths are covered.

### 2024-01-19 Paper/introduction.tex
intro

@@
 ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input to check local robustness) \cite{crown}, with all inputs either certified robust or an attack on robustness is found in the neighbourhood;
-some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $\approx 20 \%$ of inputs where neither of the decisions can be reached \cite{crown}.
+some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20 \%$ of inputs where neither of the decisions can be reached \cite{crown} and Table \ref{tab:example}.
 The main difference between these DNNs with very different behaviours lies in that the DNNs which are trained to be robust are much easier to verify, while the DNNs trained in a "natural" way are much harder to verify.
 
-In this paper, we focus on uncovering what makes the DNNs trained in a natural way so hard to verify (because for "easier" DNNs, adequate methods already exist).
+In this paper, we focus on DNNs trained in a "natural", 
+%uncovering what makes the DNNs trained in a natural way so hard to verify (
+because for "easier" DNNs, adequate methods already exist. 
 To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly, the Linear Programming approximation, PRIMA, and different versions of ($\alpha$)($\beta$)-CROWN.
@@
 While this theorem is theoretically interesting, it is not usable in practice as (almost) all networks have some compensating pairs.
-However, this notion of compensating pairs opens a first interesting optimization concerning an exact abstraction of the network using a Mixed Integer Linear Program \cite{MILP}, where the weight of each neuron is a linear variable, and each ReLU node is associated with a binary variable, so that the values that can be reached by the neuron variable is exactly the value that can be reached by the weight of this neuron considering inputs of the DNN in the fixed neighbourhood.
-While LP tools can scale to thousands of variables, MILP encoding can only be solved for a limited number of binary variables.
+However, this notion of compensating pairs opens a first interesting idea concerning an exact abstraction of the network using a Mixed Integer Linear Program \cite{MILP}, where the weight of each neuron is a linear variable, and ReLU node may be associated with binary variables (exact encoding) or linear variables (overapproximation).
+While LP tools can scale to thousands of linear variables, MILP encoding can only be solved for a limited number of binary variables.
 This suggests that a simpler encoding could be used for those ReLUs that are not on compensating pairs, as their precise outcome may not be necessary.
@@
 This allows to keep very efficiently dependencies from potentially many layers beforehand.
-We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurones.
+We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurons.
 Our method is more accurate locally, but we will tend to lose precision for dependencies created many layers ago.

### 2024-01-19 Paper/proofs.tex
update proof

@@
 				\begin{lemma}
-					If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$ and $S(c)\neq 0$, then $W_{bc}S(c)=S(b)$.
+					If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $W_{bc}S(c)=S(b)$.
 				\end{lemma}
@@
 				\begin{proof}
-					This is proved in the first section. \qed
+					This is proved in the first section of appendix. \qed
 				\end{proof}
@@
 
-				By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node: to it, any path from any input node must have zero weight.
+				By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node:  any path from any input node must have zero weight to it.
 
@@
 
-					If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$. 
+					If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$, or replacing $\max$ by $\min$. 
 				\end{lemma}

### 2024-01-19 Paper/introduction.tex
introduction

@@
 because for "easier" DNNs, adequate methods already exist. 
-To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly, the Linear Programming approximation, PRIMA, and different versions of ($\alpha$)($\beta$)-CROWN.
+To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-CROWN \cite{crown}.
 All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds.
@@
 The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.
-For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in $\beta$-CROWN).
+For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in CROWN).
 Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).
@@
 
-\noindent {\bf Comparison with related work:} Here, we will compare with some (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
-Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on some ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inaccuracy.
+\noindent {\bf Comparison with related work:} Here, we will compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
+Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inaccuracy.
 If the ReLU nodes to abstract are chosen accurately, the result should be more accurate than early stopping the MILP algorithm using all the nodes.
 
-Compared with the linear relaxation of the MILP encoding, our algorithm is strictly more accurate by design, but it will also be slower.
+Compared with the linear relaxation of the MILP encoding \cite{MILP}, our algorithm is strictly more accurate by design, but it will also be slower.
 
@@
 
-Concerning PRIMA, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do).
+Concerning PRIMA \cite{prima}, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do).
 This allows to keep very efficiently dependencies from potentially many layers beforehand.
@@
 Finally, algorithms abstracting the network (e.g.
-Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown} $\cdots$ These algorithms have been developed to be complete, so they are much slower but also more accurate than what we propose.
+Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}$\ldots$ These algorithms have been developed to be complete, so they are much slower but also more accurate than what we propose.

### 2024-01-19 Paper/introduction.tex
introduction

@@
 While some quite large DNNs (e.g.
-ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input to check local robustness) \cite{crown}, with all inputs either certified robust or an attack on robustness is found in the neighbourhood;
-some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20 \%$ of inputs where neither of the decisions can be reached \cite{crown} and Table \ref{tab:example}.
+ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of inputs where neither of the decisions can be reached \cite{crown} and Table \ref{tab:example}.
 The main difference between these DNNs with very different behaviours lies in that the DNNs which are trained to be robust are much easier to verify, while the DNNs trained in a "natural" way are much harder to verify.
@@
 We restrict the formal study to DNNs using only the standard ReLU activation function, although nothing specific prevents the results to be extended to more general architectures.
-We uncover that {\em compensations} (see next paragraph) is the phenomenon creating inaccuracies.
-We verified experimentally that indeed DNNs trained in a natural way have much more heavy compensating pairs than DNNs trained in a robust way.
+We uncover that {\em compensations}
+(see next paragraph) is the phenomenon creating inaccuracies. We verified experimentally that DNNs trained in a natural way have much more heavy compensating pairs than DNNs trained in a robust way.
 
@@
 The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound down from $17.6\%$ to $12\%$.
+As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound down from
+$20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 9, Table \ref{tab:example}).
+On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while Compensate verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).
 

### 2024-01-19 Paper/Paper_noProof.tex
introduction

@@
 	\label{tab:example}
-	\vspace{-1cm}
+	\vspace{-0.8cm}
 \end{table}
@@
 
-For DNNs easy to verify, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close to the upper bound on the $\%$ of verified images \cite{crown}.
-Compensation strength is not required in these contexts, and likely not useful, reason why we did not consider it.
+For DNNs robustly trained, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close \cite{crown} to the upper bound on the $\%$ of verified images \cite{attack}.
+Compensation strength is not required in these contexts, reason why we did not consider it.
 

### 2024-01-19 Paper/introduction.tex
introduction

@@
 The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound down from
+As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from
 $20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 9, Table \ref{tab:example}).
-On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while Compensate verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).
+On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).
 

### 2024-01-19 Paper/Paper_noProof.tex
Background

@@
 fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-$ReLU(x)=x$ for $x \geq 0$ and $f(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
+$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
 
@@
 Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the weight vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
+denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
 \begin{align*}
@@
 For $\boldsymbol{x}=\vz^0$ the vector of input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the weight of neuron $a$ when the the input is $\boldsymbol{x}$.
-A path $\pi$ will be a sequence
-$\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight $w(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
+Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
+Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
+A path $\pi$ is a sequence $\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight of $\pi$ is
+$weight(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
 
@@
 
-In this section, we describe different value (over)-abstractions that are used by efficient algorithms to certify the networks.
-Although the analysis can be approximated, the over-abstraction ensures that all behavior in the original network are possible in the overabstraction, and thus if the over abstraction is safe, then so will be the original network.
+In this section, we describe different value (over-)abstractions that are used by efficient algorithms to certify the networks.
+Over-abstractions ensure that all values in the original network are possible in the over-abstraction, and thus if we prove safety in the over-abstraction, then we will have a proof of safety for the original image.
 

### 2024-01-19 Paper/proofs.tex
update proof

@@
 			\item  $S(a_i)=0$ if 
-			for all $b_j, W_{a_i b_j}\cdot W_{b_j c} = 0$
+			for all $b_j, weigth(a_i b_j)\cdot weigth(b_j c) = 0$
 
-			\item  $S(a_i)=1$ if for all $b_j, W_{a_i b_j}\cdot W_{b_j c} \geq 0$ and there exists 
-			$j, W_{a_i b_j}\cdot W_{b_j c} > 0$
+			\item  $S(a_i)=1$ if for all $b_j, weigth(a_i b_j)\cdot weigth(b_j c) \geq 0$ and there exists 
+			$j, weigth(a_i b_j)\cdot weigth(b_j c) > 0$
 
-			\item $S(a_i)=-1$ if for all $b_j\ W_{a_i b_j}\cdot W_{b_j c} \leq 0$ and there exists 
-			$j, W_{a_i b_j}\cdot W_{b_j c} < 0$ 
+			\item $S(a_i)=-1$ if for all $b_j\ weigth(a_i b_j)\cdot weigth(b_j c) \leq 0$ and there exists 
+			$j, weigth(a_i b_j)\cdot weigth(b_j c) < 0$ 
 		\end{enumerate}
 
-	For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $W_{b_j c}$ is positive, negative, or 0 respectively. Finally, for the output node $z$, we define $S(z)=1$.
+	For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $weigth(b_j c)$ is positive, negative, or 0 respectively. Finally, for the output node $z$, we define $S(z)=1$.
 
@@
 		and $m\in L$ $n\in L'$. Then if both 
-		$w(m n) \neq 0$ and $S(n) \neq 0$, then 
-		$S(m)=S(n)\mathrm{Sign}(W_{n m})$.
+		$weigth(mn) \neq 0$ and $S(n) \neq 0$, then 
+		$S(m)=S(n)\mathrm{Sign}(weigth(n m))$.
 	\end{lemma}
@@
 		Hence there is a non zero path from $m$ to $z$: $(m n) \pi$, which is of sign 
-		$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
+		$S(n)\mathrm{Sign}(weigth(n m))$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(weigth(n m))$.
 		\hfill $\square$
@@
 Let $c$ be a node in layer $L_{i+1}$, then by definition, we have the following equation: \begin{align*}
-			c = \boldsymbol{bias}_c+\sum_{b\in L}W_{bc}\ReLU(b).
+			c = \boldsymbol{bias}_c+\sum_{b\in L}weigth(bc)\ReLU(b).
 		\end{align*}
@@
 		Therefore we have the following inequalities:\begin{align*}
-				\max(c)\leq\sum_{b \in L_i, W_{bc }>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
-			\min(c)\geq\sum_{b \in L_i, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bisa}_c
+				\max(c)\leq\sum_{b \in L_i, weigth(bc )>0}weigth(bc) \max(\hat{b}) + \sum_{b \in L_i, weigth(bc)<0}weigth(bc) \min(\hat{b}) + \boldsymbol{bisa}_c\\
+			\min(c)\geq\sum_{b \in L_i, weigth(bc)>0}weigth(bc) \min(\hat{b}) + \sum_{b \in L_i, weigth(bc)<0}weigth(bc) \max(\hat{b}) + \boldsymbol{bisa}_c
 		\end{align*}
 
-		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $W_{bc}>0$; if $S(b)=-1$, then $W_{bc}<0$; if $S(b)=0$, then $W_{bc}=0$.
+		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $weigth(bc)>0$; if $S(b)=-1$, then $weigth(bc)<0$; if $S(b)=0$, then $weigth(bc)=0$.
 
@@
 			\max(c)&\geq\Val_{\vx^*}(c) \\
-			&= \sum_{b \in L_i, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
+			&= \sum_{b \in L_i, weigth(bc)>0}weigth(bc) \max(\hat{b}) + \sum_{b \in L_i, weigth(bc)<0}weigth(bc) \min(\hat{b}) + \boldsymbol{bisa}_c\\
 			&\geq\max(c)
@@
 %		Then:
-%		$$ S(n) \max(S(n) n)=\sum_{m \in L}W_{m n} S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
-%		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} S(n)\max(S(n)\hat{m}_s)+bias_n)$$
+%		$$ S(n) \max(S(n) n)=\sum_{m \in L}weigth(m n) S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
+%		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}weigth(m n) S(n)\max(S(n)\hat{m}_s)+bias_n)$$
 %		
@@
 %		%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
-%			%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
+%			%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}weigth(m n)\min(\hat{m)s}+bias_n)$
 %		\end{lemma}
@@
 %			Assume first that $S(b)=+1$.
-%			We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
-%			If every $W_{ab} \Val(a)$ is maximized in the same time, 
+%			We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} weigth(ab) \Val(a) + bias_b$.
+%			If every $weigth(ab) \Val(a)$ is maximized in the same time, 
 %			then $\Val(b_s)= \Val(b)$ is also maximized. 
@@
 %			configuration $\boldsymbol{x}^*$.
-%			Indeed, if $W_{ab}=0$, any $\Val(a)$ can be chosen to maximize 
-%			$W_{ab}\Val(a)$. If $W_{ab}>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
-%			$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $W_{ab}\Val(a)$.
-%			Finally, if $W_{a b}<0$ then $S(a_s) = -1$, and we have 
-%			$\max(a_s) = min(a)$, maximizing $W_{ab}\Val(a)$.
+%			Indeed, if $weigth(ab)=0$, any $\Val(a)$ can be chosen to maximize 
+%			$weigth(ab)\Val(a)$. If $weigth(ab)>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
+%			$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $weigth(ab)\Val(a)$.
+%			Finally, if $weigth(a b)<0$ then $S(a_s) = -1$, and we have 
+%			$\max(a_s) = min(a)$, maximizing $weigth(ab)\Val(a)$.
 %			
 %			Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
-%			$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$
+%			$$\max(b)=\sum_{m \in L}weigth(a b) \max(a_s)+bias_b$$
 %			
@@
 %			This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
-%			$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
+%			$\ReLU(\sum_{m \in L}weigth(a )\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
 %			
@@
 			\label{cor1}
-			$$\max(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bias}_c$$
-			$$\min(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bias}_c$$
+			$$\max(c)=\sum_{b \in L, weigth(bc)>0}weigth(bc) \max(\hat{b}) + \sum_{b \in L, weigth(bc)<0}weigth(bc) \min(\hat{b}) + \boldsymbol{bias}_c$$
+			$$\min(c)=\sum_{b \in L, weigth(bc)>0}weigth(bc) \min(\hat{b}) + \sum_{b \in L, weigth(bc)<0}weigth(bc) \max(\hat{b}) + \boldsymbol{bias}_c$$
 		\end{corollary}
@@
 			The Box absraction computes its upper bound using:
-			$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + bias_n$$
+			$$\bar{f}(n)= \sum_{weigth(mn)>0} weigth(mn) \bar{f}(\hat{m}) + \sum_{weigth(mn)<0} weigth(mn) \underline{f}(\hat{m}) + bias_n$$
 
@@
 			%	\begin{enumerate}
-				%	 \item $W_{b,z}=0$, or
-				%	 \item For every input node $j\in J$, we have $W_{a_j,b}=0$.
+				%	 \item $weigth(b,z)=0$, or
+				%	 \item For every input node $j\in J$, we have $weigth(a_j,b)=0$.
 				%	\end{enumerate}
@@
 It means that $a \in J$.
-A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.
+A contradiction as 2) $weigth(a_j,b)=0$ implies weight$(\pi)=0$.
 			%	
 			%	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
-			%	Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
-			%	Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
+			%	Because 2) does not hold, there is a $j \in J$ with $weigth(a_j,b) \neq 0$, say $>0$.
+			%	Because 1) does not hold, $weigth(b,z) \neq 0$, say $>0$.
 			%	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
@@
 			%	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
-			%	$$b= B^0 +\sum_{a_i\in I} W_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
+			%	$$b= B^0 +\sum_{a_i\in I} weigth(a_i, b) a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$.
+Applying Lemma \ref{lemma1}, we obtain the statement.
 			%\end{proof}
@@
 			%
-			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}W_{b_ha_i}+B_h$ ($B_h$ is the bias). 
+			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}weigth(b_ha_i)+B_h$ ($B_h$ is the bias). 
 			%Denote by $B_{open}$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
@@
 			%\begin{align*}
-			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} weigth(b,z)\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 			%\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
-			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $W_{b,z}>0$, and the lower bound
-			%of its (LP) approximation if $W_{b,z}<0$. 
+			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $weigth(b,z)>0$, and the lower bound
+			%of its (LP) approximation if $weigth(b,z)<0$. 
 			%
-			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(W_{zb})=1$, then 
+			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(weigth(zb))=1$, then 
 			%$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
-			%and if $S(b)=\mathrm{sign}(W_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
+			%and if $S(b)=\mathrm{sign}(weigth(zb))=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
 			%Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
@@
 			%\begin{align*}
-			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
-			%	\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
+			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} weigth(b,z)\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
+			%	\sum_{b\in B_{pure}} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
 			%\end{align*} 
@@
 			%Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
-			%$W_{b,z} = 0$ and $b \in B^2$ iff $W_{b,z} \neq 0$.
+			%$weigth(b,z) = 0$ and $b \in B^2$ iff $weigth(b,z) \neq 0$.
 			%Hence:
 			%
-			%$$\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
+			%$$\sum_{b\in B_{pure}} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+			%\sum_{b\in B^2} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
 			%
-			%For $b \in B^2$, we have $W_{a_j,b}=0$ for all $j \in J$
+			%For $b \in B^2$, we have $weigth(a_j,b)=0$ for all $j \in J$
 			%by definition of $B_{pure}$ (Lemma 4.), hence
 			%
-			%$$\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
-			%=\sum_{b\in B^2} W_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
+			%$$\sum_{b\in B^2} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
+			%\sum_{b\in B^2} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
+			%=\sum_{b\in B^2} weigth(b,z) \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
 			%$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
@@
 			%Hence we have: \begin{align*}
-				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}W_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
+				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}weigth(zb)\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
 				%	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
@@
 					\begin{enumerate}
-					  	\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
-						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
+					  	\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $weigth(b,z)=0$ to denote this case, or
+						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $weigth(a_j,b)=0$ to denote this case.
 					\end{enumerate}
@@
 It means that $a \in J$.
-A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.
+A contradiction as 2) $weigth(a_j,b)=0$ implies weight$(\pi)=0$.
 
 					Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
-					Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
-					Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
+					Because 2) does not hold, there is a $j \in J$ with $weigth(a_j,b) \neq 0$, say $>0$.
+					Because 1) does not hold, $weigth(b,z) \neq 0$, say $>0$.
 					Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
@@
 				\begin{lemma}\label{lem:subnetwork}
-					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
+					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $weigth(bc)=0$.
 We call this sub-network $D_I$.
@@
 
-					1. if $b\in J$, by definition, $W_{bc}=0$.
+					1. if $b\in J$, by definition, $weigth(bc)=0$.
 
-					2. if $b\in B_{open}$, then $W_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.
+					2. if $b\in B_{open}$, then $weigth(bc)=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.
 
-					3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction. \qed
+					3. if $b\in B_{zero}$, then $weigth(bc)=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction. \qed
 				\end{proof}
@@
 				\begin{lemma}
-					If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $W_{bc}S(c)=S(b)$.
+					If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $weigth(bc)\neq 0$, then $weigth(bc)S(c)=S(b)$.
 				\end{lemma}
@@
 				\begin{proof}
-					This is because if there exists nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ not in $J$ but this means so does $c$, a contradiction.
-Therefore any $b$ such that $W_{bc}\neq 0$ is also in above set.
+					This is because if there exists nodes $b,c$ such that $weigth(bc)\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ not in $J$ but this means so does $c$, a contradiction.
+Therefore any $b$ such that $weigth(bc)\neq 0$ is also in above set.
 \qed
@@
 				%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
-					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
-					%		 + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
-					%		 +\sum_{b\in B_{zero}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
+					%		 + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
+					%		 +\sum_{b\in B_{zero}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 					%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
@@
 				%	
-				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $W_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $W_{bc}=0$. Therefore, we will have:
+				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $weigth(b,c)=0$. And similarly, for any $b\in B_{zero}$, $weigth(bc)=0$. Therefore, we will have:
 				%	
 				%	\begin{align*}
-					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 					%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
@@
 				%	\begin{align*}
-					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
+					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
 					%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
@@
 
-					If $S(c)$ is defined, then consider all $b$ such that $W_{bc}\neq 0$.
+					If $S(c)$ is defined, then consider all $b$ such that $weigth(bc)\neq 0$.
 First, $b$ cannot in $B_{zero}$; so by induction hypothesis, the value of $b$ is fixed under $\boldsymbol{x}^*_I,\boldsymbol{x}^0_J$ in MILP model.
 
-					If $b\in B_{open}$, the term is $W_{bc}\ReLU(b)$. We know then by induction hypothesis, the value for $b$ in MILP is a fixed value. Then the term $W_{bc}\ReLU(b)$ is also a fixed number.
+					If $b\in B_{open}$, the term is $weigth(bc)\ReLU(b)$. We know then by induction hypothesis, the value for $b$ in MILP is a fixed value. Then the term $weigth(bc)\ReLU(b)$ is also a fixed number.
 
-					If $b\in B_{pure}$, the term is $W_{bc}\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $S(b)$ is undefined and $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined.
+					If $b\in B_{pure}$, the term is $weigth(bc)\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $S(b)$ is undefined and $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined.
 
@@
 For either of them, $\mathrm{AppB}(b)$ will be fixed value.
-Hence, in this case, the term $W_{bc}\mathrm{AppB}(b)$ is also a fixed number.
+Hence, in this case, the term $weigth(bc)\mathrm{AppB}(b)$ is also a fixed number.
 
@@
 					(2) If $S(c)=1$, then we have the following:	\begin{align*}
-						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
-					\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$.
+						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
+					\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $weigth(bc)$: if $weigth(bc)$ is positive, then $\UB$, otherwise $\LB$.
 Notice that all $b$ displayed are that $S(b)$ defined, because if $S(b)$ undefined, then for fixed $\vx_J$, value of $b$ is fixed and will be put into the constant.
@@
 					Now by induction hypothesis part 2, if $S(b)=1$, then $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\max_{\vx_I}\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$; and if $S(b)=-1$, $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\min_{\vx_I}\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
-Moreover, since $S(c)=1$, $S(b)$ and $W_{bc}$ have the same sign.
+Moreover, since $S(c)=1$, $S(b)$ and $weigth(bc)$ have the same sign.
 And both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions.
@@
 						\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-						&constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+						&constant + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
 						= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
@@
 				%	\begin{align*}
-					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
+					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
 					%	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
-$\B$ is one of $\UB,\LB$  that, if $W_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
+$\B$ is one of $\UB,\LB$  that, if $weigth(b,c)>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
 				%	
 				%	We can simplify above equation to \begin{align*}
-					%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
+					%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
 					%	\end{align*}
@@
 					%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-					%		 &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+					%		 &B_c + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge weigth(b,c)\neq 0} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
 					%		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
@@
 					%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
-					%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
-					%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
+					%	= &B_c + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge weigth(b,c)\neq 0} weigth(b,c) \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
+					%	= &B_c + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
 					%	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).

### 2024-01-19 Paper/Paper_noProof.tex
background

@@
 Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
+denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
 \begin{align*}
-	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \vb^i\\
+	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i\\
 	\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
@@
 and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-For $\boldsymbol{x}=\vz^0$ the vector of input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
+For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
+Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
 Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
@@
 \begin{align*}
-	\forall \boldsymbol{x'} \text{ s.t. } d(x,x')\leq \varepsilon, \text{ we have }  
+	\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
 	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
@@
 
-In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\boldsymbol{x},\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
+In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\vx,\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
 \fi
@@
 
-In this section, we describe different value (over-)abstractions that are used by efficient algorithms to certify the networks.
-Over-abstractions ensure that all values in the original network are possible in the over-abstraction, and thus if we prove safety in the over-abstraction, then we will have a proof of safety for the original image.
-
-\subsection{Box and DeepPoly Abstraction}
+In this section, we describe different value (over-)abstractions on $\vz$ that are used by efficient algorithms to certify robustness around an input $\vx$.
+Over-abstractions of values include all values for $\vz$ in the neighbourhood of $\vx$, and thus a certificate for safety in the over-abstraction is a proof of safety for the original input $\vx$.
+
+\subsection{The Box and DeepPoly Abstractions}
 
@@
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (input1) {$x_1$};
+			minimum height = 20] (input1) {$n_1$};
 
 			\node[circle, draw= purple, thick, minimum width = 20,
-			minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$x_2$};
+			minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};
 
@@
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$x_3$};
-			\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$x_4$};
+			minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$n_3$};
+			\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};
 
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{x}_3$};
-			\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{x}_4$};
+			minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{n}_3$};
+			\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};
 
 			\node[circle, draw= blue, thick, minimum width = 20,
-			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$x_5$};
-			\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_6$};
+			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
+			\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};
 
@@
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{x}_5$};
+			minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{n}_5$};
 
 			\node[circle, draw= black, thick, minimum width = 20,
-			minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{x}_{6}$};
+			minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{n}_{6}$};
 
@@
 
-			\draw[->,color=green, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(x_1,0)$};
-			\draw[->,color=red, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(x_2,0)$};
+			\draw[->,color=green, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
+			\draw[->,color=red, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(n_2,0)$};
 
@@
 
-			\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(x_5,0)$};
-			\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(x_6,0)$};
+			\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(n_5,0)$};
+			\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(n_6,0)$};
 
 		\end{tikzpicture}
-		\caption{A DNN example from \cite{kpoly}, where every node is separated into 2, $x$ after the weighted sum and $\hat{x}$ after the ReLU activation function.
-The pair $(x_2 x_3 x_5,x_2 x_4 x_5)$ in green and red is compensating (weights of paths are $1,-2$).}
+		\caption{A DNN example from \cite{kpoly}: every neuron is separated into 2 nodes, $n$ pre- and $\hat{n}$ post-ReLU activation function.
+The pair $(n_2 n_3 n_5,n_2 n_4 n_5)$ in green and red is compensating (weights of paths are $1,-2$).}
 		\label{fig1}
@@
 
-An efficient and prolific line of work concerning DNN verification has been to develop value abstraction of the network.
-The idea is to compute upper and lower bounds on the values of (some) neurons in the DNN when the inputs are in a given neighbourhood, in order to conclude on the robustness without needing to compute the values exactly for all inputs.
+The idea to perform value abstraction is to compute upper and lower bounds on the values of (some) neurons in the DNN when the inputs are in a given neighbourhood, in order to conclude on the robustness without needing to compute the values exactly for all inputs (in the neighbourhood).
 
@@
 While it is fairly simple piecewise linear function with 2 modes ($x<0$ and $x \geq 0$), it is not linear.
-Considering its iterated impact along the different layers of a ReLU DNN is much more complex that it seems.
-First, let us remark that it is easy to represent exactly $\ReLU(x)$
-in case $x$ is known to be entirely positive and in the case where it is entirely negative
-(such a neuron $x$ is called stable), as in both case there is only one known linear mode involved. Hence, the sole problem remains how to treat unstable neurons.
-
-Consider the simpler abstraction, called the {\em box abstraction} \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
+Considering its iterated impact along the different layers of a ReLU DNN is much more complex than it seems.
+First, let us remark that it is easy to represent exactly $\ReLU(x)$ in case $x$ is {\em stable}, that is, either it is known to be entirely positive, order
+it is known to be entirely negative, as in both case there is only one known linear mode involved. Hence, the sole problem remains how to handle {\em unstable} neurons.
+
+Consider the simpler abstraction, called the {\em Box abstraction} \cite{deeppoly}: inductively compute the bound on each neuron of the next layer independently, by considering the weighted sum over the bounds of the previous layer, then clip the lower bound at
+$\max(0,$ lower bound$)$ to represent the ReLU function, and so on.
+For all $i$, let $x_i=\val_{\vx}(n_i)$, with $\vx=(x_1,x_2)$.
 For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $\hat{x}_3,\hat{x}_4 \in [0,2]$, and $x_5 \in [0,6]$ while $x_6 \in [0,2]$. 
-While the bounds of $x_1, \ldots, x_4$ are exact (for all $\alpha$ 
-in the range, there is an input $\vy$ such that $\val_{\vy}(x_i)=\alpha$), 
-it is no more the case from the next layer (starting in $x_5,x_6$) because of potential 
-dependencies between earlier neurons: $x_3$ reaches weight $2$ only when $x_1=x_2=2$,
-in which case $x_4$ reaches weight $0$. Hence, it is impossible that $\Val(x_5)$ reaches $6$, as it would require both $x_3$ and $x_4$ to have weight $2$.
-
-A still extremely fast algorithm that corrects some of this issue is known as {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
-hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
-For instance, $f_i \leq \Val(\hat{x}_i) \leq g_i$ with 
+While the bounds for $n_1, \ldots, n_4$ are exact (for all $\alpha$ 
+in the range, there is an input $\vy$ such that $\val_{\vy}(n_i)=\alpha$), 
+it is no more the case from the next layer (starting in $n_5,n_6$) because of potential 
+dependencies between earlier neurons: $n_3$ reaches value $2$ only when $x_1=x_2=2$,
+in which case $n_4$ reaches value $Val_{(2,2)}(n_4)=0$. Hence, it is impossible that $x_5=\Val_{\vx}(n_5)$ reaches $6$, as it would require both $n_3$ and $n_4$ to have value $2$.
+
+A still extremely fast algorithm that corrects some of this issue is {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
+hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the value of the node.
+Denote $f_i \leq x_i \leq g_i$ with e.g.  
 $f_{3}(x_3)=f_4(x_4)=0$ and 
@@
 
-While there is one optimal linear function for the upper bound $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes, there are two choices for the lower bound: $f_i(x_i) = 0$ or $f_i(x_i)=x_i$.
-In the DeepPoly algorithm, the choice is made by considering the range of an unstable neuron 
-$x_i=[\alpha,\beta]$ with $\alpha < 0 < \beta$. 
-If $|\alpha|\geq |\beta|$ then $0$ is used, while if $|\beta|>|\alpha|$ then $x_i$ (the identity function) is used. Let us call $\overline{\mbox{DeepPoly}}$ the DeepPoly algorithm such that 
-$f_i(x_i) = 0$ is always used, and $f_i(x_i) = x_i$ is never used. 
-It has a main advantage, as it subsumes the box abstraction.
-Indeed, taking an interval $x_i \in [-0.2,5]$, it gives $\ReLU(x_i) \in [0,5]$, 
+For $[\alpha,\beta]$ bounds on $x_i$, there is one optimal linear function for the upper bound $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes.
+There are two choices for the lower bound: $f^1_i(x_i) = 0$ or $f^2_i(x_i)=x_i$.
+In the DeepPoly algorithm, the choice is made by considering $\alpha < 0 < \beta$ (for unstable neurons).
+If $|\alpha|\geq |\beta|$ then $f_i=f^1_i$ is used, while if $|\beta|>|\alpha|$ then $f_i=f^2_i$ is used.
+Denote {\em $\overline{\mbox{DeepPoly}}$} the DeepPoly algorithm such that $f^1_i$ is always used, and $f^2_i$ is never used.
+Unlike DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} subsumes the {\em Box abstraction}. Indeed, taking bounds $[-0.2,5]$ on $x_i$, it gives $\ReLU(x_i) \in [0,5]$, 
 while the normal DeepPoly algorithm would only allow to conclude that $\ReLU(x_i) \in [-0.2,5]$.
@@
 
-At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction \cite{MILP}, which is a priori a complete method (but whose complete encoding is much slower). 
-Consider an unstable neuron $y \in[\alpha,\beta]$.
-The value of $\ReLU(y)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints:
+At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method (albeit much slower than DeepPoly). 
+Consider an unstable neuron $n \in[\alpha,\beta]$.
+The value $x$ of $\ReLU(n)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints \cite{MILP}:
 \vspace{-0.1cm}
 \begin{align*}
-	\hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \leq y-\alpha \cdot (1-a)
+	\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)
 \end{align*}
 
-This encoding is exact in the meaning that \cite{MILP} for all $y \in [\alpha,\beta] \setminus 0$, there is a unique solution $(a,\hat{y})$ satisfying the constraints, and we have $\hat{y}=\ReLU(y)$ (and $a$ is 0 if $y < 0$ and 1 if $y>0$, and can be either for $y=0$).
-Such an encoding can be used for all (unstable) ReLU nodes, and optimizing its value allows to certify a given image.
-However, for any networks hundreds of nodes or more, it means having hundreds of integer variables, and such network will usually not be solvable efficiently.
+From \cite{MILP}, for all $x \in [\alpha,\beta] \setminus 0$, there is a unique solution $(a,\hat{x})$ satisfying the constraints, and we have $\hat{x}=\ReLU(x)$ (and $a$ is 0 if $x < 0$ and 1 if $x>0$, and can be either for $x=0$).
+Such an encoding can be used for every (unstable) ReLU node, and optimizing its value allows to certify a given input.
+For Networks with hundreds of nodes or more, the associated MILP formula will have have hundreds of integer variables, and it will usually not be solvable efficiently.
 
@@
 As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We prove now that the LP abstraction is strictly more accurate that the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.
+We prove now that the LP abstraction is strictly more accurate that the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(n) \geq 0$ and $ReLU(n) \geq n$, while DeepPoly considers exactly one.
 
@@
 	\label{LP}
- Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
+ Given $n \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
  1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
@@
  \begin{align*}
-	 & 1) \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \leq y-\alpha \cdot (1-a), \, a \in [0,1] \\
-	 \text{and} \quad  & 2)  \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0 \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
+	 & 1) \quad \hat{n} \geq n \quad \wedge \quad \hat{n} \geq 0, \quad \wedge \quad \hat{n} \leq \beta \cdot a \quad \wedge \quad \hat{n} \leq n-\alpha \cdot (1-a), \, a \in [0,1] \\
+	 \text{and} \quad  & 2)  \quad \hat{n} \geq n \quad \wedge \quad \hat{n} \geq 0 \quad \wedge \quad \hat{n} \leq \beta \frac{n-\alpha}{\beta-\alpha}
 \end{align*} 
@@
 It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
-For that, we study the upper bound function in the variable $a \in  [0,1]$, with $y \in [\alpha,\beta]$ fixed.
-We have $\hat{y}$ in 1) upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, y - \alpha (1-a)))$, and this bound can be reached.
-The function $min(\beta \cdot a, y - \alpha (1-a))$ reaches its maximum for 
-$\beta \cdot a = y - \alpha (1-a)$, that is 
-$(\beta - \alpha) a = y - \alpha$, i.e. 
-$$ a = \frac{y - \alpha}{\beta-\alpha}$$
+For that, we study the upper bound function in the variable $a \in  [0,1]$, with $n \in [\alpha,\beta]$ fixed.
+We have $\hat{n}$ in 1) upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, n - \alpha (1-a)))$, and this bound can be reached.
+The function $min(\beta \cdot a, n - \alpha (1-a))$ reaches its maximum for 
+$\beta \cdot a = n - \alpha (1-a)$, that is 
+$(\beta - \alpha) a = n - \alpha$, i.e. 
+$$ a = \frac{n - \alpha}{\beta-\alpha}$$
 
 It thus gives an upper bound at 
-$\beta \cdot a = \beta \frac{y - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
+$\beta \cdot a = \beta \frac{n - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
 \hfill $\square$

### 2024-01-19 Paper/proofs.tex

--- 2024-01-19 Paper/proofs.tex
@@
 	and $m\in L$ $n\in L'$. Then if both 
-		$w(m n) \neq 0$ and $S(n) \neq 0$, then 
+	$W_{nm} \neq 0$ and $S(n) \neq 0$, then 
 	$S(m)=S(n)\mathrm{Sign}(W_{n m})$.
@@
 				\begin{enumerate}
-					  	\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
-						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
+					\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $weight({bz})=0$ to denote this case, or
+					\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $weight({a_jb})=0$ to denote this case.
 				\end{enumerate}

### 2024-01-19 Paper/proofs.tex
update proof

@@
 It means that $a \in J$.
-A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.
+A contradiction as 2) $weight({a_j,b})=0$ implies weight$(\pi)=0$.
 
 				Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
-				Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
-				Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
+				Because 2) does not hold, there is a $j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
+				Because 1) does not hold, $weight({b,z}) \neq 0$, say $>0$.
 				Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
@@
 				(2) If $S(c)=1$, then we have the following:	\begin{align*}
-					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
+					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{bc}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{bc} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
 				\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$.
@@
 					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-					&constant + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
+					&constant + \sum_{b\in B_{open}\cap l_i} W_{bc}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{bc} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
 					= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 

### 2024-01-19 Paper/Paper_noProof.tex
Section 3

@@
 
-MILP instances can be linearly relaxed into LP over-abstraction, where variables which were integers in 
-${0,1}$ are relaxed to be real in interval $[0,1]$, using otherwise the same encoding. 
-Solving LP instances being Polynomial time, much more efficient solution could be found, but at the price of a lack of accuracy (e.g.
+MILP instances can be linearly relaxed into LP over-abstraction, where variables which were integers in $\{0,1\}$ (binary) are relaxed to be real in interval $[0,1]$, using otherwise the same encoding.
+Solving LP instances being Polynomial time, optimizing it is much more efficient, but at the price of a lack of accuracy (e.g.
 with not as tight bounds).
@@
 As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We prove now that the LP abstraction is strictly more accurate that the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(n) \geq 0$ and $ReLU(n) \geq n$, while DeepPoly considers exactly one.
+We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while DeepPoly considers exactly one.
 
@@
 	\label{LP}
- Given $n \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
+ Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
  1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
@@
  \begin{align*}
-	 & 1) \quad \hat{n} \geq n \quad \wedge \quad \hat{n} \geq 0, \quad \wedge \quad \hat{n} \leq \beta \cdot a \quad \wedge \quad \hat{n} \leq n-\alpha \cdot (1-a), \, a \in [0,1] \\
-	 \text{and} \quad  & 2)  \quad \hat{n} \geq n \quad \wedge \quad \hat{n} \geq 0 \quad \wedge \quad \hat{n} \leq \beta \frac{n-\alpha}{\beta-\alpha}
+	 & 1) \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1] \\
+	 \text{and} \quad  & 2)  \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha}
 \end{align*} 
@@
 It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
-For that, we study the upper bound function in the variable $a \in  [0,1]$, with $n \in [\alpha,\beta]$ fixed.
-We have $\hat{n}$ in 1) upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, n - \alpha (1-a)))$, and this bound can be reached.
-The function $min(\beta \cdot a, n - \alpha (1-a))$ reaches its maximum for 
-$\beta \cdot a = n - \alpha (1-a)$, that is 
-$(\beta - \alpha) a = n - \alpha$, i.e. 
-$$ a = \frac{n - \alpha}{\beta-\alpha}$$
+For that, we study the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
+We have $\hat{x}$ in 1) is uppered bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
+The function $min(\beta \cdot a, x - \alpha (1-a))$ reaches its maximum for 
+$\beta \cdot a = x - \alpha (1-a)$, that is 
+$(\beta - \alpha) a = x - \alpha$, i.e. 
+$$ a = \frac{x - \alpha}{\beta-\alpha}$$
 
 It thus gives an upper bound at 
-$\beta \cdot a = \beta \frac{n - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
+$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
 \hfill $\square$
@@
 
-In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but too costly). 
-Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision.
-
-Formally, a pair $(\pi,\pi')$ of paths is {\em compensating} if:
+In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but 
+not efficient). 
+Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision. A pair $(\pi,\pi')$ of paths is {\em compensating} if:
 \begin{itemize}
@@
 
-For instance, on Fig.~\ref{fig1}, the paths $\pi= x_2 x_3 x_5$ has weight $1$, while the
-path $\pi'= x_2 x_4 x_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
-We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or 
-$(\pi',\pi)$ is compensating.
-
-Compensating pair of paths will make precision of the target state reduce when using overabstraction of values.
-Here, $\Val(x_5) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$).
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of exact $-x_2 \leq 1$), obtaining a bound $\Val(x_5) \leq 5$ instead of $4$.
+For instance, on Fig.~\ref{fig1}, the paths $\pi= n_2 n_3 n_5$ has weight $1$, while the
+path $\pi'= n_2 n_4 n_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
+We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or $(\pi',\pi)$ is compensating.
+
+Compensating pair of paths will make precision of the target state reduce when using overabstraction of values. Here, $x_5 \leq 4$, which is reached for $x_1=1$ and $x_2=-1$: 
+$\val_{(1,-1)}(n_5)=4$.
+However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+3}{2} \leq 2$ instead of exact $-x_2 \leq 1$), obtaining $x_5 \leq 5$ instead of the precise $x_5 \leq 4$.
 
@@
 As the weights of the paths is of opposite sign, some of these weights will cancel out, by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$.
-Further, no only do they cancel $min(|weight(\pi')|,|weight(\pi')|)$ out, but they also do not accumulate, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inaccurate analysis.
+Further, that also avoid accumulating the error, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inaccurate analysis.
 The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function.
 For instance, consider that the inputs $x_1,x_2$ lies in $[-1,-0]$.
-Then the weight at $\hat{x}_3$ will be always 0, no matter the input, and there will be no compensation to $weight(\pi')$.
+Then $\hat{x}_3$ will always be 0 for any input $\vx=(x_1,x_2) \in [-1,-0] \times [-1,-0]$, and $weight(\pi')$ will not compensate $weight(\pi')$.
 
@@
 Hence, compensation is {\em one} factor of inaccuracy. We prove now that it is actually the {\em only} reason for inaccuracy, in the following meaning.
-If there is no compensating path in the DNN, then any method/approximation at least as accurate as the {\em Box} abstraction, e.g.
-$\overline{\text{DeepPoly}}$ or {\em LP}, computes the exact upper and lower bounds for every node, that is:
+If there is no compensating path in the DNN, then any method/approximation at least as accurate as the Box abstraction, e.g.
+$\overline{\text{DeepPoly}}$ or LP, computes the exact upper and lower bounds for every node, that is:
 
@@
 	Let $n$ be any node of a DNN with {\em no} compensating path.
-For $[\alpha,\beta]$ the bounds computed by the {\em Box} abstraction for $n$, we have that for all $\gamma \in [\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n)=\gamma$.
+For $[\alpha,\beta]$ the bounds computed by the {\em Box abstraction} for $n$, we have that for all $\gamma \in [\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n)=\gamma$.
 \end{theorem}
@@
 The sketch of proof can be found in Section \ref{sec.proofs}. 
-Notice that standard {\em DeepPoly} does not satisfies the following theorem (it does not necessarily refine {\em Box}), and therefore we are not sure PRIMA or $\beta$-CROWN who refine DeepPoly do, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
+Notice that standard DeepPoly does not satisfies Theorem \ref{th1} (it does not necessarily refine Box), and therefore we are not sure PRIMA or $\beta$-CROWN that refine DeepPoly satisfies Theorem \ref{th1}, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
 Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results show in that compensation is the reason for inaccuracy.

### 2024-01-19 Paper/Paper_noProof.tex
section 4

@@
 
-While Theorem \ref{th1} is interesting to understand that compensation is a key notion for accurate verification of DNNs, it is of little use to analyze DNNs with compensations, which are actually those that are most interesting to tackle, as current efficient algorithms are not accurate enough.
+While Theorem \ref{th1} is interesting to understand that compensation is a key notion for accurate verification of DNNs, it cannot be used directly to analyze DNNs with compensations, which are actually those that are most interesting to tackle.
 Intuitively, when there are compensating paths, it seems necessary to consider exactly the (unstable) ReLU nodes that are seen along these paths. 
-Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds $[\alpha,\beta]$.
+Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds 
+$[\alpha,\beta]$.
 Let $X_n$ be the set of neurons $x$ in layer up to $k-1$ such that there is a compensating path with target $n$ passing by $x$ (but not as its source or target).
 Let $Y_n$ be the complement of this set $X_n$ of neurons in the first $k-1$ layers.
-A quite efficient way to consider exactly this set $X$ of neurons is to use MILP$_{X_n}$, the relaxation of the MILP encoding where all the nodes in $Y_n$ are linearly relaxed (thus with $|X_n|$ binary variable, one per neuron in $X_n$), and including exact bounds for every neurons $n'$ in the first $k-1$ layers.
+We denote by MILP$_{X_n}$ the relaxation of the MILP encoding where all the nodes in $Y_n$ are linearly relaxed (thus with $|X_n|$ binary variable, one per neuron in $X_n$), and including exact bounds for every neurons $n'$ in the first $k-1$ layers.
 We state now that the bounds $[\alpha,\beta]$ on neuron $n$ computed by such MILP$_{X_n}$ are accurate.
@@
 In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this threshold are not compensating strongly enough to deserve an integer variable (there are cases where the MILP algorithm is exponential in the number of integer variables), calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
+Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this threshold are not compensating strongly enough to deserve an integer variable, calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
 In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small.

### 2024-01-19 Paper/Paper_noProof.tex
up to and including section 5.2

@@
  using the compensation idea, and compare with competing efficient tools,
-  \item Evaluate the runtime of compensate($K$).
+  \item Evaluate how the runtime of compensate($K$) scale with the size of DNNs.
 \end{enumerate}
@@
 
-The local robustness verification is performed on DNNs trained for the MNIST image dataset as its the only standard DNNs (MLP $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers).
-Indeed, today's efficient methods leave at least $14\%$ to $20\%$ of the images neither certified robust nor with an attack to robustness found, making them interesting DNNs to consider where to improve accuracy of efficient techniques.
-We also test on the larger MLP $6\times 500$, not previously tested in \cite{crown}.
+The local robustness verification is performed on DNNs trained for the MNIST image dataset as its the only DNNs naturally trained ("MLP" (fully connected Multi Level Perceptron) $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers).
+Indeed, today's efficient methods leave between $12\%$ to $20\%$ of the images neither certified robust \cite{crown} nor with an attack to robustness found \cite{attack}, making them interesting DNNs to consider when improving accuracy.
 MNIST contains grayscale images of size $28 \times 28$ pixels ($752$ input neurons).
 For our evaluation, we evaluate on the standard first 1000 images of the dataset, to be directly comparable to experiments run in other papers, e.g.
-\cite{prima,crown}, except for MLP $5\times 500$ which is not reported in \cite{prima,crown} and takes a large amount of time, for which we only test on the first 200 images.
+\cite{prima,crown}.
+We also experimented on (MLP) $6\times 500$ (results not reported in \cite{prima,crown}), checking the first 200 images of the dataset, as it takes a long time to run.
 Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
@@
 
-We experiment with the smallest network (MLP $6\times 100$), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
+We experiment with the smallest network (MLP $5\times 100$ in \cite{crown}, 
+$5 \times 100$ in \cite{prima}, and abusively called $6 \times 100$ in \cite{deeppoly}), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
 We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
@@
 \label{tab:example0}
-\vspace{-0.8cm}
+%\vspace{-0.8cm}
 \end{table}
@@
 The compensating strength for $(b,b')$ is defined as $comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$.
-Indeed, the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),weight(a,b',c))$, and $b,b'$ would help compensated set set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
+Indeed, the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),$\newline $weight(a,b',c))$, and $b,b'$ would help compensated the set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
 After selecting the heaviest $(b_0,b_0')$, we can then compute $comp(b)= \sum_{b' \text{already selected}} comp(b,b')+comp(b',b)$ and select iteratively the heaviest $b$'s one by one till reaching the threshold.
@@
 
+\newpage
+
 \subsubsection*{ReLU Node in the first and second hidden layer}
@@
 We keep the previous evaluation for ranking nodes in the previous (second) layer. 
-Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$.
-We thus define
-$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min(weight(abcd),weight(ab'c'd))$ and the associated $comp(b)$, and select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
+Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ from the first layer to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$.
+We thus define:
+\vspace{-0.2cm}
+$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ 
+\vspace{-0.2cm}
+
+and the associated $comp(b)$, and select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
 
@@
 We compare choosing nodes in the second layer only with choosing nodes in both the first and second layer.
-Choosing ReLU nodes in the previous layer (layer $2$) only is never a good choice. 
+Choosing ReLU nodes in the previous layer (layer $2$) only is less accurate than 
+also choosing nodes in layer $1$.
 When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inaccurate computations ($0.059$ vs $0.574$), while it only reduces the inaccuracy by $65\%$ when choosing nodes randomly.
-Notice that this is direct inaccuracy, applying this layer after layer will even further reduce inaccuracy created by accumulation of inaccuracies.
-
-Notice that it is likely that selecting ReLU nodes up to 3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade off is unclear and we thus did not experiment.
+Notice that applying this layer after layer will even further reduce uncertainty created by accumulation of inaccuracies.
+Last, it is likely that selecting ReLU nodes in 1,2,3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade-off to evaluate the compensating strenght of such paths is unclear and we thus did not experiment.
 
@@
 \label{tab:example1}
-\vspace{-0.8cm}
+%\vspace{-0.8cm}
 \end{table}

### 2024-01-19 Paper/introduction.tex
up to and including section 5.2

@@
 As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from
-$20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 9, Table \ref{tab:example}).
+$20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 8, Table \ref{tab:example}).
 On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).

### 2024-01-19 Paper/Paper_noProof.tex
typo

@@
 
-We now turn to evaluating choosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the second layers, wrt ReLU nodes in the first and second layer.
-The bounds for nodes of the second layers are computed exactly. 
+We now turn to evaluating choosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
+The bounds for nodes of the first two layers are computed exactly. 
 Let $d$ be a neuron of the third layer.

### 2024-01-20 Paper/Paper_noProof.tex
conclusion

@@
 
+\vspace{-0.2cm}
 \section{Conclusion}
-
-In this paper, we presented the notion of compensating pairs of paths, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even very simple arithmetic algebra suffices to verify accurately DNNs.
-We verified that DNNs harder to verify indeed exhibits more paths with larger compensating strength.
-
-Based on this idea of compensating path, we proposed a novel efficient algorithm considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if all the compensating paths are covered.
-We experimentally tested that choosing $Z$ covering the paths with the strongest compensation result to very good accuracy, and runtime which can be favourable in some (but not all) cases.
-This proves that compensating strength is a promising novel concept which should be further studied to 
-improve DNN verification. We finally proposed several ways to use the compensating strength to optimize the tools even more than they are, and leave that as future work.
+\vspace{-0.2cm}
+
+In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
+We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even very simple Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
+We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, indeed exhibits paths with larger compensating strength.
+
+Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
+Last, we experimentally showed that choosing $Z$ covering {\em few} paths with the strongest compensations, results in very good accuracy, and runtime which can be favourable in some (but not all) cases.
+This proves that compensating strength is a promising novel concept which should be further studied to improve DNN verification.
+We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.
 

### 2024-01-20 Paper/Paper_noProof.tex
conclusion

@@
 In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even very simple Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
-We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, indeed exhibits paths with larger compensating strength.
+We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
+We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.
 

### 2024-01-20 Paper/Paper_noProof.tex
section 6 limitation.
left section 5

@@
 
-Accuracy of Compensate($K$) can be among the highest of the efficient verifiers.
+Accuracy of Compensate($K$) is among the highest of the efficient verifiers that do abstraction on values.
 Runtime, while never blowing-up, can be on the slow side though, in particular for larger DNNs.
@@
 The simplest is to run $\alpha$-$\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\alpha$-$\beta$-CROWN cannot conclude, possibly using more CPU cores to compute more nodes in parallel.
-Another simple way is to modify the refined BaB of $\beta$-CROWN to run Compensate($K$) on more layers than what exact MILP can do, and finish the verification using BaB.
-More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strength, which we experimentally proved to be an efficient trade-off.
+Another simple way is to modify the {\em refined} BaB of $\beta$-CROWN to run Compensate($K$) on more layers than what exact MILP can do, and finish the verification using BaB.
+More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strength.
 Also, an analysis of important nodes for the uncertain output nodes could be performed, allowing to compute much faster less accurate bounds for those nodes not important.
@@
 Still, considering ReLU nodes exactly tends to be very accurate locally, but less when the source of correlation is many layers away.
-Few important correlations a la PRIMA could be kept explicitly as linear constraints into the MILP encoding, helping to reduce the imprecision further.
+Few important correlations {\em a la} PRIMA could be kept explicitly as linear constraints in the MILP encoding, helping to reduce the inaccuracies further.
 

### 2024-01-20 Paper/Paper_noProof.tex
bibliography

@@
 \end{tabular}
-\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a Network Naturally trained and a Network Robustly trained with the same architecture and the same training set.}
+\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.}
 \label{tab:compensation}
@@
 source in layer 0 and target in layer 2, for two Networks with 5 hidden layers of 100 nodes each from the ERAN GitHub repository, one trained naturally ("$6\times100$"),
-and one trained using DiffAI ("$5\times100$"). 
+and one trained using DiffAI \cite{DiffAI} ("$5\times100$"). 
 We report in Table \ref{tab:compensation} the average compensation strength, i.e. 
@@
 over all source/target states in given layers.
-The average compensations strength are much lower in the Robust DNN than in the Natural DNN, and indeed the Robust DNN is much simpler to verify than the Natural DNN (e.g.
+The average compensations strength are much lower in the Robust DNN than in the natural DNN, and indeed the Robust DNN is much simpler to verify than the natural DNN (e.g.
 DeepPoly is more accurate and verifies more images).
@@
 
-The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes (similar to MIPplanet \cite{MIPplanet}),  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
 
@@
 	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
-	SDPFO \cite{SDPFI} which do not present favorable trade offs compared with $\beta$-CROWN. Results can be found in \cite{crown} and are performed in the same conditions so can be compared.
+	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet} which do not present favorable trade offs compared with $\beta$-CROWN.
+Results can be found in \cite{crown} and are performed in the same conditions so can be compared.
 	\item Finally, we run several version of Compensate($K$) ({\color{blue} Comp} in Table \ref{tab:example}).

### 2024-01-20 Paper/introduction.tex
bibliography

@@
 In this context, application of DNNs in safety critical applications is cautiously envisioned.
-For that to happen at a large scale, hard guarantees should be provided, so that to avoid dramatic consequences.
+For that to happen at a large scale, hard guarantees should be provided \cite{certification}, through e.g.
+incremental verification \cite{incremental}, so that to avoid dramatic consequences.
 It is the reason for the development of (hard) verification tools since 2016, with now many tools with different trade-offs from exact computation but slow (e.g.
@@
 ERAN-DeepPoly \cite{deeppoly}).
-To benchmark these tools, a competition has been run since 2019, namely VNNcomp.
-The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound" (BaB), and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
+To benchmark these tools, a competition has been run since 2019, namely VNNcomp \cite{VNNcomp}.
+The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound" (BaB) \cite{BaB}, and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
 \cite{cutting}.
 
-While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a Network, an image and a small neighbourhood around this image, 
+While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, 
 is it the case that all the images in the neighbourhood are classified in the same way.
 While some quite large DNNs (e.g.
-ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of inputs where neither of the decisions can be reached \cite{crown} and Table \ref{tab:example}.
-The main difference between these DNNs with very different behaviours lies in that the DNNs which are trained to be robust are much easier to verify, while the DNNs trained in a "natural" way are much harder to verify.
+ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
+Actually, DNNs which are trained to be robust (using DiffAI \cite{DiffAI} or PGD \cite{PGD}) are easier to verify, while the DNNs trained in a "natural" way are harder to verify.
 
-In this paper, we focus on DNNs trained in a "natural", 
+In this paper, we focus on DNNs trained in a "natural" way,
 %uncovering what makes the DNNs trained in a natural way so hard to verify (
@@
 We uncover that {\em compensations}
-(see next paragraph) is the phenomenon creating inaccuracies. We verified experimentally that DNNs trained in a natural way have much more heavy compensating pairs than DNNs trained in a robust way.
+(see next paragraph) is the phenomenon creating inaccuracies. We verified experimentally that a DNN trained in a natural way has heavier compensating pairs than DNNs trained in a robust way.
 
@@
 
-For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaB \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
+For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
 On simple networks, such as those trained robust, this is particularly efficient because branch and bound can find very efficiently the bounds focusing on the actual question, considering the important branches, while our algorithm will be less efficient as it has to consider each node one by one from the start.

### 2024-01-20 Paper/Paper_noProof.tex
typos

@@
 For that, we study the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
-We have $\hat{x}$ in 1) is uppered bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
+We have $\hat{x}$ in 1) is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
 The function $min(\beta \cdot a, x - \alpha (1-a))$ reaches its maximum for 
@@
 It thus gives an upper bound at 
-$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
+$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the upper-bound function used in DeepPoly.
 \hfill $\square$
@@
   \item Evaluate experimentally how the choice of the set $Z$ impacts the accuracy of $\MILP_Z$, and compare different choices for $K$ the size of $Z$,
-  \item Evaluate on benchmarks the percentage of certification that can be obtained
- using the compensation idea, and compare with competing efficient tools,
+  \item Evaluate on benchmarks the percentage of images that can be verified
+ using compensating strength, and compare with other value abstraction verifiers,
   \item Evaluate how the runtime of compensate($K$) scale with the size of DNNs.
@@
 Notice that applying this layer after layer will even further reduce uncertainty created by accumulation of inaccuracies.
-Last, it is likely that selecting ReLU nodes in 1,2,3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade-off to evaluate the compensating strenght of such paths is unclear and we thus did not experiment.
+Last, it is likely that selecting ReLU nodes in 1,2,3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade-off to evaluate the compensating strength of such paths is unclear and we thus did not experiment.
 
@@
 
-\subsection{Comparison to efficient Verifiers}
+\subsection{Comparison with value-abstraction Verifiers}
 
@@
 	\item ($\alpha$)$\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date.
-Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming \cite{BaB}, and heavily using GPU implementation (while we do not).
+Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and heavily using GPU implementation (while we do not).
 Performance of pure BaB on these hard DNNs is however impaired by the large number of branchs to consider.

### 2024-01-20 Paper/Paper_noProof.tex
finish a full path of the paper

@@
 This allows e.g.
-to check local robustness around an input $I$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $I$.
+to check local robustness around an input $\vx$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $\vx$.
 In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs.
@@
 We experiment with the smallest network (MLP $5\times 100$ in \cite{crown}, 
-$5 \times 100$ in \cite{prima}, and abusively called $6 \times 100$ in \cite{deeppoly}), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
+called $5 \times 100$ in \cite{prima}, and abusively $6 \times 100$ in \cite{deeppoly}, perturbation $\varepsilon=0.026$), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
 We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
@@
 
-We now turn to evaluating choosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
-The bounds for nodes of the first two layers are computed exactly. 
-Let $d$ be a neuron of the third layer.
+We now turn to evaluating the choice of ReLU nodes in two layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
+The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. Let $d$ be a neuron of the third layer.
 We keep the previous evaluation for ranking nodes in the previous (second) layer. 
@@
 also choosing nodes in layer $1$.
-When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inaccurate computations ($0.059$ vs $0.574$), while it only reduces the inaccuracy by $65\%$ when choosing nodes randomly.
+When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inaccurate computations ($0.059$ vs $0.574$), while it only reduces the uncertainty by $65\%$ when choosing nodes randomly.
 Notice that applying this layer after layer will even further reduce uncertainty created by accumulation of inaccuracies.
@@
 	50  &  1.243 & 1.432 & 1.39  \\ \hline
-	116 &  1.184 & 1.422 & 1.184  \\ \hline
+	116 (max) &  1.184 & 1.422 & 1.184  \\ \hline
 \end{tabular}
@@
 \label{tab:example1}
-%\vspace{-0.8cm}
+\vspace{-0.8cm}
 \end{table}
@@
 
-In terms of efficient verifiers we compare with, we report:
+We compare the following verifiers performing value-abstraction:
 \begin{itemize}
@@
 We report the runtime from our own implementation used in Compensate($K$).
-It shows that our purely Python implementation is not optimal ($10$-$100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
-Our aim is indeed not to have the most optimized tool, but to evaluate the accuracy of Compensation.
+It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
+Our focus is not to have the most optimized tool, but mainly to evaluate the accuracy of Compensate($K$).
 	\item PRIMA, with results reported in \cite{prima} and \cite{crown}, as it is the closest in practice with our algorithm, computing accurate bounds for all neurons (as we do), although with a different technique: they focus on explicit correlations between neurons, while we consider the correlations indirectly through a better network abstraction.
@@
 	parallelization is difficult.
-	Notice that on these MLP networks, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
+	Notice that on these DNNs, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
 This is doable on the first few layers as the number of integer variable is not too large.
@@
 	\item ($\alpha$)$\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date.
-Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and heavily using GPU implementation (while we do not).
-Performance of pure BaB on these hard DNNs is however impaired by the large number of branchs to consider.
-Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running their BaB tool.
+Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and using GPU implementation (while we do not).
+Performance of pure BaB on these
+	"hard to verify" DNNs is however impaired by the large number of branchs to consider.
+Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running the branching heuristic BaB-FSB.
 	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
@@
 
-Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall method is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
-Our method compare favorably, both in terms of time and accuracy: our fastest setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except our fast adaptative method for $5 \times 200$ which is quite pointless on this shallow DNN - the fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
+Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall pipeline is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
+Our method compare favorably, both in terms of time and accuracy: our fast adaptive setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except for $5 \times 200$ which is quite pointless on this shallow DNN - the fast fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
 Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
@@
 	\label{tab:example}
-	\vspace{-0.8cm}
+	\vspace{-1cm}
 \end{table}
 
-Compared with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), 
-the picture is more balanced, because the fundamentals of both algorithms are different. BaB 
-focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary. 
+Compared with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), the picture is more balanced, because the fundamentals of both algorithms are different.
+BaB focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary.
 Instead, we consider every node one by one from the input layer till the final layer, with the same accuracy.
-Hence our algorithm will spend a lot of time on nodes which are not necessary for the verification.
-Therefore, our naive implementation is not as efficient as the highly optimized
-$\beta$-CROWN: our implementation is 2 to 5 times slower than $\beta$-CROWN, while we are not using GPU, unlike $\beta$-CROWN.
-Things are more interesting on the accuracy front: on shallower DNNs ($5 \times 100$ and $5 \times 100$ with 5 hidden layers), the refinement with MILP treats all but the 2 last layers,
-leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using compensation: we are within $1.6\%$ of the accuracy.
-On deeper DNNs ($8 \times 100$ and $8 \times 100$ with 8 hidden layers), the refinement with MILP cannot treat the 4 last layers, and BaB has more ReLU to branch on.
-Therefore, Compensate($K$) is more accurate than $\beta$-CROWN,
-closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
-and from $17.6\%$ to $12\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than Compensate($K$) (see next Section).
+Hence Compensate($K$) will spend a lot of time on nodes which are not necessary for the verification.
+Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $2$ to $5$ times slower than $\beta$-CROWN.
+Notice that it is also not using GPUs.
+Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), BAB-refined uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting, with a small difference of less than $1.5\%$.
+On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in BAB-refined cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
+the most accurate setting of Compensate($K$) is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
+and from $17.6\%$ to $12\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in Compensate($K$) (see Section \ref{Discussion}).
 
@@
 
-Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long time out (the reason why {\em refined} BaB is more accurate on these networks).
-We verify that in Table \ref{tab:example3}, on a larger DNN learnt in a natural way, namely MLP $6 \times 500$,.
+Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long timeouts ({\em refined} BaB is more accurate than pureBaB on these networks).
+We verify that in Table \ref{tab:example3}, on a larger DNN learnt in a natural way, namely MLP $6 \times 500$.
 We tested PureBaB with two timeouts (TO), from standard 30s to an extreme 2000s, to match the average runtime of our adaptative implementation (fast mode).
 Only $3.5\%$ more images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
-Notice that the refined BaB mode of $\alpha$-$\beta$-Crown (first few layers using MILP) failed to run on this DNN (error code: NoImplementation), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as confirmed while running PRIMA (refined).
+Notice that the refined BaB mode of ($\alpha$)$\beta$-Crown (first few layers using MILP) failed to run on this DNN (error code: NoImplementation), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as confirmed while running PRIMA (refined).
 
@@
 The time per node is not constant, but it is still controlled and does not show an exponential blow-up, from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN.
-This indicates that Compensate($K$) can be run on larger DNNs without hitting the same complexity wall as BaB.
+This indicates that Compensate($K$) can be run on larger DNNs without hitting the same complexity wall as pure BaB.
 

### 2024-01-20 Paper/Paper_noProof.tex
runtime

@@
 Last, we display the average runtime per number of nodes of both fast adaptive and fast fixed compensation, for the different DNNs considered.
-The time per node is not constant, but it is still controlled and does not show an exponential blow-up, from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN.
+The runtime per node is not constant (due to $\LP(N,K)$), but it is still controlled and does not show an exponential blow-up, from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN.
 This indicates that Compensate($K$) can be run on larger DNNs without hitting the same complexity wall as pure BaB.

### 2024-01-22 Paper/proofs.tex
fix some typo in proof
update proof

@@
 
-				\qed
 			\end{proof}
@@
 			From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{thm:2} and hence Theorem \ref{th2}.
+
+			\subsubsection*{From weak to compensating}
+
+			Now, we show Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ is a compensating pair.
+
+			Cut $P,P'$ into segments $P_0,P_1,\cdots$, and $P'_0,P'_1,\cdots$ at each common node; hence each $P_i,P_i'$ have not common nodes, or are the same. Now, for node $a$, there are there cases:
+			\begin{itemize}
+				\item $a$ is a common nodes.
+
+				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the same sign.
+
+				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the different sign.
+			\end{itemize}
+
+			In the last case, $a$ is in a compensating path (the difference is that this path is not from the input to output), and will be open. So we focus on the first and second case.
+
+			For the second case, if we replace $P'$ with $P''=P'_0,\cdots,P'_{i-1},P_{i},P'_{i+1},\cdots$, then $P,P''$ is a weak compensating pair that $a$ is a common nodes.
+So we only need to consider case 1.
+
+			Therefore, choose a path $Q$ from input to output with nonzero weight that disjoint from $P,P''$.
+Now, since weights of $P,P''$ have different signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path.
+This means $a$ will be open.
+
+			Combining all discussion above, if $a$ is in a weak compensating path from input to output, then it is in a compensating path from one layer to another layer.
+Therefore, Theorem \ref{thm:2} implies Theorem \ref{th2}.
+This is what we want to show.
 

### 2024-01-22 Paper/Paper_noProof.tex
MIPplanet

@@
 $(\beta - \alpha) a = x - \alpha$, i.e. 
-$$ a = \frac{x - \alpha}{\beta-\alpha}$$
-
+$ a = \frac{x - \alpha}{\beta-\alpha}$.
 It thus gives an upper bound at 
@@
 
-The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes (similar to MIPplanet \cite{MIPplanet}),  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
 

### 2024-01-22 Paper/introduction.tex
MIPplanet

@@
 
-\noindent {\bf Comparison with related work:} Here, we will compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
-Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inaccuracy.
-If the ReLU nodes to abstract are chosen accurately, the result should be more accurate than early stopping the MILP algorithm using all the nodes.
+\noindent {\bf Comparison with related work:} we compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
+Compared with the exact encoding of a DNN using MILP \cite{MILP},
+we select a restricted number of ReLU nodes based on compensating strength to scale to larger DNNs while maintaining good accuracy. Further, compared to MIPplanet \cite{MIPplanet} which 
+uses a different selection of ReLU nodes, we compute bounds for all neurons iteratively, reducing drastically the number of ReLU nodes represented exactly for a given neuron (ReLU nodes which were considered for neurons in previous layers are not represented exactly for that neuron, while MIPplanet would need to represent all those ReLU nodes exactly), using many fast computations, more efficient than one large computation.
 

### 2024-01-22 Paper/proofs.tex
fix typos

@@
 		\item $S(n)=0$ if all path from $n$ to $z$ have 0 weight; 
-		\item $S(n)=1$ if all path from $n$ to $z$ hafe non-negative weight, and at least one path has a positive weight; 
+		\item $S(n)=1$ if all path from $n$ to $z$ have non-negative weight, and at least one path has a positive weight; 
 		\item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
@@
 
-			Now, we show Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ is a compensating pair.
+			Now, we show that Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ is a compensating pair.
 

### 2024-01-23 Paper/proofs.tex
fix typos and others

@@
 	\label{lemma1}
-	Let $L,L'$  consecutive layers of a DNN without compensation, 
-	and $m\in L$ $n\in L'$. Then if both 
+	Let $L,L'$ be consecutive layers of a DNN without compensation, 
+	and $m\in L$ $n\in L'$. If
 	$W_{nm} \neq 0$ and $S(n) \neq 0$, then 
@@
 
-	Hence there is a non zero path from $m$ to $z$: $(m n) \pi$, which is of sign 
+	So there is a non zero path from $m$ to $z$: $(m n) \pi$, whose sign is 
 	$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
@@
 
-For a node $n$, we use $n_s$ to denote $S(n)\cdot n$. 
-Notice that for $S(n)=1$, $n_s$ gets maximal value whenever $n$ gets maximal value; 
-while for $S(n)=-1$, $n_s$ gets maximal value whenever $n$ gets minimal value (and vice versa). For $S(n)=0$, $n_s=0$ and thus always reach his minimal and maximal.
+%For a node $n$, we use $n_s$ to denote $S(n)\cdot n$. 
+%Notice that for $S(n)=1$, $n_s$ gets maximal value whenever $n$ gets maximal value; 
+%while for $S(n)=-1$, $n_s$ gets maximal value whenever $n$ gets minimal value (and vice versa). For $S(n)=0$, $n_s=0$ and thus always reach his minimal and maximal.
 
@@
 
-%	\begin{lemma}
-	%		\label{lemma2}
-	%		Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
-	%		Then:
-	%		$$ S(n) \max(S(n) n)=\sum_{m \in L}W_{m n} S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
-	%		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} S(n)\max(S(n)\hat{m}_s)+bias_n)$$
-	%		
-	%		Similarly for minimal value.
-	%		
-	%		%	for minimal value,	
-	%		%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
-		%			%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
-		%		\end{lemma}
-	%		
-	%		\begin{proof}
-		%			We choose $\boldsymbol{x}^*$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
-		%			that is setting the value for node $a$ be $\max(a)$ for $S(a)=1$ and $\min(a)$ for $S(a)=-1$.
-		%			At configuration $\boldsymbol{x}^*$, every $a_s(\boldsymbol{x}^*))=\max_{\boldsymbol{x}} {a_s(\boldsymbol{x}))}=\max(a_s)$ is maximized.  
-		%			
-		%			Consider any $b$ in the first hidden layer $L_1$.
-		%			Assume first that $S(b)=+1$.
-		%			We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
-		%			If every $W_{ab} \Val(a)$ is maximized in the same time, 
-		%			then $\Val(b_s)= \Val(b)$ is also maximized. 
-		%			
-		%			We claim that this is the case at 
-		%			configuration $\boldsymbol{x}^*$.
-		%			Indeed, if $W_{ab}=0$, any $\Val(a)$ can be chosen to maximize 
-		%			$W_{ab}\Val(a)$. If $W_{ab}>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
-		%			$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $W_{ab}\Val(a)$.
-		%			Finally, if $W_{a b}<0$ then $S(a_s) = -1$, and we have 
-		%			$\max(a_s) = min(a)$, maximizing $W_{ab}\Val(a)$.
-		%			
-		%			Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
-		%			$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$
-		%			
-		%			The case $S(b)=-1$ is symmetric:
-		%			$\max(b_s)= -\min(b)$ is reached when minimizing $b$, which is also 
-		%			satisfied at $\boldsymbol{x}^*$.
-		%			In both case, $\Val(b_s)$ is maximized at $\boldsymbol{x}^*$. Notice that $\boldsymbol{x}^*$ does not depend upon $b$, so choosing $\boldsymbol{x}^*$ uniformly maximize all $\Val(b_s)$.
-		%			
-		%			This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
-		%			$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
-		%			
-		%			We proceed by induction over every layer of the DNN till the output layer, proving that 
-		%			$\max(z_s)=\max(z)$ is reached at configuration $\boldsymbol{x}^*$.
-		%			
-		%			The case for $\min$ is similar, with another input vector $\boldsymbol{x}^\sharp$ instead of $\boldsymbol{x}^*$.
-		%			\hfill $\square$
-		%		\end{proof}
-
 	As direct corollary of Lemma \ref{lem:key1}, we obtain:
@@
 
-	Notice that for all $x$, for both $S(c)=1$ or $S(c)=-1$, these two bounds are found in Lemma \ref{lemma2},
+	Notice that for all $x$, for either $S(c)=1$ or $S(c)=-1$, these two bounds are found in Lemma \ref{lemma2},
 	from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\sharp$.
@@
 	This finishes the proof for compensating pair rather than weak version.
-
-	%\section{Theorem 2}
-	%
-	%We now show that if all intermediates nodes that are on compensating pairs are opened as MILP nodes, then MILP will be correct.
-First, we do the proof with 3 layers, assuming (without loss of generality) a unique output node $z$.
-	%
-	%\begin{theorem}
-	%	\label{no_diamond_2}
-	%	Using MILP method, if every nodes $b_j$ in any compensating path pair
-	%	 $(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
-	%	 bounds computed by MILP are the exact max and min value of $z$.
-	%\end{theorem}
-	%
-	%By symetry, we only show the max side. 
-	%
-	%
-	%
-	%\begin{definition}
-	%	Let $K$ be the set of all input nodes $a_k$. 
-	%	We define a decomposition $K=I\sqcup J$ as follows:  
-	%	\begin{itemize}
-		% \item $k \in I$  if
-		% \begin{enumerate}
-			%	 \item every path from $a_k$ to $z$ has weight $\geq 0$, or
-			%	\item every path from $a_k$ to $z$ has weight $\leq 0$.
-			% \end{enumerate}
-		%That is, $a_k$ is not a source of a compensating pair.
-		%	\item $k \in J$ if $k \notin I$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
-		%	one with positive and one with negative weight.
-		%\end{itemize}
-		%\end{definition} 
-		%
-		%
-		%\begin{lemma} \label{lem:open_node}
-		%	A node $b$ in the hidden layer will not be on a compensating pair iff one of the following two happens:
-		%	\begin{enumerate}
-			%	 \item $W_{b,z}=0$, or
-			%	 \item For every input node $j\in J$, we have $W_{a_j,b}=0$.
-			%	\end{enumerate}
-		%	We denote $B_{pure}$ the set of such nodes $b$ such that at least one of the above holds.
-		%\end{lemma}
-		%
-		%\begin{proof}
-		%	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened.
-If 1), it is obvious.
-For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$.
-It means that $a \in J$.
-A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.
-		%	
-		%	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
-		%	Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
-		%	Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
-		%	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
-		%	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
-		%	Then $((a_j,b,z), \pi')$ is also a compensating pair.
-		%\end{proof}
-		%
-		%Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
-		%
-		%
-		%\begin{definition}\label{sign_of_nodes_in_I}
-		%	We define a partial sign function $S$ over nodes $n$ such that : 	
-		%	\begin{enumerate} 
-			%		 \item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
-			%		 \item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
-			%		 \item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
-			%		 \item Otherwise $S(n)$ is undefined.
-			%	\end{enumerate}
-		%\end{definition}	
-		%	
-		%Notice that $S$ is defined on all nodes $a_i$ with $i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also).
-Hence it is undefined only for nodes $a_j$ with $j \in J$.
-		%
-		%
-		%We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$.
-We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
-		%Consider $\boldsymbol{x}_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
-		%
-		%\begin{lemma} \label{lem:reach_max}
-		%	$max_a (weight_{a}(z)) = max_{\{a \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (weight_{a}(z))$
-		%	
-		%	Further, for every intermediate node $b$ in the hidden layer, for any valuation $\boldsymbol{x}^0_J$, 
-		%	we have $max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (weight_{a}(b)) = max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J,\boldsymbol{x}_I=\boldsymbol{x}_I^*\}} (weight_{a}(b))$.	
-		%\end{lemma}
-		%
-		%\begin{proof}
-		%	For the first statement, we use 
-		%	$$max_{\boldsymbol{x}_K} (weight_{\boldsymbol{x}_K}(z)) = max_{\boldsymbol{x}_J} max_{\boldsymbol{x}_I} (weight_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$
-		%	
-		%	Now, for any fixed input $\boldsymbol{x}^0_J$, we can regard $weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
-		%	as bias.
-In the simplified $D'$, there is no compensating path because of the definition of $I$.
-Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
-		%	
-		%	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
-		%	$$b= B^0 +\sum_{a_i\in I} W_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
-		%\end{proof}
-		%
-		%\subsection{MILP abstraction}
-		%
-		%Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
-		%where each variable $\alpha_b$ for the ReLU from $b^-$ to $b^+$ is:
-		%\begin{itemize}
-		%	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \in B_{pure}$
-		%	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \notin B_{pure}$
-		%\end{itemize}
-		%
-		%
-		%\begin{lemma}\label{lem:AppB=ReLU}
-		%	Let $\mathrm{AppB}$ be the upper bound of lower bound approximation functions of LP for $\ReLU$ function with known upper and lower bound (numbers) $u,l$.
-Then when $x$ reaches the extremal values (maximum or minimum values, $u$ or $l$), then $\mathrm{AppB}(x)=\ReLU(x)$.
-		%	
-		%\end{lemma}
-		%
-		%\begin{proof}
-		%	This is simply by definition of LP approximation functions.
-		%\end{proof}
-		%
-		%Notice that there is only one layer of ReLUs, in the hidden layer.
-		%Denote by $\mathrm{UB}$ the maximal bound on $z$ considering the MILP constraints above, with ReLUs being either linear or binary depending on whether $b \in B_{pure}$ or not.
-		%
-		%We want to show that $\mathrm{UB} = \max z$. As the MILP abstraction is a sound overapproximation, 
-		%it suffices to show that $\mathrm{UB}\leq \max c$.
-		%
-		%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}W_{b_ha_i}+B_h$ ($B_h$ is the bias). 
-		%Denote by $B_{open}$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
-		%$b \notin B_{pure}$. %For any subdomain $D \subseteq B_{open}$, 
-		%Let $\boldsymbol{x}^0_J$ and $\boldsymbol{x}^0_I$ be fixed inputs, and consider the associated upper bound 
-		%$\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}$. We have:
-		%%We show that this upper bound does not exceed the maximal value of $z$: 
-		%
-		%\begin{align*}
-		%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
-		%\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
-		%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $W_{b,z}>0$, and the lower bound
-		%of its (LP) approximation if $W_{b,z}<0$. 
-		%
-		%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(W_{zb})=1$, then 
-		%$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
-		%and if $S(b)=\mathrm{sign}(W_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
-		%Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
-		%
-		%\begin{align*}
-		%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
-		%	\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
-		%\end{align*} 
-		%
-		%Added FIX:
-		%Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
-		%$W_{b,z} = 0$ and $b \in B^2$ iff $W_{b,z} \neq 0$.
-		%Hence:
-		%
-		%$$\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-		%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
-		%
-		%For $b \in B^2$, we have $W_{a_j,b}=0$ for all $j \in J$
-		%by definition of $B_{pure}$ (Lemma 4.), hence
-		%
-		%$$\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
-		%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
-		%=\sum_{b\in B^2} W_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
-		%$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
-		%$weight_{\boldsymbol{x}^*_I}(b)$ is an extremal value (minimum or maximal) and 
-		%$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values.
-		%
-		%Hence we have: \begin{align*}
-			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}W_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
-			%	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
-			%	\leq & \max_{\boldsymbol{x}_J}\max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\boldsymbol{x}_J) 	= \max_{\boldsymbol{x}_K} weight_{\boldsymbol{x}_K}(z)
-			%\end{align*}
-			%
-			%Considering the maximal over all inputs $\boldsymbol{x}_J,\boldsymbol{x}_I$, we obtain 
-			%
-			%$$\mathrm{UB} = max_{\boldsymbol{x}_J,\boldsymbol{x}_I} \mathrm{UB}_{\boldsymbol{x}_J,\boldsymbol{x}_I} \leq \max_{\boldsymbol{x}_J,\boldsymbol{x}_I} weight_{\boldsymbol{x}_J,\boldsymbol{x}_I}(z)$$ And this us what we want to show.
 

### 2024-01-23 Paper/proofs.tex
fix typos and others

@@
 	\begin{lemma}
-		If a DNN has no compensating pair, then it also does not have weak compensating pair.
+		If a DNN has no compensating pair, then it also does not have weak compensating pair from an input node to the output node.
 	\end{lemma}
@@
 	\begin{proof}
-		If it has a weak compensating pair of two path, $P_1,P_2$, then there exists a segment in two paths starting from the same node and end with the same node, but the weight along two segment have different signs.
+		If it has a weak compensating pair of two paths, $P_1,P_2$, then there exists a segment in two paths starting from the same node and end with the same node, but the weight along two segment have different signs.
 And this will also be a compensating pair.
@@
 
-			In this section, we will prove theorem \ref{th2}. We will prove it by proving the following theorem:
+			In this section, we will prove theorem \ref{th2}. We will prove it by proving the following weak theorem:
 
@@
 
-				Suppose $\mathcal{N}$ is a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$.
+				Suppose $\mathcal{D}$ is a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$.
 
-				Using MILP, if every nodes $b$ in any compensating pair
+				Using MILP, if every nodes $b$ in any weak compensating pair
 				$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
@@
 					That is, $a_k$ is not a source of a weak compensating pair. 	We write $A_{pure}$ by $I$ for short.
-					\item $a_k \in A_{open}$ if $a_k \notin A_{pure}$, that is there exists two paths $\pi,\pi'$ from $k$, 
+					\item $a_k \in A_{open}$ if $a_k \notin A_{pure}$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
 					one with positive and one with negative weight. 	We write $A_{open}$ by $J$ for short.
@@
 			\begin{lemma} \label{lem:open_node_2}
-				A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
+				A node $b$ in a hidden layer will not be in a weak compensating path if and only if one of the following happens:
 				\begin{enumerate}
@@
 
-			We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.	We denote $B_{open}$ the set of all nodes $b$ in a compensating path.
+			We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.	We denote $B_{open}$ the set of all nodes $b$ in a weak compensating path.
 
@@
 			\begin{lemma}\label{lem:subnetwork}
-				$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
+				$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward.
+That is to say, if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
 We call this sub-network $D_I$.
@@
 
-			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, the sign function is no longer total (no longer defined on all nodes).
+			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. Because now we allow weak compensating paths, the sign function is no longer defined on all nodes.
 
@@
 			\begin{lemma}
-				If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $W_{bc}S(c)=S(b)$.
+				If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $Sign(W_{bc})S(c)=S(b)$.
 			\end{lemma}

### 2024-01-23 Paper/proofs.tex
fix typos

@@
 
-For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network, we write $\max(n),\min(n)$ directly, instead of $\max(\Val(n))$, $\min(\Val(n))$ or $\max_{\vx}(\Val_{\vx}(n)),\min_{\vx}(\Val_{\vx}(n))$.
+For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network without risk of confusing, we will write $\max(n),\min(n)$ directly, which means $\max(\Val(n))$, $\min(\Val(n))$ or $\max_{\vx}(\Val_{\vx}(n)),\min_{\vx}(\Val_{\vx}(n))$.
 
@@
 			We denote $\boldsymbol{x}_S$ for any subset $S$ of input nodes to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
-We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and $\Val(z)=\Val_{\boldsymbol{x}}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
-For a node $b$ that $S$ is not defined on it, since $b$ only depends on $J$, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ will be fixed.
+We also use $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and $\Val(z)=\Val_{\boldsymbol{x}}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
+For a node $b$ that $S$ is not defined on it, $b$ only depends on $J$; so, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ will be fixed.
 
@@
 			\begin{lemma}
-				In the standard framework, both $D_I$ and $D_J$ are accurate in the sense that for any $b$ in $D_I$ or $D_J$, $\UB(b)=\max\Val(b)$ and $\LB(b)=\min\Val(b)$.
+				In the standard $MILP$ framework, both $D_I$ and $D_J$ are accurate in the sense that for any $b$ in $D_I$ or $D_J$, $\UB(b)=\max(b)$ and $\LB(b)=\min(b)$.
 			\end{lemma}

### 2024-01-23 Paper/proofs.tex
fix typos

@@
 
-			We want to show that $\mathrm{UB}(z) = \max (z)$ and $\mathrm{LB}(z) = \min (z)$ for the unique output nodes, and we will prove this for all $c\notin B_{zero}$ .
+			We want to show that $\mathrm{UB}(z) = \max (z)$ and $\mathrm{LB}(z) = \min (z)$ for the unique output nodes.
+In fact, we will prove this for all $c\notin B_{zero}$ .
 As the MILP abstraction is a sound over-approximation,
-			it suffices to show that $\mathrm{UB}\leq \max (c)$ and $\mathrm{LB} \geq \min (c)$.
+			it suffices to show that $\mathrm{UB}(c)\leq \max (c)$ and $\mathrm{LB}(c) \geq \min (c)$.
 We will prove this by induction on layers from the first hidden layer to the output layer.

### 2024-01-23 Paper/proofs.tex
fix typos

@@
 				We prove this lemma by induction on layers.
-For first hidden layer $l_1$, it is obvious.
-Suppose we have proved part 1,2,3 up to layer $l_i$, then for layer $l_{i+1}$, suppose $c$ is a node in this layer.
+For first hidden layer $L_1$, it is obvious.
+Suppose we have proved part 1,2,3 up to layer $L_i$, then for layer $L_{i+1}$, suppose $c$ is a node in this layer.
 
@@
 
-			From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{thm:2} and hence Theorem \ref{th2}.
+			From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{thm:2}.
 

### 2024-01-23 Paper/proofs.tex
fix typos

@@
 
-			%\begin{lemma}\label{lem:pure_node}
-			%	For a node $c\in B_{pure}$, $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$ (and $\LB$ the same) only depends on $\boldsymbol{x}^0_I$.
-			%\end{lemma}
-			%
-			%\begin{proof}
-			%	We prove this lemma by induction. For the first hidden layer, this is trivial.
-			%	
-			%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
-				%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
-				%		 + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
-				%		 +\sum_{b\in B_{zero}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
-				%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
-			%	
-			%	
-			%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $W_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $W_{bc}=0$. Therefore, we will have:
-			%	
-			%	\begin{align*}
-				%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
-				%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
-			%	
-			%	\begin{align*}
-				%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
-				%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
-			%\end{proof}
-
 			We want to show that $\mathrm{UB}(z) = \max (z)$ and $\mathrm{LB}(z) = \min (z)$ for the unique output nodes.
@@
 
-			Now, we show that Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ is a compensating pair.
+			Now, we show that Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ form this weak compensating pair.
 
-			Cut $P,P'$ into segments $P_0,P_1,\cdots$, and $P'_0,P'_1,\cdots$ at each common node; hence each $P_i,P_i'$ have not common nodes, or are the same. Now, for node $a$, there are there cases:
+			Cut $P,P'$ into segments $P_0,P_1,\cdots$, and $P'_0,P'_1,\cdots$ at each common node; hence each $P_i,P_i'$ either have not common nodes (except the start and end nodes), or are the same.
+Now, for node $a$, there are three cases:
 			\begin{itemize}
@@
 
-			In the last case, $a$ is in a compensating path (the difference is that this path is not from the input to output), and will be open. So we focus on the first and second case.
+			In the last case, $a$ is in a compensating path (the difference is that this path is not from the input to output), and will be opened. So we focus on the first and second case.
 
@@
 
-			Therefore, choose a path $Q$ from input to output with nonzero weight that disjoint from $P,P''$.
+			Therefore, choose a path $Q$ from input to output with nonzero weight and disjoint from $P,P''$.
 Now, since weights of $P,P''$ have different signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path.
-This means $a$ will be open.
+This means $a$ will be opened.
 
@@
 This is what we want to show.
-
-			%\begin{lemma}
-			%	For the $i$-th layer $l^i$ ($1$-th layer is the first hidden layer), for a node $c\in l^i$, if $c\notin B_{zero}$ and $S(c)=1$, then:
-			%	
-			%	 1.
-if , then for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val(\boldsymbol{x}^*_I,\boldsymbol{x}^0_J)(c) = \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$, where $\boldsymbol{x}^*_I$ is described in previous section.
-More important, when $\boldsymbol{x}_I=\boldsymbol{x}^*_I$, for all node $c$ in the same layer, the approximation of $c$ is a constant number rather than an interval, and it is equal to $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$ or $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.
-			%	
-			%The similar is true for lower bound $\LB$.
-			%\end{lemma}
-
-			%\vspace*{20ex}
-			%\begin{proof}
-			%	
-			%	For $i= 1$, we have proved in previous section.
-			%	
-			%	Suppose we have proved this lemma up to layer $i$, and we are going to prove it for $i+1$-th layer. Let $c\notin B_{zero}$ be a node on $i+1$-th layer.
-			%	
-			%	By definition, we have that for any input vector $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$:
-			%	
-			%	\begin{align*}
-				%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
-				%	\end{align*} where $\mathrm{AppB}$ is the same as in previous section  whose definition is independent with $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
-$\B$ is one of $\UB,\LB$  that, if $W_{b,c}>0$, then $\B$ is $\UB$ and otherwise $\B$ is $\LB$.
-			%	
-			%	We can simplify above equation to \begin{align*}
-				%			\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I}(b)).
-				%	\end{align*}
-			%	
-			%	By induction hypothesis, since both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have that \begin{align*}
-				%		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
-				%		 &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
-				%		= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
-				%	\end{align*} The equal is because by induction hypothesis, when $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, the approximation is a constant and is equal to $\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
-			%	
-			%Now, since when $x$ reaches the max or min of $\mathrm{AppB}$'s domain, $\mathrm{AppB}(x)=\ReLU(x)$, and by induction hypothesis, for any $b\in B_{pure}\cap l_i$, $\mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))=\ReLU(B_{\boldsymbol{x}^*_I})$.
-Hence, by induction hypothesis, we will have \begin{align*}
-				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq & \ \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c) \\
-				%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge W_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^*_I}(b))\\
-				%	= &B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))\\
-				%	= & \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c).
-				%\end{align*} This finishes the proof.
-				%	\end{proof}
-			%
-			%
-			%Now, we have that for any fixed $\boldsymbol{x}^0_J$, $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)= \max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$.
-Therefore, $\max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \UB_{\boldsymbol{x}_I,\boldsymbol{x}_J}(c)= \max_{\boldsymbol{x}_I,\boldsymbol{x}_J} \Val(\boldsymbol{x}_I,\boldsymbol{x}_J)(c)$ and this is to say $\UB(c)=\max(c)$.
-This is what we want to show, and the same result holds for lower bound and minimal value.

### 2024-01-23 Paper/proofs.tex
fix typos

@@
 			\begin{proof}
-				First, we show that if one of case 1, 2 happens, then $b$ will not be on a weak compensating pair.
+				First, we show that if one of case 1, 2 happens, then $b$ will not be in a weak compensating pair.
 If 1), it is obvious.
@@
 It means that $a \in J$.
-A contradiction as 2) $weight({a_j,b})=0$ implies weight$(\pi)=0$.
+This is a contradiction as 2) $weight({a_j,b})=0$ implies weight$(\pi)=0$.
 
-				Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
-				Because 2) does not hold, there is a $j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
+				Second, we show that if neither 1 nor 2 hold, then $b$ will be in a weak compensating path.
+				Because 2) does not hold, there exists $j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
 				Because 1) does not hold, $weight({b,z}) \neq 0$, say $>0$.
@@
 				from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
-				Then $((a_j,b,z), \pi')$ is also a weak compensating pair. \qed
+				Then two paths $(a_j,b,z)$ and $\pi'$ also form a weak compensating pair. \qed
 			\end{proof}

### 2024-01-23 Paper/Paper_noProof.tex
new numbers for 8x200

@@
 Notice that applying this layer after layer will even further reduce uncertainty created by accumulation of inaccuracies.
-Last, it is likely that selecting ReLU nodes in 1,2,3 layers earlier (for nodes in layer $4+$) could further improve the accuracy, but the computational trade-off to evaluate the compensating strength of such paths is unclear and we thus did not experiment.
+Last, we did not experiment for selecting ReLU nodes in 3+ layers earlier because the trade-off of accuracy vs evaluating the compensating strength of such paths is unclear.
 
@@
 		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {\color{blue}$68.1\%$} & 
-		{\color{blue}$\mathbf{79.1\%}$} & {\color{blue}$72.6\%$} & {\color{blue}too} & $91.1 \%$ \\ 
-		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}slow} & \\ \hline
+		{\color{blue}$79.1\%$} & {\color{blue}$72.6\%$} & {\color{blue}$\mathbf{80.2\%}$} & $91.1 \%$ \\ 
+		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}612s$^\star$} & \\ \hline
 
@@
 	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
-	Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.}
+	Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
+	\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.}
 	\label{tab:example}
@@
 Hence Compensate($K$) will spend a lot of time on nodes which are not necessary for the verification.
-Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $2$ to $5$ times slower than $\beta$-CROWN.
-Notice that it is also not using GPUs.
-Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), BAB-refined uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting, with a small difference of less than $1.5\%$.
-On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in BAB-refined cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
-the most accurate setting of Compensate($K$) is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
-and from $17.6\%$ to $12\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in Compensate($K$) (see Section \ref{Discussion}).
+Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $1.4$ to
+$6.5$ times slower than $\beta$-CROWN. Notice Compensate($K$) it is not using GPUs. 
+Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), refined BaB uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting of Compensate($K$), with a small difference of less than $1.5\%$.
+On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in refined BaB cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
+the most accurate setting (slow fixed) of Compensate($K$) is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
+and from $17.6\%$ to $10.9\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in Compensate($K$) (see Section \ref{Discussion}).
 

### 2024-01-23 Paper/proofs.tex
appendix

@@
-	\section{Proof of Theorem \ref{th1}}
-
-Before the proof of two theorems, we will prove a weaker version, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes).
-We may call such pair a weak compensating pair.
+\section*{Appendix}
+As a first step to prove Theorems \ref{th1},\ref{th2}, 
+we will relax the compensating pairs notion to allows pairs of paths having nodes in common.
+Such a pair is called a {\em weak compensating pair}.
+We will then in a second step prove Theorems \ref{th1},\ref{th2} for the full definition of compensating pairs of paths.
 
@@
 then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal). 
-
-For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network without risk of confusing, we will write $\max(n),\min(n)$ directly, which means $\max(\Val(n))$, $\min(\Val(n))$ or $\max_{\vx}(\Val_{\vx}(n)),\min_{\vx}(\Val_{\vx}(n))$.
+For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network without risk of confusing, 
+we will write $\max(n)$ to denote $\max(\Val_{\vx}(n))$, and $\min(n)$ to denote $\min(\Val_{\vx}(n))$.
 
@@
 \begin{definition}[Sign of Node]\label{sign_of_nodes}
-	We define the partial sign function $S$ on neurons $n$: 	
+	We define the partial sign function $S$ on node $n$: 	
 	\begin{enumerate}
-		\item $S(n)=0$ if all path from $n$ to $z$ have 0 weight; 
+		\item $S(n)=0$ if all path from $n$ to $z$ have weight $0$; 
 		\item $S(n)=1$ if all path from $n$ to $z$ have non-negative weight, and at least one path has a positive weight; 
@@
 
-In general, $S$ may not be defined on every node (e.g.
-if there is a negative and a positive path from $a$ to $c$).
-However, if there is no compensating pair, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
-For instance, for an input node $a_i$ of any 3 layer DNN:
+In general, $S$ may not be defined on every node 
+(e.g. if there is a negative and a positive path from $a$ to $c$). 
+However, if there is no compensating pair of paths, 
+$S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
+
+For instance for any 3 layer DNN: for an input node $a_i$:
 \begin{enumerate}
@@
 For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $W_{b_j c}$ is positive, negative, or 0 respectively. Finally, for the output node $z$, we define $S(z)=1$.
+
+\section{Proof of Theorem \ref{th1}}
+
+Assume that there is a no (weakly) compensating pair of paths.
 
@@
 				Second, we show that if neither 1 nor 2 hold, then $b$ will be in a weak compensating path.
-				Because 2) does not hold, there exists $j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
+				Because 2) does not hold, there exists $a_j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
 				Because 1) does not hold, $weight({b,z}) \neq 0$, say $>0$.

### 2024-01-23 Paper/proofs.tex
proof

@@
 
+Let $\cal B$ be a neighbourhood of an input.
 First, notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
 then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal). 
-For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network without risk of confusing, 
-we will write $\max(n)$ to denote $\max(\Val_{\vx}(n))$, and $\min(n)$ to denote $\min(\Val_{\vx}(n))$.
+For convenience,
+when the neighbourhood $\cal B$ is clear, 
+we will write $\max(n)$ to denote $\max_{\vx \in \cal B}(\Val_{\vx}(n))$, and $\min(n)$ to denote $\min_{\vx \in \cal B}(\Val_{\vx}(n))$.
 
@@
 
-\begin{definition}[Sign of Node]\label{sign_of_nodes}
+\begin{definition}
+	\label{sign_of_nodes}
 	We define the partial sign function $S$ on node $n$: 	
@@
 
-\begin{lemma}[Sign]
+\begin{lemma}
 	\label{lemma1}
 	Let $L,L'$ be consecutive layers of a DNN without compensation, 
-	and $m\in L$ $n\in L'$. If
-	$W_{nm} \neq 0$ and $S(n) \neq 0$, then 
+	$m\in L$ and $n\in L'$. If $W_{m n} \neq 0$ and $S(n) \neq 0$, then 
 	$S(m)=S(n)\mathrm{Sign}(W_{n m})$.
@@
 	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $z$ with a nonzero weight of the same sign as $S(n)$. 
-
 	So there is a non zero path from $m$ to $z$: $(m n) \pi$, whose sign is 
@@
 
-Using the concept of sign, now we introduce the key lemma for our theorem.
+Using the concept of sign, now we introduce the key lemma for Theorem \ref{th1}.
 
-\begin{definition}[Star and Sharp]
+\begin{definition}
+We define the following two input vectors $\vx^{*}, \vx^{\sharp}$ in $\cal B$: 
+	\begin{itemize}
+		\item $\vx^{*}$ is the input vector defined in the following way:
+		\begin {itemize}
+		 \item $x^*_{a_i}=\max(a_i)$ if $S(a_i)\in \{0,1\}$, and
+          \item $x^*_{a_i}=\min(a_i)$ otherwise, that is when $S(a_i)=-1$.
+	\end{itemize}
 
+		\item $\vx^{\sharp}$ is the input vector defined in the following way:
 		\begin{itemize}
-		\item $\vx^{*}$ is a input vector that for every node $a_i$, if $S(a_i)=1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=-1$, then $x_{a_i}$ is the minimal value of $a_i$ (if $S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
-
-		\item  $\vx^{\sharp}$ is a input vector that for every node $a_i$, if $S(a_i)=-1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=1$, then $x_{a_i}$ is the minimal value of $a_i$ (if $S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).
+			\item $x^{\sharp}_{a_i}=\min(a_i)$ if $S(a_i)\in \{0,1\}$, and
+			\item $x^{\sharp}_{a_i}=\max(a_i)$ otherwise, that is when $S(a_i)=-1$.
+		\end{itemize}
 	\end{itemize}
@@
 \begin{lemma}\label{lem:key1}\label{lemma2}
-
-	The input $\vx^*$ maximize all nodes $n$ that $S(n)=1$ and minimize all nodes $n$ that $S(n)=-1$.
-
-	Similarly, the input $\vx^\sharp$ maximize all nodes $n$ that $S(n)=-1$ and minimize all nodes $n$ that $S(n)=1$.
+For all $n$ with $S(n)=1$, we have $\val_{\vx^*}(n) = \max(n)$
+and $\val_{\vx^{\sharp}}(n) = \min(n)$.
+For all $n$ with $S(n)=-1$, we have $\val_{\vx^*}(n) = \min(n)$
+and $\val_{\vx^{\sharp}}(n) = \max(n)$.
 \end{lemma}
@@
 	Therefore we have the following inequalities:\begin{align*}
-		\max(c)\leq\sum_{b \in L_i, W_{bc }>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
-		\min(c)\geq\sum_{b \in L_i, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bisa}_c
+		\max(c)\leq\sum_{b \in L_i, W_{bc }>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bias}_c\\
+		\min(c)\geq\sum_{b \in L_i, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bias}_c
 	\end{align*}
@@
 
-	Notice that for all $x$, for either $S(c)=1$ or $S(c)=-1$, these two bounds are found in Lemma \ref{lemma2},
-	from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\sharp$.
+	%Notice that for all $x$, for either $S(c)=1$ or $S(c)=-1$, these two bounds are found in Lemma \ref{lemma2},
+	%from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\sharp$.
 

### 2024-01-24 Paper/introduction.tex

@@
 As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from
-$20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 8, Table \ref{tab:example}).
+$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}).
 On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).

### 2024-01-24 Paper/introduction.tex
edits to intro

--- 2024-01-20 Paper/introduction.tex
@@
-In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers.
-This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rationale: it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{szegedy}\dots
+Deep neural networks have demonstrated remarkable capabilities, achieving human-like or even superior performance across a wide range of tasks.
+However, their robustness is often compromised by their susceptibility to input perturbations.
+This vulnerability has catalyzed the verification community to develop various methodologies, each presenting a unique balance between completeness and computational efficiency \cite{katz2019marabou,Reluplex,deeppoly}.
+This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools.
+While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, 
+is it the case that all the images in the neighbourhood are classified in the same way.
+While some quite large DNNs (e.g.
+ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
+Actually, DNNs which are trained to be robust (using DiffAI \cite{DiffAI} or PGD \cite{PGD}) are easier to verify, while the DNNs trained in a {\em natural} way are harder to verify.
 
-In this context, application of DNNs in safety critical applications is cautiously envisioned.
+In this work, we concentrate on DNNs that are trained naturally, given the prevalence of techniques for {\em easier} DNNs.
+Our analysis is confined to DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
+Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown}\footnote{
+ As per competition reports, $\alpha$-$\beta$-Crown verifier often surpasses other competing techniques\cite{crown};  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+}.
+Perhaps, it is worth highlighting that these tools are  sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN Is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though the DNN is indeed robust.
+To dig further into their incompleteness,we first remark that high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
+Therefore, inaccurate bounds leads to incompletness.
+
+As a starting point, we sought to diagnose properties of DNNS that make them hard to verify; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
+Our key finding is a new notion of {\em compensations} to explain the {\em hardness} of DNNs that leads to inaccuracies
+We uncover that {\em compensations} 
+(see next paragraph) is the phenomenon creating inaccuracies.
+Formally, a compensating pair is a tuple of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
+Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
+That is, it is loaded by $(w+w') weight(a)$.
+As $w,w'$ have opposite sign, they will compensate (partly) each other.
+The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
+However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which all the efficient tools try to avoid because it is very expansive (could be exponential in the number of such ReLU nodes opened).
+
+In this paper, we present three main contributions addressing the challenges of inaccuracies in neural network computations due to compensating pairs of paths. 
+\begin{enumerate}
+	\item  As a first step, we establish, through Theorem \ref{th1}, the foundational understanding that these compensating pairs are the primary source of inaccuracies.
+This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs.
+Nonetheless, this insight lays the groundwork for our innovative approach: a Mixed Integer Linear Program (MILP) formulation for exact network abstraction.
+In this formulation, neuron weights are represented as linear variables, while ReLU nodes are either encoded exactly with binary variables or approximated through linear variables.
+While Linear Programming (LP) methods adeptly manage thousands of variables, the MILP approach encounters scalability challenges due to the binary variables, suggesting the potential for a simplified encoding for ReLUs not involved in compensating pairs.
+
+\item Our second contribution, delineated in Theorem \ref{th2}, introduces a refined encoding strategy.
+By exclusively employing binary variables for ReLU nodes within compensating path pairs and linear relaxations for others, we achieve precise bounds for the majority of algorithms under consideration.
+This selective binary variable application significantly reduces the computational complexity, yielding faster-solving encodings.
+However, this approach is not without its limitations, as the prevalence of compensating paths in practical scenarios renders the precise MILP encoding computationally intensive.
+
+\item Addressing the practicality concerns, our third contribution introduces Algorithm \ref{algo1}, a pragmatic solution leveraging our theoretical insights.
+By ranking ReLU nodes based on their contribution to inaccuracies, we differentiate their treatment in the MILP model.
+This strategy involves representing the most influential nodes with binary variables while applying linear relaxation to the others, striking a balance between computational efficiency and accuracy.
+Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
+This complexity is an upper bound, as e.g.
+Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
+Keeping $K$ reasonably low thus provides an efficient algorithm.
+By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
+An additional interesting point is that it is extremely easy to parallelize, as all the nodes in the same layer can be run in parallel.
+We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
+
+\end{enumerate}
+
+%   
+% 
+%
+%In this context, application of DNNs in safety critical applications is cautiously envisioned.
 For that to happen at a large scale, hard guarantees should be provided \cite{certification}, through e.g.
@@
 \cite{cutting}.
-
-While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, 
-is it the case that all the images in the neighbourhood are classified in the same way.
-While some quite large DNNs (e.g.
+%
+%While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, 
+%is it the case that all the images in the neighbourhood are classified in the same way.
+%While some quite large DNNs (e.g.
 ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
 Actually, DNNs which are trained to be robust (using DiffAI \cite{DiffAI} or PGD \cite{PGD}) are easier to verify, while the DNNs trained in a "natural" way are harder to verify.
-
-In this paper, we focus on DNNs trained in a "natural" way,
-%uncovering what makes the DNNs trained in a natural way so hard to verify (
-because for "easier" DNNs, adequate methods already exist. 
-To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-CROWN \cite{crown}.
+%
+%
+%In this paper, we focus on DNNs trained in a "natural" way,
+%%uncovering what makes the DNNs trained in a natural way so hard to verify (
+%because for "easier" DNNs, adequate methods already exist. 
+%To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-CROWN \cite{crown}.
 All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds.
@@
 We uncover that {\em compensations}
-(see next paragraph) is the phenomenon creating inaccuracies. We verified experimentally that a DNN trained in a natural way has heavier compensating pairs than DNNs trained in a robust way.
-
-Formally, a compensating pair is a pair of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
+%(see next paragraph) is the phenomenon creating inaccuracies. We verified experimentally that a DNN trained in a natural way has heavier compensating pairs than DNNs trained in a robust way.
+%
+%Formally, a compensating pair is a pair of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
 Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
@@
 
-Our first main contribution is to formally show, in Theorem \ref{th1}, that compensation is the sole reason for the inaccuracies as (most) efficient algorithms will compute exact bounds for all neurons if there is no compensating pair of paths at all.
-While this theorem is theoretically interesting, it is not usable in practice as (almost) all networks have some compensating pairs.
+%Our first main contribution is to formally show, in Theorem \ref{th1}, that compensation is the sole reason for the inaccuracies as (most) efficient algorithms will compute exact bounds for all neurons if there is no compensating pair of paths at all.
+%While this theorem is theoretically interesting, it is not usable in practice as (almost) all networks have some compensating pairs.
 However, this notion of compensating pairs opens a first interesting idea concerning an exact abstraction of the network using a Mixed Integer Linear Program \cite{MILP}, where the weight of each neuron is a linear variable, and ReLU node may be associated with binary variables (exact encoding) or linear variables (overapproximation).
@@
 
-Our second main contribution is to show formally in Theorem \ref{th2}, that 
-encoding all ReLU nodes on a pair of compensating paths with a binary variable,
-and using linear relaxation for the other ReLU nodes, will lead to exact bounds for (most) of the algorithms considered.
+%Our second main contribution is to show formally in Theorem \ref{th2}, that 
+%encoding all ReLU nodes on a pair of compensating paths with a binary variable,
+%and using linear relaxation for the other ReLU nodes, will lead to exact bounds for (most) of the algorithms considered.
 This theorem allows to restrict the number of integer variables, and thus to obtain encodings that are faster to solve.
@@
 
-Our third main contribution is more practical, proposing Algorithm \ref{algo1} based on this knowledge that compensating pair of paths are the reason for inaccuracy.
+%Our third main contribution is more practical, proposing Algorithm \ref{algo1} based on this knowledge that compensating pair of paths are the reason for inaccuracy.
 The idea is thus to use this information to rank the ReLU nodes in terms of importance, and only keep the most important ones as binary variables, and use linear relaxation for the least important ones.
-%More precisely, the algorithm will, as DeepPoly, consider layers one by one and neurons $b$ %on this layer one by one, selecting the heaviest pairs of compensating paths ending in $b$
-%and associating these nodes with a binary variable. Then an MILP tool such as Gurobi is used %to compute the lower and upper bound for node $b$. 
-Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
+%%More precisely, the algorithm will, as DeepPoly, consider layers one by one and neurons $b$ %on this layer one by one, selecting the heaviest pairs of compensating paths ending in $b$
+%%and associating these nodes with a binary variable. Then an MILP tool such as Gurobi is used %to compute the lower and upper bound for node $b$. 
+%Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
 This complexity is an upper bound, as e.g.
@@
 Keeping $K$ reasonably low thus provides an efficient algorithm.
-By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
+%By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
 An additional interesting point is that it is extremely easy to parallelize, as all the nodes in the same layer can be run in parallel.
@@
 
-This paper does not focus on producing the most efficient tool, and we did not spend engineering efforts to optimize it.
+%I suggest we move this to experimental evaluation
+%This paper does not focus on producing the most efficient tool, and we did not spend engineering efforts to optimize it.
 The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.

### 2024-01-24 Paper/introduction.tex
minor edits

@@
 
-\item Addressing the practicality concerns, our third contribution introduces Algorithm \ref{algo1}, a pragmatic solution leveraging our theoretical insights.
-By ranking ReLU nodes based on their contribution to inaccuracies, we differentiate their treatment in the MILP model.
-This strategy involves representing the most influential nodes with binary variables while applying linear relaxation to the others, striking a balance between computational efficiency and accuracy.
-Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
+\item Addressing practical concerns, our third contribution introduces Algorithm \ref{algo1}, a pragmatic solution that leverages our theoretical insights.
+This approach ranks ReLU nodes based on their contribution to inaccuracies and differentiates their treatment in the MILP model.
+The strategy involves using binary variables to represent the most influential nodes, while applying linear relaxation to the rest, thereby striking a balance between computational efficiency and accuracy.
+Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously.
+Furthermore, our comprehensive empirical evaluation indicates that Algorithm \ref{algo1} provides favorable trade-offs between accuracy and completeness compared to existing methods.
+
+%We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
+
+%KSM: I think this is a distraction in intro, so I suggest moving to later part
+% Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
 This complexity is an upper bound, as e.g.
@@
 Keeping $K$ reasonably low thus provides an efficient algorithm.
-By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
-An additional interesting point is that it is extremely easy to parallelize, as all the nodes in the same layer can be run in parallel.
-We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
+%By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
 
@@
 
-%I suggest we move this to experimental evaluation
+%KSM: I suggest we move this to experimental evaluation
 %This paper does not focus on producing the most efficient tool, and we did not spend engineering efforts to optimize it.

### 2024-01-24 Paper/introduction.tex
minor edits

@@
 
-As a starting point, we sought to diagnose properties of DNNS that make them hard to verify; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
+As a starting point, we sought to diagnose properties of DNNs that make them hard to verify; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
 Our key finding is a new notion of {\em compensations} to explain the {\em hardness} of DNNs that leads to inaccuracies

### 2024-01-24 Paper/introduction.tex
minor edits

@@
 As a starting point, we sought to diagnose properties of DNNs that make them hard to verify; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
-Our key finding is a new notion of {\em compensations} to explain the {\em hardness} of DNNs that leads to inaccuracies
-We uncover that {\em compensations} 
-(see next paragraph) is the phenomenon creating inaccuracies.
+Our key finding is a new notion of {\em compensations} to explain the {\em hardness} of DNNs that leads to inaccuracies.
 Formally, a compensating pair is a tuple of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.

### 2024-01-24 Paper/Paper_noProof.tex
update figure
fix problems
fix mistakes
proof

@@
 \usepackage{placeins}
+\usepackage{pgfplots}
 \usepackage{url}
@@
 \begin{enumerate}
-	\item $A_{zero}= \{a \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)=0\}$.
-	\item $A_{pos}= \{a \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)\geq0\}$.
-	\item  $A_{neg}= \{a \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)\leq0\}$.
+	\item $A_{zero}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)=0\}$.
+	\item $A_{pos}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\geq0\}$.
+	\item  $A_{neg}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\leq0\}$.
 	Let $A_{pure}=A_{pos} \cup A_{neg}$.
@@
 \begin{enumerate}
-	\item $B_{zero}= \{n \mid \forall \text{ path $\pi$ from $n$ to } z, weight(\pi)=0\}$.
-	\item $B_{open}$ is the set of neurones reachable from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
+	\item $B_{zero}= \{n \mid \forall \text{ path $\rho$ from $n$ to } z, weight(\rho)=0\}$.
+	\item $B_{open}$ is the set of neurones reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
 	\item $B_{pure}$ is the set of remaining neurons.
@@
 		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {\color{blue}$68.1\%$} & 
-		{\color{blue}$79.1\%$} & {\color{blue}$72.6\%$} & {\color{blue}$\mathbf{80.2\%}$} & $91.1 \%$ \\ 
-		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}612s$^\star$} & \\ \hline
+		{\color{blue}$79.1\%$} & {\color{blue}$72.6\%$} & {\color{blue}$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
+		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}697s$^\star$} & \\ \hline
 
@@
 the most accurate setting (slow fixed) of Compensate($K$) is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
-and from $17.6\%$ to $10.9\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in Compensate($K$) (see Section \ref{Discussion}).
+and from $17.6\%$ to $10.4\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in Compensate($K$) (see Section \ref{Discussion}).
 
@@
 	\centering
-\includegraphics[scale=0.7]{Graph.png}
+\begin{tikzpicture}
+	\begin{axis}[width=12cm,height=6cm,
+		xlabel={},
+		ylabel={},
+		title={runtime (seconds per node)},
+		legend pos=north west,
+		ymin=0,
+		xtick={1,2,3,4,5}, 
+		xticklabels={$5\times 100$, $8\times 100$, $5\times 200$, $8\times 200$, $6\times 500$},
+		]
+
+		\addplot[mark=square, red] coordinates {
+			(1, 0.15)
+			(2, 0.115)
+			(3, 0.163)
+			(4, 0.1856)
+			(5, 0.308)
+		};
+		\addlegendentry{fast adaptative}
+
+		\addplot[mark=triangle, blue] coordinates {
+			(1, 0.234)
+			(2, 0.2125)
+			(3, 0.206)
+			(4, 0.3)
+		};
+		\addlegendentry{fast fixed}
+
+	\end{axis}
+\end{tikzpicture}
 \end{figure}

### 2024-01-24 Paper/proofs.tex
proof

@@
 Let $\cal B$ be a neighbourhood of an input.
-First, notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
-then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal). 
 For convenience,
@@
 we will write $\max(n)$ to denote $\max_{\vx \in \cal B}(\Val_{\vx}(n))$, and $\min(n)$ to denote $\min_{\vx \in \cal B}(\Val_{\vx}(n))$.
+Notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
+then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).
 
-The following definition is the most important concept in this proof.
+We fix a target node $z$.
+We now define the partial sign function $S^z$, denoted $S$ when $z$ is clear from the context:
 
@@
 However, if there is no compensating pair of paths, 
-$S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
+$S$ is defined on all nodes: any node fulfills one of the above cases (1),(2),(3).
 
@@
 
-\begin{lemma}\label{lem:key1}\label{lemma2}
+\begin{lemma}
+	\label{lem:key1}
+	\label{lemma2}
 For all $n$ with $S(n)=1$, we have $\val_{\vx^*}(n) = \max(n)$
@@
 For all $n$ with $S(n)=-1$, we have $\val_{\vx^*}(n) = \min(n)$
-and $\val_{\vx^{\sharp}}(n) = \max(n)$.
+and $\val_{\vx^{\sharp}}(n) = \max(n)$. Further, for $L,L'$ two consecutive layers and $n$ on layer $L'$:
+$$\max(n)=\sum_{m \in L, W_{mn}>0}W_{mn} \max(\hat{m}) + \sum_{m \in L, W_{mn}<0}W_{mn} \min(\hat{m}) + bias_n$$
+$$\min(n)=\sum_{m \in L, W_{mn}>0}W_{mn} \min(\hat{m}) + \sum_{m \in L, W_{mn}<0}W_{mn} \max(\hat{m}) + bias_n$$
+
 \end{lemma}
@@
 Suppose this lemma is true up to layer $L_i$, we need to show this for layer $L_{i+1}$.
-Let $c$ be a node in layer $L_{i+1}$, then by definition, we have the following equation: \begin{align*}
-		c = \boldsymbol{bias}_c+\sum_{b\in L}W_{bc}\ReLU(b).
+Let $n$ be a node in layer $L_{i+1}$, then by definition, we have the following equation: \begin{align*}
+		\val_{\vx}(n) = \sum_{m\in L}W_{m n}\val_{\vx}(\hat{m})) + bias_n.
 	\end{align*}
 
-	Therefore we have the following inequalities:\begin{align*}
-		\max(c)\leq\sum_{b \in L_i, W_{bc }>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bias}_c\\
-		\min(c)\geq\sum_{b \in L_i, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bias}_c
+	By induction hypothesis, when input vector is $\vx^{*}$, for every $m$, if $S(m)=1$, then $\Val_{\vx^*}(\hat{m})=\max(\hat{m})$ and if $S(\hat{m})=-1$, then $\Val_{\vx^*}(\hat{m})=\min(\hat{m})$.
+Assume that $S(n)=1$.
+By applying Lemma \ref{lemma1} and the induction hypothesis:
+	\begin{align*}
+		\val_{\vx^*}(n) = \sum_{m \in L_i, W_{mn}>0}W_{mn} \max(\hat{m}) + \sum_{m \in L_i, W_{mn}<0}W_{mn} \min(\hat{m}) + bias_n\\
 	\end{align*}
 
-	Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $W_{bc}>0$; if $S(b)=-1$, then $W_{bc}<0$; if $S(b)=0$, then $W_{bc}=0$.
+	Further, we have the following inequality:
+	\begin{align*}
+		\max(n)\leq & \sum_{m \in L_i, W_{mn }>0}W_{mn} \max(\hat{m}) + \sum_{m \in L_i, W_{mn}<0}W_{mn} \min(\hat{m}) + bias_n\\
+		\leq & \val_{\vx^*}(n)
+	\end{align*}
 
-	By induction hypothesis, when input vector is $\vx^{*}$, for every $b$, if $S(b)=1$, then $\Val_{\vx}(b)=\max(b)$ and if $S(b)=-1$, then $\Val_{\vx}(b)=\min(b)$.
+	%If $S(m)=1$, then by Lemma \ref{lemma1}, $W_{mn}>0$; if $S(m)=-1$, then $W_{mn}<0$; if $S(m)=0$, then $W_{mn}=0$.
 
-	So combining formulas and above two facts, we will have that when the input vector is $\vx^*$, \begin{align*}
-		\max(c)&\geq\Val_{\vx^*}(c) \\
-		&= \sum_{b \in L_i, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
-		&\geq\max(c)
-	\end{align*}  Hence $\max(c)=\Val_{\vx^*}(c)$.
+	By definition of $\max$, we have $\val_{\vx^*}(n) \leq \max(n)$.
+	Combining the 2 formulas, we obtain $\max(n)=\Val_{\vx^*}(n)$.
 
-	Similarly, we can prove if $S(c)=-1$, $\min(c)=\Val_{\vx^*}(c)$. And similarly, we can prove this for $x^\sharp$. This is the induction step. \qed
+	We prove similarly that $\min(n)=\Val_{\vx^\sharp}(n)$,
+	and the case $S(n)=-1$. This concludes the induction. \qed
 \end{proof}
 
+\iffalse
 	As direct corollary of Lemma \ref{lem:key1}, we obtain:
@@
 		\label{cor1}
-		$$\max(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bias}_c$$
-		$$\min(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bias}_c$$
+		$$\max(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \min(\hat{b}) + bias_c$$
+		$$\min(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \max(\hat{b}) + bias_c$$
 	\end{corollary}
+
+\fi
 
@@
 
-	Once we have above corollary, things become very clear and simple. We now show that approximations like DeepPoly will generate the same bounds 
-	$\underline{f}(x)=\min(x)$ and $\bar{f}(x)=\max(x)$.
+	\subsubsection*{Bounds generated by Value Abstraction}
 
-	\paragraph{Approximation Bounds}
+	\smallskip
 
-	To prove that Approximation Bounds are the same as the exact bounds computed above, 
-	we show that even the box abstraction (which is easier) would reach the exact bounds.
-	We proceed inductively, and prove the inductive step.
-	The initialization is obvious as Box Abstraction/DeepPoly is always exact for the initialization layer.
-
-	\begin{lemma}
-		Let $L,L'$ be two consecutive layers.
-		Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by box abstraction equals to the exact lower and upper bounds of $m$ (as expressed above), i.e.
-		$\bar{f}(m)=\max(m)$ and $\underline{f}(m)=\min(m)$.
-
-		Then Box abstraction computes the exact lower and upper bounds for every node $n$ of layer $L'$, ie $\bar{f}(n)=\max(n)$ and $\underline{f}(n)=\min(n)$.
-	\end{lemma}
+	Let $[\alpha_n,\beta_n]$ be the bounds generated by the Box abstraction.
+	We show that these bounds are exact when there is no (weak) compensating pairs of paths, i.e. for all node $n$ of the DNN, we have $\alpha_n=\min(n)$ and $\beta_n=\max(n)$.
 
 \begin{proof}
-		Suppose $n$ is a node in $L'$ such that $S(n)\neq 0$ (otherwise, it is trivial). 
-		First assume $S(n)=1$. The case $S(n)=-1$ is similar.
+	 We show that inductively. The initialization is obvious as Box Abstraction is always exact for the first layer.
 
-		The Box absraction computes its upper bound using:
-		$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + bias_n$$
+	Let $n$ be node of the DNN. We set the target $z=n$ and consider the sign function $S^z=S^n=S$ corresponding to that node. By definition, $S(n)=1$.
+
+	The Box abstraction computes its upper bound using:
+	$$\beta_n= \sum_{W_{mn}>0} W_{mn} \beta_{\hat{m}} + \sum_{W_{mn}<0} W_{mn} \alpha_{\hat{m}} + bias_n$$
 
 	By induction hypothesis, we have 
-		$\bar{f}(\hat{m})=\max(\hat{m})$ and
-		$\underline{f}(\hat{m})=\min(\hat{m})$, thus 
-		applying Corollary \ref{cor1}, we obtain
-		$\bar{f}(n)=\max(n)$ and 
-		$\underline{f}(n)=\min(n)$.
+		$\beta_{\hat{m}}=\max(\hat{m})$ and
+		$\alpha_{\hat{m}}=\min(\hat{m})$, thus 
+		applying the second part of Lemma \ref{lem:key1}, we obtain
+		$\beta_n=\max(n)$.
 
-		Now, if $\underline{f}(n)=\min(n)<0$, 
-		then $\underline{f}(\hat{n})=\min(\hat{n})=0$, 
+		Similarly, we obtain $\alpha_n=\min(n)$.
+
+		Consider now $\alpha_{\hat{n}},\beta_{\hat{n}}$.
+		If $\alpha \leq 0$ then $\alpha_{\hat{n}}=0=\max(\hat{n})$.
+		Otherwise, $\alpha_{\hat{n}}=\alpha_n=\max(\hat{n})$.
+		In both case it is exact.
+
+		Similarly, if $\beta_n=\max(n)<0$, 
+		then $\beta_{\hat{n}}=\max(\hat{n})=0$, 
 		and otherwise 
-		$\underline{f}(\hat{n})=\min(\hat{n})=\underline{f}(n)=\min(n)$.
+		$\beta_{\hat{n}}=\max(\hat{n})=\beta_n=\max(n)$.
 
-		Similarly, 
-		if $\bar{f}(n)=\max(n)<0$, 
-		then $\bar{f}(\hat{n})=\max(\hat{n})=0$, 
-		and otherwise 
-		$\bar{f}(\hat{n})=\max(\hat{n})=\bar{f}(n)=\max(n)$.
+		Hence we have equality pre and post activation function. \qed
 
-		Hence we have equality before and after ReLU in all cases. \qed
 			\end{proof}
+
+This shows the statement of Theorem 1 with the weaker statement that there is no weak compensating pairs of paths.
 
@@
 	\begin{proof}
-		If it has a weak compensating pair of two paths, $P_1,P_2$, then there exists a segment in two paths starting from the same node and end with the same node, but the weight along two segment have different signs.
-And this will also be a compensating pair.
-\qed
+		By contradiction, if there is a weak compensating pair of two paths, $\rho_1,\rho_2$, 
+		then consider the common nodes by increasing layer $n_1 \cdots n_k$ in $\rho_1,\rho_2$ (including the initial and final nodes).
+		Assume that there is no compensating pair.
+		It means that all the segment of $\rho_1,\rho_2$ from $n_i$ to $n_{i+1}$ have the same sign (they have no nodes in common but the initial and final nodes).
+		Hence $\rho_1$ and $\rho_2$ have the same sign, a contradiction with $\rho_1,\rho_2$ being a weakly compensating pair.  \qed
 	\end{proof}
 
-	This finishes the proof for compensating pair rather than weak version.
+	This finishes the proof of Theorem \ref{th1}.
+
+	\newpage
 
@@
 
-			In this section, we will prove theorem \ref{th2}. We will prove it by proving the following weak theorem:
+			In this section, we will prove theorem \ref{th2}. We first prove the following weaker theorem:
 
@@
 				Suppose $\mathcal{D}$ is a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$. 
-
-				Using MILP, if every nodes $b$ in any weak compensating pair
-				$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
-				bounds computed by MILP are the exact maximal and minimal value of $z$.
+				Let $X$ be the set of nodes $n$ such that there is a weak compensating path 
+				passing by $n$ (except its source and target nodes).
+				Then $\MILP_X$ computes the exact bounds $[\alpha,\beta]$ for $z$,
+				i.e. $\alpha=\min(z)$ and $\beta=\max(z)$.
 			\end{theorem}
@@
 			\begin{definition}
-				We define a decomposition of the input nodes set $A_{pure}\sqcup A_{open}$ as follows:  
+				We define a partition of the set $A$ of input nodes as $A_{zero} \sqcup A_{pure}\sqcup A_{open}$, with:  
 				\begin{itemize}
-					\item $a_k \in A_{pure}$  if either
+					\item $A_{zero}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\pi)=0\}$.
+
+					\item $a_k \in A_{pure}$  if $a \notin A_{zero}$ and either
 					\begin{enumerate}
@@
 					\end{enumerate}
-					That is, $a_k$ is not a source of a weak compensating pair. 	We write $A_{pure}$ by $I$ for short.
-					\item $a_k \in A_{open}$ if $a_k \notin A_{pure}$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
-					one with positive and one with negative weight. 	We write $A_{open}$ by $J$ for short.
+					That is, $a_k$ is not a source of a weak compensating pair. We denote 
+					$A_{pure}$ by $I$ for short.
+					\item $a_k \in A_{open}$ iff $a_k \notin A_{pure} \sqcup A_{zero}$, that is there exists two paths $\rho,\rho'$ from $a_k$, one with positive and one with negative weight.
+	We denote $A_{open}$ by $J$ for short.
 				\end{itemize}
@@
 			\begin{lemma} \label{lem:open_node_2}
-				A node $b$ in a hidden layer will not be in a weak compensating path if and only if one of the following happens:
+				A node $b$ in a hidden layer will not be on a weak compensating path if and only if one of the following happens:
 				\begin{enumerate}
@@
 
-			We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.	We denote $B_{open}$ the set of all nodes $b$ in a weak compensating path.
+			We denote $B_{zero}$ the set of nodes $b$ that case 1 holds, and denote $B_{pure}$ the set of nodes $b$ such that case 2 holds but case 1 does not hold.
+			We denote $B_{open}$ the set of all nodes $b$ in a weak compensating path (remaining cases).
 
@@
 			\begin{lemma}\label{lem:subnetwork}
-				$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward.
-That is to say, if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$.
-We call this sub-network $D_I$.
-In $D_I$, there is no compensating pair.
+				$B_{pure}$ and $I$ form a sub-network, that is, 
+				for $n \in B_{pure}$, for every path $\rho$ from $m$ to $n$
+				either $m \in B_{pure}\cup I$ or $weight(\rho)=0$.
 			\end{lemma}
+
+			We call $D_I$ the subnetwork  made of nodes in $B_{pure}\cup I$.
+			In $D_I$, there is no weakly compensating pair.
 
@@
 
-			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. Because now we allow weak compensating paths, the sign function is no longer defined on all nodes.
-
-			\begin{definition}\label{sign_of_nodes_in_I_2}
-				We define a partial sign function $S$ over nodes $n$ such that : 	
-				\begin{enumerate} 
-					\item if all paths from $n$ to $z$ have 0 weight, then $S(n)=0$; 
-					\item if all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, then $S(n)=1$; 
-					\item if all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, then $S(n)=-1$.
-					\item Otherwise $S(n)$ is undefined.
-				\end{enumerate}
-			\end{definition}
-
-			Notice that $S$ is defined on all nodes $a_i \in I$. For the domain of $S$, we introduce the following lemma:
+			Recall the sign function of nodes from Definition \ref{sign_of_nodes}.
+Because weak compensating paths are allowed, the sign function is no longer defined on all nodes.
+$S$ is defined on all nodes $a_i \in I$.
+			Further, we have:
 
 			\begin{lemma}\label{lem:sign}
-				For a node $b$, if there exists at least one path from a node $a_i\in I$ with nonzero weight, then  $S$ is defined on $b$.
+				For a node $n$, if there exists at least one path from a node $a_i\in I$ to $n$ with nonzero weight, then $S$ is defined on $n$.
 			\end{lemma}
@@
 			\begin{proof}
-				Otherwise, suppose there exists two paths $P_1,P_2$ from $b$ to $z$ with (strictly) different signs.
-Then consider $\langle a_i,b\rangle+P_1$ and $\langle a_i,b\rangle+P_2$, they are two paths with weights with different signs.
-This is a contradiction since $a_i\in I$.
+				By contradiction, suppose that there exists two paths $\rho_1,\rho_2$ from $n$ to $z$ with (strictly) different signs.
+The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$.
 \qed
 			\end{proof}
-			Therefore, for any node $b$  that $S$ is undefined on $b$, it only depends on input nodes in $J$.
 
+			Hence for any node $m$ such that $S$ is undefined on $m$, value of $m$ can only depends upon input nodes in $J$.
+
+			\iffalse
 			\begin{lemma}
-				If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $Sign(W_{bc})S(c)=S(b)$.
+				If $n$ is in the layer after $m$, then $S(n), S(m)$ are both defined
+				with $S(n) \neq 0$ and $W_{mn}\neq 0$, then $sign(W_{mn})S(n)=S(m)$.
 			\end{lemma}
@@
 
+			\fi
+
 			\begin{lemma}\label{lem:subnetwork2}
-				The input set $J$ with nodes that only depends on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $D_J$.
+				The input set $J \cup B_{open}$ forms a sub-network, denoted $D_J$. 
+				$S$ is undefined on all nodes of $D_J$.
 			\end{lemma}

### 2024-01-24 Paper/introduction.tex
intro

@@
-Deep neural networks have demonstrated remarkable capabilities, achieving human-like or even superior performance across a wide range of tasks.
+Deep neural networks have demonstrated remarkable capabilities, achieving \newline human-like or even superior performance across a wide range of tasks.
 However, their robustness is often compromised by their susceptibility to input perturbations.
@@
 This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools.
-While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, 
+While the verification engines are generic, the benchmarks usually focus on local robustness, i.e.
+given a DNN, an image and a small neighbourhood around this image,
 is it the case that all the images in the neighbourhood are classified in the same way.
 While some quite large DNNs (e.g.
-ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
+ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of {\em undecided} inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
 Actually, DNNs which are trained to be robust (using DiffAI \cite{DiffAI} or PGD \cite{PGD}) are easier to verify, while the DNNs trained in a {\em natural} way are harder to verify.
@@
 Our analysis is confined to DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
-Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown}\footnote{
- As per competition reports, $\alpha$-$\beta$-Crown verifier often surpasses other competing techniques\cite{crown};  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{
+	\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses other competing techniques;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
 }.
@@
 
-As a starting point, we sought to diagnose properties of DNNs that make them hard to verify; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
-Our key finding is a new notion of {\em compensations} to explain the {\em hardness} of DNNs that leads to inaccuracies.
-Formally, a compensating pair is a tuple of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
+{\color{red}
+As a starting point, we sought to understand properties of DNNs that make them hard to verify.
+Our key finding is a new notion of {\em compensations}, that leads to inaccuracies of bounds and thus explain the {\em hardness} of verifying some DNNs.} Formally, a compensating pair is a tuple of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
 Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
@@
 However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which all the efficient tools try to avoid because it is very expansive (could be exponential in the number of such ReLU nodes opened).
+%; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
 
-In this paper, we present three main contributions addressing the challenges of inaccuracies in neural network computations due to compensating pairs of paths. 
+Our three main contributions address the challenges of inaccuracies in neural network computations due to compensating pairs of paths:
 \begin{enumerate}
-	\item  As a first step, we establish, through Theorem \ref{th1}, the foundational understanding that these compensating pairs are the primary source of inaccuracies.
+	\item  Our first main contribution establishes, through Theorem \ref{th1}, the foundational understanding that the compensating pairs are the 	%primary 
+	source of {\color{red}all} inaccuracies, 
+	{\color{red} as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate.}
 	This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs.
-Nonetheless, this insight lays the groundwork for our innovative approach: a Mixed Integer Linear Program (MILP) formulation for exact network abstraction.
-In this formulation, neuron weights are represented as linear variables, while ReLU nodes are either encoded exactly with binary variables or approximated through linear variables.
-While Linear Programming (LP) methods adeptly manage thousands of variables, the MILP approach encounters scalability challenges due to the binary variables, suggesting the potential for a simplified encoding for ReLUs not involved in compensating pairs.
+Nonetheless, this insight lays the groundwork for our innovative approach, {\color{red}{\em relaxing} the usual but inefficient Mixed Integer Linear Program (MILP) formulation encoding exactly DNNs \cite{MILP}.
+To compute bounds for $z$, we encode as binary variables (the costly ones) only ReLU nodes on compensating paths {\em with target $z$}; other nodes, in particular those on compensating paths to neurons before $z$ are encoded using the much more efficient linear relaxation.
+To take into account indirectly the compensating paths to previous nodes, we inductively compute bounds for every neuron layer by layer, and use these bounds of previous neurons in the MILP encoding for $z$.
+This is more efficient, as the number of binary nodes is strongly reduced.
+However, the question remains how accurate is it?}
 
-\item Our second contribution, delineated in Theorem \ref{th2}, introduces a refined encoding strategy.
-By exclusively employing binary variables for ReLU nodes within compensating path pairs and linear relaxations for others, we achieve precise bounds for the majority of algorithms under consideration.
-This selective binary variable application significantly reduces the computational complexity, yielding faster-solving encodings.
-However, this approach is not without its limitations, as the prevalence of compensating paths in practical scenarios renders the precise MILP encoding computationally intensive.
+\item {\color{red} Our second main contribution, delineated in Theorem \ref{th2}, answers this question, showing that this abstraction is fully accurate, in that the bounds computed in such a way for neuron $z$ correspond exactly to the mininmal and maximal values reachable by inputs of the DNN.
+Again, the prevalence of compensating paths in actual DNNs renders this algorithm computationally intensive because the number of binary variables is still too high.}
 
-\item Addressing practical concerns, our third contribution introduces Algorithm \ref{algo1}, a pragmatic solution that leverages our theoretical insights.
-This approach ranks ReLU nodes based on their contribution to inaccuracies and differentiates their treatment in the MILP model.
-The strategy involves using binary variables to represent the most influential nodes, while applying linear relaxation to the rest, thereby striking a balance between computational efficiency and accuracy.
-Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously.
-Furthermore, our comprehensive empirical evaluation indicates that Algorithm \ref{algo1} provides favorable trade-offs between accuracy and completeness compared to existing methods.
+\item Our third main contribution addresses this practical concern, introducing 
+Algorithm \ref{algo1}, a pragmatic solution that leverages our theoretical insights. This approach ranks ReLU nodes based on {\color{red} 
+the weights of the compensating paths they belong to,
+and differentiates their treatment in the MILP model (binary for heavy, linear for light). 
+%Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously. Furthermore, 
+Our comprehensive empirical evaluation indicates that Algorithm \ref{algo1} provides favorable trade-offs between accuracy and completeness compared to existing methods, lowering the number of 
+undecided inputs from $17.6\%$ ($\beta$-Crown \cite{crown}) to $10.4\%$ 
+on DNN $8 \times 200$ (Table \ref{tab:example}), even verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN (Table \ref{tab:example3}).}
 
@@
 
-\smallskip
+\section{Comparison with Related Works}
 
-\noindent {\bf Comparison with related work:} we compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
+We compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
 Compared with the exact encoding of a DNN using MILP \cite{MILP},

### 2024-01-24 Paper/Paper_noProof.tex
intro
table 6 may be.

@@
 We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
-
-\newpage
 
@@
 
-\newpage
-
 Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long timeouts ({\em refined} BaB is more accurate than pureBaB on these networks).
@@
 \begin{tikzpicture}
-	\begin{axis}[width=12cm,height=6cm,
+	\begin{axis}[width=10cm,height=5cm,
 		xlabel={},
@@
 This indicates that Compensate($K$) can be run on larger DNNs without hitting the same complexity wall as pure BaB.
+
+\begin{table}[]
+	\centering
+	\begin{tabular}{|c|c|cc||cc||c|}
+		\hline
+		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
+		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}Comp (slow) \,}}
+		& Upper\\ 
+		& / CROWN & TO=300s & TO=3000s & {\color{blue}adapt} & {\color{blue}fixed} & Bound\\
+		\hline \hline
+		$8\times200$\  &   $25\%$? & $72\%$? & $75\%$? & {\color{blue}$75.5\%$?}  & {\color{blue}$\mathbf{77\%}$} & $89\%$? \\ 
+		$\epsilon = 0.015$ & 17s & 95s? & 500s? & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
+	\end{tabular}
+	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
+	\label{tab:example3}
+\end{table}
 

### 2024-01-24 Paper/Paper_noProof.tex
table 6

@@
 		title={runtime (seconds per node)},
-		legend pos=north west,
+		legend pos=south east,
 		ymin=0,

### 2024-01-24 Paper/Paper_noProof.tex
fig 5
fig2

@@
 		ylabel={},
-		title={runtime (seconds per node)},
 		legend pos=south east,
@@
 		]
+
+		\addplot[mark=triangle, blue] coordinates {
+			(1, 0.234)
+			(2, 0.2125)
+			(3, 0.206)
+			(4, 0.3)
+		};
+		\addlegendentry{fast fixed}
 
@@
 
-		\addplot[mark=triangle, blue] coordinates {
-			(1, 0.234)
-			(2, 0.2125)
-			(3, 0.206)
-			(4, 0.3)
-		};
-		\addlegendentry{fast fixed}
-
 	\end{axis}
 \end{tikzpicture}
+\caption{runtime (seconds per node)}
+\label{fig2}
 \end{figure}

### 2024-01-25 Paper/Paper_noProof.tex
table 6
introduction and state of the art

@@
 \newcommand{\B}{\mathrm{B}}
+
+\newcommand{\CMP}{{\textrm{CMP}}\ }
 
@@
 		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
-		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}Comp (slow) \,}}
+		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}\CMP slow \,}}
 		& Upper\\ 
@@
 		\hline \hline
-		$8\times200$\  &   $25\%$? & $72\%$? & $75\%$? & {\color{blue}$75.5\%$?}  & {\color{blue}$\mathbf{77\%}$} & $89\%$? \\ 
-		$\epsilon = 0.015$ & 17s & 95s? & 500s? & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
+		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
+		$\epsilon = 0.015$ & 17s & 95s? & 442s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
 	\end{tabular}
 	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
-	\label{tab:example3}
+	\label{tab:example4}
 \end{table}

### 2024-01-25 Paper/introduction.tex
introduction and state of the art

@@
 \item Our third main contribution addresses this practical concern, introducing 
-Algorithm \ref{algo1}, a pragmatic solution that leverages our theoretical insights. This approach ranks ReLU nodes based on {\color{red} 
+\CMP (Algorithm \ref{algo1}), a pragmatic solution that leverages our theoretical insights. This approach ranks ReLU nodes based on {\color{red} 
 the weights of the compensating paths they belong to,
@@
 %Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously. Furthermore, 
-Our comprehensive empirical evaluation indicates that Algorithm \ref{algo1} provides favorable trade-offs between accuracy and completeness compared to existing methods, lowering the number of 
-undecided inputs from $17.6\%$ ($\beta$-Crown \cite{crown}) to $10.4\%$ 
-on DNN $8 \times 200$ (Table \ref{tab:example}), even verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN (Table \ref{tab:example3}).}
+Our comprehensive empirical evaluation indicates that \CMP provides favorable trade-offs between accuracy and completeness compared to existing methods, 
+%lowering the number of 
+%undecided inputs from $17.6\%$ ($\beta$-Crown \cite{crown}) to $10.4\%$ 
+%on DNN $8 \times 200$ (Table \ref{tab:example}), even 
+verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN (Table \ref{tab:example3}).}
 
@@
 
-We compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
+We compare CMP with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
 Compared with the exact encoding of a DNN using MILP \cite{MILP},
 we select a restricted number of ReLU nodes based on compensating strength to scale to larger DNNs while maintaining good accuracy. Further, compared to MIPplanet \cite{MIPplanet} which 
-uses a different selection of ReLU nodes, we compute bounds for all neurons iteratively, reducing drastically the number of ReLU nodes represented exactly for a given neuron (ReLU nodes which were considered for neurons in previous layers are not represented exactly for that neuron, while MIPplanet would need to represent all those ReLU nodes exactly), using many fast computations, more efficient than one large computation.
+uses a different selection of ReLU nodes, we compute bounds for all neurons iteratively, reducing drastically the number of ReLU nodes represented exactly for a given neuron,
+%(ReLU nodes which were considered for neurons in previous layers are not represented exactly for that neuron, while MIPplanet would need to represent all those ReLU nodes exactly), 
+using many fast computations, more efficient than one large computation.
 
@@
 Concerning PRIMA \cite{prima}, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do).
-This allows to keep very efficiently dependencies from potentially many layers beforehand.
+This allows to maintain dependencies from potentially many layers beforehand.
 We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurons.
-Our method is more accurate locally, but we will tend to lose precision for dependencies created many layers ago.
-Experimental results tend to show that most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago).
+Our method is more accurate locally, but we will tend to lose precision for dependencies created several layers ago.
+Most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago).
 Also, the dependencies between nodes limit the parallelism, unlike in our method, which explains why we obtain both faster and more accurate results than PRIMA.
 
-For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
-On simple networks, such as those trained robust, this is particularly efficient because branch and bound can find very efficiently the bounds focusing on the actual question, considering the important branches, while our algorithm will be less efficient as it has to consider each node one by one from the start.
-However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider.
+$\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
+On simple networks, such as those trained robust, branch and bound is  particularly efficient as it consider the important branches for the actual property to verify, while our algorithm is less efficient as it has to consider each node one by one from the start, including nodes whose bounds are not important.
+However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider (Table \ref{tab:example3}).
 
-On such complex DNNs, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
+On such complex DNNs, PRIMA and $\alpha,\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
 In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
@@
 The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from
-$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}).
+As the depth grows, the more work is left to BaB and our algorithm is more accurate,
+%lowering the gap of verified images to the upper bound \cite{attack} down from 
+%$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}). 
 On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).

### 2024-01-25 Paper/introduction.tex
introduction and CMP

@@
 On simple networks, such as those trained robust, branch and bound is  particularly efficient as it consider the important branches for the actual property to verify, while our algorithm is less efficient as it has to consider each node one by one from the start, including nodes whose bounds are not important.
-However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider (Table \ref{tab:example3}).
+However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider:
+$\alpha,\beta$ CROWN only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly in the same time (Table \ref{tab:example3}).
 
@@
 This would be infeasible without the selection based on the compensation.
-The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and our algorithm is more accurate,
+The refined version of $\alpha,\beta$ CROWN is particularly accurate on small DNNs.
+As the depth grows, the more work is left to BaB and our algorithm is more accurate.
 %lowering the gap of verified images to the upper bound \cite{attack} down from 
 %$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}).
-On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).
 

### 2024-01-25 Paper/introduction.tex
introduction

@@
 %on DNN $8 \times 200$ (Table \ref{tab:example}), even 
-verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN (Table \ref{tab:example3}).}
+verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN trained naturally (Table \ref{tab:example3}).}
 

### 2024-01-25 Paper/introduction.tex
related work

@@
 On simple networks, such as those trained robust, branch and bound is  particularly efficient as it consider the important branches for the actual property to verify, while our algorithm is less efficient as it has to consider each node one by one from the start, including nodes whose bounds are not important.
-However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider:
-$\alpha,\beta$ CROWN only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly in the same time (Table \ref{tab:example3}).
+However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider: Branch and Bound verifies only $3.5\%$ more images ($44.5\%$ from $41\%$) by enlarging the runtime by 66x (from 30s to 2000s), see Table \ref{tab:example3}.
 

### 2024-01-25 Paper/introduction.tex
related work

@@
 The refined version of $\alpha,\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and our algorithm is more accurate.
+As the depth grows, the more work is left to BaB and \CMP is more accurate (Table \ref{tab:example}).
 %lowering the gap of verified images to the upper bound \cite{attack} down from 
@@
 Finally, algorithms abstracting the network (e.g.
-Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}$\ldots$ These algorithms have been developed to be complete, so they are much slower but also more accurate than what we propose.
+Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, \CMP $\ldots$ These algorithms have been developed to be complete, so they are much slower but also more accurate than what we propose.

### 2024-01-25 Paper/introduction.tex
edits

--- 2024-01-25 Paper/introduction.tex
@@
 	\item  Our first main contribution establishes, through Theorem \ref{th1}, the foundational understanding that the compensating pairs are the 	%primary 
-	source of {\color{red}all} inaccuracies, 
-	{\color{red} as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate.}
+	source of all inaccuracies, 
+	 as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate.
 	This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs.
-Nonetheless, this insight lays the groundwork for our innovative approach, {\color{red}{\em relaxing} the usual but inefficient Mixed Integer Linear Program (MILP) formulation encoding exactly DNNs \cite{MILP}.
+Nonetheless, this insight lays the groundwork for our innovative approach, {\em relaxing} the usual but inefficient Mixed Integer Linear Program (MILP) formulation encoding exactly DNNs \cite{MILP}.
 To compute bounds for $z$, we encode as binary variables (the costly ones) only ReLU nodes on compensating paths {\em with target $z$}; other nodes, in particular those on compensating paths to neurons before $z$ are encoded using the much more efficient linear relaxation.
@@
 This is more efficient, as the number of binary nodes is strongly reduced.
-However, the question remains how accurate is it?}
+However, the question remains how accurate is it?
 
@@
 
-\item Our third main contribution addresses this practical concern, introducing 
-\CMP (Algorithm \ref{algo1}), a pragmatic solution that leverages our theoretical insights. This approach ranks ReLU nodes based on {\color{red} 
-the weights of the compensating paths they belong to,
-and differentiates their treatment in the MILP model (binary for heavy, linear for light). 
-%Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously. Furthermore, 
-Our comprehensive empirical evaluation indicates that \CMP provides favorable trade-offs between accuracy and completeness compared to existing methods, 
-%lowering the number of 
-%undecided inputs from $17.6\%$ ($\beta$-Crown \cite{crown}) to $10.4\%$ 
-%on DNN $8 \times 200$ (Table \ref{tab:example}), even 
-verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN trained naturally (Table \ref{tab:example3}).}
+\item Our third primary contribution addresses a practical concern by introducing Algorithm \ref{algo1}, a pragmatic solution that builds on our theoretical insights.
+This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones.
+Our extensive empirical evaluation reveals that Algorithm \ref{algo1} achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
+It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$ (refer to Table \ref{tab:example}).
+Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN configuration (as detailed in Table \ref{tab:example3}).
 
@@
 
-We compare CMP with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
+We compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
 Compared with the exact encoding of a DNN using MILP \cite{MILP},
 we select a restricted number of ReLU nodes based on compensating strength to scale to larger DNNs while maintaining good accuracy. Further, compared to MIPplanet \cite{MIPplanet} which 
-uses a different selection of ReLU nodes, we compute bounds for all neurons iteratively, reducing drastically the number of ReLU nodes represented exactly for a given neuron,
-%(ReLU nodes which were considered for neurons in previous layers are not represented exactly for that neuron, while MIPplanet would need to represent all those ReLU nodes exactly), 
-using many fast computations, more efficient than one large computation.
+uses a different selection of ReLU nodes, we compute bounds for all neurons iteratively, reducing drastically the number of ReLU nodes represented exactly for a given neuron (ReLU nodes which were considered for neurons in previous layers are not represented exactly for that neuron, while MIPplanet would need to represent all those ReLU nodes exactly), using many fast computations, more efficient than one large computation.
 
@@
 Concerning PRIMA \cite{prima}, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do).
-This allows to maintain dependencies from potentially many layers beforehand.
+This allows to keep very efficiently dependencies from potentially many layers beforehand.
 We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurons.
-Our method is more accurate locally, but we will tend to lose precision for dependencies created several layers ago.
-Most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago).
+Our method is more accurate locally, but we will tend to lose precision for dependencies created many layers ago.
+Experimental results tend to show that most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago).
 Also, the dependencies between nodes limit the parallelism, unlike in our method, which explains why we obtain both faster and more accurate results than PRIMA.
 
-$\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
-On simple networks, such as those trained robust, branch and bound is  particularly efficient as it consider the important branches for the actual property to verify, while our algorithm is less efficient as it has to consider each node one by one from the start, including nodes whose bounds are not important.
-However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider: Branch and Bound verifies only $3.5\%$ more images ($44.5\%$ from $41\%$) by enlarging the runtime by 66x (from 30s to 2000s), see Table \ref{tab:example3}.
+For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
+On simple networks, such as those trained robust, this is particularly efficient because branch and bound can find very efficiently the bounds focusing on the actual question, considering the important branches, while our algorithm will be less efficient as it has to consider each node one by one from the start.
+However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider.
 
-On such complex DNNs, PRIMA and $\alpha,\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
+On such complex DNNs, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
 In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
@@
 This would be infeasible without the selection based on the compensation.
-The refined version of $\alpha,\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and our algorithm is more accurate.
-%lowering the gap of verified images to the upper bound \cite{attack} down from 
-%$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}).
+The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs.
+As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from
+$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}).
+On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).
 

### 2024-01-25 Paper/proofs.tex
proof

@@
 			\begin{lemma}\label{lem:subnetwork}
-				$B_{pure}$ and $I$ form a sub-network, that is, 
+				$I \cup B_{pure} $ forms a sub-network, denoted $D_I$. That is, 
 				for $n \in B_{pure}$, for every path $\rho$ from $m$ to $n$
 				either $m \in B_{pure}\cup I$ or $weight(\rho)=0$.
+				Further, in $D_I$, there is no (weakly) compensating pair.
 			\end{lemma}
-
-			We call $D_I$ the subnetwork  made of nodes in $B_{pure}\cup I$.
-			In $D_I$, there is no weakly compensating pair.
 
@@
 			\begin{lemma}\label{lem:subnetwork2}
-				The input set $J \cup B_{open}$ forms a sub-network, denoted $D_J$. 
-				$S$ is undefined on all nodes of $D_J$.
+				$J \cup B_{open}$ forms a sub-network, denoted $D_J$.
+				That is, for $n \in B_{open}$, for every path $\rho$ from $m$ to $n$
+				either $m \in B_{open}\cup J$ or $weight(\rho)=0$. 
+				Further, $S$ is undefined on all nodes of $D_J$.
 			\end{lemma}
@@
 			\begin{proof}
-				This is because if there exists nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ not in $J$ but this means so does $c$, a contradiction.
-Therefore any $b$ such that $W_{bc}\neq 0$ is also in above set.
-\qed
+				By contradiction, assume that there exists two nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in $D_J$ and $b \notin D_J$, then 
+				there is a path $\rho$ from an input node $a_i \notin J$ to $b$
+				 with nonzero weight. Then $\rho \cdot bc$ is a path from $a_i \notin J$ 
+				 to $c$ with non zero weight, a contradiction. \qed
 			\end{proof}
@@
 
-			We denote $\boldsymbol{x}_S$ for any subset $S$ of input nodes to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
-We also use $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and $\Val(z)=\Val_{\boldsymbol{x}}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
-For a node $b$ that $S$ is not defined on it, $b$ only depends on $J$; so, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ will be fixed.
+			For an input $\vx$ and a subset $S$ of input nodes, we denote by $\boldsymbol{x}_S$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
+We use $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and $\Val(z)=\Val_{\boldsymbol{x}}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
+			For a node $b$ for which $S$ is undefined, $b$ only depends on $J$; so, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ will be fixed.
 
@@
 			\begin{lemma} \label{lem:reach_max_2}
+				Let $b$ be an output node or a node in a hidden layers such that $S(b)=1$. Then for any valuation $\boldsymbol{x}^0_J$,	we have: 
+				$$\max_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^*,\boldsymbol{x}^0_J}(b).$$
 
-				Assume $b$ is the output node or a node in hidden layers that $S(b)=1$, then   for any valuation $\boldsymbol{x}^0_J$, 
-				we have: $$\max_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J=\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^*,\boldsymbol{x}^0_J}(b).$$
-
-				If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$, or replacing $\max$ by $\min$. 
+				If $S(b)=-1$, then a similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$. The opposite holds for $\min_{\boldsymbol{x}_I}$.
 			\end{lemma}
@@
 
-				For any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers
-				as bias.
+				For any fixed input vector $\boldsymbol{x}^0_J$, consider the DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ 
+				%and their propagation in hidden layers 	
+				as bias. We denote $\val'$ values of nodes In this DNN $D'$.
+				 We have $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z) = \val'_{\vx}(\boldsymbol{x}_I)(z)$.
+
 				In the simplified $D'$, there is no compensating path because of the definition of $I$.
@@
 
-			\subsection{MILP abstraction}
+			From Lemma \ref{lem:reach_max_2}, we have the following corrolary:
 
-			The standard MILP abstraction use the abstraction from \cite{MILP}, 
-			where each variable $\alpha_b$ for the ReLU from $b$ to $\hat{b}$ is:
-			\begin{itemize}
-				\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \notin B_{open}$
-				\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \in B_{open}$
-			\end{itemize}
+			\begin{corollary}
+			For a node $b$ with $S(b)=1$:
 
-			Now consider the MILP framework for all hidden and output nodes layer by layer (to compute their bounds, and use the bounds of previous layers to build the MILP models of current layer), with ReLUs being either linear or binary depending on whether $b \in B_{open}$ or not.
-We call this standard framework.
+			$$\max(b)=\max_{\vx_j} \val_{\vx^{\star}_I,\vx_J}(b)$$
 
-			For a node $b$ in a hidden layer or the output layer, we denote by $\UB(b)$ the upper bound on $b$ and $\LB(b)$ the lower bound on $b$ considering the MILP constraints above.
+			and for $S(b)=-1$:
 
-			\begin{lemma}
-				In the standard $MILP$ framework, both $D_I$ and $D_J$ are accurate in the sense that for any $b$ in $D_I$ or $D_J$, $\UB(b)=\max(b)$ and $\LB(b)=\min(b)$.
-			\end{lemma}
+			$$\max(b)=\max_{\vx_j} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
+			\end{corollary}
 
-			\begin{proof}
-				For $D_I$, it is because of no compensating as proved in the first section. For $D_J$, it is because all nodes are either opened or constants. \qed
-			\end{proof}
+			\subsection{$\MILP_X$ is accurate}
+
+			We denote by $X=B_{open}$, and consider $\MILP_{X}$.
+			Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$.
+
+			%\begin{lemma}
+			%	Both $D_I$ and $D_J$ are accurate in the sense that for any $b$ in $D_I$ or %$D_J$, $\UB(b)=\max(b)$ and $\LB(b)=\min(b)$.
+			%\end{lemma}
+
+			%\begin{proof}
+			%	For $D_I$, it is because of no compensating as proved in the first section. %For $D_J$, it is because all nodes are either opened or constants. \qed
+			%\end{proof}
 
@@
 			%\end{definition}
-
+\iffalse			
 			For input vectors $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$, let $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ be the upper bound in the above fixed formulation and framework while the input $\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$ is fixed: that is, besides the constraints in above MILP models, we add new constraints $\boldsymbol{x}_I,\boldsymbol{x}_J=\boldsymbol{x}^0_I,\boldsymbol{x}^0_J$.
@@
 
-			We want to show that $\mathrm{UB}(z) = \max (z)$ and $\mathrm{LB}(z) = \min (z)$ for the unique output nodes.
-In fact, we will prove this for all $c\notin B_{zero}$ .
-As the MILP abstraction is a sound over-approximation,
-			it suffices to show that $\mathrm{UB}(c)\leq \max (c)$ and $\mathrm{LB}(c) \geq \min (c)$.
-We will prove this by induction on layers from the first hidden layer to the output layer.
-More specifically, we will prove the following lemmas:
+			\fi
+
+		We want to show that $\beta= \max(z)$. As the MILP abstraction is a sound over-approximation, it suffices to show that $\beta\leq \max (c)$.
+		The case for $\alpha$ is similar.
+		%We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:
+
+\iffalse
 
@@
 			\end{lemma}
+
+\fi
 

### 2024-01-25 Paper/Paper_noProof.tex
table 6
edits

@@
 
+\newcommand{\toolname}{\ensuremath{\mathsf{Comp}}
+
 %\usepackage{amsmath, amsthm, amssymb, amsfonts}
@@
 
-Our experimental evaluations have 3 goals:
-\begin{enumerate}
-	\item Evaluate experimentally how the choice of the set $Z$ impacts the accuracy of $\MILP_Z$, and compare different choices for $K$ the size of $Z$,
-	\item Evaluate on benchmarks the percentage of images that can be verified
-	using compensating strength, and compare with other value abstraction verifiers,
-	\item Evaluate how the runtime of compensate($K$) scale with the size of DNNs.
-\end{enumerate}
-
-\subsection{Setting}
-The benchmarks were run on an AMD 5975WX ($32$ cores$@3.6$GHz, 7nm, year 2022) with 256 GB of main memory and 2 NVIDIA RTX 3090.
+We implemented a prototype of {\toolname} in Python 3.8.
+We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) with 256 GB of main memory and 2 NVIDIA RTX 3090.
 Gurobi 9.52 was used for solving MILP and LP problems.
-Our implementations for Compensate($K$) is entirely realized in Python
-$3.8.10$, and therefore not particularly optimal.
 
@@
 %, and a target label for verification.
+
+\begin{enumerate}
+	\item Evaluate experimentally how the choice of the set $Z$ impacts the accuracy of $\MILP_Z$, and compare different choices for $K$ the size of $Z$,
+	\item Evaluate on benchmarks the percentage of images that can be verified
+	using compensating strength, and compare with other value abstraction verifiers,
+	\item Evaluate how the runtime of compensate($K$) scale with the size of DNNs.
+\end{enumerate}
 
@@
 	\label{tab:example3}
-	\vspace{-1cm}
+
 \end{table}
 
-\vspace{-0.4cm}
 \begin{figure}[h!]
@@
 \end{figure}
-\vspace{-0.4cm}
 
@@
 		\hline \hline
-		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
-		$\epsilon = 0.015$ & 17s & 95s? & 442s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
+		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79.5\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
+		$\epsilon = 0.015$ & 17s & 95s? & 451s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
 	\end{tabular}

### 2024-01-25 Paper/experiments.tex

--- 2024-01-25 Paper/Paper_noProof.tex
@@
-\documentclass{llncs}
-\pagestyle{plain}
-
-%\usepackage[latin9]{inputenc}
-%\usepackage[T1]{fontenc}
-\usepackage{float}
-\usepackage{wrapfig}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\captionsetup{compatibility=false}
-% \usepackage{esint}
-\usepackage{array}
-\usepackage{epstopdf}
-\usepackage{placeins}
-\usepackage{pgfplots}
-\usepackage{url}
-\usepackage{tikz}
-\usepackage{calc}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usetikzlibrary{positioning, arrows.meta,calc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand{\vx}{\boldsymbol{x}}
-\newcommand{\vy}{\boldsymbol{y}}
-\newcommand{\vW}{\boldsymbol{W}}
-\newcommand{\vz}{\boldsymbol{z}}
-\newcommand{\vb}{\boldsymbol{bias}}
-\newcommand{\val}{{\textrm{value}}}
-\newcommand{\Val}{{\textrm{value}}}
-\newcommand{\MILP}{{\textrm{MILP}}}
-\newcommand{\LP}{{\textrm{LP}}}
-
-\newcommand{\UB}{\mathrm{UB}}
-\newcommand{\LB}{\mathrm{LB}}
-\newcommand{\ub}{\mathrm{ub}}
-\newcommand{\lb}{\mathrm{lb}}
-\newcommand{\B}{\mathrm{B}}
-
-\newcommand{\CMP}{{\textrm{CMP}}\ }
-
-\newcommand{\toolname}{\ensuremath{\mathsf{Comp}}
-
-%\usepackage{amsmath, amsthm, amssymb, amsfonts}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{corollary}{Corollary}
-%\theoremstyle{definition}
-%\newtheorem{definition}{Definition}
-
-\newcommand{\ReLU}{\mathrm{ReLU}}
-
-\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
-\date{}
-
-\begin{document}
-
-	\maketitle
-
-	\begin{abstract}
-		Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally that they are correct, with an annual competition to compare them, etc.
-Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
-This allows e.g.
-to check local robustness around an input $\vx$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $\vx$.
-In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs.
-While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern verifiers, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.
-
-		In this paper, we analyse efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
-Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other.
-It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions.
-Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes.
-These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.
-	\end{abstract}
-
-	\section{Introduction}
-
-	\input{introduction}
-
-	\section{Background}
-
-	In this paper, we will use lower case latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
-	capitalized bold for matrices $\boldsymbol{W}$, similar to notations in \cite{prima,crown}.
-	To simplify the notations, we restrict the presentation to feed-forward, 
-	fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-	$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
-
-	%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
-
-	%\subsection{Neural Network and Verification}
-
-	% testtesttesttest
-	An $\ell$-layer DNN is provided by $\ell$ weight matrices 
-	$\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
-	and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
-	We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
-	$d_0$ the input dimension, and $d_\ell$ the output dimension.
-
-	Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-	denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
-	\begin{align*}
-		{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i\\
-		\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
-	\end{align*}
-
-	The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
-	$\boldsymbol{z}$ is called pre-activation values, 
-	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
-A path $\pi$ is a sequence $\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight of $\pi$ is
-	$weight(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
-
-	\iffalse
-	and the $i$-th hidden layer is a vector in $\mathbb{R}^{d_i}$, 
-	and the output layer is a vector in $\mathbb{R}^{d'}$ or a scale. 
-	The weights, bias and activation functions decide propagate the from previous to the next layer. In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight 
-	$\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, 
-	the bias is a vector $\vb^i$ in $\mathbb{R}^{d_i}$, and the activation function 
-	is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, 
-	then the value of $i$-th layer is computed by: 
-	\begin{align*}
-		{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \vb^i\\
-		\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)).
-	\end{align*} The vector $\hat{\boldsymbol{z}}$ is called post-activation values, and $\boldsymbol{z}$ is called pre-activation values, and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer.
-In our style, we also call neurons \emph{nodes} and use $a,b,c,d$ to denote them.
-We use $W_{ab}$ to denote the weight from neuron $b$ to $a$.
-We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
-	\fi
-
-	\medskip
-
-	Concerning the verification problem, we focus for simplicity on the usual local robustness question.
-Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
-	Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
-	\begin{align*}
-		\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
-		argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
-	\end{align*}
-
-	\iffalse
-	In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
-		\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
-	\end{align*}
-
-	If so, the question of verification can turn to the following optimization question: \begin{align*}
-		\min f(\boldsymbol{x}) \ s.t. {\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ b^i\\
-		\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)), \boldsymbol{x}\in\mathcal{D}.
-	\end{align*}
-
-	In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$.
-
-	In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\vx,\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
-	\fi
-
-	\section{Value Abstraction for DNN verification}
-
-	In this section, we describe different value (over-)abstractions on $\vz$ that are used by efficient algorithms to certify robustness around an input $\vx$.
-Over-abstractions of values include all values for $\vz$ in the neighbourhood of $\vx$, and thus a certificate for safety in the over-abstraction is a proof of safety for the original input $\vx$.
-
-	\subsection{The Box and DeepPoly Abstractions}
-
-	%\begin{figure}[t!]
-	%	\centering
-	%		\includegraphics[scale=0.4]{example.png}
-	%	\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
-	%	\label{fig1}
-	%	\end{figure}
-
-\begin{figure}[t!]
-	\centering
-	\begin{tikzpicture}
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (input1) {$n_1$};
-
-		\node[circle, draw= purple, thick, minimum width = 20,
-		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};
-
-		% Hidden layers
-
-		\node (hidden10) at ($(input1) + (2.5,0.6)$) {$0$};
-
-		\node (hidden20) at ($(input1) + (2.5,-1.5-0.6)$) {$0$};
-
-		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$0$};
-
-		\node (hidden60) at ($(input1) + (7.5,-1.5-0.6)$) {$1.5$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$n_3$};
-		\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{n}_3$};
-		\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};
-
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
-		\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};
-
-		% Output layer
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{n}_5$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{n}_{6}$};
-
-		% Connections
-
-		\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
-
-		\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
-
-		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
-		\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$1$};
-
-		\draw[->,color=green, thick] (input2) -- (hidden1) node[near start, below] {$1$};
-		\draw[->,color=red, thick] (input2) -- (hidden2)node[near start, below] {$-1$};
-
-		\draw[->,color=green, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
-		\draw[->,color=red, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(n_2,0)$};
-
-		\draw[->,color=green, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
-		\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
-
-		\draw[->,color=red, thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
-		\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
-
-		\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(n_5,0)$};
-		\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(n_6,0)$};
-
-	\end{tikzpicture}
-	\caption{A DNN example from \cite{kpoly}: every neuron is separated into 2 nodes, $n$ pre- and $\hat{n}$ post-ReLU activation function.
-The pair $(n_2 n_3 n_5,n_2 n_4 n_5)$ in green and red is compensating (weights of paths are $1,-2$).}
-	\label{fig1}
-\end{figure}
-
-The idea to perform value abstraction is to compute upper and lower bounds on the values of (some) neurons in the DNN when the inputs are in a given neighbourhood, in order to conclude on the robustness without needing to compute the values exactly for all inputs (in the neighbourhood).
-
-First, remark that weighted sums is a linear function, so it is easy to represent it explicitly.
-The only problematic part to represent accurately is the ReLU function.
-While it is fairly simple piecewise linear function with 2 modes ($x<0$ and $x \geq 0$), it is not linear.
-Considering its iterated impact along the different layers of a ReLU DNN is much more complex than it seems.
-First, let us remark that it is easy to represent exactly $\ReLU(x)$ in case $x$ is {\em stable}, that is, either it is known to be entirely positive, order
-it is known to be entirely negative, as in both case there is only one known linear mode involved. Hence, the sole problem remains how to handle {\em unstable} neurons.
-
-Consider the simpler abstraction, called the {\em Box abstraction} \cite{deeppoly}: inductively compute the bound on each neuron of the next layer independently, by considering the weighted sum over the bounds of the previous layer, then clip the lower bound at
-$\max(0,$ lower bound$)$ to represent the ReLU function, and so on.
-For all $i$, let $x_i=\val_{\vx}(n_i)$, with $\vx=(x_1,x_2)$.
-For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $\hat{x}_3,\hat{x}_4 \in [0,2]$, and $x_5 \in [0,6]$ while $x_6 \in [0,2]$. 
-While the bounds for $n_1, \ldots, n_4$ are exact (for all $\alpha$ 
-in the range, there is an input $\vy$ such that $\val_{\vy}(n_i)=\alpha$), 
-it is no more the case from the next layer (starting in $n_5,n_6$) because of potential 
-dependencies between earlier neurons: $n_3$ reaches value $2$ only when $x_1=x_2=2$,
-in which case $n_4$ reaches value $Val_{(2,2)}(n_4)=0$. Hence, it is impossible that $x_5=\Val_{\vx}(n_5)$ reaches $6$, as it would require both $n_3$ and $n_4$ to have value $2$.
-
-A still extremely fast algorithm that corrects some of this issue is {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
-hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the value of the node.
-Denote $f_i \leq x_i \leq g_i$ with e.g.  
-$f_{3}(x_3)=f_4(x_4)=0$ and 
-$g_3(x_3) = \frac{x_3+2}{2}$,
-$g_4(x_4) = \frac{x_4+2}{2}$. 
-With that, we get 
-$x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
-
-For $[\alpha,\beta]$ bounds on $x_i$, there is one optimal linear function for the upper bound $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes.
-There are two choices for the lower bound: $f^1_i(x_i) = 0$ or $f^2_i(x_i)=x_i$.
-In the DeepPoly algorithm, the choice is made by considering $\alpha < 0 < \beta$ (for unstable neurons).
-If $|\alpha|\geq |\beta|$ then $f_i=f^1_i$ is used, while if $|\beta|>|\alpha|$ then $f_i=f^2_i$ is used.
-Denote {\em $\overline{\mbox{DeepPoly}}$} the DeepPoly algorithm such that $f^1_i$ is always used, and $f^2_i$ is never used.
-Unlike DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} subsumes the {\em Box abstraction}. Indeed, taking bounds $[-0.2,5]$ on $x_i$, it gives $\ReLU(x_i) \in [0,5]$, 
-while the normal DeepPoly algorithm would only allow to conclude that $\ReLU(x_i) \in [-0.2,5]$.
-
-\iffalse
-\subsection{PRIMA and $\beta$-CROWN}
-\fi
-
-\subsection{MILP and LP encodings for DNNs}
-
-At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method (albeit much slower than DeepPoly). 
-Consider an unstable neuron $n \in[\alpha,\beta]$.
-The value $x$ of $\ReLU(n)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints \cite{MILP}:
-\vspace{-0.1cm}
-\begin{align*}
-	\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)
-\end{align*}
-
-From \cite{MILP}, for all $x \in [\alpha,\beta] \setminus 0$, there is a unique solution $(a,\hat{x})$ satisfying the constraints, and we have $\hat{x}=\ReLU(x)$ (and $a$ is 0 if $x < 0$ and 1 if $x>0$, and can be either for $x=0$).
-Such an encoding can be used for every (unstable) ReLU node, and optimizing its value allows to certify a given input.
-For Networks with hundreds of nodes or more, the associated MILP formula will have have hundreds of integer variables, and it will usually not be solvable efficiently.
-
-MILP instances can be linearly relaxed into LP over-abstraction, where variables which were integers in $\{0,1\}$ (binary) are relaxed to be real in interval $[0,1]$, using otherwise the same encoding.
-Solving LP instances being Polynomial time, optimizing it is much more efficient, but at the price of a lack of accuracy (e.g.
-with not as tight bounds).
-This is called the {\em LP abstraction}.
-
-As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while DeepPoly considers exactly one.
-
-\begin{proposition}
-	\label{LP}
-	Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
-	1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
-	\vspace{-0.3cm}
-	\begin{align*}
-		& 1) \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1] \\
-		\text{and} \quad  & 2)  \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha}
-	\end{align*} 
-\end{proposition}
-
-\begin{proof}
-	Obviously, the 2 lower bound constraints are the same in 1) and 2).
-
-	It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
-For that, we study the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
-We have $\hat{x}$ in 1) is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
-	The function $min(\beta \cdot a, x - \alpha (1-a))$ reaches its maximum for 
-	$\beta \cdot a = x - \alpha (1-a)$, that is 
-	$(\beta - \alpha) a = x - \alpha$, i.e. 
-	$ a = \frac{x - \alpha}{\beta-\alpha}$.
-	It thus gives an upper bound at 
-	$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the upper-bound function used in DeepPoly.
-	\hfill $\square$
-\end{proof}
-
-\section{Compensating pairs of paths}
-\label{Sec.comp}
-
-In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but 
-not efficient). 
-Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision. A pair $(\pi,\pi')$ of paths is {\em compensating} if:
-\begin{itemize}
-	\item they have the same starting node $a$ (called {\em source} state) and ending node $b$ (called {\em target} state of $(\pi,\pi')$),
-	\item they are disjoints (the only common nodes are the source and the target),
-	\item the weights satisfy $weight(\pi') < 0 < weight(\pi)$.
-\end{itemize}
-
-For instance, on Fig.~\ref{fig1}, the paths $\pi= n_2 n_3 n_5$ has weight $1$, while the
-path $\pi'= n_2 n_4 n_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
-We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or $(\pi',\pi)$ is compensating.
-
-Compensating pair of paths will make precision of the target state reduce when using overabstraction of values. Here, $x_5 \leq 4$, which is reached for $x_1=1$ and $x_2=-1$: 
-$\val_{(1,-1)}(n_5)=4$.
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+3}{2} \leq 2$ instead of exact $-x_2 \leq 1$), obtaining $x_5 \leq 5$ instead of the precise $x_5 \leq 4$.
-
-Intuitively, the target state receives the weight from the source state from the different paths from the source to the target.
-As the weights of the paths is of opposite sign, some of these weights will cancel out, by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$.
-Further, that also avoid accumulating the error, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inaccurate analysis.
-The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function.
-For instance, consider that the inputs $x_1,x_2$ lies in $[-1,-0]$.
-Then $\hat{x}_3$ will always be 0 for any input $\vx=(x_1,x_2) \in [-1,-0] \times [-1,-0]$, and $weight(\pi')$ will not compensate $weight(\pi')$.
-
-\iffalse
-\vspace*{2ex}
-
-\begin{figure}
-	\centering
-	\begin{tikzpicture}
-
-		\node[circle, draw= purple, thick, minimum width = 20,
-		minimum height = 20] (input1) {$a$};
-
-		% Hidden layers
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (hidden1) at ($(input1) + (2,1)$) {$b$};
-		\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-1)$) {$b'$};
-
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (hidden3) at ($(input1) + (4,1)$){$c$};
-		\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-1)$) {$c'$};
-
-		% Output layer
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (output) at ($(input1) + (6,0)$){$d$};
-
-		% Connections
-		\draw[->,thick,draw= red] (input1) -- (hidden1) node[midway, below] {$1$};
-		\draw[->,thick,draw= green] (input1) -- (hidden2)node[midway, below] {$-1$};
-
-		\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
-		\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};
-
-		\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
-		\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
-	\end{tikzpicture}
-\end{figure}
-
-\vspace*{2ex}
-
-In this figure, $a$ is the input neuron; $bc,b'c'$ are nodes in the hidden layer, ($b,b'$ are pre-activation and $c,c'$ are post activation); and $d$ is the unique output neuron.
-The numbers next to the arrows are the weights.
-So, $W_{ba}=1$ and $W_{b'a}=-1$, $W_{dc}=W_{dc'}=1$.
-The pair of these two paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is a so called \emph{Compensating Pair}.
-Because its shape looks like a diamond, it is also called a Diamond.
-The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
-
-The existence of compensating pairs is key reason why simple approximation like LP or Interval Arithmetic cannot get the exact upper and lower bounds.
-If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
-
-To explain why, suppose we have another input node $a'$, such that both $a$ and $a'$ has an input interval $[0,1]$, but the weight from $a'$ to $b$ or $b'$ are both $1$.
-Then both $b$ will have an interval $[0,2]$ and $b'$ will have an interval $[-1,1]$.
-More importantly, in LP formulation, $c$ will be $b$ but $c'$ will be $0.5(b')+0.5$.
-The upper bound of $d$ will be $c+c'$, and hence $b+0.5(b')+0.5$, and hence $a+a'+0.5a'-0.5a'+0.5=0.5a+1.5a'+0.5$.
-And this will leads to a upper bound $2.5$ but this is not exact.
-
-\vspace*{2ex}
-\begin{tikzpicture}
-	\node[circle, draw= purple, thick, minimum width = 20,
-	minimum height = 20] (input1) {$a$};
-
-	\node[circle, draw= purple, thick, minimum width = 20,
-	minimum height = 20] (input2) at ($(input1) + (0,-2)$) {$a'$};
-
-	% Hidden layers
-	\node[circle, draw= blue, thick, minimum width = 20,
-	minimum height = 20] (hidden1) at ($(input1) + (2,0)$) {$b$};
-	\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-2)$) {$b'$};
-
-	\node[circle, draw= blue, thick, minimum width = 20,
-	minimum height = 20] (hidden3) at ($(input1) + (4,0)$){$c$};
-	\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-2)$) {$c'$};
-
-	% Output layer
-	\node[circle, draw= blue, thick, minimum width = 20,
-	minimum height = 20] (output) at ($(input1) + (6,-1)$){$d$};
-
-	% Connections
-	\draw[->,thick,draw= red] (input1) -- (hidden1);
-	\draw[->,thick,draw= green] (input1) -- (hidden2);
-
-	\draw[->,thick,draw= red] (input2) -- (hidden1) node[midway, below] {$1$};
-	\draw[->,thick,draw= red] (input2) -- (hidden2)node[midway, below] {$1$};
-
-	\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
-	\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};
-
-	\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
-	\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
-\end{tikzpicture}
-\vspace*{2ex}
-
-The general formal definition of compensating pair is as follows:
-
-\begin{definition} In a full-connected network with $\ReLU$ as activation function:
-
-	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes that goes consecutively through each layer. We call the first node source node and the last node target node.
-
-	2.
-The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ab}\cdot W_{bc}\cdot W_{cd}\cdot W_{ed}\cdot \cdots$$
-
-	3.
-A \emph{Compensating Pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
-
-	We also use \emph{Diamond} to call a compensating pair in the network.
-\end{definition}
-
-The following theorem shows the role of compensating pairs in the computation:
-
-\fi
-
-Hence, compensation is {\em one} factor of inaccuracy. We prove now that it is actually the {\em only} reason for inaccuracy, in the following meaning.
-If there is no compensating path in the DNN, then any method/approximation at least as accurate as the Box abstraction, e.g.
-$\overline{\text{DeepPoly}}$ or LP, computes the exact upper and lower bounds for every node, that is:
-
-\begin{table}[b!]
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\text{Source/Target Layers}  &  \text{Natural DNN} & \text{Robust DNN} & \text{Ratio Natural vs Robust} \\ \hline \hline
-		0 / 2 & 0.0304 & 0.00220  & 13.8x\\ \hline
-		1 / 3  & 0.0313 & 0.00875 & 3.58x \\ \hline
-		2 / 4  &  0.0267 & 0.00785 & 3.40x \\ \hline
-		3 / 5  &  0.0253 & 0.00804  & 3.18x \\ \hline
-	\end{tabular}
-	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.}
-	\label{tab:compensation}
-\end{table}
-
-\begin{theorem}
-	\label{th1}
-	Let $n$ be any node of a DNN with {\em no} compensating path.
-For $[\alpha,\beta]$ the bounds computed by the {\em Box abstraction} for $n$, we have that for all $\gamma \in [\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n)=\gamma$.
-\end{theorem}
-
-The sketch of proof can be found in Section \ref{sec.proofs}. 
-Notice that standard DeepPoly does not satisfies Theorem \ref{th1} (it does not necessarily refine Box), and therefore we are not sure PRIMA or $\beta$-CROWN that refine DeepPoly satisfies Theorem \ref{th1}, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
-Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results show in that compensation is the reason for inaccuracy.
-
-This result has a first interesting application: explain why some DNNs are intrinsically easier to verify than others.
-This is the case for DNNs trained adversarially to be robust, vs same architecture, but trained in a "natural" way \cite{deeppoly,prima,crown}.
-Indeed, compensating pairs is a purely structural property on the DNN learnt, rather than more semantical notions, such as the number of unstable ReLUs, which depends heavily upon the image considered and the algorithm used.
-We compare compensations with source and target separated by 1 ReLU layer, e.g.
-source in layer 0 and target in layer 2, for two Networks with 5 hidden layers of 100 nodes each from the ERAN GitHub repository, one trained naturally ("$6\times100$"),
-and one trained using DiffAI \cite{DiffAI} ("$5\times100$"). 
-We report in Table \ref{tab:compensation} the average compensation strength, i.e. 
-the average of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$
-over all source/target states in given layers.
-The average compensations strength are much lower in the Robust DNN than in the natural DNN, and indeed the Robust DNN is much simpler to verify than the natural DNN (e.g.
-DeepPoly is more accurate and verifies more images).
-
-\subsection{MILP$_{X_n}$}
-
-While Theorem \ref{th1} is interesting to understand that compensation is a key notion for accurate verification of DNNs, it cannot be used directly to analyze DNNs with compensations, which are actually those that are most interesting to tackle.
-Intuitively, when there are compensating paths, it seems necessary to consider exactly the (unstable) ReLU nodes that are seen along these paths. 
-Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds 
-$[\alpha,\beta]$.
-Let $X_n$ be the set of neurons $x$ in layer up to $k-1$ such that there is a compensating path with target $n$ passing by $x$ (but not as its source or target).
-Let $Y_n$ be the complement of this set $X_n$ of neurons in the first $k-1$ layers.
-We denote by MILP$_{X_n}$ the relaxation of the MILP encoding where all the nodes in $Y_n$ are linearly relaxed (thus with $|X_n|$ binary variable, one per neuron in $X_n$), and including exact bounds for every neurons $n'$ in the first $k-1$ layers.
-We state now that the bounds $[\alpha,\beta]$ on neuron $n$ computed by such MILP$_{X_n}$ are accurate.
-
-\begin{theorem}
-	\label{th2} 
-	Let $n$ be any node of a DNN.
-Then for $[\alpha,\beta]$ the bounds computed by MILP$_{X_n}$ for neuron $n$, for all $\gamma \in [\alpha,\beta]$, there exists an input $\vy$ such that $\val_{\vy}(n)=\gamma$.
-\end{theorem}
-
-The sketch of proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs}.
-
-\subsection{Sketch of Proofs}
-\label{sec.proofs}
-
-%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
-Consider a target neuron $z$.
-In case there is no compensating path, we can assign a sign to each neuron $n$: 0
-if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
-$-1$ if they have negative weights. Then we prove:
-
-\begin{proposition}
-	\label{prop.sign}
-	There exist two inputs $\vx^\star,\vx^\sharp$ such that ${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  ${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
-\end{proposition}
-
-Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.
-
-\smallskip
-
-Concerning Theorem \ref{th2}, consider an output node $z$.
-Let $[\alpha(z),\beta(z)]$ be the bound computed by $\MILP_{X_z}$.
-%We will show the existence of $\vx^\sharp,\vx^\star$
-%such that $\val_{\vx^\sharp}(z)=\alpha$ and $\val_{\vx^\star}(z)=\beta$,
-%and we will get the proof of Theorem 2 by a continuity argument.
-%For that, 
-We partition the input neurons from layer $0$ into:
-\begin{enumerate}
-	\item $A_{zero}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)=0\}$.
-	\item $A_{pos}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\geq0\}$.
-	\item  $A_{neg}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\leq0\}$.
-	Let $A_{pure}=A_{pos} \cup A_{neg}$.
-	\item $A_{open}$ is the set of remaining input neurons.
-\end{enumerate}
-
-We then partition the set of neurons in hidden layers: 
-\begin{enumerate}
-	\item $B_{zero}= \{n \mid \forall \text{ path $\rho$ from $n$ to } z, weight(\rho)=0\}$.
-	\item $B_{open}$ is the set of neurones reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
-	\item $B_{pure}$ is the set of remaining neurons.
-\end{enumerate}
-
-We can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
-Further, the value of any neuron $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
-nodes in $A_{pure}$ or $B_{pure}$. Therefore, applying Prop. \ref{prop.sign} on the DNN
-made of nodes from $A_{pure}$ and $B_{pure}$, we obtain 
-$\vx_{pure}^\star,\vx_{pure}^\sharp$ optimizing neurons in $A_{pure}$ or $B_{pure}$.
-We can prove that there exists input 
-$\vx^\star$ extending $\vx_{pure}^\star$
-and input $\vx_{pure}^\sharp$ extending $\vx_{pure}^\sharp$
-from $A_{pure}$ to $A_{pure} \cup A_{open}$ such that 
-$\val_{\vx^\star}(z)=\beta(z)$ and $\val_{\vx^\sharp}(z)=\alpha(z)$.
-
-The formal proofs are in appendix.
-
-\subsection{An efficient algorithm}
-
-Using Theorem \ref{th2}, one could thus obtain accurate bounds by running MILP$_{X}$ inductively on every node layer by layer, obtaining accurate bounds $[\alpha,\beta]$ that can be used to compute the next layer accurate bound.
-In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this threshold are not compensating strongly enough to deserve an integer variable, calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
-In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small.
-The pseudo-code of the algorithm is provided in Algorithm \ref{algo1}.
-
-\SetKwInput{KwInput}{Input}
-\SetKwInput{KwOutput}{Output}
-
-\begin{algorithm}[b!]
-	\caption{Compensate(K)}
-	\label{algo1}
-	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}
-
-	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}
-
-	\For{layer $k=1 \cdots \ell$}{
-		\For{neuron $n$ in layer $k$}{
-
-			Compute $Z$ a set of $K$ nodes covering the compensating pairs of paths with target $n$
-			with heaviest compensation
-
-			Run MILP$_Z$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
-		}
-	}
-\end{algorithm}
-
-This algorithm has a worst case complexity bounded by $O(N \MILP(N,K))$, 
-where $N$ is the number of nodes of the DNN, 
-and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
-We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables.
-This complexity is an upper bound, as e.g. Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
-Notice that the for loop on neurons $n$ in layer $k$ at line 2 can be realized in parallel as we only need bounds from previous layers, not from the current layer $k$, 
-leading to a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, with $\ell$ the number of layers and $N_i$ the number of neurons in layers $0, \ldots, i$.
-Hence, for $K$ small enough, Algorithm \ref{algo1} calls many times MILP (e.g. Gurobi)
-with a limited number of integer variables, which should be efficient enough, and yet be quite accurate as it can compute exactly (Theorem \ref{th2}) the highest compensating path, which we verify in the next section.
-
-\iffalse
-\section{Verification Framework}
-
-%Our experiments are carried by different version codes, and the global process has been changed.
-
-In this section, we will sketch the framework.
-
-\subsection{Structure}
-
-\subsubsection*{Precomputation}
-
-The open node chosen is the key part of the whole framework but costs a lot of time. So some computation (those do not rely on certain image and bounds) is moved to the precomputation part.
-
-%The precomputation corresponds to the simplest case: source node fixed.
-We will compute and store a limited number of paths with highest (absolute) values before running any image.
-This does not rely on other parameters or results(bounds).
-%
-%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
-This will use much less time.
-
-\subsubsection*{Process for one image} An image is the basic unit in whole process.
-The process of one image is simple: compute the concrete bounds of nodes layer by layer, use the bounds of previous layer to build MILP models of current layer.
-In one layer, nodes runs in parallel.
-
-%Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers.
-Then we will compute bounds of every node in $l_i$ in parallel using the data of bounds of previous nodes.
-The method is to build and optimize an MILP model.
-
-%Some parameters may be changed during layers.
-Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
-Here, \emph{local} is opposite to \emph{global}.
-We have global timeout parameters for images and the whole running.
-Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
-
-%The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node. 
-%
-%The precomputation corresponds to the simplest case: source node fixed.
-We will compute and store a limited number of paths with highest (absolute) values before running any image.
-This does not rely on other parameters or results(bounds).
-%
-%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
-This will use much less time.
-
-\begin{algorithm}
-	\caption{The Frame work}
-	\KwData{Input Domain: $\mathcal{D}$}
-	\KwResult{Bounds of all nodes: $\mathcal{B}$}
-
-	Constant $\mathcal{R}$  \tcp*{Stored precomputation data}
-
-	Constant $\boldsymbol{W}, \vb$ \tcp*{Weights and Bias of network}
-
-	Constant Layers = $[0,1,2\cdots,L]$ \tcp*{lists of all layer}
-
-	Constant NodesLayer = $[Nodes_0,Nodes_1,\cdots, Nodes_L]$ \tcp*{list of nodes in each layer}
-
-	Initialize $\mathcal{B}$ = \{\} \tcp*{To store upper and lower bounds of all nodes}
-
-	\For{$l$ in Layers}{
-		\If{$l$ = 0}{
-
-			$\mathcal{D}$, $\boldsymbol{W}, \vb$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
-			\tcp*{Do linear transformation  from input to the first layer}
-
-			Add \{$x$: $(UB(x),LB(x))$,$\cdots$\} to $\mathcal{B}$}
-
-		\Else{
-
-			$l$, NodesLayer $\rightarrow$ $Nodes_l$ = $[x_0,x_1,\cdots]$
-
-			\For{$x$ in $Nodes_l$}{
-				$x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}
-
-				$\mathcal{B}$, $\boldsymbol{W}, \vb$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
-
-				\While{}{$\mathcal{M}$ $\rightarrow UB(x),LB(x)$ \tcp*{Optimization}}
-
-				Add \{$x$: $(UB(x),LB(x))$\} to $\mathcal{B}$
-
-			}
-
-		}
-
-	}
-
-	\Return{$\mathcal{B}$}
-
-\end{algorithm}
-
-\subsubsection*{Process for one node}
-
-The optimization of a model consists of loops.
-For each loop, the model will do optimization by a timeout and observe the result.
-If it gets improvement, then continue the loop until the optimize bounds or the longer timeout.
-Otherwise it will give up optimization and store the best bounds obtained so far.
-
-\subsubsection*{Global Process}
-
-In the newest version, we do images by batches for 100 images each. For each batch, the running consists of three turns, very fast turn, fast turn and slow turn.
-
-In the very fast turn, it will run DeepPoly for all images to get a preliminary bounds for all nodes and verify the easiest images.
-Images verified and images with false predication will be deleted from the image list.
-
-Then sort all remain images by the size of uncertainty of DeepPoly from smaller to larger.
-The fast turn is to run the images from the smaller side to larger side until consecutive two images cannot be verified.
-All remain images and images tried but not verified will be put into the next list.
-And then run the list with parameters for slow turn.
-
-\subsection{Parameters}
-
-Parameters like open node parameter $O$ is important in the frame. Basically, all parameters will be reset after one image.
-
-\subsubsection*{Global parameters}
-
-\subsubsection*{Local parameters}
-
-$O$ and timeout parameters for loops will change frequently during the loops of one node. These change will not reset until the end of one layer or one image.
-
-\subsection{Other Setting}
-
-In our experiments, we have not used PGD-attack to exclude some images. In principle, there is no obstacle to use PGD-attack.
-\fi
-
 \section{Experimental Evaluation}
@@
 Few important correlations {\em a la} PRIMA could be kept explicitly as linear constraints in the MILP encoding, helping to reduce the inaccuracies further.
-
-\vspace{-0.2cm}
-\section{Conclusion}
-\vspace{-0.2cm}
-
-In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
-We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.
-
-Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Last, we experimentally showed that choosing $Z$ covering {\em few} paths with the strongest compensations, results in very good accuracy, and runtime which can be favourable in some (but not all) cases.
-This proves that compensating strength is a promising novel concept which should be further studied to improve DNN verification.
-We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.
-
-\newpage
-
-\bibliographystyle{plain}
-\bibliography{references}
-
-\newpage
-
-\appendix
-
-\input{proofs}
-
-\end{document}
-
-\section{Ranking of Compensating Pairs}
-
-In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.
-
-Based on No Diamond Theorem, for a target node, in its MILP model, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node.
-However, in practice, this is still too expensive because we will still need to open too many nodes.
-So we can only choose a limited number of compensating pairs and nodes.
-This is by setting a parameter $O$ such that the process only choose at most $O$ many nodes to open.
-Therefore, in this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.
-
-Basically, we do the process of open nodes chosen for one target node each time, that is, receive one target node (and other data) as input each time.
-But in principle, we can develop a method receive more than one nodes as input.
-But in our experiences, this does not work well.
-
-This process is not the unique method but the most natural way to choose open nodes. We introduce it in three steps from the simplest case to more complex case.
-
-\subsubsection*{Value of a pair}
-
-For a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.
-
-\subsection*{Case: Source node fixed}
-
-The simplest case is when we only consider compensating pairs with a fixed source node.
-
-In this case, the process is very simple: enumerate all compensating pairs, and then sort them by their values.
-Finally, from the first to the last compensating pair, pick all unstable nodes in its two paths except the target and source nodes into the list of open nodes, until $O$ many open nodes.
-
-%\subsubsection*{Sort all paths by values}
-%
-%The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.
-%
-%Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.
-%
-%\subsubsection*{Sort pairs by values}
-%
-%The second step is to sort all pairs by their values.
-Enumerate paths from the positive group and the negative group one by one and put the pairs obtained into a new list of pairs.
-Then sort all pair by their values from largest to the smallest: recall that the value of a pair $\langle P_1,P_2\rangle$ is $\min(|V_1|,|V_2|)$.
-%
-%\subsubsection*{Choosing nodes}
-%
-%The third step is to choose nodes from the list of pairs.
-According to the sorted list of pairs, enumerate pair one by one; for each pair, pick the nodes unstable in the two paths except the source and target node into the open node list.
-Repeat this process until $O$ nodes chosen or reach the end of the list.
-%
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-%
-
-\subsection*{Case: Source nodes in one layer}
-
-The more general case is when the source node can be any node in a fixed layer. In this case, the process is very similar to previous case, except the value of a pair.
-
-In this case, for a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, its value is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
-
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-
-\subsection*{Case: Source nodes in different layers}
-
-The general case is that when the location of source nodes can be in different layers.
-This case is much more complex, because the scale level of values of paths from different layers are very different: usually a weight will be very small since every layer has a large number of nodes, therefore values of longer paths are products of more small numbers, and is definitely much smaller.
-If we sort all compensating pairs from different layers directly, then a very long initial segment of this list will be occupied by compensating pairs with the shortest length.
-Therefore, we need use some scale factors when comparing values of compensating pairs of different length.
-
-In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before).
-We will dynamically adjust the values during the process of node chosen.
-In text, the process of node chosen for length 3 plus length 4 is as follows:
-
-\vspace*{1ex}
-
-1. Generate the two lists of pairs sorted by their values for source nodes in 2 layers before the target node and 3 layers before separately as in the previous case.
-
-2.
-Enumerate pair from two lists one by one by their values and pick nodes as previous case.
-When comparing the values between pairs of length 4 and pairs of length 3, multiply the numbers of nodes in 1 layer before to the value of pair of length 4.
-
-In formula, when the target node is in layer $L$, for a pair $P_3$ of length 3 with value $V_3$ and a pair $P_4$ of length 4 with value $V_4$, if we have chosen $N$ nodes in layer $L-1$.
-Then the adjusted values for $P_3$ and $P_4$ are: $$V_3, N\cdot V_4.$$ Then we pick the next pair by the adjust value in two lists.
-
-3. Repeat 2 until choosing sufficiently many nodes.
-
-\vspace*{1ex}
-
-The pseudo-code is as follows ():
-
-\begin{algorithm}
-\caption{Process for length 3 + length 4}
-\KwData{Sorted lists of length 3 + length 4}
-\KwResult{Open node list}
-
-Let $N = 0$ be the number of Chosen length 4 pair.
-
-\While{len(Open node) $<O$}{
-	Pick the first element $P_3$ in the list of length 3\;
-
-	Let $V_3$ be the value of $P_3$\;
-
-	Pick the first element $P_4$ in the list of length 4\;
-
-	Let $V_4$ be the value of $P_4$\;
-
-	\If{$V_3 > V_4 \cdot N$}{
-		Add nodes in $P_3$ into Open list\;
-		Number of Chosen lentgh pair $N$ += 1\; 
-	}
-	\Else{
-		Add nodes in $P_4$ into Open list\;
-	}
-}
-\end{algorithm}
-
-\end{document}

### 2024-01-25 Paper/introduction.tex

--- 2024-01-25 Paper/introduction.tex
@@
 This is more efficient, as the number of binary nodes is strongly reduced.
-However, the question remains how accurate is it?}
+However, the question remains how accurate is it?
 
-\item {\color{red} Our second main contribution, delineated in Theorem \ref{th2}, answers this question, showing that this abstraction is fully accurate, in that the bounds computed in such a way for neuron $z$ correspond exactly to the mininmal and maximal values reachable by inputs of the DNN.
-Again, the prevalence of compensating paths in actual DNNs renders this algorithm computationally intensive because the number of binary variables is still too high.}
+\item  Our second main contribution, delineated in Theorem \ref{th2}, answers this question, showing that this abstraction is fully accurate, in that the bounds computed in such a way for neuron $z$ correspond exactly to the mininmal and maximal values reachable by inputs of the DNN.
+Again, the prevalence of compensating paths in actual DNNs renders this algorithm computationally intensive because the number of binary variables is still too high.
 
-\item Our third main contribution addresses this practical concern, introducing 
-\CMP (Algorithm \ref{algo1}), a pragmatic solution that leverages our theoretical insights. This approach ranks ReLU nodes based on {\color{red} 
-the weights of the compensating paths they belong to,
-and differentiates their treatment in the MILP model (binary for heavy, linear for light). 
-%Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously. Furthermore, 
-Our comprehensive empirical evaluation indicates that \CMP provides favorable trade-offs between accuracy and completeness compared to existing methods, 
-%lowering the number of 
-%undecided inputs from $17.6\%$ ($\beta$-Crown \cite{crown}) to $10.4\%$ 
-%on DNN $8 \times 200$ (Table \ref{tab:example}), even 
-verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN trained naturally (Table \ref{tab:example3}).}
+\item Our third primary contribution addresses a practical concern by introducing Algorithm \ref{algo1}, a pragmatic solution that builds on our theoretical insights.
+This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones.
+Our extensive empirical evaluation reveals that Algorithm \ref{algo1} achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
+It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$ (refer to Table \ref{tab:example}).
+Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN configuration (as detailed in Table \ref{tab:example3}).
 

### 2024-01-25 Paper/Paper_noProof.tex
edits

@@
 
-\newcommand{\toolname}{\ensuremath{\mathsf{Comp}}
+\newcommand{\toolname}{\ensuremath{\mathsf{Comp}}}
 
@@
 
-\section{Experimental Evaluation}
-
-We implemented a prototype of {\toolname} in Python 3.8.
-We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) with 256 GB of main memory and 2 NVIDIA RTX 3090.
-Gurobi 9.52 was used for solving MILP and LP problems.
-
-The local robustness verification is performed on DNNs trained for the MNIST image dataset as its the only DNNs naturally trained ("MLP" (fully connected Multi Level Perceptron) $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers).
-Indeed, today's efficient methods leave between $12\%$ to $20\%$ of the images neither certified robust \cite{crown} nor with an attack to robustness found \cite{attack}, making them interesting DNNs to consider when improving accuracy.
-MNIST contains grayscale images of size $28 \times 28$ pixels ($752$ input neurons).
-For our evaluation, we evaluate on the standard first 1000 images of the dataset, to be directly comparable to experiments run in other papers, e.g.
-\cite{prima,crown}.
-We also experimented on (MLP) $6\times 500$ (results not reported in \cite{prima,crown}), checking the first 200 images of the dataset, as it takes a long time to run.
-Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
-%, and a target label for verification.
-
-\begin{enumerate}
-	\item Evaluate experimentally how the choice of the set $Z$ impacts the accuracy of $\MILP_Z$, and compare different choices for $K$ the size of $Z$,
-	\item Evaluate on benchmarks the percentage of images that can be verified
-	using compensating strength, and compare with other value abstraction verifiers,
-	\item Evaluate how the runtime of compensate($K$) scale with the size of DNNs.
-\end{enumerate}
-
-\subsection{Choosing nodes based on Compensation strength}
-
-The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-
-To measure the accuracy, we measure the uncertainty of all nodes in a layer:
-the uncertainty of a node is the range between its computed lower and upper bound. 
-We then average the uncertainty among all the nodes of the layer.
-Formally, for a node $n$ with bounds $[\alpha,\beta]$, its uncertainty $unc(a) = \beta - \alpha$, and the average uncertainty of a layer $l$ is $\dfrac{\sum_{a\in l} unc(a)}{|l|}.$
-
-We experiment with the smallest network (MLP $5\times 100$ in \cite{crown}, 
-called $5 \times 100$ in \cite{prima}, and abusively $6 \times 100$ in \cite{deeppoly}, perturbation $\varepsilon=0.026$), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
-We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
-
-\subsubsection*{ReLU Node in the first hidden layer}
-
-\begin{table}[b!]
-	\centering
-	\begin{tabular}{|c||c|c|}
-		\hline
-		\text{Number $K$ of nodes in $Z$}  &  \text{Compensate strength} & \text{Random Choice}  \\ \hline
-		\hline
-		0  &  2.22 & 2.22  \\ \hline
-		10  &  1.84 & 2.03  \\ \hline
-		20  &  1.50 & 1.82  \\ \hline
-		30  &  1.28 & 1.62  \\ \hline
-		40  &  1.14 & 1.44  \\ \hline
-		50  &  1.06 & 1.23  \\ \hline
-		61 (max) & 1.05 &  1.05 \\ \hline
-	\end{tabular}
-	\caption{Average uncertainty of $\MILP_Z$ for nodes of the second layer, for $Z$ with $K$ ReLU nodes of the first layer (compensating strength vs random choice).}
-	\label{tab:example0}
-	%\vspace{-0.8cm}
-\end{table}
-
-We first experiment with the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer.  Let $c$ be a node of the second layer.
-A compensating pair $(\pi,\pi')$ of paths with target $c$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
-The compensating strength for $(b,b')$ is defined as $comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$.
-Indeed, the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),$\newline $weight(a,b',c))$, and $b,b'$ would help compensated the set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
-After selecting the heaviest $(b_0,b_0')$, we can then compute $comp(b)= \sum_{b' \text{already selected}} comp(b,b')+comp(b',b)$ and select iteratively the heaviest $b$'s one by one till reaching the threshold.
-%We do this for all node $c$ of the second layer.
-
-We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
-The range of uncertainty created by inacurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
-Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
-We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
-
-\subsubsection*{ReLU Node in the first and second hidden layer}
-
-We now turn to evaluating the choice of ReLU nodes in two layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
-The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. Let $d$ be a neuron of the third layer.
-We keep the previous evaluation for ranking nodes in the previous (second) layer. 
-Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ from the first layer to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$.
-We thus define:
-\vspace{-0.2cm}
-$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ 
-\vspace{-0.2cm}
-
-and the associated $comp(b)$, and select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
-
-We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly from layers $1$ and $2$.
-We compare choosing nodes in the second layer only with choosing nodes in both the first and second layer.
-Choosing ReLU nodes in the previous layer (layer $2$) only is less accurate than 
-also choosing nodes in layer $1$.
-When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inaccurate computations ($0.059$ vs $0.574$), while it only reduces the uncertainty by $65\%$ when choosing nodes randomly.
-Notice that applying this layer after layer will even further reduce uncertainty created by accumulation of inaccuracies.
-Last, we did not experiment for selecting ReLU nodes in 3+ layers earlier because the trade-off of accuracy vs evaluating the compensating strength of such paths is unclear.
-
-\begin{table}[t!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|}
-		\hline
-		\text{Number $K$}  &  \text{Compensate layer} 1+2 &  \text{Compensate layer} 2 & \text{Random layer } 1+2 \\ \hline
-		\hline
-		0  &  1.758 & 1.758 & 1.758  \\ \hline
-		10  &  1.677 & 1.677 & 1.695  \\ \hline
-		20  &  1.539 & 1.567 & 1.622  \\ \hline
-		30  &  1.431 & 1.489 & 1.542  \\ \hline
-		40  &  1.329 & 1.454 & 1.47  \\ \hline
-		50  &  1.243 & 1.432 & 1.39  \\ \hline
-		116 (max) &  1.184 & 1.422 & 1.184  \\ \hline
-	\end{tabular}
-	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs random choice).}
-	\label{tab:example1}
-	\vspace{-0.8cm}
-\end{table}
-
-\subsection{Comparison with value-abstraction Verifiers}
-
-We compare the following verifiers performing value-abstraction:
-\begin{itemize}
-	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}.
-We report the runtime from our own implementation used in Compensate($K$).
-It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
-Our focus is not to have the most optimized tool, but mainly to evaluate the accuracy of Compensate($K$).
-	\item PRIMA, with results reported in \cite{prima} and \cite{crown}, as it is the closest in practice with our algorithm, computing accurate bounds for all neurons (as we do), although with a different technique: they focus on explicit correlations between neurons, while we consider the correlations indirectly through a better network abstraction.
-They use GPU while we do not.
-When computing the whole correlated space,
-	parallelization is difficult.
-	Notice that on these DNNs, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
-This is doable on the first few layers as the number of integer variable is not too large.
-By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
-	\item ($\alpha$)$\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date.
-Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and using GPU implementation (while we do not).
-Performance of pure BaB on these
-	"hard to verify" DNNs is however impaired by the large number of branchs to consider.
-Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running the branching heuristic BaB-FSB.
-	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
-	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
-	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet} which do not present favorable trade offs compared with $\beta$-CROWN.
-Results can be found in \cite{crown} and are performed in the same conditions so can be compared.
-	\item Finally, we run several version of Compensate($K$) ({\color{blue} Comp} in Table \ref{tab:example}).
-First, we have a fixed choice for $K$ ($K=60$ for fast and $K=200$ for slow), with a fall back to a lower $K$ ($K=50$ for fast and $K=60$ for slow) if the bounds found is too far from the solution found (MIPGap $>0.5$ in Gurobi).
-We run (our implementation of) DeepPoly first, then the fast version, before running slow on the remaining images.
-	Further, we also experiment with an {\em adaptative} implementation, which lowers number $K$ adaptively between layers to adapt to the growing number $N$ of linear variables, which has an impact on the overall $\MILP(N,K)$ runtime.
-This is particularly useful for deeper network where $N$ is very different between the first and the last layer.
-Again, we run first an aggressive version of fast, before going to a more conservative slow version to treat the remaining images.
-All versions compute bounds for 20 neurons of the same layer in parallel, no GPU used.
-\end{itemize}
-
-In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
-DeepPoly/CROWN is by far the fastest, but also the most inaccurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
-This is because these DNNs, although of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
-
-Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall pipeline is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
-Our method compare favorably, both in terms of time and accuracy: our fast adaptive setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except for $5 \times 200$ which is quite pointless on this shallow DNN - the fast fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
-Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
-This is very promising for this idea of compensation, which indirectly treats dependencies between the variables, which PRIMA represents explicitly.
-
-\begin{table}[t!]
-	\centering
-	\begin{tabular}{|c||c|c|c||cc|cc||c|}
-
-		\hline
-		\text{DNN}  & DeepPoly & PRIMA & $\beta$-CROWN &\multicolumn{2}{@{}c@{}|}{\color{blue}\text{ Comp (adapt.) }} & \multicolumn{2}{@{}c@{}|}{\color{blue} \text{ Comp (fixed) }} & Upper\\ 
-		& / CROWN & (refined) & (refined BaB) & {\color{blue}fast} & {\color{blue}slow} & {\color{blue}fast} &{\color{blue}slow} & Bound\\
-		\hline \hline
-
-		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {\color{blue}$57.5\%$} & {\color{blue}$66.1\%$} & {\color{blue}$65.3\%$} & {\color{blue}$68.4\%$} &  $84.2 \%$ \\ 
-		$\epsilon = 0.026$ & 5s & 159s & 102s& {\color{blue}75s} & {\color{blue}140s} & {\color{blue}117s} & {\color{blue}142s} &  \\
-		\hline
-
-		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {\color{blue}$64.3\%$} & {\color{blue}$74.7\%$} & {\color{blue}$72\%$} & {\color{blue}$76.8\%$} & 
-		$90.1 \%$\\ 
-		$\epsilon = 0.015$ & 11s & 224s & 86s & {\color{blue}163s} & {\color{blue}285s} & {\color{blue}206s} & {\color{blue}279s}  &\\ \hline \hline
-
-		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {\color{blue}$52.7\%$} & {\color{blue}$59.7\%$} & {\color{blue}$61.4\%$} & {\color{blue}$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
-		$\epsilon = 0.026$ & 8s & 301s & 103s & {\color{blue}92.3s} & {\color{blue}179s} & {\color{blue}170s} & {\color{blue}346s} & \\
-		\hline
-
-		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {\color{blue}$68.1\%$} & 
-		{\color{blue}$79.1\%$} & {\color{blue}$72.6\%$} & {\color{blue}$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
-		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}697s$^\star$} & \\ \hline
-
-		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
-		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
-	\end{tabular}
-	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
-		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
-		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.}
-	\label{tab:example}
-	\vspace{-1cm}
-\end{table}
-
-Compared with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), the picture is more balanced, because the fundamentals of both algorithms are different.
-BaB focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary.
-Instead, we consider every node one by one from the input layer till the final layer, with the same accuracy.
-Hence Compensate($K$) will spend a lot of time on nodes which are not necessary for the verification.
-Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $1.4$ to
-$6.5$ times slower than $\beta$-CROWN. Notice Compensate($K$) it is not using GPUs. 
-Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), refined BaB uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting of Compensate($K$), with a small difference of less than $1.5\%$.
-On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in refined BaB cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
-the most accurate setting (slow fixed) of Compensate($K$) is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
-and from $17.6\%$ to $10.4\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in Compensate($K$) (see Section \ref{Discussion}).
-
-Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long timeouts ({\em refined} BaB is more accurate than pureBaB on these networks).
-We verify that in Table \ref{tab:example3}, on a larger DNN learnt in a natural way, namely MLP $6 \times 500$.
-We tested PureBaB with two timeouts (TO), from standard 30s to an extreme 2000s, to match the average runtime of our adaptative implementation (fast mode).
-Only $3.5\%$ more images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
-Notice that the refined BaB mode of ($\alpha$)$\beta$-Crown (first few layers using MILP) failed to run on this DNN (error code: NoImplementation), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as confirmed while running PRIMA (refined).
-
-% test
-
-\begin{table}[t!]
-	\centering
-	\begin{tabular}{|c||c|c|cc||c||c|}
-
-		\hline
-		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (pureBaB) \,}} & 
-		{\color{blue}Comp (adapt.)} & Upper\\ 
-		& / CROWN & (refined) & TO=30s & TO=2000s & {\color{blue}fast} & Bound\\
-		\hline \hline
-		$6\times500$\  &   $26\%$ & $32.5\%$ & $41\%$ & $44.5\%$  & {\color{blue}$\mathbf{65\%}$} & $92\%$ \\ 
-		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 954s & {\color{blue}925s} &\\ \hline
-	\end{tabular}
-	\caption{$\%$ of verified images and average runtime in seconds, over 200 images.}
-	\label{tab:example3}
-
-\end{table}
-
-\begin{figure}[h!]
-	\centering
-\begin{tikzpicture}
-	\begin{axis}[width=10cm,height=5cm,
-		xlabel={},
-		ylabel={},
-		legend pos=south east,
-		ymin=0,
-		xtick={1,2,3,4,5}, 
-		xticklabels={$5\times 100$, $8\times 100$, $5\times 200$, $8\times 200$, $6\times 500$},
-		]
-
-		\addplot[mark=triangle, blue] coordinates {
-			(1, 0.234)
-			(2, 0.2125)
-			(3, 0.206)
-			(4, 0.3)
-		};
-		\addlegendentry{fast fixed}
-
-		\addplot[mark=square, red] coordinates {
-			(1, 0.15)
-			(2, 0.115)
-			(3, 0.163)
-			(4, 0.1856)
-			(5, 0.308)
-		};
-		\addlegendentry{fast adaptative}
-
-	\end{axis}
-\end{tikzpicture}
-\caption{runtime (seconds per node)}
-\label{fig2}
-\end{figure}
-
-Last, we display the average runtime per number of nodes of both fast adaptive and fast fixed compensation, for the different DNNs considered.
-The runtime per node is not constant (due to $\LP(N,K)$), but it is still controlled and does not show an exponential blow-up, from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN.
-This indicates that Compensate($K$) can be run on larger DNNs without hitting the same complexity wall as pure BaB.
-
-\begin{table}[]
-	\centering
-	\begin{tabular}{|c|c|cc||cc||c|}
-		\hline
-		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
-		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}\CMP slow \,}}
-		& Upper\\ 
-		& / CROWN & TO=300s & TO=3000s & {\color{blue}adapt} & {\color{blue}fixed} & Bound\\
-		\hline \hline
-		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79.5\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
-		$\epsilon = 0.015$ & 17s & 95s? & 451s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
-	\end{tabular}
-	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
-	\label{tab:example4}
-\end{table}
-
-\section{Limitations and Discussion}
-\label{Discussion}
-
-For DNNs robustly trained, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close \cite{crown} to the upper bound on the $\%$ of verified images \cite{attack}.
-Compensation strength is not required in these contexts, reason why we did not consider it.
-
-We only considered DNNs with ReLU activation functions in this paper.
-The reason is that MILP, which is the basic block of Compensate($K$) (and BaB for $\beta$-Crown) can handle the ReLU activation function efficiently.
-Other activation functions are abstracted in more complex ways, e.g.
-by PRIMA (unlike $\beta$-CROWN).
-Still, the compensation paradigm is  orthogonal to the activation function.
-We believe that studying the compensation strength would be useful with other activation functions as well.
-We leave that for future work.
-
-Accuracy of Compensate($K$) is among the highest of the efficient verifiers that do abstraction on values.
-Runtime, while never blowing-up, can be on the slow side though, in particular for larger DNNs.
-There are many optimizations possible.
-The simplest is to run $\alpha$-$\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\alpha$-$\beta$-CROWN cannot conclude, possibly using more CPU cores to compute more nodes in parallel.
-Another simple way is to modify the {\em refined} BaB of $\beta$-CROWN to run Compensate($K$) on more layers than what exact MILP can do, and finish the verification using BaB.
-More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strength.
-Also, an analysis of important nodes for the uncertain output nodes could be performed, allowing to compute much faster less accurate bounds for those nodes not important.
-Last, one could perform a Refinement Abstraction framework similar to \cite{atva}, \cite{elboher}, or \cite{SRGR}.
-
-On the correlation between neurons, which PRIMA encodes explicitly, our results tend to show that it is more efficient to use the compensation strength to abstract the network.
-Still, considering ReLU nodes exactly tends to be very accurate locally, but less when the source of correlation is many layers away.
-Few important correlations {\em a la} PRIMA could be kept explicitly as linear constraints in the MILP encoding, helping to reduce the inaccuracies further.
+\input{experiments}
 

### 2024-01-25 Paper/experiments.tex
edits

@@
 
-The local robustness verification is performed on DNNs trained for the MNIST image dataset as its the only DNNs naturally trained ("MLP" (fully connected Multi Level Perceptron) $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers).
-Indeed, today's efficient methods leave between $12\%$ to $20\%$ of the images neither certified robust \cite{crown} nor with an attack to robustness found \cite{attack}, making them interesting DNNs to consider when improving accuracy.
-MNIST contains grayscale images of size $28 \times 28$ pixels ($752$ input neurons).
-For our evaluation, we evaluate on the standard first 1000 images of the dataset, to be directly comparable to experiments run in other papers, e.g.
-\cite{prima,crown}.
-We also experimented on (MLP) $6\times 500$ (results not reported in \cite{prima,crown}), checking the first 200 images of the dataset, as it takes a long time to run.
+We conducted our evaluation on neural networks trained on MNIST that have been employed in prior work.
+The networks have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, and $8 \times 200$.
+It is worth remarking that despite seemingly small size, these instances are challenging for the current state of the art techniques.
+In particular, the current state of the art methods are unable to characterize $12\%$ to $20\%$ of the images as neither certified robust \cite{crown} nor find an adversarial example \cite{attack}.
+Following methodology in prior work \cite{prima,crown}, we evaluate on the first 1000 images of the dataset.
+We also experimented on MLP of size $6\times 500$ (results not reported in \cite{prima,crown}), checking the first 200 images of the dataset, given the computational overhead associated with such larger networks.
 Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
-%, and a target label for verification.
+%Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
+
+\paragraph{Baseline}: 
+We compare the following verifiers performing value-abstraction:
+\begin{itemize}
+	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}.
+We report the runtime from our own implementation used in Compensate($K$).
+It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
+	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN.
+We use the results reported in \cite{prima} and \cite{crown} respectively for instances that were also used in prior works and report results for MLP $6\times500$ instances as it was not considered in prior work.
+
+%	They use GPU while we do not. When computing the whole correlated space, 
+%	parallelization is difficult.
+%	Notice that on these DNNs, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
+This is doable on the first few layers as the number of integer variable is not too large.
+By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
+	\item ($\alpha$)$\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date. 
+%	Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and using GPU implementation (while we do not). Performance of pure BaB on these 
+%	"hard to verify" DNNs is however impaired by the large number of branchs to consider.
+Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running the branching heuristic BaB-FSB.
+%	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
+	\item It is worth remarking that we do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
+	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods\cite{crown}.
+
+\end{itemize}
+
+The  objective of our evaluation was to answer the following  questions:
 
 \begin{enumerate}
-	\item Evaluate experimentally how the choice of the set $Z$ impacts the accuracy of $\MILP_Z$, and compare different choices for $K$ the size of $Z$,
-	\item Evaluate on benchmarks the percentage of images that can be verified
-	using compensating strength, and compare with other value abstraction verifiers,
+	\item How does the the choice of  the set  $Z$ impacts the accuracy of $\MILP_Z$? 
+	\item  How does the performance, measured as the percentage of images verified, of {\toolname} compare to that of prior state of the art approaches? 
 	\item Evaluate how the runtime of compensate($K$) scale with the size of DNNs.
@@
 
-\subsection{Choosing nodes based on Compensation strength}
+\subsection{Utility of Heuristic based on Compensation Strength  }
 
-The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
+To measure the impact of the heuristic based on compensation strength, we focused on the smallest MLP (i.e.
+of size $5\times 100$ \cite{crown}) so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
+We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
 
@@
 Formally, for a node $n$ with bounds $[\alpha,\beta]$, its uncertainty $unc(a) = \beta - \alpha$, and the average uncertainty of a layer $l$ is $\dfrac{\sum_{a\in l} unc(a)}{|l|}.$
-
-We experiment with the smallest network (MLP $5\times 100$ in \cite{crown}, 
-called $5 \times 100$ in \cite{prima}, and abusively $6 \times 100$ in \cite{deeppoly}, perturbation $\varepsilon=0.026$), so that we can obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
-We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
 
@@
 
-We first experiment with the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer.  Let $c$ be a node of the second layer.
-A compensating pair $(\pi,\pi')$ of paths with target $c$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
+%KSM: I don't think this is really the place for the paragraph below
+% Let $c$ be a node of the second layer.
+%A compensating pair $(\pi,\pi')$ of paths with target $c$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
 The compensating strength for $(b,b')$ is defined as $comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$.
@@
 
+We first focus on the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer. 
 We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
@@
 \subsection{Comparison with value-abstraction Verifiers}
-
-We compare the following verifiers performing value-abstraction:
-\begin{itemize}
-	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}.
-We report the runtime from our own implementation used in Compensate($K$).
-It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
-Our focus is not to have the most optimized tool, but mainly to evaluate the accuracy of Compensate($K$).
-	\item PRIMA, with results reported in \cite{prima} and \cite{crown}, as it is the closest in practice with our algorithm, computing accurate bounds for all neurons (as we do), although with a different technique: they focus on explicit correlations between neurons, while we consider the correlations indirectly through a better network abstraction.
-They use GPU while we do not.
-When computing the whole correlated space,
-	parallelization is difficult.
-	Notice that on these DNNs, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
-This is doable on the first few layers as the number of integer variable is not too large.
-By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
-	\item ($\alpha$)$\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date.
-Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and using GPU implementation (while we do not).
-Performance of pure BaB on these
-	"hard to verify" DNNs is however impaired by the large number of branchs to consider.
-Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running the branching heuristic BaB-FSB.
-	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
-	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
-	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet} which do not present favorable trade offs compared with $\beta$-CROWN.
-Results can be found in \cite{crown} and are performed in the same conditions so can be compared.
-	\item Finally, we run several version of Compensate($K$) ({\color{blue} Comp} in Table \ref{tab:example}).
-First, we have a fixed choice for $K$ ($K=60$ for fast and $K=200$ for slow), with a fall back to a lower $K$ ($K=50$ for fast and $K=60$ for slow) if the bounds found is too far from the solution found (MIPGap $>0.5$ in Gurobi).
-We run (our implementation of) DeepPoly first, then the fast version, before running slow on the remaining images.
-	Further, we also experiment with an {\em adaptative} implementation, which lowers number $K$ adaptively between layers to adapt to the growing number $N$ of linear variables, which has an impact on the overall $\MILP(N,K)$ runtime.
-This is particularly useful for deeper network where $N$ is very different between the first and the last layer.
-Again, we run first an aggressive version of fast, before going to a more conservative slow version to treat the remaining images.
-All versions compute bounds for 20 neurons of the same layer in parallel, no GPU used.
-\end{itemize}
 

### 2024-01-26 Paper/proofs.tex
b1 preparation

@@
 					\end{enumerate}
-					That is, $a_k$ is not a source of a weak compensating pair. We denote 
+					Hence, $a_k$ is not a source of a weak compensating pair. We denote 
 					$A_{pure}$ by $I$ for short.
@@
 
+			For an input $\vx$ and a subset $S$ of input nodes, we denote by $\boldsymbol{x}_S$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
+We use $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and
+			$\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)=\Val_{\boldsymbol{x}}(z)$.
+
+			Invoking Lemma \ref{lem:subnetwork}, we can apply Theorem 1 on $D_I$, and obtain two input vectors $\boldsymbol{x}_I^*,\boldsymbol{x}_I^{\sharp}$ on $I$
+			minimizing and maximizing all the nodes in $D_I$.
+
+			\smallskip
+
 			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. 
-Because weak compensating paths are allowed, the sign function is no longer defined on all nodes.
-$S$ is defined on all nodes $a_i \in I$.
-			Further, we have:
+			Because weakly compensating paths are allowed, the sign function is no longer defined on all nodes.
+$S$ is defined for all nodes from which there is no weakly compensating pairs of paths to $z$.
+In particular, $S$ is defined on all nodes of $I$.
 
 			\begin{lemma}\label{lem:sign}
-				For a node $n$, if there exists at least one path from a node $a_i\in I$ to $n$ with nonzero weight, then $S$ is defined on $n$.
+				Let $m,n$ be two nodes, such that $S$ is defined on $m$ and there is a path $\rho$ with non zero weight to a node $n$. Then $S$ is defined on $n$
+				 (there is no compensating pair of paths from $n$ to $z$).
+				Further, $S(n)= Sign(weight(\rho)) S(m)$.
 			\end{lemma}
@@
 			\begin{proof}
-				By contradiction, suppose that there exists two paths $\rho_1,\rho_2$ from $n$ to $z$ with (strictly) different signs.
-The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$.
-\qed
+				By contradiction, assume that there exists two paths $\rho_1,\rho_2$ from 
+				$n$ to $z$ with (strictly) different signs. The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$. \qed
 			\end{proof}
 
-			Hence for any node $m$ such that $S$ is undefined on $m$, value of $m$ can only depends upon input nodes in $J$.
+			Hence, for all node $n$, either $S$ is defined on $n$, or 
+			$n$ depends only upon input nodes in $J$.
+			Let us call $D_J$ the set of such nodes which only depends upon nodes in $J$.
+			$D_J$ forms a sub-network.
+			$D_J$ contains the set of all nodes from which there is a weakly compensating pair of paths to $z$.
+			By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node: any path from any input node must have zero weight to it.
+			For a node $b$ for which $S$ is undefined, $b$ thus only depends on $J$; so, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ will be fixed.
+			Notice that $D_I \sqcup D_J$ does not cover the DNN entirely in general.
 
@@
 			\end{proof}
-
-			\fi
 
@@
 			\end{proof}
-
-			By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node: any path from any input node must have zero weight to it.
-
-			For an input $\vx$ and a subset $S$ of input nodes, we denote by $\boldsymbol{x}_S$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
-We use $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and $\Val(z)=\Val_{\boldsymbol{x}}(z)=\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)$.
-			For a node $b$ for which $S$ is undefined, $b$ only depends on $J$; so, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ will be fixed.
-
-			We define $\boldsymbol{x}_I^*$ to be the input vector such that for all $a_i \in I$, the value $x_{a_i}$ for $a_i$ gets its maximal value (if $S(a_i)=1$ or $0$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
-Similarly, we define $\boldsymbol{x}_I^\sharp$ to be the input vector such that for all $a_i \in I$, the value $x_{a_i}$ for $a_i$ gets its maximal value (if $S(a_i)=-1$ or $0$) or $a_i$ gets its minimal value (if $S(a_i)=1$).
+			\fi
 
 			\begin{lemma} \label{lem:reach_max_2}
-				Let $b$ be an output node or a node in a hidden layers such that $S(b)=1$. Then for any valuation $\boldsymbol{x}^0_J$,	we have: 
+				Let $n$ be a node on which $S$ is defined. If $S(n)=1$,
+				for any valuation $\boldsymbol{x}^0_J$,	we have: 
 				$$\max_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^*,\boldsymbol{x}^0_J}(b).$$
 
-				If $S(b)=-1$, then a similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$. The opposite holds for $\min_{\boldsymbol{x}_I}$.
+				$$\min_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^{\sharp},\boldsymbol{x}^0_J}(b).$$
+
+				If $S(b)=-1$, 
+				$$\max_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^{\sharp},\boldsymbol{x}^0_J}(b).$$
+
+				$$\min_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^{*},\boldsymbol{x}^0_J}(b).$$
+
 			\end{lemma}
@@
 			\begin{proof}	
+				Fix an input vector $\boldsymbol{x}^0_J$.
+				This also fixes the values in $D_J$.
+				Consider the DNN $D'$ with input nodes $a_i\in I$, where all the 
+				edges from $m \in D_J$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_J}(m)$) for $n$ (we summ all these bias for a neuron $n$).
+				We denote $\val'$ values of nodes in this DNN $D'$.
 
-				For any fixed input vector $\boldsymbol{x}^0_J$, consider the DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ 
-				%and their propagation in hidden layers 	
-				as bias. We denote $\val'$ values of nodes In this DNN $D'$.
-				 We have $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z) = \val'_{\vx}(\boldsymbol{x}_I)(z)$.
-
-				In the simplified $D'$, there is no compensating path because of the definition of $I$.
-Therefore we can apply Lemma \ref{lem:key1} to get that $\Val_{x_I,\boldsymbol{x}^0_J}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
+				We have $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z) = \val'_{\boldsymbol{x}_I}(z)$.
+				In the simplified $D'$, there is no weakly compensating path to $z$ because 
+				$D_J$ contains all the source of weakly compensating path to $z$.
+				Therefore we can apply Lemma \ref{lem:key1} to get that 
+				$\val'_{x_I}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and conclude by using $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z) = \val'_{\boldsymbol{x}_I}(z)$.
+The case for min is similar.
 \qed
@@
 
-			From Lemma \ref{lem:reach_max_2}, we have the following corrolary:
+			From Lemma \ref{lem:reach_max_2}, we immediatly obtain the following corollary:
 
@@
 			$$\max(b)=\max_{\vx_j} \val_{\vx^{\star}_I,\vx_J}(b)$$
-
+			$$\min(b)=\max_{\vx_j} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
 			and for $S(b)=-1$:
@@
 			$$\max(b)=\max_{\vx_j} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
+			$$\min(b)=\max_{\vx_j} \val_{\vx^{\star}_I,\vx_J}(b)$$
 			\end{corollary}

### 2024-01-26 Paper/experiments.tex
b1 preparation
edits

@@
 	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}.
-We report the runtime from our own implementation used in Compensate($K$).
+We report the runtime from our own implementation used in {\toolname}.
 It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
@@
 	\item  How does the performance, measured as the percentage of images verified, of {\toolname} compare to that of prior state of the art approaches? 
-	\item Evaluate how the runtime of compensate($K$) scale with the size of DNNs.
+	\item Evaluate how the runtime of {\toolname} scale with the size of DNNs.
 \end{enumerate}
@@
 
-\subsection{Comparison with value-abstraction Verifiers}
+\subsection{Comparison with Prior State of the Art}
 
-In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
-DeepPoly/CROWN is by far the fastest, but also the most inaccurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
-This is because these DNNs, although of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
+We present the runtime and accuracy analysis of various techniques in Table~\ref{tab:example}.
+Several observations are noteworthy: DeepPoly/CROWN is by far the fastest, yet it is also the least accurate, certifying robustness for fewer than $30\%$ of the images.
+In contrast, there are at least $82\%$ of the images for which no attack is found (attacks computed by \cite{attack} in $\beta$-CROWN).
+Similarly, while PRIMA achieves better accuracy than DeepPoly/CROWN but falls short of {\toolname}.
 
-Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall pipeline is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
-Our method compare favorably, both in terms of time and accuracy: our fast adaptive setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except for $5 \times 200$ which is quite pointless on this shallow DNN - the fast fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
+Next, we shift focus to the comparison with $\beta$-CROWN, where we observe intriguing trade-offs.
+As network sizes increase, {\toolname} demonstrates better accuracy in comparison to $\beta$-CROWN.
+As expected, there's a trade-off between runtime and accuracy: {\toolname} can verify more images, albeit at the cost of increased computation time.
+However, more often than not, our primary concern lies in running a tool for a fixed timeout to determine whether it can verify the desired property within that time.
+
+% BaB focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary.
+Instead, we consider every node one by one from the input layer till the final layer, with the same accuracy.
+Hence {\toolname} will spend a lot of time on nodes which are not necessary for the verification.
+% 
+%It is worth remarking that our prototype implementation (in Python)  Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $1.4$ to 
+%$6.5$ times slower than $\beta$-CROWN. Notice {\toolname} it is not using GPUs. 
+%Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), refined BaB uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting of {\toolname}, with a small difference of less than $1.5\%$.
+On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in refined BaB cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
+%the most accurate setting (slow fixed) of {\toolname} is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
+%and from $17.6\%$ to $10.4\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in {\toolname} (see Section \ref{Discussion}).
+
+%Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
+This is very promising for this idea of compensation, which indirectly treats dependencies between the variables, which PRIMA represents explicitly.
+
+%In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
+%DeepPoly/CROWN is by far the fastest, but also the most inaccurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
+%This is because these DNNs, although of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
+
+%Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall pipeline is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
+%Now, moving on to PRIMA, our 
+%Our method compare favorably, both in terms of time and accuracy: our fast adaptive setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except for $5 \times 200$ which is quite pointless on this shallow DNN - the fast fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
 Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
@@
 
-\begin{table}[t!]
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+
+\begin{table}[htb]
 	\centering
-	\begin{tabular}{|c||c|c|c||cc|cc||c|}
+
+		\begin{tabularx}{0.9\textwidth}{|C||C|C|C|C|C|}
 
 		\hline
-		\text{DNN}  & DeepPoly & PRIMA & $\beta$-CROWN &\multicolumn{2}{@{}c@{}|}{\color{blue}\text{ Comp (adapt.) }} & \multicolumn{2}{@{}c@{}|}{\color{blue} \text{ Comp (fixed) }} & Upper\\ 
-		& / CROWN & (refined) & (refined BaB) & {\color{blue}fast} & {\color{blue}slow} & {\color{blue}fast} &{\color{blue}slow} & Bound\\
+		\text{DNN} & \shortstack{DeepPoly/\\CROWN} & PRIMA & $\beta$-CROWN & {\toolname} & \shortstack{Upper\\Bound}\\ 
 		\hline \hline
 
-		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {\color{blue}$57.5\%$} & {\color{blue}$66.1\%$} & {\color{blue}$65.3\%$} & {\color{blue}$68.4\%$} &  $84.2 \%$ \\ 
-		$\epsilon = 0.026$ & 5s & 159s & 102s& {\color{blue}75s} & {\color{blue}140s} & {\color{blue}117s} & {\color{blue}142s} &  \\
+		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {$68.4\%$} &  $84.2 \%$ \\ 
+		$\epsilon = 0.026$ & 5s & 159s & 102s & {142s} &  \\
 		\hline
 
-		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {\color{blue}$64.3\%$} & {\color{blue}$74.7\%$} & {\color{blue}$72\%$} & {\color{blue}$76.8\%$} & 
+		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {$76.8\%$} & 
 		$90.1 \%$\\ 
-		$\epsilon = 0.015$ & 11s & 224s & 86s & {\color{blue}163s} & {\color{blue}285s} & {\color{blue}206s} & {\color{blue}279s}  &\\ \hline \hline
+		$\epsilon = 0.015$ & 11s & 224s & 86s & {279s}  &\\ \hline \hline
 
-		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {\color{blue}$52.7\%$} & {\color{blue}$59.7\%$} & {\color{blue}$61.4\%$} & {\color{blue}$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
-		$\epsilon = 0.026$ & 8s & 301s & 103s & {\color{blue}92.3s} & {\color{blue}179s} & {\color{blue}170s} & {\color{blue}346s} & \\
+		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
+		$\epsilon = 0.026$ & 8s & 301s & 103s & {346s} & \\
 		\hline
 
-		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {\color{blue}$68.1\%$} & 
-		{\color{blue}$79.1\%$} & {\color{blue}$72.6\%$} & {\color{blue}$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
-		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}697s$^\star$} & \\ \hline
+		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
+		$\epsilon = 0.015$ & 17s & 395s & 95s  & {697s$^\star$} & \\ \hline
 
@@
 		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
-	\end{tabular}
+	\end{tabularx}
+
 	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
 		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
-		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.}
+%		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.
+}
 	\label{tab:example}
-	\vspace{-1cm}
 \end{table}
 
-Compared with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), the picture is more balanced, because the fundamentals of both algorithms are different.
+%\begin{table}[t!]
+%	\centering
+%	\begin{tabular}{|c||c|c|c||cc|cc||c|}
+%		
+%		\hline
+%		\text{DNN}  & DeepPoly & PRIMA & $\beta$-CROWN &\multicolumn{2}{@{}c@{}|}{\color{blue}\text{ Comp (adapt.) }} & \multicolumn{2}{@{}c@{}|}{\color{blue} \text{ Comp (fixed) }} & Upper\\ 
+%		& / CROWN & (refined) & (refined BaB) & {\color{blue}fast} & {\color{blue}slow} & {\color{blue}fast} &{\color{blue}slow} & Bound\\
+%		\hline \hline
+%		
+%		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {\color{blue}$57.5\%$} & {\color{blue}$66.1\%$} & {\color{blue}$65.3\%$} & {\color{blue}$68.4\%$} &  $84.2 \%$ \\ 
+%		$\epsilon = 0.026$ & 5s & 159s & 102s& {\color{blue}75s} & {\color{blue}140s} & {\color{blue}117s} & {\color{blue}142s} &  \\
+%		\hline	
+%		
+%		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {\color{blue}$64.3\%$} & {\color{blue}$74.7\%$} & {\color{blue}$72\%$} & {\color{blue}$76.8\%$} & 
+%		$90.1 \%$\\ 
+%		$\epsilon = 0.015$ & 11s & 224s & 86s & {\color{blue}163s} & {\color{blue}285s} & {\color{blue}206s} & {\color{blue}279s}  &\\ \hline \hline
+%		
+%		
+%		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {\color{blue}$52.7\%$} & {\color{blue}$59.7\%$} & {\color{blue}$61.4\%$} & {\color{blue}$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
+%		$\epsilon = 0.026$ & 8s & 301s & 103s & {\color{blue}92.3s} & {\color{blue}179s} & {\color{blue}170s} & {\color{blue}346s} & \\
+%		\hline
+%		
+%		
+%		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {\color{blue}$68.1\%$} & 
+%		{\color{blue}$79.1\%$} & {\color{blue}$72.6\%$} & {\color{blue}$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
+%		$\epsilon = 0.015$ & 17s & 395s & 95s  & {\color{blue}297s} & {\color{blue}535s} & {\color{blue}$480s$} & {\color{blue}697s$^\star$} & \\ \hline
+%		
+%		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
+%		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
+%	\end{tabular}
+%	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
+%		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
+%		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.}
+%	\label{tab:example}
+%%	\vspace{-1cm}
+%\end{table}
+
+%Compared with $\beta$-CROWN (also using a refinement on the first few layers using exact MILP), the picture is more balanced, because the fundamentals of both algorithms are different.
 BaB focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary.
 Instead, we consider every node one by one from the input layer till the final layer, with the same accuracy.
-Hence Compensate($K$) will spend a lot of time on nodes which are not necessary for the verification.
+Hence {\toolname} will spend a lot of time on nodes which are not necessary for the verification.
 Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $1.4$ to
-$6.5$ times slower than $\beta$-CROWN. Notice Compensate($K$) it is not using GPUs. 
-Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), refined BaB uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting of Compensate($K$), with a small difference of less than $1.5\%$.
+%$6.5$ times slower than $\beta$-CROWN. Notice {\toolname} it is not using GPUs. 
+%Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), refined BaB uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting of {\toolname}, with a small difference of less than $1.5\%$.
 On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in refined BaB cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
-the most accurate setting (slow fixed) of Compensate($K$) is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
-and from $17.6\%$ to $10.4\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in Compensate($K$) (see Section \ref{Discussion}).
+%the most accurate setting (slow fixed) of {\toolname} is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
+%and from $17.6\%$ to $10.4\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in {\toolname} (see Section \ref{Discussion}).
 
-Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long timeouts ({\em refined} BaB is more accurate than pureBaB on these networks).
+%KSM: I think this paragraph doesn't make very convincing case. 
+%Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long timeouts ({\em refined} BaB is more accurate than pureBaB on these networks).
 We verify that in Table \ref{tab:example3}, on a larger DNN learnt in a natural way, namely MLP $6 \times 500$.
-We tested PureBaB with two timeouts (TO), from standard 30s to an extreme 2000s, to match the average runtime of our adaptative implementation (fast mode).
+%We tested PureBaB with two timeouts (TO), from standard 30s to an extreme 2000s, to match the average runtime of our adaptative implementation (fast mode).
 Only $3.5\%$ more images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
@@
 \end{table}
+
+\begin{table}[]
+	\centering
+	\begin{tabular}{|c|c|cc||cc||c|}
+		\hline
+		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
+		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}\CMP slow \,}}
+		& Upper\\ 
+		& / CROWN & TO=300s & TO=3000s & {\color{blue}adapt} & {\color{blue}fixed} & Bound\\
+		\hline \hline
+		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79.5\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
+		$\epsilon = 0.015$ & 17s & 95s? & 451s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
+	\end{tabular}
+	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
+	\label{tab:example4}
+\end{table}
+
+\subsection{Scalability of {\toolname} with Size of DNNs}
+
+We now focus on understanding the potential of {\toolname} for even larger networks than those that are usually considered in the verification community.
+To this end, Figure~\ref{fig2} presents the  average runtime per node across various DNNS.
+Observe that while  the average runtime per node isn't fixed (attributable to $\LP(N,K)$), it remains regulated, avoiding exponential increases — from 0.1s per node for the smallest DNN to 0.3s per node for the largest.
+This suggests that {\toolname} is scalable to larger DNNs, bypassing the high complexity barrier often encountered with approaches such as those based on pure branch and bound.
 
@@
 
-Last, we display the average runtime per number of nodes of both fast adaptive and fast fixed compensation, for the different DNNs considered.
-The runtime per node is not constant (due to $\LP(N,K)$), but it is still controlled and does not show an exponential blow-up, from 0.1s per node for the smallest DNN to 0.3s per node for the biggest DNN.
-This indicates that Compensate($K$) can be run on larger DNNs without hitting the same complexity wall as pure BaB.
-
-\begin{table}[]
-	\centering
-	\begin{tabular}{|c|c|cc||cc||c|}
-		\hline
-		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
-		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}\CMP slow \,}}
-		& Upper\\ 
-		& / CROWN & TO=300s & TO=3000s & {\color{blue}adapt} & {\color{blue}fixed} & Bound\\
-		\hline \hline
-		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79.5\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
-		$\epsilon = 0.015$ & 17s & 95s? & 451s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
-	\end{tabular}
-	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
-	\label{tab:example4}
-\end{table}
-
 \section{Limitations and Discussion}
@@
 We only considered DNNs with ReLU activation functions in this paper.
-The reason is that MILP, which is the basic block of Compensate($K$) (and BaB for $\beta$-Crown) can handle the ReLU activation function efficiently.
+The reason is that MILP, which is the basic block of {\toolname} (and BaB for $\beta$-Crown) can handle the ReLU activation function efficiently.
 Other activation functions are abstracted in more complex ways, e.g.
@@
 
-Accuracy of Compensate($K$) is among the highest of the efficient verifiers that do abstraction on values.
+Accuracy of {\toolname} is among the highest of the efficient verifiers that do abstraction on values.
 Runtime, while never blowing-up, can be on the slow side though, in particular for larger DNNs.
 There are many optimizations possible.
-The simplest is to run $\alpha$-$\beta$-CROWN first in the pipeline, and only use Compensate($K$) for those images for which $\alpha$-$\beta$-CROWN cannot conclude, possibly using more CPU cores to compute more nodes in parallel.
-Another simple way is to modify the {\em refined} BaB of $\beta$-CROWN to run Compensate($K$) on more layers than what exact MILP can do, and finish the verification using BaB.
+The simplest is to run $\alpha$-$\beta$-CROWN first in the pipeline, and only use {\toolname} for those images for which $\alpha$-$\beta$-CROWN cannot conclude, possibly using more CPU cores to compute more nodes in parallel.
+Another simple way is to modify the {\em refined} BaB of $\beta$-CROWN to run {\toolname} on more layers than what exact MILP can do, and finish the verification using BaB.
 More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strength.

### 2024-01-26 Paper/experiments.tex

@@
 
-\begin{table}[t!]
-	\centering
-	\begin{tabular}{|c||c|c|cc||c||c|}
+%
+%\begin{table}[t!]
+%	\centering
+%	\begin{tabular}{|c||c|c|cc||c||c|}
+%		
+%		\hline
+%		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (pureBaB) \,}} & 
+%		{\color{blue}Comp (adapt.)} & Upper\\ 
+%		& / CROWN & (refined) & TO=30s & TO=2000s & {\color{blue}fast} & Bound\\
+%		\hline \hline
+%		$6\times500$\  &   $26\%$ & $32.5\%$ & $41\%$ & $44.5\%$  & {\color{blue}$\mathbf{65\%}$} & $92\%$ \\ 
+%		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 954s & {\color{blue}925s} &\\ \hline
+%	\end{tabular}
+%	\caption{$\%$ of verified images and average runtime in seconds, over 200 images.}
+%	\label{tab:example3}
+%	
+%\end{table}
 
-		\hline
-		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (pureBaB) \,}} & 
-		{\color{blue}Comp (adapt.)} & Upper\\ 
-		& / CROWN & (refined) & TO=30s & TO=2000s & {\color{blue}fast} & Bound\\
-		\hline \hline
-		$6\times500$\  &   $26\%$ & $32.5\%$ & $41\%$ & $44.5\%$  & {\color{blue}$\mathbf{65\%}$} & $92\%$ \\ 
-		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 954s & {\color{blue}925s} &\\ \hline
-	\end{tabular}
-	\caption{$\%$ of verified images and average runtime in seconds, over 200 images.}
-	\label{tab:example3}
-
-\end{table}
-
-\begin{table}[]
-	\centering
-	\begin{tabular}{|c|c|cc||cc||c|}
-		\hline
-		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
-		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}\CMP slow \,}}
-		& Upper\\ 
-		& / CROWN & TO=300s & TO=3000s & {\color{blue}adapt} & {\color{blue}fixed} & Bound\\
-		\hline \hline
-		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79.5\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
-		$\epsilon = 0.015$ & 17s & 95s? & 451s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
-	\end{tabular}
-	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
-	\label{tab:example4}
-\end{table}
+%\begin{table}[]
+%	\centering
+%	\begin{tabular}{|c|c|cc||cc||c|}
+%		\hline
+%		\text{DNN}  & DeepPoly &  \multicolumn{2}{@{}c@{}|}{\text{ $\alpha$-$\beta$-CROWN (refinedBaB) \,}} & 
+%		\multicolumn{2}{@{}c@{}|}{\text{ \color{blue}\CMP slow \,}}
+%		& Upper\\ 
+%		& / CROWN & TO=300s & TO=3000s & {\color{blue}adapt} & {\color{blue}fixed} & Bound\\
+%		\hline \hline
+%		$8\times200$\  &   $25\%$? & $72\%$? & $\mathbf{79.5\%}$ & {\color{blue}$75.5\%$}  & {\color{blue}$77\%$} & $91\%$ \\ 
+%		$\epsilon = 0.015$ & 17s & 95s? & 451s & {\color{blue}391s} & {\color{blue}562s} &\\ \hline
+%	\end{tabular}
+%	\caption{WIP! $\%$ of verified images over 200 images. To see how refined BAB scale with TimeOut.}
+%	\label{tab:example4}
+%\end{table}
 

### 2024-01-26 Paper/proofs.tex
proof Th 3

@@
 
-			\subsection{Preparation}
+			\subsection{Proof of Theorem \ref{thm:2}}
 
@@
 				Consider the DNN $D'$ with input nodes $a_i\in I$, where all the 
-				edges from $m \in D_J$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_J}(m)$) for $n$ (we summ all these bias for a neuron $n$).
+				edges from $m \in D_J$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_J}(m)$) for $n$ (we sum all these bias for a neuron $n$).
 				We denote $\val'$ values of nodes in this DNN $D'$.
@@
 			\begin{corollary}
+				\label{corr:main}
 			For a node $b$ with $S(b)=1$:
@@
 
-			\subsection{$\MILP_X$ is accurate}
+			%\subsection{$\MILP_X$ is accurate}
 
 			We denote by $X=B_{open}$, and consider $\MILP_{X}$.
-			Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$.
+			Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$. We want to show that $\beta= \max(z)$. 
+			%As the MILP abstraction is a sound over-approximation, it suffices to show that %$\beta\leq \max (z)$.
+			The case for $\alpha$ is similar.
 
@@
 
-			\fi
-
-		We want to show that $\beta= \max(z)$. As the MILP abstraction is a sound over-approximation, it suffices to show that $\beta\leq \max (c)$.
-		The case for $\alpha$ is similar.
 		%We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:
-
-\iffalse
 
@@
 			\end{lemma}
-
-\fi
 
@@
 
-			From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{thm:2}.
+	\fi
 
-			\subsubsection*{From weak to compensating}
+We are now ready to finish the proof of Theorem \ref{thm:2}.
+
+\begin{proof}
+	We show that $\beta=\max(z)$.
+
+	We fix the input vector $\vx^*_I$ for input $I$.
+	This also fixes the values in $D_I$.
+	Consider the DNN $D'$ with input nodes $J$, where all the 
+	edges from $m \in D_I$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_I}(m)$) for $n$ (we sum all these bias for a neuron $n$).
+	We denote $\val'$ values of nodes in this DNN $D'$.
+
+	We have $\val'_{\boldsymbol{x}_J}(n)=\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n)$ 
+	for every node $n$ of $D'$. All the ReLU nodes of $D'$ are in $X$, by definition of $X$.
+Thus $\MILP_X$ will be fully accurate in $D'$. Let $\beta'$ denote its upper bound.
+We have $\beta'=\max_{\vx{_J}} (\val'_{\vx_{J}}(z)) = 
+\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n) = \max(z)$ by Corrolary \ref{corr:main}.
+Now, in $D$, $\MILP_X$ will use simple LP on $D_I$, which suffices to get the upper bound $\val_{\vx^*_I}(n)=\max(n)$ for all $n$ in $D_I$ and the values will be pushed as bias in $D'$.
+Therefore, $\beta=\beta'=\max(z)$.
+
+The case for $\alpha=min(z)$ is similar. \qed
+
+\end{proof}
+
+\subsection{From weak to compensating}
 

### 2024-01-26 Paper/proofs.tex
th3

@@
 
-			$$\max(b)=\max_{\vx_j} \val_{\vx^{\star}_I,\vx_J}(b)$$
-			$$\min(b)=\max_{\vx_j} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
+			$$\max(b)=\max_{\vx_J} \val_{\vx^{\star}_I,\vx_J}(b)$$
+			$$\min(b)=\max_{\vx_J} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
 			and for $S(b)=-1$:
 
-			$$\max(b)=\max_{\vx_j} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
-			$$\min(b)=\max_{\vx_j} \val_{\vx^{\star}_I,\vx_J}(b)$$
+			$$\max(b)=\max_{\vx_J} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
+			$$\min(b)=\max_{\vx_J} \val_{\vx^{\star}_I,\vx_J}(b)$$
 			\end{corollary}
@@
 
-			We denote by $X=B_{open}$, and consider $\MILP_{X}$.
-			Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$. We want to show that $\beta= \max(z)$. 
+			%We want to show that $\beta= \max(z)$. 
 			%As the MILP abstraction is a sound over-approximation, it suffices to show that %$\beta\leq \max (z)$.
-			The case for $\alpha$ is similar.
+			%The case for $\alpha$ is similar.
 
@@
 
-We are now ready to finish the proof of Theorem \ref{thm:2}.
+	We denote by $X=B_{open}$, and consider $\MILP_{X}$.
+	Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$. We are now ready to finish the proof of Theorem \ref{thm:2}.
 
@@
 
-			Now, we show that Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ form this weak compensating pair.
+			We now show Theorem \ref{th2} from Theorem \ref{thm:2}.
+			Assume that $n$ is a node in a weakly compensating path $\rho$.
 
-			Cut $P,P'$ into segments $P_0,P_1,\cdots$, and $P'_0,P'_1,\cdots$ at each common node; hence each $P_i,P_i'$ either have not common nodes (except the start and end nodes), or are the same.
-Now, for node $a$, there are three cases:
-			\begin{itemize}
-				\item $a$ is a common nodes.
+			There are three mutually exclusive cases:
+			\begin{enumerate}
+				\item $n$ is on a compensating pair of paths $\rho,\rho'$ to $z$ (but not its source or target), otherwise:
 
-				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the same sign.
+				\item $n$ is on a compensating pair of paths $\rho,\rho'$ to $z' \neq z$ (but not its source or target), otherwise:
 
-				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the different sign.
-			\end{itemize}
+				\item $n$ is not on any compensating pair of paths to any node (except may be as source or target).
+			\end{enumerate}
+
+			In the first case, the ReLU for $n$ will be opened, so we do not need to worry about this case.
+
+			In the other cases, the ReLU associated with node $n$ will not be in $X$ 
+			(not opened in $\MILP_X$).
+			In the second case, as we assumed without loss of generality that $z$ was the unique output node, it means that $z'$ is in a layer strictly before $z'$.
+			Consider all the possible associated $z'$.
 

### 2024-01-26 Paper/proofs.tex
th3
th2

@@
 
-\begin{proof}
+\begin{proof}[of Theorem \ref{thm:2}]
 	We show that $\beta=\max(z)$.
@@
 
-\subsection{From weak to compensating}
+\subsection{Proof of Theorem \ref{th2}}
+
+Note: it does not need directly the previous proof, although it uses the same arguments.
+We should adapt the previous argument here, and then remove B.1. altogether.
+
+We assume the fairly light hypothesis (H1) that the DNN is such that for every 2 paths $\rho_1,\rho_2$ (not necessarily disjoint) from any $m$ to any $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$.
+Further we assume without loss of generality that every node can be reached from at least one input with a path of non-zero weight (otherwise we just remove this node altogether).
+We also assume without loss of generality that there is no node which can only reach $z$ with path of weight $0$, as such nodes have no contribution to the value $\val(z)$.
+We denote $m<n$ to mean that there exists a path with non zero weight from $m$ to $n$.
+
+			\smallskip
 
 			We now show Theorem \ref{th2} from Theorem \ref{thm:2}.
-			Assume that $n$ is a node in a weakly compensating path $\rho$.
+			Let $X$ be the set of nodes on compensating paths with target $z$, but not as source or target.
 
-			There are three mutually exclusive cases:
-			\begin{enumerate}
-				\item $n$ is on a compensating pair of paths $\rho,\rho'$ to $z$ (but not its source or target), otherwise:
+			Let $Z$ be the subset of nodes $n$ of the DNN such that $S$ is defined on $n$ 
+			wrt node $z$.
+As proved earlier, $Z$ is suffix closed, i.e.
+if $m<n<z$ with $m \in Z$, then $n \in Z$.
+We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative sign.
+They form 2 independent subnetworks of the DNN.
+			$X$ can intersect both $Z_+$ and $Z_-$.
+			For nodes not in $Z$: some may be in $X$, and some may be out of $X$.
+			We call $X_+ = Z_+ \cap X$ and $X_-=Z_- \cap X$, as well as 
+			defined $Y_+,Y_-$ such that $Z_+ = X_+ \sqcup Y_+$ and $Z_- = X_- \sqcup Y_-$.
 
-				\item $n$ is on a compensating pair of paths $\rho,\rho'$ to $z' \neq z$ (but not its source or target), otherwise:
+			Because of (H1), nodes not in $Z$ (and not in the inputs) are in $X$:
+			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite sign. 
+			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
+			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight.
+Depending on the sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$.
+We call $X_*$ this subset $X$.
 
-				\item $n$ is not on any compensating pair of paths to any node (except may be as source or target).
-			\end{enumerate}
+\begin{lemma}
+	\label{lemma10}
+		Let $y \in Y_+$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
+		of paths  with weights of opposite sign with $\rho_1$ from $m$ to $y$ and 
+		with $\rho_2$ from $m$ to $z$ (even non disjoint).
+\end{lemma}
+
+\begin{proof}
+  $y \notin X$, so it is not on a pair of compensating pair with target $z$.
+  Let $\rho$ be a path from $y$ to $z$ (it has positive weight has $y \in Z_+$).
+  Hence $\rho_1 \rho, \rho_2$ have opposite sign, and they must meet before $z$.
+
+  If $\rho_1 \rho$ meets $\rho_2$ after $y$, then we use $(H_1)$ to get another disjoint path from $y$ to $z$ (it has positive weight has $y \in Z_+$), it would not meet $\rho_2$, a contradiction.
+
+  Hence $\rho_1$ must meet $\rho_2$ (that is before or at $y$).
+  Their weights must be of opposite sign, otherwise we can inductively reapplied the same argument to their suffixes.
+  Let $\rho_1=\rho_1'\rho_1''$.
+  Both $\rho_1 \cdot \rho$ and $\rho_2' \cdot \rho_1'' \cdot \rho$
+  are from $m$ to $z$ going through $y$, but with weights of opposite sign (as $\rho'_1$ and $\rho'_2$ have opposite sign).
+  Now, by $(H1)$, there exists a path $\rho_3$ disjoint from $\rho_1 \cdot \rho$ and$\rho_2' \cdot \rho_1'' \cdot \rho$ from $m$ to $z$.
+It means that we have a pair of compensating paths from $m$ tp $z$, and thus $y \in X$, a contradiction with $y \in Y_+$.
+\qed
+\end{proof}
+
+It means that if a path $\rho_1$ from $m$ to $y$ has stricly positive (resp.
+negative) weight, then all the paths from $m$ to $z$ will also have strictly positive (resp.
+negative) weights.
+It means that Sign is defined on all the $m$ that can reach $Y_+$.
+
+We have the same results for $y \in Y_-$, for paths $\rho_1, \rho_2$ of same sign:
+
+\begin{lemma}
+	\label{lemma11}
+	Let $y \in Y_-$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
+	of paths with weights of same sign with $\rho_1$ from $m$ to $y$ and 
+	with $\rho_2$ from $m$ to $z$ (even non disjoint).
+\end{lemma}
+
+Hence, we obtain as corollary:
+
+\begin{corollary}
+\label{cor:simple}
+Assume that $m < n$ with $n \in Y= Y_+ \sqcup Y_-$.
+Then $m \in Z$.
+\end{corollary}
+
+From there, we conclude that $Y$ is actually prefix-closed:
+
+\begin{lemma}
+	\label{lemma12}
+	Assume that $m < n$ with $n \in Y$.
+	Then $m \in Y$.
+\end{lemma}
+
+\begin{proof}
+Assume by contradiction that $m \notin Y$ with $m<n \in Y$.
+That is, $m \in X$, and there exists a node $m'$ with a pair of compensating paths to $z$
+passing by $m$. But now, that means that $m'<m<n<z$.
+Thus $m'$ is in $Z$, a contradiction with $m'$ the source of a pair of compensating paths.
+\qed
+\end{proof}
+
+As in the proof of Theorem \ref{thm:2}, we can then optimize $Y$ first on its own (considering the sign of every node), and consider its (direct and indirect) contribution to $z$ as biases, before optimizing the rest of the network.
+This is exactly what $\MILP_X$ is doing:
+the bias from each node of $Y$ comes from the bounds on nodes (of $Y$) computed inductively in the previous layers, and then there is a global optimization of the rest of the network (set of nodes $X$ whose ReLU are encoded exactly in $\MILP_X$).
+
+This concludes the proof of Theorem \ref{th2}
+
+\iffalse
+
+\begin{lemma}
+	There does not exist a node $m$ with $m<n^+ \in Y^+$ and $m<n^- \in Y^-$.
+	\end{lemma}
+
+	\begin{proof}
+	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
+	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same sign, 
+	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite sign than $\rho_1$.
+Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite sign.
+	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
+	We then apply Lemma \label{lemma11}, inductively then applying Lemma \label{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. \qed
+	\end{proof}
+
+	With the same arguments, we obtain:
+
+	\begin{lemma}
+	If we have $m<n \in X_*$ and $m < n^+ \in Y_+$ (or $m < n^- \in Y_-$),
+	then $n < n^+$ (or $n < n^-$), with compensating pairs of path from $m$ to $n$.
+	\end{lemma}
+
+	Last, consider the case $m<n^+ \in Y_+$ and $m < n^- \in X_-$.
 
@@
 			(not opened in $\MILP_X$).
-			In the second case, as we assumed without loss of generality that $z$ was the unique output node, it means that $z'$ is in a layer strictly before $z'$.
-			Consider all the possible associated $z'$.
-
-			In the last case, $a$ is in a compensating path (the difference is that this path is not from the input to output), and will be opened. So we focus on the first and second case.
-
-			For the second case, if we replace $P'$ with $P''=P'_0,\cdots,P'_{i-1},P_{i},P'_{i+1},\cdots$, then $P,P''$ is a weak compensating pair that $a$ is a common nodes.
-So we only need to consider case 1.
+			In the second case, as 
+			, it means that $z'$ is in a layer strictly before $z'$.
+			Consider all the possible associated target nodes $z'$ of compensating path from $n$.
 
@@
 This is what we want to show.
+			\fi

### 2024-01-27 Paper/introduction.tex
section 1 and 2

@@
 
-{\color{red}
 As a starting point, we sought to understand properties of DNNs that make them hard to verify.
-Our key finding is a new notion of {\em compensations}, that leads to inaccuracies of bounds and thus explain the {\em hardness} of verifying some DNNs.} Formally, a compensating pair is a tuple of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
+Our key finding is a new notion of {\em compensations}, that leads to inaccuracies of bounds and thus explain the {\em hardness} of verifying some DNNs.
+Formally, a compensating pair is a tuple of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
 Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
@@
 
-\item Our third primary contribution addresses a practical concern by introducing Algorithm \ref{algo1}, a pragmatic solution that builds on our theoretical insights.
+\item Our third primary contribution addresses a practical concern by 
+introducing \CMP (Algorithm \ref{algo1}), a pragmatic solution that builds on our theoretical insights.
 This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones.
-Our extensive empirical evaluation reveals that Algorithm \ref{algo1} achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
-It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$ (refer to Table \ref{tab:example}).
-Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN configuration (as detailed in Table \ref{tab:example3}).
+Our extensive empirical evaluation (refer to Table \ref{tab:example}) reveals \CMP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
+It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$.
+Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN.
 
@@
 \end{enumerate}
+
+For all these reasons, the notion of compensation is very promising, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).
 
@@
 
-Compared with the linear relaxation of the MILP encoding \cite{MILP}, our algorithm is strictly more accurate by design, but it will also be slower.
+Compared with the linear relaxation of the MILP encoding \cite{MILP}, \CMP is strictly more accurate by design, but it will also be slower.
 
@@
 It is thus more accurate than DeepPoly, but also not as efficient.
-Therefore, our algorithm will also be (much) more accurate than DeepPoly, but also not as efficient.
+Therefore, \CMP will also be (much) more accurate than DeepPoly, but also not as efficient.
 
@@
 We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurons.
-Our method is more accurate locally, but we will tend to lose precision for dependencies created several layers ago.
-Most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago).
-Also, the dependencies between nodes limit the parallelism, unlike in our method, which explains why we obtain both faster and more accurate results than PRIMA.
+Our method is more accurate for local dependencies, but will tend to lose precision for dependencies created several layers ago.
+Most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago), which explains why we obtain more accurate results than PRIMA.
 
 $\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
-On simple networks, such as those trained robust, branch and bound is  particularly efficient as it consider the important branches for the actual property to verify, while our algorithm is less efficient as it has to consider each node one by one from the start, including nodes whose bounds are not important.
-However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider: Branch and Bound verifies only $3.5\%$ more images ($44.5\%$ from $41\%$) by enlarging the runtime by 66x (from 30s to 2000s), see Table \ref{tab:example3}.
+On simple networks, such as those trained robust, branch and bound is  particularly efficient as it consider the important branches for the actual property to verify, while \CMP is less efficient as it has to consider each node one by one from the start, including nodes whose bounds are not important.
+However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider: for instance, Branch and Bound verifies only $3.5\%$ more images ($44.5\%$ from $41\%$) by enlarging the runtime by $50$ times on the larger $6 \times 5000$ DNN, and cannot close the gap with \CMP (65\% of images verified, Table \ref{tab:example}).
 
-On such complex DNNs, PRIMA and $\alpha,\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
-In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
-As it is more efficient, this can be pushed to all layers.
+On such complex DNNs, $\alpha,\beta$ CROWN (and PRIMA) resorts to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
+In \CMP, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
+As it is more efficient, we compute bounds for neurons in all the layers.
 This would be infeasible without the selection based on the compensation.
@@
 Finally, algorithms abstracting the network (e.g.
-Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, \CMP $\ldots$ These algorithms have been developed to be complete, so they are much slower but also more accurate than what we propose.
+Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, \CMP $\ldots$ These algorithms have been developed to be {\em complete}, so they are slower but also more accurate than what we propose.

### 2024-01-27 Paper/Paper_noProof.tex
edits
fixed merges
added new files

@@
 \usepackage{subcaption}
+\usepackage{tabularx}
 \captionsetup{compatibility=false}
@@
 	\subsection{The Box and DeepPoly Abstractions}
-
-	%\begin{figure}[t!]
-	%	\centering
-	%		\includegraphics[scale=0.4]{example.png}
-	%	\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
-	%	\label{fig1}
-	%	\end{figure}
 
@@
 
-\section{Compensating pairs of paths}
-\label{Sec.comp}
-
-In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but 
-not efficient). 
-Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision. A pair $(\pi,\pi')$ of paths is {\em compensating} if:
-\begin{itemize}
-	\item they have the same starting node $a$ (called {\em source} state) and ending node $b$ (called {\em target} state of $(\pi,\pi')$),
-	\item they are disjoints (the only common nodes are the source and the target),
-	\item the weights satisfy $weight(\pi') < 0 < weight(\pi)$.
-\end{itemize}
-
-For instance, on Fig.~\ref{fig1}, the paths $\pi= n_2 n_3 n_5$ has weight $1$, while the
-path $\pi'= n_2 n_4 n_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
-We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or $(\pi',\pi)$ is compensating.
-
-Compensating pair of paths will make precision of the target state reduce when using overabstraction of values. Here, $x_5 \leq 4$, which is reached for $x_1=1$ and $x_2=-1$: 
-$\val_{(1,-1)}(n_5)=4$.
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+3}{2} \leq 2$ instead of exact $-x_2 \leq 1$), obtaining $x_5 \leq 5$ instead of the precise $x_5 \leq 4$.
-
-Intuitively, the target state receives the weight from the source state from the different paths from the source to the target.
-As the weights of the paths is of opposite sign, some of these weights will cancel out, by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$.
-Further, that also avoid accumulating the error, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inaccurate analysis.
-The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function.
-For instance, consider that the inputs $x_1,x_2$ lies in $[-1,-0]$.
-Then $\hat{x}_3$ will always be 0 for any input $\vx=(x_1,x_2) \in [-1,-0] \times [-1,-0]$, and $weight(\pi')$ will not compensate $weight(\pi')$.
-
-\iffalse
-\vspace*{2ex}
-
-\begin{figure}
-	\centering
-	\begin{tikzpicture}
-
-		\node[circle, draw= purple, thick, minimum width = 20,
-		minimum height = 20] (input1) {$a$};
-
-		% Hidden layers
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (hidden1) at ($(input1) + (2,1)$) {$b$};
-		\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-1)$) {$b'$};
-
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (hidden3) at ($(input1) + (4,1)$){$c$};
-		\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-1)$) {$c'$};
-
-		% Output layer
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (output) at ($(input1) + (6,0)$){$d$};
-
-		% Connections
-		\draw[->,thick,draw= red] (input1) -- (hidden1) node[midway, below] {$1$};
-		\draw[->,thick,draw= green] (input1) -- (hidden2)node[midway, below] {$-1$};
-
-		\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
-		\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};
-
-		\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
-		\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
-	\end{tikzpicture}
-\end{figure}
-
-\vspace*{2ex}
-
-In this figure, $a$ is the input neuron; $bc,b'c'$ are nodes in the hidden layer, ($b,b'$ are pre-activation and $c,c'$ are post activation); and $d$ is the unique output neuron.
-The numbers next to the arrows are the weights.
-So, $W_{ba}=1$ and $W_{b'a}=-1$, $W_{dc}=W_{dc'}=1$.
-The pair of these two paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is a so called \emph{Compensating Pair}.
-Because its shape looks like a diamond, it is also called a Diamond.
-The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.
-
-The existence of compensating pairs is key reason why simple approximation like LP or Interval Arithmetic cannot get the exact upper and lower bounds.
-If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.
-
-To explain why, suppose we have another input node $a'$, such that both $a$ and $a'$ has an input interval $[0,1]$, but the weight from $a'$ to $b$ or $b'$ are both $1$.
-Then both $b$ will have an interval $[0,2]$ and $b'$ will have an interval $[-1,1]$.
-More importantly, in LP formulation, $c$ will be $b$ but $c'$ will be $0.5(b')+0.5$.
-The upper bound of $d$ will be $c+c'$, and hence $b+0.5(b')+0.5$, and hence $a+a'+0.5a'-0.5a'+0.5=0.5a+1.5a'+0.5$.
-And this will leads to a upper bound $2.5$ but this is not exact.
-
-\vspace*{2ex}
-\begin{tikzpicture}
-	\node[circle, draw= purple, thick, minimum width = 20,
-	minimum height = 20] (input1) {$a$};
-
-	\node[circle, draw= purple, thick, minimum width = 20,
-	minimum height = 20] (input2) at ($(input1) + (0,-2)$) {$a'$};
-
-	% Hidden layers
-	\node[circle, draw= blue, thick, minimum width = 20,
-	minimum height = 20] (hidden1) at ($(input1) + (2,0)$) {$b$};
-	\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-2)$) {$b'$};
-
-	\node[circle, draw= blue, thick, minimum width = 20,
-	minimum height = 20] (hidden3) at ($(input1) + (4,0)$){$c$};
-	\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-2)$) {$c'$};
-
-	% Output layer
-	\node[circle, draw= blue, thick, minimum width = 20,
-	minimum height = 20] (output) at ($(input1) + (6,-1)$){$d$};
-
-	% Connections
-	\draw[->,thick,draw= red] (input1) -- (hidden1);
-	\draw[->,thick,draw= green] (input1) -- (hidden2);
-
-	\draw[->,thick,draw= red] (input2) -- (hidden1) node[midway, below] {$1$};
-	\draw[->,thick,draw= red] (input2) -- (hidden2)node[midway, below] {$1$};
-
-	\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
-	\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};
-
-	\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
-	\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
-\end{tikzpicture}
-\vspace*{2ex}
-
-The general formal definition of compensating pair is as follows:
-
-\begin{definition} In a full-connected network with $\ReLU$ as activation function:
-
-	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes that goes consecutively through each layer. We call the first node source node and the last node target node.
-
-	2.
-The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ab}\cdot W_{bc}\cdot W_{cd}\cdot W_{ed}\cdot \cdots$$
-
-	3.
-A \emph{Compensating Pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).
-
-	We also use \emph{Diamond} to call a compensating pair in the network.
-\end{definition}
-
-The following theorem shows the role of compensating pairs in the computation:
-
-\fi
-
-Hence, compensation is {\em one} factor of inaccuracy. We prove now that it is actually the {\em only} reason for inaccuracy, in the following meaning.
-If there is no compensating path in the DNN, then any method/approximation at least as accurate as the Box abstraction, e.g.
-$\overline{\text{DeepPoly}}$ or LP, computes the exact upper and lower bounds for every node, that is:
-
-\begin{table}[b!]
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\text{Source/Target Layers}  &  \text{Natural DNN} & \text{Robust DNN} & \text{Ratio Natural vs Robust} \\ \hline \hline
-		0 / 2 & 0.0304 & 0.00220  & 13.8x\\ \hline
-		1 / 3  & 0.0313 & 0.00875 & 3.58x \\ \hline
-		2 / 4  &  0.0267 & 0.00785 & 3.40x \\ \hline
-		3 / 5  &  0.0253 & 0.00804  & 3.18x \\ \hline
-	\end{tabular}
-	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.}
-	\label{tab:compensation}
-\end{table}
-
-\begin{theorem}
-	\label{th1}
-	Let $n$ be any node of a DNN with {\em no} compensating path.
-For $[\alpha,\beta]$ the bounds computed by the {\em Box abstraction} for $n$, we have that for all $\gamma \in [\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n)=\gamma$.
-\end{theorem}
-
-The sketch of proof can be found in Section \ref{sec.proofs}. 
-Notice that standard DeepPoly does not satisfies Theorem \ref{th1} (it does not necessarily refine Box), and therefore we are not sure PRIMA or $\beta$-CROWN that refine DeepPoly satisfies Theorem \ref{th1}, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
-Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results show in that compensation is the reason for inaccuracy.
-
-This result has a first interesting application: explain why some DNNs are intrinsically easier to verify than others.
-This is the case for DNNs trained adversarially to be robust, vs same architecture, but trained in a "natural" way \cite{deeppoly,prima,crown}.
-Indeed, compensating pairs is a purely structural property on the DNN learnt, rather than more semantical notions, such as the number of unstable ReLUs, which depends heavily upon the image considered and the algorithm used.
-We compare compensations with source and target separated by 1 ReLU layer, e.g.
-source in layer 0 and target in layer 2, for two Networks with 5 hidden layers of 100 nodes each from the ERAN GitHub repository, one trained naturally ("$6\times100$"),
-and one trained using DiffAI \cite{DiffAI} ("$5\times100$"). 
-We report in Table \ref{tab:compensation} the average compensation strength, i.e. 
-the average of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$
-over all source/target states in given layers.
-The average compensations strength are much lower in the Robust DNN than in the natural DNN, and indeed the Robust DNN is much simpler to verify than the natural DNN (e.g.
-DeepPoly is more accurate and verifies more images).
-
-\subsection{MILP$_{X_n}$}
-
-While Theorem \ref{th1} is interesting to understand that compensation is a key notion for accurate verification of DNNs, it cannot be used directly to analyze DNNs with compensations, which are actually those that are most interesting to tackle.
-Intuitively, when there are compensating paths, it seems necessary to consider exactly the (unstable) ReLU nodes that are seen along these paths. 
-Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds 
-$[\alpha,\beta]$.
-Let $X_n$ be the set of neurons $x$ in layer up to $k-1$ such that there is a compensating path with target $n$ passing by $x$ (but not as its source or target).
-Let $Y_n$ be the complement of this set $X_n$ of neurons in the first $k-1$ layers.
-We denote by MILP$_{X_n}$ the relaxation of the MILP encoding where all the nodes in $Y_n$ are linearly relaxed (thus with $|X_n|$ binary variable, one per neuron in $X_n$), and including exact bounds for every neurons $n'$ in the first $k-1$ layers.
-We state now that the bounds $[\alpha,\beta]$ on neuron $n$ computed by such MILP$_{X_n}$ are accurate.
-
-\begin{theorem}
-	\label{th2} 
-	Let $n$ be any node of a DNN.
-Then for $[\alpha,\beta]$ the bounds computed by MILP$_{X_n}$ for neuron $n$, for all $\gamma \in [\alpha,\beta]$, there exists an input $\vy$ such that $\val_{\vy}(n)=\gamma$.
-\end{theorem}
-
-The sketch of proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs}.
-
-\subsection{Sketch of Proofs}
-\label{sec.proofs}
-
-%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
-Consider a target neuron $z$.
-In case there is no compensating path, we can assign a sign to each neuron $n$: 0
-if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
-$-1$ if they have negative weights. Then we prove:
-
-\begin{proposition}
-	\label{prop.sign}
-	There exist two inputs $\vx^\star,\vx^\sharp$ such that ${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  ${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
-\end{proposition}
-
-Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.
-
-\smallskip
-
-Concerning Theorem \ref{th2}, consider an output node $z$.
-Let $[\alpha(z),\beta(z)]$ be the bound computed by $\MILP_{X_z}$.
-%We will show the existence of $\vx^\sharp,\vx^\star$
-%such that $\val_{\vx^\sharp}(z)=\alpha$ and $\val_{\vx^\star}(z)=\beta$,
-%and we will get the proof of Theorem 2 by a continuity argument.
-%For that, 
-We partition the input neurons from layer $0$ into:
-\begin{enumerate}
-	\item $A_{zero}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)=0\}$.
-	\item $A_{pos}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\geq0\}$.
-	\item  $A_{neg}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\leq0\}$.
-	Let $A_{pure}=A_{pos} \cup A_{neg}$.
-	\item $A_{open}$ is the set of remaining input neurons.
-\end{enumerate}
-
-We then partition the set of neurons in hidden layers: 
-\begin{enumerate}
-	\item $B_{zero}= \{n \mid \forall \text{ path $\rho$ from $n$ to } z, weight(\rho)=0\}$.
-	\item $B_{open}$ is the set of neurones reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
-	\item $B_{pure}$ is the set of remaining neurons.
-\end{enumerate}
-
-We can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
-Further, the value of any neuron $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
-nodes in $A_{pure}$ or $B_{pure}$. Therefore, applying Prop. \ref{prop.sign} on the DNN
-made of nodes from $A_{pure}$ and $B_{pure}$, we obtain 
-$\vx_{pure}^\star,\vx_{pure}^\sharp$ optimizing neurons in $A_{pure}$ or $B_{pure}$.
-We can prove that there exists input 
-$\vx^\star$ extending $\vx_{pure}^\star$
-and input $\vx_{pure}^\sharp$ extending $\vx_{pure}^\sharp$
-from $A_{pure}$ to $A_{pure} \cup A_{open}$ such that 
-$\val_{\vx^\star}(z)=\beta(z)$ and $\val_{\vx^\sharp}(z)=\alpha(z)$.
-
-The formal proofs are in appendix.
-
-\subsection{An efficient algorithm}
-
-Using Theorem \ref{th2}, one could thus obtain accurate bounds by running MILP$_{X}$ inductively on every node layer by layer, obtaining accurate bounds $[\alpha,\beta]$ that can be used to compute the next layer accurate bound.
-In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this threshold are not compensating strongly enough to deserve an integer variable, calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
-In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small.
-The pseudo-code of the algorithm is provided in Algorithm \ref{algo1}.
-
-\SetKwInput{KwInput}{Input}
-\SetKwInput{KwOutput}{Output}
-
-\begin{algorithm}[b!]
-	\caption{Compensate(K)}
-	\label{algo1}
-	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}
-
-	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}
-
-	\For{layer $k=1 \cdots \ell$}{
-		\For{neuron $n$ in layer $k$}{
-
-			Compute $Z$ a set of $K$ nodes covering the compensating pairs of paths with target $n$
-			with heaviest compensation
-
-			Run MILP$_Z$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
-		}
-	}
-\end{algorithm}
-
-This algorithm has a worst case complexity bounded by $O(N \MILP(N,K))$, 
-where $N$ is the number of nodes of the DNN, 
-and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
-We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables.
-This complexity is an upper bound, as e.g. Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
-Notice that the for loop on neurons $n$ in layer $k$ at line 2 can be realized in parallel as we only need bounds from previous layers, not from the current layer $k$, 
-leading to a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, with $\ell$ the number of layers and $N_i$ the number of neurons in layers $0, \ldots, i$.
-Hence, for $K$ small enough, Algorithm \ref{algo1} calls many times MILP (e.g. Gurobi)
-with a limited number of integer variables, which should be efficient enough, and yet be quite accurate as it can compute exactly (Theorem \ref{th2}) the highest compensating path, which we verify in the next section.
-
-\iffalse
-\section{Verification Framework}
-
-%Our experiments are carried by different version codes, and the global process has been changed.
-
-In this section, we will sketch the framework.
-
-\subsection{Structure}
-
-\subsubsection*{Precomputation}
-
-The open node chosen is the key part of the whole framework but costs a lot of time. So some computation (those do not rely on certain image and bounds) is moved to the precomputation part.
-
-%The precomputation corresponds to the simplest case: source node fixed.
-We will compute and store a limited number of paths with highest (absolute) values before running any image.
-This does not rely on other parameters or results(bounds).
-%
-%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
-This will use much less time.
-
-\subsubsection*{Process for one image} An image is the basic unit in whole process.
-The process of one image is simple: compute the concrete bounds of nodes layer by layer, use the bounds of previous layer to build MILP models of current layer.
-In one layer, nodes runs in parallel.
-
-%Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers.
-Then we will compute bounds of every node in $l_i$ in parallel using the data of bounds of previous nodes.
-The method is to build and optimize an MILP model.
-
-%Some parameters may be changed during layers.
-Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters.
-Here, \emph{local} is opposite to \emph{global}.
-We have global timeout parameters for images and the whole running.
-Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.
-
-%The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node. 
-%
-%The precomputation corresponds to the simplest case: source node fixed.
-We will compute and store a limited number of paths with highest (absolute) values before running any image.
-This does not rely on other parameters or results(bounds).
-%
-%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes.
-This will use much less time.
-
-\begin{algorithm}
-	\caption{The Frame work}
-	\KwData{Input Domain: $\mathcal{D}$}
-	\KwResult{Bounds of all nodes: $\mathcal{B}$}
-
-	Constant $\mathcal{R}$  \tcp*{Stored precomputation data}
-
-	Constant $\boldsymbol{W}, \vb$ \tcp*{Weights and Bias of network}
-
-	Constant Layers = $[0,1,2\cdots,L]$ \tcp*{lists of all layer}
-
-	Constant NodesLayer = $[Nodes_0,Nodes_1,\cdots, Nodes_L]$ \tcp*{list of nodes in each layer}
-
-	Initialize $\mathcal{B}$ = \{\} \tcp*{To store upper and lower bounds of all nodes}
-
-	\For{$l$ in Layers}{
-		\If{$l$ = 0}{
-
-			$\mathcal{D}$, $\boldsymbol{W}, \vb$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
-			\tcp*{Do linear transformation  from input to the first layer}
-
-			Add \{$x$: $(UB(x),LB(x))$,$\cdots$\} to $\mathcal{B}$}
-
-		\Else{
-
-			$l$, NodesLayer $\rightarrow$ $Nodes_l$ = $[x_0,x_1,\cdots]$
-
-			\For{$x$ in $Nodes_l$}{
-				$x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}
-
-				$\mathcal{B}$, $\boldsymbol{W}, \vb$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}
-
-				\While{}{$\mathcal{M}$ $\rightarrow UB(x),LB(x)$ \tcp*{Optimization}}
-
-				Add \{$x$: $(UB(x),LB(x))$\} to $\mathcal{B}$
-
-			}
-
-		}
-
-	}
-
-	\Return{$\mathcal{B}$}
-
-\end{algorithm}
-
-\subsubsection*{Process for one node}
-
-The optimization of a model consists of loops.
-For each loop, the model will do optimization by a timeout and observe the result.
-If it gets improvement, then continue the loop until the optimize bounds or the longer timeout.
-Otherwise it will give up optimization and store the best bounds obtained so far.
-
-\subsubsection*{Global Process}
-
-In the newest version, we do images by batches for 100 images each. For each batch, the running consists of three turns, very fast turn, fast turn and slow turn.
-
-In the very fast turn, it will run DeepPoly for all images to get a preliminary bounds for all nodes and verify the easiest images.
-Images verified and images with false predication will be deleted from the image list.
-
-Then sort all remain images by the size of uncertainty of DeepPoly from smaller to larger.
-The fast turn is to run the images from the smaller side to larger side until consecutive two images cannot be verified.
-All remain images and images tried but not verified will be put into the next list.
-And then run the list with parameters for slow turn.
-
-\subsection{Parameters}
-
-Parameters like open node parameter $O$ is important in the frame. Basically, all parameters will be reset after one image.
-
-\subsubsection*{Global parameters}
-
-\subsubsection*{Local parameters}
-
-$O$ and timeout parameters for loops will change frequently during the loops of one node. These change will not reset until the end of one layer or one image.
-
-\subsection{Other Setting}
-
-In our experiments, we have not used PGD-attack to exclude some images. In principle, there is no obstacle to use PGD-attack.
-\fi
+\input{comppaths}
 

### 2024-01-27 Paper/comppaths.tex
added new files

\section{Compensating pairs of paths}
\label{Sec.comp}

In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but 
not efficient). 
Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision. A pair $(\pi,\pi')$ of paths is {\em compensating} if:
\begin{itemize}
	\item they have the same starting node $a$ (called {\em source} state) and ending node $b$ (called {\em target} state of $(\pi,\pi')$),
	\item they are disjoints (the only common nodes are the source and the target),
	\item the weights satisfy $weight(\pi') < 0 < weight(\pi)$.
\end{itemize}

For instance, on Fig.~\ref{fig1}, the paths $\pi= n_2 n_3 n_5$ has weight $1$, while the
path $\pi'= n_2 n_4 n_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or $(\pi',\pi)$ is compensating.

Compensating pair of paths will make precision of the target state reduce when using overabstraction of values. Here, $x_5 \leq 4$, which is reached for $x_1=1$ and $x_2=-1$: 
$\val_{(1,-1)}(n_5)=4$. However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+3}{2} \leq 2$ instead of exact $-x_2 \leq 1$), obtaining $x_5 \leq 5$ instead of the precise $x_5 \leq 4$.

Intuitively, the target state receives the weight from the source state from the different paths from the source to the target. As the weights of the paths is of opposite sign, some of these weights will cancel out, by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$. 
Further, that also avoid accumulating the error, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inaccurate analysis. The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function. For instance, consider that the inputs $x_1,x_2$ lies in $[-1,-0]$. Then $\hat{x}_3$ will always be 0 for any input $\vx=(x_1,x_2) \in [-1,-0] \times [-1,-0]$, and $weight(\pi')$ will not compensate $weight(\pi')$.

\iffalse
\vspace*{2ex}

\begin{figure}
	\centering
	\begin{tikzpicture}

		\node[circle, draw= purple, thick, minimum width = 20,
		minimum height = 20] (input1) {$a$};

		% Hidden layers
		\node[circle, draw= blue, thick, minimum width = 20,
		minimum height = 20] (hidden1) at ($(input1) + (2,1)$) {$b$};
		\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-1)$) {$b'$};

		\node[circle, draw= blue, thick, minimum width = 20,
		minimum height = 20] (hidden3) at ($(input1) + (4,1)$){$c$};
		\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-1)$) {$c'$};

		% Output layer
		\node[circle, draw= blue, thick, minimum width = 20,
		minimum height = 20] (output) at ($(input1) + (6,0)$){$d$};

		% Connections
		\draw[->,thick,draw= red] (input1) -- (hidden1) node[midway, below] {$1$};
		\draw[->,thick,draw= green] (input1) -- (hidden2)node[midway, below] {$-1$};

		\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
		\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};

		\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
		\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
	\end{tikzpicture}
\end{figure}

\vspace*{2ex}

In this figure, $a$ is the input neuron; $bc,b'c'$ are nodes in the hidden layer, ($b,b'$ are pre-activation and $c,c'$ are post activation); and $d$ is the unique output neuron. The numbers next to the arrows are the weights. So, $W_{ba}=1$ and $W_{b'a}=-1$, $W_{dc}=W_{dc'}=1$. The pair of these two paths, $a$ to $bc$ to $d$, and $a$ to $b'c'$ to $d$, is a so called \emph{Compensating Pair}. Because its shape looks like a diamond, it is also called a Diamond. The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.

The existence of compensating pairs is key reason why simple approximation like LP or Interval Arithmetic cannot get the exact upper and lower bounds. If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.

To explain why, suppose we have another input node $a'$, such that both $a$ and $a'$ has an input interval $[0,1]$, but the weight from $a'$ to $b$ or $b'$ are both $1$. Then both $b$ will have an interval $[0,2]$ and $b'$ will have an interval $[-1,1]$. More importantly, in LP formulation, $c$ will be $b$ but $c'$ will be $0.5(b')+0.5$. The upper bound of $d$ will be $c+c'$, and hence $b+0.5(b')+0.5$, and hence $a+a'+0.5a'-0.5a'+0.5=0.5a+1.5a'+0.5$. And this will leads to a upper bound $2.5$ but this is not exact.

\vspace*{2ex}
\begin{tikzpicture}
	\node[circle, draw= purple, thick, minimum width = 20,
	minimum height = 20] (input1) {$a$};

	\node[circle, draw= purple, thick, minimum width = 20,
	minimum height = 20] (input2) at ($(input1) + (0,-2)$) {$a'$};

	% Hidden layers
	\node[circle, draw= blue, thick, minimum width = 20,
	minimum height = 20] (hidden1) at ($(input1) + (2,0)$) {$b$};
	\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2,-2)$) {$b'$};

	\node[circle, draw= blue, thick, minimum width = 20,
	minimum height = 20] (hidden3) at ($(input1) + (4,0)$){$c$};
	\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (4,-2)$) {$c'$};

	% Output layer
	\node[circle, draw= blue, thick, minimum width = 20,
	minimum height = 20] (output) at ($(input1) + (6,-1)$){$d$};

	% Connections
	\draw[->,thick,draw= red] (input1) -- (hidden1);
	\draw[->,thick,draw= green] (input1) -- (hidden2);

	\draw[->,thick,draw= red] (input2) -- (hidden1) node[midway, below] {$1$};
	\draw[->,thick,draw= red] (input2) -- (hidden2)node[midway, below] {$1$};

	\draw[->,thick,draw= red] (hidden1) -- (hidden3) node[midway, below] {$\ReLU$};
	\draw[->,thick,draw= green] (hidden2) -- (hidden4) node[midway, below] {$\ReLU$};

	\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
	\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
\end{tikzpicture}
\vspace*{2ex}

The general formal definition of compensating pair is as follows:

\begin{definition} In a full-connected network with $\ReLU$ as activation function:

	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes that goes consecutively through each layer. We call the first node source node and the last node target node.

	2. The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ab}\cdot W_{bc}\cdot W_{cd}\cdot W_{ed}\cdot \cdots$$

	3. A \emph{Compensating Pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).

	We also use \emph{Diamond} to call a compensating pair in the network.
\end{definition}

The following theorem shows the role of compensating pairs in the computation:

\fi

Hence, compensation is {\em one} factor of inaccuracy. We prove now that it is actually the {\em only} reason for inaccuracy, in the following meaning.
If there is no compensating path in the DNN, then any method/approximation at least as accurate as the Box abstraction, e.g. $\overline{\text{DeepPoly}}$ or LP, computes the exact upper and lower bounds for every node, that is:

\begin{table}[b!]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		\text{Source/Target Layers}  &  \text{Natural DNN} & \text{Robust DNN} & \text{Ratio Natural vs Robust} \\ \hline \hline
		0 / 2 & 0.0304 & 0.00220  & 13.8x\\ \hline
		1 / 3  & 0.0313 & 0.00875 & 3.58x \\ \hline
		2 / 4  &  0.0267 & 0.00785 & 3.40x \\ \hline
		3 / 5  &  0.0253 & 0.00804  & 3.18x \\ \hline
	\end{tabular}
	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.}
	\label{tab:compensation}
\end{table}

\begin{theorem}
	\label{th1}
	Let $n$ be any node of a DNN with {\em no} compensating path. For $[\alpha,\beta]$ the bounds computed by the {\em Box abstraction} for $n$, we have that for all $\gamma \in [\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n)=\gamma$.
\end{theorem}

The sketch of proof can be found in Section \ref{sec.proofs}. 
Notice that standard DeepPoly does not satisfies Theorem \ref{th1} (it does not necessarily refine Box), and therefore we are not sure PRIMA or $\beta$-CROWN that refine DeepPoly satisfies Theorem \ref{th1}, though it would be easy to fix by using $\overline{\text{DeepPoly}}$. Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results show in that compensation is the reason for inaccuracy.

This result has a first interesting application: explain why some DNNs are intrinsically easier to verify than others. This is the case for DNNs trained adversarially to be robust, vs same architecture, but trained in a "natural" way \cite{deeppoly,prima,crown}. Indeed, compensating pairs is a purely structural property on the DNN learnt, rather than more semantical notions, such as the number of unstable ReLUs, which depends heavily upon the image considered and the algorithm used. We compare compensations with source and target separated by 1 ReLU layer, e.g. source in layer 0 and target in layer 2, for two Networks with 5 hidden layers of 100 nodes each from the ERAN GitHub repository, one trained naturally ("$6\times100$"), 
and one trained using DiffAI \cite{DiffAI} ("$5\times100$"). 
We report in Table \ref{tab:compensation} the average compensation strength, i.e. 
the average of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$
over all source/target states in given layers. The average compensations strength are much lower in the Robust DNN than in the natural DNN, and indeed the Robust DNN is much simpler to verify than the natural DNN (e.g. DeepPoly is more accurate and verifies more images).

\subsection{MILP$_{X_n}$}

While Theorem \ref{th1} is interesting to understand that compensation is a key notion for accurate verification of DNNs, it cannot be used directly to analyze DNNs with compensations, which are actually those that are most interesting to tackle.
Intuitively, when there are compensating paths, it seems necessary to consider exactly the (unstable) ReLU nodes that are seen along these paths. 
Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds 
$[\alpha,\beta]$.
Let $X_n$ be the set of neurons $x$ in layer up to $k-1$ such that there is a compensating path with target $n$ passing by $x$ (but not as its source or target). Let $Y_n$ be the complement of this set $X_n$ of neurons in the first $k-1$ layers. We denote by MILP$_{X_n}$ the relaxation of the MILP encoding where all the nodes in $Y_n$ are linearly relaxed (thus with $|X_n|$ binary variable, one per neuron in $X_n$), and including exact bounds for every neurons $n'$ in the first $k-1$ layers. We state now that the bounds $[\alpha,\beta]$ on neuron $n$ computed by such MILP$_{X_n}$ are accurate.

\begin{theorem}
	\label{th2} 
	Let $n$ be any node of a DNN. Then for $[\alpha,\beta]$ the bounds computed by MILP$_{X_n}$ for neuron $n$, for all $\gamma \in [\alpha,\beta]$, there exists an input $\vy$ such that $\val_{\vy}(n)=\gamma$.
\end{theorem}

The sketch of proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs}.

\subsection{Sketch of Proofs}
\label{sec.proofs}

%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
Consider a target neuron $z$.
In case there is no compensating path, we can assign a sign to each neuron $n$: 0
if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
$-1$ if they have negative weights. Then we prove:

\begin{proposition}
	\label{prop.sign}
	There exist two inputs $\vx^\star,\vx^\sharp$ such that ${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  ${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
\end{proposition}

Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.

\smallskip

Concerning Theorem \ref{th2}, consider an output node $z$.
Let $[\alpha(z),\beta(z)]$ be the bound computed by $\MILP_{X_z}$.
%We will show the existence of $\vx^\sharp,\vx^\star$
%such that $\val_{\vx^\sharp}(z)=\alpha$ and $\val_{\vx^\star}(z)=\beta$,
%and we will get the proof of Theorem 2 by a continuity argument.
%For that, 
We partition the input neurons from layer $0$ into:
\begin{enumerate}
	\item $A_{zero}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)=0\}$.
	\item $A_{pos}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\geq0\}$.
	\item  $A_{neg}= \{a \mid \forall \text{ path $\rho$ from $a$ to } z, weight(\rho)\leq0\}$.
	Let $A_{pure}=A_{pos} \cup A_{neg}$.
	\item $A_{open}$ is the set of remaining input neurons.
\end{enumerate}

We then partition the set of neurons in hidden layers: 
\begin{enumerate}
	\item $B_{zero}= \{n \mid \forall \text{ path $\rho$ from $n$ to } z, weight(\rho)=0\}$.
	\item $B_{open}$ is the set of neurones reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
	\item $B_{pure}$ is the set of remaining neurons.
\end{enumerate}

We can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
Further, the value of any neuron $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
nodes in $A_{pure}$ or $B_{pure}$. Therefore, applying Prop. \ref{prop.sign} on the DNN
made of nodes from $A_{pure}$ and $B_{pure}$, we obtain 
$\vx_{pure}^\star,\vx_{pure}^\sharp$ optimizing neurons in $A_{pure}$ or $B_{pure}$.
We can prove that there exists input 
$\vx^\star$ extending $\vx_{pure}^\star$
and input $\vx_{pure}^\sharp$ extending $\vx_{pure}^\sharp$
from $A_{pure}$ to $A_{pure} \cup A_{open}$ such that 
$\val_{\vx^\star}(z)=\beta(z)$ and $\val_{\vx^\sharp}(z)=\alpha(z)$.

The formal proofs are in appendix.

\subsection{An efficient algorithm}

Using Theorem \ref{th2}, one could thus obtain accurate bounds by running MILP$_{X}$ inductively on every node layer by layer, obtaining accurate bounds $[\alpha,\beta]$ that can be used to compute the next layer accurate bound. In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$. Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this threshold are not compensating strongly enough to deserve an integer variable, calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths. In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small. The pseudo-code of the algorithm is provided in Algorithm \ref{algo1}.

\SetKwInput{KwInput}{Input}
\SetKwInput{KwOutput}{Output}

\begin{algorithm}[htb]
	\caption{Compensate(K)}
	\label{algo1}
	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}

	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}

	\For{layer $k=1 \cdots \ell$}{
		\For{neuron $n$ in layer $k$}{

			Compute $Z$ a set of $K$ nodes covering the compensating pairs of paths with target $n$
			with heaviest compensation

			Run MILP$_Z$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
		}
	}
\end{algorithm}

This algorithm has a worst case complexity bounded by $O(N \MILP(N,K))$, 
where $N$ is the number of nodes of the DNN, 
and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables.
This complexity is an upper bound, as e.g. Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
Notice that the for loop on neurons $n$ in layer $k$ at line 2 can be realized in parallel as we only need bounds from previous layers, not from the current layer $k$, 
leading to a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, with $\ell$ the number of layers and $N_i$ the number of neurons in layers $0, \ldots, i$.
Hence, for $K$ small enough, Algorithm \ref{algo1} calls many times MILP (e.g. Gurobi)
with a limited number of integer variables, which should be efficient enough, and yet be quite accurate as it can compute exactly (Theorem \ref{th2}) the highest compensating path, which we verify in the next section.

\iffalse
\section{Verification Framework}

%Our experiments are carried by different version codes, and the global process has been changed.

In this section, we will sketch the framework.

\subsection{Structure}

\subsubsection*{Precomputation}

The open node chosen is the key part of the whole framework but costs a lot of time. So some computation (those do not rely on certain image and bounds) is moved to the precomputation part.

%The precomputation corresponds to the simplest case: source node fixed. We will compute and store a limited number of paths with highest (absolute) values before running any image. This does not rely on other parameters or results(bounds).
%
%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes. This will use much less time.

\subsubsection*{Process for one image} An image is the basic unit in whole process. The process of one image is simple: compute the concrete bounds of nodes layer by layer, use the bounds of previous layer to build MILP models of current layer. In one layer, nodes runs in parallel.

%Suppose we have reached a new layer $l_i$ and have upper and lower bounds of all nodes in previous layers. Then we will compute bounds of every node in $l_i$ in parallel using the data of bounds of previous nodes. The method is to build and optimize an MILP model.

%Some parameters may be changed during layers. Among all parameters, two groups are the most important: numbers of open nodes and local timeout parameters. Here, \emph{local} is opposite to \emph{global}. We have global timeout parameters for images and the whole running. Local timeout are used in one layer, one node, one model, or one loop in the optimization for a model.

%The open node chosen is the key part of the whole framework, and it will cost two much time without precomputation because we must do open node chosen for every node. 
%
%The precomputation corresponds to the simplest case: source node fixed. We will compute and store a limited number of paths with highest (absolute) values before running any image. This does not rely on other parameters or results(bounds).
%
%Before build an MILP model and when choosing open nodes list,  the program will read the reference data combining with the data of bounds to continue the computation of open nodes. This will use much less time.

\begin{algorithm}
	\caption{The Frame work}
	\KwData{Input Domain: $\mathcal{D}$}
	\KwResult{Bounds of all nodes: $\mathcal{B}$}

	Constant $\mathcal{R}$  \tcp*{Stored precomputation data}

	Constant $\boldsymbol{W}, \vb$ \tcp*{Weights and Bias of network}

	Constant Layers = $[0,1,2\cdots,L]$ \tcp*{lists of all layer}

	Constant NodesLayer = $[Nodes_0,Nodes_1,\cdots, Nodes_L]$ \tcp*{list of nodes in each layer}

	Initialize $\mathcal{B}$ = \{\} \tcp*{To store upper and lower bounds of all nodes}

	\For{$l$ in Layers}{
		\If{$l$ = 0}{

			$\mathcal{D}$, $\boldsymbol{W}, \vb$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\} 
			\tcp*{Do linear transformation  from input to the first layer}

			Add \{$x$: $(UB(x),LB(x))$,$\cdots$\} to $\mathcal{B}$}

		\Else{

			$l$, NodesLayer $\rightarrow$ $Nodes_l$ = $[x_0,x_1,\cdots]$

			\For{$x$ in $Nodes_l$}{
				$x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}

				$\mathcal{B}$, $\boldsymbol{W}, \vb$, $\mathcal{O}$ $\rightarrow \mathcal{M}$  \tcp*{MILP model $\mathcal{M}$ for node $x$}

				\While{}{$\mathcal{M}$ $\rightarrow UB(x),LB(x)$ \tcp*{Optimization}}

				Add \{$x$: $(UB(x),LB(x))$\} to $\mathcal{B}$

			}

		}

	}

	\Return{$\mathcal{B}$}

\end{algorithm}

\subsubsection*{Process for one node}

The optimization of a model consists of loops. For each loop, the model will do optimization by a timeout and observe the result. If it gets improvement, then continue the loop until the optimize bounds or the longer timeout. Otherwise it will give up optimization and store the best bounds obtained so far.

\subsubsection*{Global Process}

In the newest version, we do images by batches for 100 images each. For each batch, the running consists of three turns, very fast turn, fast turn and slow turn.

In the very fast turn, it will run DeepPoly for all images to get a preliminary bounds for all nodes and verify the easiest images. Images verified and images with false predication will be deleted from the image list.

Then sort all remain images by the size of uncertainty of DeepPoly from smaller to larger. The fast turn is to run the images from the smaller side to larger side until consecutive two images cannot be verified. All remain images and images tried but not verified will be put into the next list. And then run the list with parameters for slow turn.

\subsection{Parameters}

Parameters like open node parameter $O$ is important in the frame. Basically, all parameters will be reset after one image.

\subsubsection*{Global parameters}

\subsubsection*{Local parameters}

$O$ and timeout parameters for loops will change frequently during the loops of one node. These change will not reset until the end of one layer or one image.

\subsection{Other Setting}

In our experiments, we have not used PGD-attack to exclude some images. In principle, there is no obstacle to use PGD-attack.
\fi

### 2024-01-27 Paper/valabstraction.tex
added new files

--- 2024-01-27 Paper/Paper_noProof.tex
@@
-\documentclass{llncs}
-\pagestyle{plain}
-
-%\usepackage[latin9]{inputenc}
-%\usepackage[T1]{fontenc}
-\usepackage{float}
-\usepackage{wrapfig}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{tabularx}
-\captionsetup{compatibility=false}
-% \usepackage{esint}
-\usepackage{array}
-\usepackage{epstopdf}
-\usepackage{placeins}
-\usepackage{pgfplots}
-\usepackage{url}
-\usepackage{tikz}
-\usepackage{calc}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usetikzlibrary{positioning, arrows.meta,calc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand{\vx}{\boldsymbol{x}}
-\newcommand{\vy}{\boldsymbol{y}}
-\newcommand{\vW}{\boldsymbol{W}}
-\newcommand{\vz}{\boldsymbol{z}}
-\newcommand{\vb}{\boldsymbol{bias}}
-\newcommand{\val}{{\textrm{value}}}
-\newcommand{\Val}{{\textrm{value}}}
-\newcommand{\MILP}{{\textrm{MILP}}}
-\newcommand{\LP}{{\textrm{LP}}}
-
-\newcommand{\UB}{\mathrm{UB}}
-\newcommand{\LB}{\mathrm{LB}}
-\newcommand{\ub}{\mathrm{ub}}
-\newcommand{\lb}{\mathrm{lb}}
-\newcommand{\B}{\mathrm{B}}
-
-\newcommand{\CMP}{{\textrm{CMP}}\ }
-
-\newcommand{\toolname}{\ensuremath{\mathsf{Comp}}}
-
-%\usepackage{amsmath, amsthm, amssymb, amsfonts}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{corollary}{Corollary}
-%\theoremstyle{definition}
-%\newtheorem{definition}{Definition}
-
-\newcommand{\ReLU}{\mathrm{ReLU}}
-
-\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
-\date{}
-
-\begin{document}
-
-	\maketitle
-
-	\begin{abstract}
-		Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally that they are correct, with an annual competition to compare them, etc.
-Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
-This allows e.g.
-to check local robustness around an input $\vx$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $\vx$.
-In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs.
-While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern verifiers, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.
-
-		In this paper, we analyse efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
-Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other.
-It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions.
-Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes.
-These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.
-	\end{abstract}
-
-	\section{Introduction}
-
-	\input{introduction}
-
-	\section{Background}
-
-	In this paper, we will use lower case latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
-	capitalized bold for matrices $\boldsymbol{W}$, similar to notations in \cite{prima,crown}.
-	To simplify the notations, we restrict the presentation to feed-forward, 
-	fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-	$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
-
-	%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
-
-	%\subsection{Neural Network and Verification}
-
-	% testtesttesttest
-	An $\ell$-layer DNN is provided by $\ell$ weight matrices 
-	$\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
-	and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
-	We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
-	$d_0$ the input dimension, and $d_\ell$ the output dimension.
-
-	Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-	denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
-	\begin{align*}
-		{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i\\
-		\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
-	\end{align*}
-
-	The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
-	$\boldsymbol{z}$ is called pre-activation values, 
-	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
-A path $\pi$ is a sequence $\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight of $\pi$ is
-	$weight(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
-
-	\iffalse
-	and the $i$-th hidden layer is a vector in $\mathbb{R}^{d_i}$, 
-	and the output layer is a vector in $\mathbb{R}^{d'}$ or a scale. 
-	The weights, bias and activation functions decide propagate the from previous to the next layer. In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight 
-	$\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, 
-	the bias is a vector $\vb^i$ in $\mathbb{R}^{d_i}$, and the activation function 
-	is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, 
-	then the value of $i$-th layer is computed by: 
-	\begin{align*}
-		{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \vb^i\\
-		\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)).
-	\end{align*} The vector $\hat{\boldsymbol{z}}$ is called post-activation values, and $\boldsymbol{z}$ is called pre-activation values, and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer.
-In our style, we also call neurons \emph{nodes} and use $a,b,c,d$ to denote them.
-We use $W_{ab}$ to denote the weight from neuron $b$ to $a$.
-We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
-	\fi
-
-	\medskip
-
-	Concerning the verification problem, we focus for simplicity on the usual local robustness question.
-Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
-	Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
-	\begin{align*}
-		\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
-		argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
-	\end{align*}
-
-	\iffalse
-	In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
-		\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
-	\end{align*}
-
-	If so, the question of verification can turn to the following optimization question: \begin{align*}
-		\min f(\boldsymbol{x}) \ s.t. {\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ b^i\\
-		\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)), \boldsymbol{x}\in\mathcal{D}.
-	\end{align*}
-
-	In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$.
-
-	In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\vx,\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
-	\fi
-
 	\section{Value Abstraction for DNN verification}
@@
 \end{proof}
-
-\input{comppaths}
-
-\input{experiments}
-
-\vspace{-0.2cm}
-\section{Conclusion}
-\vspace{-0.2cm}
-
-In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
-We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.
-
-Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Last, we experimentally showed that choosing $Z$ covering {\em few} paths with the strongest compensations, results in very good accuracy, and runtime which can be favourable in some (but not all) cases.
-This proves that compensating strength is a promising novel concept which should be further studied to improve DNN verification.
-We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.
-
-\newpage
-
-\bibliographystyle{plain}
-\bibliography{references}
-
-\newpage
-
-\appendix
-
-\input{proofs}
-
-\end{document}
-
-\section{Ranking of Compensating Pairs}
-
-In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.
-
-Based on No Diamond Theorem, for a target node, in its MILP model, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node.
-However, in practice, this is still too expensive because we will still need to open too many nodes.
-So we can only choose a limited number of compensating pairs and nodes.
-This is by setting a parameter $O$ such that the process only choose at most $O$ many nodes to open.
-Therefore, in this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.
-
-Basically, we do the process of open nodes chosen for one target node each time, that is, receive one target node (and other data) as input each time.
-But in principle, we can develop a method receive more than one nodes as input.
-But in our experiences, this does not work well.
-
-This process is not the unique method but the most natural way to choose open nodes. We introduce it in three steps from the simplest case to more complex case.
-
-\subsubsection*{Value of a pair}
-
-For a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.
-
-\subsection*{Case: Source node fixed}
-
-The simplest case is when we only consider compensating pairs with a fixed source node.
-
-In this case, the process is very simple: enumerate all compensating pairs, and then sort them by their values.
-Finally, from the first to the last compensating pair, pick all unstable nodes in its two paths except the target and source nodes into the list of open nodes, until $O$ many open nodes.
-
-%\subsubsection*{Sort all paths by values}
-%
-%The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.
-%
-%Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.
-%
-%\subsubsection*{Sort pairs by values}
-%
-%The second step is to sort all pairs by their values.
-Enumerate paths from the positive group and the negative group one by one and put the pairs obtained into a new list of pairs.
-Then sort all pair by their values from largest to the smallest: recall that the value of a pair $\langle P_1,P_2\rangle$ is $\min(|V_1|,|V_2|)$.
-%
-%\subsubsection*{Choosing nodes}
-%
-%The third step is to choose nodes from the list of pairs.
-According to the sorted list of pairs, enumerate pair one by one; for each pair, pick the nodes unstable in the two paths except the source and target node into the open node list.
-Repeat this process until $O$ nodes chosen or reach the end of the list.
-%
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-%
-
-\subsection*{Case: Source nodes in one layer}
-
-The more general case is when the source node can be any node in a fixed layer. In this case, the process is very similar to previous case, except the value of a pair.
-
-In this case, for a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, its value is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
-
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-
-\subsection*{Case: Source nodes in different layers}
-
-The general case is that when the location of source nodes can be in different layers.
-This case is much more complex, because the scale level of values of paths from different layers are very different: usually a weight will be very small since every layer has a large number of nodes, therefore values of longer paths are products of more small numbers, and is definitely much smaller.
-If we sort all compensating pairs from different layers directly, then a very long initial segment of this list will be occupied by compensating pairs with the shortest length.
-Therefore, we need use some scale factors when comparing values of compensating pairs of different length.
-
-In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before).
-We will dynamically adjust the values during the process of node chosen.
-In text, the process of node chosen for length 3 plus length 4 is as follows:
-
-\vspace*{1ex}
-
-1. Generate the two lists of pairs sorted by their values for source nodes in 2 layers before the target node and 3 layers before separately as in the previous case.
-
-2.
-Enumerate pair from two lists one by one by their values and pick nodes as previous case.
-When comparing the values between pairs of length 4 and pairs of length 3, multiply the numbers of nodes in 1 layer before to the value of pair of length 4.
-
-In formula, when the target node is in layer $L$, for a pair $P_3$ of length 3 with value $V_3$ and a pair $P_4$ of length 4 with value $V_4$, if we have chosen $N$ nodes in layer $L-1$.
-Then the adjusted values for $P_3$ and $P_4$ are: $$V_3, N\cdot V_4.$$ Then we pick the next pair by the adjust value in two lists.
-
-3. Repeat 2 until choosing sufficiently many nodes.
-
-\vspace*{1ex}
-
-The pseudo-code is as follows ():
-
-\begin{algorithm}
-\caption{Process for length 3 + length 4}
-\KwData{Sorted lists of length 3 + length 4}
-\KwResult{Open node list}
-
-Let $N = 0$ be the number of Chosen length 4 pair.
-
-\While{len(Open node) $<O$}{
-	Pick the first element $P_3$ in the list of length 3\;
-
-	Let $V_3$ be the value of $P_3$\;
-
-	Pick the first element $P_4$ in the list of length 4\;
-
-	Let $V_4$ be the value of $P_4$\;
-
-	\If{$V_3 > V_4 \cdot N$}{
-		Add nodes in $P_3$ into Open list\;
-		Number of Chosen lentgh pair $N$ += 1\; 
-	}
-	\Else{
-		Add nodes in $P_4$ into Open list\;
-	}
-}
-\end{algorithm}
-
-\end{document}

### 2024-01-27 Paper/Paper_noProof.tex
added new files

@@
 
-\newcommand{\toolname}{\ensuremath{\mathsf{Comp}}}
+\newcommand{\toolname}{\CMP}
 
@@
 
-	\section{Value Abstraction for DNN verification}
-
-	In this section, we describe different value (over-)abstractions on $\vz$ that are used by efficient algorithms to certify robustness around an input $\vx$.
-Over-abstractions of values include all values for $\vz$ in the neighbourhood of $\vx$, and thus a certificate for safety in the over-abstraction is a proof of safety for the original input $\vx$.
-
-	\subsection{The Box and DeepPoly Abstractions}
-
-\begin{figure}[t!]
-	\centering
-	\begin{tikzpicture}
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (input1) {$n_1$};
-
-		\node[circle, draw= purple, thick, minimum width = 20,
-		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};
-
-		% Hidden layers
-
-		\node (hidden10) at ($(input1) + (2.5,0.6)$) {$0$};
-
-		\node (hidden20) at ($(input1) + (2.5,-1.5-0.6)$) {$0$};
-
-		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$0$};
-
-		\node (hidden60) at ($(input1) + (7.5,-1.5-0.6)$) {$1.5$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$n_3$};
-		\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{n}_3$};
-		\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};
-
-		\node[circle, draw= blue, thick, minimum width = 20,
-		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
-		\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};
-
-		% Output layer
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{n}_5$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{n}_{6}$};
-
-		% Connections
-
-		\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
-
-		\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
-
-		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
-		\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$1$};
-
-		\draw[->,color=green, thick] (input2) -- (hidden1) node[near start, below] {$1$};
-		\draw[->,color=red, thick] (input2) -- (hidden2)node[near start, below] {$-1$};
-
-		\draw[->,color=green, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
-		\draw[->,color=red, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(n_2,0)$};
-
-		\draw[->,color=green, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
-		\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
-
-		\draw[->,color=red, thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
-		\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
-
-		\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(n_5,0)$};
-		\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(n_6,0)$};
-
-	\end{tikzpicture}
-	\caption{A DNN example from \cite{kpoly}: every neuron is separated into 2 nodes, $n$ pre- and $\hat{n}$ post-ReLU activation function.
-The pair $(n_2 n_3 n_5,n_2 n_4 n_5)$ in green and red is compensating (weights of paths are $1,-2$).}
-	\label{fig1}
-\end{figure}
-
-The idea to perform value abstraction is to compute upper and lower bounds on the values of (some) neurons in the DNN when the inputs are in a given neighbourhood, in order to conclude on the robustness without needing to compute the values exactly for all inputs (in the neighbourhood).
-
-First, remark that weighted sums is a linear function, so it is easy to represent it explicitly.
-The only problematic part to represent accurately is the ReLU function.
-While it is fairly simple piecewise linear function with 2 modes ($x<0$ and $x \geq 0$), it is not linear.
-Considering its iterated impact along the different layers of a ReLU DNN is much more complex than it seems.
-First, let us remark that it is easy to represent exactly $\ReLU(x)$ in case $x$ is {\em stable}, that is, either it is known to be entirely positive, order
-it is known to be entirely negative, as in both case there is only one known linear mode involved. Hence, the sole problem remains how to handle {\em unstable} neurons.
-
-Consider the simpler abstraction, called the {\em Box abstraction} \cite{deeppoly}: inductively compute the bound on each neuron of the next layer independently, by considering the weighted sum over the bounds of the previous layer, then clip the lower bound at
-$\max(0,$ lower bound$)$ to represent the ReLU function, and so on.
-For all $i$, let $x_i=\val_{\vx}(n_i)$, with $\vx=(x_1,x_2)$.
-For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $\hat{x}_3,\hat{x}_4 \in [0,2]$, and $x_5 \in [0,6]$ while $x_6 \in [0,2]$. 
-While the bounds for $n_1, \ldots, n_4$ are exact (for all $\alpha$ 
-in the range, there is an input $\vy$ such that $\val_{\vy}(n_i)=\alpha$), 
-it is no more the case from the next layer (starting in $n_5,n_6$) because of potential 
-dependencies between earlier neurons: $n_3$ reaches value $2$ only when $x_1=x_2=2$,
-in which case $n_4$ reaches value $Val_{(2,2)}(n_4)=0$. Hence, it is impossible that $x_5=\Val_{\vx}(n_5)$ reaches $6$, as it would require both $n_3$ and $n_4$ to have value $2$.
-
-A still extremely fast algorithm that corrects some of this issue is {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
-hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the value of the node.
-Denote $f_i \leq x_i \leq g_i$ with e.g.  
-$f_{3}(x_3)=f_4(x_4)=0$ and 
-$g_3(x_3) = \frac{x_3+2}{2}$,
-$g_4(x_4) = \frac{x_4+2}{2}$. 
-With that, we get 
-$x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
-
-For $[\alpha,\beta]$ bounds on $x_i$, there is one optimal linear function for the upper bound $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes.
-There are two choices for the lower bound: $f^1_i(x_i) = 0$ or $f^2_i(x_i)=x_i$.
-In the DeepPoly algorithm, the choice is made by considering $\alpha < 0 < \beta$ (for unstable neurons).
-If $|\alpha|\geq |\beta|$ then $f_i=f^1_i$ is used, while if $|\beta|>|\alpha|$ then $f_i=f^2_i$ is used.
-Denote {\em $\overline{\mbox{DeepPoly}}$} the DeepPoly algorithm such that $f^1_i$ is always used, and $f^2_i$ is never used.
-Unlike DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} subsumes the {\em Box abstraction}. Indeed, taking bounds $[-0.2,5]$ on $x_i$, it gives $\ReLU(x_i) \in [0,5]$, 
-while the normal DeepPoly algorithm would only allow to conclude that $\ReLU(x_i) \in [-0.2,5]$.
-
-\iffalse
-\subsection{PRIMA and $\beta$-CROWN}
-\fi
-
-\subsection{MILP and LP encodings for DNNs}
-
-At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method (albeit much slower than DeepPoly). 
-Consider an unstable neuron $n \in[\alpha,\beta]$.
-The value $x$ of $\ReLU(n)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints \cite{MILP}:
-\vspace{-0.1cm}
-\begin{align*}
-	\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)
-\end{align*}
-
-From \cite{MILP}, for all $x \in [\alpha,\beta] \setminus 0$, there is a unique solution $(a,\hat{x})$ satisfying the constraints, and we have $\hat{x}=\ReLU(x)$ (and $a$ is 0 if $x < 0$ and 1 if $x>0$, and can be either for $x=0$).
-Such an encoding can be used for every (unstable) ReLU node, and optimizing its value allows to certify a given input.
-For Networks with hundreds of nodes or more, the associated MILP formula will have have hundreds of integer variables, and it will usually not be solvable efficiently.
-
-MILP instances can be linearly relaxed into LP over-abstraction, where variables which were integers in $\{0,1\}$ (binary) are relaxed to be real in interval $[0,1]$, using otherwise the same encoding.
-Solving LP instances being Polynomial time, optimizing it is much more efficient, but at the price of a lack of accuracy (e.g.
-with not as tight bounds).
-This is called the {\em LP abstraction}.
-
-As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while DeepPoly considers exactly one.
-
-\begin{proposition}
-	\label{LP}
-	Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
-	1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
-	\vspace{-0.3cm}
-	\begin{align*}
-		& 1) \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1] \\
-		\text{and} \quad  & 2)  \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha}
-	\end{align*} 
-\end{proposition}
-
-\begin{proof}
-	Obviously, the 2 lower bound constraints are the same in 1) and 2).
-
-	It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
-For that, we study the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
-We have $\hat{x}$ in 1) is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
-	The function $min(\beta \cdot a, x - \alpha (1-a))$ reaches its maximum for 
-	$\beta \cdot a = x - \alpha (1-a)$, that is 
-	$(\beta - \alpha) a = x - \alpha$, i.e. 
-	$ a = \frac{x - \alpha}{\beta-\alpha}$.
-	It thus gives an upper bound at 
-	$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the upper-bound function used in DeepPoly.
-	\hfill $\square$
-\end{proof}
+\input{valabstraction}
 

### 2024-01-27 Paper/experiments.tex
minor edit
added new files
experiments

@@
+\newpage
 \section{Experimental Evaluation}
 
-We implemented a prototype of {\toolname} in Python 3.8.
-We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) with 256 GB of main memory and 2 NVIDIA RTX 3090.
+We implemented a prototype of \toolname in Python 3.8. 
+We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
+with 256 GB of main memory and 2 NVIDIA RTX 3090. 
 Gurobi 9.52 was used for solving MILP and LP problems.
@@
 In particular, the current state of the art methods are unable to characterize $12\%$ to $20\%$ of the images as neither certified robust \cite{crown} nor find an adversarial example \cite{attack}.
+We call such images {\em undetermined}.
 Following methodology in prior work \cite{prima,crown}, we evaluate on the first 1000 images of the dataset.
-We also experimented on MLP of size $6\times 500$ (results not reported in \cite{prima,crown}), checking the first 200 images of the dataset, given the computational overhead associated with such larger networks.
+We also experimented on the network of size $6\times 500$ (results not reported in \cite{prima,crown}), checking the first 200 images of the dataset, given the computational overhead associated with such larger networks.
 Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
+All these DNNs are found in the ERAN GitHub 
+(\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided).
 %Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
@@
 	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}.
-We report the runtime from our own implementation used in {\toolname}.
+We report the runtime from our own implementation, used in {\toolname}.
 It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
-	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN.
-We use the results reported in \cite{prima} and \cite{crown} respectively for instances that were also used in prior works and report results for MLP $6\times500$ instances as it was not considered in prior work.
+	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN \cite{crown}. We use the results reported in \cite{prima} and \cite{crown} respectively for instances that were also used in prior works.
+	We report results for the $6\times500$ network as it was not reported in prior work.
 
@@
 By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
-	\item ($\alpha$)$\beta$-CROWN, with results as reported in \cite{crown}, as it is the most accurate of the efficient tool to date. 
 %	Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and using GPU implementation (while we do not). Performance of pure BaB on these 
@@
 	\item It is worth remarking that we do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
-	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods\cite{crown}.
+	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods \cite{crown}.
 
@@
 	\item How does the the choice of  the set  $Z$ impacts the accuracy of $\MILP_Z$? 
-	\item  How does the performance, measured as the percentage of images verified, of {\toolname} compare to that of prior state of the art approaches? 
-	\item Evaluate how the runtime of {\toolname} scale with the size of DNNs.
+	\item  How does the performance, measured as the percentage of images verified, of \toolname compare to that of prior state of the art approaches? 
+%	\item Evaluate how the runtime of \toolname scales with the size of DNNs.
 \end{enumerate}
@@
 %The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-To measure the impact of the heuristic based on compensation strength, we focused on the smallest MLP (i.e.
+To measure the impact of the heuristic based on compensation strength, we focused on the smallest DNN (i.e.
 of size $5\times 100$ \cite{crown}) so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
@@
 
+%KSM: I don't think this is really the place for the paragraph below
+% Let $c$ be a node of the second layer.
+%A compensating pair $(\pi,\pi')$ of paths with target $c$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
+The compensating strength for $(b,b')$ is defined as $comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$.
+Indeed, the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),$\newline $weight(a,b',c))$, and $b,b'$ would help compensated the set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
+After selecting the heaviest $(b_0,b_0')$, we can then compute $comp(b)= \sum_{b' \text{already selected}} comp(b,b')+comp(b',b)$ and select iteratively the heaviest $b$'s one by one till reaching the threshold.
+%We do this for all node $c$ of the second layer.
+
 \subsubsection*{ReLU Node in the first hidden layer}
 
-\begin{table}[b!]
+We first focus on the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer. 
+We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
+The range of uncertainty created by inacurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
+Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracies is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
+We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
+
+\begin{table}[h!]
 	\centering
@@
 
-%KSM: I don't think this is really the place for the paragraph below
-% Let $c$ be a node of the second layer.
-%A compensating pair $(\pi,\pi')$ of paths with target $c$ is thus of the form a node $a b c$ and $a b' c$, with $a$ an input node and $b,b'$ on the first layer.
-The compensating strength for $(b,b')$ is defined as $comp(b,b')=\sum_a \val_{\vx}(a) \min(weight(abc),weight(ab'c))$.
-Indeed, the pair $(a b c,a b' c)$ of path cannot compensate more than $\val_{\vx}(a) \min(weight(a,b,c),$\newline $weight(a,b',c))$, and $b,b'$ would help compensated the set of pairs of paths $\{(a b c,a b' c) \mid a$ is in the first layer$\}$.
-After selecting the heaviest $(b_0,b_0')$, we can then compute $comp(b)= \sum_{b' \text{already selected}} comp(b,b')+comp(b',b)$ and select iteratively the heaviest $b$'s one by one till reaching the threshold.
-%We do this for all node $c$ of the second layer.
-
-We first focus on the choice of nodes in the first hidden layer, and its consequences on the accuracy of nodes in the second layer. 
-We report in Table \ref{tab:example0} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly.
-The range of uncertainty created by inacurate computations is up to $1.17=2.22-1.05$, $2.22$ being the accuracy provided by LP, and $1.05$ by an exact MILP encoding of all the unstable ReLU nodes.
-Selecting $30$ out of the $61$ unstable ReLU nodes, the uncertainty created by inacurracy is reduced by $80\%$, while a random choice of nodes only leads up to roughly halving this number.
-We can deduce that selecting nodes based on compensating strength helps to select important ReLU nodes for the accuracy.
-
 \subsubsection*{ReLU Node in the first and second hidden layer}
@@
 We thus define:
-\vspace{-0.2cm}
+%\vspace{-0.2cm}
 $$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ 
-\vspace{-0.2cm}
+%\vspace{-0.2cm}
 
-and the associated $comp(b)$, and select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
+and the associated $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$. We then select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
 
@@
 
-\begin{table}[t!]	
+\begin{table}[h!]	
 	\centering
@@
 	\label{tab:example1}
-	\vspace{-0.8cm}
+	%\vspace{-0.8cm}
 \end{table}
@@
 
-We present the runtime and accuracy analysis of various techniques in Table~\ref{tab:example}.
-Several observations are noteworthy: DeepPoly/CROWN is by far the fastest, yet it is also the least accurate, certifying robustness for fewer than $30\%$ of the images.
-In contrast, there are at least $82\%$ of the images for which no attack is found (attacks computed by \cite{attack} in $\beta$-CROWN).
-Similarly, while PRIMA achieves better accuracy than DeepPoly/CROWN but falls short of {\toolname}.
+We present the runtime and accuracy analysis of various techniques in Table~\ref{tab:example}. Further, for each DNN, a PGD-attack \cite{attack} is run 
+on all the images. We report the $\%$ of images without attack, as being an {\em Upper Bound} on the $\%$ of images the vertifiers can certify.
 
-Next, we shift focus to the comparison with $\beta$-CROWN, where we observe intriguing trade-offs.
-As network sizes increase, {\toolname} demonstrates better accuracy in comparison to $\beta$-CROWN.
-As expected, there's a trade-off between runtime and accuracy: {\toolname} can verify more images, albeit at the cost of increased computation time.
+Several observations are noteworthy: DeepPoly (or CROWN) is by far the fastest, yet it is also the least accurate, certifying robustness for fewer than $30\%$ of the images.
+In contrast, there are at least $82\%$ of the images for which no attack is found.
+Similarly, PRIMA achieves better accuracy than DeepPoly/CROWN but falls short of \toolname.
+
+Next, we shift focus to the comparison with ($\alpha$)$\beta$-CROWN, where we observe intriguing trade-offs.
+On the shallowest DNNs (5 layers, $5 \times 100$, $5 \times 200$), \toolname accuracy is close to $\beta$-CROWN, within 1.5\%.
+This is because RefinedBaB used by $\beta$-CROWN, used by
+$\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough.
+
+As network sizes increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN.
+As expected, there's a trade-off between runtime and accuracy: \toolname can verify more images, albeit at the cost of increased computation time.
 However, more often than not, our primary concern lies in running a tool for a fixed timeout to determine whether it can verify the desired property within that time.
@@
 
-\begin{table}[htb]
+\begin{table}[t!]
 	\centering
-
-		\begin{tabularx}{0.9\textwidth}{|C||C|C|C|C|C|}
+	\begin{tabularx}{\textwidth}{|C||C||C|C|C||C|}
 
 		\hline
-		\text{DNN} & \shortstack{DeepPoly/\\CROWN} & PRIMA & $\beta$-CROWN & {\toolname} & \shortstack{Upper\\Bound}\\ 
+		\text{DNN} & \shortstack{Upper\\Bound} & \shortstack{DeepPoly/\\CROWN} & PRIMA & \shortstack{($\alpha$)$\beta$-\\CROWN} & \toolname \\ 
 		\hline \hline
 
-		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {$68.4\%$} &  $84.2 \%$ \\ 
-		$\epsilon = 0.026$ & 5s & 159s & 102s & {142s} &  \\
+		$5 \times100$\  & $84.2 \%$ & $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & $68.4\%$\\ 
+		$\epsilon = 0.026$ &  & 5s & 159s & 102s & 142s\\
 		\hline
 
-		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {$76.8\%$} & 
-		$90.1 \%$\\ 
-		$\epsilon = 0.015$ & 11s & 224s & 86s & {279s}  &\\ \hline \hline
+		$5 \times 200$ \  & $90.1 \%$ & $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {$76.8\%$}\\ 
+		$\epsilon = 0.015$ &  & 11s & 224s & 86s & {279s} \\ \hline \hline
 
-		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
-		$\epsilon = 0.026$ & 8s & 301s & 103s & {346s} & \\
+		$8\times100$\  & $82.0 \%$ & $29.2\%$ & $42.8\%$ & $62\%$ & {$\mathbf{65.8\%}$}\\ 
+		$\epsilon = 0.026$ &  & 8s & 301s & 103s & {346s}\\
 		\hline
 
-		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
-		$\epsilon = 0.015$ & 17s & 395s & 95s  & {697s$^\star$} & \\ \hline
+		$8\times200$\  & $91.1 \%$ & $25.9\%$ & $62.4\%$ & $73.5\%$ & {$\mathbf{80.7\%}$}\\ 
+		$\epsilon = 0.015$ &  & 17s & 395s & 95s  & {697s}\\ \hline \hline
 
-		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
-		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
+		$6\times500$\  & $92\%$ & $26\%$ & $32.5\%$ & $41\%$ & {$\mathbf{65\%}$}\\ 
+		$\epsilon = 0.035$ &  & 34s & 119s & 18.4s & {925s} \\ \hline
+
 	\end{tabularx}
 
-	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
+	\caption{$\%$ of verified images and average runtime in seconds.
 		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
-%		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.
 	}
@@
 
+\iffalse
+
 \subsection{Scalability of {\toolname} with Size of DNNs}
 
-We now focus on understanding the potential of {\toolname} for even larger networks than those that are usually considered in the verification community.
-To this end, Figure~\ref{fig2} presents the  average runtime per node across various DNNS.
-Observe that while  the average runtime per node isn't fixed (attributable to $\LP(N,K)$), it remains regulated, avoiding exponential increases — from 0.1s per node for the smallest DNN to 0.3s per node for the largest.
-This suggests that {\toolname} is scalable to larger DNNs, bypassing the high complexity barrier often encountered with approaches such as those based on pure branch and bound.
-
-\begin{figure}[h!]
+\begin{figure}[b!]
 	\centering
 	\begin{tikzpicture}
-		\begin{axis}[width=10cm,height=5cm,
+		\begin{axis}[width=10cm,height=6cm,
 			xlabel={},
@@
 
+We now focus on understanding the potential of {\toolname} for even larger networks than those that are usually considered in the verification community.
+To this end, Figure~\ref{fig2} presents the  average runtime per node across various DNNS.
+Observe that while  the average runtime per node isn't fixed (attributable to $\LP(N,K)$), it remains regulated, avoiding exponential increases — from 0.1s per node for the smallest DNN to 0.3s per node for the largest.
+This suggests that {\toolname} is scalable to larger DNNs, bypassing the high complexity barrier often encountered with approaches such as those based on pure branch and bound.
+
+\fi
+
 \section{Limitations and Discussion}

### 2024-01-27 Paper/introduction.tex

@@
 \item Our third primary contribution addresses a practical concern by 
-introducing \CMP (Algorithm \ref{algo1}), a pragmatic solution that builds on our theoretical insights.
+introducing {\CMP} (Algorithm \ref{algo1}), a pragmatic solution that builds on our theoretical insights.
 This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones.
-Our extensive empirical evaluation (refer to Table \ref{tab:example}) reveals \CMP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
+Our extensive empirical evaluation (refer to Table \ref{tab:example}) reveals {\CMP} achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
 It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$.
@@
 Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).
-
-\section{Comparison with Related Works}
-
-We compare CMP with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA.
-Compared with the exact encoding of a DNN using MILP \cite{MILP},
-we select a restricted number of ReLU nodes based on compensating strength to scale to larger DNNs while maintaining good accuracy. Further, compared to MIPplanet \cite{MIPplanet} which 
-uses a different selection of ReLU nodes, we compute bounds for all neurons iteratively, reducing drastically the number of ReLU nodes represented exactly for a given neuron,
-%(ReLU nodes which were considered for neurons in previous layers are not represented exactly for that neuron, while MIPplanet would need to represent all those ReLU nodes exactly), 
-using many fast computations, more efficient than one large computation.
-
-Compared with the linear relaxation of the MILP encoding \cite{MILP}, \CMP is strictly more accurate by design, but it will also be slower.
-
-Compared with ERAN-Deeppoly \cite{deeppoly}, which compute bounds on the value in a very efficient way, we prove that the LP encoding is strictly more accurate, which as far as we know is another novel result.
-To be more precise, DeepPoly
-abstract the weight of every node using two functions, one upper function and one lower function. While the upper function is fixed, there are 2 choices for the lower bound.
-We prove in Proposition  \ref{LP} that the LP relaxation corresponds exactly to the intersection of both choices.
-It is thus more accurate than DeepPoly, but also not as efficient.
-Therefore, \CMP will also be (much) more accurate than DeepPoly, but also not as efficient.
-
-Concerning PRIMA \cite{prima}, the idea is to keep explicitly dependencies between neurons, computing bounds layer by layer (as we do).
-This allows to maintain dependencies from potentially many layers beforehand.
-We take care of dependencies between neurons in a different way, as compensation is the reason why there are dependencies between neurons.
-Our method is more accurate for local dependencies, but will tend to lose precision for dependencies created several layers ago.
-Most of the dependencies are local, in the few last layers (because ReLU nodes will likely clip those that happened many layers ago), which explains why we obtain more accurate results than PRIMA.
-
-$\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities).
-On simple networks, such as those trained robust, branch and bound is  particularly efficient as it consider the important branches for the actual property to verify, while \CMP is less efficient as it has to consider each node one by one from the start, including nodes whose bounds are not important.
-However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider: for instance, Branch and Bound verifies only $3.5\%$ more images ($44.5\%$ from $41\%$) by enlarging the runtime by $50$ times on the larger $6 \times 5000$ DNN, and cannot close the gap with \CMP (65\% of images verified, Table \ref{tab:example}).
-
-On such complex DNNs, $\alpha,\beta$ CROWN (and PRIMA) resorts to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
-In \CMP, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
-As it is more efficient, we compute bounds for neurons in all the layers.
-This would be infeasible without the selection based on the compensation.
-The refined version of $\alpha,\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and \CMP is more accurate (Table \ref{tab:example}).
-%lowering the gap of verified images to the upper bound \cite{attack} down from 
-%$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}).
-
-Finally, algorithms abstracting the network (e.g.
-Reluplex / Marabou \cite{Reluplex,katz2019marabou}) are very different from algorithms abstracting the values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, \CMP $\ldots$ These algorithms have been developed to be {\em complete}, so they are slower but also more accurate than what we propose.

### 2024-01-27 Paper/valabstraction.tex

@@
 
-The idea to perform value abstraction is to compute upper and lower bounds on the values of (some) neurons in the DNN when the inputs are in a given neighbourhood, in order to conclude on the robustness without needing to compute the values exactly for all inputs (in the neighbourhood).
+The concept of value abstraction involves calculating upper and lower bounds for the values of certain neurons in a Deep Neural Network (DNN) when inputs fall within a specified range.
+This approach aims to assess the network's robustness without precisely computing the values for every input within that range.
 
-First, remark that weighted sums is a linear function, so it is easy to represent it explicitly.
-The only problematic part to represent accurately is the ReLU function.
-While it is fairly simple piecewise linear function with 2 modes ($x<0$ and $x \geq 0$), it is not linear.
-Considering its iterated impact along the different layers of a ReLU DNN is much more complex than it seems.
-First, let us remark that it is easy to represent exactly $\ReLU(x)$ in case $x$ is {\em stable}, that is, either it is known to be entirely positive, order
-it is known to be entirely negative, as in both case there is only one known linear mode involved. Hence, the sole problem remains how to handle {\em unstable} neurons.
+Firstly, it's important to note that weighted sums represent a linear function, which can be explicitly expressed with relative ease.
+However, the ReLU (Rectified Linear Unit) function presents a challenge in terms of accurate representation.
+Although ReLU is a relatively straightforward piecewise linear function with two modes (one for $x<0$ and another for $x \geq 0$), it is not linear.
+The complexity arises when considering the compounded effects of the ReLU function across the various layers of a ReLU DNN.
+It's worth noting that representing $\ReLU(x)$ precisely is feasible when $x$ is "stable," meaning it's consistently positive or consistently negative, as there's only one linear mode involved in each scenario.
+Consequently, the primary challenge lies in addressing "unstable" neurons, where the linearity of the function does not hold consistently.
 
-Consider the simpler abstraction, called the {\em Box abstraction} \cite{deeppoly}: inductively compute the bound on each neuron of the next layer independently, by considering the weighted sum over the bounds of the previous layer, then clip the lower bound at
-$\max(0,$ lower bound$)$ to represent the ReLU function, and so on.
-For all $i$, let $x_i=\val_{\vx}(n_i)$, with $\vx=(x_1,x_2)$.
-For instance, on the DNN example of Fig \ref{fig1}, $x_1,x_2 \in [-1,1]$, then $x_3,x_4 \in [-2,2]$, using ReLU $\hat{x}_3,\hat{x}_4 \in [0,2]$, and $x_5 \in [0,6]$ while $x_6 \in [0,2]$. 
-While the bounds for $n_1, \ldots, n_4$ are exact (for all $\alpha$ 
-in the range, there is an input $\vy$ such that $\val_{\vy}(n_i)=\alpha$), 
-it is no more the case from the next layer (starting in $n_5,n_6$) because of potential 
-dependencies between earlier neurons: $n_3$ reaches value $2$ only when $x_1=x_2=2$,
-in which case $n_4$ reaches value $Val_{(2,2)}(n_4)=0$. Hence, it is impossible that $x_5=\Val_{\vx}(n_5)$ reaches $6$, as it would require both $n_3$ and $n_4$ to have value $2$.
+Consider the simpler abstraction, termed ``Box abstraction" \cite{deeppoly}: it inductively computes the bounds for each neuron in the subsequent layer independently.
+This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth.
+For all $i$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
 
-A still extremely fast algorithm that corrects some of this issue is {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
-hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the value of the node.
-Denote $f_i \leq x_i \leq g_i$ with e.g.  
-$f_{3}(x_3)=f_4(x_4)=0$ and 
-$g_3(x_3) = \frac{x_3+2}{2}$,
-$g_4(x_4) = \frac{x_4+2}{2}$. 
-With that, we get 
-$x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
+Taking the DNN example from Fig \ref{fig1}, assume $x_1,x_2 \in [-1,1]$.
+This implies that $x_3,x_4 \in [-2,2]$.
+After applying the ReLU function, $\hat{x}3,\hat{x}4$ are constrained to $[0,2]$, leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$.
+The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val{\vy}(n_i)=\alpha$.
+However, this precision is lost from the next layer (beginning with $n_5, n_6$) due to potential dependencies among preceding neurons.
+For example, $n_3$ only attains the value $2$ when both $x_1$ and $x_2$ are $2$.
+In this case, $n_4$ would reach a value of $Val{(2,2)}(n_4)=0$.
+Consequently, it's implausible for $x_5=\Val_{\vx}(n_5)$ to reach $6$, as it would necessitate both $n_3$ and $n_4$ assuming the value $2$.
 
-For $[\alpha,\beta]$ bounds on $x_i$, there is one optimal linear function for the upper bound $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes.
-There are two choices for the lower bound: $f^1_i(x_i) = 0$ or $f^2_i(x_i)=x_i$.
-In the DeepPoly algorithm, the choice is made by considering $\alpha < 0 < \beta$ (for unstable neurons).
-If $|\alpha|\geq |\beta|$ then $f_i=f^1_i$ is used, while if $|\beta|>|\alpha|$ then $f_i=f^2_i$ is used.
-Denote {\em $\overline{\mbox{DeepPoly}}$} the DeepPoly algorithm such that $f^1_i$ is always used, and $f^2_i$ is never used.
-Unlike DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} subsumes the {\em Box abstraction}. Indeed, taking bounds $[-0.2,5]$ on $x_i$, it gives $\ReLU(x_i) \in [0,5]$, 
-while the normal DeepPoly algorithm would only allow to conclude that $\ReLU(x_i) \in [-0.2,5]$.
+An extremely efficient algorithm that addresses some issues is "DeepPoly" \cite{deeppoly}, also independently discovered as the "CROWN" algorithm \cite{crown}.
+Instead of strict bounds, for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$.
+For instance, denote $f_i \leq x_i \leq g_i$ with, for example, $f_{3}(x_3)=f_4(x_4)=0$ and $g_3(x_3) = \frac{x_3+2}{2}$, $g_4(x_4) = \frac{x_4+2}{2}$.
+This leads to $x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
+
+For bounds $[\alpha,\beta]$ on $x_i$, the optimal linear function for the upper bound is $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes.
+There are two options for the lower bound: $f^1_i(x_i) = 0$ or $f^2_i(x_i)=x_i$.
+DeepPoly selects between these based on the values of $\alpha$ and $\beta$ (for unstable neurons): if $|\alpha|\geq |\beta|$, then $f_i=f^1_i$ is chosen, otherwise, for $|\beta|>|\alpha|$, $f_i=f^2_i$ is selected.
+The variation, {\em $\overline{\mbox{DeepPoly}}$}, consistently chooses $f^1_i$, and never $f^2_i$.
+Contrary to DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} encompasses the ``Box abstraction." For instance, with bounds $[-0.2,5]$ on $x_i$, it deduces $\ReLU(x_i) \in [0,5]$, whereas  DeepPoly without box abstraction algorithm would conclude $\ReLU(x_i) \in [-0.2,5]$.
 
@@
 
-From \cite{MILP}, for all $x \in [\alpha,\beta] \setminus 0$, there is a unique solution $(a,\hat{x})$ satisfying the constraints, and we have $\hat{x}=\ReLU(x)$ (and $a$ is 0 if $x < 0$ and 1 if $x>0$, and can be either for $x=0$).
-Such an encoding can be used for every (unstable) ReLU node, and optimizing its value allows to certify a given input.
-For Networks with hundreds of nodes or more, the associated MILP formula will have have hundreds of integer variables, and it will usually not be solvable efficiently.
+It can be shown that for all $x \in [\alpha,\beta] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$.
+Here, $a$ is 0 if $x < 0$, 1 if $x>0$, and can be either if $x=0$~\cite{MILP}.
+This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help in certifying a given input.
+However, for networks with hundreds of nodes or more, the resulting MILP formulation will contain numerous integer variables and generally cannot be solved efficiently.
 
-MILP instances can be linearly relaxed into LP over-abstraction, where variables which were integers in $\{0,1\}$ (binary) are relaxed to be real in interval $[0,1]$, using otherwise the same encoding.
-Solving LP instances being Polynomial time, optimizing it is much more efficient, but at the price of a lack of accuracy (e.g.
-with not as tight bounds).
-This is called the {\em LP abstraction}.
+MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in ${0,1}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
+As solving LP instances is polynomial time, this optimization is significantly more efficient.
+However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
+This approach is termed the {\em LP abstraction}
 
-As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
-We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while DeepPoly considers exactly one.
+The following proposition shows that the LP abstraction is strictly more precise than the DeepPoly abstraction.
+This is attributed to the LP abstraction's simultaneous consideration of the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$.
+Conversely, the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.
 
@@
 	1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
-	\vspace{-0.3cm}
-	\begin{align*}
-		& 1) \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1] \\
-		\text{and} \quad  & 2)  \quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha}
-	\end{align*} 
+	\begin{align}
+& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1]  \label{eq:lp}\\
+&\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha} \label{eq:deeppoly}
+	\end{align} 
 \end{proposition}
@@
 \begin{proof}
-	Obviously, the 2 lower bound constraints are the same in 1) and 2).
+We need to show that the two upper bound constraints in Eq~\ref{eq:lp} is equivalent to the upper bound in Eq~\ref{eq:deeppoly}.
+To this end, we focus on the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
+We have $\hat{x}$ in Eq~\ref{eq:lp} is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
+Furthermore,
+	The function $\min(\beta \cdot a, x - \alpha (1-a))$ attains its maximum when $\beta \cdot a = x - \alpha (1-a)$, leading to the equation $(\beta - \alpha) a = x - \alpha$ and consequently $a = \frac{x - \alpha}{\beta-\alpha}$.
+This results in an upper bound of $\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$
 
-	It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound.
-For that, we study the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
-We have $\hat{x}$ in 1) is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
-	The function $min(\beta \cdot a, x - \alpha (1-a))$ reaches its maximum for 
-	$\beta \cdot a = x - \alpha (1-a)$, that is 
-	$(\beta - \alpha) a = x - \alpha$, i.e. 
-	$ a = \frac{x - \alpha}{\beta-\alpha}$.
-	It thus gives an upper bound at 
-	$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the upper-bound function used in DeepPoly.
-	\hfill $\square$
 \end{proof}

### 2024-01-27 Paper/relatedwork.tex
added related work

\subsection{Related Work}

We now compare {\CMP} with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art. When contrasted with the exact encoding of a DNN using MILP \cite{MILP}, we selectively target a limited number of ReLU nodes based on compensating strength. This approach scales to larger DNNs while preserving good accuracy. In comparison to MIPplanet \cite{MIPplanet}, which opts for a different selection of ReLU nodes, our strategy iteratively computes bounds for all neurons. This significantly reduces the number of ReLU nodes represented exactly for a given neuron through numerous rapid computations, proving more efficient than a single, larger computation. Furthermore, in contrast to the linear relaxation of MILP encoding \cite{MILP}, {\CMP} is inherently more precise, albeit with a slower runtime.

When examining ERAN-Deeppoly \cite{deeppoly}, which efficiently computes bounds on values, we establish that LP encoding is unequivocally more accurate. This is a novel insight, to our knowledge. DeepPoly abstracts the weight of every node using two functions: an upper function and a lower function. While the upper function is fixed, the lower function offers two choices. In Proposition \ref{LP}, we demonstrate that the LP relaxation precisely matches the intersection of these two choices. Consequently, it's more accurate than DeepPoly but less efficient, therefore making {\CMP} considerably more precise than DeepPoly, albeit less efficiently.

Regarding PRIMA \cite{prima}, the approach involves explicitly maintaining dependencies between neurons, calculating bounds layer by layer, similar to our method. This enables the retention of dependencies from many layers prior. Our method, however, handles dependencies between neurons differently, attributing them to compensation. It excels in accuracy for local dependencies but may lose precision for dependencies formed several layers back. Given that most dependencies are local, occurring in the last few layers (since ReLU nodes tend to clip those from far back), our method achieves more accurate results than PRIMA.

$\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) focus on running few instances of branch and bound (one per output neuron).  In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities. In simple networks, like those trained robustly, branch and bound is highly efficient, focusing on branches crucial for verifying the actual property. In contrast, {\CMP} is less efficient as it must individually consider each node from the start, including nodes with non-critical bounds. However, branch and bound hits a complexity barrier when verifying complex networks, such as naturally trained DNNs, due to an overwhelming number of branches. For instance, Branch and Bound verifies only 3.5\% more images (44.5\% from 41\%) by increasing runtime by 50 times on larger $6 \times 5000$ DNNs, and fails to match {\CMP}'s performance (65\% of images verified, Table \ref{tab:example}). On the other hand, for complex DNNs,  $\alpha,\beta$ CROWN (and PRIMA) resorts to a {\em refined} path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding. In {\CMP}, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength. As it is more efficient, we compute bounds for neurons in all the layers. This would be infeasible without the selection based on the compensation. The refined version of $\alpha,\beta$ CROWN is particularly accurate on small DNNs. As the depth grows, the more work is left to BaB and {\CMP} is more accurate (Table \ref{tab:example}).

Finally, algorithms such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network, and therefore,  diverge significantly from those abstracting values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, {\CMP}, and the like. These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and therefore, are often unable to handle the size of networks that can be handled by those abstract values.

### 2024-01-27 Paper/experiments.tex
main

@@
 On the shallowest DNNs (5 layers, $5 \times 100$, $5 \times 200$), \toolname accuracy is close to $\beta$-CROWN, within 1.5\%.
-This is because RefinedBaB used by $\beta$-CROWN, used by
-$\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough.
+Here, RefinedBaB used by $\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough that its very accurate.
 
-As network sizes increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN.
+As network sizes increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN. For instance, for $8 \times 100$ and $8 \times 200$, 
+RefinedBaB used by $\beta$-CROWN can only consider half of the layers. 
+On many images, there are too many branches for BaB left to consider, and it times out,
+reason why we close the gap of undetermined images from $17.6\%$ ($\beta$-CROWN) to $10.4\%$ (\toolname) in $8 \times 200$.
+
 As expected, there's a trade-off between runtime and accuracy: \toolname can verify more images, albeit at the cost of increased computation time.
-However, more often than not, our primary concern lies in running a tool for a fixed timeout to determine whether it can verify the desired property within that time.
+However, more often than not, our primary concern lies in running a tool to determine whether it can verify the desired property within a reasonable time.
+
+The last network $6 \times 500$ (trained naturally) is the largest one.
+Results were not reported in \cite{crown,prima}.
+On this larger network, the refined strategy of PRIMA and $\alpha,\beta$-CROWN is questionable, as the number of binary variables to encode even the first few layers is very large, and the efficiency of MILP unclear.
+As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are
+surprisingly inaccurate and fast in PRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined.
+We reported the standard pureBaB setting of $\alpha,\beta$-CROWN instead, with the usual 30s associated timeout.
+Accuracy on $\alpha,\beta$-CROWN was also very low, only $15\%$ more images verified than DeepPoly.
+To understand the impact of runtime, we also experimented with a 2000s timeout for $\alpha,\beta$-CROWN.
+It only improves the accuracy by $3.5\%$, at $44.5\%$, with a runtime of $954s$ ($50$ times longer than with the original $30s$ timeout).
+We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard DNN.
+For comparison, \toolname could verify more than $20\%$ more images than
+even $\alpha,\beta$-CROWN with the longest timeout, taking less than $0.3s$ per neuron to perform the verification in average per image.
 

### 2024-01-27 Paper/relatedwork.tex
relatedwork

@@
 In Proposition \ref{LP}, we demonstrate that the LP relaxation precisely matches the intersection of these two choices.
-Consequently, it's more accurate than DeepPoly but less efficient, therefore making {\CMP} considerably more precise than DeepPoly, albeit less efficiently.
+Consequently, it is more accurate than DeepPoly but less efficient.
+\CMP is considerably more precise than DeepPoly (it refines LP), albeit less efficiently.
 
@@
 It excels in accuracy for local dependencies but may lose precision for dependencies formed several layers back.
-Given that most dependencies are local, occurring in the last few layers (since ReLU nodes tend to clip those from far back), our method achieves more accurate results than PRIMA.
+Many dependencies are local, occurring in the last few layers (since ReLU nodes tend to clip those from far back), and \CMP achieves more accurate results than PRIMA.
 
@@
 For instance, Branch and Bound verifies only 3.5\% more images (44.5\% from 41\%) by increasing runtime by 50 times on larger $6 \times 5000$ DNNs, and fails to match {\CMP}'s performance (65\% of images verified, Table \ref{tab:example}).
-On the other hand, for complex DNNs,  $\alpha,\beta$ CROWN (and PRIMA) resorts to a {\em refined} path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding.
+
+For hard-to-verify DNNs that are not too large,  $\alpha,\beta$ CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding.
 In {\CMP}, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
@@
 This would be infeasible without the selection based on the compensation.
-The refined version of $\alpha,\beta$ CROWN is particularly accurate on small DNNs.
-As the depth grows, the more work is left to BaB and {\CMP} is more accurate (Table \ref{tab:example}).
+The refined version of $\alpha,\beta$-CROWN is particularly accurate on small DNNs.
+As the depth grows, the more work is left to BaB and \CMP is more accurate (Table \ref{tab:example}).
 

### 2024-01-27 Paper/experiments.tex
edits

--- 2024-01-26 Paper/experiments.tex
@@
 	\centering
-
-		\begin{tabularx}{0.9\textwidth}{|C||C|C|C|C|C|}
+	\begin{tabularx}{\textwidth}{|C||C|C|C|C|C|}
 
 		\hline
-		\text{DNN} & \shortstack{DeepPoly/\\CROWN} & PRIMA & $\beta$-CROWN & {\toolname} & \shortstack{Upper\\Bound}\\ 
+		\text{DNN} & \shortstack{Upper\\Bound} & \shortstack{DeepPoly/\\CROWN} & PRIMA & $\beta$-CROWN & {\toolname}\\ 
 		\hline \hline
 
-		$5 \times100$\  &   $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {$68.4\%$} &  $84.2 \%$ \\ 
-		$\epsilon = 0.026$ & 5s & 159s & 102s & {142s} &  \\
+		$5 \times100$\  & $84.2 \%$ & $16\%$ & $51\%$ & $\mathbf{69.9\%}$ & {$68.4\%$}\\ 
+		$\epsilon = 0.026$ &  & 5s & 159s & 102s & {142s}\\
 		\hline
 
-		$5 \times 200$ \  &  $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {$76.8\%$} & 
-		$90.1 \%$\\ 
-		$\epsilon = 0.015$ & 11s & 224s & 86s & {279s}  &\\ \hline \hline
+		$5 \times 200$ \  & $90.1 \%$ & $18.2\%$ & $69\%$ & $\mathbf{77.4\%}$ & {$76.8\%$}\\ 
+		$\epsilon = 0.015$ &  & 11s & 224s & 86s & {279s} \\ \hline \hline
 
-		$8\times100$\  &   $29.2\%$ & $42.8\%$ & $62\%$ & {$\mathbf{65.8\%}$}  & $82.0 \%$ \\ 
-		$\epsilon = 0.026$ & 8s & 301s & 103s & {346s} & \\
+		$8\times100$\  & $82.0 \%$ & $29.2\%$ & $42.8\%$ & $62\%$ & {$\mathbf{65.8\%}$}\\ 
+		$\epsilon = 0.026$ &  & 8s & 301s & 103s & {346s}\\
 		\hline
 
-		$8\times200$\  &   $25.9\%$ & $62.4\%$ & $73.5\%$ & {$\mathbf{80.7\%}$} & $91.1 \%$ \\ 
-		$\epsilon = 0.015$ & 17s & 395s & 95s  & {697s$^\star$} & \\ \hline
+		$8\times200$\  & $91.1 \%$ & $25.9\%$ & $62.4\%$ & $73.5\%$ & {$\mathbf{80.7\%}$}\\ 
+		$\epsilon = 0.015$ &  & 17s & 395s & 95s  & {697s$^\star$}\\ \hline
 
-		%6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time & \\ 
-		%$\epsilon = 0.035$ & & & & & & & & & &\\ \hline
+		$6\times500$\  & $92\%$ & $26\%$ & $32.5\%$ & $41\%$ & 65\%\\ 
+		$\epsilon = 0.035$ &  & 34s & 119s & 18.4s & 925s\\ \hline
+
 	\end{tabularx}
 
-	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
+	\caption{$\%$ of verified images and average runtime in seconds.
 		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
-%		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.
 	}
@@
 
-For DNNs robustly trained, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close \cite{crown} to the upper bound on the $\%$ of verified images \cite{attack}.
-Compensation strength is not required in these contexts, reason why we did not consider it.
+Our focus in this study was solely on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function.
+That said, it is worth remarking that the notion of compensation strength is independent of
+
+The rationale lies in the capability of MILP, the foundational component of {\toolname} (and branch-and-bound in the context of $\beta$-CROWN), to efficiently handle ReLU activations.
+
+While other activation functions can be abstracted, as seen with PRIMA (contrary to $\beta$-CROWN), the concept of compensation remains independent of the activation function used.
+We leave studying the
+
+We acknowledge the potential value in exploring compensation strength across varied activation functions and earmark this for subsequent research.
 

### 2024-01-27 Paper/experiments.tex
minor edit

--- 2024-01-27 Paper/experiments.tex
@@
 
-\section{Limitations and Discussion}
+\section{Discussion}
 \label{Discussion}
 
-For DNNs robustly trained, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close \cite{crown} to the upper bound on the $\%$ of verified images \cite{attack}.
-Compensation strength is not required in these contexts, reason why we did not consider it.
+In this work, we focused on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function.
+However, it is worth remarking that the notion of compensation strength is independent of  activation function, and therefore, an interesting direction of future work would be to explore other the impact of compensation strength-based approaches for other activation functions.
 
-We only considered DNNs with ReLU activation functions in this paper.
-The reason is that MILP, which is the basic block of {\toolname} (and BaB for $\beta$-Crown) can handle the ReLU activation function efficiently.
-Other activation functions are abstracted in more complex ways, e.g.
-by PRIMA (unlike $\beta$-CROWN).
-Still, the compensation paradigm is  orthogonal to the activation function.
-We believe that studying the compensation strength would be useful with other activation functions as well.
-We leave that for future work.
+Regarding accuracy, {\toolname} ranks highly among verifiers that abstract values.
+However, its runtime, particularly for larger DNNs, can be relatively slow, though not excessively so.
+Numerous optimization avenues exist.
+A primary strategy involves utilizing $\alpha$-$\beta$-CROWN initially in the sequence, reserving {\toolname} for images unresolved by $\alpha$-$\beta$-CROWN, potentially enhancing this with parallel node computation across additional CPU cores.
+Another tactic could involve adapting the refined branch-and-bound approach of $\beta$-CROWN to permit {\toolname} to process additional layers beyond MILP's capability, concluding the verification with BaB.
+More complex strategies might include modifying BaB to branch on unstable ReLU nodes, driven by compensation strength, or analyzing crucial nodes linked to uncertain outputs, enabling quicker computation of less precise bounds for less critical nodes.
+Furthermore, implementing a Refinement Abstraction framework, akin to methodologies in \cite{atva}, \cite{elboher}, or \cite{SRGR}, could be beneficial.
 
-Accuracy of {\toolname} is among the highest of the efficient verifiers that do abstraction on values.
-Runtime, while never blowing-up, can be on the slow side though, in particular for larger DNNs.
-There are many optimizations possible.
-The simplest is to run $\alpha$-$\beta$-CROWN first in the pipeline, and only use {\toolname} for those images for which $\alpha$-$\beta$-CROWN cannot conclude, possibly using more CPU cores to compute more nodes in parallel.
-Another simple way is to modify the {\em refined} BaB of $\beta$-CROWN to run {\toolname} on more layers than what exact MILP can do, and finish the verification using BaB.
-More involved would be to modify BaB to branch on unstable ReLU nodes guided by the compensation strength.
-Also, an analysis of important nodes for the uncertain output nodes could be performed, allowing to compute much faster less accurate bounds for those nodes not important.
-Last, one could perform a Refinement Abstraction framework similar to \cite{atva}, \cite{elboher}, or \cite{SRGR}.
-
-On the correlation between neurons, which PRIMA encodes explicitly, our results tend to show that it is more efficient to use the compensation strength to abstract the network.
-Still, considering ReLU nodes exactly tends to be very accurate locally, but less when the source of correlation is many layers away.
-Few important correlations {\em a la} PRIMA could be kept explicitly as linear constraints in the MILP encoding, helping to reduce the inaccuracies further.
+In terms of neuron correlation, a key feature explicitly encoded by PRIMA, our findings suggest that leveraging compensation strength for network abstraction is generally more effective.
+Although precise local accuracy is achieved by directly considering ReLU nodes, the accuracy diminishes when correlations originate from distant layers.
+Retaining a select few significant correlations, in the style of PRIMA, as explicit linear constraints in the MILP model, might offer a strategy to further improve accuracy.

### 2024-01-27 Paper/experiments.tex
newline

--- 2024-01-27 Paper/experiments.tex
@@
-\newpage
 \section{Experimental Evaluation}
@@
 
-Our focus in this study was solely on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function.
-That said, it is worth remarking that the notion of compensation strength is independent of
-
-The rationale lies in the capability of MILP, the foundational component of {\toolname} (and branch-and-bound in the context of $\beta$-CROWN), to efficiently handle ReLU activations.
-
-While other activation functions can be abstracted, as seen with PRIMA (contrary to $\beta$-CROWN), the concept of compensation remains independent of the activation function used.
-We leave studying the
-
-We acknowledge the potential value in exploring compensation strength across varied activation functions and earmark this for subsequent research.
+For DNNs robustly trained, $\alpha$-$\beta$-CROWN and PRIMA are excellent solutions, both very fast and very accurate, usually matching or getting very close \cite{crown} to the upper bound on the $\%$ of verified images \cite{attack}.
+Compensation strength is not required in these contexts, reason why we did not consider it.
 

### 2024-01-27 Paper/proofs.tex
proof

@@
 
-Assume that there is a no (weakly) compensating pair of paths.
+Assume that there is no (weakly) compensating pair of paths.
 
@@
 
-Using the concept of sign, now we introduce the key lemma for Theorem \ref{th1}.
+Using the concept of sign, we introduce input vectors $\vx^{*}, \vx^{\sharp}$:
 
@@
 	\end{itemize}
+\end{definition}
 
-\end{definition}
+We can then prove the following key lemma for Theorem \ref{th1}.
 
@@
 
-				Suppose $\mathcal{D}$ is a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$. 
+				Suppose $\mathcal{D}$ is a DNN with a unique output node $z$.
 				Let $X$ be the set of nodes $n$ such that there is a weak compensating path 
@@
 			\fi
+
+\newpage
+
+\subsection{Revised Proof of Theorem \ref{th2}}
+
+We assume without loss of generality that every node can be reached from at least one input with a path of non-zero weight (otherwise we just remove this node altogether).
+We also assume without loss of generality that there is no node which can only reach $z$ with path of weight $0$, as such nodes have no contribution to the value $\val(z)$.
+We denote $m<n$ to mean that there exists a path with non zero weight from $m$ to $n$.
+
+Further, we assume the fairly light {\em well-connected hypothesis} (H1) that the DNN is such that for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target).
+This hypothesis is used to remove corner cases
+which will not happen in actual DNNs, which all are well-connected.
+
+			\smallskip
+
+			We now show Theorem \ref{th2} under (H1).
+			Let $X$ be the set of nodes on compensating paths with target $z$, but not as source or target.
+
+			Let $Z$ be the subset of nodes $n$ of the DNN such that $S$ is defined on $n$ 
+			wrt node $z$.
+As proved earlier, $Z$ is suffix closed, i.e.
+if $m<n<z$ with $m \in Z$, then $n \in Z$.
+We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative sign.
+$X$ can intersect both $Z_+$ and $Z_-$.
+			We call $X_+ = Z_+ \cap X$ and $X_-=Z_- \cap X$, as well as 
+			defined $Y_+,Y_-$ such that $Z_+ = X_+ \sqcup Y_+$ and $Z_- = X_- \sqcup Y_-$.
+			We denote $Y=Y_+ \sqcup Y_-$.
+
+\begin{lemma}
+ Let $n \notin Z$. Then $n \in X$.
+\end{lemma}
+
+\begin{proof}
+			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite sign. 
+			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
+			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight.
+Depending on the sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$.
+We call $X_*$ this subset $X$.
+\qed
+\end{proof}
+
+Hence, it means that $X \sqcup Y$ partitions the set of neurons in hidden layers.
+
+\begin{lemma}
+	\label{lemma10}
+		Let $y \in Y_+$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
+		of paths  with weights of opposite sign with $\rho_1$ from $m$ to $y$ and 
+		with $\rho_2$ from $m$ to $z$ (even non disjoint).
+\end{lemma}
+
+\begin{proof}
+  $y \notin X$, so it is not on a pair of compensating pair with target $z$.
+  Let $\rho$ be a path from $y$ to $z$ (it has positive weight has $y \in Z_+$).
+  Hence $\rho_1 \rho, \rho_2$ have opposite sign, and they must meet before $z$.
+
+  If $\rho_1 \rho$ meets $\rho_2$ after $y$, then we use $(H_1)$ to get another disjoint path from $y$ to $z$ (it has positive weight has $y \in Z_+$), it would not meet $\rho_2$, a contradiction.
+
+  Hence $\rho_1$ must meet $\rho_2$ (that is before or at $y$).
+  Their weights must be of opposite sign, otherwise we can inductively reapplied the same argument to their suffixes.
+  Let $\rho_1=\rho_1'\rho_1''$.
+  Both $\rho_1 \cdot \rho$ and $\rho_2' \cdot \rho_1'' \cdot \rho$
+  are from $m$ to $z$ going through $y$, but with weights of opposite sign (as $\rho'_1$ and $\rho'_2$ have opposite sign).
+  Now, by $(H1)$, there exists a path $\rho_3$ disjoint from $\rho_1 \cdot \rho$ and$\rho_2' \cdot \rho_1'' \cdot \rho$ from $m$ to $z$.
+It means that we have a pair of compensating paths from $m$ to $z$, and thus $y \in X$, a contradiction with $y \in Y_+$.
+\qed
+\end{proof}
+
+It means that if a path $\rho_1$ from $m$ to $y$ has stricly positive (resp.
+negative) weight, then all the paths from $m$ to $z$ will also have strictly positive (resp.
+negative) weights.
+It means that Sign is defined on all the $m$ that can reach $Y_+$.
+
+We have the same results for $y \in Y_-$, for paths $\rho_1, \rho_2$ of same sign:
+
+\begin{lemma}
+	\label{lemma11}
+	Let $y \in Y_-$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
+	of paths with weights of same sign with $\rho_1$ from $m$ to $y$ and 
+	with $\rho_2$ from $m$ to $z$ (even non disjoint).
+\end{lemma}
+
+Hence, we obtain as corollary of both lemmas:
+
+\begin{corollary}
+\label{cor:simple}
+Assume that $m < n$ with $n \in Y$.
+Then $m \in Z$.
+\end{corollary}
+
+From there, we conclude that $Y$ is actually prefix-closed:
+
+\begin{lemma}
+	\label{lemma12}
+	Assume that $m < n$ with $n \in Y$.
+	Then $m \in Y$.
+\end{lemma}
+
+\begin{proof}
+Assume by contradiction that $m \notin Y$ with $m<n \in Y$.
+That is, $m \in X$, and there exists a node $m'$ with a pair of compensating paths to $z$
+passing by $m$. But now, that means that $m'<m<n<z$.
+Thus $m'$ is in $Z$, a contradiction with $m'$ the source of a pair of compensating paths.
+\qed
+\end{proof}
+
+To prove Theorem \ref{th2}, we can then optimize $Y$ first on its own (considering the sign of every node): use the same argument in Section A, the proof of Theorem \ref{th1}, we can maximize all $n$ such that $S(n)=1$ and minimize all $n$ such that $S(n)=-1$ at the same time, i.e., with the same input values.
+And for every node $n$ in $Y$, the value computed is the same as actual lower and upper bounds of $n$.
+
+Now we consider the contribution  (direct and indirect) of nodes in $Y$ to $z$ as biases.
+Let $z=\boldsymbol{bias}_z+\sum_{m\in Y} Appx(W_{mz}m)+\sum_{m\notin Y} \ReLU(W_{mz}m)$.
+Because we have pre-optimized nodes in $Y$, $\sum_{m\in Y} Appx(W_{mz}m)$ will be a constant in the following optimization, and its term $W_{mz}z$ can be regarded as a part of bias.
+
+This is similar for nodes in other layers.
+Let $n\in X$ and $n=\boldsymbol{bias}_n+\sum_{m\in Y} Appx(W_{mn}m)+\sum_{m\notin Y} \ReLU(W_{mn}m)$; similarly, $\sum_{m\in Y}Appx(W_{mn}m)$ is fixed after the first optimization.
+Thus we can regard all these terms nodes $m$ in $Y$ as bias.
+
+Moreover, what is more important is that,  for $m\in Y_+$, the pre-optimization will obtain its maximal value, and for $m\in Y_-$, this will get its minimal value.
+And for $n\in X_+$ or $n=z$, it will receive $Appx(W_{mn}m)$'s maximal values as bias either $m\in Y_+$ (then $W_{mn}>0$) or $m\in Y_-$ (then $W_{mn}<0$).
+Similar for $n\in X_-$.
+The exception is $n$ not in $Z$.
+But if $n\notin Z$, then any $m<n$ cannot in $Y$ because $Y\subseteq Z$.
+Hence, if $n$ is not in $Z$, then $n$ receives no bias from $Y$.
+
+Therefore, after the pre-optimization, for $z$ and every node $n\in X_+$, they receive nodes $m$ in $Y$ as bias, and this part of bias reaches its maximal.
+For every node $n\in X_-$,  they receive nodes $m$ in $Y$ as bias, and this part of bias reaches its minimal.
+
+Let $I$ be the set of input nodes of $Y$, and $J$ be the set of rest input nodes.
+After optimization of $Y$, the input values for $I$ are fixed, and therefore values of all nodes in $Y$.
+Consider the DNN $D'$ with input nodes $J$, where all the 
+edges from $m \in Y$ to $n$ are replaced by a bias for $n$ (we sum all these bias for a neuron $n$).
+We denote $\val'$ values of nodes in this DNN $D'$. All the ReLU nodes of $D'$ are in $X$, by definition of $X$.
+Thus $\MILP_X$ will be fully accurate in $D'$. Let $\beta'$ denote its upper bound. By the discussion earlier, we know that $\beta'=\max(z)$.
+
+Similarly, we can prove $\alpha=\min(z)$. This concludes the proof of Theorem \ref{th2}
+
+\iffalse
+
+\begin{lemma}
+	There does not exist a node $m$ with $m<n^+ \in Y^+$ and $m<n^- \in Y^-$.
+	\end{lemma}
+
+	\begin{proof}
+	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
+	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same sign, 
+	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite sign than $\rho_1$.
+Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite sign.
+	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
+	We then apply Lemma \ref{lemma11}, inductively then applying Lemma \ref{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. \qed
+	\end{proof}
+
+	With the same arguments, we obtain:
+
+	\begin{lemma}
+	If we have $m<n \in X_*$ and $m < n^+ \in Y_+$ (or $m < n^- \in Y_-$),
+	then $n < n^+$ (or $n < n^-$), with compensating pairs of path from $m$ to $n$.
+	\end{lemma}
+
+	Last, consider the case $m<n^+ \in Y_+$ and $m < n^- \in X_-$.
+
+In the first case, the ReLU for $n$ will be opened, so we do not need to worry about this case.
+
+			In the other cases, the ReLU associated with node $n$ will not be in $X$ 
+			(not opened in $\MILP_X$).
+			In the second case, as 
+			, it means that $z'$ is in a layer strictly before $z'$.
+			Consider all the possible associated target nodes $z'$ of compensating path from $n$.
+
+			Therefore, choose a path $Q$ from input to output with nonzero weight and disjoint from $P,P''$.
+Now, since weights of $P,P''$ have different signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path.
+This means $a$ will be opened.
+
+			Combining all discussion above, if $a$ is in a weak compensating path from input to output, then it is in a compensating path from one layer to another layer.
+Therefore, Theorem \ref{thm:2} implies Theorem \ref{th2}.
+This is what we want to show.
+			\fi

### 2024-01-27 Paper/comppaths.tex
minor edit

@@
 
-In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but 
-not efficient). 
-Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision. A pair $(\pi,\pi')$ of paths is {\em compensating} if:
+In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies. To this end, we first introduce a novel notion of compensating paths:
+
+\begin{definition}
+A pair $(\pi,\pi')$ of paths is {\em compensating} if:
 \begin{itemize}
@@
 \end{itemize}	
+We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or $(\pi',\pi)$ is compensating.
+\end{definition}
 
+\begin{example}
 	For instance, on Fig.~\ref{fig1}, the paths $\pi= n_2 n_3 n_5$ has weight $1$, while the
 	path $\pi'= n_2 n_4 n_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
-We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or $(\pi',\pi)$ is compensating.
+	\end{example}
 
-Compensating pair of paths will make precision of the target state reduce when using overabstraction of values. Here, $x_5 \leq 4$, which is reached for $x_1=1$ and $x_2=-1$: 
-$\val_{(1,-1)}(n_5)=4$.
-However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (contribution of $\frac{-x_2+3}{2} \leq 2$ instead of exact $-x_2 \leq 1$), obtaining $x_5 \leq 5$ instead of the precise $x_5 \leq 4$.
+The phenomenon of compensating pairs of paths significantly impacts the precision of the target state due to the overabstraction of values.
+For instance, consider a scenario where $x_5 \leq 4$ is attainable when $x_1=1$ and $x_2=-1$, leading to $\val_{(1,-1)}(n_5)=4$.
+However, the Box methodology estimates an upper limit of $6$.
+Although DeepPoly partially rectifies the dependency on $x_2$, it achieves only partial negation of the $x_2$ value owing to the excessive abstraction characteristic of ReLU.
+This results in an overestimated upper bound of $x_5 \leq 5$ through a contribution of $\frac{-x_2+3}{2} \leq 2$, as opposed to the exact calculation of $-x_2 \leq 1$, culminating in a precise upper bound of $x_5 \leq 4$.
 
-Intuitively, the target state receives the weight from the source state from the different paths from the source to the target.
-As the weights of the paths is of opposite sign, some of these weights will cancel out, by an amount up to $min(|weight(\pi')|,|weight(\pi')|)$.
-Further, that also avoid accumulating the error, in the same way as $0= |1+(-1)| \leq |1|+|-1|=2$ from an inaccurate analysis.
-The amount of compensation can however be reduced by the ReLU functions, because of clipping by the ReLU function.
-For instance, consider that the inputs $x_1,x_2$ lies in $[-1,-0]$.
-Then $\hat{x}_3$ will always be 0 for any input $\vx=(x_1,x_2) \in [-1,-0] \times [-1,-0]$, and $weight(\pi')$ will not compensate $weight(\pi')$.
+In an intuitive sense, the target state accrues weight from the source state via different paths connecting the source to the target.
+When these connecting paths possess weights of contrasting signs, a certain degree of cancellation occurs, with the extent of cancellation being up to $min(|weight(\pi')|,|weight(\pi')|)$.
+This mechanism also serves to mitigate error propagation in a manner similar to how $0 = |1+(-1)| \leq |1|+|-1| = 2$ in imprecise analyses.
+However, the ReLU functions can constrain the level of compensation due to their clipping effect.
+For instance, if the inputs $x_1, x_2$ are confined within the range $[-1,-0]$, then $\hat{x}_3$ will consistently be 0 for any input $\vx=(x_1,x_2)$ within the domain $[-1,-0] \times [-1,-0]$, thereby preventing $weight(\pi')$ from effectively counterbalancing $weight(\pi')$.
 
@@
 
-Hence, compensation is {\em one} factor of inaccuracy. We prove now that it is actually the {\em only} reason for inaccuracy, in the following meaning.
-If there is no compensating path in the DNN, then any method/approximation at least as accurate as the Box abstraction, e.g.
-$\overline{\text{DeepPoly}}$ or LP, computes the exact upper and lower bounds for every node, that is:
-
 \begin{table}[b!]
@@
 
+The discussion so far shows  that compensation is one of the possible factors contributing to inaccuracy.
+We now establish that it is indeed the sole cause of inaccuracy, in particular,  if a DNN lacks any compensating path, then any methodology that is at least as accurate as the Box abstraction, such as ${\text{DeepPoly}}$ or LP, will precisely determine the exact upper and lower bounds for every node.
+This assertion is formalized in the following theorem:
+
 \begin{theorem}
 	\label{th1}
-	Let $n$ be any node of a DNN with {\em no} compensating path.
-For $[\alpha,\beta]$ the bounds computed by the {\em Box abstraction} for $n$, we have that for all $\gamma \in [\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n)=\gamma$.
+	Consider any node $n$ within a DNN devoid of any compensating path.
+Let $[\alpha,\beta]$ represent the bounds computed by the Box abstraction for node $n$.
+Then, for every $\gamma$ within the interval $[\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n) = \gamma$.
 \end{theorem}
+\begin{proof}
+	The sketch of proof can be found in Section \ref{sec.proofs}. 
+\end{proof}
 
-The sketch of proof can be found in Section \ref{sec.proofs}. 
-Notice that standard DeepPoly does not satisfies Theorem \ref{th1} (it does not necessarily refine Box), and therefore we are not sure PRIMA or $\beta$-CROWN that refine DeepPoly satisfies Theorem \ref{th1}, though it would be easy to fix by using $\overline{\text{DeepPoly}}$.
-Anyway, in practice, it is very unlikely to have a network without any compensating path, it is more of a theoretical results show in that compensation is the reason for inaccuracy.
+This theorem underscores the significant role of compensating paths in the accuracy of bound estimation within DNNs, affirming that their absence guarantees the precision of computed bounds.
+Practically speaking, encountering a network entirely devoid of compensating paths is highly improbable, rendering this more a theoretical observation, highlighting that compensation is a key driver of inaccuracy.
 
-This result has a first interesting application: explain why some DNNs are intrinsically easier to verify than others.
-This is the case for DNNs trained adversarially to be robust, vs same architecture, but trained in a "natural" way \cite{deeppoly,prima,crown}.
-Indeed, compensating pairs is a purely structural property on the DNN learnt, rather than more semantical notions, such as the number of unstable ReLUs, which depends heavily upon the image considered and the algorithm used.
-We compare compensations with source and target separated by 1 ReLU layer, e.g.
-source in layer 0 and target in layer 2, for two Networks with 5 hidden layers of 100 nodes each from the ERAN GitHub repository, one trained naturally ("$6\times100$"),
-and one trained using DiffAI \cite{DiffAI} ("$5\times100$"). 
-We report in Table \ref{tab:compensation} the average compensation strength, i.e. 
-the average of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$
-over all source/target states in given layers.
-The average compensations strength are much lower in the Robust DNN than in the natural DNN, and indeed the Robust DNN is much simpler to verify than the natural DNN (e.g.
-DeepPoly is more accurate and verifies more images).
+%It is worth remarking that  Theorem~\ref{th1} does not directly apply to standard DeepPoly since DeepPoly does not inherently refine the Box abstraction.
+Furthermore, it is unclear whether  Theorem~\ref{th1} applies to PRIMA or $\beta$-CROWN as these techniques refine DeepPoly.
+Nevertheless, this limitation could potentially be addressed by integrating $\overline{\text{DeepPoly}}$.
+
+An intriguing application of this result lies in elucidating why certain DNNs are inherently more amenable to verification compared to others.
+This distinction is notably evident between DNNs adversarially trained for robustness and those trained naturally, utilizing the same architecture \cite{deeppoly,prima,crown}.
+Notably, the presence of compensating pairs is an intrinsic structural attribute of the learned DNN, contrasting with more semantic aspects like the number of unstable ReLUs, which are significantly influenced by the specific image and algorithm employed.
+To illustrate this point, we consider two networks, each comprising 5 hidden layers with 100 nodes, sourced from the ERAN GitHub repository.
+One is naturally trained ($6\times100$), and the other is trained using DiffAI ($5\times100$).
+In Table \ref{tab:compensation}, we present the average compensation strength, computed as the mean of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$ across all source/target states within specified layers.
+The findings reveal that the average compensation strength is considerably lower in the Robust DNN compared to the natural DNN.
+Correspondingly, the Robust DNN is substantially easier to verify than its natural counterpart, as evidenced by the enhanced accuracy and image verification rate of DeepPoly.
 
@@
 $[\alpha,\beta]$.
-Let $X_n$ be the set of neurons $x$ in layer up to $k-1$ such that there is a compensating path with target $n$ passing by $x$ (but not as its source or target).
-Let $Y_n$ be the complement of this set $X_n$ of neurons in the first $k-1$ layers.
-We denote by MILP$_{X_n}$ the relaxation of the MILP encoding where all the nodes in $Y_n$ are linearly relaxed (thus with $|X_n|$ binary variable, one per neuron in $X_n$), and including exact bounds for every neurons $n'$ in the first $k-1$ layers.
-We state now that the bounds $[\alpha,\beta]$ on neuron $n$ computed by such MILP$_{X_n}$ are accurate.
+
+Consider a neuron $n$ in layer $k$, for which we aim to establish accurate bounds $[\alpha,\beta]$.
+Define $X_n$ as the set of neurons $x$ in layers up to $k-1$, where each $x$ is part of a compensating path targeting neuron $n$, but not as the originating or terminating node of the path.
+Let $Y_n$ represent the set of all other neurons in the first $k-1$ layers, essentially serving as the complement of $X_n$.
+We introduce MILP${X_n}$, a variant of the MILP encoding where all nodes in $Y_n$ are linearly relaxed, hence incorporating $|X_n|$ binary variables, each corresponding to a neuron in $X_n$.
+Additionally, this encoding encapsulates precise bounds for every neuron $n'$ in the initial $k-1$ layers.
+We propose that the bounds $[\alpha,\beta]$ for neuron $n$, as computed by MILP${X_n}$, are accurate, thereby offering a more nuanced approach to DNN verification in scenarios involving compensating paths.
 
@@
 
-Using Theorem \ref{th2}, one could thus obtain accurate bounds by running MILP$_{X}$ inductively on every node layer by layer, obtaining accurate bounds $[\alpha,\beta]$ that can be used to compute the next layer accurate bound.
-In practice, such an algorithm would however be inefficient, as $X_n$ comprises most of the nodes from layer up to $k-1$ for $n$ on layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation that are meaningful, and consider that paths below this threshold are not compensating strongly enough to deserve an integer variable, calling $Z_n$ the resulting set of nodes on {\em strongly compensating} paths.
-In practice, one could take the $K$ nodes covering the strongest compensating pair of paths to obtain set $Z_n$, for $K$ reasonably small.
-The pseudo-code of the algorithm is provided in Algorithm \ref{algo1}.
+Leveraging Theorem \ref{th2}, it is theoretically feasible to procure accurate bounds by iteratively applying MILP$_{X}$ to each node, layer by layer.
+This sequential approach would yield precise bounds $[\alpha,\beta]$ for each node, which could then be utilized to calculate accurate bounds for subsequent layers.
+However, in a practical setting, this methodology may prove to be computationally inefficient.
+Typically, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$.
+Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation.
+Paths falling below this threshold are deemed to not warrant an individual integer variable due to insufficient compensatory strength.
+We denote the resultant subset of nodes situated on paths with substantial compensation as $Z_n$.
+In practical applications, one might consider selecting the $K$ nodes that are involved in the most significant compensating paths to construct the set $Z_n$, with $K$ being a relatively small integer.
+This strategy effectively provides a trade-off between the algorithm's performance and the precision of the results.
+The detailed steps of this approach are outlined in the pseudo-code presented in Algorithm \ref{algo1}.
 
@@
 We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables.
-This complexity is an upper bound, as e.g. Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
-Notice that the for loop on neurons $n$ in layer $k$ at line 2 can be realized in parallel as we only need bounds from previous layers, not from the current layer $k$, 
-leading to a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, with $\ell$ the number of layers and $N_i$ the number of neurons in layers $0, \ldots, i$.
-Hence, for $K$ small enough, Algorithm \ref{algo1} calls many times MILP (e.g. Gurobi)
-with a limited number of integer variables, which should be efficient enough, and yet be quite accurate as it can compute exactly (Theorem \ref{th2}) the highest compensating path, which we verify in the next section.
+
+Notably, this complexity serves as an upper bound. For instance, solvers like Gurobi are quite adept and usually don't need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
+It's worth mentioning that the for loop iterating over neurons $n$ in layer $k$, as seen in line 2, can be executed in parallel.
+This is feasible because the computation only depends on bounds from preceding layers, not the current layer $k$.
+This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$.
+
+Therefore, if $K$ is sufficiently small, Algorithm \ref{algo1} frequently invokes MILP (e.g., using Gurobi) with a manageable number of integer variables.
+This approach is expected to be efficient and yet remains fairly precise, as it can accurately compute (according to Theorem \ref{th2}) the most significant compensating path.
+The effectiveness of this strategy is further examined in the subsequent section.
 

### 2024-01-27 Paper/Paper_noProof.tex
edits
removed \newpage
minor edit

@@
 
-	\section{Background}
+	\input{relatedwork}
+
+	\section{Notations and Preliminaries}
 
@@
 
-\vspace{-0.2cm}
 \section{Conclusion}
-\vspace{-0.2cm}
 
@@
 Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Last, we experimentally showed that choosing $Z$ covering {\em few} paths with the strongest compensations, results in very good accuracy, and runtime which can be favourable in some (but not all) cases.
-This proves that compensating strength is a promising novel concept which should be further studied to improve DNN verification.
+Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation yields highly accurate results.
+Additionally, we observed that the runtime can be advantageous in certain scenarios, though not universally.
+This underscores the potential of compensating strength as an innovative and promising avenue for enhancing DNN verification.
  We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.

### 2024-01-27 Paper/proofs.tex
proof of th2

@@
 
+We now prove Theorem \ref{th2} under the fairly light {\em well-connected hypothesis} (H1) that the DNN is such that for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target).
+This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected.
+
+Further we assume without loss of generality that every node can be reached from at least one input with a path of non-zero weight (otherwise we just remove this node altogether).
+We also assume without loss of generality that there is no node which can only reach $z$ with path of weight $0$, as such nodes have no contribution to the value $\val(z)$.
+We denote $m<n$ to mean that there exists a path with non zero weight from $m$ to $n$.
+
+Under (H1), we have the following Lemma:
+
+\begin{lemma}
+  Let $n$ be on a {\em weakly} compensating pair $(\rho_1,\rho_2)$ of paths, 
+  except an input or $z$. Then there exists a compensating pair of paths 
+ $(\rho,\rho')$ including $n$, not as its source or its target.
+\end{lemma}
+
+\begin{proof}
+Let $(s,t)$ be the source and the target of $(\rho_1,\rho_2)$.
+Let an input $a$ such that $a<s$ with path $\rho_0$ between $a$ and $s$,
+and $\rho_3$  from $t$ to $z$.
+Applying (H1) to the pair 
+$(\rho_0 \cdot \rho_1 \cdot \rho_3, \rho_0\cdot \rho_2 \cdot \rho_3)$, 
+we have another (non zero weight) path $\rho'$ from $a$ to $z$ totally disjoint with these two path.
+The weights of $(\rho_0 \cdot \rho_1 \cdot \rho_3, \rho_0\cdot \rho_2 \cdot \rho_3)$
+are of opposite sign because $(\rho_1,\rho_2)$ is weakly compensating, so one of them must be of opposite sign than the weight of $\rho'$. Say its $\rho = \rho_0 \cdot \rho_1 \cdot \rho_3$
+else we pick $\rho=\rho_0\cdot \rho_2 \cdot \rho_3$.
+Then $(\rho,\rho')$ is a pair of compensating path from $a$ to $z$, and as $n$ is neither an input nor $z$, it is strictly on $\rho$.
+\end{proof}
+
+It suffices to invoke Theorem \ref{thm:2} in order to get the proof for Theorem \ref{th2},
+as the set $X$ considered in both are actually the same.
+
+\end{document}
+
+\subsection{Proof of Theorem \ref{th2}}
+
 Note: it does not need directly the previous proof, although it uses the same arguments.
@@
 We assume the fairly light hypothesis (H1) that the DNN is such that for every 2 paths $\rho_1,\rho_2$ (not necessarily disjoint) from any $m$ to any $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$.
+
 Further we assume without loss of generality that every node can be reached from at least one input with a path of non-zero weight (otherwise we just remove this node altogether).
@@
 
-To prove Theorem \ref{th2}, we can then optimize $Y$ first on its own (considering the sign of every node): use the same argument in Section A, the proof of Theorem \ref{th1}, we can maximize all $n$ such that $S(n)=1$ and minimize all $n$ such that $S(n)=-1$ at the same time, i.e., with the same input values.
-And for every node $n$ in $Y$, the value computed is the same as actual lower and upper bounds of $n$.
+To prove Theorem \ref{th2}, we can then optimize $Y$ first on its own (considering the sign of every node): we first maximize all $n$ such that $S(n)=1$ and minimize all $n$ such that 
+$S(n)=-1$ at the same time, i.e., with the same input values. And for every node $n$ in $Y$, the value computed is the same as actual lower and upper bounds of $n$.
 

### 2024-01-27 Paper/comppaths.tex
section 3

@@
 
-In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies. To this end, we first introduce a novel notion of compensating paths:
+In this section, we explore the key factor for the loss of accuracy in value 
+abstraction methodologies. To this end, we first introduce the novel notion of compensating paths:
 
@@
 
-The discussion so far shows  that compensation is one of the possible factors contributing to inaccuracy.
-We now establish that it is indeed the sole cause of inaccuracy, in particular,  if a DNN lacks any compensating path, then any methodology that is at least as accurate as the Box abstraction, such as ${\text{DeepPoly}}$ or LP, will precisely determine the exact upper and lower bounds for every node.
+The discussion so far shows  that compensation is one of the possible factors contributing to inaccuracy. We now establish that it is the sole cause of inaccuracy:
+if a DNN lacks any compensating path, then any methodology that is at least as accurate as the Box abstraction, such as LP and $\overline{\mbox{DeepPoly}}$ (but not DeepPoly), will precisely determine the exact upper and lower bounds for every node.
 This assertion is formalized in the following theorem:

### 2024-01-27 Paper/comppaths.tex
proof

@@
 \end{theorem}
-\begin{proof}
+
 The sketch of proof can be found in Section \ref{sec.proofs}.
-\end{proof}
 
@@
 Intuitively, when there are compensating paths, it seems necessary to consider exactly the (unstable) ReLU nodes that are seen along these paths. 
-Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds 
-$[\alpha,\beta]$.
+%Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds 
+%$[\alpha,\beta]$.
 
 Consider a neuron $n$ in layer $k$, for which we aim to establish accurate bounds $[\alpha,\beta]$.
-Define $X_n$ as the set of neurons $x$ in layers up to $k-1$, where each $x$ is part of a compensating path targeting neuron $n$, but not as the originating or terminating node of the path.
-Let $Y_n$ represent the set of all other neurons in the first $k-1$ layers, essentially serving as the complement of $X_n$.
+Define $X_n$ as the set of neurons $x$ in layers up to $k-1$, where each $x$ is part of a compensating path targeting neuron $n$, but not as the source or the target node of the path.
+Let $Y_n$ represents the set of all other neurons in the first $k-1$ layers, essentially serving as the complement of $X_n$.
 We introduce MILP${X_n}$, a variant of the MILP encoding where all nodes in $Y_n$ are linearly relaxed, hence incorporating $|X_n|$ binary variables, each corresponding to a neuron in $X_n$.
-Additionally, this encoding encapsulates precise bounds for every neuron $n'$ in the initial $k-1$ layers.
-We propose that the bounds $[\alpha,\beta]$ for neuron $n$, as computed by MILP${X_n}$, are accurate, thereby offering a more nuanced approach to DNN verification in scenarios involving compensating paths.
+Additionally, this encoding encapsulates bounds for every neuron $n'$ in the initial $k-1$ layers, as computed inductively in previous steps.
+That is, we do not use explicitly in $X_n$ nodes on compensating paths with target neurons before $n$ ({\em indirectly} compensating paths),
+only those with target $n$ ({directly} compensating paths).
+The contribution of these {\em indirectly} compensating paths are thus 
+only taken into account indirectly via the bounds on previous neurons computed inductively,
+and not as binary variables.
+We demonstrate now that the bounds $[\alpha,\beta]$ for neuron $n$, as computed by MILP${X_n}$, are accurate, thereby offering a more nuanced approach to DNN verification in scenarios involving compensating paths.
+We will provide the proof under a fairly light well-connected hypothesis (H1), which only DNNs where all but very few weights are 0 does not satisfy.
+
+(H1): for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ with at least 2 transitions, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target).
+This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected.
 
@@
 	\label{th2} 
+	Assume the DNN satisfies the well-connected (H1) hypothesis.
 	Let $n$ be any node of a DNN.
@@
 \label{sec.proofs}
+
+First, notice that by continuity of all the functions used in the DNNs, it suffices to show both theorem for $\gamma=\alpha$ and $\gamma=\beta$.
 

### 2024-01-27 Paper/proofs.tex
proof

@@
 Now, in $D$, $\MILP_X$ will use simple LP on $D_I$, which suffices to get the upper bound $\val_{\vx^*_I}(n)=\max(n)$ for all $n$ in $D_I$ and the values will be pushed as bias in $D'$.
-Therefore, $\beta=\beta'=\max(z)$.
+Therefore, $\beta'=\max(z)$.
 
-The case for $\alpha=min(z)$ is similar. \qed
+We now prove that $\beta=\beta'$, which terminates the proof, as The case for $\alpha=min(z)$ is similar.
+
+We prove by induction from the input layer to higher layers that the upper bound of node $n$ in $D'$, is greater than or equal to the upper bound in $D$; and similarly for the lower bound.
+We use  $\Val^{D}_{x_J^0}(n)$ to denote the range of possible values for node $n$ in MILP model of $D$ when $x_J=x_J^0$.
+This may be a single number or an interval.
+
+For any input $x_J=x_J^0$, we prove $\Val^{D'}_{x_J^0}(n) \geq \UB(\Val^{D}_{x_J^0}(n))$
+by induction:
+
+\begin{align*}
+\Val^{D'}_{x_J^0}(n) = & \boldsymbol{bias}_n+\sum_{m\in B_{pure}} \max(\ReLU(W_{mn}m))+\sum_{m\notin B_{pure}} \ReLU(W_{mn}\Val^{D'}_{x_J^0}(m))\\
+(\text{by induction})\geq & \boldsymbol{bias}_n+\sum_{m\in B_{pure}} \max(\ReLU(W_{mn}m))+\sum_{m\notin B_{pure}} \UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
+= & \boldsymbol{bias}_n+\sum_{m\in B_{pure}} \UB(\mathrm{AppB}(W_{mn}))+\sum_{m\notin B_{pure}}  \UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
+\geq & \UB(\Val^{D}_{x_J^0}(n)), \text{when } S(n)=1
+\end{align*}
+
+Hence, using the $\max$, we will have $\max(z) = \beta'\geq \beta \geq \max(z)$, and hence $\beta=\beta'=\max(z)$.
+
+\qed
 

### 2024-01-27 Paper/proofs.tex
try

--- 2024-01-27 Paper/proofs.tex
@@
 We have $\beta'=\max_{\vx{_J}} (\val'_{\vx_{J}}(z)) = 
-\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n) = \max(z)$ by Corrolary \ref{corr:main}.
+\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n) = \max(z)$ by Corollary \ref{corr:main}.
 Now, in $D$, $\MILP_X$ will use simple LP on $D_I$, which suffices to get the upper bound $\val_{\vx^*_I}(n)=\max(n)$ for all $n$ in $D_I$ and the values will be pushed as bias in $D'$.
-Therefore, $\beta=\beta'=\max(z)$.
+Therefore, $\beta'=\max(z)$.
 
-The case for $\alpha=min(z)$ is similar. \qed
+We now prove that $\beta=\beta'$, which terminates the proof, as The case for $\alpha=min(z)$ is similar.
+
+We prove by induction from the input layer to higher layers that the upper bound of node $n$ in $D'$, is greater than or equal to the upper bound in $D$; and similarly for the lower bound.
+We use  $\Val^{D}_{x_J^0}(n)$ to denote the range of possible values for node $n$ in  model $D$ or $D'$ when $x_J=x_J^0$.
+This may be a single number or an interval. 
+Denote by $\beta_{x_J^0}(m)$ (resp $\beta'_{x_J^0}(m)$) the upper bound computed by $\MILP_X$ 
+for $m$ in $D$ (resp. $D'$) when the $J$ input is fixed to be ${x_J^0}$.
+
+For any input $x_J=x_J^0$, we prove $\beta'_{x_J^0} \geq \beta_{x_J^0}$ by induction on $n$:
+
+\begin{align*}
+	\beta'_{x_J^0}(n) = & {bias}_n+\sum_{m\in B_{pure}} W_{mn} \beta'(\hat{m})
+	+\sum_{m\notin B_{pure}} W_{mn} (\beta'_{x_J^0}(\hat{m}))\\
+(\text{by induction})\geq & {bias}_n+\sum_{m\in B_{pure}} \max(\ReLU(W_{mn}m))+\sum_{m\notin B_{pure}} 
+\UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
+= & {bias}_n+\sum_{m\in B_{pure}} \UB(\mathrm{AppB}(W_{mn}))+\sum_{m\notin B_{pure}}  \UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
+\geq & \UB(\Val^{D}_{x_J^0}(n)), \text{when } S(n)=1
+\end{align*}
+
+Hence, using the $\max$ over ${x_J^0}$, 
+we will have $\max(z) = \beta'\geq \beta \geq \max(z)$, and hence $\beta=\beta'=\max(z)$.
+
+\qed
 

### 2024-01-27 Paper/comppaths.tex
proof

@@
 
-The sketch of proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs}.
+The sketch of proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs2}.
 
-\subsection{Sketch of Proofs}
+\subsection{Sketch of Proof for Theorem \ref{th1}}
 \label{sec.proofs}
@@
 if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
-$-1$ if they have negative weights. Then we prove:
+$-1$ if they have negative weights.
+
+Using the concept of sign, we introduce input vectors $\vx^{*}, \vx^{\sharp}$:
+
+\begin{definition}
+We define the following two input vectors $\vx^{*}, \vx^{\sharp}$ in $\cal B$: 
+	\begin{itemize}
+		\item $\vx^{*}$ is the input vector defined in the following way:
+		\begin {itemize}
+		 \item $x^*_{a_i}=\max(a_i)$ if $S(a_i)\in \{0,1\}$, and
+          \item $x^*_{a_i}=\min(a_i)$ otherwise, that is when $S(a_i)=-1$.
+	\end{itemize}
+
+		\item $\vx^{\sharp}$ is the input vector defined in the following way:
+		\begin{itemize}
+			\item $x^{\sharp}_{a_i}=\min(a_i)$ if $S(a_i)\in \{0,1\}$, and
+			\item $x^{\sharp}_{a_i}=\max(a_i)$ otherwise, that is when $S(a_i)=-1$.
+		\end{itemize}
+	\end{itemize}
+\end{definition}
+
+We can then prove that $\vx^\star,\vx^\sharp$ maximize and minimize conjointly all the nodes in the DNN. Notice that it does {\em not} mean that there is no dependencies between nodes.
+There can be correlations between nodes, just they do not affect the $\min$ and $\max$ bounds that can be reached in any node.
 
@@
 	\label{prop.sign}
-	There exist two inputs $\vx^\star,\vx^\sharp$ such that ${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  ${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
+	${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  
+	${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
 \end{proposition}
@@
 \smallskip
+The formal proof is in appendix A.
+
+\subsection{Sketch of Proof for Theorem \ref{th2}}
+\label{sec.proofs2}
 
@@
 
-The formal proofs are in appendix.
+\smallskip
+The formal proof is in appendix.
 

### 2024-01-27 Paper/proofs.tex
proof

@@
 for $m$ in $D$ (resp. $D'$) when the $J$ input is fixed to be ${x_J^0}$.
+We define in the same way  $\alpha_{x_J^0}(m)$ and $\alpha'_{x_J^0}(m)$ for the minimal values.
 
-For any input $x_J=x_J^0$, we prove $\beta'_{x_J^0} \geq \beta_{x_J^0}$ by induction on $n$:
+For any input $x_J=x_J^0$, we prove $\beta'_{x_J^0}(n) \geq \beta_{x_J^0}(n)$ 
+and
+$\alpha'_{x_J^0}(n) \leq \alpha_{x_J^0}(n)$ 
+by induction on $n$:
 
 \begin{align*}
-	\beta'_{x_J^0}(n) = & {bias}_n+\sum_{m\in B_{pure}} W_{mn} \beta'(\hat{m})
-	+\sum_{m\notin B_{pure}} W_{mn} (\beta'_{x_J^0}(\hat{m}))\\
-(\text{by induction})\geq & {bias}_n+\sum_{m\in B_{pure}} \max(\ReLU(W_{mn}m))+\sum_{m\notin B_{pure}} 
-\UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
-= & {bias}_n+\sum_{m\in B_{pure}} \UB(\mathrm{AppB}(W_{mn}))+\sum_{m\notin B_{pure}}  \UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
-\geq & \UB(\Val^{D}_{x_J^0}(n)), \text{when } S(n)=1
+\beta'_{x_J^0}(n) = & {bias}_n+\sum_{m\in B_{pure},W_{mn}>0} W_{mn} \beta'(\hat{m})+\sum_{m\in B_{pure},W_{mn}<0} W_{mn} \alpha'(\hat{m})\\
++&\sum_{m\notin B_{pure},W_{mn}>0} W_{mn} \beta'_{x_J^0}(\hat{m})+\sum_{m\notin B_{pure},W_{mn}<0} W_{mn} \alpha'_{x_J^0}(\hat{m})\\
+\\
+(\text{by induction})\geq & {bias}_n+\sum_{m\in B_{pure},W_{mn}>0} W_{mn} \beta'(\hat{m})+\sum_{m\in B_{pure},W_{mn}<0} W_{mn} \alpha'(\hat{m})\\
++&\sum_{m\notin B_{pure},W_{mn}>0} W_{mn} \beta_{x_J^0}(\hat{m})+\sum_{m\notin B_{pure},W_{mn}<0} W_{mn} \alpha_{x_J^0}(\hat{m})\\
+\\
+(\text{Lemma \ref{lem:key1}})= & {bias}_n+\sum_{m\in B_{pure},W_{mn}>0} W_{mn} \beta(\hat{m})+\sum_{m\in B_{pure},W_{mn}<0} W_{mn} \alpha(\hat{m})\\
++&\sum_{m\notin B_{pure},W_{mn}>0} W_{mn} \beta_{x_J^0}(\hat{m})+\sum_{m\notin B_{pure},W_{mn}<0} W_{mn} \alpha_{x_J^0}(\hat{m})\\
+\geq & \beta_{x_J^0}(n)
 \end{align*}
+
+The case for $\alpha$ is similar, proving the induction.
 

### 2024-01-27 Paper/comppaths.tex
final v

@@
 
-We can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
-Further, the value of any neuron $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
-nodes in $A_{pure}$ or $B_{pure}$. Therefore, applying Prop. \ref{prop.sign} on the DNN
-made of nodes from $A_{pure}$ and $B_{pure}$, we obtain 
-$\vx_{pure}^\star,\vx_{pure}^\sharp$ optimizing neurons in $A_{pure}$ or $B_{pure}$.
-We can prove that there exists input 
-$\vx^\star$ extending $\vx_{pure}^\star$
-and input $\vx_{pure}^\sharp$ extending $\vx_{pure}^\sharp$
-from $A_{pure}$ to $A_{pure} \cup A_{open}$ such that 
-$\val_{\vx^\star}(z)=\beta(z)$ and $\val_{\vx^\sharp}(z)=\alpha(z)$.
+We can show the following lemma:
 
-\smallskip
-The formal proof is in appendix.
+\begin{lemma}
+	$A_{pure} \cup B_{pure} $ forms a sub-network, denoted $D_I$. That is, 
+	for $n \in B_{pure}$, for every path $\rho$ from $m$ to $n$
+	either $m \in B_{pure}\cup I$ or $weight(\rho)=0$.
+\end{lemma}
+
+Hence, the value of any neuron $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
+inputs in $A_{pure}$.
+
+We cannot define the Sign function on nodes from which a compensating path can be reached.
+However, we can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
+Further, the set of nodes on which the sign funciton is defined is suffix-closed:
+
+\begin{lemma}
+	Let $m,n$ be two nodes, such that $S$ is defined on $m$ and there is a path $\rho$ with non zero weight to a node $n$. Then $S$ is defined on $n$.
+	Further, $S(n)= Sign(weight(\rho)) S(m)$.
+\end{lemma}
+
+We can apply Theorem \ref{th1} on the DNN made of nodes from $A_{pure}$ and $B_{pure}$, and obtain $\vx_{pure}^\star,\vx_{pure}^\sharp$ optimizing neurons in $A_{pure}$ or $B_{pure}$:
+
+\begin{proposition}
+For a node $b$ with $S(b)=1$:
+
+$$\max(b)=\max_{\vx_{open}} \val_{\vx^{\star}_{pure},\vx_{open}}(b)$$
+$$\min(b)=\min_{\vx_{open}} \val_{\vx^{\sharp}_{pure},\vx_{open}}(b)$$
+
+and for $S(b)=-1$:
+$$\max(b)=\max_{\vx_{open}} \val_{\vx^{\sharp}_{pure},\vx_{open}}(b)$$
+$$\min(b)=\min_{\vx_{open}} \val_{\vx^{\star}_{pure},\vx_{open}}(b)$$
+\end{proposition}
+
+Consider the DNN $D'$ with input nodes $A_{open}$, where all the 
+edges from $m \in A_{open} \cup B_{open}$ to $n$ are replaced by a bias 
+(equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^\star_{open}}(m)$) for $n$ (we sum all these bias for a neuron $n$).
+The values in $D'$ are the same as the values in $D$ for input $\vx^{\star}_{pure}$,
+which suffices to reach the maximal value of $D$.
+In $D'$, all the ReLU nodes are in $B_{open}$. 
+Hence $\MILP_{B_{open}}$ computes the bounds accurately in $D'$.
+It will compute the bound in the same way in $D$, hence we get $\beta=\max(z)$ for the target $z$. The formal proof is in appendix B.
 
@@
 This strategy effectively provides a trade-off between the algorithm's performance and the precision of the results.
-The detailed steps of this approach are outlined in the pseudo-code presented in Algorithm \ref{algo1}.
+The detailed steps of this approach are outlined in the pseudo-code for \CMP presented in Algorithm \ref{algo1}.
 
@@
 
-\begin{algorithm}[htb]
-	\caption{Compensate(K)}
+\begin{algorithm}[b!]
+	\caption{CMP($K$)}
 	\label{algo1}
@@
 
-This algorithm has a worst case complexity bounded by $O(N \MILP(N,K))$, 
+CMP($K$) has a worst case complexity bounded by $O(N \MILP(N,K))$, 
 where $N$ is the number of nodes of the DNN, 

### 2024-01-27 Paper/proofs.tex
final v

@@
 
-			For an input $\vx$ and a subset $S$ of input nodes, we denote by $\boldsymbol{x}_S$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$.
-We use $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and
+			For an input $\vx$ and a subset $S$ of input nodes, we denote by 
+			$\boldsymbol{x}_S$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$. We use $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}$ and 
 			$\Val_{\boldsymbol{x}_I,\boldsymbol{x}_J} (z)=\Val_{\boldsymbol{x}}(z)$.
@@
 
-			\iffalse
-			\begin{lemma}
-				If $n$ is in the layer after $m$, then $S(n), S(m)$ are both defined
-				with $S(n) \neq 0$ and $W_{mn}\neq 0$, then $sign(W_{mn})S(n)=S(m)$.
-			\end{lemma}
-
-			\begin{proof}
-				This is proved in the first section of appendix. \qed
-			\end{proof}
-
-			\begin{lemma}\label{lem:subnetwork2}
-				$J \cup B_{open}$ forms a sub-network, denoted $D_J$.
-				That is, for $n \in B_{open}$, for every path $\rho$ from $m$ to $n$
-				either $m \in B_{open}\cup J$ or $weight(\rho)=0$. 
-				Further, $S$ is undefined on all nodes of $D_J$.
-			\end{lemma}
-
-			\begin{proof}
-				By contradiction, assume that there exists two nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in $D_J$ and $b \notin D_J$, then 
-				there is a path $\rho$ from an input node $a_i \notin J$ to $b$
-				 with nonzero weight. Then $\rho \cdot bc$ is a path from $a_i \notin J$ 
-				 to $c$ with non zero weight, a contradiction. \qed
-			\end{proof}
-			\fi
-
 			\begin{lemma} \label{lem:reach_max_2}
@@
 				$$\min_{\boldsymbol{x}_I} (\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)) =  \Val_{\boldsymbol{x}_I^{*},\boldsymbol{x}^0_J}(b).$$	
-
 			\end{lemma}
@@
 			$$\max(b)=\max_{\vx_J} \val_{\vx^{\star}_I,\vx_J}(b)$$
-			$$\min(b)=\max_{\vx_J} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
+			$$\min(b)=\min_{\vx_J} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
 			and for $S(b)=-1$:
@@
 			$$\max(b)=\max_{\vx_J} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
-			$$\min(b)=\max_{\vx_J} \val_{\vx^{\star}_I,\vx_J}(b)$$
+			$$\min(b)=\min_{\vx_J} \val_{\vx^{\star}_I,\vx_J}(b)$$
 			\end{corollary}
@@
 	Consider the DNN $D'$ with input nodes $J$, where all the 
-	edges from $m \in D_I$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_I}(m)$) for $n$ (we sum all these bias for a neuron $n$).
+	edges from $m \in D_I$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^*_I}(m)$) for $n$ (we sum all these bias for a neuron $n$).
 We denote $\val'$ values of nodes in this DNN $D'$.

### 2024-01-27 Paper/comppaths.tex
final VERSION

@@
 However, we can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
-Further, the set of nodes on which the sign funciton is defined is suffix-closed:
+Further, the set of nodes on which the sign function is defined is suffix-closed:
 
@@
 Typically, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the the strength of compensation.
+Instead, an interesting trade off between speed and accuracy is to set a threshold on the strength of compensation.
 Paths falling below this threshold are deemed to not warrant an individual integer variable due to insufficient compensatory strength.

### 2024-01-27 Paper/introduction.tex
final v
final VERSION

@@
 Deep neural networks have demonstrated remarkable capabilities, achieving \newline human-like or even superior performance across a wide range of tasks.
-However, their robustness is often compromised by their susceptibility to input perturbations.
+However, their robustness is often compromised by their susceptibility to input perturbations \cite{szegedy}.
 This vulnerability has catalyzed the verification community to develop various methodologies, each presenting a unique balance between completeness and computational efficiency \cite{katz2019marabou,Reluplex,deeppoly}.
@@
 While the verification engines are generic, the benchmarks usually focus on local robustness, i.e.
-given a DNN, an image and a small neighbourhood around this image,
-is it the case that all the images in the neighbourhood are classified in the same way.
+given a DNN, an image and a small neighbourhood around this image, is it the case that all the images in the neighbourhood are classified in the same way.
 While some quite large DNNs (e.g.
@@
 Perhaps, it is worth highlighting that these tools are  sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN Is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though the DNN is indeed robust.
-To dig further into their incompleteness,we first remark that high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
+To dig further into their incompleteness, we first remark that high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
 Therefore, inaccurate bounds leads to incompletness.
@@
 
-\item  Our second main contribution, delineated in Theorem \ref{th2}, answers this question, showing that this abstraction is fully accurate, in that the bounds computed in such a way for neuron $z$ correspond exactly to the mininmal and maximal values reachable by inputs of the DNN.
+\item  Our second main contribution, delineated in Theorem \ref{th2}, answers this question, showing that this abstraction is fully accurate, in that the bounds computed in such a way for neuron $z$ correspond exactly to the minimal and maximal values reachable by inputs of the DNN.
 Again, the prevalence of compensating paths in actual DNNs renders this algorithm computationally intensive because the number of binary variables is still too high.

### 2024-02-14 lipschitz/Lipitschz.tex
report

--- 2024-01-27 Paper/Paper_noProof.tex
@@
 	\begin{abstract}
-		Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally that they are correct, with an annual competition to compare them, etc.
-Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
-This allows e.g.
-to check local robustness around an input $\vx$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $\vx$.
-In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs.
-While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern verifiers, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.
 
-		In this paper, we analyse efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
-Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other.
-It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions.
-Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes.
-These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.
+		Deep Neural Networks (DNNs) verification has evolved into a robust field of research, furnished with a plethora of methodologies and tools designed for formal correctness verification.
+This area even boasts an annual competition to benchmark these tools.
+Formally, the question it addresses is whether a given DNN upholds a specified property across a set of input data.
+For instance, it can ascertain local robustness around an input $\vx$ by verifying if the i-th output neuron consistently demonstrates the highest weight amongst all output neurons within a certain vicinity of $\vx$.
+In recent years, the focus has shifted towards integrating various efficient techniques—such as branch and bound, multi-neuron encoding, and MILP encoding—to optimize the balance between speed and accuracy.
+Although modern verifiers can efficiently validate relatively large DNNs (with tens of thousands of neurons), the challenge persists, especially when dealing with certain DNNs, even smaller ReLU DNNs comprising hundreds of neurons, thereby highlighting the ongoing need for innovative methodologies.
+
+		In this paper, we analyse efficient algorithms  for verifying ReLU DNNs, examining abstractions like DeepPoly, Linear Programming, PRIMA, and various versions of Crown.
+We identify the primary cause of accuracy loss: {\em compensations}.
+Compensations occur when dual paths exist between a neuron pair, with one path carrying positive weights and the other negative, leading to a partial offset.
+However, accurately quantifying this offset is complex due to the ReLU activation functions.
+Leveraging this insight, we introduce a novel approach for achieving promising speed-accuracy trade-offs.
+This involves conducting numerous queries with a limited number of 'open' ReLU nodes (considering both linear modes) rather than the traditional approach of fewer queries with potentially many 'open' ReLU nodes.
+These findings not only present practical implications but also pave the way for various applications of the concept of compensating paths in the realm of DNN verification.
+
 	\end{abstract}
@@
 
-	Concerning the verification problem, we focus for simplicity on the usual local robustness question.
+	Concerning the verification problem, we focus on the well studied local-robustness question.
 Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.

### 2024-02-14 lipschitz/valabstraction.tex
lipschitz

--- 2024-01-27 Paper/valabstraction.tex
@@
 
-The following proposition shows that the LP abstraction is strictly more precise than the DeepPoly abstraction.
-This is attributed to the LP abstraction's simultaneous consideration of the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$.
-Conversely, the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.
+The following proposition shows that the LP abstraction refines the DeepPoly abstraction. 
+The difference between the LP and the DeepPoly abstractions is that LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.
 
@@
 	The function $\min(\beta \cdot a, x - \alpha (1-a))$ attains its maximum when $\beta \cdot a = x - \alpha (1-a)$, leading to the equation $(\beta - \alpha) a = x - \alpha$ and consequently $a = \frac{x - \alpha}{\beta-\alpha}$.
-This results in an upper bound of $\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$
-
+This results in an upper bound of $\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$ \qed
 \end{proof}

### 2024-02-14 lipschitz/Lipitschz.tex
debug

@@
 
-\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
+\title{Liptschiz}
 \date{}
@@
 
-		Deep Neural Networks (DNNs) verification has evolved into a robust field of research, furnished with a plethora of methodologies and tools designed for formal correctness verification.
-This area even boasts an annual competition to benchmark these tools.
-Formally, the question it addresses is whether a given DNN upholds a specified property across a set of input data.
-For instance, it can ascertain local robustness around an input $\vx$ by verifying if the i-th output neuron consistently demonstrates the highest weight amongst all output neurons within a certain vicinity of $\vx$.
-In recent years, the focus has shifted towards integrating various efficient techniques—such as branch and bound, multi-neuron encoding, and MILP encoding—to optimize the balance between speed and accuracy.
-Although modern verifiers can efficiently validate relatively large DNNs (with tens of thousands of neurons), the challenge persists, especially when dealing with certain DNNs, even smaller ReLU DNNs comprising hundreds of neurons, thereby highlighting the ongoing need for innovative methodologies.
-
-		In this paper, we analyse efficient algorithms  for verifying ReLU DNNs, examining abstractions like DeepPoly, Linear Programming, PRIMA, and various versions of Crown.
-We identify the primary cause of accuracy loss: {\em compensations}.
-Compensations occur when dual paths exist between a neuron pair, with one path carrying positive weights and the other negative, leading to a partial offset.
-However, accurately quantifying this offset is complex due to the ReLU activation functions.
-Leveraging this insight, we introduce a novel approach for achieving promising speed-accuracy trade-offs.
-This involves conducting numerous queries with a limited number of 'open' ReLU nodes (considering both linear modes) rather than the traditional approach of fewer queries with potentially many 'open' ReLU nodes.
-These findings not only present practical implications but also pave the way for various applications of the concept of compensating paths in the realm of DNN verification.
+		Local robustness is bad. We study a more global notion, lipsitcz constant.
 
@@
 
-	\input{introduction}
-
-	\input{relatedwork}
+	TO DO.
 
@@
 
-\input{comppaths}
-
-\input{experiments}
-
 \section{Conclusion}
-
-In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
-We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.
-
-Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation yields highly accurate results.
-Additionally, we observed that the runtime can be advantageous in certain scenarios, though not universally.
-This underscores the potential of compensating strength as an innovative and promising avenue for enhancing DNN verification.
- We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.
 
@@
 \bibliography{references}
-
-\newpage
-
-\appendix
-
-\input{proofs}
 

### 2024-02-16 Reports/tech_report1.tex
Tech Report draft

\documentclass{llncs}
\pagestyle{plain}

%\usepackage[latin9]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tabularx}
\captionsetup{compatibility=false}
% \usepackage{esint}
\usepackage{array}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{pgfplots}
\usepackage{url}
\usepackage{tikz}
\usepackage{calc}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vy}{\boldsymbol{y}}
\newcommand{\vW}{\boldsymbol{W}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vb}{\boldsymbol{bias}}
\newcommand{\val}{{\textrm{value}}}
\newcommand{\Val}{{\textrm{value}}}
\newcommand{\MILP}{{\textrm{MILP}}}
\newcommand{\LP}{{\textrm{LP}}}

\newcommand{\UB}{\mathrm{UB}}
\newcommand{\LB}{\mathrm{LB}}
\newcommand{\ub}{\mathrm{ub}}
\newcommand{\lb}{\mathrm{lb}}
\newcommand{\B}{\mathrm{B}}

\newcommand{\CMP}{{\textrm{CMP}}\ }

\newcommand{\toolname}{\ensuremath{\mathsf{Comp}}}

%\usepackage{amsmath, amsthm, amssymb, amsfonts}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{corollary}{Corollary}
%\theoremstyle{definition}
%\newtheorem{definition}{Definition}

\newcommand{\ReLU}{\mathrm{ReLU}}

\title{Technical Report}
\date{}

\begin{document}

\maketitle

\section*{Introduction}

Only formal experiments will be recorded. Pre-debugging will not be recorded unless necessary.

\section{February 15 experiments}

\subsection{Rerun the gamma test}

This experiment is to rerun the interrupted experiment on14 February night.

\vspace*{1ex}

The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound.py|. And the output file name is \verb*|Gamma_V0p2_all_layers_MILP_usebounds1.txt|. It is to compute the gamma ($\gamma$). It is based on the new hyperplane constraints, use MILP model to compute the gamma from layer 5 to layer 5.

\subsubsection*{Parameters.}

\begin{itemize}
	\item \emph{Experiments Id}: 021500102024

	\item\emph{Network:} 6x100 MNIST normal.

	\item\emph{Image:} 144 (meaningless).

	\item\emph{Epsilon $\varepsilon$:} 0.001.

	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.

	\item\emph{Open $\ReLU$ number:} 17 for layer 3, 23 for layer 5, 35 for layer 7 and 9.

	\item\emph{Processes:} 20 processes in parallel.

	\item\emph{Read binary files:} \verb*|dict_bounds_gurobi_alphabeta_2024021401.b|; this file stores the alpha beta of nodes of all layers for the same network. \verb*|dict_bounds_gurobi_gamma_2024021501.b|; this file stores the gamma of nodes up to layer 3, computed by the same code.
\end{itemize}

\subsubsection*{Technical Sketch.}

The new group of hyperplane constraints is as follows: \begin{align*}
	&\hat{x}_i - \hat{x}_i' \leq \frac{1}{2} (x_i-x_i') + \frac{1}{2} \gamma_i\\
	&\hat{x}_i' - \hat{x}_i \leq \frac{1}{2} (x_i'-x_i) + \frac{1}{2}\gamma_i
\end{align*} Here, $x_i$ and $x_i'$ are the two variables corresponding to a node $i$ in previous layer, and $\gamma_i$ is the $\gamma$ of node $i$ computed in previous layer; $\hat{x}_i,\hat{x}_i'$ are variables after $\ReLU$ function.

One characteristic is that the constraints do not reply on $\alpha$ or $\beta$. So even with $\alpha,\beta$ of very poor quality, this group of constraints can work.

This running recover the last layer: in early experiments, the last layer is modified to 9 nodes. Now it is recovered to 10 nodes. Because of this, the Bootstrap data of last layer is computed.

\subsubsection*{Results.}

No result.

It seems that open-23-node for layer 5 with new hyperplane constraints is not good, at least with respect to the time cost: most nodes run out of 600s x 12, and this means we need 10 hours to do the whole layer 5.

Let's try a fewer number of open $\ReLU$ nodes.

\subsection{Rerun the gamma test: layer 5 with changed parameters}

This experiments shares some setting as previous one.

\subsubsection*{Parameters.}

\begin{itemize}
	\item\emph{Experiments Id}: 021500202024

\item\emph{Network:} 6x100 MNIST normal.

\item\emph{Image:} 144 (meaningless).

\item\emph{Epsilon $\varepsilon$:} 0.001.

\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.

\item\emph{Open $\ReLU$ number:} 17 for layer 5.

\item\emph{Processes:} 20 processes in parallel.

\item\emph{Read binary files:} \verb*|dict_bounds_gurobi_alphabeta_2024021401.b|; this file stores the alpha beta of nodes of all layers for the same network. \verb*|dict_bounds_gurobi_gamma_2024021501.b|; this file stores the gamma of nodes up to layer 3, computed by the same code.
\end{itemize}

\subsubsection*{Technical Sketch.}

The same as previous experiments.

\subsubsection*{Results.}

\begin{itemize}
	\item \emph{Log:} \verb*|Gamma_V0p2_all_layers_MILP_usebounds1.txt|

	\item \emph{Total time:} 4779s.

	\item \emph{Key results:} $\gamma$ for layer 5 is 0.9922133701854773.
\end{itemize}

Open 17 nodes is OK, but we can still increase the number of open ReLU nodes for layer 5. Perhaps open 20 nodes is a good choice.

\subsection{Rerun the gamma test: layer 7,9 with changed parameters}

This experiments shares some setting as previous ones.

\subsubsection*{Parameters.}

\begin{itemize}
	\item\emph{Experiments Id}: 021500302024

	\item\emph{Network:} 6x100 MNIST normal.

	\item\emph{Image:} 144 (meaningless).

	\item\emph{Epsilon $\varepsilon$:} 0.001.

	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.

	\item\emph{Open $\ReLU$ number:} 20 for layer 7 and 9.

	\item\emph{Processes:} 20 processes in parallel.

	\item\emph{Read binary files:} \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_15_11_40_01.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 5). 
\end{itemize}

\subsubsection*{Technical Sketch.}

The same as Experiments 021500202024.

\subsubsection*{Results.}

\begin{itemize}
	\item \emph{Log:} \verb*|Gamma_V0p2_all_layers_MILP_usebounds2.txt|

	\item \emph{Total time:} 14985.4s.

	\item \emph{Key results:} $\gamma$ for layer 7 is 4.177719108178739; $\gamma$ for layer 9 is 16.878953032158446.
\end{itemize}

\subsection{Gamma test for robust 5x100 using MILP}

This experiment is to rerun the interrupted experiment on14 February night.

\vspace*{1ex}

The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_DiffAI.py|. The output file name is \verb*|Gamma_V0p2_all_layers_5x100_robust_MILP.txt| and \verb*|Diamond_record_5_100_dictionary_with_end_layer9_2024_02_15_19_29_17.b|. It is to compute the gamma ($\gamma$). It is based on the new hyperplane constraints, use MILP model to compute the gamma of robust 5x100 from layer 1 to layer 9.

\subsubsection*{Parameters.}

\begin{itemize}
	\item \emph{Experiments Id}: 021500402024

	\item\emph{Network:} 6x100 MNIST robust.

	\item\emph{Image:} 144 (meaningless).

	\item\emph{Epsilon $\varepsilon$:} 0.001.

	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.

	\item\emph{Open $\ReLU$ number:} 17 for layer 3, 23 for layer 5, 35 for layer 7 and 9.

	\item\emph{Processes:} 20 processes in parallel.

	\item\emph{Read binary files:} No read file. I planned to read alpha-beta data, but the pre-computed alpha-beta data seems to have some problems, so I use the version that will compute the alpha beta during the running.
\end{itemize}

\subsubsection*{Technical Sketch.}

The same as other experiments today.

\subsubsection*{Results.}

\begin{itemize}
	\item \emph{Log:} \verb*|Gamma_V0p2_all_layers_5x100_robust_MILP.txt|

	\item \emph{Total time:} 19270.8s.

	\item \emph{Key results:} $\gamma$ for layer 1 to layer 9: 0.006884580440378905, 0.014342863034246162,
	0.034691083484486775, 0.09665049332723069,
	0.28105516604910674
\end{itemize}

\section{February 16 experiments}

\subsection{Rerun the gamma test: layer 3 with new settings}

\subsubsection*{Parameters.}

\begin{itemize}
	\item\emph{Experiments Id}: 021600102024

	\item\emph{Network:} 6x100 MNIST normal.

	\item\emph{Image:} 144 (meaningless).

	\item\emph{Epsilon $\varepsilon$:} 0.001.

	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.

	\item\emph{Open $\ReLU$ number:}

	\item\emph{Processes:} 20 processes in parallel.

	\item\emph{Read binary files:} 
\end{itemize}

\subsubsection*{Technical Sketch.}

The same as Feb 15's experiments.

\subsubsection*{Results.}

\end{document}

### 2024-02-16 Reports/tech_report1.tex
Update report

@@
 
+\subsubsection*{Results.} No meaningful result. The $\gamma$ is still 0.24007008332521998.
+
+\subsection{Seek the best open ReLU number for layer 3 for normal 5x100}
+
+This experiment is to find the best open ReLU number for layer 3 normal 5x100 with new hyperplane constraints: previous open 17 node is based on old constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py|.
+And the partial output file name is \verb*|Gamma_5x100_normal_layer3_seek_openrelu.txt|.
+It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 3 with different open ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 021600202024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 15,18,21,24,27 ReLU nodes for each node.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_15_11_40_01.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 5).
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+Most is the same as Feb 15's experiments.
+
 \subsubsection*{Results.}
 
+Not finished before stop, but it is very obvious that 21 is the best among all 5 cases.
+
 \end{document}

### 2024-02-17 Reports/tech_report1.tex

@@
 
+\subsection{Seek the best open ReLU number for layer 3 for normal 5x100}
+
+This experiment is to find the best open ReLU number for layer 5 normal 5x100 with new hyperplane constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py|.
+And the partial output file name is \verb*|Gamma_5x100_normal_layer5_seek_openrelu.txt|.
+It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 021600302024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 17,20,23,26,29 ReLU nodes for each node.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_15_11_40_01.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 5).
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+Most is the same as Feb 15's experiments.
+
+\subsubsection*{Results.}
+
 \end{document}

### 2024-02-19 Reports/tech_report1.tex
update tests

@@
 
-\subsection{Seek the best open ReLU number for layer 3 for normal 5x100}
+\subsection{Seek the best open ReLU number for layer 35 for normal 5x100}
 
@@
 
+\begin{itemize}
+	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer5_seek_openrelu.txt|
+
+	\item \emph{Total time:} 61891s.
+
+	\item \emph{Key results:} $\gamma$ for different open number are 0.9664584160601942,
+	0.9480190853777704,
+	0.969433533659244,
+	0.9832281749149849,
+	0.9884851087698833. This means open 20 is the best among 5 choices.
+
+	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_17_21_56_00.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_17_21_56_00.b|.
+The first stores the gamma up to layer 3, and the second stores tests result of layer 5 in addition.
+\end{itemize}
+
+\section{February 17-18 experiments}
+
+\subsection{Seek the best open ReLU number for layer 7 for normal 5x100}
+
+This experiment is to find the best open ReLU number for layer 7 normal 5x100 with new hyperplane constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py| (a copy for it is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_layer7.py|).
+And the partial output file name is \verb*|Gamma_5x100_normal_layer7_seek_openrelu.txt|.
+It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 021700202024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 20, 24, 28, 32, 36 ReLU nodes for each node.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 3 and is newly-computed).
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+Most is the same as Feb 15's experiments.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer7_seek_openrelu.txt|
+
+	\item \emph{Total time:} 40866s.
+
+	\item \emph{Key results:} $\gamma$ for different open number are 3.924847266202133,
+	3.879966384915862,
+	3.843735078541843,
+	3.834229593178003,
+	3.816831654178999. This means open 36 is the best among 5 choices.
+
+	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_18_22_11_50.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_18_22_11_50.b|.
+The first stores the gamma up to layer 5, and the second stores tests result of layer 7 in addition.
+\end{itemize}
+
 \end{document}

### 2024-02-19 Reports/tech_report1.tex
update report

@@
 This experiment is to find the best open ReLU number for layer 5 normal 5x100 with new hyperplane constraints.
+In addition, this test also compute the gamma data for layer 3 based on previous found best open number.
 
@@
 This experiment is to find the best open ReLU number for layer 7 normal 5x100 with new hyperplane constraints.
+In addition, this test also compute the gamma data for layer 5 based on previous found best open number.
 
@@
 \begin{itemize}
-	\item\emph{Experiments Id}: 021700202024
+	\item\emph{Experiments Id}: 021700102024
 
@@
 
+\subsection{Randomly choose open ReLU for layer 3 for normal 5x100}
+
+This experiment is to test the random open ReLU nodes for layer 3 normal 5x100 with new hyperplane constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py| (a copy for it is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_random.py|).
+And the partial output file name is \verb*|Gamma_5x100_normal_layer3_seek_openrelu_random.txt|.
+It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 3 with different open ReLU numbers and nodes chosen randomly.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 021700202024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 15,18,21,24,27 ReLU nodes for each node, but choose open nodes randomly.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 3 and is newly-computed).
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+Most is the same as Feb 15's experiments.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer3_seek_openrelu_random.txt|
+
+	\item \emph{Total time:} 14072.
+
+	\item \emph{Key results:} $\gamma$ for different open number are 0.28773090140361735,
+	0.2804030901915068,
+	0.2733447337312936,
+	0.26386494446982417,
+	0.2613191792848188. This is much worse than open node by our method.
+
+\end{itemize}
+
 \end{document}

### 2024-02-20 lipschitz/valabstraction.tex
add formula
test plots

@@
 \end{proof}
+
+\subsubsection*{Constraints for $\gamma$}
+
+We could get the following constraints for $\gamma$, using $y_i$ and $\hat{y}_i$ to denote the $x_i-x_i'$ and $\hat{x}_i-\hat{x}_i'$:\begin{align*}
+	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
+	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
+\end{align*} where $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-\hat{x}_i$.
+
+\begin{tikzpicture}[
+	declare function={
+		f(\x,\y)=max((\x+\y),0)-max(\x,0);
+	}]
+	\begin{axis}[axis lines=center,
+		axis on top,
+		set layers=default,
+		xrange=-3:3,
+		yrange=-2:2,
+		unit vector ratio=1 1 1,% <- HERE (taken from Phelype Oleinik's deleted answer)
+		scale=3 %<- added to compensate for the downscaling
+		% resulting from unit vector ratio=1 1 1
+		]
+		\addplot3[
+		domain=-3:3,
+		domain y=-1:1,
+		samples=40,
+		samples y=40,
+		surf,
+		] {f(\x,\y)};
+	\end{axis}
+\end{tikzpicture}

### 2024-02-20 lipschitz/valabstraction.tex
update plots

@@
 
-\begin{tikzpicture}[
-	declare function={
-		f(\x,\y)=max((\x+\y),0)-max(\x,0);
-	}]
+\hspace*{-20ex}
+
+\begin{tikzpicture}
 	\begin{axis}[axis lines=center,
@@
 				set layers=default,
-		xrange=-3:3,
+				xrange=-5:5,
 				yrange=-2:2,
-		unit vector ratio=1 1 1,% <- HERE (taken from Phelype Oleinik's deleted answer)
-		scale=3 %<- added to compensate for the downscaling
-		% resulting from unit vector ratio=1 1 1
+				unit vector ratio=1 1 1, scale=1.5,
+				view={45}{40},
 				]
-		\addplot3[
-		domain=-3:3,
-		domain y=-1:1,
-		samples=40,
-		samples y=40,
-		surf,
-		] {f(\x,\y)};
+		\addplot3[	surf,] 
+		coordinates {
+	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
+		};
+
+		\addplot3[	surf,	] 
+		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
+		};
+
+		\addplot3[	surf,	] 
+		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
+		};
+
+			\addplot3[	surf,	] 
+		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
+		};
+
 	\end{axis}
 \end{tikzpicture}
+
+%\begin{tikzpicture}[
+%	declare function={
+%		f(\x,\y)=max((\x+\y),0)-max(\x,0);
+%	}]
+%	\begin{axis}[axis lines=center,
+%		axis on top,
+%		set layers=default,
+%		xrange=-3:3,
+%		yrange=-2:2,
+%		unit vector ratio=1 1 1,% <- HERE (taken from Phelype Oleinik's deleted answer)
+%		scale=3 %<- added to compensate for the downscaling
+%		% resulting from unit vector ratio=1 1 1
+%		]
+%		\addplot3[
+%		domain=-3:3,
+%		domain y=-1:1, surf,
+%		samples=40,
+%		samples y=40,
+%		] {f(\x,\y)};
+%	\end{axis}
+%\end{tikzpicture}

### 2024-02-20 lipschitz/valabstraction.tex
update plots

@@
 \begin{tikzpicture}
-	\begin{axis}[axis lines=center,
-				axis on top,
+	\begin{axis}[	axis on top,
 				set layers=default,
@@
 				unit vector ratio=1 1 1, scale=1.5,
-				view={45}{40},
+				view={60}{50},
 				]
-		\addplot3[	surf,] 
+		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
 		coordinates {
@@
 
-		\addplot3[	surf,	] 
+		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
 		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
@@
 
-		\addplot3[	surf,	] 
+		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
 		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
@@
 
-			\addplot3[	surf,	] 
+			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
+		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
+		};
+
+	\end{axis}
+\end{tikzpicture}
+
+\hspace*{-20ex}
+
+\begin{tikzpicture}
+	\begin{axis}[	axis on top,
+		set layers=default,
+		xrange=-5:5,
+		yrange=-2:2,
+		unit vector ratio=1 1 1, scale=1.5,
+		view={35}{14},
+		]
+		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
+		coordinates {
+			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
+		};
+
+		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
+		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
+		};
+
+		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
+		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
+		};
+
+		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
 		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)

### 2024-02-20 lipschitz/valabstraction.tex
update plots

@@
 \begin{tikzpicture}
-	\begin{axis}[	axis on top,
+	\begin{axis}[	axis on top, xlabel = \(x_i\),
+		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
 				set layers=default,
-				xrange=-5:5,
-				yrange=-2:2,
+	xmax = 4, xmin = -4,
+ymax = 1, ymin = -1,		
+zmax = 1, zmin = -1,
 				unit vector ratio=1 1 1, scale=1.5,
@@
 \begin{tikzpicture}
-	\begin{axis}[	axis on top,
+	\begin{axis}[	axis on top, xlabel = \(x_i\),
+		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
 		set layers=default,
-		xrange=-5:5,
-		yrange=-2:2,
+				xmax = 4, xmin = -4,
+		ymax = 1, ymin = -1,		
+				zmax = 1, zmin = -1,
 		unit vector ratio=1 1 1, scale=1.5,

### 2024-02-20 lipschitz/valabstraction.tex
update plots

--- 2024-02-20 lipschitz/valabstraction.tex
@@
 
-\hspace*{-20ex}
+The following plot will show the above constraints:
 
 \begin{tikzpicture}
-	\begin{axis}[	axis on top,
+	\begin{axis}[
+		xlabel={$y_i$},
+		ylabel={$\hat{y}_i$},
+		xmin=-2, xmax=2,
+		ymin=-2, ymax=2,
+		axis lines=center,
+		samples=100, 
+	 unit vector ratio=1 1 1, scale=1.5, xtick   = {-2,2},
+	 xticklabels = {$-\gamma_i$,$\gamma_i$},
+	 yticklabels = {},
+		]
+		\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
+		\addplot[blue, thick] {0};
+
+			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
+
+			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.45, 1.7) {};
+	\end{axis}
+\end{tikzpicture}
+
+\vspace*{10ex}
+
+\begin{tikzpicture}
+	\begin{axis}[	axis on top, xlabel = \(x_i\),
+		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
 				set layers=default,
-				xrange=-5:5,
-				yrange=-2:2,
+	xmax = 4, xmin = -4,
+ymax = 1, ymin = -1,		
+zmax = 1, zmin = -1,
 				unit vector ratio=1 1 1, scale=1.5,
-				view={60}{50},
+				view={60}{50}, ytick   = {-1,0,1},
+				yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
+				xticklabels = {$0$}, ztick   = {-1,0,1},
+				zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
 				]
@@
 
-\hspace*{-20ex}
-
 \begin{tikzpicture}
-	\begin{axis}[	axis on top,
+	\begin{axis}[	axis on top, xlabel = \(x_i\),
+		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
 		set layers=default,
-		xrange=-5:5,
-		yrange=-2:2,
-		unit vector ratio=1 1 1, scale=1.5,
+				xmax = 4, xmin = -4,
+		ymax = 1, ymin = -1,		
+				zmax = 1, zmin = -1,
+		unit vector ratio=1 1 1, scale=1.5,  ytick   = {-1,0,1},
+		yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
+		xticklabels = {$0$}, ztick   = {-1,0,1},
+		zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
 		view={35}{14},

### 2024-02-20 lipschitz/valabstraction.tex
update plots

@@
 
+The relation between $y_i$, $x_i$ and $\hat{y}_i$ is $$\hat{y}_i = \ReLU(x_i+y_i)-\ReLU(x_i).$$ And its plots is as follows:
+
+\hspace*{-10ex}
 \begin{tikzpicture}
@@
 zmax = 1, zmin = -1,
-				unit vector ratio=1 1 1, scale=1.5,
+				unit vector ratio=1 1 1, scale=3,
 				view={60}{50}, ytick   = {-1,0,1},
@@
 
+		\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
+					\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
+
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
+		\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
+
 	\end{axis}
@@
 
+\hspace*{-15ex}
 \begin{tikzpicture}
@@
 				zmax = 1, zmin = -1,
-		unit vector ratio=1 1 1, scale=1.5,  ytick   = {-1,0,1},
+		unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
 		yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
@@
 		};
+
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
+		\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
+
+		\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
+		\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
 

### 2024-02-20 lipschitz/valabstraction.tex
update plots

@@
 		samples=100, 
-	 unit vector ratio=1 1 1, scale=1.5, xtick   = {-2,2},
+	 unit vector ratio=1 1 1, scale=1, xtick   = {-2,2},
 	 xticklabels = {$-\gamma_i$,$\gamma_i$},
@@
 
+		\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
 			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
 
-			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.45, 1.7) {};
+				\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
+			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
 	\end{axis}
@@
 
-\vspace*{10ex}
-
-The relation between $y_i$, $x_i$ and $\hat{y}_i$ is $$\hat{y}_i = \ReLU(x_i+y_i)-\ReLU(x_i).$$ And its plots is as follows:
+The relation between $y_i$, $x_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x_i+y_i)-\ReLU(x_i).$ And its plots is as follows:
 

### 2024-02-20 lipschitz/valabstraction.tex
update plots

@@
 	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
-\end{align*} where $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-\hat{x}_i$.
+\end{align*} where $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
 
@@
 
-The relation between $y_i$, $x_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x_i+y_i)-\ReLU(x_i).$ And its plots is as follows:
+The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$ And its plots is as follows:
 
@@
 \begin{tikzpicture}
-	\begin{axis}[	axis on top, xlabel = \(x_i\),
+	\begin{axis}[	axis on top, xlabel = \(x'_i\),
 		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),

### 2024-02-20 Reports/tech_report1.tex

@@
 
-\subsection{Seek the best open ReLU number for layer 35 for normal 5x100}
+\subsection{Seek the best open ReLU number for layer 5 for normal 5x100}
 
@@
 
-	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_17_21_56_00.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_17_21_56_00.b|.
+	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_16_15_24_52.b|.
 The first stores the gamma up to layer 3, and the second stores tests result of layer 5 in addition.
@@
 
+\section{February 19 experiments}
+
+\subsection{Randomly choose open ReLU for layer 5 for normal 5x100}
+
+This experiment is to test the random open ReLU nodes for layer 5 normal 5x100 with new hyperplane constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_random.py| (a copy for it is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_random2.py|).
+And the partial output file name is \verb*|Gamma_5x100_normal_layer5_seek_openrelu_random.txt|.
+It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers and nodes chosen randomly.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 021900102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 17,20,23,26,29 ReLU nodes for each node, but choose open nodes randomly.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 3 and is newly-computed).
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+Most is the same as Feb 15's experiments.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer5_seek_openrelu_random.txt| (from line 5776).
+
+	\item \emph{Total time:} 11346.9s.
+
+	\item \emph{Key results:} $\gamma$ for different open numbers are 1.1082117992614573    open 17
+	1.0902650122404043     20
+	1.0854613578404746     23
+	1.0692115311756667     26
+	1.055639230561528        29. This is much worse than open node by our method.
+
+\end{itemize}
+
 \end{document}

### 2024-02-21 lipschitz/valabstraction.tex
update one possible case of constraints

@@
 
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$ And its plots is as follows:
+The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
+
+We can use the following extra constraints (besides 4 constraints about $\hat{x}_i'=\ReLU(x_i')$) to build this relation:\begin{align*}
+	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
+	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(1-a)\alpha_i \\
+	& x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i
+\end{align*}And its plots is as follows:
 

### 2024-02-21 lipschitz/valabstraction.tex
fix typos
update

--- 2024-02-20 lipschitz/valabstraction.tex
@@
 
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$ And its plots is as follows:
+The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
+
+We can use the following extra constraints (besides 4 constraints about $\hat{x}_i'=\ReLU(x_i')$) to build this relation:
+
+\vspace*{-11ex}
+
+\begin{align*}
+	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
+	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(1-a)\alpha_i \\
+\end{align*}
+
+\vspace*{-10ex}
+
+Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
+
+The following two plots show its shape:
 

### 2024-02-22 Reports/tech_report1.tex
fix mistakes

@@
 
+\section{February 21 experiments}
+
+\subsection{Find best open ReLU for layer 3 for normal 5x100, new pure y-constraints}
+
+This experiment is to find the best open ReLU number for layer 3 normal 5x100 with new pure-y constraints constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|.
+And the partial output file name is \verb*|DL_V0p3_find_open_number_layer3_0.txt,DL_V0p3_find_open_number_layer3_1.txt,DL_V0p3_find_open_number_layer3_2.txt,DL_V0p3_find_open_number_layer3_3.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 3 with different open ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 022100102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 20,23,26,29,32 ReLU nodes for each node.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network. 
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+We will use the following new constraints, and keep the old variables and constraints (will not use them at present).
+
+The new constraints are: \begin{align*}
+	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
+	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
+\end{align*} Here, $y_i$ is the variable that represents $x_i-x'_i$, $\hat{y}_i$ represents $\hat{x}_i-\hat{x}'_i$, $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_find_open_number_layer3_0.txt,DL_V0p3_find_open_number_layer3_1.txt,DL_V0p3_find_open_number_layer3_2.txt,DL_V0p3_find_open_number_layer3_3.txt|.
+
+	\item \emph{Total time:}
+
+	\item \emph{Key results:} Due to some mistakes we only have open to 29 nodes. $\gamma$ for different open numbers are
+
+	0.2280277192602802          0.2303032016837368         open 20
+
+	0.2168232231501058          0.21899023640990567      open 23
+
+	0.20544377026809135        0.2103601628177343        open 26
+
+     0.19510091588084752   0.20836893269039397   open 29
+
+	 This is much better than previous methods.
+
+\end{itemize}
+
+\subsection{Compute the gamma of layer 3 for normal 5x100, new pure y-constraints}
+
+This experiment is to  compute the gamma of layer 3 normal 5x100 with new pure-y constraints constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|.
+And the output file name is \verb*|DL_V0p3_layer3_open_27.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 3 with open 27 ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 022100102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 27 ReLU nodes for each node.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network. 
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+We will use the following new constraints, and keep the old variables and constraints (will not use them at present).
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer3_open_27.txt|.
+
+	\item \emph{Total time:} 30740s.
+
+	\item \emph{Key results:} The average gamma of this layer is:  0.20506045995399397
+
+	The average solution for gamma of this layer is:  0.1998876293451762
+
+	\item  \emph{Binary file:} \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_21_13_58_49.b|. This file stores the gammas in this test.
+
+\end{itemize}
+
 \end{document}

### 2024-02-22 lipschitz/valabstraction.tex
fix mistakes

@@
 	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(1-a)\alpha_i \\
+	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
 \end{align*}

### 2024-02-23 Reports/tech_report1.tex
update report

@@
 
-	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+	\item\emph{Processes:} 20 processes in parallel.
 
@@
 
+\subsection{Compute the gamma of layer 5 for normal 5x100, new pure y-constraints}
+
+This experiment is to  compute the gamma of layer 5 normal 5x100 with new pure-y constraints constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|.
+And the output file name is \verb*|DL_V0p3_layer5_open_33_node_1.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 5 with open 33 ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 022200102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 33 ReLU nodes for each node.
+
+	\item\emph{Processes:} 20 processes in parallel.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_21_13_58_49.b|; this file stores all alpha beta gamma of nodes of all layers for the same network, and the gamma of layer 3 that is computed by new version.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+We will use the following new constraints, and keep the old variables and constraints (will not use them at present).
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer5_open_33_node_1.txt|.
+
+	\item \emph{Total time:} 26809.2s.
+
+	\item \emph{Key results:} The average gamma of this layer is:  0.7776875638377869
+
+	The average solution for gamma of this layer is:  0.7549862461111381
+
+	\item  \emph{Binary file:} \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_23_09_28_54.b|. This file stores the gammas in this test.
+
+\end{itemize}
+
 \end{document}

### 2024-02-23 lipschitz/valabstraction.tex
pptx

--- 2024-02-21 lipschitz/valabstraction.tex
@@
 
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
+The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$ And its plots is as follows:
 
-We can use the following extra constraints (besides 4 constraints about $\hat{x}_i'=\ReLU(x_i')$) to build this relation:\begin{align*}
-	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(1-a)\alpha_i \\
-	& x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i
-\end{align*}And its plots is as follows:
-
+\iffalse
 \hspace*{-10ex}
@@
 \end{tikzpicture}
+\fi
 

### 2024-02-23 lipschitz/valabstraction.tex
update another group of constraints

--- 2024-02-22 lipschitz/valabstraction.tex
@@
 
-\vspace*{-11ex}
-
 \begin{align*}
@@
 
-\vspace*{-10ex}
-
 Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
 
-The following two plots show its shape:
+A more direct way to establish the constraints is as follows: \begin{align*}
+	& x_i \leq a\beta_i \quad\wedge \quad x_i\geq (1-a)\alpha_i\\	
+	& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
+	&\hat{y}_i \leq -(a+a')\gamma_i \quad\wedge \quad	\hat{y}_i \geq (a+a')\gamma_i \\
+	&	\hat{y}_i \leq y_i+(2-a-a')\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (2-a-a')\gamma_i \\
+	&	\hat{y}_i \leq -x_i+(1+a-a')\beta_i \quad\wedge \quad	\hat{y}_i \geq -x_i+(1+a-a')\alpha_i \\
+	&	\hat{y}_i \leq y_i+x_i+(1+a'-a)\beta_i \quad\wedge \quad	\hat{y}_i \geq y_i+x_i+(1+a'-a)\alpha_i \\
+\end{align*}The following two plots show its shape:
 

### 2024-02-23 lipschitz/valabstraction.tex
update constraints

--- 2024-02-22 lipschitz/valabstraction.tex
@@
 
-\vspace*{-10ex}
-
 Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
 
-The following two plots show its shape:
+A more direct way to establish the constraints is as follows: \begin{align*}
+	& y+x'_i \leq a\beta_i \quad\wedge \quad y+x'_i\geq (1-a)\alpha_i\\	
+	& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
+	&\hat{y}_i \leq -a\gamma_i \quad\wedge \quad	\hat{y}_i \geq a'\gamma_i \\
+	&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
+	&	\hat{y}_i \leq -x'_i+(1-a)\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
+	&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+(1-a')(-\beta_i) \\
+\end{align*}The following two plots show its shape:
 

### 2024-02-23 lipschitz/valabstraction.tex
fix mistakes

@@
 	&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-	&	\hat{y}_i \leq -x'_i+(1-a)\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-	&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+(1-a')(-\beta_i) \\
+	&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
+	&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
 \end{align*}The following two plots show its shape:

### 2024-02-23 lipschitz/valabstraction.tex
fix typos

@@
 A more direct way to establish the constraints is as follows: \begin{align*}
-	& y+x'_i \leq a\beta_i \quad\wedge \quad y+x'_i\geq (1-a)\alpha_i\\	
+	& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
 	& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\

### 2024-02-23 lipschitz/valabstraction.tex
update

--- 2024-02-23 lipschitz/valabstraction.tex
@@
 
-Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
+Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i. $
 
 A more direct way to establish the constraints is as follows: \begin{align*}
-	& y+x'_i \leq a\beta_i \quad\wedge \quad y+x'_i\geq (1-a)\alpha_i\\	
+	& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
 	& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-	&\hat{y}_i \leq -a\gamma_i \quad\wedge \quad	\hat{y}_i \geq a'\gamma_i \\
+	&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
 	&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\

### 2024-02-26 Reports/tech_report1.tex
update report

@@
 
+\subsection{Find best open ReLU for layer 5 for normal 5x100, new pure y-constraints}
+
+This experiment is to find the best open ReLU number for layer 5 normal 5x100 with new pure-y constraints constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|.
+And the partial output file name is \verb*|DL_V0p3_layer5_find_best_number.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 022100202024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 25,28,31, 34, 37 ReLU nodes for each node.
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_21_13_58_49.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 3 using the latest method.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+We will use the following new constraints, and keep the old variables and constraints (will not use them at present).
+
+The new constraints are: \begin{align*}
+	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
+	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
+\end{align*} Here, $y_i$ is the variable that represents $x_i-x'_i$, $\hat{y}_i$ represents $\hat{x}_i-\hat{x}'_i$, $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
+
+\subsubsection*{Results.}
+
+Not completed. So here is the summary of the partial results.
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer5_find_best_number.txt|.
+
+	\item \emph{Total time:}
+
+	\item \emph{Key results:}  $\gamma$ for different open numbers are
+
+	Open 25 
+	Bound: 0.8382390973953313 , Solution: 0.8321314445556547 , Time: 306.77194131612777 2335.830235481262
+
+	Open 28 
+	Bound: 0.8147201914056824 , Solution: 0.8054690328829098 , Time: 1176.2175419330597 7200.522756814957
+
+	Open 31 
+	Bound: 0.7963056225858687 , Solution: 0.7818023933666046 , Time: 3502.1967465043067 7200.723284482956
+
+	Open 34 
+	Bound: 0.7945120282557274 , Solution: 0.7582789017028382 , Time: 5760.061596000194 7200.779401540756
+
+	Open 37 (not finished) 
+	Bound: 0.8022403621011988 , Solution: 0.7360574057164293 , Time: 4956.505218315125 7200.661721229553
+
+	It seems that 34 is the best. In following experiments, we use open 33 node.
+
+\end{itemize}
+
 \subsection{Compute the gamma of layer 5 for normal 5x100, new pure y-constraints}
@@
 \begin{itemize}
-	\item\emph{Experiments Id}: 022200102024
+	\item\emph{Experiments Id}: 022200302024
 
@@
 
+\section{February 22-25 experiments}
+
+\subsection{Find best open ReLU for layer 5 for normal 5x100, new pure y-constraints}
+
+This experiment is to find the best open ReLU number for layer 7 normal 5x100 with new pure-y constraints constraints.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|.
+And the partial output file name is \verb*|DL_V0p3_layer7_find_Best_open_number.txt,DL_V0p3_layer7_find_Best_open_number2.txt,DL_V0p3_layer7_find_Best_open_number3.txt,DL_V0p3_layer7_find_Best_open_number4.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with different open ReLU numbers.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 022500102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 30, 33, $\cdots$, 72 ReLU nodes for each node (in 3 tests).
+
+	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_23_09_28_54.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+We will use the following new constraints, and keep the old variables and constraints (will not use them at present).
+
+The new constraints are: \begin{align*}
+	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
+	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
+\end{align*} Here, $y_i$ is the variable that represents $x_i-x'_i$, $\hat{y}_i$ represents $\hat{x}_i-\hat{x}'_i$, $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
+
+\subsubsection*{Results.}
+
+Not completed. So here is the summary of the partial results.
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer7_find_Best_open_number.txt,DL_V0p3_layer7_find_Best_open_number2.txt,DL_V0p3_layer7_find_Best_open_number3.txt,DL_V0p3_layer7_find_Best_open_number4.txt|.
+
+	\item \emph{Total time:}
+
+	\item \emph{Key results:}  $\gamma$ for different open numbers are
+
+	It seems that 34 is the best. In following experiments, we use open 33 node.
+
+\end{itemize}
+
 \end{document}

### 2024-02-28 Reports/tech_report1.tex
update
update report

@@
 
-\subsection{Find best open ReLU for layer 5 for normal 5x100, new pure y-constraints}
+\subsection{Find best open ReLU for layer 7 for normal 5x100, new pure y-constraints}
 
@@
 
-	\item \emph{Key results:}  $\gamma$ for different open numbers are
+	\item \emph{Key results:} Actually, even 78,81 nodes have not reach the turning point. So the follow-up tests will use 81 node. $\gamma$ for different open numbers are
 
-	It seems that 34 is the best. In following experiments, we use open 33 node.
+\end{itemize}
+
+\section{February 27 experiments}
+
+\subsection{Compute gamma for layer 7 for normal 5x100, pure y-constraints}
+
+This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 81 node.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|.
+And the partial output file name is \verb*|DL_V0p3_layer7_open_81_node_2.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 022700102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 81 ReLU node
+
+	\item\emph{Processes:} 20 processes in parallel.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_22_15_37_07.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+We will use the following new constraints, and keep the old variables and constraints (will not use them at present).
+
+The new constraints are: \begin{align*}
+	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
+	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
+\end{align*} Here, $y_i$ is the variable that represents $x_i-x'_i$, $\hat{y}_i$ represents $\hat{x}_i-\hat{x}'_i$, $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
+
+\subsubsection*{Results.}
+
+Not completed. So here is the summary of the partial results.
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer7_open_81_node_2.txt|.
+
+	\item \emph{Total time:} 36033.7s.
+
+	\item \emph{Key results:}  The average gamma of this layer is:  2.9401721224547486
+
+	The average solution for gamma of this layer is:  2.7865989645659845.
+
+	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_27_18_03_13.b|.
 

### 2024-02-29 Reports/tech_report1.tex
update report

@@
 
+\section{February 28 experiments}
+
+\subsection{Compute gamma for layer 9 for normal 5x100, pure y-constraints}
+
+This experiment is to compute the gamma of layer 9 normal 5x100 with pure-y constraints constraints, with open 80 node.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|.
+And the partial output file name is \verb*|DL_V0p3_layer9_gamma_open_80.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 9 with open 80 ReLU.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 022800102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 80 ReLU node
+
+	\item\emph{Processes:} 20 processes in parallel.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_27_18_03_13.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+We will use the following new constraints, and keep the old variables and constraints (will not use them at present).
+
+The new constraints are: \begin{align*}
+	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
+	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
+\end{align*} Here, $y_i$ is the variable that represents $x_i-x'_i$, $\hat{y}_i$ represents $\hat{x}_i-\hat{x}'_i$, $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
+
+\subsubsection*{Results.}
+
+Not completed. So here is the summary of the partial results.
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer9_gamma_open_80.txt|.
+
+	\item \emph{Total time:} 36039.55334234238s.
+
+	\item \emph{Key results:}  The average gamma of this layer is:  10.779673641817366
+
+	The average solution for gamma of this layer is:  9.890623948009639
+
+	\item  \emph{Binary output}: It does not generate a binary file. I do not know why.
+
+\end{itemize}
+
 \end{document}

### 2024-03-04 Reports/tech_report1.tex
update report

@@
 
+\section{March 4}
+
+\subsection{Compute gamma for layer 7 for normal 5x100, pure y-constraints, with 0.25}
+
+This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 47 node.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|.
+And the partial output file name is \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 030400102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 81 ReLU node
+
+	\item\emph{Processes:} 20 processes in parallel.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_27_18_03_13.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+The same as previous experiments, except that when choosing open ReLU nodes in layer 3 and 5, we adjust the coefficient from 0.5 to 0.25.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.
+
+	\item \emph{Total time:} 36546s.
+
+	\item \emph{Key results:}  The average gamma of this layer is:  2.7275173326094007
+
+	The average solution for gamma of this layer is:  2.6553045443329144
+
+	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_02_11_26_32.b|.
+
+\end{itemize}
+
+\subsection*{Find compensating values for 6x500}
+
+For 6x500 normal, we have:
+
+layer 3:  0.016880075 0.002558308045652896.
+
+layer 5:  0.012260569 0.0025547753866600885.
+
+layer 7:  0.009393309 0.0024678166341261.
+
+layer 9:  0.01012707 0.002454717660170578.
+
+\vspace*{1ex}
+
+For 6x500 PGD 0.3:
+
+layer 3:  0.07386457 0.0007851583929458109
+
+layer 5:  0.16980232 0.006956658962832778
+
+layer 7:  0.061593153 0.007807677391123027
+
+layer 9:  0.06259781 0.007048364295146268
+
+\vspace*{1ex}
+
+For 6x500 PGD 0.1:
+
+0.059109613 0.0024193087092992493
+
+0.023277795 0.004074500587174903
+
+0.031013045 0.003997824062301744
+
+0.020129312 0.0031846138593207844
+
 \end{document}

### 2024-03-05 Reports/tech_report1.tex
update report

@@
 And the partial output file name is \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 47 ReLU.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 030400102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 47 ReLU node
+
+	\item\emph{Processes:} 20 processes in parallel.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_27_18_03_13.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+The same as previous experiments, except that when choosing open ReLU nodes in layer 3 and 5, we adjust the coefficient from 0.5 to 0.25.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.
+
+	\item \emph{Total time:} 36546s.
+
+	\item \emph{Key results:}  The average gamma of this layer is:  2.7275173326094007
+
+	The average solution for gamma of this layer is:  2.6553045443329144
+
+	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_02_11_26_32.b|.
+
+\end{itemize}
+
+\subsection*{Find compensating values for 6x500}
+
+For 6x500 normal, we have:
+
+layer 3:  0.016880075 0.002558308045652896.
+
+layer 5:  0.012260569 0.0025547753866600885.
+
+layer 7:  0.009393309 0.0024678166341261.
+
+layer 9:  0.01012707 0.002454717660170578.
+
+\vspace*{1ex}
+
+For 6x500 PGD 0.3:
+
+layer 3:  0.07386457 0.0007851583929458109
+
+layer 5:  0.16980232 0.006956658962832778
+
+layer 7:  0.061593153 0.007807677391123027
+
+layer 9:  0.06259781 0.007048364295146268
+
+\vspace*{1ex}
+
+For 6x500 PGD 0.1:
+
+0.059109613 0.0024193087092992493
+
+0.023277795 0.004074500587174903
+
+0.031013045 0.003997824062301744
+
+0.020129312 0.0031846138593207844
+
+\subsection{Compute gamma for layer 7 for normal 5x100, pure y-constraints, with 0.25, using updated code}
+
+This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 47 node.
+The major update is that now in the code of finding open ReLU node by compensating, we use $\gamma_i$ instead of $\beta_i$.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|.
+And the partial output file name is \verb*|DL_V0p7_layer7_comparison_layerWeight_5.txt|.
 It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.
@@
 \begin{itemize}
-	\item\emph{Experiments Id}: 030400102024
-
-	\item\emph{Network:} 6x100 MNIST normal.
-
-	\item\emph{Image:} 144 (meaningless).
-
-	\item\emph{Epsilon $\varepsilon$:} 0.001.
-
-	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
-
-	\item\emph{Open $\ReLU$ number:} Open 81 ReLU node
+	\item\emph{Experiments Id}: 030400302024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 47 ReLU node
 
@@
 
-The same as previous experiments, except that when choosing open ReLU nodes in layer 3 and 5, we adjust the coefficient from 0.5 to 0.25.
-
-\subsubsection*{Results.}
-
-\begin{itemize}
-	\item \emph{Log:} \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.
-
-	\item \emph{Total time:} 36546s.
-
-	\item \emph{Key results:}  The average gamma of this layer is:  2.7275173326094007
-
-	The average solution for gamma of this layer is:  2.6553045443329144
-
-	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_02_11_26_32.b|.
-
-\end{itemize}
-
-\subsection*{Find compensating values for 6x500}
-
-For 6x500 normal, we have:
-
-layer 3:  0.016880075 0.002558308045652896.
-
-layer 5:  0.012260569 0.0025547753866600885.
-
-layer 7:  0.009393309 0.0024678166341261.
-
-layer 9:  0.01012707 0.002454717660170578.
-
-\vspace*{1ex}
-
-For 6x500 PGD 0.3:
-
-layer 3:  0.07386457 0.0007851583929458109
-
-layer 5:  0.16980232 0.006956658962832778
-
-layer 7:  0.061593153 0.007807677391123027
-
-layer 9:  0.06259781 0.007048364295146268
-
-\vspace*{1ex}
-
-For 6x500 PGD 0.1:
-
-0.059109613 0.0024193087092992493
-
-0.023277795 0.004074500587174903
-
-0.031013045 0.003997824062301744
-
-0.020129312 0.0031846138593207844
+The same as previous experiments, except that when choosing open ReLU nodes in layer 3 and 5, we use $\gamma_i$ instead of $\beta_i$.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p7_layer7_comparison_layerWeight_5.txt|.
+
+	\item \emph{Total time:} 36034s.
+
+	\item \emph{Key results:}  The average gamma of this layer is:  2.7484474999036674
+
+	The average solution for gamma of this layer is:  2.4304639934792
+
+	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_04_15_32_38.b|.
+
+\end{itemize}
 

### 2024-03-07 Reports/tech_report1.tex
update report

@@
 And the partial output file name is \verb*|DL_V0p7_layer7_comparison_layerWeight_5.txt|.
-It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 47 ReLU.
 
@@
 
+\section*{March 6}
+
+\subsection{Compute gamma for layer 7 for normal 5x100, pure y-constraints, with 0.25, using updated code}
+
+This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 37 node. The major update is the new formula of finding open ReLU.
+
+\vspace*{1ex}
+
+The running code's file name is \verb*|DiamondLipschitz_V0p9_test.py|.
+And the partial output file name is \verb*|DL_V0p9_layer7_open37_c0p5_1.txt|.
+It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 37 ReLU.
+
+\subsubsection*{Parameters.}
+
+\begin{itemize}
+	\item\emph{Experiments Id}: 030600102024
+
+	\item\emph{Network:} 6x100 MNIST normal.
+
+	\item\emph{Image:} 144 (meaningless).
+
+	\item\emph{Epsilon $\varepsilon$:} 0.001.
+
+	\item\emph{Timeout:} No global timeout. The loop timeout for $\gamma$ is 600s with 12 loops at most.
+
+	\item\emph{Open $\ReLU$ number:} Open 37 ReLU node with coefficient 0.5.
+
+	\item\emph{Processes:} 20 processes in parallel.
+
+	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_27_18_03_13.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method.
+\end{itemize}
+
+\subsubsection*{Technical Sketch.}
+
+The new feature is that we update the formula of finding open ReLU nodes.
+
+\subsubsection*{Results.}
+
+\begin{itemize}
+	\item \emph{Log:} \verb*|DL_V0p9_layer7_open37_c0p5_1.txt|.
+
+	\item \emph{Total time:} 34544s.
+
+	\item \emph{Key results:}  The average gamma of this layer is:  2.7242726913878657
+
+	The average solution for gamma of this layer is:  2.521051645492814
+
+	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_06_23_12_22.b|.
+
+\end{itemize}
+
 \end{document}

### 2024-03-07 Reports/tech_report1.tex
update formulas

@@
 
+The formula is focus on the case when we need to deal with paths of length 3 and length 4. For paths of length 3, we use the standard formula to compute their weights.
+
+For length paths, in the past we multiply a coefficient  to it that is depending on the number of chosen nodes by length 3 paths.
+
+The new formula is more complex. If we use symbol $a,b,c,d$ to denote the nodes in 4 layers, and let $C$ be the set of chosen nodes by length 3 paths, then: \begin{align*}
+	W_{b,b'} = \sum_{a} \sum_{c,c'\in C} \min (|W_{abcd}|,|W_{ab'c'd}|).
+\end{align*} The sum of $a$ is over all nodes in that layer.
+
+In the code, our strategy is to update the weights of all length 4 paths when a new node is put into $C$ by a length path.
+In formula, if we use $c^*$ to denote this new node and $C$ to denote old chosen nodes, then: \begin{align*}
+	W_{b,b'}\  +\!\!= \sum_{a} \sum_{\substack{c\in C \wedge c'= c^* \ \vee\ \\c'\in C \wedge c= c^*}} \min (|W_{abcd}|,|W_{ab'c'd}|).
+\end{align*}
+
+And similar to old version, we can also multiply a coefficient when comparing weights of length 3 paths and length 4 paths, and its default value is 1.
+
 \subsubsection*{Results.}

### 2024-03-21 Reports/tech_report1.tex
update Reports
update

@@
 
-\section*{March 6}
+\section{March 6}
 
@@
 
-	\item\emph{Open $\ReLU$ number:} Open 37 ReLU node with coefficient 0.5.
+	\item\emph{Open $\ReLU$ number:} Open 37 ReLU node with open ReLU coefficient 0.5.
 
@@
 
-\end{itemize}
+	\item  However, although the new formula is supposed to be more accurate, the actual result is only a little bit better than old result. This needs to be explained.
+
+\end{itemize}
+
+\section{March 18}
+
+\subsection*{Gamma of robust 5x100 layer 5}
+
+The output binary file is \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_18_09_23_46.b|. Meanwhile, it try to find the best open number of layer 7.
 

### 2024-04-03 Reports/Summary of tests on MNIST ConvSmall.tex
About MNIST ConvSmall

\documentclass[10pt,table, UTF8]{beamer}
\mode<presentation>
{
	\usefonttheme{professionalfonts}
	\usecolortheme{orchid}
	\setbeamertemplate{theorems}[numbered]
	\setbeamertemplate{footline}[frame number]
	\setbeamertemplate{navigation symbols}{}
	\hypersetup{pdfpagemode={FullScreen}}
}
\usepackage{amsmath}
\usepackage{cite}
\def\pgfsysdriver{pgfsys -dvipdfmx.def}
\usepackage{tikz}
\tikzset{
	dline/.style ={color = blue, line width =1pt}
}
\usepackage{graphicx}
\usepackage{array}
\usepackage{fontawesome5}
\usepackage{geometry}
%\usepackage{fontspec}
%\setmainfont{Arial Unicode MS}
%\usepackage[utf8]{inputenc}
%\usepackage{ctex}
\usepackage[normalem]{ulem}
\usepackage{amsthm}
\newtheoremstyle{mydef}{}{}{\rmfamily}{}{\rmfamily}{}{ }{}
\theoremstyle{mydef}
\newtheorem{myDef}{Definition}
\newtheorem{myTheo}{Theorem}
\newtheorem{myCol}{Collory}
\newtheorem{myPro}{Proposition}
\newtheorem{myExm}{Example}
\newtheorem{myLem}{Lemma}
\numberwithin{equation}{section}
\usepackage{graphicx}

\title{Summary of ConvSmall}

\begin{document}

\begin{frame}{ConvSmall}

	\begin{enumerate}
		\item ConvSmall is CNN with 3 hidden layers.

		\vspace*{1ex}

		\item  Input layer has 28x28 = 784 nodes, the same.

		\vspace*{1ex}

		\item Layer 1 (the first hidden layer) is a convolution with 4x4 kernel. It has 16x13x13 = 2704 nodes.

		\vspace*{1ex}

		\item  Layer 3 is a convolution layer with 4x4 kernel. It has 32x5x5 = 800 nodes.

		\vspace*{1ex}

		\item  layer 5 is a FC with 100 nodes.

		\vspace*{1ex}

		\item  Output has 10 nodes as usual.
	\end{enumerate}

\end{frame}

\begin{frame}
	\frametitle{Layer 1 and 3}

	\begin{enumerate}
		\item Layer 1 is naturally accurate.

		\vspace*{2ex}

		\item  Layer 3 has a very small uncertainty, even using LP. So we do not need to worry about it.
	\end{enumerate}

\end{frame}

\begin{frame}
	\frametitle{Layer 5}

	\begin{enumerate}
		\item Layer 5 is similar as our previous networks.

		\vspace*{2ex}

		\item  If we increase the open number of ReLU nodes, then it will use more time and get more accuracy.

		\vspace*{2ex}

		\item  The computed bounds for Layer 5 is very important. I am testing the best open number: it seems that open = 300 or 250 is worse than open = 200.
	\end{enumerate}

\end{frame}

\begin{frame}{Tests of layer 5}
	\begin{table}[htbp]
		\centering
		\caption{Average uncertainty: UB - LB}
		\begin{tabular}{|c|c|c|c|c|c|}
			\hline
			case: &image 0 & image 1 & image 2 & image 3 & image 4 \\
			\hline
			open 100 all & 1.860 & 1.8285 & 1.907 & 1.813 & 1.865 \\
			open 100 unstable & 1.395 & 1.116 & 1.728 & 1.102 & 1.5205 \\
			\hline
			open 200 all & 1.702 & 1.702 & 1.847 & 1.745 & 1.739 \\
			open 200 unstable & 1.274 & 0.997 & 1.675 & 1.031 & 1.361 \\
			\hline
			open 250 all & 1.67 & 1.741 & 1.776 & 1.749 & 1.768\\
			open 250 unstable & 1.230 & 1.018 & 1.533 & 1.034 & 1.382 \\
			\hline
		\end{tabular}
	\end{table}

	Average time of open 100, 200, 250 are 467.0s, 411.8s, 501.5s (including previous layers).

\end{frame}

\begin{frame}
	\frametitle{Layer 7}

	\begin{enumerate}
		\item Layer 7 is the key problem.

		\vspace*{2ex}

		\item In previous code there are bugs so the open relu function cannot return enough nodes. Now it is fixed.

		\vspace*{2ex}

		\item  But the accuracy is still not high.

		\vspace*{2ex}

		\item  I will go to test the best open number of layer 7.

	\end{enumerate}

\end{frame}

\begin{frame}{Summary of tests}
	\begin{enumerate}
		\item  On  April 1 and 2, the early code has lots of bugs/mistakes.

		\vspace*{2ex}

		\item  Most of them are because in previous code, I sometimes assumed all hidden layers have the same number of nodes (I should not). But this is not true in ConvSmall.

		\vspace*{2ex}

		\item  Some of them are easy to find (will cause error directly). Some of them are not as evident (they will influence the open nodes chosen, but the code can run).

		\vspace*{2ex}

		\item  Now I think all such mistakes have been fixed.
	\end{enumerate}
\end{frame}

\begin{frame}{Other details}
	\begin{enumerate}
		\item ERAN: They also tried a lot to improve the accuracy and speed on ConvSmall: we can see the table in their or beta-Crown's paper.

		\vspace*{2ex}

		\item Beta-Crown: They are very very good at this network. Their average time is only 7s, and even DeepPoly need 3s per image.

		\vspace*{1ex}

		\item According to their default configuration file, they do not use refine-part/MILP to run ConvSmall. They use pure bab.
	\end{enumerate}
\end{frame}

\end{document}

### 2024-04-03 Reports/Summary of tests on MNIST ConvSmall.tex
fix typo
fix typos

@@
 
-	Average time of open 100, 200, 250 are 467.0s, 411.8s, 501.5s (including previous layers).
+	Average time of open 100, 200, 250 are 411.8s, 467.0s,  501.5s (including previous layers).
 
@@
 	\end{enumerate}
+	\vspace*{2ex}
+
+	One question is that, even I open all unstable nodes in layer 5, the bounds of layer 5 will still heavily influence the accuracy of layer 7. Why?
 

### 2024-04-15 lipics-master/proofs.tex
upload the paper in new LIPlcs format

--- 2024-01-27 Paper/proofs.tex
@@
 
+Notice that above definitions only involve weights, not bias.
+From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.
+
 We can then prove the following key lemma for Theorem \ref{th1}.
@@
 	We prove similarly that $\min(n)=\Val_{\vx^\sharp}(n)$,
-	and the case $S(n)=-1$. This concludes the induction. \qed
+	and the case $S(n)=-1$. This concludes the induction. 
 \end{proof}
@@
 
-		Hence we have equality pre and post activation function. \qed
-
+		Hence we have equality pre and post activation function.
 			\end{proof}
@@
 		It means that all the segment of $\rho_1,\rho_2$ from $n_i$ to $n_{i+1}$ have the same sign (they have no nodes in common but the initial and final nodes).
-		Hence $\rho_1$ and $\rho_2$ have the same sign, a contradiction with $\rho_1,\rho_2$ being a weakly compensating pair.  \qed
+		Hence $\rho_1$ and $\rho_2$ have the same sign, a contradiction with $\rho_1,\rho_2$ being a weakly compensating pair. 
 	\end{proof}
@@
 				from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
-				Then two paths $(a_j,b,z)$ and $\pi'$ also form a weak compensating pair. \qed
+				Then two paths $(a_j,b,z)$ and $\pi'$ also form a weak compensating pair.
 			\end{proof}
@@
 
-				3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction. \qed
+				3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction. 
 			\end{proof}
@@
 				By contradiction, assume that there exists two paths $\rho_1,\rho_2$ from 
-				$n$ to $z$ with (strictly) different signs. The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$. \qed
+				$n$ to $z$ with (strictly) different signs. The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$. 
 			\end{proof}
@@
 The case for min is similar.
-\qed
 			\end{proof}
@@
 			%\begin{proof}
-			%	For $D_I$, it is because of no compensating as proved in the first section. %For $D_J$, it is because all nodes are either opened or constants. \qed
+			%	For $D_I$, it is because of no compensating as proved in the first section. %For $D_J$, it is because all nodes are either opened or constants. 
 			%\end{proof}
@@
 			\begin{proof}
-				This is by the definition of MILP formulation and $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}, \LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$. \qed
+				This is by the definition of MILP formulation and $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}, \LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$. 
 			\end{proof}
@@
 This is for part 3.
-\qed
 
@@
 
-\begin{proof}[of Theorem \ref{thm:2}]
+\begin{proof}[Proof of Theorem \ref{thm:2}]
 	We show that $\beta=\max(z)$.
@@
 Hence, using the $\max$ over ${x_J^0}$, 
-we will have $\max(z) = \beta'\geq \beta \geq \max(z)$, and hence $\beta=\beta'=\max(z)$.
-
-\qed
-
-\end{proof}
+we will have $\max(z) = \beta'\geq \beta \geq \max(z)$, and hence $\beta=\beta'=\max(z)$.\end{proof}
 
@@
 It means that we have a pair of compensating paths from $m$ tp $z$, and thus $y \in X$, a contradiction with $y \in Y_+$.
-\qed
 \end{proof}
@@
 Thus $m'$ is in $Z$, a contradiction with $m'$ the source of a pair of compensating paths.
-\qed
 \end{proof}
@@
 	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
-	We then apply Lemma \label{lemma11}, inductively then applying Lemma \label{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. \qed
+	We then apply Lemma \label{lemma11}, inductively then applying Lemma \label{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 
 	\end{proof}
@@
 We call $X_*$ this subset $X$.
-\qed
 \end{proof}
@@
 It means that we have a pair of compensating paths from $m$ to $z$, and thus $y \in X$, a contradiction with $y \in Y_+$.
-\qed
 \end{proof}
@@
 passing by $m$. But now, that means that $m'<m<n<z$.
-Thus $m'$ is in $Z$, a contradiction with $m'$ the source of a pair of compensating paths.
-\qed
-\end{proof}
+Thus $m'$ is in $Z$, a contradiction with $m'$ the source of a pair of compensating paths.\end{proof}
 
@@
 	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
-	We then apply Lemma \ref{lemma11}, inductively then applying Lemma \ref{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. \qed
+	We then apply Lemma \ref{lemma11}, inductively then applying Lemma \ref{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 
 	\end{proof}

### 2024-04-16 lipics-master/comppaths.tex
upload the paper in new LIPlcs format
update the draft of a new figure

--- 2024-01-27 Paper/comppaths.tex
@@
 
+\begin{figure}[h]
+	\centering
+	\begin{tikzpicture}[>=stealth, node distance=2cm]
+		% Input nodes (two types)
+		\node[circle, draw, minimum size=0.5cm] (input1) at (-1,0) {$a_0$};
+		\node[circle, draw, minimum size=0.5cm] (input2) at (-2,0) {$a_1$};
+		\node[circle, draw, minimum size=0.5cm] (input3) at (-4,0) {$a_2$};
+
+		\node[circle, draw, minimum size=0.5cm] (input4) at (-5,0) {$a_3$};
+		\node[circle, draw, minimum size=0.5cm] (input5) at (-7,0) {$a_4$};
+		\node[circle, draw, minimum size=0.5cm] (input6) at (-8,0) {$a_5$};
+
+		\draw[draw=black, dashed] (-1.5,0) ellipse (1.35 and 0.75);
+		\node[below] at (-1.5,-0.75) {$A_{zero}$};
+
+		\draw[draw=black, dashed] (-2,2) ellipse (0.75 and 0.75);
+		\node[right] at (-1,2) {$B_{zero}$};
+
+		% Hidden layer nodes
+
+		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden1) at (-2,2) {$n_0$};
+
+		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden2) at (-4,2) {$n_1$};
+		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden3) at (-5,2) {$n_2$};
+
+		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden4) at (-7,2) {$n_3$};
+		\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden5) at (-8,2) {$n_4$};
+
+		\draw[draw=black, dashed] (-4.5,0) ellipse (1.35 and 0.75);
+		\node[below] at (-4.5,-0.75) {$A_{pure}$};
+
+		\draw[draw=black, dashed] (-7.5,0) ellipse (1.35 and 0.75);
+		\node[below] at (-7.5,-0.75) {$A_{open}$};
+
+		\draw[draw=black, dashed] (-4.5,2) ellipse (1.35 and 0.75);
+		\node[left] at (-3.5,3) {$B_{pure}$};
+
+		\draw[draw=black, dashed] (-7.5,2) ellipse (1.35 and 0.75);
+		\node[left] at (-8.5,1.5) {$B_{open}$};
+
+		% Output node
+		\node[circle, draw, minimum size=0.8cm, fill=red!20] (output) at (-5,4) {$z$};
+
+		% connections
+
+		\draw[->] (input1) -- (hidden1);
+
+		\draw[->] (input3) -- (hidden5);
+
+		\draw[->] (input4) -- (hidden4);
+
+%		% Connect input to hidden layer
+		\foreach \i in {3,4} {
+			\foreach \h in {3,2} {
+				\draw[->] (input\i) -- (hidden\h);
+			}
+		}
+
+		\foreach \i in {5,6} {
+			\foreach \h in {4,5} {
+				\draw[->] (input\i) -- (hidden\h);
+			}
+		}
+%		
+		% Connect hidden layer to output
+		\foreach \h in {2,3,4,5} {
+			\draw[->] (hidden\h) -- (output);
+		}
+
+%		% Input label
+%		\node[left=0.5cm of input1] {Input Layer};
+%		% Hidden label
+%		\node[right=0.5cm of hidden2] {Hidden Layer};
+%		% Output label
+%		\node[right=0.5cm of output] {Output Layer};
+	\end{tikzpicture}
+	\caption{Simple Neural Network with Different Types of Input Nodes}
+	\label{fig:neural_network_types_simplified}
+\end{figure}
+
 Concerning Theorem \ref{th2}, consider an output node $z$.
@@
 
-Notably, this complexity serves as an upper bound. For instance, solvers like Gurobi are quite adept and usually don't need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
+Notably, this complexity serves as an upper bound. For instance, solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
 It's worth mentioning that the for loop iterating over neurons $n$ in layer $k$, as seen in line 2, can be executed in parallel.

### 2024-04-16 lipics-master/proofs.tex
update

@@
 
-Notice that above definitions only involve weights, not bias.
-From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.
+{\color{red}Notice that above definitions only involve weights, not bias.
+From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.}
 
@@
 			\end{proof}
+
+							{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not involve bias, and any kind of bias will not influence our theorem.}
 
@@
 we will have $\max(z) = \beta'\geq \beta \geq \max(z)$, and hence $\beta=\beta'=\max(z)$.\end{proof}
+
+{\color{red} In all above statements and proofs, we do not use any assumption of bias, and the bias will have no influence on our discussion. }
 

### 2024-04-18 lipics-master/comppaths.tex
update the figure
update contents

@@
 	\end{tabular}
-	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.}
+	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.
+{\color{red} Compensating strength with 1 layer between source and target is straightforward, and was sufficient to show the difference between DNNs trained naturally and by DiffAI.}}
 	\label{tab:compensation}
@@
 			\foreach \h in {3,2} {
-				\draw[->] (input\i) -- (hidden\h);
+				\draw[line width=1pt, ->] (input\i) -- (hidden\h);
 			}
@@
 		% Connect hidden layer to output
-		\foreach \h in {2,3,4,5} {
+		\foreach \h in {2,3} {
+			\draw[line width=1pt,->] (hidden\h) -- (output);
+		}
+
+		\foreach \h in {4,5} {
 			\draw[->] (hidden\h) -- (output);
@@
 
-%		% Input label
-%		\node[left=0.5cm of input1] {Input Layer};
-%		% Hidden label
-%		\node[right=0.5cm of hidden2] {Hidden Layer};
-%		% Output label
-%		\node[right=0.5cm of output] {Output Layer};
+%\		% Input label
+		\node[left=0.7cm of input6] {Input Layer};
+
+		% Hidden label
+		\node[left=0.7cm of hidden5] {Hidden Layer};
+
+		% Output label
+		\node[left=0.5cm of output] {Output Layer};
 	\end{tikzpicture}
-	\caption{Simple Neural Network with Different Types of Input Nodes}
+	\caption{Definitions in the proof of Theorem \ref{th2}}
 	\label{fig:neural_network_types_simplified}

### 2024-04-19 Reports/tech_report1.tex
update report

@@
 
+The output binary file of layer 7 is \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_21_10_10_33.b|.
+
+The output of binary file of layer 9 is: \verb*|Diamond_record_5_100_dictionary_with_end_layer9_2024_03_23_21_53_04.b|
+
+The output of binary file of layer 11 is:
+
+\verb*|Diamond_record_5_100_dictionary_with_end_layer11_2024_03_24_23_38_45.b|
+
 \end{document}

### 2024-04-19 lipics-master/Paper_noProof.tex

--- 2024-01-27 Paper/Paper_noProof.tex
@@
-\documentclass{llncs}
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
 \pagestyle{plain}

### 2024-04-19 lipics-master/experiments.tex

--- 2024-01-27 Paper/experiments.tex
@@
 \newpage
+
 \section{Experimental Evaluation}
@@
 %\vspace{-0.2cm}
-$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ 
-%\vspace{-0.2cm}
-
-and the associated $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$. We then select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
+$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ and the associated $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$.
+We then select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
+{\color{red} The intuition behind the formula is simple: $\val_{\vx}(a)weight(abcd)$ is the naive contribution from node $a$ to the target $d$.
+And the min of two paths is a natural number for the strength of compensating: if one of them is very small, the effect of compensating will also be very small.}
 
@@
 
-\begin{table}[h!]	
+\begin{table}[t!]	
 	\centering
@@
 	\label{tab:example1}
-	%\vspace{-0.8cm}
+	\vspace{-0.6cm}
 \end{table}
@@
 	}
+	\vspace{-0.8cm}
 	\label{tab:example}

### 2024-04-19 lipics-master/proofs.tex
update contents
update

@@
 
-{\color{red}Notice that above definitions only involve weights, not bias.
+{\color{red}Notice that above definitions only involve weights, and do not use bias.
 From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.}
@@
 \end{proof}
+
+{\color{red} As we mentioned before, this proof does not have any requirements on the bias.}
 
@@
 
+		{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not involve bias, and any kind of bias will not influence our theorem.}
+
 			\begin{proof}
@@
 			\end{proof}
-
-							{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not involve bias, and any kind of bias will not influence our theorem.}
 
@@
 This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected.
+{\color{red} Moreover, this hypothesis only matters in the theoretical proof.
+This is because in practice, paths with zero or very small weights will have very small effect on the output, and very small effect on the models, too.
+Usually these paths will not be considered.}
 

### 2024-04-19 lipics-master/relatedwork.tex

--- 2024-01-27 Paper/relatedwork.tex
@@
 
-When examining ERAN-Deeppoly \cite{deeppoly}, which efficiently computes bounds on values, we establish that LP encoding is unequivocally more accurate.
+When examining ERAN-DeepPoly \cite{deeppoly}, which efficiently computes bounds on values, we establish that LP encoding is unequivocally more accurate.
 This is a novel insight, to our knowledge.

### 2024-04-19 lipics-master/Paper_noProof.tex
update

@@
 \date{}
+
+\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}
+
+\author{Blaise Genest}{CNRS, France \and CNRS@CREATE, Singapore \and https://perso.crans.org/genest/}{blaise.genest@cnrsatcreate.sg}{}{}
+
+\author{Kuldeep Meel}{University of Toronto, Canada \and https://www.cs.toronto.edu/~meel/}{ meel@cs.toronto.edu}{}{}
+
+\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}
+
+%\author{John Q.
+Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
 

### 2024-04-19 lipics-master/Paper_noProof.tex
update

@@
 Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
+
+\Copyright{John Q. Public and Joan R. Public} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+
+\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords
 

### 2024-04-22 lipics-master/relatedwork.tex
update MN-BAB in introduction

@@
 
+{\color{red} MN-BaB \cite{ferrari2022complete} is another state-of-the-art verifier which is a development of PRIMA.
+As shown in its name, it uses a combination technique of multi-neuron constraints and Branch and Bound.
+According to their experiments results, MN-BaB has a similar speed and accuracy as $\alpha$,$\beta$ CROWN.
+So we do not compare our experiments results to MN-BaB separately.}
+
 For hard-to-verify DNNs that are not too large,  $\alpha,\beta$ CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding.

### 2024-04-22 lipics-master/relatedwork.tex
update

--- 2024-04-19 lipics-master/relatedwork.tex
@@
 
+{\color{red} MN-BaB \cite{ferrari2022complete} is another state-of-the-art verifier which can be regarded as a development of PRIMA.
+As shown in its name, it uses a combination technique of multi-neuron constraints and Branch and Bound.
+According to their experiments results, MN-BaB has similar speed and accuracy as $\alpha$,$\beta$ CROWN.
+Therefore, we do not compare our experiments results to MN-BaB separately.}
+
 For hard-to-verify DNNs that are not too large,  $\alpha,\beta$ CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding.

### 2024-04-22 lipics-master/experiments.tex
update

@@
 We then select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
-{\color{red} The intuition behind the formula is simple: $\val_{\vx}(a)weight(abcd)$ is the naive contribution from node $a$ to the target $d$.
-And the min of two paths is a natural number for the strength of compensating: if one of them is very small, the effect of compensating will also be very small.}
+{\color{red} The intuition behind the formula is straightforward: $\val_{\vx}(a)weight(abcd)$ is the simple contribution from node $a$ to the target $d$.
+And min of two paths is a natural value to represent the strength of compensation: if one of them is very small, the effect of compensation will also be very small.}
 

### 2024-04-22 lipics-master/comppaths.tex
update

@@
 	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.
-{\color{red} Compensating strength with 1 layer between source and target is straightforward, and was sufficient to show the difference between DNNs trained naturally and by DiffAI.}}
+{\color{red} Compensation strength with 1 layer between source and target is straightforward, and was sufficient to show the difference between DNNs trained naturally and by DiffAI.}}
 	\label{tab:compensation}
@@
 			\foreach \h in {3,2} {
-				\draw[line width=1pt, ->] (input\i) -- (hidden\h);
+				\draw[line width=1.5pt, ->] (input\i) -- (hidden\h);
 			}

### 2024-04-23 lipics-master/experiments.tex
update

@@
 \end{table}
+
+{\color{red} We also do a comparison of our method and the method in paper \cite{9211410}.
+They find a formula to choose nodes in their algorithm.
+We can use the same formula in our setting, and since we only have $\ReLU$ function, that formula can be simplified to: $$V(n) = (UB(n)-LB(n))\cdot W_{nm}.$$ In this formula, $m$ is the target node, and $n$ is one of source nodes in one layer before.
+We sort all nodes $n$ by their $V(n)$ values, and choose the nodes with largest values.}
 

### 2024-04-23 lipics-master/proofs.tex

@@
 {\color{red}Notice that above definitions only involve weights, and do not use bias.
-From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.}
+As demonstrated by the following lemmas and proofs, our discussion is independent of bias, regardless of whether the bias values are very large or very small.}
 
@@
 
-{\color{red} As we mentioned before, this proof does not have any requirements on the bias.}
+{\color{red} As we mentioned earlier, this proof does not have any requirements on the bias.}
 
@@
 
-		{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not involve bias, and any kind of bias will not influence our theorem.}
+		{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not consider bias, and any kind of bias will not affect our theorem.}
 
@@
 
-{\color{red} In all above statements and proofs, we do not use any assumption of bias, and the bias will have no influence on our discussion. }
+{\color{red} In all the statements and proofs above, we do not make any assumptions about bias, and bias will not affect our discussion. }
 

### 2024-04-24 lipics-master/introduction.tex
ccby

--- 2024-01-27 Paper/introduction.tex
@@
 ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of {\em undecided} inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
-Actually, DNNs which are trained to be robust (using DiffAI \cite{DiffAI} or PGD \cite{PGD}) are easier to verify, while the DNNs trained in a {\em natural} way are harder to verify.
+Using complete verifiers, while theoretically would close the gap, fail to answer fully due to (very long) time-outs.
+Actually, the DNNs easy to verify are trained specifically (using DiffAI \cite{DiffAI} or PGD \cite{PGD}), while the DNNs harder to verify are {\em verification-agnostic} \cite{SDPFI}, trained in a {\em natural} way.
 
-In this work, we concentrate on DNNs that are trained naturally, given the prevalence of techniques for {\em easier} DNNs.
-Our analysis is confined to DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
+In this work, we concentrate on {\em verification-agnostic} DNNs, given the prevalence of techniques for {\em easier} DNNs, and also the decrease in accuracy of specifically trained DNNs \cite{Caterina}.
+Our analysis focuses on DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
 Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{
-	\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses other competing techniques;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
-}.
-Perhaps, it is worth highlighting that these tools are  sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN Is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though the DNN is indeed robust.
-To dig further into their incompleteness, we first remark that high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
+	\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+Perhaps, it is worth highlighting that these tools are  sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN Is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though the DNN is indeed robust:
+	%To dig further into their incompleteness, we first remark that 
+	the high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
 Therefore, inaccurate bounds leads to incompletness.

### 2024-04-24 lipics-master/Paper_noProof.tex
update
intro+related

@@
 
-\author{Blaise Genest}{CNRS, France \and CNRS@CREATE, Singapore \and https://perso.crans.org/genest/}{blaise.genest@cnrsatcreate.sg}{}{}
+\author{Blaise Genest}{IPAL Lab, CNRS and CNRS@CREATE, France and Singapore}{blaise.genest@cnrsatcreate.sg}{}{}
 
-\author{Kuldeep Meel}{University of Toronto, Canada \and https://www.cs.toronto.edu/~meel/}{ meel@cs.toronto.edu}{}{}
+\author{Kuldeep Meel}{University of Toronto, Canada}{ meel@cs.toronto.edu}{}{}
 
@@
 Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
+\authorrunning{Y. Liao, B. Genest, K. Meel and S. Aryaman} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
 
-\Copyright{John Q. Public and Joan R. Public} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords
+
+\Copyright{Liao Yuke, Blaise Genest, Kuldeep Meel and Shaan Aryaman} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
 
 \ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords
 

### 2024-04-24 lipics-master/introduction.tex
intro+related

@@
 
-In this work, we concentrate on {\em verification-agnostic} DNNs, given the prevalence of techniques for {\em easier} DNNs, and also the decrease in accuracy of specifically trained DNNs \cite{Caterina}.
+In this work, we concentrate on {\em verification-agnostic} DNNs, given the prevalence of techniques for {\em easier} DNNs, and also the decrease in accuracy of specifically trained DNNs (e.g.
+the large easy-to-verify ResNet network has $29\%$ accuracy \cite{prima}!).
 Our analysis focuses on DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
-Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{
-	\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
-Perhaps, it is worth highlighting that these tools are  sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN Is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though the DNN is indeed robust:
+Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima},
+MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+	The high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
+These tools are thus sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though it actually is, because of bounds inaccuracies.
 	%To dig further into their incompleteness, we first remark that 
-	the high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
-Therefore, inaccurate bounds leads to incompletness.
+	Notice that complete methods exist \cite{Reluplex,katz2019marabou,SDPFI}, but they time-out on hard instances.
+In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-CROWN \cite{crown}.
 
-As a starting point, we sought to understand properties of DNNs that make them hard to verify.
-Our key finding is a new notion of {\em compensations}, that leads to inaccuracies of bounds and thus explain the {\em hardness} of verifying some DNNs.
-Formally, a compensating pair is a tuple of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
-Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
-That is, it is loaded by $(w+w') weight(a)$.
-As $w,w'$ have opposite sign, they will compensate (partly) each other.
+%As a starting point, we sought to understand properties of DNNs that make them hard to verify.
+Our key finding is a new notion of {\em compensations}, that explains why bounds are inaccurate.
+Formally, a {\em compensating pair of paths} $(\pi,\pi')$ between neurons $a$ and $b)$ is such that $w < 0 < w'$ for $w,w'$ the products of weights seen along $\pi$ and $\pi'$ respectively.
+Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with
+$(w+w') weight(a)$ by $\pi$ and $\pi'$.
+As $w,w'$ have opposite signs, they will compensate (partly) each other.
 The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
-However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which all the efficient tools try to avoid because it is very expansive (could be exponential in the number of such ReLU nodes opened).
+However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which the efficient tools try to avoid because it is very time-consuming (combinatioral explosion as the problem is NP-hard \cite{Reluplex}).
 %; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust. 
-
-Our three main contributions address the challenges of inaccuracies in neural network computations due to compensating pairs of paths:
+Our three main contributions address the challenges of inaccuracies when verifying DNNs:
 \begin{enumerate}
 	\item  Our first main contribution establishes, through Theorem \ref{th1}, the foundational understanding that the compensating pairs are the 	%primary 
-	source of all inaccuracies, 
-	 as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate.
+	source of {\em all} inaccuracies, 
+	 as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate. This is confirmed experimentally by the fact that 
+	 DNNs easier to verified have less compensation strenght than verification agnostic DNNs. 
 	This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs.
 Nonetheless, this insight lays the groundwork for our innovative approach, {\em relaxing} the usual but inefficient Mixed Integer Linear Program (MILP) formulation encoding exactly DNNs \cite{MILP}.
-To compute bounds for $z$, we encode as binary variables (the costly ones) only ReLU nodes on compensating paths {\em with target $z$}; other nodes, in particular those on compensating paths to neurons before $z$ are encoded using the much more efficient linear relaxation.
+To compute bounds for $z$, we encode as binary variables only ReLU nodes on {\em compensating paths with target $z$}; other nodes, in particular those on compensating paths to neurons before $z$ are encoded using the much faster linear relaxation.
 To take into account indirectly the compensating paths to previous nodes, we inductively compute bounds for every neuron layer by layer, and use these bounds of previous neurons in the MILP encoding for $z$.
@@
 \item  Our second main contribution, delineated in Theorem \ref{th2}, answers this question, showing that this abstraction is fully accurate, in that the bounds computed in such a way for neuron $z$ correspond exactly to the minimal and maximal values reachable by inputs of the DNN.
-Again, the prevalence of compensating paths in actual DNNs renders this algorithm computationally intensive because the number of binary variables is still too high.
+Again, the prevalence of compensating paths in actual DNNs renders this algorithm computationally intensive because the number of binary variables is still high.
 
-\item Our third primary contribution addresses a practical concern by 
-introducing {\CMP} (Algorithm \ref{algo1}), a pragmatic solution that builds on our theoretical insights.
+\item Our third main contribution is to experimentally confirm that focusing on compensations {\em does} improve accuracy: we introduce {\CMP} (Algorithm \ref{algo1}), building on our theoretical insights.
 This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones.
@@
 It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$.
-Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN.
+Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete}) on the larger $6 \times 500$ DNN.
 
@@
 
-For all these reasons, the notion of compensation is very promising, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).
+These theoretical and experimental results both point to compensation being a promising notion, opening up many opportunities discussed in Section \ref{Discussion}.
 

### 2024-04-24 lipics-master/relatedwork.tex
intro+related

--- 2024-04-19 lipics-master/relatedwork.tex
@@
 
-We now compare {\CMP} with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art.
-When contrasted with the exact encoding of a DNN using MILP \cite{MILP}, we selectively target a limited number of ReLU nodes based on compensating strength.
-This approach scales to larger DNNs while preserving good accuracy.
-In comparison to MIPplanet \cite{MIPplanet}, which opts for a different selection of ReLU nodes, our strategy iteratively computes bounds for all neurons.
-This significantly reduces the number of ReLU nodes represented exactly for a given neuron through numerous rapid computations, proving more efficient than a single, larger computation.
-Furthermore, in contrast to the linear relaxation of MILP encoding \cite{MILP}, {\CMP} is inherently more precise, albeit with a slower runtime.
+We compare {\CMP} with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art.
+CMP scales while preserving good accuracy, through targeting a limited number of binary variables based on compensating strength, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate).
+MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP instance instead of CMP's many small instances, which significantly reduce the number of binary variables necessary for each instance.
+In \cite{9211410}, small instances are also considered, however with a straightfoward choice of binary nodes based on the weight of outgoing edge, therefore restricted to nodes in the previous layer, which is significantly less accurate than using compensating strength (see Table \ref{tab:example1}).
 
-When examining ERAN-DeepPoly \cite{deeppoly}, which efficiently computes bounds on values, we establish that LP encoding is unequivocally more accurate.
-This is a novel insight, to our knowledge.
-DeepPoly abstracts the weight of every node using two functions: an upper function and a lower function.
+ERAN-DeepPoly \cite{deeppoly} computes bounds on values very quickly, by abstracting the weight of every node using two functions: an upper function and a lower function.
 While the upper function is fixed, the lower function offers two choices.
-In Proposition \ref{LP}, we demonstrate that the LP relaxation precisely matches the intersection of these two choices.
-Consequently, it is more accurate than DeepPoly but less efficient.
-\CMP is considerably more precise than DeepPoly (it refines LP), albeit less efficiently.
+It relates to the LP encoding through the following new (to our knowledge) insight:  Proposition \ref{LP} state that the LP relaxation precisely matches the intersection of these two choices.
+Consequently, LP is more accurate (but slower) than DeepPoly, and \CMP is considerably more precise.
 
-Regarding PRIMA \cite{prima}, the approach involves explicitly maintaining dependencies between neurons, calculating bounds layer by layer, similar to our method.
+Regarding PRIMA \cite{prima}, the approach involves explicitly maintaining dependencies between neurons, calculating bounds layer by layer.
 This enables the retention of dependencies from many layers prior.
-Our method, however, handles dependencies between neurons differently, attributing them to compensation.
-It excels in accuracy for local dependencies but may lose precision for dependencies formed several layers back.
-Many dependencies are local, occurring in the last few layers (since ReLU nodes tend to clip those from far back), and \CMP achieves more accurate results than PRIMA.
+CMP, however, handles dependencies between neurons differently, attributing them to compensation.
+CMP excels in accuracy for local dependencies but may lose precision for dependencies formed several layers back.
+Experimental accuracy results in favor of CMP points to dependencies being more local than global (see Table \ref{tab:example}).
 
-$\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB}) focus on running few instances of branch and bound (one per output neuron).
+$\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete})  focus on running few instances of branch and bound (one per output neuron).
 In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities.
@@
 In contrast, {\CMP} is less efficient as it must individually consider each node from the start, including nodes with non-critical bounds.
-However, branch and bound hits a complexity barrier when verifying complex networks, such as naturally trained DNNs, due to an overwhelming number of branches.
-For instance, Branch and Bound verifies only 3.5\% more images (44.5\% from 41\%) by increasing runtime by 50 times on larger $6 \times 5000$ DNNs, and fails to match {\CMP}'s performance (65\% of images verified, Table \ref{tab:example}).
+However, branch and bound hits a complexity barrier when verifying complex networks, such as verification-agnostic DNNs, due to an overwhelming number of branches.
+For instance, Branch and Bound verifies only 3.5\% more images (44.5\% from 41\%) by increasing runtime by 50 times on larger $6 \times 500$ DNNs, and fails to match {\CMP}'s performance (65\% of images verified, Table \ref{tab:example}).
 
-For hard-to-verify DNNs that are not too large,  $\alpha,\beta$ CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding.
+%{\color{red} MN-BaB \cite{ferrari2022complete} is another state-of-the-art verifier which can be regarded as a development of PRIMA.
+As indicated by its name, it uses a combination technique of multi-neuron constraints and Branch and Bound.
+According to their experiments results, MN-BaB has similar speed and accuracy as $\alpha$,$\beta$ CROWN.
+Therefore, we do not compare our experiments results to MN-BaB separately.}
+
+For verification-agnostic DNNs that are not too large,  $\beta$-CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding.
 In {\CMP}, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
-As it is more efficient, we compute bounds for neurons in all the layers.
+As it is more efficient, we compute bounds for neurons in {\em all} the layers.
 This would be infeasible without the selection based on the compensation.
-The refined version of $\alpha,\beta$-CROWN is particularly accurate on small DNNs.
+The refined version of $\beta$-CROWN is particularly accurate on small DNNs.
 As the depth grows, the more work is left to BaB and \CMP is more accurate (Table \ref{tab:example}).
 
-Finally, algorithms such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network, and therefore,  diverge significantly from those abstracting values (PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, {\CMP}, and the like.
-These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and therefore, are often unable to handle the size of networks that can be handled by those abstract values.
+Finally, (complete) algorithms such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network, and therefore,  diverge significantly from those abstracting values e.g PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, {\CMP}.
+These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances.

### 2024-04-24 lipics-master/introduction.tex
intro

@@
 This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones.
-Our extensive empirical evaluation (refer to Table \ref{tab:example}) reveals {\CMP} achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
+Our empirical evaluation (refer to Table \ref{tab:example}) reveals {\CMP} achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
 It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$.

### 2024-04-24 lipics-master/Paper_noProof.tex
format (anonymous...)

--- 2024-04-19 lipics-master/Paper_noProof.tex
@@
 
-\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}
+%\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}
 
-\author{Blaise Genest}{CNRS, France \and CNRS@CREATE, Singapore \and https://perso.crans.org/genest/}{blaise.genest@cnrsatcreate.sg}{}{}
+%\author{Blaise Genest}{IPAL Lab, CNRS and CNRS@CREATE, France and Singapore}{blaise.genest@cnrsatcreate.sg}{}{}
 
-\author{Kuldeep Meel}{University of Toronto, Canada \and https://www.cs.toronto.edu/~meel/}{ meel@cs.toronto.edu}{}{}
+%\author{Kuldeep Meel}{University of Toronto, Canada}{ meel@cs.toronto.edu}{}{}
 
-\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}
+%\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}
 
@@
 Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
+%\authorrunning{Y. Liao, B. Genest, K. Meel and S. Aryaman} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+
+\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords
+
+%\Copyright{Liao Yuke, Blaise Genest, Kuldeep Meel and Shaan Aryaman} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\ccsdesc[100]{} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
 

### 2024-04-24 lipics-master/valabstraction.tex
continue

--- 2024-02-23 lipschitz/valabstraction.tex
@@
 
-\begin{figure}[t!]
+\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
+
+\begin{figure}[b!]
 	\centering
@@
 
-		\draw[->,color=green, thick] (input2) -- (hidden1) node[near start, below] {$1$};
+		\draw[->,color=applegreen, thick] (input2) -- (hidden1) node[near start, below] {$1$};
 		\draw[->,color=red, thick] (input2) -- (hidden2)node[near start, below] {$-1$};
 
-		\draw[->,color=green, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
+		\draw[->,color=applegreen, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
 		\draw[->,color=red, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(n_2,0)$};
 
-		\draw[->,color=green, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
+		\draw[->,color=applegreen, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
 		\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
@@
 	\end{tikzpicture}
-	\caption{A DNN example from \cite{kpoly}: every neuron is separated into 2 nodes, $n$ pre- and $\hat{n}$ post-ReLU activation function.
-The pair $(n_2 n_3 n_5,n_2 n_4 n_5)$ in green and red is compensating (weights of paths are $1,-2$).}
+	\caption{A DNN example from \cite{kpoly}: every neuron is separated into 2 nodes, 
+	$n$ pre- and $\hat{n}$ post-ReLU activation function. The pair of paths 
+	$({\color{applegreen}n_2 n_3 n_5},{\color{red}n_2 n_4 n_5})$ is {\em compensating} 
+	(weights ${\color{applegreen}1},{\color{red}-2}$).}
 	\label{fig1}
@@
 This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth.
-For all $i$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
+For all $i \geq 3$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
 
@@
 This implies that $x_3,x_4 \in [-2,2]$.
-After applying the ReLU function, $\hat{x}3,\hat{x}4$ are constrained to $[0,2]$, leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$.
-The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val{\vy}(n_i)=\alpha$.
+After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to $[0,2]$, leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$.
+The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val_{\vy}(n_i)=\alpha$.
 However, this precision is lost from the next layer (beginning with $n_5, n_6$) due to potential dependencies among preceding neurons.
-For example, $n_3$ only attains the value $2$ when both $x_1$ and $x_2$ are $2$.
-In this case, $n_4$ would reach a value of $Val{(2,2)}(n_4)=0$.
-Consequently, it's implausible for $x_5=\Val_{\vx}(n_5)$ to reach $6$, as it would necessitate both $n_3$ and $n_4$ assuming the value $2$.
+For example, it is impossible for $x_5=\Val_{\vx}(n_5)$ to reach $6$, as it would necessitate both $x_3=2$ and $x_4=2$, which is not possible at the same time as
+$x_3=2$ implies $x_1=x_2=1$ and $x_4=2$ implies $x_2=-1$ (and $x_1=1$), a contradiction.
 
-An extremely efficient algorithm that addresses some issues is "DeepPoly" \cite{deeppoly}, also independently discovered as the "CROWN" algorithm \cite{crown}.
-Instead of strict bounds, for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$.
+An extremely efficient algorithm that alleviates some of the inacuraccies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}.
+Instead of fixed bounds for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$.
 For instance, denote $f_i \leq x_i \leq g_i$ with, for example, $f_{3}(x_3)=f_4(x_4)=0$ and $g_3(x_3) = \frac{x_3+2}{2}$, $g_4(x_4) = \frac{x_4+2}{2}$.
@@
 The variation, {\em $\overline{\mbox{DeepPoly}}$}, consistently chooses $f^1_i$, and never $f^2_i$.
-Contrary to DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} encompasses the ``Box abstraction." For instance, with bounds $[-0.2,5]$ on $x_i$, it deduces $\ReLU(x_i) \in [0,5]$, whereas  DeepPoly without box abstraction algorithm would conclude $\ReLU(x_i) \in [-0.2,5]$.
+Contrary to DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} encompasses the ``Box abstraction." For instance, with bounds $[-0.2,5]$ on $x_i$,
+standard DeepPoly would conclude $\ReLU(x_i) \in [-0.2,5]$, while 
+{\em $\overline{\mbox{DeepPoly}}$} would deduce $\ReLU(x_i) \in [0,5]$ similarly as the Box abstraction.
 
@@
 
-At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method (albeit much slower than DeepPoly). 
+At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a complete (but inefficient) method. 
 Consider an unstable neuron $n \in[\alpha,\beta]$.
-The value $x$ of $\ReLU(n)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints \cite{MILP}:
+The value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $(\alpha,\beta)$ with 4 constraints \cite{MILP}:
 \vspace{-0.1cm}
@@
 
-It can be shown that for all $x \in [\alpha,\beta] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$.
+For all $x \in [\alpha,\beta] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
 Here, $a$ is 0 if $x < 0$, 1 if $x>0$, and can be either if $x=0$~\cite{MILP}.
-This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help in certifying a given input.
-However, for networks with hundreds of nodes or more, the resulting MILP formulation will contain numerous integer variables and generally cannot be solved efficiently.
+This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
+However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous integer variables and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
 
-MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in ${0,1}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
+MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
 As solving LP instances is polynomial time, this optimization is significantly more efficient.
 However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
-This approach is termed the {\em LP abstraction}
+This approach is termed the {\em LP abstraction}.
 
@@
 	\label{LP}
-	Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
-	1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
+	Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints (1) for LP and (2) for DeepPoly with both lower bounds, are equivalent:
 	\begin{align}
-& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1]  \label{eq:lp}\\
+& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, \quad a \in [0,1]  \label{eq:lp}\\
 &\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha} \label{eq:deeppoly}
@@
 \begin{proof}
-We need to show that the two upper bound constraints in Eq~\ref{eq:lp} is equivalent to the upper bound in Eq~\ref{eq:deeppoly}.
+We need to show that the two upper bound constraints on $\hat{x}$ in (1) are equivalent to the upper bound in (2).
 To this end, we focus on the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
@@
 \end{proof}
-
-\subsubsection*{Constraints for $\gamma$}
-
-We could get the following constraints for $\gamma$, using $y_i$ and $\hat{y}_i$ to denote the $x_i-x_i'$ and $\hat{x}_i-\hat{x}_i'$:\begin{align*}
-	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
-	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
-\end{align*} where $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
-
-The following plot will show the above constraints:
-
-\begin{tikzpicture}
-	\begin{axis}[
-		xlabel={$y_i$},
-		ylabel={$\hat{y}_i$},
-		xmin=-2, xmax=2,
-		ymin=-2, ymax=2,
-		axis lines=center,
-		samples=100, 
-	 unit vector ratio=1 1 1, scale=1, xtick   = {-2,2},
-	 xticklabels = {$-\gamma_i$,$\gamma_i$},
-	 yticklabels = {},
-		]
-		\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
-		\addplot[blue, thick] {0};
-
-		\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
-			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
-
-				\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
-			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
-	\end{axis}
-\end{tikzpicture}
-
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
-
-We can use the following extra constraints (besides 4 constraints about $\hat{x}_i'=\ReLU(x_i')$) to build this relation:
-
-\begin{align*}
-	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
-\end{align*}
-
-Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
-
-A more direct way to establish the constraints is as follows: \begin{align*}
-	& y+x'_i \leq a\beta_i \quad\wedge \quad y+x'_i\geq (1-a)\alpha_i\\	
-	& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-	&\hat{y}_i \leq -a\gamma_i \quad\wedge \quad	\hat{y}_i \geq a'\gamma_i \\
-	&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-	&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-	&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-\end{align*}The following two plots show its shape:
-
-\hspace*{-10ex}
-\begin{tikzpicture}
-	\begin{axis}[	axis on top, xlabel = \(x'_i\),
-		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
-				set layers=default,
-	xmax = 4, xmin = -4,
-ymax = 1, ymin = -1,		
-zmax = 1, zmin = -1,
-				unit vector ratio=1 1 1, scale=3,
-				view={60}{50}, ytick   = {-1,0,1},
-				yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
-				xticklabels = {$0$}, ztick   = {-1,0,1},
-				zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
-				]
-		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
-		coordinates {
-	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
-		};
-
-		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
-		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
-		};
-
-		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
-		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
-		};
-
-			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
-		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
-		};
-
-		\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
-					\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
-		\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
-
-	\end{axis}
-\end{tikzpicture}
-
-\hspace*{-15ex}
-\begin{tikzpicture}
-	\begin{axis}[	axis on top, xlabel = \(x'_i\),
-		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
-		set layers=default,
-				xmax = 4, xmin = -4,
-		ymax = 1, ymin = -1,		
-				zmax = 1, zmin = -1,
-		unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
-		yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
-		xticklabels = {$0$}, ztick   = {-1,0,1},
-		zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
-		view={35}{14},
-		]
-		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
-		coordinates {
-			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
-		};
-
-		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
-		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
-		};
-
-		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
-		};
-
-		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
-		};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
-		\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
-
-		\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
-		\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
-
-	\end{axis}
-\end{tikzpicture}
-
-%\begin{tikzpicture}[
-%	declare function={
-%		f(\x,\y)=max((\x+\y),0)-max(\x,0);
-%	}]
-%	\begin{axis}[axis lines=center,
-%		axis on top,
-%		set layers=default,
-%		xrange=-3:3,
-%		yrange=-2:2,
-%		unit vector ratio=1 1 1,% <- HERE (taken from Phelype Oleinik's deleted answer)
-%		scale=3 %<- added to compensate for the downscaling
-%		% resulting from unit vector ratio=1 1 1
-%		]
-%		\addplot3[
-%		domain=-3:3,
-%		domain y=-1:1, surf,
-%		samples=40,
-%		samples y=40,
-%		] {f(\x,\y)};
-%	\end{axis}
-%\end{tikzpicture}

### 2024-04-25 lipics-master/Paper_noProof.tex

@@
 
-	In this paper, we will use lower case latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
-	capitalized bold for matrices $\boldsymbol{W}$, similar to notations in \cite{prima,crown}.
+	In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
+	capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{prima,crown}.
 	To simplify the notations, we restrict the presentation to feed-forward, 
@@
 	\begin{align*}
-		{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i\\
-		\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
+		\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
+		\hat{\boldsymbol{z}}^{i} = ReLU({\boldsymbol{z}}^i).
 	\end{align*}

### 2024-04-25 lipics-master/comppaths.tex

@@
 
-The phenomenon of compensating pairs of paths significantly impacts the precision of the target state due to the overabstraction of values.
-For instance, consider a scenario where $x_5 \leq 4$ is attainable when $x_1=1$ and $x_2=-1$, leading to $\val_{(1,-1)}(n_5)=4$.
-However, the Box methodology estimates an upper limit of $6$.
-Although DeepPoly partially rectifies the dependency on $x_2$, it achieves only partial negation of the $x_2$ value owing to the excessive abstraction characteristic of ReLU.
-This results in an overestimated upper bound of $x_5 \leq 5$ through a contribution of $\frac{-x_2+3}{2} \leq 2$, as opposed to the exact calculation of $-x_2 \leq 1$, culminating in a precise upper bound of $x_5 \leq 4$.
+The phenomenon of compensating pairs of paths significantly impacts the precision of the target state due to the overabstraction of values. We have $\val_{(1,-1)}(n_5)=4$. 
+This is actually the maximum value reachable by $\val_{\vx}(n_5)$.
+However, the Box methodology estimates an upper limit $\val_{\vx}(n_5) \leq 6$ (contribution $\leq 3$ from $n_1$ plus $\leq 3$ from $n_2$ to $n_5$).
+DeepPoly rectifies the bound from the contribution of $n_2$ to $n_5$ by an (overestimated) upper bound $\frac{-x_2+3}{2} \leq 2$, leading to $\val_{\vx}(n_5) \leq 5$. 
+The exact contribution of $n_2$ to $n_5$ is actually bounded by $-x_2 \leq 1$, leading to $x_5 \leq 4$. Considering exactly $ReLU(n_3),ReLU(n_4)$ allows one to obtain 
+this precise bound $-x_2$ for the contribution of $n_2$ to $n_5$.
 
@@
 However, the ReLU functions can constrain the level of compensation due to their clipping effect.
-For instance, if the inputs $x_1, x_2$ are confined within the range $[-1,-0]$, then $\hat{x}_3$ will consistently be 0 for any input $\vx=(x_1,x_2)$ within the domain $[-1,-0] \times [-1,-0]$, thereby preventing $weight(\pi')$ from effectively counterbalancing $weight(\pi')$.
+For instance, if the inputs $x_1, x_2$ are confined within the range $[-1,-0]$, then $\hat{x}_3$ will consistently be 0 for any input $\vx=(x_1,x_2)$ within the domain $[-1,-0] \times [-1,-0]$, thereby preventing $weight(\pi')$ from effectively counterbalancing $weight(\pi)$.
 
@@
 
+\smallskip
+
+The discussion so far shows  that compensation is {\em one} of the factors contributing to inaccuracy. We now establish that it is {\em the sole cause} of inaccuracy:
+if a DNN lacks any compensating path, then any methodology that is at least as accurate as the Box abstraction, such as LP and $\overline{\mbox{DeepPoly}}$ (but not DeepPoly), will precisely determine the exact upper and lower bounds for every node.
+This assertion is formalized in the following theorem:
+
+\begin{theorem}
+	\label{th1}
+	Consider any node $n$ within a DNN devoid of any compensating path.
+Let $[\alpha,\beta]$ represent the bounds computed by the Box abstraction for node $n$.
+Then, for every $\gamma$ within the interval $[\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n) = \gamma$.
+\end{theorem}
+
+The sketch of proof can be found in Section \ref{sec.proofs}. 
+This theorem underscores the significant role of compensating paths in the accuracy of bound estimation within DNNs, affirming that their absence guarantees the precision of computed bounds.
+Practically speaking, encountering a network entirely devoid of compensating paths is highly improbable, rendering this more a theoretical observation, highlighting that compensation is a key driver of inaccuracy.
+
 \begin{table}[b!]
@@
 
-The discussion so far shows  that compensation is one of the possible factors contributing to inaccuracy. We now establish that it is the sole cause of inaccuracy:
-if a DNN lacks any compensating path, then any methodology that is at least as accurate as the Box abstraction, such as LP and $\overline{\mbox{DeepPoly}}$ (but not DeepPoly), will precisely determine the exact upper and lower bounds for every node.
-This assertion is formalized in the following theorem:
-
-\begin{theorem}
-	\label{th1}
-	Consider any node $n$ within a DNN devoid of any compensating path.
-Let $[\alpha,\beta]$ represent the bounds computed by the Box abstraction for node $n$.
-Then, for every $\gamma$ within the interval $[\alpha,\beta]$, there exists an input $\vx$ such that $\val_{\vx}(n) = \gamma$.
-\end{theorem}
-
-The sketch of proof can be found in Section \ref{sec.proofs}.
-
-This theorem underscores the significant role of compensating paths in the accuracy of bound estimation within DNNs, affirming that their absence guarantees the precision of computed bounds.
-Practically speaking, encountering a network entirely devoid of compensating paths is highly improbable, rendering this more a theoretical observation, highlighting that compensation is a key driver of inaccuracy.
-
 %It is worth remarking that  Theorem~\ref{th1} does not directly apply to standard DeepPoly since DeepPoly does not inherently refine the Box abstraction.
@@
 
-An intriguing application of this result lies in elucidating why certain DNNs are inherently more amenable to verification compared to others.
+Additionally we offer an experimental corroboration of this result:
+Consider 2 similar network, one verification agnostic and one trained robustly to be more easily verifiable (using DiffAI). TBC
+
 This distinction is notably evident between DNNs adversarially trained for robustness and those trained naturally, utilizing the same architecture \cite{deeppoly,prima,crown}.

### 2024-04-25 lipics-master/introduction.tex

@@
 
-These theoretical and experimental results both point to compensation being a promising notion, opening up many opportunities discussed in Section \ref{Discussion}.
+These theoretical and experimental results both point to compensation being a promising notion, opening up many opportunities, as discussed in Section \ref{Discussion}.
 

### 2024-04-25 lipics-master/relatedwork.tex

@@
 
-Finally, (complete) algorithms such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network, and therefore,  diverge significantly from those abstracting values e.g PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, {\CMP}.
+Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, \CMP.
 These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances.

### 2024-04-25 lipics-master/experiments.tex
update table
update data
update

--- 2024-04-22 lipics-master/experiments.tex
@@
 
+{\color{red} We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly from layers $1$ and $2$.
+	Moreover, we also compare choosing nodes in the second layer only (using method in paper \cite{9211410}) with choosing nodes in both the first and second layer.
+
+		The method in paper \cite{9211410} use a formula to value different nodes in a layer, and then choose nodes by their values.
+We can use the same formula in this comparison experiments.
+Because we only have $\ReLU$ function, that formula can be simplified to: $$V(n) = (UB(n)-LB(n))\cdot W_{nm}.$$ In this formula, $m$ is the target node, and $n$ is one of source nodes in one layer before.
+We sort all nodes $n$ by their $V(n)$ values, and choose the nodes with larger values.
+
+	Choosing ReLU nodes in the previous layer (layer $2$) only is less accurate than 
+	also choosing nodes in layer $1$.
+	When picking in both layer $1$ and $2$, choosing $50$ out of $116$ unstable ReLU nodes allows to reduce by $90\%$ the average uncertainty due to inaccurate computations ($0.059$ vs $0.574$), while it only reduces the uncertainty by $65\%$ when choosing nodes randomly.
+Notice that applying this layer after layer will even further reduce uncertainty created by accumulation of inaccuracies.
+	Last, we did not experiment for selecting ReLU nodes in 3+ layers earlier because the trade-off of accuracy vs evaluating the compensating strength of such paths is unclear.
+
+}
+
 \begin{table}[t!]	
@@
 		\hline
-		\text{Number $K$}  &  \text{Compensate layer} 1+2 &  \text{Compensate layer} 2 & \text{Random layer } 1+2 \\ \hline
+		\text{Number $K$}  &  \text{Compensate layer} 1+2 &  \text{{\color{red}Quick Method} layer} 2 & \text{Random layer } 1+2 \\ \hline
 		\hline
-		0  &  1.758 & 1.758 & 1.758  \\ \hline
-		10  &  1.677 & 1.677 & 1.695  \\ \hline
-		20  &  1.539 & 1.567 & 1.622  \\ \hline
-		30  &  1.431 & 1.489 & 1.542  \\ \hline
-		40  &  1.329 & 1.454 & 1.47  \\ \hline
-		50  &  1.243 & 1.432 & 1.39  \\ \hline
-		116 (max) &  1.184 & 1.422 & 1.184  \\ \hline
+		0  &  1.761 & 1.761 & 1.761  \\ \hline
+		10  &  1.656 & 1.651 & 1.696  \\ \hline
+		20  &  1.527 & 1.557 & 1.619  \\ \hline
+		30  &  1.402 & 1.489 & 1.546  \\ \hline
+		40  &  1.281 & 1.447 & 1.469  \\ \hline
+		50  &  1.165 & 1.426 & 1.388  \\ \hline
+		116 (max) &  0.895 & 1.424 & 0.895  \\ \hline
 	\end{tabular}
@@
 	\vspace{-0.6cm}
+
 \end{table}

### 2024-04-26 lipics-master/comppaths.tex
update figure
till experiments

@@
 \begin{example}
-	For instance, on Fig.~\ref{fig1}, the paths $\pi= n_2 n_3 n_5$ has weight $1$, while the
+	On Fig.~\ref{fig1}, the paths $\pi= n_2 n_3 n_5$ has weight $1$, while the
 	path $\pi'= n_2 n_4 n_5$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
@@
 
-The phenomenon of compensating pairs of paths significantly impacts the precision of the target state due to the overabstraction of values. We have $\val_{(1,-1)}(n_5)=4$. 
+	The phenomenon of compensating pairs of paths significantly impacts the precision of the target state due to the overabstraction of values.
+In an intuitive sense, the target state accrues weight from the source state via different paths connecting the source to the target.
+When these connecting paths possess weights of contrasting signs, a certain degree of cancellation occurs, with the extent of cancellation being up to $min(|weight(\pi')|,|weight(\pi')|)$.
+
+	For instance, on Fig.~\ref{fig1}, we have $\val_{(1,-1)}(n_5)=4$. 
 This is actually the maximum value reachable by $\val_{\vx}(n_5)$.
@@
 DeepPoly rectifies the bound from the contribution of $n_2$ to $n_5$ by an (overestimated) upper bound $\frac{-x_2+3}{2} \leq 2$, leading to $\val_{\vx}(n_5) \leq 5$. 
-The exact contribution of $n_2$ to $n_5$ is actually bounded by $-x_2 \leq 1$, leading to $x_5 \leq 4$. Considering exactly $ReLU(n_3),ReLU(n_4)$ allows one to obtain 
-this precise bound $-x_2$ for the contribution of $n_2$ to $n_5$.
+The exact contribution of $n_2$ to $n_5$ is actually bounded by $-x_2 \leq 1$, leading to $x_5 \leq 4$. 
+It s however hard to obtain this precise bound $-x_2$ for the contribution of $n_2$ to $n_5$
+without considering exactly $ReLU(n_3),ReLU(n_4)$.
 
-In an intuitive sense, the target state accrues weight from the source state via different paths connecting the source to the target.
-When these connecting paths possess weights of contrasting signs, a certain degree of cancellation occurs, with the extent of cancellation being up to $min(|weight(\pi')|,|weight(\pi')|)$.
-This mechanism also serves to mitigate error propagation in a manner similar to how $0 = |1+(-1)| \leq |1|+|-1| = 2$ in imprecise analyses.
-However, the ReLU functions can constrain the level of compensation due to their clipping effect.
+%This mechanism also serves to mitigate error propagation in a manner similar to how $0 = |1+(-1)| \leq |1|+|-1| = 2$ in imprecise analyses. 
+Indeed, the ReLU functions can constrain the level of compensation due to their clipping effect.
 For instance, if the inputs $x_1, x_2$ are confined within the range $[-1,-0]$, then $\hat{x}_3$ will consistently be 0 for any input $\vx=(x_1,x_2)$ within the domain $[-1,-0] \times [-1,-0]$, thereby preventing $weight(\pi')$ from effectively counterbalancing $weight(\pi)$.
@@
 		\hline
-		\text{Source/Target Layers}  &  \text{Natural DNN} & \text{Robust DNN} & \text{Ratio Natural vs Robust} \\ \hline \hline
-		0 / 2 & 0.0304 & 0.00220  & 13.8x\\ \hline
-		1 / 3  & 0.0313 & 0.00875 & 3.58x \\ \hline
-		2 / 4  &  0.0267 & 0.00785 & 3.40x \\ \hline
-		3 / 5  &  0.0253 & 0.00804  & 3.18x \\ \hline
+		\text{Target Layer}  &  \text{Verification-agnostic DNN} & \text{DiffAI-trained DNN} & \text{Ratio} \\ \hline \hline
+		2 & 0.0304 & 0.00220  & 13.8x\\ \hline
+		3  & 0.0313 & 0.00875 & 3.58x \\ \hline
+		4  &  0.0267 & 0.00785 & 3.40x \\ \hline
+		5  &  0.0253 & 0.00804  & 3.18x \\ \hline
 	\end{tabular}
-	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set.
-{\color{red} Compensation strength with 1 layer between source and target is straightforward, and was sufficient to show the difference between DNNs trained naturally and by DiffAI.}}
+	\caption{Average compensating strength over all pairs of paths of length 3 to nodes in the target layer, between a verification-agnostic DNN and a DNN robustly-trained using DiffAI \cite{DiffAI}.
+\vspace{-0.8cm}}
 	\label{tab:compensation}
+
 \end{table}
@@
 Additionally we offer an experimental corroboration of this result:
-Consider 2 similar network, one verification agnostic and one trained robustly to be more easily verifiable (using DiffAI). TBC
-
-This distinction is notably evident between DNNs adversarially trained for robustness and those trained naturally, utilizing the same architecture \cite{deeppoly,prima,crown}.
-Notably, the presence of compensating pairs is an intrinsic structural attribute of the learned DNN, contrasting with more semantic aspects like the number of unstable ReLUs, which are significantly influenced by the specific image and algorithm employed.
-To illustrate this point, we consider two networks, each comprising 5 hidden layers with 100 nodes, sourced from the ERAN GitHub repository.
-One is naturally trained ($6\times100$), and the other is trained using DiffAI ($5\times100$).
-In Table \ref{tab:compensation}, we present the average compensation strength, computed as the mean of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$ across all source/target states within specified layers.
-The findings reveal that the average compensation strength is considerably lower in the Robust DNN compared to the natural DNN.
-Correspondingly, the Robust DNN is substantially easier to verify than its natural counterpart, as evidenced by the enhanced accuracy and image verification rate of DeepPoly.
+Consider 2 similar networks, one verification-agnostic and one trained robustly to be more easily verifiable (using DiffAI), namely with 5 hidden layers of 100 neurons each, sourced from the ERAN GitHub repository.
+%This distinction is notably evident between DNNs adversarially trained for robustness and those trained naturally, utilizing the same architecture \cite{deeppoly,prima,crown}. 
+%To illustrate this point, we consider two networks, each comprising 5 hidden layers with 100 nodes, 
+%One is naturally trained ($6\times100$), and the other is trained using DiffAI ($5\times100$). 
+In Table \ref{tab:compensation}, we present the average compensation strength, computed as the mean of $max_{\pi,\pi'} min(|weight(\pi')|,|weight(\pi')|)$ across all source/target states separated by 1 layer.
+The findings reveal that the average compensation strength is considerably lower in the robustly trained DNN compared to the verification-agnostic DNN, which matches the fact that the former is substantially easier to verify than the later
+\cite{deeppoly}.
 
@@
 
-While Theorem \ref{th1} is interesting to understand that compensation is a key notion for accurate verification of DNNs, it cannot be used directly to analyze DNNs with compensations, which are actually those that are most interesting to tackle.
-Intuitively, when there are compensating paths, it seems necessary to consider exactly the (unstable) ReLU nodes that are seen along these paths. 
+While Theorem \ref{th1} demonstrates that compensation is a key notion for accurate verification of DNNs, it does not explicitly provide an algorithm to analyze DNNs with compensations.
+However, Theorem \ref{th1} hints to considering the ReLU nodes that are seen along the compensating paths, in an exact way to improve the accuracy.
 %Consider a neuron $n$ in layer $k$ for which we want to have accurate bounds 
@@
 Consider a neuron $n$ in layer $k$, for which we aim to establish accurate bounds $[\alpha,\beta]$.
-Define $X_n$ as the set of neurons $x$ in layers up to $k-1$, where each $x$ is part of a compensating path targeting neuron $n$, but not as the source or the target node of the path.
-Let $Y_n$ represents the set of all other neurons in the first $k-1$ layers, essentially serving as the complement of $X_n$.
-We introduce MILP${X_n}$, a variant of the MILP encoding where all nodes in $Y_n$ are linearly relaxed, hence incorporating $|X_n|$ binary variables, each corresponding to a neuron in $X_n$.
+Define $X_n$ as the set of {\em unstable} neurons $x$ in layers up to $k-1$, where each $x$ is part of a compensating path targeting neuron $n$ (except its the source node).
+Let $\overline{X_n}$ represents the set of all other neurons in the first $k-1$ layers, essentially serving as the complement of $X_n$.
+We introduce MILP${X_n}$, a variant of the MILP encoding where all nodes in $\overline{X_n}$ are linearly relaxed (if the neuron is stable, it is the exact linear mode of the ReLU), hence incorporating $|X_n|$ binary variables, each corresponding to a neuron in $X_n$.
 Additionally, this encoding encapsulates bounds for every neuron $n'$ in the initial $k-1$ layers, as computed inductively in previous steps.
-That is, we do not use explicitly in $X_n$ nodes on compensating paths with target neurons before $n$ ({\em indirectly} compensating paths),
-only those with target $n$ ({directly} compensating paths).
+That is, we do not use explicitly in $X_n$ nodes on compensating paths with target neurons before $n$ ({\em indirectly} compensating paths), only those with target $n$ ({directly} compensating paths).
 The contribution of these {\em indirectly} compensating paths are thus 
@@
 and not as binary variables.
-We demonstrate now that the bounds $[\alpha,\beta]$ for neuron $n$, as computed by MILP${X_n}$, are accurate, thereby offering a more nuanced approach to DNN verification in scenarios involving compensating paths.
-We will provide the proof under a fairly light well-connected hypothesis (H1), which only DNNs where all but very few weights are 0 does not satisfy.
+Theorem \ref{th2} states that the bounds $[\alpha,\beta]$ for neuron $n$, as computed by MILP${X_n}$, are accurate, thereby offering an algorithm for DNN verification in scenarios involving compensating paths.
+We will provide the proof under a fairly light well-connected hypothesis (H1), which only very specific DNNs does not satisfy, namely very sparse DNNs where almost all weights are 0.
+(H1) removes some corner cases, simplifying the proof.
 
-(H1): for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ with at least 2 transitions, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target).
-This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected.
+(H1) for every 2 (not necessarily totally disjoint) paths $\rho_1 \neq \rho_2$ with non-zero weight with the same source $m$ and the same target $n$ with at least 2 transitions, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target).
 
@@
 First, notice that by continuity of all the functions used in the DNNs, it suffices to show both theorem for $\gamma=\alpha$ and $\gamma=\beta$.
-
 %Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
@@
 if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
-$-1$ if they have negative weights.
-
-Using the concept of sign, we introduce input vectors $\vx^{*}, \vx^{\sharp}$:
+$-1$ if they have negative weights. %Using the concept of sign, 
+We introduce
+% input vectors 
+$\vx^{*}, \vx^{\sharp}$:
 
@@
 Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ the bounds computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity.
-
-\smallskip
-The formal proof is in appendix A.
+for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. The full proof is in appendix A.
 
@@
 
+\iffalse
 \begin{figure}[h]
@@
 
-		\draw[->] (input3) -- (hidden5);
+		\draw[line width=1.5pt,->] (input3) -- (hidden5);
 
-		\draw[->] (input4) -- (hidden4);
+		\draw[line width=1.5pt,->] (input4) -- (hidden4);
 
@@
 		\foreach \h in {2,3} {
-			\draw[line width=1pt,->] (hidden\h) -- (output);
+			\draw[line width=1.5pt,->] (hidden\h) -- (output);
 		}
@@
 \end{figure}
+\fi
 
@@
 
-Hence, the value of any neuron $n$ in $A_{pure}$ or $B_{pure}$ is entirely determined by 
+Hence, the value of any neuron $n \in B_{pure}$ is entirely determined by 
 inputs in $A_{pure}$.
@@
 \begin{proposition}
-For a node $b$ with $S(b)=1$:
+For a node $b$ with $S(b)=1$ and $b'$ with $S(b())=-1$:
 
-$$\max(b)=\max_{\vx_{open}} \val_{\vx^{\star}_{pure},\vx_{open}}(b)$$
-$$\min(b)=\min_{\vx_{open}} \val_{\vx^{\sharp}_{pure},\vx_{open}}(b)$$
-
-and for $S(b)=-1$:
-$$\max(b)=\max_{\vx_{open}} \val_{\vx^{\sharp}_{pure},\vx_{open}}(b)$$
-$$\min(b)=\min_{\vx_{open}} \val_{\vx^{\star}_{pure},\vx_{open}}(b)$$
+$$\max(b)=\max_{\vx_{open}} \val_{\vx^{\star}_{pure},\vx_{open}}(b); \quad 
+\min(b)=\min_{\vx_{open}} \val_{\vx^{\sharp}_{pure},\vx_{open}}(b)$$
+$$\max(b'))=\max_{\vx_{open}} \val_{\vx^{\sharp}_{pure},\vx_{open}}(b'); \quad \min(b')=\min_{\vx_{open}} \val_{\vx^{\star}_{pure},\vx_{open}}(b')$$
 \end{proposition}
@@
 Consider the DNN $D'$ with input nodes $A_{open}$, where all the 
-edges from $m \in A_{open} \cup B_{open}$ to $n$ are replaced by a bias 
-(equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^\star_{open}}(m)$) for $n$ (we sum all these bias for a neuron $n$).
+edges from $m \in A_{open} \cup B_{open}$ to $n$ are replaced by a bias, 
+equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^\star_{open}}(m)$ (we sum all these biases).
 The values in $D'$ are the same as the values in $D$ for input $\vx^{\star}_{pure}$,
@@
 Hence $\MILP_{B_{open}}$ computes the bounds accurately in $D'$.
-It will compute the bound in the same way in $D$, hence we get $\beta=\max(z)$ for the target $z$. The formal proof is in appendix B.
+It will compute the bound in the same way in $D$, hence we get $\beta=\max(z)$ for the target $z$. The full proof is in appendix B.
 
-\subsection{An efficient algorithm}
+\subsection{The CMP algorithm}
 
-Leveraging Theorem \ref{th2}, it is theoretically feasible to procure accurate bounds by iteratively applying MILP$_{X}$ to each node, layer by layer.
-This sequential approach would yield precise bounds $[\alpha,\beta]$ for each node, which could then be utilized to calculate accurate bounds for subsequent layers.
-However, in a practical setting, this methodology may prove to be computationally inefficient.
-Typically, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$.
+Theorem \ref{th2} theoretically computes accurate bounds by iteratively applying MILP$_{X}$ to each node, layer by layer.
+Practically, however, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$.
 Instead, an interesting trade off between speed and accuracy is to set a threshold on the strength of compensation.
@@
 This strategy effectively provides a trade-off between the algorithm's performance and the precision of the results.
-The detailed steps of this approach are outlined in the pseudo-code for \CMP presented in Algorithm \ref{algo1}.
+The pseudo-code for \CMP is presented in Algorithm \ref{algo1}.
 
@@
 and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
-We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables.
+We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound.
+Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
+It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$.
+%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
+CMP uses 20 threads.
 
-Notably, this complexity serves as an upper bound. For instance, solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
-It's worth mentioning that the for loop iterating over neurons $n$ in layer $k$, as seen in line 2, can be executed in parallel.
-This is feasible because the computation only depends on bounds from preceding layers, not the current layer $k$.
-This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$.
-
-Therefore, if $K$ is sufficiently small, Algorithm \ref{algo1} frequently invokes MILP (e.g., using Gurobi) with a manageable number of integer variables.
-This approach is expected to be efficient and yet remains fairly precise, as it can accurately compute (according to Theorem \ref{th2}) the most significant compensating path.
+If $K$ is sufficiently small, 
+%Algorithm \ref{algo1} invokes many MILP (e.g., using Gurobi) with a manageable number of %integer variables. 
+this approach is expected to be efficient and yet remains fairly precise, as it can accurately compute (according to Theorem \ref{th2}) the most significant compensating path.
 The effectiveness of this strategy is further examined in the subsequent section.

### 2024-04-26 lipics-master/experiments.tex
till experiments

@@
-\newpage
-
 \section{Experimental Evaluation}
@@
 We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
-with 256 GB of main memory and 2 NVIDIA RTX 3090. 
-Gurobi 9.52 was used for solving MILP and LP problems.
+with 256 GB of main memory and an (unused) NVIDIA RTX 3090. 
+Gurobi 9.52 was used for solving LP and MILP problems.
 
-We conducted our evaluation on neural networks trained on MNIST that have been employed in prior work.
-The networks have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, and $8 \times 200$.
-It is worth remarking that despite seemingly small size, these instances are challenging for the current state of the art techniques.
-In particular, the current state of the art methods are unable to characterize $12\%$ to $20\%$ of the images as neither certified robust \cite{crown} nor find an adversarial example \cite{attack}.
-We call such images {\em undetermined}.
-Following methodology in prior work \cite{prima,crown}, we evaluate on the first 1000 images of the dataset.
-We also experimented on the network of size $6\times 500$ (results not reported in \cite{prima,crown}), checking the first 200 images of the dataset, given the computational overhead associated with such larger networks.
+We conducted our evaluation on neural networks obtained from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided).
+These verification-agnostic DNNs have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ and $6 \times 500$.
+We selected the 4 first because they have been tested in both \cite{prima} and \cite{crown}, they have good accuracy ($>94\%$ \cite{prima}),
+and depite their small sizes there is still a large portion ($12\%$ to $20\%$) of images which are {\em undetermined} by these SOTA methods, that is images neither verified nor for which an attack has been found  \cite{attack}.
+Hence more accurate methods are useful.
+The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (still high accuracy) to understand the scaling of CMP.
+Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{crown}.
+All these DNNs tackle the MNIST benchmark, which is not a limitation as we want to validate that focusing on compensating strength improves the accuracy: we do not claim that the particular CMP implementation is the most efficient in all the situations.
+
+To obtain results comparable with \cite{prima,crown}, 
+we evaluated CMP on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ for the first 1000 images of the dataset.
+For $6\times 500$ (results not reported in \cite{prima,crown}), we run all the tools ourselves for the first 200 images, given the computational overhead associated with such larger networks.
 Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
-All these DNNs are found in the ERAN GitHub 
-(\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided).
-%Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
 
-\paragraph{Baseline}: 
+\smallskip
+
+\noindent{\bf Baseline}: 
 We compare the following verifiers performing value-abstraction:
 \begin{itemize}
-	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}.
-We report the runtime from our own implementation, used in {\toolname}.
-It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA).
-	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN \cite{crown}. We use the results reported in \cite{prima} and \cite{crown} respectively for instances that were also used in prior works.
-	We report results for the $6\times500$ network as it was not reported in prior work.
-
+	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}. We report the runtime from our  implementation in \toolname. 
+	%It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA). 
+	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN \cite{crown}. We use the results reported in \cite{prima} and \cite{crown} respectively for 
+	$5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$.
+	We report our experimental results for the $6\times500$ DNN as they are not available in prior work.
+Notice that PRIMA and CROWN run 16 CPU threads for the first 4 benchmarks, and use massively parallel (>4000 threads) GPUs on $6\times500$, compared to 20 CPU threads for CMP on all DNNs.
+	\item We also tested MN-BaB \cite{ferrari2022complete} on $6\times500$
+	(slightly lower accuracy and slower than $\alpha$,$\beta$CROWN), 
+	in line with results reported in \cite{ferrari2022complete} for other DNNs.
+Further, results for MN-BaB on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$	are not reported in \cite{ferrari2022complete} or elsewhere.
+	We thus do not include MN-BaB results in Table \ref{tab:example}, to avoid clutter.
 %	They use GPU while we do not. When computing the whole correlated space, 
@@
 %	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
-	\item It is worth remarking that we do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
-	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods \cite{crown}.
+	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
+	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods in accuracy and time \cite{crown}.
 

### 2024-04-26 lipics-master/valabstraction.tex
till experiments

@@
 The value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $(\alpha,\beta)$ with 4 constraints \cite{MILP}:
-\vspace{-0.1cm}
-\begin{align*}
-	\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)
-\end{align*}
+$\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)$.
 

### 2024-04-26 lipics-master/experiments.tex
14 pages!

@@
 
-We implemented a prototype of \toolname in Python 3.8. 
+We implemented \toolname in Python 3.8. 
 We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
-with 256 GB of main memory and an (unused) NVIDIA RTX 3090. 
+with 256 GB of main memory and an NVIDIA RTX 3090 (not used for CMP). 
 Gurobi 9.52 was used for solving LP and MILP problems.
@@
 Hence more accurate methods are useful.
-The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (still high accuracy) to understand the scaling of CMP.
+The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (very high accuracy and few attacks) to understand the scaling of CMP.
 Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{crown}.
@@
 we evaluated CMP on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ for the first 1000 images of the dataset.
-For $6\times 500$ (results not reported in \cite{prima,crown}), we run all the tools ourselves for the first 200 images, given the computational overhead associated with such larger networks.
+For $6\times 500$ (results not reported in \cite{prima,crown}), we run all the tools ourselves for the first 200 images, given the computational overhead associated with such larger network.
 Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
@@
 \begin{itemize}
-	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}. We report the runtime from our  implementation in \toolname. 
+	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}. We report the runtime from our  implementation in CMP. 
 	%It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA). 
@@
 Notice that PRIMA and CROWN run 16 CPU threads for the first 4 benchmarks, and use massively parallel (>4000 threads) GPUs on $6\times500$, compared to 20 CPU threads for CMP on all DNNs.
-	\item We also tested MN-BaB \cite{ferrari2022complete} on $6\times500$
-	(slightly lower accuracy and slower than $\alpha$,$\beta$CROWN), 
+	\item We also tested MN-BaB \cite{ferrari2022complete} on $6\times500$ using the GPU
+	(slightly lower accuracy and slower than $\alpha$,$\beta$-CROWN), 
 	in line with results reported in \cite{ferrari2022complete} for other DNNs.
@@
 	\item How does the the choice of the set $Z$ impacts the accuracy of $\MILP_Z$? 
-	\item  How does the performance, measured as the percentage of images verified, of \toolname compare to that of prior state of the art approaches? 
-%	\item Evaluate how the runtime of \toolname scales with the size of DNNs.
+	\item Can compensating strength, as implemented in CMP, outperform accuracy of the SOTA? 
 \end{enumerate}
@@
 To measure the impact of the heuristic based on compensation strength, we focused on the smallest DNN (i.e.
-of size $5\times 100$ \cite{crown}) so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
-We test over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
+$5\times 100$) so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
+We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
 
@@
 We then average the uncertainty among all the nodes of the layer.
-Formally, for a node $n$ with bounds $[\alpha,\beta]$, its uncertainty $unc(a) = \beta - \alpha$, and the average uncertainty of a layer $l$ is $\dfrac{\sum_{a\in l} unc(a)}{|l|}.$
+Formally, the uncertainty of a node $n$ with bounds $[\alpha,\beta]$ is $unc(a) = \beta - \alpha$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$
 
@@
 %We do this for all node $c$ of the second layer.
+
+\iffalse
 
@@
 \subsubsection*{ReLU Node in the first and second hidden layer}
+\fi
 
-We now turn to evaluating the choice of ReLU nodes in two layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
-The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. Let $d$ be a neuron of the third layer.
-We keep the previous evaluation for ranking nodes in the previous (second) layer. 
-Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ from the first layer to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$.
-We thus define:
-%\vspace{-0.2cm}
-$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ and the associated $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$.
-We then select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
-{\color{red} The intuition behind the formula is straightforward: $\val_{\vx}(a)weight(abcd)$ is the simple contribution from node $a$ to the target $d$.
-And min of two paths is a natural value to represent the strength of compensation: if one of them is very small, the effect of compensation will also be very small.}
+\begin{table}[t!]	
+	\centering
+	\begin{tabular}{|c||c|c|c|}
+		\hline
+		\text{Number $K$}  &  \text{Compensate} &  \text{Incoming Weights} \cite{9211410} & \text{Random} \\ \hline
+		\hline
+		0  &  1.761 & 1.761 & 1.761  \\ \hline
+		10  &  1.648 & 1.651 & 1.696  \\ \hline
+		20  &  1.527 & 1.557 & 1.619  \\ \hline
+		30  &  1.402 & 1.489 & 1.546  \\ \hline
+		40  &  1.281 & 1.447 & 1.469  \\ \hline
+		50  &  1.165 & 1.426 & 1.388  \\ \hline
+		116 (max) &  0.895 & 1.424 & 0.895  \\ \hline
+	\end{tabular}
+	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs random choice).}
+	\label{tab:example1}
+	\vspace{-0.6cm}
+\end{table}
 
-We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly from layers $1$ and $2$.
-We compare choosing nodes in the second layer only with choosing nodes in both the first and second layer.
+We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
+The bounds for nodes of the first two layers are computed exactly using the full MILP encoding.
+Let $d$ be a neuron of the third layer.
+We let $\delta_{\pi,\pi'}=1$ if $(\pi,\pi')$ is compensating, 0 otherwise.
+We evaluate the pair $(c,c')$ of nodes in the previous (second) layer in the following way: let $comp(c,c')=\sum_{b} \delta(bcd,bc'd) \val_{\vx}(b) \min( weight(bcd),weight(bc'd))$, meaning that we take into account all the sources $b$ such that $(bcd,bc'd)$ is compensating.
+
+We select the pair $(c,c')$ with the highest $comp(c,c')$, and let $Z=\{c,c'\}$.
+Then, we add nodes iteratively to $Z$, starting with the highest $comp(c)=\sum_{c' \in Z} comp(c,c')$.
+Further, we can add nodes $b$ from the first layer, taking into account compensating pairs $(a b c d, a b' c' d)$ for all $\{c,c'\} \in C$.
+Let $comp(b,b')=\sum_a \sum_{c,c' \in Z} \delta(abcd,ab'c'd) \val_{\vx}(a) \min( weight(abcd)$, $weight(ab'c'd))$ and add $b,b'$ to $Z$ with the highest $comp(b,b')$.
+We then let $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$, and iteratively select nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
+The intuition behind the formula is straightforward: $\val_{\vx}(a)weight(abcd)$ is the contribution from node $a$ to the target $d$ using $weight(abcd)$, and min of two paths is a natural value to represent the strength of compensation: if one of them is very small, the effect of compensation will also be very small.
+
+We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes from layers $1$ and $2$.
+We test using compensation, compared with a random choice, and also choice based on strength in \cite{9211410}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$.
+It is however limited to chosing ReLU in the previous layer 2.
+This choice is fine for few nodes (10,20), as there is a high corelation between $comp(c)$ being high and $W_{cd}$ being high.
+However, as soon as many nodes can be chosen in $Z$, compensate becomes much more accurate.
+Even random becomes more accurate as the number of nodes grows, as \cite{9211410} only has access to nodes $c$ in layer 2, and not to nodes $b$ in layer 1.
+For comparison, compensate is the most accurate, from 30 nodes, experimentally validating that compensating strength is the important factor to consider.
+
+\iffalse
 Choosing ReLU nodes in the previous layer (layer $2$) only is less accurate than 
@@
 }
+\fi
 
-\begin{table}[t!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|}
-		\hline
-		\text{Number $K$}  &  \text{Compensate layer} 1+2 &  \text{{\color{red}Quick Method} layer} 2 & \text{Random layer } 1+2 \\ \hline
-		\hline
-		0  &  1.761 & 1.761 & 1.761  \\ \hline
-		10  &  1.656 & 1.651 & 1.696  \\ \hline
-		20  &  1.527 & 1.557 & 1.619  \\ \hline
-		30  &  1.402 & 1.489 & 1.546  \\ \hline
-		40  &  1.281 & 1.447 & 1.469  \\ \hline
-		50  &  1.165 & 1.426 & 1.388  \\ \hline
-		116 (max) &  0.895 & 1.424 & 0.895  \\ \hline
-	\end{tabular}
-	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs random choice).}
-	\label{tab:example1}
-	\vspace{-0.6cm}
-
-\end{table}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
 
@@
 
-We present the runtime and accuracy analysis of various techniques in Table~\ref{tab:example}. Further, for each DNN, a PGD-attack \cite{attack} is run 
-on all the images. We report the $\%$ of images without attack, as being an {\em Upper Bound} on the $\%$ of images the vertifiers can certify.
+We present the accuracy analysis of various techniques in Table~\ref{tab:example}, and provide runtime for reference. Further, for each DNN, a PGD-attack \cite{attack} is run 
+on all the images. We report the $\%$ of images without attack, giving an {\em Upper Bound} on the $\%$ of images that can be certified.
 
@@
 On the shallowest DNNs (5 layers, $5 \times 100$, $5 \times 200$), \toolname accuracy is close to $\beta$-CROWN, within 1.5\%.
-Here, RefinedBaB used by $\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough that its very accurate.
-
-As network sizes increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN. For instance, for $8 \times 100$ and $8 \times 200$, 
+Here, RefinedBaB used by $\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough that it is very accurate.
+As network depth increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN. For $8 \times 100$ and $8 \times 200$, 
 RefinedBaB used by $\beta$-CROWN can only consider half of the layers. 
-On many images, there are too many branches for BaB left to consider, and it times out,
-reason why we close the gap of undetermined images from $17.6\%$ ($\beta$-CROWN) to $10.4\%$ (\toolname) in $8 \times 200$.
-
-As expected, there's a trade-off between runtime and accuracy: \toolname can verify more images, albeit at the cost of increased computation time.
-However, more often than not, our primary concern lies in running a tool to determine whether it can verify the desired property within a reasonable time.
-
-The last network $6 \times 500$ (trained naturally) is the largest one.
-Results were not reported in \cite{crown,prima}.
-On this larger network, the refined strategy of PRIMA and $\alpha,\beta$-CROWN is questionable, as the number of binary variables to encode even the first few layers is very large, and the efficiency of MILP unclear.
-As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are
-surprisingly inaccurate and fast in PRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined.
-We reported the standard pureBaB setting of $\alpha,\beta$-CROWN instead, with the usual 30s associated timeout.
-Accuracy on $\alpha,\beta$-CROWN was also very low, only $15\%$ more images verified than DeepPoly.
-To understand the impact of runtime, we also experimented with a 2000s timeout for $\alpha,\beta$-CROWN.
-It only improves the accuracy by $3.5\%$, at $44.5\%$, with a runtime of $954s$ ($50$ times longer than with the original $30s$ timeout).
-We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard DNN.
-For comparison, \toolname could verify more than $20\%$ more images than
-even $\alpha,\beta$-CROWN with the longest timeout, taking less than $0.3s$ per neuron to perform the verification in average per image.
-
-% BaB focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary.
-Instead, we consider every node one by one from the input layer till the final layer, with the same accuracy.
-Hence {\toolname} will spend a lot of time on nodes which are not necessary for the verification.
-% 
-%It is worth remarking that our prototype implementation (in Python)  Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $1.4$ to 
-%$6.5$ times slower than $\beta$-CROWN. Notice {\toolname} it is not using GPUs. 
-%Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), refined BaB uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting of {\toolname}, with a small difference of less than $1.5\%$.
-On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in refined BaB cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
-%the most accurate setting (slow fixed) of {\toolname} is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
-%and from $17.6\%$ to $10.4\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in {\toolname} (see Section \ref{Discussion}).
-
-%Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
-This is very promising for this idea of compensation, which indirectly treats dependencies between the variables, which PRIMA represents explicitly.
-
-%In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
-%DeepPoly/CROWN is by far the fastest, but also the most inaccurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
-%This is because these DNNs, although of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
-
-%Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall pipeline is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
-%Now, moving on to PRIMA, our 
-%Our method compare favorably, both in terms of time and accuracy: our fast adaptive setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except for $5 \times 200$ which is quite pointless on this shallow DNN - the fast fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
-Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
-This is very promising for this idea of compensation, which indirectly treats dependencies between the variables, which PRIMA represents explicitly.
-
-\newcolumntype{C}{>{\centering\arraybackslash}X}
+On many images, there are too many branches for BaB left to consider, and it times-out.
+As expected, there's a trade-off between runtime and accuracy: \toolname can verify more images, albeit with increased computation time.
+Overall, on $8 \times 200$, CMP closes the gap of {\em undetermined} images from $17.6\%$ ($\beta$-CROWN) to $10.4\%$ (CMP).
 
@@
 \end{table}
+
+The last network $6 \times 500$ (verification-agnostic) is the largest one. 
+Results for CMP are good, at $65\%$ of verified images, comparable with $8\times 100$, taking less than $0.3s$ per neuron to perform the verification in average per image (there are more neurons, so longer runtime was expected).
+For comparison, results for $6 \times 500$ were not reported in \cite{crown,prima}.
+On this larger network, it is unclear whether the refined strategy of PRIMA and of $(\alpha)\beta$-CROWN is applicable, as the number of binary variables to encode even the first few layers is very large.
+As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are surprisingly inaccurate and fast in refinedPRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined.
+We thus resort and reported the standard pureBaB setting of $\alpha,\beta$-CROWN, with the usual 30s associated timeout.
+Accuracy on $\alpha,\beta$-CROWN is very low, only $15\%$ more images verified than DeepPoly.
+We also provided $\alpha,\beta$-CROWN with similar average time as CMP, setting the time-out at 2000s, giving $954s$ in average runtime ($925s$ for CMP). This only improved the accuracy 
+of $\alpha,\beta$-CROWN by $3.5\%$, at $44.5\%$, with a runtime $50$ times longer.
+We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard DNN.
+We also experimented MN-BaB \cite{ferrari2022complete} on $6 \times 500$.
+Results were similar to $\alpha,\beta$-CROWN: $40\%$ (18s) [30s Time-out] and $43\%$ (1036s) [2000s Time-out]; within 1.5\% of $\alpha,\beta$-CROWN.
+For comparison, CMP could verify more than $20\%$ more images than $\alpha,\beta$-CROWN (or MN-BaB) with similar runtime (around 17min per image).
+
+% BaB focuses on the output neuron, computing bounds for it, and refining the different ReLU as necessary.
+Instead, we consider every node one by one from the input layer till the final layer, with the same accuracy.
+Hence {\toolname} will spend a lot of time on nodes which are not necessary for the verification.
+% 
+%It is worth remarking that our prototype implementation (in Python)  Therefore, our naive implementation is not as efficient as the highly optimized $\beta$-CROWN: our slow setting is $1.4$ to 
+%$6.5$ times slower than $\beta$-CROWN. Notice {\toolname} it is not using GPUs. 
+%Concerning accuracy: on shallower DNNs ($5 \times 100$ and $5 \times 200$ with $5$ hidden layers), refined BaB uses MILP on all but the last $2$ layers, leaving BaB with few ReLU nodes to branch on, and $\beta$-CROWN (refined BaB) is slightly more accurate than using the slow fixed setting of {\toolname}, with a small difference of less than $1.5\%$.
+On deeper DNNs ($8 \times 100$ and $8 \times 200$ with $8$ hidden layers), the full MILP used in refined BaB cannot treat the last $4$ layers, and BaB has more ReLU nodes to branch on:
+%the most accurate setting (slow fixed) of {\toolname} is more accurate than $\beta$-CROWN, closing the gap with the upper bound from $20\%$ to $16.2\%$ ($8 \times 100$)
+%and from $17.6\%$ to $10.4\%$ ($8 \times 200$). This is very promising for the compensation idea, which could be used in many different ways than in {\toolname} (see Section \ref{Discussion}).
+
+%Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
+This is very promising for this idea of compensation, which indirectly treats dependencies between the variables, which PRIMA represents explicitly.
+
+%In Table \ref{tab:example}, we report the accuracy and runtime of these different methods.
+%DeepPoly/CROWN is by far the fastest, but also the most inaccurate, certifying robustness for less than $30\%$ of the images, whereas there are at least $82\%$ of the images for which no attacked is found (attacks computed by \cite{attack} in $\beta$-CROWN).
+%This is because these DNNs, although of reasonable size, are hard to verify (they are trained in a natural way, with high compensation strength, see Section \ref{Sec.comp}).
+
+%Compared with PRIMA (using refinement of the first few layers by exact MILP), the overall pipeline is quite similar, looking at all the nodes one by one from the beginning of the network till the end.
+%Now, moving on to PRIMA, our 
+%Our method compare favorably, both in terms of time and accuracy: our fast adaptive setting is always faster than PRIMA, sometimes by a large margin ($>3$ times faster on $8 \times 100$ while verifying $10\%$ more images), and also more accurate (except for $5 \times 200$ which is quite pointless on this shallow DNN - the fast fixed method is both faster and more accurate than PRIMA), sometimes by a large margin (by $14 \%$  for $5 \times 100$ while being $30\%$ faster).
+Further, unlike PRIMA, we do not resort to a GPU, and our purely Python implementation is not optimal.
+This is very promising for this idea of compensation, which indirectly treats dependencies between the variables, which PRIMA represents explicitly.
 

### 2024-04-26 lipics-master/Paper_noProof.tex
till experiments
14 pages

@@
 We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
-We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.
+This is experimentally confirmed by the fact that DNNs harder to verify (verification-agnostic) also exhibit paths with larger compensating strength than  robustly-trained DNNs.
 
-Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation yields highly accurate results.
-Additionally, we observed that the runtime can be advantageous in certain scenarios, though not universally.
+Based on this idea of compensating pairs of paths, we proposed the $\MILP_{Z}$ abstraction considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
+Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation can yield highly accurate results, up to 20\% than SOTA within the same runtime, again validating the focus on compensating strength.
 This underscores the potential of compensating strength as an innovative and promising avenue for enhancing DNN verification.
  We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.
-
 \newpage

### 2024-04-26 lipics-master/experiments.tex
14 pages

@@
 	\caption{$\%$ of verified images and average runtime in seconds.
-		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
+		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}, except for $6 \times 500$ for which we run every verifier ourselves.
 	}
@@
 
-In this work, we focused on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function.
-However, it is worth remarking that the notion of compensation strength is independent of  activation function, and therefore, an interesting direction of future work would be to explore other the impact of compensation strength-based approaches for other activation functions.
+CMP ranks highly in terms of accuracy, on the moderatly large network (but challenging verification-agnostic) DNNs we experimented with.
+Even if the CMP complexity is not subject to combinatorial explosion, its runtime, particularly for larger DNNs, can be relatively slow, as CMP needs to consider every node one by one.
+Tackling much larger networks may thus need different implementation than CMP, while still benefitting from the novel compensation notion we uncovered and validated thanks to CMP.
+Numerous avenues exist:
 
-Regarding accuracy, {\toolname} ranks highly among verifiers that abstract values.
-However, its runtime, particularly for larger DNNs, can be relatively slow, though not excessively so.
-Numerous optimization avenues exist.
 A primary strategy involves utilizing $\alpha$-$\beta$-CROWN initially in the sequence, reserving {\toolname} for images unresolved by $\alpha$-$\beta$-CROWN, potentially enhancing this with parallel node computation across additional CPU cores.
@@
 Although precise local accuracy is achieved by directly considering ReLU nodes, the accuracy diminishes when correlations originate from distant layers.
-Retaining a select few significant correlations, in the style of PRIMA, as explicit linear constraints in the MILP model, might offer a strategy to further improve accuracy.
+Retaining a select few significant correlations, in the style of PRIMA, as explicit linear constraints in the MILP model, might offer a strategy to further improve accuracy while keeping the number of binary variables limited.
+
+Finally, we focused on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function.
+However, it is worth remarking that the notion of compensation strength is independent of activation function, and therefore, an interesting direction of future work would be to explore other the impact of compensation strength-based approaches for other activation functions.

### 2024-04-26 lipics-master/Paper_noProof.tex
submitted 1

@@
 Based on this idea of compensating pairs of paths, we proposed the $\MILP_{Z}$ abstraction considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation can yield highly accurate results, up to 20\% than SOTA within the same runtime, again validating the focus on compensating strength.
+Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation can yield highly accurate results, up to 20\% more accurate than SOTA within the same runtime, again validating the focus on compensating strength.
 This underscores the potential of compensating strength as an innovative and promising avenue for enhancing DNN verification.

### 2024-04-27 lipics-master/comppaths.tex
Add files via upload
update

@@
 	\item $B_{zero}= \{n \mid \forall \text{ path $\rho$ from $n$ to } z, weight(\rho)=0\}$.
-	\item $B_{open}$ is the set of neurones reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
+	\item $B_{open}$ is the set of neurons reachable with $>0$ weight from $A_{open}$ and such that there is at least one path to $z$ with non zero weight.
 	\item $B_{pure}$ is the set of remaining neurons.

### 2024-04-27 lipics-master/proofs.tex
Add files via upload
update

@@
 
-{\color{red}Notice that above definitions only involve weights, and do not use bias.
+{Notice that above definitions only involve weights, and do not use bias.
 As demonstrated by the following lemmas and proofs, our discussion is independent of bias, regardless of whether the bias values are very large or very small.}
@@
 
-{\color{red} As we mentioned earlier, this proof does not have any requirements on the bias.}
+{ As we mentioned earlier, this proof does not have any requirements on the bias.}
 
@@
 
-		{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not consider bias, and any kind of bias will not affect our theorem.}
+		{ 	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not consider bias, and any kind of bias will not affect our theorem.}
+
+		\begin{figure}[h]
+			\centering
+			\begin{tikzpicture}[>=stealth, node distance=2cm]
+				% Input nodes (two types)
+				\node[circle, draw, minimum size=0.5cm] (input1) at (-1,0) {$a_0$};
+				\node[circle, draw, minimum size=0.5cm] (input2) at (-2,0) {$a_1$};
+				\node[circle, draw, minimum size=0.5cm] (input3) at (-4,0) {$a_2$};
+
+				\node[circle, draw, minimum size=0.5cm] (input4) at (-5,0) {$a_3$};
+				\node[circle, draw, minimum size=0.5cm] (input5) at (-7,0) {$a_4$};
+				\node[circle, draw, minimum size=0.5cm] (input6) at (-8,0) {$a_5$};
+
+				\draw[draw=black, dashed] (-1.5,0) ellipse (1.35 and 0.75);
+				\node[below] at (-1.5,-0.75) {$A_{zero}$};
+
+				\draw[draw=black, dashed] (-2,2) ellipse (0.75 and 0.75);
+				\node[right] at (-1,2) {$B_{zero}$};
+
+				% Hidden layer nodes
+
+				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden1) at (-2,2) {$n_0$};
+
+				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden2) at (-4,2) {$n_1$};
+				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden3) at (-5,2) {$n_2$};
+
+				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden4) at (-7,2) {$n_3$};
+				\node[circle, draw, minimum size=0.5cm, fill=blue!20] (hidden5) at (-8,2) {$n_4$};
+
+				\draw[draw=black, dashed] (-4.5,0) ellipse (1.35 and 0.75);
+				\node[below] at (-4.5,-0.75) {$A_{pure}$};
+
+				\draw[draw=black, dashed] (-7.5,0) ellipse (1.35 and 0.75);
+				\node[below] at (-7.5,-0.75) {$A_{open}$};
+
+				\draw[draw=black, dashed] (-4.5,2) ellipse (1.35 and 0.75);
+				\node[left] at (-3.5,3) {$B_{pure}$};
+
+				\draw[draw=black, dashed] (-7.5,2) ellipse (1.35 and 0.75);
+				\node[left] at (-8.5,1.5) {$B_{open}$};
+
+				% Output node
+				\node[circle, draw, minimum size=0.8cm, fill=red!20] (output) at (-5,4) {$z$};
+
+				% connections
+
+				\draw[->] (input1) -- (hidden1);
+
+				\draw[->] (input3) -- (hidden5);
+
+				\draw[->] (input4) -- (hidden4);
+
+				%		% Connect input to hidden layer
+				\foreach \i in {3,4} {
+					\foreach \h in {3,2} {
+						\draw[line width=1.5pt, ->] (input\i) -- (hidden\h);
+					}
+				}
+
+				\foreach \i in {5,6} {
+					\foreach \h in {4,5} {
+						\draw[->] (input\i) -- (hidden\h);
+					}
+				}
+				%		
+				% Connect hidden layer to output
+				\foreach \h in {2,3} {
+					\draw[line width=1pt,->] (hidden\h) -- (output);
+				}
+
+				\foreach \h in {4,5} {
+					\draw[->] (hidden\h) -- (output);
+				}
+
+				%\		% Input label
+				\node[left=0.7cm of input6] {Input Layer};
+
+				% Hidden label
+				\node[left=0.7cm of hidden5] {Hidden Layer};
+
+				% Output label
+				\node[left=0.5cm of output] {Output Layer};
+			\end{tikzpicture}
+			\caption{Definitions in the proof of Theorem \ref{th2}}
+			\label{fig:neural_network_types_simplified}
+		\end{figure}
 
@@
 
-{\color{red} In all the statements and proofs above, we do not make any assumptions about bias, and bias will not affect our discussion. }
+{ In all the statements and proofs above, we do not make any assumptions about bias, and bias will not affect our discussion. }
 
@@
 This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected.
-{\color{red} Moreover, this hypothesis only matters in the theoretical proof.
+{ Moreover, this hypothesis only matters in the theoretical proof.
 This is because in practice, paths with zero or very small weights will have very small effect on the output, and very small effect on the models, too.

### 2024-04-27 lipics-master/valabstraction.tex
Add files via upload
update

@@
 
-An extremely efficient algorithm that alleviates some of the inacuraccies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}.
+An extremely efficient algorithm that alleviates some of the inaccuracies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}.
 Instead of fixed bounds for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$.

### 2024-04-27 lipics-master/comppaths.tex
changes

--- 2024-04-26 lipics-master/comppaths.tex
@@
 Consider a target neuron $z$.
-In case there is no compensating path, we can assign a sign to each neuron $n$: 0
+In case there is no compensating path, we can assign a "sign" $S(n)$ to each neuron $n$: $S(n)=0$
 if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
@@
 
-We can then prove that $\vx^\star,\vx^\sharp$ maximize and minimize conjointly all the nodes in the DNN. Notice that it does {\em not} mean that there is no dependencies between nodes.
-There can be correlations between nodes, just they do not affect the $\min$ and $\max$ bounds that can be reached in any node.
+We can then prove that $\vx^\star,\vx^\sharp$ maximize and minimize conjointly all the nodes in the DNN. It does {\em not} mean that there is no dependencies between nodes.
+There can be correlations between nodes, but they do not affect the $\min$ and $\max$ bounds that can be reached.
 
@@
 	\label{prop.sign}
-	${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  
-	${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
+	${\vx^\star}$ maximizes (${\vx^\sharp}$ minimizes) the value of all positive neurons 
+	and minimizes (${\vx^\sharp}$ maximizes) the value of all negative neurons.
 \end{proposition}
@@
 Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. The full proof is in appendix A.
+for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. 
+Notice that biases have no impact on $S(n)$ (it is {\em not} the sign of )nor the
+
+The full proof is in appendix A.
 

### 2024-04-27 lipics-master/experiments.tex

@@
 We test using compensation, compared with a random choice, and also choice based on strength in \cite{9211410}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$.
-It is however limited to chosing ReLU in the previous layer 2.
-This choice is fine for few nodes (10,20), as there is a high corelation between $comp(c)$ being high and $W_{cd}$ being high.
+It is however limited to choosing ReLU in the previous layer 2.
+This choice is fine for few nodes (10,20), as there is a high correlation between $comp(c)$ being high and $W_{cd}$ being high.
 However, as soon as many nodes can be chosen in $Z$, compensate becomes much more accurate.
@@
 
-CMP ranks highly in terms of accuracy, on the moderatly large network (but challenging verification-agnostic) DNNs we experimented with.
+CMP ranks highly in terms of accuracy, on the moderately large network (but challenging verification-agnostic) DNNs we experimented with.
 Even if the CMP complexity is not subject to combinatorial explosion, its runtime, particularly for larger DNNs, can be relatively slow, as CMP needs to consider every node one by one.

### 2024-04-27 lipics-master/relatedwork.tex

@@
 MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP instance instead of CMP's many small instances, which significantly reduce the number of binary variables necessary for each instance.
-In \cite{9211410}, small instances are also considered, however with a straightfoward choice of binary nodes based on the weight of outgoing edge, therefore restricted to nodes in the previous layer, which is significantly less accurate than using compensating strength (see Table \ref{tab:example1}).
+In \cite{9211410}, small instances are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edge, therefore restricted to nodes in the previous layer, which is significantly less accurate than using compensating strength (see Table \ref{tab:example1}).
 

### 2024-04-27 lipics-master/comppaths.tex
influence sign + bias

@@
 Theorem \ref{th2} states that the bounds $[\alpha,\beta]$ for neuron $n$, as computed by MILP${X_n}$, are accurate, thereby offering an algorithm for DNN verification in scenarios involving compensating paths.
-We will provide the proof under a fairly light well-connected hypothesis (H1), which only very specific DNNs does not satisfy, namely very sparse DNNs where almost all weights are 0.
+We provide the proof in Section \ref{sec.proofs2}, under a fairly light well-connected hypothesis (H1), which only very sparse DNNs where almost all weights are 0 does not satisfy.
 (H1) removes some corner cases, simplifying the proof.
 
-(H1) for every 2 (not necessarily totally disjoint) paths $\rho_1 \neq \rho_2$ with non-zero weight with the same source $m$ and the same target $n$ with at least 2 transitions, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target).
+(H1) for every 2 (not necessarily totally disjoint) paths $\rho_1 \neq \rho_2$ with at least 2 non-zero transitions with the same source $m$ and target $n$, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target).
 
@@
 
-The sketch of proof of Theorem \ref{th2} can be found in Section \ref{sec.proofs2}.
-
 \subsection{Sketch of Proof for Theorem \ref{th1}}
@@
 Consider a target neuron $z$.
-In case there is no compensating path, we can assign a "sign" $S(n)$ to each neuron $n$: $S(n)=0$
-if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
-$-1$ if they have negative weights. %Using the concept of sign, 
-We introduce
-% input vectors 
-$\vx^{*}, \vx^{\sharp}$:
+In case there is no compensating path, we can assign an "influence sign" $S(n)$ to each neuron $n$: $S(n)=0$ if all paths from $n$ to $z$ has weight 0, $S(n)=+1$ if all paths have positive weights, and $S(n)=-1$ if they have negative weights.
+E.g., $S(n)=-1$ means that $\val_{\vx}(z)$ will increase if $\val_{\vx}(n)$ decreases.
+Specifically, $S(n)$ is {\em not} the sign of $\val_{\vx}(n)$, and biases have no impact on  $S(n)$: bias in $n$ changes $\val_{\vx}(n)$, not $S(n)$, while biases in between $n$ and $z$ will not change the influence of $\val_{\vx}(n)$ over $\val_{\vx}(z)$ (though it will change $\val_{\vx}(z)$ itself).
+We introduce $\vx^{*}, \vx^{\sharp}$:
+%Using the concept of sign,
 
 \begin{definition}
-We define the following two input vectors $\vx^{*}, \vx^{\sharp}$ in $\cal B$: 
+Let $\vx^{*}, \vx^{\sharp}$ be the two input vectors in $\cal B$ such that: 
 	\begin{itemize}
@@
 We can then prove that $\vx^\star,\vx^\sharp$ maximize and minimize conjointly all the nodes in the DNN. It does {\em not} mean that there is no dependencies between nodes.
-There can be correlations between nodes, but they do not affect the $\min$ and $\max$ bounds that can be reached.
+There can be correlations between nodes, but they do not affect the $\min$ and $\max$ values that can be reached.
 
@@
 Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. 
-Notice that biases have no impact on $S(n)$ (it is {\em not} the sign of )nor the
-
-The full proof is in appendix A.
+for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. The full proof is in appendix A.
 

### 2024-04-27 lipics-master/comppaths.tex
prop 7

@@
 	\label{prop.sign}
-	${\vx^\star}$ maximizes (${\vx^\sharp}$ minimizes) the value of all positive neurons 
-	and minimizes (${\vx^\sharp}$ maximizes) the value of all negative neurons.
+	$\max_{\vx} (\val_{\vx} (n)) = \val_{\vx^\star}(n)$ if $S(n)=+1$,
+	and $\val_{\vx^\sharp}(n)$ if $S(n)=-1$; and 
+	$\min_{\vx} (\val_{\vx} (n)) = \val_{\vx^\sharp}(n)$ if $S(n)=+1$,
+	and $\val_{\vx^\star}(n)$ if $S(n)=-1$, for all $n$.
 \end{proposition}

### 2024-04-27 lipics-master/comppaths.tex
also changed in 4.3 sketch of TH5

@@
 
-We cannot define the Sign function on nodes from which a compensating path can be reached.
-However, we can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
-Further, the set of nodes on which the sign function is defined is suffix-closed:
+We cannot define the influence sign function $S$ on nodes from which a compensating path can be reached. However, we can define $S(n)$ for neurons $n$ in $A_{pure}$ and $B_{pure}$.
+Further, the set of nodes $n$ on which the $S(n)$ is defined is suffix-closed:
 

### 2024-04-27 lipics-master/experiments.tex
typo editing

@@
 As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are surprisingly inaccurate and fast in refinedPRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined.
-We thus resort and reported the standard pureBaB setting of $\alpha,\beta$-CROWN, with the usual 30s associated timeout.
+We thus resort and reported the standard pureBaB setting of $\alpha,\beta$-CROWN, with the usual 30s timeout.
 Accuracy on $\alpha,\beta$-CROWN is very low, only $15\%$ more images verified than DeepPoly.
-We also provided $\alpha,\beta$-CROWN with similar average time as CMP, setting the time-out at 2000s, giving $954s$ in average runtime ($925s$ for CMP). This only improved the accuracy 
-of $\alpha,\beta$-CROWN by $3.5\%$, at $44.5\%$, with a runtime $50$ times longer.
-We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard DNN.
+We also tested $\alpha,\beta$-CROWN with longer time-out, to understand $\alpha,\beta$-CROWN scaling.
+With time-out=$2000s$, the runtime of $\alpha,\beta$-CROWN is $954s$, comparable with $925s$ for CMP.
+This only improved the accuracy of $\alpha,\beta$-CROWN by $3.5\%$, at $44.5\%$, with a runtime $50$ times longer.
+We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard verification-agnostic DNN.
 We also experimented MN-BaB \cite{ferrari2022complete} on $6 \times 500$.

### 2024-04-29 lipics-master/proofs.tex
update

@@
 We fix a target node $z$.
-We now define the partial sign function $S^z$, denoted $S$ when $z$ is clear from the context:
+We now define the partial influence sign function $S^z$, denoted $S$ when $z$ is clear from the context:
 
@@
 	\label{sign_of_nodes}
-	We define the partial sign function $S$ on node $n$: 	
+	We define the partial influence sign function $S$ on node $n$: 	
 	\begin{enumerate}
@@
 \begin{proof}
-	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $z$ with a nonzero weight of the same sign as $S(n)$. 
-	So there is a non zero path from $m$ to $z$: $(m n) \pi$, whose sign is 
+	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $z$ with a nonzero weight of the same influence sign as $S(n)$. 
+	So there is a non zero path from $m$ to $z$: $(m n) \pi$, whose influence sign is 
 	$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
@@
 
-Using the concept of sign, we introduce input vectors $\vx^{*}, \vx^{\sharp}$:
+Using the concept of influence sign, we introduce input vectors $\vx^{*}, \vx^{\sharp}$:
 
@@
 
-	Let $n$ be node of the DNN. We set the target $z=n$ and consider the sign function $S^z=S^n=S$ corresponding to that node. By definition, $S(n)=1$.
+	Let $n$ be node of the DNN. We set the target $z=n$ and consider the influence sign function $S^z=S^n=S$ corresponding to that node. By definition, $S(n)=1$.
 
@@
 		Assume that there is no compensating pair.
-		It means that all the segment of $\rho_1,\rho_2$ from $n_i$ to $n_{i+1}$ have the same sign (they have no nodes in common but the initial and final nodes).
-		Hence $\rho_1$ and $\rho_2$ have the same sign, a contradiction with $\rho_1,\rho_2$ being a weakly compensating pair. 
+		It means that all the segment of $\rho_1,\rho_2$ from $n_i$ to $n_{i+1}$ have the same influence sign (they have no nodes in common but the initial and final nodes).
+		Hence $\rho_1$ and $\rho_2$ have the same influence sign, a contradiction with $\rho_1,\rho_2$ being a weakly compensating pair. 
 	\end{proof}
@@
 
-			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. 
-			Because weakly compensating paths are allowed, the sign function is no longer defined on all nodes.
+			Recall the influence sign function of nodes from Definition \ref{sign_of_nodes}. 
+			Because weakly compensating paths are allowed, the influence sign function is no longer defined on all nodes.
 $S$ is defined for all nodes from which there is no weakly compensating pairs of paths to $z$.
@@
 				By contradiction, assume that there exists two paths $\rho_1,\rho_2$ from 
-				$n$ to $z$ with (strictly) different signs. The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$. 
+				$n$ to $z$ with (strictly) different influence signs. The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$. 
 			\end{proof}
@@
 					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{bc}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{bc} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
-				\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$.
+				\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the influence sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$.
 Notice that all $b$ displayed are that $S(b)$ defined, because if $S(b)$ undefined, then for fixed $\vx_J$, value of $b$ is fixed and will be put into the constant.
@@
 				Now by induction hypothesis part 2, if $S(b)=1$, then $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\max_{\vx_I}\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$; and if $S(b)=-1$, $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\min_{\vx_I}\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$.
-Moreover, since $S(c)=1$, $S(b)$ and $W_{bc}$ have the same sign.
+Moreover, since $S(c)=1$, $S(b)$ and $W_{bc}$ have the same influence sign.
 And both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions.
@@
 The weights of $(\rho_0 \cdot \rho_1 \cdot \rho_3, \rho_0\cdot \rho_2 \cdot \rho_3)$
-are of opposite sign because $(\rho_1,\rho_2)$ is weakly compensating, so one of them must be of opposite sign than the weight of $\rho'$. Say its $\rho = \rho_0 \cdot \rho_1 \cdot \rho_3$
+are of opposite influence sign because $(\rho_1,\rho_2)$ is weakly compensating, so one of them must be of opposite influence sign than the weight of $\rho'$.
+Say its $\rho = \rho_0 \cdot \rho_1 \cdot \rho_3$
 else we pick $\rho=\rho_0\cdot \rho_2 \cdot \rho_3$.
@@
 if $m<n<z$ with $m \in Z$, then $n \in Z$.
-We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative sign.
+We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative influence signs.
 They form 2 independent subnetworks of the DNN.
@@
 			Because of (H1), nodes not in $Z$ (and not in the inputs) are in $X$:
-			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite sign. 
+			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite influence sign. 
 			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
 			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight.
-Depending on the sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$.
+Depending on the influence sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$.
 We call $X_*$ this subset $X$.
@@
 		Let $y \in Y_+$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
-		of paths  with weights of opposite sign with $\rho_1$ from $m$ to $y$ and 
+		of paths  with weights of opposite influence sign with $\rho_1$ from $m$ to $y$ and 
 		with $\rho_2$ from $m$ to $z$ (even non disjoint).
@@
   Let $\rho$ be a path from $y$ to $z$ (it has positive weight has $y \in Z_+$).
-  Hence $\rho_1 \rho, \rho_2$ have opposite sign, and they must meet before $z$.
+  Hence $\rho_1 \rho, \rho_2$ have opposite influence sign, and they must meet before $z$.
 
@@
   Hence $\rho_1$ must meet $\rho_2$ (that is before or at $y$).
-  Their weights must be of opposite sign, otherwise we can inductively reapplied the same argument to their suffixes.
+  Their weights must be of opposite influence sign, otherwise we can inductively reapplied the same argument to their suffixes.
   Let $\rho_1=\rho_1'\rho_1''$.
   Both $\rho_1 \cdot \rho$ and $\rho_2' \cdot \rho_1'' \cdot \rho$
-  are from $m$ to $z$ going through $y$, but with weights of opposite sign (as $\rho'_1$ and $\rho'_2$ have opposite sign).
+  are from $m$ to $z$ going through $y$, but with weights of opposite influence sign (as $\rho'_1$ and $\rho'_2$ have opposite influence sign).
   Now, by $(H1)$, there exists a path $\rho_3$ disjoint from $\rho_1 \cdot \rho$ and$\rho_2' \cdot \rho_1'' \cdot \rho$ from $m$ to $z$.
@@
 
-We have the same results for $y \in Y_-$, for paths $\rho_1, \rho_2$ of same sign:
+We have the same results for $y \in Y_-$, for paths $\rho_1, \rho_2$ of same influence sign:
 
@@
 	Let $y \in Y_-$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
-	of paths with weights of same sign with $\rho_1$ from $m$ to $y$ and 
+	of paths with weights of same influence sign with $\rho_1$ from $m$ to $y$ and 
 	with $\rho_2$ from $m$ to $z$ (even non disjoint).
@@
 
-As in the proof of Theorem \ref{thm:2}, we can then optimize $Y$ first on its own (considering the sign of every node), and consider its (direct and indirect) contribution to $z$ as biases, before optimizing the rest of the network.
+As in the proof of Theorem \ref{thm:2}, we can then optimize $Y$ first on its own (considering the influence sign of every node), and consider its (direct and indirect) contribution to $z$ as biases, before optimizing the rest of the network.
 This is exactly what $\MILP_X$ is doing:
@@
 	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
-	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same sign, 
-	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite sign than $\rho_1$.
-Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite sign.
-	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
+	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same influence sign, 
+	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite influence sign than $\rho_1$.
+Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite influence sign.
+	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite influence sign. 
 	We then apply Lemma \label{lemma11}, inductively then applying Lemma \label{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 
@@
 			Therefore, choose a path $Q$ from input to output with nonzero weight and disjoint from $P,P''$.
-Now, since weights of $P,P''$ have different signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path.
+Now, since weights of $P,P''$ have different influence signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path.
 This means $a$ will be opened.
@@
 if $m<n<z$ with $m \in Z$, then $n \in Z$.
-We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative sign.
+We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative influence signs.
 $X$ can intersect both $Z_+$ and $Z_-$.
@@
 \begin{proof}
-			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite sign. 
+			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite influence sign. 
 			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
 			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight.
-Depending on the sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$.
+Depending on the influence sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$.
 We call $X_*$ this subset $X$.
@@
 
-To prove Theorem \ref{th2}, we can then optimize $Y$ first on its own (considering the sign of every node): we first maximize all $n$ such that $S(n)=1$ and minimize all $n$ such that 
+To prove Theorem \ref{th2}, we can then optimize $Y$ first on its own (considering the influence sign of every node): we first maximize all $n$ such that $S(n)=1$ and minimize all $n$ such that 
 $S(n)=-1$ at the same time, i.e., with the same input values. And for every node $n$ in $Y$, the value computed is the same as actual lower and upper bounds of $n$.
@@
 	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
-	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same sign, 
-	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite sign than $\rho_1$.
-Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite sign.
-	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
+	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same influence sign, 
+	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite influence sign than $\rho_1$.
+Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite influence sign.
+	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite influence sign. 
 	We then apply Lemma \ref{lemma11}, inductively then applying Lemma \ref{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 

### 2024-04-30 Reports/tech_report1.tex
update report

@@
 
+\section{Nodes chosen method comparison tests}
+
+The date is 2024 04 30 (and some days before).
+
+We do two parts of test: one is for only considering length 3 paths, for layer 3 and 5. Another is considering length 3 and 4 paths, for layer 5.
+
+For part1, there is no parameter. And for part2, there is a parameter (let us call it $r$) when comparing values of nodes in layer 1 and layer 3.
+
 \end{document}

### 2024-04-30 lipics-master/experiments.tex

@@
 
-We implemented \toolname in Python 3.8. 
-We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
+We implemented \toolname in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
 with 256 GB of main memory and an NVIDIA RTX 3090 (not used for CMP).
-Gurobi 9.52 was used for solving LP and MILP problems.
 
@@
 	We report our experimental results for the $6\times500$ DNN as they are not available in prior work.
-Notice that PRIMA and CROWN run 16 CPU threads for the first 4 benchmarks, and use massively parallel (>4000 threads) GPUs on $6\times500$, compared to 20 CPU threads for CMP on all DNNs.
-	\item We also tested MN-BaB \cite{ferrari2022complete} on $6\times500$ using the GPU
+Notice that PRIMA and CROWN use massively parallel (>4000 threads) GPUs, and run 16 CPU threads for the first 4 benchmarks, compared with 20 CPU threads and no GPU for CMP.
+	\item We also tested MN-BaB \cite{ferrari2022complete} on $6\times500$
 	(slightly lower accuracy and slower than $\alpha$,$\beta$-CROWN), 
@@
 
-The  objective of our evaluation was to answer the following  questions:
+The  objectives of our evaluation was to answer the following  questions:
 

### 2024-04-30 Reports/tech_report1.tex
update report

@@
 
+When do the test of layer 5, we read the accurate bounds information (open all nodes) of layer 3: \verb*|Diamond_record_6_100image59_dictionary_with_end_layer3_2024_04_23_17_02_11.b|
+
+\subsection*{Method for part1}
+
+\subsection*{Methods for part2}
+
+The basic formula is as following:
+
+\begin{align*}
+	comp(b,b') &= \sum_{a}\sum_{c,c'\in C} u(a)\min(|W_{abcd}|,|W_{ab'c'd}|)\\
+	comp(b) &= \sum_{b'\in B} comp(b,b')
+\end{align*} Here, $d$ is the fixed target node. $B$ and $C$ are two specific sets. They can be all nodes in that layer, or more complex.
+
 \end{document}

### 2024-04-30 lipics-master/Paper_noProof.tex
some small edits

--- 2024-04-26 lipics-master/Paper_noProof.tex
@@
 \usetikzlibrary{positioning, arrows.meta,calc}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Based on this idea of compensating pairs of paths, we proposed the $\MILP_{Z}$ abstraction considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation can yield highly accurate results, up to 20\% than SOTA within the same runtime, again validating the focus on compensating strength.
+Our empirical studies revealed that CMP, selecting $Z$ to cover only {\em a few} paths with the most significant compensation, can yield highly accurate results, up to 20\% more accurate than SOTA within the same runtime, again validating the focus on compensating strength.
 This underscores the potential of compensating strength as an innovative and promising avenue for enhancing DNN verification.

### 2024-04-30 lipics-master/proofs.tex
some small edits

@@
 \section*{Appendix}
-As a first step to prove Theorems \ref{th1},\ref{th2}, 
+As a first step to prove Theorems \ref{th1} and \ref{th2}, 
 we will relax the compensating pairs notion to allows pairs of paths having nodes in common.
 Such a pair is called a {\em weak compensating pair}.
-We will then in a second step prove Theorems \ref{th1},\ref{th2} for the full definition of compensating pairs of paths.
+We will then in a second step prove Theorems \ref{th1} and \ref{th2} for the full definition of compensating pairs of paths.
 
@@
 Notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
-then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).
+then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal), for $\hat{b}=\texttt{ReLU}(b)$.
 
@@
 			\begin{theorem} \label{thm:2}	
-
 				Suppose $\mathcal{D}$ is a DNN with a unique output node $z$.

### 2024-04-30 Reports/tech_report1.tex

@@
 
+The basic formula is as following:
+
+\begin{align*}
+	comp(c,c') &= \sum_{b} u(b)\min(|W_{bcd}|,|W_{bc'd}|)\\
+	comp(c) &= \sum_{c'\in C} comp(c,c')
+\end{align*}
+Here, $d$ is the fixed target node.
+$C$ is a specific set.
+It can be the set of all nodes in that layer (denoted as ALL), or some thing more complex.
+The one we have tested is the set CURRENT: first pick two (or one) nodes by $comp(c,c')$ into the open node list, then
+
 \subsection*{Methods for part2}

### 2024-06-25 Reports/tech_report1.tex
update report

@@
 
+\subsection*{CURRENT or ALL}
+
+After a few tests, we decide to only use ALL-ALL for all cases: For length 3 part, we find ALL is significantly better; For length 4 part, ALL-ALL are the easiest to implement, and do not lose accuracy.
+
+\section{New Bootstrap Form}
+
+\section{Large test of layer 3 and layer 5 of 1023 cases}
+
+These tests consist of several parts: layer 3, layer 5 mixed 1 and 2, layer 5 open only layer 3, layer 5 open layer 1.
+
+\subsection*{Basic Scheme of tests}
+
+In each test, first use the standard/quick method to choose first 50/70 nodes for target layer. Then group 50/70 nodes in 10 groups. In $2^10-1$ cases, use corresponding nodes to open.
+
+The value $Imp(a,a',\cdots)$ of nodes $a,a',\cdots$ is the difference of average uncertainty of LP model and the model when only open nodes $a,a',\cdots$: Let $A=\{a,a',\cdots\}$, then $$Imp(A)=LP-MILP_A.$$
+
+The finding of these tests is that: $$Imp(A)\approx \sum_{a\in A} Imp(a).$$ We use $\dfrac{\sum_{a\in A} Imp(a)}{Imp(A)}$ to check how close they are.
+
+For each case $A_0$, its error means $$|\dfrac{\sum_{a\in A_0} Imp(a)}{Imp(A_0)}-Average_{A} \dfrac{\sum_{a\in A} Imp(a)}{Imp(A)}|.$$
+
+\subsection*{Layer 3}
+
+In the case, we open nodes in layer 1.
+
+The average quotient is 0.9893127409573279. The error is very small: in all 1023, no error is greater than 1\%.
+
+\subsection*{Layer 5, only open in layer 3}
+
+In this case, we open nodes in layer 3.
+
+The average quotient is 0.9930808321092559. The error is also very small: in all cases, the max error is 1.042\%.
+
+\subsection*{Layer 5, only open in layer 1}
+
+From now, the error and average become not so good. The average quotient is 0.9027497392008165, and the standard deviation of error is 3.01\%, the max error is about 10\%.
+
+\subsection*{Layer 5, both in layer 1 and layer 3}
+
+The error and average are still not so good. The average quotient is 0.8951295616274486, and the standard deviation of error is 3.7\%, the max error is about 10\%.
+
+From this we can guess that the error is mostly caused by nodes in layer 1 rather than layer 3.
+
 \end{document}

### 2024-08-14 Reports/tech_report1.tex

@@
 
+\subsection*{Layer 5, both in layer 1 and layer 3, separately}
+
+In this test we choose 30 nodes in layer 1 and 30 nodes in layer 3. Again they are grouped 5 by 5. We use $A,a,a'$ to denote nodes in layer 1, and use $B,b,b'$ to denote nodes in layer 3.
+
+And we define:  $$Imp^A(B)=MILP_{A}-MILP_{A\cup B}.$$ We still use $Imp(B)$ for $Imp^{\emptyset}(B)$.
+
+The aim of this section is to check, how can we compute $Imp^A(B)$?
+
+\subsubsection*{Based on $Imp^A$}
+
+If we use $Imp^A(b)$ to compute $Imp^A(B)$, then the accuracy is very high: $$Imp^A(B)\approx\sum_{b\in B} Imp^A(b).$$
+
+The average of $\dfrac{\sum_{b\in B} Imp^A(b)}{Imp^A(B)}$ is 1.0012830624338422, and the standard deviation over all cases is
+0.263 \%.
+
+However, this is not very useful since we must face more than one possible $A$ and we cannot compute $Imp^A(b)$ every-time.
+
+\subsubsection*{Based on $Imp$}
+
+In this case, the accuracy is relatively low: The average of $\dfrac{\sum_{b\in B} Imp(b)}{Imp^A(B)}$ is 0.8943970938704465, and the standard deviation over all cases is
+4.26 \%.
+
+However, this does not mean that $Imp(b)$ is useless.
+If we group $A$ by $\#(A)$ and compute the standard deviation group by group, then we will find it is much smaller.
+We use $\mu(n)$ to denote the average number of all $\dfrac{\sum_{b\in B} Imp(b)}{Imp^{A}(B)}$ that $\#(A)=n$.
+
+For $n$ in $0$ to $6$, $\mu(n)$ and corresponding standard deviations are:
+
+\vspace*{1ex}
+
+0.995, 0.30\%
+
+0.957, 0.98\%
+
+ 0.923, 1.68\%
+
+ 0.893, 2.25\%
+
+ 0.865, 2.71 \%
+
+ 0.839, 3.08 \%
+
+ 0.814, 3.45 \%
+
+It is reasonable that the average goes smaller and smaller.
+
+If we look at the absolute value of $Imp$, we will find that for almost all $A,B$, $$|Imp^A(B)-\frac{1}{\mu(\#(A))}(\sum_{b\in B} Imp(b))| < 0.01,$$ and this is usable.
+At least that we can still use $Imp(b)$ to sort nodes in layer 3 for any $A$.
+
+\section{Layer 7, large test 0}
+
+This is similar to the tests in last section but more simpler. We choose 35 nodes by our algorithm in layer 1, layer 3 and layer 5 separately, and group them 5 by 5 nodes.
+
+The difference is that, we do not consider all $2^{7+7+7}$ cases, but only consider about $7\times 7 \times 7$ cases: first $m\times 5$ nodes in layer 1, first $n\times 5$ nodes in layer 3 and first $l \times 5$ nodes in layer 5.
+
+We can count the information by node in layer 7.
+For example, when $n+m+l=10$ (50 nodes), we can count the best $[n,m,l]$ combinations for every node: the average is $[3.92,2.02,4.06]$.
+For $n+m+l=12$ (60 nodes), the average is $[4.92,2.81,4.27]$.
+This is consistent with our previous observations.
+
+However, although the average values are consistent with previous result, for a single node, the case can be very different: the deviation of $n,m$ is about 2, and there are a few nodes for which $m=7$ is the best.
+
 \end{document}

### 2024-08-14 ICLR25/experiments.tex
iclr25

--- 2024-04-30 lipics-master/experiments.tex
@@
 		0  &  1.761 & 1.761 & 1.761  \\ \hline
-		10  &  1.648 & 1.651 & 1.696  \\ \hline
-		20  &  1.527 & 1.557 & 1.619  \\ \hline
-		30  &  1.402 & 1.489 & 1.546  \\ \hline
-		40  &  1.281 & 1.447 & 1.469  \\ \hline
-		50  &  1.165 & 1.426 & 1.388  \\ \hline
-		116 (max) &  0.895 & 1.424 & 0.895  \\ \hline
+		10  &  1.641 & 1.651 & 1.696  \\ \hline
+		20  &  1.517 & 1.557 & 1.619  \\ \hline
+		30  &  1.392 & 1.489 & 1.546  \\ \hline
+		40  &  1.275 & 1.447 & 1.469  \\ \hline
+		50  &  1.158 & 1.426 & 1.388  \\ \hline
+		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
 	\end{tabular}
-	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs random choice).}
+	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs \cite{9211410} vs random choice).}
 	\label{tab:example1}
@@
 Here, RefinedBaB used by $\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough that it is very accurate.
-As network depth increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN. For $8 \times 100$ and $8 \times 200$, 
+As the network size increases, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN: For $8 \times 100$ and $8 \times 200$, 
 RefinedBaB used by $\beta$-CROWN can only consider half of the layers. 
@@
 For comparison, results for $6 \times 500$ were not reported in \cite{crown,prima}.
-On this larger network, it is unclear whether the refined strategy of PRIMA and of $(\alpha)\beta$-CROWN is applicable, as the number of binary variables to encode even the first few layers is very large.
-As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are surprisingly inaccurate and fast in refinedPRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined.
+On this larger network, it is unclear whether the {\em refined strategy} of PRIMA and of $(\alpha)\beta$-CROWN is applicable, as the number of binary variables to encode even the first few layers is very large.
+As a matter of fact, refinedBaB is "NotImplemented" in $(\alpha),\beta$-CROWN for this network, and the results are surprisingly inaccurate and fast in refinedPRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined.
 We thus resort and reported the standard pureBaB setting of $\alpha,\beta$-CROWN, with the usual 30s timeout.
@@
 Finally, we focused on DNNs employing ReLU activation functions since our approached on usage of MILP, which is naturally suited for ReLU activation function.
-However, it is worth remarking that the notion of compensation strength is independent of activation function, and therefore, an interesting direction of future work would be to explore other the impact of compensation strength-based approaches for other activation functions.
+However, it is worth remarking that the notion of compensation strength is independent of activation function, and therefore, an interesting direction of future work would be to explore the impact of compensation strength-based approaches for other activation functions.

### 2024-08-19 ICLR25/Paper_noProof.tex
Add paper in new format

--- 2024-04-30 lipics-master/Paper_noProof.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
+\documentclass{article} % For LaTeX2e
+\usepackage{iclr2025_conference,times}
+% Optional math commands from https://github.com/goodfeli/dlbook_notation.
+\input{math_commands.tex}
+
+\usepackage{hyperref}
+\usepackage{url}
 \pagestyle{plain}
@@
 
-\newcommand{\vx}{\boldsymbol{x}}
-\newcommand{\vy}{\boldsymbol{y}}
 \newcommand{\vW}{\boldsymbol{W}}
-\newcommand{\vz}{\boldsymbol{z}}
-\newcommand{\vb}{\boldsymbol{bias}}
+
 \newcommand{\val}{{\textrm{value}}}
@@
 
-%\usepackage{amsmath, amsthm, amssymb, amsfonts}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{corollary}{Corollary}
-%\theoremstyle{definition}
-%\newtheorem{definition}{Definition}
+\usepackage{amsmath, amsthm, amssymb, amsfonts}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
@@
 
-\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
-\date{}
+\title{Formatting Instructions for ICLR 2025 \\ Conference Submissions}
 
-%\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}
+% Authors must not appear in the submitted version. They should be hidden
+% as long as the \iclrfinalcopy macro remains commented out below.
+% Non-anonymous submissions will be rejected without review.
 
-%\author{Blaise Genest}{IPAL Lab, CNRS and CNRS@CREATE, France and Singapore}{blaise.genest@cnrsatcreate.sg}{}{}
+\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
+about author (webpage, alternative address)---\emph{not} for acknowledging
+funding agencies.  Funding acknowledgements go at the end of the paper.} \\
+Department of Computer Science\\
+Cranberry-Lemon University\\
+Pittsburgh, PA 15213, USA \\
+\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
+\And
+Ji Q. Ren \& Yevgeny LeNet \\
+Department of Computational Neuroscience \\
+University of the Witwatersrand \\
+Joburg, South Africa \\
+\texttt{\{robot,net\}@wits.ac.za} \\
+\AND
+Coauthor \\
+Affiliation \\
+Address \\
+\texttt{email}
+}
 
-%\author{Kuldeep Meel}{University of Toronto, Canada}{ meel@cs.toronto.edu}{}{}
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to \LaTeX{} to determine where to break
+% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
+% puts 3 of 4 authors names on the first line, and the last on the second
+% line, try using \AND instead of \And before the third author name.
 
-%\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
 
-%\author{John Q.
-Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
-%\authorrunning{Y. Liao, B. Genest, K. Meel and S. Aryaman} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
-
-\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords
-
-%\Copyright{Liao Yuke, Blaise Genest, Kuldeep Meel and Shaan Aryaman} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[100]{} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
+%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
@@
 \begin{abstract}
-
-		Deep Neural Networks (DNNs) verification has evolved into a robust field of research, furnished with a plethora of methodologies and tools designed for formal correctness verification.
-This area even boasts an annual competition to benchmark these tools.
-Formally, the question it addresses is whether a given DNN upholds a specified property across a set of input data.
-For instance, it can ascertain local robustness around an input $\vx$ by verifying if the i-th output neuron consistently demonstrates the highest weight amongst all output neurons within a certain vicinity of $\vx$.
-In recent years, the focus has shifted towards integrating various efficient techniques—such as branch and bound, multi-neuron encoding, and MILP encoding—to optimize the balance between speed and accuracy.
-Although modern verifiers can efficiently validate relatively large DNNs (with tens of thousands of neurons), the challenge persists, especially when dealing with certain DNNs, even smaller ReLU DNNs comprising hundreds of neurons, thereby highlighting the ongoing need for innovative methodologies.
-
-		In this paper, we analyse efficient algorithms  for verifying ReLU DNNs, examining abstractions like DeepPoly, Linear Programming, PRIMA, and various versions of Crown.
-We identify the primary cause of accuracy loss: {\em compensations}.
-Compensations occur when dual paths exist between a neuron pair, with one path carrying positive weights and the other negative, leading to a partial offset.
-However, accurately quantifying this offset is complex due to the ReLU activation functions.
-Leveraging this insight, we introduce a novel approach for achieving promising speed-accuracy trade-offs.
-This involves conducting numerous queries with a limited number of 'open' ReLU nodes (considering both linear modes) rather than the traditional approach of fewer queries with potentially many 'open' ReLU nodes.
-These findings not only present practical implications but also pave the way for various applications of the concept of compensating paths in the realm of DNN verification.
-
+The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
+right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
+The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
+line spaces precede the abstract. The abstract must be limited to one
+paragraph.
 \end{abstract}
@@
 \input{introduction}
-
+%
 \input{relatedwork}
@@
 In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-	capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{prima,crown}.
+capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in.
 To simplify the notations, we restrict the presentation to feed-forward, 
@@
 
-\bibliographystyle{plain}
 \bibliography{references}
+\bibliographystyle{iclr2025_conference}
 
@@
 \end{document}
-
-\section{Ranking of Compensating Pairs}
-
-In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.
-
-Based on No Diamond Theorem, for a target node, in its MILP model, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node.
-However, in practice, this is still too expensive because we will still need to open too many nodes.
-So we can only choose a limited number of compensating pairs and nodes.
-This is by setting a parameter $O$ such that the process only choose at most $O$ many nodes to open.
-Therefore, in this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.
-
-Basically, we do the process of open nodes chosen for one target node each time, that is, receive one target node (and other data) as input each time.
-But in principle, we can develop a method receive more than one nodes as input.
-But in our experiences, this does not work well.
-
-This process is not the unique method but the most natural way to choose open nodes. We introduce it in three steps from the simplest case to more complex case.
-
-\subsubsection*{Value of a pair}
-
-For a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.
-
-\subsection*{Case: Source node fixed}
-
-The simplest case is when we only consider compensating pairs with a fixed source node.
-
-In this case, the process is very simple: enumerate all compensating pairs, and then sort them by their values.
-Finally, from the first to the last compensating pair, pick all unstable nodes in its two paths except the target and source nodes into the list of open nodes, until $O$ many open nodes.
-
-%\subsubsection*{Sort all paths by values}
-%
-%The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.
-%
-%Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.
-%
-%\subsubsection*{Sort pairs by values}
-%
-%The second step is to sort all pairs by their values.
-Enumerate paths from the positive group and the negative group one by one and put the pairs obtained into a new list of pairs.
-Then sort all pair by their values from largest to the smallest: recall that the value of a pair $\langle P_1,P_2\rangle$ is $\min(|V_1|,|V_2|)$.
-%
-%\subsubsection*{Choosing nodes}
-%
-%The third step is to choose nodes from the list of pairs.
-According to the sorted list of pairs, enumerate pair one by one; for each pair, pick the nodes unstable in the two paths except the source and target node into the open node list.
-Repeat this process until $O$ nodes chosen or reach the end of the list.
-%
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-%
-
-\subsection*{Case: Source nodes in one layer}
-
-The more general case is when the source node can be any node in a fixed layer. In this case, the process is very similar to previous case, except the value of a pair.
-
-In this case, for a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, its value is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
-
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-
-\subsection*{Case: Source nodes in different layers}
-
-The general case is that when the location of source nodes can be in different layers.
-This case is much more complex, because the scale level of values of paths from different layers are very different: usually a weight will be very small since every layer has a large number of nodes, therefore values of longer paths are products of more small numbers, and is definitely much smaller.
-If we sort all compensating pairs from different layers directly, then a very long initial segment of this list will be occupied by compensating pairs with the shortest length.
-Therefore, we need use some scale factors when comparing values of compensating pairs of different length.
-
-In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before).
-We will dynamically adjust the values during the process of node chosen.
-In text, the process of node chosen for length 3 plus length 4 is as follows:
-
-\vspace*{1ex}
-
-1. Generate the two lists of pairs sorted by their values for source nodes in 2 layers before the target node and 3 layers before separately as in the previous case.
-
-2.
-Enumerate pair from two lists one by one by their values and pick nodes as previous case.
-When comparing the values between pairs of length 4 and pairs of length 3, multiply the numbers of nodes in 1 layer before to the value of pair of length 4.
-
-In formula, when the target node is in layer $L$, for a pair $P_3$ of length 3 with value $V_3$ and a pair $P_4$ of length 4 with value $V_4$, if we have chosen $N$ nodes in layer $L-1$.
-Then the adjusted values for $P_3$ and $P_4$ are: $$V_3, N\cdot V_4.$$ Then we pick the next pair by the adjust value in two lists.
-
-3. Repeat 2 until choosing sufficiently many nodes.
-
-\vspace*{1ex}
-
-The pseudo-code is as follows ():
-
-\begin{algorithm}
-\caption{Process for length 3 + length 4}
-\KwData{Sorted lists of length 3 + length 4}
-\KwResult{Open node list}
-
-Let $N = 0$ be the number of Chosen length 4 pair.
-
-\While{len(Open node) $<O$}{
-	Pick the first element $P_3$ in the list of length 3\;
-
-	Let $V_3$ be the value of $P_3$\;
-
-	Pick the first element $P_4$ in the list of length 4\;
-
-	Let $V_4$ be the value of $P_4$\;
-
-	\If{$V_3 > V_4 \cdot N$}{
-		Add nodes in $P_3$ into Open list\;
-		Number of Chosen lentgh pair $N$ += 1\; 
-	}
-	\Else{
-		Add nodes in $P_4$ into Open list\;
-	}
-}
-\end{algorithm}
-
-\end{document}

### 2024-08-19 ICLR25/comppaths.tex
Add paper in new format

--- 2024-04-27 lipics-master/comppaths.tex
@@
 In case there is no compensating path, we can assign an "influence sign" $S(n)$ to each neuron $n$: $S(n)=0$ if all paths from $n$ to $z$ has weight 0, $S(n)=+1$ if all paths have positive weights, and $S(n)=-1$ if they have negative weights.
-E.g., $S(n)=-1$ means that $\val_{\vx}(z)$ will increase if $\val_{\vx}(n)$ decreases.
+E.g., $S(n)=-1$ means that $\val_{\vx}(z)$ will deacrese if $\val_{\vx}(n)$ increases.
 Specifically, $S(n)$ is {\em not} the sign of $\val_{\vx}(n)$, and biases have no impact on  $S(n)$: bias in $n$ changes $\val_{\vx}(n)$, not $S(n)$, while biases in between $n$ and $z$ will not change the influence of $\val_{\vx}(n)$ over $\val_{\vx}(z)$ (though it will change $\val_{\vx}(z)$ itself).
@@
 
-Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
-for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. The full proof is in appendix A.
+We can then prove that $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
+for $[\alpha, \beta]$ computed by the Box abstraction. 
+We conclude Theorem \ref{th1} by continuity. The full proof is in appendix A.
 
@@
 \begin{proposition}
-For a node $b$ with $S(b)=1$ and $b'$ with $S(b())=-1$:
+For a node $b$ with $S(b)=1$ and $b'$ with $S(b)=-1$:
 
@@
 
-Theorem \ref{th2} theoretically computes accurate bounds by iteratively applying MILP$_{X}$ to each node, layer by layer.
+Theorem \ref{th2} theoretically computes accurate bounds by iteratively applying MILP$_{X_n}$ to each node $n$, layer by layer.
 Practically, however, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$.
@@
 
-CMP($K$) has a worst case complexity bounded by $O(N \MILP(N,K))$, 
+CMP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
 where $N$ is the number of nodes of the DNN, 

### 2024-08-19 ICLR25/introduction.tex
Add paper in new format

--- 2024-04-25 lipics-master/introduction.tex
@@
 The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
-However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which the efficient tools try to avoid because it is very time-consuming (combinatioral explosion as the problem is NP-hard \cite{Reluplex}).
+However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which the efficient tools try to avoid because it is very time-consuming (combinatorial explosion as the problem is NP-hard \cite{Reluplex}).
 %; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust. 
@@
 	 as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate. This is confirmed experimentally by the fact that 
-	 DNNs easier to verified have less compensation strenght than verification agnostic DNNs. 
+	 DNNs easier to verified have less compensation strength than verification agnostic DNNs. 
 	This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs.

### 2024-08-28 Reports/tech_report1.tex
update report

@@
 
+\section{Tests about CNN-B-adv}
+
+CNN-B-adv has 1 input layer of 3072 nodes, 3 hidden layers with node numbers: 8k, 8k, 250, and 1 output layer. Our tests is doing on the first 100 images of the default dataset.
+
+We will do 3 steps:
+
+\begin{enumerate}
+	\item Run beta-Crown with Timeout = 30s. After that, we will continue on unknown images: they are harder.
+
+	\item Run fast turn: the first mode of fast turn uses the follow: open 200 nodes by standard algorithm for layer 3, LP for layer 5, and 40 (layer 3+layer 5) + 160 (layer 1) for layer 7.
+The Timeout for layer 7 is 1 hour with 4 min a loop x 15 loops.
+
+	\item Run slow turn: the global Timeout is 10000s, so we will try a slow turn for images failed in fast turn.
+We use the data of layer 3 obtained in fast turn, and open 25 nodes for 250 nodes in layer 5.
+
+	For layer 7, the process is more complex: to decide the open numbers. The key idea is to use the improvement values obtained by formula to estimate the possible solution.
+
+	\item  Second version of fast: however, it seems to be not good.
+\end{enumerate}
+
 \end{document}

### 2024-09-12 ICLR25/formula.tex
formula section

\section*{Formula}

One of the key formula is to choose some nodes and set the corresponding variables to be binary variable in the MILP model. We will say that we open those nodes. In our algorithm, we will open nodes at most 3 layer3 before the target layer. So the formula will consists of three parts.

\subsubsection*{Observation}

The key of our formula is based on the following observation:

\begin{definition}[Improvement]

	Let $a$ be a node in the network (at least the second hidden layer) and we have computed a series of lower and upper bound for all nodes before the layer of $a$. If we consider to compute the upper bound of $a$ by the standard MILP model.

	\begin{enumerate}
		\item $M^a_X$ means the MILP model with target node $a$ and open node set $X$. $M^a_{\emptyset}$ is the LP model for $a$.

		\item For a set $X$, if the upper bound of $a$ computed from $M^a_{\emptyset}$ is $u_0$, and from $M^a_X$ is $u_X$, then the improvement (of upper bound of $a$) of $X$, $I_X$ (or $I_X^{a,u}$) is defined as : $$I_X = u_0-u_X.$$ 
	\end{enumerate}
\end{definition}

Similarly we can define the improvement of lower bound to be $I_X^{a,l} = l_X-l_0$.

Our observation (by experiments) is that \begin{align*}
	I_X \approx \sum_{b\in X} I_b.
\end{align*} Separately, if all nodes in $X$ are from the layer before $a$, then in experiments, we observe that

\begin{align*}
	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
\end{align*} And even $X$ comes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.

Therefore, based on this observation, the question to choose $X$ is convert to compute $I_b$ for nodes $b$ in 3 layers before the target layer.

\subsubsection*{Compute the improvement of a single node}

The formula to compute the improvement of a single node is the actual content of our formula. For different layers, the formula will be different.

For one layer before the target layer, it is very simple and more accurate. Notice that, either the observation in last subsection, or formula in this subsection, does not have solid theoretical proof to show they are very accurate. They are all based on experiments.

Suppose $b$ is a node one layer before $a$. To compute $I_b$, we need to run $M^a_{\emptyset}$ to compute the upper bound of $a$ first to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.

\begin{definition}
	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.

	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align*}
		I_b \approx W_{ba}(v(\hat{b})-\ReLU(v(b))).
	\end{align*}

	Specially, if $v(\hat{b})=\ReLU(v(b))$, then \begin{align*}
		I_b = W_{ba}(v(\hat{b})-\ReLU(v(b))) = 0.
	\end{align*}

	Similarly, let $v(b)$ be the value of $b$ in the LP solution of lower bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.

	Then the formula to estimate improvement of lower bound of $b$ is: \begin{align*}
		I_b \approx -W_{ba}(v(\hat{b})-\ReLU(v(b))).
	\end{align*}

\end{definition}

To explain the formula, we use upper bound and $W_{ba} > 0$ as an example. To compute the upper bound of $a$, $\hat{b}$ should be as large as possible. In the LP model, for fixed $v(b)$, the upper bound of $\hat{b}$ may be larger than $\ReLU(v(b))$. This is because in LP model, the upper bound of $v(\hat{b})$ is decided by the linear approximation rather than $\ReLU$ function. So, then node $b$ is open, if values before $v(\hat{b})$ do not change, the the upper bound of $a$ will improve by lower $v(\hat{b})$ to $\ReLU(v(b))$.

Of course changing other variables may effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major source of improvement.

For earlier layers, the formula will be more complex and less accurate. But we will still focus on the source $v(\hat{b})-\ReLU(v(b))$.

\subsubsection*{Two layers before the target layer}

Basically, we hope to use $\sum_c W_{ca}W_{bc}$ to replace the coefficient $W_{bc}$ in last subsection.

However, directly replace $W_{ba}$ with the new coefficient will lose too much accuracy. So we try to improve the accuracy by considering more details from the LP solutions.

For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative. And as we discussed in last subsection, $W_{ca}$ can decide whether $v(\hat{c})$ is more close $\ReLU(v(c))$ or the linear approximation. That is the following definition.

\begin{definition}
	For a fixed target node $a$ and a fixed source node $b$ in two layers before $a$. To compute the improvement of of upper bound of $a$ by $b$, we define the following function for nodes in 1 layer before $a$:
	\begin{align*}
		k(c) =
		\begin{cases}
			1, & \text{if } v(c) > 0 \text{ and } W_{ca} < 0\\
			0, & \text{if } v(c) \leq 0 \text{ and } W_{ca} < 0\\
			\frac{\UB(c)}{\UB(c)-\LB(c)}, & \text{if }W_{ca} > 0
		\end{cases}
	\end{align*} and use the following formula to compute the estimation of improvement: \begin{align*}
	I_b = (v(\hat{b})-\ReLU(v(b)))\sum_c W_{bc}W_{ca}k(c)
	\end{align*}

\end{definition}

However, the error is still too large. This is because the improvement of a node $c$ can not exceed its precomputed upper and lower bound (we may use $UB(c)$ and $LB(c)$ to denote them). Considering this, we may improve our formula to the following:

\begin{definition}
	For a fixed target node $a$ and a fixed source node $b$ in two layers before $a$. Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models. To compute the improvement of of upper bound of $a$ by $b$, we use the following formula:

	We define a distance function $D$:

	\begin{align*}
		&D(b) = \ReLU(v(b))-v(\hat{b})\\
			&D(c) =
		\begin{cases}
			\max(\LB(c), 0, v(c)+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }W_{ca} < 0\\
			\min(\UB(c), v(\hat{c})+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }  W_{ca} > 0
		\end{cases}\\
		&D(a) = -\sum_c D(c)W_{ca}
	\end{align*}
\end{definition}

This is the formula to compute improvement of nodes two layers before.

\subsubsection*{Formula for nodes in 3 layers before}

This formula is based on previous subsection but more complex. In some network, run this formula may cost too much time.

The key problem is that, how to compute the coefficient $k$ for nodes in 2 layers before the target layer. We use the following method to estimate the coefficient.

\begin{definition}\label{3layer}
	For a fixed target node $a$ and a fixed source node $b$ in two layers before $a$. Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models. To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model;then we define the following function $k$, so that for a node $c$ in 2 layers before the target node $a$, the value $k(c)$ is computed as:
	\begin{align*}
		&v_0 = v(\hat{c}), v_1 = \ReLU(v(c)), v_2 = \frac{\UB(c)v(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
		&k(c) =
		\begin{cases}
			\frac{v_0-v_1}{v_2-v_1}, & \text{if } v_2-v_1 > 0\\
			0.5, & \text{otherwise.}
		\end{cases}
	\end{align*} 
\end{definition}

\begin{definition}
	Continue the assumption in Definition \ref{3layer}. We define function $D$ layer by layer.

	First, $D(b) = \ReLU(v(b))-v(\hat{b})$.

For $c$ in the next layer, we define \begin{align*}
	&u_0 = \max(\LB(c),\min(\UB(c),  v(c)+D(b)W_{bc}))\\
	&u_1 = \begin{cases}
		\ReLU(u_0)+k(c)(\frac{\UB(c)u_0-\UB(c)\LB(c)}{\UB(c)-\LB(c)}-u_0), & \text{if }\LB(c) < 0\\
	u_0, & \text{if }  \LB(c) \geq 0
	\end{cases}\\
	&D(c) = u_1-v(\hat{c})
\end{align*}

	Next is to compute $D(d)$ for nodes $d$ in one layer before $a$.

	\begin{align*}
		&w_0 = \sum_C D(c)W_{cd}\\
		&w_1 = \min(\UB(d),v(d)+w_0)\\		
		&D(d) =
		\begin{cases}
			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
		\end{cases}\\
		&D(a) = -\sum_c D(d)W_{da}
	\end{align*}
\end{definition}

### 2024-09-12 ICLR25/formula.tex
update

@@
 
-This is the formula to compute improvement of nodes two layers before.
+$D(a)$ is the estimation of improvement of upper bound of $a$ by openning node $b$. This is the formula to compute improvement of nodes two layers before.
 
@@
 \begin{definition}
-	Continue the assumption in Definition \ref{3layer}. We define function $D$ layer by layer.
+	Continue the assumption in Definition \ref{3layer}. To compute the improvement of of upper bound of $a$ by $b$, we define function $D$ layer by layer.
 
@@
 	\end{align*}
-\end{definition}
+\end{definition}$D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.

### 2024-09-13 ICLR25/tables.tex
create file

The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks.

\section*{Tables}

\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	Network & Accuracy & Upper bound & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s &  0 \\ \hline
	MNIST 6$\times$100 & \% & 90\% & 33\% & 35\% & 40\% &  0 \\ \hline
	MNIST 6$\times$200 & \% & 96\% & 46\% & 49\% & 50\% &  0 \\ \hline
	MNIST 9$\times$100 & \% & 86\% & 23\% & 28\% & 28\% &  0 \\ \hline
	MNIST 9$\times$200 & \% & 91\% & 35\% & 36\% & 37\% &  0 \\ \hline
	MNIST 6$\times$500 & \% & 94\% & 41\% & 43\% & 44\% &  \% \\ \hline
	CIFAR CNN-B-adv & \% & 62\% & \% & 40\% & 42\% &  \% \\ \hline
	0 & 0 & 0 & 0 & 0 & 0 & 0  \\ \hline
\end{tabular}

\vspace*{4ex}
\begin{tabular}{|c|c|c|}
	\hline
	Verifier & Rate & Average time \\ \hline
	Marabou & 0 & 0 \\ \hline
	$\alpha,\beta$-Crown & 0 & 0 \\ \hline
	Full MILP & 0 & 0 \\ \hline
	0 & 0 & 0 \\ \hline
\end{tabular}

\vspace*{4ex}

The table of undecided images among first 100 images in database by different methods for different network.

\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
	& Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time\\ \hline
	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
	MNIST 6$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
	MNIST 9$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
	MNIST 9$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
\end{tabular}

### 2024-09-13 ICLR25/tables.tex
update

@@
-The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks.
+\section*{Tables}
 
-\section*{Tables}
+The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks. The numbers shown in the table is the rate of images in percentage.
 
@@
 	Network & Accuracy & Upper bound & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s &  0 \\ \hline
-	MNIST 6$\times$100 & \% & 90\% & 33\% & 35\% & 40\% &  0 \\ \hline
-	MNIST 6$\times$200 & \% & 96\% & 46\% & 49\% & 50\% &  0 \\ \hline
-	MNIST 9$\times$100 & \% & 86\% & 23\% & 28\% & 28\% &  0 \\ \hline
-	MNIST 9$\times$200 & \% & 91\% & 35\% & 36\% & 37\% &  0 \\ \hline
-	MNIST 6$\times$500 & \% & 94\% & 41\% & 43\% & 44\% &  \% \\ \hline
-	CIFAR CNN-B-adv & \% & 62\% & \% & 40\% & 42\% &  \% \\ \hline
+	MNIST 6$\times$100 &  & 90 & 33 & 35\% & 40  &  0 \\ \hline
+	MNIST 6$\times$200 &   & 96  & 46  & 49  & 50  &  0 \\ \hline
+	MNIST 9$\times$100 &   & 86  & 23  & 28  & 28  &  0 \\ \hline
+	MNIST 9$\times$200 &   & 91  & 35  & 36  & 37  &  0 \\ \hline
+	MNIST 6$\times$500 &   & 94  & 41  & 43  & 44  &    \\ \hline
+	CIFAR CNN-B-adv &   & 62  &   & 40  & 42  &    \\ \hline
 	0 & 0 & 0 & 0 & 0 & 0 & 0  \\ \hline
@@
 	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
-	& Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time\\ \hline
-	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 6$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 9$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 9$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
+	& Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s)\\ \hline
+	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & Rate \hfill Time & Rate \hfill Time \\ \hline
+	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & Rate \hfill Time & Rate \hfill Time \\ \hline
+	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & Rate \hfill Time & Rate \hfill Time \\ \hline
+	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & Rate \hfill Time & Rate \hfill Time \\ \hline
 	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline

### 2024-09-13 ICLR25/tables.tex
update

--- 2024-09-13 ICLR25/tables.tex
@@
-The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks.
-
 \section*{Tables}
 
-\begin{tabular}{|c|c|c|c|c|c|c|}
+The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks. The numbers shown in the table is the rate of images in percentage.
+
+\begin{tabular}{|c|c|c|c|c|c|}
 	\hline
-	Network & Accuracy & Upper bound & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s &  0 \\ \hline
-	MNIST 6$\times$100 & \% & 90\% & 33\% & 35\% & 40\% &  0 \\ \hline
-	MNIST 6$\times$200 & \% & 96\% & 46\% & 49\% & 50\% &  0 \\ \hline
-	MNIST 9$\times$100 & \% & 86\% & 23\% & 28\% & 28\% &  0 \\ \hline
-	MNIST 9$\times$200 & \% & 91\% & 35\% & 36\% & 37\% &  0 \\ \hline
-	MNIST 6$\times$500 & \% & 94\% & 41\% & 43\% & 44\% &  \% \\ \hline
-	CIFAR CNN-B-adv & \% & 62\% & \% & 40\% & 42\% &  \% \\ \hline
-	0 & 0 & 0 & 0 & 0 & 0 & 0  \\ \hline
+	Network & Accuracy & Upper bound & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s  \\ \hline
+	MNIST 6$\times$100 &  & 90 & 33 & 35 & 40   \\ \hline
+	MNIST 6$\times$200 &   & 96  & 46  & 49  & 50   \\ \hline
+	MNIST 9$\times$100 &   & 86  & 23  & 28  & 28   \\ \hline
+	MNIST 9$\times$200 &   & 91  & 35  & 36  & 37   \\ \hline
+	MNIST 6$\times$500 &   & 94  & 41  & 43  & 44   \\ \hline
+	CIFAR CNN-B-adv &   & 62  &   & 40  & 42   \\ \hline
+	0 & 0 & 0 & 0 & 0 & 0  \\ \hline
 \end{tabular}
@@
 	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
-	& Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time\\ \hline
-	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 6$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 9$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 9$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
+	& Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s)\\ \hline
+	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
+	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
+	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
+	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
+	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
 \end{tabular}

### 2024-09-15 ICLR25/Paper_noProof.tex
abstract

@@
 
-\title{Formatting Instructions for ICLR 2025 \\ Conference Submissions}
+\title{Partial MILP to improve $\alpha,\beta$-CROWN accuracy \\ for hard DNN verification instances}
 
@@
 \begin{abstract}
-The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
-right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
-The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
-line spaces precede the abstract. The abstract must be limited to one
-paragraph.
+$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best 
+trade-off between accuracy vs computational time. VNNcomp however is focusing on relatively easy verification instances (network, inputs (images)), 
+with few {\em unstable nodes}. In this paper, we consider harder verification instances, namely the usual local robustness problem, and 
+compare how different solutions out there fare.
+On such instances, $\alpha,\beta$-CROWN displays a large gap ($\approx 40\%$) between instances that can be verified, and instances with an explicit attack.
+Enabling much larger time-outs for $\alpha,\beta$-CROWN only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
+Resorting to other techniques, such as complete verifiers, does not fare better even with very large time-outs (10000s per instance): They would theoretically be able to close the gap, but with an untractable runtime on all but small instances, because the instances considered are hard.
+
+In this paper, we study the complete MILP encoding of ReLU-DNNs, provide new deep insights in the LP relaxation, which allows us to carefully craft a {\em partial MILP} solution which only considers few neurons as integer variables, the rest using the LP relaxation.
+Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
+This gives rise to a very efficient yet accurate algorithm.
+Implemented as $\alpha,\beta$-pMILP, calling first $\alpha,\beta$-CROWN with a short time-out (10s) to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances to $\approx 10\%$, while keeping a reasonable runtime ($<500s$ on average per instance).
 \end{abstract}

### 2024-09-16 ICLR25/Paper_noProof.tex
abstract
table in main doc

@@
 
+\section*{Tables}
+
+The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks. The numbers shown in the table is the rate of images in percentage.
+
+\begin{tabular}{||c|c|c||c|c|c||}
+	\hline
+	Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+	Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+
+	MNIST 6$\times$100 & 96\% & 90\% & 33\% & 35\% & 40\%   \\
+	$\epsilon = 0.026$ &  &  & ? &  18s &  1600s  \\  \hline
+    MNIST 6$\times$200 & 97\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+	$\epsilon = 0.015$ & &  & ? &  17s &  ?s  \\  \hline
+	MNIST 9$\times$100 & 95\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+	$\epsilon = 0.026$ &  &  & ? &  20s &  ?s  \\  \hline
+	MNIST 9$\times$200 & 95\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+	$\epsilon = 0.015$ & &  & 7s &  s &  ?s  \\  \hline
+	MNIST 6$\times$500 &  ? & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+	$\epsilon = 0.035$ & &  & 6s &  15s &  1002s  \\  \hline
+	CIFAR CNN-B-adv & ?  & 62\%  &  ? & 40\%  & 42\%   \\
+	 &  &  & s & s & s  \\ \hline \hline
+	CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+	Wong &  &  & 2s & 2s & 2s  \\ \hline
+
+\end{tabular}
+
+\vspace*{4ex}
+\begin{tabular}{|c|c|c|}
+	\hline
+	Verifier & Rate & Average time \\ \hline
+	Marabou & 0 & 0 \\ \hline
+	$\alpha,\beta$-Crown & 0 & 0 \\ \hline
+	Full MILP & 0 & 0 \\ \hline
+	0 & 0 & 0 \\ \hline
+\end{tabular}
+
+\vspace*{4ex}
+
+The table of undecided images among first 100 images in database by different methods for different network.
+
+\begin{tabular}{|c|c|c|c|c|c|}
+	\hline
+	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
+	& Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s)\\ \hline
+	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
+	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
+	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
+	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
+	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
+\end{tabular}
+
 	\section{Introduction}

### 2024-09-16 ICLR25/Paper_noProof.tex
edit

@@
 compare how different solutions out there fare.
-On such instances, $\alpha,\beta$-CROWN displays a large gap ($\approx 40\%$) between instances that can be verified, and instances with an explicit attack.
+On such instances, $\alpha,\beta$-CROWN displays a large gap ($20-58\%$) between instances that can be verified, and instances with an explicit attack.
 Enabling much larger time-outs for $\alpha,\beta$-CROWN only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
@@
 	$\epsilon = 0.035$ & &  & 6s &  15s &  1002s  \\  \hline
-	CIFAR CNN-B-adv & ?  & 62\%  &  ? & 40\%  & 42\%   \\
-	 &  &  & s & s & s  \\ \hline \hline
+	CIFAR CNN-B-adv & ?  & 62\%  &  40\% & 41\%  & 42\%   \\
+	 &  &  & 15s & 32s & 373s  \\ \hline \hline
 	CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-	Wong &  &  & 2s & 2s & 2s  \\ \hline
+	$\epsilon=2/255$ & : &  & 2s & 2s & 2s  \\ \hline
 

### 2024-09-16 ICLR25/Paper_noProof.tex
edits

--- 2024-09-15 ICLR25/Paper_noProof.tex
@@
 \end{abstract}
+
+\section*{Tables}
+
+The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks. The numbers shown in the table is the rate of images in percentage.
+
+\begin{tabular}{||c|c|c||c|c|c||}
+	\hline \hline
+	Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+	Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+	MNIST 6$\times$100 & 96\% & 90\% & 33\% & 35\% & 40\%   \\
+	$\epsilon = 0.026$ &  &  & ? &  18s &  1600s  \\  \hline
+    MNIST 6$\times$200 & 97\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+	$\epsilon = 0.015$ & &  & ? &  17s &  ?s  \\  \hline
+	MNIST 9$\times$100 & 95\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+	$\epsilon = 0.026$ &  &  & ? &  20s &  ?s  \\  \hline
+	MNIST 9$\times$200 & 95\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+	$\epsilon = 0.015$ & &  & 7s &  s &  ?s  \\  \hline
+	MNIST 6$\times$500 &  ? & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+	$\epsilon = 0.035$ & &  & 6s &  15s &  1002s  \\  \hline
+	CIFAR CNN-B-adv & ?  & 62\%  &  40\% & 41\%  & 42\%   \\
+	$\epsilon = 2/255$ &  &  & 15s & 32s & 373s  \\ \hline \hline
+	CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+	$\epsilon=2/255$ & : &  & 2s & 2s & 2s  \\ \hline \hline
+
+\end{tabular}
+
+SAME FORMAT for complete verifiers!!!
+
+\begin{tabular}{||c||c|c|c||}
+	\hline
+	Network &  Marabou  & Full MILP & NNenum? \\ \hline
+	MNIST 6$\times$100 & 26\% & 30\% & ?\%   \\ \hline
+	$\epsilon = 0.026$ & 6520s & 7000s s
+	 &  ?s  \\  \hline
+\end{tabular}
+
+\vspace*{4ex}
+
+Gap between verified and attackable images. Lower is better.
+%The table of undecided images among first 100 images in database by different methods for different network.
+
+\begin{tabular}{|c|c|c|c|c|c|}
+	\hline
+	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
+	& Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s)\\ \hline
+	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
+	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
+	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
+	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
+	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
+\end{tabular}
 

### 2024-09-16 ICLR25/Paper_noProof.tex
edit

@@
 Gap between verified and attackable images. Lower is better.
+M for MNIST, C for CIFAR
 %The table of undecided images among first 100 images in database by different methods for different network.
 
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{tabular}{||c||c|c|c|c||c||}
+	\hline \hline
+	Network & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\beta$-Crown & Our \\ 
+	 & TO=10s & TO=30s & TO=2000s & refine & Method \\
+
 	\hline
-	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
-	& Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s)\\ \hline
-	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
-	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
-	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
-	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
-	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
+
+	M 6$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
+	M 6$\times$200 & 50\% \hfill 6.5 & 47\% \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
+	M 9$\times$100 & 63\% \hfill 7.2 & 58\% \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
+	M 9$\times$200 & 56\% \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
+	M 6$\times$500 & ? \hfill ? & ? \hfill ? & ? \hfill ? & ? \hfill ? & Rate \hfill Time \\ \hline
+	C CNN-B-Adv & ? \hfill ? & ? \hfill ? & ? \hfill ? & ? \hfill ? & Rate \hfill Time \\ \hline \hline
+	C Resnet & 0\% \hfill 2s & 0\% \hfill 2s & 0\% \hfill 2s & 0\% \hfill 2s & 0\% \hfill 2s \\ \hline \hline
 \end{tabular}

### 2024-09-16 ICLR25/tables.tex

--- 2024-09-13 ICLR25/tables.tex
@@
-The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks.
-
 \section*{Tables}
 
-\begin{tabular}{|c|c|c|c|c|c|c|}
+The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks. The numbers shown in the table is the rate of images in percentage.
+
+\begin{table}
+	\centering
+	\caption{$\beta$-Crown}
+	\label{table_beta}
+	\begin{tabular}{||c|c|c||c|c|c||}
 		\hline
-	Network & Accuracy & Upper bound & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s &  0 \\ \hline
-	MNIST 6$\times$100 & \% & 90\% & 33\% & 35\% & 40\% &  0 \\ \hline
-	MNIST 6$\times$200 & \% & 96\% & 46\% & 49\% & 50\% &  0 \\ \hline
-	MNIST 9$\times$100 & \% & 86\% & 23\% & 28\% & 28\% &  0 \\ \hline
-	MNIST 9$\times$200 & \% & 91\% & 35\% & 36\% & 37\% &  0 \\ \hline
-	MNIST 6$\times$500 & \% & 94\% & 41\% & 43\% & 44\% &  \% \\ \hline
-	CIFAR CNN-B-adv & \% & 62\% & \% & 40\% & 42\% &  \% \\ \hline
-	0 & 0 & 0 & 0 & 0 & 0 & 0  \\ \hline
+		Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+
+		MNIST 6$\times$100 & 96\% & 90\% & 33\% & 35\% & 40\%   \\
+		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026.1s  \\  \hline
+		MNIST 6$\times$200 & 97\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930.3s  \\  \hline
+		MNIST 9$\times$100 & 95\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930.3s  \\  \hline
+		MNIST 9$\times$200 & 95\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083.1s  \\  \hline
+		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1002.5s  \\  \hline
+		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
+		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+		Wong &  &  & 2s & 2s & 2s  \\ \hline
 	\end{tabular}
+\end{table}
 
 \vspace*{4ex}
+
+The following table is the summary of running results of some complete verifier with timeout = 10000s.
+
+\begin{table}
+	\centering
+	\caption{Complete Verifiers}
+	\label{table_complete}
 	\begin{tabular}{|c|c|c|}
 		\hline
-	Verifier & Rate & Average time \\ \hline
-	Marabou & 0 & 0 \\ \hline
-	$\alpha,\beta$-Crown & 0 & 0 \\ \hline
+		Verifier & Rate(\%) & Average time (s) \\ \hline
+		Marabou & 28 & 6200  \\ \hline
+		NeVer2 & 0 & 0 \\ \hline
 		Full MILP & 0 & 0 \\ \hline
-	0 & 0 & 0 \\ \hline
 	\end{tabular}
+\end{table}
 
@@
 
+\begin{table}
+	\centering
+	\caption{Undecided images}
+	\label{table_undecided}
 	\begin{tabular}{|c|c|c|c|c|c|}
 		\hline
-	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
-	& Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time & Rate \hfill Time\\ \hline
-	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 6$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 9$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 9$\times$200 & 0 & 0 & 0 & 0 & 0 \\ \hline
-	MNIST 6$\times$100 & 0 & 0 & 0 & 0 & 0 \\ \hline
+		Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ 
+		& Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s)\\ \hline
+		MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & 13 \hfill 46 \\ \hline
+		MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & 8 \hfill 71 \\ \hline
+		MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & 15 \hfill 61 \\ \hline
+		MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & 8 \hfill 78 \\ \hline
+		MNIST 6$\times$500 & 53 \hfill 6.4 & 51 \hfill 16.4 & 50 \hfill 1002.5 & (cannot run) & 10 \hfill 402 \\ \hline
+		CIFAR CNN-B-adv & 28 \hfill 4.3 & 22 \hfill 8.7 & 20 \hfill 373 & N/A & 11 \hfill 417 \\ \hline
 	\end{tabular}
+\end{table}

### 2024-09-16 ICLR25/tables.tex
update tables.tex

--- 2024-09-13 ICLR25/tables.tex
@@
 
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{table}
+	\centering
+	\caption{$\alpha,\beta$-Crown with pure BaB}
+	\label{table_beta}
+	\begin{tabular}{||c|c|c||c|c|c||}
 		\hline
-	Network & Accuracy & Upper bound & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s  \\ \hline
-	MNIST 6$\times$100 &  & 90 & 33 & 35 & 40   \\ \hline
-	MNIST 6$\times$200 &   & 96  & 46  & 49  & 50   \\ \hline
-	MNIST 9$\times$100 &   & 86  & 23  & 28  & 28   \\ \hline
-	MNIST 9$\times$200 &   & 91  & 35  & 36  & 37   \\ \hline
-	MNIST 6$\times$500 &   & 94  & 41  & 43  & 44   \\ \hline
-	CIFAR CNN-B-adv &   & 62  &   & 40  & 42   \\ \hline
-	0 & 0 & 0 & 0 & 0 & 0  \\ \hline
+		Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+
+		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
+		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026.1s  \\  \hline
+		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930.3s  \\  \hline
+		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930.3s  \\  \hline
+		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083.1s  \\  \hline
+		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1002.5s  \\  \hline
+		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
+		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
 	\end{tabular}
+\end{table}
 
 \vspace*{4ex}
-\begin{tabular}{|c|c|c|}
+
+The following table is the summary of running results of some complete verifier with timeout = 10000s.
+
+\begin{table}
+	\centering
+	\caption{SAME FORMAT for complete verifiers!!!}
+	\label{table_complete}
+	\begin{tabular}{||c||c|c|c||}
 		\hline
-	Verifier & Rate & Average time \\ \hline
-	Marabou & 0 & 0 \\ \hline
-	$\alpha,\beta$-Crown & 0 & 0 \\ \hline
-	Full MILP & 0 & 0 \\ \hline
-	0 & 0 & 0 \\ \hline
+		Network &  Marabou  & Full MILP & NNenum? \\ \hline
+		MNIST 6$\times$100 & 26\% & 30\% & ?\%   \\ \hline
+		$\epsilon = 0.026$ & 6520s & 7000s
+		&  ?s  \\  \hline
 	\end{tabular}
+\end{table}
 
@@
 
+\begin{table}
+	\centering
+	\caption{Gap between verified and attackable images. Lower is better}
+	\label{table_undecided}
 	\begin{tabular}{|c|c|c|c|c|c|}
 		\hline
-	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
-	& Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s)\\ \hline
-	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
-	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
-	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
-	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
-	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
+		Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ 
+		& Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s)\\ \hline
+		MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & 13 \hfill 46 \\ \hline
+		MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & 8 \hfill 71 \\ \hline
+		MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & 15 \hfill 61 \\ \hline
+		MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & 8 \hfill 78 \\ \hline
+		MNIST 6$\times$500 & 53 \hfill 6.4 & 51 \hfill 16.4 & 50 \hfill 1002.5 & (cannot run) & 10 \hfill 402 \\ \hline
+		CIFAR CNN-B-adv & 28 \hfill 4.3 & 22 \hfill 8.7 & 20 \hfill 373 & N/A & 11 \hfill 417 \\ \hline
 	\end{tabular}
+\end{table}

### 2024-09-16 ICLR25/Paper_noProof.tex
table updated in main document

--- 2024-09-16 ICLR25/Paper_noProof.tex
@@
 
-\title{Partial MILP to improve $\alpha,\beta$-CROWN accuracy \\ for hard DNN verification instances}
+\title{Hybrid MILP to efficiently and accuratly \\  solve hard DNN verification instances}
 
@@
 trade-off between accuracy vs computational time. VNNcomp however is focusing on relatively easy verification instances (network, inputs (images)), 
-with few {\em unstable nodes}. In this paper, we consider harder verification instances, namely the usual local robustness problem, and 
-compare how different solutions out there fare.
+with few {\em unstable nodes}.
+In this paper, we consider harder verification instances, namely the usual local robustness problem.
 On such instances, $\alpha,\beta$-CROWN displays a large gap ($20-58\%$) between instances that can be verified, and instances with an explicit attack.
 Enabling much larger time-outs for $\alpha,\beta$-CROWN only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
-Resorting to other techniques, such as complete verifiers, does not fare better even with very large time-outs (10000s per instance): They would theoretically be able to close the gap, but with an untractable runtime on all but small instances, because the instances considered are hard.
+Resorting to other techniques, such as complete verifiers, does not fare better even with very large time-outs: They would theoretically be able to close the gap, but with an untractable runtime on all but small {\em hard} instances.
 
-In this paper, we study the complete MILP encoding of ReLU-DNNs, provide new deep insights in the LP relaxation, which allows us to carefully craft a {\em partial MILP} solution which only considers few neurons as integer variables, the rest using the LP relaxation.
+In this paper, we study the MILP encoding of ReLU-DNNs, provide new deep insights in the LP relaxation, which allows us to carefully craft a {\em partial MILP} solution which only considers few neurons as integer variables, the rest using the LP relaxation.
 Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
 This gives rise to a very efficient yet accurate algorithm.
-Implemented as $\alpha,\beta$-pMILP, calling first $\alpha,\beta$-CROWN with a short time-out (10s) to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances to $\approx 10\%$, while keeping a reasonable runtime ($<500s$ on average per instance).
+Implemented in {\em Hybrid MILP (hMILP)}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances to $\approx 10\%$, while keeping a reasonable runtime ($<500s$ on average per instance).
 \end{abstract}
@@
 
-\begin{tabular}{||c|c|c||c|c|c||}
-	\hline \hline
+\begin{table}
+	\centering
+	\begin{tabular}{||l|c|c||c|c|c||}
+		\hline
 		Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
 		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
-	MNIST 6$\times$100 & 96\% & 90\% & 33\% & 35\% & 40\%   \\
-	$\epsilon = 0.026$ &  &  & ? &  18s &  1600s  \\  \hline
-    MNIST 6$\times$200 & 97\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
-	$\epsilon = 0.015$ & &  & ? &  17s &  ?s  \\  \hline
-	MNIST 9$\times$100 & 95\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
-	$\epsilon = 0.026$ &  &  & ? &  20s &  ?s  \\  \hline
-	MNIST 9$\times$200 & 95\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
-	$\epsilon = 0.015$ & &  & 7s &  s &  ?s  \\  \hline
-	MNIST 6$\times$500 &  ? & 94\%  & 41\%  & 43\%  & 44\%   \\ 
-	$\epsilon = 0.035$ & &  & 6s &  15s &  1002s  \\  \hline
-	CIFAR CNN-B-adv & ?  & 62\%  &  40\% & 41\%  & 42\%   \\
-	$\epsilon = 2/255$ &  &  & 15s & 32s & 373s  \\ \hline \hline
+		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
+		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026.1s  \\  \hline
+		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930.3s  \\  \hline
+		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930.3s  \\  \hline
+		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083.1s  \\  \hline
+		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1002.5s  \\  \hline
+		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
 		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-	$\epsilon=2/255$ & : &  & 2s & 2s & 2s  \\ \hline \hline
-
+		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
 	\end{tabular}
+	\caption{Verification $\%$ of $\alpha,\beta$-Crown run on 7 DNNs (average runtime per image in second).
+The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
+	\label{table_beta}
+\end{table}
 
@@
 
-\begin{tabular}{||c||c|c|c||}
+\begin{table}
+	\centering
+\begin{tabular}{||l|c|c||c|c|c||}
 	\hline
-	Network &  Marabou  & Full MILP & NNenum? \\ \hline
-	MNIST 6$\times$100 & 26\% & 30\% & ?\%   \\ \hline
-	$\epsilon = 0.026$ & 6520s & 7000s s
-	 &  ?s  \\  \hline
+	Network &  Acc & Upper Bound & Marabou 2.0  & Full MILP & NNenum? \\\hline
+	MNIST 6$\times$100 & 99\% & 90\% & 26\% & 30\% & ?\%   \\
+	$\epsilon = 0.026$ & &  & 6520s & 7000s &  ?s  \\  \hline
 \end{tabular}
+\caption{Complete verifiers run on the smallest of the considered DNN. 
+Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and no complete verifier could outperform 
+$\alpha,\beta$-CROWN (40\%) for this DNN, despite the much larger average runtime. We didnt test on larger DNNs as this small one already took considerable amount of time.}
+\label{table_complete}
+\end{table}
 
@@
 Gap between verified and attackable images. Lower is better.
+M for MNIST, C for CIFAR
 %The table of undecided images among first 100 images in database by different methods for different network.
 
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{table}
+\centering
+\begin{tabular}{||l||c|c|c|c||c||}
+	\hline \hline
+	 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
+	 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
 	\hline
-	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
-	& Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s)\\ \hline
-	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
-	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
-	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
-	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
-	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
+	MNIST 6$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
+	(92s) & 13\% \bf (46s) \\ \hline
+	MNIST 6$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
+	MNIST 9$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
+	MNIST 9$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
+	MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
+	\bf 10\% (402s) \\ \hline
+	CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
+	CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
 \end{tabular}
+\caption{Gap $\%$ between attackable images and verifiable images ({\em lower is better}), as certified by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second).
+The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
+\label{table_hybrid}
+\end{table}
 

### 2024-09-16 ICLR25/tables.tex
update tables.tex
table updated in main document

@@
 	\centering
-	\caption{$\alpha,\beta$-Crown with pure BaB}
-	\label{table_beta}
 	\begin{tabular}{||c|c|c||c|c|c||}
@@
 		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
-
 		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
@@
 	\end{tabular}
+	\caption{$\alpha,\beta$-Crown with pure BaB.
+6 first Networks are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
+	\label{table_beta}
 \end{table}
@@
 		Network &  Marabou  & Full MILP & NNenum? \\ \hline
-		MNIST 6$\times$100 & 26\% & 30\% & ?\%   \\ \hline
-		$\epsilon = 0.026$ & 6520s & 7000s
+		MNIST 6$\times$100 & 28\% & 39\% & ?\%   \\ \hline
+		$\epsilon = 0.026$ & 6200s & 7000s
 		&  ?s  \\  \hline

### 2024-09-17 ICLR25/Paper_noProof.tex
tables

@@
 
-In this paper, we study the MILP encoding of ReLU-DNNs, provide new deep insights in the LP relaxation, which allows us to carefully craft a {\em partial MILP} solution which only considers few neurons as integer variables, the rest using the LP relaxation.
+In this paper, we study the MILP encoding of ReLU-DNNs, provide new deep insights in the LP relaxation, which allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation.
 Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
@@
 		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
-		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026.1s  \\  \hline
+		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
 		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
-		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930.3s  \\  \hline
+		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
 		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
-		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930.3s  \\  \hline
+		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
 		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
-		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083.1s  \\  \hline
+		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
 		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
-		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1002.5s  \\  \hline
+		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
 		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
@@
 	\centering
-\begin{tabular}{||l|c|c||c|c|c||}
+	\begin{tabular}{||c||c|c|c||}
 		\hline
-	Network &  Acc & Upper Bound & Marabou 2.0  & Full MILP & NNenum? \\\hline
-	MNIST 6$\times$100 & 99\% & 90\% & 26\% & 30\% & ?\%   \\
-	$\epsilon = 0.026$ & &  & 6520s & 7000s &  ?s  \\  \hline
+		Network &  Marabou  & & NNenum? Full MILP  \\ \hline
+		MNIST 6$\times$100 & 28\% & $\approx 30\%$ & 40 \%    \\ \hline
+		$\epsilon = 0.026$ & 6200s &  5588s & 6100s
+		  \\  \hline
 	\end{tabular}
@@
 Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and no complete verifier could outperform 
-$\alpha,\beta$-CROWN (40\%) for this DNN, despite the much larger average runtime. We didnt test on larger DNNs as this small one already took considerable amount of time.}
+$\alpha,\beta$-CROWN (40\%, 1026s) for this DNN, despite the much larger average runtime. We didnt test on larger DNNs as this small one already took considerable amount of time.}
 \label{table_complete}

### 2024-09-17 ICLR25/formula.tex
updated
update the section of formula.tex

--- 2024-09-12 ICLR25/formula.tex
@@
 
-	Let $a$ be a node in the network (at least the second hidden layer) and we have computed a series of lower and upper bound for all nodes before the layer of $a$.
-If we consider to compute the upper bound of $a$ by the standard MILP model.
+	Let $a$ be a node in the network (in the second hidden layer or deeper), and we have computed a series of lower and upper bound for all nodes before the layer of $a$.
+If we consider to compute the upper bound or lower bound of $a$ by the standard MILP model, then
 
 	\begin{enumerate}
-		\item $M^a_X$ means the MILP model with target node $a$ and open node set $X$. $M^a_{\emptyset}$ is the LP model for $a$.
+		\item Let $M^a_X$ mean the MILP model with target node $a$ and open node set $X$. Hence $M^a_{\emptyset}$ is the LP model for $a$.
 
-		\item For a set $X$, if the upper bound of $a$ computed from $M^a_{\emptyset}$ is $u_0$, and from $M^a_X$ is $u_X$, then the improvement (of upper bound of $a$) of $X$, $I_X$ (or $I_X^{a,u}$) is defined as : $$I_X = u_0-u_X.$$
+		\item For a set $X$, if the upper bound of $a$ computed from $M^a_{\emptyset}$ is $u_0$, and from $M^a_X$ is $u_X$, then the improvement (of upper bound of $a$) of $X$, $I_X^{a,u}$ (or $I_X$ if there is no risk of confusion) is defined as : $$I_X^{a,u} = u_0-u_X.$$ Similarly we can define the improvement of lower bound to be $I_X^{a,l} = l_X-l_0$.
 	\end{enumerate}
 \end{definition}
-
-Similarly we can define the improvement of lower bound to be $I_X^{a,l} = l_X-l_0$.
 
@@
 
-\begin{align*}
-	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
-\end{align*} And even $X$ comes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.
+\begin{align}
+	|(I_X - \sum_{b\in X} I_b)/I_X| << 1. \ (\text{in experiments})
+\end{align} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.
 
-Therefore, based on this observation, the question to choose $X$ is convert to compute $I_b$ for nodes $b$ in 3 layers before the target layer.
+Therefore, based on this observation, the question to choose $X$ is converted to compute $I_b$ for nodes $b$ in layers before the target layer.
+Our formula is to estimate the improvement of different individual nodes in different layers.
+For different layers, the formula will be different.
+However, neither the observation in this subsection nor the formula in the next subsection has solid theoretical proof to show that they are very accurate.
+They are all based on experiments.
 
@@
 
-The formula to compute the improvement of a single node is the actual content of our formula. For different layers, the formula will be different.
+For one layer before the target layer, it is very simple and most accurate.
 
-For one layer before the target layer, it is very simple and more accurate.
-Notice that, either the observation in last subsection, or formula in this subsection, does not have solid theoretical proof to show they are very accurate.
-They are all based on experiments.
-
-Suppose $b$ is a node one layer before $a$.
-To compute $I_b$, we need to run $M^a_{\emptyset}$ to compute the upper bound of $a$ first to obtain the solution data.
+Suppose $b$ is a node in one layer before $a$.
+To estimate $I_b$, first we need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data.
 Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
@@
 \begin{definition}
-	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.
-
-	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align*}
+	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align*}
 		I_b \approx W_{ba}(v(\hat{b})-\ReLU(v(b))).
@@
 
-	Specially, if $v(\hat{b})=\ReLU(v(b))$, then \begin{align*}
+	Specially, if $v(\hat{b})=\ReLU(v(b))$, then we can prove \begin{align*}
 		I_b = W_{ba}(v(\hat{b})-\ReLU(v(b))) = 0.
@@
 	Similarly, let $v(b)$ be the value of $b$ in the LP solution of lower bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.
-
 Then the formula to estimate improvement of lower bound of $b$ is: \begin{align*}
@@
 
-To explain the formula, we use upper bound and $W_{ba} > 0$ as an example.
+To explain the formula, we use upper bound and the case that $W_{ba} > 0$ as an example.
 To compute the upper bound of $a$, $\hat{b}$ should be as large as possible.
@@
 This is because in LP model, the upper bound of $v(\hat{b})$ is decided by the linear approximation rather than $\ReLU$ function.
-So, then node $b$ is open, if values before $v(\hat{b})$ do not change, the the upper bound of $a$ will improve by lower $v(\hat{b})$ to $\ReLU(v(b))$.
+So, when node $b$ is open, if $v(b)$ do not change, then the upper bound of $a$ will be improved because the value of $v(\hat{b})$ will be lower to $\ReLU(v(b))$.
 
-Of course changing other variables may effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major source of improvement.
-
-For earlier layers, the formula will be more complex and less accurate. But we will still focus on the source $v(\hat{b})-\ReLU(v(b))$.
+Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major source of improvement.
 
@@
 
+For earlier layers, the formula will be more complex and less accurate.
+We will still focus on the source $v(\hat{b})-\ReLU(v(b))$.
 Basically, we hope to use $\sum_c W_{ca}W_{bc}$ to replace the coefficient $W_{bc}$ in last subsection.
+However, directly using $\sum_c W_{ca}W_{bc}$ will lose too much accuracy.
+So we try to improve the accuracy by considering more details from the LP solutions.
 
-However, directly replace $W_{ba}$ with the new coefficient will lose too much accuracy. So we try to improve the accuracy by considering more details from the LP solutions.
+For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative. Next we consider the following definition.
 
-For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative.
-And as we discussed in last subsection, $W_{ca}$ can decide whether $v(\hat{c})$ is more close $\ReLU(v(c))$ or the linear approximation.
-That is the following definition.
-
-\begin{definition}
-	For a fixed target node $a$ and a fixed source node $b$ in two layers before $a$.
-To compute the improvement of of upper bound of $a$ by $b$, we define the following function for nodes in 1 layer before $a$:
+\begin{definition} \label{2layer}
+	Suppose we have a fixed target node $a$ and a fixed source node $b$ in two layers before $a$.
+Let $\UB,\LB$ be the function of precomputed upper and lower bound before the layer of $a$, and let $v$ be the function of values of nodes in the LP solution of upper bound of $a$.
+	To compute the improvement of of upper bound of $a$ by $b$, we define the following function for nodes $c$ in one layer before $a$:
 	\begin{align*}
@@
 		\end{cases}
-	\end{align*} and use the following formula to compute the estimation of improvement: \begin{align*}
-	I_b = (v(\hat{b})-\ReLU(v(b)))\sum_c W_{bc}W_{ca}k(c)
 	\end{align*} 
-
 \end{definition}
 
-However, the error is still too large.
-This is because the improvement of a node $c$ can not exceed its precomputed upper and lower bound (we may use $UB(c)$ and $LB(c)$ to denote them).
-Considering this, we may improve our formula to the following:
+We may use the following formula to estimate the improvement:  \begin{align*}
+	I_b \approx (v(\hat{b})-\ReLU(v(b)))\sum_c W_{bc}W_{ca}k(c).
+\end{align*}However, the error is still too large. This is because the improvement of a node $c$ can not exceed its precomputed upper and lower bound. Considering this, we may improve our formula.
 
 \begin{definition}
-	For a fixed target node $a$ and a fixed source node $b$ in two layers before $a$.
-Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models.
-To compute the improvement of of upper bound of $a$ by $b$, we use the following formula:
-
-	We define a distance function $D$:
-
+	Continue the assumption in Definition \ref{2layer} To compute the improvement of of upper bound of $a$ by $b$, we define a distance function $D$:
 	\begin{align*}
@@
 
-This is the formula to compute improvement of nodes two layers before.
+Then $D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$. This is the formula to compute improvement of nodes two layers before.
 
@@
 
-This formula is based on previous subsection but more complex. In some network, run this formula may cost too much time.
+This formula is based on previous subsection but more complex. In some network, run this formula may cost too much time but obtain little accuracy.
 
-The key problem is that, how to compute the coefficient $k$ for nodes in 2 layers before the target layer. We use the following method to estimate the coefficient.
+The key problem is how to compute the coefficient $k$ for nodes in two layers before the target layer. We use the following method to estimate the coefficient.
 
@@
 	\end{align*}
-\end{definition}
+\end{definition} $D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.

### 2024-09-17 ICLR25/formula.tex
update formula.tex

@@
 		\end{cases}\\
-		&D(a) = -\sum_c D(c)W_{ca}
+		&D(a) = \sum_c D(c)W_{ca}
 	\end{align*}
@@
 
-Then $D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$. This is the formula to compute improvement of nodes two layers before.
+Then $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
+For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights instead.
+This is the formula to compute improvement of nodes two layers before.
 
@@
 		\end{cases}\\
-		&D(a) = -\sum_c D(d)W_{da}
+		&D(a) = \sum_c D(d)W_{da}
 	\end{align*}
-\end{definition} $D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
+\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
+For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights  instead.

### 2024-09-17 ICLR25/Paper_noProof.tex
intro

@@
 
-\section*{Tables}
-
-The following table are the results of running $\alpha,\beta$-Crown pure BaB mode with different timeout for different networks. The numbers shown in the table is the rate of images in percentage.
-
-\begin{table}
-	\centering
-	\begin{tabular}{||l|c|c||c|c|c||}
-		\hline
-		Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
-		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
-		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
-		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
-		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
-		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
-		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
-		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
-		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
-		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
-		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
-		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
-		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
-		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
-		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
-	\end{tabular}
-	\caption{Verification $\%$ of $\alpha,\beta$-Crown run on 7 DNNs (average runtime per image in second).
-The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
-	\label{table_beta}
-\end{table}
-
-SAME FORMAT for complete verifiers!!!
-
-\begin{table}
-	\centering
-	\begin{tabular}{||c||c|c|c||}
-		\hline
-		Network &  Marabou  & & NNenum? Full MILP  \\ \hline
-		MNIST 6$\times$100 & 28\% & $\approx 30\%$ & 40 \%    \\ \hline
-		$\epsilon = 0.026$ & 6200s &  5588s & 6100s
-		  \\  \hline
-	\end{tabular}
-\caption{Complete verifiers run on the smallest of the considered DNN. 
-Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and no complete verifier could outperform 
-$\alpha,\beta$-CROWN (40\%, 1026s) for this DNN, despite the much larger average runtime. We didnt test on larger DNNs as this small one already took considerable amount of time.}
-\label{table_complete}
-\end{table}
-
-\vspace*{4ex}
-
-Gap between verified and attackable images. Lower is better.
-M for MNIST, C for CIFAR
-%The table of undecided images among first 100 images in database by different methods for different network.
-
-\begin{table}
-\centering
-\begin{tabular}{||l||c|c|c|c||c||}
-	\hline \hline
-	 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
-	 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
-	\hline
-	MNIST 6$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
-	(92s) & 13\% \bf (46s) \\ \hline
-	MNIST 6$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
-	MNIST 9$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
-	MNIST 9$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
-	MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
-	\bf 10\% (402s) \\ \hline
-	CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
-	CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
-\end{tabular}
-\caption{Gap $\%$ between attackable images and verifiable images ({\em lower is better}), as certified by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second).
-The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
-\label{table_hybrid}
-\end{table}
-
 	\section{Introduction}
@@
 
+\begin{table}
+	\centering
+	\begin{tabular}{||l||c|c|c|c||c||}
+		\hline \hline
+		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
+		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
+		\hline
+		MNIST 6$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
+		(92s) & 13\% \bf (46s) \\ \hline
+		MNIST 6$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
+		MNIST 9$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
+		MNIST 9$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
+		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
+		\bf 10\% (402s) \\ \hline
+		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
+		CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
+	\end{tabular}
+	\caption{Gap $\%$ between attackable images and verifiable images ({\em lower is better}), as certified by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second).
+The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
+	\label{table_hybrid}
+	\end{table}
+
 \input{experiments}

### 2024-09-17 ICLR25/introduction.tex
intro

@@
-Deep neural networks have demonstrated remarkable capabilities, achieving \newline human-like or even superior performance across a wide range of tasks.
+Deep neural networks (DNNs for short) have demonstrated remarkable capabilities, achieving human-like or even superior performance across a wide range of tasks.
 However, their robustness is often compromised by their susceptibility to input perturbations \cite{szegedy}.
@@
 given a DNN, an image and a small neighbourhood around this image, is it the case that all the images in the neighbourhood are classified in the same way.
-While some quite large DNNs (e.g.
-ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of {\em undecided} inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
+For the past 5 years, VNNcomp has focused on rather easy instances, that can be solved within tens of seconds (the set of the instances of a benchmark have to be solved within 6 hours - leaving e.g.
+maximum 216s Time out per instance for a 100 instances benchmark).
+For this reason, DNN verifiers in the past years have mainly focused on optimizing for such easy instances.
+
+Easy instances does not mean small DNNs:
+
+\begin{table}
+	\centering
+	\begin{tabular}{||l|c|c||c|c|c||}
+		\hline
+		Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
+		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
+		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
+		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
+		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
+		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
+		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
+		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
+	\end{tabular}
+	\caption{Verification $\%$ of $\alpha,\beta$-Crown run on 7 DNNs (average runtime per image in second).
+The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
+	\label{table_beta}
+\end{table}
+
+\begin{table}
+	\centering
+	\begin{tabular}{||l||c|c|c||}
+		\hline
+		Network &  Marabou  & NNenum? &  Full MILP  \\ \hline
+		MNIST 6$\times$100 & 28\% & $\approx 30\%$ & 40 \%    \\ \hline
+		$\epsilon = 0.026$ & 6200s &  5588s & 6100s
+		  \\  \hline
+	\end{tabular}
+\caption{Complete verifiers run on the smallest of the considered DNN. 
+Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and no complete verifier could outperform 
+$\alpha,\beta$-CROWN (40\%, 1026s) for this DNN, despite the much larger average runtime. We didnt test on larger DNNs as this small one already took considerable amount of time.}
+\label{table_complete}
+\end{table}
+
+Some quite large DNNs (e.g.
+ResNet with tens of thousands of neurons) can be verified very efficiently (in seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found.
+
+some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of {\em undecided} inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
 Using complete verifiers, while theoretically would close the gap, fail to answer fully due to (very long) time-outs.
@@
 Our analysis focuses on DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
+
 Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, 

### 2024-09-17 ICLR25/Paper_noProof.tex
intro

@@
 with few {\em unstable nodes}.
-In this paper, we consider harder verification instances, namely the usual local robustness problem.
+In this paper, we consider harder verification instances.
 On such instances, $\alpha,\beta$-CROWN displays a large gap ($20-58\%$) between instances that can be verified, and instances with an explicit attack.
@@
 
-In this paper, we study the MILP encoding of ReLU-DNNs, provide new deep insights in the LP relaxation, which allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation.
+In this paper, we study the MILP encoding of ReLU-DNNs, and provide new deep insights in the LP relaxation.
+This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation.
 Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
 This gives rise to a very efficient yet accurate algorithm.
-Implemented in {\em Hybrid MILP (hMILP)}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances to $\approx 10\%$, while keeping a reasonable runtime ($<500s$ on average per instance).
+Implemented in {\em Hybrid MILP (hMILP)}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances ($8-15\%$), while keeping a reasonable runtime ($<500s$ on average per instance).
 \end{abstract}

### 2024-09-17 ICLR25/introduction.tex
intro

--- 2024-08-19 ICLR25/introduction.tex
@@
 given a DNN, an image and a small neighbourhood around this image, is it the case that all the images in the neighbourhood are classified in the same way.
-While some quite large DNNs (e.g.
-ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of {\em undecided} inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
-Using complete verifiers, while theoretically would close the gap, fail to answer fully due to (very long) time-outs.
-Actually, the DNNs easy to verify are trained specifically (using DiffAI \cite{DiffAI} or PGD \cite{PGD}), while the DNNs harder to verify are {\em verification-agnostic} \cite{SDPFI}, trained in a {\em natural} way.
+For the past 5 years, VNNcomp has focused on rather easy instances, that can be solved within tens of seconds (the typical hard time-out is 300s).
+For this reason, DNN verifiers in the past years have mainly focused on optimizing for such easy instances.
+Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
+and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp24}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+We will thus focus in the following mostly on $\alpha,\beta$-CROWN.
 
-In this work, we concentrate on {\em verification-agnostic} DNNs, given the prevalence of techniques for {\em easier} DNNs, and also the decrease in accuracy of specifically trained DNNs (e.g.
-the large easy-to-verify ResNet network has $29\%$ accuracy \cite{prima}!).
-Our analysis focuses on DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
-Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima},
-MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-CROWN \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neighbour with a different decision.
+One issue is however that easy instances are trained specifically to be easier to verified
+e.g.
+using DiffAI \cite{DiffAI} or PGD \cite{PGD}, which can impact the accuracy of the network, i.e.
+answering correctly to an unperturbed input.
+For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct (the other $71\%$ are thus not even tested by $\alpha,\beta$-CROWN).
+While more accurate trainers for verification have been recently developped \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
+very hard verification instances into hard verification instances.
+Also, verification questions intrinsically harder than local robustness, such as 
+bounding on Lipschitz constants \cite{lipshitz} globally or asking several specification at once, makes the instance particularly harder.
+Last, there are many situation (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible ({\em verification-agnostic} networks \cite{SDPFI}).
+The bottom line is, one cannot expect only easy verification instances: hard verification instances need to be explored as well.
+
+In this paper, we focused on 6 {\em hard} ReLU-DNNs that have been previously tested in one or several of \cite{prima},\cite{SDPFI},\cite{crown}, and with a large gap ($>20\%$) between images that can be certified and the upper bound when we remove those which can be falsified.
+In turns, hard instances does not necessarily mean very large DNNs, the smallest of the DNN considered having only 500 hidden neurons, namely 5x100 for MNIST.
+We first dwelve into the scaling of $\alpha,\beta$- Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
+Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).
+
+\begin{table}[t!]
+	\centering
+	\begin{tabular}{||l|c|c||c|c|c||}
+		\hline
+		Network & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
+		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
+		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
+		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
+		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
+		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
+		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
+		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
+	\end{tabular}
+	\caption{Images verified by $\alpha,\beta$-Crown with different time-outs (TO) on 7 DNNs, and average runtime per image.
+The 6 first DNNs are hard instances.
+The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
+	\label{table_beta}
+	\vspace{-0.3cm}
+\end{table}
+
+\begin{table}[b!]
+	\centering
+	\begin{tabular}{||l|c|c||c|c|c||}
+		\hline
+		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
+		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 30\%$ & 40 \%    \\
+		$\epsilon = 0.026$ & &  &6200s &  5588s & 6100s
+		  \\  \hline
+	\end{tabular}
+\caption{Complete verifiers run on the smallest of the hard DNN with TO = 10 000s. 
+%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
+No complete verifier could outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime.}
+\label{table_complete}
+\end{table}
+
+The size of the smallest DNN (500 hidden neurons) makes it realistic to be solved by complete verifiers such as Marabou 2.0, NNenum or a Full MILP encoding. 
+While they should theoretically be able to close the gap of undecided images,
+in practice, Table \ref{table_complete} reveals that even with a very large 10 000s time out per image, none succeds to verify any more image than $\alpha,\beta$-Crown, while the runtime is $>5$ times longer.
+It seemed pointless to test complete verifier on larger networks.
+
+%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}.
+
+%\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks,
+
+%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as
+
+%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+
+%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs; It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
 The high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
@@
 	%To dig further into their incompleteness, we first remark that 
-	Notice that complete methods exist \cite{Reluplex,katz2019marabou,SDPFI}, but they time-out on hard instances.
+	%Notice that complete methods exist \cite{Reluplex,katz2019marabou,SDPFI}, but they time-out on hard instances.
 In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-CROWN \cite{crown}.
+%As a starting point, we sought to understand properties of DNNs that make them hard to verify.
 
-%As a starting point, we sought to understand properties of DNNs that make them hard to verify.
-Our key finding is a new notion of {\em compensations}, that explains why bounds are inaccurate.
+%Our key finding is a new notion of {\em compensations}, that explains why bounds are inaccurate.
 Formally, a {\em compensating pair of paths} $(\pi,\pi')$ between neurons $a$ and $b)$ is such that $w < 0 < w'$ for $w,w'$ the products of weights seen along $\pi$ and $\pi'$ respectively.
-Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with
-$(w+w') weight(a)$ by $\pi$ and $\pi'$.
+Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $(w+w') weight(a)$ by $\pi$ and $\pi'$.
 As $w,w'$ have opposite signs, they will compensate (partly) each other.
@@
 %; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
-Our three main contributions address the challenges of inaccuracies when verifying DNNs:
+
+Our three main contributions address the challenges of verifying {\em hard} DNNs efficiently:
 \begin{enumerate}
-	\item  Our first main contribution establishes, through Theorem \ref{th1}, the foundational understanding that the compensating pairs are the 	%primary 
+	\item  Our first contribution is to study LP relaxations for the complete MILP
+	encoding of ReLU-DNNs. We establish in Theorem \ref{th1} the abstraction set corresponding to the LP constraints.
+	\item This allows us to propose a measure of utility for each neuron
+
+	foundational understanding that the compensating pairs are the 	%primary 
 	source of {\em all} inaccuracies, 
@@
 \end{enumerate}
+
+We consider DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
 

### 2024-09-17 ICLR25/formula.tex

@@
 \begin{definition}
-	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align*}
+	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align}
 		I_b \approx W_{ba}(v(\hat{b})-\ReLU(v(b))).
-	\end{align*}
+	\end{align}
 
@@
 	To compute the improvement of of upper bound of $a$ by $b$, we define the following function for nodes $c$ in one layer before $a$:
-	\begin{align*}
+	\begin{align}
 		k(c) =
@@
 		\end{cases}
-	\end{align*} 
+	\end{align} 
 \end{definition}
@@
 	I_b \approx (v(\hat{b})-\ReLU(v(b)))\sum_c W_{bc}W_{ca}k(c).
-\end{align*}However, the error is still too large. This is because the improvement of a node $c$ can not exceed its precomputed upper and lower bound. Considering this, we may improve our formula.
+\end{align*}However, the error is still too large. This is because the improved value of a node $c$ can not exceed its precomputed upper and lower bound. Considering this, we can update our formula.
 
@@
 	Continue the assumption in Definition \ref{2layer} To compute the improvement of of upper bound of $a$ by $b$, we define a distance function $D$:
-	\begin{align*}
+	\begin{align}
 		&D(b) = \ReLU(v(b))-v(\hat{b})\\
@@
 		&D(a) = \sum_c D(c)W_{ca}
-	\end{align*}
+	\end{align}
 \end{definition}
@@
 
-This formula is based on previous subsection but more complex. In some network, run this formula may cost too much time but obtain little accuracy.
+This formula is based on previous subsection but more complex. In some network, running this formula may cost too much time but obtain little accuracy.
 
-The key problem is how to compute the coefficient $k$ for nodes in two layers before the target layer. We use the following method to estimate the coefficient.
+The key problem is how to compute the coefficient $k$ for nodes in two layers before the target layer. To do this, we may use the values in the solution of LP model as follows:
 
 \begin{definition}\label{3layer}
-	For a fixed target node $a$ and a fixed source node $b$ in two layers before $a$.
+	For a fixed target node $a$ and a fixed source node $b$ in three layers before $a$.
 Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models.
-To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model;then we define the following function $k$, so that for a node $c$ in 2 layers before the target node $a$, the value $k(c)$ is computed as:
-	\begin{align*}
+To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all nodes $c$ in 2 layers before the target node $a$ as follows:
+	\begin{align}
 		&v_0 = v(\hat{c}), v_1 = \ReLU(v(c)), v_2 = \frac{\UB(c)v(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
-		&k(c) =
+		&h(c) =
 		\begin{cases}
@@
 
-For $c$ in the next layer, we define \begin{align*}
+To compute $D(c)$ for nodes $c$ in two layer before $a$, we define \begin{align}
 	&u_0 = \max(\LB(c),\min(\UB(c),  v(c)+D(b)W_{bc}))\\
 	&u_1 = \begin{cases}
-		\ReLU(u_0)+k(c)(\frac{\UB(c)u_0-\UB(c)\LB(c)}{\UB(c)-\LB(c)}-u_0), & \text{if }\LB(c) < 0\\
+		\ReLU(u_0)+h(c)(\frac{\UB(c)u_0-\UB(c)\LB(c)}{\UB(c)-\LB(c)}-\ReLU(u_0)), & \text{if }\LB(c) < 0\\
 	u_0, & \text{if }  \LB(c) \geq 0
@@
 	&D(c) = u_1-v(\hat{c})
-\end{align*}
+\end{align}
 
-	Next is to compute $D(d)$ for nodes $d$ in one layer before $a$.
-
-	\begin{align*}
-		&w_0 = \sum_C D(c)W_{cd}\\
+	To compute $D(d)$ for nodes $d$ in one layer before $a$, we define 
+	\begin{align}
+		&w_0 = \sum_c D(c)W_{cd}\\
 		&w_1 = \min(\UB(d),v(d)+w_0)\\		
@@
 		&D(a) = \sum_c D(d)W_{da}
-	\end{align*}
+	\end{align}
 \end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.

### 2024-09-18 ICLR25/formula.tex
update formula.tex

@@
 
-One of the key formula is to choose some nodes and set the corresponding variables to be binary variable in the MILP model.
-We will say that we open those nodes.
+The formula is to choose some nodes and set the corresponding variables to be binary variable in the MILP model.
+For convenience, we will say that we open those nodes, or nodes are opened to describe that those nodes' variable are set to be binary.
 In our algorithm, we will open nodes at most 3 layer3 before the target layer.

### 2024-09-18 ICLR25/formula.tex
update formula.tex

@@
 
-Our observation (by experiments) is that \begin{align*}
+Our observation (by experiments) is that \begin{align}
 	I_X \approx \sum_{b\in X} I_b.
-\end{align*} Separately, if all nodes in $X$ are from the layer before $a$, then in experiments, we observe that
+\end{align} Separately, if all nodes in $X$ are from one layer before $a$, then in experiments, we observe that
 
 \begin{align}
-	|(I_X - \sum_{b\in X} I_b)/I_X| << 1. \ (\text{in experiments})
+	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
 \end{align} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.
@@
 
-For one layer before the target layer, it is very simple and most accurate.
-
+For one layer before the target layer, the formula is simple and most accurate.
 Suppose $b$ is a node in one layer before $a$.
@@
 \begin{definition}
-	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align}
+	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}=\ReLU(b)$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align}
 		I_b \approx W_{ba}(v(\hat{b})-\ReLU(v(b))).
@@
 
-	Specially, if $v(\hat{b})=\ReLU(v(b))$, then we can prove \begin{align*}
+	Specially, if $v(\hat{b})=\ReLU(v(b))$, then we will have \begin{align*}
 		I_b = W_{ba}(v(\hat{b})-\ReLU(v(b))) = 0.
@@
 
-Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major source of improvement.
+Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major part of improvement.
 

### 2024-09-18 ICLR25/formula.tex
update formula.tex

@@
 
-For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative. Next we consider the following definition.
+For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative, that will be the following definition.
 

### 2024-09-18 ICLR25/formula.tex
update formula.tex

@@
 
-For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative, that will be the following definition.
+For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative, which is the following definition.
 
 \begin{definition} \label{2layer}
-	Suppose we have a fixed target node $a$ and a fixed source node $b$ in two layers before $a$.
+	Suppose we have a fixed target node $a$, and a fixed source node $b$ in two layers before $a$.
 Let $\UB,\LB$ be the function of precomputed upper and lower bound before the layer of $a$, and let $v$ be the function of values of nodes in the LP solution of upper bound of $a$.
-	To compute the improvement of of upper bound of $a$ by $b$, we define the following function for nodes $c$ in one layer before $a$:
+	To compute the improvement of of upper bound of $a$ by $b$, we define the following function $k$ for nodes $c$ in one layer before $a$:
 	\begin{align}
@@
 \begin{definition}
-	Continue the assumption in Definition \ref{2layer} To compute the improvement of of upper bound of $a$ by $b$, we define a distance function $D$:
+	Continue the assumption in Definition \ref{2layer}. To compute the improvement of of upper bound of $a$ by $b$, we define a distance function $D$:
 	\begin{align}
@@
 		\end{cases}\\
-		&D(a) = \sum_c D(d)W_{da}
+		&D(a) = \sum_d D(d)W_{da}
 	\end{align}

### 2024-09-18 ICLR25/formula.tex
update formula.tex

@@
 Then $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
-For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights instead.
+For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{ca}$ instead.
 This is the formula to compute improvement of nodes two layers before.
@@
 
-This formula is based on previous subsection but more complex. In some network, running this formula may cost too much time but obtain little accuracy.
+This formula is based on previous subsection but more complex. In some network, running this formula may cost too much time.
 
@@
 \begin{definition}\label{3layer}
-	For a fixed target node $a$ and a fixed source node $b$ in three layers before $a$.
+	Suppose we have a fixed target node $a$ and a fixed source node $b$ in three layers before $a$.
 Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models.
@@
 \end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
-For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights  instead.
+For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{da}$  instead.

### 2024-09-19 ICLR25/introduction.tex
intro + related

@@
 Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-CROWN \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neighbour with a different decision.
-One issue is however that easy instances are trained specifically to be easier to verified
+One issue is however that easy instances are trained specifically to be easier to verify
 e.g.
@@
 
-In this paper, we focused on 6 {\em hard} ReLU-DNNs that have been previously tested in one or several of \cite{prima},\cite{SDPFI},\cite{crown}, and with a large gap ($>20\%$) between images that can be certified and the upper bound when we remove those which can be falsified.
+In this paper, we focused on 6 {\em hard} ReLU-DNNs that have been previously tested in one or both of \cite{SDPFI},\cite{crown}, and with a large gap ($>20\%$) between images that can be certified and the upper bound when we remove those which can be falsified.
 In turns, hard instances does not necessarily mean very large DNNs, the smallest of the DNN considered having only 500 hidden neurons, namely 5x100 for MNIST.
@@
 		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
-		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 30\%$ & 40 \%    \\
-		$\epsilon = 0.026$ & &  &6200s &  5588s & 6100s
+		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
+		$\epsilon = 0.026$ & &  &6200s &  5220s & 6100s
 		  \\  \hline
+		  MNIST 6$\times$100 & 99\% & 90\% & 28\% & $40\%$ & 37 \%    \\
+		  TO=2000s & &  & 1250s  & 1343s & 1466s \\  \hline	
 	\end{tabular}
@@
 \begin{enumerate}
-	\item  Our first contribution is to study LP relaxations for the complete MILP
-	encoding of ReLU-DNNs. We establish in Theorem \ref{th1} the abstraction set corresponding to the LP constraints.
-	\item This allows us to propose a measure of utility for each neuron
+	\item  Our first contribution is to study the LP relaxation for the complete MILP
+	encoding of ReLU-DNNs. We establish in Proposition \ref{LP} an explicit abstraction set corresponding to the LP constraints.
+	\item This allows us to propose a measure of utility for each neuron, providing an upper bound on the improvement on accuracy made if we treat this neuron with an integer variable instead of the LP relaxation.
+Choosing the neurons with the top utility and encoding them with integer variables gives rise to a partial MILP which is much more efficient than previous attempts \cite{9211410}, necessitating much less integer variables for the same accuracy.
 
-	foundational understanding that the compensating pairs are the 	%primary 
-	source of {\em all} inaccuracies, 
-	 as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate. This is confirmed experimentally by the fact that 
-	 DNNs easier to verified have less compensation strength than verification agnostic DNNs. 
-	This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs.
-Nonetheless, this insight lays the groundwork for our innovative approach, {\em relaxing} the usual but inefficient Mixed Integer Linear Program (MILP) formulation encoding exactly DNNs \cite{MILP}.
-To compute bounds for $z$, we encode as binary variables only ReLU nodes on {\em compensating paths with target $z$}; other nodes, in particular those on compensating paths to neurons before $z$ are encoded using the much faster linear relaxation.
-To take into account indirectly the compensating paths to previous nodes, we inductively compute bounds for every neuron layer by layer, and use these bounds of previous neurons in the MILP encoding for $z$.
-This is more efficient, as the number of binary nodes is strongly reduced.
-However, the question remains how accurate is it?
-
-\item  Our second main contribution, delineated in Theorem \ref{th2}, answers this question, showing that this abstraction is fully accurate, in that the bounds computed in such a way for neuron $z$ correspond exactly to the minimal and maximal values reachable by inputs of the DNN.
-Again, the prevalence of compensating paths in actual DNNs renders this algorithm computationally intensive because the number of binary variables is still high.
-
-\item Our third main contribution is to experimentally confirm that focusing on compensations {\em does} improve accuracy: we introduce {\CMP} (Algorithm \ref{algo1}), building on our theoretical insights.
-This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones.
-Our empirical evaluation (refer to Table \ref{tab:example}) reveals {\CMP} achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
-It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$.
-Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete}) on the larger $6 \times 500$ DNN.
-
+\item We then propose a new verifier, called Hybrid MILP, invoking first 
+$\alpha,\beta$-CROWN with short time-out to settle the easy instances.
+On those (hard) instances which are neither certified nor falsified, we call our partial MILP with few neurons encoded as integer variables.
+Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
+It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-CROWN with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance (46-420s).
+It scale to fairly large networks such as CNN-B-Adv \cite{SDPFI} for the CIFAR10 benchmark, with more than 20.000 neurons.
 %We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
-
 %KSM: I think this is a distraction in intro, so I suggest moving to later part
@@
 %By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
-
 \end{enumerate}
 
-We consider DNNs employing the standard ReLU activation function, though our findings potentially extend to more sophisticated architectures.
-
-These theoretical and experimental results both point to compensation being a promising notion, opening up many opportunities, as discussed in Section \ref{Discussion}.
+Limitation: We consider DNNs employing the standard ReLU activation function, though our findings should extend to other activation functions, following similar extention by \cite{??}.
 

### 2024-09-19 ICLR25/relatedwork.tex
intro + related

--- 2024-04-25 lipics-master/relatedwork.tex
@@
 CMP scales while preserving good accuracy, through targeting a limited number of binary variables based on compensating strength, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate).
-MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP instance instead of CMP's many small instances, which significantly reduce the number of binary variables necessary for each instance.
-In \cite{9211410}, small instances are also considered, however with a straightfoward choice of binary nodes based on the weight of outgoing edge, therefore restricted to nodes in the previous layer, which is significantly less accurate than using compensating strength (see Table \ref{tab:example1}).
+MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of CMP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding.
+In \cite{9211410}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.
 
-ERAN-DeepPoly \cite{deeppoly} computes bounds on values very quickly, by abstracting the weight of every node using two functions: an upper function and a lower function.
+Hybrid MILP can be seen as a refinement of $\alpha,\beta$-Crown~\cite{crown}, though its refined accurate path is vastly different than the base Branch and Bound technique used in 
+$\alpha,\beta$ CROWN, BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete}, which call BaB once per output neuron.
+In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities.
+In simple networks, like those trained robustly, branch and bound is highly efficient, focusing on branches crucial for verifying the actual property.
+However, branch and bound hits a complexity barrier when verifying harder instances, due to an overwhelming number of branches, as displayed in Table \ref{table_beta}.
+This is not the csae of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.
+That shortcoming was already witnessed in \cite{crown}, and
+a very specific solution
+
+Last, ERAN-DeepPoly \cite{deeppoly} computes bounds on values very quickly, by abstracting the weight of every node using two functions: an upper function and a lower function.
 While the upper function is fixed, the lower function offers two choices.
 It relates to the LP encoding through the following new (to our knowledge) insight:  Proposition \ref{LP} state that the LP relaxation precisely matches the intersection of these two choices.
-Consequently, LP is more accurate (but slower) than DeepPoly, and \CMP is considerably more precise.
-
+Consequently, LP is more accurate (but slower) than DeepPoly, and Hybrid MILP is considerably more precise.
 Regarding PRIMA \cite{prima}, the approach involves explicitly maintaining dependencies between neurons, calculating bounds layer by layer.
-This enables the retention of dependencies from many layers prior.
-CMP, however, handles dependencies between neurons differently, attributing them to compensation.
-CMP excels in accuracy for local dependencies but may lose precision for dependencies formed several layers back.
-Experimental accuracy results in favor of CMP points to dependencies being more local than global (see Table \ref{tab:example}).
-
-$\alpha,\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete})  focus on running few instances of branch and bound (one per output neuron).
-In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities.
-In simple networks, like those trained robustly, branch and bound is highly efficient, focusing on branches crucial for verifying the actual property.
-In contrast, {\CMP} is less efficient as it must individually consider each node from the start, including nodes with non-critical bounds.
-However, branch and bound hits a complexity barrier when verifying complex networks, such as verification-agnostic DNNs, due to an overwhelming number of branches.
-For instance, Branch and Bound verifies only 3.5\% more images (44.5\% from 41\%) by increasing runtime by 50 times on larger $6 \times 500$ DNNs, and fails to match {\CMP}'s performance (65\% of images verified, Table \ref{tab:example}).
 
@@
 
-Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, \CMP.
-These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances.
+Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, Hybrid MILP.
+These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances as shown in Table \ref{table_complete}.

### 2024-09-19 ICLR25/formula.tex

@@
 	I_X \approx \sum_{b\in X} I_b.
-\end{align} Separately, if all nodes in $X$ are from one layer before $a$, then in experiments, we observe that
+\end{align} Especially, if all nodes in $X$ are from one layer before $a$, then in experiments, we observe that
 
-\begin{align}
+\begin{align*}
 	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
-\end{align} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.
+\end{align*} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.
 
@@
 	Suppose we have a fixed target node $a$ and a fixed source node $b$ in three layers before $a$.
-Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models.
+Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bounds used in building MILP models.
 To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all nodes $c$ in 2 layers before the target node $a$ as follows:

### 2024-09-19 ICLR25/introduction.tex
update reference

--- 2024-09-17 ICLR25/introduction.tex
@@
 Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
-and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp24}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
 We will thus focus in the following mostly on $\alpha,\beta$-CROWN.
@@
 		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
-		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 30\%$ & 40 \%    \\
-		$\epsilon = 0.026$ & &  &6200s &  5588s & 6100s
+		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
+		$\epsilon = 0.026$ & &  &6200s &  5220s & 6100s
 		  \\  \hline

### 2024-09-19 ICLR25/relatedwork.tex

@@
 This is not the csae of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.
-That shortcoming was already witnessed in \cite{crown}, and
-a very specific solution
+That shortcoming for hard instances was witnessed in \cite{crown}, and a very specific solution using the full MILP encoding for the first few layers of a DNN was drafted, following similar proposal \cite{MILP2}.
+There are two key issues with this techniques: it is slow, as every neurons up to the layer are encoded using an integer variable, and it cannot scale to DNN with many neurons, making it not that accurate for intermediate networks (e.g.
+9x100,9x200, Table \ref{table_hybrid}), and not usable for larger DNNs (6x500, CNN-B-Adv), whereas Hybrid MILP does scale.
 
@@
 
-For verification-agnostic DNNs that are not too large,  $\beta$-CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding.
+%For verification-agnostic DNNs that are not too large,  $\beta$-CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding.
 In {\CMP}, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength.
@@
 
-Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, Hybrid MILP.
+Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, $\alpha,\beta$-CROWN)\cite{prima,crown}, Hybrid MILP.
 These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances as shown in Table \ref{table_complete}.

### 2024-09-19 ICLR25/formula.tex
section 4

@@
-\section*{Formula}
+\section{Important neurons for accuracy and Utility function.}
 
-The formula is to choose some nodes and set the corresponding variables to be binary variable in the MILP model.
-For convenience, we will say that we open those nodes, or nodes are opened to describe that those nodes' variable are set to be binary.
-In our algorithm, we will open nodes at most 3 layer3 before the target layer.
-So the formula will consists of three parts.
+In this section, we evaluate how each neuron would impact the accuracy of encoding this neuron with an integer (actually binary) or a linear variable.
+We will say we open a node when this node is selected with a binary variable.
+We denote by $X$ a choice of set of open nodes, and by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
 
-\subsubsection*{Observation}
+Let $z$ be a neuron of the DNN we want to evaluate, for instance computing an upper bound on the value it can take.
+We denote by $n< z$ the fact that a neuron appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
+Let us denote (Sol\_max$_X^z(n))_{n \leq z})$ is a solution of $\mathcal{M}_X$ 
+maximizing $z$. In particular, Sol\_max$_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
 
-The key of our formula is based on the following observation:
+Consider (Sol\_max$_\emptyset^z(n))_{n \leq z})$ (this is obtained by {\em one} call to an LP solver, so can be obtained very efficiently).
+An accurate utility function is to evaluate 
+Improve\_max$^z(a)=$ Sol\_max$_\emptyset^z(z) -$ Sol\_max$_{\{a\}}^z(z)$, 
+representing how much opening neuron $a < z$ reduces the maximum computed for $z$
+compared with using only LP. 
+Similarly, we define (Sol\_min$_\emptyset^z(n))_{n \leq z})$ and 
+Improve\_min$_a^z$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
+would however be very time consuming when the number of neurons $a$ to evaluate is large.
 
-\begin{definition}[Improvement]
+Instead, we focus on the following upper bounding of Improve\_max$_a^z$, thanks to Proposition \ref{LP}.
 
-	Let $a$ be a node in the network (in the second hidden layer or deeper), and we have computed a series of lower and upper bound for all nodes before the layer of $a$.
-If we consider to compute the upper bound or lower bound of $a$ by the standard MILP model, then
+%\subsubsection*{Observation}
 
-	\begin{enumerate}
-		\item Let $M^a_X$ mean the MILP model with target node $a$ and open node set $X$. Hence $M^a_{\emptyset}$ is the LP model for $a$.
+%The key of our formula is based on the following observation:
 
-		\item For a set $X$, if the upper bound of $a$ computed from $M^a_{\emptyset}$ is $u_0$, and from $M^a_X$ is $u_X$, then the improvement (of upper bound of $a$) of $X$, $I_X^{a,u}$ (or $I_X$ if there is no risk of confusion) is defined as : $$I_X^{a,u} = u_0-u_X.$$ Similarly we can define the improvement of lower bound to be $I_X^{a,l} = l_X-l_0$.
-	\end{enumerate}
-\end{definition}
+%Our observation (by experiments) is that \begin{align}
+%	I_X \approx \sum_{b\in X} I_b.
+%\end{align} Especially, if all nodes in $X$ are from one layer before $a$, then in %experiments, we observe that
 
-Our observation (by experiments) is that \begin{align}
-	I_X \approx \sum_{b\in X} I_b.
-\end{align} Especially, if all nodes in $X$ are from one layer before $a$, then in experiments, we observe that
-
+\iffalse
 \begin{align*}
@@
 
+In our algorithm, we will open nodes at most 3 layer3 before the target layer. So the formula will consists of three parts.
+
 \subsubsection*{Compute the improvement of a single node}
+\fi
 
-For one layer before the target layer, the formula is simple and most accurate.
-Suppose $b$ is a node in one layer before $a$.
-To estimate $I_b$, first we need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data.
-Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
+\subsection*{One Layer before $z$}
+
+%For one layer before the target layer, the formula is simple and most accurate. 
+Suppose $a$ is a node in one layer before $z$. To estimate Improve\_max$_a^z$:
+%we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
 
 \begin{definition}
-	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}=\ReLU(b)$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align}
-		I_b \approx W_{ba}(v(\hat{b})-\ReLU(v(b))).
+	For all nodes $n$, let $sol(n)=$Sol\_max$_\emptyset^z(n)$ be the value of node $a$
+	in the solution of the LP instance Sol\_max$_\emptyset^z$ to maximize $z$.
+
+	We define : 
+	\begin{align}
+		Utility\_max^z(a) = W_{az} \times (sol(\hat{a})- \ReLU(sol(a))).
 	\end{align}
 
-	Specially, if $v(\hat{b})=\ReLU(v(b))$, then we will have \begin{align*}
-		I_b = W_{ba}(v(\hat{b})-\ReLU(v(b))) = 0.
-	\end{align*}
+	%In particular, if $v(\hat{a})=\ReLU(v(a))$, then we will have 
+	%\begin{align*}
+%		Utility^z(a) = 0.
+%	\end{align*}
+
+We have that :
+
+\begin{proposition}
+$0 \leq Improve\_max^z(a) \leq Utility\_\max^z(a)$. 
+\end{proposition}
+
+\begin{proof}
+Indeed, consider $(sol'(n))_{n \leq z})_{n \leq z})$ with
+$sol'(n)=sol(n)$ for all $n \notin \{z,\hat{a}\}$.
+In particular,  $sol'(a) = sol(a)$.
+
+Now, define $sol'(\hat{a}) = \ReLU(v(a))$. 
+That is,  
+sol'$(\hat{a})$ is the correct value for $\hat{a}$ (obtained if we open node $a$), 
+compared to the LP abstraction for $sol(\hat{a})$.
+
+Last, we define $sol'(z)=sol(z) + W_{az} \times (\ReLU(sol(a)) - sol(\hat{a})) = sol(z) - Utility\_max_z(a)$.
+
+Now, it is easy to check that $(sol'(n))_{n \leq z}$ satisfies the constraints in 
+$\mathcal{M}_{\{a\}}$, as openning $a$ changes the value of $\hat{a}$ from
+$sol(\hat{a})$ to $\ReLU(sol(a))$, and the contribution from $a$ to $z$ is 
+$W_{az}$. As $sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $sol'(z) \leq$ Sol\_max$_{\{a\}}^z(z)$. That is, 
+$sol(z)-sol'(z) \geq sol(z) -$ Sol\_max$_{\{a\}}^z(z)$, i.e. 
+$Improve\_max^z(a) \leq Utility\_\max^z(a)$.
+\end{proof}
 

### 2024-09-19 ICLR25/experiments.tex
update
update a table

@@
 
+%
 We implemented \toolname in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
@@
 	\centering
-	\begin{tabular}{|c||c|c|c|}
+	\begin{tabular}{|c||c|c|c|c|}
 		\hline
-		\text{Number $K$}  &  \text{Compensate} &  \text{Incoming Weights} \cite{9211410} & \text{Random} \\ \hline
+		\text{Number $K$}  &  \text{Without ratio} &\text{With ratio} &  \text{Incoming Weights} \cite{ DivideAndSlide} & \text{Random} \\ \hline
 		\hline
-		0  &  1.761 & 1.761 & 1.761  \\ \hline
-		10  &  1.641 & 1.651 & 1.696  \\ \hline
-		20  &  1.517 & 1.557 & 1.619  \\ \hline
-		30  &  1.392 & 1.489 & 1.546  \\ \hline
-		40  &  1.275 & 1.447 & 1.469  \\ \hline
-		50  &  1.158 & 1.426 & 1.388  \\ \hline
-		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
+		0  &   1.761  & 1.761 & 1.761 & 1.761  \\ \hline
+		5  & 1.532  & 1.533 & &   \\ \hline
+		10  & 1.371 & 1.373 & 1.651 & 1.696  \\ \hline
+		15  & 1.247 & 1.244 &   &   \\ \hline
+		20  & 1.145 & 1.136 & 1.557 & 1.619  \\ \hline
+		25  & 1.061 & 1.057 &  &   \\ \hline
+		30  & 0.989 & 1.067 & 1.489 & 1.546  \\ \hline
+		35  & 0.934 & 1.091 &  &   \\ \hline
+		40  &  & & 1.447 & 1.469  \\ \hline
+		50  &  & & 1.426 & 1.388  \\ \hline
+		116 (max) &  0.895 & 0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
 	\end{tabular}
-	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs \cite{9211410} vs random choice).}
+	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs \cite{ DivideAndSlide} vs random choice).}
 	\label{tab:example1}
@@
 We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes from layers $1$ and $2$.
-We test using compensation, compared with a random choice, and also choice based on strength in \cite{9211410}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$.
+We test using compensation, compared with a random choice, and also choice based on strength in \cite{ DivideAndSlide}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$.
 It is however limited to choosing ReLU in the previous layer 2.
@@
 However, as soon as many nodes can be chosen in $Z$, compensate becomes much more accurate.
-Even random becomes more accurate as the number of nodes grows, as \cite{9211410} only has access to nodes $c$ in layer 2, and not to nodes $b$ in layer 1.
+Even random becomes more accurate as the number of nodes grows, as \cite{ DivideAndSlide} only has access to nodes $c$ in layer 2, and not to nodes $b$ in layer 1.
 For comparison, compensate is the most accurate, from 30 nodes, experimentally validating that compensating strength is the important factor to consider.
@@
 {\color{red} We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly from layers $1$ and $2$.
-	Moreover, we also compare choosing nodes in the second layer only (using method in paper \cite{9211410}) with choosing nodes in both the first and second layer.
+	Moreover, we also compare choosing nodes in the second layer only (using method in paper \cite{ DivideAndSlide}) with choosing nodes in both the first and second layer.
 
-		The method in paper \cite{9211410} use a formula to value different nodes in a layer, and then choose nodes by their values.
+		The method in paper \cite{ DivideAndSlide} use a formula to value different nodes in a layer, and then choose nodes by their values.
 We can use the same formula in this comparison experiments.

### 2024-09-19 ICLR25/introduction.tex

@@
 
-Limitation: We consider DNNs employing the standard ReLU activation function, though our findings should extend to other activation functions, following similar extention by \cite{??}.
+Limitation: We consider DNNs employing the standard ReLU activation function, though our findings should extend to other activation functions, following similar extention by \cite{DivideAndSlide}.
 

### 2024-09-20 ICLR25/formula.tex
update formula.tex

@@
 In this section, we evaluate how each neuron would impact the accuracy of encoding this neuron with an integer (actually binary) or a linear variable.
-We will say we open a node when this node is selected with a binary variable.
-We denote by $X$ a choice of set of open nodes, and by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
+We will say we open a neuron when this neuron is selected with a binary variable.
+We denote by $X$ a choice of set of open neurons, and by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
 
@@
 %	I_X \approx \sum_{b\in X} I_b.
-%\end{align} Especially, if all nodes in $X$ are from one layer before $a$, then in %experiments, we observe that
+%\end{align} Especially, if all neurons in $X$ are from one layer before $a$, then in %experiments, we observe that
 
@@
 	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
-\end{align*} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.
+\end{align*} Even $X$ contains neurons from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.
 
-Therefore, based on this observation, the question to choose $X$ is converted to compute $I_b$ for nodes $b$ in layers before the target layer.
-Our formula is to estimate the improvement of different individual nodes in different layers.
+Therefore, based on this observation, the question to choose $X$ is converted to compute $I_b$ for neurons $b$ in layers before the target layer.
+Our formula is to estimate the improvement of different individual neurons in different layers.
 For different layers, the formula will be different.
@@
 
-In our algorithm, we will open nodes at most 3 layer3 before the target layer. So the formula will consists of three parts.
+In our algorithm, we will open neurons at most 3 layer3 before the target layer. So the formula will consists of three parts.
 
-\subsubsection*{Compute the improvement of a single node}
+\subsubsection*{Compute the improvement of a single neuron}
 \fi
@@
 %For one layer before the target layer, the formula is simple and most accurate. 
-Suppose $a$ is a node in one layer before $z$. To estimate Improve\_max$_a^z$:
+Suppose $a$ is a neuron in one layer before $z$. To estimate Improve\_max$_a^z$:
 %we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
@@
 \begin{definition}
-	For all nodes $n$, let $sol(n)=$Sol\_max$_\emptyset^z(n)$ be the value of node $a$
+	For all neurons $n$, let $sol(n)=$Sol\_max$_\emptyset^z(n)$ be the value of neuron $a$
 	in the solution of the LP instance Sol\_max$_\emptyset^z$ to maximize $z$.
@@
 
-	%In particular, if $v(\hat{a})=\ReLU(v(a))$, then we will have 
+	%In particular, if $sol(\hat{a})=\ReLU(sol(a))$, then we will have 
 	%\begin{align*}
@@
 
-Now, define $sol'(\hat{a}) = \ReLU(v(a))$. 
+Now, define $sol'(\hat{a}) = \ReLU(sol(a))$. 
 That is,  
-sol'$(\hat{a})$ is the correct value for $\hat{a}$ (obtained if we open node $a$), 
+sol'$(\hat{a})$ is the correct value for $\hat{a}$ (obtained if we open neuron $a$), 
 compared to the LP abstraction for $sol(\hat{a})$.
@@
 
-	Similarly, let $v(b)$ be the value of $b$ in the LP solution of lower bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.
+%	
+%	Similarly, let $sol(b)$ be the value of $b$ in the LP solution of lower bound of $a$, and $sol(\hat{b})$ be the value of $\hat{b}$.
 Then the formula to estimate improvement of lower bound of $b$ is: \begin{align*}
-		I_b \approx -W_{ba}(v(\hat{b})-\ReLU(v(b))).
-	\end{align*}
+%		Improve\_min^z(b) \approx -W_{ba}(sol(\hat{b})-\ReLU(sol(b))).
+%	\end{align*}
 
@@
 
-To explain the formula, we use upper bound and the case that $W_{ba} > 0$ as an example.
+%To explain the formula, we use upper bound and the case that $W_{ba} > 0$ as an example.
 To compute the upper bound of $a$, $\hat{b}$ should be as large as possible.
-In the LP model, for fixed $v(b)$, the upper bound of $\hat{b}$ may be larger than $\ReLU(v(b))$.
-This is because in LP model, the upper bound of $v(\hat{b})$ is decided by the linear approximation rather than $\ReLU$ function.
-So, when node $b$ is open, if $v(b)$ do not change, then the upper bound of $a$ will be improved because the value of $v(\hat{b})$ will be lower to $\ReLU(v(b))$.
+In the LP model, for fixed $sol(b)$, the upper bound of $\hat{b}$ may be larger than $\ReLU(sol(b))$.
+This is because in LP model, the upper bound of $sol(\hat{b})$ is decided by the linear approximation rather than $\ReLU$ function.
+So, when neuron $b$ is open, if $sol(b)$ do not change, then the upper bound of $a$ will be improved because the value of $sol(\hat{b})$ will be lower to $\ReLU(sol(b))$.
+% 			
+%Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $sol(\hat{b})$ to $\ReLU(sol(b))$ is the major part of improvement.
 
-Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major part of improvement.
+\subsubsection*{Two Layer before $z$}
 
-\subsubsection*{Two layers before the target layer}
+Suppose $a$ is a neuron in two layers before $z$, we use $b$ to denote neurons in the layer between $a$ and $z$.
 
-For earlier layers, the formula will be more complex and less accurate.
-We will still focus on the source $v(\hat{b})-\ReLU(v(b))$.
-Basically, we hope to use $\sum_c W_{ca}W_{bc}$ to replace the coefficient $W_{bc}$ in last subsection.
-However, directly using $\sum_c W_{ca}W_{bc}$ will lose too much accuracy.
+In this case, the formula will be more complex and less accurate.
+We will still focus on the source $sol(\hat{a})-\ReLU(sol(a))$.
+Basically, we hope to use $\sum_b W_{bz}W_{ab}$ to replace the coefficient $W_{az}$ in last subsection.
+However, directly using $\sum_b W_{bz}W_{ab}$ will lose too much accuracy.
 So we try to improve the accuracy by considering more details from the LP solutions.
 
-For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative, which is the following definition.
+To estimate Improve\_max$_a^z$ , we consider the following help function:
 
 \begin{definition} \label{2layer}
-	Suppose we have a fixed target node $a$, and a fixed source node $b$ in two layers before $a$.
-Let $\UB,\LB$ be the function of precomputed upper and lower bound before the layer of $a$, and let $v$ be the function of values of nodes in the LP solution of upper bound of $a$.
-	To compute the improvement of of upper bound of $a$ by $b$, we define the following function $k$ for nodes $c$ in one layer before $a$:
+	Let $\UB,\LB$ be the function of precomputed upper and lower bound before the layer of $z$.
+	We define the following function $k$ for neurons $b$ in one layer before $z$:
 	\begin{align}
-		k(c) =
+		k(b) =
 		\begin{cases}
-			1, & \text{if } v(c) > 0 \text{ and } W_{ca} < 0\\
-			0, & \text{if } v(c) \leq 0 \text{ and } W_{ca} < 0\\
-			\frac{\UB(c)}{\UB(c)-\LB(c)}, & \text{if }W_{ca} > 0
+			1, & \text{if } sol(b) > 0 \text{ and } W_{bz} < 0\\
+			0, & \text{if } sol(b) \leq 0 \text{ and } W_{bz} < 0\\
+			\frac{\UB(b)}{\UB(b)-\LB(b)}, & \text{if }W_{bz} > 0
 		\end{cases}
@@
 We may use the following formula to estimate the improvement:  \begin{align*}
-	I_b \approx (v(\hat{b})-\ReLU(v(b)))\sum_c W_{bc}W_{ca}k(c).
-\end{align*}However, the error is still too large. This is because the improved value of a node $c$ can not exceed its precomputed upper and lower bound. Considering this, we can update our formula.
+	Improve\_max^z(a) \approx (sol(\hat{a})-\ReLU(sol(a)))\sum_b W_{bz}W_{ab}k(b).
+\end{align*}However, the error is still too large. This is because the improved value of a neuron $b$ can not exceed its precomputed upper and lower bound. Considering this, we can update our formula.
 
 \begin{definition}
-	Continue the assumption in Definition \ref{2layer}. To compute the improvement of of upper bound of $a$ by $b$, we define a distance function $D$:
+	Continue the assumption in Definition \ref{2layer}. To compute the improvement of of upper bound of $z$ by $a$, we define a distance function $D$:
 	\begin{align}
-		&D(b) = \ReLU(v(b))-v(\hat{b})\\
-			&D(c) =
+		&D(a) = \ReLU(sol(a))-sol(\hat{a})\\
+			&D(b) =
 		\begin{cases}
-			\max(\LB(c), 0, v(c)+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }W_{ca} < 0\\
-			\min(\UB(c), v(\hat{c})+D(b)k(c)W_{bc})-v(\hat{c}), & \text{if }  W_{ca} > 0
+			\max(\LB(b), 0, sol(b)+D(a)k(b)W_{ab})-sol(\hat{b}), & \text{if }W_{bz} < 0\\
+			\min(\UB(b), sol(\hat{b})+D(a)k(b)W_{ab})-sol(\hat{b}), & \text{if }  W_{bz} > 0
 		\end{cases}\\
-		&D(a) = \sum_c D(c)W_{ca}
+		&D(z) = \sum_b D(b)W_{bz}\\
+		&Utility\_max^z(a) = -D(z)
 	\end{align}
 \end{definition}
+ This is the formula to compute improvement of neurons two layers before.
 
-Then $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
-For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{ca}$ instead.
-This is the formula to compute improvement of nodes two layers before.
-
-\subsubsection*{Formula for nodes in 3 layers before}
+\subsubsection*{Three Layer before $z$}
 
@@
 
-The key problem is how to compute the coefficient $k$ for nodes in two layers before the target layer. To do this, we may use the values in the solution of LP model as follows:
+The key problem is how to compute the coefficient $k$ for neurons in two layers before the target layer. To do this, we may use the values in the solution of LP model as follows:
 
 \begin{definition}\label{3layer}
-	Suppose we have a fixed target node $a$ and a fixed source node $b$ in three layers before $a$.
+	Suppose we have a fixed target neuron $a$ and a fixed source neuron $b$ in three layers before $a$.
 Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bounds used in building MILP models.
-To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all nodes $c$ in 2 layers before the target node $a$ as follows:
+To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all neurons $c$ in 2 layers before the target neuron $a$ as follows:
 	\begin{align}
-		&v_0 = v(\hat{c}), v_1 = \ReLU(v(c)), v_2 = \frac{\UB(c)v(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
+		&v_0 = sol(\hat{c}), v_1 = \ReLU(sol(c)), v_2 = \frac{\UB(c)sol(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
 		&h(c) =
@@
 
-	First, $D(b) = \ReLU(v(b))-v(\hat{b})$.
+	First, $D(b) = \ReLU(sol(b))-sol(\hat{b})$.
 
-To compute $D(c)$ for nodes $c$ in two layer before $a$, we define \begin{align}
-	&u_0 = \max(\LB(c),\min(\UB(c),  v(c)+D(b)W_{bc}))\\
+To compute $D(c)$ for neurons $c$ in two layer before $a$, we define \begin{align}
+	&u_0 = \max(\LB(c),\min(\UB(c),  sol(c)+D(b)W_{bc}))\\
 	&u_1 = \begin{cases}
@@
 	\end{cases}\\
-	&D(c) = u_1-v(\hat{c})
+	&D(c) = u_1-sol(\hat{c})
 \end{align}
 
-	To compute $D(d)$ for nodes $d$ in one layer before $a$, we define 
+	To compute $D(d)$ for neurons $d$ in one layer before $a$, we define 
 	\begin{align}
 		&w_0 = \sum_c D(c)W_{cd}\\
-		&w_1 = \min(\UB(d),v(d)+w_0)\\		
+		&w_1 = \min(\UB(d),sol(d)+w_0)\\		
 		&D(d) =
 		\begin{cases}
-			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
-		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
-		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
+			w_1-sol({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
+		k(d)(w_1-sol({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
+		\ReLU(w_1)-sol(\hat{d})	, & \text{if }  W_{da} < 0
 		\end{cases}\\
@@
 	\end{align}
-\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
+\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening neuron $b$.
 For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{da}$  instead.

### 2024-09-20 ICLR25/formula.tex
upDate
update formula.tex

@@
 
+Suppose $a$ is a neuron in three layers before $z$, we use $b$ to denote neurons in two layer before $z$ and $c$ to denote neurons in one layer before $z$ and.
+
 This formula is based on previous subsection but more complex. In some network, running this formula may cost too much time.
@@
 \begin{definition}\label{3layer}
-	Suppose we have a fixed target neuron $a$ and a fixed source neuron $b$ in three layers before $a$.
 Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bounds used in building MILP models.
-To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all neurons $c$ in 2 layers before the target neuron $a$ as follows:
+We define the following function $h$ for all neurons $b$ in two layers before the target neuron $z$ as follows:
 	\begin{align}
-		&v_0 = sol(\hat{c}), v_1 = \ReLU(sol(c)), v_2 = \frac{\UB(c)sol(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
-		&h(c) =
+		&v_0 = sol(\hat{b}), v_1 = \ReLU(sol(b)), v_2 = \frac{\UB(b)sol(b)-\UB(b)\LB(b)}{\UB(b)-\LB(b)}\\
+		&h(b) =
 		\begin{cases}
@@
 \begin{definition}
-	Continue the assumption in Definition \ref{3layer}. To compute the improvement of of upper bound of $a$ by $b$, we define function $D$ layer by layer.
+	Continue the assumption in Definition \ref{3layer}. We define function $D$ layer by layer.
 
-	First, $D(b) = \ReLU(sol(b))-sol(\hat{b})$.
+	First, $D(a) = \ReLU(sol(a))-sol(\hat{a})$.
 
-To compute $D(c)$ for neurons $c$ in two layer before $a$, we define \begin{align}
-	&u_0 = \max(\LB(c),\min(\UB(c),  sol(c)+D(b)W_{bc}))\\
+To compute $D(b)$ for neurons $b$ in two layer before $z$, we define \begin{align}
+	&u_0 = \max(\LB(b),\min(\UB(b),  sol(b)+D(a)W_{ab}))\\
 	&u_1 = \begin{cases}
-		\ReLU(u_0)+h(c)(\frac{\UB(c)u_0-\UB(c)\LB(c)}{\UB(c)-\LB(c)}-\ReLU(u_0)), & \text{if }\LB(c) < 0\\
-	u_0, & \text{if }  \LB(c) \geq 0
+		\ReLU(u_0)+h(b)(\frac{\UB(c)u_0-\UB(b)\LB(b)}{\UB(b)-\LB(b)}-\ReLU(u_0)), & \text{if }\LB(b) < 0\\
+	u_0, & \text{if }  \LB(b) \geq 0
 	\end{cases}\\
-	&D(c) = u_1-sol(\hat{c})
+	&D(b) = u_1-sol(\hat{b})
 \end{align}
 
-	To compute $D(d)$ for neurons $d$ in one layer before $a$, we define 
+	To compute $D(c)$ for neurons $c$ in one layer before $z$, we define 
 	\begin{align}
-		&w_0 = \sum_c D(c)W_{cd}\\
-		&w_1 = \min(\UB(d),sol(d)+w_0)\\		
-		&D(d) =
+		&w_0 = \sum_b D(b)W_{bc}\\
+		&w_1 = \min(\UB(c),sol(c)+w_0)\\		
+		&D(c) =
 		\begin{cases}
-			w_1-sol({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
-		k(d)(w_1-sol({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
-		\ReLU(w_1)-sol(\hat{d})	, & \text{if }  W_{da} < 0
+			w_1-sol({c}), & \text{if }W_{cz} > 0 \text{ and } \LB(c)\geq 0\\
+		k(c)(w_1-sol({c})), & \text{if }W_{cz} > 0 \text{ and } \LB(c)< 0\\
+		\ReLU(w_1)-sol(\hat{c})	, & \text{if }  W_{cz} < 0
 		\end{cases}\\
-		&D(a) = \sum_d D(d)W_{da}
+		&D(z) = \sum_c D(c)W_{cz}\\
+		&Utility\_max^z(a) = -D(z)
 	\end{align}
-\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening neuron $b$.
-For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{da}$  instead.
+\end{definition}

### 2024-09-20 ICLR25/experiments.tex
table
formula

@@
 	\centering
-	\begin{tabular}{|c||c|c|c|c|}
+	\begin{tabular}{|c||c|c|c|}
 		\hline
-		\text{Number $K$}  &  \text{Without ratio} &\text{With ratio} &  \text{Incoming Weights} \cite{ DivideAndSlide} & \text{Random} \\ \hline
+		\text{Number $K$}  &  \bf Utility&  \text{Incoming Weights} \cite{ DivideAndSlide} & \text{Random} \\ \hline
 		\hline
-		0  &   1.761  & 1.761 & 1.761 & 1.761  \\ \hline
-		5  & 1.532  & 1.533 & &   \\ \hline
-		10  & 1.371 & 1.373 & 1.651 & 1.696  \\ \hline
-		15  & 1.247 & 1.244 &   &   \\ \hline
-		20  & 1.145 & 1.136 & 1.557 & 1.619  \\ \hline
-		25  & 1.061 & 1.057 &  &   \\ \hline
-		30  & 0.989 & 1.067 & 1.489 & 1.546  \\ \hline
-		35  & 0.934 & 1.091 &  &   \\ \hline
-		40  &  & & 1.447 & 1.469  \\ \hline
-		50  &  & & 1.426 & 1.388  \\ \hline
-		116 (max) &  0.895 & 0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
+		0  &   1.761  & 1.761 & 1.761  \\ \hline
+		5  & \bf 1.532  & &   \\ \hline
+		10  & \bf 1.371  & 1.651 & 1.696  \\ \hline
+		15  & \bf 1.247  &   &   \\ \hline
+		20  & \bf 1.145  & 1.557 & 1.619  \\ \hline
+		25  & \bf 1.061  &  &   \\ \hline
+		30  & \bf 0.989  & 1.489 & 1.546  \\ \hline
+		35  & \bf 0.934  &  &   \\ \hline
+		40  & \bf 0.914 & 1.447 & 1.469  \\ \hline
+		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
 	\end{tabular}
-	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs \cite{ DivideAndSlide} vs random choice).}
+	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (utility function vs \cite{ DivideAndSlide} vs random choice).}
 	\label{tab:example1}

### 2024-09-20 ICLR25/formula.tex
formula

--- 2024-09-20 ICLR25/formula.tex
@@
 We denote by $n< z$ the fact that a neuron appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
-Let us denote (Sol\_max$_X^z(n))_{n \leq z})$ is a solution of $\mathcal{M}_X$ 
+Let us denote (Sol\_max$_X^z(n))_{n \leq z}$ is a solution of $\mathcal{M}_X$ 
 maximizing $z$. In particular, Sol\_max$_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
 
-Consider (Sol\_max$_\emptyset^z(n))_{n \leq z})$ (this is obtained by {\em one} call to an LP solver, so can be obtained very efficiently).
+Consider (Sol\_max$_\emptyset^z(n))_{n \leq z}$ (this is obtained by {\em one} call to an LP solver, so can be obtained very efficiently).
 An accurate utility function is to evaluate 
@@
 compared with using only LP. 
-Similarly, we define (Sol\_min$_\emptyset^z(n))_{n \leq z})$ and 
+We have Improve\_max$^z(a)\geq 0$ as Sol\_max$_{\{a\}}^z$ fullfils all the constraints of 
+$\mathcal{M}_\emptyset$, so Sol\_max$_{\{a\}}^z(z) \leq$ Sol\_max$_\emptyset^z(z)$.
+
+Similarly, we define (Sol\_min$_\emptyset^z(n))_{n \leq z}$ and 
 Improve\_min$_a^z$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
 would however be very time consuming when the number of neurons $a$ to evaluate is large.
-
-Instead, we focus on the following upper bounding of Improve\_max$_a^z$, thanks to Proposition \ref{LP}.
+Instead, we focus on the following upper bounding of Improve\_max$_a^z$.
 
@@
 \subsubsection*{Compute the improvement of a single neuron}
-\fi
 
@@
 
-%For one layer before the target layer, the formula is simple and most accurate. 
-Suppose $a$ is a neuron in one layer before $z$. To estimate Improve\_max$_a^z$:
-%we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
+\fi
 
-\begin{definition}
 For all neurons $n$, let $sol(n)=$Sol\_max$_\emptyset^z(n)$ be the value of neuron $a$
@@
 
-	We define : 
+%For one layer before the target layer, the formula is simple and most accurate. 
+To estimate Improve\_max$_a^z$, we define Utility\_max$^z(a)$, first for neurons $a$ one layer before $z$:
+%we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
+
 	\begin{align}
-		Utility\_max^z(a) = W_{az} \times (sol(\hat{a})- \ReLU(sol(a))).
+		Utility\_max^z(a) = |W_{az} \times (sol(\hat{a})- \ReLU(sol(a)))|.
 	\end{align}
@@
 \begin{proof}
-Indeed, consider $(sol'(n))_{n \leq z})_{n \leq z})$ with
+Consider $(sol'(n))_{n \leq z})_{n \leq z})$ with
 $sol'(n)=sol(n)$ for all $n \notin \{z,\hat{a}\}$.
@@
 
+Thus, Utility\_max$^z(a)$ can be used to approximate 
+Improve\_max$^z(a)$. In particular, consider a very frequent case where $W_{az}<0$.
+In this case, to maximize $z$, the LP engine sets $sol(\hat{a})$ to its minimal value\dots which happens to be $sol(\hat{a})=ReLU(a)$, thanks to Proposition \ref{LP}. 
+In this frequent case, we have Utility\_max$^z(a)=0$, and thus Improve\_max$^z(a)=0$. 
+In particular, this node will have the smallest utility (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  Sol\_max$_{\{a\}}^z(z)$. 
+This is one stricking difference (but not the only one) with choosing utility based on 
+$|W_{az}|$ \cite{DivideAndSlide}.
+
 %	
@@
 %	\end{align*}
-
-\end{definition}
 
@@
 
-\subsubsection*{Two Layer before $z$}
+\medskip
 
-Suppose $a$ is a neuron in two layers before $z$, we use $b$ to denote neurons in the layer between $a$ and $z$.
+Now, consider neurons $a$ two layers before $z$.
+We use $b$ to denote neurons in the layer between $a$ and $z$.
+If we open $a$, then the change in the weight of $a$ will still be $sol(\hat{a})-\ReLU(sol(a))$ as above.
+Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b$ in the intermediate layer.
+Based on Proposition \ref{LP}, we can evaluate how opening $a$ impacts each value of 
+$\hat{b}$, through coefficient $k(\hat{b})$, by using the upper and lower bound
+$\UB(b),\LB(b)$:
+\begin{itemize}
+ \item If $W_{bz}\leq0$, then $k(\hat{b})=W_{ab}$ if $sol(b) > 0$, and $k(\hat{b})=0$ if $sol(b) < 0$
+ \item If $W_{bz}>0$, then $k(\hat{b})=W_{ab} \frac{\UB(b)}{\UB(b)-\LB(b)}$
+\end{itemize}
+%$\sum_b W_{bz}W_{ab}$ to replace the coefficient $W_{az}$ in last subsection.
 
-In this case, the formula will be more complex and less accurate.
-We will still focus on the source $sol(\hat{a})-\ReLU(sol(a))$.
-Basically, we hope to use $\sum_b W_{bz}W_{ab}$ to replace the coefficient $W_{az}$ in last subsection.
-However, directly using $\sum_b W_{bz}W_{ab}$ will lose too much accuracy.
-So we try to improve the accuracy by considering more details from the LP solutions.
+%To estimate Improve\_max$_a^z$ , 
+Indeed, if $W_{bz}\leq0$, then the LP solver sets $sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $ReLU(b)$ according to Proposition \ref{LP}.
+If $sol(b) < 0$, then we have a clip at $sol(\hat{b})=ReLU(b)=0$ and opening $a$ does not help. If $sol(b) > 0$, then we have $sol(\hat{b})=ReLU(b)=b$ and every change from 
+$a$ is reflected with a coefficient $W_{ab}$ on $b$. 
+Last, if $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
+sets $sol(\hat{b}) = sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)}$ to maximize $z$.
 
-To estimate Improve\_max$_a^z$ , we consider the following help function:
+%We then define 
+%\begin{align*}
+%	Utility\_max^z(a) = (sol(\hat{a})-\ReLU(sol(a)))\sum_b k(b).
+%\end{align*}
 
-\begin{definition} \label{2layer}
-	Let $\UB,\LB$ be the function of precomputed upper and lower bound before the layer of $z$.
-	We define the following function $k$ for neurons $b$ in one layer before $z$:
-	\begin{align}
-		k(b) =
+We define a distance $D$ to account for the fact that a neuron $b$ 
+can not exceed $\LB(b),\UB(b)$:
+	\begin{align*}
+		&D(\hat{a}) = sol(\hat{a}) - \ReLU(sol(a)) \geq 0\\
+			&D(\hat{b}) =
 		\begin{cases}
-			1, & \text{if } sol(b) > 0 \text{ and } W_{bz} < 0\\
-			0, & \text{if } sol(b) \leq 0 \text{ and } W_{bz} < 0\\
-			\frac{\UB(b)}{\UB(b)-\LB(b)}, & \text{if }W_{bz} > 0
+			sol(\hat{b}) - \min(\UB(b), sol(\hat{b}) - D(\hat{a}) k(\hat{b})), & \text{if }  W_{bz} > 0 \\
+			sol(\hat{b}) - \max(\LB(b), 0, sol(\hat{b}) -D(\hat{a}) k(\hat{b})), & \text{if }W_{bz} < 0\\
 		\end{cases}
-	\end{align} 
-\end{definition}
+		\end{align*}
 
-We may use the following formula to estimate the improvement:  \begin{align*}
-	Improve\_max^z(a) \approx (sol(\hat{a})-\ReLU(sol(a)))\sum_b W_{bz}W_{ab}k(b).
-\end{align*}However, the error is still too large. This is because the improved value of a neuron $b$ can not exceed its precomputed upper and lower bound. Considering this, we can update our formula.
+We can now set
 
-\begin{definition}
-	Continue the assumption in Definition \ref{2layer}. To compute the improvement of of upper bound of $z$ by $a$, we define a distance function $D$:
-	\begin{align}
-		&D(a) = \ReLU(sol(a))-sol(\hat{a})\\
-			&D(b) =
-		\begin{cases}
-			\max(\LB(b), 0, sol(b)+D(a)k(b)W_{ab})-sol(\hat{b}), & \text{if }W_{bz} < 0\\
-			\min(\UB(b), sol(\hat{b})+D(a)k(b)W_{ab})-sol(\hat{b}), & \text{if }  W_{bz} > 0
-		\end{cases}\\
-		&D(z) = \sum_b D(b)W_{bz}\\
-		&Utility\_max^z(a) = -D(z)
-	\end{align}
-\end{definition}
- This is the formula to compute improvement of neurons two layers before.
+$$ Utility\_max^z(a) = \sum_b W_{bz} D(\hat{b})$$
 
+We proceed inductively in the same way to define Utility$\_max^z(a)$ for deeper neuron $a$.
+
+\iffalse
 \subsubsection*{Three Layer before  $z$}
@@
 For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{da}$  instead.
+
+\fi

### 2024-09-20 ICLR25/formula.tex

@@
 \begin{definition}
-	Continue the assumption in Definition \ref{3layer}. To compute the improvement of of upper bound of $a$ by $b$, we define function $D$ layer by layer.
+	Continue the assumption in Definition \ref{3layer}. We define function $D$ layer by layer.
 
-	First, $D(b) = \ReLU(sol(b))-sol(\hat{b})$.
+	First, $D(a) = \ReLU(sol(a))-sol(\hat{a})$.
 
-To compute $D(c)$ for neurons $c$ in two layer before $a$, we define \begin{align}
-	&u_0 = \max(\LB(c),\min(\UB(c),  sol(c)+D(b)W_{bc}))\\
+To compute $D(b)$ for neurons $b$ in two layer before $z$, we define \begin{align}
+	&u_0 = \max(\LB(b),\min(\UB(b),  sol(b)+D(a)W_{ab}))\\
 	&u_1 = \begin{cases}
-		\ReLU(u_0)+h(c)(\frac{\UB(c)u_0-\UB(c)\LB(c)}{\UB(c)-\LB(c)}-\ReLU(u_0)), & \text{if }\LB(c) < 0\\
-	u_0, & \text{if }  \LB(c) \geq 0
+		\ReLU(u_0)+h(b)(\frac{\UB(c)u_0-\UB(b)\LB(b)}{\UB(b)-\LB(b)}-\ReLU(u_0)), & \text{if }\LB(b) < 0\\
+	u_0, & \text{if }  \LB(b) \geq 0
 	\end{cases}\\
-	&D(c) = u_1-sol(\hat{c})
+	&D(b) = u_1-sol(\hat{b})
 \end{align}
 
-	To compute $D(d)$ for neurons $d$ in one layer before $a$, we define 
+	To compute $D(c)$ for neurons $c$ in one layer before $z$, we define 
 	\begin{align}
-		&w_0 = \sum_c D(c)W_{cd}\\
-		&w_1 = \min(\UB(d),sol(d)+w_0)\\		
-		&D(d) =
+		&w_0 = \sum_b D(b)W_{bc}\\
+		&w_1 = \min(\UB(c),sol(c)+w_0)\\		
+		&D(c) =
 		\begin{cases}
-			w_1-sol({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
-		k(d)(w_1-sol({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
-		\ReLU(w_1)-sol(\hat{d})	, & \text{if }  W_{da} < 0
+			w_1-sol({c}), & \text{if }W_{cz} > 0 \text{ and } \LB(c)\geq 0\\
+		k(c)(w_1-sol({c})), & \text{if }W_{cz} > 0 \text{ and } \LB(c)< 0\\
+		\ReLU(w_1)-sol(\hat{c})	, & \text{if }  W_{cz} < 0
 		\end{cases}\\
-		&D(a) = \sum_d D(d)W_{da}
+		&D(z) = \sum_c D(c)W_{cz}\\
+		&Utility\_max^z(a) = -D(z)
 	\end{align}
-\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening neuron $b$.
-For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{da}$  instead.
+\end{definition}
 

### 2024-09-20 ICLR25/Paper_noProof.tex
section 4
experiments.

@@
 
-\newcommand{\toolname}{\CMP}
+\newcommand{\toolname}{Hybrid MILP}
 
@@
 Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
-This gives rise to a very efficient yet accurate algorithm.
-Implemented in {\em Hybrid MILP (hMILP)}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances ($8-15\%$), while keeping a reasonable runtime ($<500s$ on average per instance).
+Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances ($8\%$-$15\%$), while keeping a reasonable runtime ($46s$-$417s$ on average per instance).
 \end{abstract}
@@
 
-\input{comppaths}
-
-\begin{table}
-	\centering
-	\begin{tabular}{||l||c|c|c|c||c||}
-		\hline \hline
-		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
-		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
-		\hline
-		MNIST 6$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
-		(92s) & 13\% \bf (46s) \\ \hline
-		MNIST 6$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
-		MNIST 9$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
-		MNIST 9$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
-		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
-		\bf 10\% (402s) \\ \hline
-		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
-		CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
-	\end{tabular}
-	\caption{Gap $\%$ between attackable images and verifiable images ({\em lower is better}), as certified by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second).
-The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained to be easy to verify using Wong, but with a very low accuracy level), provided for reference.}
-	\label{table_hybrid}
-	\end{table}
+\input{formula}
 

### 2024-09-20 ICLR25/experiments.tex
experiments.

@@
 %
-We implemented \toolname in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
-with 256 GB of main memory and an NVIDIA RTX 3090 (not used for CMP).
-
-We conducted our evaluation on neural networks obtained from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided).
-These verification-agnostic DNNs have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ and $6 \times 500$.
-We selected the 4 first because they have been tested in both \cite{prima} and \cite{crown}, they have good accuracy ($>94\%$ \cite{prima}),
-and depite their small sizes there is still a large portion ($12\%$ to $20\%$) of images which are {\em undetermined} by these SOTA methods, that is images neither verified nor for which an attack has been found  \cite{attack}.
-Hence more accurate methods are useful.
-The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (very high accuracy and few attacks) to understand the scaling of CMP.
-Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{crown}.
-All these DNNs tackle the MNIST benchmark, which is not a limitation as we want to validate that focusing on compensating strength improves the accuracy: we do not claim that the particular CMP implementation is the most efficient in all the situations.
-
-To obtain results comparable with \cite{prima,crown}, 
-we evaluated CMP on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ for the first 1000 images of the dataset.
-For $6\times 500$ (results not reported in \cite{prima,crown}), we run all the tools ourselves for the first 200 images, given the computational overhead associated with such larger network.
-Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
-
-\smallskip
-
-\noindent{\bf Baseline}: 
-We compare the following verifiers performing value-abstraction:
-\begin{itemize}
-	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}. We report the runtime from our  implementation in CMP. 
-	%It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA). 
-	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN \cite{crown}. We use the results reported in \cite{prima} and \cite{crown} respectively for 
-	$5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$.
-	We report our experimental results for the $6\times500$ DNN as they are not available in prior work.
-Notice that PRIMA and CROWN use massively parallel (>4000 threads) GPUs, and run 16 CPU threads for the first 4 benchmarks, compared with 20 CPU threads and no GPU for CMP.
-	\item We also tested MN-BaB \cite{ferrari2022complete} on $6\times500$
-	(slightly lower accuracy and slower than $\alpha$,$\beta$-CROWN), 
-	in line with results reported in \cite{ferrari2022complete} for other DNNs.
-Further, results for MN-BaB on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$	are not reported in \cite{ferrari2022complete} or elsewhere.
-	We thus do not include MN-BaB results in Table \ref{tab:example}, to avoid clutter.
-%	They use GPU while we do not. When computing the whole correlated space, 
-%	parallelization is difficult.
-%	Notice that on these DNNs, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
-This is doable on the first few layers as the number of integer variable is not too large.
-By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
-%	Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and using GPU implementation (while we do not). Performance of pure BaB on these 
-%	"hard to verify" DNNs is however impaired by the large number of branchs to consider.
-Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running the branching heuristic BaB-FSB.
-%	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
-	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
-	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods in accuracy and time \cite{crown}.
-
-\end{itemize}
+We implemented \toolname\ in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
+with 256 GB of main memory and an NVIDIA RTX 3090.
 
@@
 \begin{enumerate}
-	\item How does the the choice of the set $Z$ impacts the accuracy of $\MILP_Z$? 
-	\item Can compensating strength, as implemented in CMP, outperform accuracy of the SOTA? 
+	\item How does the the choice of the set $X$ impacts the accuracy of $\MILP_X$? 
+	\item How accurate is Hybrid MILP, and how efficient is it?
 \end{enumerate}
 
-\subsection{Utility of Heuristic based on Compensation Strength  }
+\subsection{Evaluation of the Utility function to choose nodes to open}
 
 %The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-To measure the impact of the heuristic based on compensation strength, we focused on the smallest DNN (i.e.
-$5\times 100$) so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
+To measure the impact of the utility function to select nodes to open, we focused on a small hard DNN, namely $5\times 100$, so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
 We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
-
 To measure the accuracy, we measure the uncertainty of all nodes in a layer:
@@
 
-\begin{table}[t!]	
+\begin{table}[b!]	
 	\centering
@@
 		\hline
-		\text{Number $K$}  &  \bf Utility&  \text{Incoming Weights} \cite{ DivideAndSlide} & \text{Random} \\ \hline
+		\text{Number $K$}  &  \bf Utility&  \text{Strength} \cite{ DivideAndSlide} & \text{Random} \\ \hline
 		\hline
@@
 		35  & \bf 0.934  &  &   \\ \hline
-		40  & \bf 0.914 & 1.447 & 1.469  \\ \hline
+		40  & \bf 0.921 & 1.447 & 1.469  \\ \hline
 		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
 	\end{tabular}
-	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (utility function vs \cite{ DivideAndSlide} vs random choice).}
+	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer (our utility function vs \cite{ DivideAndSlide} vs random choice).}
 	\label{tab:example1}
@@
 The bounds for nodes of the first two layers are computed exactly using the full MILP encoding.
-Let $d$ be a neuron of the third layer.
-We let $\delta_{\pi,\pi'}=1$ if $(\pi,\pi')$ is compensating, 0 otherwise.
-We evaluate the pair $(c,c')$ of nodes in the previous (second) layer in the following way: let $comp(c,c')=\sum_{b} \delta(bcd,bc'd) \val_{\vx}(b) \min( weight(bcd),weight(bc'd))$, meaning that we take into account all the sources $b$ such that $(bcd,bc'd)$ is compensating.
+We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our utility function, vs choosing $K$ nodes from layers $1$ and $2$.
+We compared with a random choice in the first two layers, and also choice based on strength in \cite{DivideAndSlide}, defined as
+$strength(n) = (UB(n)-LB(n))\cdot |W_{cd}|$, which is thus limited to the previous (2sd hidden layer).
 
-We select the pair $(c,c')$ with the highest $comp(c,c')$, and let $Z=\{c,c'\}$.
-Then, we add nodes iteratively to $Z$, starting with the highest $comp(c)=\sum_{c' \in Z} comp(c,c')$.
-Further, we can add nodes $b$ from the first layer, taking into account compensating pairs $(a b c d, a b' c' d)$ for all $\{c,c'\} \in C$.
-Let $comp(b,b')=\sum_a \sum_{c,c' \in Z} \delta(abcd,ab'c'd) \val_{\vx}(a) \min( weight(abcd)$, $weight(ab'c'd))$ and add $b,b'$ to $Z$ with the highest $comp(b,b')$.
-We then let $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$, and iteratively select nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
-The intuition behind the formula is straightforward: $\val_{\vx}(a)weight(abcd)$ is the contribution from node $a$ to the target $d$ using $weight(abcd)$, and min of two paths is a natural value to represent the strength of compensation: if one of them is very small, the effect of compensation will also be very small.
-
-We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes from layers $1$ and $2$.
-We test using compensation, compared with a random choice, and also choice based on strength in \cite{ DivideAndSlide}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$.
-It is however limited to choosing ReLU in the previous layer 2.
-This choice is fine for few nodes (10,20), as there is a high correlation between $comp(c)$ being high and $W_{cd}$ being high.
-However, as soon as many nodes can be chosen in $Z$, compensate becomes much more accurate.
-Even random becomes more accurate as the number of nodes grows, as \cite{ DivideAndSlide} only has access to nodes $c$ in layer 2, and not to nodes $b$ in layer 1.
-For comparison, compensate is the most accurate, from 30 nodes, experimentally validating that compensating strength is the important factor to consider.
+The Utility function reveals to select very important nodes: already with 35 out of 116 nodes, the accuracy is improved by $95\%$ what can be done if all 116 nodes are opened compared with LP (K=0).
+It is also much more accurate than using Incoming weights: already with 5 (resp.
+10) nodes chosen by our utility function is more accurate than $20$ (resp.
+$40$) nodes chosen by Incoming weights.
+That is more than 4 reduction in the number of nodes necessary for similar accuracy.
+Random is even worst Strength up to 30 nodes, then selecting in earlier layers appear to be more useful as there are not so many nodes to open in the previous layer.
 
@@
 
-\subsection{Comparison with Prior State of the Art}
+\subsection{Comparison with $\alpha,\beta$ Crown}
+
+We conducted our evaluation on the neural networks tested in \cite{crown},
+which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.
+
+Namely, these are 6 {\em hard} ReLU-DNNs: 5 MNIST DNN from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided) as well as 1 CIFAR CNN from 
+\cite{AdversarialTrainingAndProvableDefenses}, also see \cite{SDPFI}. 
+For reference, we also report an easy but very large ResNet Network for CIFAR10, already tested with $\alpha,\beta$ CROWN.
+We report in Table \ref{table_hybrid} the $\%$ of undecided images, that is the $\%$ of images than can be neither falsified (by $\alpha,\beta$-CROWN) nor verified by the tested verifier, among the 100 first images for each MNIST or CIFAR10 benchmark.
+
+\begin{table}[t!]
+	\centering
+	\begin{tabular}{||l||c|c|c|c||c||}
+		\hline \hline
+		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
+		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
+		\hline
+		MNIST 5$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
+		(92s) & 13\% \bf (46s) \\ \hline
+		MNIST 5$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
+		MNIST 8$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
+		MNIST 8$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
+		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
+		\bf 10\% (402s) \\ \hline
+		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
+		CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
+	\end{tabular}
+	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second).
+The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
+	\label{table_hybrid}
+	\end{table}
+
+Interpretation: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN, 
+as it is called first and it is sufficient to have $0\%$ undecided images, as shown even on the very large ResNet.
+
+On hard instances (the 6 first DNNs tested), Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, 10 times less even on smaller DNNs.
+It can scale up to quite large hard CNN instances, such as CNN-B-Adv with 2M parameters and 20K activations.
+
+Compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%$-$43\%$ wrt $\alpha,\beta$-Crown with TO of 2000s.
+It is also from 20x faster on smaller networks to similar time on the largest DNN.
+Compared with $\alpha,\beta$-Crown with a time-out of TO=30s, the accuracy gap is even larger (e.g.
+$11\%$ for CNN-B-Adv, i.e.
+half undecided images), although the average runtime is also obviously larger (solving hard istances takes longer than solving easy instances).
+
+Last, compared with refined $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5x100, 5x200), refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than our Hybrid MILP, but with longer runtime (up to 2x on 5x100).
+On intermediate DNNs (8x100,8x200), full MILP invoked by refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images, while having longer runtime.
+Last, refined $\beta$-Crown cannot scale to larger instances (6x500, CNN-B-Adv), while Hybrid MILP can.
+
+\iffalse
+
+These verification-agnostic DNNs have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ and $6 \times 500$.
+We selected the 4 first because they have been tested in both \cite{prima} and \cite{crown}, they have good accuracy ($>94\%$ \cite{prima}),
+and depite their small sizes there is still a large portion ($12\%$ to $20\%$) of images which are {\em undetermined} by these SOTA methods, that is images neither verified nor for which an attack has been found  \cite{attack}.
+Hence more accurate methods are useful.
+The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (very high accuracy and few attacks) to understand the scaling of CMP.
+Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{crown}.
+All these DNNs tackle the MNIST benchmark, which is not a limitation as we want to validate that focusing on compensating strength improves the accuracy: we do not claim that the particular CMP implementation is the most efficient in all the situations.
+
+To obtain results comparable with \cite{prima,crown}, 
+we evaluated CMP on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ for the first 1000 images of the dataset.
+For $6\times 500$ (results not reported in \cite{prima,crown}), we run all the tools ourselves for the first 200 images, given the computational overhead associated with such larger network.
+Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
+
+\smallskip
+
+\noindent{\bf Baseline}: 
+We compare the following verifiers performing value-abstraction:
+\begin{itemize}
+	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}. We report the runtime from our  implementation in CMP. 
+	%It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA). 
+	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN \cite{crown}. We use the results reported in \cite{prima} and \cite{crown} respectively for 
+	$5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$.
+	We report our experimental results for the $6\times500$ DNN as they are not available in prior work.
+Notice that PRIMA and CROWN use massively parallel (>4000 threads) GPUs, and run 16 CPU threads for the first 4 benchmarks, compared with 20 CPU threads and no GPU for CMP.
+	\item We also tested MN-BaB \cite{ferrari2022complete} on $6\times500$
+	(slightly lower accuracy and slower than $\alpha$,$\beta$-CROWN), 
+	in line with results reported in \cite{ferrari2022complete} for other DNNs.
+Further, results for MN-BaB on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$	are not reported in \cite{ferrari2022complete} or elsewhere.
+	We thus do not include MN-BaB results in Table \ref{tab:example}, to avoid clutter.
+%	They use GPU while we do not. When computing the whole correlated space, 
+%	parallelization is difficult.
+%	Notice that on these DNNs, PRIMA resort to refined bounds on the first few layers (3 or 4) using exact MILP encoding of all the nodes (which is easily parallelized - 16 nodes considered in parallel in PRIMA).
+This is doable on the first few layers as the number of integer variable is not too large.
+By comparison, we run MILP on all the layers, but with a bounded number of integer variables to control the runtime and to scale to all the layers.
+%	Its main idea is to implement a very efficient Branch and Bound (BaB) verification tool, subsuming BaBSR \cite{BaB}, and using GPU implementation (while we do not). Performance of pure BaB on these 
+%	"hard to verify" DNNs is however impaired by the large number of branchs to consider.
+Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running the branching heuristic BaB-FSB.
+%	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
+	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
+	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods in accuracy and time \cite{crown}.
+
+\end{itemize}
 
@@
 However, it is worth remarking that the notion of compensation strength is independent of activation function, and therefore, an interesting direction of future work would be to explore the impact of compensation strength-based approaches for other activation functions.
+\fi

### 2024-09-20 ICLR25/introduction.tex
experiments.

@@
 
-In this paper, we focused on 6 {\em hard} ReLU-DNNs that have been previously tested in one or both of \cite{SDPFI},\cite{crown}, and with a large gap ($>20\%$) between images that can be certified and the upper bound when we remove those which can be falsified.
-In turns, hard instances does not necessarily mean very large DNNs, the smallest of the DNN considered having only 500 hidden neurons, namely 5x100 for MNIST.
+In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($>20\%$) between images that can be certified 
+by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.
+In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely 5x100 for MNIST.
 We first dwelve into the scaling of $\alpha,\beta$- Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
@@
 		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
-		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
+		MNIST 5$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
 		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
-		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+		MNIST 5$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
 		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
-		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+		MNIST 8$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
 		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
-		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+		MNIST 8$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
 		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
@@
 		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
-		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
+		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
 		$\epsilon = 0.026$ & &  &6200s &  5220s & 6100s
 		  \\  \hline
-		  MNIST 6$\times$100 & 99\% & 90\% & 28\% & $40\%$ & 37 \%    \\
+		  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $40\%$ & 37 \%    \\
 		  TO=2000s & &  & 1250s  & 1343s & 1466s \\  \hline	

### 2024-09-20 ICLR25/Paper_noProof.tex
exp + conclu

@@
 
-In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
-This is experimentally confirmed by the fact that DNNs harder to verify (verification-agnostic) also exhibit paths with larger compensating strength than  robustly-trained DNNs.
-
-Based on this idea of compensating pairs of paths, we proposed the $\MILP_{Z}$ abstraction considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Our empirical studies revealed that CMP, selecting $Z$ to cover only {\em a few} paths with the most significant compensation, can yield highly accurate results, up to 20\% more accurate than SOTA within the same runtime, again validating the focus on compensating strength.
-This underscores the potential of compensating strength as an innovative and promising avenue for enhancing DNN verification.
-We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.
+In this paper, we studied the LP relaxation of the exact MILP encoding of ReLU-DNNs.
+It allowed us to accurately assess when the relaxation of a node impacts very little 
+the accuracy, and when it impacts the accuracy importantly, in which case representing it with a binary/integer variable is preferable.
+This allows us to select a small set of important neurons to encode as a binary variables, while improving accuracy drastically, necessitating $>4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
+Our empirical studies revealed that Hybrid MILP, can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp) within the same runtime.
+This opens a lot of perspective, among which: verifying efficiently hard instances; certifying robustness of images for larger $\epsilon$ neighbourhoods, verifying global rather than local properties \cite{lipshitz}.
 \newpage

### 2024-09-20 ICLR25/experiments.tex
exp + conclu

@@
 Namely, these are 6 {\em hard} ReLU-DNNs: 5 MNIST DNN from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided) as well as 1 CIFAR CNN from 
-\cite{AdversarialTrainingAndProvableDefenses}, also see \cite{SDPFI}. 
+\cite{AdversarialTrainingAndProvableDefenses}, also see \cite{SDPFI}, with the same $\epsilon$ setting.
 For reference, we also report an easy but very large ResNet Network for CIFAR10, already tested with $\alpha,\beta$ CROWN.
-We report in Table \ref{table_hybrid} the $\%$ of undecided images, that is the $\%$ of images than can be neither falsified (by $\alpha,\beta$-CROWN) nor verified by the tested verifier, among the 100 first images for each MNIST or CIFAR10 benchmark.
+We report in Table \ref{table_hybrid} the $\%$ of undecided images, that is the $\%$ of images than can be neither falsified (by $\alpha,\beta$-CROWN) nor verified by the tested verifier, among the 100 first images for each MNIST or CIFAR10 benchmark, the exact same setting and DNNs as used in Table \ref{table_beta}.
 
@@
 Last, refined $\beta$-Crown cannot scale to larger instances (6x500, CNN-B-Adv), while Hybrid MILP can.
+
+\subsection{Finer Grain evaluation of Accuracy}
+
+In order to evaluate the accuracy of Hybrid MILP in a finer way, showcasing 
+the capabilities to have a very accurate and efficient verifier, we consider
+a quantitative questions for each image, rather than a pure yes (verified)/ no (not verified) question.
+Namely, we compute the $\epsilon$ for which the verifier can certify local-robustness around a given image, which makes sense as there is little rationale in setting a particular $\epsilon$ (which is however the usual local-robustness setting).
+
+For that, we considered the DNN 6x500, and the 20 first images from the MNIST benchmark.
+We first run the attack from $\alpha,\beta$-Crown for varying $\epsilon$, using a binary search, to set up an upper bound on $\epsilon$ (the initialization is $\epsilon \in [0,1]$).
+Then we run binary search with a global time out of $10 000s$, initialized from $0$ to this upper bound, where each call is either to $\alpha,\beta$-Crown with TO=2000s, or Hybrid MILP.
+We report the results (upper bound, best bound verified by $\alpha,\beta$-Crown and by Hybrid MILP) for each image. We report the results in Fig. \ref{fig2}
+
+\begin{figure}[t!]
+	\begin{centering}
+\includegraphics[scale=0.5]{epsilon.png}.
+\caption{$\epsilon$-robustness proved after $10 000s$ for each of the 20 first images of MNIST.}
+\label{fig2}
+	\end{centering}
+\end{figure}
+
+Analysis: in 90\% of the cases, Hybrid MILP is very close to the upper bound.
+On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible the upper bound did not find a close attack to robustness.
+
+Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, but for 2 cases where $\alpha,\beta$-CROWN is already very close to the upper bond.
+On average, the $\epsilon$ gap to upper bound is $0.014$ for Hybrid MILP, and $0.42$ for
+$\alpha,\beta$-CROWN.
+
+\subsection{Comparison with other Verifiers?}
+
+We volontarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider much finer parameter choice without too much cluter.
+
+Notice that several other verifiers were already reported \cite{crown} on these same DNNs, with defavorable comparison towards $\alpha,\beta$-CROWN (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc).
+Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd
+of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN.
+Concerning MnBAB \cite{ferrari2022complete}, it compares slightly defavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv \cite{ferrari2022complete}, and we also run it for the MNIST DNNs, and it was slightly slower and less accurate than $\alpha,\beta$-CROWN at several time-out settings.
+Last, Pyrat code is not open source, which made running it impossible.
 

### 2024-09-22 ICLR25/introduction.tex
valabstraction

@@
 	\item This allows us to propose a measure of utility for each neuron, providing an upper bound on the improvement on accuracy made if we treat this neuron with an integer variable instead of the LP relaxation.
-Choosing the neurons with the top utility and encoding them with integer variables gives rise to a partial MILP which is much more efficient than previous attempts \cite{9211410}, necessitating much less integer variables for the same accuracy.
+Choosing the neurons with the top utility and encoding them with integer variables gives rise to a partial MILP which is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating much less integer variables for the same accuracy.
 

### 2024-09-22 ICLR25/relatedwork.tex
valabstraction

@@
 MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of CMP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding.
-In \cite{9211410}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.
+In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.
 

### 2024-09-22 ICLR25/valabstraction.tex
Add paper in new format
valabstraction

--- 2024-04-27 lipics-master/valabstraction.tex
@@
 
-\subsection{The Box and DeepPoly Abstractions}
+\subsection{The Box Abstractions}
 
-\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
+%\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
 
-\begin{figure}[b!]
+The concept of value abstraction involves calculating upper and lower bounds for the values of certain neurons in a Deep Neural Network (DNN) when inputs fall within a specified range.
+This approach aims to assess the network's robustness without precisely computing the values for every input within that range.
+
+Firstly, it's important to note that weighted sums represent a linear function, which can be explicitly expressed with relative ease.
+However, the ReLU (Rectified Linear Unit) function presents a challenge in terms of accurate representation.
+Although ReLU is a relatively straightforward piecewise linear function with two modes (one for $x<0$ and another for $x \geq 0$), it is not linear.
+The complexity arises when considering the compounded effects of the ReLU function across the various layers of a ReLU DNN.
+It's worth noting that representing $\ReLU(x)$ precisely is feasible when $x$ is "{\em stable}", meaning it's consistently positive or consistently negative, as there's only one linear mode involved in each scenario.
+Consequently, the primary challenge lies in addressing "{\em unstable}" neurons, where the linearity of the function does not hold consistently.
+
+\begin{figure}[t!]
 	\centering
@@
 
-		\node[circle, draw= purple, thick, minimum width = 20,
+		\node[circle, draw= black, thick, minimum width = 20,
 		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};
@@
 
-		\node[circle, draw= blue, thick, minimum width = 20,
+		\node[circle, draw= black, thick, minimum width = 20,
 		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
@@
 
-		% Connections
-
 		\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
@@
 
-		\draw[->,color=applegreen, thick] (input2) -- (hidden1) node[near start, below] {$1$};
-		\draw[->,color=red, thick] (input2) -- (hidden2)node[near start, below] {$-1$};
+		\draw[->, thick] (input2) -- (hidden1) node[near start, below] {$1$};
+		\draw[->, thick] (input2) -- (hidden2)node[near start, below] {$-1$};
 
-		\draw[->,color=applegreen, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
-		\draw[->,color=red, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(n_2,0)$};
+		\draw[->, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
+		\draw[->, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(n_2,0)$};
 
-		\draw[->,color=applegreen, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
+		\draw[->,thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
 		\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
 
-		\draw[->,color=red, thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
+		\draw[->,thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
 		\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
@@
 
+		% Connections
+
 	\end{tikzpicture}
-	\caption{A DNN example from \cite{kpoly}: every neuron is separated into 2 nodes, 
-	$n$ pre- and $\hat{n}$ post-ReLU activation function. The pair of paths 
-	$({\color{applegreen}n_2 n_3 n_5},{\color{red}n_2 n_4 n_5})$ is {\em compensating} 
-	(weights ${\color{applegreen}1},{\color{red}-2}$).}
+	\caption{A DNN. Every neuron is separated into 2 nodes, 
+	$n$ pre- and $\hat{n}$ post-ReLU activation.} 
+	%The pair of paths 	$({\color{applegreen}n_2 n_3 n_5},{\color{red}n_2 n_4 n_5})$ is {\em compensating} 	(weights ${\color{applegreen}1},{\color{red}-2}$).}
 	\label{fig1}
 \end{figure}
-
-The concept of value abstraction involves calculating upper and lower bounds for the values of certain neurons in a Deep Neural Network (DNN) when inputs fall within a specified range.
-This approach aims to assess the network's robustness without precisely computing the values for every input within that range.
-
-Firstly, it's important to note that weighted sums represent a linear function, which can be explicitly expressed with relative ease.
-However, the ReLU (Rectified Linear Unit) function presents a challenge in terms of accurate representation.
-Although ReLU is a relatively straightforward piecewise linear function with two modes (one for $x<0$ and another for $x \geq 0$), it is not linear.
-The complexity arises when considering the compounded effects of the ReLU function across the various layers of a ReLU DNN.
-It's worth noting that representing $\ReLU(x)$ precisely is feasible when $x$ is "stable," meaning it's consistently positive or consistently negative, as there's only one linear mode involved in each scenario.
-Consequently, the primary challenge lies in addressing "unstable" neurons, where the linearity of the function does not hold consistently.
 
@@
 For all $i \geq 3$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
-
 Taking the DNN example from Fig \ref{fig1}, assume $x_1,x_2 \in [-1,1]$.
@@
 
+\iffalse
 An extremely efficient algorithm that alleviates some of the inaccuracies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}.
@@
 This leads to $x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
-
 For bounds $[\alpha,\beta]$ on $x_i$, the optimal linear function for the upper bound is $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes.
@@
 DeepPoly selects between these based on the values of $\alpha$ and $\beta$ (for unstable neurons): if $|\alpha|\geq |\beta|$, then $f_i=f^1_i$ is chosen, otherwise, for $|\beta|>|\alpha|$, $f_i=f^2_i$ is selected.
-The variation, {\em $\overline{\mbox{DeepPoly}}$}, consistently chooses $f^1_i$, and never $f^2_i$.
-Contrary to DeepPoly, {\em $\overline{\mbox{DeepPoly}}$} encompasses the ``Box abstraction." For instance, with bounds $[-0.2,5]$ on $x_i$,
-standard DeepPoly would conclude $\ReLU(x_i) \in [-0.2,5]$, while 
-{\em $\overline{\mbox{DeepPoly}}$} would deduce $\ReLU(x_i) \in [0,5]$ similarly as the Box abstraction.
-
-\iffalse
-\subsection{PRIMA and $\beta$-CROWN}
 \fi
 
-\subsection{MILP and LP encodings for DNNs}
+\subsection{MILP, LP and partial MILP encodings for DNNs}
 
@@
 This approach is termed the {\em LP abstraction}.
+
+In this paper, we propose to use {\em partial MILP}, to get interesting trade-offs between accuracy and runtime: 
+for a set of unstable neurons $X$, we denote by MILP$_X$ the MILP encoding where variables encoding $X$ are binary, and other variables are linear variables using the LP relaxation.
+We say that nodes in $X$ are {\em opened}.
+To further limit the number of binary variables needed for a given accuracy, we devise the same iterative approach as the box abstraction or DeepPoly \cite{deeppoly}, computing lower 
+and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a layer, that are used when computing values of the next layer, thus necessitating less variables from previous layers.
+
+The crucial factor in such an approach is to {\em select} few opened neurons in $X$ which are the most important for the accuracy.
+An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (UB(a)-LB(a))$.
+To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP abstraction.
 

### 2024-09-23 ICLR25/valabstraction.tex
prop LP

@@
 
-The following proposition shows that the LP abstraction refines the DeepPoly abstraction. 
-The difference between the LP and the DeepPoly abstractions is that LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.
+Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$. 
+Let $x$ represent the input value of $n$, hence with 
+$\LB(n) < x < \UB(n)$, and $\hat{x}$ representing $ReLU(x)$. 
+Then we have:
 
@@
 	\label{LP}
-	Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints (1) for LP and (2) for DeepPoly with both lower bounds, are equivalent:
+	The LP relaxation on $\hat{x}$ is equivalent with the following system of constraints:
 	\begin{align}
-& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, \quad a \in [0,1]  \label{eq:lp}\\
-&\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha} \label{eq:deeppoly}
+		\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} \label{eq:deeppoly}
+		%& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, \quad a \in [0,1]  \label{eq:lp}\\
 	\end{align} 
@@
 \begin{proof}
-We need to show that the two upper bound constraints on $\hat{x}$ in (1) are equivalent to the upper bound in (2).
+We need to show that the three constraints 
+$\hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, \quad a \in [0,1]$ translates to $\hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)}$. 
 To this end, we focus on the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
-We have $\hat{x}$ in Eq~\ref{eq:lp} is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
+We have $\hat{x}$ is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
 Furthermore,
@@
 \end{proof}
+
+Notice that this is close to the DeepPoly abstractions \cite{deeppoly}, but LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.

### 2024-09-23 ICLR25/introduction.tex
NUMBERS
upto date

@@
 		\hline
-		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
-		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
-		$\epsilon = 0.026$ & &  &6200s &  5220s & 6100s
+		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum &  Full MILP  \\ \hline
+		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $49\%$ & 40 \%    \\
+		$\epsilon = 0.026$ & &  &6200s &  4995s & 6100s
 		  \\  \hline
-		  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $40\%$ & 37 \%    \\
-		  TO=2000s & &  & 1250s  & 1343s & 1466s \\  \hline	
+		%  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $46\%$ & 37 \%    \\
+		%  TO=2000s & &  & 1250s  & 1194s & 1466s \\  \hline	
 	\end{tabular}
@@
 %Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-No complete verifier could outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime.}
+Complete verifier barely outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime, 
+still very far from the upper bound.}
 \label{table_complete}

### 2024-09-23 ICLR25/valabstraction.tex
upto date

@@
 	\label{LP}
-	The LP relaxation on $\hat{x}$ is equivalent with the following system of constraints:
+	The LP relaxation on $\hat{x}$ is equivalent with:
 	\begin{align}
-		\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} \label{eq:deeppoly}
+		\ReLU(x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} \label{eq:deeppoly}
 		%& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, \quad a \in [0,1]  \label{eq:lp}\\
@@
 \begin{proof}
-We need to show that the three constraints 
-$\hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, \quad a \in [0,1]$ translates to $\hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)}$. 
-To this end, we focus on the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
-We have $\hat{x}$ is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
-Furthermore,
-	The function $\min(\beta \cdot a, x - \alpha (1-a))$ attains its maximum when $\beta \cdot a = x - \alpha (1-a)$, leading to the equation $(\beta - \alpha) a = x - \alpha$ and consequently $a = \frac{x - \alpha}{\beta-\alpha}$.
-This results in an upper bound of $\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$ \qed
+The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediatly equivalent with $\hat{x} \geq \ReLU(x)$.
+
+We now show that the three constraints 
+$\hat{x} \leq \UB(n) \cdot a \, \wedge \, \hat{x} \leq x-\LB(n) \cdot (1-a) \, \wedge \, a \in [0,1]$ translates into $\hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)}$. 
+We have $\hat{x}$ is upper bounded by $max_{a \in [0,1]} (min(\UB(n) \cdot a, x - \LB(n) (1-a)))$, and this bound can be reached.
+Furthermore, using standard function analysis tools (derivative...), we can show that the function $a \mapsto \min(\UB(n) \cdot a, x - \LB(n) (1-a))$ attains its maximum when $\UB(n) \cdot a = x - \LB(n) (1-a)$, leading to the equation $(\UB(n) - \UB(n)) a = x - \LB(n)$ and consequently $a = \frac{x - \LB(n)}{\UB(n)-\LB(n)}$.
+This results in an upper bound $\hat{x} \leq \UB(n) \frac{x - \LB(n)}{\UB(n)-\LB(n)}$, which can be reached, hence the equivalence.
 \end{proof}
 
-Notice that this is close to the DeepPoly abstractions \cite{deeppoly}, but LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.
+Notice that this is close to the DeepPoly abstractions \cite{deeppoly}, but LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $\ReLU(x) \geq 0$ and $\ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.

### 2024-09-23 ICLR25/experiments.tex
update

@@
 We compared with a random choice in the first two layers, and also choice based on strength in \cite{DivideAndSlide}, defined as
-$strength(n) = (UB(n)-LB(n))\cdot |W_{cd}|$, which is thus limited to the previous (2sd hidden layer).
+$strength(n) = (\UB(n)-\LB(n))\cdot |W_{cd}|$, which is thus limited to the previous (2sd hidden layer).
 

### 2024-09-23 ICLR25/valabstraction.tex
update

@@
 The crucial factor in such an approach is to {\em select} few opened neurons in $X$ which are the most important for the accuracy.
-An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (UB(a)-LB(a))$.
+An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.
 To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP abstraction.

### 2024-09-23 ICLR25/formula.tex
formula
for
form
update

@@
 An accurate utility function is to evaluate 
-Improve\_max$^z(a)=$ Sol\_max$_\emptyset^z(z) -$ Sol\_max$_{\{a\}}^z(z)$, 
+$\Improve\_max^z(a)=$ Sol\_max$_\emptyset^z(z) -$ Sol\_max$_{\{a\}}^z(z)$, 
 representing how much opening neuron $a < z$ reduces the maximum computed for $z$
 compared with using only LP. 
-We have Improve\_max$^z(a)\geq 0$ as Sol\_max$_{\{a\}}^z$ fullfils all the constraints of 
+We have $\Improve\_max^z(a)\geq 0$ as Sol\_max$_{\{a\}}^z$ fullfils all the constraints of 
 $\mathcal{M}_\emptyset$, so Sol\_max$_{\{a\}}^z(z) \leq$ Sol\_max$_\emptyset^z(z)$.
-
 Similarly, we define (Sol\_min$_\emptyset^z(n))_{n \leq z}$ and 
-Improve\_min$_a^z$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
+$\Improve\_min_a^z$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
 would however be very time consuming when the number of neurons $a$ to evaluate is large.
-Instead, we focus on the following upper bounding of Improve\_max$_a^z$.
+Instead, we focus on the following upper bounding of $\Improve\_max_a^z$.
 
@@
 in the solution of the LP instance Sol\_max$_\emptyset^z$ to maximize $z$.
-
 %For one layer before the target layer, the formula is simple and most accurate. 
-To estimate Improve\_max$_a^z$, we define Utility\_max$^z(a)$, first for neurons $a$ one layer before $z$:
+To estimate $\Improve\_max_a^z$, we define $\Utility$\_max$^z(a)$, first for neurons $a$ one layer before $z$:
 %we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
@@
 	\begin{align}
-		Utility\_max^z(a) = |W_{az} \times (sol(\hat{a})- \ReLU(sol(a)))|.
+		\Utility\_max^z(a) = |W_{az} \times (sol(\hat{a})- \ReLU(sol(a)))|.
 	\end{align}
@@
 \begin{proposition}
-$0 \leq Improve\_max^z(a) \leq Utility\_\max^z(a)$. 
+$0 \leq \Improve\_max^z(a) \leq \Utility\_\max^z(a)$. 
 \end{proposition}
@@
 $sol(z)-sol'(z) \geq sol(z) -$ Sol\_max$_{\{a\}}^z(z)$, i.e. 
-$Improve\_max^z(a) \leq Utility\_\max^z(a)$.
+$\Improve\_max^z(a) \leq Utility\_\max^z(a)$.
 \end{proof}
@@
 Thus, Utility\_max$^z(a)$ can be used to approximate 
-Improve\_max$^z(a)$. In particular, consider a very frequent case where $W_{az}<0$.
-In this case, to maximize $z$, the LP engine sets $sol(\hat{a})$ to its minimal value\dots which happens to be $sol(\hat{a})=ReLU(a)$, thanks to Proposition \ref{LP}. 
-In this frequent case, we have Utility\_max$^z(a)=0$, and thus Improve\_max$^z(a)=0$. 
+$\Improve\_max^z(a)$. In particular, consider a very frequent case where $W_{az}<0$.
+In this case, to maximize $z$, the LP engine sets $sol(\hat{a})$ to its minimal value\dots which happens to be $sol(\hat{a})=\ReLU(a)$, thanks to Proposition \ref{LP}. 
+In this frequent case, we have Utility\_max$^z(a)=0$, and thus $\Improve\_max^z(a)=0$. 
 In particular, this node will have the smallest utility (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  Sol\_max$_{\{a\}}^z(z)$. 
@@
 
-%To estimate Improve\_max$_a^z$ , 
-Indeed, if $W_{bz}\leq0$, then the LP solver sets $sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $ReLU(b)$ according to Proposition \ref{LP}.
-If $sol(b) < 0$, then we have a clip at $sol(\hat{b})=ReLU(b)=0$ and opening $a$ does not help. If $sol(b) > 0$, then we have $sol(\hat{b})=ReLU(b)=b$ and every change from 
-$a$ is reflected with a coefficient $W_{ab}$ on $b$. 
+%To estimate $\Improve\_max_a^z$ , 
+Indeed, if $W_{bz}\leq0$, then the LP solver sets $sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
+If $sol(b) < 0$, then we have a clip at $sol(\hat{b})=\ReLU(b)=0$ and opening $a$ does not help. If $sol(b) > 0$, then we have $sol(\hat{b})=\ReLU(b)=sol(b)$ and every change from 
+$a$ is reflected with a coefficient $W_{ab}$ on $\hat{b}$. 
 Last, if $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
@@
 
-We define a distance $D$ to account for the fact that a neuron $b$ 
+We define a difference $\Delta$ to account for the fact that a neuron $b$ 
 can not exceed $\LB(b),\UB(b)$:
 	\begin{align*}
-		&D(\hat{a}) = sol(\hat{a}) - \ReLU(sol(a)) \geq 0\\
-			&D(\hat{b}) =
+		&\Delta(\hat{a}) = sol(\hat{a}) - \ReLU(sol(a)) \geq 0\\
+			&\Delta(\hat{b}) =
 		\begin{cases}
-			sol(\hat{b}) - \min(\UB(b), sol(\hat{b}) - D(\hat{a}) k(\hat{b})), & \text{if }  W_{bz} > 0 \\
-			sol(\hat{b}) - \max(\LB(b), 0, sol(\hat{b}) -D(\hat{a}) k(\hat{b})), & \text{if }W_{bz} < 0\\
+			sol(\hat{b}) - \min(\UB(b), sol(\hat{b}) - \Delta(\hat{a}) k(\hat{b})), & \text{if }  W_{bz} > 0 \\
+			sol(\hat{b}) - \max(\LB(b), 0, sol(\hat{b}) -\Delta(\hat{a}) k(\hat{b})), & \text{if }W_{bz} < 0\\
 		\end{cases}
@@
 
-$$ Utility\_max^z(a) = \sum_b W_{bz} D(\hat{b})$$
+$$ \Utility\_max^z(a) = \sum_b W_{bz} \Delta(\hat{b})$$
 
-We proceed inductively in the same way to define Utility$\_max^z(a)$ for deeper neuron $a$.
+We proceed inductively in the same way to define $\Utility\_max^z(a)$ for deeper neuron $a$.
 
@@
 
-	First, $D(a) = \ReLU(sol(a))-sol(\hat{a})$.
+	First, $\Delta(a) = \ReLU(sol(a))-sol(\hat{a})$.
 
-To compute $D(b)$ for neurons $b$ in two layer before $z$, we define \begin{align}
-	&u_0 = \max(\LB(b),\min(\UB(b),  sol(b)+D(a)W_{ab}))\\
+To compute $\Delta(b)$ for neurons $b$ in two layer before $z$, we define \begin{align}
+	&u_0 = \max(\LB(b),\min(\UB(b),  sol(b)+\Delta(a)W_{ab}))\\
 	&u_1 = \begin{cases}
@@
 	\end{cases}\\
-	&D(b) = u_1-sol(\hat{b})
+	&\Delta(b) = u_1-sol(\hat{b})
 \end{align}
 
-	To compute $D(c)$ for neurons $c$ in one layer before $z$, we define 
+	To compute $\Delta(c)$ for neurons $c$ in one layer before $z$, we define 
 	\begin{align}
-		&w_0 = \sum_b D(b)W_{bc}\\
+		&w_0 = \sum_b \Delta(b)W_{bc}\\
 		&w_1 = \min(\UB(c),sol(c)+w_0)\\		
-		&D(c) =
+		&\Delta(c) =
 		\begin{cases}
@@
 		\end{cases}\\
-		&D(z) = \sum_c D(c)W_{cz}\\
-		&Utility\_max^z(a) = -D(z)
+		&\Delta(z) = \sum_c \Delta(c)W_{cz}\\
+		&\Utility\_max^z(a) = -\Delta(z)
 	\end{align}

### 2024-09-23 ICLR25/valabstraction.tex
update

@@
 
-\iffalse
-An extremely efficient algorithm that alleviates some of the inaccuracies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}.
+%\iffalse
+%An extremely efficient algorithm that alleviates some of the inaccuracies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}.
 Instead of fixed bounds for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$.
@@
 This leads to $x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
-For bounds $[\alpha,\beta]$ on $x_i$, the optimal linear function for the upper bound is $g_i(x_i)= \beta \frac{x_i-\alpha}{\beta-\alpha}$ for ReLU nodes.
+For bounds $[\UB,\LB]$ on $x_i$, the optimal linear function for the upper bound is $g_i(x_i)=\LB \frac{x_i-\alpha}{\LB-\UB}$ for ReLU nodes.
 There are two options for the lower bound: $f^1_i(x_i) = 0$ or $f^2_i(x_i)=x_i$.
 DeepPoly selects between these based on the values of $\alpha$ and $\beta$ (for unstable neurons): if $|\alpha|\geq |\beta|$, then $f_i=f^1_i$ is chosen, otherwise, for $|\beta|>|\alpha|$, $f_i=f^2_i$ is selected.
-\fi
+%\fi
 
@@
 At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a complete (but inefficient) method. 
-Consider an unstable neuron $n \in[\alpha,\beta]$.
-The value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $(\alpha,\beta)$ with 4 constraints \cite{MILP}:
-$\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)$.
+Consider an unstable neuron $n \in[\UB,\LB]$.
+The value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $(\UB,\LB)$ with 4 constraints \cite{MILP}:
+$\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB \cdot a \quad \wedge \quad \hat{x} \leq x-\UB \cdot (1-a)$.
 
-For all $x \in [\alpha,\beta] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
+For all $x \in [\UB,\LB] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
 Here, $a$ is 0 if $x < 0$, 1 if $x>0$, and can be either if $x=0$~\cite{MILP}.

### 2024-09-23 ICLR25/introduction.tex
update

@@
 However, their robustness is often compromised by their susceptibility to input perturbations \cite{szegedy}.
-This vulnerability has catalyzed the verification community to develop various methodologies, each presenting a unique balance between completeness and computational efficiency \cite{katz2019marabou,Reluplex,deeppoly}.
+This vulnerability has catalyzed the verification community to develop various methodologies, each presenting a unique balance between completeness and computational efficiency \cite{Marabou,Reluplex,deeppoly}.
 This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools.

### 2024-09-23 ICLR25/relatedwork.tex
update

@@
 
-Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, $\alpha,\beta$-CROWN)\cite{prima,crown}, Hybrid MILP.
+Finally, methods such as Reluplex / Marabou \cite{Reluplex,Marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, $\alpha,\beta$-CROWN)\cite{prima,crown}, Hybrid MILP.
 These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances as shown in Table \ref{table_complete}.

### 2024-09-23 ICLR25/Paper_noProof.tex
valabstraction
update

@@
 \newcommand{\LP}{{\textrm{LP}}}
+\newcommand{\Improve}{\mathrm{Improve}}
+\newcommand{\Utility}{\mathrm{Utility}}
 
@@
 Our empirical studies revealed that Hybrid MILP, can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp) within the same runtime.
-This opens a lot of perspective, among which: verifying efficiently hard instances; certifying robustness of images for larger $\epsilon$ neighbourhoods, verifying global rather than local properties \cite{lipshitz}.
+This opens a lot of perspective, among which: verifying efficiently hard instances; certifying robustness of images for larger $\epsilon$ neighbourhoods; verifying global rather than local properties \cite{lipshitz}.
+
 \newpage

### 2024-09-23 ICLR25/experiments.tex
update

@@
 
-On hard instances (the 6 first DNNs tested), Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, 10 times less even on smaller DNNs.
-It can scale up to quite large hard CNN instances, such as CNN-B-Adv with 2M parameters and 20K activations.
+On hard instances (the 6 first DNNs tested), Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, and even 10 times less on smaller DNNs.
+It can scale up to quite large hard DNNs, such as CNN-B-Adv with 2M parameters and 20K activations.
 
@@
 
-Last, compared with refined $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5x100, 5x200), refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than our Hybrid MILP, but with longer runtime (up to 2x on 5x100).
+Last, compared with refined $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5x100, 5x200), refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than  Hybrid MILP, but with longer runtime (up to 2x on 5x100).
 On intermediate DNNs (8x100,8x200), full MILP invoked by refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images, while having longer runtime.

### 2024-09-23 ICLR25/introduction.tex
update

@@
 	\end{tabular}
-\caption{Complete verifiers run on the smallest of the hard DNN with TO = 10 000s. 
+\caption{Result of complete verifiers on the hard 5x100 with TO = 10 000s. 
 %Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-Complete verifier barely outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime, 
-still very far from the upper bound.}
+Complete verifier barely (9\% out of 50\%) 
+outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite much larger runtime.}
 \label{table_complete}
@@
 While they should theoretically be able to close the gap of undecided images,
-in practice, Table \ref{table_complete} reveals that even with a very large 10 000s time out per image, none succeds to verify any more image than $\alpha,\beta$-Crown, while the runtime is $>5$ times longer.
-It seemed pointless to test complete verifier on larger networks.
+in practice, Table \ref{table_complete} reveals that only NNenum succeds to verify 9\% more images out of the 50\% undecided images by $\alpha,\beta$-Crown, and with a very large runtime of almost 5000s per image.
+It seemed pointless to test complete verifiers on larger networks.
 

### 2024-09-23 ICLR25/experiments.tex
exp

@@
 
-Notice that several other verifiers were already reported \cite{crown} on these same DNNs, with defavorable comparison towards $\alpha,\beta$-CROWN (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc).
+Notice that results for several other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with defavorable comparison vs $\alpha,\beta$-CROWN.
 Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd
@@
 Concerning MnBAB \cite{ferrari2022complete}, it compares slightly defavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv \cite{ferrari2022complete}, and we also run it for the MNIST DNNs, and it was slightly slower and less accurate than $\alpha,\beta$-CROWN at several time-out settings.
-Last, Pyrat code is not open source, which made running it impossible.
+Last, Pyrat code (2sd in the latest VNNComp) is not open source, which made running it impossible.
 

### 2024-09-24 ICLR25/relatedwork.tex

@@
 
-We compare {\CMP} with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art.
-CMP scales while preserving good accuracy, through targeting a limited number of binary variables based on compensating strength, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate).
-MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of CMP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding.
+We compare Hybrid MILP with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art.
+It scales while preserving good accuracy, through targeting a limited number of binary variables, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate).
+MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of Hybrid MILP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding.
 In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.

### 2024-09-24 ICLR25/experiments.tex
update

@@
 	\centering
-	\begin{tabular}{|c||c|c|c|}
+	\begin{tabular}{|c||c|c|c|c|c|}
 		\hline
-		\text{Number $K$}  &  \bf Utility&  \text{Strength} \cite{ DivideAndSlide} & \text{Random} \\ \hline
+		\text{Number $K$}  &  \bf Utility& Utility& \text{Strength} \cite{ DivideAndSlide} & \text{Random} &\text{Random}\\ \hline
 		\hline
-		0  &   1.761  & 1.761 & 1.761  \\ \hline
-		5  & \bf 1.532  & &   \\ \hline
-		10  & \bf 1.371  & 1.651 & 1.696  \\ \hline
-		15  & \bf 1.247  &   &   \\ \hline
-		20  & \bf 1.145  & 1.557 & 1.619  \\ \hline
-		25  & \bf 1.061  &  &   \\ \hline
-		30  & \bf 0.989  & 1.489 & 1.546  \\ \hline
-		35  & \bf 0.934  &  &   \\ \hline
-		40  & \bf 0.921 & 1.447 & 1.469  \\ \hline
-		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
+		0  &   1.761  && 1.761 & 1.761  &\\ \hline
+		5  & \bf 1.532  && 1.704 &  1.729& \\ \hline
+		10  & \bf 1.371  && 1.651 & 1.696 & \\ \hline
+		15  & \bf 1.247  &&  1.599 &  1.653& \\ \hline
+		20  & \bf 1.145  && 1.557 & 1.619 & \\ \hline
+		25  & \bf 1.061  && 1.519 &  1.586 &\\ \hline
+		30  & \bf 0.989  && 1.489 & 1.546 & \\ \hline
+		35  & \bf 0.934  && 1.465 & 1.502 &\\ \hline
+		40  & \bf 0.921 && 1.447 & 1.469 & \\ \hline
+		116 (max) &  0.895 &1.424& 1.424 (max=$61$) & 0.895 &1.424  \\ \hline
 	\end{tabular}
@@
 Namely, these are 6 {\em hard} ReLU-DNNs: 5 MNIST DNN from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided) as well as 1 CIFAR CNN from 
-\cite{AdversarialTrainingAndProvableDefenses}, also see \cite{SDPFI}, with the same $\epsilon$ setting.
+\cite{AdversarialTrainingAndProvableDefenses} (the network file we use is from \url{https://github.com/Verified-Intelligence/alpha-beta-CROWN}), also see \cite{SDPFI}, with the same $\epsilon$ setting.
 For reference, we also report an easy but very large ResNet Network for CIFAR10, already tested with $\alpha,\beta$ CROWN.

### 2024-09-24 ICLR25/formula.tex
update

@@
 We denote by $n< z$ the fact that a neuron appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
-Let us denote (Sol\_max$_X^z(n))_{n \leq z}$ is a solution of $\mathcal{M}_X$ 
-maximizing $z$. In particular, Sol\_max$_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
+Let us denote ($\Sol\_\max_X^z(n))_{n \leq z}$ is a solution of $\mathcal{M}_X$ 
+maximizing $z$. In particular, $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
 
-Consider (Sol\_max$_\emptyset^z(n))_{n \leq z}$ (this is obtained by {\em one} call to an LP solver, so can be obtained very efficiently).
+Consider ($\Sol\_\max_\emptyset^z(n))_{n \leq z}$ (this is obtained by {\em one} call to an LP solver, so can be obtained very efficiently).
 An accurate utility function is to evaluate 
-$\Improve\_max^z(a)=$ Sol\_max$_\emptyset^z(z) -$ Sol\_max$_{\{a\}}^z(z)$, 
+$\Improve\_\max^z(a)=$ $\Sol\_\max_\emptyset^z(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, 
 representing how much opening neuron $a < z$ reduces the maximum computed for $z$
 compared with using only LP. 
-We have $\Improve\_max^z(a)\geq 0$ as Sol\_max$_{\{a\}}^z$ fullfils all the constraints of 
-$\mathcal{M}_\emptyset$, so Sol\_max$_{\{a\}}^z(z) \leq$ Sol\_max$_\emptyset^z(z)$.
-Similarly, we define (Sol\_min$_\emptyset^z(n))_{n \leq z}$ and 
-$\Improve\_min_a^z$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
+We have $\Improve\_\max^z(a)\geq 0$ as $\Sol\_\max_{\{a\}}^z$ fullfils all the constraints of 
+$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{a\}}^z(z) \leq$ $\Sol\_\max_\emptyset^z(z)$.
+Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
+$\Improve\_\min^z(a)$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
 would however be very time consuming when the number of neurons $a$ to evaluate is large.
-Instead, we focus on the following upper bounding of $\Improve\_max_a^z$.
+Instead, we focus on the following upper bounding of $\Improve\_\max^z(a)$.
 
@@
 
-For all neurons $n$, let $sol(n)=$Sol\_max$_\emptyset^z(n)$ be the value of neuron $a$
-in the solution of the LP instance Sol\_max$_\emptyset^z$ to maximize $z$.
+For all neurons $n$, let $\sol(n)=$$\Sol\_\max_\emptyset^z(n)$ be the value of neuron $a$
+in the solution of the LP instance $\Sol\_\max_\emptyset^z$ to maximize $z$.
 %For one layer before the target layer, the formula is simple and most accurate. 
-To estimate $\Improve\_max_a^z$, we define $\Utility$\_max$^z(a)$, first for neurons $a$ one layer before $z$:
+To estimate $\Improve\_\max^z(a)$, we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$:
 %we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
@@
 	\begin{align}
-		\Utility\_max^z(a) = |W_{az} \times (sol(\hat{a})- \ReLU(sol(a)))|.
+		\Utility\_\max\nolimits^z(a) = |W_{az} \times (\sol(\hat{a})- \ReLU(\sol(a)))|.
 	\end{align}
 
-	%In particular, if $sol(\hat{a})=\ReLU(sol(a))$, then we will have 
+	%In particular, if $\sol(\hat{a})=\ReLU(\sol(a))$, then we will have 
 	%\begin{align*}
@@
 \begin{proposition}
-$0 \leq \Improve\_max^z(a) \leq \Utility\_\max^z(a)$. 
+$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
 \end{proposition}
@@
 \begin{proof}
-Consider $(sol'(n))_{n \leq z})_{n \leq z})$ with
-$sol'(n)=sol(n)$ for all $n \notin \{z,\hat{a}\}$.
-In particular,  $sol'(a) = sol(a)$.
+Consider $(\sol'(n))_{n \leq z})_{n \leq z})$ with
+$\sol'(n)=\sol(n)$ for all $n \notin \{z,\hat{a}\}$.
+In particular,  $\sol'(a) = \sol(a)$.
 
-Now, define $sol'(\hat{a}) = \ReLU(sol(a))$. 
+Now, define $\sol'(\hat{a}) = \ReLU(\sol(a))$. 
 That is,  
-sol'$(\hat{a})$ is the correct value for $\hat{a}$ (obtained if we open neuron $a$), 
-compared to the LP abstraction for $sol(\hat{a})$.
+$\sol'(\hat{a})$ is the correct value for $\hat{a}$ (obtained if we open neuron $a$), 
+compared to the LP abstraction for $\sol(\hat{a})$.
 
-Last, we define $sol'(z)=sol(z) + W_{az} \times (\ReLU(sol(a)) - sol(\hat{a})) = sol(z) - Utility\_max_z(a)$.
+Last, we define $\sol'(z)=\sol(z) + W_{az} \times (\ReLU(\sol(a)) - \sol(\hat{a})) = \sol(z) - \Utility\_\max^z(a)$.
 
-Now, it is easy to check that $(sol'(n))_{n \leq z}$ satisfies the constraints in 
-$\mathcal{M}_{\{a\}}$, as openning $a$ changes the value of $\hat{a}$ from
-$sol(\hat{a})$ to $\ReLU(sol(a))$, and the contribution from $a$ to $z$ is 
-$W_{az}$. As $sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $sol'(z) \leq$ Sol\_max$_{\{a\}}^z(z)$. That is, 
-$sol(z)-sol'(z) \geq sol(z) -$ Sol\_max$_{\{a\}}^z(z)$, i.e. 
-$\Improve\_max^z(a) \leq Utility\_\max^z(a)$.
+Now, it is easy to check that $(\sol'(n))_{n \leq z}$ satisfies the constraints in 
+$\mathcal{M}_{\{a\}}$, as opening $a$ changes the value of $\hat{a}$ from
+$\sol(\hat{a})$ to $\ReLU(\sol(a))$, and the contribution from $a$ to $z$ is 
+$W_{az}$. As $\sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $\sol'(z) \leq$ $\Sol\_\max_{\{a\}}^z(z)$. That is, 
+$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
+$\Improve\_\max^z(a) \leq \Utility\_\max^z(a)$.
 \end{proof}
 
-Thus, Utility\_max$^z(a)$ can be used to approximate 
-$\Improve\_max^z(a)$. In particular, consider a very frequent case where $W_{az}<0$.
-In this case, to maximize $z$, the LP engine sets $sol(\hat{a})$ to its minimal value\dots which happens to be $sol(\hat{a})=\ReLU(a)$, thanks to Proposition \ref{LP}. 
-In this frequent case, we have Utility\_max$^z(a)=0$, and thus $\Improve\_max^z(a)=0$. 
-In particular, this node will have the smallest utility (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  Sol\_max$_{\{a\}}^z(z)$. 
+Thus, $\Utility\_\max^z(a)$ can be used to approximate 
+$\Improve\_\max^z(a)$. In particular, consider a very frequent case where $W_{az}<0$.
+In this case, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value\dots which happens to be $\sol(\hat{a})=\ReLU(a)$, thanks to Proposition \ref{LP}. 
+In this frequent case, we have $\Utility\_\max^z(a)=0$, and thus $\Improve\_\max^z(a)=0$. 
+In particular, this node will have the smallest utility (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$. 
 This is one stricking difference (but not the only one) with choosing utility based on 
@@
 %	
-%	Similarly, let $sol(b)$ be the value of $b$ in the LP solution of lower bound of $a$, and $sol(\hat{b})$ be the value of $\hat{b}$.
+%	Similarly, let $\sol(b)$ be the value of $b$ in the LP solution of lower bound of $a$, and $\sol(\hat{b})$ be the value of $\hat{b}$.
 Then the formula to estimate improvement of lower bound of $b$ is: \begin{align*}
-%		Improve\_min^z(b) \approx -W_{ba}(sol(\hat{b})-\ReLU(sol(b))).
+%		Improve\_min^z(b) \approx -W_{ba}(\sol(\hat{b})-\ReLU(\sol(b))).
 %	\end{align*}
@@
 To compute the upper bound of $a$, $\hat{b}$ should be as large as possible.
-In the LP model, for fixed $sol(b)$, the upper bound of $\hat{b}$ may be larger than $\ReLU(sol(b))$.
-This is because in LP model, the upper bound of $sol(\hat{b})$ is decided by the linear approximation rather than $\ReLU$ function.
-So, when neuron $b$ is open, if $sol(b)$ do not change, then the upper bound of $a$ will be improved because the value of $sol(\hat{b})$ will be lower to $\ReLU(sol(b))$.
+In the LP model, for fixed $\sol(b)$, the upper bound of $\hat{b}$ may be larger than $\ReLU(\sol(b))$.
+This is because in LP model, the upper bound of $\sol(\hat{b})$ is decided by the linear approximation rather than $\ReLU$ function.
+So, when neuron $b$ is open, if $\sol(b)$ do not change, then the upper bound of $a$ will be improved because the value of $\sol(\hat{b})$ will be lower to $\ReLU(\sol(b))$.
 % 			
-%Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $sol(\hat{b})$ to $\ReLU(sol(b))$ is the major part of improvement.
+%Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $\sol(\hat{b})$ to $\ReLU(\sol(b))$ is the major part of improvement.
 
@@
 We use $b$ to denote neurons in the layer between $a$ and $z$.
-If we open $a$, then the change in the weight of $a$ will still be $sol(\hat{a})-\ReLU(sol(a))$ as above.
+If we open $a$, then the change in the weight of $a$ will still be $\sol(\hat{a})-\ReLU(\sol(a))$ as above.
 Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b$ in the intermediate layer.
@@
 \begin{itemize}
- \item If $W_{bz}\leq0$, then $k(\hat{b})=W_{ab}$ if $sol(b) > 0$, and $k(\hat{b})=0$ if $sol(b) < 0$
+ \item If $W_{bz}\leq0$, then $k(\hat{b})=W_{ab}$ if $\sol(b) > 0$, and $k(\hat{b})=0$ if $\sol(b) < 0$
  \item If $W_{bz}>0$, then $k(\hat{b})=W_{ab} \frac{\UB(b)}{\UB(b)-\LB(b)}$
@@
 
-%To estimate $\Improve\_max_a^z$ , 
-Indeed, if $W_{bz}\leq0$, then the LP solver sets $sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
-If $sol(b) < 0$, then we have a clip at $sol(\hat{b})=\ReLU(b)=0$ and opening $a$ does not help. If $sol(b) > 0$, then we have $sol(\hat{b})=\ReLU(b)=sol(b)$ and every change from 
+%To estimate $\Improve\_\max_a^z$ , 
+Indeed, if $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
+If $\sol(b) < 0$, then we have a clip at $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ does not help. If $\sol(b) > 0$, then we have $\sol(\hat{b})=\ReLU(b)=\sol(b)$ and every change from 
 $a$ is reflected with a coefficient $W_{ab}$ on $\hat{b}$. 
 Last, if $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
-sets $sol(\hat{b}) = sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)}$ to maximize $z$.
+sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)}$ to maximize $z$.
 
@@
 %\begin{align*}
-%	Utility\_max^z(a) = (sol(\hat{a})-\ReLU(sol(a)))\sum_b k(b).
+%	Utility\_max^z(a) = (\sol(\hat{a})-\ReLU(\sol(a)))\sum_b k(b).
 %\end{align*}
@@
 	\begin{align*}
-		&\Delta(\hat{a}) = sol(\hat{a}) - \ReLU(sol(a)) \geq 0\\
+		&\Delta(\hat{a}) = \sol(\hat{a}) - \ReLU(\sol(a)) \geq 0\\
 			&\Delta(\hat{b}) =
 		\begin{cases}
-			sol(\hat{b}) - \min(\UB(b), sol(\hat{b}) - \Delta(\hat{a}) k(\hat{b})), & \text{if }  W_{bz} > 0 \\
-			sol(\hat{b}) - \max(\LB(b), 0, sol(\hat{b}) -\Delta(\hat{a}) k(\hat{b})), & \text{if }W_{bz} < 0\\
+			\sol(\hat{b}) - \min(\UB(b), \sol(\hat{b}) - \Delta(\hat{a}) k(\hat{b})), & \text{if }  W_{bz} > 0 \\
+			\sol(\hat{b}) - \max(\LB(b), 0, \sol(\hat{b}) -\Delta(\hat{a}) k(\hat{b})), & \text{if }W_{bz} < 0\\
 		\end{cases}
@@
 
-$$ \Utility\_max^z(a) = \sum_b W_{bz} \Delta(\hat{b})$$
+$$ \Utility\_\max\nolimits^z(a) = \sum_b W_{bz} \Delta(\hat{b})$$
 
-We proceed inductively in the same way to define $\Utility\_max^z(a)$ for deeper neuron $a$.
+We proceed inductively in the same way to define $\Utility\_\max^z(a)$ for deeper neuron $a$.
 
@@
 	\begin{align}
-		&v_0 = sol(\hat{b}), v_1 = \ReLU(sol(b)), v_2 = \frac{\UB(b)sol(b)-\UB(b)\LB(b)}{\UB(b)-\LB(b)}\\
+		&v_0 = \sol(\hat{b}), v_1 = \ReLU(\sol(b)), v_2 = \frac{\UB(b)\sol(b)-\UB(b)\LB(b)}{\UB(b)-\LB(b)}\\
 		&h(b) =
@@
 
-	First, $\Delta(a) = \ReLU(sol(a))-sol(\hat{a})$.
+	First, $\Delta(a) = \ReLU(\sol(a))-\sol(\hat{a})$.
 
 To compute $\Delta(b)$ for neurons $b$ in two layer before $z$, we define \begin{align}
-	&u_0 = \max(\LB(b),\min(\UB(b),  sol(b)+\Delta(a)W_{ab}))\\
+	&u_0 = \max(\LB(b),\min(\UB(b),  \sol(b)+\Delta(a)W_{ab}))\\
 	&u_1 = \begin{cases}
@@
 	\end{cases}\\
-	&\Delta(b) = u_1-sol(\hat{b})
+	&\Delta(b) = u_1-\sol(\hat{b})
 \end{align}
@@
 		&w_0 = \sum_b \Delta(b)W_{bc}\\
-		&w_1 = \min(\UB(c),sol(c)+w_0)\\		
+		&w_1 = \min(\UB(c),\sol(c)+w_0)\\		
 		&\Delta(c) =
 		\begin{cases}
-			w_1-sol({c}), & \text{if }W_{cz} > 0 \text{ and } \LB(c)\geq 0\\
-		k(c)(w_1-sol({c})), & \text{if }W_{cz} > 0 \text{ and } \LB(c)< 0\\
-		\ReLU(w_1)-sol(\hat{c})	, & \text{if }  W_{cz} < 0
+			w_1-\sol({c}), & \text{if }W_{cz} > 0 \text{ and } \LB(c)\geq 0\\
+		k(c)(w_1-\sol({c})), & \text{if }W_{cz} > 0 \text{ and } \LB(c)< 0\\
+		\ReLU(w_1)-\sol(\hat{c})	, & \text{if }  W_{cz} < 0
 		\end{cases}\\
 		&\Delta(z) = \sum_c \Delta(c)W_{cz}\\
-		&\Utility\_max^z(a) = -\Delta(z)
+		&\Utility\_\max^z(a) = -\Delta(z)
 	\end{align}

### 2024-09-24 ICLR25/formula.tex
update formula.tex

@@
 Based on Proposition \ref{LP}, we can evaluate how opening $a$ impacts each value of 
-$\hat{b}$, through coefficient $k(\hat{b})$, by using the upper and lower bound
-$\UB(b),\LB(b)$:
-\begin{itemize}
- \item If $W_{bz}\leq0$, then $k(\hat{b})=W_{ab}$ if $\sol(b) > 0$, and $k(\hat{b})=0$ if $\sol(b) < 0$
- \item If $W_{bz}>0$, then $k(\hat{b})=W_{ab} \frac{\UB(b)}{\UB(b)-\LB(b)}$
-\end{itemize}
-%$\sum_b W_{bz}W_{ab}$ to replace the coefficient $W_{az}$ in last subsection.
+$\hat{b}$,  by using the upper and lower bound
+$\UB(b),\LB(b)$.
 
-%To estimate $\Improve\_\max_a^z$ , 
 Indeed, if $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
@@
 		&\Delta(\hat{a}) = \sol(\hat{a}) - \ReLU(\sol(a)) \geq 0\\
+		&\Delta(b) = \begin{cases}
+			\max(W_{ab}\Delta(\hat{a}),\LB(b)-\sol(b)),  &\text{ if }  W_{ab} < 0 \\
+			\min(W_{ab}\Delta(\hat{a}),\UB(b)-\sol(b)),  &\text{ if }  W_{ab} > 0 \\
+		\end{cases}\\
 			&\Delta(\hat{b}) =
 		\begin{cases}
-			\sol(\hat{b}) - \min(\UB(b), \sol(\hat{b}) - \Delta(\hat{a}) k(\hat{b})), & \text{if }  W_{bz} > 0 \\
-			\sol(\hat{b}) - \max(\LB(b), 0, \sol(\hat{b}) -\Delta(\hat{a}) k(\hat{b})), & \text{if }W_{bz} < 0\\
+			\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} > 0 \text{ and } \sol(b)\geq0\\
+				\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} > 0 \text{ and } \sol(b)<0\\
+		 \frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} < 0\\
 		\end{cases}
@@
 We can now set 
-
-$$ \Utility\_\max\nolimits^z(a) = \sum_b W_{bz} \Delta(\hat{b})$$
+$$ \Utility\_\max\nolimits^z(a) = \sum_b W_{bz} \Delta(\hat{b}).$$
 

### 2024-09-24 ICLR25/experiments.tex
update table
update

@@
 We then average the uncertainty among all the nodes of the layer.
-Formally, the uncertainty of a node $n$ with bounds $[\alpha,\beta]$ is $unc(a) = \beta - \alpha$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$
+Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is $unc(a) = \UB - \LB$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$
 
@@
 		\hline
-		\text{Number $K$}  &  \bf Utility& Utility& \text{Strength} \cite{ DivideAndSlide} & \text{Random} &\text{Random}\\ \hline
+		\text{Number $K$}  &  \bf Utility& Utility (1 layer)& \text{} \cite{ DivideAndSlide} & \text{Random} &\text{Random (1 layer)}\\ \hline
 		\hline
-		0  &   1.761  && 1.761 & 1.761  &\\ \hline
-		5  & \bf 1.532  && 1.704 &  1.729& \\ \hline
-		10  & \bf 1.371  && 1.651 & 1.696 & \\ \hline
-		15  & \bf 1.247  &&  1.599 &  1.653& \\ \hline
-		20  & \bf 1.145  && 1.557 & 1.619 & \\ \hline
-		25  & \bf 1.061  && 1.519 &  1.586 &\\ \hline
-		30  & \bf 0.989  && 1.489 & 1.546 & \\ \hline
-		35  & \bf 0.934  && 1.465 & 1.502 &\\ \hline
-		40  & \bf 0.921 && 1.447 & 1.469 & \\ \hline
+		0  &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline
+		5  & \bf 1.532  &1.603& 1.704 &  1.729&  1.729 \\ \hline
+		10  & \bf 1.371  & 1.517& 1.651 & 1.696 & 1.701\\ \hline
+		15  & \bf 1.247  &1.466&  1.599 &  1.653& 1.671\\ \hline
+		20  & \bf 1.145  &1.438& 1.557 & 1.619 & 1.635\\ \hline
+		25  & \bf 1.061  &1.427& 1.519 &  1.586 &1.601\\ \hline
+		30  & \bf 0.989  &1.425& 1.489 & 1.546 & 1.574\\ \hline
+		35  & \bf 0.934  &1.424& 1.465 & 1.502 &1.542\\ \hline
+		40  & \bf 0.921 &1.424& 1.447 & 1.469 & 1.512\\ \hline
 		116 (max) &  0.895 &1.424& 1.424 (max=$61$) & 0.895 &1.424  \\ \hline
@@
 
-\subsection{Comparison with $\alpha,\beta$ Crown}
+\subsection{Comparison with $\alpha,\beta$-Crown}
 

### 2024-09-24 ICLR25/experiments.tex
update table

@@
 		\hline
-		\text{Number $K$}  &  \bf Utility& Utility (1 layer)& \text{} \cite{ DivideAndSlide} & \text{Random} &\text{Random (1 layer)}\\ \hline
+			&\multicolumn{3}{c|}{Neurons in Layer 2}&\multicolumn{2}{c|}{Neurons in Layer 1 and 2}\\\cline{2-6}
+		\text{Number $K$}  & \text{Random} & \cite{ DivideAndSlide} & \bf Utility& \text{Random} &\bf Utility\\ \hline
 		\hline
 		0  &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline
-		5  & \bf 1.532  &1.603& 1.704 &  1.729&  1.729 \\ \hline
-		10  & \bf 1.371  & 1.517& 1.651 & 1.696 & 1.701\\ \hline
-		15  & \bf 1.247  &1.466&  1.599 &  1.653& 1.671\\ \hline
-		20  & \bf 1.145  &1.438& 1.557 & 1.619 & 1.635\\ \hline
-		25  & \bf 1.061  &1.427& 1.519 &  1.586 &1.601\\ \hline
-		30  & \bf 0.989  &1.425& 1.489 & 1.546 & 1.574\\ \hline
-		35  & \bf 0.934  &1.424& 1.465 & 1.502 &1.542\\ \hline
-		40  & \bf 0.921 &1.424& 1.447 & 1.469 & 1.512\\ \hline
-		116 (max) &  0.895 &1.424& 1.424 (max=$61$) & 0.895 &1.424  \\ \hline
+		5  & \bf   1.729&1.603& 1.704 &  1.729&  1.532 \\ \hline
+		10  & \bf  1.701 & 1.517& 1.651 & 1.696 & 1.371\\ \hline
+		15  & \bf  1.671 &1.466&  1.599 &  1.653& 1.247\\ \hline
+		20  & \bf  1.635 &1.438& 1.557 & 1.619 & 1.145\\ \hline
+		25  & \bf  1.601 &1.427& 1.519 &  1.586 &1.061\\ \hline
+		30  & \bf 1.574 &1.425& 1.489 & 1.546 & 0.989 \\ \hline
+		35  & \bf  1.542 &1.424& 1.465 & 1.502 &0.934 \\ \hline
+		40  & \bf 1.512 &1.424& 1.447 & 1.469 &0.921 \\ \hline
+		116 (max) & 1.424  &1.424& 1.424 (max=$61$) & 0.895 &0.895   \\ \hline
 	\end{tabular}

### 2024-09-24 ICLR25/formula.tex
section 3 and 4

@@
 Let $z$ be a neuron of the DNN we want to evaluate, for instance computing an upper bound on the value it can take.
-We denote by $n< z$ the fact that a neuron appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
-Let us denote ($\Sol\_\max_X^z(n))_{n \leq z}$ is a solution of $\mathcal{M}_X$ 
+We denote by $n < z$ the fact that a neuron $n$appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
+Let us denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ 
 maximizing $z$. In particular, $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
 
-Consider ($\Sol\_\max_\emptyset^z(n))_{n \leq z}$ (this is obtained by {\em one} call to an LP solver, so can be obtained very efficiently).
-An accurate utility function is to evaluate 
+Consider ($\Sol\_\max_\emptyset^z(n))_{n \leq z}$ (this can be obtained very efficiently by {\em one} call to an LP solver). An accurate utility function is to evaluate 
 $\Improve\_\max^z(a)=$ $\Sol\_\max_\emptyset^z(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, 
@@
 %For one layer before the target layer, the formula is simple and most accurate. 
-To estimate $\Improve\_\max^z(a)$, we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$:
+To estimate $\Improve\_\max^z(a)$, we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$, by computing by how much the value of $z$ will change if $a$ is opened
+and other values remain the same - in particular, $value(\hat{a})=\ReLU(sol(a))$. We define:
 %we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
@@
 	\begin{align}
-		\Utility\_\max\nolimits^z(a) = |W_{az} \times (\sol(\hat{a})- \ReLU(\sol(a)))|.
+		\Utility\_\max\nolimits^z(a) = W_{az} \times (\sol(\hat{a})- \ReLU(\sol(a))).
 	\end{align}
@@
 
-We have that :
-
-\begin{proposition}
-$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
-\end{proposition}
-
-\begin{proof}
-Consider $(\sol'(n))_{n \leq z})_{n \leq z})$ with
-$\sol'(n)=\sol(n)$ for all $n \notin \{z,\hat{a}\}$.
-In particular,  $\sol'(a) = \sol(a)$.
-
-Now, define $\sol'(\hat{a}) = \ReLU(\sol(a))$. 
-That is,  
-$\sol'(\hat{a})$ is the correct value for $\hat{a}$ (obtained if we open neuron $a$), 
-compared to the LP abstraction for $\sol(\hat{a})$.
-
-Last, we define $\sol'(z)=\sol(z) + W_{az} \times (\ReLU(\sol(a)) - \sol(\hat{a})) = \sol(z) - \Utility\_\max^z(a)$.
-
-Now, it is easy to check that $(\sol'(n))_{n \leq z}$ satisfies the constraints in 
-$\mathcal{M}_{\{a\}}$, as opening $a$ changes the value of $\hat{a}$ from
-$\sol(\hat{a})$ to $\ReLU(\sol(a))$, and the contribution from $a$ to $z$ is 
-$W_{az}$. As $\sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $\sol'(z) \leq$ $\Sol\_\max_{\{a\}}^z(z)$. That is, 
-$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
-$\Improve\_\max^z(a) \leq \Utility\_\max^z(a)$.
-\end{proof}
-
-Thus, $\Utility\_\max^z(a)$ can be used to approximate 
-$\Improve\_\max^z(a)$. In particular, consider a very frequent case where $W_{az}<0$.
-In this case, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value\dots which happens to be $\sol(\hat{a})=\ReLU(a)$, thanks to Proposition \ref{LP}. 
-In this frequent case, we have $\Utility\_\max^z(a)=0$, and thus $\Improve\_\max^z(a)=0$. 
-In particular, this node will have the smallest utility (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$. 
+In the case $W_{az}<0$, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value, which is $\sol(\hat{a})=\ReLU(a)$ thanks to Proposition \ref{LP}.
+In this case, we have $\Utility\_\max^z(a)=0$.
+Thus, we have $\Utility\_\max^z(a) \geq 0$ in all cases
+as $\sol(\hat{a}) \geq \ReLU(a)$. 
+We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}.
+Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$.
+In particular, for all nodes $a$ with $W_{az}< 0$,
+this node will have the smallest $\Utility\_\max\nolimits^z(a)=0$ (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$.
 This is one stricking difference (but not the only one) with choosing utility based on
@@
 
-Now, consider neurons $a$ two layers before $z$.
-We use $b$ to denote neurons in the layer between $a$ and $z$.
-If we open $a$, then the change in the weight of $a$ will still be $\sol(\hat{a})-\ReLU(\sol(a))$ as above.
-Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b$ in the intermediate layer.
-Based on Proposition \ref{LP}, we can evaluate how opening $a$ impacts each value of 
-$\hat{b}$,  by using the upper and lower bound
-$\UB(b),\LB(b)$.
+Now, consider neurons $a$ two layers before $z$. We use $b$ to denote neurons in the layer $\ell$ between $a$ and $z$. 
+If we open $a$, then the change $\Delta(a)$ in the weight of $a$ is 
+$\Delta(a)=\ReLU(\sol(a)) - \sol(\hat{a}) \leq 0$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b \in \ell$. 
+We let $\Delta(b) = W_{ab}\Delta(\hat{a})$.
+Based on Proposition \ref{LP}, we can evaluate the impact 
+$\Delta(\hat{b})$ of opening $a$ on each value of $\hat{b}$, by using the upper and lower bound $\UB(b),\LB(b)$:
 
-Indeed, if $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
-If $\sol(b) < 0$, then we have a clip at $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ does not help. If $\sol(b) > 0$, then we have $\sol(\hat{b})=\ReLU(b)=\sol(b)$ and every change from 
-$a$ is reflected with a coefficient $W_{ab}$ on $\hat{b}$. 
-Last, if $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
-sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)}$ to maximize $z$.
+	\begin{align*}
+		&\Delta(\hat{b}) =
+		\begin{cases}
+			\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
+			\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
+			\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
+		\end{cases}
+		\end{align*}
+
+Indeed, if $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
+sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)} +$ Cst to maximize $z$.
+Changing $b$ by $\Delta(b)$ thus results in changing $\sol(\hat{b})$ by 
+$\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b)$.
+If $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
+If $\sol(b) < 0$, then we have $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ change the 0 value only if $\sol(b)+\Delta(b)>0$. If $\sol(b) > 0$, then 
+$\sol(\hat{b})=\ReLU(\sol(b))=\sol(b)$, and the change to $\hat{b}$ will be 
+the full $\Delta(b)$, unless $\Delta(b) < -\sol(b) < 0$ in which case it is 
+$-\sol(b)$. We then set:
 
@@
 
-We define a difference $\Delta$ to account for the fact that a neuron $b$ 
-can not exceed $\LB(b),\UB(b)$:
-	\begin{align*}
-		&\Delta(\hat{a}) = \sol(\hat{a}) - \ReLU(\sol(a)) \geq 0\\
-		&\Delta(b) = \begin{cases}
-			\max(W_{ab}\Delta(\hat{a}),\LB(b)-\sol(b)),  &\text{ if }  W_{ab} < 0 \\
-			\min(W_{ab}\Delta(\hat{a}),\UB(b)-\sol(b)),  &\text{ if }  W_{ab} > 0 \\
-		\end{cases}\\
-			&\Delta(\hat{b}) =
-		\begin{cases}
-			\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} > 0 \text{ and } \sol(b)\geq0\\
-				\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} > 0 \text{ and } \sol(b)<0\\
-		 \frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} < 0\\
-		\end{cases}
-		\end{align*}
+$$ \Utility\_\max\nolimits^z(a) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})$$
 
-We can now set 
-$$ \Utility\_\max\nolimits^z(a) = \sum_b W_{bz} \Delta(\hat{b}).$$
+\begin{proposition}
+	\label{prop2}
+		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
+	\end{proposition}
 
-We proceed inductively in the same way to define $\Utility\_\max^z(a)$ for deeper neuron $a$.
+	\begin{proof}
+    Consider $\sol'(n))_{n \leq z})$ with
+	$\sol'(n)=\sol(n)$ for all $n \notin \{z,\hat{a}\} \cup \{b,\hat{b} \mid b \in \ell\}$. In particular,  $\sol'(a) = \sol(a)$.
+	Now, define $\sol'(\hat{a}) = \ReLU(\sol(a))$. 
+	That is, $\sol'(\hat{a})$ is the correct value for $\hat{a}$, obtained if we open neuron $a$, compared to the LP abstraction for $\sol(\hat{a})$.
+	We also define $\sol'(b)=\sol(b)+\Delta(b)$ and 
+	$\sol'(\hat{b})=\sol(\hat{b}) + \Delta(\hat{b})$.
+	Last, $\sol'(z)=\sol(z) + \sum_{b \in \ell} W_{bz} \Delta(\hat{b})$.
+	% = \sol(z) - \Utility\_\max\nolimits^z(a)$.
+
+	It is easy to check that $(\sol'(n))_{n \leq z}$ satisfies the constraints in 
+	$\mathcal{M}_{\{a\}}$, as opening $a$ changes the value of $\hat{a}$ from
+	$\sol(\hat{a})$ to $\ReLU(\sol(a))$, and the contribution from $a$ to $b,\hat{b},z$ 
+	are respected.
+	As $\sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $\sol'(z) \leq$ $\Sol\_\max_{\{a\}}^z(z)$. That is, 
+	$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
+	$\Improve\_\max^z(a) \leq \Utility\_\max^z(a)$.
+	In particular, we have that $\Utility\_\max^z(a) \geq 0$, which was not obvious from the definition.
+	\end{proof}
+
+We can proceed inductively in the same way to define $\Utility\_\max^z(a)$ for deeper neurons $a$.
 

### 2024-09-24 ICLR25/valabstraction.tex
update
section 3 and 4

@@
 
-%\iffalse
-%An extremely efficient algorithm that alleviates some of the inaccuracies is DeepPoly \cite{deeppoly}, also independently discovered as the CROWN algorithm \cite{crown}.
-Instead of fixed bounds for each neuron $n$ in layer $k$, DeepPoly maintains two affine functions representing the lower and upper bounds of the neuron's value, based on inputs from the previous layer $k-1$.
-For instance, denote $f_i \leq x_i \leq g_i$ with, for example, $f_{3}(x_3)=f_4(x_4)=0$ and $g_3(x_3) = \frac{x_3+2}{2}$, $g_4(x_4) = \frac{x_4+2}{2}$.
-This leads to $x_5 \leq g_3(x_3) + 2 g_4(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5$.
-For bounds $[\UB,\LB]$ on $x_i$, the optimal linear function for the upper bound is $g_i(x_i)=\LB \frac{x_i-\alpha}{\LB-\UB}$ for ReLU nodes.
-There are two options for the lower bound: $f^1_i(x_i) = 0$ or $f^2_i(x_i)=x_i$.
-DeepPoly selects between these based on the values of $\alpha$ and $\beta$ (for unstable neurons): if $|\alpha|\geq |\beta|$, then $f_i=f^1_i$ is chosen, otherwise, for $|\beta|>|\alpha|$, $f_i=f^2_i$ is selected.
-%\fi
-
 \subsection{MILP, LP and partial MILP encodings for DNNs}
@@
 At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a complete (but inefficient) method. 
-Consider an unstable neuron $n \in[\UB,\LB]$.
-The value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $(\UB,\LB)$ with 4 constraints \cite{MILP}:
-$\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB \cdot a \quad \wedge \quad \hat{x} \leq x-\UB \cdot (1-a)$.
+Consider an unstable neuron $n$, whose value $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$.
+The value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one 
+integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
 
-For all $x \in [\UB,\LB] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
-Here, $a$ is 0 if $x < 0$, 1 if $x>0$, and can be either if $x=0$~\cite{MILP}.
+$$\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\UB(n) \cdot (1-a)$$
+
+For all $x \in [\LB(n),\UB(n)] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
+The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$.
 This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
@@
 Let $x$ represent the input value of $n$, hence with 
-$\LB(n) < x < \UB(n)$, and $\hat{x}$ representing $ReLU(x)$. 
-Then we have:
+$\LB(n) < x < \UB(n)$, and $\hat{x}$ representing $\ReLU(x)$. 
+We have:
 
@@
 		\ReLU(x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} \label{eq:deeppoly}
-		%& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, \quad a \in [0,1]  \label{eq:lp}\\
 	\end{align} 

### 2024-09-24 ICLR25/formula.tex
fix

@@
 Now, consider neurons $a$ two layers before $z$. We use $b$ to denote neurons in the layer $\ell$ between $a$ and $z$. 
-If we open $a$, then the change $\Delta(a)$ in the weight of $a$ is 
-$\Delta(a)=\ReLU(\sol(a)) - \sol(\hat{a}) \leq 0$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b \in \ell$. 
+If we open $a$ without changing its value $\sol(a)$, then the change $\Delta(\hat{a})$ in the weight of $\hat{a}$ is 
+$\Delta(\hat{a})=\ReLU(\sol(a)) - \sol(\hat{a}) \leq 0$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b \in \ell$. 
 We let $\Delta(b) = W_{ab}\Delta(\hat{a})$.

### 2024-09-24 ICLR25/formula.tex
section 4

@@
 
-In the case $W_{az}<0$, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value, which is $\sol(\hat{a})=\ReLU(a)$ thanks to Proposition \ref{LP}.
+In the case $W_{az}<0$, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value, which is $\sol(\hat{a})=\ReLU(\sol(a))$ thanks to Prop.~\ref{LP}.
 In this case, we have $\Utility\_\max^z(a)=0$.
 Thus, we have $\Utility\_\max^z(a) \geq 0$ in all cases
-as $\sol(\hat{a}) \geq \ReLU(a)$. 
+as $\sol(\hat{a}) \geq \ReLU(\sol(a))$ by Prop.~\ref{LP}. 
 We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}.

### 2024-09-24 ICLR25/experiments.tex
Utility evaluation

--- 2024-09-24 ICLR25/experiments.tex
@@
 
-\subsection{Evaluation of the Utility function to choose nodes to open}
+\subsection{Evaluation of the Utility function to choose neurons to open}
 
 %The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-To measure the impact of the utility function to select nodes to open, we focused on a small hard DNN, namely $5\times 100$, so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN.
-We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
+To measure the impact of the utility function to select neurons to open, we focused on a small hard DNN, namely $5\times 100$, so as to be able to compute exact bounds for the first few layers using a full MILP encoding of the DNN for comparison purpose.
+We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K=|X|$ the size of set $X$.
 To measure the accuracy, we measure the uncertainty of all nodes in a layer:
@@
 
-\begin{table}[b!]	
+We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
+The bounds for nodes of the first two layers are computed exactly using the full MILP encoding.
+We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our {\bf Utility} function, compared with a random choice, both for nodes exclusively from the previous Layer 2 or from both Layers 1 and 2.
+We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{cd}|$ \cite{DivideAndSlide}, which is limited to the previous Layer 2.
+
+\begin{table}[h!]	
 	\centering
-	\begin{tabular}{|c||c|c|c|c|c|}
+	\begin{tabular}{|c||c|c|c||c|c|}
 		\hline
-		\text{Number $K$}  &  \bf Utility& Utility (1 layer)& \text{} \cite{ DivideAndSlide} & \text{Random} &\text{Random (1 layer)}\\ \hline
+			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=61$}&\multicolumn{2}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-6}
+		\text{$|X|$}  & \text{Random} & \cite{ DivideAndSlide} & \bf Utility& \text{Random} &\bf Utility\\ \hline
 		\hline
-		0  &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline
-		5  & \bf 1.532  &1.603& 1.704 &  1.729&  1.729 \\ \hline
-		10  & \bf 1.371  & 1.517& 1.651 & 1.696 & 1.701\\ \hline
-		15  & \bf 1.247  &1.466&  1.599 &  1.653& 1.671\\ \hline
-		20  & \bf 1.145  &1.438& 1.557 & 1.619 & 1.635\\ \hline
-		25  & \bf 1.061  &1.427& 1.519 &  1.586 &1.601\\ \hline
-		30  & \bf 0.989  &1.425& 1.489 & 1.546 & 1.574\\ \hline
-		35  & \bf 0.934  &1.424& 1.465 & 1.502 &1.542\\ \hline
-		40  & \bf 0.921 &1.424& 1.447 & 1.469 & 1.512\\ \hline
-		116 (max) &  0.895 &1.424& 1.424 (max=$61$) & 0.895 &1.424  \\ \hline
+		0  (LP) &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline \hline
+		5  &   1.729&1.704 & 1.603&  1.729&  \bf 1.532 \\ \hline
+		10  &  1.701 &  1.651 &1.517& 1.696 & \bf  1.371\\ \hline
+		15  & 1.671 &  1.599 &1.466&  1.653& \bf  1.247\\ \hline
+		20  &  1.635 & 1.557&1.438 & 1.619 & \bf  1.145\\ \hline
+		25  &  1.601 & 1.519 &1.427&  1.586 & \bf 1.061\\ \hline
+		30  & 1.574 & 1.489 &1.425& 1.546 & \bf  0.989 \\ \hline
+		35  &  1.542 & 1.465&1.424 & 1.502 & \bf 0.934 \\ \hline
+		40  & 1.512 & 1.447 &1.424& 1.469 & \bf 0.921 \\ \hline \hline
+		max & 1.424  &1.424& 1.424 & 0.895 & 0.895   \\ \hline
 	\end{tabular}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer (our utility function vs \cite{ DivideAndSlide} vs random choice).}
+	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
 	\label{tab:example1}
-	\vspace{-0.6cm}
+	%\vspace{-0.6cm}
 \end{table}
 
-We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
-The bounds for nodes of the first two layers are computed exactly using the full MILP encoding.
-We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our utility function, vs choosing $K$ nodes from layers $1$ and $2$.
-We compared with a random choice in the first two layers, and also choice based on strength in \cite{DivideAndSlide}, defined as
-$strength(n) = (\UB(n)-\LB(n))\cdot |W_{cd}|$, which is thus limited to the previous (2sd hidden layer).
-
-The Utility function reveals to select very important nodes: already with 35 out of 116 nodes, the accuracy is improved by $95\%$ what can be done if all 116 nodes are opened compared with LP (K=0).
-It is also much more accurate than using Incoming weights: already with 5 (resp.
-10) nodes chosen by our utility function is more accurate than $20$ (resp.
-$40$) nodes chosen by Incoming weights.
-That is more than 4 reduction in the number of nodes necessary for similar accuracy.
-Random is even worst Strength up to 30 nodes, then selecting in earlier layers appear to be more useful as there are not so many nodes to open in the previous layer.
+The Utility function selects very important neurons:
+ to achieve the same accuracy than \cite{DivideAndSlide}, $2.5$ time fewer nodes (10 vs 25) are necessary when picking in the same previous Layer 2.
+The ability from {\bf Utility} to compare neurons from different layers enables even better frugality: $4$ time fewer nodes (5 vs 20, 10 vs 40) are necessary to reach the same accuracy than \cite{DivideAndSlide}.
+Overall, choosing 35 neurons by {\bf Utility} improves accuracy by $95\%$ of what can be done if all $|X|=116$ nodes are opened compared with LP (corresponding to $|X|=0$).
 

### 2024-09-24 ICLR25/experiments.tex
experiments

@@
 	\centering
-	\begin{tabular}{||l||c|c|c|c||c||}
+	\begin{tabular}{||l||c|c|c||c||c||}
 		\hline \hline
-		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & Hybrid \\ 
-		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & MILP \\ 
+		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & \bf Hybrid \\ 
+		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & \bf MILP \\ 
 		\hline
@@
 
-Interpretation: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN, 
+{\em Analysis}: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN, 
 as it is called first and it is sufficient to have $0\%$ undecided images, as shown even on the very large ResNet.
@@
 
-Compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%$-$43\%$ wrt $\alpha,\beta$-Crown with TO of 2000s.
+Compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%$-$43\%$. 
 It is also from 20x faster on smaller networks to similar time on the largest DNN.
@@
 
-Last, compared with refined $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5x100, 5x200), refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than  Hybrid MILP, but with longer runtime (up to 2x on 5x100).
-On intermediate DNNs (8x100,8x200), full MILP invoked by refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images, while having longer runtime.
-Last, refined $\beta$-Crown cannot scale to larger instances (6x500, CNN-B-Adv), while Hybrid MILP can.
+Last, compared with {\em Refined} $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5$\times$100, 5$\times$200), Refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than  Hybrid MILP, but with longer runtime (up to 2 times on 5$\times$100).
+On intermediate DNNs (8$\times$100,8$\times$200), full MILP invoked by Refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images (that is double on 8$\times$200), while having longer runtime.
+Last but not least, Refined $\beta$-Crown cannot scale to larger instances (6$\times$500, CNN-B-Adv), while Hybrid MILP can.
 
@@
 
-Analysis: in 90\% of the cases, Hybrid MILP is very close to the upper bound.
+{\em Analysis}: in 90\% of the cases, Hybrid MILP is very close to the upper bound.
 On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible the upper bound did not find a close attack to robustness.

### 2024-09-24 ICLR25/experiments.tex
exp

@@
 We then average the uncertainty among all the nodes of the layer.
-Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is $unc(a) = \UB - \LB$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$
+Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB - \LB$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$
 

### 2024-09-24 ICLR25/Paper_noProof.tex
update
update table
some clean up

@@
 \usepackage{calc}
+\usepackage{array}
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
@@
 \newcommand{\Utility}{\mathrm{Utility}}
+\newcommand{\Sol}{\mathrm{Sol}}
+\newcommand{\sol}{\mathrm{sol}}
 
@@
 
-In this paper, we study the MILP encoding of ReLU-DNNs, and provide new deep insights in the LP relaxation.
+In this paper, we study the MILP encoding of ReLU-DNNs, and provide new insights in the LP relaxation.
 This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation.
@@
 the accuracy, and when it impacts the accuracy importantly, in which case representing it with a binary/integer variable is preferable.
-This allows us to select a small set of important neurons to encode as a binary variables, while improving accuracy drastically, necessitating $>4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
-Our empirical studies revealed that Hybrid MILP, can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp) within the same runtime.
-This opens a lot of perspective, among which: verifying efficiently hard instances; certifying robustness of images for larger $\epsilon$ neighbourhoods; verifying global rather than local properties \cite{lipshitz}.
+This allows us to select a small set of important neurons to encode as a binary variables, improving accuracy drastically.
+Our automated choice of opened neurons necessitates $>4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
+Our empirical studies revealed that Hybrid MILP, can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp), with the same runtime.
+The reason is that $\alpha,\beta$-Crown can scale to large easy DNNs, but does not scale to 
+hard even small DNNs: it hits a complexity wall, similarly as other compeating solutions.
+This opens a lot of perspectives, among which: verifying efficiently other hard instances; certifying $\epsilon$-robustness of images for $\epsilon$ as large as possible;
+verifying global rather than local properties \cite{lipshitz}.
 

### 2024-09-24 ICLR25/experiments.tex
some clean up

@@
 We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our {\bf Utility} function, compared with a random choice, both for nodes exclusively from the previous Layer 2 or from both Layers 1 and 2.
-We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{cd}|$ \cite{DivideAndSlide}, which is limited to the previous Layer 2.
+We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$ \cite{DivideAndSlide}, which is limited to the previous Layer 2.
 
@@
 
-We conducted our evaluation on the neural networks tested in \cite{crown},
-which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.
-
-Namely, these are 6 {\em hard} ReLU-DNNs: 5 MNIST DNN from the ERAN GitHub (\url{https://github.com/eth-sri/eran}, the 4th to the 8th DNNs provided) as well as 1 CIFAR CNN from 
-\cite{AdversarialTrainingAndProvableDefenses} (the network file we use is from \url{https://github.com/Verified-Intelligence/alpha-beta-CROWN}), also see \cite{SDPFI}, with the same $\epsilon$ setting.
+We conducted our evaluation on the neural networks tested in \cite{crown}
+which display a large number ($\geq 20\%$) of images undecided  by $\alpha,\beta$-Crown.
+That is, these DNNs are {\em hard} to verify.
+Namely, these are 6 ReLU-DNNs: 5 MNIST DNN that can be found in the \href{https://github.com/eth-sri/eran}{ERAN GitHub}
+(the 4th to the 8th DNNs provided) as well as 1 CIFAR CNN from 
+\cite{AdversarialTrainingAndProvableDefenses}, see also \cite{SDPFI}, 
+which can be downloaded from the \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN}{$\alpha,\beta$-Crown GitHub}. 
+We commit to the same $\epsilon$ settings as in \cite{crown}, that are recalled in Table \ref{table_beta}. 
 For reference, we also report an easy but very large ResNet Network for CIFAR10, already tested with $\alpha,\beta$ CROWN. 
-We report in Table \ref{table_hybrid} the $\%$ of undecided images, that is the $\%$ of images than can be neither falsified (by $\alpha,\beta$-CROWN) nor verified by the tested verifier, among the 100 first images for each MNIST or CIFAR10 benchmark, the exact same setting and DNNs as used in Table \ref{table_beta}.
+We report in Table \ref{table_hybrid} the $\%$ of undecided images, that is the $\%$ of images than can be neither falsified (by $\alpha,\beta$-CROWN) nor verified by the tested verifier, among the 100 first images for each MNIST or CIFAR10 benchmark.
+The exact same DNNs and $\epsilon$ are used in Tables \ref{table_beta} and \ref{table_hybrid}.
 
@@
 
-Compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%$-$43\%$. 
+Compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%-43\%$. 
 It is also from 20x faster on smaller networks to similar time on the largest DNN.
@@
 Last, compared with {\em Refined} $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5$\times$100, 5$\times$200), Refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than  Hybrid MILP, but with longer runtime (up to 2 times on 5$\times$100).
-On intermediate DNNs (8$\times$100,8$\times$200), full MILP invoked by Refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images (that is double on 8$\times$200), while having longer runtime.
+On intermediate DNNs (8$\times$100, 8$\times$200), full MILP invoked by Refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images (that is double on 8$\times$200), while having longer runtime.
 Last but not least, Refined $\beta$-Crown cannot scale to larger instances (6$\times$500, CNN-B-Adv), while Hybrid MILP can.
@@
 
-Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, but for 2 cases where $\alpha,\beta$-CROWN is already very close to the upper bond.
-On average, the $\epsilon$ gap to upper bound is $0.014$ for Hybrid MILP, and $0.42$ for
+Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, except for 2 cases where $\alpha,\beta$-CROWN is already very close to the upper bound.
+On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, and $0.042$ for
 $\alpha,\beta$-CROWN.
@@
 
-We volontarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider much finer parameter choice without too much cluter.
+We volontarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much cluter.
 

### 2024-09-24 ICLR25/introduction.tex
update
some clean up

@@
 Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
-and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
-We will thus focus in the following mostly on $\alpha,\beta$-CROWN.
+and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-Crown \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+We will thus focus in the following mostly on $\alpha,\beta$-Crown.
 
-Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-CROWN \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neighbour with a different decision.
+Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-Crown \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neighbour with a different decision.
 One issue is however that easy instances are trained specifically to be easier to verify
@@
 answering correctly to an unperturbed input.
-For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct (the other $71\%$ are thus not even tested by $\alpha,\beta$-CROWN).
+For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct (the other $71\%$ are thus not even tested by $\alpha,\beta$-Crown).
 While more accurate trainers for verification have been recently developped \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
@@
 bounding on Lipschitz constants \cite{lipshitz} globally or asking several specification at once, makes the instance particularly harder.
-Last, there are many situation (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible ({\em verification-agnostic} networks \cite{SDPFI}).
-The bottom line is, one cannot expect only easy verification instances: hard verification instances need to be explored as well.
+Last, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks \cite{SDPFI}.
+The bottom line is, one cannot expect only {\em easy} verification instances: {\em hard} verification instances need to be explored as well.
 
-In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($>20\%$) between images that can be certified 
-by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.
-In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely 5x100 for MNIST.
-We first dwelve into the scaling of $\alpha,\beta$- Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
+In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified 
+by $\alpha,\beta$-Crown and the upper bound when we remove those which can be falsified.
+In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely MNIST 5$\times$100.
+We first dwelve into the scaling of $\alpha,\beta$-Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
 Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).
@@
 Complete verifier barely (9\% out of 50\%) 
-outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite much larger runtime.}
+outperform $\alpha,\beta$-Crown (40\%, 1026s), despite much larger runtime.}
 \label{table_complete}
@@
 
-The size of the smallest DNN (500 hidden neurons) makes it realistic to be solved by complete verifiers such as Marabou 2.0, NNenum or a Full MILP encoding. 
+The size of the smallest DNN (500 hidden neurons) makes it believable to be solved by complete verifiers such as Marabou 2.0, NNenum or a Full MILP encoding. 
 While they should theoretically be able to close the gap of undecided images,
-in practice, Table \ref{table_complete} reveals that only NNenum succeds to verify 9\% more images out of the 50\% undecided images by $\alpha,\beta$-Crown, and with a very large runtime of almost 5000s per image.
+in practice, even with a large 10 000s Time-out, Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images, and with a very large runtime of almost 5000s per image.
 It seemed pointless to test complete verifiers on larger networks.
@@
 
-%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-Crown \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
 
-%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs; It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-Crown \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs; It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
 The high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
@@
 	%Notice that complete methods exist \cite{Reluplex,katz2019marabou,SDPFI}, but they time-out on hard instances.
-In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-CROWN \cite{crown}.
+In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-Crown \cite{crown}.
 %As a starting point, we sought to understand properties of DNNs that make them hard to verify.
@@
 	encoding of ReLU-DNNs. We establish in Proposition \ref{LP} an explicit abstraction set corresponding to the LP constraints.
+
 	\item This allows us to propose a measure of utility for each neuron, providing an upper bound on the improvement on accuracy made if we treat this neuron with an integer variable instead of the LP relaxation.
@@
 \item We then propose a new verifier, called Hybrid MILP, invoking first 
-$\alpha,\beta$-CROWN with short time-out to settle the easy instances.
+$\alpha,\beta$-Crown with short time-out to settle the easy instances.
 On those (hard) instances which are neither certified nor falsified, we call our partial MILP with few neurons encoded as integer variables.
 Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
-It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-CROWN with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance (46-420s).
+It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-Crown with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance (46-420s).
 It scale to fairly large networks such as CNN-B-Adv \cite{SDPFI} for the CIFAR10 benchmark, with more than 20.000 neurons.
@@
 %because for "easier" DNNs, adequate methods already exist. 
-%To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-CROWN \cite{crown}.
+%To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-Crown \cite{crown}.
 All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds.
@@
 The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.
-For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in CROWN).
+For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in Crown).
 Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).

### 2024-09-24 ICLR25/introduction.tex
clean up

@@
 \begin{enumerate}
-	\item  Our first contribution is to study the LP relaxation for the complete MILP
-	encoding of ReLU-DNNs. We establish in Proposition \ref{LP} an explicit abstraction set corresponding to the LP constraints.
+	\item  Our first contribution is to study the LP relaxation for the exact MILP
+	encoding of ReLU-DNNs. We establish in Proposition \ref{LP} an explicit abstraction set corresponding to the linear constraints imposed by the LP relaxation.
 
-	\item This allows us to propose a measure of utility for each neuron, providing an upper bound on the improvement on accuracy made if we treat this neuron with an integer variable instead of the LP relaxation.
-Choosing the neurons with the top utility and encoding them with integer variables gives rise to a partial MILP which is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating much less integer variables for the same accuracy.
+	\item This allows us to propose a measure of utility for each neuron, providing a proved upper bound (Proposition \ref{prop2}) on the improvement on accuracy made if we treat this neuron with an integer variable instead of the LP relaxation.
+Choosing the neurons with the top utility and encoding them with integer variables gives rise to a partial MILP which is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating 4 times less integer variables for the same accuracy (Table \ref{tab:example1}).
 
@@
 Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
-It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-Crown with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance (46-420s).
-It scale to fairly large networks such as CNN-B-Adv \cite{SDPFI} for the CIFAR10 benchmark, with more than 20.000 neurons.
+It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-Crown with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance ($46-420$s), Table \ref{table_hybrid}.
+It scales to fairly large networks such as CNN-B-Adv \cite{SDPFI} for the CIFAR10 benchmark, with more than 20 000 neurons.
 %We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).

### 2024-09-24 ICLR25/experiments.tex
clean up

@@
 		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
-		CIFAR Resnet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
+		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
 	\end{tabular}
@@
 
-For that, we considered the DNN 6x500, and the 20 first images from the MNIST benchmark.
+For that, we considered the challenging DNN MNIST $6 \times 500$, and the 20 first images from the MNIST benchmark.
 We first run the attack from $\alpha,\beta$-Crown for varying $\epsilon$, using a binary search, to set up an upper bound on $\epsilon$ (the initialization is $\epsilon \in [0,1]$).
-Then we run binary search with a global time out of $10 000s$, initialized from $0$ to this upper bound, where each call is either to $\alpha,\beta$-Crown with TO=2000s, or Hybrid MILP.
+Then we run binary search with a global time-out of $10 000s$, initialized from $0$ to this upper bound, where each call is either to $\alpha,\beta$-Crown with TO=2000s, or Hybrid MILP.
 We report the results (upper bound, best bound verified by $\alpha,\beta$-Crown and by Hybrid MILP) for each image. We report the results in Fig. \ref{fig2}
@@
 {\em Analysis}: in 90\% of the cases, Hybrid MILP is very close to the upper bound.
-On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible the upper bound did not find a close attack to robustness.
+On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible that the falsifier missed a closer attack to robustness.
 
-Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, except for 2 cases where $\alpha,\beta$-CROWN is already very close to the upper bound.
-On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, and $0.042$ for
-$\alpha,\beta$-CROWN.
+Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, except for 2 cases (images 8 and 18) where $\alpha,\beta$-CROWN is already very close to the upper bound.
+On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, and $0.042$ for $\alpha,\beta$-CROWN.
 

### 2024-09-24 ICLR25/Paper_noProof.tex
clean up

@@
 The reason is that $\alpha,\beta$-Crown can scale to large easy DNNs, but does not scale to 
-hard even small DNNs: it hits a complexity wall, similarly as other compeating solutions.
+hard even small DNNs: it hits a complexity barrier, similarly as other compeating solutions.
 This opens a lot of perspectives, among which: verifying efficiently other hard instances; certifying $\epsilon$-robustness of images for $\epsilon$ as large as possible;

### 2024-09-24 ICLR25/valabstraction.tex
clean up

@@
 
-%\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
+\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
 
@@
 
-		\node[circle, draw= black, thick, minimum width = 20,
+		\node[circle, draw= applegreen, thick, minimum width = 20,
 		minimum height = 20] (input1) {$n_1$};
 
-		\node[circle, draw= black, thick, minimum width = 20,
+		\node[circle, draw= applegreen, thick, minimum width = 20,
 		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};
@@
 
-		\node[circle, draw= black, thick, minimum width = 20,
+		\node[circle, draw= blue, thick, minimum width = 20,
 		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$n_3$};
-		\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};
+		\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};
 
-		\node[circle, draw= black, thick, minimum width = 20,
+		\node[circle, draw= blue, thick, minimum width = 20,
 		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{n}_3$};
-		\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};
+		\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};
 
-		\node[circle, draw= black, thick, minimum width = 20,
+		\node[circle, draw= red, thick, minimum width = 20,
 		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
-		\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};
+		\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};
 
 		% Output layer
-		\node[circle, draw= black, thick, minimum width = 20,
+		\node[circle, draw= blue, thick, minimum width = 20,
 		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{n}_5$};
 
-		\node[circle, draw= black, thick, minimum width = 20,
+		\node[circle, draw= blue, thick, minimum width = 20,
 		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{n}_{6}$};

### 2024-09-25 ICLR25/experiments.tex

@@
 Then we run binary search with a global time-out of $10 000s$, initialized from $0$ to this upper bound, where each call is either to $\alpha,\beta$-Crown with TO=2000s, or Hybrid MILP.
-We report the results (upper bound, best bound verified by $\alpha,\beta$-Crown and by Hybrid MILP) for each image. We report the results in Fig. \ref{fig2}
+We report the results (upper bound, best bound verified by $\alpha,\beta$-Crown and by Hybrid MILP) for each image. We report the results in Fig. \ref{fig2}.
 
@@
 \includegraphics[scale=0.5]{epsilon.png}.
-\caption{$\epsilon$-robustness proved after $10 000s$ for each of the 20 first images of MNIST.}
+\caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ on each of the 20 first images of MNIST.}
 \label{fig2}
@@
 Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, except for 2 cases (images 8 and 18) where $\alpha,\beta$-CROWN is already very close to the upper bound.
-On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, and $0.042$ for $\alpha,\beta$-CROWN.
+On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, 3 times smaller than the $0.042$ gap for $\alpha,\beta$-CROWN.
 

### 2024-09-25 ICLR25/formula.tex
edit section 4

@@
 
-	\begin{align}
-		\Utility\_\max\nolimits^z(a) = W_{az} \times (\sol(\hat{a})- \ReLU(\sol(a))).
-	\end{align}
+	$$\Utility\_\max\nolimits^z(a) = W_{az} \times (\sol(\hat{a})- \ReLU(\sol(a)))$$
 
@@
 
-Now, consider neurons $a$ two layers before $z$. We use $b$ to denote neurons in the layer $\ell$ between $a$ and $z$. 
+Now, consider neuron a $a$ two layers before $z$. We use $b$ to denote neurons in the layer $\ell$ between $a$ and $z$. 
 If we open $a$ without changing its value $\sol(a)$, then the change $\Delta(\hat{a})$ in the weight of $\hat{a}$ is 
-$\Delta(\hat{a})=\ReLU(\sol(a)) - \sol(\hat{a}) \leq 0$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b \in \ell$. 
-We let $\Delta(b) = W_{ab}\Delta(\hat{a})$.
+$\Delta(\hat{a})=\ReLU(\sol(a)) - \sol(\hat{a}) \leq 0$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through $\ell$. 
+We let $\Delta(b) = W_{ab}\Delta(\hat{a})$ for all $b \in \ell$.
 Based on Proposition \ref{LP}, we can evaluate the impact 
-$\Delta(\hat{b})$ of opening $a$ on each value of $\hat{b}$, by using the upper and lower bound $\UB(b),\LB(b)$:
+$\Delta(\hat{b})$ of opening $a$ on the value of each $\hat{b}$, by using the upper and lower bound $\UB(b),\LB(b)$:
 
@@
 	$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
-	$\Improve\_\max^z(a) \leq \Utility\_\max^z(a)$.
+	$ \Utility\_\max^z(a) \geq \Improve\_\max^z(a)$.
 	In particular, we have that $\Utility\_\max^z(a) \geq 0$, which was not obvious from the definition.

### 2024-09-25 ICLR25/experiments.tex
update

@@
 	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, refined $\beta$-Crown and Hybrid MILP, run on 7 DNNs (average runtime per image in second).
-The 6 first DNNs are hard instances, while the last one (ResNet) is an easy instance (it is trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
+	\caption{Undecided images ($\%$, {\em lower is better}), TO UPDATE.}
 	\label{table_hybrid}

### 2024-09-25 ICLR25/Paper_noProof.tex
update
abstract

@@
 \pagestyle{plain}
+\usepackage{threeparttable}
 
@@
 $\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best 
-trade-off between accuracy vs computational time. VNNcomp however is focusing on relatively easy verification instances (network, inputs (images)), 
-with few {\em unstable nodes}.
-In this paper, we consider harder verification instances.
-On such instances, $\alpha,\beta$-CROWN displays a large gap ($20-58\%$) between instances that can be verified, and instances with an explicit attack.
-Enabling much larger time-outs for $\alpha,\beta$-CROWN only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
+trade-off between accuracy and runtime.
+VNNcomp however is focusing on relatively easy verification instances, with few unstable neurons.
+In this paper, we consider {\em harder} verification instances, on which $\alpha,\beta$-Crown displays a large number ($20-58\%$) of undecided instances, that is, instances that can neither be verified, nor an explicit attack can be found.
+Enabling larger time-outs for $\alpha,\beta$-Crown only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
 Resorting to other techniques, such as complete verifiers, does not fare better even with very large time-outs: They would theoretically be able to close the gap, but with an untractable runtime on all but small {\em hard} instances.
@@
 Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
-Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-CROWN fails, produces a very accurate yet efficient verifier, reducing tremendously the gap of undecided instances ($8\%$-$15\%$), while keeping a reasonable runtime ($46s$-$417s$ on average per instance).
+Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-Crowb fails, produces a very accurate yet efficient verifier, reducing tremendously the number of undecided instances ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance).
 \end{abstract}

### 2024-09-25 ICLR25/experiments.tex
clean up

@@
 	\end{tabular}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
+	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
 	\label{tab:example1}
@@
 		MNIST 8$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
-		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
+		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & $-$ & 
 		\bf 10\% (402s) \\ \hline
-		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
-		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
+		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
+		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
 	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), TO UPDATE.}
+	\caption{Undecided images ($\%$, {\em lower is better}) as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown and Hybrid MILP on 7 DNNs (average runtime per image).
+The 6 first DNNs are hard instances.
+The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
 	\label{table_hybrid}
@@
 
-We volontarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much cluter.
+We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
 
-Notice that results for several other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with defavorable comparison vs $\alpha,\beta$-CROWN.
+Notice that results for several other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN.
 Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd
 of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN.
-Concerning MnBAB \cite{ferrari2022complete}, it compares slightly defavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv \cite{ferrari2022complete}, and we also run it for the MNIST DNNs, and it was slightly slower and less accurate than $\alpha,\beta$-CROWN at several time-out settings.
+Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings.
 Last, Pyrat code (2sd in the latest VNNComp) is not open source, which made running it impossible.

### 2024-09-26 ICLR25/Paper_noProof.tex
abstract

@@
 trade-off between accuracy and runtime.
-VNNcomp however is focusing on relatively easy verification instances, with few unstable neurons.
+VNNcomp however is focusing on relatively easy verification instances.
 In this paper, we consider {\em harder} verification instances, on which $\alpha,\beta$-Crown displays a large number ($20-58\%$) of undecided instances, that is, instances that can neither be verified, nor an explicit attack can be found.
@@
 Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
-Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-Crowb fails, produces a very accurate yet efficient verifier, reducing tremendously the number of undecided instances ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance).
+Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-Crown fails, produces a very accurate yet efficient verifier, reducing tremendously the number of undecided instances ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance).
 \end{abstract}

### 2024-09-27 ICLR25/Paper_noProof.tex
statement

@@
 
+{\bf Reproducibility Statement:} 
+We tested twice outlier results to confirm them, making sure of reproducibility on the given hardware. Precise details on the settings used are provided in the appendix.
+Additional results are also provided in the appendix.
+Tested DNNs as well as MNIST and CIFAR10 DataSet are freely available.
+The source code of Hybrid MILP will be provided on GitHub after acceptance (needing Gurobi as well as $\alpha,\beta$-Crown).
+
 \newpage

### 2024-09-28 ICLR25/experiments.tex
statement
polish

@@
 %
-We implemented \toolname\ in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
-with 256 GB of main memory and an NVIDIA RTX 3090.
+We implemented \toolname\ in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems.
+We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz, 5nm) with 256 GB of main memory and 2 NVIDIA RTX 4090.
 
@@
 Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings.
-Last, Pyrat code (2sd in the latest VNNComp) is not open source, which made running it impossible.
+Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible.
 

### 2024-09-28 ICLR25/introduction.tex
polish

@@
 For this reason, DNN verifiers in the past years have mainly focused on optimizing for such easy instances.
-Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
+Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT
+\cite{pyrat}, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
 and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-Crown \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
@@
 e.g.
-using DiffAI \cite{DiffAI} or PGD \cite{PGD}, which can impact the accuracy of the network, i.e.
+using DiffAI \cite{DiffAI} PGD \cite{PGD}, which can impact the accuracy of the network, i.e.
 answering correctly to an unperturbed input.
 For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct (the other $71\%$ are thus not even tested by $\alpha,\beta$-Crown).
-While more accurate trainers for verification have been recently developped \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
+While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
 very hard verification instances into hard verification instances.
@@
 	$\alpha,\beta$-Crown with short time-out to settle the easy instances.
-On those (hard) instances which are neither certified nor falsified, we call our partial MILP with few neurons encoded as integer variables.
+On those ({\em hard}) instances which are neither certified nor falsified, we call our partial MILP with few neurons encoded as integer variables.
 Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.

### 2024-09-28 ICLR25/relatedwork.tex
polish

@@
 That shortcoming for hard instances was witnessed in \cite{crown}, and a very specific solution using the full MILP encoding for the first few layers of a DNN was drafted, following similar proposal \cite{MILP2}.
-There are two key issues with this techniques: it is slow, as every neurons up to the layer are encoded using an integer variable, and it cannot scale to DNN with many neurons, making it not that accurate for intermediate networks (e.g.
-9x100,9x200, Table \ref{table_hybrid}), and not usable for larger DNNs (6x500, CNN-B-Adv), whereas Hybrid MILP does scale.
+There are two key issues with this techniques: it is slow, as every neurons up to the layer are encoded using an integer variable, and it cannot scale to DNNs with many neurons, making it not that accurate for intermediate networks (e.g.
+$9\times100$, $9\times200$, Table \ref{table_hybrid}), and not usable for larger DNNs ($6\times500$, CNN-B-Adv), whereas Hybrid MILP does scale.
 

### 2024-11-20 ICLR25/introduction.tex
blue to integrate the different comments

@@
 \begin{enumerate}
-	\item  Our first contribution is to study the LP relaxation for the exact MILP
-	encoding of ReLU-DNNs. We establish in Proposition \ref{LP} an explicit abstraction set corresponding to the linear constraints imposed by the LP relaxation.
+	\item  Our first contribution studies the {\em LP relaxation} of the exact MILP encoding of ReLUs.
+{\color{blue} We establish in Proposition \ref{LP} its equivalence with the so-called "triangular abstraction"}.
 
-	\item This allows us to propose a measure of utility for each neuron, providing a proved upper bound (Proposition \ref{prop2}) on the improvement on accuracy made if we treat this neuron with an integer variable instead of the LP relaxation.
-Choosing the neurons with the top utility and encoding them with integer variables gives rise to a partial MILP which is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating 4 times less integer variables for the same accuracy (Table \ref{tab:example1}).
+	\item {\color{blue} It allows us to choose through a novel Utility function 
+	few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP).
+Specifically, the novelty of Utility resides in the use of the solution to an (efficient) full LP call on the node $z$ we want to bound.
+Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}).
+pMILP is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating $\approx 4$ times less integer variables for the same accuracy (Table \ref{tab:example1}), because Utility focuses on the solution local to the input, rather than on the DNN.
+To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g.
+\cite{ferrari2022complete,crown}.}
 
-	\item We then propose a new verifier, called Hybrid MILP, invoking first 
+	\item We then propose a new verifier, called {\em Hybrid MILP}, invoking first 
 	$\alpha,\beta$-Crown with short time-out to settle the easy instances.
-On those ({\em hard}) instances which are neither certified nor falsified, we call our partial MILP with few neurons encoded as integer variables.
+On those ({\em hard}) instances which are neither certified nor falsified, we call pMILP with few neurons encoded as integer variables.
 Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
 It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-Crown with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance ($46-420$s), Table \ref{table_hybrid}.
-It scales to fairly large networks such as CNN-B-Adv \cite{SDPFI} for the CIFAR10 benchmark, with more than 20 000 neurons.
+It scales to fairly large networks such as CIFAR-10 CNN-B-Adv \cite{SDPFI}, with more than 20 000 neurons.
 %We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).

### 2024-11-21 ICLR25/Paper_noProof.tex
fix a few typos

@@
 In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in.
+capitalized bold $\boldsymbol{W}$ for matrices, \textcolor{red}{similar to notations in}.
 To simplify the notations, we restrict the presentation to feed-forward, 

### 2024-11-21 ICLR25/formula.tex
update a draft formula to general case
update
modif
fix a few typos

@@
 Let $z$ be a neuron of the DNN we want to evaluate, for instance computing an upper bound on the value it can take.
-We denote by $n < z$ the fact that a neuron $n$appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
+We denote by $n < z$ the fact that a neuron $n$ appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
 Let us denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ 
@@
 \iffalse
+We use the following formula for general cases, i.e. possibly more than 3 layers. We use $a$ to denote the source node, and use $b,c$ to denote that $b$ is in one layer before $c$.
+
+\begin{align*}
+	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
+	\Delta_0(b) &= \sum_{b} W_{bc}\Delta(\hat{b})\\
+		\Delta(c) &= \min(\max((\sol(c)+\Delta_0(c),\LB(c))),\UB(c))-\sol(c)\\
+		\Delta(\hat{c}) &=
+		\begin{cases}
+		\Delta(c)\frac{\LB(c) - \sol(\hat{c})}{\LB(c) - \sol(c)},  &\text{if } \LB(c)< \sol(c) < 0\\
+		\Delta(c)\frac{\UB(c) - \sol(\hat{c})}{\UB(c) - \sol(c)},  &\text{if }  0< \sol(c) < \UB(c)\\
+			\Delta(c),  &\text{else } 	 
+		\end{cases}
+\end{align*}
+
 \subsubsection*{Three Layer before  $z$}

### 2024-11-21 ICLR25/valabstraction.tex
fix some typos

@@
 We have $\hat{x}$ is upper bounded by $max_{a \in [0,1]} (min(\UB(n) \cdot a, x - \LB(n) (1-a)))$, and this bound can be reached.
-Furthermore, using standard function analysis tools (derivative...), we can show that the function $a \mapsto \min(\UB(n) \cdot a, x - \LB(n) (1-a))$ attains its maximum when $\UB(n) \cdot a = x - \LB(n) (1-a)$, leading to the equation $(\UB(n) - \UB(n)) a = x - \LB(n)$ and consequently $a = \frac{x - \LB(n)}{\UB(n)-\LB(n)}$.
+Furthermore, using standard function analysis tools (derivative...), we can show that the function $a \mapsto \min(\UB(n) \cdot a, x - \LB(n) (1-a))$ attains its maximum when $\UB(n) \cdot a = x - \LB(n) (1-a)$, leading to the equation $(\UB(n) - \LB(n)) a = x - \LB(n)$ and consequently $a = \frac{x - \LB(n)}{\UB(n)-\LB(n)}$.
 This results in an upper bound $\hat{x} \leq \UB(n) \frac{x - \LB(n)}{\UB(n)-\LB(n)}$, which can be reached, hence the equivalence.

### 2024-11-21 ICLR25/Paper_noProof.tex
rework

--- 2024-09-27 ICLR25/Paper_noProof.tex
@@
 In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in.
+capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \textcolor{blue}{\cite{crown}}.
 To simplify the notations, we restrict the presentation to feed-forward, 

### 2024-11-21 ICLR25/formula.tex
fix some typos
rework

@@
-\section{Important neurons for accuracy and Utility function.}
+\section{Utility function choosing neurons important for accuracy.}
 
-In this section, we evaluate how each neuron would impact the accuracy of encoding this neuron with an integer (actually binary) or a linear variable.
-We will say we open a neuron when this neuron is selected with a binary variable.
-We denote by $X$ a choice of set of open neurons, and by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
+\label{sec4}
 
-Let $z$ be a neuron of the DNN we want to evaluate, for instance computing an upper bound on the value it can take.
-We denote by $n < z$ the fact that a neuron $n$ appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
-Let us denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ 
-maximizing $z$. In particular, $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
+In this section, we evaluate how each neuron would impact the accuracy of encoding this neuron with a binary or a linear variable, using Proposition \ref{LP}.
+A neuron is {\em open} when it is represented as a binary variable.
+For $X$ a set of open neurons, we denote by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
 
-Consider ($\Sol\_\max_\emptyset^z(n))_{n \leq z}$ (this can be obtained very efficiently by {\em one} call to an LP solver). An accurate utility function is to evaluate 
-$\Improve\_\max^z(a)=$ $\Sol\_\max_\emptyset^z(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, 
-representing how much opening neuron $a < z$ reduces the maximum computed for $z$
+Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
+We write $n < z$ if neuron {\color{blue} $n$ is} on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
+We denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$.
+In particular, $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
+
+Consider $(sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
+%(this can be obtained very efficiently by {\em one} call to an LP solver).
+Function
+$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
+accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
 compared with using only LP. 
-We have $\Improve\_\max^z(a)\geq 0$ as $\Sol\_\max_{\{a\}}^z$ fullfils all the constraints of 
-$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{a\}}^z(z) \leq$ $\Sol\_\max_\emptyset^z(z)$.
+We have $\Improve\_\max^z(n)\geq 0$ as $\Sol\_\max_{\{n\}}^z$ fulfills all the constraints of 
+$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{n\}}^z(z) \leq \sol(z)$.
 Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
-$\Improve\_\min^z(a)$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
+$\Improve\_\min^z(n)$. Calling MILP on $\mathcal{M}_{\{n\}}$ for each neuron $n \leq z$
 would however be very time consuming when the number of neurons $a$ to evaluate is large.
-Instead, we focus on the following upper bounding of $\Improve\_\max^z(a)$.
+{\color{blue} 
+That's why as far as we know, in competing heuristics to rank important nodes (e.g. \cite{huang2017safety,crown}), no call to solvers are made.
+%Instead, we focus on the following $\Utility\_\max\nolimits^z(n)$ function upper bounding $\Improve\_\max^z(n)$. 
+The novelty of our Utility function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, which is very efficient and negligible wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes, as hinted by Proposition \ref{prop2}.
 
@@
 
-For all neurons $n$, let $\sol(n)=$$\Sol\_\max_\emptyset^z(n)$ be the value of neuron $a$
-in the solution of the LP instance $\Sol\_\max_\emptyset^z$ to maximize $z$.
+%For all neurons $n$, let $\sol(n)=$$\Sol\_\max_\emptyset^z(n)$ be the value of neuron $a$
+%in the solution of the LP instance $\Sol\_\max_\emptyset^z$ to maximize $z$.
 %For one layer before the target layer, the formula is simple and most accurate. 
-To estimate $\Improve\_\max^z(a)$, we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$, by computing by how much the value of $z$ will change if $a$ is opened
-and other values remain the same - in particular, $value(\hat{a})=\ReLU(sol(a))$. We define:
+%To estimate $\Improve\_\max^z(a)$,
+
+For a neuron $b$ on the layer before the layer $\ell_z$, we define:
+
+%we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$, by computing by how much the value of $z$ will change if $a$ is opened
+%and other values remain the same - in particular, $value(\hat{a})=\ReLU(sol(a))$. We define:
 %we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
-
-	$$\Utility\_\max\nolimits^z(a) = W_{az} \times (\sol(\hat{a})- \ReLU(\sol(a)))$$
+\vspace{-0.4cm}
+	$$\Utility\_\max\nolimits^z(b) = W_{bz} \times (\sol(\hat{b})- \ReLU(\sol(b)))$$
+\vspace{-0.4cm}
 
@@
 
-In the case $W_{az}<0$, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value, which is $\sol(\hat{a})=\ReLU(\sol(a))$ thanks to Prop.~\ref{LP}.
-In this case, we have $\Utility\_\max^z(a)=0$.
-Thus, we have $\Utility\_\max^z(a) \geq 0$ in all cases
-as $\sol(\hat{a}) \geq \ReLU(\sol(a))$ by Prop.~\ref{LP}. 
-We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}.
+Notice that if $W_{bz}<0$, the LP engine sets $\sol(\hat{b})$ to its minimal value
+to maximize $z$, which is $\sol(\hat{b})=\ReLU(\sol(b))$ thanks to Proposition~\ref{LP}. 
+In this case, we have $\Utility\_\max^z(b)=0$.
+Thus, we have $\Utility\_\max^z(b) \geq 0$ in all cases
+as $\sol(\hat{b}) \geq \ReLU(\sol(b))$ by Proposition~\ref{LP}.
+
+For a neuron a $a$ two layers before $\ell_z$, 
+$b$ denoting neurons in the layer $\ell$ just before $\ell_z$, 
+we define:
+
+\begin{align*}
+	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
+	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
+	\forall b \in \ell, \Delta(\hat{b}) &=
+	\begin{cases}
+		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
+		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
+		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
+	\end{cases}\\
+	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
+\end{align*}
+
+%We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}.
+
+Informally, $\Delta(\hat{a}), \Delta(b), \Delta(\hat{b})$ approximate the improvement on the accuracy of $\hat{a}, b, \hat{b}$ when computing $\ReLU(a)$ 
+using the exact MILP encoding instead of LP. Using Prop. \ref{LP}, we show:
+
+\begin{proposition}
+	\label{prop2}
+		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
+\end{proposition}
+
 Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$. 
@@
 this node will have the smallest $\Utility\_\max\nolimits^z(a)=0$ (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$.
-This is one stricking difference (but not the only one) with choosing utility based on
+This is one striking difference (but not the only one) with choosing utility based on
 $|W_{az}|$ \cite{DivideAndSlide}.
@@
 
-\medskip
+	\begin{proof}
+    Consider $\sol'(n)_{n \leq z}$ with
+	$\sol'(n)=\sol(n)$ for all $n \notin \{z,\hat{a}\} \cup \{b,\hat{b} \mid b \in \ell\}$. In particular,  $\sol'(a) = \sol(a)$.
+	Now, define $\sol'(\hat{a}) = \ReLU(\sol(a))$. 
+	That is, $\sol'(\hat{a})$ is the correct value for $\hat{a}$, obtained if we open neuron $a$, compared to the LP abstraction for $\sol(\hat{a})$.
+	We define $\sol'(b)=\sol(b)+\Delta(b)$ and 
+	$\sol'(\hat{b})=\sol(\hat{b}) + \Delta(\hat{b})$.
+	Last, $\sol'(z)=\sol(z) + \sum_{b \in \ell} W_{bz} \Delta(\hat{b})$.
+	We will show:
+	\begin{equation}
+		\label{eq12}
+		(\sol'(n))_{n \leq z} \text{ satisfies the constraints in } \mathcal{M}_{\{a\}}
+	\end{equation} 
+	This suffices to conclude: as
+	$\sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $\sol'(z) \leq$ $\Sol\_\max_{\{a\}}^z(z)$. That is, 
+	$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
+	$ \Utility\_\max^z(a) \geq \Improve\_\max^z(a)$.
+	In particular, we have that $\Utility\_\max^z(a) \geq 0$, which was not obvious from the definition.
 
-Now, consider neuron a $a$ two layers before $z$. We use $b$ to denote neurons in the layer $\ell$ between $a$ and $z$. 
+	Finally, we show (\ref{eq12}). First, opening $a$ changes the value of $\hat{a}$ from
+	$\sol(\hat{a})$ to $\ReLU(\sol(a)) = sol(\hat{a}) + \Delta(a)$, 
+	and from $sol(b)$ to $sol(b) + \Delta(b)$.
+	The case of $\Delta(\hat{b})$ is the most interesting:
+	If $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
+sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)} +$ Cst to maximize $z$.
+Changing $b$ by $\Delta(b)$ thus results in changing $\sol(\hat{b})$ by 
+$\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b)$.
+If $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
+If $\sol(b) < 0$, then we have $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ change the 0 value only if $\sol(b)+\Delta(b)>0$. If $\sol(b) > 0$, then 
+$\sol(\hat{b})=\ReLU(\sol(b))=\sol(b)$, and the change to $\hat{b}$ will be 
+the full $\Delta(b)$, unless $\Delta(b) < -\sol(b) < 0$ in which case it is 
+$-\sol(b)$.
+		\end{proof}
+	}
+
+	\iffalse
+
 	If we open $a$ without changing its value $\sol(a)$, then the change $\Delta(\hat{a})$ in the weight of $\hat{a}$ is 
@@
 $$ \Utility\_\max\nolimits^z(a) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})$$
-
-\begin{proposition}
-	\label{prop2}
-		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
-	\end{proposition}
-
-	\begin{proof}
-    Consider $\sol'(n))_{n \leq z})$ with
-	$\sol'(n)=\sol(n)$ for all $n \notin \{z,\hat{a}\} \cup \{b,\hat{b} \mid b \in \ell\}$. In particular,  $\sol'(a) = \sol(a)$.
-	Now, define $\sol'(\hat{a}) = \ReLU(\sol(a))$. 
-	That is, $\sol'(\hat{a})$ is the correct value for $\hat{a}$, obtained if we open neuron $a$, compared to the LP abstraction for $\sol(\hat{a})$.
-	We also define $\sol'(b)=\sol(b)+\Delta(b)$ and 
-	$\sol'(\hat{b})=\sol(\hat{b}) + \Delta(\hat{b})$.
-	Last, $\sol'(z)=\sol(z) + \sum_{b \in \ell} W_{bz} \Delta(\hat{b})$.
-	% = \sol(z) - \Utility\_\max\nolimits^z(a)$.
-
-	It is easy to check that $(\sol'(n))_{n \leq z}$ satisfies the constraints in 
-	$\mathcal{M}_{\{a\}}$, as opening $a$ changes the value of $\hat{a}$ from
-	$\sol(\hat{a})$ to $\ReLU(\sol(a))$, and the contribution from $a$ to $b,\hat{b},z$ 
-	are respected.
-	As $\sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $\sol'(z) \leq$ $\Sol\_\max_{\{a\}}^z(z)$. That is, 
-	$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
-	$ \Utility\_\max^z(a) \geq \Improve\_\max^z(a)$.
-	In particular, we have that $\Utility\_\max^z(a) \geq 0$, which was not obvious from the definition.
-	\end{proof}
+\fi
 

### 2024-11-21 ICLR25/introduction.tex
rework

@@
 answering correctly to an unperturbed input.
-For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct (the other $71\%$ are thus not even tested by $\alpha,\beta$-Crown).
+For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct {\color{blue}\cite{prima}} (the other $71\%$ are thus not  tested).
 While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.

### 2024-11-21 ICLR25/valabstraction.tex
rework

@@
 
-Consider the simpler abstraction, termed ``Box abstraction" \cite{deeppoly}: it inductively computes the bounds for each neuron in the subsequent layer independently.
+Consider the simpler abstraction, termed ``Box abstraction", {\color{blue} recalled e.g.
+in \cite{deeppoly}}: it inductively computes the bounds for each neuron in the subsequent layer independently.
 This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth.
@@
 
+{\color{blue} In \cite{DBLP_Ehlers17, deeppoly} and others, the {\em triangular abstraction} was proposed:
+\begin{align}
+	\ReLU(x) = max (0,x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} 
+	\label{eq:deeppoly}
+\end{align} 
+It has two lower bounds (the 0 and identity functions), and one upper bound. 
+DeepPoly \cite{deeppoly} chooses one of the two lower bounds for each neuron $x$, giving rise to a greedy quadratic-time algorithm to compute very fast an abstraction of the value of $\hat{x}$ (but not that accurately).
+}
+
 \subsection{MILP, LP and partial MILP encodings for DNNs}
@@
 
-$$\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\UB(n) \cdot (1-a)$$
+\vspace{-0.4cm}
+\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\UB(n) \cdot (1-a)
+\label{eq11}
+\end{equation}
 
@@
 An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.
-To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP abstraction.
+To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP relaxation of (\ref{eq11}).
+We obtain:
 
-Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$. 
-Let $x$ represent the input value of $n$, hence with 
-$\LB(n) < x < \UB(n)$, and $\hat{x}$ representing $\ReLU(x)$. 
-We have:
+%Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$. 
+%Let $x$ represent the input value of $n$, hence with 
+%$\LB(n) < x < \UB(n)$, and $\hat{x}$ representing $\ReLU(x)$. 
+%We have:
 
@@
 	\label{LP}
-	The LP relaxation on $\hat{x}$ is equivalent with:
-	\begin{align}
-		\ReLU(x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} \label{eq:deeppoly}
-	\end{align} 
+	{\color{blue} The LP relaxation of (\ref{eq11}) is equivalent with the triangular abstraction 	(\ref{eq:deeppoly}).}
 \end{proposition}
 
+{\color{blue}
+To the best of our knowledge, we could not find such an equivalence stated in the bibliography, although the proof is simple.
+This result will be instrumental for our Utility function (Section \ref{sec4}).}
+
 \begin{proof}
+	Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$.
 The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediatly equivalent with $\hat{x} \geq \ReLU(x)$.
@@
 \end{proof}
-
-Notice that this is close to the DeepPoly abstractions \cite{deeppoly}, but LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $\ReLU(x) \geq 0$ and $\ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.

### 2024-11-21 ICLR25/formula.tex
typo

@@
 %Instead, we focus on the following $\Utility\_\max\nolimits^z(n)$ function upper bounding $\Improve\_\max^z(n)$. 
-The novelty of our Utility function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, which is very efficient and negligible wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes, as hinted by Proposition \ref{prop2}.
+The novelty of our Utility function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, which is very efficient and negligible wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes, see Table \ref{tab:example1} and Proposition \ref{prop2} later.
 
@@
 Informally, $\Delta(\hat{a}), \Delta(b), \Delta(\hat{b})$ approximate the improvement on the accuracy of $\hat{a}, b, \hat{b}$ when computing $\ReLU(a)$ 
-using the exact MILP encoding instead of LP. Using Prop. \ref{LP}, we show:
+using the exact MILP encoding instead of LP. Using Proposition \ref{LP}, we show:
 

### 2024-11-25 ICLR25/Paper_noProof.tex
edit
about propositon 1

@@
 Enabling larger time-outs for $\alpha,\beta$-Crown only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
-Resorting to other techniques, such as complete verifiers, does not fare better even with very large time-outs: They would theoretically be able to close the gap, but with an untractable runtime on all but small {\em hard} instances.
+Resorting to slow complete verifiers, does not fare better even with very large time-outs: They would theoretically be able to close the gap, but with an untractable runtime on all but small {\em hard} instances.
 
-In this paper, we study the MILP encoding of ReLU-DNNs, and provide new insights in the LP relaxation.
-This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation.
+In this paper, {\color{blue}
+%we study the MILP encoding of ReLU-DNNs.
+%, and provide new insights in the LP relaxation. 
+we propose a novel Utility function that selects neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
+the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input. }
+%This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation. 
 Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
@@
 We tested twice outlier results to confirm them, making sure of reproducibility on the given hardware. Precise details on the settings used are provided in the appendix.
-Additional results are also provided in the appendix.
+Additional results {\color{blue}(e.g. ablation studies)} are also provided in the appendix.
 Tested DNNs as well as MNIST and CIFAR10 DataSet are freely available.
@@
 
-\newpage
+\bigskip
 

### 2024-11-25 ICLR25/introduction.tex
typo
about propositon 1

@@
 
-Our three main contributions address the challenges of verifying {\em hard} DNNs efficiently:
+{\color{blue} Our main contributions address the challenges of verifying {\em hard} DNNs efficiently:}
 \begin{enumerate}
-	\item  Our first contribution studies the {\em LP relaxation} of the exact MILP encoding of ReLUs.
+	%\item  Our first contribution studies the {\em LP relaxation} of the exact MILP encoding of ReLUs.
 {\color{blue} We establish in Proposition \ref{LP} its equivalence with the so-called "triangular abstraction"}.
 
-	\item {\color{blue} It allows us to choose through a novel Utility function 
-	few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP).
-Specifically, the novelty of Utility resides in the use of the solution to an (efficient) full LP call on the node $z$ we want to bound.
+	\item {\color{blue} We designed a novel Utility function to choose few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP).
+Specifically, the novelty of Utility resides in the use of the solution to an (efficient LP) solver on the node $z$ we want to bound.
 Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}).
-pMILP is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating $\approx 4$ times less integer variables for the same accuracy (Table \ref{tab:example1}), because Utility focuses on the solution local to the input, rather than on the DNN.
+pMILP is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating $\approx 4$ times less integer variables for the same accuracy
+	(Table \ref{tab:example1}), because Utility focuses on the solution local to the input, rather than on the DNN.
 To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g.

### 2024-11-25 ICLR25/valabstraction.tex
about propositon 1

@@
 An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.
-To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP relaxation of (\ref{eq11}).
-We obtain:
+To obtain a more accurate measure, that
+%can also scale to deeper layers and 
+is not limited to open nodes from the immediate previous layer, 
+{\color{blue} we invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:}
 
@@
 
-{\color{blue}
-To the best of our knowledge, we could not find such an equivalence stated in the bibliography, although the proof is simple.
+%{\color{blue}
+%To the best of our knowledge, we could not find such an equivalence stated in the bibliography, although the proof is simple.
 This result will be instrumental for our Utility function (Section \ref{sec4}).}

### 2024-11-26 ICLR25/introduction.tex
intro

@@
 Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}).
-pMILP is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating $\approx 4$ times less integer variables for the same accuracy
-	(Table \ref{tab:example1}), because Utility focuses on the solution local to the input, rather than on the DNN.
+Because pMILP focuses on the gain (binary - linear),
+	it is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})) than previous attempts, which consider the full contribution of a neuron.
 To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g.

### 2024-11-26 ICLR25/experiments.tex
exp
polish
fork of appendix. Please use proofsb.tex

@@
 The bounds for nodes of the first two layers are computed exactly using the full MILP encoding.
-We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our {\bf Utility} function, compared with a random choice, both for nodes exclusively from the previous Layer 2 or from both Layers 1 and 2.
-We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$ \cite{DivideAndSlide}, which is limited to the previous Layer 2.
+We report in Figure \ref{fig_table3} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our {\bf Utility} function, compared with a random choice, both for nodes exclusively from the previous Layer 2 or from both Layers 1 and 2.
+We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$ \cite{DivideAndSlide}, opening nodes in Layer 2 only.
 
+\iffalse
 \begin{table}[h!]	
 	\centering
-	\begin{tabular}{|c||c|c|c||c|c|}
+	\begin{tabular}{|c||c|c|c||c|c|c|}
 		\hline
-			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=61$}&\multicolumn{2}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-6}
-		\text{$|X|$}  & \text{Random} & \cite{ DivideAndSlide} & \bf Utility& \text{Random} &\bf Utility\\ \hline
+			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-7}
+		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} &BSR &\bf Utility\\ \hline
 		\hline
-		0  (LP) &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline \hline
-		5  &   1.729&1.704 & 1.603&  1.729&  \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.517& 1.696 & \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.466&  1.653& \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.438 & 1.619 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.427&  1.586 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.425& 1.546 & \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.424 & 1.502 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.424& 1.469 & \bf 0.921 \\ \hline \hline
-		max & 1.424  &1.424& 1.424 & 0.895 & 0.895   \\ \hline
+		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761\\ \hline \hline
+		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 &  \bf 1.532 \\ \hline
+		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& \bf  1.371\\ \hline
+		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& \bf  1.247\\ \hline
+		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & \bf  1.145\\ \hline
+		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & \bf 1.061\\ \hline
+		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& \bf  0.989 \\ \hline
+		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & \bf 0.934 \\ \hline
+		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& \bf 0.921 \\ \hline \hline
+		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895   \\ \hline
 	\end{tabular}
@@
 \end{table}
+\fi
 
@@
 Overall, choosing 35 neurons by {\bf Utility} improves accuracy by $95\%$ of what can be done if all $|X|=116$ nodes are opened compared with LP (corresponding to $|X|=0$).
+
+\begin{figure}[h!]
+	\centering
+	\vspace*{-0.3cm}
+	\includegraphics[height=7.5cm]{Plot for table 3}.
+	\vspace*{-0.4cm}
+	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
+	\label{fig_table3}
+\end{figure}
 

### 2024-11-26 ICLR25/proofsb.tex
fork of appendix. Please use proofsb.tex

\newpage

\section*{Appendix}

{\color{blue}
\section{Parameter settings}

\subsection*{Setting for $\alpha,\beta$-Crown}

The networks were already tested by $\alpha,\beta$-Crown \cite{crown}. We thus simply reused the parameter files from \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN/blob/main/complete_verifier/exp_configs/beta_crown/}{their Github}, 
except for time-out which we explicitly mention.

e.g., for CNN-B-Adv: "solver: batch size: 512 beta-crown: iteration: 20" and
for MNIST 5x100: "solver: batch size: 1024 beta-crown: iteration: 20".

We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to. From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-Crown on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP. The conclusion are thus unchanged.
}

\subsection*{Setting for Hybrid MILP}

Hybird MILP first call $\alpha,\beta$-Crown with short time-out (TO), then call partial MILP on those inputs which was neither certified nor falsified by this run of $\alpha,\beta$-Crown. We are using two settings of TO, for smaller DNNs we use T0$=10s$, and for the two larger ones, we use TO$=30s$.

The setting for partial MILP for fully-connected DNNs is about how many neurons need to be opened (once set, the selection is automatic). The runtime depending crucially upon the number of open ReLU neurons, we set it quite tightly, only allowing few neuron deviation to accommodate to a particularly accurate/inaccurate bound computation (measure by the weight of the remaining Utility function). As complexity increases with the layer considered, as the size of the MILP model grows, we lower this number with the depth, only committing to an intermediate number for the output neuron (the number of output neurons  is smaller than hidden layer, and this is the most important computation). We experimentally set this number so that each computing the bounds in each hidden layer takes around the same time. Remember that in layer 1, partial MILP is not necessary and propagating bounds using interval arithmetic is already exact. We open [48,48] to compute bounds for hidden layer 2, [21,24] for layer 3, [11,14] for layer 4, [6,9] for layer 5, [3,6] for layer 6, [2,5] for layer 7, [1,4] for hidden layer 8 (if any), and we open [14,17] for the output layer.
{\color{blue} The exact number of open nodes in the range [a,a+3] is decided automatically for each neuron being computed : ReLUs are ranked according to their value by Utility, and the a top ReLUs are open. Then, ReLUs ranked a+1,a+2, a+3 are opened if their Utility value is larger than a small threshold. We set the threshold at 0.01. It should be seen as a way to save runtime when Utility knows that the next node by ranking (a+i) will not impact accuracy much (thanks to the upper bound from Proposition \ref{prop2}).}

\begin{table}[b!]
	\centering
	\begin{tabular}{||l||c|c||}
		\hline \hline
		Network & TO for $\alpha,\beta$-Crown  & Minimum number of Open neurons  \\ 		  
		\hline
		MNIST $5 \times 100$ & 10s  & 48,21,11,6,14  \\ \hline
		MNIST $5 \times 200$ & 10s & 48,21,11,6,14  \\ \hline
		MNIST $8 \times 100$ & 10s  & 48,21,11,6,3,2,1,14  \\ \hline
		MNIST $8 \times 200$ & 10s & 48,21,11,6,3,2,1,14  \\ \hline
		MNIST $6 \times 500$ & 30s & 48,21,11,6,3,14 \\ \hline
		CIFAR CNN-B-adv & 30s & 200, 0, 45 \\ \hline \hline
	\end{tabular}
	\caption{Settings of Hybrid MILP for the different {\em hard} instances}
	\label{table20}
	\end{table}

For convolutional CNNs, the strategy is adapted, as there is much more neurons, but in a shallower architecture and not fully connected. 
The second layer is computed accurately, opening 200 neurons, which is manageable as there is only one ReLU layer to consider, and accuracy here is crucial.
We do not open any nodes in the third layer (the first fully connected layer) if the output layer is the next one (which is the case for CNN-B-Adv), and instead rely on the choice of important nodes for the output layer. Otherwise, we open 20 neurons.
In the output layer, we open at least 45 neurons (there is less output neurons than nodes in the previous layer), and enlarge the number of open neurons (up to 300) till we find an upper bound, that is a best current MILP solution, of around +0.1 (this 0.1 was experimentally set as target, a good balance between accuracy and efficiency), and compute a guaranteed lower bound (the goal is to guarantee the bound is $>0$).

In Table \ref{table20}, we sum-up the TO and minimum open numbers for each DNN considered.

{\color{blue}
$\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU, while Partial MILP uses 20 CPU-threads.}

Notice that a different balance between accuracy and runtime could be set. For instance, we set up the numbers of open neurons to have similar runtime as Refined $\beta$-Crown for the first 4 DNNs ($50s-100s$). We could easily target better accuracy (e.g. for $8 \times 100$ with a relatively high $15\%$ undecided images) by increasing the number of open neurons, with a trade-off on runtime (current runtime is at $61s$).
By comparison, the sweet spot for $\alpha,\beta$-Crown seems to be around TO$=30s$, enlarging the time-out having very little impact on accuracy but large impact on runtime
(Table \ref{table_beta}).

{\color{blue}
Last, for Gurobi, we use a custom MIP-Gap (from $0.001$ to $0.1$) and time-out parameters, depending on the seen improvement and the possibility to make a node stable. This is low level implementation details that will be available in the code once the paper is accepted.
}

{\color{blue}

\section{Pseudocode and Complexity Analysis}

We first provide the pseudo code for pMILP in Algorithm \ref{algo1}.

\SetKwInput{KwInput}{Input}
\SetKwInput{KwOutput}{Output}

\begin{algorithm}[h!]
	\caption{pMILP($K$)}
	\label{algo1}
	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}

	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}

	\For{layer $k=1 \cdots \ell$}{
		\For{neuron $n$ in layer $k$}{

			Compute $X$ a set of $K$ nodes with the highest Utility for target neuron $n$.

			Run MILP$_X$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
		}
	}
\end{algorithm}

%We then analyse its complexity.
%First, notice that the complexity to rnu Utility is negligible wrt the Run MILP$_X$.

pMILP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound. Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$. 
%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
%pMILP uses 20 threads.

If $K$ is sufficiently small, 
%Algorithm \ref{algo1} invokes many MILP (e.g., using Gurobi) with a manageable number of %integer variables. 
this approach is expected to be efficient. 
The crucial part is thus to find few neurons which are particularly important when computing neuron $n$. This is where our novel Utility function outperforms previous solutions, by using an call to an (LP) solver to obtain a solution, which is novel as far as we know. This solutions allows to optimizing the choice of open nodes for the particular input considers, and appears significantly better than previous attempts, explaining the efficiency of the method.

For comparison, refined $\beta$-Crown and refined Prima used all the nodes up to a certain layer as binary variables, which is particularly inefficient, see Table \ref{table12} and Fig. \ref{fig4}. Hence, it can only be applied to small DNNs (it is implemented only up to MNNIST 8x200), while pMILP scales to at least 20.000 neurons (CNN-B-Adv).
\cite{DivideAndSlide} is the closest to pMILP, also implementing a choice of nodes as binary variables. However, their choice is particularly inefficient, as revealed by Table  
\ref{tab:example1}, needing 4 times the number of open nodes for the same accuracy as our Utility function.

\section{Ablation studies}

In this section, we consider ablation studies to understand how each feature enables the efficiency of pMILP.

\subsection*{Time scaling with open nodes}

First, we explore the time scaling with different number of open nodes, for our full Utility function using nodes in the last two layers (Layer 1 and 2), providing finer details than in Table 3, with the same setting, i.e. previous layer being computed with full MILP.

\begin{table}[h!]
		\centering
		\hspace*{4ex}
		\begin{subtable}[b]{0.45\textwidth}
		\begin{tabular}{|c|c|c|}
		\hline
		$|X|$ & Time & Uncertainty\\ 
		\hline	0 & 2.6 & 1.760946128\\
		\hline	1 & 7.3 & 1.702986873\\
		\hline	2 & 11.1 & 1.65469034\\
		\hline	3 & 16.3 & 1.612137282\\
		\hline	4 & 15.5 & 1.571001109\\
		\hline	5 & 15.7 & 1.531925404\\
		\hline	6 & 15.8 & 1.49535638\\
		\hline	7 & 16.4 & 1.46189314\\
		\hline	8 &  15.8 & 1.4299535\\
		\hline	9 &  17.2 & 1.4006364\\
		\hline	10 & 22.5 & 1.3711203\\
		\hline	11 & 27.2 & 1.3438245\\
		\hline	12 & 21.6 & 1.3183356\\
		\hline	13 & 28.7 & 1.2938690\\
		\hline	14 & 29.6 & 1.2690507\\
		\hline	15 & 24.5 & 1.2475106\\
		\hline
	  \end{tabular}
	\end{subtable}
	\hfill
	\begin{subtable}[b]{0.45\textwidth}
		\begin{tabular}{|c|c|c|}
			\hline
			$|X|$ & Time & Uncertainty\\ 
		\hline	16 & 31.9 & 1.2243065\\
		\hline	17 & 28.6 & 1.2031791\\
		\hline	18 & 30.4 & 1.1839474\\
		\hline	19 & 34.0 & 1.1644653\\
		\hline	20 & 42.1 & 1.1456181\\
		\hline	21 & 47.6 & 1.1261252\\
		\hline	22 & 62.7 & 1.1089745\\
		\hline	23 & 70.0 & 1.0931242\\
		\hline	24 & 70.8 & 1.0773088\\
		\hline	25 & 139.9 & 1.060928\\
		\hline	26 & 154.2 & 1.045715\\
		\hline	27 & 213.1 & 1.030605 \\
		\hline	28 & 211.3 & 1.016058\\
		\hline	29 & 373.1 & 1.001374\\
		\hline max=116 & 3300 & 0.895\\ 
		\hline		
	  \end{tabular}
     \end{subtable}
	  \caption{Time and uncertainty scaling of pMILP with number of nodes.}
    	\label{table14}
\end{table}

\begin{figure}[b!]
	\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Layer3_comparison}.
	\caption{Time and uncertainty scaling of pMILP with number of nodes.
	Time is using logscale.}
	\label{fig3}
\end{figure}

The exponential complexity with the number of nodes can be seen on Figure \ref{fig3}, where time is represented using logarithmic scale. The flat area in the middle is Gurobi having good heuristic to avoid considering all $2^K$ cases when $K<21$ is not too large, but not working so well for $K>25$. Notice that when certifying, pMILP uses $|X| \in$ 21-24, which is a good trade off between time and accuracy.

\subsubsection*{Usefulness of computing previous layers accurately}

Then, we explore the usefulness of computing accurately each layer inductively.
For that, we keep the setting of Table 3 and Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.

\begin{figure}[t!]
	\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
	\caption{Time and uncertainty scaling of table \ref{table15}.
		Time is using logscale.}
	\label{fig3LP}
\end{figure}

\begin{table}[h!]
	\centering
\begin{tabular}{|c|c|c|c|}
	\hline
	$|X|$ & Time &  With LP for layer 2 & With MILP for layer 2 \\ 
	\hline	5 & 9.3 & 3.24737  &1.532\\
	\hline	10 & 10.6 & 3.02214 & 1.371\\
	\hline	15 & 11.9 & 2.82383  &1.247\\
	\hline	20 & 13.1 & 2.63862 & 1.145\\
	\hline	25 & 16.0 & 2.47324 & 1.061\\
	\hline	30 & 28.3 & 2.32793  &0.989\\
	\hline	35 & 48.1 & 2.19506 & 0.934\\
	\hline	40 & 89.4 & 2.07107 & 0.921\\	
	\hline

\end{tabular}
\caption{Comparison of accuracy in layer 3 from computing layer 2 inaccurately using LP vs (from computing layer 2 accurately using MILP)}
\label{table15}
\end{table}

This experiment explains the rationale to use divide and conquer protocol, using many calls
(one for each neuron) with relatively small number $|X|$ of open nodes rather than fewer calls to MILP with larger number $|X|$ of open nodes. This is clear already with only 1 layer before.

%		\begin{figure}[h]\hspace*{-1cm}
%		\includegraphics[scale=0.6]{Layzr3_comparison.png}.
%		\caption{Comparison of layer3 when layer 1 is MILP or LP}
%\label{fig4}
%	\end{figure}

\subsubsection*{restricting number of open nodes (pMILP) vs setting time-outs (full MILP)}

Running full MILP till a small MIP-Gap (typically 0.001) is reached is extremely time inefficient.

Instead, the standard strategy is to set a reasonable time-out and use whatever bound has been generated. We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.

\begin{figure}[t]\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Layer7_comparison.png}.
	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
	\label{fig4}
\end{figure}

\begin{table}[h!]
	\centering
	\hspace*{4ex}
\begin{subtable}[b]{0.45\textwidth}
	\centering
		\begin{tabular}{|c|c|c|}
	\hline
		$|X|$ & Time & Uncertainty\\ 
	\hline1 &	14 & 3.233021901\\
\hline	2 & 15.2 & 3.140309921\\
\hline	3 & 17.21 & 3.059083103\\
\hline 4 &	17.4 & 2.986166762\\
\hline	5 &19.2 & 2.856229765\\
\hline	6 &20.9 & 2.799248232\\
\hline	7 &23.7 & 2.746167245\\
\hline	8 &26.6 & 2.69485246\\	
	\hline
	\end{tabular}
	\caption{pMILP}
\end{subtable}
\hfill
\begin{subtable}[b]{0.45\textwidth}
	\centering
		\begin{tabular}{|c|c|}
		\hline
		Time & Uncertainty\\ 
		\hline	21.1 & 3.348236261\\
		\hline	27.6 & 3.24604282\\
		\hline	38.2 & 3.196640184\\
		\hline	47.1 & 3.164298172\\
		\hline	56.7 & 3.146913614\\
		\hline	106.7 & 3.108035223\\
		\hline	156.3 & 2.900438725\\
		\hline	205.8 & 2.848648426\\	
		\hline	406.7 & 2.800268264 \\	
		\hline	606.1 & 2.737064255\\	
		\hline
	\end{tabular}
		\caption{full MILP}
\end{subtable}
	\caption{Comparison of bounding the number of nodes for pMILP and 
	using different time outs for full MILP. In both settings, lower and upper bounds of previous layers are the same (computed by pMILP).}
	\label{table12}
	\end{table}

pMILP obtains 2.8 accuracy in $<21$ seconds (with 7 open nodes), while full MILP needs 400 seconds to obtain it, a 19x speed up. For 2.7 accuracy, the speedup is $>>$ 22.

Figure \ref{fig4} shows that choosing nodes is much more efficient for time/accuracy trade-off than setting time outs and use full MILP. And this is for the smallest DNN we considered (500 hidden neurons, far from the biggest 20k neuron DNN we experimented with)

}

\subsection{Table for Figure \ref{fig_table3}}

Finall, we provide the table corresponding to the Figure \ref{fig_table3}

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-7}
		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} &BSR &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 &  \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}

\section{Comparison with other DNN verifiers}

In the following, we provide results comparing $\alpha,\beta$-Crown to other verifiers, to justify our use of $\alpha,\beta$-Crown as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.

\subsection*{Comparison $\alpha,\beta$-Crown vs PRIMA}

\begin{table}[b!]
	\centering
	\begin{tabular}{||l||c|c||c||}
		\hline \hline
		Network & $\alpha,\beta$-Crown & Refined $\beta$-Crown & PRIMA \\ 		  
		\hline
		MNIST $5 \times 100$ & N/A  & 14.3\% (102s) & 33.2\% (159s)\\ \hline
		MNIST $5 \times 200$ & N/A & 13.7\% (86s) & 21.1\% (224s) \\ \hline
		MNIST $8 \times 100$ & N/A  & 20.0\% (103s) & 39.2\% (301s)   \\ \hline
		MNIST $8 \times 200$ & N/A & 17.6\% (95s) & 28.7\% (395s)  \\ \hline
		MNIST $6 \times 500$ & 51\% (16s) & $-$ & 64\% (117s) \\ \hline
		CIFAR CNN-B-adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
		CIFAR ResNet & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves. N/A means that \cite{crown} did not report the numbers, while $-$ means that Refined $\beta$-Crown cannot be run on these DNNs.}
	\label{table9}
	%\begin{tablenotes}
	%	\footnotesize
%		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
%		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
%		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
%	\end{tablenotes}
	\end{table}

	PRIMA \cite{prima} is a major verifier in the ERAN toolkit. In Table \ref{table9}, we report the comparison between PRIMA and $\alpha,\beta$-Crown, mainly from \cite{crown}. The setting is mainly similar from ours, but numbers are not perfectly comparable as the images tested are not  exactly the same (1000 first or 200 first images for CNN-B-Adv), vs 100 first in Tables \ref{table_hybrid}, \ref{table_beta}. Also, time-out settings and hardware are slightly different. The overall picture is anyway the same.

Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-Crown. However, it is slower and less accurate than Refined $\beta$-Crown.
On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-Crown, while the runtime is $>5$ times larger.
Hence, Hybrid MILP is more accurate than Prima with similar runtime or faster.

Notice that kPoly \cite{kpoly}, OptC2V \cite{optC2V}, SDP-FO \cite{SDPFI} numbers were also reported in \cite{crown} on these networks, with even more unfavorable results.

\subsection*{Comparison $\alpha,\beta$-Crown vs MN-BaB}

MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-Crown. Results in \cite{ferrari2022complete}
are close to those of $\alpha,\beta$-Crown. However, none of the {\em hard} networks from \cite{crown} that we consider have been tested. We thus tested three representative {\em hard} DNNs (first 100 images) to understand how MN-BaB fairs on such hard instances, and report the numbers in Table \ref{table10}. Results are directly comparable with Table \ref{table_hybrid}.

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c|c||c|c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & MN-BaB & MN-BaB \\ 
		 Network & TO=30s & TO=2000s &  TO=30s & TO=2000s \\ 
		\hline
		MNIST $5 \times 100$ & 55\% (19s) & 50\%(1026s) & 60\% (19s) & 50\% (1027s) \\ \hline
		MNIST $6 \times 500$ & 51\% (16s) & 50\% (1002s) & 58\% (18s) & 55\% (1036s) \\ \hline
		CIFAR CNN-B-adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, and MN-BaB}
	\label{table10}
\end{table}

Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-Crown. Notice the specially high number of undecided images for CNN-B-Adv with TO=30s, probably meaning that 30s is too small for MN-BaB on this large DNN.
Hence, Hybrid MILP is more accurate than MN-BaB with similar runtime or faster.

	\subsection*{Comparison $\alpha,\beta$-Crown vs NNenum}

NNenum \cite{nnenum} is a complete verifier with good performance according to VNNcomp.
It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-Crown. The experiments section in \cite{nnenum} does not report
the {\em hard} DNNs we are considering. We tried to experiment it on the same MNIST 
$6 \times 500$ and CIFAR CNN-B-adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-Crown, on both 
MNIST $5 \times 100$ and CIFAR CNN-B-Adv. 
On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-Crown, but far from the accuracy Hybrid MILP.
On CIFAR CNN-B-adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c||c||c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & NNenum & Hybrid\\ 
		 Network & TO=2000s &  TO=2000s & MILP\\ 
		\hline
		MNIST $5 \times 100$ & 50\%(1026s) & 44\% (1046s) & \bf 13\% (46s)\\ \hline
		CIFAR CNN-B-adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown and NNenum with 2000s time-out, and Hybrid MILP}.
	\label{table11}
\end{table}

{\color{blue}

\section{Average vs max time per pMILP call}

We provide in Table \ref{table112} the average as well as maximum time to perform $MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
For 6x500, we provide results for two different $\varepsilon$, following our test from Figure \ref{fig2}.

\begin{table}[h!]
	\centering
	\begin{tabular}{||l|c|c||}
		\hline
		Network & average time & maximum time \\ \hline
		MNIST 5$\times$100 & 0.41s & 1.87 \\
		$\epsilon = 0.026$ &  & \\  \hline
		MNIST 5$\times$200 &  0.75s & 5.31s \\ 
		$\epsilon = 0.015$ & & \\  \hline
		MNIST 8$\times$100 & 0.39s & 1.41s \\
		$\epsilon = 0.026$ & &  \\  \hline
		MNIST 8$\times$200 & 0.49s & 1.63s \\ 
		$\epsilon = 0.015$ & & \\  \hline
		MNIST 6$\times$500 & &   \\ 
		$\epsilon = 0.035$ & 1.4s & 3.5s \\ 
		$\epsilon = 0.1$ & 44.6s & 310s \\  \hline 
		CIFAR CNN-B-adv &  & \\
		$\epsilon = 2/255$& 1s & 609s \\ \hline \hline
	\end{tabular}
	\caption{average and maximum time per $\MILP_X$ calls for image 3 (MNIST) and image 76 (CIFAR10).}
	\label{table112}
\end{table}

Notice that DNN 6$\times$ 500 and $\epsilon=0.1$ is a very hard instance as being very close to the falsification $\epsilon \approx 0.11$. This is thus not representative of the average case. Also,  on this image 3, pMILP succeeds to verify $\epsilon= 1.054$, while $\alpha,\beta$-CROWN can only certify $\epsilon = 0.0467$ within the 10 000s Time-out.

For CNN-B-Adv, the very long maximum time for a MILP call is an outlier: it happens only for one output layer, for which the number $K$ of open nodes is particularly large (around 200 out of 20000 neurons) to certify this hard image 76. Indeed, the average time is at $1s$. Notice that this does not lead to a runtime of 20.000s, as 20 threads are used by pMILP 
in parallel (similar to competing solutions, except $\alpha,\beta$-CROWN which uses $>4096$ GPU cores).

}

\section{SR Heuristic for choosing nodes}

Here we provide the formula of BaB-SR from paper \cite{BaB}.

\begin{align*}
	\nu_{n+1} &= -1&\\
	\hat{\nu}_k &= W^T_kv_{k+1}, k = n,\cdots,1 &\\
	\nu_{k,j} &= \begin{cases}
		0  &\text{ if }u_{k[j]}<0 \hspace*{2ex}(j\in\mathcal{I}^-_k)\\
		\hat{\nu}_{k[j]} &\text{ if }l_{k[j]}>0 \hspace*{2.5ex}(j\in\mathcal{I}^-_k)\\
		\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_-  &\text{ otherwise } \hspace*{3ex}(j\in\mathcal{I}_k)\\ 
	\end{cases}\\
	&\hspace*{22ex}\text{for } k = n,\cdots,2&
\end{align*}and\begin{align*}
	s_{i[j]} = |\max(v_{i[j]}b_{i-1[j]},(v_{i[j]}-1)b_{i-1[j]})-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+|
\end{align*}

\end{document}

\subsection*{Formula for ResNet}

Consider a ResNet, like ResNet4b, we list the formula for an Add layer.

Suppose we are dealing with an Add layer $l$, target node $z$, with previous layer $l_1$ and shortcut connection previous layer $l_2$, starting from a layer $l_0$, that is:
\begin{align*}
	l &= l_1+l_2\\
	l_2 &= Conv_{W_2}(\ReLU(l_0))\\
	l_1' &= Conv_{W'_1}(\ReLU(l_0))\\
	l_1 &= Conv_{W_1}(\ReLU(l'_{1}))
\end{align*}The paths are $$l_0\rightarrow \ReLU(l_0)\rightarrow l_2\rightarrow l,$$ and $$l_0\rightarrow \ReLU(l_0)\rightarrow l'_1\rightarrow \ReLU(l_1')\rightarrow l_1\rightarrow l.$$

So, for nodes in layer $l_1'$, we can use the same formula as previous section, i.e., the formula at the end of page 6: for a node $b$ in $l_1'$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$, 
\begin{align*}
\Utility\_\max\nolimits^x(b) &= W_{bx} \times (\sol(\hat{b})- \ReLU(\sol(b)))\\
\Utility\_\max\nolimits^z(b) &= \Utility\_\max\nolimits^x(b)
\end{align*}

For nodes in layer $l_0$, the simple idea is to consider both paths, and sum up the utilities of two paths. For a node $a$ in $l_0$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$ ,
\begin{align*}
		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
		\Utility_\_\max\nolimits^y(a) &= -W_{ay} \Delta(\hat{a})\\
	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
	\forall b \in \ell, \Delta(\hat{b}) &=
	\begin{cases}
		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bx} > 0\\
		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)\geq0\\
		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)<0		 
	\end{cases}\\
	\Utility\_\max\nolimits^x(a) &= -\sum_{b \in \ell} W_{bx} \Delta(\hat{b})\\
	\Utility\_\max\nolimits^z(a) &= \Utility\_\max\nolimits^x(a)+\Utility\_\max\nolimits^y(a)
\end{align*}

\section{Formula for Utility}

Recall that for nodes $a,b$, we use 
$\hat{a}, \hat{b}$ to denote variable after ReLU functions, and
$\Delta(a),\Delta(\hat{a}),\Delta(b),\Delta(\hat{b})$ to denote the changes of those variables. $a$ means the source node, and $b$ means nodes one layer after $a$, and $z$ is 2 layers after $a$ and one after $b$.

The utility function for a node $a$ wrt neuron $z$ is defined inductively as follows:

\begin{align*}
	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
	\Delta(b) &= W_{ab}\Delta(\hat{a})\\
	\Delta(\hat{b}) &=
	\begin{cases}
		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
	\end{cases}\\
	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
\end{align*}

}

### 2024-11-26 ICLR25/proofsb.tex
update

@@
 
-\begin{figure}[t!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
-	\caption{Time and uncertainty scaling of table \ref{table15}.
-		Time is using logscale.}
-	\label{fig3LP}
-\end{figure}
-
 \begin{table}[h!]
@@
 
+\begin{figure}[b!]
+	\hspace*{-0.8cm}
+	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
+	\caption{Time and uncertainty scaling of table 7.
+		Time is using logscale.}
+	\label{fig3LP}
+\end{figure}
+
 This experiment explains the rationale to use divide and conquer protocol, using many calls
@@
 We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.
-
-\begin{figure}[t]\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer7_comparison.png}.
-	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
-	\label{fig4}
-\end{figure}
 
@@
 
+\begin{figure}[h]\hspace*{-0.8cm}
+	\includegraphics[scale=0.6]{Layer7_comparison.png}.
+	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
+	\label{fig4}
+\end{figure}
+
 Figure \ref{fig4} shows that choosing nodes is much more efficient for time/accuracy trade-off than setting time outs and use full MILP.
@@
 }
-
-\subsection{Table for Figure \ref{fig_table3}}
-
-Finall, we provide the table corresponding to the Figure \ref{fig_table3}
-
-\begin{table}[h!]	
-	\centering
-	\begin{tabular}{|c||c|c|c||c|c|c|}
-		\hline
-			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-7}
-		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} &BSR &\bf Utility\\ \hline
-		\hline
-		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761\\ \hline \hline
-		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 &  \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& \bf 0.921 \\ \hline \hline
-		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895   \\ \hline
-	\end{tabular}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
-	\label{tab:example1}
-	%\vspace{-0.6cm}
-\end{table}
 
@@
 
-\section{SR Heuristic for choosing nodes}
-
-Here we provide the formula of BaB-SR from paper \cite{BaB}.
+Here we cite the formula of BaBSR from paper \cite{BaB}.
 
@@
 \end{align*}
+
+\begin{figure}[b!]
+	\hspace*{-0.8cm}
+	\includegraphics[scale=0.6]{Plot for table 3}.
+	\caption{Plot for table 3}
+	\label{fig_table3}
+\end{figure}
+
+\begin{table}[h!]	
+	\centering
+	\begin{tabular}{|c||c|c|c|c|}
+		\hline
+		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
+		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
+		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
+		5  & 1.729& 1.7138 &  &\bf 1.532 \\ \hline
+		10  & 1.696 & 1.6775& &\bf  1.371\\ \hline
+		15  &   1.653& 1.6392& &\bf  1.247\\ \hline
+		20  &   1.619 &1.5938 & &\bf  1.145\\ \hline
+		25  &    1.586 &1.5534 & &\bf 1.061\\ \hline
+		30  &  1.546 & 1.5166& &\bf  0.989 \\ \hline
+		35  &   1.502 & 1.4788 & &\bf 0.934 \\ \hline
+		40  &  1.469 & 1.4395& &\bf 0.921 \\ \hline \hline
+		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
+	\end{tabular}
+	\caption{BSR and FSB}
+	\label{BSRandFSB}
+	%\vspace{-0.6cm}
+\end{table}
 

### 2024-11-26 ICLR25/proofsb.tex
update

@@
 		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
-		5  & 1.729& 1.7138 &  &\bf 1.532 \\ \hline
-		10  & 1.696 & 1.6775& &\bf  1.371\\ \hline
-		15  &   1.653& 1.6392& &\bf  1.247\\ \hline
-		20  &   1.619 &1.5938 & &\bf  1.145\\ \hline
-		25  &    1.586 &1.5534 & &\bf 1.061\\ \hline
-		30  &  1.546 & 1.5166& &\bf  0.989 \\ \hline
-		35  &   1.502 & 1.4788 & &\bf 0.934 \\ \hline
-		40  &  1.469 & 1.4395& &\bf 0.921 \\ \hline \hline
+		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
+		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
+		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
+		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
+		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
+		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
+		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
+		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
 		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline

### 2024-11-26 ICLR25/proofsb.tex

@@
-\newpage
+\vspace{-0.6cm}
 
@@
 
-We first provide the pseudo code for pMILP in Algorithm \ref{algo1}.
-
 \SetKwInput{KwInput}{Input}
@@
 
+We provide the pseudo code for pMILP in Algorithm \ref{algo1}.
 pMILP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
@@
 
+We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
+Further, we tested with the SR  and FSB heuristics \cite{BaB} to choose important nodes for BaB (Branch and Bound).
+SR and FSB result in particularly low accuracy, even worse than \cite{DivideAndSlide} which only focus on neurons one layer before, and far away from Utility.
+FSB is also performing worse than SR when choosing nodes for pMILP, while for BaB, it is the opposite situation.
+This means that the heuristic to choose nodes important for BaB is not adapted to choose nodes for pMILP, although \cite{DivideAndSlide} heuristic is also choosing neurons based on importance of neurons for the consider ReLU.
+
+\begin{table}[h!]	
+	\centering
+	\begin{tabular}{|c||c|c|c||c|c|c|c|}
+		\hline
+			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-8}
+		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
+		\hline
+		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
+		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 & 1.7182 & \bf 1.532 \\ \hline
+		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& 1.6803 & \bf  1.371\\ \hline
+		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& 1.6475 & \bf  1.247\\ \hline
+		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & 1.6174 & \bf  1.145\\ \hline
+		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & 1.5788 & \bf 1.061\\ \hline
+		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& 1.5413 & \bf  0.989 \\ \hline
+		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & 1.4972 & \bf 0.934 \\ \hline
+		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& 1.4514 & \bf 0.921 \\ \hline \hline
+		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
+	\end{tabular}
+	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs SR vs FSB vs random choice.}
+	\label{tab:example1}
+	%\vspace{-0.6cm}
+\end{table}
+
+\newpage
+
 \subsubsection*{Usefulness of computing previous layers accurately}
@@
 Then, we explore the usefulness of computing accurately each layer inductively.
-For that, we keep the setting of Table 3 and Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
+For that, we keep the setting of Figure \ref{fig3} / Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
+
+\begin{figure}[h!]
+	\hspace*{-0.8cm}
+	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
+	\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.
+	Time is using logscale.}
+	\label{fig3LP}
+\end{figure}
 
@@
 	\hline	
-
 \end{tabular}
-\caption{Comparison of accuracy in layer 3 from computing layer 2 inaccurately using LP vs (from computing layer 2 accurately using MILP)}
+\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.}
 \label{table15}
 \end{table}
-
-\begin{figure}[b!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
-	\caption{Time and uncertainty scaling of table 7.
-		Time is using logscale.}
-	\label{fig3LP}
-\end{figure}
 
@@
 
+\newpage
+
 \subsubsection*{restricting number of open nodes (pMILP) vs setting time-outs (full MILP)}
@@
 We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.
+
+\begin{figure}[h!]\hspace*{-0.8cm}
+	\includegraphics[scale=0.6]{Layer7_comparison.png}.
+	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
+	\label{fig4}
+\end{figure}
 
@@
 
-\begin{figure}[h]\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer7_comparison.png}.
-	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
-	\label{fig4}
-\end{figure}
-
 Figure \ref{fig4} shows that choosing nodes is much more efficient for time/accuracy trade-off than setting time outs and use full MILP.
 And this is for the smallest DNN we considered (500 hidden neurons, far from the biggest 20k neuron DNN we experimented with)
-
-}
 
@@
 
-Here we cite the formula of BaBSR from paper \cite{BaB}.
+\end{document}
+
+\section{SR Heuristic for choosing nodes}
+
+Here we provide the formula of BaB-SR from paper \cite{BaB}.
 

### 2024-11-26 ICLR25/Paper_noProof.tex
fork of appendix. Please use proofsb.tex
full pass

@@
 %, and provide new insights in the LP relaxation. 
-we propose a novel Utility function that selects neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
+we propose a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
 the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input. }
@@
 \section{Conclusion}
-
-In this paper, we studied the LP relaxation of the exact MILP encoding of ReLU-DNNs.
-It allowed us to accurately assess when the relaxation of a node impacts very little 
-the accuracy, and when it impacts the accuracy importantly, in which case representing it with a binary/integer variable is preferable.
-This allows us to select a small set of important neurons to encode as a binary variables, improving accuracy drastically.
-Our automated choice of opened neurons necessitates $>4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
-Our empirical studies revealed that Hybrid MILP, can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp), with the same runtime.
-The reason is that $\alpha,\beta$-Crown can scale to large easy DNNs, but does not scale to 
-hard even small DNNs: it hits a complexity barrier, similarly as other compeating solutions.
+{\color{blue}
+In this paper, we developed a novel Utility function to select few ReLU nodes to consider with binary variables to compute accurately bounds on neurons of DNNs.
+The novelties are that it focuses on {\em improvement} wrt a given input, rather than on generic {\em sensitivity} of a neuron wrt to a ReLU node, and it uses the solution of one call to an (efficient LP) solver to evaluate this improvement.
+This makes the choice particularly efficient, necessitating $\approx4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy.}
+Our empirical studies revealed that this can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp), with the same runtime, for DNNs with up to 20 000 neurons.
+The reason is that $\alpha,\beta$-Crown hits a complexity barrier, similarly as other competing solutions, when considering hard (even small) DNNs.
 This opens a lot of perspectives, among which: verifying efficiently other hard instances; certifying $\epsilon$-robustness of images for $\epsilon$ as large as possible;
@@
 
-\input{proofs}
+\input{proofsb}
 

### 2024-11-26 ICLR25/experiments.tex
full pass

@@
 
-We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
+We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier to date, and to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
 
-Notice that results for several other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN.
+Notice that results for other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN.
 Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd

### 2024-11-26 ICLR25/formula.tex
full pass

--- 2024-11-21 ICLR25/formula.tex
@@
 
-In this section, we evaluate how each neuron would impact the accuracy of encoding this neuron with a binary or a linear variable, using Proposition \ref{LP}.
-A neuron is {\em open} when it is represented as a binary variable.
-For $X$ a set of open neurons, we denote by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
+In this section, we evaluate how each ReLU would impact the accuracy if encoded as a binary or a linear variable, using Proposition \ref{LP}.
+A ReLU is said {\em open} when it is represented as a binary variable.
+For $X$ a set of open ReLUs, we denote by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
+
+{\color{blue} 
+Usually, heuristics to choose $X$ are based on evaluating the {\em sensitivity} of a neuron $z$ wrt the ReLU nodes,
+that is how much a ReLU value impacts the value of $z$, and rank the ReLU nodes accordingly.
+This is the case of \cite{DivideAndSlide}, but also more generally of heuristics for BaB \cite{BaB,ferrari2022complete}, such as SR and FSB.
+%Our Utility function does not follow this approach.
+Instead, Utility considers the {\em improvement} from opening a neuron $n$, that is the difference for the value of $z$ between considering $\ReLU(n)$ exactly or using its LP relaxation $\LP(n)$.
+Indeed, it is not rare that
+$z$ is sensitive to ReLU node $n$, and yet $\LP(n)$ already provides an accurate approximation of $\ReLU(n)$.
+In this case, usual heuristics would open $n$, while it would only improve the value of $z$ in a limited way.
+}
 
@@
 Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
-$\Improve\_\min^z(n)$. Calling MILP on $\mathcal{M}_{\{n\}}$ for each neuron $n \leq z$
+$\Improve\_\min^z(n)$. Calling MILP on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$
 would however be very time consuming when the number of neurons $a$ to evaluate is large.
 {\color{blue} 
-That's why as far as we know, in competing heuristics to rank important nodes (e.g. \cite{huang2017safety,crown}), no call to solvers are made.
+The main novelty of our Utility function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Table \ref{tab:example1}).
+
+\iffalse
+That's why as far as we know, in competing heuristics to rank important nodes (e.g. \cite{BaB,huang2017safety,ferrari2022complete}), no call to solvers are made.
 %Instead, we focus on the following $\Utility\_\max\nolimits^z(n)$ function upper bounding $\Improve\_\max^z(n)$. 
-The novelty of our Utility function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, which is very efficient and negligible wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes, as hinted by Proposition \ref{prop2}.
+\fi
 
@@
 
-For a neuron $b$ on the layer before the layer $\ell_z$, we define:
-
 %we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$, by computing by how much the value of $z$ will change if $a$ is opened
@@
 %we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
+
+For a neuron $b$ on the layer before the layer $\ell_z$, we define:
+
 \vspace{-0.4cm}
@@
 
-Notice that if $W_{bz}<0$, the LP engine sets $\sol(\hat{b})$ to its minimal value
-to maximize $z$, which is $\sol(\hat{b})=\ReLU(\sol(b))$ thanks to Proposition~\ref{LP}. 
-In this case, we have $\Utility\_\max^z(b)=0$.
-Thus, we have $\Utility\_\max^z(b) \geq 0$ in all cases
-as $\sol(\hat{b}) \geq \ReLU(\sol(b))$ by Proposition~\ref{LP}.
+Consider $b$ with $W_{bz}<0$: to maximize $z$, the value of $\sol(\hat{b})$ is minimized, 
+which is $\sol(\hat{b})=\ReLU(\sol(b))$ thanks to Proposition~\ref{LP}. 
+Even if $z$ is sensitive to this ReLU $b$, the improvement of $b$ is 0.
+Utility does not open it as $\Utility\_\max^z(b)=0$, whereas usual heuristics would.
 
@@
 Informally, $\Delta(\hat{a}), \Delta(b), \Delta(\hat{b})$ approximate the improvement on the accuracy of $\hat{a}, b, \hat{b}$ when computing $\ReLU(a)$ 
-using the exact MILP encoding instead of LP. Using Prop. \ref{LP}, we show:
+using the exact MILP encoding instead of LP. Using Proposition \ref{LP}, we show:
+}
 
@@
 		\end{proof}
-	}
 

### 2024-11-26 ICLR25/introduction.tex
exp
full pass

@@
 Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}).
-Because pMILP focuses on the gain (binary - linear),
-	it is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})) than previous attempts, which consider the full contribution of a neuron.
+Because pMILP focuses on the {\em improvement} (binary - linear), it is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})) than previous attempts, which consider the generic {\em sensitivity} to this neuron.
 To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g.
-\cite{ferrari2022complete,crown}.}
+\cite{BaB,ferrari2022complete}.}
 

### 2024-11-26 ICLR25/proofsb.tex
full pass

@@
 We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
-Further, we tested with the SR  and FSB heuristics \cite{BaB} to choose important nodes for BaB (Branch and Bound).
-SR and FSB result in particularly low accuracy, even worse than \cite{DivideAndSlide} which only focus on neurons one layer before, and far away from Utility.
-FSB is also performing worse than SR when choosing nodes for pMILP, while for BaB, it is the opposite situation.
-This means that the heuristic to choose nodes important for BaB is not adapted to choose nodes for pMILP, although \cite{DivideAndSlide} heuristic is also choosing neurons based on importance of neurons for the consider ReLU.
+Further, we tested with the SR and FSB heuristics \cite{BaB}, that chooses nodes to branch on for BaB (Branch and Bound).
+When used instead to open nodes for pMILP, SR and FSB result in particularly low accuracy:
+even though SR, FSB and \cite{DivideAndSlide} heuristic are all choosing ReLUs based on sensitivity of the target neuron $z$, SR and FSB are worse than \cite{DivideAndSlide} which only opens neurons one layer before, and far away from Utility.
+Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite situation.
+This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.
 

### 2024-11-26 ICLR25/valabstraction.tex
full pass

@@
 
-The crucial factor in such an approach is to {\em select} few opened neurons in $X$ which are the most important for the accuracy.
-An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.
+The crucial factor in such an approach is to {\em select} few opened ReLU nodes in $X$ which are the most important for the accuracy.
+An extreme strategy was adopted in \cite{DivideAndSlide}, where only ReLU nodes of the immediate previous layer can be opened, and the measure to choose ReLU $a$ when computing the bounds for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.
 To obtain a more accurate measure, that 

### 2024-11-27 ICLR25/proofsb.tex
update table
update

@@
 	\centering
-	\begin{tabular}{|c||c|c|c||c|c|c|c|}
+	\begin{tabular}{|c||c|c|c|c|c||c|c|c|c|}
 		\hline
-			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-8}
-		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
+			&\multicolumn{5}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-10}
+		\text{$|X|$}  & \text{Random} & Huang &SR&FSB& \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
 		\hline
-		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
-		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 & 1.7182 & \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& 1.6803 & \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& 1.6475 & \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & 1.6174 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & 1.5788 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& 1.5413 & \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & 1.4972 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& 1.4514 & \bf 0.921 \\ \hline \hline
-		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
+		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
+		5  &   1.729&1.704 &1.7200&1.7197& 1.603&  1.729& 1.7133 & 1.7149 & \bf 1.532 \\ \hline
+		10  &  1.701 &  1.651 &1.6840&1.6851&1.517& 1.696 & 1.6674& 1.6714 & \bf  1.371\\ \hline
+		15  & 1.671 &  1.599 &1.6502& 1.6516&1.466&  1.653& 1.6230& 1.6251 & \bf  1.247\\ \hline
+		20  &  1.635 & 1.557&1.6190&1.6199&1.438 & 1.619 &1.5764 & 1.5812 & \bf  1.145\\ \hline
+		25  &  1.601 & 1.519 &1.5887&1.5886&1.427&  1.586 &1.5322 & 1.5388 & \bf 1.061\\ \hline
+		30  & 1.574 & 1.489 &1.5584&1.5604&1.425& 1.546 &  1.4914& 1.4982 & \bf  0.989 \\ \hline
+		35  &  1.542 & 1.465&1.5289&1.5305&1.424 & 1.502 & 1.4481 & 1.4600 & \bf 0.934 \\ \hline
+		40  & 1.512 & 1.447 &1.4985&1.5001&1.424& 1.469 & 1.4070& 1.4187 & \bf 0.921 \\ \hline \hline
+		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
 	\end{tabular}
@@
 \end{table}
+
+	\begin{figure}[h!]
+		\centering
+		\vspace*{-0.3cm}
+		\includegraphics[height=9cm]{New Plot for table 3}.
+		\vspace*{-0.4cm}
+		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
+		\label{fig_table3_new}
+	\end{figure}
 

### 2024-11-27 ICLR25/proofsb.tex
appendix

--- 2024-11-26 ICLR25/proofsb.tex
@@
 When used instead to open nodes for pMILP, SR and FSB result in particularly low accuracy:
-even though SR, FSB and \cite{DivideAndSlide} heuristic are all choosing ReLUs based on sensitivity of the target neuron $z$, SR and FSB are worse than \cite{DivideAndSlide} which only opens neurons one layer before, and far away from Utility.
-Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite situation.
+even though SR, FSB and \cite{DivideAndSlide} heuristic are all choosing ReLUs based on sensitivity of the target neuron $z$, SR and FSB are worse than \cite{DivideAndSlide} which only opens neurons one layer before (except when all ReLUs of the previous layers are open), and far worse than Utility.
+Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite.
 This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.
@@
 		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
-		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 & 1.7182 & \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& 1.6803 & \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& 1.6475 & \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & 1.6174 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & 1.5788 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& 1.5413 & \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & 1.4972 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& 1.4514 & \bf 0.921 \\ \hline \hline
+		5  &   1.729&1.704 & 1.603&  1.729& 1.7133 & 1.7149 & \bf 1.532 \\ \hline
+		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6674& 1.6714 & \bf  1.371\\ \hline
+		15  & 1.671 &  1.599 &1.466&  1.653& 1.6230& 1.6251 & \bf  1.247\\ \hline
+		20  &  1.635 & 1.557&1.438 & 1.619 &1.5764 & 1.5812 & \bf  1.145\\ \hline
+		25  &  1.601 & 1.519 &1.427&  1.586 &1.5322 & 1.5388 & \bf 1.061\\ \hline
+		30  & 1.574 & 1.489 &1.425& 1.546 &  1.4914& 1.4982 & \bf  0.989 \\ \hline
+		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4481 & 1.4600 & \bf 0.934 \\ \hline
+		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4070& 1.4187 & \bf 0.921 \\ \hline \hline
 		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
@@
 \end{table}
+
+	\begin{figure}[h!]
+		\centering
+		\vspace*{-0.3cm}
+		\includegraphics[height=9cm]{New Plot for table 3}.
+		\vspace*{-0.4cm}
+		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
+		\label{fig_table3_new}
+	\end{figure}
 

### 2024-11-27 ICLR25/proofsb.tex

--- 2024-11-27 ICLR25/proofsb.tex
@@
 		\vspace*{-0.4cm}
-		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
+		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
 		\label{fig_table3_new}

### 2024-11-27 lipics-master/comppaths.tex
commit

@@
 
-Theorem \ref{th2} theoretically computes accurate bounds by iteratively applying MILP$_{X}$ to each node, layer by layer.
-Practically, however, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$.
-Instead, an interesting trade off between speed and accuracy is to set a threshold on the strength of compensation.
-Paths falling below this threshold are deemed to not warrant an individual integer variable due to insufficient compensatory strength.
-We denote the resultant subset of nodes situated on paths with substantial compensation as $Z_n$.
-In practical applications, one might consider selecting the $K$ nodes that are involved in the most significant compensating paths to construct the set $Z_n$, with $K$ being a relatively small integer.
-This strategy effectively provides a trade-off between the algorithm's performance and the precision of the results.
-The pseudo-code for \CMP is presented in Algorithm \ref{algo1}.
+pMILP computes accurate bounds by iteratively calling itself to each node $n$, 
+layer by layer, as presented in Algorithm \ref{algo1}.
 
@@
 
-CMP($K$) has a worst case complexity bounded by $O(N \MILP(N,K))$, 
+pMILP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
 where $N$ is the number of nodes of the DNN, 

### 2024-11-27 ICLR25/proofsb.tex
appendix

@@
 Further, we tested with the SR and FSB heuristics \cite{BaB}, that chooses nodes to branch on for BaB (Branch and Bound).
-When used instead to open nodes for pMILP, SR and FSB result in particularly low accuracy:
-even though SR, FSB and \cite{DivideAndSlide} heuristic are all choosing ReLUs based on sensitivity of the target neuron $z$, SR and FSB are worse than \cite{DivideAndSlide} which only opens neurons one layer before (except when all ReLUs of the previous layers are open), and far worse than Utility.
+When SE and FSR are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
+\ref{fig_table3_new}: SR and FSB are worse than \cite{DivideAndSlide} for $<35$ oepn ReLU nodes, although unlike the latter, the former can rank ReLU nodes in several layer before (which helps them a bit), and far worse than Utility.
 Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite.
@@
 	\end{tabular}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs SR vs FSB vs random choice.}
+	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
 	\label{tab:example1}

### 2024-11-27 ICLR25/proofsb.tex
proofs
appendix

@@
 We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
-Further, we tested with the SR and FSB heuristics \cite{BaB}, that chooses nodes to branch on for BaB (Branch and Bound).
+Further, we tested with the SR \cite{BaB} and FSB heuristics \cite{FSB}, that chooses nodes to branch on for BaB (Branch and Bound).
 When SE and FSR are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
-\ref{fig_table3_new}: SR and FSB are worse than \cite{DivideAndSlide} for $<35$ oepn ReLU nodes, although unlike the latter, the former can rank ReLU nodes in several layer before (which helps them a bit), and far worse than Utility.
-Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite.
+\ref{fig_table3_new}: SR and FSB are worse than \cite{DivideAndSlide} for $<35$ open ReLU nodes, although unlike the latter, they can rank ReLU nodes in several layer before (which helps them a bit), and far worse than Utility.
+Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite \cite{FSB}.
 This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.

### 2025-01-22 CAV 2025 TODO/relatedwork.tex
Create the folder

--- 2024-09-28 ICLR25/relatedwork.tex
@@
 MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of Hybrid MILP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding.
-In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.
+In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy.
+% as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.
 
@@
 However, branch and bound hits a complexity barrier when verifying harder instances, due to an overwhelming number of branches, as displayed in Table \ref{table_beta}.
-This is not the csae of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.
+This is not the case of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.
 That shortcoming for hard instances was witnessed in \cite{crown}, and a very specific solution using the full MILP encoding for the first few layers of a DNN was drafted, following similar proposal \cite{MILP2}.
-There are two key issues with this techniques: it is slow, as every neurons up to the layer are encoded using an integer variable, and it cannot scale to DNNs with many neurons, making it not that accurate for intermediate networks (e.g.
+The main issue is that it is slow
+and it cannot scale to DNNs with many neurons, as every neurons are encoded using an integer variable, making it not that accurate for intermediate networks (e.g.
 $9\times100$, $9\times200$, Table \ref{table_hybrid}), and not usable for larger DNNs ($6\times500$, CNN-B-Adv), whereas Hybrid MILP does scale.
@@
 Consequently, LP is more accurate (but slower) than DeepPoly, and Hybrid MILP is considerably more precise.
-Regarding PRIMA \cite{prima}, the approach involves explicitly maintaining dependencies between neurons, calculating bounds layer by layer.
+Regarding PRIMA \cite{prima}, the approach involves explicitly maintaining dependencies between neurons.
 

### 2025-01-22 CAV 2025 TODO/Paper_noProof.tex
update

--- 2024-11-26 ICLR25/Paper_noProof.tex
@@
-\documentclass{article} % For LaTeX2e
-\usepackage{iclr2025_conference,times}
-% Optional math commands from https://github.com/goodfeli/dlbook_notation.
-\input{math_commands.tex}
+\documentclass{llncs}
 
@@
 \usepackage{threeparttable}
+\input{math_commands.tex}
 
@@
 \newcommand{\B}{\mathrm{B}}
+\usepackage{amsmath, amssymb, amsfonts}
+
+\newcommand{\ReLU}{\mathrm{ReLU}}
 
@@
 
-\usepackage{amsmath, amsthm, amssymb, amsfonts}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
+\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
+\date{}
 
-\newcommand{\ReLU}{\mathrm{ReLU}}
-
-\title{Hybrid MILP to efficiently and accuratly \\  solve hard DNN verification instances}
-
-% Authors must not appear in the submitted version. They should be hidden
-% as long as the \iclrfinalcopy macro remains commented out below.
-% Non-anonymous submissions will be rejected without review.
-
-\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
-about author (webpage, alternative address)---\emph{not} for acknowledging
-funding agencies.  Funding acknowledgements go at the end of the paper.} \\
-Department of Computer Science\\
-Cranberry-Lemon University\\
-Pittsburgh, PA 15213, USA \\
-\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
-\And
-Ji Q. Ren \& Yevgeny LeNet \\
-Department of Computational Neuroscience \\
-University of the Witwatersrand \\
-Joburg, South Africa \\
-\texttt{\{robot,net\}@wits.ac.za} \\
-\AND
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email}
-}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to \LaTeX{} to determine where to break
-% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
-% puts 3 of 4 authors names on the first line, and the last on the second
-% line, try using \AND instead of \And before the third author name.
-
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
-
-%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
-
-\maketitle
-
-\begin{abstract}
-$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best 
-trade-off between accuracy and runtime.
-VNNcomp however is focusing on relatively easy verification instances.
-In this paper, we consider {\em harder} verification instances, on which $\alpha,\beta$-Crown displays a large number ($20-58\%$) of undecided instances, that is, instances that can neither be verified, nor an explicit attack can be found.
-Enabling larger time-outs for $\alpha,\beta$-Crown only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
-Resorting to slow complete verifiers, does not fare better even with very large time-outs: They would theoretically be able to close the gap, but with an untractable runtime on all but small {\em hard} instances.
-
-In this paper, {\color{blue}
-%we study the MILP encoding of ReLU-DNNs.
-%, and provide new insights in the LP relaxation. 
-we propose a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
-the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input. }
-%This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation. 
-Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy.
-Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-Crown fails, produces a very accurate yet efficient verifier, reducing tremendously the number of undecided instances ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance).
-\end{abstract}
 
@@
 
-\input{valabstraction}
+%\input{valabstraction}
 
@@
 \bibliography{references}
-\bibliographystyle{iclr2025_conference}
+\bibliographystyle{plain}
 

### 2025-01-22 CAV 2025 TODO/Paper_noProof.tex
update

--- 2024-11-26 ICLR25/Paper_noProof.tex
@@
 
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
 \newcommand{\toolname}{Hybrid MILP}
 
-\usepackage{amsmath, amsthm, amssymb, amsfonts}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
+\title{Hybrid MILP to efficiently and accuratly \\  solve hard DNN verification instances}
+\date{}
 
-\newcommand{\ReLU}{\mathrm{ReLU}}
+%\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
+%		about author (webpage, alternative address)---\emph{not} for acknowledging
+%		funding agencies.  Funding acknowledgements go at the end of the paper.} \\
+%	Department of Computer Science\\
+%	Cranberry-Lemon University\\
+%	Pittsburgh, PA 15213, USA \\
+%	\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
+%	\And
+%	Ji Q. Ren \& Yevgeny LeNet \\
+%	Department of Computational Neuroscience \\
+%	University of the Witwatersrand \\
+%	Joburg, South Africa \\
+%	\texttt{\{robot,net\}@wits.ac.za} \\
+%	\AND
+%	Coauthor \\
+%	Affiliation \\
+%	Address \\
+%	\texttt{email}
+%}
 
-\title{Hybrid MILP to efficiently and accuratly \\  solve hard DNN verification instances}
-
-% Authors must not appear in the submitted version. They should be hidden
-% as long as the \iclrfinalcopy macro remains commented out below.
-% Non-anonymous submissions will be rejected without review.
-
-\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
-about author (webpage, alternative address)---\emph{not} for acknowledging
-funding agencies.  Funding acknowledgements go at the end of the paper.} \\
-Department of Computer Science\\
-Cranberry-Lemon University\\
-Pittsburgh, PA 15213, USA \\
-\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
-\And
-Ji Q. Ren \& Yevgeny LeNet \\
-Department of Computational Neuroscience \\
-University of the Witwatersrand \\
-Joburg, South Africa \\
-\texttt{\{robot,net\}@wits.ac.za} \\
-\AND
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email}
-}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to \LaTeX{} to determine where to break
-% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
-% puts 3 of 4 authors names on the first line, and the last on the second
-% line, try using \AND instead of \And before the third author name.
-
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
-
-%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}

### 2025-01-23 CAV 2025 TODO/Comparison.tex
Add a section

\section{Comparison of methods.}

\begin{tikzpicture}[scale=1, >=stealth]

	% Draw axes
	\draw[->] (-5,0) -- (4,0) node[right] {$x$};
	\draw[->] (0,-1) -- (0,3) node[above] {$y$};

	% Draw ReLU function
	\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
	\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(0.5,-0.4)}] {$y = \ReLU(x)$};
	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-0.5,0.4)}] {$y = \frac{\UB}{\UB-\LB} x-\frac{\UB\LB}{\UB-\LB}$};

%	% Add labels
%	\draw[dashed] (2,0) -- (2,2) -- (0,2); % Optional grid
%	\node[below left] at (0,0) {$0$};
%	
%	% Add tick marks
%	\foreach \x in {1,2}
%	\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {\x};
%	\foreach \y in {1,2}
%	\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {\y};

\end{tikzpicture}

### 2025-01-23 CAV 2025 TODO/Comparison.tex
update

@@
 \section{Comparison of methods.}
+
+\label{sec4p5}
+
+Here we use the FSB formula from the paper {Improved Branch and Bound for Neural Network
+Verification via Lagrangian Decomposition}
+
+\begin{align*}
+	\bm{\bar{\lambda}}_{n-1} =& -W^T_n\bm{1},  	\bm{\bar{\lambda}}_{k-1} = W^T_k\big(\dfrac{[\hat{\bm{u}_k}]_+}{[\hat{\bm{u}_k}]_+-[\hat{\bm{l}_k}]_-}\odot\bm{\bar{\lambda}}_{k}\big) &k\in [2,n-1]\\
+	\bm{s}_{SR} =& \lvert\max\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert &\\
+	&\odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}&k\in [1,n-1]\\
+	\bm{s}_{FSB} =& \lvert\min\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert &\\
+	&\odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}&k\in [1,n-1]\\
+\end{align*}
+
+\begin{figure}[t!]
+	\centering
+	\begin{tikzpicture}
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (input1) {$n_1$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};
+
+		% Hidden layers
+
+		\node (hidden10) at ($(input1) + (2.5,0.6)$) {$0$};
+
+		\node (hidden20) at ($(input1) + (2.5,-1.5-0.6)$) {$0$};
+
+		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$0$};
+
+		\node (hidden60) at ($(input1) + (7.5,-1.5-0.6)$) {$1.5$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$n_3$};
+		\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{n}_3$};
+		\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
+		\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};
+
+		% Output layer
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{n}_5$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{n}_{6}$};
+
+		% Connections
+
+		\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
+
+		\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
+
+		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
+		\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$1$};
+
+		\draw[->,thick] (input2) -- (hidden1) node[near start, below] {$1$};
+		\draw[->, thick] (input2) -- (hidden2)node[near start, below] {$-1$};
+
+		\draw[->, thick] (hidden1) -- (hidden3) node[midway, above] {$\max(n_1,0)$};
+		\draw[->, thick] (hidden2) -- (hidden4) node[midway, above] {$\max(n_2,0)$};
+
+		\draw[->, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
+		\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};
+
+		\draw[->,thick] (hidden4) -- (hidden5)node[near start, below] {$2$};
+		\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
+
+		\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(n_5,0)$};
+		\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(n_6,0)$};
+
+	\end{tikzpicture}
+	\caption{}
+\end{figure}
 
@@
 	\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(0.5,-0.4)}] {$y = \ReLU(x)$};
-	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-0.5,0.4)}] {$y = \frac{\UB}{\UB-\LB} x-\frac{\UB\LB}{\UB-\LB}$};
+	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-0.5,0.2)}] {$y = \frac{\UB}{\UB-\LB} x-\frac{\UB\LB}{\UB-\LB}$};
 

### 2025-01-25 CAV 2025 TODO/Paper_noProof.tex
update
Add a section
intro

@@
 \input{math_commands.tex}
-
 %\usepackage[latin9]{inputenc}
@@
 
-\title{Hybrid MILP to efficiently and accuratly \\  solve hard DNN verification instances}
+\title{Solution-aware vs global ReLU ranking: \\
+partial MILP strikes back for DNN verification}
 \date{}
@@
 	\begin{abstract}
-		$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best 
-		trade-off between accuracy and runtime.
-VNNcomp however is focusing on relatively easy verification instances.
-In this paper, we consider {\em harder} verification instances, on which $\alpha,\beta$-Crown displays a large number ($20-58\%$) of undecided instances, that is, instances that can neither be verified, nor an explicit attack can be found.
-Enabling larger time-outs for $\alpha,\beta$-Crown only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time.
-Resorting to slow complete verifiers, does not fare better even with very large time-outs: They would theoretically be able to close the gap, but with an untractable runtime on all but small {\em hard} instances.
+		$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), 
+		as the DNN verifier with the best trade-off between accuracy and runtime. 
+		VNNcomp however is focusing on relatively easy verification problems.
+		There are many problems however which are much harder to verify, and for which
+		$\alpha,\beta$-Crown does not scale, even by enlarging tremendously the time-outs.
+		Other techniques do not scale either.
 
-		In this paper, {\color{blue}
-			%we study the MILP encoding of ReLU-DNNs.
-			%, and provide new insights in the LP relaxation. 
-			we propose a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
-			the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input. }
+		In this paper, we work on a fundamental problem to enable scaling to more complex problems:
+
+		propose a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
+		the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input.
 		%This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation. 

### 2025-01-25 CAV 2025 TODO/experiments.tex

--- 2024-11-26 ICLR25/experiments.tex
@@
 	\vspace*{-0.3cm}
-	\includegraphics[height=7.5cm]{Plot for table 3}.
+	\includegraphics[height=8cm]{Plot for table 3}.
 	\vspace*{-0.4cm}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
+	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs random choice.}
 	\label{fig_table3}
@@
 	\begin{centering}
-\includegraphics[scale=0.5]{epsilon.png}.
+\includegraphics[scale=0.6]{epsilon.png}.
 \caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ on each of the 20 first images of MNIST.}
@@
 Notice that results for other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN.
-Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd
+Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd
 of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN.

### 2025-01-26 CAV 2025 TODO/Paper_noProof.tex
title abstract intro

--- 2025-01-22 CAV 2025 TODO/Paper_noProof.tex
@@
 
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
 \newcommand{\toolname}{Hybrid MILP}
 
-\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
+\title{Solution-aware vs global ReLU selection: \\
+partial MILP strikes back for DNN verification}
 \date{}
 
+%\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
+%		about author (webpage, alternative address)---\emph{not} for acknowledging
+%		funding agencies.  Funding acknowledgements go at the end of the paper.} \\
+%	Department of Computer Science\\
+%	Cranberry-Lemon University\\
+%	Pittsburgh, PA 15213, USA \\
+%	\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
+%	\And
+%	Ji Q. Ren \& Yevgeny LeNet \\
+%	Department of Computational Neuroscience \\
+%	University of the Witwatersrand \\
+%	Joburg, South Africa \\
+%	\texttt{\{robot,net\}@wits.ac.za} \\
+%	\AND
+%	Coauthor \\
+%	Affiliation \\
+%	Address \\
+%	\texttt{email}
+%}
+
 \begin{document}
+
+	\maketitle
+
+	\begin{abstract}
+		Branch and Bound (BaB) is considered as the most efficient technique for DNN verification: it can propagate bounds over numerous branches, to accurately under- and over-approximate values a given neuron can take even in large DNNs, enabling formal verification of properties such as local robustness.
+Nevertheless, the number of branches grows {\em exponentially} with important variables, and there are complex instances for which the number of branches is too large to handle even using BaB.
+In these cases, providing more time to BaB is not efficient, as the number of branches treated is {\em linear} with the time-out.
+Such cases arise with verification-agnostic DNNs, non-local properties (e.g.
+global robustness, computing Lipschitz bound, compressed sensing), etc.
+		%The fact that pure BaB is not that efficient for e.g.
+verification-agnostic (even very small) DNNs has been witnessed before.
+The workaround, e.g.
+in {\em refined} $\alpha,\beta$-CROWN, was to precompute very accurate bounds for the first few neurons of the DNN using a complete full MILP encoding.
+Non-surprisingly, this very slow technique does not scale but to small DNNs.
+		%Indeed, one of its implementation, $\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best trade-off between accuracy and runtime. 
+		%VNNcomp however is focusing on relatively easy verification problems.
+
+        To handle complex instances, we revisit a divide-and-conquer approach to break down the complexity: instead of few complex BaB calls, we rely on many small {\em partial} MILP calls.
+The crucial step is to select very few but very important ReLUs to treat using (costly) binary variables.
+The previous attempts were suboptimal in that respect.
+In this paper, we propose a novel {\em solution-aware} ReLU ranking (SAR), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU ranking (GR) functions.
+We compare them theoretically as well as experimentally.
+Surprisingly perhaps, the most accurate solution (SAR) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GR) to {\em rank} within this selection.
+Compared with previous attempts, SAR reduces the number of integer variables by around 4 times while maintaining the same level of accuracy.
+Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CIFAR CNNs with 20 000 nodes.
+
+		%a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem.
+The novelty resides in the use of the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input.
+		%This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation.
+
+	\end{abstract}
 
@@
 
+\input{Comparison}
+
 \input{experiments}

### 2025-01-26 CAV 2025 TODO/introduction.tex
fix mistakes
title abstract intro

--- 2024-11-26 ICLR25/introduction.tex
@@
 For this reason, DNN verifiers in the past years have mainly focused on optimizing for such easy instances.
-Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT
+Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT
 \cite{pyrat}, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
 and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-Crown \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
-We will thus focus in the following mostly on $\alpha,\beta$-Crown.
-
-Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-Crown \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neighbour with a different decision.
-One issue is however that easy instances are trained specifically to be easier to verify
-e.g.
-using DiffAI \cite{DiffAI} PGD \cite{PGD}, which can impact the accuracy of the network, i.e.
-answering correctly to an unperturbed input.
-For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct {\color{blue}\cite{prima}} (the other $71\%$ are thus not  tested).
-While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
-very hard verification instances into hard verification instances.
-Also, verification questions intrinsically harder than local robustness, such as 
-bounding on Lipschitz constants \cite{lipshitz} globally or asking several specification at once, makes the instance particularly harder.
-Last, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks \cite{SDPFI}.
-The bottom line is, one cannot expect only {\em easy} verification instances: {\em hard} verification instances need to be explored as well.
-
-In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified 
-by $\alpha,\beta$-Crown and the upper bound when we remove those which can be falsified.
-In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely MNIST 5$\times$100.
-We first dwelve into the scaling of $\alpha,\beta$-Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
-Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).
+We will thus compare mainly with $\alpha,\beta$-Crown experiments as gold standard in the following\footnote{GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us}.
 
@@
 \end{table}
+
+$\alpha,\beta$-CROWN, as well as BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete},
+rely on Branch and Bound technique (BaB), which call BaB once per output neuron (few calls).
+In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities.
+For easy instances, BaB is highly efficient as all branches can be pruned early.
+However, BaB methods hit a complexity barrier when verifying more complex instances, due to an overwhelming number of branches (exponential in the height of branches that cannot be pruned as they need too many variables to branch over).
+This can be clearly witnessed on the verification-agnostic DNNs of Table \ref{table_beta} (6 first DNNs), where vastly enlarging the time-out only enable to verify few more \% of images, leaving a large proportion ($20\%-50\%$) of images undecided despite the large runtime.
+As argued in \cite{SDPFI}, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks, and such cases should be treated as well as DNNs specifically trained to be easy to verify, e.g.
+using \cite{TrainingforVerification}.
+Verification-agnostic are the simplest instances to demonstrate the scaling behavior of BaB using standard local robustness implementations.
+Other complex instances include solving non-local properties, e.g.
+global robustness computed through Lipschitz bound \cite{lipshitz}, compressed sensing \cite{sensing}, etc.
+The bottom line is that one cannot expect to have only easy instances to solve.
+It is important to notice that that number of activation functions of the DNN is a poor indicator of the hardness of the instance, e.g.
+$5 \times 100$ with 500 ReLUs is far harder to certify ($50\%$ undecided images) than 100 times bigger ResNet ($0\%$ undecided images), see Table \ref{table_beta}.
+
+		%The fact that pure BaB is not that efficient for e.g.
+verification-agnostic (even very small) DNNs has been witnessed before.
+The workaround, e.g.
+in {\em refined} $\alpha,\beta$-CROWN, was to precompute very accurate bounds for the first few neurons of the DNN using a complete full MILP encoding.
+Non-surprisingly, this very slow technique does not scale but to small DNNs.
+
+%Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-Crown \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neigbhour with a different decision.
+One issue is however that easy instances are trained specifically to be easier to verify e.g.
+using DiffAI \cite{DiffAI} PGD \cite{PGD}, which can impact the accuracy of the network, i.e.
+answering correctly to an unperturbed input.
+For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct {\color{blue}\cite{prima}} (the other $71\%$ are thus not  tested).
+While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
+very hard verification instances into hard verification instances.
+Also, verification questions intrinsically harder than local robustness, such as bounding on Lipschitz constants globally or asking several specification at once, makes the instance particularly harder.
+Last, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks.
+The bottom line is, one cannot expect only {\em easy} verification instances: {\em hard} verification instances need to be explored as well.
+
+In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified 
+by $\alpha,\beta$-Crown and the upper bound when we remove those which can be falsified.
+In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely MNIST 5$\times$100.
+We first dwelve into the scaling of $\alpha,\beta$-Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
+Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).
 
@@
 To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g.
-\cite{BaB,ferrari2022complete}.}
+\cite{BaB,FSB}.}
 

### 2025-01-26 CAV 2025 TODO/relatedwork.tex
title abstract intro

@@
 
-Hybrid MILP can be seen as a refinement of $\alpha,\beta$-Crown~\cite{crown}, though its refined accurate path is vastly different than the base Branch and Bound technique used in 
-$\alpha,\beta$ CROWN, BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete}, which call BaB once per output neuron.
-In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities.
-In simple networks, like those trained robustly, branch and bound is highly efficient, focusing on branches crucial for verifying the actual property.
-However, branch and bound hits a complexity barrier when verifying harder instances, due to an overwhelming number of branches, as displayed in Table \ref{table_beta}.
+Hybrid MILP can be seen as a refinement of $\alpha,\beta$-Crown~\cite{crown}, though its refined accurate path is vastly different than the base.
 This is not the case of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.

### 2025-01-26 CAV 2025 TODO/Comparison.tex
update

--- 2025-01-23 CAV 2025 TODO/Comparison.tex
@@
-\section{Comparison of methods.}
+\section{Comparison of other methods.}
 
+\label{sec4p5}
+
+Here we list the FSB formula from the paper \cite{FSB}:
+
+\begin{align*}
+	\bm{\bar{\lambda}}_{n-1} =& -W^T_n\bm{1}, \hspace*{10ex}  	\bm{\bar{\lambda}}_{k-1} = W^T_k\big(\dfrac{[\hat{\bm{u}_k}]_+}{[\hat{\bm{u}_k}]_+-[\hat{\bm{l}_k}]_-}\odot\bm{\bar{\lambda}}_{k}\big) \hspace*{-10ex}  &k\in [2,n-1]\\
+	\bm{s}_{SR} =& \lvert\max\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert &\\
+	&\odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}&k\in [1,n-1]\\
+	\bm{s}_{FSB} =& \lvert\min\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert &\\
+	&\odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}&k\in [1,n-1]\\
+\end{align*}
+
+\begin{figure}[t!]
+	\centering
+	\begin{tikzpicture}
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (input1) {$n$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n'$};
+
+		% Hidden layers
+
+		\node (hidden10) at ($(input1) + (2.5,0.6)$) {$[-1,1]$};
+
+		\node (hidden20) at ($(input1) + (2.5,-1.5-0.6)$) {$[-10,11]$};
+
+		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$[-1,0.5]$};
+
+		\node (hidden60) at ($(input1) + (7.5,-1.5-0.6)$) {$[0,0.5]$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$a$};
+		\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$a'$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{a}$};
+		\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{a}'$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$b$};
+		\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$b'$};
+
+		% Output layer
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{b}$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{b}'$};
+
+			\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (output3) at ($(input1) + (12.5,0)$){$z$};
+
+		% Connections
+
+		\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
+
+		\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
+
+		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
+		\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$-10$};
+
+		\draw[->, thick] (input2) -- (hidden2)node[near start, below] {$0.5$};
+
+		\draw[->, thick] (hidden1) -- (hidden3);
+		\draw[->, thick] (hidden2) -- (hidden4);
+
+		\draw[->, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};
+
+		\draw[->,thick] (hidden4) -- (hidden5)node[near start, below] {$1$};
+		\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
+
+		\draw[->,thick] (hidden5) -- (output1);
+		\draw[->,thick] (hidden6) -- (output2);
+
+		\draw[->,thick] (output1) -- (output3)node[near start, below] {$-100$};
+		\draw[->,thick] (output2) -- (output3)node[near start, below] {$1$};
+
+	\end{tikzpicture}
+	\caption{}
+	\label{img:FSB_example}
+\end{figure}
+
+\begin{figure}[t!]
 \begin{tikzpicture}[scale=1, >=stealth]
@@
 	\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(0.5,-0.4)}] {$y = \ReLU(x)$};
-	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-0.5,0.4)}] {$y = \frac{\UB}{\UB-\LB} x-\frac{\UB\LB}{\UB-\LB}$};
+	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-5,-1.5)}] {$y = \frac{\UB}{\UB-\LB} x-\frac{\UB\cdot\LB}{\UB-\LB}$};
 
-%	% Add labels
-%	\draw[dashed] (2,0) -- (2,2) -- (0,2); % Optional grid
-%	\node[below left] at (0,0) {$0$};
-%	
-%	% Add tick marks
-%	\foreach \x in {1,2}
-%	\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {\x};
-%	\foreach \y in {1,2}
-%	\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {\y};
+	% Add labels
+	\draw[dashed] (2.5,0) -- (2.5,2.5) -- (0,2.5); % Optional grid
+	\node[below left] at (0,0) {$0$};
+
+	% Add tick marks
+
+	\foreach \x in {2.5}
+	\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\UB$};
+	\foreach \x in {-3}
+	\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\LB$};
+
+	\foreach \y in {2.5}
+	\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {$\UB$};
+
+	\draw (-1,0.1) -- (-1,-0.1) node[below] {$\sol(a)$};
+	\draw[dashed] (-1,0) -- (-1,0.9) -- (0,0.9);
+	\draw (-0.1,0.9) -- (0.1,0.9) node[right, shift={(-0.1,0.13)}] {$\sol(\hat{a})$};
+	\node at (-0.5,0.4) {$\Delta(a)$};
 
 \end{tikzpicture}
+	\caption{}
+\label{img:Utility}
+\end{figure}
+
+\subsection*{An example when FSB is not accurate}
+
+See the figure \ref{img:FSB_example}. When the algorithm considers neurons in the layer of $a,a'$, FSB will think $a$ is important, but Utility will think it is not important (Utility value is 0).
+
+Although this example is extreme, similar situations frequently occur in practice.
+
+\subsection*{Comparison on MNIST}
+
+Here we use the network named MNIST $5\times 100$ and a hard image to compare the effect of FSB and Utility function.
+
+We fix an intermediate bound data for layers before the third hidden layer, and use different methods based on this bound to compute the upper and lower bounds of neurons in the second and third hidden layer.
+
+The plot shows that when only considering neurons in one layer before the target layer, we are significantly better.
+
+\subsection*{Comparison on CIFAR10}
+
+Here we use the network named CNN-B-adv and a hard image to compare the effect of FSB and Utility function.
+
+We fix an intermediate bound data for layers before the target layers, and use different methods based on this bound to compute the output layer.
+
+The plot shows that our Utility function is significantly better than FSB, and other methods.

### 2025-01-26 CAV 2025 TODO/introduction.tex
intro

@@
 	\caption{Images verified by $\alpha,\beta$-Crown with different time-outs (TO) on 7 DNNs, and average runtime per image.
-The 6 first DNNs are hard instances.
+The 6 first DNNs are complex instances.
 The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
@@
 However, BaB methods hit a complexity barrier when verifying more complex instances, due to an overwhelming number of branches (exponential in the height of branches that cannot be pruned as they need too many variables to branch over).
-This can be clearly witnessed on the verification-agnostic DNNs of Table \ref{table_beta} (6 first DNNs), where vastly enlarging the time-out only enable to verify few more \% of images, leaving a large proportion ($20\%-50\%$) of images undecided despite the large runtime.
+This can be clearly witnessed on the verification-agnostic \cite{SDPFI} DNNs of Table \ref{table_beta} (6 first DNNs), where vastly enlarging the time-out only enables to verify few more \% of images, leaving a large proportion ($20\%-50\%$) of images undecided despite the large runtime.
 As argued in \cite{SDPFI}, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks, and such cases should be treated as well as DNNs specifically trained to be easy to verify, e.g.
 using \cite{TrainingforVerification}.
-Verification-agnostic are the simplest instances to demonstrate the scaling behavior of BaB using standard local robustness implementations.
+Verification-agnostic are the simplest instances to demonstrate the scaling behavior of BaB on complex instances using standard local robustness implementations.
 Other complex instances include solving non-local properties, e.g.
 global robustness computed through Lipschitz bound \cite{lipshitz}, compressed sensing \cite{sensing}, etc.
-The bottom line is that one cannot expect to have only easy instances to solve.
+The bottom line is that one cannot expect to have only easy instances to verify.
 It is important to notice that that number of activation functions of the DNN is a poor indicator of the hardness of the instance, e.g.
-$5 \times 100$ with 500 ReLUs is far harder to certify ($50\%$ undecided images) than 100 times bigger ResNet ($0\%$ undecided images), see Table \ref{table_beta}.
+$5 \times 100$ with 500 ReLUs is far more complex to certify ($50\%$ undecided images) than 100 times bigger ResNet ($0\%$ undecided images), see Table \ref{table_beta}.
 
@@
 
-In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified 
-by $\alpha,\beta$-Crown and the upper bound when we remove those which can be falsified.
+%In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-Crown and the upper bound when we remove those which can be falsified.
 In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely MNIST 5$\times$100.
@@
 	\end{tabular}
-\caption{Result of complete verifiers on the hard 5x100 with TO = 10 000s. 
+\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
 %Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-Complete verifier barely (9\% out of 50\%) 
-outperform $\alpha,\beta$-Crown (40\%, 1026s), despite much larger runtime.}
+Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-Crown (40\%), at the cost of a much larger runtime (4995s vs 1026s).}
 \label{table_complete}
@@
 
-The size of the smallest DNN (500 hidden neurons) makes it believable to be solved by complete verifiers such as Marabou 2.0, NNenum or a Full MILP encoding. 
-While they should theoretically be able to close the gap of undecided images,
-in practice, even with a large 10 000s Time-out, Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images, and with a very large runtime of almost 5000s per image.
-It seemed pointless to test complete verifiers on larger networks.
+Other standard non-BaB methods such as Marabou 2.0, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image.
+It appeared pointless to test these verifiers on larger networks.
 
@@
 
-{\color{blue} Our main contributions address the challenges of verifying {\em hard} DNNs efficiently:} 
+Our main contributions address the challenges to verify {\em complex} instances efficiently, as current methods are not appropriate to verify such instances:
 \begin{enumerate}
@@
 
-	\item {\color{blue} We designed a novel Utility function to choose few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP).
+	\item We revisit the idea from \cite{DivideAndSlide} to consider small calls to a partial MILP (pMILP) solver, i.e.
+with few binary variables encoding few ReLU functions exactly, to compute bounds for each neuron inductively, hence many ($O(n)$, the number of neuron) small calls, with a complexity exponential only in the few binary variables.
+Compared to the few (one per output neuron) complex call to BaB, each with a worst case complexity exponential in the number of neurons of the DNN (which is far from the actual complexity thanks to pruning branches in BaB - but which can be too large as we shown in the 6 first DNNs of Table \ref{table_beta}).
+Two questions arise: how to select few very important ReLUs?, and is computing the bounds of intermediate neurons a good trade-off compared with the theoretical loss of accuracy due to selecting only some binary ReLUs?
+Answer to these questions were not looking very promising judging by previous attempt \cite{DivideAndSlide}, which was using a simple selection heuristic of nodes in the previous layer only.
+
+	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global ranking (GR) functions to choose ReLU for pMILP. 
+	These revealed to be much more accurate than the simple heuristic in 
+	\cite{DivideAndSlide}.
+We uncover however one case (out of 4) where the exact function that GR tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode.
+This implies that these strategies may not be that accurate, because they do not know the mode to choose from.
+We then designed a novel solution-aware ranking (SAR), which uses the solution of a unique LP call, that provides the mode to consider.
+Theoretically, we show that SAR is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAR value implies that the ReLU is unnecessary.
+Experimentally, we further show that SAR is very close to the actual improvement, closer than GR, and that overall, the accuracy from SAR is significantly better than GR.
+Compared with the heuristic in \cite{DivideAndSlide}, SAR is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GR would be better suited, which we verify experimentally.
+
+	%	\item {\color{blue} We designed a novel Utility function to choose few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP).
 Specifically, the novelty of Utility resides in the use of the solution to an (efficient LP) solver on the node $z$ we want to bound.
@@
 
-	\item We then propose a new verifier, called {\em Hybrid MILP}, invoking first 
-	$\alpha,\beta$-Crown with short time-out to settle the easy instances.
+	\item For the second question, we propose a new verifier, called {\em Hybrid MILP}, invoking first 	$\alpha,\beta$-Crown with short time-out to settle the easy instances.
 On those ({\em hard}) instances which are neither certified nor falsified, we call pMILP with few neurons encoded as integer variables.

### 2025-01-26 CAV 2025 TODO/relatedwork.tex
related

@@
 
-Hybrid MILP can be seen as a refinement of $\alpha,\beta$-Crown~\cite{crown}, though its refined accurate path is vastly different than the base.
+The fact that pure BaB is not that efficient for e.g.
+verification-agnostic (even very small) DNNs has been witnessed before \cite{MILP2}.
+The workaround, e.g.
+in {\em refined} $\alpha,\beta$-CROWN, was to precompute very accurate bounds for the first few neurons of the DNN using a complete full MILP encoding, and then rely on a BaB call from that refined bounds (more complex calls to full MIPL and BaB).
+Non-surprisingly, this very slow technique does not scale but to small DNNs (max 2000 ReLU activation functions).
+Hybrid MILP on the other hand relies only on small calls: it is much more efficient on small DNNs, and it can scale to larger DNNs as well: we demonstrated strong performance with at least one order of magnitude larger networks (CNN-B-Adv).
+
+%Hybrid MILP can be seen as a refinement of $\alpha,\beta$-Crown~\cite{crown}, though its refined accurate path is vastly different than the base.
 This is not the case of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.
-That shortcoming for hard instances was witnessed in \cite{crown}, and a very specific solution using the full MILP encoding for the first few layers of a DNN was drafted, following similar proposal \cite{MILP2}.
+%That shortcoming for hard instances was witnessed in \cite{crown}, and a very specific solution using the full MILP encoding for the first few layers of a DNN was drafted, following similar proposal \cite{MILP2}.
 The main issue is that it is slow
-and it cannot scale to DNNs with many neurons, as every neurons are encoded using an integer variable, making it not that accurate for intermediate networks (e.g.
+%and it cannot scale to DNNs with many neurons, as every neurons are encoded using an integer variable, making it not that accurate for intermediate networks (e.g.
 $9\times100$, $9\times200$, Table \ref{table_hybrid}), and not usable for larger DNNs ($6\times500$, CNN-B-Adv), whereas Hybrid MILP does scale.
@@
 While the upper function is fixed, the lower function offers two choices.
-It relates to the LP encoding through the following new (to our knowledge) insight:  Proposition \ref{LP} state that the LP relaxation precisely matches the intersection of these two choices.
+It relates to the LP encoding through the following new (to our knowledge) insight:  Proposition \ref{LP} \cite{alessandro} states that the LP relaxation precisely matches the intersection of these two choices.
 Consequently, LP is more accurate (but slower) than DeepPoly, and Hybrid MILP is considerably more precise.
@@
 Finally, methods such as Reluplex / Marabou \cite{Reluplex,Marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, $\alpha,\beta$-CROWN)\cite{prima,crown}, Hybrid MILP.
-These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances as shown in Table \ref{table_complete}.
+These network-abstraction algorithms are designed to be {\em intrinsically complete} (rather than asymptotically complete as BaB), but this comes at the price of significant scalability challenges, and in practice they time-out on complex instances as shown in Table \ref{table_complete}.

### 2025-01-26 CAV 2025 TODO/introduction.tex
related
paper

@@
 $5 \times 100$ with 500 ReLUs is far more complex to certify ($50\%$ undecided images) than 100 times bigger ResNet ($0\%$ undecided images), see Table \ref{table_beta}.
-
-		%The fact that pure BaB is not that efficient for e.g.
-verification-agnostic (even very small) DNNs has been witnessed before.
-The workaround, e.g.
-in {\em refined} $\alpha,\beta$-CROWN, was to precompute very accurate bounds for the first few neurons of the DNN using a complete full MILP encoding.
-Non-surprisingly, this very slow technique does not scale but to small DNNs.
 
@@
 
-Limitation: We consider DNNs employing the standard ReLU activation function, though our findings should extend to other activation functions, following similar extention by \cite{DivideAndSlide}.
+Limitation: We consider DNNs employing the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}.
 

### 2025-01-26 CAV 2025 TODO/valabstraction.tex
fix

--- 2024-11-26 ICLR25/valabstraction.tex
@@
 is not limited to open nodes from the immediate previous layer, 
-{\color{blue} we invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:}
+{\color{blue} we invoke a folklore result \cite{alessandro} on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:}
 
@@
 	\label{LP}
-	{\color{blue} The LP relaxation of (\ref{eq11}) is equivalent with the triangular abstraction 	(\ref{eq:deeppoly}).}
+	The LP relaxation of (\ref{eq11}) is equivalent with the triangular abstraction 	(\ref{eq:deeppoly}).
 \end{proposition}
@@
 	Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$.
-The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediatly equivalent with $\hat{x} \geq \ReLU(x)$.
+The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediately equivalent with $\hat{x} \geq \ReLU(x)$.
 

### 2025-01-26 CAV 2025 TODO/Paper_noProof.tex
paper
fix
valabs

@@
 \date{}
-
-%\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
-%		about author (webpage, alternative address)---\emph{not} for acknowledging
-%		funding agencies.  Funding acknowledgements go at the end of the paper.} \\
-%	Department of Computer Science\\
-%	Cranberry-Lemon University\\
-%	Pittsburgh, PA 15213, USA \\
-%	\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
-%	\And
-%	Ji Q. Ren \& Yevgeny LeNet \\
-%	Department of Computational Neuroscience \\
-%	University of the Witwatersrand \\
-%	Joburg, South Africa \\
-%	\texttt{\{robot,net\}@wits.ac.za} \\
-%	\AND
-%	Coauthor \\
-%	Affiliation \\
-%	Address \\
-%	\texttt{email}
-%}
 
@@
 
-%\input{valabstraction}
+\input{valabstraction}
 
@@
 
-{\bf Reproducibility Statement:} 
-We tested twice outlier results to confirm them, making sure of reproducibility on the given hardware. Precise details on the settings used are provided in the appendix.
-Additional results {\color{blue}(e.g. ablation studies)} are also provided in the appendix.
+%{\bf Reproducibility Statement:} We tested twice outlier results to confirm them, making sure of reproducibility on the given hardware.
+Precise details on the settings used are provided in the appendix.
+Additional results {\color{blue}(e.g.
+ablation studies)} are also provided in the appendix.
 Tested DNNs as well as MNIST and CIFAR10 DataSet are freely available.

### 2025-01-26 CAV 2025 TODO/proofsb.tex
valabs

--- 2024-11-27 ICLR25/proofsb.tex
@@
 
-\section{Pseudocode and Complexity Analysis}
-
-\SetKwInput{KwInput}{Input}
-\SetKwInput{KwOutput}{Output}
-
-\begin{algorithm}[h!]
-	\caption{pMILP($K$)}
-	\label{algo1}
-	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}
-
-	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}
-
-	\For{layer $k=1 \cdots \ell$}{
-		\For{neuron $n$ in layer $k$}{
-
-			Compute $X$ a set of $K$ nodes with the highest Utility for target neuron $n$.
-
-			Run MILP$_X$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
-		}
-	}
-\end{algorithm}
-
-%We then analyse its complexity.
-%First, notice that the complexity to rnu Utility is negligible wrt the Run MILP$_X$.
-
-We provide the pseudo code for pMILP in Algorithm \ref{algo1}.
-pMILP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
-where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
-We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound.
-Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
-It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$.
-%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
-%pMILP uses 20 threads.
-
-If $K$ is sufficiently small, 
-%Algorithm \ref{algo1} invokes many MILP (e.g., using Gurobi) with a manageable number of %integer variables. 
-this approach is expected to be efficient. 
-The crucial part is thus to find few neurons which are particularly important when computing neuron $n$.
-This is where our novel Utility function outperforms previous solutions, by using an call to an (LP) solver to obtain a solution, which is novel as far as we know.
-This solutions allows to optimizing the choice of open nodes for the particular input considers, and appears significantly better than previous attempts, explaining the efficiency of the method.
-
-For comparison, refined $\beta$-Crown and refined Prima used all the nodes up to a certain layer as binary variables, which is particularly inefficient, see Table \ref{table12} and Fig.
-\ref{fig4}.
-Hence, it can only be applied to small DNNs (it is implemented only up to MNNIST 8x200), while pMILP scales to at least 20.000 neurons (CNN-B-Adv).
-\cite{DivideAndSlide} is the closest to pMILP, also implementing a choice of nodes as binary variables. However, their choice is particularly inefficient, as revealed by Table  
-\ref{tab:example1}, needing 4 times the number of open nodes for the same accuracy as our Utility function.
-
 \section{Ablation studies}
@@
 Further, we tested with the SR \cite{BaB} and FSB heuristics \cite{FSB}, that chooses nodes to branch on for BaB (Branch and Bound).
-When SE and FSR are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
+When SR and FSB are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
 \ref{fig_table3_new}: SR and FSB are worse than \cite{DivideAndSlide} for $<35$ open ReLU nodes, although unlike the latter, they can rank ReLU nodes in several layer before (which helps them a bit), and far worse than Utility.
@@
 		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
-		5  &   1.729&1.704 &1.7200&1.7197& 1.603&  1.729& 1.7133 & 1.7149 & \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.6840&1.6851&1.517& 1.696 & 1.6674& 1.6714 & \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.6502& 1.6516&1.466&  1.653& 1.6230& 1.6251 & \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.6190&1.6199&1.438 & 1.619 &1.5764 & 1.5812 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.5887&1.5886&1.427&  1.586 &1.5322 & 1.5388 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.5584&1.5604&1.425& 1.546 &  1.4914& 1.4982 & \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.5289&1.5305&1.424 & 1.502 & 1.4481 & 1.4600 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.4985&1.5001&1.424& 1.469 & 1.4070& 1.4187 & \bf 0.921 \\ \hline \hline
+		5  &   1.729&1.704 &1.6933&1.6934& 1.603&  1.729& 1.6533 & 1.6574 & \bf 1.532 \\ \hline
+		10  &  1.701 &  1.651 &1.6432&1.6393&1.517& 1.696 &  1.5672& 1.5741 & \bf  1.371\\ \hline
+		15  & 1.671 &  1.599 &1.6061& 1.5996&1.466&  1.653& 1.4954& 1.5007 & \bf  1.247\\ \hline
+		20  &  1.635 & 1.557&1.5730&1.5674&1.438 & 1.619 &1.4321 & 1.4385 & \bf  1.145\\ \hline
+		25  &  1.601 & 1.519 &1.5431&1.5405&1.427&  1.586 &1.3783 & 1.3823 & \bf 1.061\\ \hline
+		30  & 1.574 & 1.489 &1.5129&1.5151&1.425& 1.546 &  1.3328& 1.3330 & \bf  0.989 \\ \hline
+		35  &  1.542 & 1.465&1.4871&1.4899&1.424 & 1.502 & 1.2891 & 1.2934 & \bf 0.934 \\ \hline
+		40  & 1.512 & 1.447 &1.4659&1.4686&1.424& 1.469 & 1.2574& 1.2630 & \bf 0.921 \\ \hline \hline
 		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline

### 2025-01-26 CAV 2025 TODO/valabstraction.tex
valabs

@@
 
-\subsection{MILP, LP and partial MILP encodings for DNNs}
+\subsection{MILP, and LP encodings for DNNs}
 
@@
 This approach is termed the {\em LP abstraction}.
-
-In this paper, we propose to use {\em partial MILP}, to get interesting trade-offs between accuracy and runtime: 
-for a set of unstable neurons $X$, we denote by MILP$_X$ the MILP encoding where variables encoding $X$ are binary, and other variables are linear variables using the LP relaxation.
-We say that nodes in $X$ are {\em opened}.
-To further limit the number of binary variables needed for a given accuracy, we devise the same iterative approach as the box abstraction or DeepPoly \cite{deeppoly}, computing lower 
-and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a layer, that are used when computing values of the next layer, thus necessitating less variables from previous layers.
-
-The crucial factor in such an approach is to {\em select} few opened ReLU nodes in $X$ which are the most important for the accuracy.
-An extreme strategy was adopted in \cite{DivideAndSlide}, where only ReLU nodes of the immediate previous layer can be opened, and the measure to choose ReLU $a$ when computing the bounds for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.
-To obtain a more accurate measure, that 
-%can also scale to deeper layers and 
-is not limited to open nodes from the immediate previous layer, 
-{\color{blue} we invoke a folklore result \cite{alessandro} on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:}
+We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:
 
@@
 \begin{proposition}
+	\cite{alessandro}
 	\label{LP}
@@
 \end{proof}
+
+\section{Partial MILP}
+
+In this paper, we revisit the use of {\em partial MILP} (see \cite{DivideAndSlide}), to get interesting trade-offs between accuracy and runtime: 
+for a set of unstable neurons $X$, we denote by MILP$_X$ the MILP encoding where variables encoding $X$ are binary, and other variables are linear variables using the LP relaxation.
+We say that nodes in $X$ are {\em opened}.
+To further limit the number of binary variables needed for a given accuracy, we devise the same iterative approach as the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a layer, that are used when computing values of the next layer, thus necessitating less variables from previous layers.
+
+%To obtain a more accurate measure, that 
+%can also scale to deeper layers and 
+%is not limited to open nodes from the immediate previous layer,
+
+\SetKwInput{KwInput}{Input}
+\SetKwInput{KwOutput}{Output}
+
+\begin{algorithm}[h!]
+	\caption{pMILP($K$)}
+	\label{algo1}
+	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}
+
+	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}
+
+	\For{layer $k=1 \cdots \ell$}{
+		\For{neuron $n$ in layer $k$}{
+
+			Compute $X$ a set of $K$ nodes with the highest Utility for target neuron $n$.
+
+			Run MILP$_X$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
+		}
+	}
+\end{algorithm}
+
+%We then analyse its complexity.
+%First, notice that the complexity to rnu Utility is negligible wrt the Run MILP$_X$.
+
+We provide the pseudo code for pMILP in Algorithm \ref{algo1}.
+pMILP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
+where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
+We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound.
+Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
+It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$.
+This worst-case complexity compares favorably when $K<<N$ with the worst-case complexity of BaB which would be $O(out \times 2^N)$, where $out$ is the number of output neurons.
+Of course, actual complexity is always much better than the worst case, thanks to different heuristics, such as pruning, which is what happens for easy instances, for which the linear cost $N$ in pMILP (which cannot be avoided) is actually the limiting factor.
+Only experimental results can tell whether the accuracy lost using reduced variables in pMILP can be a good trade off vs efficiency, both depending on the number $K$ chosen.
+%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
+%pMILP uses 20 threads.
+
+If $K$ is sufficiently small, 
+%Algorithm \ref{algo1} invokes many MILP (e.g., using Gurobi) with a manageable number of %integer variables. 
+this approach is expected to be efficient.
+The crucial part is thus to find few neurons which are particularly important when computing neuron $n$.
+This is where our novel Utility function outperforms previous solutions, by using an call to an (LP) solver to obtain a solution, which is novel as far as we know.
+This solutions allows to optimizing the choice of open nodes for the particular input considers, and appears significantly better than previous attempts, explaining the efficiency of the method.
+
+%For comparison, refined $\beta$-Crown and refined Prima used all the nodes up to a certain layer as binary variables, which is particularly inefficient, see Table \ref{table12} and Fig.
+\ref{fig4}.
+Hence, it can only be applied to small DNNs (it is implemented only up to MNNIST 8x200), while pMILP scales to at least 20.000 neurons (CNN-B-Adv).\cite{DivideAndSlide} is the closest to pMILP, also implementing a choice of nodes as binary variables.
+However, their choice is particularly inefficient, as revealed by Table \ref{tab:example1}, needing 4 times the number of open nodes for the same accuracy as our Utility function.
+
+The crucial factor in such an approach is to {\em select} few opened ReLU nodes in $X$ which are the most important for the accuracy.
+An extreme strategy was adopted in \cite{DivideAndSlide}, where only ReLU nodes of the immediate previous layer can be opened, and the measure to choose ReLU $a$ when computing the bounds for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.

### 2025-01-27 CAV 2025 TODO/Comparison.tex
work

@@
-\section{Comparison of other methods.}
+\section{Global Ranking Functions}
 
@@
 
-Here we list the FSB formula from the paper \cite{FSB}:
+First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions, selecting a node to branch on for BaB, global ranking (GR) functions to select nodes for pMILP.
+Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP.
+They both work by backpropagating gradients vectors $\bm{\bar{\lambda}}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected.
+To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be $r(\bm{u}_k)=\frac{\UB(\bm{u}_k)}{\UB(\bm{u}_k)-\LB(\bm{u}_k)}$.
 
 \begin{align*}
-	\bm{\bar{\lambda}}_{n-1} =& -W^T_n\bm{1}, \hspace*{10ex}  	\bm{\bar{\lambda}}_{k-1} = W^T_k\big(\dfrac{[\hat{\bm{u}_k}]_+}{[\hat{\bm{u}_k}]_+-[\hat{\bm{l}_k}]_-}\odot\bm{\bar{\lambda}}_{k}\big) \hspace*{-10ex}  &k\in [2,n-1]\\
-	\bm{s}_{SR} =& \lvert\max\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert &\\
-	&\odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}&k\in [1,n-1]\\
-	\bm{s}_{FSB} =& \lvert\min\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert &\\
-	&\odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}&k\in [1,n-1]\\
+\bm{\bar{\lambda}}_{n-1} = -W^T_n\bm{1}, \hspace*{4ex}  	\bm{\bar{\lambda}}_{k-1} = W^T_k\big(\dfrac{[\hat{\bm{u}_k}]_+}{[\hat{\bm{u}_k}]_+-[\hat{\bm{l}_k}]_-}\odot\bm{\bar{\lambda}}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
 \end{align*}
 
-\begin{figure}[t!]
+Then, the scoring functions $\bm{s}_{SR}$ and $\bm{s}_{FSB}$ for ReLUs in layer $k$ are computed by approximating how each node would impact the neurons in layer $n$, by also factoring in the bias $\bm{b}_k$:
+
+\begin{align*}
+	\bm{s}_{SR}(k) =& \lvert\max\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert \odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0} \\
+	\bm{s}_{FSB}(k) =& \lvert\min\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert \odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}
+\end{align*}
+
+\begin{figure}[b!]
 	\centering

### 2025-01-27 CAV 2025 TODO/valabstraction.tex
work

@@
 this approach is expected to be efficient. 
-The crucial part is thus to find few neurons which are particularly important when computing neuron $n$.
-This is where our novel Utility function outperforms previous solutions, by using an call to an (LP) solver to obtain a solution, which is novel as far as we know.
+%The crucial part is thus to find few neurons which are particularly important when computing neuron $n$. 
+%This is where our novel Utility function outperforms previous solutions, by using an call to an (LP) solver to obtain a solution, which is novel as far as we know.
 This solutions allows to optimizing the choice of open nodes for the particular input considers, and appears significantly better than previous attempts, explaining the efficiency of the method.
-
 %For comparison, refined $\beta$-Crown and refined Prima used all the nodes up to a certain layer as binary variables, which is particularly inefficient, see Table \ref{table12} and Fig.
@@
 However, their choice is particularly inefficient, as revealed by Table \ref{tab:example1}, needing 4 times the number of open nodes for the same accuracy as our Utility function.
-
-The crucial factor in such an approach is to {\em select} few opened ReLU nodes in $X$ which are the most important for the accuracy.
-An extreme strategy was adopted in \cite{DivideAndSlide}, where only ReLU nodes of the immediate previous layer can be opened, and the measure to choose ReLU $a$ when computing the bounds for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.
+The crucial factor in such an approach is to {\em select} few opened ReLU nodes in $X$ which are the most important for the accuracy. An extreme strategy was adopted in 
+\cite{DivideAndSlide}, where only ReLU nodes of the immediate previous layer can be opened, and the measure to choose ReLU $a$ when computing the bounds for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$.

### 2025-01-27 CAV 2025 TODO/Comparison.tex
comparison

@@
 
-Then, the scoring functions $\bm{s}_{SR}$ and $\bm{s}_{FSB}$ for ReLUs in layer $k$ are computed by approximating how each node would impact the neurons in layer $n$, by also factoring in the bias $\bm{b}_k$:
+Then, the scoring functions $\bm{s}_{SR}$ and $\bm{s}_{FSB}$ for ReLUs in layer $k$ are computed by approximating how each node would impact the neurons in layer $n$, by also factoring in the bias $\bm{b}_k$ in different ways:
 
 \begin{align*}
-	\bm{s}_{SR}(k) =& \lvert\max\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert \odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0} \\
-	\bm{s}_{FSB}(k) =& \lvert\min\{0,\bm{\bar{\lambda}}_{k}\odot\bm{b}_{k}\}-\frac{\hat{\bm{u}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}}_k\odot\bm{\bar{\lambda}}_{k}\odot\bm{{b}}_{k}+\frac{\hat{\bm{u}}_k\odot\hat{\bm{l}}_k}{\hat{\bm{u}}_k-\hat{\bm{l}}_k}\odot[\bm{\bar{\lambda}}_{k}]_+\rvert \odot\bm{1}_{\hat{\bm{u}}_k>0,\hat{\bm{l}}_k<0}
+	\bm{s}_{SR}(k) =& %\bm{1}_{\bm{u}_k>0,\bm{l}_k<0} \odot
+	\Biggl\lvert r(\bm{u}_k) \odot \LB(\bm{u}_k) \odot \max(\bm{\lambda}_{k},0)
+	+ \max\{0,\bm{\lambda}_{k}\odot\bm{b}_{k}\}-r(\bm{u}_k) \odot\bm{\lambda}_{k}\odot\bm{{b}}_{k}
+	\Biggr\rvert  \\
+	\bm{s}_{FSB}(k) =& \Biggl\lvert r(\bm{u}_k) \odot \LB(\bm{u}_k) \odot \max(\bm{\lambda}_{k},0)
+	+ \min\{0,\bm{\lambda}_{k}\odot\bm{b}_{k}\}-r(\bm{u}_k) \odot\bm{\lambda}_{k}\odot\bm{{b}}_{k}
+	\Biggr\rvert
 \end{align*}
+
+In case where the bias is 0, then there is no difference between $s_{SR}$ and $s_{FSB}$.
+Then, unstable ReLU (with $\LB(u_k) < 0 < \UB(u_k)$) are ranked using these scores, to select the most important ReLUs, as stable ReLUs are linear, thus they are already treated correctly.
+
+Consider the example in Fig. \ref{img:FSB_example}.
+We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
+Let us do a case analysis:
+The most favorable cases are $c < 0 < d$ and $d < 0 < c$: 
+as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
+Now, $a$ and $\hat{a}$ need to be minimized in order to maximize $z$, because $cd <0$. 
+For the triangle approximation, having a value $sol(a)$ for $a$, the minimal value for $\hat{a}$ is $\ReLU(sol(a))$.
+If we open $a$, then the value for $\hat{a}$ will also be $\ReLU(sol(a))$.
+That is, opening this ReLU is not helping in the approximation of $z$, as correctly predicted by the score.
+
+Case $c>0,d>0$: $s_{FSB}(a)=\frac{cd}{4}$.
+Indeed, the value of $a,\hat{a},b,\hat{b}$ should be maximized to maximize the value of $z$, because $W_{bz}=d>0$ and $W_{ab}=c>0$.
+Hence each variation of $b$ by $\Delta(b)$ will have an impact $r(b) \cdot \Delta(b)$.
+Now, let us call $sol(a)$ the maximum value for $a$.
+Then the maximum value for $\hat{a}$ is $r(a)\cdot (sol(a)-LB(a))$ according to the triangle approximation when $\ReLU(a)$ is not opened. Now, if $\ReLU(a)$ is opened, then 
+the value of $\hat{a}$ is $\ReLU(sol(a))$: the difference is at most $r(a) \cdot LB(a) = \frac{1}{2}$.
+Going through $b$, the difference is at most $\frac{c}{2}$, which means a difference at most $\frac{c}{4}$ for $\hat(b)$, considering the upper bound of the triangle approximation, meaning a difference at most $\frac{cd}{4}$, which is what is computed by
+$s_{FSB}(a)$. Of course, the difference of opening $\ReLU(a)$ could also be 0 e.g. if $\sol(a)=\LB(a)$ or $\sol(a)=\UB(a)$.
+
+The last case is the most problematic: 
+Case $c<0,d<0$, implying that $s_{FSB}(a)=\frac{cd}{4}$.
 
@@
 
-		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$[-1,0.5]$};
+		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$[-1,1]$};
 
@@
 
-		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
-		\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$-10$};
+		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$c$};
+		\draw[->,thick] (input1) -- (hidden2)node[near start, below] {$-10$};
 
@@
 
-		\draw[->,thick] (hidden4) -- (hidden5)node[near start, below] {$1$};
+		\draw[->,thick] (hidden4) -- (hidden5)node[near start, above] {$1$};
 		\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
@@
 
-		\draw[->,thick] (output1) -- (output3)node[near start, below] {$-100$};
+		\draw[->,thick] (output1) -- (output3)node[near start, above] {$d$};
 		\draw[->,thick] (output2) -- (output3)node[near start, below] {$1$};
@@
 		% Draw axes
-	\draw[->] (-5,0) -- (4,0) node[right] {$x$};
-	\draw[->] (0,-1) -- (0,3) node[above] {$y$};
+		\draw[->] (-5,0) -- (4,0) node[right] {$b$};
+		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{b}$};
 
@@
 		\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
-	\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(0.5,-0.4)}] {$y = \ReLU(x)$};
-	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-5,-1.5)}] {$y = \frac{\UB}{\UB-\LB} x-\frac{\UB\cdot\LB}{\UB-\LB}$};
+		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{b} = \ReLU(b)$};
+		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-6.5,-2)}] {$\hat{b} = \frac{\UB}{\UB-\LB} (b-\LB)$};
+
+		% Add labels
+		\draw[dashed] (2.5,0) -- (2.5,2.5) -- (0,2.5); % Optional grid
+		\node[below left] at (0,0) {$0$};
+
+		% Add tick marks
+
+		\foreach \x in {2.5}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\UB$};
+		\foreach \x in {-3}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\LB$};
+
+		\foreach \y in {2.5}
+		\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {$\UB$};
+
+	\end{tikzpicture}
+		\caption{Triangle approximation}
+	\label{img:FSB}
+	\end{figure}
+
+\begin{figure}[t!]
+\begin{tikzpicture}[scale=1, >=stealth]
+
+	% Draw axes
+	\draw[->] (-5,0) -- (4,0) node[right] {$b$};
+	\draw[->] (0,-1) -- (0,3) node[above] {$\hat{b}$};
+
+	% Draw ReLU function
+	\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
+	\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{b} = \ReLU(b)$};
+	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-6.5,-2)}] {$\hat{b} = \frac{\UB}{\UB-\LB} b-\frac{\UB\cdot\LB}{\UB-\LB}$};
 
@@
 	\caption{}
-\label{img:Utility}
+\label{img:Utility2}
 \end{figure}

### 2025-01-27 CAV 2025 TODO/Comparison.tex
update

@@
 Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP.
-They both work by backpropagating gradients vectors $\bm{\bar{\lambda}}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected.
+They both work by backpropagating gradients vectors $\bm{\lambda}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected.
 To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be $r(\bm{u}_k)=\frac{\UB(\bm{u}_k)}{\UB(\bm{u}_k)-\LB(\bm{u}_k)}$.
@@
 \begin{align*}
-\bm{\bar{\lambda}}_{n-1} = -W^T_n\bm{1}, \hspace*{4ex}  	\bm{\bar{\lambda}}_{k-1} = W^T_k\big(\dfrac{[\hat{\bm{u}_k}]_+}{[\hat{\bm{u}_k}]_+-[\hat{\bm{l}_k}]_-}\odot\bm{\bar{\lambda}}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
+\bm{\lambda}_{n-1} = -W^T_n\bm{1}, \hspace*{4ex}  	\bm{\lambda}_{k-1} = W^T_k\big(\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))}\odot\bm{\lambda}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
 \end{align*}

### 2025-01-27 CAV 2025 TODO/Comparison.tex
update

@@
 
-First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions, selecting a node to branch on for BaB, global ranking (GR) functions to select nodes for pMILP.
+First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions (replacing the symbols from the original paper with those used in our paper.), selecting a node to branch on for BaB, global ranking (GR) functions to select nodes for pMILP.
 Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP.
@@
 \begin{align*}
-\bm{\lambda}_{n-1} = -W^T_n\bm{1}, \hspace*{4ex}  	\bm{\lambda}_{k-1} = W^T_k\big(\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))}\odot\bm{\lambda}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
+\bm{\lambda}_{n-1} = -{(\bm{W}^n)}^T\bm{1}, \hspace*{4ex}  	\bm{\lambda}_{k-1} = {(\bm{W}^k)}^T\big(\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))}\odot\bm{\lambda}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
 \end{align*}
@@
 
-	\draw (-1,0.1) -- (-1,-0.1) node[below] {$\sol(a)$};
+	\draw (-1,0.1) -- (-1,-0.1) node[below] {$\sol(b)$};
 	\draw[dashed] (-1,0) -- (-1,0.9) -- (0,0.9);
-	\draw (-0.1,0.9) -- (0.1,0.9) node[right, shift={(-0.1,0.13)}] {$\sol(\hat{a})$};
-	\node at (-0.5,0.4) {$\Delta(a)$};
+	\draw (-0.1,0.9) -- (0.1,0.9) node[right, shift={(-0.1,0.13)}] {$\sol(\hat{b})$};
+	\node at (-0.5,0.4) {$\Delta(b)$};
 

### 2025-01-27 CAV 2025 TODO/Comparison.tex
comparison

@@
 They both work by backpropagating gradients vectors $\bm{\lambda}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected.
-To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be $r(\bm{u}_k)=\frac{\UB(\bm{u}_k)}{\UB(\bm{u}_k)-\LB(\bm{u}_k)}$.
+To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be
+$r(\bm{u}_k)=\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))} \in [0,1]$.
 
 \begin{align*}
-\bm{\lambda}_{n-1} = -{(\bm{W}^n)}^T\bm{1}, \hspace*{4ex}  	\bm{\lambda}_{k-1} = {(\bm{W}^k)}^T\big(\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))}\odot\bm{\lambda}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
+\bm{\lambda}_{n-1} = -{(\bm{W}^n)}^T\bm{1}, \hspace*{4ex}  	\bm{\lambda}_{k-1} = {(\bm{W}^k)}^T\big( r(\bm{u}_k) \odot\bm{\lambda}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
 \end{align*}
@@
 
-Consider the example in Fig. \ref{img:FSB_example}.
-We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
-Let us do a case analysis:
-The most favorable cases are $c < 0 < d$ and $d < 0 < c$: 
-as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
-Now, $a$ and $\hat{a}$ need to be minimized in order to maximize $z$, because $cd <0$. 
-For the triangle approximation, having a value $sol(a)$ for $a$, the minimal value for $\hat{a}$ is $\ReLU(sol(a))$.
-If we open $a$, then the value for $\hat{a}$ will also be $\ReLU(sol(a))$.
-That is, opening this ReLU is not helping in the approximation of $z$, as correctly predicted by the score.
-
-Case $c>0,d>0$: $s_{FSB}(a)=\frac{cd}{4}$.
-Indeed, the value of $a,\hat{a},b,\hat{b}$ should be maximized to maximize the value of $z$, because $W_{bz}=d>0$ and $W_{ab}=c>0$.
-Hence each variation of $b$ by $\Delta(b)$ will have an impact $r(b) \cdot \Delta(b)$.
-Now, let us call $sol(a)$ the maximum value for $a$.
-Then the maximum value for $\hat{a}$ is $r(a)\cdot (sol(a)-LB(a))$ according to the triangle approximation when $\ReLU(a)$ is not opened. Now, if $\ReLU(a)$ is opened, then 
-the value of $\hat{a}$ is $\ReLU(sol(a))$: the difference is at most $r(a) \cdot LB(a) = \frac{1}{2}$.
-Going through $b$, the difference is at most $\frac{c}{2}$, which means a difference at most $\frac{c}{4}$ for $\hat(b)$, considering the upper bound of the triangle approximation, meaning a difference at most $\frac{cd}{4}$, which is what is computed by
-$s_{FSB}(a)$. Of course, the difference of opening $\ReLU(a)$ could also be 0 e.g. if $\sol(a)=\LB(a)$ or $\sol(a)=\UB(a)$.
-
-The last case is the most problematic: 
-Case $c<0,d<0$, implying that $s_{FSB}(a)=\frac{cd}{4}$.
-
-\begin{figure}[b!]
+\begin{figure}[t!]
 	\centering
@@
 
-		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$c$};
+		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
 		\draw[->,thick] (input1) -- (hidden2)node[near start, below] {$-10$};
@@
 
-		\draw[->, thick] (hidden3) -- (hidden5) node[near start, above] {$1$};
+		\draw[->, thick] (hidden3) -- (hidden5) node[near start, above] {{\color{red}$c$}};
 
@@
 
-		\draw[->,thick] (output1) -- (output3)node[near start, above] {$d$};
+		\draw[->,thick] (output1) -- (output3)node[near start, above] {{\color{red}$d$}};
 		\draw[->,thick] (output2) -- (output3)node[near start, below] {$1$};
@@
 	\end{tikzpicture}
-	\caption{}
+	\caption{A simple example with parametric weights {\color{red}$c$} and {\color{red}$d$}}
 	\label{img:FSB_example}
@@
 
+Consider the example in Fig. \ref{img:FSB_example}. It has no bias so $s_{SR}=s_{FSB}$.
+We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
+Let us do a case analysis:
+The most favorable cases are $c < 0 < d$ and $d < 0 < c$: 
+as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
+Now, $a$ and $\hat{a}$ need to be minimized in order to maximize $z$, because $cd <0$. 
+For the triangle approximation (see Fig.
+\ref{triangle}), having a value $sol(a)$ for $a$, the minimal value for $\hat{a}$ is $\ReLU(sol(a))$.
+If we open $a$, then the value for $\hat{a}$ will also be $\ReLU(sol(a))$.
+That is, opening this ReLU is not helping in the approximation of $z$, as correctly predicted by the score $s_{FSB}(a)= 0$.
+
+Case $c>0,d>0$: $s_{FSB}(a)=\frac{cd}{4}$.
+The value of $a,\hat{a},b,\hat{b}$ should be maximized to maximize the value of $z$, because $W_{bz}=d>0$ and $W_{ab}=c>0$. 
+%Each variation of $b$ by $\Delta(b)$ will have an impact $r(b) \cdot \Delta(b)=\frac{\Delta(b)}{2}$ on the value of $\hat{b}$, and thus $\frac{d \Delta(b)}{2}$ on $z$. 
+Now, let us call $sol(a)$ the maximum value for $a$.
+The maximum value for $\hat{a}$ is $r(a)\cdot (sol(a)-LB(a))$ according to the triangle approximation when $\ReLU(a)$ is not opened. Now, if $\ReLU(a)$ is opened, then 
+the value of $\hat{a}$ is $\ReLU(sol(a))$: the difference is at most $r(a) \cdot LB(a) = \frac{1}{2}$.
+The difference $\Delta(b)$ for the value of $b$ is thus at most $\frac{c}{2}$, which means a difference at most $\frac{c}{4}$ for $\hat{b}$, using the upper function of the triangle approximation of rate $r(b)$, as the value of $\hat{b}$ should be maximized.
+This means a difference of at most $\frac{cd}{4}$ on the value of $z$, which is what is computed by $s_{FSB}(a)$.
+Of course, the difference of opening $\ReLU(a)$ could also be 0 e.g.
+if $\sol(a)=\LB(a)$ or $\sol(a)=\UB(a)$.
+
+The last case is the most problematic: 
+Case $c<0,d<0$, implying that $s_{FSB}(a)=\frac{cd}{4}$, because $cd >0$.
+As for the case of $c>0, d>0$, opening $\ReLU(a)$ will have an impact on the value of $\hat{a}$,
+at most $\frac{1}{2}$, and hence a change $\Delta(b)$ of at most $\frac{c}{4}$ on the value of $b$.
+However, as $d<0$, value of $\hat{b}$ needs to be minimized. That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$.
+That is, the change in $\hat{b}$ will be either 0 in case $sol(b)<0$ (phase 0 of ReLU),
+or $\Delta(b)<\frac{c}{2}$ otherwise (phase Id of ReLU), that is, $z$ will be modified by 
+either 0 or $d \Delta(b)<\frac{cd}{2}$, as compared with $s_{FSB}(a)=\frac{cd}{4}$.
+
 \begin{figure}[t!]
-	\begin{tikzpicture}[scale=1, >=stealth]
+	\begin{tikzpicture}[scale=0.8, >=stealth]
 
 		% Draw axes
-		\draw[->] (-5,0) -- (4,0) node[right] {$b$};
-		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{b}$};
+		\draw[->] (-5,0) -- (4,0) node[right] {$a$};
+		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{a}$};
 
@@
 		\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
-		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{b} = \ReLU(b)$};
-		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-6.5,-2)}] {$\hat{b} = \frac{\UB}{\UB-\LB} (b-\LB)$};
+		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{a} = \ReLU(a)$};
+		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-6.5,-2)}] {$\hat{a} = \frac{\UB}{\UB-\LB} (a-\LB)$};
 
@@
 		\caption{Triangle approximation}
-	\label{img:FSB}
+	\label{triangle}
 	\end{figure}
 
+We call {\em global rankings} (GR) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution $sol(a),sol(b)$ values.
+This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.
+
+\iffalse
 \begin{figure}[t!]
@@
 	\caption{}
-\label{img:Utility2}
+\label{img:Utility}
 \end{figure}
+\fi
 
+\iffalse
 \subsection*{An example when FSB is not accurate}
@@
 The plot shows that our Utility function is significantly better than FSB, and other methods.
+\fi

### 2025-01-27 CAV 2025 TODO/Comparison.tex
scale
compar

@@
 As for the case of $c>0, d>0$, opening $\ReLU(a)$ will have an impact on the value of $\hat{a}$,
-at most $\frac{1}{2}$, and hence a change $\Delta(b)$ of at most $\frac{c}{4}$ on the value of $b$.
-However, as $d<0$, value of $\hat{b}$ needs to be minimized. That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$.
-That is, the change in $\hat{b}$ will be either 0 in case $sol(b)<0$ (phase 0 of ReLU),
+at most $\frac{1}{2}$, and hence a change $\Delta(b)$ of at most $\frac{c}{2}$ on the value of $b$.
+However, as $d<0$, value of $\hat{b}$ needs to be minimized.
+That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$, and the change in $\hat{b}$ will be either 0 in case $sol(b)<0$ (phase 0 of ReLU),
 or $\Delta(b)<\frac{c}{2}$ otherwise (phase Id of ReLU), that is, $z$ will be modified by 
@@
 \begin{figure}[t!]
-	\begin{tikzpicture}[scale=0.8, >=stealth]
+	\begin{tikzpicture}[scale=1, >=stealth]
 

### 2025-01-27 CAV 2025 TODO/formula.tex
formula

--- 2024-11-26 ICLR25/formula.tex
@@
-\section{Utility function choosing neurons important for accuracy.}
+\section{Solution-Aware Scoring.}
 
@@
 
-In this section, we evaluate how each ReLU would impact the accuracy if encoded as a binary or a linear variable, using Proposition \ref{LP}.
-A ReLU is said {\em open} when it is represented as a binary variable.
-For $X$ a set of open ReLUs, we denote by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.
-
-{\color{blue} 
-Usually, heuristics to choose $X$ are based on evaluating the {\em sensitivity} of a neuron $z$ wrt the ReLU nodes,
-that is how much a ReLU value impacts the value of $z$, and rank the ReLU nodes accordingly.
-This is the case of \cite{DivideAndSlide}, but also more generally of heuristics for BaB \cite{BaB,ferrari2022complete}, such as SR and FSB.
-%Our Utility function does not follow this approach.
-Instead, Utility considers the {\em improvement} from opening a neuron $n$, that is the difference for the value of $z$ between considering $\ReLU(n)$ exactly or using its LP relaxation $\LP(n)$.
-Indeed, it is not rare that
-$z$ is sensitive to ReLU node $n$, and yet $\LP(n)$ already provides an accurate approximation of $\ReLU(n)$.
-In this case, usual heuristics would open $n$, while it would only improve the value of $z$ in a limited way.
-}
+In this section, we propose a novel {\em Solution-Aware Scoring} (SAS),
+to evaluate accurately how opening a ReLU impacts the accuracy.
+To do so, SAS considers explicitly the {\em difference} $\Delta(z)$ on the value of target node $z$ from opening $\ReLU(a)$, that is the difference for the value of $z$ between considering $\ReLU(a)$ exactly or using its LP relaxation $\LP(a)$, using the solution to a unique full LP call, which is resonnably fast to obtain.
+To compute $\Delta(z)$, intermediate $\Delta(b),\Delta(\hat{b})$ are computed inductively.
+%Indeed, it is not rare that $z$ is sensitive to ReLU node $n$, and yet $\LP(n)$ already provides an accurate approximation of $\ReLU(n)$.
+%In this case, usual heuristics would open $n$, while it would only improve the value of $z$ in a limited way.
 
@@
 {\color{blue} 
-The main novelty of our Utility function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Table \ref{tab:example1}).
+The main novelty of our SAS function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Table \ref{tab:example1}).
 
@@
 
-For a neuron a $a$ two layers before $\ell_z$, 
+Recall the rate $r(b)=\frac{\max(0,\UB(b))}{\max(0,\UB(b))-\min(0,\LB(b))} \in [0,1]$.
+For a neuron $a$ two layers before $\ell_z$, 
 $b$ denoting neurons in the layer $\ell$ just before $\ell_z$, 
@@
 	\begin{cases}
-		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
+		%\Delta(b),  & \text{if } W_{bz} > 0 \text{ and } \LB(b)\geq 0\\
+		r(b)\Delta(b),%\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  
+		&\text{if }W_{bz} > 0 \\ % \text{ and } \LB(b)<0\\
 		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
@@
 
+%\begin{tikzpicture}[scale=1, >=stealth]
+%	
+%	% Draw axes
+%	\draw[->] (-5,0) -- (4,0) node[right] {$x$};
+%	\draw[->] (0,-1) -- (0,3) node[above] {$y$};
+%	
+%	% Draw ReLU function
+%	\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
+%	\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(0.5,-0.4)}] {$y = \ReLU(x)$};
+%	\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-0.5,0.4)}] {$y = \frac{\UB}{\UB-\LB} x-\frac{\UB\LB}{\UB-\LB}$};
+%	
+%%	% Add labels
+%%	\draw[dashed] (2,0) -- (2,2) -- (0,2); % Optional grid
+%%	\node[below left] at (0,0) {$0$};
+%%	
+%%	% Add tick marks
+%%	\foreach \x in {1,2}
+%%	\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {\x};
+%%	\foreach \y in {1,2}
+%%	\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {\y};
+%	
+%\end{tikzpicture}
+
 %We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}.
 
-Informally, $\Delta(\hat{a}), \Delta(b), \Delta(\hat{b})$ approximate the improvement on the accuracy of $\hat{a}, b, \hat{b}$ when computing $\ReLU(a)$ 
-using the exact MILP encoding instead of LP. Using Proposition \ref{LP}, we show:
+%Informally, $\Delta(\hat{a}), \Delta(b), \Delta(\hat{b})$ approximate the improvement on the accuracy of $\hat{a}, b, \hat{b}$ when computing $\ReLU(a)$ using the exact MILP encoding instead of LP.
+
+Notice that $\Utility$ does not need to consider bias explicitly, unlike $s_{FSB},s_{SR}$,
+as they are already accounted for in the solution considered. 
+There are two main differences with $s_{FSB}$: 
+First, $\Delta(\hat{a})$ is defined exactly, with $\ReLU(\sol(a))-\sol(\hat{a})$,
+whereas the corresponding $\Delta_{FSB}(\hat{a})$ is approximated as $\LB(a) r(a)$, 
+which is only an upper bound of $\ReLU(\sol(a))-\sol(\hat{a})$.
+More importantly, the corresponding $\Delta_{FSB}(\hat{b})$ is always $r(b) \Delta(b)$, whereas SAS adapts to the case when $W_{bz}<0$, correctly considering the 0 phase of $ReLU(b)$ when $\sol(b)\geq 0$, and the ID phase when $\sol(b)<0$.
+Assuming that the solution to maximize $z$ does not change when opening $\ReLU(a)$
+on neurons independant of $a$, then $\Utility$ is exact.
+This is not the case for $s_{FSB}$ because of the two previously mentionned cases.
+Further, even when the global solution changes, we can show that $\Utility$ is a safe overapproximation, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b) > 0$):
 }
@@
 Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$. 
-In particular, for all nodes $a$ with $W_{az}< 0$,
-this node will have the smallest $\Utility\_\max\nolimits^z(a)=0$ (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$.
-This is one striking difference (but not the only one) with choosing utility based on
-$|W_{az}|$ \cite{DivideAndSlide}.
+In particular, for all nodes $a$ with $\Utility\_\max\nolimits^z(a)=0$, 
+we are sure that this node is not having any impact on $\Sol\_\max_{\{a\}}^z(z)$. 
+%This is one striking difference (but not the only one) with choosing utility based on 
+%$|W_{az}|$ \cite{DivideAndSlide}.
 
@@
 
+While $\Utility$ is a priori a more accurate way to select neurons to open in partial MILP (that will be verified in Table \ref{tab:example}), global scoring functions have two advantages: first, they are faster to compute (a unique backpropagation is sufficient, while SAS needs one full LP call to recover the solution, plus a forward propagation for each node $a$).
+This is not an issue for selecting nodes for partial MILP, as there is a single selection step.
+But this would be potentially more problematic for choosing branching nodes.
+A trade off could be to precompute $s_{FSB}$ and only on the most promising nodes run $\Utility$.
+The second shortcoming is the other side of the coin to consider improvement local to a solution: in the case of branching, one of the branch imposes to be far from the solution, 
+while global scoring is as (in)accurate for both branches. We will verify that using GS for ordering nodes after the SAS selection is actually more efficient, for this very reason.
+
 \iffalse

### 2025-01-27 CAV 2025 TODO/experiments.tex
exp

@@
 We implemented \toolname\ in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems.
-We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz, 5nm) with 256 GB of main memory and 2 NVIDIA RTX 4090.
-
+We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
 The  objectives of our evaluation was to answer the following  questions:
@@
 
-\subsection{Evaluation of the Utility function to choose neurons to open}
+\subsection{Comparison between different scoring functions.}
 
 %The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-To measure the impact of the utility function to select neurons to open, we focused on a small hard DNN, namely $5\times 100$, so as to be able to compute exact bounds for the first few layers using a full MILP encoding of the DNN for comparison purpose.
-We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K=|X|$ the size of set $X$.
-To measure the accuracy, we measure the uncertainty of all nodes in a layer:
+To measure the impact of the scoring function to select neurons to open, 
+we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
+We tested over the $\vx=37$th image in the CIFAR dataset.
+To measure the accuracy, we measure the uncertainty of all nodes in the 4th layer:
 the uncertainty of a node is the range between its computed lower and upper bound. 
@@
 Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB - \LB$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$
+
+\begin{figure}[b!]
+	\centering
+	\vspace*{-0.3cm}
+	\includegraphics[height=7cm]{open.png}.
+	\vspace*{-0.4cm}
+	\caption{Average uncertainty of pMILP for neurons of the fourth layer of CNN-B-Adv, 
+	when opening between 0 and 30 ReLUs, chosen randomly vs Huang \cite{DivideAndSlide} vs 
+	$s_{FSB}$ vs $\Utility$ (with time-out=900s).}
+	\label{fig_table3}
+\end{figure}
 
@@
 
-We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
+%We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
 The bounds for nodes of the first two layers are computed exactly using the full MILP encoding.
-We report in Figure \ref{fig_table3} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our {\bf Utility} function, compared with a random choice, both for nodes exclusively from the previous Layer 2 or from both Layers 1 and 2.
-We compared with choosing based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$ \cite{DivideAndSlide}, opening nodes in Layer 2 only.
+We report in Figure \ref{fig_table3} the average uncertainty of $\MILP_X$ following the 
+choice of the $K$ heaviest neurons of SAS, compared with a random choice, with Huang \cite{DivideAndSlide}, based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$, and with GS.
 
@@
 
-The Utility function selects very important neurons:
- to achieve the same accuracy than \cite{DivideAndSlide}, $2.5$ time fewer nodes (10 vs 25) are necessary when picking in the same previous Layer 2.
-The ability from {\bf Utility} to compare neurons from different layers enables even better frugality: $4$ time fewer nodes (5 vs 20, 10 vs 40) are necessary to reach the same accuracy than \cite{DivideAndSlide}.
-Overall, choosing 35 neurons by {\bf Utility} improves accuracy by $95\%$ of what can be done if all $|X|=116$ nodes are opened compared with LP (corresponding to $|X|=0$).
+Overall, SAS is more accurate than GS, more accurate than Huang, more accurate than random choice of variables. SAS significantly outperforms other solutions, 
+with around 3 times less binary variables for the same accuracy (10 v 30, 6 vs 16).
+Each individual node of the last layer display a similar pattern, and the pattern is similar for different images (not displayed).
 
-\begin{figure}[h!]
-	\centering
-	\vspace*{-0.3cm}
-	\includegraphics[height=8cm]{Plot for table 3}.
-	\vspace*{-0.4cm}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs random choice.}
-	\label{fig_table3}
-\end{figure}
+We also experimented on fixing an ordering on variable in Gurobi, with a fixed selection of nodes by SAS.
+Indeed, Gurobi relies on a BaB procedure to compute bounds.
+The standard Gurobi procedure is adaptative in each branch.
+We compared vs the fix order provided by SAS, as well as the fixed order provided by FSB, for both accuracy and runtime (lower is better).
+
+We obtained the following:
+Gurobi order:
+30nodes : 1, 3.987387317631171, 260.4883162975311, 
+45nodes : 1, 4.015747873604205, 265.53007888793945, 
+60nodes : 1, 4.053423060042739, 262.1407461166382,
+
+FSB order:
+30nodes : 1, 3.9879578118285317, 246.69000577926636, 
+45nodes : 1, 4.018561938508719, 247.65485453605652
+60nodes : 1, 4.032634363809192, 247.81136560440063,
+
+SAS order:
+30nodes : 1, 3.9933637922653995, 264.4269104003906, 
+45nodes : 1, 4.0307741092892035, 266.20811343193054, 
+60nodes : 1, 4.060220618788057, 262.93414759635925,
+
+Here,  SAS is as efficient as Gurobi, although the ordering is fixed, meaning that the ordering compensates for the non adaptivity.
+However, the fixed GS ordering (with the SAS selection) is even better, with slightly better accuracy and lower runtime.
+As explained earlier, this is due to the fact that global ordering is preferable when branching on choices far from the optimal solution.
 

### 2025-01-27 CAV 2025 TODO/formula.tex
exp

@@
 Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
-We write $n < z$ if neuron {\color{blue} $n$ is} on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
+We write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
 We denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$.
@@
 {\color{blue} 
-The main novelty of our SAS function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Table \ref{tab:example1}).
+The main novelty of our SAS function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Fig.
+\ref{fig_table3}).
 
@@
 
-We can proceed inductively in the same way to define $\Utility\_\max^z(a)$ for deeper neurons $a$.
+We proceed inductively to define $\Utility\_\max^z(a)$ for deeper neurons $a$.
 
-While $\Utility$ is a priori a more accurate way to select neurons to open in partial MILP (that will be verified in Table \ref{tab:example}), global scoring functions have two advantages: first, they are faster to compute (a unique backpropagation is sufficient, while SAS needs one full LP call to recover the solution, plus a forward propagation for each node $a$).
+While $\Utility$ is a priori a more accurate way to select neurons to open in partial MILP (that will be verified in Fig.
+\ref{fig_table3}), global scoring functions have two advantages: first, they are faster to compute (a unique backpropagation is sufficient, while SAS needs one full LP call to recover the solution, plus a forward propagation for each node $a$).
 This is not an issue for selecting nodes for partial MILP, as there is a single selection step.
-But this would be potentially more problematic for choosing branching nodes.
-A trade off could be to precompute $s_{FSB}$ and only on the most promising nodes run $\Utility$.
-The second shortcoming is the other side of the coin to consider improvement local to a solution: in the case of branching, one of the branch imposes to be far from the solution, 
-while global scoring is as (in)accurate for both branches. We will verify that using GS for ordering nodes after the SAS selection is actually more efficient, for this very reason.
+This would be potentially problematic for choosing branching nodes in BaB, at each branch.
+A trade off could be to precompute FSB and only on the most promising nodes run $\Utility$.
+The second shortcoming is the other side of the coin to consider improvement local to a solution: in the case of branching, one of the branch imposes to be far from the solution and $\Utility$ is not accurate on that branch, while global scoring is as (in)accurate for both branches.
+We will verify that using GS for ordering nodes after the SAS selection is actually more efficient, for this very reason.
 

### 2025-01-28 CAV 2025 TODO/experiments.tex
exp

@@
 We then average the uncertainty among all the nodes of the layer.
-Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB - \LB$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$
+Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB(a) - \LB(a)$. The average uncertainty of layer $\ell$ is 
+$$\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$$
 
@@
 with around 3 times less binary variables for the same accuracy (10 v 30, 6 vs 16).
-Each individual node of the last layer display a similar pattern, and the pattern is similar for different images (not displayed).
+Each individual node of the last layer displays a similar pattern, and the pattern is similar for different images (not displayed).
 
-We also experimented on fixing an ordering on variable in Gurobi, with a fixed selection of nodes by SAS.
+We also experimented in Table \ref{table.order} on fixing an ordering on variable in Gurobi, with a fixed selection of nodes by SAS.
 Indeed, Gurobi relies on a BaB procedure to compute bounds.
@@
 
-We obtained the following:
-Gurobi order:
-30nodes : 1, 3.987387317631171, 260.4883162975311, 
-45nodes : 1, 4.015747873604205, 265.53007888793945, 
-60nodes : 1, 4.053423060042739, 262.1407461166382,
-
-FSB order:
-30nodes : 1, 3.9879578118285317, 246.69000577926636, 
-45nodes : 1, 4.018561938508719, 247.65485453605652
-60nodes : 1, 4.032634363809192, 247.81136560440063,
-
-SAS order:
-30nodes : 1, 3.9933637922653995, 264.4269104003906, 
-45nodes : 1, 4.0307741092892035, 266.20811343193054, 
-60nodes : 1, 4.060220618788057, 262.93414759635925,
+\begin{table}[h!]	
+	\centering
+	\begin{tabular}{|c||c c|c c|c c|}
+		\hline
+		  & \multicolumn{2}{c|}{30 open ReLUs} & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs} \\ 
+		 order & uncert & time & uncert & time & uncert & time \\
+		\hline \hline
+		Gurobi &   3.987  & 260s  & 4.016 & 266s& 4.053 & 262s\\ 
+		SAS &   3.989  & 264s  & 4.031 & 266s& 4.060 & 263s\\
+		FSB &   3.988  & {\bf 246s}  & 4.018 & {\bf 248s}& 4.033 & {\bf 248s}\\ \hline
+	\end{tabular}
+	\caption{Comparison of different ordering with selection of ReLUs by SAS.}
+	\label{table.order}
+	%\vspace{-0.6cm}
+\end{table}
 

### 2025-01-28 CAV 2025 TODO/Comparison.tex
push

@@
-\section{Global Ranking Functions}
+\section{Global Scoring Functions}
 
@@
 
-First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions (replacing the symbols from the original paper with those used in our paper.), selecting a node to branch on for BaB, global ranking (GR) functions to select nodes for pMILP.
+First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions (replacing the symbols from the original paper with those used in our paper.), selecting a node to branch on for BaB, {\em  global scoring} (GS) functions to select nodes for pMILP.
 Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP.
@@
 
-We call {\em global rankings} (GR) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution $sol(a),sol(b)$ values.
+We call {\em global scoring} (GS) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution $sol(a),sol(b)$ values.
 This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.

### 2025-01-28 CAV 2025 TODO/Comparison.tex
comp

@@
 To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be
-$r(\bm{u}_k)=\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))} \in [0,1]$.
+$r(\bm{u}_k)=\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))} \in [0,1]$, 
+with $r(b)=0$ iff $\UB(b)\leq 0$ and $r(b)=1$ iff $\LB(b)\geq 0$.
 

### 2025-01-28 CAV 2025 TODO/Paper_noProof.tex
work
comparison
formula
exp

@@
 \newcommand{\Improve}{\mathrm{Improve}}
-\newcommand{\Utility}{\mathrm{Utility}}
+\newcommand{\Utility}{\mathrm{SAS}}
 \newcommand{\Sol}{\mathrm{Sol}}
@@
 
+\input{Comparison}
+
 \input{formula}
-
-\input{Comparison}
 
@@
 \section{Conclusion}
-{\color{blue}
-	In this paper, we developed a novel Utility function to select few ReLU nodes to consider with binary variables to compute accurately bounds on neurons of DNNs.
-The novelties are that it focuses on {\em improvement} wrt a given input, rather than on generic {\em sensitivity} of a neuron wrt to a ReLU node, and it uses the solution of one call to an (efficient LP) solver to evaluate this improvement.
-This makes the choice particularly efficient, necessitating $\approx4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy.}
-Our empirical studies revealed that this can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp), with the same runtime, for DNNs with up to 20 000 neurons.
-The reason is that $\alpha,\beta$-Crown hits a complexity barrier, similarly as other competing solutions, when considering hard (even small) DNNs.
-This opens a lot of perspectives, among which: verifying efficiently other hard instances; certifying $\epsilon$-robustness of images for $\epsilon$ as large as possible;
-verifying global rather than local properties \cite{lipshitz}.
+In this paper, we developed a novel solution-aware scoring (SAS) function to select few ReLU nodes to consider with binary variables to compute accurately bounds in DNNs. 
+The solution awareness allows SAS to compute an accurate score for each ReLU, which enables partial MILP to be very efficient, necessitating $\approx4$x less binary variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
+As the worst-case complexity is exponential in the number of binary variables, this big leap ahead has large implication in terms of scalability to larger DNNs, making it possible to verify quite large DNNs such as CNN-B-Adv with 2M parameters and 20000 activation functions.
+
+While $\alpha,\beta$-Crown is known to be extremely efficient to solve easier verification instances, we exhibit many cases (complex instances) where its worst-case exponential complexity in the number of ReLUs is tangible, with unfavorable scaling (Table \ref{table_beta}).
+Resorting to Hybrid MILP, a divide-and-conquer approach \cite{DivideAndSlide}, revisited thanks to the very efficient solution-aware scoring, revealed to be a much better trade-off than augmenting $\alpha,\beta$-Crown time-outs, with $8\%$ to $40\%$ less undecided images at ISO runtime.
+
+Last, we adapted BaB-SR \cite{BaB} and FSB \cite{FSB} as global scoring (GS) functions. 
+We compare them both theoretically and experimentally with solution-aware scoring: While GS are not as accurate as SAS for ReLU {\em selection}, they are better suited to select the {\em order} with which to branch over this selection, at least when the order is static and does not depend upon the branch.
+This opens up interesting future research directions, to hybridize different scoring for different tasks;  e.g.
+verifying global \cite{lipshitz}, \cite{sensing} rather than local (robustness) properties.
 

### 2025-01-28 CAV 2025 TODO/experiments.tex
comp
exp

@@
 %
-We implemented \toolname\ in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems.
+We implemented \toolname\ in Python 3.8: it first calls $\alpha,\beta$-Crown with small time out (10s for small and 30s for larger DNNs), and then call pMILP on the undecided inputs.
+Gurobi 9.52 was used for solving LP and MILP problems.
 We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
@@
 
-We also experimented in Table \ref{table.order} on fixing an ordering on variable in Gurobi, with a fixed selection of nodes by SAS.
-Indeed, Gurobi relies on a BaB procedure to compute bounds.
-The standard Gurobi procedure is adaptative in each branch.
-We compared vs the fix order provided by SAS, as well as the fixed order provided by FSB, for both accuracy and runtime (lower is better).
+Gurobi relies on a BaB procedure to compute bounds.
+The standard Gurobi ordering of variables is adaptative in each branch.
+We report in Table \ref{table.order} experiments on changing the ordering on variables in Gurobi, when the selection of ReLUs is fixed by SAS.
+We compared it with the static order provided by SAS, as well as the static order provided by GS, for runtime at a fixed accuracy (MIPGAP=0.01, so $1\%$ of difference in uncertainty is possible).
+The test are done on the same CIFAR image 85  and CNN-B-Adv.
 
-\begin{table}[h!]	
+\begin{table}[t]	
 	\centering
-	\begin{tabular}{|c||c c|c c|c c|}
+	\begin{tabular}{|c||c c|c c|c c|c c|}
 		\hline
-		  & \multicolumn{2}{c|}{30 open ReLUs} & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs} \\ 
-		 order & uncert & time & uncert & time & uncert & time \\
+		  & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{50 open ReLUs} 
+		  & \multicolumn{2}{c|}{55 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs}\\ 
+		 order & uncert & time & uncert & time & uncert & time & uncert & time \\
 		\hline \hline
-		Gurobi &   3.987  & 260s  & 4.016 & 266s& 4.053 & 262s\\ 
-		SAS &   3.989  & 264s  & 4.031 & 266s& 4.060 & 263s\\
-		FSB &   3.988  & {\bf 246s}  & 4.018 & {\bf 248s}& 4.033 & {\bf 248s}\\ \hline
+		Gurobi &  & 252s & &  & & &   & 306s  \\ 
+		SAS (static) &  & 448s & &  & & &   & 971s \\
+		GS (static) & & {\bf 251s} & &  &  & &  & {\bf 281s} \\ \hline
 	\end{tabular}
-	\caption{Comparison of different ordering with selection of ReLUs by SAS.}
+	\caption{Comparison of different orderings with selection of ReLUs by SAS.}
 	\label{table.order}
@@
 
-Here,  SAS is as efficient as Gurobi, although the ordering is fixed, meaning that the ordering compensates for the non adaptivity.
-However, the fixed GS ordering (with the SAS selection) is even better, with slightly better accuracy and lower runtime.
-As explained earlier, this is due to the fact that global ordering is preferable when branching on choices far from the optimal solution.
+SAS ordering is particularly counter-productive because it is static, and it is accurate only for one branch (the most complicated one), whereas Gurobi can adapt the order to each branch.
+However, the GS ordering (with the SAS selection) is better as it is general and not local to a solution, with better runtime than Gurobi, although it is static whereas Gurobi order is adaptative.
+Using SAS order for the solution branch, and GS ordering for other branches should be more efficient, but we cannot experiment that within the closed source Gurobi solver.
 
@@
 
-We conducted our evaluation on the neural networks tested in \cite{crown}
-which display a large number ($\geq 20\%$) of images undecided  by $\alpha,\beta$-Crown.
-That is, these DNNs are {\em hard} to verify.
+To assess the verification efficiency and runtime vs $\alpha,\beta$-Crown, we 
+conducted evaluations on the neural networks which are {\em complex} to verify, from \cite{crown}.
 Namely, these are 6 ReLU-DNNs: 5 MNIST DNN that can be found in the \href{https://github.com/eth-sri/eran}{ERAN GitHub}
@@
 The 6 first DNNs are hard instances.
-The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
+The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify), provided for reference.}
 	\label{table_hybrid}
@@
 
-{\em Analysis}: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN, 
-as it is called first and it is sufficient to have $0\%$ undecided images, as shown even on the very large ResNet.
-
-On hard instances (the 6 first DNNs tested), Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, and even 10 times less on smaller DNNs.
+{\em Analysis}: overall, Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, and even 10 times less on smaller DNNs.
 It can scale up to quite large hard DNNs, such as CNN-B-Adv with 2M parameters and 20K activations.
 
-Compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%-43\%$. 
+Compared with $\alpha,\beta$-Crown:
+on easy instances (see the very large ResNet), Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN, as $\alpha,\beta$-CROWN is called first because it is very efficient for such instances.
+
+On hard instances (the 6 first DNNs tested), compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%-43\%$.
 It is also from 20x faster on smaller networks to similar time on the largest DNN.
@@
 Last, compared with {\em Refined} $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5$\times$100, 5$\times$200), Refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than  Hybrid MILP, but with longer runtime (up to 2 times on 5$\times$100).
-On intermediate DNNs (8$\times$100, 8$\times$200), full MILP invoked by Refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images (that is double on 8$\times$200), while having longer runtime.
+As size of DNNs grows (8$\times$100, 8$\times$200), full MILP invoked by Refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images (that is double on 8$\times$200), while having longer runtime.
 Last but not least, Refined $\beta$-Crown cannot scale to larger instances (6$\times$500, CNN-B-Adv), while Hybrid MILP can.
@@
 
-We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier to date, and to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
+We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
+
+Interestingly, GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us.
+We report result from \cite{cutting} pertinent to the DNNs we tested, and copy the comparison with $\alpha,\beta$-Crown.
+While results are similar to ours, they do not use exactly the same number of input images than in our test, and thus it is not directly comparable.
+On CNN-B-Adv, GCP-CROWN is $2\%$ more accurate (with higher runtime) than 
+$\alpha,\beta$-Crown with 90s TO, so it is safe to consider that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-Crown with 2000s TO,  is significantly more accurate than GCP-CROWN on this quite large DNN.
 
 Notice that results for other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN.
-Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd
-of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN.
+Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN.
 Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings.
 Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible.
+Details can be found in the appendix.
+Also, ablation studies showing what each feature of Hybrid MILP is bringing can be found in the appendix.
 

### 2025-01-29 CAV 2025 TODO/Paper_noProof.tex
exp
all

@@
 The previous attempts were suboptimal in that respect.
-In this paper, we propose a novel {\em solution-aware} ReLU ranking (SAR), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU ranking (GR) functions.
+In this paper, we propose a novel {\em solution-aware} ReLU scoring (SAS), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU scoring (GS) functions.
 We compare them theoretically as well as experimentally.
-Surprisingly perhaps, the most accurate solution (SAR) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GR) to {\em rank} within this selection.
-Compared with previous attempts, SAR reduces the number of integer variables by around 4 times while maintaining the same level of accuracy.
+Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em rank} within this selection.
+Compared with previous attempts, SAS reduces the number of integer variables by around 4 times while maintaining the same level of accuracy.
 Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CIFAR CNNs with 20 000 nodes.

### 2025-01-29 CAV 2025 TODO/experiments.tex
exp
all

@@
 Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB(a) - \LB(a)$. The average uncertainty of layer $\ell$ is 
-$$\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$$
+$\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$
 
-\begin{figure}[b!]
+\begin{figure}[t!]
 	\centering
@@
 
-\begin{table}[t]	
+\begin{table}[b!]	
 	\centering
@@
 	\label{table.order}
-	%\vspace{-0.6cm}
+
 \end{table}
@@
 The 6 first DNNs are hard instances.
-The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify), provided for reference.}
+The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify), provided for reference.
+	\vspace{-1cm}}
 	\label{table_hybrid}
@@
 
+\subsection{Comparison with other Verifiers?}
+
+We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
+
+Interestingly, GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us.
+We provide in Table \ref{table_gcp} results from the Table 3 page 9 of \cite{cutting}, experimenting with different verifiers on the most interesting CIFAR CNN-B-Adv.
+Notice that results are not exactly comparable with ours because the testing images are not the same (ours has $62\%$ upper bound while \cite{cutting} has $65\%$ upper bound, so the image set in \cite{cutting} are slightly easier).
+There, GCP-CROWN is $2\%$ more accurate (with higher runtime) than $\alpha,\beta$-Crown with 90s TO, so we can deduce that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-Crown with 2000s TO, is significantly more accurate than GCP-CROWN.
+
+\begin{table}[b!]
+	\centering
+	\begin{tabular}{||c||c|c|c|c|c||}
+		\hline
+		Upper Bound & SDP-FO & PRIMA & refined $\beta$-Crown & $\beta$-Crown & GCP-Crown \\  \hline
+		65\% & 32.8\% & 38\% & 27\% & 46.5\% & 48.5\% \\
+		$\epsilon = 2/255$ & $>25$h & $344$s & $361$s & $32$s &  $58$s  \\  \hline
+	\end{tabular}
+	\caption{Images verified by different verifiers on CIFAR CNN-B-adv from \cite{cutting}.
+	Results are not directly comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
+	\label{table_gcp}
+	\vspace{-0.3cm}
+\end{table}
+
+Results on other networks from other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported \cite{crown} on other tested DNNs, with unfavorable comparison vs $\alpha,\beta$-CROWN.
+Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on complex (even small) instances.
+Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em complex} MNIST DNNs at several time-out settings.
+Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible.
+Details can be found in the appendix.
+Also, ablation studies showing what each feature of Hybrid MILP is bringing can be found in the appendix.
+
 \subsection{Finer Grain evaluation of Accuracy}
@@
 \includegraphics[scale=0.6]{epsilon.png}.
-\caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ on each of the 20 first images of MNIST.}
+\caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ for the 20 first images.}
 \label{fig2}
@@
 On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible that the falsifier missed a closer attack to robustness.
-
-Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, except for 2 cases (images 8 and 18) where $\alpha,\beta$-CROWN is already very close to the upper bound.
 On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, 3 times smaller than the $0.042$ gap for $\alpha,\beta$-CROWN.
-
-\subsection{Comparison with other Verifiers?}
-
-We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
-
-Interestingly, GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us.
-We report result from \cite{cutting} pertinent to the DNNs we tested, and copy the comparison with $\alpha,\beta$-Crown.
-While results are similar to ours, they do not use exactly the same number of input images than in our test, and thus it is not directly comparable.
-On CNN-B-Adv, GCP-CROWN is $2\%$ more accurate (with higher runtime) than 
-$\alpha,\beta$-Crown with 90s TO, so it is safe to consider that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-Crown with 2000s TO,  is significantly more accurate than GCP-CROWN on this quite large DNN.
-
-Notice that results for other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN.
-Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN.
-Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings.
-Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible.
-Details can be found in the appendix.
-Also, ablation studies showing what each feature of Hybrid MILP is bringing can be found in the appendix.
 

### 2025-01-29 CAV 2025 TODO/formula.tex
all

@@
 would however be very time consuming when the number of neurons $a$ to evaluate is large.
-{\color{blue} 
 The main novelty of our SAS function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Fig.
@@
 Further, even when the global solution changes, we can show that $\Utility$ is a safe overapproximation, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b) > 0$):
-}
 

### 2025-01-29 CAV 2025 TODO/introduction.tex
all

@@
 The 6 first DNNs are complex instances.
-The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
+The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
+	\vspace{-0.5cm}}
 	\label{table_beta}
-	\vspace{-0.3cm}
 \end{table}
@@
 %Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-Crown (40\%), at the cost of a much larger runtime (4995s vs 1026s).}
+Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-Crown (40\%), at the cost of a much larger runtime (4995s vs 1026s).
+\vspace{-0.5cm}}
 \label{table_complete}
@@
 
-Other standard non-BaB methods such as Marabou 2.0, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image.
+Other standard non-BaB methods such as Marabou, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image.
 It appeared pointless to test these verifiers on larger networks.
@@
 
-	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global ranking (GR) functions to choose ReLU for pMILP. 
+	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global scoring (GS) functions to choose ReLU for pMILP. 
 	These revealed to be much more accurate than the simple heuristic in 
 	\cite{DivideAndSlide}.
-We uncover however one case (out of 4) where the exact function that GR tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode.
+We uncover however one case (out of 4) where the exact function that GS tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode.
 This implies that these strategies may not be that accurate, because they do not know the mode to choose from.
-We then designed a novel solution-aware ranking (SAR), which uses the solution of a unique LP call, that provides the mode to consider.
-Theoretically, we show that SAR is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAR value implies that the ReLU is unnecessary.
-Experimentally, we further show that SAR is very close to the actual improvement, closer than GR, and that overall, the accuracy from SAR is significantly better than GR.
-Compared with the heuristic in \cite{DivideAndSlide}, SAR is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GR would be better suited, which we verify experimentally.
+We then designed a novel solution-aware scoring (SAS), which uses the solution of a unique LP call, that provides the mode to consider.
+Theoretically, we show that SAS is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAS value implies that the ReLU is unnecessary.
+Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.
+Compared with the heuristic in \cite{DivideAndSlide}, SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
 

### 2025-01-29 CAV 2025 TODO/Comparison.tex
update the plot
update
formula

@@
 
-First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions (replacing the symbols from the original paper with those used in our paper.), selecting a node to branch on for BaB, {\em  global scoring} (GS) functions to select nodes for pMILP.
+First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions, %(replacing the symbols from the original paper with those used in our paper.)
+ selecting a node to branch on for BaB, {\em  global scoring} (GS) functions to select nodes for pMILP.
 Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP.
@@
 Then, the scoring functions $\bm{s}_{SR}$ and $\bm{s}_{FSB}$ for ReLUs in layer $k$ are computed by approximating how each node would impact the neurons in layer $n$, by also factoring in the bias $\bm{b}_k$ in different ways:
+
+\begin{figure}[t!]
+	\centering
+	\begin{tikzpicture}
+
+		\node (input1) {};
+
+		%\node (input2) at ($(input1) + (0,-1.5)$) {$n'$};
+
+		% Hidden layers
+
+		\node (hidden10) at ($(input1) + (2,0.6)$) {$[-1,1]$};
+
+		\node (hidden20) at ($(input1) + (2.5,-1.5-0.6)$) {};
+
+		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$[-1,1]$};
+
+		\node (hidden60) at ($(input1) + (7.5,-1.5-0.6)$) {};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden1) at ($(input1) + (2,0)$) {$a$};
+		%\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$a'$};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{a}$};
+		\node (hidden4) at ($(input1) + (5.5,-1)$) {};
+
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$b$};
+		%\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$b'$};
+
+		% Output layer
+		\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{b}$};
+
+		\node (output2) at ($(input1) + (10.5,-1)$){};
+
+			\node[circle, draw= black, thick, minimum width = 20,
+		minimum height = 20] (output3) at ($(input1) + (12.5,0)$){$z$};
+
+		% Connections
+
+		%\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
+
+		% \draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
+
+		\draw[->,thick] (input1) -- (hidden1) node[midway, above] {};
+		%\draw[->,thick] (input1) -- (hidden2)node[near start, below] {$-10$};
+
+		% \draw[->, thick] (input2) -- (hidden2)node[near start, below] {$0.5$};
+
+		\draw[->, thick] (hidden1) -- (hidden3) node[midway, above] {ReLU?};
+		%\draw[->, thick] (hidden2) -- (hidden4);
+
+		\draw[->, thick] (hidden3) -- (hidden5) node[midway, above] {{\color{red}$c$}};
+
+		\draw[->,thick] (hidden4) -- (hidden5)node[near start, above] {};
+		%\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
+
+		\draw[->,thick] (hidden5) -- (output1) node[midway, above] {LP ReLU};
+		%\draw[->,thick] (hidden6) -- (output2);
+
+		\draw[->,thick] (output1) -- (output3)node[midway, above] {{\color{red}$d$}};
+		\draw[->,thick] (output2) -- (output3)node[near start, below] {};
+
+	\end{tikzpicture}
+	\vspace{-0.8cm}
+	\caption{A simple example with parametric weights {\color{red}$c$} and {\color{red}$d$}}
+	\label{img:FSB_example}
+\end{figure}
+
+\begin{figure}[b!]
+	\begin{centering}
+	\begin{tikzpicture}[scale=1, >=stealth]
+
+		% Draw axes
+		\draw[->] (-5,0) -- (4,0) node[right] {$a$};
+		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{a}$};
+
+		% Draw ReLU function
+		\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
+		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{a} = \ReLU(a)$};
+		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-5.7,-2)}] {$\hat{a} = r(a) (a-\LB)$};
+
+		% Add labels
+		\draw[dashed] (2.5,0) -- (2.5,2.5) -- (0,2.5); % Optional grid
+		\node[below left] at (0,0) {$0$};
+
+		% Add tick marks
+
+		\foreach \x in {2.5}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\UB$};
+		\foreach \x in {-3}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\LB$};
+
+		\foreach \y in {2.5}
+		\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {$\UB$};
+
+	\end{tikzpicture}
+		\caption{Triangle approximation
+		\vspace{-0.3cm}}
+	\label{triangle}
+	\end{centering}
+	\end{figure}
 
@@
 	Then, unstable ReLU (with $\LB(u_k) < 0 < \UB(u_k)$) are ranked using these scores, to select the most important ReLUs, as stable ReLUs are linear, thus they are already treated correctly.
-
-\begin{figure}[t!]
-	\centering
-	\begin{tikzpicture}
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (input1) {$n$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n'$};
-
-		% Hidden layers
-
-		\node (hidden10) at ($(input1) + (2.5,0.6)$) {$[-1,1]$};
-
-		\node (hidden20) at ($(input1) + (2.5,-1.5-0.6)$) {$[-10,11]$};
-
-		\node (hidden50) at ($(input1) + (7.5,0.6)$) {$[-1,1]$};
-
-		\node (hidden60) at ($(input1) + (7.5,-1.5-0.6)$) {$[0,0.5]$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$a$};
-		\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$a'$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{a}$};
-		\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{a}'$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$b$};
-		\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$b'$};
-
-		% Output layer
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{b}$};
-
-		\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{b}'$};
-
-			\node[circle, draw= black, thick, minimum width = 20,
-		minimum height = 20] (output3) at ($(input1) + (12.5,0)$){$z$};
-
-		% Connections
-
-		\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};
-
-		\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};
-
-		\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
-		\draw[->,thick] (input1) -- (hidden2)node[near start, below] {$-10$};
-
-		\draw[->, thick] (input2) -- (hidden2)node[near start, below] {$0.5$};
-
-		\draw[->, thick] (hidden1) -- (hidden3);
-		\draw[->, thick] (hidden2) -- (hidden4);
-
-		\draw[->, thick] (hidden3) -- (hidden5) node[near start, above] {{\color{red}$c$}};
-
-		\draw[->,thick] (hidden4) -- (hidden5)node[near start, above] {$1$};
-		\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};
-
-		\draw[->,thick] (hidden5) -- (output1);
-		\draw[->,thick] (hidden6) -- (output2);
-
-		\draw[->,thick] (output1) -- (output3)node[near start, above] {{\color{red}$d$}};
-		\draw[->,thick] (output2) -- (output3)node[near start, below] {$1$};
-
-	\end{tikzpicture}
-	\caption{A simple example with parametric weights {\color{red}$c$} and {\color{red}$d$}}
-	\label{img:FSB_example}
-\end{figure}
 
@@
 either 0 or $d \Delta(b)<\frac{cd}{2}$, as compared with $s_{FSB}(a)=\frac{cd}{4}$.
-
-\begin{figure}[t!]
-	\begin{tikzpicture}[scale=1, >=stealth]
-
-		% Draw axes
-		\draw[->] (-5,0) -- (4,0) node[right] {$a$};
-		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{a}$};
-
-		% Draw ReLU function
-		\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
-		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{a} = \ReLU(a)$};
-		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-6.5,-2)}] {$\hat{a} = \frac{\UB}{\UB-\LB} (a-\LB)$};
-
-		% Add labels
-		\draw[dashed] (2.5,0) -- (2.5,2.5) -- (0,2.5); % Optional grid
-		\node[below left] at (0,0) {$0$};
-
-		% Add tick marks
-
-		\foreach \x in {2.5}
-		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\UB$};
-		\foreach \x in {-3}
-		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\LB$};
-
-		\foreach \y in {2.5}
-		\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {$\UB$};
-
-	\end{tikzpicture}
-		\caption{Triangle approximation}
-	\label{triangle}
-	\end{figure}
 

### 2025-01-29 CAV 2025 TODO/Paper_noProof.tex
formula

@@
 \usepackage{tabularx}
+\usepackage{cases}
 \captionsetup{compatibility=false}
@@
 In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \textcolor{blue}{\cite{crown}}.
+capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{crown}.
 To simplify the notations, we restrict the presentation to feed-forward, 

### 2025-01-29 CAV 2025 TODO/experiments.tex
formula

@@
 \section{Experimental Evaluation}
+
+\begin{figure}[b!]
+	\centering
+	\vspace*{-0.3cm}
+	\includegraphics[height=7cm]{open.png}.
+	\vspace*{-0.4cm}
+	\caption{Average uncertainty of pMILP for neurons of the fourth layer of CNN-B-Adv, 
+	when opening between 0 and 30 ReLUs, chosen randomly vs Huang \cite{DivideAndSlide} vs 
+	$s_{FSB}$ vs $\Utility$ (with time-out=900s).}
+	\label{fig_table3}
+\end{figure}
 
@@
 $\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$
-
-\begin{figure}[t!]
-	\centering
-	\vspace*{-0.3cm}
-	\includegraphics[height=7cm]{open.png}.
-	\vspace*{-0.4cm}
-	\caption{Average uncertainty of pMILP for neurons of the fourth layer of CNN-B-Adv, 
-	when opening between 0 and 30 ReLUs, chosen randomly vs Huang \cite{DivideAndSlide} vs 
-	$s_{FSB}$ vs $\Utility$ (with time-out=900s).}
-	\label{fig_table3}
-\end{figure}
 
@@
 We report in Table \ref{table.order} experiments on changing the ordering on variables in Gurobi, when the selection of ReLUs is fixed by SAS.
-We compared it with the static order provided by SAS, as well as the static order provided by GS, for runtime at a fixed accuracy (MIPGAP=0.01, so $1\%$ of difference in uncertainty is possible).
+We compared it with the static order provided by SAS, as well as the static order provided by GS, for runtime at a fixed accuracy, where we report the distance to verify the image.
 The test are done on the same CIFAR image 85  and CNN-B-Adv.
 
-\begin{table}[b!]	
+\begin{table}[t!]	
 	\centering
@@
 		  & \multicolumn{2}{c|}{55 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs}\\ 
-		 order & uncert & time & uncert & time & uncert & time & uncert & time \\
+		 order & distance & time & distance & time & distance & time & distance & time \\
 		\hline \hline
-		Gurobi &  & 252s & &  & & &   & 306s  \\ 
-		SAS (static) &  & 448s & &  & & &   & 971s \\
-		GS (static) & & {\bf 251s} & &  &  & &  & {\bf 281s} \\ \hline
+		Gurobi & 0.384 & 252s & &  & & & 0.315  & 306s  \\ 
+		SAS (static) & 0.384 & 448s & &  & & & 0.355  & 971s \\
+		GS (static) & 0.384 & {\bf 251s} & &  &  & & 0.315 & {\bf 281s} \\ \hline
 	\end{tabular}
@@
 
+\begin{figure}[b!]
+	\begin{centering}
+\includegraphics[scale=0.6]{epsilon.png}.
+\caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ for the 20 first images.}
+\label{fig2}
+	\end{centering}
+\end{figure}
+
 In order to evaluate the accuracy of Hybrid MILP in a finer way, showcasing 
@@
 
-\begin{figure}[t!]
-	\begin{centering}
-\includegraphics[scale=0.6]{epsilon.png}.
-\caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ for the 20 first images.}
-\label{fig2}
-	\end{centering}
-\end{figure}
-
 {\em Analysis}: in 90\% of the cases, Hybrid MILP is very close to the upper bound.
-On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible that the falsifier missed a closer attack to robustness.
+On 2 images (10, 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so the falsifier may have missed a closer attack to robustness.
 On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, 3 times smaller than the $0.042$ gap for $\alpha,\beta$-CROWN.

### 2025-01-29 CAV 2025 TODO/formula.tex
formula

@@
 %In this case, usual heuristics would open $n$, while it would only improve the value of $z$ in a limited way.
-
 Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
 We write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
-We denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$.
-In particular, $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
+We denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$: $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.
 
@@
 Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
-$\Improve\_\min^z(n)$. Calling MILP on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$
+$\Improve\_\min^z(n)$. 
+Calling MILP on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$
 would however be very time consuming when the number of neurons $a$ to evaluate is large.
-The main novelty of our SAS function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Fig.
+Instead, the SAS function uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Fig.
 \ref{fig_table3}).
@@
 we define:
+\vspace{-0.4cm}
 
-\begin{align*}
-	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
-	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
-	\forall b \in \ell, \Delta(\hat{b}) &=
-	\begin{cases}
-		%\Delta(b),  & \text{if } W_{bz} > 0 \text{ and } \LB(b)\geq 0\\
-		r(b)\Delta(b),%\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  
-		&\text{if }W_{bz} > 0 \\ % \text{ and } \LB(b)<0\\
-		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
-		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
-	\end{cases}\\
-	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
-\end{align*}
+\begin{flalign*}
+	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})&&\\
+	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})&&\\	
+\end{flalign*}
+
+\vspace{-1.2cm}
+
+\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
+		r(b)\Delta(b), & for $W_{bz} > 0$ \\
+		\max(\Delta(b),-\sol(b)), & for $W_{bz} < 0$ and $\sol(b)\geq0$\\
+		\max(0,\Delta(b)+\sol(b)), & for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
+\end{subnumcases}
+\vspace{-0.4cm}
+\begin{flalign*}
+	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})&&
+\end{flalign*}
+
+\begin{figure}[b!]
+	\begin{centering}
+	\begin{tikzpicture}[scale=1, >=stealth]
+
+		% Draw axes
+		\draw[->] (-5,0) -- (4,0) node[right] {$b$};
+		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{b}$};
+
+		% Draw ReLU function
+		\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
+		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(0.35,-0.55)}] {$\hat{b} = \ReLU(b)$};
+		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-5.7,-2)}] {$\hat{b} = r(b) (b-\LB)$};
+
+		% Add labels
+		\draw[dashed] (2.5,0) -- (2.5,2.5) -- (0,2.5); % Optional grid
+		\node[below left] at (0,0) {};
+
+		% Add tick marks
+
+		\foreach \x in {2.5}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\UB$};
+		\foreach \x in {-3}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\LB$};
+
+		\foreach \y in {2.5}
+		\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {$\UB$};
+
+		\draw[<->, thick] (0.1, 0.1) -- (0.9, 0.9) node[above,shift={(0.65,-0.45)}] {$case$ (b)}
+		node[below,shift={(-0.1,-1.10)}] {$sol(b)\Delta(b)$}
+		node[above,shift={(-1.35,-0.55)}] {$\Delta(\hat{b})$};
+		\filldraw[black] (0.5, 0.5) circle (1.5pt);
+		\filldraw[black] (0.5, 0) circle (1.5pt);
+		\draw[<->, thick] (0.1, 0) -- (0.9, 0);
+		\draw[dashed] (0.5,0) -- (0.5,1.6); % Optional grid
+
+		\draw[<->, thick] (-0.5, 0) -- (-1.5, 0) node[above,shift={(0.6,0)}] {$case$ (c)}
+		node[below,shift={(0.6,-0.15)}] {$sol(b)\Delta(b)$};
+		\filldraw[black] (-1, 0) circle (1.5pt);
+
+		\draw[<->, thick] (0.1, 1.375) -- (0.9, 1.75) node[above,shift={(-0.3,0)}] {$case$ (a)}
+		node[above,shift={(-1.4,-0.45)}] {$\Delta(\hat{b})$};
+		\filldraw[black] (0.5, 1.6) circle (1.5pt);
+
+		\draw[<->, thick] (0, 0.1) -- (0, 0.9);
+
+		\draw[<->, thick] (0, 1.375) -- (0, 1.75);
+
+	\end{tikzpicture}
+	\caption{Different cases for $\ReLU(b)$
+	 \vspace{-0.3cm}}
+	\label{node:b}
+\end{centering}
+\end{figure}
 
@@
 whereas the corresponding $\Delta_{FSB}(\hat{a})$ is approximated as $\LB(a) r(a)$, 
-which is only an upper bound of $\ReLU(\sol(a))-\sol(\hat{a})$.
-More importantly, the corresponding $\Delta_{FSB}(\hat{b})$ is always $r(b) \Delta(b)$, whereas SAS adapts to the case when $W_{bz}<0$, correctly considering the 0 phase of $ReLU(b)$ when $\sol(b)\geq 0$, and the ID phase when $\sol(b)<0$.
+which is only an upper bound. %of $\ReLU(\sol(a))-\sol(\hat{a})$.
+More importantly, the corresponding $\Delta_{FSB}(\hat{b})$ is always $r(b) \Delta(b)$, whereas SAS adapts to the 3 cases (see Fig.
+\ref{node:b}), correctly considering the 0 phase of $ReLU(b)$ when $\sol(b)\geq 0$, and the ID phase when $\sol(b)<0$.
 Assuming that the solution to maximize $z$ does not change when opening $\ReLU(a)$
-on neurons independant of $a$, then $\Utility$ is exact.
-This is not the case for $s_{FSB}$ because of the two previously mentionned cases.
+on neurons independent of $a$, then $\Utility$ is exact.
+This is not the case for $s_{FSB}$ because of the two previously mentioned cases.
 Further, even when the global solution changes, we can show that $\Utility$ is a safe overapproximation, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b) > 0$):

### 2025-01-29 CAV 2025 TODO/valabstraction.tex
update
formula

@@
 
-Consider the simpler abstraction, termed ``Box abstraction", {\color{blue} recalled e.g.
-in \cite{deeppoly}}: it inductively computes the bounds for each neuron in the subsequent layer independently.
+Consider the simpler abstraction, termed ``Box abstraction", recalled e.g.
+in \cite{deeppoly}: it inductively computes the bounds for each neuron in the subsequent layer independently.
 This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth.
@@
 
-{\color{blue} In \cite{DBLP_Ehlers17, deeppoly} and others, the {\em triangular abstraction} was proposed:
+In \cite{DBLP_Ehlers17,deeppoly} and others, the {\em triangular abstraction} was proposed:
 \begin{align}
-	\ReLU(x) = max (0,x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} 
+	\ReLU(x) = \max (0,x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} 
 	\label{eq:deeppoly}
@@
 DeepPoly \cite{deeppoly} chooses one of the two lower bounds for each neuron $x$, giving rise to a greedy quadratic-time algorithm to compute very fast an abstraction of the value of $\hat{x}$ (but not that accurately).
-}
 

### 2025-01-30 CAV 2025 TODO/experiments.tex
exp

@@
 		\hline
-		  & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{50 open ReLUs} 
+		  Image 85& \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{50 open ReLUs} 
 		  & \multicolumn{2}{c|}{55 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs}\\ 

### 2025-01-30 CAV 2025 TODO/experiments.tex
exp

@@
 	\caption{Average uncertainty of pMILP for neurons of the fourth layer of CNN-B-Adv, 
-	when opening between 0 and 30 ReLUs, chosen randomly vs Huang \cite{DivideAndSlide} vs 
-	$s_{FSB}$ vs $\Utility$ (with time-out=900s).}
+	when selecting between 0 and 30 ReLUs with different scoring functions.}
 	\label{fig_table3}
@@
 The  objectives of our evaluation was to answer the following  questions:
+\vspace{-0.1cm}
 
@@
 %The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-To measure the impact of the scoring function to select neurons to open, 
+First, we measured the distance between SAS or GS and real improvement for all nodes in the first two layers of $5 \times 100$ wrt the accuracy of nodes in the third layer.
+On average, the distance using GS is 4 times larger than using SAS.
+
+Then, to measure the impact of the scoring function to select neurons to open, 
 we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
@@
 We compared it with the static order provided by SAS, as well as the static order provided by GS, for runtime at a fixed accuracy, where we report the distance to verify the image.
-The test are done on the same CIFAR image 85  and CNN-B-Adv.
+The test are done on CIFAR image 85 and CNN-B-Adv.
 
@@
 	\end{tabular}
-	\caption{Comparison of different orderings with selection of ReLUs by SAS.}
+	\caption{Comparison of different orderings with selection of ReLUs by SAS.
+	\vspace{-0.4cm}}
 	\label{table.order}
-
 \end{table}
 
-SAS ordering is particularly counter-productive because it is static, and it is accurate only for one branch (the most complicated one), whereas Gurobi can adapt the order to each branch.
-However, the GS ordering (with the SAS selection) is better as it is general and not local to a solution, with better runtime than Gurobi, although it is static whereas Gurobi order is adaptative.
-Using SAS order for the solution branch, and GS ordering for other branches should be more efficient, but we cannot experiment that within the closed source Gurobi solver.
+SAS ordering is particularly counter-productive because it is accurate only for one branch (the most complicated one), whereas Gurobi can adapt the order to each branch.
+However, the GS ordering (with the SAS selection) is better as it is general and not local to a solution, with better runtime than Gurobi, despite its staticness whereas Gurobi order is adaptative.
+Using SAS order for the solution branch, and GS ordering for other branches should be more efficient, but we cannot experiment that within the closed-source Gurobi solver.
 
@@
 We report in Table \ref{table_hybrid} the $\%$ of undecided images, that is the $\%$ of images than can be neither falsified (by $\alpha,\beta$-CROWN) nor verified by the tested verifier, among the 100 first images for each MNIST or CIFAR10 benchmark.
-The exact same DNNs and $\epsilon$ are used in Tables \ref{table_beta} and \ref{table_hybrid}.
+The exact same DNNs, image set and $\epsilon$ are used in Tables \ref{table_beta} and \ref{table_hybrid}.
 

### 2025-01-30 CAV 2025 TODO/formula.tex
exp

@@
 	The case of $\Delta(\hat{b})$ is the most interesting:
-	If $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
-sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)} +$ Cst to maximize $z$.
+	If (a) $W_{bz}>0$, to maximize $z$, the LP solver sets $\sol(\hat{b})$ to the maximal possible value, which is 
+	$r(b) \sol(b)+$ Cst according to Proposition \ref{LP}.
 Changing $b$ by $\Delta(b)$ thus results in changing $\sol(\hat{b})$ by 
-$\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b)$.
+$r(b) \Delta(b)$.
 If $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
-If $\sol(b) < 0$, then we have $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ change the 0 value only if $\sol(b)+\Delta(b)>0$. If $\sol(b) > 0$, then 
+If (b) $\sol(b) > 0$, then 
 $\sol(\hat{b})=\ReLU(\sol(b))=\sol(b)$, and the change to $\hat{b}$ will be 
@@
 $-\sol(b)$.
+If (c) $\sol(b) < 0$, then we have $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ moves away 
+from 0 only if $\sol(b)+\Delta(b)>0$. 
+ \qed
 		\end{proof}

### 2025-01-30 CAV 2025 TODO/Comparison.tex
comp

@@
 
-		\draw[->, thick] (hidden1) -- (hidden3) node[midway, above] {ReLU?};
+		\draw[->, thick] (hidden1) -- (hidden3) node[midway, above] {open ReLU?};
 		%\draw[->, thick] (hidden2) -- (hidden4);
@@
 
-We call {\em global scoring} (GS) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution $sol(a),sol(b)$ values.
+We call {\em global scoring} (GS) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution values $sol(a),sol(b)$.
 This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.

### 2025-01-31 CAV 2025 TODO/proofsb.tex
update

@@
 
-{\color{blue}
 \section{Parameter settings}
 
-\subsection*{Setting for $\alpha,\beta$-Crown}
-
-The networks were already tested by $\alpha,\beta$-Crown \cite{crown}.
+%{\color{blue}
+%
+%
+%\subsection*{Setting for $\alpha,\beta$-Crown}
+%
+%The networks were already tested by $\alpha,\beta$-Crown \cite{crown}.
 We thus simply reused the parameter files from \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN/blob/main/complete_verifier/exp_configs/beta_crown/}{their Github},
-except for time-out which we explicitly mention.
-
-e.g., for CNN-B-Adv: "solver: batch size: 512 beta-crown: iteration: 20" and
-for MNIST 5x100: "solver: batch size: 1024 beta-crown: iteration: 20".
-
-We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to.
+%except for time-out which we explicitly mention.
+%
+%e.g., for CNN-B-Adv: "solver: batch size: 512 beta-crown: iteration: 20" and
+%for MNIST 5x100: "solver: batch size: 1024 beta-crown: iteration: 20".
+%
+%We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to.
 From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-Crown on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP.
 The conclusion are thus unchanged.
-}
+%}
 
@@
 
-{\color{blue}
-
-\section{Ablation studies}
-
-In this section, we consider ablation studies to understand how each feature enables the efficiency of pMILP.
-
-\subsection*{Time scaling with open nodes}
-
-First, we explore the time scaling with different number of open nodes, for our full Utility function using nodes in the last two layers (Layer 1 and 2), providing finer details than in Table 3, with the same setting, i.e.
+%{\color{blue}
+%
+%
+%
+%
+%
+%\section{Ablation studies}	
+%
+%In this section, we consider ablation studies to understand how each feature enables the efficiency of pMILP.
+%
+%\subsection*{Time scaling with open nodes}	
+%
+%First, we explore the time scaling with different number of open nodes, for our full Utility function using nodes in the last two layers (Layer 1 and 2), providing finer details than in Table 3, with the same setting, i.e.
 previous layer being computed with full MILP.
-
-\begin{table}[h!]
-		\centering
-		\hspace*{4ex}
-		\begin{subtable}[b]{0.45\textwidth}
-		\begin{tabular}{|c|c|c|}
-		\hline
-		$|X|$ & Time & Uncertainty\\ 
-		\hline	0 & 2.6 & 1.760946128\\
-		\hline	1 & 7.3 & 1.702986873\\
-		\hline	2 & 11.1 & 1.65469034\\
-		\hline	3 & 16.3 & 1.612137282\\
-		\hline	4 & 15.5 & 1.571001109\\
-		\hline	5 & 15.7 & 1.531925404\\
-		\hline	6 & 15.8 & 1.49535638\\
-		\hline	7 & 16.4 & 1.46189314\\
-		\hline	8 &  15.8 & 1.4299535\\
-		\hline	9 &  17.2 & 1.4006364\\
-		\hline	10 & 22.5 & 1.3711203\\
-		\hline	11 & 27.2 & 1.3438245\\
-		\hline	12 & 21.6 & 1.3183356\\
-		\hline	13 & 28.7 & 1.2938690\\
-		\hline	14 & 29.6 & 1.2690507\\
-		\hline	15 & 24.5 & 1.2475106\\
-		\hline
-	  \end{tabular}
-	\end{subtable}
-	\hfill
-	\begin{subtable}[b]{0.45\textwidth}
-		\begin{tabular}{|c|c|c|}
-			\hline
-			$|X|$ & Time & Uncertainty\\ 
-		\hline	16 & 31.9 & 1.2243065\\
-		\hline	17 & 28.6 & 1.2031791\\
-		\hline	18 & 30.4 & 1.1839474\\
-		\hline	19 & 34.0 & 1.1644653\\
-		\hline	20 & 42.1 & 1.1456181\\
-		\hline	21 & 47.6 & 1.1261252\\
-		\hline	22 & 62.7 & 1.1089745\\
-		\hline	23 & 70.0 & 1.0931242\\
-		\hline	24 & 70.8 & 1.0773088\\
-		\hline	25 & 139.9 & 1.060928\\
-		\hline	26 & 154.2 & 1.045715\\
-		\hline	27 & 213.1 & 1.030605 \\
-		\hline	28 & 211.3 & 1.016058\\
-		\hline	29 & 373.1 & 1.001374\\
-		\hline max=116 & 3300 & 0.895\\ 
-		\hline		
-	  \end{tabular}
-     \end{subtable}
-	  \caption{Time and uncertainty scaling of pMILP with number of nodes.}
-    	\label{table14}
-\end{table}
-
-\begin{figure}[b!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer3_comparison}.
-	\caption{Time and uncertainty scaling of pMILP with number of nodes.
-	Time is using logscale.}
-	\label{fig3}
-\end{figure}
-
-The exponential complexity with the number of nodes can be seen on Figure \ref{fig3}, where time is represented using logarithmic scale.
+%
+%
+%
+%
+%
+%\begin{table}[h!]
+%		\centering
+%		\hspace*{4ex}
+%		\begin{subtable}[b]{0.45\textwidth}
+%		\begin{tabular}{|c|c|c|}
+%		\hline
+%		$|X|$ & Time & Uncertainty\\ 
+%		\hline	0 & 2.6 & 1.760946128\\
+%		\hline	1 & 7.3 & 1.702986873\\
+%		\hline	2 & 11.1 & 1.65469034\\
+%		\hline	3 & 16.3 & 1.612137282\\
+%		\hline	4 & 15.5 & 1.571001109\\
+%		\hline	5 & 15.7 & 1.531925404\\
+%		\hline	6 & 15.8 & 1.49535638\\
+%		\hline	7 & 16.4 & 1.46189314\\
+%		\hline	8 &  15.8 & 1.4299535\\
+%		\hline	9 &  17.2 & 1.4006364\\
+%		\hline	10 & 22.5 & 1.3711203\\
+%		\hline	11 & 27.2 & 1.3438245\\
+%		\hline	12 & 21.6 & 1.3183356\\
+%		\hline	13 & 28.7 & 1.2938690\\
+%		\hline	14 & 29.6 & 1.2690507\\
+%		\hline	15 & 24.5 & 1.2475106\\
+%		\hline
+%	  \end{tabular}
+%	\end{subtable}
+%	\hfill
+%	\begin{subtable}[b]{0.45\textwidth}
+%		\begin{tabular}{|c|c|c|}
+%			\hline
+%			$|X|$ & Time & Uncertainty\\ 
+%		\hline	16 & 31.9 & 1.2243065\\
+%		\hline	17 & 28.6 & 1.2031791\\
+%		\hline	18 & 30.4 & 1.1839474\\
+%		\hline	19 & 34.0 & 1.1644653\\
+%		\hline	20 & 42.1 & 1.1456181\\
+%		\hline	21 & 47.6 & 1.1261252\\
+%		\hline	22 & 62.7 & 1.1089745\\
+%		\hline	23 & 70.0 & 1.0931242\\
+%		\hline	24 & 70.8 & 1.0773088\\
+%		\hline	25 & 139.9 & 1.060928\\
+%		\hline	26 & 154.2 & 1.045715\\
+%		\hline	27 & 213.1 & 1.030605 \\
+%		\hline	28 & 211.3 & 1.016058\\
+%		\hline	29 & 373.1 & 1.001374\\
+%		\hline max=116 & 3300 & 0.895\\ 
+%		\hline		
+%	  \end{tabular}
+%     \end{subtable}
+%	  \caption{Time and uncertainty scaling of pMILP with number of nodes.}
+%    	\label{table14}
+%\end{table}
+%
+%
+%\begin{figure}[b!]
+%	\hspace*{-0.8cm}
+%	\includegraphics[scale=0.6]{Layer3_comparison}.
+%	\caption{Time and uncertainty scaling of pMILP with number of nodes.
+%	Time is using logscale.}
+%	\label{fig3}
+%\end{figure}
+%
+%
+%The exponential complexity with the number of nodes can be seen on Figure \ref{fig3}, where time is represented using logarithmic scale.
 The flat area in the middle is Gurobi having good heuristic to avoid considering all $2^K$ cases when $K<21$ is not too large, but not working so well for $K>25$.
 Notice that when certifying, pMILP uses $|X| \in$ 21-24, which is a good trade off between time and accuracy.
-
-We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
-Further, we tested with the SR \cite{BaB} and FSB heuristics \cite{FSB}, that chooses nodes to branch on for BaB (Branch and Bound).
+%
+%
+%%We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
+%%Further, we tested with the SR \cite{BaB} and FSB heuristics \cite{FSB}, that chooses nodes to branch on for BaB (Branch and Bound).
 When SR and FSB are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
@@
 This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.
-
-\begin{table}[h!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|c|c||c|c|c|c|}
-		\hline
-			&\multicolumn{5}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-10}
-		\text{$|X|$}  & \text{Random} & Huang &SR&FSB& \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
-		\hline
-		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
-		5  &   1.729&1.704 &1.6933&1.6934& 1.603&  1.729& 1.6533 & 1.6574 & \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.6432&1.6393&1.517& 1.696 &  1.5672& 1.5741 & \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.6061& 1.5996&1.466&  1.653& 1.4954& 1.5007 & \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.5730&1.5674&1.438 & 1.619 &1.4321 & 1.4385 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.5431&1.5405&1.427&  1.586 &1.3783 & 1.3823 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.5129&1.5151&1.425& 1.546 &  1.3328& 1.3330 & \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.4871&1.4899&1.424 & 1.502 & 1.2891 & 1.2934 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.4659&1.4686&1.424& 1.469 & 1.2574& 1.2630 & \bf 0.921 \\ \hline \hline
-		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
-	\end{tabular}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-	\label{tab:example1}
-	%\vspace{-0.6cm}
-\end{table}
-
-	\begin{figure}[h!]
-		\centering
-		\vspace*{-0.3cm}
-		\includegraphics[height=9cm]{New Plot for table 3}.
-		\vspace*{-0.4cm}
-		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-		\label{fig_table3_new}
-	\end{figure}
-
-\newpage
-
-\subsubsection*{Usefulness of computing previous layers accurately}
-
-Then, we explore the usefulness of computing accurately each layer inductively.
-For that, we keep the setting of Figure \ref{fig3} / Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
-
-\begin{figure}[h!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
-	\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.
-	Time is using logscale.}
-	\label{fig3LP}
-\end{figure}
-
-\begin{table}[h!]
-	\centering
-\begin{tabular}{|c|c|c|c|}
-	\hline
-	$|X|$ & Time &  With LP for layer 2 & With MILP for layer 2 \\ 
-	\hline	5 & 9.3 & 3.24737  &1.532\\
-	\hline	10 & 10.6 & 3.02214 & 1.371\\
-	\hline	15 & 11.9 & 2.82383  &1.247\\
-	\hline	20 & 13.1 & 2.63862 & 1.145\\
-	\hline	25 & 16.0 & 2.47324 & 1.061\\
-	\hline	30 & 28.3 & 2.32793  &0.989\\
-	\hline	35 & 48.1 & 2.19506 & 0.934\\
-	\hline	40 & 89.4 & 2.07107 & 0.921\\	
-	\hline	
-\end{tabular}
-\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.}
-\label{table15}
-\end{table}
-
-This experiment explains the rationale to use divide and conquer protocol, using many calls
-(one for each neuron) with relatively small number $|X|$ of open nodes rather than fewer calls to MILP with larger number $|X|$ of open nodes. This is clear already with only 1 layer before.
-
-%		\begin{figure}[h]\hspace*{-1cm}
-%		\includegraphics[scale=0.6]{Layzr3_comparison.png}.
-%		\caption{Comparison of layer3 when layer 1 is MILP or LP}
-%\label{fig4}
-%	\end{figure}
-
-\newpage
-
-\subsubsection*{restricting number of open nodes (pMILP) vs setting time-outs (full MILP)}
-
-Running full MILP till a small MIP-Gap (typically 0.001) is reached is extremely time inefficient.
-
-Instead, the standard strategy is to set a reasonable time-out and use whatever bound has been generated.
+%
+%%\begin{table}[h!]	
+%%	\centering
+%%	\begin{tabular}{|c||c|c|c|c|c||c|c|c|c|}
+%%		\hline
+%%			&\multicolumn{5}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-10}
+%%		\text{$|X|$}  & \text{Random} & Huang &SR&FSB& \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
+%%		\hline
+%%		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
+%%		5  &   1.729&1.704 &1.6933&1.6934& 1.603&  1.729& 1.6533 & 1.6574 & \bf 1.532 \\ \hline
+%%		10  &  1.701 &  1.651 &1.6432&1.6393&1.517& 1.696 &  1.5672& 1.5741 & \bf  1.371\\ \hline
+%%		15  & 1.671 &  1.599 &1.6061& 1.5996&1.466&  1.653& 1.4954& 1.5007 & \bf  1.247\\ \hline
+%%		20  &  1.635 & 1.557&1.5730&1.5674&1.438 & 1.619 &1.4321 & 1.4385 & \bf  1.145\\ \hline
+%%		25  &  1.601 & 1.519 &1.5431&1.5405&1.427&  1.586 &1.3783 & 1.3823 & \bf 1.061\\ \hline
+%%		30  & 1.574 & 1.489 &1.5129&1.5151&1.425& 1.546 &  1.3328& 1.3330 & \bf  0.989 \\ \hline
+%%		35  &  1.542 & 1.465&1.4871&1.4899&1.424 & 1.502 & 1.2891 & 1.2934 & \bf 0.934 \\ \hline
+%%		40  & 1.512 & 1.447 &1.4659&1.4686&1.424& 1.469 & 1.2574& 1.2630 & \bf 0.921 \\ \hline \hline
+%%		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
+%%	\end{tabular}
+%%	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
+%%	\label{tab:example1}
+%%	%\vspace{-0.6cm}
+%%\end{table}
+%%
+%
+%
+%%	\begin{figure}[h!]
+%%		\centering
+%%		\vspace*{-0.3cm}
+%%		\includegraphics[height=9cm]{New Plot for table 3}.
+%%		\vspace*{-0.4cm}
+%%		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
+%%		\label{fig_table3_new}
+%%	\end{figure}
+%
+%
+%
+%
+%\newpage
+%
+%\subsubsection*{Usefulness of computing previous layers accurately}	
+%
+%
+%Then, we explore the usefulness of computing accurately each layer inductively.
+%For that, we keep the setting of Figure \ref{fig3} / Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
+%
+%
+%\begin{figure}[h!]
+%	\hspace*{-0.8cm}
+%	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
+%	\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.
+%	Time is using logscale.}
+%	\label{fig3LP}
+%\end{figure}
+%
+%
+%
+%
+%
+%
+%
+%
+%\begin{table}[h!]
+%	\centering
+%\begin{tabular}{|c|c|c|c|}
+%	\hline
+%	$|X|$ & Time &  With LP for layer 2 & With MILP for layer 2 \\ 
+%	\hline	5 & 9.3 & 3.24737  &1.532\\
+%	\hline	10 & 10.6 & 3.02214 & 1.371\\
+%	\hline	15 & 11.9 & 2.82383  &1.247\\
+%	\hline	20 & 13.1 & 2.63862 & 1.145\\
+%	\hline	25 & 16.0 & 2.47324 & 1.061\\
+%	\hline	30 & 28.3 & 2.32793  &0.989\\
+%	\hline	35 & 48.1 & 2.19506 & 0.934\\
+%	\hline	40 & 89.4 & 2.07107 & 0.921\\	
+%	\hline	
+%\end{tabular}
+%\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.}
+%\label{table15}
+%\end{table}
+%
+%
+%
+%%This experiment explains the rationale to use divide and conquer protocol, using many calls
+%%(one for each neuron) with relatively small number $|X|$ of open nodes rather than fewer calls to MILP with larger number $|X|$ of open nodes. This is clear already with only 1 layer before.
+%
+%
+%	
+%%		\begin{figure}[h]\hspace*{-1cm}
+%%		\includegraphics[scale=0.6]{Layzr3_comparison.png}.
+%%		\caption{Comparison of layer3 when layer 1 is MILP or LP}
+%%\label{fig4}
+%%	\end{figure}
+%
+%
+%\newpage
+%
+%\subsubsection*{restricting number of open nodes (pMILP) vs setting time-outs (full MILP)}	
+%
+%Running full MILP till a small MIP-Gap (typically 0.001) is reached is extremely time inefficient.
+%
+%Instead, the standard strategy is to set a reasonable time-out and use whatever bound has been generated.
 We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.
-
-\begin{figure}[h!]\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer7_comparison.png}.
-	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
-	\label{fig4}
-\end{figure}
-
-\begin{table}[h!]
-	\centering
-	\hspace*{4ex}
-\begin{subtable}[b]{0.45\textwidth}
-	\centering
-		\begin{tabular}{|c|c|c|}
-	\hline
-		$|X|$ & Time & Uncertainty\\ 
-	\hline1 &	14 & 3.233021901\\
-\hline	2 & 15.2 & 3.140309921\\
-\hline	3 & 17.21 & 3.059083103\\
-\hline 4 &	17.4 & 2.986166762\\
-\hline	5 &19.2 & 2.856229765\\
-\hline	6 &20.9 & 2.799248232\\
-\hline	7 &23.7 & 2.746167245\\
-\hline	8 &26.6 & 2.69485246\\	
-	\hline
-	\end{tabular}
-	\caption{pMILP}
-\end{subtable}
-\hfill
-\begin{subtable}[b]{0.45\textwidth}
-	\centering
-		\begin{tabular}{|c|c|}
-		\hline
-		Time & Uncertainty\\ 
-		\hline	21.1 & 3.348236261\\
-		\hline	27.6 & 3.24604282\\
-		\hline	38.2 & 3.196640184\\
-		\hline	47.1 & 3.164298172\\
-		\hline	56.7 & 3.146913614\\
-		\hline	106.7 & 3.108035223\\
-		\hline	156.3 & 2.900438725\\
-		\hline	205.8 & 2.848648426\\	
-		\hline	406.7 & 2.800268264 \\	
-		\hline	606.1 & 2.737064255\\	
-		\hline
-	\end{tabular}
-		\caption{full MILP}
-\end{subtable}
-	\caption{Comparison of bounding the number of nodes for pMILP and 
-	using different time outs for full MILP. In both settings, lower and upper bounds of previous layers are the same (computed by pMILP).}
-	\label{table12}
-	\end{table}
-
-pMILP obtains 2.8 accuracy in $<21$ seconds (with 7 open nodes), while full MILP needs 400 seconds to obtain it, a 19x speed up. For 2.7 accuracy, the speedup is $>>$ 22.
-
-Figure \ref{fig4} shows that choosing nodes is much more efficient for time/accuracy trade-off than setting time outs and use full MILP.
+%
+%\begin{figure}[h!]\hspace*{-0.8cm}
+%	\includegraphics[scale=0.6]{Layer7_comparison.png}.
+%	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
+%	\label{fig4}
+%\end{figure}
+%
+%
+%
+%\begin{table}[h!]
+%	\centering
+%	\hspace*{4ex}
+%\begin{subtable}[b]{0.45\textwidth}
+%	\centering
+%		\begin{tabular}{|c|c|c|}
+%	\hline
+%		$|X|$ & Time & Uncertainty\\ 
+%	\hline1 &	14 & 3.233021901\\
+%\hline	2 & 15.2 & 3.140309921\\
+%\hline	3 & 17.21 & 3.059083103\\
+%\hline 4 &	17.4 & 2.986166762\\
+%\hline	5 &19.2 & 2.856229765\\
+%\hline	6 &20.9 & 2.799248232\\
+%\hline	7 &23.7 & 2.746167245\\
+%\hline	8 &26.6 & 2.69485246\\	
+%	\hline
+%	\end{tabular}
+%	\caption{pMILP}
+%\end{subtable}
+%\hfill
+%\begin{subtable}[b]{0.45\textwidth}
+%	\centering
+%		\begin{tabular}{|c|c|}
+%		\hline
+%		Time & Uncertainty\\ 
+%		\hline	21.1 & 3.348236261\\
+%		\hline	27.6 & 3.24604282\\
+%		\hline	38.2 & 3.196640184\\
+%		\hline	47.1 & 3.164298172\\
+%		\hline	56.7 & 3.146913614\\
+%		\hline	106.7 & 3.108035223\\
+%		\hline	156.3 & 2.900438725\\
+%		\hline	205.8 & 2.848648426\\	
+%		\hline	406.7 & 2.800268264 \\	
+%		\hline	606.1 & 2.737064255\\	
+%		\hline
+%	\end{tabular}
+%		\caption{full MILP}
+%\end{subtable}
+%	\caption{Comparison of bounding the number of nodes for pMILP and 
+%	using different time outs for full MILP. In both settings, lower and upper bounds of previous layers are the same (computed by pMILP).}
+%	\label{table12}
+%	\end{table}
+%
+%	
+%
+%	
+%
+%pMILP obtains 2.8 accuracy in $<21$ seconds (with 7 open nodes), while full MILP needs 400 seconds to obtain it, a 19x speed up. For 2.7 accuracy, the speedup is $>>$ 22.
+%
+%
+%
+%Figure \ref{fig4} shows that choosing nodes is much more efficient for time/accuracy trade-off than setting time outs and use full MILP.
 And this is for the smallest DNN we considered (500 hidden neurons, far from the biggest 20k neuron DNN we experimented with)
 
-\section{Comparison with other DNN verifiers}
-
-In the following, we provide results comparing $\alpha,\beta$-Crown to other verifiers, to justify our use of $\alpha,\beta$-Crown as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.
-
-\subsection*{Comparison $\alpha,\beta$-Crown vs PRIMA}
-
-\begin{table}[b!]
-	\centering
-	\begin{tabular}{||l||c|c||c||}
-		\hline \hline
-		Network & $\alpha,\beta$-Crown & Refined $\beta$-Crown & PRIMA \\ 		  
-		\hline
-		MNIST $5 \times 100$ & N/A  & 14.3\% (102s) & 33.2\% (159s)\\ \hline
-		MNIST $5 \times 200$ & N/A & 13.7\% (86s) & 21.1\% (224s) \\ \hline
-		MNIST $8 \times 100$ & N/A  & 20.0\% (103s) & 39.2\% (301s)   \\ \hline
-		MNIST $8 \times 200$ & N/A & 17.6\% (95s) & 28.7\% (395s)  \\ \hline
-		MNIST $6 \times 500$ & 51\% (16s) & $-$ & 64\% (117s) \\ \hline
-		CIFAR CNN-B-adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
-		CIFAR ResNet & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
-	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves.
+%\section{Comparison with other DNN verifiers}
+%
+%In the following, we provide results comparing $\alpha,\beta$-Crown to other verifiers, to justify our use of $\alpha,\beta$-Crown as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.
+%
+%
+%\subsection*{Comparison $\alpha,\beta$-Crown vs PRIMA}
+%
+%
+%\begin{table}[b!]
+%	\centering
+%	\begin{tabular}{||l||c|c||c||}
+%		\hline \hline
+%		Network & $\alpha,\beta$-Crown & Refined $\beta$-Crown & PRIMA \\ 		  
+%		\hline
+%		MNIST $5 \times 100$ & N/A  & 14.3\% (102s) & 33.2\% (159s)\\ \hline
+%		MNIST $5 \times 200$ & N/A & 13.7\% (86s) & 21.1\% (224s) \\ \hline
+%		MNIST $8 \times 100$ & N/A  & 20.0\% (103s) & 39.2\% (301s)   \\ \hline
+%		MNIST $8 \times 200$ & N/A & 17.6\% (95s) & 28.7\% (395s)  \\ \hline
+%		MNIST $6 \times 500$ & 51\% (16s) & $-$ & 64\% (117s) \\ \hline
+%		CIFAR CNN-B-adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
+%		CIFAR ResNet & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
+%	\end{tabular}
+%	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves.
 N/A means that \cite{crown} did not report the numbers, while $-$ means that Refined $\beta$-Crown cannot be run on these DNNs.}
-	\label{table9}
-	%\begin{tablenotes}
-	%	\footnotesize
-%		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
-%		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
-%		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
-%	\end{tablenotes}
-	\end{table}
-
-	PRIMA \cite{prima} is a major verifier in the ERAN toolkit.
+%	\label{table9}
+%	%\begin{tablenotes}
+%	%	\footnotesize
+%%		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
+%%		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
+%%		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
+%%	\end{tablenotes}
+%	\end{table}
+%
+%
+%%	PRIMA \cite{prima} is a major verifier in the ERAN toolkit.
 In Table \ref{table9}, we report the comparison between PRIMA and $\alpha,\beta$-Crown, mainly from \cite{crown}.
@@
 The overall picture is anyway the same.
-
-Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-Crown. However, it is slower and less accurate than Refined $\beta$-Crown.
-On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-Crown, while the runtime is $>5$ times larger.
-Hence, Hybrid MILP is more accurate than Prima with similar runtime or faster.
-
-Notice that kPoly \cite{kpoly}, OptC2V \cite{optC2V}, SDP-FO \cite{SDPFI} numbers were also reported in \cite{crown} on these networks, with even more unfavorable results.
-
-\subsection*{Comparison $\alpha,\beta$-Crown vs MN-BaB}
-
-MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-Crown. Results in \cite{ferrari2022complete}
-are close to those of $\alpha,\beta$-Crown.
+%
+%
+%%Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-Crown. However, it is slower and less accurate than Refined $\beta$-Crown.
+%%On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-Crown, while the runtime is $>5$ times larger.
+%%Hence, Hybrid MILP is more accurate than Prima with similar runtime or faster.
+%%
+%%Notice that kPoly \cite{kpoly}, OptC2V \cite{optC2V}, SDP-FO \cite{SDPFI} numbers were also reported in \cite{crown} on these networks, with even more unfavorable results.
+%%
+%%\subsection*{Comparison $\alpha,\beta$-Crown vs MN-BaB}
+%%
+%%MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-Crown. Results in \cite{ferrari2022complete}
+%%are close to those of $\alpha,\beta$-Crown.
 However, none of the {\em hard} networks from \cite{crown} that we consider have been tested.
@@
 Results are directly comparable with Table \ref{table_hybrid}.
-
-\begin{table}[h!]
-	\centering
-	\begin{tabular}{||l||c|c||c|c||}
-		\hline \hline
-		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & MN-BaB & MN-BaB \\ 
-		 Network & TO=30s & TO=2000s &  TO=30s & TO=2000s \\ 
-		\hline
-		MNIST $5 \times 100$ & 55\% (19s) & 50\%(1026s) & 60\% (19s) & 50\% (1027s) \\ \hline
-		MNIST $6 \times 500$ & 51\% (16s) & 50\% (1002s) & 58\% (18s) & 55\% (1036s) \\ \hline
-		CIFAR CNN-B-adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
-	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, and MN-BaB}
-	\label{table10}
-\end{table}
-
-Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-Crown.
+%%
+%%
+%%\begin{table}[h!]
+%%	\centering
+%%	\begin{tabular}{||l||c|c||c|c||}
+%%		\hline \hline
+%%		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & MN-BaB & MN-BaB \\ 
+%%		 Network & TO=30s & TO=2000s &  TO=30s & TO=2000s \\ 
+%%		\hline
+%%		MNIST $5 \times 100$ & 55\% (19s) & 50\%(1026s) & 60\% (19s) & 50\% (1027s) \\ \hline
+%%		MNIST $6 \times 500$ & 51\% (16s) & 50\% (1002s) & 58\% (18s) & 55\% (1036s) \\ \hline
+%%		CIFAR CNN-B-adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
+%%	\end{tabular}
+%%	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, and MN-BaB}
+%%	\label{table10}
+%%\end{table}
+%%
+%%Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-Crown.
 Notice the specially high number of undecided images for CNN-B-Adv with TO=30s, probably meaning that 30s is too small for MN-BaB on this large DNN.
-Hence, Hybrid MILP is more accurate than MN-BaB with similar runtime or faster.
-
-	\subsection*{Comparison $\alpha,\beta$-Crown vs NNenum}
-
-NNenum \cite{nnenum} is a complete verifier with good performance according to VNNcomp.
-It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-Crown. The experiments section in \cite{nnenum} does not report
-the {\em hard} DNNs we are considering. We tried to experiment it on the same MNIST 
-$6 \times 500$ and CIFAR CNN-B-adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
-We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-Crown, on both 
-MNIST $5 \times 100$ and CIFAR CNN-B-Adv. 
-On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-Crown, but far from the accuracy Hybrid MILP.
-On CIFAR CNN-B-adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.
-
-\begin{table}[h!]
-	\centering
-	\begin{tabular}{||l||c||c||c||c||}
-		\hline \hline
-		 & $\alpha,\beta$-Crown & NNenum & Hybrid\\ 
-		 Network & TO=2000s &  TO=2000s & MILP\\ 
-		\hline
-		MNIST $5 \times 100$ & 50\%(1026s) & 44\% (1046s) & \bf 13\% (46s)\\ \hline
-		CIFAR CNN-B-adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
-	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown and NNenum with 2000s time-out, and Hybrid MILP}.
-	\label{table11}
-\end{table}
-
-{\color{blue}
-
-\section{Average vs max time per pMILP call}
-
-We provide in Table \ref{table112} the average as well as maximum time to perform $MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
-For 6x500, we provide results for two different $\varepsilon$, following our test from Figure \ref{fig2}.
-
-\begin{table}[h!]
-	\centering
-	\begin{tabular}{||l|c|c||}
-		\hline
-		Network & average time & maximum time \\ \hline
-		MNIST 5$\times$100 & 0.41s & 1.87 \\
-		$\epsilon = 0.026$ &  & \\  \hline
-		MNIST 5$\times$200 &  0.75s & 5.31s \\ 
-		$\epsilon = 0.015$ & & \\  \hline
-		MNIST 8$\times$100 & 0.39s & 1.41s \\
-		$\epsilon = 0.026$ & &  \\  \hline
-		MNIST 8$\times$200 & 0.49s & 1.63s \\ 
-		$\epsilon = 0.015$ & & \\  \hline
-		MNIST 6$\times$500 & &   \\ 
-		$\epsilon = 0.035$ & 1.4s & 3.5s \\ 
-		$\epsilon = 0.1$ & 44.6s & 310s \\  \hline 
-		CIFAR CNN-B-adv &  & \\
-		$\epsilon = 2/255$& 1s & 609s \\ \hline \hline
-	\end{tabular}
-	\caption{average and maximum time per $\MILP_X$ calls for image 3 (MNIST) and image 76 (CIFAR10).}
-	\label{table112}
-\end{table}
-
-Notice that DNN 6$\times$ 500 and $\epsilon=0.1$ is a very hard instance as being very close to the falsification $\epsilon \approx 0.11$.
+%%Hence, Hybrid MILP is more accurate than MN-BaB with similar runtime or faster.
+%%
+%%
+%%
+%%	\subsection*{Comparison $\alpha,\beta$-Crown vs NNenum}
+%%
+%%NNenum \cite{nnenum} is a complete verifier with good performance according to VNNcomp.
+%%It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-Crown. The experiments section in \cite{nnenum} does not report
+%%the {\em hard} DNNs we are considering. We tried to experiment it on the same MNIST 
+%%$6 \times 500$ and CIFAR CNN-B-adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
+%%We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-Crown, on both 
+%%MNIST $5 \times 100$ and CIFAR CNN-B-Adv. 
+%%On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-Crown, but far from the accuracy Hybrid MILP.
+%%On CIFAR CNN-B-adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.
+%
+%
+%\begin{table}[h!]
+%	\centering
+%	\begin{tabular}{||l||c||c||c||c||}
+%		\hline \hline
+%		 & $\alpha,\beta$-Crown & NNenum & Hybrid\\ 
+%		 Network & TO=2000s &  TO=2000s & MILP\\ 
+%		\hline
+%		MNIST $5 \times 100$ & 50\%(1026s) & 44\% (1046s) & \bf 13\% (46s)\\ \hline
+%		CIFAR CNN-B-adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
+%	\end{tabular}
+%	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown and NNenum with 2000s time-out, and Hybrid MILP}.
+%	\label{table11}
+%\end{table}
+%
+%
+%%{\color{blue}
+%%
+%%\section{Average vs max time per pMILP call}
+%%
+%%We provide in Table \ref{table112} the average as well as maximum time to perform $MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
+%%For 6x500, we provide results for two different $\varepsilon$, following our test from Figure \ref{fig2}.
+%%
+%%\begin{table}[h!]
+%%	\centering
+%%	\begin{tabular}{||l|c|c||}
+%%		\hline
+%%		Network & average time & maximum time \\ \hline
+%%		MNIST 5$\times$100 & 0.41s & 1.87 \\
+%%		$\epsilon = 0.026$ &  & \\  \hline
+%%		MNIST 5$\times$200 &  0.75s & 5.31s \\ 
+%%		$\epsilon = 0.015$ & & \\  \hline
+%%		MNIST 8$\times$100 & 0.39s & 1.41s \\
+%%		$\epsilon = 0.026$ & &  \\  \hline
+%%		MNIST 8$\times$200 & 0.49s & 1.63s \\ 
+%%		$\epsilon = 0.015$ & & \\  \hline
+%%		MNIST 6$\times$500 & &   \\ 
+%%		$\epsilon = 0.035$ & 1.4s & 3.5s \\ 
+%%		$\epsilon = 0.1$ & 44.6s & 310s \\  \hline 
+%%		CIFAR CNN-B-adv &  & \\
+%%		$\epsilon = 2/255$& 1s & 609s \\ \hline \hline
+%%	\end{tabular}
+%%	\caption{average and maximum time per $\MILP_X$ calls for image 3 (MNIST) and image 76 (CIFAR10).}
+%%	\label{table112}
+%%\end{table}
+%
+%%Notice that DNN 6$\times$ 500 and $\epsilon=0.1$ is a very hard instance as being very close to the falsification $\epsilon \approx 0.11$.
 This is thus not representative of the average case.
 Also,  on this image 3, pMILP succeeds to verify $\epsilon= 1.054$, while $\alpha,\beta$-CROWN can only certify $\epsilon = 0.0467$ within the 10 000s Time-out.
-
-For CNN-B-Adv, the very long maximum time for a MILP call is an outlier: it happens only for one output layer, for which the number $K$ of open nodes is particularly large (around 200 out of 20000 neurons) to certify this hard image 76.
+%%
+%%For CNN-B-Adv, the very long maximum time for a MILP call is an outlier: it happens only for one output layer, for which the number $K$ of open nodes is particularly large (around 200 out of 20000 neurons) to certify this hard image 76.
 Indeed, the average time is at $1s$.
 Notice that this does not lead to a runtime of 20.000s, as 20 threads are used by pMILP
-in parallel (similar to competing solutions, except $\alpha,\beta$-CROWN which uses $>4096$ GPU cores).
-
-}
-
-\end{document}
-
-\section{SR Heuristic for choosing nodes}
-
-Here we provide the formula of BaB-SR from paper \cite{BaB}.
-
-\begin{align*}
-	\nu_{n+1} &= -1&\\
-	\hat{\nu}_k &= W^T_kv_{k+1}, k = n,\cdots,1 &\\
-	\nu_{k,j} &= \begin{cases}
-		0  &\text{ if }u_{k[j]}<0 \hspace*{2ex}(j\in\mathcal{I}^-_k)\\
-		\hat{\nu}_{k[j]} &\text{ if }l_{k[j]}>0 \hspace*{2.5ex}(j\in\mathcal{I}^-_k)\\
-		\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_-  &\text{ otherwise } \hspace*{3ex}(j\in\mathcal{I}_k)\\ 
-	\end{cases}\\
-	&\hspace*{22ex}\text{for } k = n,\cdots,2&
-\end{align*}and\begin{align*}
-	s_{i[j]} = |\max(v_{i[j]}b_{i-1[j]},(v_{i[j]}-1)b_{i-1[j]})-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+|
-\end{align*}
-
-\begin{figure}[b!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Plot for table 3}.
-	\caption{Plot for table 3}
-	\label{fig_table3}
-\end{figure}
-
-\begin{table}[h!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|c|}
-		\hline
-		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
-		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
-		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
-		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
-		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
-		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
-		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
-		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
-		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
-		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
-		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
-		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
-	\end{tabular}
-	\caption{BSR and FSB}
-	\label{BSRandFSB}
-	%\vspace{-0.6cm}
-\end{table}
-
-\end{document}
-
-\subsection*{Formula for ResNet}
-
-Consider a ResNet, like ResNet4b, we list the formula for an Add layer.
-
-Suppose we are dealing with an Add layer $l$, target node $z$, with previous layer $l_1$ and shortcut connection previous layer $l_2$, starting from a layer $l_0$, that is:
-\begin{align*}
-	l &= l_1+l_2\\
-	l_2 &= Conv_{W_2}(\ReLU(l_0))\\
-	l_1' &= Conv_{W'_1}(\ReLU(l_0))\\
-	l_1 &= Conv_{W_1}(\ReLU(l'_{1}))
-\end{align*}The paths are $$l_0\rightarrow \ReLU(l_0)\rightarrow l_2\rightarrow l,$$ and $$l_0\rightarrow \ReLU(l_0)\rightarrow l'_1\rightarrow \ReLU(l_1')\rightarrow l_1\rightarrow l.$$
-
-So, for nodes in layer $l_1'$, we can use the same formula as previous section, i.e., the formula at the end of page 6: for a node $b$ in $l_1'$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$,
-\begin{align*}
-\Utility\_\max\nolimits^x(b) &= W_{bx} \times (\sol(\hat{b})- \ReLU(\sol(b)))\\
-\Utility\_\max\nolimits^z(b) &= \Utility\_\max\nolimits^x(b)
-\end{align*}
-
-For nodes in layer $l_0$, the simple idea is to consider both paths, and sum up the utilities of two paths. For a node $a$ in $l_0$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$ ,
-\begin{align*}
-		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
-		\Utility_\_\max\nolimits^y(a) &= -W_{ay} \Delta(\hat{a})\\
-	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
-	\forall b \in \ell, \Delta(\hat{b}) &=
-	\begin{cases}
-		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bx} > 0\\
-		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)\geq0\\
-		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)<0		 
-	\end{cases}\\
-	\Utility\_\max\nolimits^x(a) &= -\sum_{b \in \ell} W_{bx} \Delta(\hat{b})\\
-	\Utility\_\max\nolimits^z(a) &= \Utility\_\max\nolimits^x(a)+\Utility\_\max\nolimits^y(a)
-\end{align*}
-
-\section{Formula for Utility}
-
-Recall that for nodes $a,b$, we use 
-$\hat{a}, \hat{b}$ to denote variable after ReLU functions, and
-$\Delta(a),\Delta(\hat{a}),\Delta(b),\Delta(\hat{b})$ to denote the changes of those variables.
+%%in parallel (similar to competing solutions, except $\alpha,\beta$-CROWN which uses $>4096$ GPU cores).
+%%
+%%
+%%}
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%\end{document}
+%
+%
+%\section{SR Heuristic for choosing nodes}
+%
+%Here we provide the formula of BaB-SR from paper \cite{BaB}.
+%
+%\begin{align*}
+%	\nu_{n+1} &= -1&\\
+%	\hat{\nu}_k &= W^T_kv_{k+1}, k = n,\cdots,1 &\\
+%	\nu_{k,j} &= \begin{cases}
+%		0  &\text{ if }u_{k[j]}<0 \hspace*{2ex}(j\in\mathcal{I}^-_k)\\
+%		\hat{\nu}_{k[j]} &\text{ if }l_{k[j]}>0 \hspace*{2.5ex}(j\in\mathcal{I}^-_k)\\
+%		\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_-  &\text{ otherwise } \hspace*{3ex}(j\in\mathcal{I}_k)\\ 
+%	\end{cases}\\
+%	&\hspace*{22ex}\text{for } k = n,\cdots,2&
+%\end{align*}and\begin{align*}
+%	s_{i[j]} = |\max(v_{i[j]}b_{i-1[j]},(v_{i[j]}-1)b_{i-1[j]})-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+|
+%\end{align*}
+%
+%
+%\begin{figure}[b!]
+%	\hspace*{-0.8cm}
+%	\includegraphics[scale=0.6]{Plot for table 3}.
+%	\caption{Plot for table 3}
+%	\label{fig_table3}
+%\end{figure}
+%
+%
+%\begin{table}[h!]	
+%	\centering
+%	\begin{tabular}{|c||c|c|c|c|}
+%		\hline
+%		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
+%		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
+%		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
+%		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
+%		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
+%		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
+%		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
+%		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
+%		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
+%		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
+%		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
+%		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
+%	\end{tabular}
+%	\caption{BSR and FSB}
+%	\label{BSRandFSB}
+%	%\vspace{-0.6cm}
+%\end{table}
+%
+%
+%
+%\end{document}
+%
+%
+%
+%
+%\subsection*{Formula for ResNet}
+%
+%Consider a ResNet, like ResNet4b, we list the formula for an Add layer.
+%
+%Suppose we are dealing with an Add layer $l$, target node $z$, with previous layer $l_1$ and shortcut connection previous layer $l_2$, starting from a layer $l_0$, that is:
+%\begin{align*}
+%	l &= l_1+l_2\\
+%	l_2 &= Conv_{W_2}(\ReLU(l_0))\\
+%	l_1' &= Conv_{W'_1}(\ReLU(l_0))\\
+%	l_1 &= Conv_{W_1}(\ReLU(l'_{1}))
+%\end{align*}The paths are $$l_0\rightarrow \ReLU(l_0)\rightarrow l_2\rightarrow l,$$ and $$l_0\rightarrow \ReLU(l_0)\rightarrow l'_1\rightarrow \ReLU(l_1')\rightarrow l_1\rightarrow l.$$
+%
+%So, for nodes in layer $l_1'$, we can use the same formula as previous section, i.e., the formula at the end of page 6: for a node $b$ in $l_1'$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$,
+%\begin{align*}
+%\Utility\_\max\nolimits^x(b) &= W_{bx} \times (\sol(\hat{b})- \ReLU(\sol(b)))\\
+%\Utility\_\max\nolimits^z(b) &= \Utility\_\max\nolimits^x(b)
+%\end{align*}
+%
+%For nodes in layer $l_0$, the simple idea is to consider both paths, and sum up the utilities of two paths. For a node $a$ in $l_0$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$ ,
+%\begin{align*}
+%		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
+%		\Utility_\_\max\nolimits^y(a) &= -W_{ay} \Delta(\hat{a})\\
+%	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
+%	\forall b \in \ell, \Delta(\hat{b}) &=
+%	\begin{cases}
+%		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bx} > 0\\
+%		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)\geq0\\
+%		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)<0		 
+%	\end{cases}\\
+%	\Utility\_\max\nolimits^x(a) &= -\sum_{b \in \ell} W_{bx} \Delta(\hat{b})\\
+%	\Utility\_\max\nolimits^z(a) &= \Utility\_\max\nolimits^x(a)+\Utility\_\max\nolimits^y(a)
+%\end{align*}
+%
+%	
+%	
+%		
+%	
+%
+%
+%\section{Formula for Utility}
+%
+%
+%Recall that for nodes $a,b$, we use 
+%$\hat{a}, \hat{b}$ to denote variable after ReLU functions, and
+%$\Delta(a),\Delta(\hat{a}),\Delta(b),\Delta(\hat{b})$ to denote the changes of those variables.
 $a$ means the source node, and $b$ means nodes one layer after $a$, and $z$ is 2 layers after $a$ and one after $b$.
-
-The utility function for a node $a$ wrt neuron $z$ is defined inductively as follows:
-
-\begin{align*}
-	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
-	\Delta(b) &= W_{ab}\Delta(\hat{a})\\
-	\Delta(\hat{b}) &=
-	\begin{cases}
-		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
-		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
-		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
-	\end{cases}\\
-	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
-\end{align*}
-
-}
+%
+%The utility function for a node $a$ wrt neuron $z$ is defined inductively as follows:
+%
+%
+%\begin{align*}
+%	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
+%	\Delta(b) &= W_{ab}\Delta(\hat{a})\\
+%	\Delta(\hat{b}) &=
+%	\begin{cases}
+%		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
+%		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
+%		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
+%	\end{cases}\\
+%	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
+%\end{align*}
+%
+%}

### 2025-01-31 CAV 2025 TODO/proofsb.tex
update

@@
 We open [48,48] to compute bounds for hidden layer 2, [21,24] for layer 3, [11,14] for layer 4, [6,9] for layer 5, [3,6] for layer 6, [2,5] for layer 7, [1,4] for hidden layer 8 (if any), and we open [14,17] for the output layer.
-{\color{blue} The exact number of open nodes in the range [a,a+3] is decided automatically for each neuron being computed : ReLUs are ranked according to their value by Utility, and the a top ReLUs are open.
+%{\color{blue} The exact number of open nodes in the range [a,a+3] is decided automatically for each neuron being computed : ReLUs are ranked according to their value by Utility, and the a top ReLUs are open.
 Then, ReLUs ranked a+1,a+2, a+3 are opened if their Utility value is larger than a small threshold.
@@
 In Table \ref{table20}, we sum-up the TO and minimum open numbers for each DNN considered.
-
-{\color{blue}
-$\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU, while Partial MILP uses 20 CPU-threads.}
+%
+%{\color{blue}
+%$\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU, while Partial MILP uses 20 CPU-threads.}
 
@@
 
-{\color{blue}
-Last, for Gurobi, we use a custom MIP-Gap (from $0.001$ to $0.1$) and time-out parameters, depending on the seen improvement and the possibility to make a node stable.
+%{\color{blue}
+%Last, for Gurobi, we use a custom MIP-Gap (from $0.001$ to $0.1$) and time-out parameters, depending on the seen improvement and the possibility to make a node stable.
 This is low level implementation details that will be available in the code once the paper is accepted.
-}
-
-%{\color{blue}
-%
-%
-%
-%
-%
-%\section{Ablation studies}	
-%
-%In this section, we consider ablation studies to understand how each feature enables the efficiency of pMILP.
-%
-%\subsection*{Time scaling with open nodes}	
-%
-%First, we explore the time scaling with different number of open nodes, for our full Utility function using nodes in the last two layers (Layer 1 and 2), providing finer details than in Table 3, with the same setting, i.e.
-previous layer being computed with full MILP.
-%
-%
-%
-%
-%
-%\begin{table}[h!]
-%		\centering
-%		\hspace*{4ex}
-%		\begin{subtable}[b]{0.45\textwidth}
-%		\begin{tabular}{|c|c|c|}
-%		\hline
-%		$|X|$ & Time & Uncertainty\\ 
-%		\hline	0 & 2.6 & 1.760946128\\
-%		\hline	1 & 7.3 & 1.702986873\\
-%		\hline	2 & 11.1 & 1.65469034\\
-%		\hline	3 & 16.3 & 1.612137282\\
-%		\hline	4 & 15.5 & 1.571001109\\
-%		\hline	5 & 15.7 & 1.531925404\\
-%		\hline	6 & 15.8 & 1.49535638\\
-%		\hline	7 & 16.4 & 1.46189314\\
-%		\hline	8 &  15.8 & 1.4299535\\
-%		\hline	9 &  17.2 & 1.4006364\\
-%		\hline	10 & 22.5 & 1.3711203\\
-%		\hline	11 & 27.2 & 1.3438245\\
-%		\hline	12 & 21.6 & 1.3183356\\
-%		\hline	13 & 28.7 & 1.2938690\\
-%		\hline	14 & 29.6 & 1.2690507\\
-%		\hline	15 & 24.5 & 1.2475106\\
-%		\hline
-%	  \end{tabular}
-%	\end{subtable}
-%	\hfill
-%	\begin{subtable}[b]{0.45\textwidth}
-%		\begin{tabular}{|c|c|c|}
-%			\hline
-%			$|X|$ & Time & Uncertainty\\ 
-%		\hline	16 & 31.9 & 1.2243065\\
-%		\hline	17 & 28.6 & 1.2031791\\
-%		\hline	18 & 30.4 & 1.1839474\\
-%		\hline	19 & 34.0 & 1.1644653\\
-%		\hline	20 & 42.1 & 1.1456181\\
-%		\hline	21 & 47.6 & 1.1261252\\
-%		\hline	22 & 62.7 & 1.1089745\\
-%		\hline	23 & 70.0 & 1.0931242\\
-%		\hline	24 & 70.8 & 1.0773088\\
-%		\hline	25 & 139.9 & 1.060928\\
-%		\hline	26 & 154.2 & 1.045715\\
-%		\hline	27 & 213.1 & 1.030605 \\
-%		\hline	28 & 211.3 & 1.016058\\
-%		\hline	29 & 373.1 & 1.001374\\
-%		\hline max=116 & 3300 & 0.895\\ 
-%		\hline		
-%	  \end{tabular}
-%     \end{subtable}
-%	  \caption{Time and uncertainty scaling of pMILP with number of nodes.}
-%    	\label{table14}
-%\end{table}
-%
-%
-%\begin{figure}[b!]
-%	\hspace*{-0.8cm}
-%	\includegraphics[scale=0.6]{Layer3_comparison}.
-%	\caption{Time and uncertainty scaling of pMILP with number of nodes.
-%	Time is using logscale.}
-%	\label{fig3}
-%\end{figure}
-%
-%
-%The exponential complexity with the number of nodes can be seen on Figure \ref{fig3}, where time is represented using logarithmic scale.
-The flat area in the middle is Gurobi having good heuristic to avoid considering all $2^K$ cases when $K<21$ is not too large, but not working so well for $K>25$.
-Notice that when certifying, pMILP uses $|X| \in$ 21-24, which is a good trade off between time and accuracy.
-%
-%
-%%We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
-%%Further, we tested with the SR \cite{BaB} and FSB heuristics \cite{FSB}, that chooses nodes to branch on for BaB (Branch and Bound).
-When SR and FSB are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
-\ref{fig_table3_new}: SR and FSB are worse than \cite{DivideAndSlide} for $<35$ open ReLU nodes, although unlike the latter, they can rank ReLU nodes in several layer before (which helps them a bit), and far worse than Utility.
-Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite \cite{FSB}.
-This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.
-%
-%%\begin{table}[h!]	
-%%	\centering
-%%	\begin{tabular}{|c||c|c|c|c|c||c|c|c|c|}
-%%		\hline
-%%			&\multicolumn{5}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-10}
-%%		\text{$|X|$}  & \text{Random} & Huang &SR&FSB& \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
-%%		\hline
-%%		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
-%%		5  &   1.729&1.704 &1.6933&1.6934& 1.603&  1.729& 1.6533 & 1.6574 & \bf 1.532 \\ \hline
-%%		10  &  1.701 &  1.651 &1.6432&1.6393&1.517& 1.696 &  1.5672& 1.5741 & \bf  1.371\\ \hline
-%%		15  & 1.671 &  1.599 &1.6061& 1.5996&1.466&  1.653& 1.4954& 1.5007 & \bf  1.247\\ \hline
-%%		20  &  1.635 & 1.557&1.5730&1.5674&1.438 & 1.619 &1.4321 & 1.4385 & \bf  1.145\\ \hline
-%%		25  &  1.601 & 1.519 &1.5431&1.5405&1.427&  1.586 &1.3783 & 1.3823 & \bf 1.061\\ \hline
-%%		30  & 1.574 & 1.489 &1.5129&1.5151&1.425& 1.546 &  1.3328& 1.3330 & \bf  0.989 \\ \hline
-%%		35  &  1.542 & 1.465&1.4871&1.4899&1.424 & 1.502 & 1.2891 & 1.2934 & \bf 0.934 \\ \hline
-%%		40  & 1.512 & 1.447 &1.4659&1.4686&1.424& 1.469 & 1.2574& 1.2630 & \bf 0.921 \\ \hline \hline
-%%		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
-%%	\end{tabular}
-%%	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-%%	\label{tab:example1}
-%%	%\vspace{-0.6cm}
-%%\end{table}
-%%
-%
-%
-%%	\begin{figure}[h!]
-%%		\centering
-%%		\vspace*{-0.3cm}
-%%		\includegraphics[height=9cm]{New Plot for table 3}.
-%%		\vspace*{-0.4cm}
-%%		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-%%		\label{fig_table3_new}
-%%	\end{figure}
-%
-%
-%
-%
-%\newpage
-%
-%\subsubsection*{Usefulness of computing previous layers accurately}	
-%
-%
-%Then, we explore the usefulness of computing accurately each layer inductively.
-%For that, we keep the setting of Figure \ref{fig3} / Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
-%
-%
-%\begin{figure}[h!]
-%	\hspace*{-0.8cm}
-%	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
-%	\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.
-%	Time is using logscale.}
-%	\label{fig3LP}
-%\end{figure}
-%
-%
-%
-%
-%
-%
-%
-%
-%\begin{table}[h!]
-%	\centering
-%\begin{tabular}{|c|c|c|c|}
-%	\hline
-%	$|X|$ & Time &  With LP for layer 2 & With MILP for layer 2 \\ 
-%	\hline	5 & 9.3 & 3.24737  &1.532\\
-%	\hline	10 & 10.6 & 3.02214 & 1.371\\
-%	\hline	15 & 11.9 & 2.82383  &1.247\\
-%	\hline	20 & 13.1 & 2.63862 & 1.145\\
-%	\hline	25 & 16.0 & 2.47324 & 1.061\\
-%	\hline	30 & 28.3 & 2.32793  &0.989\\
-%	\hline	35 & 48.1 & 2.19506 & 0.934\\
-%	\hline	40 & 89.4 & 2.07107 & 0.921\\	
-%	\hline	
-%\end{tabular}
-%\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.}
-%\label{table15}
-%\end{table}
-%
-%
-%
-%%This experiment explains the rationale to use divide and conquer protocol, using many calls
-%%(one for each neuron) with relatively small number $|X|$ of open nodes rather than fewer calls to MILP with larger number $|X|$ of open nodes. This is clear already with only 1 layer before.
-%
-%
-%	
-%%		\begin{figure}[h]\hspace*{-1cm}
-%%		\includegraphics[scale=0.6]{Layzr3_comparison.png}.
-%%		\caption{Comparison of layer3 when layer 1 is MILP or LP}
-%%\label{fig4}
-%%	\end{figure}
-%
-%
-%\newpage
-%
-%\subsubsection*{restricting number of open nodes (pMILP) vs setting time-outs (full MILP)}	
-%
-%Running full MILP till a small MIP-Gap (typically 0.001) is reached is extremely time inefficient.
-%
-%Instead, the standard strategy is to set a reasonable time-out and use whatever bound has been generated.
-We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.
-%
-%\begin{figure}[h!]\hspace*{-0.8cm}
-%	\includegraphics[scale=0.6]{Layer7_comparison.png}.
-%	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
-%	\label{fig4}
-%\end{figure}
-%
-%
-%
-%\begin{table}[h!]
-%	\centering
-%	\hspace*{4ex}
-%\begin{subtable}[b]{0.45\textwidth}
-%	\centering
-%		\begin{tabular}{|c|c|c|}
-%	\hline
-%		$|X|$ & Time & Uncertainty\\ 
-%	\hline1 &	14 & 3.233021901\\
-%\hline	2 & 15.2 & 3.140309921\\
-%\hline	3 & 17.21 & 3.059083103\\
-%\hline 4 &	17.4 & 2.986166762\\
-%\hline	5 &19.2 & 2.856229765\\
-%\hline	6 &20.9 & 2.799248232\\
-%\hline	7 &23.7 & 2.746167245\\
-%\hline	8 &26.6 & 2.69485246\\	
-%	\hline
-%	\end{tabular}
-%	\caption{pMILP}
-%\end{subtable}
-%\hfill
-%\begin{subtable}[b]{0.45\textwidth}
-%	\centering
-%		\begin{tabular}{|c|c|}
-%		\hline
-%		Time & Uncertainty\\ 
-%		\hline	21.1 & 3.348236261\\
-%		\hline	27.6 & 3.24604282\\
-%		\hline	38.2 & 3.196640184\\
-%		\hline	47.1 & 3.164298172\\
-%		\hline	56.7 & 3.146913614\\
-%		\hline	106.7 & 3.108035223\\
-%		\hline	156.3 & 2.900438725\\
-%		\hline	205.8 & 2.848648426\\	
-%		\hline	406.7 & 2.800268264 \\	
-%		\hline	606.1 & 2.737064255\\	
-%		\hline
-%	\end{tabular}
-%		\caption{full MILP}
-%\end{subtable}
-%	\caption{Comparison of bounding the number of nodes for pMILP and 
-%	using different time outs for full MILP. In both settings, lower and upper bounds of previous layers are the same (computed by pMILP).}
-%	\label{table12}
-%	\end{table}
-%
-%	
-%
-%	
-%
-%pMILP obtains 2.8 accuracy in $<21$ seconds (with 7 open nodes), while full MILP needs 400 seconds to obtain it, a 19x speed up. For 2.7 accuracy, the speedup is $>>$ 22.
-%
-%
-%
-%Figure \ref{fig4} shows that choosing nodes is much more efficient for time/accuracy trade-off than setting time outs and use full MILP.
-And this is for the smallest DNN we considered (500 hidden neurons, far from the biggest 20k neuron DNN we experimented with)
-
-%\section{Comparison with other DNN verifiers}
-%
-%In the following, we provide results comparing $\alpha,\beta$-Crown to other verifiers, to justify our use of $\alpha,\beta$-Crown as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.
-%
-%
-%\subsection*{Comparison $\alpha,\beta$-Crown vs PRIMA}
-%
-%
-%\begin{table}[b!]
-%	\centering
-%	\begin{tabular}{||l||c|c||c||}
-%		\hline \hline
-%		Network & $\alpha,\beta$-Crown & Refined $\beta$-Crown & PRIMA \\ 		  
-%		\hline
-%		MNIST $5 \times 100$ & N/A  & 14.3\% (102s) & 33.2\% (159s)\\ \hline
-%		MNIST $5 \times 200$ & N/A & 13.7\% (86s) & 21.1\% (224s) \\ \hline
-%		MNIST $8 \times 100$ & N/A  & 20.0\% (103s) & 39.2\% (301s)   \\ \hline
-%		MNIST $8 \times 200$ & N/A & 17.6\% (95s) & 28.7\% (395s)  \\ \hline
-%		MNIST $6 \times 500$ & 51\% (16s) & $-$ & 64\% (117s) \\ \hline
-%		CIFAR CNN-B-adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
-%		CIFAR ResNet & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
-%	\end{tabular}
-%	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves.
-N/A means that \cite{crown} did not report the numbers, while $-$ means that Refined $\beta$-Crown cannot be run on these DNNs.}
-%	\label{table9}
-%	%\begin{tablenotes}
-%	%	\footnotesize
-%%		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
-%%		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
-%%		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
-%%	\end{tablenotes}
-%	\end{table}
-%
-%
-%%	PRIMA \cite{prima} is a major verifier in the ERAN toolkit.
-In Table \ref{table9}, we report the comparison between PRIMA and $\alpha,\beta$-Crown, mainly from \cite{crown}.
-The setting is mainly similar from ours, but numbers are not perfectly comparable as the images tested are not  exactly the same (1000 first or 200 first images for CNN-B-Adv), vs 100 first in Tables \ref{table_hybrid}, \ref{table_beta}.
-Also, time-out settings and hardware are slightly different.
-The overall picture is anyway the same.
-%
-%
-%%Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-Crown. However, it is slower and less accurate than Refined $\beta$-Crown.
-%%On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-Crown, while the runtime is $>5$ times larger.
-%%Hence, Hybrid MILP is more accurate than Prima with similar runtime or faster.
-%%
-%%Notice that kPoly \cite{kpoly}, OptC2V \cite{optC2V}, SDP-FO \cite{SDPFI} numbers were also reported in \cite{crown} on these networks, with even more unfavorable results.
-%%
-%%\subsection*{Comparison $\alpha,\beta$-Crown vs MN-BaB}
-%%
-%%MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-Crown. Results in \cite{ferrari2022complete}
-%%are close to those of $\alpha,\beta$-Crown.
-However, none of the {\em hard} networks from \cite{crown} that we consider have been tested.
-We thus tested three representative {\em hard} DNNs (first 100 images) to understand how MN-BaB fairs on such hard instances, and report the numbers in Table \ref{table10}.
-Results are directly comparable with Table \ref{table_hybrid}.
-%%
-%%
-%%\begin{table}[h!]
-%%	\centering
-%%	\begin{tabular}{||l||c|c||c|c||}
-%%		\hline \hline
-%%		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & MN-BaB & MN-BaB \\ 
-%%		 Network & TO=30s & TO=2000s &  TO=30s & TO=2000s \\ 
-%%		\hline
-%%		MNIST $5 \times 100$ & 55\% (19s) & 50\%(1026s) & 60\% (19s) & 50\% (1027s) \\ \hline
-%%		MNIST $6 \times 500$ & 51\% (16s) & 50\% (1002s) & 58\% (18s) & 55\% (1036s) \\ \hline
-%%		CIFAR CNN-B-adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
-%%	\end{tabular}
-%%	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, and MN-BaB}
-%%	\label{table10}
-%%\end{table}
-%%
-%%Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-Crown.
-Notice the specially high number of undecided images for CNN-B-Adv with TO=30s, probably meaning that 30s is too small for MN-BaB on this large DNN.
-%%Hence, Hybrid MILP is more accurate than MN-BaB with similar runtime or faster.
-%%
-%%
-%%
-%%	\subsection*{Comparison $\alpha,\beta$-Crown vs NNenum}
-%%
-%%NNenum \cite{nnenum} is a complete verifier with good performance according to VNNcomp.
-%%It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-Crown. The experiments section in \cite{nnenum} does not report
-%%the {\em hard} DNNs we are considering. We tried to experiment it on the same MNIST 
-%%$6 \times 500$ and CIFAR CNN-B-adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
-%%We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-Crown, on both 
-%%MNIST $5 \times 100$ and CIFAR CNN-B-Adv. 
-%%On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-Crown, but far from the accuracy Hybrid MILP.
-%%On CIFAR CNN-B-adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.
-%
-%
-%\begin{table}[h!]
-%	\centering
-%	\begin{tabular}{||l||c||c||c||c||}
-%		\hline \hline
-%		 & $\alpha,\beta$-Crown & NNenum & Hybrid\\ 
-%		 Network & TO=2000s &  TO=2000s & MILP\\ 
-%		\hline
-%		MNIST $5 \times 100$ & 50\%(1026s) & 44\% (1046s) & \bf 13\% (46s)\\ \hline
-%		CIFAR CNN-B-adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
-%	\end{tabular}
-%	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown and NNenum with 2000s time-out, and Hybrid MILP}.
-%	\label{table11}
-%\end{table}
-%
-%
-%%{\color{blue}
-%%
-%%\section{Average vs max time per pMILP call}
-%%
-%%We provide in Table \ref{table112} the average as well as maximum time to perform $MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
-%%For 6x500, we provide results for two different $\varepsilon$, following our test from Figure \ref{fig2}.
-%%
-%%\begin{table}[h!]
-%%	\centering
-%%	\begin{tabular}{||l|c|c||}
-%%		\hline
-%%		Network & average time & maximum time \\ \hline
-%%		MNIST 5$\times$100 & 0.41s & 1.87 \\
-%%		$\epsilon = 0.026$ &  & \\  \hline
-%%		MNIST 5$\times$200 &  0.75s & 5.31s \\ 
-%%		$\epsilon = 0.015$ & & \\  \hline
-%%		MNIST 8$\times$100 & 0.39s & 1.41s \\
-%%		$\epsilon = 0.026$ & &  \\  \hline
-%%		MNIST 8$\times$200 & 0.49s & 1.63s \\ 
-%%		$\epsilon = 0.015$ & & \\  \hline
-%%		MNIST 6$\times$500 & &   \\ 
-%%		$\epsilon = 0.035$ & 1.4s & 3.5s \\ 
-%%		$\epsilon = 0.1$ & 44.6s & 310s \\  \hline 
-%%		CIFAR CNN-B-adv &  & \\
-%%		$\epsilon = 2/255$& 1s & 609s \\ \hline \hline
-%%	\end{tabular}
-%%	\caption{average and maximum time per $\MILP_X$ calls for image 3 (MNIST) and image 76 (CIFAR10).}
-%%	\label{table112}
-%%\end{table}
-%
-%%Notice that DNN 6$\times$ 500 and $\epsilon=0.1$ is a very hard instance as being very close to the falsification $\epsilon \approx 0.11$.
-This is thus not representative of the average case.
-Also,  on this image 3, pMILP succeeds to verify $\epsilon= 1.054$, while $\alpha,\beta$-CROWN can only certify $\epsilon = 0.0467$ within the 10 000s Time-out.
-%%
-%%For CNN-B-Adv, the very long maximum time for a MILP call is an outlier: it happens only for one output layer, for which the number $K$ of open nodes is particularly large (around 200 out of 20000 neurons) to certify this hard image 76.
-Indeed, the average time is at $1s$.
-Notice that this does not lead to a runtime of 20.000s, as 20 threads are used by pMILP
-%%in parallel (similar to competing solutions, except $\alpha,\beta$-CROWN which uses $>4096$ GPU cores).
-%%
-%%
-%%}
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%\end{document}
-%
-%
-%\section{SR Heuristic for choosing nodes}
-%
-%Here we provide the formula of BaB-SR from paper \cite{BaB}.
-%
-%\begin{align*}
-%	\nu_{n+1} &= -1&\\
-%	\hat{\nu}_k &= W^T_kv_{k+1}, k = n,\cdots,1 &\\
-%	\nu_{k,j} &= \begin{cases}
-%		0  &\text{ if }u_{k[j]}<0 \hspace*{2ex}(j\in\mathcal{I}^-_k)\\
-%		\hat{\nu}_{k[j]} &\text{ if }l_{k[j]}>0 \hspace*{2.5ex}(j\in\mathcal{I}^-_k)\\
-%		\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_-  &\text{ otherwise } \hspace*{3ex}(j\in\mathcal{I}_k)\\ 
-%	\end{cases}\\
-%	&\hspace*{22ex}\text{for } k = n,\cdots,2&
-%\end{align*}and\begin{align*}
-%	s_{i[j]} = |\max(v_{i[j]}b_{i-1[j]},(v_{i[j]}-1)b_{i-1[j]})-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+|
-%\end{align*}
-%
-%
-%\begin{figure}[b!]
-%	\hspace*{-0.8cm}
-%	\includegraphics[scale=0.6]{Plot for table 3}.
-%	\caption{Plot for table 3}
-%	\label{fig_table3}
-%\end{figure}
-%
-%
-%\begin{table}[h!]	
-%	\centering
-%	\begin{tabular}{|c||c|c|c|c|}
-%		\hline
-%		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
-%		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
-%		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
-%		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
-%		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
-%		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
-%		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
-%		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
-%		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
-%		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
-%		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
-%		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
-%	\end{tabular}
-%	\caption{BSR and FSB}
-%	\label{BSRandFSB}
-%	%\vspace{-0.6cm}
-%\end{table}
-%
-%
-%
-%\end{document}
-%
-%
-%
-%
-%\subsection*{Formula for ResNet}
-%
-%Consider a ResNet, like ResNet4b, we list the formula for an Add layer.
-%
-%Suppose we are dealing with an Add layer $l$, target node $z$, with previous layer $l_1$ and shortcut connection previous layer $l_2$, starting from a layer $l_0$, that is:
-%\begin{align*}
-%	l &= l_1+l_2\\
-%	l_2 &= Conv_{W_2}(\ReLU(l_0))\\
-%	l_1' &= Conv_{W'_1}(\ReLU(l_0))\\
-%	l_1 &= Conv_{W_1}(\ReLU(l'_{1}))
-%\end{align*}The paths are $$l_0\rightarrow \ReLU(l_0)\rightarrow l_2\rightarrow l,$$ and $$l_0\rightarrow \ReLU(l_0)\rightarrow l'_1\rightarrow \ReLU(l_1')\rightarrow l_1\rightarrow l.$$
-%
-%So, for nodes in layer $l_1'$, we can use the same formula as previous section, i.e., the formula at the end of page 6: for a node $b$ in $l_1'$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$,
-%\begin{align*}
-%\Utility\_\max\nolimits^x(b) &= W_{bx} \times (\sol(\hat{b})- \ReLU(\sol(b)))\\
-%\Utility\_\max\nolimits^z(b) &= \Utility\_\max\nolimits^x(b)
-%\end{align*}
-%
-%For nodes in layer $l_0$, the simple idea is to consider both paths, and sum up the utilities of two paths. For a node $a$ in $l_0$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$ ,
-%\begin{align*}
-%		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
-%		\Utility_\_\max\nolimits^y(a) &= -W_{ay} \Delta(\hat{a})\\
-%	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
-%	\forall b \in \ell, \Delta(\hat{b}) &=
-%	\begin{cases}
-%		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bx} > 0\\
-%		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)\geq0\\
-%		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)<0		 
-%	\end{cases}\\
-%	\Utility\_\max\nolimits^x(a) &= -\sum_{b \in \ell} W_{bx} \Delta(\hat{b})\\
-%	\Utility\_\max\nolimits^z(a) &= \Utility\_\max\nolimits^x(a)+\Utility\_\max\nolimits^y(a)
-%\end{align*}
-%
-%	
-%	
-%		
-%	
-%
-%
-%\section{Formula for Utility}
-%
-%
-%Recall that for nodes $a,b$, we use 
-%$\hat{a}, \hat{b}$ to denote variable after ReLU functions, and
-%$\Delta(a),\Delta(\hat{a}),\Delta(b),\Delta(\hat{b})$ to denote the changes of those variables.
-$a$ means the source node, and $b$ means nodes one layer after $a$, and $z$ is 2 layers after $a$ and one after $b$.
-%
-%The utility function for a node $a$ wrt neuron $z$ is defined inductively as follows:
-%
-%
-%\begin{align*}
-%	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
-%	\Delta(b) &= W_{ab}\Delta(\hat{a})\\
-%	\Delta(\hat{b}) &=
-%	\begin{cases}
-%		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
-%		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
-%		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
-%	\end{cases}\\
-%	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
-%\end{align*}
-%
 %}

### 2025-01-31 CAV 2025 TODO/proofsb.tex
recover the file
update

--- 2025-01-26 CAV 2025 TODO/proofsb.tex
@@
 
-{\color{blue}
 \section{Parameter settings}
@@
 The conclusion are thus unchanged.
-}
 
@@
 We open [48,48] to compute bounds for hidden layer 2, [21,24] for layer 3, [11,14] for layer 4, [6,9] for layer 5, [3,6] for layer 6, [2,5] for layer 7, [1,4] for hidden layer 8 (if any), and we open [14,17] for the output layer.
-{\color{blue} The exact number of open nodes in the range [a,a+3] is decided automatically for each neuron being computed : ReLUs are ranked according to their value by Utility, and the a top ReLUs are open.
+ The exact number of open nodes in the range [a,a+3] is decided automatically for each neuron being computed : ReLUs are ranked according to their value by Utility, and the a top ReLUs are open.
 Then, ReLUs ranked a+1,a+2, a+3 are opened if their Utility value is larger than a small threshold.
 We set the threshold at 0.01.
-It should be seen as a way to save runtime when Utility knows that the next node by ranking (a+i) will not impact accuracy much (thanks to the upper bound from Proposition \ref{prop2}).}
+It should be seen as a way to save runtime when Utility knows that the next node by ranking (a+i) will not impact accuracy much (thanks to the upper bound from Proposition \ref{prop2}).
 
@@
 
-{\color{blue}
-$\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU, while Partial MILP uses 20 CPU-threads.}
+$\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU, while Partial MILP uses 20 CPU-threads.
 
@@
 
-{\color{blue}
 Last, for Gurobi, we use a custom MIP-Gap (from $0.001$ to $0.1$) and time-out parameters, depending on the seen improvement and the possibility to make a node stable.
 This is low level implementation details that will be available in the code once the paper is accepted.
-}
-
-{\color{blue}
 
@@
 
-We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
-Further, we tested with the SR \cite{BaB} and FSB heuristics \cite{FSB}, that chooses nodes to branch on for BaB (Branch and Bound).
+%
+%We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
+%Further, we tested with the SR \cite{BaB} and FSB heuristics \cite{FSB}, that chooses nodes to branch on for BaB (Branch and Bound).
 When SR and FSB are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
@@
 This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.
-
-\begin{table}[h!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|c|c||c|c|c|c|}
-		\hline
-			&\multicolumn{5}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-10}
-		\text{$|X|$}  & \text{Random} & Huang &SR&FSB& \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
-		\hline
-		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
-		5  &   1.729&1.704 &1.6933&1.6934& 1.603&  1.729& 1.6533 & 1.6574 & \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.6432&1.6393&1.517& 1.696 &  1.5672& 1.5741 & \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.6061& 1.5996&1.466&  1.653& 1.4954& 1.5007 & \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.5730&1.5674&1.438 & 1.619 &1.4321 & 1.4385 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.5431&1.5405&1.427&  1.586 &1.3783 & 1.3823 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.5129&1.5151&1.425& 1.546 &  1.3328& 1.3330 & \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.4871&1.4899&1.424 & 1.502 & 1.2891 & 1.2934 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.4659&1.4686&1.424& 1.469 & 1.2574& 1.2630 & \bf 0.921 \\ \hline \hline
-		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
-	\end{tabular}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-	\label{tab:example1}
-	%\vspace{-0.6cm}
-\end{table}
-
-	\begin{figure}[h!]
-		\centering
-		\vspace*{-0.3cm}
-		\includegraphics[height=9cm]{New Plot for table 3}.
-		\vspace*{-0.4cm}
-		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-		\label{fig_table3_new}
-	\end{figure}
+%
+%\begin{table}[h!]	
+%	\centering
+%	\begin{tabular}{|c||c|c|c|c|c||c|c|c|c|}
+%		\hline
+%			&\multicolumn{5}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-10}
+%		\text{$|X|$}  & \text{Random} & Huang &SR&FSB& \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
+%		\hline
+%		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
+%		5  &   1.729&1.704 &1.6933&1.6934& 1.603&  1.729& 1.6533 & 1.6574 & \bf 1.532 \\ \hline
+%		10  &  1.701 &  1.651 &1.6432&1.6393&1.517& 1.696 &  1.5672& 1.5741 & \bf  1.371\\ \hline
+%		15  & 1.671 &  1.599 &1.6061& 1.5996&1.466&  1.653& 1.4954& 1.5007 & \bf  1.247\\ \hline
+%		20  &  1.635 & 1.557&1.5730&1.5674&1.438 & 1.619 &1.4321 & 1.4385 & \bf  1.145\\ \hline
+%		25  &  1.601 & 1.519 &1.5431&1.5405&1.427&  1.586 &1.3783 & 1.3823 & \bf 1.061\\ \hline
+%		30  & 1.574 & 1.489 &1.5129&1.5151&1.425& 1.546 &  1.3328& 1.3330 & \bf  0.989 \\ \hline
+%		35  &  1.542 & 1.465&1.4871&1.4899&1.424 & 1.502 & 1.2891 & 1.2934 & \bf 0.934 \\ \hline
+%		40  & 1.512 & 1.447 &1.4659&1.4686&1.424& 1.469 & 1.2574& 1.2630 & \bf 0.921 \\ \hline \hline
+%		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
+%	\end{tabular}
+%	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
+%	\label{tab:example1}
+%	%\vspace{-0.6cm}
+%\end{table}
+%
+%
+%
+%	\begin{figure}[h!]
+%		\centering
+%		\vspace*{-0.3cm}
+%		\includegraphics[height=9cm]{New Plot for table 3}.
+%		\vspace*{-0.4cm}
+%		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
+%		\label{fig_table3_new}
+%	\end{figure}
 
@@
 	\label{table9}
-	%\begin{tablenotes}
-	%	\footnotesize
-%		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
-%		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
-%		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
-%	\end{tablenotes}
+	\begin{tablenotes}
+		\footnotesize
+		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
+		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
+		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
+	\end{tablenotes}
 	\end{table}
@@
 
-{\color{blue}
-
 \section{Average vs max time per pMILP call}
@@
 in parallel (similar to competing solutions, except $\alpha,\beta$-CROWN which uses $>4096$ GPU cores).
-
-}
 

### 2025-01-31 CAV 2025 TODO/introduction.tex
update and mark a problem

@@
 Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.
-Compared with the heuristic in \cite{DivideAndSlide}, SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
+Compared with the heuristic in \cite{DivideAndSlide}, {\color{red} SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1}))}.We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
 

### 2025-01-31 CAV 2025 TODO/proofsb.tex
update
update and mark a problem

@@
 Then, we explore the usefulness of computing accurately each layer inductively.
-For that, we keep the setting of Figure \ref{fig3} / Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
+For that, we keep the setting of  Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
 
@@
 
-\section{SR Heuristic for choosing nodes}
-
-Here we provide the formula of BaB-SR from paper \cite{BaB}.
-
-\begin{align*}
-	\nu_{n+1} &= -1&\\
-	\hat{\nu}_k &= W^T_kv_{k+1}, k = n,\cdots,1 &\\
-	\nu_{k,j} &= \begin{cases}
-		0  &\text{ if }u_{k[j]}<0 \hspace*{2ex}(j\in\mathcal{I}^-_k)\\
-		\hat{\nu}_{k[j]} &\text{ if }l_{k[j]}>0 \hspace*{2.5ex}(j\in\mathcal{I}^-_k)\\
-		\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_-  &\text{ otherwise } \hspace*{3ex}(j\in\mathcal{I}_k)\\ 
-	\end{cases}\\
-	&\hspace*{22ex}\text{for } k = n,\cdots,2&
-\end{align*}and\begin{align*}
-	s_{i[j]} = |\max(v_{i[j]}b_{i-1[j]},(v_{i[j]}-1)b_{i-1[j]})-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+|
-\end{align*}
-
-\begin{figure}[b!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Plot for table 3}.
-	\caption{Plot for table 3}
-	\label{fig_table3}
-\end{figure}
-
-\begin{table}[h!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|c|}
-		\hline
-		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
-		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
-		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
-		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
-		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
-		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
-		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
-		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
-		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
-		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
-		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
-		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
-	\end{tabular}
-	\caption{BSR and FSB}
-	\label{BSRandFSB}
-	%\vspace{-0.6cm}
-\end{table}
-
-\end{document}
-
-\subsection*{Formula for ResNet}
-
-Consider a ResNet, like ResNet4b, we list the formula for an Add layer.
-
-Suppose we are dealing with an Add layer $l$, target node $z$, with previous layer $l_1$ and shortcut connection previous layer $l_2$, starting from a layer $l_0$, that is:
-\begin{align*}
-	l &= l_1+l_2\\
-	l_2 &= Conv_{W_2}(\ReLU(l_0))\\
-	l_1' &= Conv_{W'_1}(\ReLU(l_0))\\
-	l_1 &= Conv_{W_1}(\ReLU(l'_{1}))
-\end{align*}The paths are $$l_0\rightarrow \ReLU(l_0)\rightarrow l_2\rightarrow l,$$ and $$l_0\rightarrow \ReLU(l_0)\rightarrow l'_1\rightarrow \ReLU(l_1')\rightarrow l_1\rightarrow l.$$
-
-So, for nodes in layer $l_1'$, we can use the same formula as previous section, i.e., the formula at the end of page 6: for a node $b$ in $l_1'$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$,
-\begin{align*}
-\Utility\_\max\nolimits^x(b) &= W_{bx} \times (\sol(\hat{b})- \ReLU(\sol(b)))\\
-\Utility\_\max\nolimits^z(b) &= \Utility\_\max\nolimits^x(b)
-\end{align*}
-
-For nodes in layer $l_0$, the simple idea is to consider both paths, and sum up the utilities of two paths. For a node $a$ in $l_0$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$ ,
-\begin{align*}
-		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
-		\Utility_\_\max\nolimits^y(a) &= -W_{ay} \Delta(\hat{a})\\
-	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
-	\forall b \in \ell, \Delta(\hat{b}) &=
-	\begin{cases}
-		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bx} > 0\\
-		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)\geq0\\
-		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)<0		 
-	\end{cases}\\
-	\Utility\_\max\nolimits^x(a) &= -\sum_{b \in \ell} W_{bx} \Delta(\hat{b})\\
-	\Utility\_\max\nolimits^z(a) &= \Utility\_\max\nolimits^x(a)+\Utility\_\max\nolimits^y(a)
-\end{align*}
-
-\section{Formula for Utility}
-
-Recall that for nodes $a,b$, we use 
-$\hat{a}, \hat{b}$ to denote variable after ReLU functions, and
-$\Delta(a),\Delta(\hat{a}),\Delta(b),\Delta(\hat{b})$ to denote the changes of those variables.
+%
+%\section{SR Heuristic for choosing nodes}
+%
+%Here we provide the formula of BaB-SR from paper \cite{BaB}.
+%
+%\begin{align*}
+%	\nu_{n+1} &= -1&\\
+%	\hat{\nu}_k &= W^T_kv_{k+1}, k = n,\cdots,1 &\\
+%	\nu_{k,j} &= \begin{cases}
+%		0  &\text{ if }u_{k[j]}<0 \hspace*{2ex}(j\in\mathcal{I}^-_k)\\
+%		\hat{\nu}_{k[j]} &\text{ if }l_{k[j]}>0 \hspace*{2.5ex}(j\in\mathcal{I}^-_k)\\
+%		\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_-  &\text{ otherwise } \hspace*{3ex}(j\in\mathcal{I}_k)\\ 
+%	\end{cases}\\
+%	&\hspace*{22ex}\text{for } k = n,\cdots,2&
+%\end{align*}and\begin{align*}
+%	s_{i[j]} = |\max(v_{i[j]}b_{i-1[j]},(v_{i[j]}-1)b_{i-1[j]})-\frac{u_{k[j]}}{u_{k[j]}-l_{k[j]}}[\hat{\nu}_{k[j]}]_+|
+%\end{align*}
+%
+%
+%\begin{figure}[b!]
+%	\hspace*{-0.8cm}
+%	\includegraphics[scale=0.6]{Plot for table 3}.
+%	\caption{Plot for table 3}
+%	\label{fig_table3}
+%\end{figure}
+%
+%
+%\begin{table}[h!]	
+%	\centering
+%	\begin{tabular}{|c||c|c|c|c|}
+%		\hline
+%		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
+%		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
+%		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
+%		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
+%		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
+%		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
+%		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
+%		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
+%		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
+%		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
+%		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
+%		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
+%	\end{tabular}
+%	\caption{BSR and FSB}
+%	\label{BSRandFSB}
+%	%\vspace{-0.6cm}
+%\end{table}
+%
+%
+%
+%\end{document}
+%
+%
+%
+%
+%\subsection*{Formula for ResNet}
+%
+%Consider a ResNet, like ResNet4b, we list the formula for an Add layer.
+%
+%Suppose we are dealing with an Add layer $l$, target node $z$, with previous layer $l_1$ and shortcut connection previous layer $l_2$, starting from a layer $l_0$, that is:
+%\begin{align*}
+%	l &= l_1+l_2\\
+%	l_2 &= Conv_{W_2}(\ReLU(l_0))\\
+%	l_1' &= Conv_{W'_1}(\ReLU(l_0))\\
+%	l_1 &= Conv_{W_1}(\ReLU(l'_{1}))
+%\end{align*}The paths are $$l_0\rightarrow \ReLU(l_0)\rightarrow l_2\rightarrow l,$$ and $$l_0\rightarrow \ReLU(l_0)\rightarrow l'_1\rightarrow \ReLU(l_1')\rightarrow l_1\rightarrow l.$$
+%
+%So, for nodes in layer $l_1'$, we can use the same formula as previous section, i.e., the formula at the end of page 6: for a node $b$ in $l_1'$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$,
+%\begin{align*}
+%\Utility\_\max\nolimits^x(b) &= W_{bx} \times (\sol(\hat{b})- \ReLU(\sol(b)))\\
+%\Utility\_\max\nolimits^z(b) &= \Utility\_\max\nolimits^x(b)
+%\end{align*}
+%
+%For nodes in layer $l_0$, the simple idea is to consider both paths, and sum up the utilities of two paths. For a node $a$ in $l_0$, suppose $z=x+y$ for $x$ in layer $l_1$ and $y$ in $l_2$ ,
+%\begin{align*}
+%		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
+%		\Utility_\_\max\nolimits^y(a) &= -W_{ay} \Delta(\hat{a})\\
+%	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
+%	\forall b \in \ell, \Delta(\hat{b}) &=
+%	\begin{cases}
+%		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bx} > 0\\
+%		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)\geq0\\
+%		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bx} < 0 \text{ and } \sol(b)<0		 
+%	\end{cases}\\
+%	\Utility\_\max\nolimits^x(a) &= -\sum_{b \in \ell} W_{bx} \Delta(\hat{b})\\
+%	\Utility\_\max\nolimits^z(a) &= \Utility\_\max\nolimits^x(a)+\Utility\_\max\nolimits^y(a)
+%\end{align*}
+%
+%	
+%	
+%		
+%	
+%
+%
+%\section{Formula for Utility}
+%
+%
+%Recall that for nodes $a,b$, we use 
+%$\hat{a}, \hat{b}$ to denote variable after ReLU functions, and
+%$\Delta(a),\Delta(\hat{a}),\Delta(b),\Delta(\hat{b})$ to denote the changes of those variables.
 $a$ means the source node, and $b$ means nodes one layer after $a$, and $z$ is 2 layers after $a$ and one after $b$.
-
-The utility function for a node $a$ wrt neuron $z$ is defined inductively as follows:
-
-\begin{align*}
-	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
-	\Delta(b) &= W_{ab}\Delta(\hat{a})\\
-	\Delta(\hat{b}) &=
-	\begin{cases}
-		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
-		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
-		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
-	\end{cases}\\
-	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
-\end{align*}
-
-}
+%
+%The utility function for a node $a$ wrt neuron $z$ is defined inductively as follows:
+%
+%
+%\begin{align*}
+%	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
+%	\Delta(b) &= W_{ab}\Delta(\hat{a})\\
+%	\Delta(\hat{b}) &=
+%	\begin{cases}
+%		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
+%		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
+%		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
+%	\end{cases}\\
+%	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
+%\end{align*}
+%
+%}

### 2025-01-31 CAV 2025 TODO/introduction.tex
update

--- 2025-01-29 CAV 2025 TODO/introduction.tex
@@
 Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.
-Compared with the heuristic in \cite{DivideAndSlide}, SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
+Compared with the heuristic in \cite{DivideAndSlide},  SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Plot \ref{fig_table3})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
 

### 2025-01-31 CAV 2025 TODO/introduction.tex
update

@@
 Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.
-Compared with the heuristic in \cite{DivideAndSlide},  SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Plot \ref{fig_table3})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
+Compared with the heuristic in \cite{DivideAndSlide},  SAS is much more efficient ($\approx 6$ times less integer variables for same accuracy (Plot \ref{fig_table3})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
 

### 2025-01-31 CAV 2025 TODO/Paper_noProof.tex
intro

@@
 We compare them theoretically as well as experimentally.
-Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em rank} within this selection.
-Compared with previous attempts, SAS reduces the number of integer variables by around 4 times while maintaining the same level of accuracy.
+Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em branch} within this selection.
+Compared with previous attempts, SAS reduces the number of binary variables by around 6 times while maintaining the same level of accuracy.
 Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CIFAR CNNs with 20 000 nodes.

### 2025-01-31 CAV 2025 TODO/introduction.tex
intro

@@
 Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.
-Compared with the heuristic in \cite{DivideAndSlide},  SAS is much more efficient ($\approx 6$ times less integer variables for same accuracy (Plot \ref{fig_table3})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
+Compared with the heuristic in \cite{DivideAndSlide},  SAS is much more efficient ($\approx 6$ times less binary variables for same accuracy (Plot \ref{fig_table3})).
+We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
 
@@
 	\item For the second question, we propose a new verifier, called {\em Hybrid MILP}, invoking first 	$\alpha,\beta$-Crown with short time-out to settle the easy instances.
-On those ({\em hard}) instances which are neither certified nor falsified, we call pMILP with few neurons encoded as integer variables.
+On those ({\em hard}) instances which are neither certified nor falsified, we call pMILP with few neurons encoded as binary variables.
 Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.

### 2025-01-31 CAV 2025 TODO/Paper_noProof.tex
overall pass

@@
 In this paper, we developed a novel solution-aware scoring (SAS) function to select few ReLU nodes to consider with binary variables to compute accurately bounds in DNNs. 
-The solution awareness allows SAS to compute an accurate score for each ReLU, which enables partial MILP to be very efficient, necessitating $\approx4$x less binary variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
+The solution awareness allows SAS to compute an accurate score for each ReLU, which enables partial MILP to be very efficient, necessitating $\approx6$x less binary variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
 As the worst-case complexity is exponential in the number of binary variables, this big leap ahead has large implication in terms of scalability to larger DNNs, making it possible to verify quite large DNNs such as CNN-B-Adv with 2M parameters and 20000 activation functions.
@@
 Last, we adapted BaB-SR \cite{BaB} and FSB \cite{FSB} as global scoring (GS) functions. 
-We compare them both theoretically and experimentally with solution-aware scoring: While GS are not as accurate as SAS for ReLU {\em selection}, they are better suited to select the {\em order} with which to branch over this selection, at least when the order is static and does not depend upon the branch.
+We compared GS with SAS both theoretically and experimentally with solution-aware scoring: While GS are not as efficient as SAS for ReLU {\em selection} (2x more binary variables needed), GS functions generate {\em static order} more adapted to every branch of a BaB process.
 This opens up interesting future research directions, to hybridize different scoring for different tasks;  e.g.

### 2025-01-31 CAV 2025 TODO/experiments.tex
update the plot
update the table
overall pass

@@
 	\vspace*{-0.3cm}
-	\includegraphics[height=7cm]{open.png}.
+	\includegraphics[height=7cm]{CNN-B-ADV_layer7_comparison_image85.png}.
 	\vspace*{-0.4cm}
@@
 we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
-We tested over the $\vx=37$th image in the CIFAR dataset.
+We tested over the $\vx=85$th image in the CIFAR dataset.
 To measure the accuracy, we measure the uncertainty of all nodes in the 4th layer:
@@
 Overall, SAS is more accurate than GS, more accurate than Huang, more accurate than random choice of variables. SAS significantly outperforms other solutions, 
-with around 3 times less binary variables for the same accuracy (10 v 30, 6 vs 16).
-Each individual node of the last layer displays a similar pattern, and the pattern is similar for different images (not displayed).
+with 2 times less binary variables for the same accuracy (10 vs 22) vs GS and 6 times vs Huang (4 vs 24).
+Each node of the 4th layer displays a similar pattern, and the pattern is similar for different images (see appendix).
+
+\smallskip
 
 Gurobi relies on a BaB procedure to compute bounds.
-The standard Gurobi ordering of variables is adaptative in each branch.
-We report in Table \ref{table.order} experiments on changing the ordering on variables in Gurobi, when the selection of ReLUs is fixed by SAS.
-We compared it with the static order provided by SAS, as well as the static order provided by GS, for runtime at a fixed accuracy, where we report the distance to verify the image.
-The test are done on CIFAR image 85 and CNN-B-Adv.
+We report in Table \ref{table.order} experiments on changing the ordering on variables in Gurobi, when the selection of ReLUs is fixed by SAS on CNN-B-Adv Image 85.
+We compared
+the standard Gurobi ordering of variables, which is adaptative in each branch, 
+with the static order provided by SAS, as well as the static order provided by GS, wrt runtime at a fixed accuracy (we report the {\em distance} to verify the image).
 
@@
 		\hline \hline
-		Gurobi & 0.384 & 252s & &  & & & 0.315  & 306s  \\ 
-		SAS (static) & 0.384 & 448s & &  & & & 0.355  & 971s \\
-		GS (static) & 0.384 & {\bf 251s} & &  &  & & 0.315 & {\bf 281s} \\ \hline
+		Gurobi & 0.384 & 252s & 0.368&265  &0.342 & 287& 0.315  & 306s  \\ 
+		SAS (static) & 0.384 & 448s & 0.368&759  &0.365 &971 & 0.355  & 971s \\
+		GS (static) & 0.384 & {\bf 251s} &0.368 &{\bf 253}  & 0.342 &{\bf 270} & 0.315 & {\bf 281s} \\ \hline
 	\end{tabular}
@@
 SAS ordering is particularly counter-productive because it is accurate only for one branch (the most complicated one), whereas Gurobi can adapt the order to each branch.
-However, the GS ordering (with the SAS selection) is better as it is general and not local to a solution, with better runtime than Gurobi, despite its staticness whereas Gurobi order is adaptative.
+However, the GS {\em ordering} (with the SAS {\em selection}) is better as it is general and not local to a solution, with better runtime than Gurobi, despite its staticness whereas Gurobi order is adaptative.
 Using SAS order for the solution branch, and GS ordering for other branches should be more efficient, but we cannot experiment that within the closed-source Gurobi solver.
@@
 To assess the verification efficiency and runtime vs $\alpha,\beta$-Crown, we 
-conducted evaluations on the neural networks which are {\em complex} to verify, from \cite{crown}.
-Namely, these are 6 ReLU-DNNs: 5 MNIST DNN that can be found in the \href{https://github.com/eth-sri/eran}{ERAN GitHub}
+conducted evaluations  on neural networks tested in \cite{crown} which are mostly {\em complex} to verify (as easy instances are already appropriately taken care of).
+Namely, 6 ReLU-DNNs: 5 MNIST DNN that can be found in the \href{https://github.com/eth-sri/eran}{ERAN GitHub}
 (the 4th to the 8th DNNs provided) as well as 1 CIFAR CNN from 
@@
 
+\newpage
+
 {\em Analysis}: overall, Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, and even 10 times less on smaller DNNs.
-It can scale up to quite large hard DNNs, such as CNN-B-Adv with 2M parameters and 20K activations.
+It can scale up to quite large hard DNNs, such as CNN-B-Adv with 2M parameters and 20K activation functions.
 
-Compared with $\alpha,\beta$-Crown:
-on easy instances (see the very large ResNet), Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN, as $\alpha,\beta$-CROWN is called first because it is very efficient for such instances.
+Compared with $\alpha,\beta$-Crown: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN (e.g.
+even on the very large ResNet), since Hybrid MILP calls first $\alpha,\beta$-CROWN as it is very efficient for easy instances.
 
-On hard instances (the 6 first DNNs tested), compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, it is much more accurate, with a reduction of undecided images by $9\%-43\%$.
+On hard instances (the 6 first DNNs tested), compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, Hybrid MILP is much more accurate, with a reduction of undecided images by $9\%-43\%$.
 It is also from 20x faster on smaller networks to similar time on the largest DNN.
@@
 $11\%$ for CNN-B-Adv, i.e.
-half undecided images), although the average runtime is also obviously larger (solving hard istances takes longer than solving easy instances).
+half the undecided images), although the average runtime is also obviously larger (solving hard instances takes longer than solving easy instances).
 

### 2025-01-31 CAV 2025 TODO/proofsb.tex
update
overall pass

@@
 
-\subsection*{Setting for $\alpha,\beta$-Crown}
-
-The networks were already tested by $\alpha,\beta$-Crown \cite{crown}.
-We thus simply reused the parameter files from \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN/blob/main/complete_verifier/exp_configs/beta_crown/}{their Github},
-except for time-out which we explicitly mention.
-
-e.g., for CNN-B-Adv: "solver: batch size: 512 beta-crown: iteration: 20" and
-for MNIST 5x100: "solver: batch size: 1024 beta-crown: iteration: 20".
-
-We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to.
-From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-Crown on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP.
-The conclusion are thus unchanged.
-
 \subsection*{Setting for Hybrid MILP}
@@
 
+Partial MILP uses 20 CPU-threads, while $\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU,
+
 The setting for partial MILP for fully-connected DNNs is about how many neurons need to be opened (once set, the selection is automatic).
-The runtime depending crucially upon the number of open ReLU neurons, we set it quite tightly, only allowing few neuron deviation to accommodate to a particularly accurate/inaccurate bound computation (measure by the weight of the remaining Utility function).
+The runtime depending crucially upon the number of open ReLU neurons, we set it quite tightly, only allowing few neuron deviation to accommodate to a particularly accurate/inaccurate bound computation (measured by the weight of the remaining SAS score).
 As complexity increases with the layer considered, as the size of the MILP model grows, we lower this number with the depth, only committing to an intermediate number for the output neuron (the number of output neurons  is smaller than hidden layer, and this is the most important computation).
@@
 We open [48,48] to compute bounds for hidden layer 2, [21,24] for layer 3, [11,14] for layer 4, [6,9] for layer 5, [3,6] for layer 6, [2,5] for layer 7, [1,4] for hidden layer 8 (if any), and we open [14,17] for the output layer.
- The exact number of open nodes in the range [a,a+3] is decided automatically for each neuron being computed : ReLUs are ranked according to their value by Utility, and the a top ReLUs are open.
-Then, ReLUs ranked a+1,a+2, a+3 are opened if their Utility value is larger than a small threshold.
+ The exact number of open nodes in the range [a,a+3] is decided automatically for each neuron being computed : ReLUs are ranked according to their value by SAS, and the a top ReLUs are open.
+Then, ReLUs ranked a+1,a+2, a+3 are opened if their SAS value is larger than a small threshold.
 We set the threshold at 0.01.
-It should be seen as a way to save runtime when Utility knows that the next node by ranking (a+i) will not impact accuracy much (thanks to the upper bound from Proposition \ref{prop2}).
+It should be seen as a way to save runtime when SAS knows that the next node by ranking (a+i) will not impact accuracy much (thanks to the upper bound from Proposition \ref{prop2}).
 
-\begin{table}[b!]
+\begin{table}[t!]
 	\centering
@@
 
-In Table \ref{table20}, we sum-up the TO and minimum open numbers for each DNN considered.
+Table \ref{table20} sums up the TO and the minimum numbers of ReLU opened.
+%for each DNN considered.
 
-$\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU, while Partial MILP uses 20 CPU-threads.
+Last, for Gurobi, we use a custom MIP-Gap (from $0.001$ to $0.1$) and time-out parameters, depending on the seen improvement and the possibility to make a node stable.
+This is low level implementation details that will be available in the code once the paper is accepted.
 
@@
 
-Last, for Gurobi, we use a custom MIP-Gap (from $0.001$ to $0.1$) and time-out parameters, depending on the seen improvement and the possibility to make a node stable.
-This is low level implementation details that will be available in the code once the paper is accepted.
+\subsection*{Setting for $\alpha,\beta$-Crown}
 
-\section{Ablation studies}
+The networks were already tested by $\alpha,\beta$-Crown \cite{crown}.
+We thus simply reused the parameter files from \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN/blob/main/complete_verifier/exp_configs/beta_crown/}{their Github},
+except for time-out which we explicitly mention:
+e.g. for CNN-B-Adv: "solver: batch size: 512 beta-crown: iteration: 20"; and
+for MNIST 5x100: "solver: batch size: 1024 beta-crown: iteration: 20".
 
-In this section, we consider ablation studies to understand how each feature enables the efficiency of pMILP.
+%We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to.
+From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-Crown on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP.
+The conclusion are thus unchanged.
+
+\section{Additional experiments including Ablation studies}
+
+First, we provide Fig.~\ref{fig5}, similar to 
+Fig.~\ref{fig_table3} but on a different image, namely 37.
+It display similar pattern as image 85, with an even larger difference between SAS and GS (around 3x more binary variables are necessary for GS to match the accuracy of SAS).
+
+\begin{figure}[h!]
+	\hspace*{-0.8cm}
+	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image37}
+	\caption{Comparison of different methods with image 37.}
+	\label{fig5}
+\end{figure}
+
+Further, we consider ablation studies to understand how each feature enables the efficiency of pMILP.
 
@@
 
-First, we explore the time scaling with different number of open nodes, for our full Utility function using nodes in the last two layers (Layer 1 and 2), providing finer details than in Table 3, with the same setting, i.e.
-previous layer being computed with full MILP.
+First, we explore the time scaling with different number of open nodes, for SAS using nodes in the last two layers (Layer 1 and 2) wrt nodes of layer 3 of $5\times 100$ on image 59 of MNIST, presented in Table \ref{table14} and Fig.
+\ref{fig3}.
+% providing finer details than in Table 3, with the same setting, i.e. previous layer being computed with full MILP.
 
-\begin{table}[h!]
+\begin{table}[t!]
 		\centering
@@
 
-\begin{figure}[b!]
-	\hspace*{-0.8cm}
+\begin{figure}[h!]
+	\vspace*{-0.8cm}
 	\includegraphics[scale=0.6]{Layer3_comparison}.
@@
 %	\end{figure}
-
-\newpage
 
@@
 
-\begin{table}[b!]
+\begin{table}[h!]
 	\centering

### 2025-02-01 CAV 2025 TODO/proofsb.tex
appendux

@@
 
-First, we provide Fig.~\ref{fig5}, similar to 
+First, we provide in Fig.~\ref{fig55} the distance to verify Image 85 (which is an extremely hard image), comparing SAS with GS in runtime and not just in number of ReLUs to open.
+The {\em distance to verify} an image is specifically the lower bound of {\em one} output neuron (in the 4th layer of CNN-B-Adv), the furthest away from verification, (the local robustness objective asks the difference between the value of the output neuron corresponding to the correct class and the value of any other output neuron to be positive).
+Compared with Fig.~\ref{fig_table3}, we consider a unique neuron rather than an average over all the neuron of the 4th layer.
+This explains why the curve is much less smooth.
+This provides an idea of the runtime scaling with the number of ReLUs opened.
+
+\begin{figure}[b!]
+	\hspace*{-0.8cm}
+	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_min.png}
+	\caption{Distance to verify vs runtime: comparison between SAS and GS for different number of ReLUs open.}
+	\label{fig55}
+\end{figure}
+
+The difference of distance to verify between SAS and GS ISO number of ReLUs is very large.
+However, as the ReLUs opened by GS are not as important as the ReLUs opened by SAS, the runtime of GS ISO number of ReLUs is faster than for SAS.
+Still, the important metric here is runtime ISO accuracy (distance to verify), which is clearly favorable for SAS, close to 2x faster.
+Importantly, the accuracy gain by SAS is very predictable, with improvement with each open ReLUs, while it is much more erratic for GS.
+This helps setting a fixed number of ReLUs.
+Also, SAS reaches accuracy which would be hard to match by GS in number of ReLUs to open, needing an extremely high number of open ReLUs, and thus, a uncertain high runtime.
+
+Then, we provide Fig.~\ref{fig5}, similar to 
 Fig.~\ref{fig_table3} but on a different image, namely 37.
@@
 \begin{figure}[h!]
-	\hspace*{-0.8cm}
+	\hspace*{-1cm}
 	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image37}

### 2025-04-03 ATVA 2025/relatedwork.tex
Create folder

--- 2025-01-26 CAV 2025 TODO/relatedwork.tex
@@
 While the upper function is fixed, the lower function offers two choices.
-It relates to the LP encoding through the following new (to our knowledge) insight:  Proposition \ref{LP} \cite{alessandro} states that the LP relaxation precisely matches the intersection of these two choices.
+It relates to the LP encoding through Proposition \ref{LP} \cite{alessandro}: the LP relaxation precisely matches the intersection of these two choices.
 Consequently, LP is more accurate (but slower) than DeepPoly, and Hybrid MILP is considerably more precise.

### 2025-04-03 ATVA 2025/experiments.tex
update

--- 2025-01-31 CAV 2025 TODO/experiments.tex
@@
 \end{figure}
+
+\textcolor{red}{The number of open nodes we considered for the 5 F(ully)C(onnected)NNs depend neither on the image nor on the particular FCNN, only on the depth of the layer, because the runtime depends crucially on this factor.
+For FCNNs, we use a simple /2 rule between the number of open nodes of layer+1 vs layer (except last layer=14).
+For other architectures, we set the number of nodes to obtain similar runtime per layer, by testing a couple of neurons per layer, and use it for all images.}
 
@@
 The exact same DNNs, image set and $\epsilon$ are used in Tables \ref{table_beta} and \ref{table_hybrid}.
+
+\textcolor{red}{MNIST FCNN networks use the same open numbers sequence for all images, based on layer depth.
+CIFAR ConvolutionalNN uses another sequence (the same for all images) [AppendixA, Table6 p22].}
 

### 2025-04-08 ATVA 2025/proofsb.tex
update

--- 2025-02-01 CAV 2025 TODO/proofsb.tex
@@
 We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.
+
+\textcolor{red}{Direct MILP encodings are inefficient!
+Even the advanced Gurobi MILP solver struggle to sort out all neurons – see Fig11 page27: direct MILP encoding is $>10$ times slower on same instance ($>300s$ vs $<30s$ for similar accuracy) wrt considering only 8 open nodes selected with SAS (more open nodes lead to larger differences).
+Our main contribution is a way to select the most important nodes, and it helps Gurobi tremendously.
+This is the whole point of the paper!}
 

### 2025-04-08 ATVA 2025/Paper_noProof.tex
Create folder
update formate
update

--- 2025-01-31 CAV 2025 TODO/Paper_noProof.tex
@@
 \documentclass{llncs}
-
 \usepackage{hyperref}
@@
 \usepackage{wrapfig}
+\usepackage{lineno}
 \usepackage{amsmath}
@@
 	\maketitle
-
+	\linenumbers
 	\begin{abstract}
@@
 \section{Introduction}
+
+\textcolor{red}{HyperParameter selection [Reviewer1]:
+	The number of open nodes we considered for the 5 F(ully)C(onnected)NNs depend neither on the image nor on the particular FCNN, only on the depth of the layer, because the runtime depends crucially on this factor.
+For FCNNs, we use a simple /2 rule between the number of open nodes of layer+1 vs layer (except last layer=14).
+For other architectures, we set the number of nodes to obtain similar runtime per layer, by testing a couple of neurons per layer, and use it for all images.
+	In Table 4, are the same number of open nodes considered? [Reviewer3]
+	MNIST FCNN networks use the same open numbers sequence for all images, based on layer depth. CIFAR ConvolutionalNN uses another sequence (the same for all images) [AppendixA, Table6 p22].
+	Scaling [Reviewer1]:
+	Currently, for hard instances, there is no alternative  to pMILP (hundreds of seconds), other methods being $>>10$ times slower.	
+	Comprehensive experimental evaluation with all tools [Reviewer2]:
+	We did run and reported other tools as best as we could (see also appendixC (Table11...)).
+Reporting *some* experimental numbers from other papers (Figure5) is standard in the DNN verification community (eg [26]).}
 
@@
 \input{experiments}
+\input{Lipschitz}
 

### 2025-04-09 ATVA 2025/Comparison.tex
update

--- 2025-01-30 CAV 2025 TODO/Comparison.tex
@@
 \label{sec4p5}
+
+\textcolor{red}{Fig2 page10 is intended as a running example: We show how $s_{FSB}$ behaves on Fig2 (page10-11).
+Page12 (Fig4 and above), we explain how SAS computes the same case and compares with FSB.
+We will add explicit references to the case $c<0,d<0$ leading to $s_{FSB}=\frac{cd}{4}$, which corresponds in Figure4 to either case
+	(b) $\Delta(\hat{b})=\Delta(b)<\frac{c}{2}$ leading to $s_{SAS}=d\Delta(b)<\frac{cd}{2}$ or
+	(c) $\Delta(\hat{b})=0$ leading to $s_{SAS}=0$.}
 

### 2025-04-09 ATVA 2025/experiments.tex
update

@@
 There, GCP-CROWN is $2\%$ more accurate (with higher runtime) than $\alpha,\beta$-Crown with 90s TO, so we can deduce that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-Crown with 2000s TO, is significantly more accurate than GCP-CROWN.
+
+\textcolor{red}{Currently, for hard instances, there is no alternative  to pMILP (hundreds of seconds), other methods being $>>10$ times slower.}
+
+\textcolor{red}{We did run and reported other tools as best as we could (see also appendixC (Table11...)).
+Reporting *some* experimental numbers from other papers (Figure5) is standard in the DNN verification community (eg [26]).}
 

### 2025-04-14 ATVA 2025/Paper_noProof.tex
update
remove the section of Lipschitz
abstract

--- 2025-01-31 CAV 2025 TODO/Paper_noProof.tex
@@
 Such cases arise with verification-agnostic DNNs, non-local properties (e.g.
-global robustness, computing Lipschitz bound, compressed sensing), etc.
+global robustness, computing Lipschitz bound), etc.
 		%The fact that pure BaB is not that efficient for e.g.
@@
 The previous attempts were suboptimal in that respect.
-In this paper, we propose a novel {\em solution-aware} ReLU scoring (SAS), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU scoring (GS) functions.
-We compare them theoretically as well as experimentally.
-Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em branch} within this selection.
-Compared with previous attempts, SAS reduces the number of binary variables by around 6 times while maintaining the same level of accuracy.
+To select these important ReLU variables, we propose a novel {\em solution-aware} ReLU scoring (SAS), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU scoring (GS) functions.
+		We compare them theoretically as well as experimentally: SAS is more efficient to {\em select} a set of variables, while GS is more efficient at {\em ordering} this selection.
+		%Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em branch} within this selection.
+		Compared with previous attempts, SAS reduces the number of binary variables by around 6 times, while maintaining the same level of accuracy.
 Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CIFAR CNNs with 20 000 nodes.
@@
 \input{experiments}
+%\input{Lipschitz}
 

### 2025-04-15 ATVA 2025/Paper_noProof.tex
intro

@@
 		Compared with previous attempts, SAS reduces the number of binary variables by around 6 times, while maintaining the same level of accuracy.
-Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CIFAR CNNs with 20 000 nodes.
+Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CNNs with 20 000 nodes.
 

### 2025-04-15 ATVA 2025/introduction.tex
update
intro

--- 2025-01-31 CAV 2025 TODO/introduction.tex
@@
 	\centering
-	\begin{tabular}{||l|c|c||c|c|c||}
+	\begin{tabular}{||l|c|c|c||c|c|c||}
 		\hline
-		Network & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
-		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
-		MNIST 5$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
-		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
-		MNIST 5$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
-		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
-		MNIST 8$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
-		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
-		MNIST 8$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
-		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
-		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
-		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
-		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
-		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
-		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
+		Network & nbr & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+		Perturbation & activ &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+		MNIST 5$\times$100 & 500 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
+		$\epsilon = 0.026$ & ReLU & &  & 6.9s &  18.9s &  1026s  \\  \hline
+		MNIST 5$\times$200 & 1000 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
+		$\epsilon = 0.015$ & ReLU & &  & 6.5s &  16.6s &  930s  \\  \hline
+		MNIST 8$\times$100 & 800 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
+		$\epsilon = 0.026$ & ReLU &  &  & 7.2s &  20.1s &  930s  \\  \hline
+		MNIST 8$\times$200 & 1600 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
+		$\epsilon = 0.015$ & ReLU & &  & 6.8s &  18.2s &  1083s  \\  \hline
+		MNIST 6$\times$500 & 3000 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
+		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
+		CIFAR CNN-B-adv &  {\color{red} 2xxxx}  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
+		CIFAR ResNet &   {\color{red} 8xxxx}             & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+		$\epsilon = 2/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
 	\end{tabular}
@@
 Other complex instances include solving non-local properties, e.g.
-global robustness computed through Lipschitz bound \cite{lipshitz}, compressed sensing \cite{sensing}, etc.
+global robustness computed through Lipschitz bound \cite{lipshitz}, etc.
 The bottom line is that one cannot expect to have only easy instances to verify.
-It is important to notice that that number of activation functions of the DNN is a poor indicator of the hardness of the instance, e.g.
+It is important to notice that the number of activation functions of the DNN is a poor indicator of the hardness of the instance, e.g.
 $5 \times 100$ with 500 ReLUs is far more complex to certify ($50\%$ undecided images) than 100 times bigger ResNet ($0\%$ undecided images), see Table \ref{table_beta}.
@@
 
-	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global scoring (GS) functions to choose ReLU for pMILP. 
+	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, {\em global scoring ({\sf GS})} functions to choose ReLU for pMILP. 
 	These revealed to be much more accurate than the simple heuristic in 
 	\cite{DivideAndSlide}.
-We uncover however one case (out of 4) where the exact function that GS tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode.
-This implies that these strategies may not be that accurate, because they do not know the mode to choose from.
-We then designed a novel solution-aware scoring (SAS), which uses the solution of a unique LP call, that provides the mode to consider.
-Theoretically, we show that SAS is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAS value implies that the ReLU is unnecessary.
-Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.
-Compared with the heuristic in \cite{DivideAndSlide},  SAS is much more efficient ($\approx 6$ times less binary variables for same accuracy (Plot \ref{fig_table3})).
+We uncover however that the {\em improvement function} that GS tries to approximate depends heavily upon the mode of the ReLU function, and as this mode is unavailable to GS, there are many cases in which {\sf GS} is far from the improvement (with both under or over-approximation cases).
+
+	\item We thus designed a {\em novel solution-aware scoring ({\sf SAS})}, which uses the solution of a unique LP call, that provides the mode to consider.
+Theoretically, we show that {\sf SAS} is always an over-approximation of the improvement (Proposition \ref{prop2}), which implies that a small {\sf SAS} value implies that the ReLU is unnecessary.
+Experimentally, we further show that {\sf SAS} is very close to the actual improvement, closer than {\sf GS}, and that overall, the accuracy from SAS is significantly better than {\sf GS}.
+Compared with the heuristic in \cite{DivideAndSlide},  {\sf SAS} is much more efficient ($\approx 6$ times less binary variables for same accuracy (Fig.
+\ref{fig_table3})).
 We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
+
+	\item Compared with many calls using full MILP (all the ReLUs encoded as binary variables), which is {\em asymptotically } more accurate than {\sf SAS, GS} encoding a subset of ReLUs as binary and others as linear variables (the model in full MILP is fully accurate, while {\sf SAS} and {\sf GS} are abstractions), in practice, every reasonable time-out leads to better practical accuracy of {\sf SAS, GS}.
 

### 2025-04-16 ATVA 2025/Paper_noProof.tex
intro

@@
 	\begin{abstract}
-		Branch and Bound (BaB) is considered as the most efficient technique for DNN verification: it can propagate bounds over numerous branches, to accurately under- and over-approximate values a given neuron can take even in large DNNs, enabling formal verification of properties such as local robustness.
+		Branch and Bound (BaB) is considered as the most efficient technique for DNN verification: it can propagate bounds over numerous branches, 
+		to accurately approximate values a given neuron can take even in large DNNs, enabling formal verification of properties such as local robustness.
 Nevertheless, the number of branches grows {\em exponentially} with important variables, and there are complex instances for which the number of branches is too large to handle even using BaB.

### 2025-04-16 ATVA 2025/introduction.tex
intro

@@
 		Network & nbr & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
-		Perturbation & activ &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
+		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
 		MNIST 5$\times$100 & 500 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
@@
 	\item We revisit the idea from \cite{DivideAndSlide} to consider small calls to a partial MILP (pMILP) solver, i.e.
-with few binary variables encoding few ReLU functions exactly, to compute bounds for each neuron inductively, hence many ($O(n)$, the number of neuron) small calls, with a complexity exponential only in the few binary variables.
+with few binary variables encoding few ReLU functions exactly (other being encoded with more efficient but less accurate linear variables), to compute bounds for each neuron inductively, hence many ($O(n)$, the number of neuron) small calls, with a complexity exponential only in the few binary variables (Section 4).
 Compared to the few (one per output neuron) complex call to BaB, each with a worst case complexity exponential in the number of neurons of the DNN (which is far from the actual complexity thanks to pruning branches in BaB - but which can be too large as we shown in the 6 first DNNs of Table \ref{table_beta}).
@@
 
-	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, {\em global scoring ({\sf GS})} functions to choose ReLU for pMILP. 
+	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, {\em global scoring ({\sf GS})} functions to choose important ReLUs (Section 5).
 These revealed to be much more accurate than the simple heuristic in
 	\cite{DivideAndSlide}.
-We uncover however that the {\em improvement function} that GS tries to approximate depends heavily upon the mode of the ReLU function, and as this mode is unavailable to GS, there are many cases in which {\sf GS} is far from the improvement (with both under or over-approximation cases).
+However, we also uncover that the {\em improvement function} that {\sf GS} tries to approximate depends heavily upon the mode of the ReLU function, and as this mode is unavailable to {\sf GS}, there are many cases in which {\sf GS} is far from the improvement (with both under or over-approximation of the improvement function).
 
-	\item We thus designed a {\em novel solution-aware scoring ({\sf SAS})}, which uses the solution of a unique LP call, that provides the mode to consider.
+	\item We thus designed a {\em novel solution-aware scoring ({\sf SAS})}, which uses the solution of a unique LP call, that provides the mode to consider (Section 6).
 Theoretically, we show that {\sf SAS} is always an over-approximation of the improvement (Proposition \ref{prop2}), which implies that a small {\sf SAS} value implies that the ReLU is unnecessary.
@@
 Compared with the heuristic in \cite{DivideAndSlide},  {\sf SAS} is much more efficient ($\approx 6$ times less binary variables for same accuracy (Fig.
-\ref{fig_table3})).
-We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
+\ref{fig_table3}).
+We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally ({\color{red}see Fig.
+\ref{fig_branch}}).
 
-	\item Compared with many calls using full MILP (all the ReLUs encoded as binary variables), which is {\em asymptotically } more accurate than {\sf SAS, GS} encoding a subset of ReLUs as binary and others as linear variables (the model in full MILP is fully accurate, while {\sf SAS} and {\sf GS} are abstractions), in practice, every reasonable time-out leads to better practical accuracy of {\sf SAS, GS}.
+	\item Compared with many calls using full MILP, where all the ReLUs are encoded as binary variables, {\sf SAS} (and {\sf GS}) encode only a subset of ReLUs as binary and others as linear variables.
+The model in full MILP is fully accurate, while {\sf SAS} (and {\sf GS})
+	are abstractions, and thus much faster to solve. 
+	While full MILP is thus {\em asymptotically} more accurate than {\sf SAS} and {\sf GS}, {\em experimentally}, every reasonable time-out leads to much better practical accuracy of {\sf SAS} (and {\sf GS}) ({\color{red}see Fig.
+\ref{fig_timeout}}).
 
@@
 
-Limitation: We consider DNNs employing the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}.
+Limitation: We consider DNNs employing the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}, with updated MILP models e.g.
+for {\color{red} softmax}.
 

### 2025-04-16 ATVA 2025/introduction.tex
update

@@
 		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
-		CIFAR CNN-B-adv &  {\color{red} 2xxxx}  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		CIFAR CNN-B-adv &  {\color{red} 16634}  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
 		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline

### 2025-04-16 ATVA 2025/introduction.tex
update table

@@
 		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
-		CIFAR ResNet &   {\color{red} 8xxxx}             & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-		$\epsilon = 2/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
+		CIFAR ResNet &   {\color{red}  107496}             & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+		$\epsilon = 8/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
 	\end{tabular}

### 2025-04-16 ATVA 2025/introduction.tex
update

@@
 \ref{fig_table3}).
-We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally ({\color{red}see Fig.
-\ref{fig_branch}}).
+We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally ({\color{red}see Table.
+\ref{table.order}}).
 

### 2025-04-17 ATVA 2025/proofsb.tex
update

@@
 	\hspace*{-0.8cm}
-	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_min.png}
-	\caption{Distance to verify vs runtime: comparison between SAS and GS for different number of ReLUs open.}
+	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
+	\caption{Distance to verify vs runtime: comparison between SAS, GS, full MILP and Huang's method for different number of ReLUs open.}
 	\label{fig55}

### 2025-04-17 ATVA 2025/valabstraction.tex
intro
varbastrat

--- 2025-01-29 CAV 2025 TODO/valabstraction.tex
@@
 
-\subsection{MILP, and LP encodings for DNNs}
+\subsection{MILP and LP encodings for DNNs}
 
@@
 This results in an upper bound $\hat{x} \leq \UB(n) \frac{x - \LB(n)}{\UB(n)-\LB(n)}$, which can be reached, hence the equivalence.
+\qed
 \end{proof}
@@
 
-In this paper, we revisit the use of {\em partial MILP} (see \cite{DivideAndSlide}), to get interesting trade-offs between accuracy and runtime: 
-for a set of unstable neurons $X$, we denote by MILP$_X$ the MILP encoding where variables encoding $X$ are binary, and other variables are linear variables using the LP relaxation.
+{\color{red}
+In this paper, we revisit the use of {\em partial MILP} (pMILP for short, see \cite{DivideAndSlide}), to get interesting trade-offs between accuracy and runtime.
+Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: pMILP$_X(n)$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding (equation (2) Section 3.2), where variable $a$ is
+\begin{itemize}
+\item binary for neurons in $X$ (exact encoding of the ReLU),
+\item linear for neurons not in $X$ (linear relaxation).
+\end{itemize}
+
+Formally, we denote by MILP$_X$ the MILP encoding where the variable $a$ encoding $\ReLU(y)$ is binary for $y\in X$, and linear for $y\notin X$, whether $y$ is unstable or stable. 
 We say that nodes in $X$ are {\em opened}. 
-To further limit the number of binary variables needed for a given accuracy, we devise the same iterative approach as the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a layer, that are used when computing values of the next layer, thus necessitating less variables from previous layers.
+That is, if $X$ is a strict subset of the set of all unstable neurons, then 
+MILP$_X$ is an abstraction of the constraints in the full MILP model.
+If $X$ covers all unstable neurons, then MILP$_X$ is exact as there is only one linear mode for stable variables.
+The worst-case complexity to solve MILP$_X$ is NP-complete in $|X|$, ie the number of binary variables.
+
+\smallskip
+
+To reduce the runtime, we will limit the size of subset $X$.
+This a priori hurts accuracy.
+To recover some of this accuracy, we do a trade-off in Algorithm \ref{algo1} pMILP$_K$, using an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
+So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.
+}
+
+\medskip
 
@@
 
-\begin{algorithm}[h!]
-	\caption{pMILP($K$)}
+\begin{algorithm}[t!]
+	\caption{pMILP$_K$}
 	\label{algo1}
-	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$ (input neighbourhood)}
+	\KwInput{Bounds $[\LB(m),\UB(m)]$ for nodes $m$ at layer $0$}
 
-	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}
+	\KwOutput{Bounds $[\LB(n),\UB(n)]$ for every node $n$}
 
-	\For{layer $k=1 \cdots \ell$}{
+	\For{layer $k=1, \ldots, \ell$}{
 		\For{neuron $n$ in layer $k$}{
 
-			Compute $X$ a set of $K$ nodes with the highest Utility for target neuron $n$.
+			Compute $X$ a set of $K$ nodes most important for target neuron $n$.
 
-			Run MILP$_X$ to obtain $[\alpha_n,\beta_n]$ from bounds of neurons in layers $< k$
+			Run pMILP$_X(n)$ to obtain $[\LB(n),\UB(n)]$ using $\MILP_X$ and additional constraints $\bigvee_{m \text{ in layer } <k} \val(m) \in [\LB(m),\UB(m)]$.
 		}
@@
 
-We provide the pseudo code for pMILP in Algorithm \ref{algo1}.
-pMILP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
+We provide the pseudo code for pMILP$_K$ in Algorithm \ref{algo1}.
+pMILP$_K$ has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
 where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.

### 2025-04-17 ATVA 2025/valabstraction.tex
pmilp

@@
 
-Formally, we denote by MILP$_X$ the MILP encoding where the variable $a$ encoding $\ReLU(y)$ is binary for $y\in X$, and linear for $y\notin X$, whether $y$ is unstable or stable. 
+Formally, we denote by MILP$_X$ the MILP encoding where the variable $a$ encoding $\ReLU(y)$ is binary for $y\in X$, and linear for $y\notin X$ ($y$ being unstable or stable). 
 We say that nodes in $X$ are {\em opened}. 
@@
 This a priori hurts accuracy.
-To recover some of this accuracy, we do a trade-off in Algorithm \ref{algo1} pMILP$_K$, using an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
+To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
 So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.

### 2025-04-17 ATVA 2025/Comparison.tex
comparison

--- 2025-01-30 CAV 2025 TODO/Comparison.tex
@@
 
-First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions, %(replacing the symbols from the original paper with those used in our paper.)
- selecting a node to branch on for BaB, {\em  global scoring} (GS) functions to select nodes for pMILP.
-Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP.
+%\textcolor{red}{Fig2 page10 is intended as a running example: We show how $s_{FSB}$ behaves on Fig2 (page10-11).
+Page12 (Fig4 and above), we explain how SAS computes the same case and compares with FSB.
+We will add explicit references to the case $c<0,d<0$ leading to $s_{FSB}=\frac{cd}{4}$, which corresponds in Figure4 to either case
+%	(b) $\Delta(\hat{b})=\Delta(b)<\frac{c}{2}$ leading to $s_{SAS}=d\Delta(b)<\frac{cd}{2}$ or
+%	(c) $\Delta(\hat{b})=0$ leading to $s_{SAS}=0$.}
+
+To select nodes $X$ for pMILP$_X$, we first adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions, %(replacing the symbols from the original paper with those used in our paper.)
+ which originally iteratively select one node to branch on for BaB.
+ Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the 
+ BaB bounding step is not adapted for pMILP. 
+ We will call such functions {\em  global scoring} (GS) functions.
+
  They both work by backpropagating gradients vectors $\bm{\lambda}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected.
@@
 
-Then, the scoring functions $\bm{s}_{SR}$ and $\bm{s}_{FSB}$ for ReLUs in layer $k$ are computed by approximating how each node would impact the neurons in layer $n$, by also factoring in the bias $\bm{b}_k$ in different ways:
+Then, the scoring functions $\bm{s}_{SR}$ and $\bm{s}_{FSB}$ for ReLUs in layer $k$ are computed by approximating how each node would impact the neurons in layer $n$, using the computed $\bm{\lambda}$, differeing only in how they handle the bias $\bm{b}_k$:
 
-\begin{figure}[t!]
+\begin{align*}
+	\bm{s}_{SR}(k) =& %\bm{1}_{\bm{u}_k>0,\bm{l}_k<0} \odot
+	\Biggl\lvert r(\bm{u}_k) \odot \LB(\bm{u}_k) \odot \max(\bm{\lambda}_{k},0)
+	+ \max\{0,\bm{\lambda}_{k}\odot\bm{b}_{k}\}-r(\bm{u}_k) \odot\bm{\lambda}_{k}\odot\bm{{b}}_{k}
+	\Biggr\rvert  \\
+	\bm{s}_{FSB}(k) =& \Biggl\lvert r(\bm{u}_k) \odot \LB(\bm{u}_k) \odot \max(\bm{\lambda}_{k},0)
+	+ \min\{0,\bm{\lambda}_{k}\odot\bm{b}_{k}\}-r(\bm{u}_k) \odot\bm{\lambda}_{k}\odot\bm{{b}}_{k}
+	\Biggr\rvert
+\end{align*}
+
+\begin{figure}[b!]
 	\centering
@@
 	\vspace{-0.8cm}
-	\caption{A simple example with parametric weights {\color{red}$c$} and {\color{red}$d$}}
+	\caption{A running example with parametric weights {\color{red}$c$} and {\color{red}$d$}}
 	\label{img:FSB_example}
@@
 
-\begin{figure}[b!]
+	%In case where the bias is 0, then there is no difference between $s_{SR}$ and $s_{FSB}$.
+	Then, ReLU are ranked using these scores, to select the most important unstable ReLUs
+	(with $\LB(u_k) < 0 < \UB(u_k)$).
+	% as stable ReLUs are linear, thus they are already treated correctly.
+
+\noindent {\em Running Example:} Consider Fig. \ref{img:FSB_example}. 
+It has no bias, so $s_{SR}=s_{FSB}$.
+We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
+Consider the real improvement on the {\em maximal bound} computed by pMILP$_X(z)$ when opening the $\ReLU$ of node $a$ ($X=\{a\}$) compared with $X=\emptyset$, and compare with 
+$s_{FSB}(a)$. Let us do a case analysis:
+
+The most favorable cases are $c < 0 < d$ and $d < 0 < c$: 
+as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
+Because $cd <0$, both $a$ and $\hat{a}$ need to be minimized by pMILP in order to maximize the value of $z$.
+The LP approximation ($X=\emptyset$) matches the triangle approximation represented in Fig.
+\ref{triangle}: having a value $sol(a)$ for $a$, the minimal value for $\hat{a}$ is $\ReLU(sol(a))$.
+If we open $a$ ($X=\{a\}$), then the value for $\hat{a}$ will also be $\ReLU(sol(a))$.
+That is, opening this ReLU is not helping in computing $\UB(z)$, as correctly predicted by the score $s_{FSB}(a)= 0$.
+
+\begin{figure}[t!]
 	\begin{centering}
@@
 	\end{figure}
-
-	\begin{align*}
-		\bm{s}_{SR}(k) =& %\bm{1}_{\bm{u}_k>0,\bm{l}_k<0} \odot
-		\Biggl\lvert r(\bm{u}_k) \odot \LB(\bm{u}_k) \odot \max(\bm{\lambda}_{k},0)
-		+ \max\{0,\bm{\lambda}_{k}\odot\bm{b}_{k}\}-r(\bm{u}_k) \odot\bm{\lambda}_{k}\odot\bm{{b}}_{k}
-		\Biggr\rvert  \\
-		\bm{s}_{FSB}(k) =& \Biggl\lvert r(\bm{u}_k) \odot \LB(\bm{u}_k) \odot \max(\bm{\lambda}_{k},0)
-		+ \min\{0,\bm{\lambda}_{k}\odot\bm{b}_{k}\}-r(\bm{u}_k) \odot\bm{\lambda}_{k}\odot\bm{{b}}_{k}
-		\Biggr\rvert
-	\end{align*}
-
-	In case where the bias is 0, then there is no difference between $s_{SR}$ and $s_{FSB}$.
-	Then, unstable ReLU (with $\LB(u_k) < 0 < \UB(u_k)$) are ranked using these scores, to select the most important ReLUs, as stable ReLUs are linear, thus they are already treated correctly.
-
-Consider the example in Fig. \ref{img:FSB_example}. It has no bias so $s_{SR}=s_{FSB}$.
-We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
-Let us do a case analysis:
-The most favorable cases are $c < 0 < d$ and $d < 0 < c$: 
-as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
-Now, $a$ and $\hat{a}$ need to be minimized in order to maximize $z$, because $cd <0$. 
-For the triangle approximation (see Fig.
-\ref{triangle}), having a value $sol(a)$ for $a$, the minimal value for $\hat{a}$ is $\ReLU(sol(a))$.
-If we open $a$, then the value for $\hat{a}$ will also be $\ReLU(sol(a))$.
-That is, opening this ReLU is not helping in the approximation of $z$, as correctly predicted by the score $s_{FSB}(a)= 0$.
 

### 2025-04-19 ATVA 2025/Comparison.tex
comparison

@@
 
+	{\color{red}
 \noindent {\em Running Example:} Consider Fig. \ref{img:FSB_example}. 
-It has no bias, so $s_{SR}=s_{FSB}$.
-We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
-Consider the real improvement on the {\em maximal bound} computed by pMILP$_X(z)$ when opening the $\ReLU$ of node $a$ ($X=\{a\}$) compared with $X=\emptyset$, and compare with 
-$s_{FSB}(a)$. Let us do a case analysis:
+It has no bias, so $s_{SR}=s_{FSB}$. We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
+The value of $s_{FSB}(a)$ depends on the signs of $c,d$.
+
+Compare $s_{FSB}(a)$ with $imp(a)$, the real improvement on the {\em maximal bound} computed by pMILP$_X(z)$ when opening the $\ReLU$ of node $a$ ($X=\{a\}$), yielding 
+$\val(\hat{a}) = \ReLU(\val(a))$, versus having $X=\emptyset$, for which 
+$\val(\hat{a})$ can be any value in the triangle approximation (Figure \ref{triangle})), 
+according to Prop. \ref{lp}.
 
@@
 as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
-Because $cd <0$, both $a$ and $\hat{a}$ need to be minimized by pMILP in order to maximize the value of $z$.
-The LP approximation ($X=\emptyset$) matches the triangle approximation represented in Fig.
-\ref{triangle}: having a value $sol(a)$ for $a$, the minimal value for $\hat{a}$ is $\ReLU(sol(a))$.
-If we open $a$ ($X=\{a\}$), then the value for $\hat{a}$ will also be $\ReLU(sol(a))$.
-That is, opening this ReLU is not helping in computing $\UB(z)$, as correctly predicted by the score $s_{FSB}(a)= 0$.
+Because $cd <0$, both $a$ and $\hat{a}$ need to be minimized by MILP$_X$ in order to maximize the value of $z$. For $X=\emptyset$, the LP approximation (=MILP$_\emptyset$) will thus 
+set $\val(\hat{a}) = \ReLU(\val(a))$ as this is the minimum value in the triangle approximation. Notice that opening $X=\{a\}$ yields the same $\val(\hat{a}) = \ReLU(\val(a))$.
+That is, opening node $a$ is not improving the bound $\UB(z)$, as correctly predicted by the score $s_{FSB}(a)= imp(a) = 0$.
 
@@
 	\end{tikzpicture}
-		\caption{Triangle approximation
+		\caption{Triangle approximation with $r(a)=\frac{1}{2}$
 		\vspace{-0.3cm}}
@@
 
-Case $c>0,d>0$: $s_{FSB}(a)=\frac{cd}{4}$.
+Case $c>0,d>0$: we have $s_{FSB}(a)=\frac{cd}{4}$.
 The value of $a,\hat{a},b,\hat{b}$ should be maximized to maximize the value of $z$, because $W_{bz}=d>0$ and $W_{ab}=c>0$. 
 %Each variation of $b$ by $\Delta(b)$ will have an impact $r(b) \cdot \Delta(b)=\frac{\Delta(b)}{2}$ on the value of $\hat{b}$, and thus $\frac{d \Delta(b)}{2}$ on $z$. 
-Now, let us call $sol(a)$ the maximum value for $a$.
-The maximum value for $\hat{a}$ is $r(a)\cdot (sol(a)-LB(a))$ according to the triangle approximation when $\ReLU(a)$ is not opened. Now, if $\ReLU(a)$ is opened, then 
-the value of $\hat{a}$ is $\ReLU(sol(a))$: the difference is at most $r(a) \cdot LB(a) = \frac{1}{2}$.
-The difference $\Delta(b)$ for the value of $b$ is thus at most $\frac{c}{2}$, which means a difference at most $\frac{c}{4}$ for $\hat{b}$, using the upper function of the triangle approximation of rate $r(b)$, as the value of $\hat{b}$ should be maximized.
-This means a difference of at most $\frac{cd}{4}$ on the value of $z$, which is what is computed by $s_{FSB}(a)$.
-Of course, the difference of opening $\ReLU(a)$ could also be 0 e.g.
-if $\sol(a)=\LB(a)$ or $\sol(a)=\UB(a)$.
+Now, let us call $val(a)$ the maximum value for $a$ 
+(same for MILP$_\emptyset$ and MILP$_{\{a\}}$).
+The maximum value for $\hat{a}$ under LP ($X=\emptyset$) is 
+$\frac{1}{2} \cdot (\val(a)-LB(a))$ following the triangle approximation. 
+Now, if $X=\{a\}$, then the value of $\hat{a}$ is $\ReLU(\val(a))$: the difference is 
+between 0 (for $\val(a)\in \{LB,UB\}$) and $\frac{1}{2}$ (for $\val(a)=0$). 
+The difference $\Delta(b)$ for the value of $b$ is thus between 0 and $\frac{c}{2}$, which means a difference at most $\frac{c}{4}$ for $\hat{b}$, using the upper function of the triangle approximation of rate $r(b)$, as the value of $\hat{b}$ should be maximized.
+This means a difference $imp(a) \in [0, \frac{cd}{4}]$ on the value of $z$ (depending on the maximal value $val(a)$), to compare with the fixed $s_{FSB}(a)=\frac{cd}{4}$.
 
@@
 Case $c<0,d<0$, implying that $s_{FSB}(a)=\frac{cd}{4}$, because $cd >0$.
-As for the case of $c>0, d>0$, opening $\ReLU(a)$ will have an impact on the value of $\hat{a}$,
-at most $\frac{1}{2}$, and hence a change $\Delta(b)$ of at most $\frac{c}{2}$ on the value of $b$.
-However, as $d<0$, value of $\hat{b}$ needs to be minimized.
-That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$, and the change in $\hat{b}$ will be either 0 in case $sol(b)<0$ (phase 0 of ReLU),
-or $\Delta(b)<\frac{c}{2}$ otherwise (phase Id of ReLU), that is, $z$ will be modified by 
-either 0 or $d \Delta(b)<\frac{cd}{2}$, as compared with $s_{FSB}(a)=\frac{cd}{4}$.
+Opening $\ReLU(a)$ will have the same impact on the value of $\hat{a}$ then $b$
+than in case $c>0,d>0$, with difference of $\val(b)$ between $[0,\frac{c}{2}]$.
+However, as $d<0$, value of $\hat{b}$ needs to be minimized to maximize the value of $z$.
+That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$, and the change in $\hat{b}$ will be either 0 in case $\val(b)<0$,
+or $\Delta(b) \in [0,\frac{c}{2}]$ for $\val(b)>0$.
+That is, $z$ will be modified by either $imp(a)=0$ or $imp(a) = d \Delta(b)$, to be compared with the fix value $s_{FSB}(a)=\frac{cd}{4}$, which is not always an overapproximation, it is possible that $imp(a)=\frac{cd}{2} > s_{FSB}(a)$, for $val(a)=0$ and $val(b)>0$.
 
-We call {\em global scoring} (GS) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution values $sol(a),sol(b)$.
-This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.
+We call {\em global scoring} (GS) these functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the values 
+$\val(a),\val(b)$ maximizing $z$. Following this novel analysis of $s_{FSB},s_{SR}$, next Section presents a novel scoring function more accurate wrt $imp(a)$.
+
+	}
 

### 2025-04-21 ATVA 2025/Comparison.tex
compar

@@
 
-Compare $s_{FSB}(a)$ with $imp(a)$, the real improvement on the {\em maximal bound} computed by pMILP$_X(z)$ when opening the $\ReLU$ of node $a$ ($X=\{a\}$), yielding 
-$\val(\hat{a}) = \ReLU(\val(a))$, versus having $X=\emptyset$, for which 
-$\val(\hat{a})$ can be any value in the triangle approximation (Figure \ref{triangle})), 
-according to Prop. \ref{lp}.
+We perform a novel comparison between $s_{FSB}(a)$ and $\Delta(z)$, the difference on the {\em maximal bound} computed by pMILP$_X(z)$ when opening the $\ReLU$ of node $a$ ($X=\{a\}$), yielding $\val(\hat{a}) = \ReLU(\val(a))$, versus having $X=\emptyset$, for which
+$\val(\hat{a})$ can be any value in the triangle approximation (Prop. \ref{LP}, Fig. \ref{triangle})).
 
@@
 set $\val(\hat{a}) = \ReLU(\val(a))$ as this is the minimum value in the triangle approximation. Notice that opening $X=\{a\}$ yields the same $\val(\hat{a}) = \ReLU(\val(a))$.
-That is, opening node $a$ is not improving the bound $\UB(z)$, as correctly predicted by the score $s_{FSB}(a)= imp(a) = 0$.
+That is, opening node $a$ is not improving the bound $\UB(z)$, as correctly predicted by the score $s_{FSB}(a)= \Delta(a) = 0$.
 
@@
 $\frac{1}{2} \cdot (\val(a)-LB(a))$ following the triangle approximation. 
-Now, if $X=\{a\}$, then the value of $\hat{a}$ is $\ReLU(\val(a))$: the difference is 
-between 0 (for $\val(a)\in \{LB,UB\}$) and $\frac{1}{2}$ (for $\val(a)=0$). 
-The difference $\Delta(b)$ for the value of $b$ is thus between 0 and $\frac{c}{2}$, which means a difference at most $\frac{c}{4}$ for $\hat{b}$, using the upper function of the triangle approximation of rate $r(b)$, as the value of $\hat{b}$ should be maximized.
-This means a difference $imp(a) \in [0, \frac{cd}{4}]$ on the value of $z$ (depending on the maximal value $val(a)$), to compare with the fixed $s_{FSB}(a)=\frac{cd}{4}$.
+Now, if $X=\{a\}$, then the value of $\hat{a}$ is $\ReLU(\val(a))$: the difference 
+$\Delta(\hat{a})$ is between 0 (for $\val(a)\in \{LB,UB\}$) and $\frac{1}{2}$ (for $\val(a)=0$).
+The difference $\Delta(b)$ for the value of $b$ is thus between 0 and $\frac{c}{2}$, which means $\Delta(\hat{b}) \in [0, \frac{c}{4}]$, using the upper function of the triangle approximation of rate $r(b)=\frac{1}{2}$, as the value of $\hat{b}$ should be maximized.
+This means a difference $\Delta(z) \in [0, \frac{cd}{4}]$ 
+(depending on the maximal value $val(a)$), to compare with the fixed 
+$s_{FSB}(a)=\frac{cd}{4}$.
 
@@
 Case $c<0,d<0$, implying that $s_{FSB}(a)=\frac{cd}{4}$, because $cd >0$.
-Opening $\ReLU(a)$ will have the same impact on the value of $\hat{a}$ then $b$
-than in case $c>0,d>0$, with difference of $\val(b)$ between $[0,\frac{c}{2}]$.
-However, as $d<0$, value of $\hat{b}$ needs to be minimized to maximize the value of $z$.
-That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$, and the change in $\hat{b}$ will be either 0 in case $\val(b)<0$,
+Opening $\ReLU(a)$ will have the same impact on the value of $\hat{a},b$ 
+than in case $c>0,d>0$, with $\Delta(b) \in [0,\frac{c}{2}]$.
+However, as $d<0$, value of $\hat{b}$ needs to be minimized to maximize the value of $z$. That is, the value of $\hat{b}$ will be the value of $\ReLU(sol(b))$, and the change 
+$\Delta(\hat{b})$ will be either 0 in case $\val(b)<0$,
 or $\Delta(b) \in [0,\frac{c}{2}]$ for $\val(b)>0$.
-That is, $z$ will be modified by either $imp(a)=0$ or $imp(a) = d \Delta(b)$, to be compared with the fix value $s_{FSB}(a)=\frac{cd}{4}$, which is not always an overapproximation, it is possible that $imp(a)=\frac{cd}{2} > s_{FSB}(a)$, for $val(a)=0$ and $val(b)>0$.
+That is, $z$ will be modified by either $\Delta(z)=0$ or $\Delta(z) = d \Delta(b)$, to be compared with the fix value $s_{FSB}(a)=\frac{cd}{4}$, which is not always an overapproximation: we have $\Delta(z)=\frac{cd}{2} > s_{FSB}(a)$,
+if $\val(a)=0$ and $\val(b)>0$.
 
 We call {\em global scoring} (GS) these functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the values 
-$\val(a),\val(b)$ maximizing $z$. Following this novel analysis of $s_{FSB},s_{SR}$, next Section presents a novel scoring function more accurate wrt $imp(a)$.
+$\val(a),\val(b)$ maximizing $z$. Following this analysis of $s_{FSB},s_{SR}$, 
+next Section presents a novel scoring function more accurate wrt $\Delta(z)$.
 

### 2025-04-21 ATVA 2025/formula.tex
update
compar

--- 2025-01-30 CAV 2025 TODO/formula.tex
@@
 
-In this section, we propose a novel {\em Solution-Aware Scoring} (SAS),
+In this section, we propose {\em Solution-Aware Scoring} (SAS),
 to evaluate accurately how opening a ReLU impacts the accuracy.
-To do so, SAS considers explicitly the {\em difference} $\Delta(z)$ on the value of target node $z$ from opening $\ReLU(a)$, that is the difference for the value of $z$ between considering $\ReLU(a)$ exactly or using its LP relaxation $\LP(a)$, using the solution to a unique full LP call, which is resonnably fast to obtain.
-To compute $\Delta(z)$, intermediate $\Delta(b),\Delta(\hat{b})$ are computed inductively.
+To do so, SAS considers explicitly a solution to a unique LP call, which is reasonably fast to obtain as there is no binary variables (polynomial time). 
+%To compute $\Delta(z)$, intermediate $\Delta(b),\Delta(\hat{b})$ are computed inductively.
 %Indeed, it is not rare that $z$ is sensitive to ReLU node $n$, and yet $\LP(n)$ already provides an accurate approximation of $\ReLU(n)$.
@@
 $\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{n\}}^z(z) \leq \sol(z)$.
-Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
-$\Improve\_\min^z(n)$. 
-Calling MILP on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$
-would however be very time consuming when the number of neurons $a$ to evaluate is large.
-Instead, the SAS function uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Fig.
-\ref{fig_table3}).
+%Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
+%$\Improve\_\min^z(n)$. 
+Computing exactly $\Improve\_\max^z(n)$ would need a MILP call on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$, which would be very time consuming.
+Instead, the SAS function uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$
+(Fig. \ref{fig_table3}).
 
@@
 
-For a neuron $b$ on the layer before the layer $\ell_z$, we define:
+For a neuron $b$ on the layer before layer $\ell_z$, we define:
 
@@
 
-Consider $b$ with $W_{bz}<0$: to maximize $z$, the value of $\sol(\hat{b})$ is minimized, 
-which is $\sol(\hat{b})=\ReLU(\sol(b))$ thanks to Proposition~\ref{LP}. 
-Even if $z$ is sensitive to this ReLU $b$, the improvement of $b$ is 0.
-Utility does not open it as $\Utility\_\max^z(b)=0$, whereas usual heuristics would.
+\noindent {\em Comparison:} consider $b$ with $W_{bz}<0$: 
+to maximize $z$, the value of $\sol(\hat{b})$ is minimized by LP, 
+ie $\sol(\hat{b})=\ReLU(\sol(b))$ thanks to Proposition~\ref{LP}. 
+Thus, we have $\Utility\_\max^z(b)=0=\Improve_{max}^z(b)$.
+Notice that the original scoring function $|W_{bz}|(\UB(b)-\LB(b))$ \cite{DivideAndSlide}  would be possibly very large in this case.
+However, {\sf GS} scoring functions from BaB-SR and FSB would also accurately compute  $s_{FSB}(b)=s_{SR}=0$.
+Notice that $\Utility$ does not need to consider bias explicitly, unlike $s_{FSB},s_{SR}$,
+as they are already accounted for in the solution considered.
 
+\medskip
+
+Consider a neuron $a$ two layers before $\ell_z$, 
+$b$ denoting neurons in the layer $\ell$ just before $\ell_z$.
 Recall the rate $r(b)=\frac{\max(0,\UB(b))}{\max(0,\UB(b))-\min(0,\LB(b))} \in [0,1]$.
-For a neuron $a$ two layers before $\ell_z$, 
-$b$ denoting neurons in the layer $\ell$ just before $\ell_z$, 
-we define:
-\vspace{-0.4cm}
+We define:
 
@@
 \end{subnumcases}
-\vspace{-0.4cm}
+
 \begin{flalign*}
-	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})&&
+	\Utility\_\max\nolimits^z(a) &= \Delta(z) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})&&
 \end{flalign*}
@@
 
-Notice that $\Utility$ does not need to consider bias explicitly, unlike $s_{FSB},s_{SR}$,
-as they are already accounted for in the solution considered. 
-There are two main differences with $s_{FSB}$: 
-First, $\Delta(\hat{a})$ is defined exactly, with $\ReLU(\sol(a))-\sol(\hat{a})$,
-whereas the corresponding $\Delta_{FSB}(\hat{a})$ is approximated as $\LB(a) r(a)$, 
-which is only an upper bound. %of $\ReLU(\sol(a))-\sol(\hat{a})$.
-More importantly, the corresponding $\Delta_{FSB}(\hat{b})$ is always $r(b) \Delta(b)$, whereas SAS adapts to the 3 cases (see Fig.
-\ref{node:b}), correctly considering the 0 phase of $ReLU(b)$ when $\sol(b)\geq 0$, and the ID phase when $\sol(b)<0$.
-Assuming that the solution to maximize $z$ does not change when opening $\ReLU(a)$
-on neurons independent of $a$, then $\Utility$ is exact.
-This is not the case for $s_{FSB}$ because of the two previously mentioned cases.
-Further, even when the global solution changes, we can show that $\Utility$ is a safe overapproximation, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b) > 0$):
+{\color{red}
+\noindent {\em Comparison:} First, the original \cite{DivideAndSlide} does not propose a formula for node $a$ two layers before $z$. 
+Consider again the running example of Fig. \ref{img:FSB_example}. 
+In the case $c\cdot d<0$, we have $\Utility\_\max\nolimits^z(a)=\Improve_{max}^z(b)=s_{FSB}(a)=s_{SR}(a)=0$, as $\Delta(\hat{a})=0$. In the case $c>0,d>0$, 
+$\Delta(\hat{a}) = \ReLU(\sol(a))-\sol(\hat{a})$ is precise,
+whereas the corresponding $\Delta_{FSB}(\hat{a}) = \LB(a) r(a)$ is only an upperbound.
+The last case $c<0,d<0$ is the most extreme: 
+$\Delta(\hat{b})$ adapts to the case (b),(c) in Fig. \ref{node:b} leveraging the value $\sol(b)$, which yields very different values, whereas the corresponding $\Delta_{FSB}(\hat{b})$
+is always $r(b) \Delta_{FSB}(b)$. For $sol(b)<<0$, we will have 
+$\Delta(\hat{b})=0<\Delta_{FSB}(\hat{b})$.
+For $sol(b)>>0$, we will have 
+$\Delta(\hat{b})=\Delta(b) > \frac{1}{2}\Delta_{FSB}(\hat{b})$ 
+as $r(b)=\frac{1}{2}$. We can show that $\Utility$ is a safe overapproximation of 
+$\Improve\_\max^z(a)$, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b)>>0$):
+}
 
@@
 
-Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$. 
 In particular, for all nodes $a$ with $\Utility\_\max\nolimits^z(a)=0$, 
@@
 
+%\textcolor{red}{$s_{FSB}$ *is* in Figure 5, under label “GS” (global-scoring). $s_{SR}$ is very slightly worst, reason why we did not report it.}
+
 \iffalse

### 2025-04-21 ATVA 2025/formula.tex
comp form

@@
 
-\begin{figure}[b!]
+\begin{figure}[t!]
 	\begin{centering}
@@
 
-We proceed inductively to define $\Utility\_\max^z(a)$ for deeper neurons $a$.
+%We proceed inductively to define $\Utility\_\max^z(a)$ for deeper neurons $a$.
 
+\iffalse
 While $\Utility$ is a priori a more accurate way to select neurons to open in partial MILP (that will be verified in Fig.
-\ref{fig_table3}), global scoring functions have two advantages: first, they are faster to compute (a unique backpropagation is sufficient, while SAS needs one full LP call to recover the solution, plus a forward propagation for each node $a$).
+\ref{fig_table3}), global scoring functions have two advantages: first, they are faster to compute (a unique backpropagation is sufficient, while SAS needs one LP call to recover the solution, plus a forward propagation for each node $a$).
 This is not an issue for selecting nodes for partial MILP, as there is a single selection step.
@@
 We will verify that using GS for ordering nodes after the SAS selection is actually more efficient, for this very reason.
+\fi
 

### 2025-04-21 ATVA 2025/experiments.tex
exp

@@
 \end{figure}
-
-\textcolor{red}{The number of open nodes we considered for the 5 F(ully)C(onnected)NNs depend neither on the image nor on the particular FCNN, only on the depth of the layer, because the runtime depends crucially on this factor.
-For FCNNs, we use a simple /2 rule between the number of open nodes of layer+1 vs layer (except last layer=14).
-For other architectures, we set the number of nodes to obtain similar runtime per layer, by testing a couple of neurons per layer, and use it for all images.}
 
@@
 
-\subsection{Comparison between different scoring functions.}
+\subsection{Comparison between different scoring functions (accuracy).}
 
 %The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
-First, we measured the distance between SAS or GS and real improvement for all nodes in the first two layers of $5 \times 100$ wrt the accuracy of nodes in the third layer.
+%First, we measured the distance between SAS or GS and real improvement for all nodes in the first two layers of $5 \times 100$ wrt the accuracy of nodes in the third layer.
 On average, the distance using GS is 4 times larger than using SAS.
 
-Then, to measure the impact of the scoring function to select neurons to open, 
+%Then, 
+To measure the impact of the scoring function to select neurons to open, 
 we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
@@
 We report in Figure \ref{fig_table3} the average uncertainty of $\MILP_X$ following the 
-choice of the $K$ heaviest neurons of SAS, compared with a random choice, with Huang \cite{DivideAndSlide}, based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$, and with GS.
+choice of the $K$ heaviest neurons of SAS, compared with a random choice, with Huang \cite{DivideAndSlide}, based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$, and with GS (here, $s_{FSB}$).
 
@@
 		\hline \hline
-		Gurobi & 0.384 & 252s & 0.368&265  &0.342 & 287& 0.315  & 306s  \\ 
-		SAS (static) & 0.384 & 448s & 0.368&759  &0.365 &971 & 0.355  & 971s \\
-		GS (static) & 0.384 & {\bf 251s} &0.368 &{\bf 253}  & 0.342 &{\bf 270} & 0.315 & {\bf 281s} \\ \hline
+		Gurobi & 0.384 & 252s & 0.368&265s  &0.342 & 287s& 0.315  & 306s  \\ 
+		SAS (static) & 0.384 & 448s & 0.368&759s  &0.365 &971s & 0.355  & 971s \\
+		GS (static) & 0.384 & {\bf 251s} &0.368 &{\bf 253s}  & 0.342 &{\bf 270s} & 0.315 & {\bf 281s} \\ \hline
 	\end{tabular}
@@
 However, the GS {\em ordering} (with the SAS {\em selection}) is better as it is general and not local to a solution, with better runtime than Gurobi, despite its staticness whereas Gurobi order is adaptative.
-Using SAS order for the solution branch, and GS ordering for other branches should be more efficient, but we cannot experiment that within the closed-source Gurobi solver.
+% Using SAS order for the solution branch, and GS ordering for other branches should be more efficient, but we cannot experiment that within the closed-source Gurobi solver.
 
@@
 
+\subsection{Comparison with MILP (time and accuracy)}
+
+Restricting the set $X$ of open ReLU nodes potentially hurts accuracy. 
+Another strategy could be to still compute inductively accurate bounds for each nodes,
+replacing pMILP ({\sf SAS, GS}, etc.) with a full MILP model, and stopping it early after some fixed time-out (100s,250s, $\ldots$, 2000s).
+
+We evaluate in Figure \ref{fig555} the full MILP and different pMILP models on the output layer of CNN-B-Adv. The bounds for hidden layers have been computed with the same SAS method.
+We compare the {\em distance to verify} the same Image 85, specifically the lower bound of an output neuron, the furthest away from verification.
+%(the local robustness objective asks the difference between the value of the output neuron corresponding to the correct class and the value of any other output neuron to be positive). 
+The curve is not as smooth as in Fig.~\ref{fig_table3}, as a unique neuron is considered rather than an average over neurons.
+
+\begin{figure}[t!]
+	\hspace*{-0.8cm}
+	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
+	\caption{Distance to verify vs runtime: comparison between SAS, GS, full MILP and Huang's method for different number of ReLUs open / time-outs.}
+	\label{fig555}
+\end{figure}
+
+{\sf SAS} (even {\sf GS}$=s_{FSB}$) is much more accurate than full MILP for every reasonable time-outs considered, with >10 times fastest runtime at better accuracy.
+The reason is that even the advanced MILP solver Gurobi struggles to sort out all ReLUs, and that is when having accurate scoring functions as {\sf SAS }is particularly important.
+
+The difference of distance to verify between SAS and GS ISO number of ReLUs is very large.
+However, as the ReLUs opened by GS are not as important as the ReLUs opened by SAS, the runtime of GS ISO number of ReLUs is faster than for SAS.
+Still, the important metric here is runtime ISO accuracy (distance to verify), which is clearly favorable for SAS, close to 2x faster.
+Importantly, the accuracy gain by SAS is very predictable, with improvement with each open ReLUs, while it is much more erratic for GS.
+This helps setting a fixed number of ReLUs.
+Also, SAS reaches accuracy which would be hard to match by GS in number of ReLUs to open, needing an extremely high number of open ReLUs, and thus, a uncertain high runtime.
+
 \subsection{Comparison with $\alpha,\beta$-Crown}
+
+\textcolor{red}{The number of open nodes we considered for the 5 F(ully)C(onnected)NNs depend neither on the image nor on the particular FCNN, only on the depth of the layer, because the runtime depends crucially on this factor.
+For FCNNs, we use a simple /2 rule between the number of open nodes of layer+1 vs layer (except last layer=14).
+For other architectures, we set the number of nodes to obtain similar runtime per layer, by testing a couple of neurons per layer, and use it for all images.}
 
@@
 	\end{table}
-
-\newpage
 
@@
 
+\iffalse
 \subsection{Finer Grain evaluation of Accuracy}
@@
 On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, 3 times smaller than the $0.042$ gap for $\alpha,\beta$-CROWN.
+
+\fi
 

### 2025-04-21 ATVA 2025/experiments.tex
exp

@@
 	\hspace*{-0.8cm}
-	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
+	\includegraphics[scale=0.5]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
 	\caption{Distance to verify vs runtime: comparison between SAS, GS, full MILP and Huang's method for different number of ReLUs open / time-outs.}
@@
 
-{\sf SAS} (even {\sf GS}$=s_{FSB}$) is much more accurate than full MILP for every reasonable time-outs considered, with >10 times fastest runtime at better accuracy.
-The reason is that even the advanced MILP solver Gurobi struggles to sort out all ReLUs, and that is when having accurate scoring functions as {\sf SAS }is particularly important.
-
-The difference of distance to verify between SAS and GS ISO number of ReLUs is very large.
-However, as the ReLUs opened by GS are not as important as the ReLUs opened by SAS, the runtime of GS ISO number of ReLUs is faster than for SAS.
-Still, the important metric here is runtime ISO accuracy (distance to verify), which is clearly favorable for SAS, close to 2x faster.
-Importantly, the accuracy gain by SAS is very predictable, with improvement with each open ReLUs, while it is much more erratic for GS.
-This helps setting a fixed number of ReLUs.
-Also, SAS reaches accuracy which would be hard to match by GS in number of ReLUs to open, needing an extremely high number of open ReLUs, and thus, a uncertain high runtime.
+{\sf SAS} (even {\sf GS}$=s_{FSB}$) is much more accurate than full MILP for every reasonable time-outs considered, with $>10$ times fastest runtime at better accuracy.
+The reason is that even the advanced MILP solver Gurobi struggles to sort out all ReLUs.
+It is thus particulary important to have accurate scoring functions as {\sf SAS}, in order to optimize both accuracy and runtime.
+Huang \cite{DivideAndSlide} is limited in ReLUs in the previous layer, reason why it is stuck at relatively poor accuracy.
+The accuracy/runtime curve from {\sf GS} is closer to {\sf SAS} than the number of nodes / accuracy curve of Fig.
+\ref{fig_table3}.
+This is because some ReLU nodes deemed important by {\sf GS} are not important for accuracy, but they are also not penalizing runtime too much.
+Still, {\sf SAS} is faster than {\sf GS} at  every accuracy.
+Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance over different output neurons in runtime compared with {\sf GS} for similar accuracy
+(not displayed), which helps setting a number of ReLU nodes to open.
 

### 2025-04-21 ATVA 2025/Paper_noProof.tex
final

@@
 \section{Conclusion}
-In this paper, we developed a novel solution-aware scoring (SAS) function to select few ReLU nodes to consider with binary variables to compute accurately bounds in DNNs. 
-The solution awareness allows SAS to compute an accurate score for each ReLU, which enables partial MILP to be very efficient, necessitating $\approx6$x less binary variables than previous proposals \cite{DivideAndSlide} for the same accuracy.
-As the worst-case complexity is exponential in the number of binary variables, this big leap ahead has large implication in terms of scalability to larger DNNs, making it possible to verify quite large DNNs such as CNN-B-Adv with 2M parameters and 20000 activation functions.
+In this paper, we developed a novel solution-aware scoring ({\sf SAS}) function to select few ReLU nodes to consider with binary variables to compute accurately bounds in DNNs. 
+The solution awareness allows SAS to compute an accurate score for each ReLU, which enables partial MILP to be very efficient, necessitating $\approx6$x less binary variables than previous proposals \cite{DivideAndSlide} for the same accuracy, and $\approx2$x less than {\sf GS} scoring adapted from FSB \cite{FSB}.
+As the worst-case complexity is exponential in the number of binary variables, this has large implication in terms of scalability to larger DNNs, making it possible to verify accurately quite large DNNs such as CNN-B-Adv with 2M parameters.
 
 While $\alpha,\beta$-Crown is known to be extremely efficient to solve easier verification instances, we exhibit many cases (complex instances) where its worst-case exponential complexity in the number of ReLUs is tangible, with unfavorable scaling (Table \ref{table_beta}).
-Resorting to Hybrid MILP, a divide-and-conquer approach \cite{DivideAndSlide}, revisited thanks to the very efficient solution-aware scoring, revealed to be a much better trade-off than augmenting $\alpha,\beta$-Crown time-outs, with $8\%$ to $40\%$ less undecided images at ISO runtime.
+Resorting to Hybrid MILP, a divide-and-conquer approach \cite{DivideAndSlide}, revisited thanks to the very efficient {\sf SAS}, revealed to be a much better trade-off than augmenting $\alpha,\beta$-Crown time-outs, with $8\%$ to $40\%$ less undecided images at ISO runtime.
+Currently, for hard instances, there is no alternative to partial MILP, other methods being $>10$ times slower.
 
-Last, we adapted BaB-SR \cite{BaB} and FSB \cite{FSB} as global scoring (GS) functions. 
-We compared GS with SAS both theoretically and experimentally with solution-aware scoring: While GS are not as efficient as SAS for ReLU {\em selection} (2x more binary variables needed), GS functions generate {\em static order} more adapted to every branch of a BaB process.
-This opens up interesting future research directions, to hybridize different scoring for different tasks;  e.g.
-verifying global \cite{lipshitz}, \cite{sensing} rather than local (robustness) properties.
+This opens up interesting future research directions, to verify global \cite{lipshitz}, \cite{sensing} rather than local (robustness) properties, which need very accurate methodology
+and give rise to hard instances as the range of each neuron is no more local to a narrow neighborhood (and thus almost all ReLUs are unstable, with both modes possible).
+
+%Last, we adapted BaB-SR \cite{BaB} and FSB \cite{FSB} as global scoring (GS) functions. 
+%We compared GS with SAS both theoretically and experimentally with solution-aware scoring: While GS are not as efficient as SAS for ReLU {\em selection} (2x more binary variables needed), GS functions generate {\em static order} more adapted to every branch of a BaB process.
 

### 2025-04-21 ATVA 2025/experiments.tex
final

@@
 We report in Figure \ref{fig_table3} the average uncertainty of $\MILP_X$ following the 
-choice of the $K$ heaviest neurons of SAS, compared with a random choice, with Huang \cite{DivideAndSlide}, based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$, and with GS (here, $s_{FSB}$).
+choice of the $K$ heaviest neurons of {\sf SAS}, compared with a random choice, with Huang \cite{DivideAndSlide}, based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$, and with GS (here, $s_{FSB}$).
 
@@
 
-Overall, SAS is more accurate than GS, more accurate than Huang, more accurate than random choice of variables. SAS significantly outperforms other solutions, 
+Overall, {\sf SAS} is more accurate than GS, more accurate than Huang, more accurate than random choice of variables. {\sf SAS} significantly outperforms other solutions, 
 with 2 times less binary variables for the same accuracy (10 vs 22) vs GS and 6 times vs Huang (4 vs 24).
@@
 Gurobi relies on a BaB procedure to compute bounds.
-We report in Table \ref{table.order} experiments on changing the ordering on variables in Gurobi, when the selection of ReLUs is fixed by SAS on CNN-B-Adv Image 85.
+We report in Table \ref{table.order} experiments on changing the ordering on variables in Gurobi, when the selection of ReLUs is fixed by {\sf SAS} on CNN-B-Adv Image 85.
 We compared
 the standard Gurobi ordering of variables, which is adaptative in each branch, 
-with the static order provided by SAS, as well as the static order provided by GS, wrt runtime at a fixed accuracy (we report the {\em distance} to verify the image).
+with the static order provided by {\sf SAS}, as well as the static order provided by GS, wrt runtime at a fixed accuracy (we report the {\em distance} to verify the image).
 
@@
 		Gurobi & 0.384 & 252s & 0.368&265s  &0.342 & 287s& 0.315  & 306s  \\ 
-		SAS (static) & 0.384 & 448s & 0.368&759s  &0.365 &971s & 0.355  & 971s \\
-		GS (static) & 0.384 & {\bf 251s} &0.368 &{\bf 253s}  & 0.342 &{\bf 270s} & 0.315 & {\bf 281s} \\ \hline
+		{\sf SAS} (static) & 0.384 & 448s & 0.368&759s  &0.365 &971s & 0.355  & 971s \\
+		{\sf GS} (static) & 0.384 & {\bf 251s} &0.368 &{\bf 253s}  & 0.342 &{\bf 270s} & 0.315 & {\bf 281s} \\ \hline
 	\end{tabular}
-	\caption{Comparison of different orderings with selection of ReLUs by SAS.
+	\caption{Comparison of different orderings with selection of ReLUs by {\sf SAS}.
 	\vspace{-0.4cm}}
@@
 
-SAS ordering is particularly counter-productive because it is accurate only for one branch (the most complicated one), whereas Gurobi can adapt the order to each branch.
-However, the GS {\em ordering} (with the SAS {\em selection}) is better as it is general and not local to a solution, with better runtime than Gurobi, despite its staticness whereas Gurobi order is adaptative.
+{\sf SAS} ordering is particularly counter-productive because it is accurate only for one branch (the most complicated one), whereas Gurobi can adapt the order to each branch.
+However, the GS {\em ordering} (with the {\sf SAS} {\em selection}) is better as it is general and not local to a solution, with better runtime than Gurobi, despite its staticness whereas Gurobi order is adaptative.
 % Using SAS order for the solution branch, and GS ordering for other branches should be more efficient, but we cannot experiment that within the closed-source Gurobi solver.
@@
 
-We evaluate in Figure \ref{fig555} the full MILP and different pMILP models on the output layer of CNN-B-Adv. The bounds for hidden layers have been computed with the same SAS method.
+We evaluate in Figure \ref{fig555} the full MILP and different pMILP models on the output layer of CNN-B-Adv. The bounds for hidden layers have been computed with the same {\sf SAS} method.
 We compare the {\em distance to verify} the same Image 85, specifically the lower bound of an output neuron, the furthest away from verification.
@@
 	\includegraphics[scale=0.5]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
-	\caption{Distance to verify vs runtime: comparison between SAS, GS, full MILP and Huang's method for different number of ReLUs open / time-outs.}
+	\caption{Distance to verify vs runtime: comparison between {\sf SAS}, GS, full MILP and Huang's method for different number of opened ReLUs / time-outs.}
 	\label{fig555}
@@
 Still, {\sf SAS} is faster than {\sf GS} at  every accuracy.
-Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance over different output neurons in runtime compared with {\sf GS} for similar accuracy
+Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance in runtime  over different output neurons compared with {\sf GS} for similar accuracy
 (not displayed), which helps setting a number of ReLU nodes to open.
@@
 \subsection{Comparison with $\alpha,\beta$-Crown}
-
-\textcolor{red}{The number of open nodes we considered for the 5 F(ully)C(onnected)NNs depend neither on the image nor on the particular FCNN, only on the depth of the layer, because the runtime depends crucially on this factor.
-For FCNNs, we use a simple /2 rule between the number of open nodes of layer+1 vs layer (except last layer=14).
-For other architectures, we set the number of nodes to obtain similar runtime per layer, by testing a couple of neurons per layer, and use it for all images.}
 
@@
 
-\textcolor{red}{MNIST FCNN networks use the same open numbers sequence for all images, based on layer depth.
+\iffalse
+\textcolor{red}{The number of open nodes we considered for the 5 F(ully)C(onnected)NNs depend neither on the image nor on the particular FCNN, only on the depth of the layer, because the runtime depends crucially on this factor.
+For FCNNs, we use a simple /2 rule between the number of open nodes of layer+1 vs layer (except last layer=14).
+For other architectures, we set the number of nodes to obtain similar runtime per layer, by testing a couple of neurons per layer, and use it for all images.
+MNIST FCNN networks use the same open numbers sequence for all images, based on layer depth.
 CIFAR ConvolutionalNN uses another sequence (the same for all images) [AppendixA, Table6 p22].}
+\fi
 
@@
 {\em Analysis}: overall, Hybrid MILP is very accurate, only leaving $8\%$-$15\%$ of images undecided, with runtime taking less than $500s$ in average per image, and even 10 times less on smaller DNNs.
-It can scale up to quite large hard DNNs, such as CNN-B-Adv with 2M parameters and 20K activation functions.
+It can scale up to quite large hard DNNs, such as CNN-B-Adv with 2M parameters.
 
@@
 
-\textcolor{red}{Currently, for hard instances, there is no alternative  to pMILP (hundreds of seconds), other methods being $>>10$ times slower.}
-
-\textcolor{red}{We did run and reported other tools as best as we could (see also appendixC (Table11...)).
+%\textcolor{red}{We did run and reported other tools as best as we could (see also appendixC (Table11...)).
 Reporting *some* experimental numbers from other papers (Figure5) is standard in the DNN verification community (eg [26]).}
@@
 	\end{tabular}
-	\caption{Images verified by different verifiers on CIFAR CNN-B-adv from \cite{cutting}.
-	Results are not directly comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
+	\caption{Images verified by different verifiers ($\%$, higher is better) on CIFAR CNN-B-adv. Results, from \cite{cutting}, are not fully comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
 	\label{table_gcp}

### 2025-04-21 ATVA 2025/experiments.tex
final

@@
 
-\subsection{Comparison with other Verifiers?}
+\subsection{Comparison with other Verifiers}
 
-We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
+We voluntarily limited the comparison so far to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
 

### 2025-04-22 ATVA 2025/proofsb.tex
update

--- 2025-04-08 ATVA 2025/proofsb.tex
@@
 
-First, we provide in Fig.~\ref{fig55} the distance to verify Image 85 (which is an extremely hard image), comparing SAS with GS in runtime and not just in number of ReLUs to open.
+%First, we provide in Fig.~\ref{fig55} the distance to verify Image 85 (which is an extremely hard image), comparing SAS with GS in runtime and not just in number of ReLUs to open.
 The {\em distance to verify} an image is specifically the lower bound of {\em one} output neuron (in the 4th layer of CNN-B-Adv), the furthest away from verification, (the local robustness objective asks the difference between the value of the output neuron corresponding to the correct class and the value of any other output neuron to be positive).
@@
 This provides an idea of the runtime scaling with the number of ReLUs opened.
-
-\begin{figure}[b!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_min.png}
-	\caption{Distance to verify vs runtime: comparison between SAS and GS for different number of ReLUs open.}
-	\label{fig55}
-\end{figure}
+%
+%\begin{figure}[b!]
+%	\hspace*{-0.8cm}
+%	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
+%	\caption{Distance to verify vs runtime: comparison between SAS, GS, full MILP and Huang's method for different number of ReLUs open.}
+%	\label{fig55}
+%\end{figure}
 

### 2025-04-23 ATVA 2025/Paper_noProof.tex
update

@@
 To simplify the notations, we restrict the presentation to feed-forward, 
-fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
+fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $\ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
+$\ReLU(x)=x$ for $x \geq 0$ and $\ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
 
@@
 	\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
-	\hat{\boldsymbol{z}}^{i} = ReLU({\boldsymbol{z}}^i).
+	\hat{\boldsymbol{z}}^{i} = \ReLU({\boldsymbol{z}}^i).
 \end{align*}

### 2025-04-23 ATVA 2025/formula.tex
update

@@
 
-Consider $(sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
+Consider $(\sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
 %(this can be obtained very efficiently by {\em one} call to an LP solver).
@@
 Computing exactly $\Improve\_\max^z(n)$ would need a MILP call on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$, which would be very time consuming.
-Instead, the SAS function uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$
+Instead, the SAS function uses a (single) LP call to compute $(\sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$
 (Fig. \ref{fig_table3}).

### 2025-04-23 ATVA 2025/Paper_noProof.tex
fix

@@
 The previous attempts were suboptimal in that respect.
-To select these important ReLU variables, we propose a novel {\em solution-aware} ReLU scoring (SAS), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU scoring (GS) functions.
-		We compare them theoretically as well as experimentally: SAS is more efficient to {\em select} a set of variables, while GS is more efficient at {\em ordering} this selection.
+To select these important ReLU variables, we propose a novel {\em solution-aware} ReLU scoring ({\sf SAS}), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU scoring ({\sf GS}) functions.
+		We compare them theoretically as well as experimentally, and {\sf SAS} is more efficient at selecting a set of variables to open using binary variables.
+		%, while GS is more efficient at {\em ordering} this selection.
 		%Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em branch} within this selection.
 		Compared with previous attempts, SAS reduces the number of binary variables by around 6 times, while maintaining the same level of accuracy.
-Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CNNs with 20 000 nodes.
+Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance),
+		even for fairly large CNNs with 2 million parameters.
 
@@
 Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
-A path $\pi$ is a sequence $\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight of $\pi$ is
-$weight(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
+%A path $\pi$ is a sequence $\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight of $\pi$ is 
+%$weight(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
 

### 2025-04-23 ATVA 2025/experiments.tex
fix

@@
 To measure the impact of the scoring function to select neurons to open, 
-we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
-We tested over the $\vx=85$th image in the CIFAR dataset.
+we considered the complex CNN-B-Adv, which has 16634 nodes. 
+We tested over the $\vx=85$th image in the CIFAR-10 dataset.
 To measure the accuracy, we measure the uncertainty of all nodes in the 4th layer:
@@
 We report in Figure \ref{fig_table3} the average uncertainty of $\MILP_X$ following the 
-choice of the $K$ heaviest neurons of {\sf SAS}, compared with a random choice, with Huang \cite{DivideAndSlide}, based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$, and with GS (here, $s_{FSB}$).
+choice of the $K$ heaviest neurons of {\sf SAS}, compared with a random choice, with Huang \cite{DivideAndSlide}, based on strength$(n) = (\UB(n)-\LB(n))\cdot |W_{nz}|$, and with {\sf GS} (here, $s_{FSB}$).
 
@@
 Overall, {\sf SAS} is more accurate than GS, more accurate than Huang, more accurate than random choice of variables. {\sf SAS} significantly outperforms other solutions, 
-with 2 times less binary variables for the same accuracy (10 vs 22) vs GS and 6 times vs Huang (4 vs 24).
+with 2 times less binary variables for the same accuracy (10 vs 22) vs {\sf GS} and 6 times vs Huang \cite{DivideAndSlide} (4 vs 24).
 Each node of the 4th layer displays a similar pattern, and the pattern is similar for different images (see appendix).

### 2025-04-23 ATVA 2025/introduction.tex
update
fix

--- 2025-04-16 ATVA 2025/introduction.tex
@@
 		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
-		CIFAR CNN-B-adv &  {\color{red} 16634}  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		CIFAR CNN-B-adv &  16634  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
 		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
-		CIFAR ResNet &   {\color{red} 8xxxx}             & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-		$\epsilon = 2/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
+		CIFAR ResNet &   107496  & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
+		$\epsilon = 8/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
 	\end{tabular}
@@
 \ref{fig_table3}).
-We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally ({\color{red}see Fig.
-\ref{fig_branch}}).
+	%We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally (see Table.
+\ref{table.order}).
 
@@
 	are abstractions, and thus much faster to solve. 
-	While full MILP is thus {\em asymptotically} more accurate than {\sf SAS} and {\sf GS}, {\em experimentally}, every reasonable time-out leads to much better practical accuracy of {\sf SAS} (and {\sf GS}) ({\color{red}see Fig.
-\ref{fig_timeout}}).
+	While full MILP is thus {\em asymptotically} more accurate than {\sf SAS} and {\sf GS}, {\em experimentally}, every reasonable time-out leads to much better practical accuracy of {\sf SAS} (and {\sf GS}) (see Fig.
+\ref{fig555}).
 
@@
 It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-Crown with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance ($46-420$s), Table \ref{table_hybrid}.
-It scales to fairly large networks such as CIFAR-10 CNN-B-Adv \cite{SDPFI}, with more than 20 000 neurons.
+It scales to fairly large networks such as CIFAR-10 CNN-B-Adv \cite{SDPFI}, with more than 2 million parameters.
 %We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
@@
 Limitation: We consider DNNs employing the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}, with updated MILP models e.g.
-for {\color{red} softmax}.
+for maxpool.
+
+\newpage
 

### 2025-04-23 ATVA 2025/valabstraction.tex
fix

@@
 
-{\color{red}
 In this paper, we revisit the use of {\em partial MILP} (pMILP for short, see \cite{DivideAndSlide}), to get interesting trade-offs between accuracy and runtime.
-Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: pMILP$_X(n)$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding (equation (2) Section 3.2), where variable $a$ is
+Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: pMILP$_X(n)$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding (equation (2) Section 3.2), where variable $a$ is:
 \begin{itemize}
@@
 So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.
-}
 

### 2025-04-23 ATVA 2025/proofsb.tex
update table
update
update plot

@@
 %\end{figure}
+
+\begin{table}
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
+		\hline
+	0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
+	\hline
+	2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
+	\hline
+	3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
+	\hline
+	4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
+	\hline
+	5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
+	\hline
+	6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
+	\hline
+	7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
+	\hline
+	8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
+	\hline
+	9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
+	\hline
+		Average & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
+	\hline
+		Variant & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
+	\hline
+	\end{tabular}
+	\vspace*{1ex}
+	 \caption{Time cost and accuracy by SAS (open 30 nodes and 14 nodes) and GS (open 30 nodes). Here, smaller $\UB$ means higher accuracy and positive means verified.}
+\end{table}
 
@@
 We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.
-
-\textcolor{red}{Direct MILP encodings are inefficient!
-Even the advanced Gurobi MILP solver struggle to sort out all neurons – see Fig11 page27: direct MILP encoding is $>10$ times slower on same instance ($>300s$ vs $<30s$ for similar accuracy) wrt considering only 8 open nodes selected with SAS (more open nodes lead to larger differences).
-Our main contribution is a way to select the most important nodes, and it helps Gurobi tremendously.
-This is the whole point of the paper!}
 

### 2025-04-23 ATVA 2025/experiments.tex
update plot
update

@@
 Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance in runtime  over different output neurons compared with {\sf GS} for similar accuracy
-(not displayed), which helps setting a number of ReLU nodes to open.
+(see table \ref{SAS_GS_similarTO}), which helps setting a number of ReLU nodes to open.
+
+\begin{table}
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
+		\hline
+		0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
+		\hline
+		2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
+		\hline
+		3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
+		\hline
+		4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
+		\hline
+		5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
+		\hline
+		6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
+		\hline
+		7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
+		\hline
+		8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
+		\hline
+		9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
+		\hline
+		Average & -3.1647624
+		 & 70.3
+		  & -3.129414017 & 78.6
+		  \\
+		\hline
+		Variance & 
+		 & 184
+		  &  & 359
+		   \\
+		\hline
+	\end{tabular}
+	\vspace*{1ex}
+	\caption{Time cost and accuracy by SAS and GS. Here, smaller $\UB$ means higher accuracy and negative means verified.}
+	\label{SAS_GS_similarTO}
+\end{table}
 

### 2025-04-24 ATVA 2025/experiments.tex
update

@@
 
+%	\begin{tabular}{|c|c|c|c|c|}
+%	\hline
+%	NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
+%	\hline
+%	0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
+%	\hline
+%	2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
+%	\hline
+%	3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
+%	\hline
+%	4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
+%	\hline
+%	5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
+%	\hline
+%	6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
+%	\hline
+%	7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
+%	\hline
+%	8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
+%	\hline
+%	9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
+%	\hline
+%	Average & -3.1647624
+%	& 70.3
+%	& -3.129414017 & 78.6
+%	\\
+%	\hline
+%	Variance & 
+%	& 184
+%	&  & 359
+%	\\
+%	\hline
+%\end{tabular}
+
 \begin{table}
-	\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|}
 	\hline
-		NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
+	Node & 0 &  2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 &Avg& Var \\
 	\hline
-		0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
+	SAS & -1.47 & -4.56 & -4.48 & -3.46 & -5.6 & -3.06 & -4.17 & 0.639 & -2.33 &-3.16& \\
 	\hline
-		2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
+	Time/s & 66.9 & 54.8 & 69.9 & 88.8 & 94.8 & 63.3 & 73.4 & 56.7 & 64.6 &70.3& 184\\
 	\hline
-		3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
+	GS & -1.38 & -4.54 & -4.45 & -3.48 & -5.7 & -2.98 & -4.08 & 0.726 & -2.28 &-3.13&\\
 	\hline
-		4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
-		\hline
-		5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
-		\hline
-		6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
-		\hline
-		7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
-		\hline
-		8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
-		\hline
-		9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
-		\hline
-		Average & -3.1647624
-		 & 70.3
-		  & -3.129414017 & 78.6
-		  \\
-		\hline
-		Variance & 
-		 & 184
-		  &  & 359
-		   \\
+	Time/s & 71.6 & 84.9 & 71.2 & 113 & 93.7 & 68.5 & 88.6 & 46.5 & 69.4 &78.6&359\\
 	\hline

### 2025-04-24 ATVA 2025/experiments.tex
final?

--- 2025-04-23 ATVA 2025/experiments.tex
@@
 \ref{fig_table3}.
-This is because some ReLU nodes deemed important by {\sf GS} are not important for accuracy, but they are also not penalizing runtime too much.
+This is because many ReLU nodes deemed important by {\sf GS} are not relevant for accuracy, but they are also not penalizing runtime.
 Still, {\sf SAS} is faster than {\sf GS} at  every accuracy.
-Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance in runtime  over different output neurons compared with {\sf GS} for similar accuracy
-(not displayed), which helps setting a number of ReLU nodes to open.
+Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance in runtime over different output neurons compared with {\sf GS} for similar accuracy (see table \ref{SAS_GS_similarTO} in Appendix), which helps setting a number of ReLU nodes to open.
+
+%	\begin{tabular}{|c|c|c|c|c|}
+%	\hline
+%	NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
+%	\hline
+%	0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
+%	\hline
+%	2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
+%	\hline
+%	3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
+%	\hline
+%	4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
+%	\hline
+%	5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
+%	\hline
+%	6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
+%	\hline
+%	7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
+%	\hline
+%	8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
+%	\hline
+%	9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
+%	\hline
+%	Average & -3.1647624
+%	& 70.3
+%	& -3.129414017 & 78.6
+%	\\
+%	\hline
+%	Variance & 
+%	& 184
+%	&  & 359
+%	\\
+%	\hline
+%\end{tabular}
 

### 2025-04-24 ATVA 2025/formula.tex
an advise sample
final?

@@
 
-{\color{red}
-\noindent {\em Comparison:} First, the original \cite{DivideAndSlide} does not propose a formula for node $a$ two layers before $z$. 
+\noindent {\em Comparison:} First, the original \cite{DivideAndSlide} does not propose a formula for node $a$ two layers before $z$. So we will compare {\sf SAS} with {\sf GS}.
 Consider again the running example of Fig. \ref{img:FSB_example}.
-In the case $c\cdot d<0$, we have $\Utility\_\max\nolimits^z(a)=\Improve_{max}^z(b)=s_{FSB}(a)=s_{SR}(a)=0$, as $\Delta(\hat{a})=0$. In the case $c>0,d>0$, 
+
+In the case $c\cdot d<0$, we have $\Utility\_\max\nolimits^z(a)=\Improve_{max}^z(b)=s_{FSB}(a)=s_{SR}(a)=0$, as $\Delta(\hat{a})=0$.
+
+In the case $c>0,d>0$, 
 $\Delta(\hat{a}) = \ReLU(\sol(a))-\sol(\hat{a})$ is precise,
 whereas the corresponding $\Delta_{FSB}(\hat{a}) = \LB(a) r(a)$ is only an upperbound.
+
 The last case $c<0,d<0$ is the most extreme: 
 $\Delta(\hat{b})$ adapts to the case (b),(c) in Fig. \ref{node:b} leveraging the value $\sol(b)$, which yields very different values, whereas the corresponding $\Delta_{FSB}(\hat{b})$
-is always $r(b) \Delta_{FSB}(b)$. For $sol(b)<<0$, we will have 
+is always $r(b) \Delta_{FSB}(b)$: 
+\begin{itemize}
+\item For $sol(b)<<0$, we will have 
 $\Delta(\hat{b})=0<\Delta_{FSB}(\hat{b})$.
-For $sol(b)>>0$, we will have 
+\item For $sol(b)>>0$, we will have 
 $\Delta(\hat{b})=\Delta(b) > \frac{1}{2}\Delta_{FSB}(\hat{b})$ 
-as $r(b)=\frac{1}{2}$. We can show that $\Utility$ is a safe overapproximation of 
+as $r(b)=\frac{1}{2}$.
+\end{itemize}
+
+Further, we can show that $\Utility$ is a safe overapproximation of 
 $\Improve\_\max^z(a)$, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b)>>0$):
-}
 

### 2025-04-24 ATVA 2025/proofsb.tex
final?

--- 2025-04-22 ATVA 2025/proofsb.tex
@@
 
+First, we provide Fig.~\ref{fig5}, similar to 
+Fig.~\ref{fig_table3} but on a different image, namely 37.
+It display similar pattern as image 85, with an even larger difference between SAS and GS (around 3x more binary variables are necessary for GS to match the accuracy of SAS).
+
+\begin{figure}[h!]
+	\hspace*{-1cm}
+	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image37}
+	\caption{Comparison of different methods with image 37.}
+	\label{fig5}
+\end{figure}
+
 %First, we provide in Fig.~\ref{fig55} the distance to verify Image 85 (which is an extremely hard image), comparing SAS with GS in runtime and not just in number of ReLUs to open.
@@
 
-The difference of distance to verify between SAS and GS ISO number of ReLUs is very large.
-However, as the ReLUs opened by GS are not as important as the ReLUs opened by SAS, the runtime of GS ISO number of ReLUs is faster than for SAS.
-Still, the important metric here is runtime ISO accuracy (distance to verify), which is clearly favorable for SAS, close to 2x faster.
-Importantly, the accuracy gain by SAS is very predictable, with improvement with each open ReLUs, while it is much more erratic for GS.
-This helps setting a fixed number of ReLUs.
-Also, SAS reaches accuracy which would be hard to match by GS in number of ReLUs to open, needing an extremely high number of open ReLUs, and thus, a uncertain high runtime.
+\begin{table}
+	\begin{tabular}{|c||>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}|>{\centering\arraybackslash}p{6ex}||>{\centering\arraybackslash}p{6ex}||>{\centering\arraybackslash}p{6ex}|}
+		\hline
+		Output Node & 0 &  2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 &Avg& Var \\
+		\hline
+		{\sf SAS} distance & -1.47 & -4.56 & -4.48 & -3.46 & -5.6 & -3.06 & -4.17 & 0.639 & -2.33 &-3.16& \\
+		Time (s) & 66.9 & 54.8 & 69.9 & 88.8 & 94.8 & 63.3 & 73.4 & 56.7 & 64.6 &70.3& 184\\
+		\hline
+		{\sf GS} distance & -1.38 & -4.54 & -4.45 & -3.48 & -5.7 & -2.98 & -4.08 & 0.726 & -2.28 &-3.13&\\
+		Time (s) & 71.6 & 84.9 & 71.2 & 113 & 93.7 & 68.5 & 88.6 & 46.5 & 69.4 &78.6&359\\
+		\hline
+	\end{tabular}
+		\vspace*{1ex}
+		\caption{Distance to verify and runtime (lower is better) for different output nodes for image 85. Here, negative distance means the node is verified.}
+		\label{SAS_GS_similarTO}
+	\end{table}
 
-Then, we provide Fig.~\ref{fig5}, similar to 
-Fig.~\ref{fig_table3} but on a different image, namely 37.
-It display similar pattern as image 85, with an even larger difference between SAS and GS (around 3x more binary variables are necessary for GS to match the accuracy of SAS).
-
-\begin{figure}[h!]
-	\hspace*{-1cm}
-	\includegraphics[scale=0.55]{CNN-B-ADV_layer7_comparison_image37}
-	\caption{Comparison of different methods with image 37.}
-	\label{fig5}
-\end{figure}
+Then, we provide Table \ref{SAS_GS_similarTO} to show the runtime variability of {\sf GS} and {\sf SAS}.
+The number of opens nodes for {\sf SAS} is 14 and the number of open nodes for {\sf GS} is 30, to account for the lack of accuracy of SAS, making the average distance to verify similar between both ($-3.16$ vs $-3.13$).
+The runtime variability between different output nodes is twice as high for {\sf GS} vs {\sf SAS}, because the number of irrelevant nodes chosen by {\sf GS} is inpredictable.
+If this number is high, then the runtime can be particularly short (node 8), with also a worse accuracy; while if it is low (e.g.
+4), then the runtime is particularly long.
+This does not necesarily translates into better accuracy, e.g.
+node 2 where the runtime is much longer for {\sf GS} vs {\sf SAS}, while the accuracy is also lower.
+{\sf SAS} displays much less variability in time between different output nodes as most nodes are relevant.
 
@@
 
-\newpage
-
 \subsubsection*{restricting number of open nodes (pMILP) vs setting time-outs (full MILP)}

### 2025-04-25 ATVA 2025/proofsb.tex
update plot
small update

@@
 Hybird MILP first call $\alpha,\beta$-Crown with short time-out (TO), then call partial MILP on those inputs which was neither certified nor falsified by this run of $\alpha,\beta$-Crown.
-We are using two settings of TO, for smaller DNNs we use T0$=10s$, and for the two larger ones, we use TO$=30s$.
+We are using two settings of TO, for smaller DNNs we use TO$=10s$, and for the two larger ones, we use TO$=30s$.
 
@@
 On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-Crown, while the runtime is $>5$ times larger.
-Hence, Hybrid MILP is more accurate than Prima with similar runtime or faster.
+Hence, Hybrid MILP is more accurate than PRIMA with similar runtime or faster.
 

### 2025-04-25 ATVA 2025/proofsb.tex
samll update

@@
 
-We provide in Table \ref{table112} the average as well as maximum time to perform $MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
-For 6x500, we provide results for two different $\varepsilon$, following our test from Figure \ref{fig2}.
+We provide in Table \ref{table112} the average as well as maximum time to perform $\MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
+For 6x500, we provide results for two different $\varepsilon$.
+
+%, following our test from Figure \ref{fig2}.
 

### 2025-04-28 ATVA 2025/Paper_noProof.tex
update some words

@@
 		Compared with previous attempts, SAS reduces the number of binary variables by around 6 times, while maintaining the same level of accuracy.
-Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance),
+Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-CROWN with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance),
 		even for fairly large CNNs with 2 million parameters.
@@
 
-While $\alpha,\beta$-Crown is known to be extremely efficient to solve easier verification instances, we exhibit many cases (complex instances) where its worst-case exponential complexity in the number of ReLUs is tangible, with unfavorable scaling (Table \ref{table_beta}).
-Resorting to Hybrid MILP, a divide-and-conquer approach \cite{DivideAndSlide}, revisited thanks to the very efficient {\sf SAS}, revealed to be a much better trade-off than augmenting $\alpha,\beta$-Crown time-outs, with $8\%$ to $40\%$ less undecided images at ISO runtime.
+While $\alpha,\beta$-CROWN is known to be extremely efficient to solve easier verification instances, we exhibit many cases (complex instances) where its worst-case exponential complexity in the number of ReLUs is tangible, with unfavorable scaling (Table \ref{table_beta}).
+Resorting to Hybrid MILP, a divide-and-conquer approach \cite{DivideAndSlide}, revisited thanks to the very efficient {\sf SAS}, revealed to be a much better trade-off than augmenting $\alpha,\beta$-CROWN time-outs, with $8\%$ to $40\%$ less undecided images at ISO runtime.
 Currently, for hard instances, there is no alternative to partial MILP, other methods being $>10$ times slower.
@@
 Tested DNNs as well as MNIST and CIFAR10 DataSet are freely available.
-The source code of Hybrid MILP will be provided on GitHub after acceptance (needing Gurobi as well as $\alpha,\beta$-Crown).
+The source code of Hybrid MILP will be provided on GitHub after acceptance (needing Gurobi as well as $\alpha,\beta$-CROWN).
 

### 2025-04-28 ATVA 2025/experiments.tex
update some words

@@
 %
-We implemented \toolname\ in Python 3.8: it first calls $\alpha,\beta$-Crown with small time out (10s for small and 30s for larger DNNs), and then call pMILP on the undecided inputs.
+We implemented \toolname\ in Python 3.8: it first calls $\alpha,\beta$-CROWN with small time out (10s for small and 30s for larger DNNs), and then call pMILP on the undecided inputs.
 Gurobi 9.52 was used for solving LP and MILP problems.
@@
 
-\subsection{Comparison with $\alpha,\beta$-Crown}
+\subsection{Comparison with $\alpha,\beta$-CROWN}
 
-To assess the verification efficiency and runtime vs $\alpha,\beta$-Crown, we 
-conducted evaluations  on neural networks tested in \cite{crown} which are mostly {\em complex} to verify (as easy instances are already appropriately taken care of).
+To assess the verification efficiency and runtime vs $\alpha,\beta$-CROWN, we 
+conducted evaluations  on neural networks tested in \cite{CROWN} which are mostly {\em complex} to verify (as easy instances are already appropriately taken care of).
 Namely, 6 ReLU-DNNs: 5 MNIST DNN that can be found in the \href{https://github.com/eth-sri/eran}{ERAN GitHub}
@@
 \cite{AdversarialTrainingAndProvableDefenses}, see also \cite{SDPFI}, 
-which can be downloaded from the \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN}{$\alpha,\beta$-Crown GitHub}. 
-We commit to the same $\epsilon$ settings as in \cite{crown}, that are recalled in Table \ref{table_beta}. 
+which can be downloaded from the \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN}{$\alpha,\beta$-CROWN GitHub}. 
+We commit to the same $\epsilon$ settings as in \cite{CROWN}, that are recalled in Table \ref{table_beta}. 
 For reference, we also report an easy but very large ResNet Network for CIFAR10, already tested with $\alpha,\beta$ CROWN. 
@@
 		\hline \hline
-		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & \bf Hybrid \\ 
-		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & \bf MILP \\ 
+		 & $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN & Refined & \bf Hybrid \\ 
+		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-CROWN & \bf MILP \\ 
 		\hline
@@
 		\bf 10\% (402s) \\ \hline
-		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
+		CIFAR CNN-B-Adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
 		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
 	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}) as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown and Hybrid MILP on 7 DNNs (average runtime per image).
+	\caption{Undecided images ($\%$, {\em lower is better}) as computed by $\alpha,\beta$-CROWN, Refined $\beta$-CROWN and Hybrid MILP on 7 DNNs (average runtime per image).
 The 6 first DNNs are hard instances.
@@
 
-Compared with $\alpha,\beta$-Crown: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN (e.g.
+Compared with $\alpha,\beta$-CROWN: on easy instances, Hybrid MILP is virtually similar to $\alpha,\beta$-CROWN (e.g.
 even on the very large ResNet), since Hybrid MILP calls first $\alpha,\beta$-CROWN as it is very efficient for easy instances.
 
-On hard instances (the 6 first DNNs tested), compared with $\alpha,\beta$-Crown with a time-out of TO=2000s, Hybrid MILP is much more accurate, with a reduction of undecided images by $9\%-43\%$.
+On hard instances (the 6 first DNNs tested), compared with $\alpha,\beta$-CROWN with a time-out of TO=2000s, Hybrid MILP is much more accurate, with a reduction of undecided images by $9\%-43\%$.
 It is also from 20x faster on smaller networks to similar time on the largest DNN.
-Compared with $\alpha,\beta$-Crown with a time-out of TO=30s, the accuracy gap is even larger (e.g.
+Compared with $\alpha,\beta$-CROWN with a time-out of TO=30s, the accuracy gap is even larger (e.g.
 $11\%$ for CNN-B-Adv, i.e.
@@
 
-Last, compared with {\em Refined} $\beta$-Crown, we can observe three patterns: on the shallowest DNNs (5$\times$100, 5$\times$200), Refined $\beta$-Crown can run full MILP on almost all nodes, reaching almost the same accuracy than  Hybrid MILP, but with longer runtime (up to 2 times on 5$\times$100).
-As size of DNNs grows (8$\times$100, 8$\times$200), full MILP invoked by Refined $\beta$-Crown can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images (that is double on 8$\times$200), while having longer runtime.
-Last but not least, Refined $\beta$-Crown cannot scale to larger instances (6$\times$500, CNN-B-Adv), while Hybrid MILP can.
+Last, compared with {\em Refined} $\beta$-CROWN, we can observe three patterns: on the shallowest DNNs (5$\times$100, 5$\times$200), Refined $\beta$-CROWN can run full MILP on almost all nodes, reaching almost the same accuracy than  Hybrid MILP, but with longer runtime (up to 2 times on 5$\times$100).
+As size of DNNs grows (8$\times$100, 8$\times$200), full MILP invoked by Refined $\beta$-CROWN can only be run on a fraction of the neurons, and the accuracy is not as good as Hybrid MILP, with $6\%-8\%$ more undecided images (that is double on 8$\times$200), while having longer runtime.
+Last but not least, Refined $\beta$-CROWN cannot scale to larger instances (6$\times$500, CNN-B-Adv), while Hybrid MILP can.
 
@@
 
-We voluntarily limited the comparison so far to $\alpha,\beta$-Crown because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.
+We voluntarily limited the comparison so far to $\alpha,\beta$-CROWN because it is one of the most efficient verifier to date, which allowed us to consider a spectrum of parameters to understand $\alpha,\beta$-CROWN scaling without too much clutter.
 
-Interestingly, GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us.
+Interestingly, GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-CROWN on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us.
 We provide in Table \ref{table_gcp} results from the Table 3 page 9 of \cite{cutting}, experimenting with different verifiers on the most interesting CIFAR CNN-B-Adv.
 Notice that results are not exactly comparable with ours because the testing images are not the same (ours has $62\%$ upper bound while \cite{cutting} has $65\%$ upper bound, so the image set in \cite{cutting} are slightly easier).
-There, GCP-CROWN is $2\%$ more accurate (with higher runtime) than $\alpha,\beta$-Crown with 90s TO, so we can deduce that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-Crown with 2000s TO, is significantly more accurate than GCP-CROWN.
+There, GCP-CROWN is $2\%$ more accurate (with higher runtime) than $\alpha,\beta$-CROWN with 90s TO, so we can deduce that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-CROWN with 2000s TO, is significantly more accurate than GCP-CROWN.
 
@@
 		\hline
-		Upper Bound & SDP-FO & PRIMA & refined $\beta$-Crown & $\beta$-Crown & GCP-Crown \\  \hline
+		Upper Bound & SDP-FO & PRIMA & refined $\beta$-CROWN & $\beta$-CROWN & GCP-CROWN \\  \hline
 		65\% & 32.8\% & 38\% & 27\% & 46.5\% & 48.5\% \\
@@
 	\end{tabular}
-	\caption{Images verified by different verifiers ($\%$, higher is better) on CIFAR CNN-B-adv. Results, from \cite{cutting}, are not fully comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
+	\caption{Images verified by different verifiers ($\%$, higher is better) on CIFAR CNN-B-Adv. Results, from \cite{cutting}, are not fully comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
 	\label{table_gcp}
@@
 
-Results on other networks from other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported \cite{crown} on other tested DNNs, with unfavorable comparison vs $\alpha,\beta$-CROWN.
+Results on other networks from other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported \cite{CROWN} on other tested DNNs, with unfavorable comparison vs $\alpha,\beta$-CROWN.
 Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on complex (even small) instances.
@@
 For that, we considered the challenging DNN MNIST $6 \times 500$, and the 20 first images from the MNIST benchmark.
-We first run the attack from $\alpha,\beta$-Crown for varying $\epsilon$, using a binary search, to set up an upper bound on $\epsilon$ (the initialization is $\epsilon \in [0,1]$).
-Then we run binary search with a global time-out of $10 000s$, initialized from $0$ to this upper bound, where each call is either to $\alpha,\beta$-Crown with TO=2000s, or Hybrid MILP.
-We report the results (upper bound, best bound verified by $\alpha,\beta$-Crown and by Hybrid MILP) for each image. We report the results in Fig. \ref{fig2}.
+We first run the attack from $\alpha,\beta$-CROWN for varying $\epsilon$, using a binary search, to set up an upper bound on $\epsilon$ (the initialization is $\epsilon \in [0,1]$).
+Then we run binary search with a global time-out of $10 000s$, initialized from $0$ to this upper bound, where each call is either to $\alpha,\beta$-CROWN with TO=2000s, or Hybrid MILP.
+We report the results (upper bound, best bound verified by $\alpha,\beta$-CROWN and by Hybrid MILP) for each image. We report the results in Fig. \ref{fig2}.
 
@@
 These verification-agnostic DNNs have varying sizes: $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ and $6 \times 500$.
-We selected the 4 first because they have been tested in both \cite{prima} and \cite{crown}, they have good accuracy ($>94\%$ \cite{prima}),
+We selected the 4 first because they have been tested in both \cite{prima} and \cite{CROWN}, they have good accuracy ($>94\%$ \cite{prima}),
 and depite their small sizes there is still a large portion ($12\%$ to $20\%$) of images which are {\em undetermined} by these SOTA methods, that is images neither verified nor for which an attack has been found  \cite{attack}.
@@
 The next DNN in the list was the larger $6 \times 500$ DNN, which seemed an interesting challenge (very high accuracy and few attacks) to understand the scaling of CMP.
-Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{crown}.
+Interestingly, tests on $6 \times 500$ were not reported in \cite{prima} nor in \cite{CROWN}.
 All these DNNs tackle the MNIST benchmark, which is not a limitation as we want to validate that focusing on compensating strength improves the accuracy: we do not claim that the particular CMP implementation is the most efficient in all the situations.
 
-To obtain results comparable with \cite{prima,crown}, 
+To obtain results comparable with \cite{prima,CROWN}, 
 we evaluated CMP on $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$ for the first 1000 images of the dataset.
-For $6\times 500$ (results not reported in \cite{prima,crown}), we run all the tools ourselves for the first 200 images, given the computational overhead associated with such larger network.
+For $6\times 500$ (results not reported in \cite{prima,CROWN}), we run all the tools ourselves for the first 200 images, given the computational overhead associated with such larger network.
 Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
@@
 \begin{itemize}
-	\item DeepPoly \cite{deeppoly}/ CROWN \cite{crown}. We report the runtime from our  implementation in CMP. 
+	\item DeepPoly \cite{deeppoly}/ CROWN \cite{CROWN}. We report the runtime from our  implementation in CMP. 
 	%It shows that our purely Python implementation is not optimal ($10$ to $100$ times slower than the implementation in ($\alpha$)($\beta$)CROWN, ERAN and PRIMA). 
-	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN \cite{crown}. We use the results reported in \cite{prima} and \cite{crown} respectively for 
+	\item PRIMA~\cite{prima} and $(\alpha)\beta$ CROWN \cite{CROWN}. We use the results reported in \cite{prima} and \cite{CROWN} respectively for 
 	$5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$.
@@
 Similarly as PRIMA, $\beta$-CROWN resorts to refining the bounds of the first few layers using an exact MILP encoding, also computing 16 nodes in parallel, before running the branching heuristic BaB-FSB.
-%	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{crown,prima}).
+%	\item We also experimented with the latest versions of $\alpha$-$\beta$-CROWN (October 2023) and PRIMA (2022) on MLP $6 \times 500$ (results not reported in \cite{CROWN,prima}).
 	\item We do not report results from kPoly \cite{kpoly}, OptC2V \cite{optC2V}, 
-	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods in accuracy and time \cite{crown}.
+	SDPFO \cite{SDPFI}, MIPplanet \cite{MIPplanet}, as $(\alpha)\beta$-CROWN has been shown to outperform these methods in accuracy and time \cite{CROWN}.
 
@@
 	\caption{$\%$ of verified images and average runtime in seconds.
-		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}, except for $6 \times 500$ for which we run every verifier ourselves.
+		Results for PRIMA, $\beta$-CROWN and the upper bound on the $\%$ are from \cite{CROWN}, except for $6 \times 500$ for which we run every verifier ourselves.
 	}
@@
 Results for CMP are good, at $65\%$ of verified images, comparable with $8\times 100$, taking less than $0.3s$ per neuron to perform the verification in average per image (there are more neurons, so longer runtime was expected).
-For comparison, results for $6 \times 500$ were not reported in \cite{crown,prima}.
+For comparison, results for $6 \times 500$ were not reported in \cite{CROWN,prima}.
 On this larger network, it is unclear whether the {\em refined strategy} of PRIMA and of $(\alpha)\beta$-CROWN is applicable, as the number of binary variables to encode even the first few layers is very large.
@@
 %	\caption{$\%$ of verified images and average runtime in seconds, over 1000 images. 
-%		Results for PRIMA, $\beta$-Crown and the upper bound on the $\%$ are from \cite{crown}.
+%		Results for PRIMA, $\beta$-CROWN and the upper bound on the $\%$ are from \cite{CROWN}.
 %		\newline $^\star$ For $8 \times 200$, slow fixed results are obtained after running slow adaptative.}
@@
 %KSM: I think this paragraph doesn't make very convincing case. 
-%Importantly, ($\alpha$)$\beta$-Crown, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long timeouts ({\em refined} BaB is more accurate than pureBaB on these networks).
+%Importantly, ($\alpha$)$\beta$-CROWN, while efficient, can face a (complexity) wall, when the number of branches becomes too extreme for BaB to work: either BaB succeds fast, or it will not suceed even with very long timeouts ({\em refined} BaB is more accurate than pureBaB on these networks).
 We verify that in Table \ref{tab:example3}, on a larger DNN learnt in a natural way, namely MLP $6 \times 500$.
@@
 Only $3.5\%$ more images could be ceritifed by extending the TO from 30s to 2000s, certifying $20\%$ less images than our prototype in the same time.
-Notice that the refined BaB mode of ($\alpha$)$\beta$-Crown (first few layers using MILP) failed to run on this DNN (error code: NoImplementation), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as confirmed while running PRIMA (refined).
+Notice that the refined BaB mode of ($\alpha$)$\beta$-CROWN (first few layers using MILP) failed to run on this DNN (error code: NoImplementation), and we were unable to fix the problem, which is not really surprising as running exact MILP with so many integer variables is not likely to be efficient, as confirmed while running PRIMA (refined).
 

### 2025-04-28 ATVA 2025/introduction.tex
update some words

@@
 \cite{pyrat}, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
-and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-Crown \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
-We will thus compare mainly with $\alpha,\beta$-Crown experiments as gold standard in the following\footnote{GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us}.
+and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+We will thus compare mainly with $\alpha,\beta$-CROWN experiments as gold standard in the following\footnote{GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-CROWN on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us}.
 
@@
 		\hline
-		Network & nbr & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
+		Network & nbr & Accuracy & Upper  & $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
 		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
@@
 		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
-		CIFAR CNN-B-adv &  16634  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
+		CIFAR CNN-B--Adv &  16634  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
 		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
@@
 	\end{tabular}
-	\caption{Images verified by $\alpha,\beta$-Crown with different time-outs (TO) on 7 DNNs, and average runtime per image.
+	\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
 The 6 first DNNs are complex instances.
@@
 
-%Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-Crown \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neigbhour with a different decision.
+%Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-CROWN \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neigbhour with a different decision.
 One issue is however that easy instances are trained specifically to be easier to verify e.g.
@@
 
-%In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-Crown and the upper bound when we remove those which can be falsified.
+%In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.
 In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely MNIST 5$\times$100.
-We first dwelve into the scaling of $\alpha,\beta$-Crown, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
+We first dwelve into the scaling of $\alpha,\beta$-CROWN, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
 Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).
@@
 %Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-Crown (40\%), at the cost of a much larger runtime (4995s vs 1026s).
+Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
 \vspace{-0.5cm}}
@@
 
-Other standard non-BaB methods such as Marabou, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image.
+Other standard non-BaB methods such as Marabou, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-CROWN, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image.
 It appeared pointless to test these verifiers on larger networks.
@@
 
-%\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks,
+%\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks,
 
@@
 
-%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-Crown \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
 
-%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-Crown \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-Crown \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs; It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
+%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs; It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
 The high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
@@
 	%Notice that complete methods exist \cite{Reluplex,katz2019marabou,SDPFI}, but they time-out on hard instances.
-In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-Crown \cite{crown}.
+In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-CROWN \cite{crown}.
 %As a starting point, we sought to understand properties of DNNs that make them hard to verify.
@@
 
-	\item For the second question, we propose a new verifier, called {\em Hybrid MILP}, invoking first 	$\alpha,\beta$-Crown with short time-out to settle the easy instances.
+	\item For the second question, we propose a new verifier, called {\em Hybrid MILP}, invoking first 	$\alpha,\beta$-CROWN with short time-out to settle the easy instances.
 On those ({\em hard}) instances which are neither certified nor falsified, we call pMILP with few neurons encoded as binary variables.
 Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
-It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-Crown with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance ($46-420$s), Table \ref{table_hybrid}.
+It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-CROWN with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance ($46-420$s), Table \ref{table_hybrid}.
 It scales to fairly large networks such as CIFAR-10 CNN-B-Adv \cite{SDPFI}, with more than 2 million parameters.
@@
 To benchmark these tools, a competition has been run since 2019, namely VNNcomp \cite{VNNcomp}.
-The current overall better performing verifier is $\alpha$-$\beta$-Crown \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound" (BaB) \cite{BaB}, and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
+The current overall better performing verifier is $\alpha$-$\beta$-CROWN \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound" (BaB) \cite{BaB}, and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
 \cite{cutting}.
@@
 %because for "easier" DNNs, adequate methods already exist. 
-%To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-Crown \cite{crown}.
+%To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-CROWN \cite{crown}.
 All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds.
@@
 The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.
-For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in Crown).
+For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in CROWN).
 Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).

### 2025-04-28 ATVA 2025/valabstraction.tex
fix a mistake
update
update some words

@@
 \begin{align}
-	\ReLU(x) = \max (0,x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} 
+	\ReLU(x) = \max (0,x) \leq \hat{x} \leq \UB \frac{x-\LB}{\UB-\LB} 
 	\label{eq:deeppoly}
@@
 At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a complete (but inefficient) method. 
-Consider an unstable neuron $n$, whose value $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$.
+Consider an unstable neuron $n$, whose value $x \in [\LB,\UB]$ with $\LB<0<\UB$.
 The value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one 
-integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
+integer (actually even binary) variable $a$ valued in $\{0,1\}$, using constants $\UB,\LB$ with 4 constraints \cite{MILP}:
 
 \vspace{-0.4cm}
-\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\UB(n) \cdot (1-a)
+\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \UB \cdot a \quad \wedge \quad \hat{x} \leq x-\LB \cdot (1-a)
 \label{eq11}
@@
 
-For all $x \in [\LB(n),\UB(n)] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
+For all $x \in [\LB,\UB] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
 The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$.
@@
 \begin{proof}
-	Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$.
+	Consider an unstable neuron $n$, that is $\LB < 0 < \UB$.
 The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediately equivalent with $\hat{x} \geq \ReLU(x)$.
@@
 We now show that the three constraints 
-$\hat{x} \leq \UB(n) \cdot a \, \wedge \, \hat{x} \leq x-\LB(n) \cdot (1-a) \, \wedge \, a \in [0,1]$ translates into $\hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)}$. 
-We have $\hat{x}$ is upper bounded by $max_{a \in [0,1]} (min(\UB(n) \cdot a, x - \LB(n) (1-a)))$, and this bound can be reached.
-Furthermore, using standard function analysis tools (derivative...), we can show that the function $a \mapsto \min(\UB(n) \cdot a, x - \LB(n) (1-a))$ attains its maximum when $\UB(n) \cdot a = x - \LB(n) (1-a)$, leading to the equation $(\UB(n) - \LB(n)) a = x - \LB(n)$ and consequently $a = \frac{x - \LB(n)}{\UB(n)-\LB(n)}$.
-This results in an upper bound $\hat{x} \leq \UB(n) \frac{x - \LB(n)}{\UB(n)-\LB(n)}$, which can be reached, hence the equivalence.
+$\hat{x} \leq \UB \cdot a \, \wedge \, \hat{x} \leq x-\LB \cdot (1-a) \, \wedge \, a \in [0,1]$ translates into $\hat{x} \leq \UB \frac{x-\LB}{\UB-\LB}$. 
+We have $\hat{x}$ is upper bounded by $max_{a \in [0,1]} (min(\UB \cdot a, x - \LB (1-a)))$, and this bound can be reached.
+Furthermore, using standard function analysis tools (derivative...), we can show that the function $a \mapsto \min(\UB \cdot a, x - \LB (1-a))$ attains its maximum when $\UB \cdot a = x - \LB (1-a)$, leading to the equation $(\UB - \LB) a = x - \LB$ and consequently $a = \frac{x - \LB}{\UB-\LB}$.
+This results in an upper bound $\hat{x} \leq \UB \frac{x - \LB}{\UB-\LB}$, which can be reached, hence the equivalence.
 \qed
@@
 This a priori hurts accuracy.
-To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB(n),\UB(n)$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
+To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB,\UB$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
 So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.
@@
 
-	\KwOutput{Bounds $[\LB(n),\UB(n)]$ for every node $n$}
+	\KwOutput{Bounds $[\LB,\UB]$ for every node $n$}
 

### 2025-04-28 ATVA 2025/relatedwork.tex
small update

@@
 The workaround, e.g.
-in {\em refined} $\alpha,\beta$-CROWN, was to precompute very accurate bounds for the first few neurons of the DNN using a complete full MILP encoding, and then rely on a BaB call from that refined bounds (more complex calls to full MIPL and BaB).
+in {\em refined} $\alpha,\beta$-CROWN, was to precompute very accurate bounds for the first few neurons of the DNN using a complete full MILP encoding, and then rely on a BaB call from that refined bounds (more complex calls to full MILP and BaB).
 Non-surprisingly, this very slow technique does not scale but to small DNNs (max 2000 ReLU activation functions).

### 2025-05-06 lipschitz/Lipschitz_a_proposition.tex
update

--- 2025-04-23 ATVA 2025/Paper_noProof.tex
@@
 
-	\maketitle
-	\linenumbers
-	\begin{abstract}
-		Branch and Bound (BaB) is considered as the most efficient technique for DNN verification: it can propagate bounds over numerous branches, 
-		to accurately approximate values a given neuron can take even in large DNNs, enabling formal verification of properties such as local robustness.
-Nevertheless, the number of branches grows {\em exponentially} with important variables, and there are complex instances for which the number of branches is too large to handle even using BaB.
-In these cases, providing more time to BaB is not efficient, as the number of branches treated is {\em linear} with the time-out.
-Such cases arise with verification-agnostic DNNs, non-local properties (e.g.
-global robustness, computing Lipschitz bound), etc.
-		%The fact that pure BaB is not that efficient for e.g.
-verification-agnostic (even very small) DNNs has been witnessed before.
-The workaround, e.g.
-in {\em refined} $\alpha,\beta$-CROWN, was to precompute very accurate bounds for the first few neurons of the DNN using a complete full MILP encoding.
-Non-surprisingly, this very slow technique does not scale but to small DNNs.
-		%Indeed, one of its implementation, $\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best trade-off between accuracy and runtime. 
-		%VNNcomp however is focusing on relatively easy verification problems.
+\begin{definition}
+	Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
 
-        To handle complex instances, we revisit a divide-and-conquer approach to break down the complexity: instead of few complex BaB calls, we rely on many small {\em partial} MILP calls.
-The crucial step is to select very few but very important ReLUs to treat using (costly) binary variables.
-The previous attempts were suboptimal in that respect.
-To select these important ReLU variables, we propose a novel {\em solution-aware} ReLU scoring (SAS), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU scoring (GS) functions.
-		We compare them theoretically as well as experimentally: SAS is more efficient to {\em select} a set of variables, while GS is more efficient at {\em ordering} this selection.
-		%Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em branch} within this selection.
-		Compared with previous attempts, SAS reduces the number of binary variables by around 6 times, while maintaining the same level of accuracy.
-Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CNNs with 20 000 nodes.
+	For a number $\epsilon > 0$, $K_\epsilon$ is the smallest number such that for any $d\geq \epsilon$, any input $x,y$.
+	\begin{align*}
+	 |x-y| \leq d \implies |f(x)-f(y)| \leq dK_\epsilon 
+	\end{align*}
+\end{definition}
 
-		%a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem.
-The novelty resides in the use of the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input.
-		%This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation.
+\begin{proposition}
 
-	\end{abstract}
+	Continue above definition.
+Suppose for a number $\epsilon$ we have $K_\epsilon$, then for any number $ \epsilon N\leq d\leq \epsilon(N+1)$ for an integer $N \geq 1$, we have that $$K_d \leq K_\epsilon\frac{N+1}{N}.$$
+\end{proposition}
 
-\section{Introduction}
+\begin{proof}
+By assumption, $d \in [\epsilon N  , \epsilon(N+1)]$ .
 
-\input{introduction}
-%
-\input{relatedwork}
+	For any $x, y$ that $|x-y| \leq d$, we have $|x-y| \leq \epsilon(N+1) $.
+Then we can divide the line segment between $x, y$ into $N+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{N+1} = y$ such that $|x_i-x_{i+1}| \leq \epsilon$.
+Then we can apply the definition of $K_\epsilon$ for each pieces.
 
-\section{Notations and Preliminaries}
-
-In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{crown}.
-To simplify the notations, we restrict the presentation to feed-forward, 
-fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $\ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-$\ReLU(x)=x$ for $x \geq 0$ and $\ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
-
-%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
-
-%\subsection{Neural Network and Verification}
-
-% testtesttesttest
-An $\ell$-layer DNN is provided by $\ell$ weight matrices 
-$\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
-and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
-We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
-$d_0$ the input dimension, and $d_\ell$ the output dimension.
-
-Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
+	Therefore, we have that, for any two inputs $x,y$:
 		\begin{align*}
-	\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
-	\hat{\boldsymbol{z}}^{i} = \ReLU({\boldsymbol{z}}^i).
+		|x-y| \leq d \implies |f(x)-f(y)| \leq  \epsilon(N+1) K_\epsilon
 	\end{align*}
 
-The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
-$\boldsymbol{z}$ is called pre-activation values, 
-and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
-A path $\pi$ is a sequence $\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight of $\pi$ is
-$weight(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
+	Hence by the definition, we have that $$K_d <= \dfrac{\epsilon(N+1) K_\epsilon }{d}<=\dfrac{\epsilon(N+1)K_\epsilon}{\epsilon N} = K_\epsilon\frac{N+1}{N}.$$
 
-\iffalse
-and the $i$-th hidden layer is a vector in $\mathbb{R}^{d_i}$, 
-and the output layer is a vector in $\mathbb{R}^{d'}$ or a scale. 
-The weights, bias and activation functions decide propagate the from previous to the next layer. In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight 
-$\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, 
-the bias is a vector $\vb^i$ in $\mathbb{R}^{d_i}$, and the activation function 
-is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, 
-then the value of $i$-th layer is computed by: 
-\begin{align*}
-	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \vb^i\\
-	\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)).
-\end{align*} The vector $\hat{\boldsymbol{z}}$ is called post-activation values, and $\boldsymbol{z}$ is called pre-activation values, and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer.
-In our style, we also call neurons \emph{nodes} and use $a,b,c,d$ to denote them.
-We use $W_{ab}$ to denote the weight from neuron $b$ to $a$.
-We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
-\fi
+	This is what we want to show.
 
-\medskip
+\end{proof}
 
-Concerning the verification problem, we focus on the well studied local-robustness question.
-Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
-Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
-\begin{align*}
-	\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
-	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
-\end{align*}
+\begin{corollary}
+	\begin{enumerate}
+		\item Continue the definition.
+Suppose for a number $\epsilon$ we have $K_\epsilon$, then for any number $d\geq \epsilon N$ for an integer $N \geq 1$, we have that $$K_d \leq K_\epsilon\frac{N+1}{N}.$$
 
-\iffalse
-In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
-	\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
-\end{align*}
+		\item 	If we care about $\epsilon$ and compute the Lipschitz constant of $0.5 \epsilon$ and get $K$, then we can use Lipschizt constant $\leq K\frac{2+1}{2}$ for general larger $\epsilon$.
+		\item 	Similarly, if we compute Lipschitz constant for any $\epsilon$ and get $K$, then we can use Lipschitz constant $K\frac{1+1}{1}$ for any larger $\epsilon$.
+	\end{enumerate}
+\end{corollary}
 
-If so, the question of verification can turn to the following optimization question: \begin{align*}
-	\min f(\boldsymbol{x}) \ s.t. {\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ b^i\\
-	\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)), \boldsymbol{x}\in\mathcal{D}.
-\end{align*}
+\begin{proof}
+	All three are simply application of the proposition.
+\end{proof}
 
-In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$.
+\begin{proposition}
 
-In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\vx,\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
-\fi
-
-\input{valabstraction}
-
-\input{Comparison}
-
-\input{formula}
-
-\input{experiments}
-%\input{Lipschitz}
-
-\section{Conclusion}
-In this paper, we developed a novel solution-aware scoring ({\sf SAS}) function to select few ReLU nodes to consider with binary variables to compute accurately bounds in DNNs. 
-The solution awareness allows SAS to compute an accurate score for each ReLU, which enables partial MILP to be very efficient, necessitating $\approx6$x less binary variables than previous proposals \cite{DivideAndSlide} for the same accuracy, and $\approx2$x less than {\sf GS} scoring adapted from FSB \cite{FSB}.
-As the worst-case complexity is exponential in the number of binary variables, this has large implication in terms of scalability to larger DNNs, making it possible to verify accurately quite large DNNs such as CNN-B-Adv with 2M parameters.
-
-While $\alpha,\beta$-Crown is known to be extremely efficient to solve easier verification instances, we exhibit many cases (complex instances) where its worst-case exponential complexity in the number of ReLUs is tangible, with unfavorable scaling (Table \ref{table_beta}).
-Resorting to Hybrid MILP, a divide-and-conquer approach \cite{DivideAndSlide}, revisited thanks to the very efficient {\sf SAS}, revealed to be a much better trade-off than augmenting $\alpha,\beta$-Crown time-outs, with $8\%$ to $40\%$ less undecided images at ISO runtime.
-Currently, for hard instances, there is no alternative to partial MILP, other methods being $>10$ times slower.
-
-This opens up interesting future research directions, to verify global \cite{lipshitz}, \cite{sensing} rather than local (robustness) properties, which need very accurate methodology
-and give rise to hard instances as the range of each neuron is no more local to a narrow neighborhood (and thus almost all ReLUs are unstable, with both modes possible).
-
-%Last, we adapted BaB-SR \cite{BaB} and FSB \cite{FSB} as global scoring (GS) functions. 
-%We compared GS with SAS both theoretically and experimentally with solution-aware scoring: While GS are not as efficient as SAS for ReLU {\em selection} (2x more binary variables needed), GS functions generate {\em static order} more adapted to every branch of a BaB process.
-
-%{\bf Reproducibility Statement:} We tested twice outlier results to confirm them, making sure of reproducibility on the given hardware.
-Precise details on the settings used are provided in the appendix.
-Additional results {\color{blue}(e.g.
-ablation studies)} are also provided in the appendix.
-Tested DNNs as well as MNIST and CIFAR10 DataSet are freely available.
-The source code of Hybrid MILP will be provided on GitHub after acceptance (needing Gurobi as well as $\alpha,\beta$-Crown).
-
-\newpage
-
-\bibliography{references}
-\bibliographystyle{plain}
-
-\bigskip
-
-\appendix
-
-\input{proofsb}
+\end{proposition}
 

### 2025-05-06 lipschitz/Lipschitz_a_proposition.tex
update the proposition

@@
 
-	For a number $\epsilon > 0$, $K_\epsilon$ is the smallest number such that for any $d\geq \epsilon$, any input $x,y$.
-	\begin{align*}
+	For a number $\epsilon > 0$, $K_\epsilon$ is the smallest number such that for any $d\geq \epsilon$, any inputs $x,y$:\begin{align*}
 	 |x-y| \leq d \implies |f(x)-f(y)| \leq dK_\epsilon 
@@
 
-		\item 	If we care about $\epsilon$ and compute the Lipschitz constant of $0.5 \epsilon$ and get $K$, then we can use Lipschizt constant $\leq K\frac{2+1}{2}$ for general larger $\epsilon$.
-		\item 	Similarly, if we compute Lipschitz constant for any $\epsilon$ and get $K$, then we can use Lipschitz constant $K\frac{1+1}{1}$ for any larger $\epsilon$.
+		\item Therefore, for any inputs $x,y$ that $|x-y|\geq N\epsilon$ for an integer $N\geq 1$, \begin{align*}
+			\dfrac{|f(x)-f(y)|}{|x-y|}\leq K_\epsilon\frac{N+1}{N}
+		\end{align*}
+
+		\item 	If for a number $\epsilon$, we get the value of $K_{0.5 \epsilon}$, then we will have a Lipschizt constant $\frac{2+1}{2}K_{0.5 \epsilon}$ working for $|x-y|\geq\epsilon$.
+
+		\item 	Similarly, if for a number $\epsilon$, we get the value of $K_{\epsilon}$, then we will have a Lipschizt constant $\frac{1+1}{1}K_{\epsilon}$ working for $|x-y|\geq\epsilon$.
 	\end{enumerate}
@@
 \begin{proposition}
+	Continue the definition. Suppose we have a number $K$ that for any $d$ in one of $\epsilon, 1.1\epsilon, 1.2\epsilon, \cdots, 1.9\epsilon$, we have $K_d\leq K$.
 
+	Then, for any two inputs $x,y$,if $|x-y|\geq \epsilon$, then $\dfrac{|f(x)-f(y)|}{|x-y|}\leq 1.1 K$. 
 \end{proposition}
 
+\begin{proof}
+	Let $x,y$ be any two inputs, we need to show that if $|x-y|\geq \epsilon$, then $\dfrac{|f(x)-f(y)|}{|x-y|}\leq 1.1 K$.
+
+	If $|x-y| \geq 10\epsilon$, this is clear by above corollary part 2. So we need to consider $\epsilon\leq |x-y|< 10\epsilon$.
+
+	For any inputs $x,y$ that $\epsilon\leq|x-y|< 10\epsilon$, there exists a sum $x_1+x_2+\cdots+x_n$ by numbers from (allowing repetitions) $\epsilon, 1.1\epsilon, 1.2\epsilon, \cdots, 1.9\epsilon$ such that \begin{align*}
+	 \epsilon \leq x_1+x_2+\cdots+x_n -0.1\epsilon \leq |x-y| \leq x_1+x_2+\cdots+x_n
+	\end{align*}
+
+	By assumption, divide the line segment from $x$ to $y$ into pieces according to $x_1, x_2,\cdots,x_n$, then we will have $$|f(x)-f(y)|\leq Kx_1+Kx_2+\cdots+Kx_n.$$
+
+	Hence,\begin{align*}
+		\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Kx_1+Kx_2+\cdots+Kx_n}{x_1+x_2+\cdots+x_n -0.1\epsilon}\\
+		& = K\cdot( 1+  \dfrac{0.1\epsilon}{x_1+x_2+\cdots+x_n -0.1\epsilon})\\
+		& \leq K\cdot( 1+  \dfrac{0.1\epsilon}{\epsilon})\\
+		& \leq 1.1 K
+	\end{align*}
+
+\end{proof}
+
 \end{document}

### 2025-05-06 lipschitz/Lipitschz.tex
update the draft

@@
 \documentclass{llncs}
+\usepackage{hyperref}
+\usepackage{url}
 \pagestyle{plain}
-
+\usepackage{threeparttable}
+\input{math_commands.tex}
 %\usepackage[latin9]{inputenc}
@@
 \usepackage{calc}
+\usepackage{array}
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
 \usetikzlibrary{positioning, arrows.meta,calc}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\LP}{{\textrm{LP}}}
+\newcommand{\Improve}{\mathrm{Improve}}
+\newcommand{\Utility}{\mathrm{SAS}}
+\newcommand{\Sol}{\mathrm{Sol}}
+\newcommand{\sol}{\mathrm{sol}}
 
@@
 
-\newcommand{\toolname}{\CMP}
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+\newcommand{\toolname}{Hybrid MILP}
 
-%\usepackage{amsmath, amsthm, amssymb, amsfonts}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{corollary}{Corollary}
-%\theoremstyle{definition}
-%\newtheorem{definition}{Definition}
-
-\newcommand{\ReLU}{\mathrm{ReLU}}
-
-\title{Liptschiz}
+\title{Solution-aware vs global ReLU selection: \\
+	partial MILP strikes back for DNN verification}
 \date{}
@@
 	\maketitle
-
+	\linenumbers
 	\begin{abstract}
-
-		Local robustness is bad. We study a more global notion, lipsitcz constant.
-
+		TODO
 	\end{abstract}
@@
 
-	TO DO.
-
 	\section{Notations and Preliminaries}
 
-	In this paper, we will use lower case latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
-	capitalized bold for matrices $\boldsymbol{W}$, similar to notations in \cite{prima,crown}.
+	In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
+	capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{crown}.
 	To simplify the notations, we restrict the presentation to feed-forward, 
-	fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-	$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
+	fully connected ReLU Deep Neural Networks (DNN for short), where the activation function is $\ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
+	$\ReLU(x)=x$ for $x \geq 0$ and $\ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
 
@@
 	\begin{align*}
-		{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i\\
-		\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
+		\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
+		\hat{\boldsymbol{z}}^{i} = \ReLU({\boldsymbol{z}}^i).
 	\end{align*}
@@
 Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
-A path $\pi$ is a sequence $\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight of $\pi$ is
-	$weight(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.
+
+	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
+
+	%Concerning the verification problem, we focus on the well studied local-robustness question.
+Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
+	%Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
+	%\begin{align*}
+	%	\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
+	%	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
+	%\end{align*}
+
+	\section{pMILP and Local robustness}
+
+	\subsection{MILP and LP encodings for DNNs}
+
+	Mixed Integer Linear Programming (MILP) value abstraction is a complete (but inefficient) method. 
+	For an unstable neuron $n$ that its value $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$, the value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one 
+	integer variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
+
+	\vspace{-0.4cm}
+	\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \UB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\LB(n) \cdot (1-a)
+		\label{eq11}
+	\end{equation}
+
+	%For all $x \in [\LB(n),\UB(n)] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
+The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$.
+This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
+However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous integer variables and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
+
+	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
+As solving LP instances is polynomial time, this optimization is significantly more efficient.
+However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
+This approach is termed the {\em LP abstraction}.
+We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:
+
+	\subsection{partial MILP}
+
+	We will use {\em partial MILP} (pMILP for short, see \cite{DivideAndSlide}) to get trade-offs between accuracy and runtime. Here, we extract the explanation from paper CITE.
+
+	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the partial MILP based on $X$ to compute neuron $n$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding, where variable $a$ is:
+	\begin{itemize}
+		\item binary for neurons in $X$ (exact encoding of the ReLU),
+		\item linear for neurons not in $X$ (linear relaxation).
+	\end{itemize}
+	We will denote above case by MILP$_X$ or $\mathcal{M}_X$. Informally, we say that a node is opened if it is in $X$.
+
+	If $X$ covers all unstable neurons, then MILP$_X$ is exact. But then the time cost may be very large (exponential growth).
+
+	To reduce the runtime, we will limit the size of subset $X$.
+This a priori hurts accuracy.
+To recover some of this accuracy, we use an iterative approach: computing lower and upper bounds $\LB,\UB$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
+
+	\subsection{SAS}
+
+	In pMILP, to decide the set $X$, we introduce the method {\em Solution-Aware Scoring} (SAS)
+	to evaluate accurately how opening a ReLU impacts the accuracy. Again, here we use the definition from paper CITE. For details and explanation, see CITE.
+
+	Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
+For each node $n<z$, we denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$: $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$; and we denote $(\sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$ a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
+Moreover,  we define the function
+	$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
+	accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
+	compared with using only LP.
+
+	First, SAS will call solvers to compute the LP model to get a solution, which is reasonably fast as there is no binary variables.
+
+	Next, for a neuron $b$ on the layer before layer $\ell_z$, we define:
+
+	\vspace{-0.4cm}
+	$$\Utility\_\max\nolimits^z(b) = W_{bz} \times (\sol(\hat{b})- \ReLU(\sol(b)))$$
+	\vspace{-0.4cm}
+
+	And for a neuron $a$ two layers before $\ell_z$, 
+	$b$ denoting neurons in the layer $\ell$ just before $\ell_z$.
+	Recall the rate $r(b)=\frac{\max(0,\UB(b))}{\max(0,\UB(b))-\min(0,\LB(b))} \in [0,1]$.
+	We define:
+
+	\begin{flalign*}
+		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})&&\\
+		\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})&&\\	
+	\end{flalign*}
+
+	\vspace{-1.2cm}
+
+	\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
+		r(b)\Delta(b), & for $W_{bz} > 0$ \\
+		\max(\Delta(b),-\sol(b)), & for $W_{bz} < 0$ and $\sol(b)\geq0$\\
+		\max(0,\Delta(b)+\sol(b)), & for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
+	\end{subnumcases}
+
+	\begin{flalign*}
+		\Utility\_\max\nolimits^z(a) &= \Delta(z) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})&&
+	\end{flalign*}
+
+	From paper CITE, we know that $\Utility$ is a safe overapproximation in the sense of following proposition:
+
+	\begin{proposition}
+		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
+	\end{proposition}
+
+	\section{Global robustness and Lipschitz constant}
+
+	\subsection{MILP and LP encodings for DNNs}
+
+	At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method (albeit much slower than DeepPoly). 
+	Consider an unstable neuron $n \in[\alpha,\beta]$.
+The value $x$ of $\ReLU(n)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints \cite{MILP}:
+	\vspace{-0.1cm}
+	\begin{align*}
+		\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)
+	\end{align*}
+
+	It can be shown that for all $x \in [\alpha,\beta] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$.
+Here, $a$ is 0 if $x < 0$, 1 if $x>0$, and can be either if $x=0$~\cite{MILP}.
+This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help in certifying a given input.
+However, for networks with hundreds of nodes or more, the resulting MILP formulation will contain numerous integer variables and generally cannot be solved efficiently.
+
+	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in ${0,1}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
+As solving LP instances is polynomial time, this optimization is significantly more efficient.
+However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
+This approach is termed the {\em LP abstraction}
+
+	The following proposition shows that the LP abstraction refines the DeepPoly abstraction. 
+	The difference between the LP and the DeepPoly abstractions is that LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.
+
+	\begin{proposition}
+		\label{LP}
+		Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
+		1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
+		\begin{align}
+			& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1]  \label{eq:lp}\\
+			&\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha} \label{eq:deeppoly}
+		\end{align} 
+	\end{proposition}
+
+	\begin{proof}
+		We need to show that the two upper bound constraints in Eq~\ref{eq:lp} is equivalent to the upper bound in Eq~\ref{eq:deeppoly}.
+To this end, we focus on the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
+We have $\hat{x}$ in Eq~\ref{eq:lp} is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
+Furthermore,
+		The function $\min(\beta \cdot a, x - \alpha (1-a))$ attains its maximum when $\beta \cdot a = x - \alpha (1-a)$, leading to the equation $(\beta - \alpha) a = x - \alpha$ and consequently $a = \frac{x - \alpha}{\beta-\alpha}$.
+This results in an upper bound of $\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$ \qed
+	\end{proof}
+
+	\subsubsection*{Constraints for $\gamma$}
+
+	We could get the following constraints for $\gamma$, using $y_i$ and $\hat{y}_i$ to denote the $x_i-x_i'$ and $\hat{x}_i-\hat{x}_i'$:\begin{align*}
+		\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y}_i \geq y_i - a \gamma_i\\
+		\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y}_i \leq y_i + (1-a) \gamma_i,
+	\end{align*} where $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
+
+	The following plot will show the above constraints:
+
+	\begin{tikzpicture}
+		\begin{axis}[
+			xlabel={$y_i$},
+			ylabel={$\hat{y}_i$},
+			xmin=-2, xmax=2,
+			ymin=-2, ymax=2,
+			axis lines=center,
+			samples=100, 
+			unit vector ratio=1 1 1, scale=1, xtick   = {-2,2},
+			xticklabels = {$-\gamma_i$,$\gamma_i$},
+			yticklabels = {},
+			]
+			\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
+			\addplot[blue, thick] {0};
+
+			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
+			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
+
+			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
+			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
+		\end{axis}
+	\end{tikzpicture}
+
+	The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
+
+	We can use the following extra constraints (besides 4 constraints about $\hat{x}_i'=\ReLU(x_i')$) to build this relation:
+
+	\begin{align*}
+		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
+		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
+	\end{align*}
+
+	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
+
+	A more direct way to establish the constraints is as follows: \begin{align*}
+		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
+		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
+		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
+		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
+		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
+		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
+	\end{align*}The following two plots show its shape:
 
 	\iffalse
-	and the $i$-th hidden layer is a vector in $\mathbb{R}^{d_i}$, 
-	and the output layer is a vector in $\mathbb{R}^{d'}$ or a scale. 
-	The weights, bias and activation functions decide propagate the from previous to the next layer. In formula, from layer $l_{i-1}$ to layer $l_{i}$, the weight 
-	$\boldsymbol{W}^i$ is matrix of $d_i\times d_{i-1}$, 
-	the bias is a vector $\vb^i$ in $\mathbb{R}^{d_i}$, and the activation function 
-	is $\sigma$, then  if the $i-1$-th layer is $\hat{\boldsymbol{z}}^{(i-1)}$, 
-	then the value of $i$-th layer is computed by: 
-	\begin{align*}
-		{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \vb^i\\
-		\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)).
-	\end{align*} The vector $\hat{\boldsymbol{z}}$ is called post-activation values, and $\boldsymbol{z}$ is called pre-activation values, and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer.
-In our style, we also call neurons \emph{nodes} and use $a,b,c,d$ to denote them.
-We use $W_{ab}$ to denote the weight from neuron $b$ to $a$.
-We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.
+	\hspace*{-10ex}
+	\begin{tikzpicture}
+		\begin{axis}[	axis on top, xlabel = \(x'_i\),
+			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
+			set layers=default,
+			xmax = 4, xmin = -4,
+			ymax = 1, ymin = -1,		
+			zmax = 1, zmin = -1,
+			unit vector ratio=1 1 1, scale=3,
+			view={60}{50}, ytick   = {-1,0,1},
+			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
+			xticklabels = {$0$}, ztick   = {-1,0,1},
+			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
+			]
+			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
+			coordinates {
+				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
+			};
+
+			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
+			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
+			};
+
+			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
+			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
+			};
+
+			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
+			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
+			};
+
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
+			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
+
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
+			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
+
+		\end{axis}
+	\end{tikzpicture}
 	\fi
 
-	\medskip
+	\hspace*{-15ex}
+	\begin{tikzpicture}
+		\begin{axis}[	axis on top, xlabel = \(x'_i\),
+			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
+			set layers=default,
+			xmax = 4, xmin = -4,
+			ymax = 1, ymin = -1,		
+			zmax = 1, zmin = -1,
+			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
+			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
+			xticklabels = {$0$}, ztick   = {-1,0,1},
+			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
+			view={35}{14},
+			]
+			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
+			coordinates {
+				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
+			};
 
-	Concerning the verification problem, we focus on the well studied local-robustness question.
-Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
-	Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
-	\begin{align*}
-		\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
-		argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
-	\end{align*}
+			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
+			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
+			};
 
-	\iffalse
-	In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
-		\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
-	\end{align*}
+			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
+			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
+			};
 
-	If so, the question of verification can turn to the following optimization question: \begin{align*}
-		\min f(\boldsymbol{x}) \ s.t. {\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ b^i\\
-		\hat{\boldsymbol{z}}^{i}(n) &= \sigma({\boldsymbol{z}}^i(n)), \boldsymbol{x}\in\mathcal{D}.
-	\end{align*}
+			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
+			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
+			};
 
-	In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$.
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
+			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
 
-	In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\vx,\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
-	\fi
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
+			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
 
-\input{valabstraction}
+		\end{axis}
+	\end{tikzpicture}
 
@@
 
-\newpage
+	TODO
 
+	\bibliography{references}
 	\bibliographystyle{plain}
-\bibliography{references}
+
+	\bigskip
+
+	\appendix
 
 \end{document}
-
-\section{Ranking of Compensating Pairs}
-
-In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.
-
-Based on No Diamond Theorem, for a target node, in its MILP model, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node.
-However, in practice, this is still too expensive because we will still need to open too many nodes.
-So we can only choose a limited number of compensating pairs and nodes.
-This is by setting a parameter $O$ such that the process only choose at most $O$ many nodes to open.
-Therefore, in this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.
-
-Basically, we do the process of open nodes chosen for one target node each time, that is, receive one target node (and other data) as input each time.
-But in principle, we can develop a method receive more than one nodes as input.
-But in our experiences, this does not work well.
-
-This process is not the unique method but the most natural way to choose open nodes. We introduce it in three steps from the simplest case to more complex case.
-
-\subsubsection*{Value of a pair}
-
-For a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.
-
-\subsection*{Case: Source node fixed}
-
-The simplest case is when we only consider compensating pairs with a fixed source node.
-
-In this case, the process is very simple: enumerate all compensating pairs, and then sort them by their values.
-Finally, from the first to the last compensating pair, pick all unstable nodes in its two paths except the target and source nodes into the list of open nodes, until $O$ many open nodes.
-
-%\subsubsection*{Sort all paths by values}
-%
-%The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.
-%
-%Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.
-%
-%\subsubsection*{Sort pairs by values}
-%
-%The second step is to sort all pairs by their values.
-Enumerate paths from the positive group and the negative group one by one and put the pairs obtained into a new list of pairs.
-Then sort all pair by their values from largest to the smallest: recall that the value of a pair $\langle P_1,P_2\rangle$ is $\min(|V_1|,|V_2|)$.
-%
-%\subsubsection*{Choosing nodes}
-%
-%The third step is to choose nodes from the list of pairs.
-According to the sorted list of pairs, enumerate pair one by one; for each pair, pick the nodes unstable in the two paths except the source and target node into the open node list.
-Repeat this process until $O$ nodes chosen or reach the end of the list.
-%
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-%
-
-\subsection*{Case: Source nodes in one layer}
-
-The more general case is when the source node can be any node in a fixed layer. In this case, the process is very similar to previous case, except the value of a pair.
-
-In this case, for a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, its value is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.
-
-%\subsubsection*{Pseudocode}
-%
-%The following needs a chart of pseudo-code
-%
-%\vspace*{1ex}
-%
-%1. Enumerate all path from the fixed source node to the target node. 
-%
-%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
-%
-%3. Divide all paths into two group: positive paths and negative paths.
-%
-%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
-%
-%5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.
-%
-%6.
-From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node.
-%
-%7. Repeat 6 until choosing sufficiently many nodes.
-
-\subsection*{Case: Source nodes in different layers}
-
-The general case is that when the location of source nodes can be in different layers.
-This case is much more complex, because the scale level of values of paths from different layers are very different: usually a weight will be very small since every layer has a large number of nodes, therefore values of longer paths are products of more small numbers, and is definitely much smaller.
-If we sort all compensating pairs from different layers directly, then a very long initial segment of this list will be occupied by compensating pairs with the shortest length.
-Therefore, we need use some scale factors when comparing values of compensating pairs of different length.
-
-In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before).
-We will dynamically adjust the values during the process of node chosen.
-In text, the process of node chosen for length 3 plus length 4 is as follows:
-
-\vspace*{1ex}
-
-1. Generate the two lists of pairs sorted by their values for source nodes in 2 layers before the target node and 3 layers before separately as in the previous case.
-
-2.
-Enumerate pair from two lists one by one by their values and pick nodes as previous case.
-When comparing the values between pairs of length 4 and pairs of length 3, multiply the numbers of nodes in 1 layer before to the value of pair of length 4.
-
-In formula, when the target node is in layer $L$, for a pair $P_3$ of length 3 with value $V_3$ and a pair $P_4$ of length 4 with value $V_4$, if we have chosen $N$ nodes in layer $L-1$.
-Then the adjusted values for $P_3$ and $P_4$ are: $$V_3, N\cdot V_4.$$ Then we pick the next pair by the adjust value in two lists.
-
-3. Repeat 2 until choosing sufficiently many nodes.
-
-\vspace*{1ex}
-
-The pseudo-code is as follows ():
-
-\begin{algorithm}
-\caption{Process for length 3 + length 4}
-\KwData{Sorted lists of length 3 + length 4}
-\KwResult{Open node list}
-
-Let $N = 0$ be the number of Chosen length 4 pair.
-
-\While{len(Open node) $<O$}{
-	Pick the first element $P_3$ in the list of length 3\;
-
-	Let $V_3$ be the value of $P_3$\;
-
-	Pick the first element $P_4$ in the list of length 4\;
-
-	Let $V_4$ be the value of $P_4$\;
-
-	\If{$V_3 > V_4 \cdot N$}{
-		Add nodes in $P_3$ into Open list\;
-		Number of Chosen lentgh pair $N$ += 1\; 
-	}
-	\Else{
-		Add nodes in $P_4$ into Open list\;
-	}
-}
-\end{algorithm}
-
-\end{document}

### 2025-05-06 lipschitz/Lipitschz.tex
update

@@
 \newcommand{\vW}{\boldsymbol{W}}
-
 \newcommand{\val}{{\textrm{value}}}
@@
 \newcommand{\sol}{\mathrm{sol}}
-
 \newcommand{\UB}{\mathrm{UB}}
@@
 \usepackage{amsmath, amssymb, amsfonts}
-
 \newcommand{\ReLU}{\mathrm{ReLU}}
-
 \newcommand{\CMP}{{\textrm{CMP}}\ }
-
 \newcommand{\fix}{\marginpar{FIX}}
@@
 
-\title{Solution-aware vs global ReLU selection: \\
-	partial MILP strikes back for DNN verification}
+\title{Global case}
 \date{}
@@
 	\section{Global robustness and Lipschitz constant}
-
-	\subsection{MILP and LP encodings for DNNs}
-
-	At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction, which is a priori a complete method (albeit much slower than DeepPoly). 
-	Consider an unstable neuron $n \in[\alpha,\beta]$.
-The value $x$ of $\ReLU(n)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints \cite{MILP}:
-	\vspace{-0.1cm}
-	\begin{align*}
-		\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a)
-	\end{align*}
-
-	It can be shown that for all $x \in [\alpha,\beta] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$.
-Here, $a$ is 0 if $x < 0$, 1 if $x>0$, and can be either if $x=0$~\cite{MILP}.
-This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help in certifying a given input.
-However, for networks with hundreds of nodes or more, the resulting MILP formulation will contain numerous integer variables and generally cannot be solved efficiently.
-
-	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in ${0,1}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
-As solving LP instances is polynomial time, this optimization is significantly more efficient.
-However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
-This approach is termed the {\em LP abstraction}
-
-	The following proposition shows that the LP abstraction refines the DeepPoly abstraction. 
-	The difference between the LP and the DeepPoly abstractions is that LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $ReLU(x) \geq 0$ and $ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.
-
-	\begin{proposition}
-		\label{LP}
-		Given $x \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
-		1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
-		\begin{align}
-			& \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \beta \cdot a \quad \wedge \quad \hat{x} \leq x-\alpha \cdot (1-a), \, a \in [0,1]  \label{eq:lp}\\
-			&\hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0 \quad \wedge \quad \hat{x} \leq \beta \frac{x-\alpha}{\beta-\alpha} \label{eq:deeppoly}
-		\end{align} 
-	\end{proposition}
-
-	\begin{proof}
-		We need to show that the two upper bound constraints in Eq~\ref{eq:lp} is equivalent to the upper bound in Eq~\ref{eq:deeppoly}.
-To this end, we focus on the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed.
-We have $\hat{x}$ in Eq~\ref{eq:lp} is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached.
-Furthermore,
-		The function $\min(\beta \cdot a, x - \alpha (1-a))$ attains its maximum when $\beta \cdot a = x - \alpha (1-a)$, leading to the equation $(\beta - \alpha) a = x - \alpha$ and consequently $a = \frac{x - \alpha}{\beta-\alpha}$.
-This results in an upper bound of $\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$ \qed
-	\end{proof}
 

### 2025-05-06 lipschitz/Lipitschz.tex
update

@@
 Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.
+Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
 
-	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
+	Concerning the verification problem, we focus on the global-robustness question.
+Global robustness asks to determine how the output of a neural network will be affected under a certain kind of small perturbations to any possible input.
+In this view, Lipschitz continuity is a good characterization of global robustness.
 
-	%Concerning the verification problem, we focus on the well studied local-robustness question.
-Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input.
-	%Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
-	%\begin{align*}
-	%	\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
-	%	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
-	%\end{align*}
+	Recall the definition of Lipschitz continuity:
+	 under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
+	\begin{align*}
+		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
+	\end{align*}
+
+	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:
+
+	\begin{align*}
+		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
+		&  |\boldsymbol{x}-\boldsymbol{y}| < \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\epsilon)
+	\end{align*}
 

### 2025-05-06 lipschitz/Lipitschz.tex
update

@@
 	\end{align*} 
-
 	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:
-
 	\begin{align*}
@@
 	\end{align*} 
+	In terms of the code, it is compute an optimization question respect to a certain number $\epsilon$:	\begin{align*}
+			\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
+	\end{align*} We can use this maximum value to estimate the Lipschitz constant.
 

### 2025-05-06 lipschitz/Lipitschz.tex
update

@@
 	\end{align*} 
-	In terms of the code, it is compute an optimization question respect to a certain number $\epsilon$:	\begin{align*}
+	In terms of the code, it is compute an optimization question respect to a certain number $\epsilon$:	\begin{align}\label{global_robustness}
 			\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
-	\end{align*} We can use this maximum value to estimate the Lipschitz constant.
+	\end{align} We can use this maximum value to estimate the Lipschitz constant.
 
-	\section{pMILP and Local robustness}
+	\section{Local robustness and pMILP}
 
 	\subsection{MILP and LP encodings for DNNs}
+
+	First we introduce some concepts for local robustness question.
 
@@
 
-	\section{Global robustness and Lipschitz constant}
+	\section{Modeling for global robustness}
 
-	\subsubsection*{Constraints for $\gamma$}
+	We can modify the MILP model for local robustness to compute the question of global robustness \ref{global_robustness}.
+
+	\subsubsection{Cloned model}
+
+	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra constraints:
+
+	\subsubsection{Simplified models}
+
+	Constraints for $\gamma$
 

### 2025-05-06 lipschitz/Lipitschz.tex
update

@@
 This approach is termed the {\em LP abstraction}.
-We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:
+We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.
 
@@
 
-	\subsubsection{Cloned model}
+	\subsection{Cloned model}
 
-	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra constraints:
+	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra variables and constraints:
 
-	\subsubsection{Simplified models}
+	\subsection{Simplified models}
 

### 2025-05-07 lipschitz/Lipitschz.tex
update

@@
 
+	The global structure is as follows, using Gurobi as an example:
+	\begin{enumerate}
+		\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable. 
+		\item For each pre-activation node in a hidden layer and each output node, set linear constraints relating them to the post-activation or input nodes they connect to.
+		\item Between pre- and post- activation nodes, set the MILP constraint described above.
+	\end{enumerate}
 	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.

### 2025-05-07 lipschitz/Lipitschz.tex
update

--- 2025-05-06 lipschitz/Lipitschz.tex
@@
 
+	The global structure is as follows, using Gurobi as an example:
+	\begin{enumerate}
+		\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable. 
+		\item Set constraints for input nodes.
+		\item For each pre-activation node in a hidden layer (and each output node), set linear constraints relating them to the post-activation or input nodes in the previous layer they connect to.
+		\item Between pre- and post- activation nodes, set the MILP constraint described above.
+	\end{enumerate} We use $\mathcal{M}$ to denote the whole MILP model.
+In practice, we may only consider the network up to a certain hidden layer.
+In that case, the pre-activation nodes of that layer serve as the output nodes of the model $\mathcal{M}$.
+
 	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
@@
 
+	\subsection{Cloned model}
 		We can modify the MILP model for local robustness to compute the question of global robustness \ref{global_robustness}.
 
-	\subsection{Cloned model}
+	The most straight way is to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (including inputs and outputs) with some extra constraints:
 
-	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra variables and constraints:
+	\begin{enumerate}
+		\item Add constraints for input nodes between $\mathcal{M},\mathcal{M}'$ for the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon$.
+
+		\item Set optimization target to be the difference of two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (since we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
+	\end{enumerate}
+
+	This model
 

### 2025-05-07 lipschitz/Lipitschz.tex
update

@@
 
-	This model
+	This large model contains twice as many binary variables as $\mathcal{M}$.
+The computational cost of solving an MILP model is known to grow roughly exponentially with the number of binary variables, hence it will cost much more time.
 
-	\subsection{Simplified models}
+	Therefore we need to relax more binary variables to continue variables, and/or simplify the model.
+
+	\subsection{Simplified model}
+
+	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $\gamma_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then $\gamma_i=x_i-x'_i$.
+
+	Now the constraints for $\gamma$ variables between pre-activation and post-activation is as follows:
 

### 2025-05-07 lipschitz/Lipitschz.tex
update

@@
 
-	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $\gamma_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then $\gamma_i=x_i-x'_i$.
+	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then $y_i=x_i-x'_i$.
 
@@
 
-	Constraints for $\gamma$
+	Let $y_i$ and $\hat{y}_i$ be $x_i-x_i'$ and $\hat{x}_i-\hat{x}_i'$. Then we know the relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
 
-	We could get the following constraints for $\gamma$, using $y_i$ and $\hat{y}_i$ to denote the $x_i-x_i'$ and $\hat{x}_i-\hat{x}_i'$:\begin{align*}
+	Suppose we already know the upper (and lower by symmetry) bound $\gamma_i$ of $y_i$, then
+	we can use the following constraints:\begin{align*}
 		\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y}_i \geq y_i - a \gamma_i\\
 		\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y}_i \leq y_i + (1-a) \gamma_i,
-	\end{align*} where $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.
+	\end{align*} where $a$ is a binary variable.
 
@@
 
-	The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
+	Now we can introduce this simplified model:
+
+\begin{enumerate}
+	\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable $y_i$. 
+	\item Set constraints for input nodes.
+	\item Set linear constraints . In this case, since the meaning of $y_i$ is $x_i-x'_i$, this constraints will not use the bias.
+	\item Between pre- and post- activation nodes, set the MILP constraint described above.
+\end{enumerate}
+
+	The speed of this model is much faster, comparable to the MILP model for local robustness. However, in practice, this model sometimes lose much accuracy.
+
+	\subsection{Another simplified model}
+
+	The second simplified model is more complex than the first.
 

### 2025-05-07 lipschitz 2025/Lipitschz_old.tex
create a new folder

--- 2024-01-27 Paper/Paper_noProof.tex
@@
 \usepackage{graphicx}
+\usepackage{tikz}
+\usepackage{tikz-3dplot}
 \usepackage{subcaption}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \newcommand{\vx}{\boldsymbol{x}}
@@
 	\begin{abstract}
-		Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally that they are correct, with an annual competition to compare them, etc.
-Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN.
-This allows e.g.
-to check local robustness around an input $\vx$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $\vx$.
-In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs.
-While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern verifiers, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.
 
-		In this paper, we analyse efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}.
-Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other.
-It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions.
-Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes.
-These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.
+		Local robustness is bad. We study a more global notion, lipsitcz constant.
+
 	\end{abstract}
@@
 
-	\input{introduction}
+	TO DO.
 
-	\section{Background}
+	\section{Notations and Preliminaries}
 
@@
 
-\input{comppaths}
-
-\input{experiments}
-
-\vspace{-0.2cm}
 \section{Conclusion}
-\vspace{-0.2cm}
-
-In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs.
-We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs.
-We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.
-
-Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$.
-Last, we experimentally showed that choosing $Z$ covering {\em few} paths with the strongest compensations, results in very good accuracy, and runtime which can be favourable in some (but not all) cases.
-This proves that compensating strength is a promising novel concept which should be further studied to improve DNN verification.
-We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.
 

### 2025-05-08 lipschitz 2025/Lipitschz.tex
update

--- 2025-05-07 lipschitz/Lipitschz.tex
@@
 
+	\section{Global robustness and Lipschitz constant}
+
 	Recall the definition of Lipschitz continuity:
@@
 	\end{align*} 
-	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:
+	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\varepsilon$:
 	\begin{align*}
-		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
-		&  |\boldsymbol{x}-\boldsymbol{y}| < \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\epsilon)
+		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \varepsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
+		&  |\boldsymbol{x}-\boldsymbol{y}| < \varepsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\varepsilon)
 	\end{align*} 
-	In terms of the code, it is compute an optimization question respect to a certain number $\epsilon$:	\begin{align}\label{global_robustness}
-			\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
+	In terms of the code, it is compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
+		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
 	\end{align} We can use this maximum value to estimate the Lipschitz constant.
 
-	\section{Local robustness and pMILP}
+		\begin{definition}[$\varepsilon$-diff bound]
+		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
+
+		For a number $\varepsilon\in\mathbb{R}$, an $\varepsilon$-diff bound $D_\varepsilon$ is a number such that for any inputs $x,y$: \begin{align*}
+			|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D_\varepsilon \cdot \varepsilon
+		\end{align*}
+
+	\end{definition}
+
+	\begin{definition}[Lipschitz above $\varepsilon$ constant ]
+		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
+
+		For a number $\varepsilon\in\mathbb{R}$, a Lipschitz above $\varepsilon$ constant  $K_\varepsilon$,  is a number such that for any inputs $x,y$: \begin{align*}
+			|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot |x-y|\\
+			|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot \varepsilon\\
+		\end{align*}
+
+	\end{definition}
+
+	\begin{proposition}
+
+		Suppose $D$ is an $\varepsilon$-diff bound for $f(x)$. Then for any $N\in\mathbb{Z}^+$, $D\frac{N+1}{N}$ is a Lipschitz about $N\varepsilon$ constant.
+
+		In formula, for any two inputs $x,y$, if \begin{align*}
+			|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D \cdot \varepsilon,
+		\end{align*} then 	 \begin{align*}
+			|x-y|\geq N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
+			|x-y|<N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot N\varepsilon\\
+		\end{align*}
+	\end{proposition}
+
+	\begin{proof} We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
+
+		The first case, $|x-y|\geq N\varepsilon$.
+Then we assume $|x-y| \in [M\varepsilon ,  (M+1)\varepsilon]$ for another integer $M\geq N$.
+Then we can divide the line segment between $x, y$ into $M+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{M+1} = y$ such that $|x_i-x_{i+1}| \leq \varepsilon$ and apply the definition of $\varepsilon$-diff bound $D$ for each pieces:\begin{align*}
+			|f(x)-f(y)| &= |f(x_{M+1})-f(x_M)+\cdots+f(x_1)-f(x_0)|\\
+			&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
+			&\leq D\varepsilon + \cdots +D\varepsilon \\
+			&= (M+1)D\varepsilon
+		\end{align*}
+		Hence\begin{align*}
+			|f(x)-f(y)| &\leq (M+1)D\varepsilon \\
+			&\leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
+			&= D\cdot\frac{M+1}{M} |x-y|\\
+			&\leq   D\cdot\frac{N+1}{N} |x-y|
+		\end{align*}
+		The second case, $|x-y|< N\varepsilon$.
+Similarly we can divide the line segment between $x, y$ into $N$ pieces and then $|f(x)-f(y)|\leq D N\varepsilon\leq |f(x)-f(y)|\leq D \frac{N+1}{N} N\varepsilon$.
+
+		This is what we want to show.
+	\end{proof}
+
+	\begin{proposition}
+		For any $N\in\mathbb{Z}^+$, suppose for any $a$ in $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$, $D$ is an $a$-diff bound for $f(x)$.
+
+		Then $D\frac{N+1}{N}$ is a Lipschitz about $\varepsilon$ constant:\begin{align*}
+			|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
+			|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot \varepsilon\\
+		\end{align*}
+	\end{proposition}
+
+	\begin{proof}
+		We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
+
+		For the case that $|x-y|<\varepsilon$, this is trivial by definition.
+
+		For the case that $|x-y|\geq \varepsilon$, there exists a sum $x_1+x_2+\cdots+x_n$ by numbers from (allowing repetitions) $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$ such that \begin{align*}
+			\varepsilon \leq x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon \leq |x-y| \leq x_1+x_2+\cdots+x_n
+		\end{align*}
+		By assumption, divide the line segment from $x$ to $y$ into pieces according to $x_1, x_2,\cdots,x_n$, then we will have $$|f(x)-f(y)|\leq Dx_1+Dx_2+\cdots+Dx_n.$$
+
+		Hence,\begin{align*}
+			\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
+			& = D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon})\\
+			& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})\\
+			& = D \frac{N+1}{N} 
+		\end{align*}
+
+	\end{proof}
+
+	\section{pMILP for local robustness}
 
@@
 	\begin{enumerate}
-		\item Add constraints for input nodes between $\mathcal{M},\mathcal{M}'$ for the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon$.
+		\item Add constraints for input nodes between $\mathcal{M},\mathcal{M}'$ for the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon$.
 

### 2025-05-08 lipschitz 2025/Lipitschz.tex
update

@@
 	\end{align*} 
-	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\varepsilon$:
-	\begin{align*}
-		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \varepsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
-		&  |\boldsymbol{x}-\boldsymbol{y}| < \varepsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\varepsilon)
-	\end{align*} 
-	In terms of the code, it is compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
+	In our practice of global robustness of computation, we will compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
 		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
-	\end{align} We can use this maximum value to estimate the Lipschitz constant.
+	\end{align} And this will lead to the following definition
 
@@
 	\end{definition}
+
+	From $\varepsilon$-diff bound, we cannot directly obtain a Lipschitz bound for the function, but we can get the following weaker bound:
 

### 2025-05-08 lipschitz 2025/Lipitschz.tex
update

@@
 	\end{align*} 
-	In our practice of global robustness of computation, we will compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
+	In our practice, when we need global robustness, we will compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
 		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
@@
 		\end{align*}
-		Hence\begin{align*}
+		Hence,\begin{align*}
 			|f(x)-f(y)| &\leq (M+1)D\varepsilon \\
@@
 
+	In practice, Lipschitz above $\varepsilon$ constant is already sufficient to use: this is because in most cases, we care about the absolute difference when the input changes, not the ratio.
+Therefore, the computation of $\varepsilon$-diff bound can satisfy our aim.
+
+	Moreover, we have the following proposition connecting $\varepsilon$-diff bound and Lipschitz above $\varepsilon$ constant.
+
 	\begin{proposition}
@@
 	\end{proposition}
-
 	\begin{proof}

### 2025-05-09 lipschitz 2025/Lipitschz.tex
update

--- 2025-05-08 lipschitz 2025/Lipitschz.tex
@@
 			&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
-			&\leq D\varepsilon + \cdots +D\varepsilon \\
-			&= (M+1)D\varepsilon
+			&\leq D\varepsilon + \cdots +D\varepsilon = (M+1)D\varepsilon
 		\end{align*}
-		Hence\begin{align*}
-			|f(x)-f(y)| &\leq (M+1)D\varepsilon \\
-			&\leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
-			&= D\cdot\frac{M+1}{M} |x-y|\\
-			&\leq   D\cdot\frac{N+1}{N} |x-y|
+		Hence,\begin{align*}
+			|f(x)-f(y)| &\leq (M+1)D\varepsilon \leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
+			&= D\cdot\frac{M+1}{M} |x-y|	\leq   D\cdot\frac{N+1}{N} |x-y|		
 		\end{align*}
@@
 	\end{proof}
+
+	In practice, Lipschitz above $\varepsilon$ constant is already sufficient, since in most cases we care about the absolute difference under input perturbations, not the ratio.
+By combining the above proposition, the computation of $\varepsilon$-diff bound can satisfy our aim.
+
+	Moreover, we have one more proposition connecting $\varepsilon$-diff bound and Lipschitz above $\varepsilon$ constant.
 
@@
 			\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
-			& = D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon})\\
-			& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})\\
-			& = D \frac{N+1}{N} 
+			& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})= D \frac{N+1}{N}\\
 		\end{align*}

### 2025-05-09 lipschitz 2025/Lipitschz.tex
update

@@
 		\begin{definition}[$\varepsilon$-diff bound]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
+		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
 
@@
 
-	\begin{definition}[Lipschitz above $\varepsilon$ constant ]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
+	\begin{definition}[Lipschitz above $\varepsilon$ constant]
+		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
 
@@
 
-		In formula, for any two inputs $x,y$, if \begin{align*}
+		That is, for any two inputs $x,y$, if \begin{align*}
 			|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D \cdot \varepsilon,
@@
 
-		This is what we want to show.
+		This ends the proof.
 	\end{proof}
@@
 		\end{align*}
-
+		This ends the proof.
 	\end{proof}
@@
 
-	\subsection{Cloned model}
-		We can modify the MILP model for local robustness to compute the question of global robustness \ref{global_robustness}.
-
-	The most straight way is to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (including inputs and outputs) with some extra constraints:
-
+	\subsection{Using Two Identical Models}
+	The most straightforward way is to use two identical MILP models, that is to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (including inputs and outputs) with extra constraints:
 	\begin{enumerate}
-		\item Add constraints for input nodes between $\mathcal{M},\mathcal{M}'$ for the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon$.
-
-		\item Set optimization target to be the difference of two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (since we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
+		\item Add constraints for connecting input nodes $\mathcal{M},\mathcal{M}'$ to meet the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon$.
+		\item Set the optimization objective as the difference between two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (because we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
 	\end{enumerate}
-
 	This large model contains twice as many binary variables as $\mathcal{M}$.
-The computational cost of solving an MILP model is known to grow roughly exponentially with the number of binary variables, hence it will cost much more time.
+The computational cost of solving an MILP model grows roughly exponentially with the number of binary variables, hence it will cost much more time.
 
@@
 
-	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then $y_i=x_i-x'_i$.
-
-	Now the constraints for $\gamma$ variables between pre-activation and post-activation is as follows:
-
-	Let $y_i$ and $\hat{y}_i$ be $x_i-x_i'$ and $\hat{x}_i-\hat{x}_i'$. Then we know the relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
+	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
+The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
 
@@
 
-	The following plot will show the above constraints:
+	The following plot shows the above constraints:
 
-	\begin{tikzpicture}
+	\hspace*{10ex}\begin{tikzpicture}
 		\begin{axis}[
@@
 
-	Now we can introduce this simplified model:
-
+   Using these constraints, we can sketch the simplified model:
 \begin{enumerate}

### 2025-05-09 lipschitz 2025/Lipitschz.tex
update

@@
 
-	Suppose we already know the upper (and lower by symmetry) bound $\gamma_i$ of $y_i$, then
-	we can use the following constraints:\begin{align*}
+	Given  $\gamma_i$ be the upper bound of $y_i$, then constraints for $\hat{y}_i$ are the follows:\begin{align*}
 		\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y}_i \geq y_i - a \gamma_i\\
@@
 
-	The following plot shows the above constraints:
+	The following plot illustrates the constraints described above.
 
@@
 
-   Using these constraints, we can sketch the simplified model:
+   Based on above constraints, we can sketch this simplified model:
 \begin{enumerate}
@@
 
-	The speed of this model is much faster, comparable to the MILP model for local robustness. However, in practice, this model sometimes lose much accuracy.
+	The advantage of this simplified model is that it only contains the number of binary variables as MILP model for local robustness, hence the running speed of this is much faster comparing to the previous one.
+The cost is a loss of accuracy when the time is infinite.
 
-	\subsection{Another simplified model}
+	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
+
+	\subsection{Strength of the simplified model}
 

### 2025-05-09 lipschitz 2025/Lipitschz.tex
update

@@
 
-	The advantage of this simplified model is that it only contains the number of binary variables as MILP model for local robustness, hence the running speed of this is much faster comparing to the previous one.
+	The key point is that, we can relax all other binary variables for $\hat{x}_i = \ReLU(x_i)$ and $\hat{x}'_i = \ReLU(x'_i)$.
+	Then the simplified model is that it only contains the number of binary variables as MILP model for local robustness, hence the running speed of this is much faster comparing to the previous one.
 The cost is a loss of accuracy when the time is infinite.
@@
 
-	\subsection{Strength of the simplified model}
+	\subsection{Improvement of the simplified model}
 
-	The second simplified model is more complex than the first.
+	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed.
 
-	We can use the following extra constraints (besides 4 constraints about $\hat{x}_i'=\ReLU(x_i')$) to build this relation:
+%	The exact constraints for $$ \begin{align*}
+%		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
+%		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
+%	\end{align*} 
+%	
+%	
+%	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
 
-	\begin{align*}
-		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
-	\end{align*}
-
-	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
-
-	A more direct way to establish the constraints is as follows: \begin{align*}
+	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ are the follows: \begin{align*}
 		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
@@
 		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-	\end{align*}The following two plots show its shape:
+	\end{align*}Here, $a,a'$ are the binary variables, and $a'$ also play the role binary for $\hat{x}'_i=\ReLU(x'_i)$.
 
-	\iffalse
+	The following plot illustrates the constraints described above.
+
 	\hspace*{-10ex}
-	\begin{tikzpicture}
-		\begin{axis}[	axis on top, xlabel = \(x'_i\),
-			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
-			set layers=default,
-			xmax = 4, xmin = -4,
-			ymax = 1, ymin = -1,		
-			zmax = 1, zmin = -1,
-			unit vector ratio=1 1 1, scale=3,
-			view={60}{50}, ytick   = {-1,0,1},
-			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
-			xticklabels = {$0$}, ztick   = {-1,0,1},
-			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
-			]
-			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates {
-				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
-			};
-
-			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
-			};
-
-			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
-			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
-			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
-
-		\end{axis}
-	\end{tikzpicture}
-	\fi
-
-	\hspace*{-15ex}
 	\begin{tikzpicture}

### 2025-05-13 lipschitz 2025/Lipitschz.tex
update

@@
 
+However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which leads us to find another modeling approaches.
+
 	\subsection{Simplified model}
@@
 	\subsection{Improvement of the simplified model}
-
 	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed.
+(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
 
@@
 
-	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ are the follows: \begin{align*}
+	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with$\hat{x}'_i=\ReLU(x'_i)$) are the follows: \begin{align*}
 		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
@@
 		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-	\end{align*}Here, $a,a'$ are the binary variables, and $a'$ also play the role binary for $\hat{x}'_i=\ReLU(x'_i)$.
+	\end{align*}Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$.
+The constraints for $x_i$s are not necessary, or at least their MILP constraints can be relaxed to LP without reducing accuracy.
 
@@
 
+	A variant of the above model is to distinguish the binary variables $a'$s in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$, and relax all the latter ones.
+
+	\section{Experiments}
+
 	\section{Conclusion}

### 2025-05-14 lipschitz 2025/Lipitschz.tex
update

@@
 
-	\subsection{Improvement of the simplified model}
+	\subsection{Improving the Accuracy of the Simplified Model}
 	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed.
@@
 
+	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
+Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
+
 	A variant of the above model is to distinguish the binary variables $a'$s in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$, and relax all the latter ones.

### 2025-05-14 lipschitz 2025/Lipitschz.tex
update

@@
 
-	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with$\hat{x}'_i=\ReLU(x'_i)$) are the follows: \begin{align*}
-		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
-		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
-		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-	\end{align*}Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$.
+	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with$\hat{x}'_i=\ReLU(x'_i)$) are the follows:
+	\begin{align*}
+		& \begin{aligned}
+			y_i + x'_i &\leq a\beta_i        &\quad\quad
+			y_i + x'_i &\geq (1-a)\alpha_i \\
+			x'_i       &\leq a'\beta_i       & 
+			x'_i       &\geq (1-a')\alpha_i \\
+			\hat{y}_i  &\leq a\gamma_i       &
+			\hat{y}_i  &\geq -a'\gamma_i \\
+			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
+			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
+			\hat{y}_i  &\leq -x'_i + a\beta_i &
+			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
+			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
+			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
+		\end{aligned}
+	\end{align*} Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$.
 The constraints for $x_i$s are not necessary, or at least their MILP constraints can be relaxed to LP without reducing accuracy.
+
+%	\begin{align*}
+%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
+%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
+%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
+%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
+%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
+%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
+%	\end{align*}
 

### 2025-05-14 lipschitz 2025/Lipitschz.tex
update

@@
 
-	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with$\hat{x}'_i=\ReLU(x'_i)$) are the follows:
+	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
+	the accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with $\hat{x}'_i=\ReLU(x'_i)$) are the follows:
 	\begin{align*}
@@
 
-	\section{Experiments}
+	\section{Experimental Evaluation}
+
+	We implemented our code in Python 3.8.
+	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
+
+	We will do experiments on two networks for MNIST dataset and another physical model.
+
+	Among two MNIST $5\times 100$  full-connected DNN, one is a normally trained neural network and another is for trained for adversarial robustness.
+We call them MNIST $5\times100$-normal and MNIST $5\times 100$-DiffAI.
+They have the same structure: 5 hidden layer with 100 neurons each, 10 outputs and 784 inputs.
+
+	The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.
+
+	\subsection{Comparison of different modelings}
+
+	\subsection{Comparison of different scoring algorithms}
 

### 2025-05-14 lipschitz 2025/Lipitschz.tex
update

@@
 
-	\subsection{Simplified model}
+	\subsection{A Simplified model}
 
-	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
+	To avoid above problem, we introduce a simplified model that is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
 The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
@@
 	Given  $\gamma_i$ be the upper bound of $y_i$, then constraints for $\hat{y}_i$ are the follows:\begin{align*}
-		\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y}_i \geq y_i - a \gamma_i\\
-		\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y}_i \leq y_i + (1-a) \gamma_i,
+	\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
+	\hat{y}_i &\geq (a-1) \gamma_i           &\quad \hat{y}_i &\leq y_i + (1-a) \gamma_i
 	\end{align*} where $a$ is a binary variable.
@@
 	We will do experiments on two networks for MNIST dataset and another physical model.
-
-	Among two MNIST $5\times 100$  full-connected DNN, one is a normally trained neural network and another is for trained for adversarial robustness.
-We call them MNIST $5\times100$-normal and MNIST $5\times 100$-DiffAI.
-They have the same structure: 5 hidden layer with 100 neurons each, 10 outputs and 784 inputs.
-
+Two MNIST have the same structure.
+They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons.
+One of them is a normally trained neural network and another is for trained for adversarial robustness.
+We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI.
+As the name shows MNIST $5\times 100$-DiffAI has a better robustness.
 The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.

### 2025-05-20 lipschitz 2025/Lipitschz.tex
update

@@
 	\subsection{Using Two Identical Models}
-	The most straightforward way is to use two identical MILP models, that is to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (including inputs and outputs) with extra constraints:
+	The most straightforward way is to use two identical MILP models, i.e., to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (and their own constraints) plus some extra constraints:
 	\begin{enumerate}
@@
 	This large model contains twice as many binary variables as $\mathcal{M}$.
-The computational cost of solving an MILP model grows roughly exponentially with the number of binary variables, hence it will cost much more time.
+The computational cost of solving an MILP model grows roughly exponentially with the number of binary variables, and hence it will cost much more time.
 
-	Therefore we need to relax more binary variables to continue variables, and/or simplify the model.
-
-However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which leads us to find another modeling approaches.
+We may relax some constraints (by changing binary variables to continuous variables) as in the case of local robustness.
+However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which motivates us to explore other modeling approaches.
 
@@
 
-	To avoid above problem, we introduce a simplified model that is to use one variable to the difference of each two variables, which we use $y_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
+	To avoid above problem, we introduce a simplified model that is to use one variable $y_i$ to represent the difference of each two variables: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
 The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
 
-	Given  $\gamma_i$ be the upper bound of $y_i$, then constraints for $\hat{y}_i$ are the follows:\begin{align*}
+	Given  $\gamma_i$ be the upper bound of $y_i$, the constraints for $\hat{y}_i$ are the follows:\begin{align*}
 	\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
@@
 
-	The key point is that, we can relax all other binary variables for $\hat{x}_i = \ReLU(x_i)$ and $\hat{x}'_i = \ReLU(x'_i)$.
-	Then the simplified model is that it only contains the number of binary variables as MILP model for local robustness, hence the running speed of this is much faster comparing to the previous one.
-The cost is a loss of accuracy when the time is infinite.
+	The key point is that, although this model sets 3 variables (and their binary variables) for each node in the network, only $y_i$  contributes to the final results, and we can ignore $x_i,x_i'$ (and their binary variables) during the optimization.
 
-	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
+	As a result, we can relax the binary variables used to $\hat{x}_i = \ReLU(x_i)$ and $\hat{x}'_i = \ReLU(x'_i)$.
 
+	Now the simplified model contains the same number of binary variables as the MILP model for local robustness.
+Hence this model runs much faster compared to the previous one.
+The trade-off is lower accuracy compared to the first model under unlimited time.
+In practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
+
+%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
+%	
 	\subsection{Improving the Accuracy of the Simplified Model}

### 2025-05-20 lipschitz 2025/Lipitschz.tex
update

@@
 	\subsection{Improving the Accuracy of the Simplified Model}
-	We can improve the accuracy of the simplified model by simply changing the constraints, which is a trade-off between accuracy and speed.
-(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
+	We can improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.
+
+%	(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
 
@@
 	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
-	the accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with $\hat{x}'_i=\ReLU(x'_i)$) are the follows:
+	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
 	\begin{align*}
@@
 		\end{aligned}
-	\end{align*} Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$.
-The constraints for $x_i$s are not necessary, or at least their MILP constraints can be relaxed to LP without reducing accuracy.
+	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
+
+	Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
 

### 2025-05-21 lipschitz 2025/Lipitschz.tex
update

@@
 
-	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
+	In practice, when we relax the constraints for a node, we will convert $a_i$ and $a_i'$ to continuous variables together.
+In principle, we can also choose to change  only one of those two binary variables.
+
+%	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
 Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
 
-	A variant of the above model is to distinguish the binary variables $a'$s in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$, and relax all the latter ones.
+	A special relaxation approach of this model is to treat the binary variables $a'$ appearing in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$ as distinct variables, and relax only the latter.
 

### 2025-05-21 lipschitz 2025/Lipitschz.tex
update

@@
 
+	One major disadvantage of this model is that the solution obtained through optimization may not be valid-i.e., the output computed by the network on the optimized inputs may not equal the output value in the solution.
+Nevertheless, it is meaningful to compute the upper bound.
+
 %	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
@@
 	\subsection{Improving the Accuracy of the Simplified Model}
-	We can improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.
+	We can remove the disadvantage and improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.
 
@@
 
+	This approach has a similar disadvantage as the model in previous section :the output computed by the network on the optimized inputs may not equal the output value in the solution.
+Similarly, it is meaningful to compute the upper bound using this approach.
+
 	\section{Experimental Evaluation}

### 2025-05-21 lipschitz 2025/Lipitschz.tex
update

@@
 
-	This approach has a similar disadvantage as the model in previous section :the output computed by the network on the optimized inputs may not equal the output value in the solution.
+	This approach has a similar disadvantage as the model in the previous section: the output computed by the network on the optimized inputs may not equal the output value in the solution.
 Similarly, it is meaningful to compute the upper bound using this approach.

### 2025-05-22 lipschitz 2025/introduction.tex
update

--- 2025-04-28 ATVA 2025/introduction.tex
@@
 We will thus compare mainly with $\alpha,\beta$-CROWN experiments as gold standard in the following\footnote{GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-CROWN on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us}.
-
-\begin{table}[t!]
-	\centering
-	\begin{tabular}{||l|c|c|c||c|c|c||}
-		\hline
-		Network & nbr & Accuracy & Upper  & $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
-		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
-		MNIST 5$\times$100 & 500 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
-		$\epsilon = 0.026$ & ReLU & &  & 6.9s &  18.9s &  1026s  \\  \hline
-		MNIST 5$\times$200 & 1000 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
-		$\epsilon = 0.015$ & ReLU & &  & 6.5s &  16.6s &  930s  \\  \hline
-		MNIST 8$\times$100 & 800 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
-		$\epsilon = 0.026$ & ReLU &  &  & 7.2s &  20.1s &  930s  \\  \hline
-		MNIST 8$\times$200 & 1600 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
-		$\epsilon = 0.015$ & ReLU & &  & 6.8s &  18.2s &  1083s  \\  \hline
-		MNIST 6$\times$500 & 3000 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
-		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
-		CIFAR CNN-B--Adv &  16634  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
-		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
-		CIFAR ResNet &   107496  & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-		$\epsilon = 8/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
-	\end{tabular}
-	\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
-The 6 first DNNs are complex instances.
-The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
-	\vspace{-0.5cm}}
-	\label{table_beta}
-\end{table}
-
-$\alpha,\beta$-CROWN, as well as BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete},
-rely on Branch and Bound technique (BaB), which call BaB once per output neuron (few calls).
-In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities.
-For easy instances, BaB is highly efficient as all branches can be pruned early.
-However, BaB methods hit a complexity barrier when verifying more complex instances, due to an overwhelming number of branches (exponential in the height of branches that cannot be pruned as they need too many variables to branch over).
-This can be clearly witnessed on the verification-agnostic \cite{SDPFI} DNNs of Table \ref{table_beta} (6 first DNNs), where vastly enlarging the time-out only enables to verify few more \% of images, leaving a large proportion ($20\%-50\%$) of images undecided despite the large runtime.
-As argued in \cite{SDPFI}, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks, and such cases should be treated as well as DNNs specifically trained to be easy to verify, e.g.
-using \cite{TrainingforVerification}.
-Verification-agnostic are the simplest instances to demonstrate the scaling behavior of BaB on complex instances using standard local robustness implementations.
-Other complex instances include solving non-local properties, e.g.
-global robustness computed through Lipschitz bound \cite{lipshitz}, etc.
-The bottom line is that one cannot expect to have only easy instances to verify.
-It is important to notice that the number of activation functions of the DNN is a poor indicator of the hardness of the instance, e.g.
-$5 \times 100$ with 500 ReLUs is far more complex to certify ($50\%$ undecided images) than 100 times bigger ResNet ($0\%$ undecided images), see Table \ref{table_beta}.
-
-%Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-CROWN \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neigbhour with a different decision.
-One issue is however that easy instances are trained specifically to be easier to verify e.g.
-using DiffAI \cite{DiffAI} PGD \cite{PGD}, which can impact the accuracy of the network, i.e.
-answering correctly to an unperturbed input.
-For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct {\color{blue}\cite{prima}} (the other $71\%$ are thus not  tested).
-While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
-very hard verification instances into hard verification instances.
-Also, verification questions intrinsically harder than local robustness, such as bounding on Lipschitz constants globally or asking several specification at once, makes the instance particularly harder.
-Last, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks.
-The bottom line is, one cannot expect only {\em easy} verification instances: {\em hard} verification instances need to be explored as well.
-
-%In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.
-In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely MNIST 5$\times$100.
-We first dwelve into the scaling of $\alpha,\beta$-CROWN, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
-Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).
-
-\begin{table}[t!]
-	\centering
-	\begin{tabular}{||l|c|c||c|c|c||}
-		\hline
-		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum &  Full MILP  \\ \hline
-		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $49\%$ & 40 \%    \\
-		$\epsilon = 0.026$ & &  &6200s &  4995s & 6100s
-		  \\  \hline
-		%  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $46\%$ & 37 \%    \\
-		%  TO=2000s & &  & 1250s  & 1194s & 1466s \\  \hline	
-	\end{tabular}
-\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
-%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
-\vspace{-0.5cm}}
-\label{table_complete}
-\end{table}
-
-Other standard non-BaB methods such as Marabou, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-CROWN, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image.
-It appeared pointless to test these verifiers on larger networks.
-
-%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}.
-
-%\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks,
-
-%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as
-
-%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
-
-%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs; It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
-The high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
-These tools are thus sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though it actually is, because of bounds inaccuracies.
-	%To dig further into their incompleteness, we first remark that 
-	%Notice that complete methods exist \cite{Reluplex,katz2019marabou,SDPFI}, but they time-out on hard instances.
-In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-CROWN \cite{crown}.
-%As a starting point, we sought to understand properties of DNNs that make them hard to verify.
-
-%Our key finding is a new notion of {\em compensations}, that explains why bounds are inaccurate.
-Formally, a {\em compensating pair of paths} $(\pi,\pi')$ between neurons $a$ and $b)$ is such that $w < 0 < w'$ for $w,w'$ the products of weights seen along $\pi$ and $\pi'$ respectively.
-Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $(w+w') weight(a)$ by $\pi$ and $\pi'$.
-As $w,w'$ have opposite signs, they will compensate (partly) each other.
-The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
-However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which the efficient tools try to avoid because it is very time-consuming (combinatorial explosion as the problem is NP-hard \cite{Reluplex}).
-%; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
-
-Our main contributions address the challenges to verify {\em complex} instances efficiently, as current methods are not appropriate to verify such instances:
-\begin{enumerate}
-	%\item  Our first contribution studies the {\em LP relaxation} of the exact MILP encoding of ReLUs.
-{\color{blue} We establish in Proposition \ref{LP} its equivalence with the so-called "triangular abstraction"}.
-
-	\item We revisit the idea from \cite{DivideAndSlide} to consider small calls to a partial MILP (pMILP) solver, i.e.
-with few binary variables encoding few ReLU functions exactly (other being encoded with more efficient but less accurate linear variables), to compute bounds for each neuron inductively, hence many ($O(n)$, the number of neuron) small calls, with a complexity exponential only in the few binary variables (Section 4).
-Compared to the few (one per output neuron) complex call to BaB, each with a worst case complexity exponential in the number of neurons of the DNN (which is far from the actual complexity thanks to pruning branches in BaB - but which can be too large as we shown in the 6 first DNNs of Table \ref{table_beta}).
-Two questions arise: how to select few very important ReLUs?, and is computing the bounds of intermediate neurons a good trade-off compared with the theoretical loss of accuracy due to selecting only some binary ReLUs?
-Answer to these questions were not looking very promising judging by previous attempt \cite{DivideAndSlide}, which was using a simple selection heuristic of nodes in the previous layer only.
-
-	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, {\em global scoring ({\sf GS})} functions to choose important ReLUs (Section 5).
-These revealed to be much more accurate than the simple heuristic in
-	\cite{DivideAndSlide}.
-However, we also uncover that the {\em improvement function} that {\sf GS} tries to approximate depends heavily upon the mode of the ReLU function, and as this mode is unavailable to {\sf GS}, there are many cases in which {\sf GS} is far from the improvement (with both under or over-approximation of the improvement function).
-
-	\item We thus designed a {\em novel solution-aware scoring ({\sf SAS})}, which uses the solution of a unique LP call, that provides the mode to consider (Section 6).
-Theoretically, we show that {\sf SAS} is always an over-approximation of the improvement (Proposition \ref{prop2}), which implies that a small {\sf SAS} value implies that the ReLU is unnecessary.
-Experimentally, we further show that {\sf SAS} is very close to the actual improvement, closer than {\sf GS}, and that overall, the accuracy from SAS is significantly better than {\sf GS}.
-Compared with the heuristic in \cite{DivideAndSlide},  {\sf SAS} is much more efficient ($\approx 6$ times less binary variables for same accuracy (Fig.
-\ref{fig_table3}).
-	%We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally (see Table.
-\ref{table.order}).
-
-	\item Compared with many calls using full MILP, where all the ReLUs are encoded as binary variables, {\sf SAS} (and {\sf GS}) encode only a subset of ReLUs as binary and others as linear variables.
-The model in full MILP is fully accurate, while {\sf SAS} (and {\sf GS})
-	are abstractions, and thus much faster to solve. 
-	While full MILP is thus {\em asymptotically} more accurate than {\sf SAS} and {\sf GS}, {\em experimentally}, every reasonable time-out leads to much better practical accuracy of {\sf SAS} (and {\sf GS}) (see Fig.
-\ref{fig555}).
-
-	%	\item {\color{blue} We designed a novel Utility function to choose few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP).
-Specifically, the novelty of Utility resides in the use of the solution to an (efficient LP) solver on the node $z$ we want to bound.
-Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}).
-Because pMILP focuses on the {\em improvement} (binary - linear), it is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})) than previous attempts, which consider the generic {\em sensitivity} to this neuron.
-To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g.
-\cite{BaB,FSB}.}
-
-	\item For the second question, we propose a new verifier, called {\em Hybrid MILP}, invoking first 	$\alpha,\beta$-CROWN with short time-out to settle the easy instances.
-On those ({\em hard}) instances which are neither certified nor falsified, we call pMILP with few neurons encoded as binary variables.
-Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
-It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-CROWN with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance ($46-420$s), Table \ref{table_hybrid}.
-It scales to fairly large networks such as CIFAR-10 CNN-B-Adv \cite{SDPFI}, with more than 2 million parameters.
-%We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
-%KSM: I think this is a distraction in intro, so I suggest moving to later part
-% Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
-This complexity is an upper bound, as e.g.
-Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
-Keeping $K$ reasonably low thus provides an efficient algorithm.
-%By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
-\end{enumerate}
-
-Limitation: We consider DNNs employing the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}, with updated MILP models e.g.
-for maxpool.
-
-\newpage
-
-%   
-% 
-%
-%In this context, application of DNNs in safety critical applications is cautiously envisioned.
-For that to happen at a large scale, hard guarantees should be provided \cite{certification}, through e.g.
-incremental verification \cite{incremental}, so that to avoid dramatic consequences.
-It is the reason for the development of (hard) verification tools since 2016, with now many tools with different trade-offs from exact computation but slow (e.g.
-Marabou \cite{katz2019marabou}/Reluplex\cite{Reluplex}), up to very efficient but also incomplete (e.g.
-ERAN-DeepPoly \cite{deeppoly}).
-To benchmark these tools, a competition has been run since 2019, namely VNNcomp \cite{VNNcomp}.
-The current overall better performing verifier is $\alpha$-$\beta$-CROWN \cite{crown}, a fairly sophisticatedly engineered tool based mainly on "branch and bound" (BaB) \cite{BaB}, and which can scale all the way from complete on smaller DNNs \cite{xu2020fast} up to very efficient on larger DNNs, constantly upgraded, e.g.
-\cite{cutting}.
-%
-%While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, 
-%is it the case that all the images in the neighbourhood are classified in the same way.
-%While some quite large DNNs (e.g.
-ResNet with tens of thousands of neurons) can be verified very efficiently (tens of seconds per input) \cite{crown}, with all inputs either certified robust or an attack on robustness is found; some smaller DNNs (with hundreds of neurons, only using the simpler ReLU activation function) cannot be analysed fully, with $12-20\%$ of inputs where neither of the decisions can be reached (\cite{crown} and Table \ref{tab:example}).
-Actually, DNNs which are trained to be robust (using DiffAI \cite{DiffAI} or PGD \cite{PGD}) are easier to verify, while the DNNs trained in a "natural" way are harder to verify.
-%
-%
-%In this paper, we focus on DNNs trained in a "natural" way,
-%%uncovering what makes the DNNs trained in a natural way so hard to verify (
-%because for "easier" DNNs, adequate methods already exist. 
-%To do so, we analyse the abstraction mechanisms at the heart of several efficient algorithms, namely Eran-DeepPoly \cite{deeppoly}, the Linear Programming approximation \cite{MILP}, PRIMA \cite{prima}, and different versions of ($\alpha$)($\beta$)-CROWN \cite{crown}.
-All these algorithms compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and conclude based on such bounds.
-For instance, if for all image $I'$ in the neighbourhood of image $I$, we have $weight_{I'}(n'-n) < 0$ for $n$ the output neuron corresponding to the expected class, then we know that the DNN is robust in the neighbourhood of image $I$.
-We restrict the formal study to DNNs using only the standard ReLU activation function, although nothing specific prevents the results to be extended to more general architectures.
-We uncover that {\em compensations}
-%(see next paragraph) is the phenomenon creating inaccuracies. We verified experimentally that a DNN trained in a natural way has heavier compensating pairs than DNNs trained in a robust way.
-%
-%Formally, a compensating pair is a pair of paths $(\pi,\pi')$ between a pair of neurons $(a,b)$, such that we have $w < 0 < w'$, for $w,w'$ the products of weight seen along $\pi$ and $\pi'$.
-Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $w \cdot weight(a)$ by $\pi$, while it is loaded with $w' \cdot weight(a)$ by $\pi'$.
-That is, it is loaded by $(w+w') weight(a)$.
-As $w,w'$ have opposite sign, they will compensate (partly) each other.
-The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
-However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which all the efficient tools try to avoid because it is very expansive (could be exponential in the number of such ReLU nodes opened).
-
-%Our first main contribution is to formally show, in Theorem \ref{th1}, that compensation is the sole reason for the inaccuracies as (most) efficient algorithms will compute exact bounds for all neurons if there is no compensating pair of paths at all.
-%While this theorem is theoretically interesting, it is not usable in practice as (almost) all networks have some compensating pairs.
-However, this notion of compensating pairs opens a first interesting idea concerning an exact abstraction of the network using a Mixed Integer Linear Program \cite{MILP}, where the weight of each neuron is a linear variable, and ReLU node may be associated with binary variables (exact encoding) or linear variables (overapproximation).
-While LP tools can scale to thousands of linear variables, MILP encoding can only be solved for a limited number of binary variables.
-This suggests that a simpler encoding could be used for those ReLUs that are not on compensating pairs, as their precise outcome may not be necessary.
-
-%Our second main contribution is to show formally in Theorem \ref{th2}, that 
-%encoding all ReLU nodes on a pair of compensating paths with a binary variable,
-%and using linear relaxation for the other ReLU nodes, will lead to exact bounds for (most) of the algorithms considered.
-This theorem allows to restrict the number of integer variables, and thus to obtain encodings that are faster to solve.
-Practically, however, (almost) all ReLU nodes are on some compensating path, and using this exact restricted MILP encoding will be too time consuming.
-
-%Our third main contribution is more practical, proposing Algorithm \ref{algo1} based on this knowledge that compensating pair of paths are the reason for inaccuracy.
-The idea is thus to use this information to rank the ReLU nodes in terms of importance, and only keep the most important ones as binary variables, and use linear relaxation for the least important ones.
-%%More precisely, the algorithm will, as DeepPoly, consider layers one by one and neurons $b$ %on this layer one by one, selecting the heaviest pairs of compensating paths ending in $b$
-%%and associating these nodes with a binary variable. Then an MILP tool such as Gurobi is used %to compute the lower and upper bound for node $b$. 
-%Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
-This complexity is an upper bound, as e.g.
-Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
-Keeping $K$ reasonably low thus provides an efficient algorithm.
-%By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
-An additional interesting point is that it is extremely easy to parallelize, as all the nodes in the same layer can be run in parallel.
-We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
-
-%KSM: I suggest we move this to experimental evaluation
-%This paper does not focus on producing the most efficient tool, and we did not spend engineering efforts to optimize it.
-The focus is instead on the novel notion of compensation, the associated methodology and its evaluation.
-For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in CROWN).
-Still, evaluation of the methodology versus even the most efficient tools reveals a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification (see Section \ref{Discussion}).

### 2025-06-18 ATVA 2025/Comparison.tex
comp form
final?
update some changes and answers

@@
 
-\begin{figure}[b!]
+	%In case where the bias is 0, then there is no difference between $s_{SR}$ and $s_{FSB}$.
+	Then, ReLU are ranked using these scores, to select the most important unstable ReLUs
+	(with $\LB(u_k) < 0 < \UB(u_k)$).
+	% as stable ReLUs are linear, thus they are already treated correctly.
+
+\noindent {\em Running Example:} Consider Fig. \ref{img:FSB_example}. 
+It has no bias, so $s_{SR}=s_{FSB}$. We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
+The value of $s_{FSB}(a)$ depends on the signs of $c,d$.
+
+We perform a novel comparison between $s_{FSB}(a)$ and $\Delta(z)$, the difference on the {\em maximal bound} computed by pMILP$_X(z)$ when opening the $\ReLU$ of node $a$ ($X=\{a\}$), yielding $\val(\hat{a}) = \ReLU(\val(a))$, versus having $X=\emptyset$, for which
+$\val(\hat{a})$ can be any value in the triangle approximation (Prop. \ref{LP}).
+%, Fig. \ref{triangle})).
+
+The most favorable cases are $c < 0 < d$ and $d < 0 < c$: 
+as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
+Because $cd <0$, both $a$ and $\hat{a}$ need to be minimized by MILP$_X$ in order to maximize the value of $z$. For $X=\emptyset$, the LP approximation (=MILP$_\emptyset$) will thus 
+set $\val(\hat{a}) = \ReLU(\val(a))$ as this is the minimum value in the triangle approximation. Notice that opening $X=\{a\}$ yields the same $\val(\hat{a}) = \ReLU(\val(a))$.
+That is, opening node $a$ is not improving the bound $\UB(z)$, as correctly predicted by the score $s_{FSB}(a)= \Delta(a) = 0$.
+
+\iffalse
+\begin{figure}[t!]
+	\begin{centering}
+	\begin{tikzpicture}[scale=1, >=stealth]
+
+		% Draw axes
+		\draw[->] (-5,0) -- (4,0) node[right] {$a$};
+		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{a}$};
+
+		% Draw ReLU function
+		\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
+		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{a} = \ReLU(a)$};
+		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-5.7,-2)}] {$\hat{a} = r(a) (a-\LB)$};
+
+		% Add labels
+		\draw[dashed] (2.5,0) -- (2.5,2.5) -- (0,2.5); % Optional grid
+		\node[below left] at (0,0) {$0$};
+
+		% Add tick marks
+
+		\foreach \x in {2.5}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\UB$};
+		\foreach \x in {-3}
+		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\LB$};
+
+		\foreach \y in {2.5}
+		\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {$\UB$};
+
+	\end{tikzpicture}
+		\caption{Triangle approximation with $r(a)=\frac{1}{2}$
+		\vspace{-0.3cm}}
+	\label{triangle}
+	\end{centering}
+	\end{figure}
+\fi
+
+Case $c>0,d>0$: we have $s_{FSB}(a)=\frac{cd}{4}$.
+The value of $a,\hat{a},b,\hat{b}$ should be maximized to maximize the value of $z$, because $W_{bz}=d>0$ and $W_{ab}=c>0$. 
+%Each variation of $b$ by $\Delta(b)$ will have an impact $r(b) \cdot \Delta(b)=\frac{\Delta(b)}{2}$ on the value of $\hat{b}$, and thus $\frac{d \Delta(b)}{2}$ on $z$. 
+Now, let us call $val(a)$ the maximum value for $a$ 
+(same for MILP$_\emptyset$ and MILP$_{\{a\}}$).
+The maximum value for $\hat{a}$ under LP ($X=\emptyset$) is 
+$\frac{1}{2} \cdot (\val(a)-LB(a))$ following the triangle approximation. 
+Now, if $X=\{a\}$, then the value of $\hat{a}$ is $\ReLU(\val(a))$: the difference 
+$\Delta(\hat{a})$ is between 0 (for $\val(a)\in \{LB,UB\}$) and $\frac{1}{2}$ (for $\val(a)=0$).
+The difference $\Delta(b)$ for the value of $b$ is thus between 0 and $\frac{c}{2}$, which means $\Delta(\hat{b}) \in [0, \frac{c}{4}]$, using the upper function of the triangle approximation of rate $r(b)=\frac{1}{2}$, as the value of $\hat{b}$ should be maximized.
+This means a difference $\Delta(z) \in [0, \frac{cd}{4}]$ 
+(depending on the maximal value $val(a)$), to compare with the fixed 
+$s_{FSB}(a)=\frac{cd}{4}$.
+
+\begin{figure}[t!]
 	\centering
@@
 
-	%In case where the bias is 0, then there is no difference between $s_{SR}$ and $s_{FSB}$.
-	Then, ReLU are ranked using these scores, to select the most important unstable ReLUs
-	(with $\LB(u_k) < 0 < \UB(u_k)$).
-	% as stable ReLUs are linear, thus they are already treated correctly.
-
-	{\color{red}
-\noindent {\em Running Example:} Consider Fig. \ref{img:FSB_example}. 
-It has no bias, so $s_{SR}=s_{FSB}$. We have $\lambda(b)=d$, $\lambda(a)=\frac{cd}{2}$.
-The value of $s_{FSB}(a)$ depends on the signs of $c,d$.
-
-We perform a novel comparison between $s_{FSB}(a)$ and $\Delta(z)$, the difference on the {\em maximal bound} computed by pMILP$_X(z)$ when opening the $\ReLU$ of node $a$ ($X=\{a\}$), yielding $\val(\hat{a}) = \ReLU(\val(a))$, versus having $X=\emptyset$, for which
-$\val(\hat{a})$ can be any value in the triangle approximation (Prop. \ref{LP}, Fig. \ref{triangle})).
-
-The most favorable cases are $c < 0 < d$ and $d < 0 < c$: 
-as $cd <0$, we have $s_{FSB}(a)=\max(0,\frac{cd}{4}) = 0$.
-Because $cd <0$, both $a$ and $\hat{a}$ need to be minimized by MILP$_X$ in order to maximize the value of $z$. For $X=\emptyset$, the LP approximation (=MILP$_\emptyset$) will thus 
-set $\val(\hat{a}) = \ReLU(\val(a))$ as this is the minimum value in the triangle approximation. Notice that opening $X=\{a\}$ yields the same $\val(\hat{a}) = \ReLU(\val(a))$.
-That is, opening node $a$ is not improving the bound $\UB(z)$, as correctly predicted by the score $s_{FSB}(a)= \Delta(a) = 0$.
-
-\begin{figure}[t!]
-	\begin{centering}
-	\begin{tikzpicture}[scale=1, >=stealth]
-
-		% Draw axes
-		\draw[->] (-5,0) -- (4,0) node[right] {$a$};
-		\draw[->] (0,-1) -- (0,3) node[above] {$\hat{a}$};
-
-		% Draw ReLU function
-		\draw[line width=0.4mm, blue] (-3,0) -- (0,0);
-		\draw[thick, blue] (0,0) -- (2.5,2.5) node[below, shift={(-1.1,-1.9)}] {$\hat{a} = \ReLU(a)$};
-		\draw[thick, blue] (-3,0) -- (2.5,2.5) node[above, shift={(-5.7,-2)}] {$\hat{a} = r(a) (a-\LB)$};
-
-		% Add labels
-		\draw[dashed] (2.5,0) -- (2.5,2.5) -- (0,2.5); % Optional grid
-		\node[below left] at (0,0) {$0$};
-
-		% Add tick marks
-
-		\foreach \x in {2.5}
-		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\UB$};
-		\foreach \x in {-3}
-		\draw[shift={(\x,0)}] (0,0.1) -- (0,-0.1) node[below] {$\LB$};
-
-		\foreach \y in {2.5}
-		\draw[shift={(0,\y)}] (0.1,0) -- (-0.1,0) node[left] {$\UB$};
-
-	\end{tikzpicture}
-		\caption{Triangle approximation with $r(a)=\frac{1}{2}$
-		\vspace{-0.3cm}}
-	\label{triangle}
-	\end{centering}
-	\end{figure}
-
-Case $c>0,d>0$: we have $s_{FSB}(a)=\frac{cd}{4}$.
-The value of $a,\hat{a},b,\hat{b}$ should be maximized to maximize the value of $z$, because $W_{bz}=d>0$ and $W_{ab}=c>0$. 
-%Each variation of $b$ by $\Delta(b)$ will have an impact $r(b) \cdot \Delta(b)=\frac{\Delta(b)}{2}$ on the value of $\hat{b}$, and thus $\frac{d \Delta(b)}{2}$ on $z$. 
-Now, let us call $val(a)$ the maximum value for $a$ 
-(same for MILP$_\emptyset$ and MILP$_{\{a\}}$).
-The maximum value for $\hat{a}$ under LP ($X=\emptyset$) is 
-$\frac{1}{2} \cdot (\val(a)-LB(a))$ following the triangle approximation. 
-Now, if $X=\{a\}$, then the value of $\hat{a}$ is $\ReLU(\val(a))$: the difference 
-$\Delta(\hat{a})$ is between 0 (for $\val(a)\in \{LB,UB\}$) and $\frac{1}{2}$ (for $\val(a)=0$).
-The difference $\Delta(b)$ for the value of $b$ is thus between 0 and $\frac{c}{2}$, which means $\Delta(\hat{b}) \in [0, \frac{c}{4}]$, using the upper function of the triangle approximation of rate $r(b)=\frac{1}{2}$, as the value of $\hat{b}$ should be maximized.
-This means a difference $\Delta(z) \in [0, \frac{cd}{4}]$ 
-(depending on the maximal value $val(a)$), to compare with the fixed 
-$s_{FSB}(a)=\frac{cd}{4}$.
-
 The last case is the most problematic: 
@@
 
-We call {\em global scoring} (GS) these functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the values 
+We call {\em global scoring} (GS) these functions $s_{FSB},s_{SR}$  because they score ReLUs as \textcolor{red}{accurately} as possible, considering that they do not have access to the values 
 $\val(a),\val(b)$ maximizing $z$. Following this analysis of $s_{FSB},s_{SR}$, 
 next Section presents a novel scoring function more accurate wrt $\Delta(z)$.
-
-	}
 

### 2025-06-18 ATVA 2025/experiments.tex
update some changes and answers

@@
 To assess the verification efficiency and runtime vs $\alpha,\beta$-CROWN, we 
-conducted evaluations  on neural networks tested in \cite{CROWN} which are mostly {\em complex} to verify (as easy instances are already appropriately taken care of).
+conducted evaluations  on neural networks tested in \cite{crown} which are mostly {\em complex} to verify (as easy instances are already appropriately taken care of).
 Namely, 6 ReLU-DNNs: 5 MNIST DNN that can be found in the \href{https://github.com/eth-sri/eran}{ERAN GitHub}
@@
 which can be downloaded from the \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN}{$\alpha,\beta$-CROWN GitHub}. 
-We commit to the same $\epsilon$ settings as in \cite{CROWN}, that are recalled in Table \ref{table_beta}. 
+We commit to the same $\epsilon$ settings as in \cite{crown}, that are recalled in Table \ref{table_beta}. 
 For reference, we also report an easy but very large ResNet Network for CIFAR10, already tested with $\alpha,\beta$ CROWN. 
@@
 
-Results on other networks from other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported \cite{CROWN} on other tested DNNs, with unfavorable comparison vs $\alpha,\beta$-CROWN.
+Results on other networks from other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported \cite{crown} on other tested DNNs, with unfavorable comparison vs $\alpha,\beta$-CROWN.
 Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on complex (even small) instances.
 Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em complex} MNIST DNNs at several time-out settings.
-Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible.
+Last, Pyrat \cite{pyrat} (2\textcolor{red}{nd} in the latest VNNComp) is not open source, which made running it impossible.
 Details can be found in the appendix.

### 2025-06-18 ATVA 2025/introduction.tex
small update
update some changes and answers

@@
 Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT
-\cite{pyrat}, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
-and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+\cite{pyrat}, respectively 4th, 3rd and 2\textcolor{red}{nd} of the last VNNcomp'24 \cite{VNNcomp24}
+and 5th, 2\textcolor{red}{nd} and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2\textcolor{red}{nd} in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
 We will thus compare mainly with $\alpha,\beta$-CROWN experiments as gold standard in the following\footnote{GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-CROWN on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us}.
@@
 		\hline
-		Network & nbr & Accuracy & Upper  & $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
+		Network & nbr & Accuracy \textcolor{red}{$^*$}  & Upper  \textcolor{red}{$^*$}& $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
 		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
@@
 	\end{tabular}
+	\begin{minipage}{0.9\linewidth}
+		\footnotesize
+		\textcolor{red}{\textsuperscript{*} Accuracy means the accuracy of the network itself on test set, and Upper Bound is 100\% the percentage of unsafe examples.} \\
+	\end{minipage}
 	\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
@@
 Compared with the heuristic in \cite{DivideAndSlide},  {\sf SAS} is much more efficient ($\approx 6$ times less binary variables for same accuracy (Fig.
-\ref{fig_table3}).
+\ref{fig_table3})).
 	%We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally (see Table.

### 2025-06-18 ATVA 2025/relatedwork.tex
update some changes and answers

@@
 MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of Hybrid MILP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding.
-In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy.
+In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more \textcolor{red}{binary variables} (thus runtime) to reach the same accuracy.
 % as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.

### 2025-06-18 ATVA 2025/valabstraction.tex
update some changes and answers

@@
 This implies that $x_3,x_4 \in [-2,2]$.
-After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to $[0,2]$, leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$.
+After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to \textcolor{red}{$[1.5,3.5]$} , leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$.
 The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val_{\vy}(n_i)=\alpha$.
@@
 This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
-However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous integer variables and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
+However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous \textcolor{red}{binary variables} and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
 
@@
 This a priori hurts accuracy.
-To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB,\UB$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
+To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB,\UB$ for neurons $n$ of \textcolor{red}{each layer} iteratively, that are used when computing values of the next layer.
 So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.
@@
 pMILP$_K$ has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
-where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
+where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ \textcolor{red}{binary variables} and $N$ linear variables.
 We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound.

### 2025-07-16 ATVA 2025/Final_version/Comparison.tex
update the final version

--- 2025-06-18 ATVA 2025/Comparison.tex
@@
 
-%\textcolor{red}{Fig2 page10 is intended as a running example: We show how $s_{FSB}$ behaves on Fig2 (page10-11).
+%{Fig2 page10 is intended as a running example: We show how $s_{FSB}$ behaves on Fig2 (page10-11).
 Page12 (Fig4 and above), we explain how SAS computes the same case and compares with FSB.
@@
 
-\begin{align*}
+\begin{align}
 \bm{\lambda}_{n-1} = -{(\bm{W}^n)}^T\bm{1}, \hspace*{4ex}  	\bm{\lambda}_{k-1} = {(\bm{W}^k)}^T\big( r(\bm{u}_k) \odot\bm{\lambda}_{k}\big) \hspace*{4ex}  k\in [n-1,2]
-\end{align*}
+\end{align}
 
@@
 
-We call {\em global scoring} (GS) these functions $s_{FSB},s_{SR}$  because they score ReLUs as \textcolor{red}{accurately} as possible, considering that they do not have access to the values 
+We call {\em global scoring} (GS) these functions $s_{FSB},s_{SR}$  because they score ReLUs as {accurately} as possible, considering that they do not have access to the values 
 $\val(a),\val(b)$ maximizing $z$. Following this analysis of $s_{FSB},s_{SR}$, 

### 2025-07-16 ATVA 2025/Final_version/Lipschitz.tex
update the final version

\section{Lipschitz}

We will introduce some formulas.

\subsection*{GS formula}

$$v=\frac{\gamma}{4}\cdot\lambda_a\cdot\sign(\lambda_a).$$

Here, $\lambda_a$ is computed by backward-propagation as usual (the formula at the end of page 9), but use $-\gamma$ as $\LB$ and $\gamma$ as $\UB$.

\subsection*{SAS formula}

 $$v = \Delta(\hat{a})\cdot\lambda_a.$$

Here, the computation of $\Delta(\hat{a})$ is as follows:

\begin{subnumcases}{\Delta(\hat{a}) =}
\sol(a)-\sol(\hat{a}), &for $\lambda_a > 0$ and $\sol(a) \geq 0$\\
-\sol(\hat{a}), &for $\lambda_a > 0$ and $\sol(a) \leq 0$\\
-\sol(\hat{a}), &for $\lambda_a < 0$ and $\sol(a) \geq 0$\\
\sol(a)-\sol(\hat{a}), &for $\lambda_a < 0$ and $\sol(a) \leq 0$	 
\end{subnumcases}

### 2025-07-16 ATVA 2025/Final_version/Paper_noProof.tex
update the final version

--- 2025-04-28 ATVA 2025/Paper_noProof.tex
@@
-\documentclass{llncs}
+\documentclass[runningheads]{llncs}
 \usepackage{hyperref}
 \usepackage{url}
+\usepackage[T1]{fontenc}
+\usepackage{graphicx}
 \pagestyle{plain}
@@
 
-\title{Solution-aware vs global ReLU selection: \\
-partial MILP strikes back for DNN verification}
-\date{}
+%
+%\date{}
 
@@
 
-	\maketitle
+	\title{Solution-aware vs global ReLU selection: \\
+		partial MILP strikes back for DNN verification}
+
+\author{Yuke Liao\inst{1}\orcidID{0009-0004-3763-686X} \and
+	Blaise Genest\inst{2,3}\orcidID{0000-0002-5758-1876} \and
+	Kuldeep S. Meel\inst{4}\orcidID{0000-0001-9423-5270}
+	\and
+	Shaan Aryaman\inst{5}\orcidID{0000-0001-7576-0766}}
+%
+\authorrunning{F. Author et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{CNRS@CREATE, Singapore \email{yuke.liao@cnrsatcreate.sg} \and The corresponding author\\
+	CNRS@CREATE, Singapore \email{blaise.genest@cnrsatcreate.sg}\and
+	CNRS, France
+	\email{blaise.genest@cnrs.fr}\\
+ \and
+	University of Toronto,  Toronto, Canada \\\email{meel@cs.toronto.edu}
+	\and
+	NYU Courant Institute of Mathematical Sciences, New York, USA\\ \email{aryaman.shaan@gmail.com}}
+%
+\maketitle              % typeset the header of the contribution
+%
+
 	\linenumbers
@@
 denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
-\begin{align*}
+\begin{align}
 	\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
 	\hat{\boldsymbol{z}}^{i} = \ReLU({\boldsymbol{z}}^i).
-\end{align*}
+\end{align}
 
@@
 Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
-\begin{align*}
+
+	\begin{align}
 	\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
-	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
-\end{align*}
+	{argmax (f(\boldsymbol{x'})) = argmax(f(\boldsymbol{x}))}
+\end{align}
 

### 2025-07-16 ATVA 2025/Final_version/formula_part2.tex
update the final version

\section{Three or More Layer before  $z$.}

Suppose $a$ is a neuron in three or more layers before $z$, we use $b$ to denote neurons in the next layer after $a$ and $c$ to denote neurons in two layers after $a$ and so on.

This formula is based on previous subsection but more complex. In some network, running this formula may cost too much time.

\begin{definition}\label{3layer}
Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bounds used in building MILP models. We define the following function $h$ for all neurons $b$ in layers between $a$ and $z$ as follows:
	\begin{align}
		&v_0 = sol(\hat{b}), v_1 = \ReLU(sol(b)), v_2 = \frac{\UB(b)sol(b)-\UB(b)\LB(b)}{\UB(b)-\LB(b)}\\
		&h(b) =
		\begin{cases}
			\frac{v_0-v_1}{v_2-v_1}, & \text{if } v_2-v_1 > 0\\
			0.5, & \text{otherwise.}
		\end{cases}
	\end{align} 
\end{definition}

\begin{definition}
	Continue the assumption in Definition \ref{3layer}. We define function $D$ layer by layer.

	First, $D(a) = \ReLU(sol(a))-sol(\hat{a})$.

Next we define all neurons $b$ in one layer after $a$: \begin{align}
	&u_0 = \max(\LB(b),\min(\UB(b),  sol(b)+D(a)W_{ab}))\\
	&u_1 = \begin{cases}
		\ReLU(u_0)+h(b)(\frac{\UB(c)u_0-\UB(b)\LB(b)}{\UB(b)-\LB(b)}-\ReLU(u_0)), & \text{if }\LB(b) < 0\\
	u_0, & \text{if }  \LB(b) \geq 0
	\end{cases}\\
	&D(b) = u_1-sol(\hat{b})
\end{align}

	Suppose $y$ is a neuron in at least one layer before $z$, and we have defined $D(x)$ for all neurons $x$ in layers before $y$, we define $D(y)$ as follows:
	\begin{align}
		&w_0 = \sum_x D(x)W_{xy}\\
		&w_1 = \min(\UB(y),sol(y)+w_0)\\		
		&D(y) =
		\begin{cases}
			w_1-sol({y}), & \text{if }W_{yz} > 0 \text{ and } \LB(y)\geq 0\\
		k(y)(w_1-sol({y})), & \text{if }W_{yz} > 0 \text{ and } \LB(y)< 0\\
		\ReLU(w_1)-sol(\hat{y})	, & \text{if }  W_{yz} < 0
		\end{cases}\\
	\end{align}	Finally, 	\begin{align*}
	&D(z) = \sum_y D(y)W_{yz}\\
	&Utility\_max^z(a) = -D(z)
	\end{align*}

\end{definition}

### 2025-07-16 ATVA 2025/Final_version/introduction.tex
update the final version

--- 2025-04-28 ATVA 2025/introduction.tex
@@
 Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT
-\cite{pyrat}, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
-and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+\cite{pyrat}, respectively 4th, 3rd and 2{nd} of the last VNNcomp'24 \cite{VNNcomp24}
+and 5th, 2{nd} and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2{nd} in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
 We will thus compare mainly with $\alpha,\beta$-CROWN experiments as gold standard in the following\footnote{GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-CROWN on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us}.
@@
 \begin{table}[t!]
+	\vspace{-1.0cm}
 	\centering
+		\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
+The 6 first DNNs are complex instances.
+The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
+	}
 	\begin{tabular}{||l|c|c|c||c|c|c||}
 		\hline
-		Network & nbr & Accuracy & Upper  & $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
+		Network & nbr & Accuracy {$^*$}  & Upper  {$^*$}& $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
 		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
@@
 	\end{tabular}
-	\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
-The 6 first DNNs are complex instances.
-The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
-	\vspace{-0.5cm}}
+	\begin{minipage}{0.9\linewidth}
+		\footnotesize
+		{\textsuperscript{*} Accuracy means the accuracy of the network itself on test set, and Upper Bound is 100\% the percentage of unsafe examples.} \\
+	\end{minipage}
 	\label{table_beta}
+		\vspace{-0.5cm}
 \end{table}
@@
 	\centering
+	\vspace{-0.35cm}
+	\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
+		%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
+		Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
+		}
 	\begin{tabular}{||l|c|c||c|c|c||}
@@
 	\end{tabular}
-\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
-%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
-\vspace{-0.5cm}}
+	\vspace{-0.65cm}
 \label{table_complete}

### 2025-07-16 ATVA 2025/Final_version/proofs.tex
update the final version

--- 2024-11-27 ICLR25/proofsb.tex
@@
-\vspace{-0.6cm}
+\newpage
 
@@
 
+We first provide the pseudo code for pMILP in Algorithm \ref{algo1}.
+
 \SetKwInput{KwInput}{Input}
@@
 
-We provide the pseudo code for pMILP in Algorithm \ref{algo1}.
 pMILP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
@@
 
-We also provide in Table \ref{tab:example1} the raw numbers used to produce Figure \ref{fig_table3}.
-Further, we tested with the SR and FSB heuristics \cite{BaB}, that chooses nodes to branch on for BaB (Branch and Bound).
-When SE and FSR are used to choose open nodes for pMILP, the accuracy is low as shown on Fig.
-\ref{fig_table3_new}: SR and FSB are worse than \cite{DivideAndSlide} for $<35$ oepn ReLU nodes, although unlike the latter, the former can rank ReLU nodes in several layer before (which helps them a bit), and far worse than Utility.
-Further, FSB is performing worse than SR when choosing nodes for pMILP, while to choose nodes to branch on for BaB, it is the opposite.
-This likely means that the heuristic to choose nodes to branch for BaB is not adapted to choose nodes to open for pMILP.
-
-\begin{table}[h!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|c|c||c|c|c|c|}
-		\hline
-			&\multicolumn{5}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{4}{c|}{$X \subseteq$ Layers 1\&2, max $=116$} \\\cline{2-10}
-		\text{$|X|$}  & \text{Random} & Huang &SR&FSB& \bf Utility& \text{Random} & SR & FSB &\bf Utility\\ \hline
-		\hline
-		0  (LP) &   1.761  &1.761&1.761&1.761& 1.761 & 1.761  &  1.761& 1.761 & 1.761\\ \hline \hline
-		5  &   1.729&1.704 &1.7200&1.7197& 1.603&  1.729& 1.7133 & 1.7149 & \bf 1.532 \\ \hline
-		10  &  1.701 &  1.651 &1.6840&1.6851&1.517& 1.696 & 1.6674& 1.6714 & \bf  1.371\\ \hline
-		15  & 1.671 &  1.599 &1.6502& 1.6516&1.466&  1.653& 1.6230& 1.6251 & \bf  1.247\\ \hline
-		20  &  1.635 & 1.557&1.6190&1.6199&1.438 & 1.619 &1.5764 & 1.5812 & \bf  1.145\\ \hline
-		25  &  1.601 & 1.519 &1.5887&1.5886&1.427&  1.586 &1.5322 & 1.5388 & \bf 1.061\\ \hline
-		30  & 1.574 & 1.489 &1.5584&1.5604&1.425& 1.546 &  1.4914& 1.4982 & \bf  0.989 \\ \hline
-		35  &  1.542 & 1.465&1.5289&1.5305&1.424 & 1.502 & 1.4481 & 1.4600 & \bf 0.934 \\ \hline
-		40  & 1.512 & 1.447 &1.4985&1.5001&1.424& 1.469 & 1.4070& 1.4187 & \bf 0.921 \\ \hline \hline
-		max & 1.424  &1.424&1.424&1.424& 1.424 & 0.895 & 0.895 & 0.895 & 0.895   \\ \hline
-	\end{tabular}
-	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-	\label{tab:example1}
-	%\vspace{-0.6cm}
-\end{table}
-
-	\begin{figure}[h!]
-		\centering
-		\vspace*{-0.3cm}
-		\includegraphics[height=9cm]{New Plot for table 3}.
-		\vspace*{-0.4cm}
-		\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, with ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs vs SR vs FSB vs random.}
-		\label{fig_table3_new}
-	\end{figure}
-
-\newpage
-
 \subsubsection*{Usefulness of computing previous layers accurately}
@@
 Then, we explore the usefulness of computing accurately each layer inductively.
-For that, we keep the setting of Figure \ref{fig3} / Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
-
-\begin{figure}[h!]
-	\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
-	\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.
-	Time is using logscale.}
-	\label{fig3LP}
-\end{figure}
+For that, we keep the setting of Table 3 and Table \ref{table14}, but computing the previous layer with LP rather than with full MILP.
 
@@
 	\hline
+
 \end{tabular}
-\caption{Comparison of accuracy in layer 3 when layer 2 is computed inaccurately using LP vs when layer 2 computed accurately using MILP.}
+\caption{Comparison of accuracy in layer 3 from computing layer 2 inaccurately using LP vs (from computing layer 2 accurately using MILP)}
 \label{table15}
 \end{table}
+
+\begin{figure}[b!]
+	\hspace*{-0.8cm}
+	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
+	\caption{Time and uncertainty scaling of table 7.
+		Time is using logscale.}
+	\label{fig3LP}
+\end{figure}
 
@@
 We compare this standard strategy with the pMILP strategy of setting a priori a number of open nodes.
-
-\begin{figure}[h!]\hspace*{-0.8cm}
-	\includegraphics[scale=0.6]{Layer7_comparison.png}.
-	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
-	\label{fig4}
-\end{figure}
 
@@
 
+\begin{figure}[h]\hspace*{-0.8cm}
+	\includegraphics[scale=0.6]{Layer7_comparison.png}.
+	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
+	\label{fig4}
+\end{figure}
+
 Figure \ref{fig4} shows that choosing nodes is much more efficient for time/accuracy trade-off than setting time outs and use full MILP.
 And this is for the smallest DNN we considered (500 hidden neurons, far from the biggest 20k neuron DNN we experimented with)
+
+}
 
@@
 
-\end{document}
-
-\section{SR Heuristic for choosing nodes}
-
-Here we provide the formula of BaB-SR from paper \cite{BaB}.
+Here we cite the formula of BaBSR from paper \cite{BaB}.
 
@@
 \end{figure}
-
-\begin{table}[h!]	
-	\centering
-	\begin{tabular}{|c||c|c|c|c|}
-		\hline
-		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
-		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
-		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
-		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
-		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
-		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
-		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
-		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
-		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
-		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
-		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
-		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
-	\end{tabular}
-	\caption{BSR and FSB}
-	\label{BSRandFSB}
-	%\vspace{-0.6cm}
-\end{table}
 

### 2025-07-16 ATVA 2025/Final_version/proofsb.tex
update the final version

--- 2025-04-25 ATVA 2025/proofsb.tex
@@
 
-Hybird MILP first call $\alpha,\beta$-Crown with short time-out (TO), then call partial MILP on those inputs which was neither certified nor falsified by this run of $\alpha,\beta$-Crown.
+Hybird MILP first call $\alpha,\beta$-CROWN with short time-out (TO), then call partial MILP on those inputs which was neither certified nor falsified by this run of $\alpha,\beta$-CROWN.
 We are using two settings of TO, for smaller DNNs we use TO$=10s$, and for the two larger ones, we use TO$=30s$.
 
-Partial MILP uses 20 CPU-threads, while $\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU,
+Partial MILP uses 20 CPU-threads, while $\alpha,\beta$-CROWN uses massively parallel ($>$4096 threads) GPU,
 
@@
 		\hline \hline
-		Network & TO for $\alpha,\beta$-Crown  & Minimum number of Open neurons  \\ 		  
+		Network & TO for $\alpha,\beta$-CROWN  & Minimum number of Open neurons  \\ 		  
 		\hline
@@
 		MNIST $6 \times 500$ & 30s & 48,21,11,6,3,14 \\ \hline
-		CIFAR CNN-B-adv & 30s & 200, 0, 45 \\ \hline \hline
+		CIFAR CNN-B-Adv & 30s & 200, 0, 45 \\ \hline \hline
 	\end{tabular}
@@
 Notice that a different balance between accuracy and runtime could be set.
-For instance, we set up the numbers of open neurons to have similar runtime as Refined $\beta$-Crown for the first 4 DNNs ($50s-100s$).
+For instance, we set up the numbers of open neurons to have similar runtime as Refined $\beta$-CROWN for the first 4 DNNs ($50s-100s$).
 We could easily target better accuracy (e.g.
 for $8 \times 100$ with a relatively high $15\%$ undecided images) by increasing the number of open neurons, with a trade-off on runtime (current runtime is at $61s$).
-By comparison, the sweet spot for $\alpha,\beta$-Crown seems to be around TO$=30s$, enlarging the time-out having very little impact on accuracy but large impact on runtime
+By comparison, the sweet spot for $\alpha,\beta$-CROWN seems to be around TO$=30s$, enlarging the time-out having very little impact on accuracy but large impact on runtime
 (Table \ref{table_beta}).
 
-\subsection*{Setting for $\alpha,\beta$-Crown}
+\subsection*{Setting for $\alpha,\beta$-CROWN}
 
-The networks were already tested by $\alpha,\beta$-Crown \cite{crown}.
+The networks were already tested by $\alpha,\beta$-CROWN \cite{crown}.
 We thus simply reused the parameter files from \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN/blob/main/complete_verifier/exp_configs/beta_crown/}{their Github},
@@
 %We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to.
-From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-Crown on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP.
+From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-CROWN on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP.
 The conclusion are thus unchanged.
@@
 
-In the following, we provide results comparing $\alpha,\beta$-Crown to other verifiers, to justify our use of $\alpha,\beta$-Crown as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.
+In the following, we provide results comparing $\alpha,\beta$-CROWN to other verifiers, to justify our use of $\alpha,\beta$-CROWN as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.
 
-\subsection*{Comparison $\alpha,\beta$-Crown vs PRIMA}
+\subsection*{Comparison $\alpha,\beta$-CROWN vs PRIMA}
 
@@
 		\hline \hline
-		Network & $\alpha,\beta$-Crown & Refined $\beta$-Crown & PRIMA \\ 		  
+		Network & $\alpha,\beta$-CROWN & Refined $\beta$-CROWN & PRIMA \\ 		  
 		\hline
@@
 		MNIST $6 \times 500$ & 51\% (16s) & $-$ & 64\% (117s) \\ \hline
-		CIFAR CNN-B-adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
+		CIFAR CNN-B-Adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
 		CIFAR ResNet & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
 	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves.
-N/A means that \cite{crown} did not report the numbers, while $-$ means that Refined $\beta$-Crown cannot be run on these DNNs.}
+	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-CROWN, Refined $\beta$-CROWN, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves.
+N/A means that \cite{crown} did not report the numbers, while $-$ means that Refined $\beta$-CROWN cannot be run on these DNNs.}
 	\label{table9}
@@
 	PRIMA \cite{prima} is a major verifier in the ERAN toolkit.
-In Table \ref{table9}, we report the comparison between PRIMA and $\alpha,\beta$-Crown, mainly from \cite{crown}.
+In Table \ref{table9}, we report the comparison between PRIMA and $\alpha,\beta$-CROWN, mainly from \cite{crown}.
 The setting is mainly similar from ours, but numbers are not perfectly comparable as the images tested are not  exactly the same (1000 first or 200 first images for CNN-B-Adv), vs 100 first in Tables \ref{table_hybrid}, \ref{table_beta}.
@@
 
-Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-Crown. However, it is slower and less accurate than Refined $\beta$-Crown.
-On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-Crown, while the runtime is $>5$ times larger.
+Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-CROWN. However, it is slower and less accurate than Refined $\beta$-CROWN.
+On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-CROWN, while the runtime is $>5$ times larger.
 Hence, Hybrid MILP is more accurate than PRIMA with similar runtime or faster.
@@
 
-\subsection*{Comparison $\alpha,\beta$-Crown vs MN-BaB}
+\subsection*{Comparison $\alpha,\beta$-CROWN vs MN-BaB}
 
-MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-Crown. Results in \cite{ferrari2022complete}
-are close to those of $\alpha,\beta$-Crown.
+MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-CROWN. Results in \cite{ferrari2022complete}
+are close to those of $\alpha,\beta$-CROWN.
 However, none of the {\em hard} networks from \cite{crown} that we consider have been tested.
@@
 		\hline \hline
-		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & MN-BaB & MN-BaB \\ 
+		 & $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN & MN-BaB & MN-BaB \\ 
 		 Network & TO=30s & TO=2000s &  TO=30s & TO=2000s \\ 
@@
 		MNIST $6 \times 500$ & 51\% (16s) & 50\% (1002s) & 58\% (18s) & 55\% (1036s) \\ \hline
-		CIFAR CNN-B-adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
+		CIFAR CNN-B-Adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
 	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, and MN-BaB}
+	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-CROWN, and MN-BaB}
 	\label{table10}
@@
 
-Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-Crown.
+Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-CROWN.
 Notice the specially high number of undecided images for CNN-B-Adv with TO=30s, probably meaning that 30s is too small for MN-BaB on this large DNN.
@@
 
-	\subsection*{Comparison $\alpha,\beta$-Crown vs NNenum}
+	\subsection*{Comparison $\alpha,\beta$-CROWN vs NNenum}
 
 NNenum \cite{nnenum} is a complete verifier with good performance according to VNNcomp.
-It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-Crown. The experiments section in \cite{nnenum} does not report
+It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-CROWN. The experiments section in \cite{nnenum} does not report
 the {\em hard} DNNs we are considering. We tried to experiment it on the same MNIST 
-$6 \times 500$ and CIFAR CNN-B-adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
-We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-Crown, on both 
+$6 \times 500$ and CIFAR CNN-B-Adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
+We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-CROWN, on both 
 MNIST $5 \times 100$ and CIFAR CNN-B-Adv. 
-On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-Crown, but far from the accuracy Hybrid MILP.
-On CIFAR CNN-B-adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.
+On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-CROWN, but far from the accuracy Hybrid MILP.
+On CIFAR CNN-B-Adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.
 
@@
 		\hline \hline
-		 & $\alpha,\beta$-Crown & NNenum & Hybrid\\ 
+		 & $\alpha,\beta$-CROWN & NNenum & Hybrid\\ 
 		 Network & TO=2000s &  TO=2000s & MILP\\ 
@@
 		MNIST $5 \times 100$ & 50\%(1026s) & 44\% (1046s) & \bf 13\% (46s)\\ \hline
-		CIFAR CNN-B-adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
+		CIFAR CNN-B-Adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
 	\end{tabular}
-	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown and NNenum with 2000s time-out, and Hybrid MILP}.
+	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-CROWN and NNenum with 2000s time-out, and Hybrid MILP}.
 	\label{table11}
@@
 		$\epsilon = 0.1$ & 44.6s & 310s \\  \hline 
-		CIFAR CNN-B-adv &  & \\
+		CIFAR CNN-B-Adv &  & \\
 		$\epsilon = 2/255$& 1s & 609s \\ \hline \hline

### 2025-07-16 ATVA 2025/Final_version/relatedwork.tex
update the final version

--- 2025-04-28 ATVA 2025/relatedwork.tex
@@
 MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of Hybrid MILP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding.
-In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy.
+In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more {binary variables} (thus runtime) to reach the same accuracy.
 % as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.

### 2025-07-16 ATVA 2025/Final_version/valabstraction.tex
update the final version

--- 2025-04-28 ATVA 2025/valabstraction.tex
@@
 This implies that $x_3,x_4 \in [-2,2]$.
-After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to $[0,2]$, leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$.
+After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to {$[1.5,3.5]$} , leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$.
 The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val_{\vy}(n_i)=\alpha$.
@@
 This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
-However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous integer variables and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
+However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous {binary variables} and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
 
@@
 This a priori hurts accuracy.
-To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB,\UB$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
+To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB,\UB$ for neurons $n$ of {each layer} iteratively, that are used when computing values of the next layer.
 So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.
@@
 pMILP$_K$ has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
-where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
+where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ {binary variables} and $N$ linear variables.
 We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound.

### 2025-07-23 ATVA 2025/Final_version/experiments.tex
update the final version
update draft of final version
ATVA25

--- 2025-06-18 ATVA 2025/experiments.tex
@@
 	\centering
-	\vspace*{-0.3cm}
+%	\vspace*{-0.3cm}
 	\includegraphics[height=7cm]{CNN-B-ADV_layer7_comparison_image85.png}.
-	\vspace*{-0.4cm}
+%	\vspace*{-0.4cm}
 	\caption{Average uncertainty of pMILP for neurons of the fourth layer of CNN-B-Adv, 
@@
 with 2 times less binary variables for the same accuracy (10 vs 22) vs {\sf GS} and 6 times vs Huang \cite{DivideAndSlide} (4 vs 24).
-Each node of the 4th layer displays a similar pattern, and the pattern is similar for different images (see appendix).
+Each node of the 4th layer displays a similar pattern, and the pattern is similar for different images.
 
@@
 	\centering
+	\caption{Comparison of different orderings with selection of ReLUs by {\sf SAS}.
+	}
+	\label{table.order}
 	\begin{tabular}{|c||c c|c c|c c|c c|}
@@
 	\end{tabular}
-	\caption{Comparison of different orderings with selection of ReLUs by {\sf SAS}.
-	\vspace{-0.4cm}}
-	\label{table.order}
+%		\vspace{-0.6cm}
 \end{table}
@@
 
-\begin{figure}[t!]
-	\hspace*{-0.8cm}
+\begin{figure}[b!]
+%	\hspace*{-0.8cm}
 	\includegraphics[scale=0.5]{CNN-B-ADV_layer7_comparison_image85_4methods.png}
@@
 Still, {\sf SAS} is faster than {\sf GS} at  every accuracy.
-Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance in runtime over different output neurons compared with {\sf GS} for similar accuracy (see table \ref{SAS_GS_similarTO} in Appendix), which helps setting a number of ReLU nodes to open.
+Importantly, {\sf SAS} is more deterministic in its runtime given a number of ReLU nodes, with half the variance in runtime over different output neurons compared with {\sf GS} for similar accuracy, which helps setting a number of ReLU nodes to open.
 
@@
 
+\subsection{Ablation study: on usefulness of computing previous layers accurately}
+
+We explore the usefulness of computing accurately bounds for each neuron inductively on the layers, 
+even on small networks. For that, we consider MNIST $5 \times 100$, computing bounds for nodes of layer 3, comparing when bounds for neurons of layer 2
+have been computed inaccurately using LP rather than with the more accurate (partial) MILP.
+
+\begin{figure}[b!]
+	\vspace*{-0.8cm}
+	\includegraphics[scale=0.55]{Layer3_comparison_LP}.
+	\caption{Comparison of accuracy in layer 3 when bounds for neurons in layer 2 is computed inaccurately using LP vs when bounds of layer 2 are computed accurately using pMILP.
+	Time is using logscale.}
+	\label{fig3LP}
+\end{figure}
+
+This experiment explains the rationale to use divide and conquer methodology, 
+using many calls (one for each neuron) of pMILP with relatively small number $|X|$ of open ReLUs 
+rather than few calls (one per output neuron) of pMILP with larger number $|X|$ of open nodes. 
+The benefit is clear already from layer 3, obtaining much tighter bounds (lower uncertainty) when bounds for neurons in layer 2 have been computed accurately using pMILP.
+
 \subsection{Comparison with $\alpha,\beta$-CROWN}
@@
 		\bf 10\% (402s) \\ \hline
-		CIFAR CNN-B-Adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
-		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
+		CNN-B-Adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
+		ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
 	\end{tabular}
@@
 The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify), provided for reference.
-	\vspace{-1cm}}
+	}
 	\label{table_hybrid}
+%	\vspace*{-0.7cm}
 	\end{table}
@@
 
-\begin{table}[t!]
+\begin{table}[b!]
+%	\vspace{-0.1cm}
 	\centering
+		\caption{Images verified by different verifiers ($\%$, higher is better) on CIFAR CNN-B-Adv. Results, from \cite{cutting}, are not fully comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
+	\label{table_gcp}
 	\begin{tabular}{||c||c|c|c|c|c||}
@@
 	\end{tabular}
-	\caption{Images verified by different verifiers ($\%$, higher is better) on CIFAR CNN-B-Adv. Results, from \cite{cutting}, are not fully comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
-	\label{table_gcp}
-	\vspace{-0.3cm}
+%	\vspace{-0.6cm}
 \end{table}
@@
 Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on complex (even small) instances.
-Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em complex} MNIST DNNs at several time-out settings.
-Last, Pyrat \cite{pyrat} (2\textcolor{red}{nd} in the latest VNNComp) is not open source, which made running it impossible.
-Details can be found in the appendix.
-Also, ablation studies showing what each feature of Hybrid MILP is bringing can be found in the appendix.
+Concerning MnBAB \cite{ferrari2022complete}, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em complex} MNIST DNNs at several time-out settings.
+Last, Pyrat \cite{pyrat} (2nd in the latest VNNComp) is not open source, which made running it impossible.
+%Details can be found in the appendix. Also, ablation studies showing what each feature of Hybrid MILP is bringing can be found in the appendix.
 

### 2025-07-23 ATVA 2025/Final_version/relatedwork.tex
ATVA25

@@
 % as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.
+
+Compared with \cite{atva}, which uses pMILP in an abstraction refinement loop, 
+they iteratively call pMILP to obtain bounds for the same output neuron, opening more and more ReLUs.
+This scales only to limited size DNN (500 neurons), because of the fact that many ReLUs need to be open (and then Gurobi takes a lot of time) and the iterative nature which cannot be parallelized, unlike our method which scales up to 20.000 neurons.
+
+%Instead, we call pMILP on each hidden neuron *once*, layer per layer (divide and conquer), with a fixed limited number of open ReLUs thanks to our novel SAS selection.
+%pMILP opens the most important ReLUs for a given neuron.
 

### 2025-07-23 ATVA 2025/Final_version/ATVA25.tex
ATVA25
authors

--- 2025-07-16 ATVA 2025/Final_version/Paper_noProof.tex
@@
 \usepackage{wrapfig}
-\usepackage{lineno}
+%\usepackage{lineno}
 \usepackage{amsmath}
@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage[misc]{ifsym}
 \usetikzlibrary{positioning, arrows.meta,calc}
@@
 
-\author{Yuke Liao\inst{1}\orcidID{0009-0004-3763-686X} \and
+\author{Yuke Liao \Letter \inst{1}\orcidID{0009-0004-3763-686X} \and
 	Blaise Genest\inst{2,3}\orcidID{0000-0002-5758-1876} \and
-	Kuldeep S. Meel\inst{4}\orcidID{0000-0001-9423-5270}
+	Kuldeep Meel\inst{4}\orcidID{0000-0001-9423-5270}
 	\and
@@
 %
-\authorrunning{F. Author et al.}
+\authorrunning{Y. Liao, B. Genest, K. Meel, S. Aryaman}
 % First names are abbreviated in the running head.
@@
 %
-\institute{CNRS@CREATE, Singapore \email{yuke.liao@cnrsatcreate.sg} \and The corresponding author\\
-	CNRS@CREATE, Singapore \email{blaise.genest@cnrsatcreate.sg}\and
-	CNRS, France
-	\email{blaise.genest@cnrs.fr}\\
+\institute{CNRS@CREATE, Singapore \email{yuke.liao@cnrsatcreate.sg} 
+\and CNRS@CREATE \& IPAL, Singapore \email{blaise.genest@cnrsatcreate.sg}\and
+	CNRS, IPAL, France \email{blaise.genest@cnrs.fr}\\
  \and
@@
 
-	\linenumbers
+	%\linenumbers
+
 	\begin{abstract}
@@
 
-This opens up interesting future research directions, to verify global \cite{lipshitz}, \cite{sensing} rather than local (robustness) properties, which need very accurate methodology
-and give rise to hard instances as the range of each neuron is no more local to a narrow neighborhood (and thus almost all ReLUs are unstable, with both modes possible).
+This opens up interesting future research directions, 
+to verify global \cite{lipshitz}, rather than local (robustness) properties, which need very accurate methodology
+and give rise to hard instances as the range of each neuron is no more local to a narrow neighborhood 
+(most ReLUs are unstable, with both modes possible).
 
@@
 
-\newpage
+\smallskip
+{\bf Acknowledgement:} 
+This research was conducted as part of the DesCartes program and 
+was supported by the National Research Foundation, Prime Minister's Office, Singapore, 
+under the Campus for Research Excellence and Technological Enterprise
+(CREATE) program, and partially supported by ANR-23-PEIA-0006 SAIF.
 
@@
 
-\bigskip
-
-\appendix
-
-\input{proofsb}
-
 \end{document}

### 2025-07-23 ATVA 2025/Final_version/Paper_noProof.tex
update draft of final version
update the draft of final version
authors

@@
 \usepackage{array}
+\usepackage[misc]{ifsym}
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
@@
 \bibliographystyle{plain}
+
+\newpage
 
@@
 
+%
 \input{proofsb}

### 2025-07-25 AAAI2026/Lipschitz_a_proposition.tex
correct the version

--- 2025-05-21 lipschitz 2025/Lipitschz.tex
@@
 \newcommand{\vW}{\boldsymbol{W}}
+
 \newcommand{\val}{{\textrm{value}}}
@@
 \newcommand{\sol}{\mathrm{sol}}
+
 \newcommand{\UB}{\mathrm{UB}}
@@
 \usepackage{amsmath, amssymb, amsfonts}
+
 \newcommand{\ReLU}{\mathrm{ReLU}}
+
 \newcommand{\CMP}{{\textrm{CMP}}\ }
+
 \newcommand{\fix}{\marginpar{FIX}}
@@
 
-\title{Global case}
+\title{Solution-aware vs global ReLU selection: \\
+partial MILP strikes back for DNN verification}
 \date{}
@@
 
-	\maketitle
-	\linenumbers
-	\begin{abstract}
-		TODO
-	\end{abstract}
-
-	\section{Introduction}
-
-	\section{Notations and Preliminaries}
-
-	In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-	capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{crown}.
-	To simplify the notations, we restrict the presentation to feed-forward, 
-	fully connected ReLU Deep Neural Networks (DNN for short), where the activation function is $\ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-	$\ReLU(x)=x$ for $x \geq 0$ and $\ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
-
-	%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
-
-	%\subsection{Neural Network and Verification}
-
-	% testtesttesttest
-	An $\ell$-layer DNN is provided by $\ell$ weight matrices 
-	$\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
-	and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
-	We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
-	$d_0$ the input dimension, and $d_\ell$ the output dimension.
-
-	Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-	denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
-	\begin{align*}
-		\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
-		\hat{\boldsymbol{z}}^{i} = \ReLU({\boldsymbol{z}}^i).
-	\end{align*}
-
-	The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
-	$\boldsymbol{z}$ is called pre-activation values, 
-	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
-
-	Concerning the verification problem, we focus on the global-robustness question.
-Global robustness asks to determine how the output of a neural network will be affected under a certain kind of small perturbations to any possible input.
-In this view, Lipschitz continuity is a good characterization of global robustness.
-
-	\section{Global robustness and Lipschitz constant}
-
-	Recall the definition of Lipschitz continuity:
-	under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
-	\begin{align*}
-		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
-	\end{align*} 
-	In our practice, when we need global robustness, we will compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
-		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
-	\end{align} And this will lead to the following definition
-
 	\begin{definition}[$\varepsilon$-diff bound]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
+	Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
 
@@
 
-	From $\varepsilon$-diff bound, we cannot directly obtain a Lipschitz bound for the function, but we can get the following weaker bound:
-
-	\begin{definition}[Lipschitz above $\varepsilon$ constant]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
+\begin{definition}[Lipschitz above $\varepsilon$ constant ]
+	Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
 
@@
 
-		That is, for any two inputs $x,y$, if \begin{align*}
+	In formula, for any two inputs $x,y$, if \begin{align*}
 		|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D \cdot \varepsilon,
@@
 		&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
-			&\leq D\varepsilon + \cdots +D\varepsilon = (M+1)D\varepsilon
+		&\leq D\varepsilon + \cdots +D\varepsilon \\
+		&= (M+1)D\varepsilon
 	\end{align*}
-		Hence,\begin{align*}
-			|f(x)-f(y)| &\leq (M+1)D\varepsilon \leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
-			&= D\cdot\frac{M+1}{M} |x-y|	\leq   D\cdot\frac{N+1}{N} |x-y|		
+	Hence\begin{align*}
+		|f(x)-f(y)| &\leq (M+1)D\varepsilon \\
+		&\leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
+		&= D\cdot\frac{M+1}{M} |x-y|\\
+		&\leq   D\cdot\frac{N+1}{N} |x-y|
 	\end{align*}
@@
 
-		This ends the proof.
+	This is what we want to show.
 \end{proof}
-
-	In practice, Lipschitz above $\varepsilon$ constant is already sufficient, since in most cases we care about the absolute difference under input perturbations, not the ratio.
-By combining the above proposition, the computation of $\varepsilon$-diff bound can satisfy our aim.
-
-	Moreover, we have one more proposition connecting $\varepsilon$-diff bound and Lipschitz above $\varepsilon$ constant.
 
@@
 \end{proposition}
+
 \begin{proof}
@@
 		\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
-			& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})= D \frac{N+1}{N}\\
+		& = D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon})\\
+		& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})\\
+		& = D \frac{N+1}{N} 
 	\end{align*}
-		This ends the proof.
+
 \end{proof}
 
-	\section{pMILP for local robustness}
-
-	\subsection{MILP and LP encodings for DNNs}
-
-	First we introduce some concepts for local robustness question.
-
-	Mixed Integer Linear Programming (MILP) value abstraction is a complete (but inefficient) method. 
-	For an unstable neuron $n$ that its value $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$, the value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one 
-	integer variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
-
-	\vspace{-0.4cm}
-	\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \UB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\LB(n) \cdot (1-a)
-		\label{eq11}
-	\end{equation}
-
-	%For all $x \in [\LB(n),\UB(n)] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
-The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$.
-This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
-However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous integer variables and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
-
-	The global structure is as follows, using Gurobi as an example:
-	\begin{enumerate}
-		\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable. 
-		\item Set constraints for input nodes.
-		\item For each pre-activation node in a hidden layer (and each output node), set linear constraints relating them to the post-activation or input nodes in the previous layer they connect to.
-		\item Between pre- and post- activation nodes, set the MILP constraint described above.
-	\end{enumerate} We use $\mathcal{M}$ to denote the whole MILP model.
-In practice, we may only consider the network up to a certain hidden layer.
-In that case, the pre-activation nodes of that layer serve as the output nodes of the model $\mathcal{M}$.
-
-	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
-As solving LP instances is polynomial time, this optimization is significantly more efficient.
-However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
-This approach is termed the {\em LP abstraction}.
-We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.
-
-	\subsection{partial MILP}
-
-	We will use {\em partial MILP} (pMILP for short, see \cite{DivideAndSlide}) to get trade-offs between accuracy and runtime. Here, we extract the explanation from paper CITE.
-
-	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the partial MILP based on $X$ to compute neuron $n$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding, where variable $a$ is:
-	\begin{itemize}
-		\item binary for neurons in $X$ (exact encoding of the ReLU),
-		\item linear for neurons not in $X$ (linear relaxation).
-	\end{itemize}
-	We will denote above case by MILP$_X$ or $\mathcal{M}_X$. Informally, we say that a node is opened if it is in $X$.
-
-	If $X$ covers all unstable neurons, then MILP$_X$ is exact. But then the time cost may be very large (exponential growth).
-
-	To reduce the runtime, we will limit the size of subset $X$.
-This a priori hurts accuracy.
-To recover some of this accuracy, we use an iterative approach: computing lower and upper bounds $\LB,\UB$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
-
-	\subsection{SAS}
-
-	In pMILP, to decide the set $X$, we introduce the method {\em Solution-Aware Scoring} (SAS)
-	to evaluate accurately how opening a ReLU impacts the accuracy. Again, here we use the definition from paper CITE. For details and explanation, see CITE.
-
-	Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
-For each node $n<z$, we denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$: $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$; and we denote $(\sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$ a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
-Moreover,  we define the function
-	$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
-	accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
-	compared with using only LP.
-
-	First, SAS will call solvers to compute the LP model to get a solution, which is reasonably fast as there is no binary variables.
-
-	Next, for a neuron $b$ on the layer before layer $\ell_z$, we define:
-
-	\vspace{-0.4cm}
-	$$\Utility\_\max\nolimits^z(b) = W_{bz} \times (\sol(\hat{b})- \ReLU(\sol(b)))$$
-	\vspace{-0.4cm}
-
-	And for a neuron $a$ two layers before $\ell_z$, 
-	$b$ denoting neurons in the layer $\ell$ just before $\ell_z$.
-	Recall the rate $r(b)=\frac{\max(0,\UB(b))}{\max(0,\UB(b))-\min(0,\LB(b))} \in [0,1]$.
-	We define:
-
-	\begin{flalign*}
-		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})&&\\
-		\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})&&\\	
-	\end{flalign*}
-
-	\vspace{-1.2cm}
-
-	\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
-		r(b)\Delta(b), & for $W_{bz} > 0$ \\
-		\max(\Delta(b),-\sol(b)), & for $W_{bz} < 0$ and $\sol(b)\geq0$\\
-		\max(0,\Delta(b)+\sol(b)), & for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
-	\end{subnumcases}
-
-	\begin{flalign*}
-		\Utility\_\max\nolimits^z(a) &= \Delta(z) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})&&
-	\end{flalign*}
-
-	From paper CITE, we know that $\Utility$ is a safe overapproximation in the sense of following proposition:
-
-	\begin{proposition}
-		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
-	\end{proposition}
-
-	\section{Modeling for global robustness}
-
-	\subsection{Using Two Identical Models}
-	The most straightforward way is to use two identical MILP models, i.e., to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (and their own constraints) plus some extra constraints:
-	\begin{enumerate}
-		\item Add constraints for connecting input nodes $\mathcal{M},\mathcal{M}'$ to meet the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon$.
-		\item Set the optimization objective as the difference between two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (because we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
-	\end{enumerate}
-	This large model contains twice as many binary variables as $\mathcal{M}$.
-The computational cost of solving an MILP model grows roughly exponentially with the number of binary variables, and hence it will cost much more time.
-
-We may relax some constraints (by changing binary variables to continuous variables) as in the case of local robustness.
-However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which motivates us to explore other modeling approaches.
-
-	\subsection{A Simplified model}
-
-	To avoid above problem, we introduce a simplified model that is to use one variable $y_i$ to represent the difference of each two variables: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
-
-	Given  $\gamma_i$ be the upper bound of $y_i$, the constraints for $\hat{y}_i$ are the follows:\begin{align*}
-	\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
-	\hat{y}_i &\geq (a-1) \gamma_i           &\quad \hat{y}_i &\leq y_i + (1-a) \gamma_i
-	\end{align*} where $a$ is a binary variable.
-
-	The following plot illustrates the constraints described above.
-
-	\hspace*{10ex}\begin{tikzpicture}
-		\begin{axis}[
-			xlabel={$y_i$},
-			ylabel={$\hat{y}_i$},
-			xmin=-2, xmax=2,
-			ymin=-2, ymax=2,
-			axis lines=center,
-			samples=100, 
-			unit vector ratio=1 1 1, scale=1, xtick   = {-2,2},
-			xticklabels = {$-\gamma_i$,$\gamma_i$},
-			yticklabels = {},
-			]
-			\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
-			\addplot[blue, thick] {0};
-
-			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
-			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
-
-			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
-			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
-		\end{axis}
-	\end{tikzpicture}
-
-   Based on above constraints, we can sketch this simplified model:
-\begin{enumerate}
-	\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable $y_i$. 
-	\item Set constraints for input nodes.
-	\item Set linear constraints . In this case, since the meaning of $y_i$ is $x_i-x'_i$, this constraints will not use the bias.
-	\item Between pre- and post- activation nodes, set the MILP constraint described above.
-\end{enumerate}
-
-	The key point is that, although this model sets 3 variables (and their binary variables) for each node in the network, only $y_i$  contributes to the final results, and we can ignore $x_i,x_i'$ (and their binary variables) during the optimization.
-
-	As a result, we can relax the binary variables used to $\hat{x}_i = \ReLU(x_i)$ and $\hat{x}'_i = \ReLU(x'_i)$.
-
-	Now the simplified model contains the same number of binary variables as the MILP model for local robustness.
-Hence this model runs much faster compared to the previous one.
-The trade-off is lower accuracy compared to the first model under unlimited time.
-In practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
-
-%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
-%	
-	\subsection{Improving the Accuracy of the Simplified Model}
-	We can improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.
-
-%	(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
-
-%	The exact constraints for $$ \begin{align*}
-%		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-%		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
-%	\end{align*} 
-%	
-%	
-%	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
-
-	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
-	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
-	\begin{align*}
-		& \begin{aligned}
-			y_i + x'_i &\leq a\beta_i        &\quad\quad
-			y_i + x'_i &\geq (1-a)\alpha_i \\
-			x'_i       &\leq a'\beta_i       & 
-			x'_i       &\geq (1-a')\alpha_i \\
-			\hat{y}_i  &\leq a\gamma_i       &
-			\hat{y}_i  &\geq -a'\gamma_i \\
-			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
-			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
-			\hat{y}_i  &\leq -x'_i + a\beta_i &
-			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
-			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
-			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
-		\end{aligned}
-	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
-
-	Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
-
-%	\begin{align*}
-%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
-%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
-%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-%	\end{align*}
-
-	The following plot illustrates the constraints described above.
-
-	\hspace*{-10ex}
-	\begin{tikzpicture}
-		\begin{axis}[	axis on top, xlabel = \(x'_i\),
-			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
-			set layers=default,
-			xmax = 4, xmin = -4,
-			ymax = 1, ymin = -1,		
-			zmax = 1, zmin = -1,
-			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
-			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
-			xticklabels = {$0$}, ztick   = {-1,0,1},
-			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
-			view={35}{14},
-			]
-			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates {
-				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
-			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
-			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
-
-		\end{axis}
-	\end{tikzpicture}
-
-	In practice, when we relax the constraints for a node, we will convert $a_i$ and $a_i'$ to continuous variables together.
-In principle, we can also choose to change  only one of those two binary variables.
-
-%	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
-Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
-
-	A special relaxation approach of this model is to treat the binary variables $a'$ appearing in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$ as distinct variables, and relax only the latter.
-
-	\section{Experimental Evaluation}
-
-	We implemented our code in Python 3.8.
-	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
-
-	We will do experiments on two networks for MNIST dataset and another physical model.
-Two MNIST have the same structure.
-They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons.
-One of them is a normally trained neural network and another is for trained for adversarial robustness.
-We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI.
-As the name shows MNIST $5\times 100$-DiffAI has a better robustness.
-The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.
-
-	\subsection{Comparison of different modelings}
-
-	\subsection{Comparison of different scoring algorithms}
-
-	\section{Conclusion}
-
-	TODO
-
-	\bibliography{references}
-	\bibliographystyle{plain}
-
-	\bigskip
-
-	\appendix
-
 \end{document}

### 2025-07-25 AAAI2026/Lipitschz.tex
correct the version
add tables

--- 2025-05-21 lipschitz 2025/Lipitschz.tex
@@
 
+	\input{introduction}
+
 	\section{Notations and Preliminaries}
@@
 		\end{align*}		
-
 	\end{definition}
@@
 
-	\begin{proof} We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
+	\begin{proof} We fix the number $N\in\mathbb{Z}^+$ and assume that we have two inputs $x, y$.
 
@@
 
-	\subsection{Comparison of different modelings}
+	\subsection{Experiment results for Pipe system}
 
-	\subsection{Comparison of different scoring algorithms}
+	For the pipe system, to find a example of large difference on outputs is one of the main aims.
+
+	The network of Pipe system is relatively simple and in the tests, we will open all $\ReLU$ nodes.
+
+	We will compare the results of different modeling methods.
+
+\begin{tabular}{|l|l|l|l|l|}\hline
+L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
+	1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
+	3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
+	3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
+	2v,open 100 &     0.046719 &  0.024364 &                      0.024436 & 10922 \\\hline
+\end{tabular}
+
+	And
+
+	\begin{tabular}{|l|l|l|l|l|}\hline
+	 L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
+		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
+		3v,open 100 &     0.041382 &  0.025433 &                      0.016638 &  1082 \\\hline
+		3v,open 100 &      0.03496 &  0.027206 &                      0.021607 & 14523 \\\hline
+		3v,open 100 &     0.032906 &  0.027655 &                      0.016481 & 72126 \\\hline
+		2v,open 100 &     0.041787 &  0.022805 &                      0.022882 &  1082 \\\hline
+		2v,open 100 &     0.035964 &  0.023563 &                      0.023608 & 14523 \\\hline
+	\end{tabular}
+
+	\subsection{Experiment results for MNIST}
+
+	\begin{tabular}{|l|l|l|l|l|l|}\hline
+		& Method & Bound & Solution & Real & Time \\\hline
+		54 & 2v,open 75x5 & 21.013510 & 8.467282 & 0.222900 & 43200 \\\hline
+		55 & 2v,open 90x5 & 12.009719 & 3.440846 & 0.258480 & 43200 \\\hline
+		56 & 2v,open 97x5 & 20.646000 & 1.915210 & 0.372200 & 129626 \\\hline
+		57 & 2v,open 100x5 & 8.760835 & nan & nan & 43200 \\\hline
+		58 & 2v,open 100x5 & 8.257397 & nan & nan & 259200 \\\hline
+		59 & 1v,open 75x5 & 17.472430 & 0.908984 & 0.091740 & 43200 \\\hline
+	\end{tabular}
 

### 2025-07-25 AAAI2026/Lipitschz.tex
title + abstract

@@
 
-\title{Global case}
+\title{Order reduction and partial MILP models \\
+for Global Robustness of DNNs.}
 \date{}
@@
 	\begin{abstract}
-		TODO
+Most DNNs are brittle to small perturbations. Extensive works have thus been performed to verify robustness for DNNs.
+However, these works mostly consider local robustness, i.e. in the neighborhood of an image.
+While local robustness is useful to have an idea how often non robust images happen, 
+by repeating the verification on 1000 or 10000 pre obtained images, 
+the main shortcoming is that we have no guarantee that a specific new incoming image, e.g. in a video feed, is robust:
+The verification process takes too long and requires too much ressources to be performed online on embedded systems.
+
+In this paper, we consider global robustness, that is guarantees on robustness irrespective of a (set of) local images.
+For that, we consider the switch of values between the different decision classes of a DNN due to a given perturbation. 
+The verification question is much more complex, as the number of complex variables doubles (from the deviation image to the image and its deviation).
+Further, the values each neuron can take is no more in a small neighbourhood. 
+Therefore, the global verification process becomes much harder.
+To obtain useable bounds, we use the most accurate process to date, 
+using partial MILP (pMILP) methodology. We propose several such pMILP models for global robustness, with different trade-offs.
+Last, we use order reduction techniques to reduce the space of image considered, 
+avoiding unrealistic inputs, by using linear PCA. 
+This results into usable bounds, allowing in real time to certify robustness for $>83\%$ of incoming images 
+in the MNIST benchmark, as well as for a surrogate computing the hidden plastic strain 
+associated to a deformation map of a pipe.
 	\end{abstract}
@@
 
-	\input{introduction}
+	%\input{introduction}
 

### 2025-07-26 AAAI2026/Lipitschz.tex
abstract

@@
 \title{Order reduction and partial MILP models \\
-for Global Robustness of DNNs.}
+for certifying Robustness of DNNs globally.}
 \date{}
@@
 The verification question is much more complex, as the number of complex variables doubles (from the deviation image to the image and its deviation).
-Further, the values each neuron can take is no more in a small neighbourhood. 
+Further, the values each neuron can take is no more in a small neighborhood. 
 Therefore, the global verification process becomes much harder.
 To obtain useable bounds, we use the most accurate process to date, 
-using partial MILP (pMILP) methodology. We propose several such pMILP models for global robustness, with different trade-offs.
+using partial MILP (pMILP) methodology. 
+We propose several such pMILP models for global robustness, with different trade-offs.
 Last, we use order reduction techniques to reduce the space of image considered, 
 avoiding unrealistic inputs, by using linear PCA. 
-This results into usable bounds, allowing in real time to certify robustness for $>83\%$ of incoming images 
-in the MNIST benchmark, as well as for a surrogate computing the hidden plastic strain 
+This results into usable bounds, allowing in real time to certify robustness for $>87\%$ of incoming images 
+in the MNIST benchmark for a L1 perturbation of $\frac{1}{2}$, as well as for a surrogate computing the hidden plastic strain 
 associated to a deformation map of a pipe.

### 2025-07-26 AAAI2026/introduction.tex
intro (from ATVA)

--- 2025-07-16 ATVA 2025/Final_version/introduction.tex
@@
 \begin{table}[t!]
-	\vspace{-1.0cm}
+%	\vspace{-1.0cm}
 	\centering
-		\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
-The 6 first DNNs are complex instances.
-The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
-	}
 	\begin{tabular}{||l|c|c|c||c|c|c||}
 		\hline
-		Network & nbr & Accuracy {$^*$}  & Upper  {$^*$}& $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
+		Network & nbr & Accur.  & Upper & $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
 		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
@@
 	\end{tabular}
-	\begin{minipage}{0.9\linewidth}
-		\footnotesize
-		{\textsuperscript{*} Accuracy means the accuracy of the network itself on test set, and Upper Bound is 100\% the percentage of unsafe examples.} \\
-	\end{minipage}
+%	\begin{minipage}{0.9\linewidth}
+%		\footnotesize
+%		{\textsuperscript{*} Accuracy means the accuracy of the network itself on test set, and Upper Bound is 100\% the percentage of unsafe examples.} \\
+%	\end{minipage}
+		\caption{Accuracy of DNN (class predicted vs ground truth), upper bound on robustness (robustness attacks found on remaining images), and $\%$ of images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
+The 6 first DNNs are complex instances.
+The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
+	}
 \label{table_beta}
-		\vspace{-0.5cm}
+%		\vspace{-0.5cm}
 \end{table}
@@
 
-\begin{table}[t!]
+\begin{table}[b!]
 	\centering
-	\vspace{-0.35cm}
-	\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
-		%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-		Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
-		}
+%	\vspace{-0.35cm}
 	\begin{tabular}{||l|c|c||c|c|c||}
@@
 	\end{tabular}
-	\vspace{-0.65cm}
+%	\vspace{-0.65cm}
+	\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
+		%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
+		Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
+		}
 \label{table_complete}
@@
 
-\newpage
+%\newpage
 

### 2025-07-26 AAAI2026/Lipitschz.tex
intro (from ATVA)
abstract

@@
 
-In this paper, we consider global robustness, that is guarantees on robustness irrespective of a (set of) local images.
+In this paper, we consider {\em global} robustness, that is guarantees on robustness not restricted to a set of local images.
 For that, we consider the switch of values between the different decision classes of a DNN due to a given perturbation. 
@@
 avoiding unrealistic inputs, by using linear PCA. 
-This results into usable bounds, allowing in real time to certify robustness for $>87\%$ of incoming images 
-in the MNIST benchmark for a L1 perturbation of $\frac{1}{2}$, as well as for a surrogate computing the hidden plastic strain 
+This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $\frac{1}{2}$, as well as for a surrogate computing the hidden plastic strain
 associated to a deformation map of a pipe.
@@
 
-	%\input{introduction}
+	\input{introduction}
 

### 2025-07-26 AAAI2026/Lipitschz.tex
abstract

@@
 However, these works mostly consider local robustness, i.e. in the neighborhood of an image.
-While local robustness is useful to have an idea how often non robust images happen, 
-by repeating the verification on 1000 or 10000 pre obtained images, 
-the main shortcoming is that we have no guarantee that a specific new incoming image, e.g. in a video feed, is robust:
-The verification process takes too long and requires too much ressources to be performed online on embedded systems.
+While local robustness is useful to have an idea how often non robust images happen, by repeating the verification on 1000 or 10000 pre-obtained images, the main shortcoming is that we have no guarantee that a specific new incoming image, e.g.
+in a video feed, is robust: The verification process takes too long and requires too much resources to be performed online on embedded systems.
 
-In this paper, we consider {\em global} robustness, that is guarantees on robustness not restricted to a set of local images.
-For that, we consider the switch of values between the different decision classes of a DNN due to a given perturbation. 
-The verification question is much more complex, as the number of complex variables doubles (from the deviation image to the image and its deviation).
+In this paper, we consider {\em global} robustness, that is, guarantees not restricted to a set of local images.
+For that, we consider {\em bounds} on the switch of values between the different decision classes of a DNN due to a given perturbation.
+The verification question is much harder than local robustness, as the number of complex variables doubles (from the deviation image to the image and its deviation).
 Further, the values each neuron can take is no more in a small neighborhood.
-Therefore, the global verification process becomes much harder.
-To obtain useable bounds, we use the most accurate process to date, 
-using partial MILP (pMILP) methodology. 
-We propose several such pMILP models for global robustness, with different trade-offs.
-Last, we use order reduction techniques to reduce the space of image considered, 
-avoiding unrealistic inputs, by using linear PCA. 
-This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $\frac{1}{2}$, as well as for a surrogate computing the hidden plastic strain
-associated to a deformation map of a pipe.
+Therefore, the global verification process is very complex.
+To obtain useable bounds, we develop several novel partial MILP models for global robustness, with different trade-offs.
+Last, we use order reduction techniques to reduce the space of images considered, avoiding unrealistic inputs, by using linear PCA.
+This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $0.5$, as well as for a surrogate computing the hidden plastic strain associated to a deformation map of a pipe.
 	\end{abstract}

### 2025-07-27 AAAI2026/abstract.tex
Add abstract.tex & use it in main

Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research into methods to verify their robustness. However, most existing methods focus on local robustness, i.e., the model's behavior in the neighboorhood of an specific input (e.g., an image). While local robustness enables to evaluate how often non robust images appear in a large dataset (e.g., by repeating the verification on 10000 pre-obtained images), it fails to provide guarantees on whether a new specific incoming image is robust, e.g., real-time inputs in a video stream. Moreover, current verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.

In this paper, we consider {\em global} robustness, that is, guarantees not restricted to a set of local images. We focus on deriving {\em bounds} on the variation of output values across different decision classes of a DNN under a given perturbation. This global verification problem is significantly more complex than local robustness, as the number of variables doubles (from the deviation image to the image and its deviation). Further, the values each neuron can take are no longer limited to a small neighborhood. To obtain usable bounds, we develop several novel partial MILP models for global robustness, with different trade-offs. Last, we use order reduction techniques to reduce the space of images considered, avoiding unrealistic inputs, by using principal component analysis (PCA). Hence, we are able to certify in real time the robustness for 87\% of incoming images in the MNIST benchmark for an $\ell_1$-perturbation of 0.5, as well as for a surrogate computing the latent plastic strain associated with a pipe deformation map.

### 2025-07-28 AAAI2026/Lipitschz.tex
Add abstract.tex & use it in main
Update Lipitschz.tex
update template (need to adjust content, especailly tables)

@@
-\documentclass{llncs}
-\usepackage{hyperref}
-\usepackage{url}
+%File: anonymous-submission-latex-2026.tex
+\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
+\usepackage[submission]{aaai2026}  % DO NOT CHANGE THIS
+\usepackage{times}  % DO NOT CHANGE THIS
+\usepackage{helvet}  % DO NOT CHANGE THIS
+\usepackage{courier}  % DO NOT CHANGE THIS
+\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
+\usepackage{graphicx} % DO NOT CHANGE THIS
+\urlstyle{rm} % DO NOT CHANGE THIS
+\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\frenchspacing  % DO NOT CHANGE THIS
+\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
+\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
+%
+% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \pagestyle{plain}
@@
 \input{math_commands.tex}
-%\usepackage[latin9]{inputenc}
-%\usepackage[T1]{fontenc}
-\usepackage{float}
-\usepackage{wrapfig}
 \usepackage{lineno}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
 \usepackage{subcaption}
@@
 \captionsetup{compatibility=false}
-% \usepackage{esint}
-\usepackage{array}
 \usepackage{epstopdf}
@@
 \usepackage{pgfplots}
-\usepackage{url}
 \usepackage{tikz}
@@
 \usepackage{array}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
 \usetikzlibrary{positioning, arrows.meta,calc}
+\usepackage{newfloat}
+\usepackage{listings}
+\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
+\lstset{%
+	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
+	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
+	aboveskip=0pt,belowskip=0pt,%
+	showstringspaces=false,tabsize=2,breaklines=true}
+\floatstyle{ruled}
+\newfloat{listing}{tb}{lst}{}
+\floatname{listing}{Listing}
+%
+% Keep the \pdfinfo as shown here. There's no need
+% for you to add the /Title and /Author tags.
+\pdfinfo{
+	/TemplateVersion (2026.1)
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{Order reduction and partial MILP models \\
+	for certifying Robustness of DNNs globally.}
+\date{}
+\author{
+	%Authors
+	% All authors must be in the same font size and format.
+	Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
+	AAAI Style Contributions by Pater Patel Schneider,
+	Sunil Issar,\\
+	J. Scott Penberthy,
+	George Ferguson,
+	Hans Guesgen,
+	Francisco Cruz\equalcontrib,
+	Marc Pujol-Gonzalez\equalcontrib
+}
+\affiliations{
+	%Afiliations
+	\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
+	% If you have multiple authors and multiple affiliations
+	% use superscripts in text and roman font to identify them.
+	% For example,
 
+	% Sunil Issar\textsuperscript{\rm 2},
+	% J. Scott Penberthy\textsuperscript{\rm 3},
+	% George Ferguson\textsuperscript{\rm 4},
+	% Hans Guesgen\textsuperscript{\rm 5}
+	% Note that the comma should be placed after the superscript
+
+	1101 Pennsylvania Ave, NW Suite 300\\
+	Washington, DC 20004 USA\\
+	% email address must be in roman text type, not monospace or sans serif
+	proceedings-questions@aaai.org
+	%
+	% See more examples next
+}
+
+%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
+\iffalse
+\title{My Publication Title --- Single Author}
+\author {
+	Author Name
+}
+\affiliations{
+	Affiliation\\
+	Affiliation Line 2\\
+	name@example.com
+}
+\fi
+
+\iffalse
+%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
+\title{My Publication Title --- Multiple Authors}
+\author {
+	% Authors
+	First Author Name\textsuperscript{\rm 1},
+	Second Author Name\textsuperscript{\rm 2},
+	Third Author Name\textsuperscript{\rm 1}
+}
+\affiliations {
+	% Affiliations
+	\textsuperscript{\rm 1}Affiliation 1\\
+	\textsuperscript{\rm 2}Affiliation 2\\
+	firstAuthor@affiliation1.com, secondAuthor@affilation2.com, thirdAuthor@affiliation1.com
+}
+\fi
+
+\newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}
 \newcommand{\vW}{\boldsymbol{W}}
@@
 
-\title{Order reduction and partial MILP models \\
-for certifying Robustness of DNNs globally.}
-\date{}
+% REMOVE THIS: bibentry
+% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
+\usepackage{bibentry}
+% END REMOVE bibentry
 
@@
 	\maketitle
-	\linenumbers
+
 	\begin{abstract}
+		\input{abstract.tex}
+		\iffalse
 		Most DNNs are brittle to small perturbations. Extensive works have thus been performed to verify robustness for DNNs.
@@
 		This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $0.5$, as well as for a surrogate computing the hidden plastic strain associated to a deformation map of a pipe.
+		\fi
 	\end{abstract}
@@
 
-	\begin{proof} We fix the number $N\in\mathbb{Z}^+$ and assume that we have two inputs $x, y$.
+	\textbf{Proof.} We fix the number $N\in\mathbb{Z}^+$ and assume that we have two inputs $x, y$.
 
@@
 	This ends the proof.
-	\end{proof}
+	\hfill $\square$
 
@@
 	\end{proposition}
-	\begin{proof}
+
+	\textbf{Proof.}
 	We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
@@
 
-	\section{Conclusion}
-
-	TODO
+	\bigskip
 
 	\bibliography{references}
-	\bibliographystyle{plain}
-
-	\bigskip
-
-	\appendix
 

### 2025-07-28 AAAI2026/introduction.tex
intro

--- 2025-07-16 ATVA 2025/Final_version/introduction.tex
@@
 This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools.
-While the verification engines are generic, the benchmarks usually focus on local robustness, i.e.
-given a DNN, an image and a small neighbourhood around this image, is it the case that all the images in the neighbourhood are classified in the same way.
-For the past 5 years, VNNcomp has focused on rather easy instances, that can be solved within tens of seconds (the typical hard time-out is 300s).
-For this reason, DNN verifiers in the past years have mainly focused on optimizing for such easy instances.
-Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT
-\cite{pyrat}, respectively 4th, 3rd and 2{nd} of the last VNNcomp'24 \cite{VNNcomp24}
-and 5th, 2{nd} and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2{nd} in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
-We will thus compare mainly with $\alpha,\beta$-CROWN experiments as gold standard in the following\footnote{GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-CROWN on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us}.
+Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT \cite{pyrat} MnBAB \cite{ferrari2022complete}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
 
-\begin{table}[t!]
-	\vspace{-1.0cm}
-	\centering
-		\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image.
-The 6 first DNNs are complex instances.
-The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
-	}
-	\begin{tabular}{||l|c|c|c||c|c|c||}
-		\hline
-		Network & nbr & Accuracy {$^*$}  & Upper  {$^*$}& $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
-		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
-		MNIST 5$\times$100 & 500 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
-		$\epsilon = 0.026$ & ReLU & &  & 6.9s &  18.9s &  1026s  \\  \hline
-		MNIST 5$\times$200 & 1000 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
-		$\epsilon = 0.015$ & ReLU & &  & 6.5s &  16.6s &  930s  \\  \hline
-		MNIST 8$\times$100 & 800 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
-		$\epsilon = 0.026$ & ReLU &  &  & 7.2s &  20.1s &  930s  \\  \hline
-		MNIST 8$\times$200 & 1600 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
-		$\epsilon = 0.015$ & ReLU & &  & 6.8s &  18.2s &  1083s  \\  \hline
-		MNIST 6$\times$500 & 3000 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
-		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
-		CIFAR CNN-B--Adv &  16634  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
-		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
-		CIFAR ResNet &   107496  & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
-		$\epsilon = 8/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
-	\end{tabular}
-	\begin{minipage}{0.9\linewidth}
-		\footnotesize
-		{\textsuperscript{*} Accuracy means the accuracy of the network itself on test set, and Upper Bound is 100\% the percentage of unsafe examples.} \\
-	\end{minipage}
-	\label{table_beta}
-		\vspace{-0.5cm}
-\end{table}
+The benchmarks usually focus on local robustness, i.e.
+given a DNN, an image and a small neighborhood around this image, is it the case that all the images in the neighborhood are classified in the same way.
 

### 2025-07-28 AAAI2026/Lipitschz.tex
update
lip
adjust the tables

@@
 	\hspace*{-10ex}
-	\begin{tikzpicture}
+	\begin{tikzpicture}[scale=0.65]
 		\begin{axis}[	axis on top, xlabel = \(x'_i\),
@@
 	\begin{tabular}{|l|l|l|l|l|}\hline
-		L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
+		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
 		1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
@@
 	\begin{tabular}{|l|l|l|l|l|}\hline
-		L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
+		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
 		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline

### 2025-07-28 AAAI2026/Lipitschz.tex
update tables

@@
 		\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
-		r(b)\Delta(b), & for $W_{bz} > 0$ \\
-		\max(\Delta(b),-\sol(b)), & for $W_{bz} < 0$ and $\sol(b)\geq0$\\
-		\max(0,\Delta(b)+\sol(b)), & for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
+			r(b)\Delta(b),&for $W_{bz} > 0$ \\
+			\max(\Delta(b),-\sol(b)),&for $W_{bz} < 0$ and $\sol(b)\geq0$\\
+			\max(0,\Delta(b)+\sol(b)),&for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
 		\end{subnumcases}
@@
 	\begin{proposition}
-		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
+		$0 \leq \Improve\max^z(a) \leq \Utility\max^z(a)$. 
 	\end{proposition}
@@
 		& \begin{aligned}
-			y_i + x'_i &\leq a\beta_i        &\quad\quad
-			y_i + x'_i &\geq (1-a)\alpha_i \\
+			y_i + x'_i &\leq a\beta_i        &
+			y_i &+ x'_i \geq (1-a)\alpha_i \\
 			x'_i       &\leq a'\beta_i       & 
@@
 
+	\vspace*{1ex}
+
 	\begin{tabular}{|l|l|l|l|l|}\hline
-		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
+		$\|d\|_1\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
 		1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
@@
 
+		\vspace*{1ex}
+
 	And
 
+		\vspace*{1ex}
+
 	\begin{tabular}{|l|l|l|l|l|}\hline
-		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
+		$\|d\|_1\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
 		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
@@
 
-	\begin{tabular}{|l|l|l|l|l|l|}\hline
-		& Method & Bound & Solution & Real & Time \\\hline
-		54 & 2v,open 75x5 & 21.013510 & 8.467282 & 0.222900 & 43200 \\\hline
-		55 & 2v,open 90x5 & 12.009719 & 3.440846 & 0.258480 & 43200 \\\hline
-		56 & 2v,open 97x5 & 20.646000 & 1.915210 & 0.372200 & 129626 \\\hline
-		57 & 2v,open 100x5 & 8.760835 & nan & nan & 43200 \\\hline
-		58 & 2v,open 100x5 & 8.257397 & nan & nan & 259200 \\\hline
-		59 & 1v,open 75x5 & 17.472430 & 0.908984 & 0.091740 & 43200 \\\hline
+	\begin{tabular}{|l|l|l|l|l|}\hline
+		 Method & Bound & Solution & Real & Time \\\hline
+		 2v,open 75x5 & 21.0135 & 8.4672& 0.2229 & 43200 \\\hline
+		2v,open 90x5 & 12.0097 & 3.4408 & 0.2584 & 43200 \\\hline
+	 2v,open 97x5 & 20.6460 & 1.9152 & 0.3722 & 129626 \\\hline
+	 2v,open 100x5 & 8.7608 & nan & nan & 43200 \\\hline
+		 2v,open 100x5 & 8.2573 & nan & nan & 259200 \\\hline
+		 1v,open 75x5 & 17.4724 & 0.9089 & 0.0917 & 43200 \\\hline
 	\end{tabular}

### 2025-07-28 AAAI2026/abstract.tex
intro

@@
 Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research into methods to verify their robustness.
-However, most existing methods focus on local robustness, i.e., the model's behavior in the neighboorhood of an specific input (e.g., an image).
-While local robustness enables to evaluate how often non robust images appear in a large dataset (e.g., by repeating the verification on 10000 pre-obtained images), it fails to provide guarantees on whether a new specific incoming image is robust, e.g., real-time inputs in a video stream.
-Moreover, current verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.
+Most existing methods focus on local robustness, i.e., the model's behavior in the neighborhood of a specific input.
+While local robustness enables to evaluate how often non robust images appear in a large dataset (e.g., by repeating the verification on 1000 pre-obtained images), it fails to provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream.
+Moreover, most verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.
 
@@
 To obtain usable bounds, we develop several novel partial MILP models for global robustness, with different trade-offs.
-Last, we use order reduction techniques to reduce the space of images considered, avoiding unrealistic inputs, by using principal component analysis (PCA).
-Hence, we are able to certify in real time the robustness for 87\% of incoming images in the MNIST benchmark for an $\ell_1$-perturbation of 0.5, as well as for a surrogate computing the latent plastic strain associated with a pipe deformation map.
+Last, we use order reduction techniques to reduce the space of inputs considered, avoiding unrealistic images, by using principal component analysis (PCA).
+This results into
+the real-time  certification of the robustness for $87\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of 0.5, as well as for a surrogate computing the
+%latent
+plastic strain associated with a pipe deformation map.

### 2025-07-28 AAAI2026/introduction.tex
intro

@@
 
-The benchmarks usually focus on local robustness, i.e.
-given a DNN, an image and a small neighborhood around this image, is it the case that all the images in the neighborhood are classified in the same way.
+The benchmarks usually focus on {\em local} robustness, i.e.
+given a DNN, an image and a small neighborhood around this image, is it the case that all the images in the neighborhood are classified in the same way by the DNN?
+The neighborhood is provided by a maximal perturbation of the input image, often an $L_0$ perturbation, i.e.
+every subpixel of the input image can vary in a very small range, typically
+$\frac{2}{255}$ (that is 2 levels of grey/blue/right/green), as $L_0$ is perfectly linear and perturbations of subpixels are independent.
+While the $L_0$ norm is the easiest to handle, it is not necessarily the most meaningful perturbation.
+More importantly, verification tools for local robustness are hard to be used in a real-time decision making pipeline: considering an autonomous car with a video feed from the dashboard, it is computationally too intensive to certify in few ms images of the feed to e.g.
+skip non robust images (or operate in a degraded mode - e.g.
+driving safely) and only consider certified robust ones for the decision-making process.
 
-$\alpha,\beta$-CROWN, as well as BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete},
-rely on Branch and Bound technique (BaB), which call BaB once per output neuron (few calls).
-In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities.
-For easy instances, BaB is highly efficient as all branches can be pruned early.
-However, BaB methods hit a complexity barrier when verifying more complex instances, due to an overwhelming number of branches (exponential in the height of branches that cannot be pruned as they need too many variables to branch over).
-This can be clearly witnessed on the verification-agnostic \cite{SDPFI} DNNs of Table \ref{table_beta} (6 first DNNs), where vastly enlarging the time-out only enables to verify few more \% of images, leaving a large proportion ($20\%-50\%$) of images undecided despite the large runtime.
-As argued in \cite{SDPFI}, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks, and such cases should be treated as well as DNNs specifically trained to be easy to verify, e.g.
-using \cite{TrainingforVerification}.
-Verification-agnostic are the simplest instances to demonstrate the scaling behavior of BaB on complex instances using standard local robustness implementations.
-Other complex instances include solving non-local properties, e.g.
-global robustness computed through Lipschitz bound \cite{lipshitz}, etc.
-The bottom line is that one cannot expect to have only easy instances to verify.
-It is important to notice that the number of activation functions of the DNN is a poor indicator of the hardness of the instance, e.g.
-$5 \times 100$ with 500 ReLUs is far more complex to certify ($50\%$ undecided images) than 100 times bigger ResNet ($0\%$ undecided images), see Table \ref{table_beta}.
+\smallskip
 
-%Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-CROWN \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neigbhour with a different decision.
-One issue is however that easy instances are trained specifically to be easier to verify e.g.
-using DiffAI \cite{DiffAI} PGD \cite{PGD}, which can impact the accuracy of the network, i.e.
-answering correctly to an unperturbed input.
-For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct {\color{blue}\cite{prima}} (the other $71\%$ are thus not  tested).
-While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g.
-very hard verification instances into hard verification instances.
-Also, verification questions intrinsically harder than local robustness, such as bounding on Lipschitz constants globally or asking several specification at once, makes the instance particularly harder.
-Last, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks.
-The bottom line is, one cannot expect only {\em easy} verification instances: {\em hard} verification instances need to be explored as well.
+In this paper, we consider {\em global} robustness, that is we do not restrict the certification process to the neighborhood of an input.
+We propose a two steps procedure.
+The first step, performed offline once,
+computes global bounds on the shift between 
+output values of different decision classes due to the perturbation. That is, considering decision classes $A$ and $B$ and perturbation $\varepsilon$, compute 
+{\em global bound} $B^\varepsilon_{A,B} \geq \max_{I,I', |I-I'| \leq \epsilon}(value_{I}(A) - value_{I}(B) + value_{I'}(B) - value_{I'}(A))$, where $value_{J}(X)$ is the output value of class $X \in \{A,B\}$ for input image $J \in \{I,I'\}$.
+Notice that as
+$I,I',A,B$ have symetrical roles, we can choose $B^\varepsilon_{A,B} = B^\varepsilon_{B,A}$. Also, as $I,I'$ have symetrical role, the minimum value is exactly $-$ the maximum value. 
+%Hence, if we have $n$ decision classes, we only have to compute $n (n-1)/2$ bounds. 
+Bound $B^\varepsilon_{A,B}$ needs to be computed once for a DNN, 
+and it is valid over the whole input space; compared with $k$ computations for {\em local robustness}, once for each of the $k$ input images, with results only valid for these $k$ images.
 
-%In this paper, we focused on the 6 {\em hard} ReLU-DNNs that have been previously tested in \cite{crown}, which display a large gap ($\geq 20\%$) between images that can be certified by $\alpha,\beta$-CROWN and the upper bound when we remove those which can be falsified.
-In turns, hard instances does not necessarily mean very large DNNs, the smallest of these hard DNNs having only 500 hidden neurons, namely MNIST 5$\times$100.
-We first dwelve into the scaling of $\alpha,\beta$-CROWN, to understand how longer Time-Out (TO) affects the number of undecided images and the runtime.
-Table \ref{table_beta} reveals that even allowing for 200 times longer time outs only improves the verification from 2\% to 8\%, leaving a considerable $20\%-50\%$ gap of undecided images, while necessitating vastly longer runtime (300s-1000s in average per instance).
+The second step is real-time, being performed with the DNN inference of the image $I$ considered: it suffices to consider the class $A$ with the highest output value $value_{I}(A)$, and check whether for every other class $B \neq A$,
+$value_{I}(A) - value_{I}(B) > B^\varepsilon_{A,B}$. 
+If this is the case, then we are certified that image $I$ is robust for perturbation $\varepsilon$, because $\varepsilon$-perturbed image $I'$ could at most get  $value_{I'}(B) \leq B^\varepsilon_{A,B}  - (value_{I}(A) - value_{I}(B))  + value_{I'}(A) < value_{I'}(A)$, hence $A$ is also the predicted class for image $I'$.
+Otherwise, one could either skip image $I$ (in a video feed), or use safer degraded mode in the decision making process till a more trustable robust image is received.
 
-\begin{table}[b!]
-	\centering
-%	\vspace{-0.35cm}
-	\begin{tabular}{||l|c|c||c|c|c||}
-		\hline
-		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum &  Full MILP  \\ \hline
-		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $49\%$ & 40 \%    \\
-		$\epsilon = 0.026$ & &  &6200s &  4995s & 6100s
-		  \\  \hline
-		%  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $46\%$ & 37 \%    \\
-		%  TO=2000s & &  & 1250s  & 1194s & 1466s \\  \hline	
-	\end{tabular}
-%	\vspace{-0.65cm}
-	\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
-		%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
-		Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
-		}
-\label{table_complete}
-\end{table}
-
-Other standard non-BaB methods such as Marabou, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-CROWN, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image.
-It appeared pointless to test these verifiers on larger networks.
-
-%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}.
-
-%\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks,
-
-%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as
-
-%Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs;  It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
-
-%Our investigation delves into the core abstraction mechanisms integral to several prominent algorithms, such as Eran-DeepPoly \cite{deeppoly}, Linear Programming \cite{MILP}, PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete} and various implementations of ($\alpha$)($\beta$)-CROWN \cite{crown,xu2020fast}\footnote{\cite{VNNcomp} reports that $\alpha,\beta$-CROWN \cite{crown,xu2020fast} often surpasses in accuracy other competing techniques, even complete ones due to (even long) time-outs; It maintains completeness for smaller DNNs \cite{xu2020fast}, and showcases impressive efficiency for larger networks, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.}.
-The high-level approach followed by all these techniques is to compute lower or/and upper bounds for the values of neurons (abstraction on values) for inputs in the considered input region, and then finally conclude based on the bounds of neurons in the output layer.
-These tools are thus sound but not necessarily complete, i.e., when these tools certify a DNN to be robust for a particular image $I$, then the corresponding DNN is indeed robust but it may happen that the tool is unable to certify a DNN to be robust even though it actually is, because of bounds inaccuracies.
-	%To dig further into their incompleteness, we first remark that 
-	%Notice that complete methods exist \cite{Reluplex,katz2019marabou,SDPFI}, but they time-out on hard instances.
-In practice, the most accurate today's results are obtained using ($\alpha$)($\beta$)-CROWN \cite{crown}.
-%As a starting point, we sought to understand properties of DNNs that make them hard to verify.
-
-%Our key finding is a new notion of {\em compensations}, that explains why bounds are inaccurate.
-Formally, a {\em compensating pair of paths} $(\pi,\pi')$ between neurons $a$ and $b)$ is such that $w < 0 < w'$ for $w,w'$ the products of weights seen along $\pi$ and $\pi'$ respectively.
-Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with $(w+w') weight(a)$ by $\pi$ and $\pi'$.
-As $w,w'$ have opposite signs, they will compensate (partly) each other.
-The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$.
-However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which the efficient tools try to avoid because it is very time-consuming (combinatorial explosion as the problem is NP-hard \cite{Reluplex}).
-%; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust.
-
-Our main contributions address the challenges to verify {\em complex} instances efficiently, as current methods are not appropriate to verify such instances:
+Our main contributions address the challenges to compute the {\em global bounds} $B^\varepsilon(A,B)$, for $A,B$ output neurons of a DNN:
 \begin{enumerate}

### 2025-07-28 AAAI2026/abstract.tex
intro

@@
 Last, we use order reduction techniques to reduce the space of inputs considered, avoiding unrealistic images, by using principal component analysis (PCA).
-This results into
-the real-time  certification of the robustness for $87\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of 0.5, as well as for a surrogate computing the
+This results into the real-time  certification of the robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of 0.5, as well as for a surrogate computing the
 %latent

### 2025-07-28 AAAI2026/introduction.tex
intro

@@
 computes global bounds on the shift between 
-output values of different decision classes due to the perturbation. That is, considering decision classes $A$ and $B$ and perturbation $\varepsilon$, compute 
-{\em global bound} $B^\varepsilon_{A,B} \geq \max_{I,I', |I-I'| \leq \epsilon}(value_{I}(A) - value_{I}(B) + value_{I'}(B) - value_{I'}(A))$, where $value_{J}(X)$ is the output value of class $X \in \{A,B\}$ for input image $J \in \{I,I'\}$.
+output values of different decision classes due to the perturbation. That is, considering decision classes $C$ and $D$ and perturbation $\varepsilon$, compute 
+{\em global bound} $\beta^\varepsilon_{C,D} \geq \max_{I,I', |I-I'| \leq \epsilon}(value_{I}(C) - value_{I}(D) + value_{I'}(D) - value_{I'}(C))$, where $value_{J}(X)$ is the output value of class $X \in \{C,D\}$ for input image $J \in \{I,I'\}$.
 Notice that as
-$I,I',A,B$ have symetrical roles, we can choose $B^\varepsilon_{A,B} = B^\varepsilon_{B,A}$. Also, as $I,I'$ have symetrical role, the minimum value is exactly $-$ the maximum value. 
+$I,I',C,D$ have symetrical roles, we can choose $\beta^\varepsilon_{D,C} = \beta^\varepsilon_{C,D}$. Also, as $I,I'$ have symetrical role, the minimum value is exactly $-$ the maximum value. 
 %Hence, if we have $n$ decision classes, we only have to compute $n (n-1)/2$ bounds. 
-Bound $B^\varepsilon_{A,B}$ needs to be computed once for a DNN, 
+Bound $\beta^\varepsilon_{C,D}$ needs to be computed once for a DNN, 
 and it is valid over the whole input space; compared with $k$ computations for {\em local robustness}, once for each of the $k$ input images, with results only valid for these $k$ images.
 
-The second step is real-time, being performed with the DNN inference of the image $I$ considered: it suffices to consider the class $A$ with the highest output value $value_{I}(A)$, and check whether for every other class $B \neq A$,
-$value_{I}(A) - value_{I}(B) > B^\varepsilon_{A,B}$. 
-If this is the case, then we are certified that image $I$ is robust for perturbation $\varepsilon$, because $\varepsilon$-perturbed image $I'$ could at most get  $value_{I'}(B) \leq B^\varepsilon_{A,B}  - (value_{I}(A) - value_{I}(B))  + value_{I'}(A) < value_{I'}(A)$, hence $A$ is also the predicted class for image $I'$.
+The second step is real-time, being performed with the DNN inference of the image $I$ considered: it suffices to consider the class $C$ with the highest output value $value_{I}(C)$, and check whether for every other class $D \neq C$,
+$value_{I}(C) - value_{I}(D) > \beta^\varepsilon_{C,D}$. 
+If this is the case, then we are certified that image $I$ is robust for perturbation $\varepsilon$, because $\varepsilon$-perturbed image $I'$ could at most get  $value_{I'}(D) \leq \beta^\varepsilon_{C,D}  - (value_{I}(C) - value_{I}(D))  + value_{I'}(C) < value_{I'}(C)$, hence $C$ is also the predicted class for image $I'$.
 Otherwise, one could either skip image $I$ (in a video feed), or use safer degraded mode in the decision making process till a more trustable robust image is received.
 
-Our main contributions address the challenges to compute the {\em global bounds} $B^\varepsilon(A,B)$, for $A,B$ output neurons of a DNN:
+Our main contributions address the challenges to compute the {\em global bounds} $\beta^\varepsilon(C,D)$, for $C,D$ output neurons:
 \begin{enumerate}
@@
 
-	\item We revisit the idea from \cite{DivideAndSlide} to consider small calls to a partial MILP (pMILP) solver, i.e.
-with few binary variables encoding few ReLU functions exactly (other being encoded with more efficient but less accurate linear variables), to compute bounds for each neuron inductively, hence many ($O(n)$, the number of neuron) small calls, with a complexity exponential only in the few binary variables (Section 4).
-Compared to the few (one per output neuron) complex call to BaB, each with a worst case complexity exponential in the number of neurons of the DNN (which is far from the actual complexity thanks to pruning branches in BaB - but which can be too large as we shown in the 6 first DNNs of Table \ref{table_beta}).
-Two questions arise: how to select few very important ReLUs?, and is computing the bounds of intermediate neurons a good trade-off compared with the theoretical loss of accuracy due to selecting only some binary ReLUs?
-Answer to these questions were not looking very promising judging by previous attempt \cite{DivideAndSlide}, which was using a simple selection heuristic of nodes in the previous layer only.
+	\item Since the problem is a very hard verification problem, as the values each neuron can take is no more bound to a small neighborhood, we choose to follow the accurate MILP technique in \cite{ATVA25}.
+Technically, the number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed.
+	Recall that the worst case complexity of MILP is exponential in the number of binary variables.
+A straightforward MILP model would be to use the {\em classical MILP model} \cite{MILP} for each of these variables.
+While the full MILP model is exact, it is too computationally intensive to be run for anything but small DNNs.
+As explained in \cite{ATVA25}, many variables need to be linearly relaxed
+	to reach useable bounds.
+The main issue with the classical model is that its linear relaxations is extremely inaccurate, as the variables are independent of each other.
+Instead, we develop another exact MILP model,
+	called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}).
+We study and encode exactly how the diff variables evolve after passing through a ReLU (figure \ref{fig.2v}).
+In this model, the linear relaxation is much more accurate, as each
+	{\em diff variable} can be bounded 	after a ReLU as a function of the value of the {\em diff variables} before the ReLU.
+We propose 2 lighter models, namely the {\em "3v" model} which decouples one of the variable (less constraint means less accuracy), as well as an efficient {\em "1v" model} only considering the {\em diff variables} but forgetting the value of the perturbed neurons (with half the binary variables).
 
-	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, {\em global scoring ({\sf GS})} functions to choose important ReLUs (Section 5).
-These revealed to be much more accurate than the simple heuristic in
-	\cite{DivideAndSlide}.
-However, we also uncover that the {\em improvement function} that {\sf GS} tries to approximate depends heavily upon the mode of the ReLU function, and as this mode is unavailable to {\sf GS}, there are many cases in which {\sf GS} is far from the improvement (with both under or over-approximation of the improvement function).
+	\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation.
 
-	\item We thus designed a {\em novel solution-aware scoring ({\sf SAS})}, which uses the solution of a unique LP call, that provides the mode to consider (Section 6).
-Theoretically, we show that {\sf SAS} is always an over-approximation of the improvement (Proposition \ref{prop2}), which implies that a small {\sf SAS} value implies that the ReLU is unnecessary.
-Experimentally, we further show that {\sf SAS} is very close to the actual improvement, closer than {\sf GS}, and that overall, the accuracy from SAS is significantly better than {\sf GS}.
-Compared with the heuristic in \cite{DivideAndSlide},  {\sf SAS} is much more efficient ($\approx 6$ times less binary variables for same accuracy (Fig.
-\ref{fig_table3})).
-	%We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally (see Table.
-\ref{table.order}).
+	\item Results obtained on the full input space have several shortcomings: while the bounds are fully correct, they are also particularly pessimistic, as all inputs, including absolutely improbable ones very far away from anything the network has been trained on, need to be accounted for.
+Also, the runtime to obtain the bound is particularly long.
+Finally, when asking for worst-case
+	scenarios, improbable images are generated.
+To solve this problem, we restrict the input space to ignore all these improbable inputs, using model order reduction techniques from engineerial science \cite{aiware}.
 
-	\item Compared with many calls using full MILP, where all the ReLUs are encoded as binary variables, {\sf SAS} (and {\sf GS}) encode only a subset of ReLUs as binary and others as linear variables.
-The model in full MILP is fully accurate, while {\sf SAS} (and {\sf GS})
-	are abstractions, and thus much faster to solve. 
-	While full MILP is thus {\em asymptotically} more accurate than {\sf SAS} and {\sf GS}, {\em experimentally}, every reasonable time-out leads to much better practical accuracy of {\sf SAS} (and {\sf GS}) (see Fig.
-\ref{fig555}).
-
-	%	\item {\color{blue} We designed a novel Utility function to choose few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP).
-Specifically, the novelty of Utility resides in the use of the solution to an (efficient LP) solver on the node $z$ we want to bound.
-Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}).
-Because pMILP focuses on the {\em improvement} (binary - linear), it is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})) than previous attempts, which consider the generic {\em sensitivity} to this neuron.
-To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g.
-\cite{BaB,FSB}.}
-
-	\item For the second question, we propose a new verifier, called {\em Hybrid MILP}, invoking first 	$\alpha,\beta$-CROWN with short time-out to settle the easy instances.
-On those ({\em hard}) instances which are neither certified nor falsified, we call pMILP with few neurons encoded as binary variables.
-Experimental evaluation reveals that Hybrid MILP achieves a beneficial balance between accuracy and completeness compared to prevailing methods.
-It reduces the proportion of undecided inputs from $20-58\%$ ($\alpha,\beta$-CROWN with 2000s TO) to $8-15\%$, while taking a reasonable average time per instance ($46-420$s), Table \ref{table_hybrid}.
-It scales to fairly large networks such as CIFAR-10 CNN-B-Adv \cite{SDPFI}, with more than 2 million parameters.
-%We verify experimentally that the algorithm offers interesting trade-offs, by testing on local robustness for DNNs trained "naturally" (and thus difficult to verify).
-%KSM: I think this is a distraction in intro, so I suggest moving to later part
-% Overall, the worst case complexity of algorithm \ref{algo1} is lower than $O(N 2^K LP(N))$, where $N$ is the number of nodes of the DNN, $K$ the number of ReLU nodes selected as binary variable, and $LP(N)$ is the (polynomial time) complexity of solving a linear program representing a DNN with $N$ nodes.
-This complexity is an upper bound, as e.g.
-Gurobi is fairly efficient and never need to consider all of the $2^K$ ReLU configurations to compute the bounds.
-Keeping $K$ reasonably low thus provides an efficient algorithm.
-%By design, it will never run into a complexity wall (unlike the full MILP encoding), although it can take a while on large networks because of the linear factor $N$ in the number of nodes.
 \end{enumerate}

### 2025-07-28 AAAI2026/introduction.tex
intro

@@
 Technically, the number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed.
-	Recall that the worst case complexity of MILP is exponential in the number of binary variables.
+	Recall that the worst case complexity of MILP is exponential in the number of binary variables \cite{DivideAndSlide}.
 A straightforward MILP model would be to use the {\em classical MILP model} \cite{MILP} for each of these variables.
 While the full MILP model is exact, it is too computationally intensive to be run for anything but small DNNs.
-As explained in \cite{ATVA25}, many variables need to be linearly relaxed
-	to reach useable bounds.
+As explained in \cite{ATVA25}, many variables need to be linearly relaxed to reach useable bounds.
 The main issue with the classical model is that its linear relaxations is extremely inaccurate, as the variables are independent of each other.
-Instead, we develop another exact MILP model,
-	called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}).
+Instead, we develop another exact MILP model, called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}).
 We study and encode exactly how the diff variables evolve after passing through a ReLU (figure \ref{fig.2v}).
@@
 	\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation.
+The chosen number of binary variables depends upon the complexity of the DNN as well as the targeted runtime.
+
+   \item  In terms of perturbations, we consider conjunctions of $L_0$ and $L_1$ norms, which allows to accurately describe perturbations.
+For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_0$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$ perturbation).
+While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, we explain how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary to encode $L1$ perturbations).
 
@@
 Also, the runtime to obtain the bound is particularly long.
-Finally, when asking for worst-case
-	scenarios, improbable images are generated.
-To solve this problem, we restrict the input space to ignore all these improbable inputs, using model order reduction techniques from engineerial science \cite{aiware}.
+Finally, when computing worst-case
+	pairs (image, perturbation), improbable images are generated, hence these  are not meaningful.
+To solve this problem, we restrict the input space to ignore improbable inputs, using model order reduction techniques from engineering science \cite{aiware}.
+Specifically, we use Principal Component Analysis (PCA) to reduce the space to a linear input space.
+We choose the number of dimensions of the space to equal the accuracy of the DNN on the reduced space.
+	%(using a projection to the reduced space then the inverse projection to obtain a very similar image understandable by the DNN). 
+	On the MNIST benchmark, this means 20 linear dimensions to match the $97\%$ accuracy of the DNN we considered, instead of the 768 dimensions of the full image space.
+Using PCA, which is linear, makes it easy to specify perturbations on the actual image (where it is meaningful) rather than on the reduced space.
 
+\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in real time that $86\%$ of the images are robust for an $L_1$ perturbation of $0.5$, resp.
+$53\%$ for an $L_1$ perturbation of $1$.
+We finally experimented our MILP models for {\em regression} tasks, considering a DNN surrogate built from a slow physical finite element model, providing the deformation and the plastic strain of a pipe \cite{aiware}.
+The DNN has been learnt on a reduced order basis already of dimension 10, from thousands of input dimensions.
+For regression, the aim is to understand if the DNN surrogate that has been learnt is brittle to small perturbations, which could make it unfaithful to the physical model.
+Here we want to obtain bounds (which is what our models provide), as well as generating worst-case (image,perturbation) pair close to the bound, where the strain is particularly different, that can be run in the physical model to understand whether the DNN surrogate is faithful.
+Our tool was helpful to provide limited bounds, as well as almost matching worst-case (image,perturbation) pair that was confirmed in the physical model.
+
+\item In both cases, the best bounds were obtained using the "3v" model, as the theoretically more accurate "2v" model did not converge enough even after a very large timeout.
+Still, when trying to produce worst case pairs (image, perturbation), which is somehow easier than certifying bounds as heuristics to guide towards a solution can be used, the "2v" model found worser-case solutions.
+Last, the "1v" model produced bounds as good as the "2v" models and much faster than the "3v" models, although slightly larger.
+That is, all 3 models we propose have favorable trade-offs in different contexts.
 \end{enumerate}

### 2025-07-28 AAAI2026/introduction.tex
intro

@@
 More importantly, verification tools for local robustness are hard to be used in a real-time decision making pipeline: considering an autonomous car with a video feed from the dashboard, it is computationally too intensive to certify in few ms images of the feed to e.g.
-skip non robust images (or operate in a degraded mode - e.g.
-driving safely) and only consider certified robust ones for the decision-making process.
+skip non-robust images and only consider certified robust images for the decision-making process.
 
@@
 {\em global bound} $\beta^\varepsilon_{C,D} \geq \max_{I,I', |I-I'| \leq \epsilon}(value_{I}(C) - value_{I}(D) + value_{I'}(D) - value_{I'}(C))$, where $value_{J}(X)$ is the output value of class $X \in \{C,D\}$ for input image $J \in \{I,I'\}$.
-Notice that as
-$I,I',C,D$ have symetrical roles, we can choose $\beta^\varepsilon_{D,C} = \beta^\varepsilon_{C,D}$. Also, as $I,I'$ have symetrical role, the minimum value is exactly $-$ the maximum value. 
+%Notice that as $I,I',C,D$ have symetrical roles, we can choose $\beta^\varepsilon_{D,C} = \beta^\varepsilon_{C,D}$.
+Also, as $I,I'$ have symetrcal role, the minimum value is exactly $-$ the maximum value.
 %Hence, if we have $n$ decision classes, we only have to compute $n (n-1)/2$ bounds. 
@@
 If this is the case, then we are certified that image $I$ is robust for perturbation $\varepsilon$, because $\varepsilon$-perturbed image $I'$ could at most get  $value_{I'}(D) \leq \beta^\varepsilon_{C,D}  - (value_{I}(C) - value_{I}(D))  + value_{I'}(C) < value_{I'}(C)$, hence $C$ is also the predicted class for image $I'$.
-Otherwise, one could either skip image $I$ (in a video feed), or use safer degraded mode in the decision making process till a more trustable robust image is received.
+Otherwise, one could either skip image $I$ (in a video feed), or use safer degraded mode in the decision making process till a trustable robust image is received.
 
@@
 
-	\item Since the problem is a very hard verification problem, as the values each neuron can take is no more bound to a small neighborhood, we choose to follow the accurate MILP technique in \cite{ATVA25}.
-Technically, the number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed.
+	\item Since the problem is a very hard verification problem (the values each neuron can take is not bound to a small neighborhood), we follow the accurate MILP technique in \cite{ATVA25}.
+The number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed.
 Recall that the worst case complexity of MILP is exponential in the number of binary variables \cite{DivideAndSlide}.
@@
 	{\em diff variable} can be bounded 	after a ReLU as a function of the value of the {\em diff variables} before the ReLU.
-We propose 2 lighter models, namely the {\em "3v" model} which decouples one of the variable (less constraint means less accuracy), as well as an efficient {\em "1v" model} only considering the {\em diff variables} but forgetting the value of the perturbed neurons (with half the binary variables).
+We propose 2 lighter models, namely the {\em "3v" model} which decouples one of the variable (less constraint means less accuracy), as well as an efficient {\em "1v" model} only considering the {\em diff variables} but forgetting the value of the perturbed neurons (with half the (binary) variables).
 
@@
 For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_0$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$ perturbation).
-While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, we explain how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary to encode $L1$ perturbations).
+While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, we explain how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
 
@@
 For regression, the aim is to understand if the DNN surrogate that has been learnt is brittle to small perturbations, which could make it unfaithful to the physical model.
-Here we want to obtain bounds (which is what our models provide), as well as generating worst-case (image,perturbation) pair close to the bound, where the strain is particularly different, that can be run in the physical model to understand whether the DNN surrogate is faithful.
+Here we want to obtain bounds (which is what our models provide), as well as generating worst-case (image,perturbation) pair, where the strain is particularly different, close to the bound, and that can be run in the physical model to understand whether the DNN surrogate is faithful.
 Our tool was helpful to provide limited bounds, as well as almost matching worst-case (image,perturbation) pair that was confirmed in the physical model.
@@
 Last, the "1v" model produced bounds as good as the "2v" models and much faster than the "3v" models, although slightly larger.
-That is, all 3 models we propose have favorable trade-offs in different contexts.
+That is, all 3 MILP models we propose have favorable trade-offs in different contexts.
 \end{enumerate}
 
-Limitation: We consider DNNs employing the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}, with updated MILP models e.g.
+Limitation: We consider the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}, with updated MILP models e.g.
 for maxpool.

### 2025-07-28 AAAI2026/Lipitschz.tex
intro
experiments

@@
-%File: anonymous-submission-latex-2026.tex
 \documentclass[letterpaper]{article} % DO NOT CHANGE THIS
@@
 
+	\begin{figure}[b!]
+		\centering
 	\hspace*{10ex}\begin{tikzpicture}
@@
 	\end{tikzpicture}
+\caption{The possible values of $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ depending on $\val(y_i) = \val(x_i)-\val(x'_i)$.}
+	\label{fig.1v}
+\end{figure}
 
@@
 
-	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
-	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
-	\begin{align*}
-		& \begin{aligned}
-			y_i + x'_i &\leq a\beta_i        &
-			y_i &+ x'_i \geq (1-a)\alpha_i \\
-			x'_i       &\leq a'\beta_i       & 
-			x'_i       &\geq (1-a')\alpha_i \\
-			\hat{y}_i  &\leq a\gamma_i       &
-			\hat{y}_i  &\geq -a'\gamma_i \\
-			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
-			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
-			\hat{y}_i  &\leq -x'_i + a\beta_i &
-			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
-			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
-			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
-		\end{aligned}
-	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
-
-	Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
-
-	%	\begin{align*}
-		%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
-		%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-		%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
-		%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-		%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-		%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-		%	\end{align*}
-
-	The following plot illustrates the constraints described above.
-
+	\begin{figure}[b!]
+		\centering
 	\hspace*{-10ex}
@@
 	\end{tikzpicture}
+	\caption{The outcome $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ 
+	depending on $\val(y_i) = \val(x_i)-\val(x'_i)$ and on $\val(x'_i)$.}
+	\label{fig.2v}
+\end{figure}
+
+Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
+	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
+	\begin{align*}
+		& \begin{aligned}
+			y_i + x'_i &\leq a\beta_i        &
+			y_i &+ x'_i \geq (1-a)\alpha_i \\
+			x'_i       &\leq a'\beta_i       & 
+			x'_i       &\geq (1-a')\alpha_i \\
+			\hat{y}_i  &\leq a\gamma_i       &
+			\hat{y}_i  &\geq -a'\gamma_i \\
+			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
+			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
+			\hat{y}_i  &\leq -x'_i + a\beta_i &
+			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
+			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
+			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
+		\end{aligned}
+	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
+
+Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
+
+	%	\begin{align*}
+		%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
+		%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
+		%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
+		%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
+		%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
+		%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
+		%	\end{align*}
+
+	The following plot illustrates the constraints described above.
 
@@
 
-	\subsection{Experiment results for Pipe system}
+	\subsection{Experiment results for robustness (MNIST)}
+
+	\begin{table}[h!]
+	\begin{tabular}{|l|c|c|c|c|}\hline
+		 $L_1 \leq 0.5$ & Bound & Solution & Real & Time \\\hline
+		 2v,open 75x5 & 21.0135 & 8.4672& 0.2229 & 43200 \\\hline
+		2v,open 90x5 & 12.0097 & 3.4408 & 0.2584 & 43200 \\\hline
+	 2v,open 97x5 & 20.6460 & 1.9152 & 0.3722 & 129626 \\\hline
+	 2v,open 100x5 & 8.7608 & nan & nan & 43200 \\\hline
+		 2v,open 100x5 & 8.2573 & nan & nan & 259200 \\\hline
+		 1v,open 75x5 & 17.4724 & 0.9089 & 0.0917 & 43200 \\\hline
+	\end{tabular}
+	\caption{Comparison of "1v", "3v" and "2v" models on the full dimension MNIST DNN.
+with a fixed timeout of 1000s, 14523s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
+\end{table}
+
+	\subsection{Experiment results for regression (Pipe strain)}
 
@@
 
+	\iffalse
+	\begin{table}[h!]
 	\begin{tabular}{|l|l|l|l|l|}\hline
-		$\|d\|_1\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
-		1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
+		$L_1\leq 0.83$ &        Bound $\downarrow$ &  Solution $\uparrow$ &      Real $\uparrow$ &  Time \\\hline
+		1v,open 100 &     {\bf 0.035613} &  0.035613 &                       0.01288 & 10608 \\\hline
 		3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
-		3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
-		2v,open 100 &     0.046719 &  0.024364 &                      0.024436 & 10922 \\\hline
+		%3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
+		2v,open 100 &     0.046719 &  0.024364 &  {\bf 0.024436} & 10922 \\\hline
 	\end{tabular}
+	\caption{Comparison of 1v,2v and 3v models on the pipe system with a fixed timeout of 10.000s.}
+\end{table}
+\fi
 
-		\vspace*{1ex}
-
-	And
-
-		\vspace*{1ex}
-
+	\begin{table}[h!]
 	\begin{tabular}{|l|l|l|l|l|}\hline
-		$\|d\|_1\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
-		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
-		3v,open 100 &     0.041382 &  0.025433 &                      0.016638 &  1082 \\\hline
-		3v,open 100 &      0.03496 &  0.027206 &                      0.021607 & 14523 \\\hline
-		3v,open 100 &     0.032906 &  0.027655 &                      0.016481 & 72126 \\\hline
-		2v,open 100 &     0.041787 &  0.022805 &                      0.022882 &  1082 \\\hline
-		2v,open 100 &     0.035964 &  0.023563 &                      0.023608 & 14523 \\\hline
+		$L_1\leq 0.83$ &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ &  Time \\\hline \hline
+		1v, $100 \times 1$ &     {\bf 0.0356} &  0.0356 & 0.0191 &   1000s \\\hline
+		3v, $100 \times 3$&     0.0414 &  0.0254 &  0.0166 &  1000s \\\hline
+		2v, $100 \times 2$&     0.0418 &  0.0229 &   {\bf 0.0229} &  1000s \\\hline \hline
+		3v, $90 \times 3$&      ?? &  ?? &  ?? & 14523s \\\hline
+		3v, $100 \times 3$&      {\bf 0.0350} &  0.0272 &  0.0216 & 14523s \\\hline
+		2v, $90 \times 2$&     ?? &  ?? &   ?? & 14523s \\\hline
+		2v, $100 \times 2$&     0.0360 &  0.0236 &    {\bf 0.0236} & 14523s \\\hline \hline
+		3v, $100 \times 3$&     {\bf 0.0329} &  0.0277 &  0.0165 & 72126s \\\hline
+		2v, $100 \times 2$&     ?? &  ?? &  {\bf ??} & 72126s \\\hline
 	\end{tabular}
-
-	\subsection{Experiment results for MNIST}
-
-	\begin{tabular}{|l|l|l|l|l|}\hline
-		 Method & Bound & Solution & Real & Time \\\hline
-		 2v,open 75x5 & 21.0135 & 8.4672& 0.2229 & 43200 \\\hline
-		2v,open 90x5 & 12.0097 & 3.4408 & 0.2584 & 43200 \\\hline
-	 2v,open 97x5 & 20.6460 & 1.9152 & 0.3722 & 129626 \\\hline
-	 2v,open 100x5 & 8.7608 & nan & nan & 43200 \\\hline
-		 2v,open 100x5 & 8.2573 & nan & nan & 259200 \\\hline
-		 1v,open 75x5 & 17.4724 & 0.9089 & 0.0917 & 43200 \\\hline
-	\end{tabular}
+	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14523s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
+\end{table}
 

### 2025-07-28 AAAI2026/Lipitschz.tex
experiments

@@
 
-	\begin{figure}[b!]
+	\begin{figure}[t!]
 		\centering
@@
 	\begin{table}[h!]
-	\begin{tabular}{|l|c|c|c|c|}\hline
-		 $L_1 \leq 0.5$ & Bound & Solution & Real & Time \\\hline
-		 2v,open 75x5 & 21.0135 & 8.4672& 0.2229 & 43200 \\\hline
-		2v,open 90x5 & 12.0097 & 3.4408 & 0.2584 & 43200 \\\hline
-	 2v,open 97x5 & 20.6460 & 1.9152 & 0.3722 & 129626 \\\hline
-	 2v,open 100x5 & 8.7608 & nan & nan & 43200 \\\hline
-		 2v,open 100x5 & 8.2573 & nan & nan & 259200 \\\hline
-		 1v,open 75x5 & 17.4724 & 0.9089 & 0.0917 & 43200 \\\hline
+	\begin{tabular}{|l|c|c|c|c|}\hline\hline
+		$L_1\leq 0.5$ &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ &  Time \\\hline \hline
+		1v, $375 \times 1$ & 17.4724 & 0.9089  ?? & 0.0917 & 43200s \\\hline 
+		2v, $375 \times 2$ & 21.0135 & 8.4672& 0.2229 & 43200s \\\hline		
+		2v, $450 \times 2$ & 12.0097 & 3.4408 & {\bf 0.2584} & 43200s \\\hline
+		1v, $500 \times 1$ & ?? & ?? & ?? & 43200s \\\hline 
+		3v, $500 \times 3$ & ?? & ?? & ?? & 43200s \\\hline 
+	 2v, $500 \times 2$ & {\bf 8.7608} & nan & nan & 43200s \\\hline\hline
+
+	 2v, $485 \times 2$ & 20.6460 & 1.9152 & {\bf 0.3722} & 130000s \\\hline\hline
+
+		 2v, $500 \times 2$ & {\bf 8.2573} & nan & nan & 260000s \\\hline\hline
+
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models on the full dimension MNIST DNN.
-with a fixed timeout of 1000s, 14523s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
+	\caption{Comparison of "1v", "3v" and "2v" models 
+	to obtain bounds on $\beta^{0.5}_{0,1}$ on the {\bf full dimension} MNIST DNN, for timeouts of 43200s, 130000s and 260000s, where 375, 450, 485 or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+\end{table}
+
+On the full space, we reach bounds of $8.2$ (on $\beta^{.5}_{0,1}$), which is too pessimistic as it allows to certify 0 image robust.
+The worst-case found by the "2v" $485 \times 2$ binary variables after 130000s only displays a difference of
+$0.37$, $20 \times$ away from the bound found.
+
+\begin{figure*}[t!]
+	\centering
+\includegraphics[scale=0.5]{image.png} \hspace{0.8cm}
+\includegraphics[scale=0.5]{perturb.png}
+\caption{An improbable image and its perturbation (difference around x=11, y=18) 
+with maximal $\beta^{.5}_{0,1}=0.37$ for MNIST as obtained by the "2v" $485 \times 2$ model in full 758 dimension image space.}
+\end{figure*}
+
+\paragraph{Reduced space}
+
+We now consider a PCA model order reduction to avoid considering improbable images, 
+speed up obtaining the bounds, and obtain less pessimistic bounds.
+We settle on 20 orders, as the MNIST DNN considered run on a images obtained from projecting to the reduced order and projected back to the full dimension 
+display the same accuracy of $97$\% as the DNN on the original images, meaning no accuracy is lost from reducing to 20 dimensions, which is the only thing which matters.
+On such a reduced space, bounds obtained are much more precise, and one can certify robustness of images online.
+
+	\begin{table}[h!]
+	\begin{tabular}{|l|c|c|c|c|}\hline\hline
+		$L_1\leq 0.5$ &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ &  Time \\\hline \hline
+
+1v, $?? \times 1$ & ?? & ?? & ?? & ?? \\\hline 
+		3v, $?? \times 3$ & ?? & ?? & ?? & ?? \\\hline 
+	 2v, $?? \times 2$ & ?? & ?? & ?? & ?? \\\hline\hline
+
+		1v, $?? \times 1$ & ?? & ?? & ?? & ?? \\\hline 
+		3v, $?? \times 3$ & ?? & ?? & ?? & ?? \\\hline 
+	 2v, $?? \times 2$ & ?? & ?? & ?? & ?? \\\hline\hline
+
+	\end{tabular}
+	\caption{Comparison of "1v", "3v" and "2v" models 
+	to obtain bounds on $\beta^{0.5}_{0,1}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of ??s, and ??s , where ??,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+\end{table}
+
+\begin{figure*}[t!]
+	\centering
+\includegraphics[scale=0.5]{redimage.png} \hspace{0.8cm}
+\includegraphics[scale=0.5]{redperturb.png}
+\caption{An image and its perturbation from the 20-dimension reduced space with maximal $\beta^{.5}_{0,1}=0.17$ for MNIST as obtained by the "2v" $500 \times 2$ model.}
+\end{figure*}
+
+\begin{table}[h!]
+	\begin{tabular}{|l|c|c|c|c|}\hline\hline
+		model &    $L_1\leq 0.5$ & $L_1\leq 1$ & $L_1\leq 1.5$ &  $L_1\leq 2$ \\\hline \hline
+		1v, $? \times 1$ & $80 \%$ & $32\%$ & $7\%$ & $0\%$ \\\hline
+		3v, $? \times 3$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
+		2v, $? \times 2$ & ?? & ?? & ?? & ?? \\\hline \hline
+	\end{tabular}
+	\caption{Comparison of "1v", "3v" and "2v" models 
+	in the percentage of images they can certify in real-time for different values of $L_1$ perturbations.}
 \end{table}
@@
 	For the pipe system, to find a example of large difference on outputs is one of the main aims.
+
+	\begin{figure*}[t!]
+\includegraphics[scale=0.5]{deform.png} \hspace{0.8cm}
+\includegraphics[scale=0.5]{strain.png}
+\caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" $100 \times 2$ model.}
+\end{figure*}
 
@@
 	\begin{table}[h!]
-	\begin{tabular}{|l|l|l|l|l|}\hline
+	\begin{tabular}{|l|c|c|c|c|}\hline\hline
 		$L_1\leq 0.83$ &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ &  Time \\\hline \hline
-		1v, $100 \times 1$ &     {\bf 0.0356} &  0.0356 & 0.0191 &   1000s \\\hline
+		1v, $100 \times 1$ &     {\bf 0.0356} &  $0.0356$ & $0.0191$ &   1000s \\\hline
 		3v, $100 \times 3$&     0.0414 &  0.0254 &  0.0166 &  1000s \\\hline
@@
 		3v, $100 \times 3$&     {\bf 0.0329} &  0.0277 &  0.0165 & 72126s \\\hline
-		2v, $100 \times 2$&     ?? &  ?? &  {\bf ??} & 72126s \\\hline
+		2v, $100 \times 2$&     ?? &  ?? &  {\bf ??} & 72126s \\\hline\hline
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14523s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
+	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14523s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.
+	L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}
 \end{table}
 
-	\bigskip
+	\newpage
+
+	\hfill
+
+	\newpage
 

### 2025-07-29 AAAI2026/Lipitschz.tex
update table
notation

@@
 
-	\section{Notations and Preliminaries}
-
-	In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-	capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{crown}.
-	To simplify the notations, we restrict the presentation to feed-forward, 
-	fully connected ReLU Deep Neural Networks (DNN for short), where the activation function is $\ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-	$\ReLU(x)=x$ for $x \geq 0$ and $\ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
-
-	%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
-
-	%\subsection{Neural Network and Verification}
-
-	% testtesttesttest
-	An $\ell$-layer DNN is provided by $\ell$ weight matrices 
-	$\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
-	and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
-	We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
-	$d_0$ the input dimension, and $d_\ell$ the output dimension.
-
-	Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-	denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
-	\begin{align*}
-		\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
-		\hat{\boldsymbol{z}}^{i} = \ReLU({\boldsymbol{z}}^i).
-	\end{align*}
-
-	The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
-	$\boldsymbol{z}$ is called pre-activation values, 
-	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
-
-	Concerning the verification problem, we focus on the global-robustness question.
-Global robustness asks to determine how the output of a neural network will be affected under a certain kind of small perturbations to any possible input.
-In this view, Lipschitz continuity is a good characterization of global robustness.
-
-	\section{Global robustness and Lipschitz constant}
-
-	Recall the definition of Lipschitz continuity:
-	under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
-	\begin{align*}
-		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
-	\end{align*} 
-	In our practice, when we need global robustness, we will compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
-		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
-	\end{align} And this will lead to the following definition
-
-	\begin{definition}[$\varepsilon$-diff bound]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
-
-		For a number $\varepsilon\in\mathbb{R}$, an $\varepsilon$-diff bound $D_\varepsilon$ is a number such that for any inputs $x,y$: \begin{align*}
-			|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D_\varepsilon \cdot \varepsilon
-		\end{align*}
-
-	\end{definition}
-
-	From $\varepsilon$-diff bound, we cannot directly obtain a Lipschitz bound for the function, but we can get the following weaker bound:
-
-	\begin{definition}[Lipschitz above $\varepsilon$ constant]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
-
-		For a number $\varepsilon\in\mathbb{R}$, a Lipschitz above $\varepsilon$ constant  $K_\varepsilon$,  is a number such that for any inputs $x,y$: \begin{align*}
-			|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot |x-y|\\
-			|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot \varepsilon\\
-		\end{align*}		
-	\end{definition}
-
-	\begin{proposition}
-
-		Suppose $D$ is an $\varepsilon$-diff bound for $f(x)$. Then for any $N\in\mathbb{Z}^+$, $D\frac{N+1}{N}$ is a Lipschitz about $N\varepsilon$ constant.
-
-		That is, for any two inputs $x,y$, if \begin{align*}
-			|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D \cdot \varepsilon,
-		\end{align*} then 	 \begin{align*}
-			|x-y|\geq N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
-			|x-y|<N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot N\varepsilon\\
-		\end{align*}
-	\end{proposition}
-
-	\textbf{Proof.} We fix the number $N\in\mathbb{Z}^+$ and assume that we have two inputs $x, y$.
-
-	The first case, $|x-y|\geq N\varepsilon$.
-Then we assume $|x-y| \in [M\varepsilon ,  (M+1)\varepsilon]$ for another integer $M\geq N$.
-Then we can divide the line segment between $x, y$ into $M+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{M+1} = y$ such that $|x_i-x_{i+1}| \leq \varepsilon$ and apply the definition of $\varepsilon$-diff bound $D$ for each pieces:\begin{align*}
-		|f(x)-f(y)| &= |f(x_{M+1})-f(x_M)+\cdots+f(x_1)-f(x_0)|\\
-		&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
-		&\leq D\varepsilon + \cdots +D\varepsilon = (M+1)D\varepsilon
-	\end{align*}
-	Hence,\begin{align*}
-		|f(x)-f(y)| &\leq (M+1)D\varepsilon \leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
-		&= D\cdot\frac{M+1}{M} |x-y|	\leq   D\cdot\frac{N+1}{N} |x-y|		
-	\end{align*}
-	The second case, $|x-y|< N\varepsilon$.
-Similarly we can divide the line segment between $x, y$ into $N$ pieces and then $|f(x)-f(y)|\leq D N\varepsilon\leq |f(x)-f(y)|\leq D \frac{N+1}{N} N\varepsilon$.
-
-	This ends the proof.
-	\hfill $\square$
-
-	In practice, Lipschitz above $\varepsilon$ constant is already sufficient, since in most cases we care about the absolute difference under input perturbations, not the ratio.
-By combining the above proposition, the computation of $\varepsilon$-diff bound can satisfy our aim.
-
-	Moreover, we have one more proposition connecting $\varepsilon$-diff bound and Lipschitz above $\varepsilon$ constant.
-
-	\begin{proposition}
-		For any $N\in\mathbb{Z}^+$, suppose for any $a$ in $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$, $D$ is an $a$-diff bound for $f(x)$.
-
-		Then $D\frac{N+1}{N}$ is a Lipschitz about $\varepsilon$ constant:\begin{align*}
-			|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
-			|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot \varepsilon\\
-		\end{align*}
-	\end{proposition}
-
-	\textbf{Proof.}
-	We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
-
-	For the case that $|x-y|<\varepsilon$, this is trivial by definition.
-
-	For the case that $|x-y|\geq \varepsilon$, there exists a sum $x_1+x_2+\cdots+x_n$ by numbers from (allowing repetitions) $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$ such that \begin{align*}
-		\varepsilon \leq x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon \leq |x-y| \leq x_1+x_2+\cdots+x_n
-	\end{align*}
-	By assumption, divide the line segment from $x$ to $y$ into pieces according to $x_1, x_2,\cdots,x_n$, then we will have $$|f(x)-f(y)|\leq Dx_1+Dx_2+\cdots+Dx_n.$$
-
-	Hence,\begin{align*}
-		\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
-		& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})= D \frac{N+1}{N}\\
-	\end{align*}
-	This ends the proof.
-	\hfill $\square$
-
-	\section{pMILP for local robustness}
-
-	\subsection{MILP and LP encodings for DNNs}
-
-	First we introduce some concepts for local robustness question.
-
-	Mixed Integer Linear Programming (MILP) value abstraction is a complete (but inefficient) method. 
-	For an unstable neuron $n$ that its value $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$, the value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one 
-	integer variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
-
-	\vspace{-0.4cm}
-	\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \UB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\LB(n) \cdot (1-a)
-		\label{eq11}
-	\end{equation}
-
-	%For all $x \in [\LB(n),\UB(n)] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
-The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$.
-This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
-However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous integer variables and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
-
-	The global structure is as follows, using Gurobi as an example:
-	\begin{enumerate}
-		\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable. 
-		\item Set constraints for input nodes.
-		\item For each pre-activation node in a hidden layer (and each output node), set linear constraints relating them to the post-activation or input nodes in the previous layer they connect to.
-		\item Between pre- and post- activation nodes, set the MILP constraint described above.
-	\end{enumerate} We use $\mathcal{M}$ to denote the whole MILP model.
-In practice, we may only consider the network up to a certain hidden layer.
-In that case, the pre-activation nodes of that layer serve as the output nodes of the model $\mathcal{M}$.
-
-	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
-As solving LP instances is polynomial time, this optimization is significantly more efficient.
-However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
-This approach is termed the {\em LP abstraction}.
-We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.
-
-	\subsection{partial MILP}
-
-	We will use {\em partial MILP} (pMILP for short, see \cite{DivideAndSlide}) to get trade-offs between accuracy and runtime. Here, we extract the explanation from paper CITE.
-
-	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the partial MILP based on $X$ to compute neuron $n$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding, where variable $a$ is:
-	\begin{itemize}
-		\item binary for neurons in $X$ (exact encoding of the ReLU),
-		\item linear for neurons not in $X$ (linear relaxation).
-	\end{itemize}
-	We will denote above case by MILP$_X$ or $\mathcal{M}_X$. Informally, we say that a node is opened if it is in $X$.
-
-	If $X$ covers all unstable neurons, then MILP$_X$ is exact. But then the time cost may be very large (exponential growth).
-
-	To reduce the runtime, we will limit the size of subset $X$.
-This a priori hurts accuracy.
-To recover some of this accuracy, we use an iterative approach: computing lower and upper bounds $\LB,\UB$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
-
-	\subsection{SAS}
-
-	In pMILP, to decide the set $X$, we introduce the method {\em Solution-Aware Scoring} (SAS)
-	to evaluate accurately how opening a ReLU impacts the accuracy. Again, here we use the definition from paper CITE. For details and explanation, see CITE.
-
-	Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
-For each node $n<z$, we denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$: $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$; and we denote $(\sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$ a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
-Moreover,  we define the function
-	$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
-	accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
-	compared with using only LP.
-
-	First, SAS will call solvers to compute the LP model to get a solution, which is reasonably fast as there is no binary variables.
-
-	Next, for a neuron $b$ on the layer before layer $\ell_z$, we define:
-
-	\vspace{-0.4cm}
-	$$\Utility\_\max\nolimits^z(b) = W_{bz} \times (\sol(\hat{b})- \ReLU(\sol(b)))$$
-	\vspace{-0.4cm}
-
-	And for a neuron $a$ two layers before $\ell_z$, 
-	$b$ denoting neurons in the layer $\ell$ just before $\ell_z$.
-	Recall the rate $r(b)=\frac{\max(0,\UB(b))}{\max(0,\UB(b))-\min(0,\LB(b))} \in [0,1]$.
-	We define:
-
-	\begin{flalign*}
-		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})&&\\
-		\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})&&\\	
-	\end{flalign*}
-
-	\vspace{-1.2cm}
-
-		\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
-			r(b)\Delta(b),&for $W_{bz} > 0$ \\
-			\max(\Delta(b),-\sol(b)),&for $W_{bz} < 0$ and $\sol(b)\geq0$\\
-			\max(0,\Delta(b)+\sol(b)),&for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
-		\end{subnumcases}
-
-	\begin{flalign*}
-		\Utility\_\max\nolimits^z(a) &= \Delta(z) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})&&
-	\end{flalign*}
-
-	From paper CITE, we know that $\Utility$ is a safe overapproximation in the sense of following proposition:
-
-	\begin{proposition}
-		$0 \leq \Improve\max^z(a) \leq \Utility\max^z(a)$. 
-	\end{proposition}
+	\input{notation}
 
@@
 		3v, $? \times 3$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
-		2v, $? \times 2$ & ?? & ?? & ?? & ?? \\\hline \hline
+		2v, $? \times 2$ & 84\% & 51\% & 16\% & 4\% \\\hline \hline
 	\end{tabular}
@@
 		3v, $100 \times 3$&     {\bf 0.0329} &  0.0277 &  0.0165 & 72126s \\\hline
-		2v, $100 \times 2$&     ?? &  ?? &  {\bf ??} & 72126s \\\hline\hline
+		2v, $100 \times 2$&     0.03375 &  0.0244 &  {\bf 0.0245} & 72126s \\\hline\hline
 	\end{tabular}

### 2025-07-29 AAAI2026/notation.tex
notation

--- 2025-05-21 lipschitz 2025/Lipitschz.tex
@@
-\documentclass{llncs}
-\usepackage{hyperref}
-\usepackage{url}
-\pagestyle{plain}
-\usepackage{threeparttable}
-\input{math_commands.tex}
-%\usepackage[latin9]{inputenc}
-%\usepackage[T1]{fontenc}
-\usepackage{float}
-\usepackage{wrapfig}
-\usepackage{lineno}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{tabularx}
-\usepackage{cases}
-\captionsetup{compatibility=false}
-% \usepackage{esint}
-\usepackage{array}
-\usepackage{epstopdf}
-\usepackage{placeins}
-\usepackage{pgfplots}
-\usepackage{url}
-\usepackage{tikz}
-\usepackage{calc}
-\usepackage{array}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usetikzlibrary{positioning, arrows.meta,calc}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand{\vW}{\boldsymbol{W}}
-\newcommand{\val}{{\textrm{value}}}
-\newcommand{\Val}{{\textrm{value}}}
-\newcommand{\MILP}{{\textrm{MILP}}}
-\newcommand{\LP}{{\textrm{LP}}}
-\newcommand{\Improve}{\mathrm{Improve}}
-\newcommand{\Utility}{\mathrm{SAS}}
-\newcommand{\Sol}{\mathrm{Sol}}
-\newcommand{\sol}{\mathrm{sol}}
-\newcommand{\UB}{\mathrm{UB}}
-\newcommand{\LB}{\mathrm{LB}}
-\newcommand{\ub}{\mathrm{ub}}
-\newcommand{\lb}{\mathrm{lb}}
-\newcommand{\B}{\mathrm{B}}
-\usepackage{amsmath, amssymb, amsfonts}
-\newcommand{\ReLU}{\mathrm{ReLU}}
-\newcommand{\CMP}{{\textrm{CMP}}\ }
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
-\newcommand{\toolname}{Hybrid MILP}
-
-\title{Global case}
-\date{}
-
-\begin{document}
-
-	\maketitle
-	\linenumbers
-	\begin{abstract}
-		TODO
-	\end{abstract}
-
-	\section{Introduction}
-
 \section{Notations and Preliminaries}
@@
 
-	\begin{proof} We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
+	\textbf{Proof.} We fix the number $N\in\mathbb{Z}^+$ and assume that we have two inputs $x, y$.
 
@@
 	\begin{proposition}
-		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
+		$0 \leq \Improve\max^z(a) \leq \Utility\max^z(a)$. 
 	\end{proposition}
-
-	\section{Modeling for global robustness}
-
-	\subsection{Using Two Identical Models}
-	The most straightforward way is to use two identical MILP models, i.e., to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (and their own constraints) plus some extra constraints:
-	\begin{enumerate}
-		\item Add constraints for connecting input nodes $\mathcal{M},\mathcal{M}'$ to meet the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon$.
-		\item Set the optimization objective as the difference between two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (because we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
-	\end{enumerate}
-	This large model contains twice as many binary variables as $\mathcal{M}$.
-The computational cost of solving an MILP model grows roughly exponentially with the number of binary variables, and hence it will cost much more time.
-
-We may relax some constraints (by changing binary variables to continuous variables) as in the case of local robustness.
-However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which motivates us to explore other modeling approaches.
-
-	\subsection{A Simplified model}
-
-	To avoid above problem, we introduce a simplified model that is to use one variable $y_i$ to represent the difference of each two variables: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
-
-	Given  $\gamma_i$ be the upper bound of $y_i$, the constraints for $\hat{y}_i$ are the follows:\begin{align*}
-	\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
-	\hat{y}_i &\geq (a-1) \gamma_i           &\quad \hat{y}_i &\leq y_i + (1-a) \gamma_i
-	\end{align*} where $a$ is a binary variable.
-
-	The following plot illustrates the constraints described above.
-
-	\hspace*{10ex}\begin{tikzpicture}
-		\begin{axis}[
-			xlabel={$y_i$},
-			ylabel={$\hat{y}_i$},
-			xmin=-2, xmax=2,
-			ymin=-2, ymax=2,
-			axis lines=center,
-			samples=100, 
-			unit vector ratio=1 1 1, scale=1, xtick   = {-2,2},
-			xticklabels = {$-\gamma_i$,$\gamma_i$},
-			yticklabels = {},
-			]
-			\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
-			\addplot[blue, thick] {0};
-
-			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
-			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
-
-			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
-			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
-		\end{axis}
-	\end{tikzpicture}
-
-   Based on above constraints, we can sketch this simplified model:
-\begin{enumerate}
-	\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable $y_i$. 
-	\item Set constraints for input nodes.
-	\item Set linear constraints . In this case, since the meaning of $y_i$ is $x_i-x'_i$, this constraints will not use the bias.
-	\item Between pre- and post- activation nodes, set the MILP constraint described above.
-\end{enumerate}
-
-	The key point is that, although this model sets 3 variables (and their binary variables) for each node in the network, only $y_i$  contributes to the final results, and we can ignore $x_i,x_i'$ (and their binary variables) during the optimization.
-
-	As a result, we can relax the binary variables used to $\hat{x}_i = \ReLU(x_i)$ and $\hat{x}'_i = \ReLU(x'_i)$.
-
-	Now the simplified model contains the same number of binary variables as the MILP model for local robustness.
-Hence this model runs much faster compared to the previous one.
-The trade-off is lower accuracy compared to the first model under unlimited time.
-In practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
-
-%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
-%	
-	\subsection{Improving the Accuracy of the Simplified Model}
-	We can improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.
-
-%	(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
-
-%	The exact constraints for $$ \begin{align*}
-%		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-%		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
-%	\end{align*} 
-%	
-%	
-%	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
-
-	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
-	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
-	\begin{align*}
-		& \begin{aligned}
-			y_i + x'_i &\leq a\beta_i        &\quad\quad
-			y_i + x'_i &\geq (1-a)\alpha_i \\
-			x'_i       &\leq a'\beta_i       & 
-			x'_i       &\geq (1-a')\alpha_i \\
-			\hat{y}_i  &\leq a\gamma_i       &
-			\hat{y}_i  &\geq -a'\gamma_i \\
-			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
-			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
-			\hat{y}_i  &\leq -x'_i + a\beta_i &
-			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
-			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
-			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
-		\end{aligned}
-	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
-
-	Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
-
-%	\begin{align*}
-%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
-%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
-%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-%	\end{align*}
-
-	The following plot illustrates the constraints described above.
-
-	\hspace*{-10ex}
-	\begin{tikzpicture}
-		\begin{axis}[	axis on top, xlabel = \(x'_i\),
-			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
-			set layers=default,
-			xmax = 4, xmin = -4,
-			ymax = 1, ymin = -1,		
-			zmax = 1, zmin = -1,
-			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
-			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
-			xticklabels = {$0$}, ztick   = {-1,0,1},
-			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
-			view={35}{14},
-			]
-			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates {
-				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
-			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
-			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
-
-		\end{axis}
-	\end{tikzpicture}
-
-	In practice, when we relax the constraints for a node, we will convert $a_i$ and $a_i'$ to continuous variables together.
-In principle, we can also choose to change  only one of those two binary variables.
-
-%	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
-Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
-
-	A special relaxation approach of this model is to treat the binary variables $a'$ appearing in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$ as distinct variables, and relax only the latter.
-
-	\section{Experimental Evaluation}
-
-	We implemented our code in Python 3.8.
-	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
-
-	We will do experiments on two networks for MNIST dataset and another physical model.
-Two MNIST have the same structure.
-They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons.
-One of them is a normally trained neural network and another is for trained for adversarial robustness.
-We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI.
-As the name shows MNIST $5\times 100$-DiffAI has a better robustness.
-The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.
-
-	\subsection{Comparison of different modelings}
-
-	\subsection{Comparison of different scoring algorithms}
-
-	\section{Conclusion}
-
-	TODO
-
-	\bibliography{references}
-	\bibliographystyle{plain}
-
-	\bigskip
-
-	\appendix
-
-\end{document}

### 2025-07-29 AAAI2026/Lipitschz.tex
notation

@@
 
-	\section{Modeling for global robustness}
-
-	\subsection{Using Two Identical Models}
-	The most straightforward way is to use two identical MILP models, i.e., to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (and their own constraints) plus some extra constraints:
-	\begin{enumerate}
-		\item Add constraints for connecting input nodes $\mathcal{M},\mathcal{M}'$ to meet the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon$.
-		\item Set the optimization objective as the difference between two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (because we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
-	\end{enumerate}
-	This large model contains twice as many binary variables as $\mathcal{M}$.
-The computational cost of solving an MILP model grows roughly exponentially with the number of binary variables, and hence it will cost much more time.
-
-	We may relax some constraints (by changing binary variables to continuous variables) as in the case of local robustness.
-However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which motivates us to explore other modeling approaches.
-
-	\subsection{A Simplified model}
-
-	To avoid above problem, we introduce a simplified model that is to use one variable $y_i$ to represent the difference of each two variables: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
-
-	Given  $\gamma_i$ be the upper bound of $y_i$, the constraints for $\hat{y}_i$ are the follows:\begin{align*}
-		\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
-		\hat{y}_i &\geq (a-1) \gamma_i           &\quad \hat{y}_i &\leq y_i + (1-a) \gamma_i
-	\end{align*} where $a$ is a binary variable.
-
-	The following plot illustrates the constraints described above.
-
-	\begin{figure}[b!]
-		\centering
-	\hspace*{10ex}\begin{tikzpicture}
-		\begin{axis}[
-			xlabel={$y_i$},
-			ylabel={$\hat{y}_i$},
-			xmin=-2, xmax=2,
-			ymin=-2, ymax=2,
-			axis lines=center,
-			samples=100, 
-			unit vector ratio=1 1 1, scale=1, xtick   = {-2,2},
-			xticklabels = {$-\gamma_i$,$\gamma_i$},
-			yticklabels = {},
-			]
-			\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
-			\addplot[blue, thick] {0};
-
-			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
-			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
-
-			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
-			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
-		\end{axis}
-	\end{tikzpicture}
-\caption{The possible values of $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ depending on $\val(y_i) = \val(x_i)-\val(x'_i)$.}
-	\label{fig.1v}
-\end{figure}
-
-	Based on above constraints, we can sketch this simplified model:
-	\begin{enumerate}
-		\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable $y_i$. 
-		\item Set constraints for input nodes.
-		\item Set linear constraints . In this case, since the meaning of $y_i$ is $x_i-x'_i$, this constraints will not use the bias.
-		\item Between pre- and post- activation nodes, set the MILP constraint described above.
-	\end{enumerate}
-
-	The key point is that, although this model sets 3 variables (and their binary variables) for each node in the network, only $y_i$  contributes to the final results, and we can ignore $x_i,x_i'$ (and their binary variables) during the optimization.
-
-	As a result, we can relax the binary variables used to $\hat{x}_i = \ReLU(x_i)$ and $\hat{x}'_i = \ReLU(x'_i)$.
-
-	Now the simplified model contains the same number of binary variables as the MILP model for local robustness.
-Hence this model runs much faster compared to the previous one.
-The trade-off is lower accuracy compared to the first model under unlimited time.
-In practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
-
-	One major disadvantage of this model is that the solution obtained through optimization may not be valid-i.e., the output computed by the network on the optimized inputs may not equal the output value in the solution.
-Nevertheless, it is meaningful to compute the upper bound.
-
-	%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
-	%	
-	\subsection{Improving the Accuracy of the Simplified Model}
-	We can remove the disadvantage and improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.
-
-	%	(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
-
-	%	The exact constraints for $$ \begin{align*}
-		%		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-		%		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
-		%	\end{align*} 
-	%	
-	%	
-	%	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
-
-	\begin{figure}[t!]
-		\centering
-	\hspace*{-10ex}
-	\begin{tikzpicture}[scale=0.65]
-		\begin{axis}[	axis on top, xlabel = \(x'_i\),
-			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
-			set layers=default,
-			xmax = 4, xmin = -4,
-			ymax = 1, ymin = -1,		
-			zmax = 1, zmin = -1,
-			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
-			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
-			xticklabels = {$0$}, ztick   = {-1,0,1},
-			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
-			view={35}{14},
-			]
-			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates {
-				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
-			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
-			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
-
-		\end{axis}
-	\end{tikzpicture}
-	\caption{The outcome $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ 
-	depending on $\val(y_i) = \val(x_i)-\val(x'_i)$ and on $\val(x'_i)$.}
-	\label{fig.2v}
-\end{figure}
-
-Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
-	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
-	\begin{align*}
-		& \begin{aligned}
-			y_i + x'_i &\leq a\beta_i        &
-			y_i &+ x'_i \geq (1-a)\alpha_i \\
-			x'_i       &\leq a'\beta_i       & 
-			x'_i       &\geq (1-a')\alpha_i \\
-			\hat{y}_i  &\leq a\gamma_i       &
-			\hat{y}_i  &\geq -a'\gamma_i \\
-			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
-			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
-			\hat{y}_i  &\leq -x'_i + a\beta_i &
-			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
-			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
-			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
-		\end{aligned}
-	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
-
-Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
-
-	%	\begin{align*}
-		%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
-		%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-		%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
-		%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-		%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-		%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-		%	\end{align*}
-
-	The following plot illustrates the constraints described above.
-
-	In practice, when we relax the constraints for a node, we will convert $a_i$ and $a_i'$ to continuous variables together.
-In principle, we can also choose to change  only one of those two binary variables.
-
-	%	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
-Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
-
-	A special relaxation approach of this model is to treat the binary variables $a'$ appearing in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$ as distinct variables, and relax only the latter.
-
-	This approach has a similar disadvantage as the model in the previous section: the output computed by the network on the optimized inputs may not equal the output value in the solution.
-Similarly, it is meaningful to compute the upper bound using this approach.
+	\input{global}
 

### 2025-07-29 AAAI2026/global.tex
notation

--- 2025-05-21 lipschitz 2025/Lipitschz.tex
@@
-\documentclass{llncs}
-\usepackage{hyperref}
-\usepackage{url}
-\pagestyle{plain}
-\usepackage{threeparttable}
-\input{math_commands.tex}
-%\usepackage[latin9]{inputenc}
-%\usepackage[T1]{fontenc}
-\usepackage{float}
-\usepackage{wrapfig}
-\usepackage{lineno}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{tabularx}
-\usepackage{cases}
-\captionsetup{compatibility=false}
-% \usepackage{esint}
-\usepackage{array}
-\usepackage{epstopdf}
-\usepackage{placeins}
-\usepackage{pgfplots}
-\usepackage{url}
-\usepackage{tikz}
-\usepackage{calc}
-\usepackage{array}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usetikzlibrary{positioning, arrows.meta,calc}
+	\section{Modeling for global verification}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\subsection{Classical encoding}
 
-\newcommand{\vW}{\boldsymbol{W}}
-\newcommand{\val}{{\textrm{value}}}
-\newcommand{\Val}{{\textrm{value}}}
-\newcommand{\MILP}{{\textrm{MILP}}}
-\newcommand{\LP}{{\textrm{LP}}}
-\newcommand{\Improve}{\mathrm{Improve}}
-\newcommand{\Utility}{\mathrm{SAS}}
-\newcommand{\Sol}{\mathrm{Sol}}
-\newcommand{\sol}{\mathrm{sol}}
-\newcommand{\UB}{\mathrm{UB}}
-\newcommand{\LB}{\mathrm{LB}}
-\newcommand{\ub}{\mathrm{ub}}
-\newcommand{\lb}{\mathrm{lb}}
-\newcommand{\B}{\mathrm{B}}
-\usepackage{amsmath, amssymb, amsfonts}
-\newcommand{\ReLU}{\mathrm{ReLU}}
-\newcommand{\CMP}{{\textrm{CMP}}\ }
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
-\newcommand{\toolname}{Hybrid MILP}
+    The most straightforward idea to encode the global verification question is to 
+    consider variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ and of its perturbation $I'$,
+    using the classical encoding (\ref{eq11}) for each variable, that we call $\mathcal{M}^{classical}$.
 
-\title{Global case}
-\date{}
+    use two identical MILP models, one for 
+    , i.e., to build a model
 
-\begin{document}
-
-	\maketitle
-	\linenumbers
-	\begin{abstract}
-		TODO
-	\end{abstract}
-
-	\section{Introduction}
-
-	\section{Notations and Preliminaries}
-
-	In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
-	capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{crown}.
-	To simplify the notations, we restrict the presentation to feed-forward, 
-	fully connected ReLU Deep Neural Networks (DNN for short), where the activation function is $\ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
-	$\ReLU(x)=x$ for $x \geq 0$ and $\ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.
-
-	%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.
-
-	%\subsection{Neural Network and Verification}
-
-	% testtesttesttest
-	An $\ell$-layer DNN is provided by $\ell$ weight matrices 
-	$\boldsymbol{W}^i \in \mathbb{R}^{d_i\times d_{i-1}}$
-	and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
-	We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
-	$d_0$ the input dimension, and $d_\ell$ the output dimension.
-
-	Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
-	denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the value vectors $\boldsymbol{z}^i,\hat{\vz}^i$ at layer $1 \leq i \leq \ell$ with
-	\begin{align*}
-		\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i \qquad \, \qquad
-		\hat{\boldsymbol{z}}^{i} = \ReLU({\boldsymbol{z}}^i).
-	\end{align*}
-
-	The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
-	$\boldsymbol{z}$ is called pre-activation values, 
-	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
-Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
-
-	Concerning the verification problem, we focus on the global-robustness question.
-Global robustness asks to determine how the output of a neural network will be affected under a certain kind of small perturbations to any possible input.
-In this view, Lipschitz continuity is a good characterization of global robustness.
-
-	\section{Global robustness and Lipschitz constant}
-
-	Recall the definition of Lipschitz continuity:
-	under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
-	\begin{align*}
-		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
-	\end{align*} 
-	In our practice, when we need global robustness, we will compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
-		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
-	\end{align} And this will lead to the following definition
-
-		\begin{definition}[$\varepsilon$-diff bound]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
-
-		For a number $\varepsilon\in\mathbb{R}$, an $\varepsilon$-diff bound $D_\varepsilon$ is a number such that for any inputs $x,y$: \begin{align*}
-			|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D_\varepsilon \cdot \varepsilon
-		\end{align*}
-
-	\end{definition}
-
-	From $\varepsilon$-diff bound, we cannot directly obtain a Lipschitz bound for the function, but we can get the following weaker bound:
-
-	\begin{definition}[Lipschitz above $\varepsilon$ constant]
-		Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is $L_\infty$ norm.
-
-		For a number $\varepsilon\in\mathbb{R}$, a Lipschitz above $\varepsilon$ constant  $K_\varepsilon$,  is a number such that for any inputs $x,y$: \begin{align*}
-			|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot |x-y|\\
-			|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot \varepsilon\\
-		\end{align*}
-
-	\end{definition}
-
-	\begin{proposition}
-
-		Suppose $D$ is an $\varepsilon$-diff bound for $f(x)$. Then for any $N\in\mathbb{Z}^+$, $D\frac{N+1}{N}$ is a Lipschitz about $N\varepsilon$ constant.
-
-		That is, for any two inputs $x,y$, if \begin{align*}
-			|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D \cdot \varepsilon,
-		\end{align*} then 	 \begin{align*}
-			|x-y|\geq N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
-			|x-y|<N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot N\varepsilon\\
-		\end{align*}
-	\end{proposition}
-
-	\begin{proof} We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
-
-		The first case, $|x-y|\geq N\varepsilon$.
-Then we assume $|x-y| \in [M\varepsilon ,  (M+1)\varepsilon]$ for another integer $M\geq N$.
-Then we can divide the line segment between $x, y$ into $M+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{M+1} = y$ such that $|x_i-x_{i+1}| \leq \varepsilon$ and apply the definition of $\varepsilon$-diff bound $D$ for each pieces:\begin{align*}
-			|f(x)-f(y)| &= |f(x_{M+1})-f(x_M)+\cdots+f(x_1)-f(x_0)|\\
-			&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
-			&\leq D\varepsilon + \cdots +D\varepsilon = (M+1)D\varepsilon
-		\end{align*}
-		Hence,\begin{align*}
-			|f(x)-f(y)| &\leq (M+1)D\varepsilon \leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
-			&= D\cdot\frac{M+1}{M} |x-y|	\leq   D\cdot\frac{N+1}{N} |x-y|		
-		\end{align*}
-		The second case, $|x-y|< N\varepsilon$.
-Similarly we can divide the line segment between $x, y$ into $N$ pieces and then $|f(x)-f(y)|\leq D N\varepsilon\leq |f(x)-f(y)|\leq D \frac{N+1}{N} N\varepsilon$.
-
-		This ends the proof.
-	\end{proof}
-
-	In practice, Lipschitz above $\varepsilon$ constant is already sufficient, since in most cases we care about the absolute difference under input perturbations, not the ratio.
-By combining the above proposition, the computation of $\varepsilon$-diff bound can satisfy our aim.
-
-	Moreover, we have one more proposition connecting $\varepsilon$-diff bound and Lipschitz above $\varepsilon$ constant.
-
-	\begin{proposition}
-		For any $N\in\mathbb{Z}^+$, suppose for any $a$ in $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$, $D$ is an $a$-diff bound for $f(x)$.
-
-		Then $D\frac{N+1}{N}$ is a Lipschitz about $\varepsilon$ constant:\begin{align*}
-			|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
-			|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot \varepsilon\\
-		\end{align*}
-	\end{proposition}
-	\begin{proof}
-		We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
-
-		For the case that $|x-y|<\varepsilon$, this is trivial by definition.
-
-		For the case that $|x-y|\geq \varepsilon$, there exists a sum $x_1+x_2+\cdots+x_n$ by numbers from (allowing repetitions) $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$ such that \begin{align*}
-			\varepsilon \leq x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon \leq |x-y| \leq x_1+x_2+\cdots+x_n
-		\end{align*}
-		By assumption, divide the line segment from $x$ to $y$ into pieces according to $x_1, x_2,\cdots,x_n$, then we will have $$|f(x)-f(y)|\leq Dx_1+Dx_2+\cdots+Dx_n.$$
-
-			Hence,\begin{align*}
-			\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
-			& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})= D \frac{N+1}{N}\\
-		\end{align*}
-		This ends the proof.
-	\end{proof}
-
-	\section{pMILP for local robustness}
-
-	\subsection{MILP and LP encodings for DNNs}
-
-	First we introduce some concepts for local robustness question.
-
-	Mixed Integer Linear Programming (MILP) value abstraction is a complete (but inefficient) method. 
-	For an unstable neuron $n$ that its value $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$, the value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one 
-	integer variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
-
-	\vspace{-0.4cm}
-	\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \UB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\LB(n) \cdot (1-a)
-		\label{eq11}
-	\end{equation}
-
-	%For all $x \in [\LB(n),\UB(n)] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}.
-The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$.
-This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds.
-However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous integer variables and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.
-
-	The global structure is as follows, using Gurobi as an example:
-	\begin{enumerate}
-		\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable. 
-		\item Set constraints for input nodes.
-		\item For each pre-activation node in a hidden layer (and each output node), set linear constraints relating them to the post-activation or input nodes in the previous layer they connect to.
-		\item Between pre- and post- activation nodes, set the MILP constraint described above.
-	\end{enumerate} We use $\mathcal{M}$ to denote the whole MILP model.
-In practice, we may only consider the network up to a certain hidden layer.
-In that case, the pre-activation nodes of that layer serve as the output nodes of the model $\mathcal{M}$.
-
-	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
-As solving LP instances is polynomial time, this optimization is significantly more efficient.
-However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
-This approach is termed the {\em LP abstraction}.
-We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.
-
-	\subsection{partial MILP}
-
-	We will use {\em partial MILP} (pMILP for short, see \cite{DivideAndSlide}) to get trade-offs between accuracy and runtime. Here, we extract the explanation from paper CITE.
-
-	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the partial MILP based on $X$ to compute neuron $n$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding, where variable $a$ is:
-	\begin{itemize}
-		\item binary for neurons in $X$ (exact encoding of the ReLU),
-		\item linear for neurons not in $X$ (linear relaxation).
-	\end{itemize}
-	We will denote above case by MILP$_X$ or $\mathcal{M}_X$. Informally, we say that a node is opened if it is in $X$.
-
-	If $X$ covers all unstable neurons, then MILP$_X$ is exact. But then the time cost may be very large (exponential growth).
-
-	To reduce the runtime, we will limit the size of subset $X$.
-This a priori hurts accuracy.
-To recover some of this accuracy, we use an iterative approach: computing lower and upper bounds $\LB,\UB$ for neurons $n$ of a each layer iteratively, that are used when computing values of the next layer.
-
-	\subsection{SAS}
-
-	In pMILP, to decide the set $X$, we introduce the method {\em Solution-Aware Scoring} (SAS)
-	to evaluate accurately how opening a ReLU impacts the accuracy. Again, here we use the definition from paper CITE. For details and explanation, see CITE.
-
-	Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
-For each node $n<z$, we denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$: $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$; and we denote $(\sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$ a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
-Moreover,  we define the function
-	$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
-	accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
-	compared with using only LP.
-
-	First, SAS will call solvers to compute the LP model to get a solution, which is reasonably fast as there is no binary variables.
-
-	Next, for a neuron $b$ on the layer before layer $\ell_z$, we define:
-
-	\vspace{-0.4cm}
-	$$\Utility\_\max\nolimits^z(b) = W_{bz} \times (\sol(\hat{b})- \ReLU(\sol(b)))$$
-	\vspace{-0.4cm}
-
-	And for a neuron $a$ two layers before $\ell_z$, 
-	$b$ denoting neurons in the layer $\ell$ just before $\ell_z$.
-	Recall the rate $r(b)=\frac{\max(0,\UB(b))}{\max(0,\UB(b))-\min(0,\LB(b))} \in [0,1]$.
-	We define:
-
-	\begin{flalign*}
-		\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})&&\\
-		\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})&&\\	
-	\end{flalign*}
-
-	\vspace{-1.2cm}
-
-	\begin{subnumcases}{\forall b \in \ell, \Delta(\hat{b}) =}
-		r(b)\Delta(b), & for $W_{bz} > 0$ \\
-		\max(\Delta(b),-\sol(b)), & for $W_{bz} < 0$ and $\sol(b)\geq0$\\
-		\max(0,\Delta(b)+\sol(b)), & for $W_{bz} < 0$ and $\sol(b)<0$ \quad \, \quad \, \quad		 
-	\end{subnumcases}
-
-	\begin{flalign*}
-		\Utility\_\max\nolimits^z(a) &= \Delta(z) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})&&
-	\end{flalign*}
-
-	From paper CITE, we know that $\Utility$ is a safe overapproximation in the sense of following proposition:
-
-	\begin{proposition}
-		$0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$. 
-	\end{proposition}
-
-	\section{Modeling for global robustness}
-
-	\subsection{Using Two Identical Models}
-	The most straightforward way is to use two identical MILP models, i.e., to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (and their own constraints) plus some extra constraints:
+    based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (and their own constraints) plus some extra constraints:
 	\begin{enumerate}
@@
 
-	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
-	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
-	\begin{align*}
-		& \begin{aligned}
-			y_i + x'_i &\leq a\beta_i        &\quad\quad
-			y_i + x'_i &\geq (1-a)\alpha_i \\
-			x'_i       &\leq a'\beta_i       & 
-			x'_i       &\geq (1-a')\alpha_i \\
-			\hat{y}_i  &\leq a\gamma_i       &
-			\hat{y}_i  &\geq -a'\gamma_i \\
-			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
-			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
-			\hat{y}_i  &\leq -x'_i + a\beta_i &
-			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
-			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
-			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
-		\end{aligned}
-	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
-
-	Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
-
-%	\begin{align*}
-%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
-%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
-%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-%	\end{align*}
-
-	The following plot illustrates the constraints described above.
-
+	\begin{figure}[t!]
+		\centering
 	\hspace*{-10ex}
-	\begin{tikzpicture}
+	\begin{tikzpicture}[scale=0.65]
 		\begin{axis}[	axis on top, xlabel = \(x'_i\),
@@
 Similarly, it is meaningful to compute the upper bound using this approach.
-
-	\section{Experimental Evaluation}
-
-	We implemented our code in Python 3.8.
-	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
-
-	We will do experiments on two networks for MNIST dataset and another physical model.
-Two MNIST have the same structure.
-They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons.
-One of them is a normally trained neural network and another is for trained for adversarial robustness.
-We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI.
-As the name shows MNIST $5\times 100$-DiffAI has a better robustness.
-The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.
-
-	\subsection{Comparison of different modelings}
-
-	\subsection{Comparison of different scoring algorithms}
-
-	\section{Conclusion}
-
-	TODO
-
-	\bibliography{references}
-	\bibliographystyle{plain}
-
-	\bigskip
-
-	\appendix
-
-\end{document}

### 2025-07-29 AAAI2026/notation.tex
notation

@@
 
-	Concerning the verification problem, we focus on the global-robustness question.
+    In this paper, we consider the global verification problem, where we optimize over all image $I$ and all perturbation $I'$ of $I$ with $|I-I'| \leq \varepsilon$.
+	We will consider three kinds of variables:
+    \begin{itemize}
+    \item $x_j,\hat{x}_j$, for nodes $j$ with input image $I$, 
+    \item $x'_j,\hat{x}'_j$, for nodes $j$ with input the perturbed $I'$, 
+    \item  $y_j = x_j - x'_j$ the {\em diff variable}, with 
+    $\hat{y}_j = \hat{x}_j - \hat{x}'_j$ (and {\em not} 
+    $\hat{y}_i = \ReLU(x_j-x'_j)$). 
+    \end{itemize}
+
+    %Concerning the verification problem, we focus on the global-robustness question.
 Global robustness asks to determine how the output of a neural network will be affected under a certain kind of small perturbations to any possible input.
 In this view, Lipschitz continuity is a good characterization of global robustness.
+
+	\iffalse
 
@@
 
-	\section{pMILP for local robustness}
+	\fi
 
-	\subsection{MILP and LP encodings for DNNs}
+	\section{(partial) MILP}
 
-	First we introduce some concepts for local robustness question.
+	\subsection{MILP encoding for local ReLU and LP relaxation}
 
-	Mixed Integer Linear Programming (MILP) value abstraction is a complete (but inefficient) method. 
-	For an unstable neuron $n$ that its value $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$, the value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one 
-	integer variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
+	Mixed Integer Linear Programming (MILP) value abstraction is an accurate encoding of ReLU DNNs. For an unstable neuron $n$, that is with values 
+    $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$, 
+    the value $\hat{x}$ of $\ReLU(x)$ can be encoded exactly in an MILP formula with one binary / integer variable $a$ valued in $\{0,1\}$, using constants $\UB(n),\LB(n)$ with 4 constraints \cite{MILP}:
 
 	\vspace{-0.4cm}
-	\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \UB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\LB(n) \cdot (1-a)
+	\begin{equation} 
+        \hat{x} \geq x \, \wedge \, \hat{x} \geq 0 \, \wedge \, \hat{x} \leq \UB(n) a \, \wedge \, \hat{x} \leq x-\LB(n) (1-a)
 		\label{eq11}
 	\end{equation}
+
+\begin{proposition}
+\cite{MILP}
+A solution $x,\hat{x},a$  of the above MILP program satisfies $\hat{x} = \ReLU(x)$,
+and $a=1$ if $x> 0$ and $a=0$ if $x< 0$ (both are possible if $x=0$).
+\end{proposition}
 
@@
 
+    \iffalse
 	The global structure is as follows, using Gurobi as an example:
@@
 		\item Between pre- and post- activation nodes, set the MILP constraint described above.
-	\end{enumerate} We use $\mathcal{M}$ to denote the whole MILP model.
-In practice, we may only consider the network up to a certain hidden layer.
-In that case, the pre-activation nodes of that layer serve as the output nodes of the model $\mathcal{M}$.
+	\end{enumerate}
 
-	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
+    \fi
+
+    We use $\mathcal{M}$ to denote the whole MILP model, where each unstable ReLU are encoded in the above way with one integer variable.
+This is often too computationally intensive, as the worst-case complexity of MILP is exponential in the number of integer variables \cite{DivideAndSlide}.
+
+	MILP instances can be linearly relaxed into LP over-abstraction, where variables $a$ originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding.
 As solving LP instances is polynomial time, this optimization is significantly more efficient.
@@
 This approach is termed the {\em LP abstraction}.
-We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.
+    % We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.
 
-	\subsection{partial MILP}
+	%\subsection{partial MILP}
 
-	We will use {\em partial MILP} (pMILP for short, see \cite{DivideAndSlide}) to get trade-offs between accuracy and runtime. Here, we extract the explanation from paper CITE.
-
-	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the partial MILP based on $X$ to compute neuron $n$ simply calls Gurobi to minimize/maximize the value of $n$ with the MILP model encoding, where variable $a$ is:
+	Intermediate between these 2 extreme cases, there is {\em partial MILP} 
+    (pMILP for short) to get trade-offs between accuracy and runtime:
+	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the pMILP based on $X$ to compute neuron $n$ uses the MILP encpoding (\ref{eq11}), where variable $a$ is:
 	\begin{itemize}
@@
 	\end{itemize}
-	We will denote above case by MILP$_X$ or $\mathcal{M}_X$. Informally, we say that a node is opened if it is in $X$.
+	We will denote the above model by MILP$_X$. We say that a node is {\em opened} if it is in $X$.
 
-	If $X$ covers all unstable neurons, then MILP$_X$ is exact. But then the time cost may be very large (exponential growth).
-
-	To reduce the runtime, we will limit the size of subset $X$.
+	%To reduce the runtime, we will limit the size of subset $X$.
 This a priori hurts accuracy.
@@
 
+	\iffalse
 	\subsection{SAS}
@@
 	\end{proposition}
+	\fi

### 2025-07-29 AAAI2026/a_trick.tex
update a trick

\subsection*{A trick of $L_1$ norm constraints on input}

A trick to set $L_1$ norm constraints on the input space into linear constraints is described below.

Suppose the dimension of input space is $n$, and $x_i,i\leq n$ are the input variables, $\vec{x}$ is the input vector, and we hope to set a constraints of $\vec{x}$ that $\|\vec{x}\| \leq c$,  then we can set the constraints by add variables $A_i,i<n$ with the only constraints \begin{align}\label{L1constraint}\begin{cases}
	A_i \geq x_i &\text{ for }i \leq n\\ 
	A_i\geq -x_i &\text{ for }i \leq n\\
	\Sigma_{i\leq n} A_i \leq c	&\end{cases}
\end{align}

We show that this constraint is equivalent to $\|\vec{x}\| \leq c$.

The first two lines of constraints \ref{L1constraint} is equivalent to that $A_i\geq |x_i|$. So the whole constraints is non-weaker than $\|\vec{x}\| \leq c$.

Next, for every instance that satisfy $\|\vec{x}\| \leq c$, then there is also an instance which satisfy constraints \ref{L1constraint}: simply let all $A_i = |x_i|$. And this shows that $\|\vec{x}\| \leq c$ is non-weaker than constraints \ref{L1constraint}. Therefore they are equivalent.

### 2025-07-29 AAAI2026/global.tex
update proof
global

@@
 
-	\subsection{Classical encoding}
+	\subsection{Extending the classical encoding}
 
@@
     consider variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ and of its perturbation $I'$,
-    using the classical encoding (\ref{eq11}) for each variable, that we call $\mathcal{M}^{classical}$.
+    using the classical encoding (\ref{eq11}) \cite{MILP} for each variable, 
+    that we call $\mathcal{M}^{classical}$.
+    Further:
+    \begin{enumerate}
+		\item For each input nodes $x_j,x'_j$ of $I,I'$, we add constraints
+        $|x_j-x'_j| \leq \varepsilon$ 
+        ($L_\infty$-perturbation - see next section for $L_1$).
+		\item We set the optimization objective as maximize $x_i - x_j +x'_j - x'_i$ to compute $\beta^\varepsilon_{i,j}=\beta^\varepsilon_{j,i}$.
+	\end{enumerate}
 
-    use two identical MILP models, one for 
-    , i.e., to build a model
+	This model contains twice as many (binary) variables as for local robustness. As the worst-case complexity of solving an MILP model 
+    is exponential in the number of binary variables, it will be computationally intractable to compute $\beta^\varepsilon_{i,j}$ in this way, but for very small DNNs.
+As explained in the previous section, the standard way is to rely on relaxing at least some of the binary variables into linear variables.
 
-    based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (and their own constraints) plus some extra constraints:
-	\begin{enumerate}
-		\item Add constraints for connecting input nodes $\mathcal{M},\mathcal{M}'$ to meet the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon$.
-		\item Set the optimization objective as the difference between two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (because we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
-	\end{enumerate}
-	This large model contains twice as many binary variables as $\mathcal{M}$.
-The computational cost of solving an MILP model grows roughly exponentially with the number of binary variables, and hence it will cost much more time.
+    The problem is that the LP relaxation of this classical encoding is extremely inaccurate, as variables $x_j,x'_j$ dependencies are due solely on the function definition through common ancestor variables in previous layers - as this is approximated with LP, most of the dependencies will be lost.
 
-	We may relax some constraints (by changing binary variables to continuous variables) as in the case of local robustness.
-However, the problem is that even relaxing a few nodes can cause a significant loss of accuracy, which motivates us to explore other modeling approaches.
+    On top of being an issue with partial MILP models, LP relaxation is also used during the Branch and Bound process internal to MILP solvers to provide bounds for each branch.
+So even when all variables are opened and the MILP model is fully accurate, the classical encoding will likely not be efficient as well.
+
+    We will check that in table \ref{table.classical} in Section Experimental Evaluation.
+
+	\subsection{A novel "2v" model with {\em diff variables}}
+
+    The idea to circumvent the loss of dependencies when applying linear relaxation is to switch the variables towards $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with
+    $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$.
+Intuitively, the diff variables will be small as they will be carrying the difference between both the image $I$ and its perturbation $I'$.
+    We will use the classical MILP encoding for $\hat{x}'_j$.
+    However, we cannot apply the classical MILP encoding (\ref{eq11}) \cite{MILP} on the diff variable $\hat{y}_j$. Instead we study the function of 
+    $\hat{y}_j$ given $y_j$ and $x'_j$, and encode it into a novel MILP model.
+    A first important observation is that $I,I'$ being perfectly symetrical,
+    for $\gamma_i$ being a upper bound of $y_i$, then $-\gamma_i$ is a lower bound 
+    for $y_i$.
+
+	%	(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
+
+	%	The exact constraints for $$ \begin{align*}
+		%		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
+		%		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
+		%	\end{align*} 
+	%	
+	%	
+	%	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
+
+	We first display on Figure \ref{fig.2v} the function $f(x'_i,y_i)=\hat{y}_i$, when we know that $y_i \in [- \gamma_i, \gamma_i]$.
+When $x'_i < -\gamma_i$, then $x_i <0$ and we have $\hat{y}_i = \ReLU(x_i) - \ReLU(x'_i) = 0-0=0$.
+    For $x'_i > \gamma_i$, we have $x_i >0$ and $\hat{y}_i=y_i$. Between these two linear planes, we have two more linear planes presenting intermediate cases, so 4 linear planes in total.
+
+	\begin{figure}[b!]
+		\centering
+	\hspace*{-5ex}
+	\begin{tikzpicture}[scale=0.65]
+		\begin{axis}[	axis on top, xlabel = \(x'_i\),
+			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
+			set layers=default,
+			xmax = 4, xmin = -4,
+			ymax = 1, ymin = -1,		
+			zmax = 1, zmin = -1,
+			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
+			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
+			xticklabels = {$0$}, ztick   = {-1,0,1},
+			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
+			view={35}{14},
+			]
+			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
+			coordinates {
+				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
+			};
+
+			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
+			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
+			};
+
+			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
+			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
+			};
+
+			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
+			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
+			};
+
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
+			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
+
+			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
+			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
+
+		\end{axis}
+	\end{tikzpicture}
+	\caption{The outcome $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ 
+	depending on $\val(y_i) = \val(x_i)-\val(x'_i)$ and on $\val(x'_i)$.}
+	\label{fig.2v}
+\end{figure}
+
+Assuming that $y_i \in [-\gamma_i, \gamma_i]$,
+and that $x'_i \in [\alpha_i,\beta_i]$,
+we have that $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ is the solution of:
+	\begin{align*}
+		& \begin{aligned}
+			y_i + x'_i &\leq a\beta_i        &
+			y_i &+ x'_i \geq (1-a)\alpha_i \\
+			x'_i       &\leq a'\beta_i       & 
+			x'_i       &\geq (1-a')\alpha_i \\
+			\hat{y}_i  &\leq a\gamma_i       &
+			\hat{y}_i  &\geq -a'\gamma_i \\
+			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
+			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
+			\hat{y}_i  &\leq -x'_i + a\beta_i &
+			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
+			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
+			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
+		\end{aligned}
+	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
+
+Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
+
+	%	\begin{align*}
+		%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
+		%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
+		%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
+		%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
+		%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
+		%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
+		%	\end{align*}
+
+	The following plot illustrates the constraints described above.
+
+	In practice, when we relax the constraints for a node, we will convert $a_i$ and $a_i'$ to continuous variables together.
+In principle, we can also choose to change  only one of those two binary variables.
+
+	%	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
+Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
+
+	A special relaxation approach of this model is to treat the binary variables $a'$ appearing in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$ as distinct variables, and relax only the latter.
+
+	This approach has a similar disadvantage as the model in the previous section: the output computed by the network on the optimized inputs may not equal the output value in the solution.
+Similarly, it is meaningful to compute the upper bound using this approach.
 
@@
 	%
-	\subsection{Improving the Accuracy of the Simplified Model}
-	We can remove the disadvantage and improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.
-
-	%	(This model has the same binary set, although the meaning of binary variable for $y_i$ is somehow different.)
-
-	%	The exact constraints for $$ \begin{align*}
-		%		&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
-		%		&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
-		%	\end{align*} 
-	%	
-	%	
-	%	Moreover, we can add two more natural constraints: $x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i.$
-
-	\begin{figure}[t!]
-		\centering
-	\hspace*{-10ex}
-	\begin{tikzpicture}[scale=0.65]
-		\begin{axis}[	axis on top, xlabel = \(x'_i\),
-			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
-			set layers=default,
-			xmax = 4, xmin = -4,
-			ymax = 1, ymin = -1,		
-			zmax = 1, zmin = -1,
-			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
-			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
-			xticklabels = {$0$}, ztick   = {-1,0,1},
-			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
-			view={35}{14},
-			]
-			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates {
-				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
-			coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
-			};
-
-			\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
-			coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
-			};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
-			\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};
-
-			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
-			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};
-
-		\end{axis}
-	\end{tikzpicture}
-	\caption{The outcome $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ 
-	depending on $\val(y_i) = \val(x_i)-\val(x'_i)$ and on $\val(x'_i)$.}
-	\label{fig.2v}
-\end{figure}
-
-Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
-	the precise  constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (along with $\hat{x}'_i=\ReLU(x'_i)$) are as follows:
-	\begin{align*}
-		& \begin{aligned}
-			y_i + x'_i &\leq a\beta_i        &
-			y_i &+ x'_i \geq (1-a)\alpha_i \\
-			x'_i       &\leq a'\beta_i       & 
-			x'_i       &\geq (1-a')\alpha_i \\
-			\hat{y}_i  &\leq a\gamma_i       &
-			\hat{y}_i  &\geq -a'\gamma_i \\
-			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
-			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
-			\hat{y}_i  &\leq -x'_i + a\beta_i &
-			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
-			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
-			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
-		\end{aligned}
-	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
-
-Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
-
-	%	\begin{align*}
-		%		& y_i+x'_i \leq a\beta_i \quad\wedge \quad y_i+x'_i\geq (1-a)\alpha_i\\	
-		%		& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
-		%		&\hat{y}_i \leq a\gamma_i \quad\wedge \quad	\hat{y}_i \geq -a'\gamma_i \\
-		%		&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
-		%		&	\hat{y}_i \leq -x'_i+a\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
-		%		&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+a'(-\beta_i) \\
-		%	\end{align*}
-
-	The following plot illustrates the constraints described above.
-
-	In practice, when we relax the constraints for a node, we will convert $a_i$ and $a_i'$ to continuous variables together.
-In principle, we can also choose to change  only one of those two binary variables.
-
-	%	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
-Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
-
-	A special relaxation approach of this model is to treat the binary variables $a'$ appearing in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$ as distinct variables, and relax only the latter.
-
-	This approach has a similar disadvantage as the model in the previous section: the output computed by the network on the optimized inputs may not equal the output value in the solution.
-Similarly, it is meaningful to compute the upper bound using this approach.

### 2025-07-29 AAAI2026/notation.tex
global

@@
 	and $\ell$ bias vectors $\vb^i \in \mathbb{R}^{d_i}$, for $i=1, \ldots, \ell$.
-	We call $d_i$ the number of neurons of hidden layer $i \in \{1, \ldots, \ell-1\}$,
+	We call $d_i$ the number of neurons of hidden layer 
+	$i \in \{1, \ldots, \ell-1\}$,
 	$d_0$ the input dimension, and $d_\ell$ the output dimension.
@@
     We use $\mathcal{M}$ to denote the whole MILP model, where each unstable ReLU are encoded in the above way with one integer variable. 
-This is often too computationally intensive, as the worst-case complexity of MILP is exponential in the number of integer variables \cite{DivideAndSlide}.
+	The encoding from $(\hat{x}_j)_{j \text{ in layer } i}$ to 
+	$(x_{j'})_{j' \text{ in layer } i+1}$ variables is simply the linear combination 
+	$\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i$.
+	This exact MILP encoding is often too computationally intensive, as the worst-case complexity of MILP is exponential in the number of integer variables \cite{DivideAndSlide}.
 
@@
 	Intermediate between these 2 extreme cases, there is {\em partial MILP} 
-    (pMILP for short) to get trade-offs between accuracy and runtime:
+    (pMILP for short) to get trade-offs between accuracy and runtime
+	\cite{DivideAndSlide}:
 	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the pMILP based on $X$ to compute neuron $n$ uses the MILP encpoding (\ref{eq11}), where variable $a$ is:

### 2025-07-29 AAAI2026/a_trick.tex

@@
 Therefore they are equivalent.
+
+\subsection*{A proof of constraints}
+
+We will show that the constraints corresponding to \ref{fig.2v} is exact.
+
+We only need to consider all cases of binary variable. First, we know the constraints for $\hat{x_i}'=\ReLU(x_i')$ are exact.
+
+We have 2 binary variables and 4 cases in total. We only need to check that, in all 4 cases, $$\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$$
+
+Case 1: if $a = 1$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 4.
+
+Case 2: if $a = 1$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i+x'_i$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 6.
+
+Case 3: if $a = 0$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = 0$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 3.
+
+Case 4: if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 5.

### 2025-07-29 AAAI2026/Lipitschz.tex
update a trick
Update Lipitschz.tex
update table
update
commit

@@
 
+	\input{a_trick}
+
 	\section{Experimental Evaluation}
@@
 
-		1v, $?? \times 1$ & ?? & ?? & ?? & ?? \\\hline 
-		3v, $?? \times 3$ & ?? & ?? & ?? & ?? \\\hline 
-	 2v, $?? \times 2$ & ?? & ?? & ?? & ?? \\\hline\hline
+		1v, $500 \times 1$ & 1.508 & 0.1856 & 0.0575 & 14400 \\\hline 
+		3v, $500 \times 3$ & 1.256 & 0.1336 & 0.0950 & 14400 \\\hline 
+	 2v, $500 \times 2$ & 1.2417 & 0.0224 & 0.0224 & 14400 \\\hline\hline
 
@@
 	\caption{Comparison of "1v", "3v" and "2v" models 
-	to obtain bounds on $\beta^{0.5}_{0,1}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of ??s, and ??s , where ??,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+	to obtain bounds on $\beta^{.5}_{0,1}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of ??s, and ??s , where ??,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
 \end{table}

### 2025-07-29 AAAI2026/Lipitschz.tex
global

--- 2025-07-29 AAAI2026/Lipitschz.tex
@@
 
-	\section{Experimental Evaluation}
+	\input{a_trick}
 
-	We implemented our code in Python 3.8.
-	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
-
-	We will do experiments on two networks for MNIST dataset and another physical model.
-Two MNIST have the same structure.
-They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons.
-One of them is a normally trained neural network and another is for trained for adversarial robustness.
-We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI.
-As the name shows MNIST $5\times 100$-DiffAI has a better robustness.
-The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.
-
-	\subsection{Experiment results for robustness (MNIST)}
-
-	\begin{table}[h!]
-	\begin{tabular}{|l|c|c|c|c|}\hline\hline
-		$L_1\leq 0.5$ &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ &  Time \\\hline \hline
-		1v, $375 \times 1$ & 17.4724 & 0.9089  ?? & 0.0917 & 43200s \\\hline 
-		2v, $375 \times 2$ & 21.0135 & 8.4672& 0.2229 & 43200s \\\hline		
-		2v, $450 \times 2$ & 12.0097 & 3.4408 & {\bf 0.2584} & 43200s \\\hline
-		1v, $500 \times 1$ & ?? & ?? & ?? & 43200s \\\hline 
-		3v, $500 \times 3$ & ?? & ?? & ?? & 43200s \\\hline 
-	 2v, $500 \times 2$ & {\bf 8.7608} & nan & nan & 43200s \\\hline\hline
-
-	 2v, $485 \times 2$ & 20.6460 & 1.9152 & {\bf 0.3722} & 130000s \\\hline\hline
-
-		 2v, $500 \times 2$ & {\bf 8.2573} & nan & nan & 260000s \\\hline\hline
-
-	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models 
-	to obtain bounds on $\beta^{0.5}_{0,1}$ on the {\bf full dimension} MNIST DNN, for timeouts of 43200s, 130000s and 260000s, where 375, 450, 485 or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
-\end{table}
-
-On the full space, we reach bounds of $8.2$ (on $\beta^{.5}_{0,1}$), which is too pessimistic as it allows to certify 0 image robust.
-The worst-case found by the "2v" $485 \times 2$ binary variables after 130000s only displays a difference of
-$0.37$, $20 \times$ away from the bound found.
-
-\begin{figure*}[t!]
-	\centering
-\includegraphics[scale=0.5]{image.png} \hspace{0.8cm}
-\includegraphics[scale=0.5]{perturb.png}
-\caption{An improbable image and its perturbation (difference around x=11, y=18) 
-with maximal $\beta^{.5}_{0,1}=0.37$ for MNIST as obtained by the "2v" $485 \times 2$ model in full 758 dimension image space.}
-\end{figure*}
-
-\paragraph{Reduced space}
-
-We now consider a PCA model order reduction to avoid considering improbable images, 
-speed up obtaining the bounds, and obtain less pessimistic bounds.
-We settle on 20 orders, as the MNIST DNN considered run on a images obtained from projecting to the reduced order and projected back to the full dimension 
-display the same accuracy of $97$\% as the DNN on the original images, meaning no accuracy is lost from reducing to 20 dimensions, which is the only thing which matters.
-On such a reduced space, bounds obtained are much more precise, and one can certify robustness of images online.
-
-	\begin{table}[h!]
-	\begin{tabular}{|l|c|c|c|c|}\hline\hline
-		$L_1\leq 0.5$ &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ &  Time \\\hline \hline
-
-1v, $?? \times 1$ & ?? & ?? & ?? & ?? \\\hline 
-		3v, $?? \times 3$ & ?? & ?? & ?? & ?? \\\hline 
-	 2v, $?? \times 2$ & ?? & ?? & ?? & ?? \\\hline\hline
-
-		1v, $?? \times 1$ & ?? & ?? & ?? & ?? \\\hline 
-		3v, $?? \times 3$ & ?? & ?? & ?? & ?? \\\hline 
-	 2v, $?? \times 2$ & ?? & ?? & ?? & ?? \\\hline\hline
-
-	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models 
-	to obtain bounds on $\beta^{0.5}_{0,1}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of ??s, and ??s , where ??,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
-\end{table}
-
-\begin{figure*}[t!]
-	\centering
-\includegraphics[scale=0.5]{redimage.png} \hspace{0.8cm}
-\includegraphics[scale=0.5]{redperturb.png}
-\caption{An image and its perturbation from the 20-dimension reduced space with maximal $\beta^{.5}_{0,1}=0.17$ for MNIST as obtained by the "2v" $500 \times 2$ model.}
-\end{figure*}
-
-\begin{table}[h!]
-	\begin{tabular}{|l|c|c|c|c|}\hline\hline
-		model &    $L_1\leq 0.5$ & $L_1\leq 1$ & $L_1\leq 1.5$ &  $L_1\leq 2$ \\\hline \hline
-		1v, $? \times 1$ & $80 \%$ & $32\%$ & $7\%$ & $0\%$ \\\hline
-		3v, $? \times 3$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
-		2v, $? \times 2$ & 84\% & 51\% & 16\% & 4\% \\\hline \hline
-	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models 
-	in the percentage of images they can certify in real-time for different values of $L_1$ perturbations.}
-\end{table}
-
-\subsection{Experiment results for regression (Pipe strain)}
-
-	For the pipe system, to find a example of large difference on outputs is one of the main aims.
-
-	\begin{figure*}[t!]
-\includegraphics[scale=0.5]{deform.png} \hspace{0.8cm}
-\includegraphics[scale=0.5]{strain.png}
-\caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" $100 \times 2$ model.}
-\end{figure*}
-
-	The network of Pipe system is relatively simple and in the tests, we will open all $\ReLU$ nodes.
-
-	We will compare the results of different modeling methods.
-
-	\vspace*{1ex}
-
-	\iffalse
-	\begin{table}[h!]
-	\begin{tabular}{|l|l|l|l|l|}\hline
-		$L_1\leq 0.83$ &        Bound $\downarrow$ &  Solution $\uparrow$ &      Real $\uparrow$ &  Time \\\hline
-		1v,open 100 &     {\bf 0.035613} &  0.035613 &                       0.01288 & 10608 \\\hline
-		3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
-		%3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
-		2v,open 100 &     0.046719 &  0.024364 &  {\bf 0.024436} & 10922 \\\hline
-	\end{tabular}
-	\caption{Comparison of 1v,2v and 3v models on the pipe system with a fixed timeout of 10.000s.}
-\end{table}
-\fi
-
-	\begin{table}[h!]
-	\begin{tabular}{|l|c|c|c|c|}\hline\hline
-		$L_1\leq 0.83$ &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ &  Time \\\hline \hline
-		1v, $100 \times 1$ &     {\bf 0.0356} &  $0.0356$ & $0.0191$ &   1000s \\\hline
-		3v, $100 \times 3$&     0.0414 &  0.0254 &  0.0166 &  1000s \\\hline
-		2v, $100 \times 2$&     0.0418 &  0.0229 &   {\bf 0.0229} &  1000s \\\hline \hline
-		3v, $90 \times 3$&      ?? &  ?? &  ?? & 14523s \\\hline
-		3v, $100 \times 3$&      {\bf 0.0350} &  0.0272 &  0.0216 & 14523s \\\hline
-		2v, $90 \times 2$&     ?? &  ?? &   ?? & 14523s \\\hline
-		2v, $100 \times 2$&     0.0360 &  0.0236 &    {\bf 0.0236} & 14523s \\\hline \hline
-		3v, $100 \times 3$&     {\bf 0.0329} &  0.0277 &  0.0165 & 72126s \\\hline
-		2v, $100 \times 2$&     0.03375 &  0.0244 &  {\bf 0.0245} & 72126s \\\hline\hline
-	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14523s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.
-	L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}
-\end{table}
+	\input{experiments}
 

### 2025-07-29 AAAI2026/global.tex
global

@@
-	\section{Modeling for global verification}
+	\section{MILP Models for global verification}
 
@@
 When $x'_i < -\gamma_i$, then $x_i <0$ and we have $\hat{y}_i = \ReLU(x_i) - \ReLU(x'_i) = 0-0=0$.
-    For $x'_i > \gamma_i$, we have $x_i >0$ and $\hat{y}_i=y_i$. Between these two linear planes, we have two more linear planes presenting intermediate cases, so 4 linear planes in total.
+    For $x'_i > \gamma_i$, we have $x_i >0$ and $\hat{y}_i=
+    \ReLU(x_i)-\ReLU(x'_i)=x_i - x'_i = y_i$. 
+    Between these two linear planes, we have two more linear planes presenting intermediate cases, so 4 linear planes in total.
 
@@
 			\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};			
-
 		\end{axis}
 	\end{tikzpicture}
-	\caption{The outcome $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ 
-	depending on $\val(y_i) = \val(x_i)-\val(x'_i)$ and on $\val(x'_i)$.}
+	\caption{The function computing $\hat{y}_i=\ReLU(x_i)-\ReLU(x'_i)$ 
+	depending on $y_i = x_i- x'_i$ and on $x'_i$.}
 	\label{fig.2v}
@@
 
+Recall first that we use the classical MILP encoding 
+for $\hat{x}'_i=\ReLU(x'_i)$, using one binary variable $a'$. We reuse 
+$a'$ (with its value already settled, see Proposition \ref{Prop1}) 
+in the encoding of $\hat{y}_i = \ReLU(x_i)-\ReLU(x'_i)$:
+
+\begin{proposition}
 Assuming that $y_i \in [-\gamma_i, \gamma_i]$,
 and that $x'_i \in [\alpha_i,\beta_i]$,
-we have that $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ is the solution of:
+we have that $\hat{y}_i = \ReLU(x_i=x'_i+y_i)-\ReLU(x'_i)$ is the solution of:
 	\begin{align*}
@@
 		\end{aligned}
-	\end{align*} Here, $a,a'$ are binary variables, and $a'$ is also the binary variable in the constraints for $\hat{x}'_i=\ReLU(x'_i)$.
+	\end{align*} 
+    where $a,a'$ are binary variables, 
+    and $a'$ is shared with the classical MILP
+    encoding for $\hat{x}'_i=\ReLU(x'_i)$.
+\end{proposition}
+
+So to encode both $\hat{y}_i$ and $\hat{x}_i$, we need 2 binary variables altogether, as the classical encoding.
+
+%\begin{proof}
+PROOF????
+%\end{proof}
 

### 2025-07-29 AAAI2026/notation.tex
global

@@
 \cite{MILP}
+\label{Prop1}
 A solution $x,\hat{x},a$  of the above MILP program satisfies $\hat{x} = \ReLU(x)$,

### 2025-07-29 AAAI2026/global.tex
global

@@
 \begin{proposition}
+    \label{Prop2}
 Assuming that $y_i \in [-\gamma_i, \gamma_i]$,
@@
 	\end{align*} 
-    where $a,a'$ are binary variables, 
+    where $a,a' \in \{0,1\}$ are binary variables, 
     and $a'$ is shared with the classical MILP
@@
 
-So to encode both $\hat{y}_i$ and $\hat{x}_i$, we need 2 binary variables altogether, as the classical encoding.
+So to encode both $\hat{y}_i$ and $\hat{x}_i$, we need 2 binary variables altogether, similar to the classical encoding.
+
+The LP relaxation of this model contains important bounds, including 
+    $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$
+    (see subsection "1v" model), which is not the case of the classical model.
+
+\paragraph{A proof of Prop.~\ref{Prop2}}
+
+We do a case analysis depending on the value of both binary variables. 
+First, we know the constraints for $\hat{x_i}'=\ReLU(x_i')$ are exact (see 
+Prop.~\ref{Prop1}).
+
+We have 2 binary variables and 4 cases in total. We only need to check that, in all 4 cases, $$\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$$
+
+Case 1: if $a = 1$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 4.
+
+Case 2: if $a = 1$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i+x'_i$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 6.
+
+Case 3: if $a = 0$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = 0$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 3.
+
+Case 4: if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 5.
 
 %\begin{proof}
-PROOF????
+
 %\end{proof}
-
-Similar to the second model, the constraints on $x_i$ for $\hat{x}_i=\ReLU(x_i)$ are not necessary, or at least can be relaxed without any loss in accuracy.
 
@@
 
-	The following plot illustrates the constraints described above.
-
-	In practice, when we relax the constraints for a node, we will convert $a_i$ and $a_i'$ to continuous variables together.
-In principle, we can also choose to change  only one of those two binary variables.
-
 	%	The relaxation of this model is similar: let $a$s and $a'$s be continuous variables instead of binary/integer variables.
 Unlike the first model in this section, relaxing a few nodes does not lose too much accuracy.
-
-	A special relaxation approach of this model is to treat the binary variables $a'$ appearing in the above constraints and the binary variables for $\hat{x}'_i=\ReLU(x'_i)$ as distinct variables, and relax only the latter.
-
-	This approach has a similar disadvantage as the model in the previous section: the output computed by the network on the optimized inputs may not equal the output value in the solution.
-Similarly, it is meaningful to compute the upper bound using this approach.
-
-	\subsection{A Simplified model}
-
-	To avoid above problem, we introduce a simplified model that is to use one variable $y_i$ to represent the difference of each two variables: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then we set $y_i=x_i-x'_i$ and and $\hat{y}_i=\hat{x}_i-\hat{x}_i'$.
-The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$
-
-	Given  $\gamma_i$ be the upper bound of $y_i$, the constraints for $\hat{y}_i$ are the follows:\begin{align*}
-		\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
-		\hat{y}_i &\geq (a-1) \gamma_i           &\quad \hat{y}_i &\leq y_i + (1-a) \gamma_i
-	\end{align*} where $a$ is a binary variable.
-
-	The following plot illustrates the constraints described above.
 
@@
 	\end{tikzpicture}
-\caption{The possible values of $\val(\hat{y}_i)=\ReLU(\val(x_i))-\ReLU(\val(x'_i))$ depending on $\val(y_i) = \val(x_i)-\val(x'_i)$.}
+\caption{The possible values of $\hat{y}_i=\ReLU(x_i)-\ReLU(x'_i)$ depending on $y_i = x_i-x'_i$ for the "1v" model.}
 	\label{fig.1v}
@@
 
+    \subsection{A decoupled "3v" model}
+
+	Besides doing LP relaxation on some of the binary variables, we propose a 
+    variant of the "2v" model: the binary variables $a'$ appearing in 
+    Prop.
+\ref{Prop2} can be decoupled from the binary variable appearing in the classical encoding of $x'_i = \ReLU(x'_i)$.
+While this means having 3 binary variables per unstable ReLU (which warrants the name "3v" model), the fact that these variables are decouples remove a lot of constraints in the MILP encoding, and actually helps the solver.
+The decoupling also means that the "3v" model is not as accurate as the "2v" model.
+
+	\subsection{The efficient "1v" model}
+
+	To simplify further and limit the number of (binary) variables, 
+    we introduce an efficient "1v" model which only uses the diff variables $y_i,\hat{y}_i$.
+Again, we study the range of values $\hat{y}_i$ can take according to the value of $y_i$, as depicted in Fig.~\ref{fig.1v}.
+This is a projection of Fig.~\ref{fig.2v} onto $y_i,\hat{y}_i$.
+
+    \begin{proposition}
+    \label{prop3}
+    Given $y_i \in [-\gamma_i,\gamma_i]$, 
+    $\hat{y}_i$ is a solution of the following MILP program :\begin{align*}
+		\hat{y}_i &\leq a \gamma_i               &\quad \hat{y}_i &\geq y_i - a \gamma_i \\
+		\hat{y}_i &\geq (a-1) \gamma_i           &\quad \hat{y}_i &\leq y_i + (1-a) \gamma_i
+	\end{align*} where $a \in \{0,1\}$ is a binary variable.
+	\end{proposition}
+
+    We can easily check that the LP relaxation of this MILP program is exactly 
+    $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$, 
+    {\bf LIAO please do on Fig2: as depicted in broken lines on Fig.~\ref{fig.1v}}.
+
+	\iffalse
 	Based on above constraints, we can sketch this simplified model:
@@
 	As a result, we can relax the binary variables used to $\hat{x}_i = \ReLU(x_i)$ and $\hat{x}'_i = \ReLU(x'_i)$.
+	\fi
 
-	Now the simplified model contains the same number of binary variables as the MILP model for local robustness.
-Hence this model runs much faster compared to the previous one.
-The trade-off is lower accuracy compared to the first model under unlimited time.
-In practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
-
-	One major disadvantage of this model is that the solution obtained through optimization may not be valid-i.e., the output computed by the network on the optimized inputs may not equal the output value in the solution.
-Nevertheless, it is meaningful to compute the upper bound.
+	The "1v" model contains the same number of (binary) variables as the MILP model for local robustness, but it is not as accurate as the "3v" or "2v" models.
 

### 2025-07-31 AAAI2026/related.tex
related

\section{Related Work}

Some works 
Leino et al. [2021]; Zhang et al. [2022a] Sun et al. [2022]  Chen et al. [2021], REGLO focus on training a network to be - rather than proving that the DNN is as we do - gobally robust ....

Other work estimate global robustness bounds, but without hard verification certificates Bastani et al. [2016]; Ruan et al. [2019], Gopinath et al. [2018], e.g. using probabilistic guarantees  Levy et al. [2023]; Mangal et al. [2019].

Closer to our paper, several works consider a kind of global Lipschitz bound, to understand how the output change with input perturbations, as \cite{marabou} and \cite{ITNE,GROCET}. However, they do not consider whether the classification changes.

The most related work is Vhagar, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants). They do not however report actual 
real-time certified robust percentage, as we do ($86\%$ of real-time
certified robust image for $L_1$-perturbations). Last, the hyper-adversarial attack to find better lower bounds seems extremely efficient, and we will consider it in the future.

Technically, none of the MILP base work \cite{Vhagar,ITNE,GROCET} 
consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even the "1v" MILP model. However, \cite{ITNE,GROCET} 
defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our model, Eq. (3) from \cite{ITNE} corresponding essentially to it. \cite{Vhagar} do things differently, adding per neuron constraints, recovering .

### 2025-07-31 AAAI2026/related.tex
related

@@
 
-Some works 
-Leino et al. [2021]; Zhang et al. [2022a] Sun et al. [2022]  Chen et al. [2021], REGLO focus on training a network to be - rather than proving that the DNN is as we do - gobally robust ....
-
-Other work estimate global robustness bounds, but without hard verification certificates Bastani et al.
+Some works CITE
+Leino et al. [2021]; Zhang et al. [2022a] Sun et al. [2022]  Chen et al. [2021], REGLO focus on training a network to be - rather than proving that the DNN is as we do - gobally robust .
+Other work estimate global robustness bounds, but without hard verification certificates CITE Bastani et al.
 [2016]; Ruan et al.
@@
 
-The most related work is Vhagar, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants). They do not however report actual 
-real-time certified robust percentage, as we do ($86\%$ of real-time
-certified robust image for $L_1$-perturbations). Last, the hyper-adversarial attack to find better lower bounds seems extremely efficient, and we will consider it in the future.
+The most related work is Vhagar \cite{Vhagar}, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants). They do not however report actual 
+real-time certified robust percentage, as we do in Table \ref{table.cert}.
+Last, the hyper-adversarial attack to find better lower bounds seems extremely efficient, and we will consider it in the future.
 
 Technically, none of the MILP base work \cite{Vhagar,ITNE,GROCET} 
-consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even the "1v" MILP model. However, \cite{ITNE,GROCET} 
-defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our model, Eq.
+consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even the "1v" model. However, \cite{ITNE,GROCET} 
+defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our modelS, Eq.
 (3) from \cite{ITNE} corresponding essentially to it.

### 2025-07-31 AAAI2026/related.tex
related

@@
 
-Closer to our paper, several works consider a kind of global Lipschitz bound, to understand how the output change with input perturbations, as \cite{marabou} and \cite{ITNE,GROCET}.
+Closer to our paper, several works consider a kind of global Lipschitz bound, to understand how the output change with input perturbations, as \cite{Marabou} and \cite{ITNE,GROCET}.
 However, they do not consider whether the classification changes.
@@
 real-time certified robust percentage, as we do in Table \ref{table.cert}.
-Last, the hyper-adversarial attack to find better lower bounds seems extremely efficient, and we will consider it in the future.
+Last, their hyper-adversarial attack to find better lower bounds seems extremely efficient, and we will consider it in the future.
 
 Technically, none of the MILP base work \cite{Vhagar,ITNE,GROCET} 
-consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even the "1v" model. However, \cite{ITNE,GROCET} 
+consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE,GROCET} 
 defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our modelS, Eq.
 (3) from \cite{ITNE} corresponding essentially to it.
-\cite{Vhagar} do things differently, adding per neuron constraints, recovering .
+\cite{Vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem.

### 2025-07-31 AAAI2026/experiments.tex
experiments.tex

	\section{Experimental Evaluation}

	We implemented our code in Python 3.8.
	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.

	We will do experiments on two networks for MNIST dataset and another physical model. Two MNIST have the same structure. They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons. One of them is a normally trained neural network and another is for trained for adversarial robustness. We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI. As the name shows MNIST $5\times 100$-DiffAI has a better robustness. The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.

For each benchmark, we report three value: the bound obtained (lower value is better),
the solution obtained (distance to the bound depicts how close the model has converged),
and worst-case (higher is better) which is taking the the solution as input to the DNN. For a fully accurate model ("2v" or classical and all variables binary),
the worst-case will equal the solution, otherwise, it will be smaller.

\subsection{Classical vs our "2v" model}

\begin{table}[h!]
	\begin{tabular}{|l|c|c|c|}\hline\hline
		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
	Classical, $50 \times 2$ &    $.320$ &  $.320$ & $.017$ 
    \\\hline
    2v model, $50 \times 2$ &    {\bf .040} &  $.037$ & {\bf .018} 
    \\\hline \hline
    Classical, $100 \times 2$ &  .186  &  $.022$ & $.022$ 
    \\\hline
	2v model, $100 \times 2$&     {\bf .042} &  $.023$ &   {\bf .023} 
    \\\hline \hline
	\end{tabular}
	\caption{Comparison of the classical encoding with our "2v" model on the pipe system with a fixed timeout of 1000s, with either $50 \times 2$, 
    or the full $100 \times 2$ binary variables.}
    \label{table.classical}
\end{table}

	\subsection{Experimental results for robustness (MNIST)}

	\begin{table}[h!]
	\begin{tabular}{|l|c|c|c|c|}\hline\hline
		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ &  Time(s) \\\hline \hline
		1v, $375 \times 1$ & 17.472 & .909 & .092 & 43200 \\\hline 
		2v, $375 \times 2$ & 21.013 & 8.467& .223 & 43200 \\\hline		
		2v, $450 \times 2$ & 12.010 & 3.441 & {\bf .258} & 43200 \\\hline
		1v, $500 \times 1$ & ?? & ?? & ?? & 43200 \\\hline 
		3v, $500 \times 3$ & ?? & ?? & ?? & 43200 \\\hline 
	 2v, $500 \times 2$ & {\bf 8.761} & nan & nan & 43200 \\\hline\hline

	 2v, $485 \times 2$ & 20.646 & 1.915 & {\bf .372} & 130000 \\\hline\hline

		 2v, $500 \times 2$ & {\bf 8.257} & nan & nan & 260000 \\\hline\hline

	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models 
	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf full dimension} MNIST DNN, for timeouts of 43200s, 130000s and 260000s, where 375, 450, 485 or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
\end{table}

On the full space, we reach bounds of $8.2$ (on $\beta^{.5}_{6,8}$), which is too pessimistic as it allows to certify 0 image robust. The worst-case found by the "2v" $485 \times 2$ binary variables after 130000s only displays a difference of 
$0.37$, $20 \times$ away from the bound found.

\begin{figure*}[t!]
	\centering
\includegraphics[scale=0.5]{image.png} \hspace{0.8cm}
\includegraphics[scale=0.5]{perturb.png}
\caption{An improbable image and its perturbation (difference at x=13, y=18) 
with maximal $\beta^{.5}_{6,8}=0.37$ for MNIST as obtained by the "2v" $485 \times 2$ model in full 784 dimension image space.}
\end{figure*}

\paragraph{Reduced space}

We now consider a PCA model order reduction to avoid considering improbable images, 
speed up obtaining the bounds, and obtain less pessimistic bounds.
We settle on 20 orders, as the MNIST DNN considered run on a images obtained from projecting to the reduced order and projected back to the full dimension 
display the same accuracy of $97$\% as the DNN on the original images, meaning no accuracy is lost from reducing to 20 dimensions, which is the only thing which matters. On such a reduced space, bounds obtained are much more precise, and one can certify robustness of images online.

	\begin{table}[h!]
	\begin{tabular}{||l||c|c|c||}\hline\hline
		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ \\\hline \hline
1v, $400 \times 1$ & $1.414$ &  $.691$ & $.010$ \\\hline 
3v, $400 \times 3$ & $1.186$ & $.600$ & $.003$ \\\hline 
2v, $400 \times 2$ & $1.274$ & $.566$ & $.002$ \\\hline\hline

1v, $475 \times 1$ &  $1.408$ & $.301$ & $.008$  \\\hline 
3v, $475 \times 3$ &  $1.153$ & $.250$ & $.006$ \\ \hline 
2v, $475 \times 2$ &  $1.247$ & $.1957$ & $.019$ \\\hline\hline

1v, $500 \times 1$ & $1.412$ & $.161$ & .057 \\\hline 
3v, $500 \times 3$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
2v, $500 \times 2$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline

	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models 
	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of 14400s, where 400, 475,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
\end{table}

\begin{figure*}[t!]
	\centering
\includegraphics[scale=0.5]{redimage.png} \hspace{0.8cm}
\includegraphics[scale=0.5]{redperturb.png}
\caption{An image and its perturbation from the 20-dimension reduced space with maximal $\beta^{.5}_{6,8}=.084$ for MNIST as obtained by the "2v" $500 \times 2$ model.}
\end{figure*}

\begin{table}[h!]
	\begin{tabular}{||l||c|c|c|c||}\hline\hline
		model &    $L_1\leq 0.5$ & $L_1\leq 1$ & $L_1\leq 1.5$ &  $L_1\leq 2$ \\\hline \hline
		1v, $500\times1$ & $80 \%$ & $32\%$ & $7\%$ & $0\%$ \\\hline
		3v, $500 \times 3$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
		2v, $500 \times 2$ & 84\% & 51\% & 16\% & {\bf 4\%} \\\hline \hline
	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models 
	in the percentage of images they can certify in real-time for different values of $L_1$-perturbations.}
    \label{table.cert}
\end{table}

\subsection{Experiment results for regression (Pipe strain)}

	For the pipe system, to find a example of large difference on outputs is one of the main aims.

	\begin{figure*}[t!]
\includegraphics[scale=0.5]{deform.png} \hspace{0.8cm}
\includegraphics[scale=0.5]{strain.png}
\caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" $100 \times 2$ model.}
\end{figure*}

	The network of Pipe system is relatively simple and in the tests, we will open all $\ReLU$ nodes.

	We will compare the results of different modeling methods.

	\vspace*{1ex}

	\iffalse
	\begin{table}[h!]
	\begin{tabular}{|l|l|l|l|l|}\hline
		$L_1\leq 0.83$ &        Bound $\downarrow$ &  Solution $\uparrow$ &      Real $\uparrow$ &  Time \\\hline
		1v,open 100 &     {\bf 0.035613} &  0.035613 &                       0.01288 & 10608 \\\hline
		3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
		%3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
		2v,open 100 &     0.046719 &  0.024364 &  {\bf 0.024436} & 10922 \\\hline
	\end{tabular}
	\caption{Comparison of 1v,2v and 3v models on the pipe system with a fixed timeout of 10.000s.}
\end{table}
\fi

	\begin{table}[h!]
	\begin{tabular}{||l||c|c|c|c||}\hline\hline
		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ &  Time(s) \\\hline \hline
		1v, $100 \times 1$ &     {\bf .0356} &  $.0356$ & $.0191$ &  1000 \\\hline
		3v, $100 \times 3$&     .0414 &  .0254 &  .0166 &  1000 \\\hline
		2v, $100 \times 2$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline \hline
		3v, $97 \times 3$&      ?? &  ?? &  ?? & 14440 \\\hline
		3v, $100 \times 3$&      {\bf .0350} &  .0272 &  .0216 & 14440 \\\hline
		2v, $97 \times 2$&     ?? &  ?? &   ?? & 14440 \\\hline
		2v, $100 \times 2$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline \hline
		3v, $100 \times 3$&     {\bf .0329} &  .0277 &  .0165 & 72000 \\\hline
		2v, $100 \times 2$&     .0337 &  .0245 &  {\bf .0245} & 72000 \\\hline\hline
	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14440s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.
	L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}
\end{table}

### 2025-07-31 AAAI2026/related.tex
related

@@
 
-The most related work is Vhagar \cite{Vhagar}, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants). They do not however report actual 
+The most related work is Vhagar \cite{vhagar}, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants). They do not however report actual 
 real-time certified robust percentage, as we do in Table \ref{table.cert}.
@@
 
-Technically, none of the MILP base work \cite{Vhagar,ITNE,GROCET} 
+Technically, none of the MILP base work \cite{vhagar,ITNE,GROCET} 
 consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE,GROCET} 
@@
 (3) from \cite{ITNE} corresponding essentially to it.
-\cite{Vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem.
+\cite{vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem.

### 2025-07-31 AAAI2026/experiments.tex
exp

@@
 	We implemented our code in Python 3.8.
-	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
+	Gurobi 9.52 was used for solving the MILP problems. We conducted our evaluation on an AMD Threadripper 7970X ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.
 
-	We will do experiments on two networks for MNIST dataset and another physical model.
-Two MNIST have the same structure.
-They are full-connected DNN with 5, 10 outputs and 784 inputs; each hidden layer has 100 neurons.
-One of them is a normally trained neural network and another is for trained for adversarial robustness.
-We call them MNIST $5\times100$-Normal and MNIST $5\times 100$-DiffAI.
-As the name shows MNIST $5\times 100$-DiffAI has a better robustness.
-The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.
+	We consider two DNNs: one for MNIST, namely a pre-trained $5\times 100$ (available at \url{https://github.com/eth-sri/eran}), a 5 fully connected layers DNN, with 100 neurons each,	trained with diff AI \cite{deeppoly}.
+	Although it is relatively small, it is also of good quality with $97\%$ accuracy on classification, but it is not easy to certify for global robustness (the size of a network can be deceptive to know whether they are easy or hard to verify \cite{ATVA25}).
+	The second one is a 2 fully connected layers, 50 neurons each, learnt as a surrogate model, with 10 reduced input and 10 reduced output, that predict the plastic strain in 3000 points of a mesh over a pipe given the deformation of each of this 3000 points (through a PCA order reduction encoding all 3000 points with 10 dimensions in input and 26 dimensions in output), from \cite{aiware}.
+
+	MNIST is a classification benchmark, we thus report different bound $\beta^{\epsilon}_{i,j}$
+	for an $L_1$-deformation $\leq .5$. The pipe considers a mixture of $L_1 \leq 3.9$ and $L_\infty \leq 0.2$ perturbations, corresponding to physically pertinent dimensions, and 
+	maximizes the sum of the difference in output of 10 selected points in the mesh between an input and its deformation.
 
@@
 the solution obtained (distance to the bound depicts how close the model has converged),
-and worst-case (higher is better) which is taking the the solution as input to the DNN. For a fully accurate model ("2v" or classical and all variables binary),
+and worst-case (higher is better) which is taking the solution as input to the DNN. For a fully accurate model ("2v" or classical and all variables binary),
 the worst-case will equal the solution, otherwise, it will be smaller.
@@
 \subsection{Classical vs our "2v" model}
+
+We start by evaluating how accurate the 2v model is vs the classical encoding, both when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
+We use the pipe models which is easier to handle, and set the time-out at 1000s for both models.
 
@@
 \end{table}
+
+We confirm both that the LP relaxation of the classical model is extremely poor, with bounds 8 times worst than using our "2v" model.
+Further, even using a fully accurate mode with all 100x2 variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.
 

### 2025-07-31 AAAI2026/related.tex
exp

@@
 consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE,GROCET} 
-defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our modelS, Eq.
+defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our models, Eq.
 (3) from \cite{ITNE} corresponding essentially to it.

### 2025-07-31 AAAI2026/experiments.tex
exp

@@
 	MNIST is a classification benchmark, we thus report different bound $\beta^{\epsilon}_{i,j}$
-	for an $L_1$-deformation $\leq .5$. The pipe considers a mixture of $L_1 \leq 3.9$ and $L_\infty \leq 0.2$ perturbations, corresponding to physically pertinent dimensions, and 
+	for an $L_1$-deformation $\leq .5$. The pipe considers a conjunction of $L_1 \leq 3.9$ and $L_\infty \leq 0.2$ perturbations, corresponding to physically pertinent dimensions, and 
 	maximizes the sum of the difference in output of 10 selected points in the mesh between an input and its deformation.
@@
 and worst-case (higher is better) which is taking the solution as input to the DNN. For a fully accurate model ("2v" or classical and all variables binary),
-the worst-case will equal the solution, otherwise, it will be smaller.
+the worst-case will equal the solution, otherwise, it will be smaller due to abstraction.
 
@@
 We start by evaluating how accurate the 2v model is vs the classical encoding, both when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
-We use the pipe models which is easier to handle, and set the time-out at 1000s for both models.
+We use the pipe models which is easier to verify, and set the time-out at 1000s for both models.
 
@@
 
-We confirm both that the LP relaxation of the classical model is extremely poor, with bounds 8 times worst than using our "2v" model.
-Further, even using a fully accurate mode with all 100x2 variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.
+We confirm that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model.
+Further, even using a fully accurate model with all $100 \times 2$ variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.
 

### 2025-07-31 AAAI2026/abstract.tex
global pass

@@
 Last, we use order reduction techniques to reduce the space of inputs considered, avoiding unrealistic images, by using principal component analysis (PCA).
-This results into the real-time  certification of the robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of 0.5, as well as for a surrogate computing the
+This results into the real-time  certification of the robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of $.5$, as well as for a surrogate computing the
 %latent

### 2025-07-31 AAAI2026/experiments.tex
global pass

@@
 
-For each benchmark, we report three value: the bound obtained (lower value is better),
+For each benchmark, we report three values: the bound obtained (lower value is better),
 the solution obtained (distance to the bound depicts how close the model has converged),
@@
 
+We then turn to the MNIST classification benchmark, and report one particular bound $\beta^{.5}_{i,j}$, namely for $i=6,j=8$ as a confusion between a 6 and a 8 is possible, provided in Table \ref{table.mnist}.
+
 	\begin{table}[h!]
@@
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models 
+	\caption{TO BE UPDATED. Comparison of "1v", "3v" and "2v" models 
 	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf full dimension} MNIST DNN, for timeouts of 43200s, 130000s and 260000s, where 375, 450, 485 or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+	\label{table.mnist}
 \end{table}
 
-On the full space, we reach bounds of $8.2$ (on $\beta^{.5}_{6,8}$), which is too pessimistic as it allows to certify 0 image robust.
-The worst-case found by the "2v" $485 \times 2$ binary variables after 130000s only displays a difference of
-$0.37$, $20 \times$ away from the bound found.
+On the full space, the best bounds $(\beta^{.5}_{i,j})_{i < j \leq 10}$ reached are too pessimistic: they allow to certify no image robust in real-time.
+One of the reason, besides that the verification question is very complicated with 1000 binary variables for the accurate model, is that working in the full $784$ dimensional space allow for very unlikely inputs, far away from what the DNN has learnt from, making the search very long and the bound very pessimistic.
+As an illustration of that, we display on Fig.~\ref{fig3} the worst-case as found by our models, which is very improbable to be ever encountered in the MNIST benchmark.
 
@@
 with maximal $\beta^{.5}_{6,8}=0.37$ for MNIST as obtained by the "2v" $485 \times 2$ model in full 784 dimension image space.}
+\label{fig3}
 \end{figure*}
@@
 
-We now consider a PCA model order reduction to avoid considering improbable images, 
-speed up obtaining the bounds, and obtain less pessimistic bounds.
-We settle on 20 orders, as the MNIST DNN considered run on a images obtained from projecting to the reduced order and projected back to the full dimension 
-display the same accuracy of $97$\% as the DNN on the original images, meaning no accuracy is lost from reducing to 20 dimensions, which is the only thing which matters.
-On such a reduced space, bounds obtained are much more precise, and one can certify robustness of images online.
+To remove improbable images and limit the space of search, 
+we consider a PCA model order reduction: We settled on reduction to 20 dimensions, because the MNIST $100 \times 5$ DNN considered, once run on images obtained from projecting to the reduced order and projected back to the full dimensional space displays the same accuracy of $97$\% as the DNN on the original images.
+This means that considering the reduced 20 dimensional space
+does not incur any loss in accuracy, which is the only thing which matters.
+On this reduced space, bounds obtained are much more precise, and one can concretly certify in real-time robustness of images.
 
@@
 	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of 14400s, where 400, 475,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+	\label{table.reduced}
 \end{table}
+
+We report in Table \ref{table.reduced} the same $\beta^{.5}_{6,8}$
+as in Table \ref{table.mnist}, obtained with the same time-out. The bounds are directly comparable: $\beta^{.5}_{6,8}$ obtained using the reduced dimension is $\approx 8$ times smaller
+than when using the full dimension.
+With these bounds, most images ($86\%$) can be certified in real-time robust for a perturbation $L_1 \leq .5$, and even $53\%$ with a perturbation $L_1 \leq 1$ twice as large, see Table \ref{table.cert}.
+We illustrate that improbable images are removed by displaying in Fig.~\ref{fig4} the worst-case obtained for $\beta^{.5}_{6,8}$, which indeed looks like a realistic MNIST instance.
 
@@
 \caption{An image and its perturbation from the 20-dimension reduced space with maximal $\beta^{.5}_{6,8}=.084$ for MNIST as obtained by the "2v" $500 \times 2$ model.}
+\label{fig4}
 \end{figure*}
@@
 
-	For the pipe system, to find a example of large difference on outputs is one of the main aims.
+	For the pipe system, we compared in Table \ref{table.pipe} the different models "1v","2v","3v" to produce bounds on the sum of the difference of strain over 10 specific points of the mesh, for a physically relevant perturbation of the deformation.
+The bounds we found are quite accurate, with a best bound of ".0329" obtained by the "3v" model, slightly better than the bound $.0337$ found within the same time by the "2v" model, and better than the bound found $0.356$ by the "1v" model, although this bound has been found 70 times faster due to the simpler model.
+The certified lower bound is not so far, at $.245$, found by the fully accurate "2v" model when all the variables are binary.
+We did chcek that this worst-case found, displayed in Fig.
+\ref{fig5}, which is not too far from the actual worst case $<.0337$, is coherent wit the physical Finite Element system the DNN has been learnt from, hence this is not an hallucination due to the brittleness of the DNN learnt.
 
@@
 \caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" $100 \times 2$ model.}
+\label{fig5}
 \end{figure*}
-
-	The network of Pipe system is relatively simple and in the tests, we will open all $\ReLU$ nodes.
-
-	We will compare the results of different modeling methods.
 
@@
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14440s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.
-	L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}
+	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14440s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
+	%L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}
+	\label{table.pipe}
 \end{table}

### 2025-07-31 AAAI2026/global.tex
related
global pass

@@
-	\section{MILP Models for global verification}
+	\section{MILP Models for global robustness}
 
@@
 
-    The most straightforward idea to encode the global verification question is to 
-    consider variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ and of its perturbation $I'$,
-    using the classical encoding (\ref{eq11}) \cite{MILP} for each variable, 
-    that we call $\mathcal{M}^{classical}$.
+    To encode global robustness, \cite{lipshitz,vhagar} consider 
+	variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ 
+	and of its perturbation $I'$,
+    using the classical encoding (\ref{eq11}) \cite{MILP} for each variable.
     Further:
     \begin{enumerate}
-		\item For each input nodes $x_j,x'_j$ of $I,I'$, we add constraints
+		\item For each input nodes $x_j,x'_j$ of $I,I'$, add constraints
         $|x_j-x'_j| \leq \varepsilon$ 
-        ($L_\infty$-perturbation - see next section for $L_1$).
-		\item We set the optimization objective as maximize $x_i - x_j +x'_j - x'_i$ to compute $\beta^\varepsilon_{i,j}=\beta^\varepsilon_{j,i}$.
+        ($L_\infty$-perturbation - see later for $L_1$).
+		\item The optimization objective is to maximize $x_C - x_D +x'_D - x'_C$ 
+		to compute $\beta^\varepsilon_{C,D}=\beta^\varepsilon_{D,C}$, 
+		for $C \neq D$ two decision classes.
 	\end{enumerate}
 
-	This model contains twice as many (binary) variables as for local robustness. As the worst-case complexity of solving an MILP model 
-    is exponential in the number of binary variables, it will be computationally intractable to compute $\beta^\varepsilon_{i,j}$ in this way, but for very small DNNs.
-As explained in the previous section, the standard way is to rely on relaxing at least some of the binary variables into linear variables.
+	We call this encoding $\mathcal{M}^{classical}$.
+	It contains twice as many (binary) variables as for local robustness. 
+	%As the worst-case complexity of solving an MILP model is exponential in the number of binary variables, it will be computationally intractable to compute $\beta^\varepsilon_{i,j}$ in this way, but for very small DNNs.
+	As explained in the previous section, the standard way to make the model more efficient is to rely on relaxing at least some of the binary variables into linear variables.
 
     The problem is that the LP relaxation of this classical encoding is extremely inaccurate, as variables $x_j,x'_j$ dependencies are due solely on the function definition through common ancestor variables in previous layers - as this is approximated with LP, most of the dependencies will be lost.
-
 On top of being an issue with partial MILP models, LP relaxation is also used during the Branch and Bound process internal to MILP solvers to provide bounds for each branch.
 So even when all variables are opened and the MILP model is fully accurate, the classical encoding will likely not be efficient as well.
-
-    We will check that in table \ref{table.classical} in Section Experimental Evaluation.
+Notice that this was already witnessed in \cite{lipshitz}, and some additional constraints were added to make the classical model more accurate.
+We will compare the different methods in table \ref{table.classical}.
 
@@
 
-    The idea to circumvent the loss of dependencies when applying linear relaxation is to switch the variables towards $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with
-    $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$.
+	We now present our novel faithful "2v" model.
+    First, we consider variables $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with     $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$, as already proposed in \cite{lipshitz}.
 	Intuitively, the diff variables will be small as they will be carrying the difference between both the image $I$ and its perturbation $I'$.
     We will use the classical MILP encoding for $\hat{x}'_j$.
-    However, we cannot apply the classical MILP encoding (\ref{eq11}) \cite{MILP} on the diff variable $\hat{y}_j$. Instead we study the function of 
+
+    However, unlike \cite{lipshitz}, we do not apply the classical MILP encoding (\ref{eq11}) \cite{MILP} on the diff variable $\hat{y}_j$. Instead we study the function of 
     $\hat{y}_j$ given $y_j$ and $x'_j$, and encode it into a novel MILP model.
@@
 
+	\iffalse
 \paragraph{A proof of Prop.~\ref{Prop2}}
@@
 Case 4: if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 5.
+
+\fi
 
@@
 
-	\begin{figure}[b!]
+    \subsection{A decoupled "3v" model}
+
+	Besides doing LP relaxation on some of the binary variables, we propose a 
+    variant of the "2v" model: the binary variables $a'$ appearing in 
+    Prop.
+\ref{Prop2} can be decoupled from the binary variable appearing in the classical encoding of $x'_i = \ReLU(x'_i)$.
+While this means having 3 binary variables per unstable ReLU (which warrants the name "3v" model), the fact that these variables are decouples remove a lot of constraints in the MILP encoding, and actually helps the solver.
+The decoupling also means that the "3v" model is not as accurate as the "2v" model.
+
+	\subsection{The efficient "1v" model}
+
+		\begin{figure}[t!]
 		\centering
@@
 \end{figure}
-
-    \subsection{A decoupled "3v" model}
-
-	Besides doing LP relaxation on some of the binary variables, we propose a 
-    variant of the "2v" model: the binary variables $a'$ appearing in 
-    Prop.
-\ref{Prop2} can be decoupled from the binary variable appearing in the classical encoding of $x'_i = \ReLU(x'_i)$.
-While this means having 3 binary variables per unstable ReLU (which warrants the name "3v" model), the fact that these variables are decouples remove a lot of constraints in the MILP encoding, and actually helps the solver.
-The decoupling also means that the "3v" model is not as accurate as the "2v" model.
-
-	\subsection{The efficient "1v" model}
 

### 2025-07-31 AAAI2026/introduction.tex
global pass

@@
 This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools.
-Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT \cite{pyrat} MnBAB \cite{ferrari2022complete}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT \cite{pyrat} MnBAB \cite{ferrari2022complete}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
 
@@
 given a DNN, an image and a small neighborhood around this image, is it the case that all the images in the neighborhood are classified in the same way by the DNN?
-The neighborhood is provided by a maximal perturbation of the input image, often an $L_0$ perturbation, i.e.
-every subpixel of the input image can vary in a very small range, typically
-$\frac{2}{255}$ (that is 2 levels of grey/blue/right/green), as $L_0$ is perfectly linear and perturbations of subpixels are independent.
-While the $L_0$ norm is the easiest to handle, it is not necessarily the most meaningful perturbation.
+The neighborhood is provided by a maximal perturbation of the input image, often an $L_\infty$ perturbation, i.e.
+every subpixel of the input image can vary in a very small range, typically $\frac{2}{255}$ (that is 2 levels of grey/blue/right/green), as $L_\infty$ is perfectly linear and perturbations of subpixels are independent.
+While the $L_\infty$ norm is the easiest to handle, it is not necessarily the most meaningful perturbation.
 More importantly, verification tools for local robustness are hard to be used in a real-time decision making pipeline: considering an autonomous car with a video feed from the dashboard, it is computationally too intensive to certify in few ms images of the feed to e.g.
@@
 
-In this paper, we consider {\em global} robustness, that is we do not restrict the certification process to the neighborhood of an input.
-We propose a two steps procedure.
-The first step, performed offline once,
-computes global bounds on the shift between 
-output values of different decision classes due to the perturbation. That is, considering decision classes $C$ and $D$ and perturbation $\varepsilon$, compute 
+In this paper, we consider {\em global} robustness, that is we do not restrict the certification process to the neighborhood of an input. We follow a two steps procedure. 
+The first step, performed offline once, computes global bounds on the shift between 
+output values of different decision classes due to the perturbation, as proposed in \cite{vhagar}. 
+That is, considering decision classes $C$ and $D$ and perturbation $\varepsilon$, compute 
 {\em global bound} $\beta^\varepsilon_{C,D} \geq \max_{I,I', |I-I'| \leq \epsilon}(value_{I}(C) - value_{I}(D) + value_{I'}(D) - value_{I'}(C))$, where $value_{J}(X)$ is the output value of class $X \in \{C,D\}$ for input image $J \in \{I,I'\}$.
@@
 
-	\item Since the problem is a very hard verification problem (the values each neuron can take is not bound to a small neighborhood), we follow the accurate MILP technique in \cite{ATVA25}.
-The number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed.
-Recall that the worst case complexity of MILP is exponential in the number of binary variables \cite{DivideAndSlide}.
-A straightforward MILP model would be to use the {\em classical MILP model} \cite{MILP} for each of these variables.
-While the full MILP model is exact, it is too computationally intensive to be run for anything but small DNNs.
-As explained in \cite{ATVA25}, many variables need to be linearly relaxed to reach useable bounds.
+	\item We develop a novel exact MILP encoding for the global robustness problem,
+	called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}).
+We study and encode exactly in MILP how the {\em diff variables} evolve after passing through a ReLU (Prop.~\ref{Prop2}).
+Compared with the
+	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz},
+	the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other.
+This was witnessed in \cite{lipshitz}, and constraints encoding a part of the linear relaxation of our "2v" model were added explicitly.
+Experimentally,
+	our "2v" model provides more accurate bounds than competing models, in the same runtime
+	(Table \ref{table.classical}).
+	%The number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed.
+	%Recall that the worst case complexity of MILP is exponential in the number of binary variables \cite{DivideAndSlide}. 
+	%A straightforward MILP model would be to use the  for each of these variables, as in \cite{vhagar,lipshitz}.
 The main issue with the classical model is that its linear relaxations is extremely inaccurate, as the variables are independent of each other.
-Instead, we develop another exact MILP model, called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}).
-We study and encode exactly how the diff variables evolve after passing through a ReLU (figure \ref{fig.2v}).
-In this model, the linear relaxation is much more accurate, as each
-	{\em diff variable} can be bounded 	after a ReLU as a function of the value of the {\em diff variables} before the ReLU.
-We propose 2 lighter models, namely the {\em "3v" model} which decouples one of the variable (less constraint means less accuracy), as well as an efficient {\em "1v" model} only considering the {\em diff variables} but forgetting the value of the perturbed neurons (with half the (binary) variables).
+Instead, we develop another exact MILP model,
+	Further, we develop two abstract MILP models, namely the {\em "3v" model} which decouples one of the variable, helping the solver, as well as an efficient {\em "1v" model} only considering the {\em diff variables} but forgetting the value of the perturbed neurons.
 
-	\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation.
+	%\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation.
 The chosen number of binary variables depends upon the complexity of the DNN as well as the targeted runtime.
 
-   \item  In terms of perturbations, we consider conjunctions of $L_0$ and $L_1$ norms, which allows to accurately describe perturbations.
-For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_0$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$ perturbation).
-While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, we explain how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
+   \item  In terms of perturbations, we consider conjunctions of $L_\infty$ and $L_1$ norms, which allows to accurately describe perturbations.
+For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_\infty$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$ perturbation).
+While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop \ref{prop3} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
 
@@
 Also, the runtime to obtain the bound is particularly long.
-Finally, when computing worst-case
-	pairs (image, perturbation), improbable images are generated, hence these  are not meaningful.
+	%Finally, when computing worst-case 
+	%pairs (image, perturbation), improbable images are generated, hence these  are not meaningful. 
 	To solve this problem, we restrict the input space to ignore improbable inputs, using model order reduction techniques from engineering science \cite{aiware}.
@@
 	%(using a projection to the reduced space then the inverse projection to obtain a very similar image understandable by the DNN). 
-	On the MNIST benchmark, this means 20 linear dimensions to match the $97\%$ accuracy of the DNN we considered, instead of the 768 dimensions of the full image space.
+	On the MNIST benchmark, this means 20 linear dimensions to match the $97\%$ accuracy of the DNN we considered, instead of the 784 dimensions of the full image space.
 Using PCA, which is linear, makes it easy to specify perturbations on the actual image (where it is meaningful) rather than on the reduced space.
 
-\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in real time that $86\%$ of the images are robust for an $L_1$ perturbation of $0.5$, resp.
+\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in real time that $86\%$ of the images are robust for an $L_1$ perturbation of $.5$, resp.
 $53\%$ for an $L_1$ perturbation of $1$.
-We finally experimented our MILP models for {\em regression} tasks, considering a DNN surrogate built from a slow physical finite element model, providing the deformation and the plastic strain of a pipe \cite{aiware}.
+We finally experimented our MILP models for a {\em regression} task as well, considering a DNN surrogate built from a slow physical finite element model, providing the deformation and the plastic strain of a pipe \cite{aiware}.
 The DNN has been learnt on a reduced order basis already of dimension 10, from thousands of input dimensions.
@@
 Here we want to obtain bounds (which is what our models provide), as well as generating worst-case (image,perturbation) pair, where the strain is particularly different, close to the bound, and that can be run in the physical model to understand whether the DNN surrogate is faithful.
-Our tool was helpful to provide limited bounds, as well as almost matching worst-case (image,perturbation) pair that was confirmed in the physical model.
-
-\item In both cases, the best bounds were obtained using the "3v" model, as the theoretically more accurate "2v" model did not converge enough even after a very large timeout.
-Still, when trying to produce worst case pairs (image, perturbation), which is somehow easier than certifying bounds as heuristics to guide towards a solution can be used, the "2v" model found worser-case solutions.
-Last, the "1v" model produced bounds as good as the "2v" models and much faster than the "3v" models, although slightly larger.
-That is, all 3 MILP models we propose have favorable trade-offs in different contexts.
+Our tool was helpful to provide limited bounds, as well as an almost matching worst-case (image,perturbation) pair that was confirmed in the physical model.
+Overall, the "2v" model generates accurate bounds. The decoupling of variables generating the "3v" model offers good trade-offs, reaching slightly lower bounds in the same runtime. 
+The "1v" model is faster to converge, but also generates larger bounds, unless runtime is very restricted (Table \ref{table.pipe}).
 \end{enumerate}

### 2025-07-31 AAAI2026/notation.tex
global pass

@@
     $\hat{y}_j = \hat{x}_j - \hat{x}'_j$ (and {\em not} 
-    $\hat{y}_i = \ReLU(x_j-x'_j)$). 
+    $\hat{y}_i = \ReLU(x_j-x'_j)$), similarly than in the ITNE model \cite{lipshitz}. 
     \end{itemize}
@@
 
-	\section{(partial) MILP}
+	%\section{MILP for local robustness}
 
@@
 
-	Mixed Integer Linear Programming (MILP) value abstraction is an accurate encoding of ReLU DNNs. For an unstable neuron $n$, that is with values 
+	Mixed Integer Linear Programming (MILP) can encode faithfully ReLU DNNs:
+	For an unstable neuron $n$, that is with values 
     $x \in [\LB(n),\UB(n)]$ with $\LB(n)<0<\UB(n)$, 
@@
 
-    We use $\mathcal{M}$ to denote the whole MILP model, where each unstable ReLU are encoded in the above way with one integer variable. 
+    Let $\mathcal{M}$ denote the whole MILP model, where each unstable ReLU are encoded in the above way with one integer variable. 
 	The encoding from $(\hat{x}_j)_{j \text{ in layer } i}$ to 

### 2025-08-01 AAAI2026/experiments.tex
experiments

@@
 
-\subsection{Classical vs our "2v" model}
+\subsection{Classical vs our "2v" model vs ITNE}
 
-We start by evaluating how accurate the 2v model is vs the classical encoding, both when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
-We use the pipe models which is easier to verify, and set the time-out at 1000s for both models.
+We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement in Gurobi by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
+(3) of \cite{lipshitz} (and also to the relaxation of our "1v" model).
+We compare when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
+We use the pipe models which is easier to verify, and set the time-out at 1000s for all models.
 
@@
     \\\hline
-    2v model, $50 \times 2$ &    {\bf .040} &  $.037$ & {\bf .018} 
+	ITNE, $50 \times 2$ &    $.042$ &  $.037$ & $.022$
+	\\ \hline
+    2v model, $50 \times 2$ &    {\bf .040} &  $.037$ &  $.018$ 
     \\\hline \hline
     Classical, $100 \times 2$ &  .186  &  $.022$ & $.022$ 
+    \\\hline
+	ITNE, $100 \times 2$ &    $.045$ &  $.023$ & {\bf .023} 
     \\\hline
@@
 	\end{tabular}
-	\caption{Comparison of the classical encoding with our "2v" model on the pipe system with a fixed timeout of 1000s, with either $50 \times 2$, 
+	\caption{Comparison of the classical encoding, ITNE and our "2v" model on the pipe system with a fixed timeout of 1000s, with either $50 \times 2$, 
     or the full $100 \times 2$ binary variables.}
@@
 
-We confirm that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model.
+Table \ref{table.classical}, $50 \times 2$, confirms that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model, when 50 variables use LP relaxation only.
+Adding explicitly LP relaxation constraints of Eq.
+(3) from \cite{lipshitz} recovers most but not all the bound of the "2v" model.
+
 Further, even using a fully accurate model with all $100 \times 2$ variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.
+Again,
+Eq. (3) from \cite{lipshitz} recovers most but not all the accuracy of the "2v" model.
+Overall, the "2v" model produces better bounds, even with short time-outs, despite its higher complexity.
 
@@
 
-We then turn to the MNIST classification benchmark, and report one particular bound $\beta^{.5}_{i,j}$, namely for $i=6,j=8$ as a confusion between a 6 and a 8 is possible, provided in Table \ref{table.mnist}.
+We then turn to the MNIST classification benchmark, and report 
+in Table \ref{table.mnist} one particular bound $\beta^{.5}_{i,j}$, namely for $i=6,j=8$ as confusion between 6 and 8 happens.
 
 	\begin{table}[h!]
-	\begin{tabular}{|l|c|c|c|c|}\hline\hline
-		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ &  Time(s) \\\hline \hline
-		1v, $375 \times 1$ & 17.472 & .909 & .092 & 43200 \\\hline 
-		2v, $375 \times 2$ & 21.013 & 8.467& .223 & 43200 \\\hline		
-		2v, $450 \times 2$ & 12.010 & 3.441 & {\bf .258} & 43200 \\\hline
-		1v, $500 \times 1$ & ?? & ?? & ?? & 43200 \\\hline 
-		3v, $500 \times 3$ & ?? & ?? & ?? & 43200 \\\hline 
-	 2v, $500 \times 2$ & {\bf 8.761} & nan & nan & 43200 \\\hline\hline
-
-	 2v, $485 \times 2$ & 20.646 & 1.915 & {\bf .372} & 130000 \\\hline\hline
-
-		 2v, $500 \times 2$ & {\bf 8.257} & nan & nan & 260000 \\\hline\hline
-
+		\centering
+	\begin{tabular}{||l||c|c|c||}\hline\hline
+		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
+		1v, $500 \times 1$ & $15.67$ & $.620$ & $.012$ \\\hline 
+		3v, $500 \times 3$ & $16.09$ & $.755$ & {\bf .207} \\\hline 
+	    2v, $500 \times 2$ & {\bf 8.99} & nan & nan \\\hline\hline	 
 	\end{tabular}
-	\caption{TO BE UPDATED. Comparison of "1v", "3v" and "2v" models 
-	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf full dimension} MNIST DNN, for timeouts of 43200s, 130000s and 260000s, where 375, 450, 485 or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+	\caption{Comparison of "1v", "3v" and "2v" models 
+	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf full dimension} MNIST DNN, 
+	for timeouts of $14400$s, when all 500 ($\times 1$, $\times 2$, $\times 3$) variables are binary.}
 	\label{table.mnist}
@@
 \caption{An improbable image and its perturbation (difference at x=13, y=18) 
-with maximal $\beta^{.5}_{6,8}=0.37$ for MNIST as obtained by the "2v" $485 \times 2$ model in full 784 dimension image space.}
+with maximal $\beta^{.5}_{6,8}=0.207$ for MNIST as obtained by the "3v" $500 \times 2$ model in {\bf full 784 dimension} image space.}
 \label{fig3}
@@
 
+\begin{figure*}[t!]
+	\centering
+\includegraphics[scale=0.5]{redimage.png} \hspace{0.8cm}
+\includegraphics[scale=0.5]{redperturb.png}
+\caption{An image and its perturbation from the {\bf 20-dimension reduced space} with maximal $\beta^{.5}_{6,8}=.084$ for MNIST as obtained by the "2v" $500 \times 2$ model.}
+\label{fig4}
+\end{figure*}
+
 \paragraph{Reduced space}
+
+\begin{table}[b!]
+	\centering
+	\begin{tabular}{||l||c|c|c||}\hline\hline
+		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ \\\hline \hline
+%1v, $400 \times 1$ & $1.414$ &  $.691$ & $.010$ \\\hline 
+%3v, $400 \times 3$ & $1.186$ & $.600$ & $.003$ \\\hline 
+%2v, $400 \times 2$ & $1.274$ & $.566$ & $.002$ \\\hline\hline
+
+%1v, $475 \times 1$ &  $1.408$ & $.301$ & $.008$  \\\hline 
+%3v, $475 \times 3$ &  $1.153$ & $.250$ & $.006$ \\ \hline 
+%2v, $475 \times 2$ &  $1.247$ & $.1957$ & $.019$ \\\hline\hline
+
+1v, $500 \times 1$ & $1.412$ & $.161$ & .057 \\\hline 
+3v, $500 \times 3$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
+2v, $500 \times 2$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline
+
+	\end{tabular}
+	\caption{Comparison of "1v", "3v" and "2v" models 
+	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of 14400s, where 
+	all the %400, 475,  or 
+	500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+	\label{table.reduced}
+\end{table}
 
@@
 
-	\begin{table}[h!]
-	\begin{tabular}{||l||c|c|c||}\hline\hline
-		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ \\\hline \hline
-1v, $400 \times 1$ & $1.414$ &  $.691$ & $.010$ \\\hline 
-3v, $400 \times 3$ & $1.186$ & $.600$ & $.003$ \\\hline 
-2v, $400 \times 2$ & $1.274$ & $.566$ & $.002$ \\\hline\hline
-
-1v, $475 \times 1$ &  $1.408$ & $.301$ & $.008$  \\\hline 
-3v, $475 \times 3$ &  $1.153$ & $.250$ & $.006$ \\ \hline 
-2v, $475 \times 2$ &  $1.247$ & $.1957$ & $.019$ \\\hline\hline
-
-1v, $500 \times 1$ & $1.412$ & $.161$ & .057 \\\hline 
-3v, $500 \times 3$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
-2v, $500 \times 2$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline
-
-	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models 
-	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of 14400s, where 400, 475,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
-	\label{table.reduced}
-\end{table}
-
-We report in Table \ref{table.reduced} the same $\beta^{.5}_{6,8}$
-as in Table \ref{table.mnist}, obtained with the same time-out. The bounds are directly comparable: $\beta^{.5}_{6,8}$ obtained using the reduced dimension is $\approx 8$ times smaller
-than when using the full dimension.
-With these bounds, most images ($86\%$) can be certified in real-time robust for a perturbation $L_1 \leq .5$, and even $53\%$ with a perturbation $L_1 \leq 1$ twice as large, see Table \ref{table.cert}.
-We illustrate that improbable images are removed by displaying in Fig.~\ref{fig4} the worst-case obtained for $\beta^{.5}_{6,8}$, which indeed looks like a realistic MNIST instance.
-
-\begin{figure*}[t!]
-	\centering
-\includegraphics[scale=0.5]{redimage.png} \hspace{0.8cm}
-\includegraphics[scale=0.5]{redperturb.png}
-\caption{An image and its perturbation from the 20-dimension reduced space with maximal $\beta^{.5}_{6,8}=.084$ for MNIST as obtained by the "2v" $500 \times 2$ model.}
-\label{fig4}
-\end{figure*}
-
-\begin{table}[h!]
+\begin{table}[b!]
 	\begin{tabular}{||l||c|c|c|c||}\hline\hline
@@
 	\caption{Comparison of "1v", "3v" and "2v" models 
-	in the percentage of images they can certify in real-time for different values of $L_1$-perturbations.}
+	in the percentage of images certified robust in real-time 
+	using the computed $(\beta^{.5}_{i,j})_{i < j \leq 10}$  for different values of $L_1$-perturbations.}
     \label{table.cert}
@@
 
+We report in Table \ref{table.reduced} the same $\beta^{.5}_{6,8}$
+as in Table \ref{table.mnist}, obtained with the same time-out.
+The bounds are directly comparable: the best $\beta^{.5}_{6,8}$ obtained using the reduced dimension is $\approx 8$ times smaller than when using the full dimension ($1.137$ vs $8.99$).
+With these bounds, most images ($86\%$) can be certified in real-time robust for a perturbation $L_1 \leq .5$, and even $53\%$ with a perturbation $L_1 \leq 1$ twice as large, see Table \ref{table.cert}.
+We illustrate that improbable images are removed by displaying in Fig.~\ref{fig4} the worst-case obtained for $\beta^{.5}_{6,8}$, which indeed looks like a realistic MNIST instance.
+
 \subsection{Experiment results for regression (Pipe strain)}
-
-	For the pipe system, we compared in Table \ref{table.pipe} the different models "1v","2v","3v" to produce bounds on the sum of the difference of strain over 10 specific points of the mesh, for a physically relevant perturbation of the deformation.
-The bounds we found are quite accurate, with a best bound of ".0329" obtained by the "3v" model, slightly better than the bound $.0337$ found within the same time by the "2v" model, and better than the bound found $0.356$ by the "1v" model, although this bound has been found 70 times faster due to the simpler model.
-The certified lower bound is not so far, at $.245$, found by the fully accurate "2v" model when all the variables are binary.
-We did chcek that this worst-case found, displayed in Fig.
-\ref{fig5}, which is not too far from the actual worst case $<.0337$, is coherent wit the physical Finite Element system the DNN has been learnt from, hence this is not an hallucination due to the brittleness of the DNN learnt.
 
@@
 \end{figure*}
+
+	For the pipe system, we compared in Table \ref{table.pipe} the different models "1v","2v","3v" to produce bounds on the sum of the difference of strain over 10 specific points of the mesh, for a physically relevant perturbation of the deformation.
+The bounds we found are quite accurate, with a best bound of ".0329" obtained by the "3v" model, slightly better than the bound $.0337$ found within the same time by the "2v" model, and better than the bound found $0.356$ by the "1v" model, although this bound has been found 70 times faster due to the simpler model.
+The certified lower bound is not so far, at $.245$, found by the fully accurate "2v" model when all the variables are binary.
+We did check that this worst-case found, displayed in Fig.
+\ref{fig5}, which is not too far from the actual worst case $<.0337$, is coherent wit the physical Finite Element system the DNN has been learnt from, hence this is not an hallucination due to the brittleness of the DNN learnt.
 
@@
 		2v, $100 \times 2$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline \hline
-		3v, $97 \times 3$&      ?? &  ?? &  ?? & 14440 \\\hline
+		%3v, $97 \times 3$&      ?? &  ?? &  ?? & 14440 \\\hline
 		3v, $100 \times 3$&      {\bf .0350} &  .0272 &  .0216 & 14440 \\\hline
-		2v, $97 \times 2$&     ?? &  ?? &   ?? & 14440 \\\hline
+		%2v, $97 \times 2$&     ?? &  ?? &   ?? & 14440 \\\hline
 		2v, $100 \times 2$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline \hline

### 2025-08-01 AAAI2026/introduction.tex
experiments

@@
 	the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other.
-This was witnessed in \cite{lipshitz}, and constraints encoding a part of the linear relaxation of our "2v" model were added explicitly.
-Experimentally,
+This was observed in \cite{lipshitz}, and constraints encoding
+	a part of the linear relaxation of our "2v" model were added explicitly. Experimentally, 
 	our "2v" model provides more accurate bounds than competing models, in the same runtime
@@
 Instead, we develop another exact MILP model,
-	Further, we develop two abstract MILP models, namely the {\em "3v" model} which decouples one of the variable, helping the solver, as well as an efficient {\em "1v" model} only considering the {\em diff variables} but forgetting the value of the perturbed neurons.
-
+	Further, we develop two abstract MILP models, namely the "3v" model which decouples the 
+	{\em non-diff binary variables} of the "2v" model, resulting in looser bounds but with lower runtimes, as well as a computationally efficient "1v" model that only considers the 
+	{\em diff variables}, however resulting in much looser bounds.
 	%\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation.
@@
 For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_\infty$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$ perturbation).
-While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop \ref{prop3} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
+While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop.~\ref{prop3} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
 

### 2025-08-01 AAAI2026/Lipitschz.tex
related
global pass

@@
 
-\title{Order reduction and partial MILP models \\
-	for certifying Robustness of DNNs globally.}
+\title{Order reduction and MILP models for certifying Robustness of DNNs globally.}
 \date{}
@@
 
-	\newpage
+	\vspace{-0.5cm}
+	\input{related}
 
-	\hfill
+\section{Conclusion}
+
+In this paper, we introduced a novel "2v" MILP model for global verification question, which is 4 to 8 times more accurate than the classical MILP model,
+and more accurate than the ITNE model of \cite{lipshitz}, see Table \ref{table.classical}. Using our "3v" or "1v" models abstracting away some features,
+ even better bounds are reached (Tables 3, 4, 5).
+We also explained how to support $L_1$ perturbations efficiently on top of classical $L_\infty$ perturbations (Prop \ref{prop.l1}).
+To further lower the bounds by $\approx 8$ times, we resort to model order reduction, reducing the space of search closer to the space of the training dataset, without sacrificing DNN accuracy ($97\%$).
+This results into, to the best of our knowledge, the first time real-time robustness certification is reported for a DNN, with $86\%$ of robustness for a $L_1$-perturbation of $.5$ and $53\%$ of robustness for a $L_1$-perturbation of $1$.
+Still, global verification is only at its beginning, and combining different methods is necessary to scale to more complex DNNs.
 

### 2025-08-01 AAAI2026/experiments.tex
global pass

@@
 	MNIST is a classification benchmark, we thus report different bound $\beta^{\epsilon}_{i,j}$
-	for an $L_1$-deformation $\leq .5$. The pipe considers a conjunction of $L_1 \leq 3.9$ and $L_\infty \leq 0.2$ perturbations, corresponding to physically pertinent dimensions, and 
-	maximizes the sum of the difference in output of 10 selected points in the mesh between an input and its deformation.
+	for an $L_1$-deformation $\leq .5$. The pipe considers a conjunction of 
+	$L_1 \leq 3.9$ and $L_\infty \leq .02$ perturbations, corresponding to physically pertinent dimensions, and maximizes the sum of the difference in output of 10 selected points in the mesh between an input and its deformation.
 
@@
 
-We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement in Gurobi by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
-(3) of \cite{lipshitz} (and also to the relaxation of our "1v" model).
-We compare when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
-We use the pipe models which is easier to verify, and set the time-out at 1000s for all models.
-
-\begin{table}[h!]
+\begin{table}[b!]
+	\centering
 	\begin{tabular}{|l|c|c|c|}\hline\hline
@@
     \\\hline
-	ITNE, $100 \times 2$ &    $.045$ &  $.023$ & {\bf .023} 
+	ITNE, $100 \times 2$ &    $.045$ &  $.023$ & .023
     \\\hline
-	2v model, $100 \times 2$&     {\bf .042} &  $.023$ &   {\bf .023} 
+	2v model, $100 \times 2$&     {\bf .042} &  $.023$ &   .023 
     \\\hline \hline
@@
 \end{table}
+
+We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement in Gurobi by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
+(3) of \cite{lipshitz} (and also to the relaxation of our "1v" model).
+We compare when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
+We use the pipe models which is easier to verify, and set the time-out at 1000s for all models.
 
@@
 		3v, $500 \times 3$ & $16.09$ & $.755$ & {\bf .207} \\\hline 
-	    2v, $500 \times 2$ & {\bf 8.99} & nan & nan \\\hline\hline	 
+	    2v, $500 \times 2$ & {\bf 8.99} & n/a & n/a \\\hline\hline	 
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models 
-	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf full dimension} MNIST DNN, 
+	\caption{Bounds on $\beta^{.5}_{6,8}$ 
+	obtained by the "1v", "3v" and "2v" models 
+	on the {\bf full dimension} MNIST DNN, 
 	for timeouts of $14400$s, when all 500 ($\times 1$, $\times 2$, $\times 3$) variables are binary.}
@@
 
-\paragraph{Reduced space}
-
 \begin{table}[b!]
@@
 	\caption{Comparison of "1v", "3v" and "2v" models 
-	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of 14400s, where 
-	all the %400, 475,  or 
+	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension} reduced order MNIST DNN, for timeout of 14400s, where 
+	all %400, 475,  or 
 	500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
@@
 
-To remove improbable images and limit the space of search, 
-we consider a PCA model order reduction: We settled on reduction to 20 dimensions, because the MNIST $100 \times 5$ DNN considered, once run on images obtained from projecting to the reduced order and projected back to the full dimensional space displays the same accuracy of $97$\% as the DNN on the original images.
-This means that considering the reduced 20 dimensional space
-does not incur any loss in accuracy, which is the only thing which matters.
-On this reduced space, bounds obtained are much more precise, and one can concretly certify in real-time robustness of images.
+\paragraph{Reduced Space}
 
@@
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models 
-	in the percentage of images certified robust in real-time 
-	using the computed $(\beta^{.5}_{i,j})_{i < j \leq 10}$  for different values of $L_1$-perturbations.}
+	\caption{Percentage of images certified robust in real-time 
+	using the computed $(\beta^{.5}_{i,j})_{i < j \leq 10}$ 
+	by the "1v", "3v" and "2v" models, for different values of $L_1$-perturbations.}
     \label{table.cert}
 \end{table}
+
+To remove improbable images and limit the space of search, 
+we consider a PCA model order reduction: We reduced to 20 dimensions, because the MNIST $100 \times 5$ DNN considered, once run on images obtained from projecting to the 20 dimension space and projected back to the full dimension space displays the same accuracy of $97$\% as the DNN on the original images.
+This means that considering the reduced 20 dimensional space
+does not incur any loss in accuracy, which is the only thing which matters. On this reduced space, bounds obtained are much more precise, and one can certify in real-time robustness of images.
 
@@
 We did check that this worst-case found, displayed in Fig.
-\ref{fig5}, which is not too far from the actual worst case $<.0337$, is coherent wit the physical Finite Element system the DNN has been learnt from, hence this is not an hallucination due to the brittleness of the DNN learnt.
+\ref{fig5} and which is not too far from the actual worst case that is known to be $<.0329$, is coherent wit the physical Finite Element system the DNN has been learnt from, hence this is not an hallucination due to the brittleness of the DNN learnt.
 
@@
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with a fixed timeout of 1000s, 14440s and 72126s, where 90 ($\times 2$, $\times 3$) or all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
+	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with timeouts of 1000s, 14440s and 72000s, where all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
 	%L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}

### 2025-08-01 AAAI2026/global.tex
global pass

@@
 	\end{tikzpicture}
-\caption{The possible values of $\hat{y}_i=\ReLU(x_i)-\ReLU(x'_i)$ depending on $y_i = x_i-x'_i$ for the "1v" model.}
+\caption{The possible values of $\hat{y}_i=\ReLU(x_i)-\ReLU(x'_i)$ depending on $y_i = x_i-x'_i$ for the "1v" model. {\bf LIAO please depict LP relaxation in broken lines}.
+    }
 	\label{fig.1v}
@@
 
-    We can easily check that the LP relaxation of this MILP program is exactly 
-    $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$, 
-    {\bf LIAO please do on Fig2: as depicted in broken lines on Fig.~\ref{fig.1v}}.
+    We can easily check that the LP relaxation of this MILP program,
+	depicted in broken lines on Fig.~\ref{fig.1v}, is exactly: 
+    \begin{equation}
+		\label{eq.lpr}
+	  \frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}
+	\end{equation}
+
+	As the "1v" model is a projection of the "2v" and the "3v" models, 
+	the LP relaxations of the "2v" and the "3v" models contain (\ref{eq.lpr}).
+	Notice that (\ref{eq.lpr}) corresponds to Eq. (3) in \cite{lipshitz}, 
+	which is added explicitly to the classical model in their ITNE model.
 
@@
 
-	The "1v" model contains the same number of (binary) variables as the MILP model for local robustness, but it is not as accurate as the "3v" or "2v" models.
+	%The "1v" model contains the same number of (binary) variables as the MILP model for local robustness, but it is not as accurate as the "3v" or "2v" models.
 

### 2025-08-01 AAAI2026/introduction.tex
global pass

@@
 For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_\infty$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$ perturbation).
-While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop.~\ref{prop3} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
+While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop.~\ref{prop.l1} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
 

### 2025-08-01 AAAI2026/related.tex
global pass

@@
 
-The most related work is Vhagar \cite{vhagar}, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants). They do not however report actual 
-real-time certified robust percentage, as we do in Table \ref{table.cert}.
-Last, their hyper-adversarial attack to find better lower bounds seems extremely efficient, and we will consider it in the future.
+The most related work is Vhagar \cite{vhagar}, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants).
+They do not however report real-time certified robust percentage, as in Table \ref{table.cert}.
+Last, their hyper-adversarial attack to find better lower bounds seems very efficient, and we will consider it in the future.
 
-Technically, none of the MILP base work \cite{vhagar,ITNE,GROCET} 
-consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE,GROCET} 
+Technically, none of the MILP base work \cite{vhagar,ITNE} 
+consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE} 
 defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our models, Eq.
-(3) from \cite{ITNE} corresponding essentially to it.
+(3) in \cite{ITNE} corresponding essentially to it.
 \cite{vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem.

### 2025-08-02 AAAI2026/Lipitschz.tex
full paper

--- 2025-07-29 AAAI2026/Lipitschz.tex
@@
 
-	\newpage
+	%\vspace{-0.5cm}
+	\input{related}
 
-	\hfill
+\section{Conclusion}
+
+In this paper, we introduced a novel "2v" MILP model for global verification questions, which is 4 to 8 times more accurate than the classical MILP model,
+and more accurate than the ITNE model of \cite{lipshitz}, see 
+Table \ref{table.classical}. 
+Using our "3v" or "1v" models abstracting away some features of the "2v" model,
+ even better bounds are reached (Tables 3, 4, 5).
+We also explained how to support $L_1$-perturbations efficiently on top of classical $L_\infty$ perturbations (Prop \ref{prop.l1}).
+To further lower the bounds by $> 10$ times, we resort to model order reduction, reducing the space of search closer to the space of the training dataset, without sacrificing DNN accuracy ($97\%$).
+This results into, to the best of our knowledge, the first time real-time robustness certification is reported for a DNN, with $86\%$ of robustness for a $L_1$-perturbation of $.5$ and $53\%$ of robustness for a $L_1$-perturbation twice as large of $1$.
+Still, global verification is only at its beginning, and combining different methods is necessary to scale to more complex DNNs.
 

### 2025-08-02 AAAI2026/experiments.tex
full paper

@@
 	\centering
-	\begin{tabular}{|l|c|c|c|}\hline\hline
+	\begin{tabular}{||l|c|c|c||}\hline\hline
 		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
@@
 We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement in Gurobi by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
-(3) of \cite{lipshitz} (and also to the relaxation of our "1v" model).
+(3) of \cite{lipshitz} (and also to our (\ref{eq.lpr})).
 We compare when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
@@
 		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
-		1v, $500 \times 1$ & $15.67$ & $.620$ & $.012$ \\\hline 
-		3v, $500 \times 3$ & $16.09$ & $.755$ & {\bf .207} \\\hline 
-	    2v, $500 \times 2$ & {\bf 8.99} & n/a & n/a \\\hline\hline	 
+		1v, $500 \times 1$ & {\bf 14.97} & $.845$ & $.009$ \\\hline 
+		3v, $500 \times 3$ & $17.66$ & $.813$ & {\bf .518} \\\hline 
+	    2v, $500 \times 2$ & $16.49$ & n/a & n/a \\\hline\hline	 
 	\end{tabular}
@@
 	\centering
-\includegraphics[scale=0.5]{image.png} \hspace{0.8cm}
-\includegraphics[scale=0.5]{perturb.png}
-\caption{An improbable image and its perturbation (difference at x=13, y=18) 
-with maximal $\beta^{.5}_{6,8}=0.207$ for MNIST as obtained by the "3v" $500 \times 2$ model in {\bf full 784 dimension} image space.}
+\includegraphics[scale=0.6]{image.png} \hspace{1.5cm}
+\includegraphics[scale=0.6]{perturb.png}
+\caption{An improbable image and its perturbation ($L1$-difference of $.5$ in a unique pixel at x=14, y=8 from top) with maximal $\beta^{.5}_{6,8}=0.518$ for MNIST as obtained by the "3v" $500 \times 2$ model in {\bf full 784 dimension} image space.}
 \label{fig3}
@@
 	\centering
-\includegraphics[scale=0.5]{redimage.png} \hspace{0.8cm}
+\includegraphics[scale=0.5]{redimage.png} \hspace{1.5cm}
 \includegraphics[scale=0.5]{redperturb.png}
@@
 as in Table \ref{table.mnist}, obtained with the same time-out.
-The bounds are directly comparable: the best $\beta^{.5}_{6,8}$ obtained using the reduced dimension is $\approx 8$ times smaller than when using the full dimension ($1.137$ vs $8.99$).
+The bounds are directly comparable: the best $\beta^{.5}_{6,8}$ obtained using the reduced dimension is $>10$ times smaller than when using the full dimension ($1.137$ vs $14.97$).
 With these bounds, most images ($86\%$) can be certified in real-time robust for a perturbation $L_1 \leq .5$, and even $53\%$ with a perturbation $L_1 \leq 1$ twice as large, see Table \ref{table.cert}.
@@
 \end{table}
+
+\newpage
+
+\noindent {\bf Supplementary material content:} We provide in supplementary materials additional content, in particular results with reduced number of binary variables.
+We also provide the proof of Prop.~\ref{Prop2}, and explanations on the reduced-order dimension pipeline.

### 2025-08-02 AAAI2026/related.tex
full paper

@@
 
-Some works CITE
-Leino et al. [2021]; Zhang et al. [2022a] Sun et al. [2022]  Chen et al. [2021], REGLO focus on training a network to be - rather than proving that the DNN is as we do - gobally robust .
-Other work estimate global robustness bounds, but without hard verification certificates CITE Bastani et al.
-[2016]; Ruan et al.
-[2019], Gopinath et al.
-[2018], e.g.
-using probabilistic guarantees  Levy et al.
-[2023]; Mangal et al.
-[2019].
+Some works \cite{Leino,Zhang22a,Sun22,Chen21,REGLO} focus on training a network to be - rather than proving the DNN is - globally robust.
+Other works \cite{Bastani16,Ruan19,Gopinath18} estimate global robustness bounds, but without hard verification certificates, e.g. using probabilistic guarantees 
+\cite{Levy23,Mangal19}.
 
-Closer to our paper, several works consider a kind of global Lipschitz bound, to understand how the output change with input perturbations, as \cite{Marabou} and \cite{ITNE,GROCET}.
+Closer to our paper, several works  \cite{Marabou,lipshitz,GROCET} consider a global certified restricted Lipschitz bound, to understand how the output change with input perturbations.
 However, they do not consider whether the classification changes.
@@
 (3) in \cite{ITNE} corresponding essentially to it.
-\cite{vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem.
+\cite{vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem, which is well-adapted to occlusion and patches but less to $L_1$ perturbations.

### 2025-08-02 AAAI2026/abstract.tex
title!!

--- 2025-07-28 AAAI2026/abstract.tex
@@
 Further, the values each neuron can take are no longer limited to a small neighborhood.
-To obtain usable bounds, we develop several novel partial MILP models for global robustness, with different trade-offs.
+To obtain usable bounds, we develop several novel  MILP models for global robustness, with different trade-offs.
 Last, we use order reduction techniques to reduce the space of inputs considered, avoiding unrealistic images, by using principal component analysis (PCA).
-This results into the real-time  certification of the robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of 0.5, as well as for a surrogate computing the
+This results into the {\em real-time} certification of the robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of $.5$, as well as for a surrogate computing the
 %latent

### 2025-08-02 AAAI2026/experiments.tex
title!!

@@
 \includegraphics[scale=0.6]{perturb.png}
-\caption{An improbable image and its perturbation ($L1$-difference of $.5$ in a unique pixel at x=14, y=8 from top) with maximal $\beta^{.5}_{6,8}=0.518$ for MNIST as obtained by the "3v" $500 \times 2$ model in {\bf full 784 dimension} image space.}
+\caption{An improbable image for MNIST and its perturbation ($L1$-difference of $.5$ in a unique pixel at x=14, y=8 from top) with maximal $\beta^{.5}_{6,8}=0.518$, as obtained by the "3v" $500 \times 2$ model in {\bf full 784 dimension} image space.}
 \label{fig3}
@@
 \includegraphics[scale=0.5]{redperturb.png}
-\caption{An image and its perturbation from the {\bf 20-dimension reduced space} with maximal $\beta^{.5}_{6,8}=.084$ for MNIST as obtained by the "2v" $500 \times 2$ model.}
+\caption{An image for MNIST and its perturbation from the {\bf 20-dimension reduced space} with maximal $\beta^{.5}_{6,8}=.084$, as obtained by the "2v" $500 \times 2$ model.}
 \label{fig4}

### 2025-08-02 AAAI2026/introduction.tex
title!!

@@
 given a DNN, an image and a small neighborhood around this image, is it the case that all the images in the neighborhood are classified in the same way by the DNN?
-The neighborhood is provided by a maximal perturbation of the input image, often an $L_\infty$ perturbation, i.e.
+The neighborhood is provided by a maximal perturbation of the input image, often an
+$L_\infty$-perturbation, i.e.
 every subpixel of the input image can vary in a very small range, typically $\frac{2}{255}$ (that is 2 levels of grey/blue/right/green), as $L_\infty$ is perfectly linear and perturbations of subpixels are independent.
-While the $L_\infty$ norm is the easiest to handle, it is not necessarily the most meaningful perturbation.
-More importantly, verification tools for local robustness are hard to be used in a real-time decision making pipeline: considering an autonomous car with a video feed from the dashboard, it is computationally too intensive to certify in few ms images of the feed to e.g.
-skip non-robust images and only consider certified robust images for the decision-making process.
+While the $L_\infty$-norm is the easiest to handle, it is not necessarily the most meaningful perturbation.
+More importantly, verification tools for local robustness are too computationally-intensive to be used in a real-time decision making pipeline: considering an autonomous car with a video feed from the dashboard,
+images of the feed cannot be certified robust in few ms to e.g. skip non-robust images and only consider certified robust images for the decision-making process.
 
@@
 	%pairs (image, perturbation), improbable images are generated, hence these  are not meaningful. 
-	To solve this problem, we restrict the input space to ignore improbable inputs, using model order reduction techniques from engineering science \cite{aiware}.
+	To solve this problem, we restrict the input space to ignore improbable inputs, using model order reduction techniques from engineering science \cite{Paco}.
 Specifically, we use Principal Component Analysis (PCA) to reduce the space to a linear input space.
@@
 
-\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in real time that $86\%$ of the images are robust for an $L_1$ perturbation of $.5$, resp.
+\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in {\em real-time} that $86\%$ of the images are robust for an $L_1$ perturbation of $.5$, resp.
 $53\%$ for an $L_1$ perturbation of $1$.
@@
 The DNN has been learnt on a reduced order basis already of dimension 10, from thousands of input dimensions.
-For regression, the aim is to understand if the DNN surrogate that has been learnt is brittle to small perturbations, which could make it unfaithful to the physical model.
+The aim is to understand if the DNN surrogate that has been learnt is brittle to small perturbations, which could make it unfaithful to the physical model.
 Here we want to obtain bounds (which is what our models provide), as well as generating worst-case (image,perturbation) pair, where the strain is particularly different, close to the bound, and that can be run in the physical model to understand whether the DNN surrogate is faithful.

### 2025-08-02 AAAI2026/Lipitschz.tex
title!!
final?

@@
 
-\title{Order reduction and MILP models for certifying Robustness of DNNs globally.}
+\title{Order reduction and MILP models for real-time DNN robustness certification.}
 \date{}
@@
 
+	\newpage
+
 	\input{experiments}
@@
 and more accurate than the ITNE model of \cite{lipshitz}, see 
-Table \ref{table.classical}. 
-Using our "3v" or "1v" models abstracting away some features of the "2v" model,
+Table \ref{table.classical}. Using our "3v" or "1v" models abstracting away some features of the "2v" model,
  even better bounds are reached (Tables 3, 4, 5).
-We also explained how to support $L_1$-perturbations efficiently on top of classical $L_\infty$ perturbations (Prop \ref{prop.l1}).
+We also explained how to support $L_1$-perturbations efficiently on top of classical $L_\infty$-perturbations (Prop \ref{prop.l1}).
 To further lower the bounds by $> 10$ times, we resort to model order reduction, reducing the space of search closer to the space of the training dataset, without sacrificing DNN accuracy ($97\%$).
-This results into, to the best of our knowledge, the first time real-time robustness certification is reported for a DNN, with $86\%$ of robustness for a $L_1$-perturbation of $.5$ and $53\%$ of robustness for a $L_1$-perturbation twice as large of $1$.
+This results into, to the best of our knowledge, the first {\em real-time} robustness certification reported for a DNN, with $86\%$ of robustness for an $L_1$-perturbation of $.5$ and $53\%$ of robustness for an $L_1$-perturbation twice as large of $1$.
 Still, global verification is only at its beginning, and combining different methods is necessary to scale to more complex DNNs.

### 2025-08-02 AAAI2026/experiments.tex
final?

@@
 	Although it is relatively small, it is also of good quality with $97\%$ accuracy on classification, but it is not easy to certify for global robustness (the size of a network can be deceptive to know whether they are easy or hard to verify \cite{ATVA25}).
-	The second one is a 2 fully connected layers, 50 neurons each, learnt as a surrogate model, with 10 reduced input and 10 reduced output, that predict the plastic strain in 3000 points of a mesh over a pipe given the deformation of each of this 3000 points (through a PCA order reduction encoding all 3000 points with 10 dimensions in input and 26 dimensions in output), from \cite{aiware}.
+	The second one is a 2 fully connected layers, 50 neurons each, learnt as a surrogate model, with 10 reduced input and 26 reduced output, that predictS the plastic strain in 3000 points of a mesh over a pipe given the deformation of each of this 3000 points (through a PCA order reduction \cite{Paco} encoding all 3000 points with 10 dimensions in input and 26 dimensions in output), from \cite{aiware}.
 
-	MNIST is a classification benchmark, we thus report different bound $\beta^{\epsilon}_{i,j}$
-	for an $L_1$-deformation $\leq .5$. The pipe considers a conjunction of 
-	$L_1 \leq 3.9$ and $L_\infty \leq .02$ perturbations, corresponding to physically pertinent dimensions, and maximizes the sum of the difference in output of 10 selected points in the mesh between an input and its deformation.
+	MNIST is a classification benchmark, we thus compute the different $\beta^{\varepsilon}_{i,j}$ bounds, for an $L_1$-deformation $\varepsilon = \leq .5$. 
+	The pipe considers a conjunction of 
+	$L_1 \leq 3.9$ and $L_\infty \leq .02$ perturbations, physically pertinent dimensions, and maximizes the sum of the difference in output of 10 selected points in the mesh between input and its deformation.
 
-For each benchmark, we report three values: the bound obtained (lower value is better),
-the solution obtained (distance to the bound depicts how close the model has converged),
-and worst-case (higher is better) which is taking the solution as input to the DNN. For a fully accurate model ("2v" or classical and all variables binary),
-the worst-case will equal the solution, otherwise, it will be smaller due to abstraction.
+For each benchmark, we report three values: the bound obtained (lower value is better), the solution obtained (distance to the bound depicts how close the model has converged), and worst-case (higher is better), that is the value reached when considering the solution as input to the DNN.
+For a fully accurate model ("2v" or classical and all variables binary), the worst-case will equal the solution, otherwise, it will be smaller due to abstraction.
 
@@
 We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement in Gurobi by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
-(3) of \cite{lipshitz} (and also to our (\ref{eq.lpr})).
+(3) of \cite{ITNE} (and also to our (\ref{eq.lpr})).
 We compare when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
@@
 
-Table \ref{table.classical}, $50 \times 2$, confirms that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model, when 50 variables use LP relaxation only.
+Table \ref{table.classical}, $50 \times 2$, confirms that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model, when 50 variables use LP relaxation.
 Adding explicitly LP relaxation constraints of Eq.
-(3) from \cite{lipshitz} recovers most but not all the bound of the "2v" model.
+(3) from \cite{ITNE} recovers most but not all the bound of the "2v" model.
 
@@
 Again,
-Eq. (3) from \cite{lipshitz} recovers most but not all the accuracy of the "2v" model.
+Eq. (3) from \cite{ITNE} recovers most but not all the accuracy of the "2v" model.
 Overall, the "2v" model produces better bounds, even with short time-outs, despite its higher complexity.
@@
 
-On the full space, the best bounds $(\beta^{.5}_{i,j})_{i < j \leq 10}$ reached are too pessimistic: they allow to certify no image robust in real-time.
-One of the reason, besides that the verification question is very complicated with 1000 binary variables for the accurate model, is that working in the full $784$ dimensional space allow for very unlikely inputs, far away from what the DNN has learnt from, making the search very long and the bound very pessimistic.
+On the full space, the best bounds $(\beta^{.5}_{i,j})_{i < j \leq 10}$ reached are too pessimistic: no image can be certified robust in real-time.
+One of the reason, besides that the verification question is very complicated with 1000 binary variables for the accurate model, is that working in the full $784$ dimensional space allows for very unlikely inputs, far away from what the DNN has learnt from, making the search very long and the bound very pessimistic.
 As an illustration of that, we display on Fig.~\ref{fig3} the worst-case as found by our models, which is very improbable to be ever encountered in the MNIST benchmark.
@@
 To remove improbable images and limit the space of search, 
-we consider a PCA model order reduction: We reduced to 20 dimensions, because the MNIST $100 \times 5$ DNN considered, once run on images obtained from projecting to the 20 dimension space and projected back to the full dimension space displays the same accuracy of $97$\% as the DNN on the original images.
+we consider a PCA model order reduction \cite{Paco}: We reduced to 20 dimensions, because the MNIST $100 \times 5$ DNN considered, once run on images obtained from projecting to the 20 dimension space and projected back to the full dimension space displays the same accuracy of $97$\% as the DNN on the original images.
 This means that considering the reduced 20 dimensional space
@@
 
-\subsection{Experiment results for regression (Pipe strain)}
+\subsection{Experimental results for regression (Pipe strain)}
 
@@
 	For the pipe system, we compared in Table \ref{table.pipe} the different models "1v","2v","3v" to produce bounds on the sum of the difference of strain over 10 specific points of the mesh, for a physically relevant perturbation of the deformation.
-The bounds we found are quite accurate, with a best bound of ".0329" obtained by the "3v" model, slightly better than the bound $.0337$ found within the same time by the "2v" model, and better than the bound found $0.356$ by the "1v" model, although this bound has been found 70 times faster due to the simpler model.
-The certified lower bound is not so far, at $.245$, found by the fully accurate "2v" model when all the variables are binary.
+The bounds we found are quite accurate, with a best bound of $.0329$ obtained by the "3v" model, slightly better than the bound $.0337$ found within the same time by the "2v" model, and better than the bound found $0.356$ by the "1v" model, although this bound has been found 70 times faster due to the simpler model.
+The certified lower bound is not too far, at $.245$, found by the fully accurate "2v" model when all the variables are binary.
 We did check that this worst-case found, displayed in Fig.
-\ref{fig5} and which is not too far from the actual worst case that is known to be $<.0329$, is coherent wit the physical Finite Element system the DNN has been learnt from, hence this is not an hallucination due to the brittleness of the DNN learnt.
+\ref{fig5} and which is not too far from the actual worst case that is known to be $<.0329$, is coherent with the physical dinite element model the DNN surrogate has been learnt from, hence this is not an hallucination due to the brittleness of the learnt DNN.
 

### 2025-08-02 AAAI2026/global.tex
Add files via upload
full paper
final?

@@
 
-    To encode global robustness, \cite{lipshitz,vhagar} consider 
+    To encode global robustness, \cite{vhagar} considers
 	variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ 
 	and of its perturbation $I'$, 
-    using the classical encoding (\ref{eq11}) \cite{MILP} for each variable.
+	using the classical encoding (\ref{eq11}) \cite{MILP} 
+	to compute $\hat{x}_i, \hat{x}'_i$ from $x_i, x'_i$
+	for each $i$.
     Further:
@@
 	%As the worst-case complexity of solving an MILP model is exponential in the number of binary variables, it will be computationally intractable to compute $\beta^\varepsilon_{i,j}$ in this way, but for very small DNNs.
-	As explained in the previous section, the standard way to make the model more efficient is to rely on relaxing at least some of the binary variables into linear variables.
+	As explained in the previous section, the standard way to make the model more efficient is to rely on Linearly relaxing some of the binary variables into linear variables.
 
@@
 On top of being an issue with partial MILP models, LP relaxation is also used during the Branch and Bound process internal to MILP solvers to provide bounds for each branch.
-So even when all variables are opened and the MILP model is fully accurate, the classical encoding will likely not be efficient as well.
-Notice that this was already witnessed in \cite{lipshitz}, and some additional constraints were added to make the classical model more accurate.
-We will compare the different methods in table \ref{table.classical}.
+So even when all variables are binary, the classical MILP encoding
+	of \cite{MILP}, while fully accurate, will likely not result into accurate bounds as well.
+Notice that this was already witnessed in \cite{ITNE}, and some additional constraints were added to make the classical model more accurate:
+	the diff variables were defined, although to pass the ReLU the classical  
+	MILP encoding was used, but with added specific constraints (Eq. (3) in 
+	\cite{ITNE}). We will compare the different methods in Table \ref{table.classical}.
 
@@
 	We now present our novel faithful "2v" model.
-    First, we consider variables $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with     $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$, as already proposed in \cite{lipshitz}.
+    First, we consider variables $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with     $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$, as already proposed in \cite{ITNE}.
 	Intuitively, the diff variables will be small as they will be carrying the difference between both the image $I$ and its perturbation $I'$.
@@
 
-    However, unlike \cite{lipshitz}, we do not apply the classical MILP encoding (\ref{eq11}) \cite{MILP} on the diff variable $\hat{y}_j$. Instead we study the function of 
+    However, unlike the Interleaving Twin-Network Encoding (ITNE) \cite{ITNE} which relies on the classical MILP encoding (\ref{eq11}) \cite{MILP} to compute $\hat{y}_j$ from the difference between 
+	$\ReLU(x'_j + y_j) = \ReLU(x_j) = \hat{x_j}$
+	and $\hat{x}'_j$, we compute $\hat{y}_j$ directly, without resorting to the classical encoding. To do so, we study the function of 
     $\hat{y}_j$ given $y_j$ and $x'_j$, and encode it into a novel MILP model.
-    A first important observation is that $I,I'$ being perfectly symetrical,
-    for $\gamma_i$ being a upper bound of $y_i$, then $-\gamma_i$ is a lower bound 
-    for $y_i$.
+    A first important observation is that $I,I'$ being perfectly symmetrical,
+    assuming that $\gamma_i$ is an upper bound of $y_i$, then $-\gamma_i$ is a lower bound for $y_i$.
 
@@
 
-	We first display on Figure \ref{fig.2v} the function $f(x'_i,y_i)=\hat{y}_i$, when we know that $y_i \in [- \gamma_i, \gamma_i]$.
-When $x'_i < -\gamma_i$, then $x_i <0$ and we have $\hat{y}_i = \ReLU(x_i) - \ReLU(x'_i) = 0-0=0$.
-    For $x'_i > \gamma_i$, we have $x_i >0$ and $\hat{y}_i=
+	We first display on Figure \ref{fig.2v} the function $f(x'_i,y_i)=\hat{y}_i$, granted that $y_i \in [- \gamma_i, \gamma_i]$. 
+	When $x'_i \leq 0$ and $x_i = x'_i+y_i \leq 0$, then we have $\hat{y}_i = \ReLU(x_i) - \ReLU(x'_i) = 0-0=0$. For $x'_i \geq 0$ and $x_i = x'_i+y_i \geq 0$, we have $\hat{y}_i=
     \ReLU(x_i)-\ReLU(x'_i)=x_i - x'_i = y_i$. 
@@
 
+\newpage
+
 \begin{proposition}
@@
 
-So to encode both $\hat{y}_i$ and $\hat{x}_i$, we need 2 binary variables altogether, similar to the classical encoding.
+So to encode both $\hat{y}_i$ and $\hat{x}_i$, we need 2 binary variables altogether, similar to the classical encoding. The proof of Prop. \ref{Prop2} can be found in the supplementary materials.
 
@@
     $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$
-    (see subsection "1v" model), which is not the case of the classical model.
+    (see subsection The eficient "1v" model for a formal sketch), which is not the case of the classical model.
 
@@
 			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
-			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};
+			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.24, -2.2) {};
 
 			\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
-			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
+			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.65) {};
+		\addplot[dashed, thick, blue] coordinates {(-2,-2) (2,0)};
+			\addplot[dashed, thick, blue] coordinates {(-2,0) (2,2)};
+			\node[label={above:\scriptsize $LP\ relaxation$}] at (axis cs: -0.7, 0.8) {};
+			\node[label={above:\scriptsize $LP\ relaxation$}] at (axis cs: 0.5, -1.4) {};
 		\end{axis}
 	\end{tikzpicture}
-\caption{The possible values of $\hat{y}_i=\ReLU(x_i)-\ReLU(x'_i)$ depending on $y_i = x_i-x'_i$ for the "1v" model. {\bf LIAO please depict LP relaxation in broken lines}.
-    }
+\caption{The possible values of $\hat{y}_i=\ReLU(x_i)-\ReLU(x'_i)$ depending on $y_i = x_i-x'_i$ for the "1v" model.}
 	\label{fig.1v}
@@
 This is a projection of Fig.~\ref{fig.2v} onto $y_i,\hat{y}_i$.
+
+\newpage
 
@@
 
-	As the "1v" model is a projection of the "2v" and the "3v" models, 
+	As the "1v" model is a projection of the "2v" and also of the "3v" models, 
 	the LP relaxations of the "2v" and the "3v" models contain (\ref{eq.lpr}).
-	Notice that (\ref{eq.lpr}) corresponds to Eq. (3) in \cite{lipshitz}, 
+	Notice that (\ref{eq.lpr}) corresponds to Eq. (3) in \cite{ITNE}, 
 	which is added explicitly to the classical model in their ITNE model.

### 2025-08-02 AAAI2026/introduction.tex
final?

@@
 	To solve this problem, we restrict the input space to ignore improbable inputs, using model order reduction techniques from engineering science \cite{Paco}.
-Specifically, we use Principal Component Analysis (PCA) to reduce the space to a linear input space.
-We choose the number of dimensions of the space to equal the accuracy of the DNN on the reduced space.
+Specifically, we use Principal Component Analysis (PCA) to reduce the space
+	to a linear input space. We choose the number of dimensions of the space to equal the accuracy of the DNN on the reduced space. 
 	%(using a projection to the reduced space then the inverse projection to obtain a very similar image understandable by the DNN). 
@@
 
-\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in {\em real-time} that $86\%$ of the images are robust for an $L_1$ perturbation of $.5$, resp.
-$53\%$ for an $L_1$ perturbation of $1$.
+\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in {\em real-time} that $86\%$ of the images are robust for an $L_1$-perturbation of $.5$, resp.
+$53\%$ for an
+$L_1$-perturbation of $1$.
 We finally experimented our MILP models for a {\em regression} task as well, considering a DNN surrogate built from a slow physical finite element model, providing the deformation and the plastic strain of a pipe \cite{aiware}.

### 2025-08-02 AAAI2026/notation.tex
final?

@@
 	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
-	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output.
-Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
+	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output. Finally, pre- and post-activation neurons are called \emph{nodes}.
+	% and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$.
 Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.
 
-    In this paper, we consider the global verification problem, where we optimize over all image $I$ and all perturbation $I'$ of $I$ with $|I-I'| \leq \varepsilon$.
+    In this paper, we consider the {\em global} verification problem, where we optimize over all image $I$ and all perturbation $I'$ of $I$ with $|I-I'| \leq \varepsilon$.
 	We will consider three kinds of variables:
@@
     $\hat{y}_j = \hat{x}_j - \hat{x}'_j$ (and {\em not} 
-    $\hat{y}_i = \ReLU(x_j-x'_j)$), similarly than in the ITNE model \cite{lipshitz}. 
+    $\hat{y}_i = \ReLU(x_j-x'_j)$), similarly than in the 
+	Interleaving Twin-Network Encoding (ITNE) model \cite{lipshitz}. 
     \end{itemize}
@@
 
-	\subsection{MILP encoding for local ReLU and LP relaxation}
+	\subsection{MILP encoding for local ReLU}
 
@@
 
-    Let $\mathcal{M}$ denote the whole MILP model, where each unstable ReLU are encoded in the above way with one integer variable. 
-	The encoding from $(\hat{x}_j)_{j \text{ in layer } i}$ to 
+    In the whole MILP model, each unstable ReLU is encoded in the above way with one integer variable. The encoding from $(\hat{x}_j)_{j \text{ in layer } i}$ to 
 	$(x_{j'})_{j' \text{ in layer } i+1}$ variables is simply the linear combination 
 	$\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i$.
-	This exact MILP encoding is often too computationally intensive, as the worst-case complexity of MILP is exponential in the number of integer variables \cite{DivideAndSlide}.
+	%This exact MILP encoding is often too computationally intensive, as the worst-case complexity of MILP is exponential in the number of integer variables \cite{DivideAndSlide}.
+
+    \subsection{LP relaxation}
 
@@
 However, this efficiency comes at the cost of precision, often resulting in less stringent bounds.
-This approach is termed the {\em LP abstraction}.
+This approach is termed the {\em LP relaxation}.
     % We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.
@@
 	\end{itemize}
-	We will denote the above model by MILP$_X$. We say that a node is {\em opened} if it is in $X$.
+
+	%We will denote the above model by MILP$_X$. We say that a node is {\em opened} if it is in $X$.
 

### 2025-08-02 AAAI2026/related.tex
final?

@@
 
-The most related work is Vhagar \cite{vhagar}, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$ perturbations (and variants).
-They do not however report real-time certified robust percentage, as in Table \ref{table.cert}.
+The most related work is Vhagar \cite{vhagar}, which also computes $\beta^\varepsilon_{i,j}$ bounds, but limited to $L_\infty$-perturbations (and variants).
+They do not however report {\em real-time} certified robust percentage, as in Table \ref{table.cert}.
 Last, their hyper-adversarial attack to find better lower bounds seems very efficient, and we will consider it in the future.
@@
 Technically, none of the MILP base work \cite{vhagar,ITNE} 
-consider $L_1$ bounds. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE} 
-defines the {\em diff variables} $y,\hat{y}$, adding explicitely the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our models, Eq.
+consider $L_1$-perturbations. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE} 
+defines the {\em diff variables} $y,\hat{y}$, adding explicitly the linear relaxation $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by our models, Eq.
 (3) in \cite{ITNE} corresponding essentially to it.
-\cite{vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem, which is well-adapted to occlusion and patches but less to $L_1$ perturbations.
+\cite{vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem, which is well-adapted to occlusion and patches but less to $L_1$-perturbations.

### 2025-08-02 AAAI2026/abstract.tex
typos

@@
 Most existing methods focus on local robustness, i.e., the model's behavior in the neighborhood of a specific input.
-While local robustness enables to evaluate how often non robust images appear in a large dataset (e.g., by repeating the verification on 1000 pre-obtained images), it fails to provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream.
+While local robustness enables to evaluate how often non-robust images appear in a large dataset (e.g., by repeating the verification on 1000 pre-obtained images), it fails to provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream.
 Moreover, most verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.

### 2025-08-02 AAAI2026/introduction.tex
typos

@@
 
-Our main contributions address the challenges to compute the {\em global bounds} $\beta^\varepsilon(C,D)$, for $C,D$ output neurons:
+Our main contributions address the challenges to compute the {\em global bounds} $\beta^\varepsilon_{C,D}$, for $C,D$ output neurons:
 \begin{enumerate}
@@
 Compared with the
-	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz},
+	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz, ITNE},
 	the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other.
-This was observed in \cite{lipshitz}, and constraints encoding
+This was observed in \cite{lipshitz, ITNE}, and constraints encoding
 	a part of the linear relaxation of our "2v" model were added explicitly. Experimentally, 
@@
 
-   \item  In terms of perturbations, we consider conjunctions of $L_\infty$ and $L_1$ norms, which allows to accurately describe perturbations.
-For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_\infty$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$ perturbation).
-While $L_1$ perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop.~\ref{prop.l1} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
+   \item  In terms of perturbations, we consider conjunctions of $L_\infty$- and $L_1$-norms, which allow to accurately describe perturbations.
+For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_\infty$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$-perturbation).
+While $L_1$-perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop.~\ref{prop.l1} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
 
@@
 We finally experimented our MILP models for a {\em regression} task as well, considering a DNN surrogate built from a slow physical finite element model, providing the deformation and the plastic strain of a pipe \cite{aiware}.
-The DNN has been learnt on a reduced order basis already of dimension 10, from thousands of input dimensions.
+The DNN has been learnt on a already reduced basis of dimension 10, from thousands of input dimensions.
 The aim is to understand if the DNN surrogate that has been learnt is brittle to small perturbations, which could make it unfaithful to the physical model.
@@
 Our tool was helpful to provide limited bounds, as well as an almost matching worst-case (image,perturbation) pair that was confirmed in the physical model.
-Overall, the "2v" model generates accurate bounds. The decoupling of variables generating the "3v" model offers good trade-offs, reaching slightly lower bounds in the same runtime. 
-The "1v" model is faster to converge, but also generates larger bounds, unless runtime is very restricted (Table \ref{table.pipe}).
+Overall, the "2v" model generates accurate bounds.
+The decoupling of variables generating the "3v" model offers good trade-offs, reaching slightly better bounds in the same runtime.
+The "1v" model converges faster  but bounds are looser, a good trade-off when runtime is limited and problem is complex (Tables \ref{table.mnist},\ref{table.pipe}).
 \end{enumerate}

### 2025-08-02 AAAI2026/notation.tex
typos

@@
 
-    In this paper, we consider the {\em global} verification problem, where we optimize over all image $I$ and all perturbation $I'$ of $I$ with $|I-I'| \leq \varepsilon$.
+    In this paper, we consider the {\em global} verification problem, where we optimize over all images $I$ and perturbations $I'$ of $I$ with $|I-I'| \leq \varepsilon$.
 We will consider three kinds of variables:
@@
     $\hat{y}_i = \ReLU(x_j-x'_j)$), similarly than in the 
-	Interleaving Twin-Network Encoding (ITNE) model \cite{lipshitz}. 
+	Interleaving Twin-Network Encoding (ITNE) model of \cite{lipshitz, ITNE}. 
     \end{itemize}

### 2025-08-02 AAAI2026/Lipitschz.tex
final?

@@
 In this paper, we introduced a novel "2v" MILP model for global verification questions, which is 4 to 8 times more accurate than the classical MILP model,
-and more accurate than the ITNE model of \cite{lipshitz}, see 
+and more accurate than the ITNE model of \cite{lipshitz,ITNE}, see 
 Table \ref{table.classical}. Using our "3v" or "1v" models abstracting away some features of the "2v" model,

### 2025-08-02 AAAI2026/experiments.tex
final?

@@
 
-	We consider two DNNs: one for MNIST, namely a pre-trained $5\times 100$ (available at \url{https://github.com/eth-sri/eran}), a 5 fully connected layers DNN, with 100 neurons each,	trained with diff AI \cite{deeppoly}.
+	We consider two DNNs: one for MNIST, namely a pre-trained $5\times 100$ (available at \url{https://github.com/eth-sri/eran}), a 5 fully connected layers DNN, with 100 neurons each,	trained with diffAI \cite{deeppoly}.
 	Although it is relatively small, it is also of good quality with $97\%$ accuracy on classification, but it is not easy to certify for global robustness (the size of a network can be deceptive to know whether they are easy or hard to verify \cite{ATVA25}).
-	The second one is a 2 fully connected layers, 50 neurons each, learnt as a surrogate model, with 10 reduced input and 26 reduced output, that predictS the plastic strain in 3000 points of a mesh over a pipe given the deformation of each of this 3000 points (through a PCA order reduction \cite{Paco} encoding all 3000 points with 10 dimensions in input and 26 dimensions in output), from \cite{aiware}.
+	The second one is a 2 fully connected layers, 50 neurons each, learnt as a surrogate model, with 10 reduced input and 26 reduced output, that predicts the plastic strain in 3000 points of a mesh over a pipe given the deformation of each of this 3000 points (through a PCA order reduction \cite{Paco} encoding all 3000 points with 10 dimensions in input and 26 dimensions in output), from \cite{aiware}.
 
@@
 
-We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement in Gurobi by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
+We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
 (3) of \cite{ITNE} (and also to our (\ref{eq.lpr})).
 We compare when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly.
-We use the pipe models which is easier to verify, and set the time-out at 1000s for all models.
+We consider the pipe surrogate as it is easier to verify, and set the time-out at 1000s for all models.
 
@@
 On the full space, the best bounds $(\beta^{.5}_{i,j})_{i < j \leq 10}$ reached are too pessimistic: no image can be certified robust in real-time.
-One of the reason, besides that the verification question is very complicated with 1000 binary variables for the accurate model, is that working in the full $784$ dimensional space allows for very unlikely inputs, far away from what the DNN has learnt from, making the search very long and the bound very pessimistic.
+One of the reason, besides that the verification question is very complicated with 1000 binary variables for the accurate model, is that working in the full $784$ dimensional space allows for very unlikely inputs, far away from the training dataset, making the search space overly large.
 As an illustration of that, we display on Fig.~\ref{fig3} the worst-case as found by our models, which is very improbable to be ever encountered in the MNIST benchmark.

### 2025-08-02 AAAI2026/global.tex
final?

@@
 	%As the worst-case complexity of solving an MILP model is exponential in the number of binary variables, it will be computationally intractable to compute $\beta^\varepsilon_{i,j}$ in this way, but for very small DNNs.
-	As explained in the previous section, the standard way to make the model more efficient is to rely on Linearly relaxing some of the binary variables into linear variables.
+	As explained in the previous section, the standard way to make the model more efficient is to rely on 
+	linearly relaxing some of the binary variables into linear variables.
 
@@
 	We now present our novel faithful "2v" model.
-    First, we consider variables $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with     $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$, as already proposed in \cite{ITNE}.
+    First, we consider variables $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with     $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$, as already proposed in \cite{lipshitz,ITNE}.
 	Intuitively, the diff variables will be small as they will be carrying the difference between both the image $I$ and its perturbation $I'$.
@@
 
-    However, unlike the Interleaving Twin-Network Encoding (ITNE) \cite{ITNE} which relies on the classical MILP encoding (\ref{eq11}) \cite{MILP} to compute $\hat{y}_j$ from the difference between 
+    However, unlike the Interleaving Twin-Network Encoding (ITNE) of \cite{lipshitz,ITNE} which relies on the classical MILP encoding (\ref{eq11}) \cite{MILP} to compute $\hat{y}_j$ from the difference between
 	$\ReLU(x'_j + y_j) = \ReLU(x_j) = \hat{x_j}$
@@
 \ref{Prop2} can be decoupled from the binary variable appearing in the classical encoding of $x'_i = \ReLU(x'_i)$.
-While this means having 3 binary variables per unstable ReLU (which warrants the name "3v" model), the fact that these variables are decouples remove a lot of constraints in the MILP encoding, and actually helps the solver.
+While this means having 3 binary variables per unstable ReLU (which warrants the name "3v" model), the fact that these variables are decoupled removes a lot of constraints in the MILP encoding, and actually helps the solver.
 The decoupling also means that the "3v" model is not as accurate as the "2v" model.

### 2025-08-02 AAAI2026/related.tex
final?

@@
 
-Closer to our paper, several works  \cite{Marabou,lipshitz,GROCET} consider a global certified restricted Lipschitz bound, to understand how the output change with input perturbations.
+Closer to our paper, several works  \cite{Marabou,lipshitz,ITNE,GROCET} consider a global certified restricted Lipschitz bound, to understand how the output change with input perturbations.
 However, they do not consider whether the classification changes.
@@
 
-Technically, none of the MILP base work \cite{vhagar,ITNE} 
+Technically, none of the MILP base work \cite{vhagar,lipshitz,ITNE} 
 consider $L_1$-perturbations. Further, they use the classical MILP encoding from \cite{MILP}, and not our novel "2v" model, nor even our "1v" model. However, \cite{ITNE} 

### 2025-08-02 AAAI2026/global.tex
polish

@@
 		to compute $\beta^\varepsilon_{C,D}=\beta^\varepsilon_{D,C}$, 
-		for $C \neq D$ two decision classes.
+		for $C \neq D$  decision classes, as proposed in \cite{vhagar}.
 	\end{enumerate}

### 2025-08-02 AAAI2026/experiments.tex
polish

@@
 
-We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz}, that we reimplement by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
+We start by evaluating how accurate the 2v model is vs the classical encoding vs the interleaving twin-network encoding (ITNE) from \cite{lipshitz,ITNE}, that we reimplement by considering the classical encoding plus the explicit constraints $\frac{x_i-x_i' - \gamma}{2} \leq \hat{x}_i-\hat{x}_i' \leq \frac{x_i-x_i' + \gamma}{2}$, corresponding to Eq.
 (3) of \cite{ITNE} (and also to our (\ref{eq.lpr})).

### 2025-08-04 AAAI2026/PCA.tex
sup

\section{Explanations on PCA model order reduction}

Some words on PCA, learn of 2 Matrix full-dim to reduced-dim and back.

Then how we use it (pictures and text).

### 2025-08-04 AAAI2026/Sup.tex
sup

--- 2025-08-02 AAAI2026/Lipitschz.tex
@@
 
-\title{Order reduction and MILP models for real-time DNN robustness certification.}
+\title{Order reduction and MILP models for real-time DNN robustness certification. \\ Supplementary Material}
 \date{}
@@
 
+	\iffalse
 	\begin{abstract}
 		\input{abstract.tex}
-		\iffalse
+
 		Most DNNs are brittle to small perturbations. Extensive works have thus been performed to verify robustness for DNNs.
@@
 		This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $0.5$, as well as for a surrogate computing the hidden plastic strain associated to a deformation map of a pipe.
+	\end{abstract}
 	\fi
-	\end{abstract}
-
-	\section{Introduction}
-
-	\input{introduction}
-
-	\input{notation}
-
-	\input{global}
-
-	\input{a_trick}
-
-	\newpage
-
-	\input{experiments}
-
-	%\vspace{-0.5cm}
-	\input{related}
-
-\section{Conclusion}
-
-In this paper, we introduced a novel "2v" MILP model for global verification questions, which is 4 to 8 times more accurate than the classical MILP model,
-and more accurate than the ITNE model of \cite{lipshitz}, see 
-Table \ref{table.classical}. Using our "3v" or "1v" models abstracting away some features of the "2v" model,
- even better bounds are reached (Tables 3, 4, 5).
-We also explained how to support $L_1$-perturbations efficiently on top of classical $L_\infty$-perturbations (Prop \ref{prop.l1}).
-To further lower the bounds by $> 10$ times, we resort to model order reduction, reducing the space of search closer to the space of the training dataset, without sacrificing DNN accuracy ($97\%$).
-This results into, to the best of our knowledge, the first {\em real-time} robustness certification reported for a DNN, with $86\%$ of robustness for an $L_1$-perturbation of $.5$ and $53\%$ of robustness for an $L_1$-perturbation twice as large of $1$.
-Still, global verification is only at its beginning, and combining different methods is necessary to scale to more complex DNNs.
-
-	\newpage
-
-	\bibliography{references}
 

### 2025-08-04 AAAI2026/Sup.tex
typo

@@
 
+	\section{Proof of Proposition 2}
+
+	We do a case analysis depending on the value of both binary variables. 
+First, we know the constraints for $\hat{x_i}'=\ReLU(x_i')$ are exact (see 
+Prop.~\ref{Prop1}).
+
+We have 2 binary variables and 4 cases in total. We only need to check that, in all 4 cases, $$\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$$
+
+Case 1: if $a = 1$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 4.
+
+Case 2: if $a = 1$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i+x'_i$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 6.
+
+Case 3: if $a = 0$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = 0$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 3.
+
+Case 4: if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 5.
+
+\input{PCA}
+
+\input{moreexp}
+
 \end{document}

### 2025-08-04 AAAI2026/Sup.tex
reults
moreexp

@@
 
+Recall first that we use the classical MILP encoding 
+for $\hat{x}'_i=\ReLU(x'_i)$, using one binary variable $a'$. We reuse 
+$a'$ (with its value already settled, see Proposition 1 in the main paper) 
+in the encoding of $\hat{y}_i = \ReLU(x_i)-\ReLU(x'_i)$:
+
+\addtocounter{proposition}{1}
+
+\begin{proposition}
+Assuming that $y_i \in [-\gamma_i, \gamma_i]$,
+and that $x'_i \in [\alpha_i,\beta_i]$,
+we have that $\hat{y}_i = \ReLU(x_i=x'_i+y_i)-\ReLU(x'_i)$ is the solution of:
+	\begin{align*}
+		& \begin{aligned}
+			y_i + x'_i &\leq a\beta_i        &
+			y_i &+ x'_i \geq (1-a)\alpha_i \\
+			x'_i       &\leq a'\beta_i       & 
+			x'_i       &\geq (1-a')\alpha_i \\
+			\hat{y}_i  &\leq a\gamma_i       &
+			\hat{y}_i  &\geq -a'\gamma_i \\
+			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
+			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
+			\hat{y}_i  &\leq -x'_i + a\beta_i &
+			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
+			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
+			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
+		\end{aligned}
+	\end{align*} 
+    where $a,a' \in \{0,1\}$ are binary variables, 
+    and $a'$ is shared with the classical MILP
+    encoding for $\hat{x}'_i=\ReLU(x'_i)$.
+\end{proposition}
+
 	We do a case analysis depending on the value of both binary variables. 
-First, we know the constraints for $\hat{x_i}'=\ReLU(x_i')$ are exact (see 
-Prop.~\ref{Prop1}).
+First, we know the constraints for $\hat{x_i}'=\ReLU(x_i')$ are exact.
 
@@
 
+\newpage
+
 \input{PCA}

### 2025-08-05 AAAI2026/PCA.tex
pca figures
images as PDF
pca text p1

@@
 
-Some words on PCA, learn of 2 Matrix full-dim to reduced-dim and back.
+%Some words on PCA, learn of 2 Matrix full-dim to reduced-dim and back.
+%Then how we use it (pictures and text).
 
-Then how we use it (pictures and text).
+Figure~\ref{fig.MNIST} illustrates the pipeline used for MNIST benchmark. The MNIST dataset was used to directly train a MNIST DNN, achieving 97\% accuracy, as denoted by ``Training''. 
+%
+It was also used to obtain the PCA encoding and decoding, transforming the images into a reduced basis.
+The number of PCA dimensions was chosen such that the exploitation accuracy remains constant.
+That is, encoding into a PCA basis and decoding it results in the same accuracy, as illustrated in ``Exploitation''.
+%
+Last, for the ``bound computation'', we determine an $L_1$-perturbation $\varepsilon$.
+The search space for bound computation is 20-dimensional.
+However, the bound itself is computed on the full-space.
+This is possible since PCA is a \emph{linear operation} based on the eigenvectors of the covariance matrix and its transpose for the PCA decoding (inverse).
+
+\begin{figure*}[]
+	\centering
+	\includegraphics[scale=0.9]{MNIST.pdf} \hspace{1.5cm}
+	\caption{Training, exploitation and bound computation on the MNIST dataset.
+Note that PCA encoding/decoding used back-to-back allow to maintain the same accuracy.
+In addition, the bound is computed on the full-space even though the analysis is performed on the reduced space.}
+	\label{fig.MNIST}
+\end{figure*}
+
+Figure~\ref{fig.PIPE} illsutrates the same pipeline used in the pipe strain case.
+In this case, two different PCA are used.
+The first one is learned with the deformation training dataset and the second is learned with the plastic strain one.
+
+The surrogate is then learned from the reduced deformation to the reduced plastic strain. ETC ETC
+
+\begin{figure*}[]
+	\centering
+	\includegraphics[scale=0.9]{PIPE.pdf} \hspace{1.5cm}
+	\caption{PIPE.}
+	\label{fig.PIPE}
+\end{figure*}

### 2025-08-05 AAAI2026/PCA.tex
fig 2 description rough draft

@@
 Note that PCA encoding/decoding used back-to-back allow to maintain the same accuracy.
-In addition, the bound is computed on the full-space even though the analysis is performed on the reduced space.}
+In addition, the bound is computed on the full-space even though the analysis is performed on the reduced space.
+dim = dimension.}
 	\label{fig.MNIST}
@@
 
-Figure~\ref{fig.PIPE} illsutrates the same pipeline used in the pipe strain case.
+Figure~\ref{fig.PIPE} illustrates the same pipeline used in the pipe strain case.
 In this case, two different PCA are used.
 The first one is learned with the deformation training dataset and the second is learned with the plastic strain one.
-
-The surrogate is then learned from the reduced deformation to the reduced plastic strain. ETC ETC
+%
+The surrogate is then learned from the reduced deformation to the reduced plastic strain. 
+%
+For exploitation, we obtain the deformation, use the PCA basis to obtain a reduced deformation, fed the reduced deformation to the surrogate obtaining the reduced strain and decode the strain (apply PCA inverse), obtaining the strain in the full pipe geometry.
+Similarly to the MNIST case, we obtain a bound $\varepsilon$ on the input space by solving the MILP problem as proposed on the input dimension.
 
@@
 	\includegraphics[scale=0.9]{PIPE.pdf} \hspace{1.5cm}
-	\caption{PIPE.}
+	\caption{Training and bound computation on the pipe use case.
+Note that two PCA are used, one for the input space (deformation) and another for the output space (plastic strain).
+The exploitation and bound computation must then use a pipeline that: (1) reduces the deformation; (2) obtain a reduced strain with the surrogate and (3) decodes the reduced strain using the PCA inverse.
+dim = dimension.}
 	\label{fig.PIPE}

### 2025-08-05 AAAI2026/Sup.tex
capitalize section headings

@@
 
-\title{Order reduction and MILP models for real-time DNN robustness certification. \\ Supplementary Material}
+\title{Order Reduction and MILP Models for Real-Time DNN Robustness Certification \\ Supplementary Material}
 \date{}
@@
 
-	\iffalse
-	\begin{abstract}
-		\input{abstract.tex}
-
-		Most DNNs are brittle to small perturbations. Extensive works have thus been performed to verify robustness for DNNs.
-		However, these works mostly consider local robustness, i.e. in the neighborhood of an image.
-		While local robustness is useful to have an idea how often non robust images happen, by repeating the verification on 1000 or 10000 pre-obtained images, the main shortcoming is that we have no guarantee that a specific new incoming image, e.g.
-in a video feed, is robust: The verification process takes too long and requires too much resources to be performed online on embedded systems.
-
-		In this paper, we consider {\em global} robustness, that is, guarantees not restricted to a set of local images.
-For that, we consider {\em bounds} on the switch of values between the different decision classes of a DNN due to a given perturbation.
-		The verification question is much harder than local robustness, as the number of complex variables doubles (from the deviation image to the image and its deviation).
-		Further, the values each neuron can take is no more in a small neighborhood.
-		Therefore, the global verification process is very complex.
-		To obtain useable bounds, we develop several novel partial MILP models for global robustness, with different trade-offs.
-Last, we use order reduction techniques to reduce the space of images considered, avoiding unrealistic inputs, by using linear PCA.
-		This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $0.5$, as well as for a surrogate computing the hidden plastic strain associated to a deformation map of a pipe.
-	\end{abstract}
-	\fi
-
 \section{Proof of Proposition 2}
@@
 
-Case 1: if $a = 1$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 4.
+\textbf{Case 1:} if $a = 1$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i$ based on  $\hat{x'_i} = x'_i$.
+This is true by the two inequalities in line 4.
 
-Case 2: if $a = 1$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i+x'_i$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 6.
+\textbf{Case 2:}  if $a = 1$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i+x'_i$ based on  $\hat{x'_i} = 0$.
+This is true by the two inequalities in line 6.
 
-Case 3: if $a = 0$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = 0$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 3.
+\textbf{Case 3:} if $a = 0$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = 0$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 3.
 
-Case 4: if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 5.
+\textbf{Case 4:} if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$.
+This is true by the two inequalities in line 5.
 

### 2025-08-05 AAAI2026/PCA.tex

--- 2025-08-04 AAAI2026/PCA.tex
@@
-\section{Explanations on PCA model order reduction}
+\section{PCA for Model Order Reduction and Bound Computation}
 
-Some words on PCA, learn of 2 Matrix full-dim to reduced-dim and back.
+%Some words on PCA, learn of 2 Matrix full-dim to reduced-dim and back.
+%Then, how we use it (pictures and text).
 
-Then how we use it (pictures and text).
+Figure~\ref{fig.MNIST} depicts the pipeline used for computing global bounds on the MNIST dataset.
+Firstly, the MNIST dataset is used to train an MNIST DNN, obtaining 97\% of classification accuracy, as denoted in ``Training''.
+%
+In parallel, principal component analysis (PCA) is used to obtain a lower-dimensional representation of the input images, yielding the PCA encoding and the PCA decoding.
+The PCA encoding transforms the input space (784-dimensional) into a 20-dimensional output image, and the PCA decoding reverses that operation, reconstructing a 784-dimensional image.
+%
+The number of retained PCA components is selected to ensure that the MNIST DNN's classification accuracy on reconstructed images (i.e., after PCA encoding and decoding) remains the same as the MNIST DNN used directly on the full-dimensional MNIST images.
+This phase is referred to as ``Exploitation''.
+%
+Lastly, in the ``Bound Computation'' step, we compute an $L_1$ perturbation bound $\varepsilon$.
+Note that the bound itself is calculated on the full space, even though the bound computation is performed on the 20-dimensional latent space.
+This is possible since PCA is a \emph{linear operation} based on the eigenvectors of the covariance matrix and its transpose for the PCA decoding (inverse).
+
+%
+%It was also used to obtain the PCA encoding and decoding, transforming the images into a reduced basis.
+The number of PCA dimensions was chosen such that the exploitation accuracy remains constant.
+That is, encoding into a PCA basis and decoding it results in the same accuracy, as illustrated in ``Exploitation''.
+%
+%Last, for the ``bound computation'', we determine an $L_1$-perturbation $\varepsilon$.
+The search space for bound computation is 20-dimensional.
+However, the bound itself is computed on the full space.
+This is possible since PCA is a \emph{linear operation} based on the eigenvectors of the covariance matrix and its transpose for the PCA decoding (inverse).
+
+\begin{figure*}
+    \centering
+    \includegraphics[scale=0.9]{MNIST.pdf} \hspace{1.5cm}
+    \caption{Training, exploitation, and bound computation on the MNIST dataset.
+Note that PCA encoding/decoding used back-to-back can maintain the same accuracy as the original network where PCA is not used.
+In addition, the bound is computed on the full space even though the analysis is performed on the reduced space.
+dim = dimension.}
+    \label{fig.MNIST}
+\end{figure*}
+
+Figure~\ref{fig.PIPE} illustrates the same pipeline used in the pipe strain case.
+In this case, two different PCAs are used.
+The first one is learned with the deformation training dataset, and the second is learned with the plastic strain one.
+%
+The surrogate is then learned from the reduced deformation to the reduced plastic strain. 
+%
+For exploitation, we obtain the deformation, use the PCA basis to obtain a reduced deformation, feed the reduced deformation to the surrogate, obtain the reduced strain, and decode the strain (apply PCA inverse), obtaining the strain in the full pipe geometry.
+Similarly to the MNIST case, we obtain a bound $\varepsilon$ on the input space by solving the MILP problem as proposed on the input dimension.
+
+\begin{figure*}
+    \centering
+    \includegraphics[scale=0.9]{PIPE.pdf} \hspace{1.5cm}
+    \caption{Training and bound computation on the pipe use case.
+Note that two PCAs are used, one for the input space (deformation) and another for the output space (plastic strain).
+The exploitation and bound computation must then use a pipeline that: (1) reduces the deformation; (2) obtains a reduced strain with the surrogate, and (3) decodes the reduced strain using the PCA inverse.
+dim = dimension.}
+    \label{fig.PIPE}
+\end{figure*}

### 2025-08-05 AAAI2026/PCA.tex
supplementary full

--- 2025-08-05 AAAI2026/PCA.tex
@@
-\section{Explanations on PCA model order reduction}
+\section{PCA Model Order Reduction for Bound Computation}
 
 %Some words on PCA, learn of 2 Matrix full-dim to reduced-dim and back.
-%Then how we use it (pictures and text).
+%Then, how we use it (pictures and text).
 
-Figure~\ref{fig.MNIST} illustrates the pipeline used for MNIST benchmark. The MNIST dataset was used to directly train a MNIST DNN, achieving 97\% accuracy, as denoted by ``Training''. 
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[scale=0.9]{MNIST.pdf} \hspace{1.5cm}
+    \caption{Training, exploitation, and bound computation on the MNIST dataset.}
+    \label{fig.MNIST}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[scale=0.9]{PIPE.pdf} \hspace{1.5cm}
+    \caption{Training and bound computation on the pipe use case. 
+    Note that two PCAs are used, one for the input space (deformation) and another for the output space (plastic strain).
+The exploitation and bound computation must then use a pipeline that: (1) reduces the deformation; (2) obtains a reduced strain with the surrogate, and (3) decodes the reduced strain from the reduced to the full dimension.}
+    \label{fig.PIPE}
+\end{figure*}
+
+PCA (Chinesta et al. 2017) is a linear technique to reduce the dimension of a dataset while keeping its main information.
+From a dataset, the eigen vectors are computed, depicting the most important linear components of this dataset.
+projecting over the first few main eigen vectors is a powerful model order reduction technique ({\em encoding} / {\em reducing from the full dimension}). 
+It is easy to go from the reduce dimension back to the full dimension
+by adding each of the first few eigen vectors times the coefficient in the reduced basis ({\em decoding}).
+
+Figure~\ref{fig.MNIST} depicts the pipeline used for computing:
+
+\begin{enumerate}
+\item  the PCA encoding and decoding as well as the MNSIT DNN from the MNIST Training DataSet ({\em Training}).
+We choose to reduce the dimension from 784 to 20, using the 20 first eigen vectors from PCA, with a PCA encoder and a PCA decoder.
+
+\item {\em In exploitation}, we check whether a test dataset has the same accuracy (class predicted matches the ground truth) 
+going directly through the MNIST DNN than when being encoded and decoded by the PCA decoding first.
+The number of retained PCA dimensions (20) is selected to ensure that the MNIST DNN's classification accuracy on reconstructed images (i.e., after PCA encoding and decoding) remains the same $97$\% as the MNIST DNN used directly on the full-dimensional MNIST images.
 %
-It was also used to obtain the PCA encoding and decoding, transforming the images into a reduced basis.
+\item {\em In Bound Computation}, we consider as input the 20 ($\times 2$: input and perturbed input) reduced PCA dimensions, from which all other variables are fixed.
+However, we can define 784 $\times 2$ linear variables corresponding to the original image $I$ and its perturbation $I'$ before PCA encoding, as the constraints between these and the input are linear.
+We fix the $L_1$-perturbation $\varepsilon$ on the image $I$ and its deformation $I'$, rather than on the inputs, as its where it is meaningful.
+Finally, the goal is to optimize the value of $o_6 -o_8+ o'_8 - o'-6$,  where $o_C$ is the output neuron of the DNN corresponding to class $C \in \{0,\ldots, 9\}$.
+\end{enumerate}
+
+%
+%It was also used to obtain the PCA encoding and decoding, transforming the images into a reduced basis.
 The number of PCA dimensions was chosen such that the exploitation accuracy remains constant.
@@
 %
-Last, for the ``bound computation'', we determine an $L_1$-perturbation $\varepsilon$.
+%Last, for the ``bound computation'', we determine an $L_1$-perturbation $\varepsilon$.
 The search space for bound computation is 20-dimensional.
-However, the bound itself is computed on the full-space.
+However, the bound itself is computed on the full space.
 This is possible since PCA is a \emph{linear operation} based on the eigenvectors of the covariance matrix and its transpose for the PCA decoding (inverse).
 
-\begin{figure*}[]
-	\centering
-	\includegraphics[scale=0.9]{MNIST.pdf} \hspace{1.5cm}
-	\caption{Training, exploitation and bound computation on the MNIST dataset.
-Note that PCA encoding/decoding used back-to-back allow to maintain the same accuracy.
-In addition, the bound is computed on the full-space even though the analysis is performed on the reduced space.}
-	\label{fig.MNIST}
-\end{figure*}
+\newpage
 
-Figure~\ref{fig.PIPE} illsutrates the same pipeline used in the pipe strain case.
-In this case, two different PCA are used.
-The first one is learned with the deformation training dataset and the second is learned with the plastic strain one.
+Figure~\ref{fig.PIPE} illustrates the pipeline used in the pipe strain case. 
+Two different PCA reductions are used. The first one on the deformation training dataset, 
+and the second on the plastic strain one.
+%
+The surrogate is then learned from the reduced deformation to the reduced plastic strain. 
+%
 
-The surrogate is then learned from the reduced deformation to the reduced plastic strain. ETC ETC
+To predict the plastic strain (which is not directly observable), we thus consider the deformation (which is directly observable), reduce it using the PCA reduction to obtain the reduced deformation, call the surrogate model, obtain the associated predicted reduced strain, and decode the reduced strain, obtaining the strain of the pipe in the full 3000 dimensions.
+Similarly to the MNIST case, we consider as input the 10 $\times 2$ dimensions of reduced deformation, but also consider 3000 $\times 2$ linear variables corresponding to the deformation and its perturbation, with linear constraints between them and the inputs (provided by the PCA matrix), and set the $L_1$ perturbation $\varepsilon$ over the Deformation and its perturbation, on which things are physically meaningful.
+The surrogate outputs 26 output dimensions ($\times 2$) of reduced strain, but again 
+as we have the linear PCA decoder explicitly, we can define the optimization goal 
+in terms of optimizing the difference over 10 specific points in the full geometry (where thigs are physically relevant), rather than on the reduced strain space.
 
-\begin{figure*}[]
-	\centering
-	\includegraphics[scale=0.9]{PIPE.pdf} \hspace{1.5cm}
-	\caption{PIPE.}
-	\label{fig.PIPE}
-\end{figure*}
+\newpage

### 2025-08-05 AAAI2026/Sup.tex
more exp
supplementary full

@@
 
+\section{Reproducibility Checklist}
+
+This paper:
+\begin{itemize}
+\item Includes a conceptual outline and/or pseudocode description of AI methods introduced {\bf yes}
+\item Clearly delineates statements that are opinions, hypothesis, and speculation from objective facts and results {\bf yes}
+\item Provides well marked pedagogical references for less-familiare readers to gain background necessary to replicate the paper {\bf yes}
+\item Does this paper make theoretical contributions? {\bf yes}
+\end{itemize}
+
+if yes, then:
+
+\begin{itemize}
+\item All assumptions and restrictions are stated clearly and formally. {\bf yes}
+\item All novel claims are stated formally (e.g., in theorem statements). {\bf yes}
+\item Proofs of all novel claims are included. {\bf yes} (in the supplementary material)
+\item Proof sketches or intuitions are given for complex and/or novel results. {\bf yes}
+\item Appropriate citations to theoretical tools used are given. {\bf yes}
+\item All theoretical claims are demonstrated empirically to hold. {\bf yes}
+\item All experimental code used to eliminate or disprove claims is included. {\bf yes}
+\end{itemize}
+
 \section{Proof of Proposition 2}
@@
 \addtocounter{proposition}{1}
+\addtocounter{table}{1}
 
@@
 
-\newpage
-
 \input{PCA}

### 2025-08-05 AAAI2026/PCA.tex
typos

@@
 From a dataset, the eigen vectors are computed, depicting the most important linear components of this dataset.
-projecting over the first few main eigen vectors is a powerful model order reduction technique ({\em encoding} / {\em reducing from the full dimension}). 
+Projecting over the first few main eigen vectors is a powerful model order reduction technique ({\em encoding} / {\em reducing from the full dimension}). 
 It is easy to go from the reduce dimension back to the full dimension
-by adding each of the first few eigen vectors times the coefficient in the reduced basis ({\em decoding}).
+by making the product between the reduced vector and the first few eigen vectors ({\em decoding}).
 
-Figure~\ref{fig.MNIST} depicts the pipeline used for computing:
+Figure~\ref{fig.MNIST} depicts the MNIST pipeline on reduced dimensions, computing:
 
@@
 The number of retained PCA dimensions (20) is selected to ensure that the MNIST DNN's classification accuracy on reconstructed images (i.e., after PCA encoding and decoding) remains the same $97$\% as the MNIST DNN used directly on the full-dimensional MNIST images.
+It ensures no loss of accuracy.
 %
-\item {\em In Bound Computation}, we consider as input the 20 ($\times 2$: input and perturbed input) reduced PCA dimensions, from which all other variables are fixed.
+\item {\em In Bound Computation}, we consider as input the 20 ($\times 2$: input and perturbed input') reduced PCA dimensions, from which all other variables are fixed.
 However, we can define 784 $\times 2$ linear variables corresponding to the original image $I$ and its perturbation $I'$ before PCA encoding, as the constraints between these and the input are linear.
-We fix the $L_1$-perturbation $\varepsilon$ on the image $I$ and its deformation $I'$, rather than on the inputs, as its where it is meaningful.
-Finally, the goal is to optimize the value of $o_6 -o_8+ o'_8 - o'-6$,  where $o_C$ is the output neuron of the DNN corresponding to class $C \in \{0,\ldots, 9\}$.
+We fix the $L_1$-perturbation $\varepsilon$ on the image $I$ and its deformation $I'$, rather than on the inputs, as that is where it is meaningful.
+Finally, the goal is to optimize the value of $o_6 -o_8+ o'_8 - o'_6$,  where $o_C$ is the output neuron of the DNN corresponding to class $C \in \{0,\ldots, 9\}$.
 \end{enumerate}
@@
 To predict the plastic strain (which is not directly observable), we thus consider the deformation (which is directly observable), reduce it using the PCA reduction to obtain the reduced deformation, call the surrogate model, obtain the associated predicted reduced strain, and decode the reduced strain, obtaining the strain of the pipe in the full 3000 dimensions.
-Similarly to the MNIST case, we consider as input the 10 $\times 2$ dimensions of reduced deformation, but also consider 3000 $\times 2$ linear variables corresponding to the deformation and its perturbation, with linear constraints between them and the inputs (provided by the PCA matrix), and set the $L_1$ perturbation $\varepsilon$ over the Deformation and its perturbation, on which things are physically meaningful.
+Similarly to the MNIST case, we consider as input the 10 $\times 2$ dimensions of reduced deformation, but also consider 3000 $\times 2$ linear variables corresponding to the deformation and its perturbation, with linear constraints between them and the inputs (provided by the PCA encoder, which is given under the form of a matrix), and set the $L_1$ perturbation $\varepsilon$ over the Deformation and its perturbation, where it is physically meaningful.
 The surrogate outputs 26 output dimensions ($\times 2$) of reduced strain, but again 

### 2025-09-01 AAAI2026/experiments.tex
update the new test for pipe system
TIMES REMOVED

@@
 	\begin{tabular}{||l|c|c|c||}\hline\hline
-		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
-	Classical, $50 \times 2$ &    $.320$ &  $.320$ & $.017$ 
+		model, nbr binary var &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
+	Classical, $100$ &    $.320$ &  $.320$ & $.017$ 
     \\\hline
-	ITNE, $50 \times 2$ &    $.042$ &  $.037$ & $.022$
+	ITNE, $100$ &    $.042$ &  $.037$ & $.022$
 	\\ \hline
-    2v model, $50 \times 2$ &    {\bf .040} &  $.037$ &  $.018$ 
+    2v model, $100$ &    {\bf .040} &  $.037$ &  $.018$ 
     \\\hline \hline
-    Classical, $100 \times 2$ &  .186  &  $.022$ & $.022$ 
+     2v model New, $100$ &    {\bf .039} &  $.029$ &  $.020$ 
+    \\\hline \hline
+    Classical, $200$ &  .186  &  $.022$ & $.022$ 
     \\\hline
-	ITNE, $100 \times 2$ &    $.045$ &  $.023$ & .023
+	ITNE, $200$ &    $.045$ &  $.023$ & .023
     \\\hline
-	2v model, $100 \times 2$&     {\bf .042} &  $.023$ &   .023 
+	2v model, $200$&     {\bf .042} &  $.023$ &   .023 
     \\\hline \hline
 	\end{tabular}
-	\caption{Comparison of the classical encoding, ITNE and our "2v" model on the pipe system with a fixed timeout of 1000s, with either $50 \times 2$, 
-    or the full $100 \times 2$ binary variables.}
+	\caption{Comparison of the classical encoding, ITNE and our "2v" model on the pipe system with a fixed timeout of 1000s, with either $100$, 
+    or the full $200$ binary variables.}
     \label{table.classical}
@@
 
-Table \ref{table.classical}, $50 \times 2$, confirms that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model, when 50 variables use LP relaxation.
+Table \ref{table.classical}, $100$, confirms that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model, when 50 variables use LP relaxation.
 Adding explicitly LP relaxation constraints of Eq.
@@
 
-Further, even using a fully accurate model with all $100 \times 2$ variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.
+Further, even using a fully accurate model with all $100$ variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.
 Again,
@@
 	\begin{tabular}{||l||c|c|c||}\hline\hline
-		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
-		1v, $500 \times 1$ & {\bf 14.97} & $.845$ & $.009$ \\\hline 
-		3v, $500 \times 3$ & $17.66$ & $.813$ & {\bf .518} \\\hline 
-	    2v, $500 \times 2$ & $16.49$ & n/a & n/a \\\hline\hline	 
+		model, nbr binary var &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
+		1v, $500$ & {\bf 14.97} & $.845$ & $.009$ \\\hline 
+		3v, $1000$ & $17.66$ & $.813$ & {\bf .518} \\\hline 
+	    2v, $1000$ & $16.49$ & n/a & n/a \\\hline\hline	 
 	\end{tabular}
@@
 	on the {\bf full dimension} MNIST DNN, 
-	for timeouts of $14400$s, when all 500 ($\times 1$, $\times 2$, $\times 3$) variables are binary.}
+	for timeouts of $14400$s, when all 500 / 1000 variables are binary.}
 	\label{table.mnist}
@@
 \includegraphics[scale=0.6]{perturb.png}
-\caption{An improbable image for MNIST and its perturbation ($L1$-difference of $.5$ in a unique pixel at x=14, y=8 from top) with maximal $\beta^{.5}_{6,8}=0.518$, as obtained by the "3v" $500 \times 2$ model in {\bf full 784 dimension} image space.}
+\caption{An improbable image for MNIST and its perturbation ($L1$-difference of $.5$ in a unique pixel at x=14, y=8 from top) with maximal $\beta^{.5}_{6,8}=0.518$, as obtained by the "3v" model in {\bf full 784 dimension} image space.}
 \label{fig3}
@@
 \includegraphics[scale=0.5]{redperturb.png}
-\caption{An image for MNIST and its perturbation from the {\bf 20-dimension reduced space} with maximal $\beta^{.5}_{6,8}=.084$, as obtained by the "2v" $500 \times 2$ model.}
+\caption{An image for MNIST and its perturbation from the {\bf 20-dimension reduced space} with maximal $\beta^{.5}_{6,8}=.084$, as obtained by the "2v" model with $1000$ binary variables.}
 \label{fig4}
@@
 	\begin{tabular}{||l||c|c|c||}\hline\hline
-		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ \\\hline \hline
+		model, nbr binary var &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ \\\hline \hline
 %1v, $400 \times 1$ & $1.414$ &  $.691$ & $.010$ \\\hline 
@@
 
-1v, $500 \times 1$ & $1.412$ & $.161$ & .057 \\\hline 
-3v, $500 \times 3$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
-2v, $500 \times 2$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline
+1v, $500$ & $1.412$ & $.161$ & .057 \\\hline 
+3v, $1000$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
+2v, $1000$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline
 
@@
 	all %400, 475,  or 
-	500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
+	neurons use 500 / 1000 binary variables.}
 	\label{table.reduced}
@@
 	\begin{tabular}{||l||c|c|c|c||}\hline\hline
-		model &    $L_1\leq 0.5$ & $L_1\leq 1$ & $L_1\leq 1.5$ &  $L_1\leq 2$ \\\hline \hline
-		1v, $500\times1$ & $80 \%$ & $32\%$ & $7\%$ & $0\%$ \\\hline
-		3v, $500 \times 3$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
-		2v, $500 \times 2$ & 84\% & 51\% & 16\% & {\bf 4\%} \\\hline \hline
+		model, nbr &    $L_1\leq 0.5$ & $L_1\leq 1$ & $L_1\leq 1.5$ &  $L_1\leq 2$ \\\hline \hline
+		1v, $500$ & $80 \%$ & $32\%$ & $7\%$ & $0\%$ \\\hline
+		3v, $1000$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
+		2v, $1000$ & 84\% & 51\% & 16\% & {\bf 4\%} \\\hline \hline
 	\end{tabular}
@@
 \includegraphics[scale=0.5]{strain.png}
-\caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" $100 \times 2$ model.}
+\caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" model with $200 $ binary variable.}
 \label{fig5}
@@
 	\begin{tabular}{||l||c|c|c|c||}\hline\hline
-		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ &  Time(s) \\\hline \hline
-		1v, $100 \times 1$ &     {\bf .0356} &  $.0356$ & $.0191$ &  1000 \\\hline
-		3v, $100 \times 3$&     .0414 &  .0254 &  .0166 &  1000 \\\hline
-		2v, $100 \times 2$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline \hline
+		model, nbr&        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ &  Time(s) \\\hline \hline
+		1v, $100$ &     {\bf .0356} &  $.0356$ & $.0191$ &  1000 \\\hline
+		3v, $200$&     .0414 &  .0254 &  .0166 &  1000 \\\hline
+		2v, $200$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline \hline
 		%3v, $97 \times 3$&      ?? &  ?? &  ?? & 14440 \\\hline
-		3v, $100 \times 3$&      {\bf .0350} &  .0272 &  .0216 & 14440 \\\hline
+		3v, $200$&      {\bf .0350} &  .0272 &  .0216 & 14440 \\\hline
 		%2v, $97 \times 2$&     ?? &  ?? &   ?? & 14440 \\\hline
-		2v, $100 \times 2$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline \hline
-		3v, $100 \times 3$&     {\bf .0329} &  .0277 &  .0165 & 72000 \\\hline
-		2v, $100 \times 2$&     .0337 &  .0245 &  {\bf .0245} & 72000 \\\hline\hline
+		2v, $200$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline \hline
+		3v, $200$&     {\bf .0329} &  .0277 &  .0165 & 72000 \\\hline
+		2v, $200$&     .0337 &  .0245 &  {\bf .0245} & 72000 \\\hline\hline
 	\end{tabular}
-	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with timeouts of 1000s, 14440s and 72000s, where all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
+	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with timeouts of 1000s, 14440s and 72000s, where all neurons use 100 / 200 binary variables.}
 	%L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}

### 2025-11-10 CAV 2026/CAV2026_main.tex
Add CAV2026 folder

--- 2025-08-02 AAAI2026/Lipitschz.tex
@@
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai2026}  % DO NOT CHANGE THIS
+\documentclass[runningheads]{llncs}
+\usepackage[T1]{fontenc}
+
 \usepackage{times}  % DO NOT CHANGE THIS
@@
 \floatname{listing}{Listing}
-%
-% Keep the \pdfinfo as shown here. There's no need
-% for you to add the /Title and /Author tags.
-\pdfinfo{
-	/TemplateVersion (2026.1)
-}
-
-\title{Order reduction and MILP models for real-time DNN robustness certification.}
-\date{}
-\author{
-	%Authors
-	% All authors must be in the same font size and format.
-	Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
-	AAAI Style Contributions by Pater Patel Schneider,
-	Sunil Issar,\\
-	J. Scott Penberthy,
-	George Ferguson,
-	Hans Guesgen,
-	Francisco Cruz\equalcontrib,
-	Marc Pujol-Gonzalez\equalcontrib
-}
-\affiliations{
-	%Afiliations
-	\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
-	% If you have multiple authors and multiple affiliations
-	% use superscripts in text and roman font to identify them.
-	% For example,
-
-	% Sunil Issar\textsuperscript{\rm 2},
-	% J. Scott Penberthy\textsuperscript{\rm 3},
-	% George Ferguson\textsuperscript{\rm 4},
-	% Hans Guesgen\textsuperscript{\rm 5}
-	% Note that the comma should be placed after the superscript
-
-	1101 Pennsylvania Ave, NW Suite 300\\
-	Washington, DC 20004 USA\\
-	% email address must be in roman text type, not monospace or sans serif
-	proceedings-questions@aaai.org
-	%
-	% See more examples next
-}
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse
-\title{My Publication Title --- Single Author}
-\author {
-	Author Name
-}
-\affiliations{
-	Affiliation\\
-	Affiliation Line 2\\
-	name@example.com
-}
-\fi
-
-\iffalse
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\title{My Publication Title --- Multiple Authors}
-\author {
-	% Authors
-	First Author Name\textsuperscript{\rm 1},
-	Second Author Name\textsuperscript{\rm 2},
-	Third Author Name\textsuperscript{\rm 1}
-}
-\affiliations {
-	% Affiliations
-	\textsuperscript{\rm 1}Affiliation 1\\
-	\textsuperscript{\rm 2}Affiliation 2\\
-	firstAuthor@affiliation1.com, secondAuthor@affilation2.com, thirdAuthor@affiliation1.com
-}
-\fi
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{definition}{Definition}
 \newcommand{\vW}{\boldsymbol{W}}
@@
 \begin{document}
+
+\title{Order reduction and MILP models for real-time DNN robustness certification.}
+\date{}
 
@@
 
+\bibliographystyle{plain} 
 \bibliography{references}
-
 \end{document}

### 2025-11-10 CAV 2026/a_trick.tex
Add CAV2026 folder

\subsection*{Encoding $L_1$-perturbations with linear variables}

Let $\vec{x}=(x_i)_{i\leq n}$ be an input vector, with $n$ dimensions.

\begin{proposition}
	\label{prop.l1}
Define $n$ linear variables $(A_i)_{i<n}$ with the constraints 
\begin{align}\label{L1constraint}\begin{cases}
	A_i \geq x_i &\text{ for }i \leq n\\ 
	A_i\geq -x_i &\text{ for }i \leq n\\
	\sum_{i\leq n} A_i \leq c	&\end{cases}
\end{align}

This is equivalent with asking $||\vec{x}||_{L_1} = \sum_{i\leq n} |x_i| \leq c$.
\end{proposition}

The proof is simple: the first two lines of constraints (\ref{L1constraint}) are equivalent with $A_i \geq |x_i|$. So the whole constraint (\ref{L1constraint}) 
implies that $\sum_{i\leq n} |x_i| \leq c$.

Conversely, for every instance that satisfies $\sum_{i\leq n} |x_i| \leq c$, then there is also an instance which satisfies constraints (\ref{L1constraint}),  by defining $A_i = |x_i|$ for all $i \leq n$.

This shows that constraints (\ref{L1constraint}) is equivalent with 
$||\vec{x}||_{L_1} = \sum_{i\leq n} |x_i| \leq c$.

### 2025-11-10 CAV 2026/global.tex
Add CAV2026 folder

--- 2025-08-02 AAAI2026/global.tex
@@
 Notice that this was already witnessed in \cite{ITNE}, and some additional constraints were added to make the classical model more accurate:
-	the diff variables were defined, although to pass the ReLU the classical  
+	the {\em diff variables} were defined, although to pass the ReLU the classical  
 	MILP encoding was used, but with added specific constraints (Eq. (3) in 
@@
     First, we consider variables $x'_j,\hat{x}'_j, y_j, \hat{y}_j$, where $y_j, \hat{y}_j$ are the {\em diff variables}, with     $y_j = x_j - x'_j$ and $\hat{y}_j= \hat{x}_j - \hat{x}'_j$, as already proposed in \cite{lipshitz,ITNE}.
-	Intuitively, the diff variables will be small as they will be carrying the difference between both the image $I$ and its perturbation $I'$.
+	Intuitively, the {\em diff values} will be small as they will be carrying the difference between both the image $I$ and its perturbation $I'$.
     We will use the classical MILP encoding for $\hat{x}'_j$.
@@
     Prop.
-\ref{Prop2} can be decoupled from the binary variable appearing in the classical encoding of $x'_i = \ReLU(x'_i)$.
+\ref{Prop2} can be decoupled from the binary variable appearing in the classical encoding of $\hat{x}'_i = \ReLU(x'_i)$.
 While this means having 3 binary variables per unstable ReLU (which warrants the name "3v" model), the fact that these variables are decoupled removes a lot of constraints in the MILP encoding, and actually helps the solver.

### 2025-11-10 CAV 2026/introduction.tex
Add CAV2026 folder

--- 2025-08-02 AAAI2026/introduction.tex
@@
 The decoupling of variables generating the "3v" model offers good trade-offs, reaching slightly better bounds in the same runtime.
-The "1v" model converges faster  but bounds are looser, a good trade-off when runtime is limited and problem is complex (Tables \ref{table.mnist},\ref{table.pipe}).
+The "1v" model converges faster  but bounds are looser, a good trade-off when runtime is limited or problem is complex (Tables \ref{table.mnist},\ref{table.pipe}).
 \end{enumerate}

### 2025-11-10 CAV 2026/notation.tex
Add CAV2026 folder

--- 2025-08-02 AAAI2026/notation.tex
@@
 \label{Prop1}
-A solution $x,\hat{x},a$  of the above MILP program satisfies $\hat{x} = \ReLU(x)$,
-and $a=1$ if $x> 0$ and $a=0$ if $x< 0$ (both are possible if $x=0$).
+A solution $x,\hat{x},a$  of the above MILP program (\ref{eq11}) satisfies $\hat{x} = \ReLU(x)$,
+and $a=1$ if $x> 0$ and $a=0$ if $x< 0$ (both $a=0,1$ are possible if $x=0$).
 \end{proposition}
@@
 
-    In the whole MILP model, each unstable ReLU is encoded in the above way with one integer variable. The encoding from $(\hat{x}_j)_{j \text{ in layer } i}$ to 
+    The encoding from $(\hat{x}_j)_{j \text{ in layer } i}$ to 
 	$(x_{j'})_{j' \text{ in layer } i+1}$ variables is simply the linear combination 
 	$\boldsymbol{z}^{i} = \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{i-1}+ \vb^i$.
+	Hence the full MILP model uses exactly as many binary variables as 
+	unstable ReLUs.
 	%This exact MILP encoding is often too computationally intensive, as the worst-case complexity of MILP is exponential in the number of integer variables \cite{DivideAndSlide}.
@@
 	\cite{DivideAndSlide}:
-	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the pMILP based on $X$ to compute neuron $n$ uses the MILP encpoding (\ref{eq11}), where variable $a$ is:
+	Let $X$ be a subset of the set of unstable neurons, and $n$ a neuron for which we want to compute upper and lower bounds on values: the pMILP based on $X$ to compute neuron $n$ uses the MILP encoding (\ref{eq11}), where variable $a$ is:
 	\begin{itemize}

### 2025-11-10 CAV 2026/PCA.tex
update CAV2026 folder

--- 2025-08-05 AAAI2026/PCA.tex
@@
 PCA (Chinesta et al. 2017) is a linear technique to reduce the dimension of a dataset while keeping its main information.
-From a dataset, the eigen vectors are computed, depicting the most important linear components of this dataset.
-Projecting over the first few main eigen vectors is a powerful model order reduction technique ({\em encoding} / {\em reducing from the full dimension}). 
-It is easy to go from the reduce dimension back to the full dimension
-by making the product between the reduced vector and the first few eigen vectors ({\em decoding}).
+From a dataset, the eigenvectors are computed, defining the most important linear components of this dataset.
+Projecting over the first few main eigenvectors is a powerful model order reduction technique ({\em encoding} / {\em reducing from the full dimension}). 
+It is easy to go from the reduced dimension back to the full dimension
+by making the product between the reduced vector and the first few eigenvectors ({\em decoding}).
 
@@
 \begin{enumerate}
-\item  the PCA encoding and decoding as well as the MNSIT DNN from the MNIST Training DataSet ({\em Training}).
-We choose to reduce the dimension from 784 to 20, using the 20 first eigen vectors from PCA, with a PCA encoder and a PCA decoder.
+\item the PCA encoding and decoding as well as the MNIST DNN from the MNIST Training DataSet ({\em Training}).
+We choose to reduce the dimension from 784 to 20, using the first 20 eigen vectors from PCA, with a PCA encoder and a PCA decoder.
 
 \item {\em In exploitation}, we check whether a test dataset has the same accuracy (class predicted matches the ground truth) 
-going directly through the MNIST DNN than when being encoded and decoded by the PCA decoding first.
+going directly through the MNIST DNN rather than being encoded and decoded by the PCA decoding first.
 The number of retained PCA dimensions (20) is selected to ensure that the MNIST DNN's classification accuracy on reconstructed images (i.e., after PCA encoding and decoding) remains the same $97$\% as the MNIST DNN used directly on the full-dimensional MNIST images.
@@
 Figure~\ref{fig.PIPE} illustrates the pipeline used in the pipe strain case. 
-Two different PCA reductions are used. The first one on the deformation training dataset, 
-and the second on the plastic strain one.
+Two different PCA reductions are used. The first one is on the deformation training dataset, 
+and the second is on the plastic strain one.
 %
@@
 To predict the plastic strain (which is not directly observable), we thus consider the deformation (which is directly observable), reduce it using the PCA reduction to obtain the reduced deformation, call the surrogate model, obtain the associated predicted reduced strain, and decode the reduced strain, obtaining the strain of the pipe in the full 3000 dimensions.
-Similarly to the MNIST case, we consider as input the 10 $\times 2$ dimensions of reduced deformation, but also consider 3000 $\times 2$ linear variables corresponding to the deformation and its perturbation, with linear constraints between them and the inputs (provided by the PCA encoder, which is given under the form of a matrix), and set the $L_1$ perturbation $\varepsilon$ over the Deformation and its perturbation, where it is physically meaningful.
-The surrogate outputs 26 output dimensions ($\times 2$) of reduced strain, but again 
-as we have the linear PCA decoder explicitly, we can define the optimization goal 
-in terms of optimizing the difference over 10 specific points in the full geometry (where thigs are physically relevant), rather than on the reduced strain space.
+Similarly to the MNIST case, we consider as input the 10 $\times 2$ dimensions of reduced deformation, but also consider 3000 $\times 2$ linear variables corresponding to the deformation and its perturbation, with linear constraints between them and the inputs (provided by the PCA encoder, which is given under the form of a matrix), and set the $L_1$ perturbation $\varepsilon$ over the deformation and its perturbation, where it is physically meaningful.
+The surrogate outputs 26 output dimensions ($\times 2$) of reduced strain, but again, as we have the linear PCA decoder explicitly, we can define the optimization goal in terms of optimizing the difference over 10 specific points in the full geometry (where it is are physically relevant), rather than on the reduced strain space.
 

### 2025-11-10 CAV 2026/Sup.tex
update CAV2026 folder

--- 2025-08-05 AAAI2026/Sup.tex
@@
 \floatname{listing}{Listing}
-%
-% Keep the \pdfinfo as shown here. There's no need
-% for you to add the /Title and /Author tags.
-\pdfinfo{
-	/TemplateVersion (2026.1)
-}
-
-\title{Order Reduction and MILP Models for Real-Time DNN Robustness Certification \\ Supplementary Material}
-\date{}
-\author{
-	%Authors
-	% All authors must be in the same font size and format.
-	Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
-	AAAI Style Contributions by Pater Patel Schneider,
-	Sunil Issar,\\
-	J. Scott Penberthy,
-	George Ferguson,
-	Hans Guesgen,
-	Francisco Cruz\equalcontrib,
-	Marc Pujol-Gonzalez\equalcontrib
-}
-\affiliations{
-	%Afiliations
-	\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
-	% If you have multiple authors and multiple affiliations
-	% use superscripts in text and roman font to identify them.
-	% For example,
-
-	% Sunil Issar\textsuperscript{\rm 2},
-	% J. Scott Penberthy\textsuperscript{\rm 3},
-	% George Ferguson\textsuperscript{\rm 4},
-	% Hans Guesgen\textsuperscript{\rm 5}
-	% Note that the comma should be placed after the superscript
-
-	1101 Pennsylvania Ave, NW Suite 300\\
-	Washington, DC 20004 USA\\
-	% email address must be in roman text type, not monospace or sans serif
-	proceedings-questions@aaai.org
-	%
-	% See more examples next
-}
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse
-\title{My Publication Title --- Single Author}
-\author {
-	Author Name
-}
-\affiliations{
-	Affiliation\\
-	Affiliation Line 2\\
-	name@example.com
-}
-\fi
-
-\iffalse
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\title{My Publication Title --- Multiple Authors}
-\author {
-	% Authors
-	First Author Name\textsuperscript{\rm 1},
-	Second Author Name\textsuperscript{\rm 2},
-	Third Author Name\textsuperscript{\rm 1}
-}
-\affiliations {
-	% Affiliations
-	\textsuperscript{\rm 1}Affiliation 1\\
-	\textsuperscript{\rm 2}Affiliation 2\\
-	firstAuthor@affiliation1.com, secondAuthor@affilation2.com, thirdAuthor@affiliation1.com
-}
-\fi
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{definition}{Definition}
 \newcommand{\vW}{\boldsymbol{W}}
@@
 \usepackage{bibentry}
-% END REMOVE bibentry
 
@@
 \item Clearly delineates statements that are opinions, hypothesis, and speculation from objective facts and results {\bf yes}
-\item Provides well marked pedagogical references for less-familiare readers to gain background necessary to replicate the paper {\bf yes}
+\item Provides well marked pedagogical references for less-familiar readers to gain background necessary to replicate the paper {\bf yes}
 \item Does this paper make theoretical contributions? {\bf yes}

### 2025-11-10 CAV 2026/introduction.tex
update

@@
 Compared with the
-	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz, ITNE},
+	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz,ITNE},
 	the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other.
-This was observed in \cite{lipshitz, ITNE}, and constraints encoding
+This was observed in \cite{lipshitz,ITNE}, and constraints encoding
 	a part of the linear relaxation of our "2v" model were added explicitly. Experimentally, 

### 2025-11-10 CAV 2026/notation.tex
update

@@
     $\hat{y}_i = \ReLU(x_j-x'_j)$), similarly than in the 
-	Interleaving Twin-Network Encoding (ITNE) model of \cite{lipshitz, ITNE}. 
+	Interleaving Twin-Network Encoding (ITNE) model of \cite{lipshitz,ITNE}. 
     \end{itemize}

### 2025-11-11 AAAI2026/a_trick.tex
rr

--- 2025-07-29 AAAI2026/a_trick.tex
@@
-\subsection*{A trick of $L_1$ norm constraints on input}
+\subsection*{Encoding $L_1$-perturbations with linear variables}
 
-A trick to set $L_1$ norm constraints on the input space into linear constraints is described below.
+Let $\vec{x}=(x_i)_{i\leq n}$ be an input vector, with $n$ dimensions.
 
-Suppose the dimension of input space is $n$, and $x_i,i\leq n$ are the input variables, $\vec{x}$ is the input vector, and we hope to set a constraints of $\vec{x}$ that $\|\vec{x}\| \leq c$,  then we can set the constraints by add variables $A_i,i<n$ with the only constraints \begin{align}\label{L1constraint}\begin{cases}
+\begin{proposition}
+	\label{prop.l1}
+Define $n$ linear variables $(A_i)_{i<n}$ with the constraints 
+\begin{align}\label{L1constraint}\begin{cases}
 	A_i \geq x_i &\text{ for }i \leq n\\ 
 	A_i\geq -x_i &\text{ for }i \leq n\\
-	\Sigma_{i\leq n} A_i \leq c	&\end{cases}
+	\sum_{i\leq n} A_i \leq c	&\end{cases}
 \end{align}
 
-We show that this constraint is equivalent to $\|\vec{x}\| \leq c$.
+This is equivalent with asking $||\vec{x}||_{L_1} = \sum_{i\leq n} |x_i| \leq c$.
+\end{proposition}
 
-The first two lines of constraints \ref{L1constraint} is equivalent to that $A_i\geq |x_i|$. So the whole constraints is non-weaker than $\|\vec{x}\| \leq c$.
+The proof is simple: the first two lines of constraints (\ref{L1constraint}) are equivalent with $A_i \geq |x_i|$. So the whole constraint (\ref{L1constraint}) 
+implies that $\sum_{i\leq n} |x_i| \leq c$.
 
-Next, for every instance that satisfy $\|\vec{x}\| \leq c$, then there is also an instance which satisfy constraints \ref{L1constraint}: simply let all $A_i = |x_i|$.
-And this shows that $\|\vec{x}\| \leq c$ is non-weaker than constraints \ref{L1constraint}.
-Therefore they are equivalent.
+Conversely, for every instance that satisfies $\sum_{i\leq n} |x_i| \leq c$, then there is also an instance which satisfies constraints (\ref{L1constraint}),  by defining $A_i = |x_i|$ for all $i \leq n$.
+
+This shows that constraints (\ref{L1constraint}) is equivalent with 
+$||\vec{x}||_{L_1} = \sum_{i\leq n} |x_i| \leq c$.

### 2025-11-11 AAAI2026/abstract.tex
rr

@@
 Last, we use order reduction techniques to reduce the space of inputs considered, avoiding unrealistic images, by using principal component analysis (PCA).
-This results into the {\em real-time} certification of the robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of $.5$, as well as for a surrogate computing the
+These bounds ensure the {\em real-time} certification of robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of $.5$, as well as faitfhulness of a surrogate computing the
 %latent
-plastic strain associated with a pipe deformation map.
+plastic strain due to the deformation of a pipe.

### 2025-11-11 AAAI2026/related.tex
rr

@@
-\section{Related Work}
+\section{Related Work on Global Robustness}
 
@@
 
-Closer to our paper, several works  \cite{Marabou,lipshitz,ITNE,GROCET} consider a global certified restricted Lipschitz bound, to understand how the output change with input perturbations.
+More related, several works  \cite{Marabou,lipshitz,ITNE,GROCET} consider certifying {\em restricted} Lipschitz bound, to understand how the output can change given an input perturbations.
 However, they do not consider whether the classification changes.

### 2025-11-11 CAV 2025 TODO/iclr2025_conference.tex
rr

\documentclass{article} % For LaTeX2e
\usepackage{iclr2025_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}

\title{Formatting Instructions for ICLR 2025 \\ Conference Submissions}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

\maketitle

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

\section{Submission of conference papers to ICLR 2025}

ICLR requires electronic submissions, processed by
\url{https://openreview.net/}. See ICLR's website for more instructions.

If your paper is ultimately accepted, the statement {\tt
  {\textbackslash}iclrfinalcopy} should be inserted to adjust the
format to the camera ready requirements.

The format for the submissions is a variant of the NeurIPS format.
Please read carefully the instructions below, and follow them
faithfully.

\subsection{Style}

Papers to be submitted to ICLR 2025 must be prepared according to the
instructions presented here.

%% Please note that we have introduced automatic line number generation
%% into the style file for \LaTeXe. This is to help reviewers
%% refer to specific lines of the paper when they make their comments. Please do
%% NOT refer to these line numbers in your paper as they will be removed from the
%% style file for the final version of accepted papers.

Authors are required to use the ICLR \LaTeX{} style files obtainable at the
ICLR website. Please make sure you use the current files and
not previous versions. Tweaking the style files may be grounds for rejection.

\subsection{Retrieval of style files}

The style files for ICLR and other conference information are available online at:
\begin{center}
   \url{http://www.iclr.cc/}
\end{center}
The file \verb+iclr2025_conference.pdf+ contains these
instructions and illustrates the
various formatting requirements your ICLR paper must satisfy.
Submissions must be made using \LaTeX{} and the style files
\verb+iclr2025_conference.sty+ and \verb+iclr2025_conference.bst+ (to be used with \LaTeX{}2e). The file
\verb+iclr2025_conference.tex+ may be used as a ``shell'' for writing your paper. All you
have to do is replace the author, title, abstract, and text of the paper with
your own.

The formatting instructions contained in these style files are summarized in
sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
preferred typeface throughout. Paragraphs are separated by 1/2~line space,
with no indentation.

Paper title is 17~point, in small caps and left-aligned.
All pages should start at 1~inch (6~picas) from the top of the page.

Authors' names are
set in boldface, and each name is placed above its corresponding
address. The lead author's name is to be listed first, and
the co-authors' names are set to follow. Authors sharing the
same address can be on the same line.

Please pay special attention to the instructions in section \ref{others}
regarding figures, tables, acknowledgments, and references.

There will be a strict upper limit of 10 pages for the main text of the initial submission, with unlimited additional pages for citations.

\section{Headings: first level}
\label{headings}

First level headings are in small caps,
flush left and in point size 12. One line space before the first level
heading and 1/2~line space after the first level heading.

\subsection{Headings: second level}

Second level headings are in small caps,
flush left and in point size 10. One line space before the second level
heading and 1/2~line space after the second level heading.

\subsubsection{Headings: third level}

Third level headings are in small caps,
flush left and in point size 10. One line space before the third level
heading and 1/2~line space after the third level heading.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone, regardless of the formatter being used.

\subsection{Citations within the text}

Citations within the text should be based on the \texttt{natbib} package
and include the authors' last names and year (with the ``et~al.'' construct
for more than two authors). When the authors or the publication are
included in the sentence, the citation should not be in parenthesis using \verb|\citet{}| (as
in ``See \citet{Hinton06} for more information.''). Otherwise, the citation
should be in parenthesis using \verb|\citep{}| (as in ``Deep learning shows promise to make progress
towards AI~\citep{Bengio+chapter2007}.'').

The corresponding references are to be listed in alphabetical order of
authors, in the \textsc{References} section. As to the format of the
references themselves, any style is acceptable as long as it is used
consistently.

\subsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first footnote} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches
(12~picas).\footnote{Sample of the second footnote}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction; art work should not be
hand-drawn. The figure number and caption always appear after the
figure. Place one line space before the figure caption, and one line
space after the figure. The figure caption is lower case (except for
first word and proper nouns); figures are numbered consecutively.

Make sure the figure caption does not get separated from the figure.
Leave sufficient space to avoid splitting the figure and figure caption.

You may use color figures.
However, it is best for the
figure captions and the paper body to make sense if the paper is printed
either in black/white or in color.
\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible. Do not use hand-drawn
tables. The table number and title always appear before the table. See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the table
title, and one line space after the table. The table title must be lower case
(except for first word and proper nouns); tables are numbered consecutively.

\begin{table}[t]
\caption{Sample table title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
\\ \hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\section{Default Notation}

In an attempt to encourage standardized notation, we have included the
notation file from the textbook, \textit{Deep Learning}
\cite{goodfellow2016deep} available at
\url{https://github.com/goodfeli/dlbook_notation/}.  Use of this style
is not required and can be disabled by commenting out
\texttt{math\_commands.tex}.

\centerline{\bf Numbers and Arrays}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1in}p{3.25in}}
$\displaystyle a$ & A scalar (integer or real)\\
$\displaystyle \va$ & A vector\\
$\displaystyle \mA$ & A matrix\\
$\displaystyle \tA$ & A tensor\\
$\displaystyle \mI_n$ & Identity matrix with $n$ rows and $n$ columns\\
$\displaystyle \mI$ & Identity matrix with dimensionality implied by context\\
$\displaystyle \ve^{(i)}$ & Standard basis vector $[0,\dots,0,1,0,\dots,0]$ with a 1 at position $i$\\
$\displaystyle \text{diag}(\va)$ & A square, diagonal matrix with diagonal entries given by $\va$\\
$\displaystyle \ra$ & A scalar random variable\\
$\displaystyle \rva$ & A vector-valued random variable\\
$\displaystyle \rmA$ & A matrix-valued random variable\\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Sets and Graphs}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \sA$ & A set\\
$\displaystyle \R$ & The set of real numbers \\
$\displaystyle \{0, 1\}$ & The set containing 0 and 1 \\
$\displaystyle \{0, 1, \dots, n \}$ & The set of all integers between $0$ and $n$\\
$\displaystyle [a, b]$ & The real interval including $a$ and $b$\\
$\displaystyle (a, b]$ & The real interval excluding $a$ but including $b$\\
$\displaystyle \sA \backslash \sB$ & Set subtraction, i.e., the set containing the elements of $\sA$ that are not in $\sB$\\
$\displaystyle \gG$ & A graph\\
$\displaystyle \parents_\gG(\ervx_i)$ & The parents of $\ervx_i$ in $\gG$
\end{tabular}
\vspace{0.25cm}

\centerline{\bf Indexing}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \eva_i$ & Element $i$ of vector $\va$, with indexing starting at 1 \\
$\displaystyle \eva_{-i}$ & All elements of vector $\va$ except for element $i$ \\
$\displaystyle \emA_{i,j}$ & Element $i, j$ of matrix $\mA$ \\
$\displaystyle \mA_{i, :}$ & Row $i$ of matrix $\mA$ \\
$\displaystyle \mA_{:, i}$ & Column $i$ of matrix $\mA$ \\
$\displaystyle \etA_{i, j, k}$ & Element $(i, j, k)$ of a 3-D tensor $\tA$\\
$\displaystyle \tA_{:, :, i}$ & 2-D slice of a 3-D tensor\\
$\displaystyle \erva_i$ & Element $i$ of the random vector $\rva$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Calculus}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
% NOTE: the [2ex] on the next line adds extra height to that row of the table.
% Without that command, the fraction on the first line is too tall and collides
% with the fraction on the second line.
$\displaystyle\frac{d y} {d x}$ & Derivative of $y$ with respect to $x$\\ [2ex]
$\displaystyle \frac{\partial y} {\partial x} $ & Partial derivative of $y$ with respect to $x$ \\
$\displaystyle \nabla_\vx y $ & Gradient of $y$ with respect to $\vx$ \\
$\displaystyle \nabla_\mX y $ & Matrix derivatives of $y$ with respect to $\mX$ \\
$\displaystyle \nabla_\tX y $ & Tensor containing derivatives of $y$ with respect to $\tX$ \\
$\displaystyle \frac{\partial f}{\partial \vx} $ & Jacobian matrix $\mJ \in \R^{m\times n}$ of $f: \R^n \rightarrow \R^m$\\
$\displaystyle \nabla_\vx^2 f(\vx)\text{ or }\mH( f)(\vx)$ & The Hessian matrix of $f$ at input point $\vx$\\
$\displaystyle \int f(\vx) d\vx $ & Definite integral over the entire domain of $\vx$ \\
$\displaystyle \int_\sS f(\vx) d\vx$ & Definite integral with respect to $\vx$ over the set $\sS$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Probability and Information Theory}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle P(\ra)$ & A probability distribution over a discrete variable\\
$\displaystyle p(\ra)$ & A probability distribution over a continuous variable, or over
a variable whose type has not been specified\\
$\displaystyle \ra \sim P$ & Random variable $\ra$ has distribution $P$\\% so thing on left of \sim should always be a random variable, with name beginning with \r
$\displaystyle  \E_{\rx\sim P} [ f(x) ]\text{ or } \E f(x)$ & Expectation of $f(x)$ with respect to $P(\rx)$ \\
$\displaystyle \Var(f(x)) $ &  Variance of $f(x)$ under $P(\rx)$ \\
$\displaystyle \Cov(f(x),g(x)) $ & Covariance of $f(x)$ and $g(x)$ under $P(\rx)$\\
$\displaystyle H(\rx) $ & Shannon entropy of the random variable $\rx$\\
$\displaystyle \KL ( P \Vert Q ) $ & Kullback-Leibler divergence of P and Q \\
$\displaystyle \mathcal{N} ( \vx ; \vmu , \mSigma)$ & Gaussian distribution %
over $\vx$ with mean $\vmu$ and covariance $\mSigma$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Functions}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle f: \sA \rightarrow \sB$ & The function $f$ with domain $\sA$ and range $\sB$\\
$\displaystyle f \circ g $ & Composition of the functions $f$ and $g$ \\
  $\displaystyle f(\vx ; \vtheta) $ & A function of $\vx$ parametrized by $\vtheta$.
  (Sometimes we write $f(\vx)$ and omit the argument $\vtheta$ to lighten notation) \\
$\displaystyle \log x$ & Natural logarithm of $x$ \\
$\displaystyle \sigma(x)$ & Logistic sigmoid, $\displaystyle \frac{1} {1 + \exp(-x)}$ \\
$\displaystyle \zeta(x)$ & Softplus, $\log(1 + \exp(x))$ \\
$\displaystyle || \vx ||_p $ & $\normlp$ norm of $\vx$ \\
$\displaystyle || \vx || $ & $\normltwo$ norm of $\vx$ \\
$\displaystyle x^+$ & Positive part of $x$, i.e., $\max(0,x)$\\
$\displaystyle \1_\mathrm{condition}$ & is 1 if the condition is true, 0 otherwise\\
\end{tabular}
\egroup
\vspace{0.25cm}

\section{Final instructions}
Do not change any aspects of the formatting parameters in the style files.
In particular, do not modify the width or length of the rectangle the text
should fit into, and do not change font sizes (except perhaps in the
\textsc{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PostScript or PDF files}

Please prepare PostScript or PDF files with paper size ``US Letter'', and
not, for example, ``A4''. The -t
letter option on dvips will produce US Letter files.

Consider directly generating PDF files using \verb+pdflatex+
(especially if you are a MiKTeX user).
PDF figures must be substituted for EPS figures, however.

Otherwise, please generate your PostScript and PDF files with the following commands:
\begin{verbatim}
dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
ps2pdf mypaper.ps mypaper.pdf
\end{verbatim}

\subsection{Margins in LaTeX}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+
from the graphicx package. Always specify the figure width as a multiple of
the line width as in the example below using .eps graphics
\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.eps}
\end{verbatim}
or % Apr 2009 addition
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
for .pdf graphics.
See section~4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})

A number of width problems arise when LaTeX cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command.

\subsubsection*{Author Contributions}
If you'd like to, you may include  a section for author contributions as is done
in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Use unnumbered third level headings for the acknowledgments. All
acknowledgments, including those to funding agencies, go at the end of the paper.

\bibliography{iclr2025_conference}
\bibliographystyle{iclr2025_conference}

\appendix
\section{Appendix}
You may include other additional sections here.

\end{document}

### 2025-11-11 lipschitz 2025/Lipschitz_a_proposition.tex
create a new folder
rr

--- 2025-05-06 lipschitz/Lipschitz_a_proposition.tex
@@
 
-\begin{definition}
+	\begin{definition}[$\varepsilon$-diff bound]
 	Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
 
-	For a number $\epsilon > 0$, $K_\epsilon$ is the smallest number such that for any $d\geq \epsilon$, any input $x,y$.
-	\begin{align*}
-	 |x-y| \leq d \implies |f(x)-f(y)| \leq dK_\epsilon 
+	For a number $\varepsilon\in\mathbb{R}$, an $\varepsilon$-diff bound $D_\varepsilon$ is a number such that for any inputs $x,y$: \begin{align*}
+	|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D_\varepsilon \cdot \varepsilon
 \end{align*}
+
+	\end{definition}
+
+\begin{definition}[Lipschitz above $\varepsilon$ constant ]
+	Suppose we have a function $f$ from $\mathbb{R}^n$ to $\mathbb{R}^m$ and $||$ is the $L_\infty$ norm.
+
+	For a number $\varepsilon\in\mathbb{R}$, a Lipschitz above $\varepsilon$ constant  $K_\varepsilon$,  is a number such that for any inputs $x,y$: \begin{align*}
+	|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot |x-y|\\
+	|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq K_\varepsilon \cdot \varepsilon\\
+	\end{align*}
+
 \end{definition}
@@
 
-	Continue above definition.
-Suppose for a number $\epsilon$ we have $K_\epsilon$, then for any number $ \epsilon N\leq d\leq \epsilon(N+1)$ for an integer $N \geq 1$, we have that $$K_d \leq K_\epsilon\frac{N+1}{N}.$$
+	Suppose $D$ is an $\varepsilon$-diff bound for $f(x)$. Then for any $N\in\mathbb{Z}^+$, $D\frac{N+1}{N}$ is a Lipschitz about $N\varepsilon$ constant.
+
+	In formula, for any two inputs $x,y$, if \begin{align*}
+		|x-y|\leq \varepsilon \implies |f(x)-f(y)| \leq D \cdot \varepsilon,
+	\end{align*} then 	 \begin{align*}
+	|x-y|\geq N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
+	|x-y|<N\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot N\varepsilon\\
+	\end{align*}
+\end{proposition}
+
+\begin{proof} We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
+
+	The first case, $|x-y|\geq N\varepsilon$.
+Then we assume $|x-y| \in [M\varepsilon ,  (M+1)\varepsilon]$ for another integer $M\geq N$.
+Then we can divide the line segment between $x, y$ into $M+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{M+1} = y$ such that $|x_i-x_{i+1}| \leq \varepsilon$ and apply the definition of $\varepsilon$-diff bound $D$ for each pieces:\begin{align*}
+		|f(x)-f(y)| &= |f(x_{M+1})-f(x_M)+\cdots+f(x_1)-f(x_0)|\\
+		&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
+		&\leq D\varepsilon + \cdots +D\varepsilon \\
+		&= (M+1)D\varepsilon
+	\end{align*}
+	Hence\begin{align*}
+		|f(x)-f(y)| &\leq (M+1)D\varepsilon \\
+		&\leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
+		&= D\cdot\frac{M+1}{M} |x-y|\\
+		&\leq   D\cdot\frac{N+1}{N} |x-y|
+	\end{align*}
+	The second case, $|x-y|< N\varepsilon$.
+Similarly we can divide the line segment between $x, y$ into $N$ pieces and then $|f(x)-f(y)|\leq D N\varepsilon\leq |f(x)-f(y)|\leq D \frac{N+1}{N} N\varepsilon$.
+
+	This is what we want to show.
+\end{proof}
+
+\begin{proposition}
+For any $N\in\mathbb{Z}^+$, suppose for any $a$ in $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$, $D$ is an $a$-diff bound for $f(x)$.
+
+Then $D\frac{N+1}{N}$ is a Lipschitz about $\varepsilon$ constant:\begin{align*}
+	|x-y|\geq \varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot |x-y|\\
+	|x-y|<\varepsilon &\implies |f(x)-f(y)| \leq D\frac{N+1}{N} \cdot \varepsilon\\
+\end{align*}
 \end{proposition}
@@
 \begin{proof}
-By assumption, $d \in [\epsilon N  , \epsilon(N+1)]$ .
+We fix the number $N\in\mathbb{Z}^+$ and assume we have two inputs $x, y$.
 
-	For any $x, y$ that $|x-y| \leq d$, we have $|x-y| \leq \epsilon(N+1) $.
-Then we can divide the line segment between $x, y$ into $N+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{N+1} = y$ such that $|x_i-x_{i+1}| \leq \epsilon$.
-Then we can apply the definition of $K_\epsilon$ for each pieces.
+For the case that $|x-y|<\varepsilon$, this is trivial by definition.
 
-	Therefore, we have that, for any two inputs $x,y$:
-		\begin{align*}
-		|x-y| \leq d \implies |f(x)-f(y)| \leq  \epsilon(N+1) K_\epsilon
+For the case that $|x-y|\geq \varepsilon$, there exists a sum $x_1+x_2+\cdots+x_n$ by numbers from (allowing repetitions) $\{\frac{N}{N}\varepsilon,\frac{N+1}{N}\varepsilon,\cdots, \frac{2N-1}{N}\varepsilon\}$ such that \begin{align*}
+	 \varepsilon \leq x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon \leq |x-y| \leq x_1+x_2+\cdots+x_n
 	\end{align*}
+	By assumption, divide the line segment from $x$ to $y$ into pieces according to $x_1, x_2,\cdots,x_n$, then we will have $$|f(x)-f(y)|\leq Dx_1+Dx_2+\cdots+Dx_n.$$
 
-	Hence by the definition, we have that $$K_d <= \dfrac{\epsilon(N+1) K_\epsilon }{d}<=\dfrac{\epsilon(N+1)K_\epsilon}{\epsilon N} = K_\epsilon\frac{N+1}{N}.$$
-
-	This is what we want to show.
+	Hence,\begin{align*}
+		\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
+		& = D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon})\\
+		& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})\\
+		& = D \frac{N+1}{N} 
+	\end{align*}
 
@@
 
-\begin{corollary}
-	\begin{enumerate}
-		\item Continue the definition.
-Suppose for a number $\epsilon$ we have $K_\epsilon$, then for any number $d\geq \epsilon N$ for an integer $N \geq 1$, we have that $$K_d \leq K_\epsilon\frac{N+1}{N}.$$
-
-		\item 	If we care about $\epsilon$ and compute the Lipschitz constant of $0.5 \epsilon$ and get $K$, then we can use Lipschizt constant $\leq K\frac{2+1}{2}$ for general larger $\epsilon$.
-		\item 	Similarly, if we compute Lipschitz constant for any $\epsilon$ and get $K$, then we can use Lipschitz constant $K\frac{1+1}{1}$ for any larger $\epsilon$.
-	\end{enumerate}
-\end{corollary}
-
-\begin{proof}
-	All three are simply application of the proposition.
-\end{proof}
-
-\begin{proposition}
-
-\end{proposition}
-
 \end{document}

### 2025-11-11 CAV 2026/experiments.tex
Add CAV2026 folder
try
1000s
sentences

--- 2025-09-01 AAAI2026/experiments.tex
@@
 
+\subsection{Global Robustness Comparison vs Vhagar and ITNE}
+
+To be able to compare with Vhagar, we have to use Vhagar benchmarks: 
+perturbation they consider (here $L_\infty=0.05$) on their DNNs (here Conv1 for MNIST, FMNIST and CIFAR-10), for which the reduction rules of integer variables are implemented.
+We test with 1000s Time-Out, as well as one test with 14400s time out, showing that much longer time-out does not have a big impact on the result.
+
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{||c|c|c|c|c||}\hline\hline
+	Benchmark & model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
+	MNIST   & Vhagar &  & & 
+    \\
+	M-Conv1 & ITNE &  & & 
+	\\ 
+    TO=1000s & 2v &   & & 
+    \\\hline
+
+	FMNIST & Vhagar &  ? &  ? & ? 
+    \\
+	F-Conv1  & ITNE &  $29.17$ &  $22.55$ & $22.55$
+	\\ 
+    TO=1000s & 2v &  {\bf 23.08} &  $23.02$ &  $23.02$ 
+    \\\hline
+
+	FMNIST & Vhagar &  $37.01$ &  $22.06$ & $22.06$ 
+    \\
+	F-Conv1  & ITNE &  $29.17$ &  $22.55$ & $22.55$
+	\\ 
+    TO=14400s & 2v &    {\bf 22.84} &  $22.53$ &  $22.53$ 
+    \\\hline
+
+	CIFAR-10  & Vhagar &  & & 
+    \\
+	C-Conv1  & ITNE &  & & 
+	\\ 
+    TO=1000s & 2v &    & & 
+    \\\hline \hline
+
+     \end{tabular}
+	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation.}
+    \label{table.classical}
+\end{table}
+
 	\subsection{Experimental results for robustness (MNIST)}
@@
 		3v, $1000$ & $17.66$ & $.813$ & {\bf .518} \\\hline 
+		2v ITNE, $1000$ & $19.08$ & n/a & n/a \\\hline 
+		2v ITNE, $1000$ & $19.38$ & $.185$ & $.185$ \\\hline 
 	    2v, $1000$ & $16.49$ & n/a & n/a \\\hline\hline	 
@@
 3v, $1000$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
-2v, $1000$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline
+2v, $1000$ &  $1.182$ & $.084$& {\bf .084}  \\\hline
+ITNE, $1000$ &  $1.371$ & $.085$& {\bf .085}  \\\hline\hline
 
@@
 		3v, $200$&     .0414 &  .0254 &  .0166 &  1000 \\\hline
-		2v, $200$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline \hline
+		2v, $200$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline 
+		2v ITNE, $200$&  .0446  & .0227 &  .0221  &  1000 \\\hline\hline
 		%3v, $97 \times 3$&      ?? &  ?? &  ?? & 14440 \\\hline
@@
 		%2v, $97 \times 2$&     ?? &  ?? &   ?? & 14440 \\\hline
-		2v, $200$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline \hline
+		2v, $200$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline 
+		2v ITNE, $200$& .0424  &  .0237  & .0228   &  14400 \\\hline\hline
 		3v, $200$&     {\bf .0329} &  .0277 &  .0165 & 72000 \\\hline
-		2v, $200$&     .0337 &  .0245 &  {\bf .0245} & 72000 \\\hline\hline
+		2v, $200$&     .0337 &  .0245 &  {\bf .0245} & 72000 \\\hline
+		2v ITNE, $200$&  .04159 & .0241 &  .0228  &  72000 \\\hline\hline
 	\end{tabular}

### 2025-11-13 CAV 2026/experiments.tex
results
RESULTS + SPREAD

@@
 To be able to compare with Vhagar, we have to use Vhagar benchmarks: 
-perturbation they consider (here $L_\infty=0.05$) on their DNNs (here Conv1 for MNIST, FMNIST and CIFAR-10), for which the reduction rules of integer variables are implemented.
+perturbation they consider (here $L_\infty=0.05$) on their DNNs (here Conv1 for MNIST, FMNIST and CIFAR-10), for which the reduction rules of binary variables are implemented.
 We test with 1000s Time-Out, as well as one test with 14400s time out, showing that much longer time-out does not have a big impact on the result.
+
+The spread is the average over all cases of the relative distance between the bound to the highest worst-case for that case.
 
@@
 	\centering
-	\begin{tabular}{||c|c|c|c|c||}\hline\hline
-	Benchmark & model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
-	MNIST   & Vhagar &  & & 
+	\begin{tabular}{||c||c|c|c|c|c||}\hline\hline
+	Benchmark & model & Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ & $\%$ of spread $\downarrow$ \\\hline \hline
+	MNIST   & Vhagar & 20.51 & 9.20 & 9.20 & 118 $\%$
     \\
-	M-Conv1 & ITNE &  & & 
+	M-Conv1 & ITNE & 12.77 & 9.41 & 9.41 & 35 $\%$
 	\\ 
-    TO=1000s & 2v &   & & 
+    TO=1000s & "2v" & {\bf 11.59}  & 9.38 & 9.38 & {\bf 23 $\%$}
+    \\\hline \hline
+
+	FMNIST & Vhagar &  ? &  ? & ? & ?
+    \\
+	F-Conv1  & ITNE &  $27.57$ &  $22.12$ & $22.12$ & 23 $\%$
+	\\ 
+    TO=1000s & "2v" &  {\bf 23.67} &  $22.31$ &  $22.31$ & {\bf 6 $\%$}
     \\\hline
 
-	FMNIST & Vhagar &  ? &  ? & ? 
+	FMNIST & Vhagar &  $37.01$ &  $22.06$ & $22.06$ & 67 $\%$
     \\
-	F-Conv1  & ITNE &  $29.17$ &  $22.55$ & $22.55$
+	F-Conv1  & ITNE &  $24.56$ &  $22.20$ & $22.20$ & 10 $\%$
 	\\ 
-    TO=1000s & 2v &  {\bf 23.08} &  $23.02$ &  $23.02$ 
-    \\\hline
+    TO=14400s & "2v" &    {\bf 22.84} &  $22.53$ &  $22.53$ & {\bf 1 $\%$}
+    \\\hline \hline
 
-	FMNIST & Vhagar &  $37.01$ &  $22.06$ & $22.06$ 
+	CIFAR-10  & Vhagar & does & not & run & 
     \\
-	F-Conv1  & ITNE &  $29.17$ &  $22.55$ & $22.55$
+	C-Conv1  & ITNE &  & & &
 	\\ 
-    TO=14400s & 2v &    {\bf 22.84} &  $22.53$ &  $22.53$ 
-    \\\hline
-
-	CIFAR-10  & Vhagar &  & & 
-    \\
-	C-Conv1  & ITNE &  & & 
-	\\ 
-    TO=1000s & 2v &    & & 
+    TO=1000s & "2v" &    & & &
     \\\hline \hline

### 2025-11-15 CAV 2026/CAV2026_main.tex
abstract and title

@@
 
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
+%\usepackage{times}  % DO NOT CHANGE THIS
+%\usepackage{helvet}  % DO NOT CHANGE THIS
+%\usepackage{courier}  % DO NOT CHANGE THIS
+
 \usepackage[hyphens]{url}  % DO NOT CHANGE THIS
 \usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+
+%\urlstyle{rm} % DO NOT CHANGE THIS
+%\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+%\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+
+%\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
 \frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
+%\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
+%\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
 %
 % These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
+
 \usepackage{algorithm}
@@
 
-\title{Order reduction and MILP models for real-time DNN robustness certification.}
+\title{{\em Global} MILP models and PCA for \\ {\em real-time} DNN robustness certification}
 \date{}
@@
 
-\bibliographystyle{plain} 
+\bibliographystyle{splncs04}
 \bibliography{references}

### 2025-11-15 CAV 2026/abstract.tex
abstract and title

--- 2025-08-02 AAAI2026/abstract.tex
@@
 Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research into methods to verify their robustness.
-Most existing methods focus on local robustness, i.e., the model's behavior in the neighborhood of a specific input.
-While local robustness enables to evaluate how often non-robust images appear in a large dataset (e.g., by repeating the verification on 1000 pre-obtained images), it fails to provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream.
+Most existing methods focus on {\em local} robustness, i.e., the model's behavior in the neighborhood of a specific input.
+Local robustness does {\em not} provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream.
 Moreover, most verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.
 
-In this paper, we consider {\em global} robustness, that is, guarantees not restricted to a set of local images.
-We focus on deriving {\em bounds} on the variation of output values across different decision classes of a DNN under a given perturbation.
-This global verification problem is significantly more complex than local robustness, as the number of variables doubles (from the deviation image to the image and its deviation).
-Further, the values each neuron can take are no longer limited to a small neighborhood.
-To obtain usable bounds, we develop several novel  MILP models for global robustness, with different trade-offs.
-Last, we use order reduction techniques to reduce the space of inputs considered, avoiding unrealistic images, by using principal component analysis (PCA).
-This results into the {\em real-time} certification of the robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of $.5$, as well as for a surrogate computing the
-%latent
-plastic strain associated with a pipe deformation map.
+In this paper, we consider {\em global} robustness, which is significantly more complex than local robustness, as %the number of variables doubles (from the deviation image to the image and its deviation).
+Further,
+the values each neuron can take are no longer limited to a small neighborhood. 
+%, that is, guarantees not restricted to a set of local images. 
+We focus on deriving {\em bounds} on the variation of output values across different decision classes of a DNN, given $L_\infty$- {\em and} $L_1$-perturbations.
+To obtain usable bounds, we develop {\em global}  MILP models for global robustness, more efficient than the classical encoding and its variants.
+Last, we reduce the space dimension, focusing on realistic images, by using principal component analysis (PCA).
+These bounds ensure the {\em real-time} certification of robustness for $69\%$ (resp.
+$86\%$) of incoming images for an $L_1$-perturbation of $1$ (resp.
+$.5$), adding only $0.0005s$ of latency using a single CPU core.

### 2025-11-15 CAV 2026/abstract.tex
abstract

@@
-Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research into methods to verify their robustness.
-Most existing methods focus on {\em local} robustness, i.e., the model's behavior in the neighborhood of a specific input.
-Local robustness does {\em not} provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream.
-Moreover, most verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.
+Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research to verify their robustness. 
+Most existing methods focus on {\em offline local} robustness, i.e., the model's behavior in the neighborhood of specific inputs. Local robustness 
+%does {\em not} provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream. Moreover, most verification 
+techniques are impractical to guarantee robustness of {\em real-time} inputs
+on embedded systems, due to excessive latency and computational intensivity.
 
@@
 Last, we reduce the space dimension, focusing on realistic images, by using principal component analysis (PCA).
-These bounds ensure the {\em real-time} certification of robustness for $69\%$ (resp.
+These bounds enable the {\em real-time} certification of robustness for $69\%$ (resp.
 $86\%$) of incoming images for an $L_1$-perturbation of $1$ (resp.

### 2025-11-15 CAV 2026/experiments.tex
RESULTS
typo
mnist full
abstract

@@
 
-\subsection{Global Robustness Comparison vs Vhagar and ITNE}
+\subsection{Comparison with Vhagar and ITNE ($L_\infty$)}
 
@@
 
-The spread is the average over all cases of the relative distance between the bound to the highest worst-case for that case.
+The spread is the average over all cases of the relative distance between the bound and the highest worst-case found for that case.
 
@@
 
-	FMNIST & Vhagar &  ? &  ? & ? & ?
+	FMNIST & Vhagar &  $41.52$ & $21.23$ & $21.23$ & 93 $\%$ 
     \\
-	F-Conv1  & ITNE &  $27.57$ &  $22.12$ & $22.12$ & 23 $\%$
+	F-Conv1  & ITNE &  $27.57$ &  $22.12$ & $22.12$ & 24 $\%$
 	\\ 
@@
 
-	FMNIST & Vhagar &  $37.01$ &  $22.06$ & $22.06$ & 67 $\%$
+	FMNIST & Vhagar &  $37.26$ &  $22.00$ & $22.00$ & 72 $\%$
     \\
@@
 	\\ 
-    TO=14400s & "2v" &    {\bf 22.84} &  $22.53$ &  $22.53$ & {\bf 1 $\%$}
+    TO=14400s & "2v" &    {\bf 22.56} &  $22.32$ &  $22.32$ & {\bf 1 $\%$}
     \\\hline \hline

### 2025-11-15 CAV 2026/abstract.tex
intro and title

@@
-Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research to verify their robustness. 
-Most existing methods focus on {\em offline local} robustness, i.e., the model's behavior in the neighborhood of specific inputs. Local robustness 
+Deep neural networks (DNNs) are often brittle to small perturbations, which has led to extensive research to verify their robustness. 
+Most existing methods focus on {\em local} robustness, i.e., verification in the neighborhood of fixed specific inputs. Local robustness 
 %does {\em not} provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream. Moreover, most verification 
@@
 We focus on deriving {\em bounds} on the variation of output values across different decision classes of a DNN, given $L_\infty$- {\em and} $L_1$-perturbations.
-To obtain usable bounds, we develop {\em global}  MILP models for global robustness, more efficient than the classical encoding and its variants.
-Last, we reduce the space dimension, focusing on realistic images, by using principal component analysis (PCA).
+We develop a novel {\em diff}  MILP model, more efficient than the classical MILP encoding and its variants for global robustness.
+To obtain better bounds, we reduce the space dimension by using principal component analysis (PCA), focusing on {\em realistic} inputs.
 These bounds enable the {\em real-time} certification of robustness for $69\%$ (resp.
 $86\%$) of incoming images for an $L_1$-perturbation of $1$ (resp.
-$.5$), adding only $0.0005s$ of latency using a single CPU core.
+$.5$), adding only $0.0005s$ of latency using only a single CPU core.

### 2025-11-15 CAV 2026/introduction.tex
intro and title

@@
 This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools.
-Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT \cite{pyrat} MnBAB \cite{ferrari2022complete}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
+Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, and PyRAT \cite{pyrat} MnBAB \cite{ferrari2022complete}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and $\alpha,\beta$-CROWN \cite{crown,xu2020fast},
+%the winner of the last 4 VNNcomp, benefiting from 
+based on branch-and-bound based methodology \cite{cutting,BaB}.
 
-The benchmarks usually focus on {\em local} robustness, i.e.
+These tools %benchmarks usually 
+focus on {\em local} robustness, i.e.
 given a DNN, an image and a small neighborhood around this image, is it the case that all the images in the neighborhood are classified in the same way by the DNN?
 The neighborhood is provided by a maximal perturbation of the input image, often an
-$L_\infty$-perturbation, i.e.
-every subpixel of the input image can vary in a very small range, typically $\frac{2}{255}$ (that is 2 levels of grey/blue/right/green), as $L_\infty$ is perfectly linear and perturbations of subpixels are independent.
-While the $L_\infty$-norm is the easiest to handle, it is not necessarily the most meaningful perturbation.
-More importantly, verification tools for local robustness are too computationally-intensive to be used in a real-time decision making pipeline: considering an autonomous car with a video feed from the dashboard,
-images of the feed cannot be certified robust in few ms to e.g. skip non-robust images and only consider certified robust images for the decision-making process.
+$L_\infty$-perturbation, i.e. every subpixel of the input image can vary in a very small range, typically $\frac{2}{255}$ (that is 2 levels of grey/blue/right/green). 
+Although it is not necessarily the most meaningful perturbation,
+$L_\infty$ is the usual choice because it is perfectly linear and specifies 
+subpixel perturbations independantly, which is easier to verify. 
+Importantly, these verification tools for local robustness are too computationally-intensive to be used in a real-time decision making pipeline: considering an autonomous car with a video feed from the dashboard,
+images of the feed cannot be certified robust in few ms on embedded hardware to e.g. skip non-robust images and only consider certified robust images.
+% for the decision-making process.
 
@@
 
-In this paper, we consider {\em global} robustness, that is we do not restrict the certification process to the neighborhood of an input. We follow a two steps procedure. 
+In this paper, we consider {\em global} robustness, that is we do not restrict the certification process to the neighborhood of a fix input. We follow a two steps procedure. 
 The first step, performed offline once, computes global bounds on the shift between 
-output values of different decision classes due to the perturbation, as proposed in \cite{vhagar}. 
-That is, considering decision classes $C$ and $D$ and perturbation $\varepsilon$, compute 
+output values of different decision classes due to the perturbation, close to \cite{vhagar}. That is, considering decision classes $C$ and $D$ and perturbation $\varepsilon$, compute 
 {\em global bound} $\beta^\varepsilon_{C,D} \geq \max_{I,I', |I-I'| \leq \epsilon}(value_{I}(C) - value_{I}(D) + value_{I'}(D) - value_{I'}(C))$, where $value_{J}(X)$ is the output value of class $X \in \{C,D\}$ for input image $J \in \{I,I'\}$.
@@
 Bound $\beta^\varepsilon_{C,D}$ needs to be computed once for a DNN, 
-and it is valid over the whole input space; compared with $k$ computations for {\em local robustness}, once for each of the $k$ input images, with results only valid for these $k$ images.
+and it is valid over the whole input space; compared with $k$ calls to 
+{\em local} robustness, once for each of the $k$ input images, with results only valid for these $k$ images.
 
@@
 If this is the case, then we are certified that image $I$ is robust for perturbation $\varepsilon$, because $\varepsilon$-perturbed image $I'$ could at most get  $value_{I'}(D) \leq \beta^\varepsilon_{C,D}  - (value_{I}(C) - value_{I}(D))  + value_{I'}(C) < value_{I'}(C)$, hence $C$ is also the predicted class for image $I'$.
-Otherwise, one could either skip image $I$ (in a video feed), or use safer degraded mode in the decision making process till a trustable robust image is received.
+This typically needs a couple of tens CPU instructions, which can be performed under 1ms (mili-second) on a single CPU core.
+If the image is not certified robust, one could either skip image $I$ (in a video feed), or use safer degraded mode in the decision making process till a trustable robust image is received.
 
 Our main contributions address the challenges to compute the {\em global bounds} $\beta^\varepsilon_{C,D}$, for $C,D$ output neurons:
+% for standard ReLU DNNs (e.g. \cite{vhagar}). Our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}:
+%, with updated MILP models e.g. for maxpool:
 \begin{enumerate}
@@
 
-	\item We develop a novel exact MILP encoding for the global robustness problem,
-	called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}).
-We study and encode exactly in MILP how the {\em diff variables} evolve after passing through a ReLU (Prop.~\ref{Prop2}).
-Compared with the
-	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz,ITNE},
-	the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other.
+	\item We develop a novel {\em diff MILP encoding} for the global robustness problem, %called the {\em "2v" model}, 
+	where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}, introduced in \cite{diff}).
+We study and encode how the {\em diff variables} evolve after passing through a ReLU (Prop.~\ref{Prop2}).
+Compared with the {\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz,ITNE}, which considers the input and the perturbation but not their difference ({\em diff variable}), we keep the same number of 2 binary variables per ReLU.
+Experimentally however,
+	%the results are more accurate for the same runtime.
+	%the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other.
 This was observed in \cite{lipshitz,ITNE}, and constraints encoding
-	a part of the linear relaxation of our "2v" model were added explicitly. Experimentally, 
-	our "2v" model provides more accurate bounds than competing models, in the same runtime
+	%a part of the linear relaxation of our "2v" model were added explicitly. 
+	%Experimentally, 
+	our {\em diff MILP model} provides more accurate bounds at a given runtime
 	(Table \ref{table.classical}).
@@
 Instead, we develop another exact MILP model,
-	Further, we develop two abstract MILP models, namely the "3v" model which decouples the 
-	{\em non-diff binary variables} of the "2v" model, resulting in looser bounds but with lower runtimes, as well as a computationally efficient "1v" model that only considers the 
-	{\em diff variables}, however resulting in much looser bounds.
+	\item Further from the {\em diff MILP model}, which is exact, 
+	we develop two abstract MILP models, which are more efficient but also possibly less accurate.
+	Namely, the "1b+2" model replaces the 2 binary variables by 1 binary (for the diff variable) and 2 linear variables (linear relaxation for the perturbation); while the "1b" model has a unique binary variable per ReLU, only considering the {\em diff variables}.
 	%\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation.
@@
    \item  In terms of perturbations, we consider conjunctions of $L_\infty$- and $L_1$-norms, which allow to accurately describe perturbations.
-For instance, "each subpixel is perturbed by at most $\frac{20}{255}$ ($L_\infty$) and the sum of the absolute value of perturbations over all subpixels is at most $\frac{150}{255}$" ($L_1$-perturbation).
+For instance, "each subpixel is perturbed by at most $\frac{50}{255}$ ($L_\infty$) and the sum of the absolute value of perturbations over all subpixels is at most $1$" ($L_1$-perturbation).
 While $L_1$-perturbations are not linear (because of the absolute values), reason for which it is seldom used, Prop.~\ref{prop.l1} shows how to use it as a perturbation in the MILP model without incurring any expansive binary variables (only cheap linear variables are necessary).
+Check \cite{L1paper-by-AI} ??
 
-	\item Results obtained on the full input space have several shortcomings: while the bounds are fully correct, they are also particularly pessimistic, as all inputs, including absolutely improbable ones very far away from anything the network has been trained on, need to be accounted for.
-Also, the runtime to obtain the bound is particularly long.
+	\item Bounds obtained on the full input space are particularly pessimistic, as all inputs, including improbable ones far away from the training dataset, called (Out of Distribution) {\em OOD inputs} \cite{OOD}), need to be accounted for.
+	%As a result, the runtime to obtain the bound is particularly long. 
 	%Finally, when computing worst-case 
 	%pairs (image, perturbation), improbable images are generated, hence these  are not meaningful. 
-	To solve this problem, we restrict the input space to ignore improbable inputs, using model order reduction techniques from engineering science \cite{Paco}.
-Specifically, we use Principal Component Analysis (PCA) to reduce the space
-	to a linear input space. We choose the number of dimensions of the space to equal the accuracy of the DNN on the reduced space. 
+	To address that, we consider model order reduction techniques from engineering science \cite{Paco}. Specifically, we use Principal Component Analysis (PCA) to represent faithfully realistic inputs.
+	OOD	inputs may be represented unfaithfully - but the DNN is unlikely to provide reasonable answer on such inputs anyway.
+	%	focus on reduce the space to a linear input space. We choose the number of dimensions of the space to equal the accuracy of the DNN on the reduced space. 
 	%(using a projection to the reduced space then the inverse projection to obtain a very similar image understandable by the DNN). 
-	On the MNIST benchmark, this means 20 linear dimensions to match the $97\%$ accuracy of the DNN we considered, instead of the 784 dimensions of the full image space.
-Using PCA, which is linear, makes it easy to specify perturbations on the actual image (where it is meaningful) rather than on the reduced space.
+	For instance, using just $20$ out of 784 dimensions suffices to represent faithfully MNIST inputs, without losing accuracy for the DNN on MNIST inputs.
+	%On the MNIST benchmark, this means 20 linear dimensions to match the $97\%$ accuracy of the DNN we considered, instead of the 784 dimensions of the full image space. 
+	%Using PCA, which is linear, makes it easy to specify perturbations on the actual image (where it is meaningful) rather than on the reduced space.
 
-\item Experimentally, this allows to obtain bounds for a considered pre-trained DNN for MNIST (with accuracy $97\%$) that can certify in {\em real-time} that $86\%$ of the images are robust for an $L_1$-perturbation of $.5$, resp.
-$53\%$ for an
-$L_1$-perturbation of $1$.
-We finally experimented our MILP models for a {\em regression} task as well, considering a DNN surrogate built from a slow physical finite element model, providing the deformation and the plastic strain of a pipe \cite{aiware}.
-The DNN has been learnt on a already reduced basis of dimension 10, from thousands of input dimensions.
-The aim is to understand if the DNN surrogate that has been learnt is brittle to small perturbations, which could make it unfaithful to the physical model.
-Here we want to obtain bounds (which is what our models provide), as well as generating worst-case (image,perturbation) pair, where the strain is particularly different, close to the bound, and that can be run in the physical model to understand whether the DNN surrogate is faithful.
-Our tool was helpful to provide limited bounds, as well as an almost matching worst-case (image,perturbation) pair that was confirmed in the physical model.
-Overall, the "2v" model generates accurate bounds.
-The decoupling of variables generating the "3v" model offers good trade-offs, reaching slightly better bounds in the same runtime.
-The "1v" model converges faster  but bounds are looser, a good trade-off when runtime is limited or problem is complex (Tables \ref{table.mnist},\ref{table.pipe}).
+\item Experimentally, the exact {\em diff MILP model} computes bounds 
+$\beta_{C,D}$ which are 1 order of magnitude better than with the classical MILP encoding, and much closer (Table \ref{table.classical}) to the lower bound than with variants of the classical encoding; namely Vhagar \cite{vhagar} which reduces the number of binary variables in a complete fashion; and ITNE \cite{ITNE} which adds linear relaxation for the diff variables.
+Our "1b+2" variant offers good trade-offs, reaching better bounds in the same runtime as the diff MILP model.
+The "1b" model converges faster but bounds are looser, interesting when runtime is very limited or problem is very complex (Tables \ref{table.mnist},\ref{table.pipe}).
+Overall, the "1b+2" model obtains bounds $\beta_{C,D}$ which enables the robustness certification of $69\%$ of MNIST images for an $L_1$-perturbation of $1$, resp.
+$89\%$ for $.5$.
+The online process adds only
+0.0005s of latency per image, and 2000 images/second can be treated per CPU core.
 \end{enumerate}
-
-Limitation: We consider the standard ReLU activation function, though our findings can be extended to other activation functions, following similar extention by \cite{DivideAndSlide}, with updated MILP models e.g.
-for maxpool.
 

### 2025-11-15 CAV 2026/introduction.tex
INTRO

@@
 Compared with the {\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz,ITNE}, which considers the input and the perturbation but not their difference ({\em diff variable}), we keep the same number of 2 binary variables per ReLU.
-Experimentally however,
 	%the results are more accurate for the same runtime.
@@
 	%Experimentally, 
-	our {\em diff MILP model} provides more accurate bounds at a given runtime
-	(Table \ref{table.classical}).
+	However, our {\em diff MILP model} is more efficient, one reason being 
+	the accuracy of its linear relaxation.
 	%The number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed.
@@
 
-\item Experimentally, the exact {\em diff MILP model} computes bounds 
-$\beta_{C,D}$ which are 1 order of magnitude better than with the classical MILP encoding, and much closer (Table \ref{table.classical}) to the lower bound than with variants of the classical encoding; namely Vhagar \cite{vhagar} which reduces the number of binary variables in a complete fashion; and ITNE \cite{ITNE} which adds linear relaxation for the diff variables.
+\item Experimentally, the exact {\em diff MILP model} computes upper bounds 
+which are 1 order of magnitude better than with the classical MILP encoding, and much closer (Table \ref{table.classical}) to the lower bounds than with variants of the classical encoding; namely reducing the number of binary variables in a complete fashion (Vhagar \cite{vhagar}); or adding linear relaxation for the diff variables (ITNE \cite{ITNE}).
 Our "1b+2" variant offers good trade-offs, reaching better bounds in the same runtime as the diff MILP model.
 The "1b" model converges faster but bounds are looser, interesting when runtime is very limited or problem is very complex (Tables \ref{table.mnist},\ref{table.pipe}).
-Overall, the "1b+2" model obtains bounds $\beta_{C,D}$ which enables the robustness certification of $69\%$ of MNIST images for an $L_1$-perturbation of $1$, resp.
+Further, using PCA reduces $\beta_{C,D}$ by up to an order of magnitude.
+Overall, the "1b+2" model using PCA enables the robustness certification of $69\%$ of MNIST images for an $L_1$-perturbation of $1$, resp.
 $89\%$ for $.5$.
-The online process adds only
-0.0005s of latency per image, and 2000 images/second can be treated per CPU core.
+The online process adds only 0.0005s of latency per image, and 2000 images/second can be treated per CPU core.
 \end{enumerate}

### 2025-11-20 CAV 2026/global.tex
exp + global

@@
 	\section{MILP Models for global robustness}
+
+	\subsection{Optimization objective for real-time verification}
+
+As explained in the introduction, the objective we want to maximize is 
+$\beta^{\text{perturb}}_{C,D} = x_C - x_D +x'_D - x'_C$, 
+for $x_C,x_D$ the value associated with the output neurons $C,D$ from input image $I$, and $x'_C,x'_D$ from perturbation $I'$. These bounds 
+$\beta^{\text{perturb}}_{C,D}$ will allow us to verify in real-time 
+whether a new incoming image can be certified to be robust for the perturbation.
+
+Different bounds were proposed in \cite{vhagar}, for an evaluation purpose rather than to verify images in real-time.
+
+TODO: DEF OF BOUNDS IN VHAGAR. CALL BOUNDS $\alpha_C,D$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$.
+Notice that $\alpha_C,D$ is not symetrical, while 
+$\beta^{\text{perturb}}_{C,D}$ is.
 
@@
 
-    To encode global robustness, \cite{vhagar} considers
-	variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ 
-	and of its perturbation $I'$, 
-	using the classical encoding (\ref{eq11}) \cite{MILP} 
-	to compute $\hat{x}_i, \hat{x}'_i$ from $x_i, x'_i$
-	for each $i$.
-    Further:
+    To encode global robustness in MILP, the classical way, used (with variants) by \cite{vhagar,ITNE}, is to consider variables $x_j,\hat{x}_j$ and 
+	$x'_j,\hat{x}'_j$, encoding the value of neuron $j$ obtained from the image $I$ and from its perturbation $I'$, respectively. Further:
 	\begin{enumerate}
-		\item For each input nodes $x_j,x'_j$ of $I,I'$, add constraints
-        $|x_j-x'_j| \leq \varepsilon$ 
-        ($L_\infty$-perturbation - see later for $L_1$).
-		\item The optimization objective is to maximize $x_C - x_D +x'_D - x'_C$ 
-		to compute $\beta^\varepsilon_{C,D}=\beta^\varepsilon_{D,C}$, 
-		for $C \neq D$  decision classes, as proposed in \cite{vhagar}.
+		\item For each input neuron $j,j$ of $I,I'$, there is constraint
+        $|x_j-x'_j| \leq \varepsilon$ to encode the $L_\infty$-perturbation 
+		(see later how we encode $L_1$ perturbations).
+		\item For each neuron $j$, we have the Re ReLU constraints 
+		from the classical encoding (\ref{eq11}) \cite{MILP}
+		for both $\hat{x}_j$ and $\hat{x'}_j$ independently.
 	\end{enumerate}

### 2025-11-20 CAV 2026/introduction.tex
exp + global

@@
 	we develop two abstract MILP models, which are more efficient but also possibly less accurate.
-	Namely, the "1b+2" model replaces the 2 binary variables by 1 binary (for the diff variable) and 2 linear variables (linear relaxation for the perturbation); while the "1b" model has a unique binary variable per ReLU, only considering the {\em diff variables}.
+Namely, the "2b+1" model, decoupling one binary variable into 2 variables: 1 binary and the other using linear relaxation; while the "1b" model has a unique binary variable per ReLU, only considering the {\em diff variables}.
 	%\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation.

### 2025-12-03 CAV 2026/experiments.tex
exp + global
new table
something
update the table
updated the table
fixed table

@@
 
-The spread is the average over all cases of the relative distance between the bound and the highest worst-case found for that case.
+The gap is the average over all cases of the relative distance between the bound and the highest worst-case found for that case.
+
+\iffalse
 
@@
 	\begin{tabular}{||c||c|c|c|c|c||}\hline\hline
-	Benchmark & model & Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ & $\%$ of spread $\downarrow$ \\\hline \hline
+	Benchmark & model & Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ & $\%$ of gap $\downarrow$ \\\hline \hline
 	MNIST   & Vhagar & 20.51 & 9.20 & 9.20 & 118 $\%$
@@
 	\\ 
-    TO=1000s & "2v" & {\bf 11.59}  & 9.38 & 9.38 & {\bf 23 $\%$}
+    TO=1000s & {\em Diff} & {\bf 11.59}  & 9.38 & 9.38 & {\bf 23 $\%$}
     \\\hline \hline
@@
 	\\ 
-    TO=1000s & "2v" &  {\bf 23.67} &  $22.31$ &  $22.31$ & {\bf 6 $\%$}
+    TO=1000s & {\em Diff} &  {\bf 23.67} &  $22.31$ &  $22.31$ & {\bf 6 $\%$}
     \\\hline
@@
 	\\ 
-    TO=14400s & "2v" &    {\bf 22.56} &  $22.32$ &  $22.32$ & {\bf 1 $\%$}
+    TO=14400s & {\em Diff} &    {\bf 22.56} &  $22.32$ &  $22.32$ & {\bf 1 $\%$}
     \\\hline \hline
 
-	CIFAR-10  & Vhagar & does & not & run & 
+	CIFAR-10  & Vhagar & does & not & run & -
+    \\
+	C-Conv1  & ITNE & 28.61 & 11.58 & 11.58 & $33\%$
+	\\ 
+    TO=1000s & {\em Diff} &  25.93  & 14.43 & 14.43 & $24\%$
+	\\
+	& {\em 2b+1} &  25.31 & 19.77 & - & $23\%$
+	\\
+	& Best &  {\bf 23.44}  &  &  & {\bf 16} $\%$
+    \\\hline
+
+	CIFAR-10  & Vhagar & does & not & run & -
     \\
@@
 	\\ 
-    TO=1000s & "2v" &    & & &
+    TO=14400s & {\em Diff} &  {\bf 20.67}  & 19.03 & 19.03 & {\bf 6} $\%$
+	\\
+	 & {\em 2b+1} &  {\bf }  &  &  & $\%$
     \\\hline \hline
@@
 	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation.}
+    \label{table.classical}
+\end{table}
+
+\fi
+
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{||c||c|c|c||c|c||c|}\hline\hline
+	Benchmark & MILP model: & Vhagar &  ITNE & {\em Diff} & {\em 2b+1} & {\em Best} \\\hline \hline
+	MNIST-C1  & Bound $\downarrow$ &  20.80 & 12.32 & {11.14} & {\bf 10.95} & 10.85
+    \\
+	TO=1000s & $\%$ of gap $\downarrow$ & 120$\%$ & 29 $\%$ & {17} $\%$ & {\bf 15} $\%$& 14 $\%$
+	\\ \hline
+	TO=14400s  & Bound $\downarrow$ & 17.54 & 11.15 & {\bf 10.14} & 10.29 & 10.07
+    \\
+	 & $\%$ of gap $\downarrow$ &  84$\%$ & 17 $\%$ & {\bf 7} $\%$ & 8 $\%$ & 6 $\%$
+
+    \\\hline \hline
+
+	FMNIST-C1 & Bound $\downarrow$ & 41.52 & 26.61 & {\bf 23.27}  & 24.09 & 22.78
+    \\
+	TO=1000s & $\%$ of gap $\downarrow$ & 93 $\%$ & 20 $\%$ & {\bf 5} $\%$ & 10 $\%$ & 3 $\%$
+    \\\hline
+
+	TO=14400s & Bound $\downarrow$ & 37.26 & 24.06 & {\bf 22.42 } & 23.80 & 22.34
+    \\
+	 & $\%$ of gap $\downarrow$ & 72 $\%$ &  9 $\%$ & {\bf 1} $\%$ & 9 $\%$ & 0.6 $\%$
+    \\\hline \hline
+
+	CIFAR-C1  & Bound $\downarrow$ & ? & 27.15 & 25.94 & {\bf 24.52}& 23.29
+    \\
+	TO=1000s & $\%$ of gap $\downarrow$ & ? & 28 $\%$ & 24 $\%$& 
+	{\bf 20} $\%$ & 15 $\%$
+	\\\hline
+
+	TO=14400s  & Bound $\downarrow$ & ? & 22.73 & {\bf 21.77} & 21.81 & 20.38
+    \\
+	 & $\%$ of gap $\downarrow$ & ? & 12 $\%$ & {\bf 10} $\%$& {\bf 10} $\%$& 5$\%$
+		\\\hline \hline
+
+     \end{tabular}
+	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation, average over all bounds $\beta_{i,j}$.
+{\em Best} uses the best between our {\em Diff} and our {\em 2b+1} for each $i,j$.
+Lower gaps using {\em Best} means that there are cases where {\em Diff} is much better than {\em 2b+1}, and cases where it is the opposite.}
     \label{table.classical}

### 2025-12-04 CAV 2026/global.tex
global

@@
 
-As explained in the introduction, the objective we want to maximize is 
-$\beta^{\text{perturb}}_{C,D} = x_C - x_D +x'_D - x'_C$, 
-for $x_C,x_D$ the value associated with the output neurons $C,D$ from input image $I$, and $x'_C,x'_D$ from perturbation $I'$. These bounds 
-$\beta^{\text{perturb}}_{C,D}$ will allow us to verify in real-time 
-whether a new incoming image can be certified to be robust for the perturbation.
+As explained in the introduction, the objective we want to approximate is 
+$\beta^{\text{perturb}}_{C,D} = \max_{|I-I'| \leq \text{perturb}}(x_C - x_D +x'_D - x'_C)$, for $x_C,x_D$ the value associated with output neurons $C,D$ from any input image $I$, and $x'_C,x'_D$ from its perturbed image $I'$.
+Upper bounds  $\bar{\beta}^{\text{perturb}}_{C,D} \geq \beta^{\text{perturb}}_{C,D}$ will allow us to verify in real-time whether a new incoming image can be certified to be robust for the perturbation.
+Lower bounds
+$\underline{\beta}^{\text{perturb}}_{C,D} \leq \beta^{\text{perturb}}_{C,D}$
+will allow us to evaluate how large is the gap 
+$(\bar{\beta}^{\text{perturb}}_{C,D} - \underline{\beta}^{\text{perturb}}_{C,D}) / \underline{\beta}^{\text{perturb}}_{C,D}$.
+MILP solvers, e.g.
+Gurobi, provide both an upper bound ("bound") $\bar{\beta}^{\text{perturb}}_{C,D}$
+as well as a lower bound ("solution") $\underline{\beta}^{\text{perturb}}_{C,D}$.
 
-Different bounds were proposed in \cite{vhagar}, for an evaluation purpose rather than to verify images in real-time.
+Different bounds were proposed in \cite{vhagar}, for an evaluation purpose (how narrow is the gap between the upper and lower bound) rather than to verify images in real-time.
 
-TODO: DEF OF BOUNDS IN VHAGAR. CALL BOUNDS $\alpha_C,D$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$.
-Notice that $\alpha_C,D$ is not symetrical, while 
+TODO: DEF OF BOUNDS IN VHAGAR. CALL BOUNDS 
+$\alpha^{\text{perturb}}_{C,D}$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$.
+Notice that $\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 
 $\beta^{\text{perturb}}_{C,D}$ is.

### 2025-12-04 CAV 2026/global.tex
update the definition

@@
 
-TODO: DEF OF BOUNDS IN VHAGAR. CALL BOUNDS 
-$\alpha^{\text{perturb}}_{C,D}$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$.
+The bounds in Vhagar, 
+$\alpha^{\text{perturb}}_{C,D}$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$. The formal definition, \begin{align*}
+	\alpha^{\text{perturb}}_{C,D} &= \max_{|I-I'| \leq \text{perturb}} (x_C-\max_{E\neq C}x_E) \\
+	&\text{s.t. }  (x'_D-\max_{E\neq D}x'_E)\geq 0
+\end{align*}
 Notice that $\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 

### 2025-12-08 CAV 2026/global.tex
one line
alpha

--- 2025-12-04 CAV 2026/global.tex
@@
 Different bounds were proposed in \cite{vhagar}, for an evaluation purpose (how narrow is the gap between the upper and lower bound) rather than to verify images in real-time.
+Namely, Vhagar defines $\alpha^{\text{perturb}}_{C,D}$, computing the perturbation necessary to switch an image classified as $C$ into an image classified as $D$:
+\begin{align*}
+	\alpha^{\text{perturb}}_{C,D} &= \max_{|I-I'| \leq \text{perturb}} (x_C-\max_{E\neq C}x_E) &\text{s.t. }  x'_D \geq \max_{E\neq D}x'_E \wedge x_C \geq \max_{E\neq C}x_E 
+\end{align*}
 
-TODO: DEF OF BOUNDS IN VHAGAR. CALL BOUNDS 
-$\alpha^{\text{perturb}}_{C,D}$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$.
-Notice that $\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 
+Notice that  
+$\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 
 $\beta^{\text{perturb}}_{C,D}$ is.

### 2025-12-11 CAV 2026/CAV2026B/CAV2026_a_proof.tex
add the proof tex

\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}

\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\usepackage{algorithm}
\usepackage{algorithmic}
\pagestyle{plain}
\usepackage{threeparttable}
\input{math_commands.tex}
\usepackage{lineno}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{cases}
\captionsetup{compatibility=false}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{calc}
\usepackage{array}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}
\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%\newtheorem{proposition}{Proposition}
%\newtheorem{definition}{Definition}
\newcommand{\vW}{\boldsymbol{W}}
\newcommand{\val}{{\textrm{value}}}
\newcommand{\Val}{{\textrm{value}}}
\newcommand{\MILP}{{\textrm{MILP}}}
\newcommand{\LP}{{\textrm{LP}}}
\newcommand{\Improve}{\mathrm{Improve}}
\newcommand{\Utility}{\mathrm{SAS}}
\newcommand{\Sol}{\mathrm{Sol}}
\newcommand{\sol}{\mathrm{sol}}
\newcommand{\UB}{\mathrm{UB}}
\newcommand{\LB}{\mathrm{LB}}
\newcommand{\ub}{\mathrm{ub}}
\newcommand{\lb}{\mathrm{lb}}
\newcommand{\B}{\mathrm{B}}
\usepackage{amsmath, amssymb, amsfonts}
\newcommand{\ReLU}{\mathrm{ReLU}}
\newcommand{\CMP}{{\textrm{CMP}}\ }
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\toolname}{Hybrid MILP}

\usepackage{bibentry}

\begin{document}

	\begin{definition}
		A system $S$ is a 5-tuple $(X,C,succ, U, I)$ that \begin{itemize}
			\item $X\subseteq \mathbb{R}^n$ is the full space;
			\item The control set $C$ is a set and the successor $succ$ is a function from $X\times C$ to $2^X$;
			\item $U\subseteq X$ is the unsafe region, and nonempty set $I\subseteq X$ disjoint from $U$;
		\end{itemize}

		The system of $S$ under perturbation of at most $\delta$, $S_\delta$, is a system with the same $(X,U,C,I)$ but a $succ_\delta$ function defined as follows: \begin{align*}
		succ_\delta(x,c) &= B_\delta(succ(x,c))\\
		&= \{z:\exists y\in succ(x,c)\ \ d(y,z)<\delta\}.
		\end{align*} Here $d$ can be an arbitrary kind of distance ($L_2, L_\infty$ and so on).
	\end{definition}

	Definition of policy:

	\begin{definition} 
		 \begin{itemize}
			\item For a system $S = (X,C,succ, U, I)$, a policy $p$ is a function $p: X\rightarrow C$ and the function $succ_p: X\rightarrow 2^X$ is defined by $succ_p(x) = succ(x,p(x))$.
			\item A policy $p$ is piecewise continuous (piecewise Lipschitz continuous) DT if there exists a decision tree (DT) $\mathcal{T}$ that defines $p$, i.e., each leaf $i$ of $\mathcal{T}$ is assigned a continuous (Lipschitz continuous) function $f_i(x)$ defined on $X$, and $p$ is defined by
			\[
			p(x) = f_i(x) \quad \text{if } \mathcal{T}(x)=i.
			\]
		\end{itemize}
	\end{definition}

Now we define the reachable set $R$ and $R_\delta$.

\begin{definition}
	For a system $S=(X,C,succ, U, I)$ with policy $p$, the reachable set $R(I)$ is the union of all sequence $\{x_n:n\in\mathbb{N}\}$ that is a run by $S$ and $p$, i.e., $\{x_n:n\in\mathbb{N}\}$ satisfies \begin{align*}
		x_0&\in I\\
		x_{n+1} &\in succ_p(x_n), n\in\mathbb{N}
	\end{align*}

	And the reachable set under perturbation of at most $\delta$ is the union of all sequence $\{x_n:n\in\mathbb{N}\}$ that is a run by $S_\delta$ and $p$, i.e., $\{x_n:n\in\mathbb{N}\}$ satisfies \begin{align*}
		x_0&\in I\\
		x_{n+1} &\in B_\delta(succ_p(x_n)), n\in\mathbb{N}
	\end{align*}
\end{definition}

Next we define safety.

\begin{definition}
	For a system $S=(X,C,succ, U, I)$, a policy $p$ is safe if $R(I)$ is disjoint from $U$. A policy $p$ is robustly safe if for some $\delta$, $R_\delta(I)$ is disjoint from $U$.
\end{definition}

Next we define certificate.

\begin{definition}
	For a system $S$ and policy $p$, a certificate is a function $f : A \rightarrow \{0,1\}$ such that:
	\begin{itemize}
		\item $f^{-1}(1)\supseteq I$, $f^{-1}(1)\cap U = \emptyset$.

		\item For any $x$ and $x'$ such that $f(x)=1$, we have $x' \in succ_p(x)$ $f(x')=1$.
	\end{itemize}

A certificate $f$ is DT if there exists a decision tree (DT) $\mathcal{T}$ that defines $f$, i.e., each leaf $i$ of $\mathcal{T}$ is assigned a number $a_i \in \{0,1\}$, and $f$ is defined by
\[
f(x) = a_i \quad \text{if } \mathcal{T}(x)=i.
\]

\end{definition}

\begin{theorem}
	If a piecewise Lipschitz continuous DT policy $p$ is robustly safe, then
	there exists a DT certificate for safety. 
\end{theorem}

From now, we fix a system $S$ and assume $p$ is a piecewise Lipschitz continuous DT policy which is robustly safe for $\delta>0$.

The proof is in three steps: \begin{itemize}
	\item First, we will show, $R(I)$ has an open neighborhood contained in $R_\delta(I)$ and hence disjoint with $U$.

	\item Second, we will show $R(I)$ is attractive in a neighborhood. 
\end{itemize}

\begin{lemma}
	$B_\delta(R(I))\subseteq R_\delta(I)$.
\end{lemma}

\begin{proof}
	Trivial.
\end{proof}

\begin{lemma}
	There exists a polytopes decompose of $X=\bigcup_{Q_i\in \mathcal{Q}} Q_i$ (they may include or exclude their boundaries) and Lipschitz continuous functions $f_i$ assigned for each polytopes that can define $p$:\begin{align*}
		p(x) = f_i(x)\quad \text{if }x\in Q_i
	\end{align*}
\end{lemma}

\begin{proof}
	This is because $p$ is a piecewise  Lipschitz continuous DT policy.
\end{proof}

\begin{lemma}
	For each $Q_i$, there exists $\varepsilon >0$ such that $R(I)\cap Q_i$ is attractive in the region $B_\varepsilon(R(I)\cap Q_i)\cap Q_i$.
\end{lemma}

\begin{proof}
	In this proof, we use $R_i$ to denote $R(I)\cap Q_i$.
\end{proof}

%\begin{lemma}
%	Let $S$ be a system with policy $p$ and initial region $I$. For any $x\in R_r(I)$ and any $\varepsilon$, we have
%	\[
%	B_\varepsilon(x) \subseteq R_{r+\varepsilon }(I).
%	\]
%	Hence $B_\varepsilon(R_r(I)) \subseteq R_{r+\varepsilon}(I)$.
%\end{lemma}
%
%\begin{proof}
%	To prove this lemma, fix $x \in R_r(I)$.
%	
%	We assume $x = x_{n+1}$ and $x_{n+1} = p(x_n)+d_n$ with $|d_n|<r$ and $x_n\in R_r(I)\cup I\subseteq R_{r+\varepsilon}(I)\cup I$. Then, we have \[
%	B_{\varepsilon}(x) \subseteq B_{|d_n| + \varepsilon}(p(x_n)) \subseteq B_{r + \varepsilon}(p(x_n)).
%	\]
%	
%	By definition, since $x_n\in R_{r+\varepsilon}(I)\cup I$, $B_{r + \varepsilon}(p(x_n))\subseteq R_{r+\varepsilon}(I)$.
%	So,
%	\[
%B_{\varepsilon}(x) \subseteq
%	B_{r + \varepsilon}(p(x_n))\subseteq R_{r+\varepsilon}(I).
%	\]
%	This completes the proof.
%\end{proof}
%
%\vspace*{2ex}
%
%Notice that if $B_\varepsilon(R_r(I)) \subseteq R_{r+\varepsilon}(I)$, then $\operatorname{cl}(R_r(I)) \subseteq \operatorname{int}(R_{r+\varepsilon}(I))$. 
%
%\begin{proof}[of Theorem 1]
%	
%	We assume that $S$ is $\delta$-robustly safe.
%	
%	From Lemma 1, we can see that \begin{itemize}
%		\item $\operatorname{cl}(R(I)) \subseteq \operatorname{int}(R_\delta(I))$.
%		
%		\item Every point in $R(I)$ is at least a distance $\delta$ away from the boundary of $R_\delta(I)$.
%	\end{itemize}   
%	
%	
%	Therefore, we can partition the space into hypercubes of side length $\frac{\delta}{2\sqrt{n}}$ where $n$ is the dimension, and cover $R(I)$ with these hypercubes. Those hypercubes are in $R_\delta(I)$, and even $R_{\delta/2}(I)$.
%	
%	Put them together, we can get the following conclusion:
%	\begin{itemize}
%		\item There is a union of polytopes $\bigcup_{P \in \mathcal{P}} P$ contained in   $R_{\delta}(I)$ that covers $R(I)$.
%
%		\item Any point start from $\bigcup_{P \in \mathcal{P}} P$ following $S$ without perturbation will never enter $U$, and has a minimal distance from $U$.
%	\end{itemize}
%\end{proof}

\end{document}

### 2025-12-11 CAV2026B_cart_pole/CAV2026_a_proof.tex
update the proof

--- 2025-12-11 CAV 2026/CAV2026B/CAV2026_a_proof.tex
@@
 \begin{lemma}
-	$B_\delta(R(I))\subseteq R_\delta(I)$.
+	$B_{\delta/2}(R_{\delta/2}(I))\subseteq R_\delta(I)$.
 \end{lemma}
@@
 \begin{lemma}
-	There exists a polytopes decompose of $X=\bigcup_{Q_i\in \mathcal{Q}} Q_i$ (they may include or exclude their boundaries) and Lipschitz continuous functions $f_i$ assigned for each polytopes that can define $p$:\begin{align*}
+	There exists a finite polytopes decompose of $X=\bigcup_{i\in I,\ I\text{ is finite}} Q_i$ (they may include or exclude their boundaries) and Lipschitz continuous functions $f_i$ assigned for each polytopes that can define $p$:\begin{align*}
 		p(x) = f_i(x)\quad \text{if }x\in Q_i
@@
 \begin{lemma}
-	For each $Q_i$, there exists $\varepsilon >0$ such that $R(I)\cap Q_i$ is attractive in the region $B_\varepsilon(R(I)\cap Q_i)\cap Q_i$.
+	There exists $\varepsilon >0$ such that $R_{\delta/2}(I)$ is attractive in the region $\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$.
 \end{lemma}
@@
 \begin{proof}
-	In this proof, we use $R_i$ to denote $R(I)\cap Q_i$.
+	In this proof, we use $R_i$ to denote each $R_{\delta/2}(I)\cap Q_i$. We need to show $R_{\delta/2}(I)$ is attractive in $\bigcup_{i\in I}B_\varepsilon(R_i)\cap Q_i$.
+
+	By assumption and definition, each $Q_i$ is assigned with a Lipschitz continuous function $f_i$ with Lipschitz constant $K_i$. Let $K = \max_{i\in I} K_i$ and $\varepsilon = \frac{\delta}{2K+1}$.
+
+	For a point $y$ in $B_\varepsilon(R_i)\cap Q_i$, there exists $x\in R_i$ such that $d(x,y)<\varepsilon$. We consider $succ_p(y)$ and $succ_p(x)$.
+
+	Since $x,y\in Q_i$, $d(p(x),p(y))\leq K_i d(x,y) < K \varepsilon<\delta/2$.
+Because $x\in R_i\subseteq R_{\delta/2}(I)$, by definition, since $succ_p(y)\in B_{K_i\varepsilon}(succ_p(x))$ and $x\in R_{\delta/2}(I)$, then $succ_p(y)\in R_{\delta/2}(I)$.
+
+	This is what we want to show.
 \end{proof}
+
+\begin{lemma}
+	There is a region $A$ satisfying the following:
+	\begin{itemize}
+			\item A is a union of polytopes.
+		\item $A\supseteq R_{\delta/2}(I)$
+		\item $A\subseteq\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$
+	\end{itemize}
+	Hence, from $A$ we can construct a DT certificate.
+\end{lemma}
 

### 2025-12-11 CAV 2026/experiments.tex
global
update the table
TYPO

@@
 
-	CIFAR-C1  & Bound $\downarrow$ & ? & 27.15 & 25.94 & {\bf 24.52}& 23.29
+	CIFAR-C1  & Bound $\downarrow$ & 36.57* & 27.15 & 25.94 & {\bf 24.52}& 23.29
     \\
-	TO=1000s & $\%$ of gap $\downarrow$ & ? & 28 $\%$ & 24 $\%$& 
+	TO=1000s & $\%$ of gap $\downarrow$ & 55* $\%$ & 28 $\%$ & 24 $\%$& 
 	{\bf 20} $\%$ & 15 $\%$
@@
 
-	TO=14400s  & Bound $\downarrow$ & ? & 22.73 & {\bf 21.77} & 21.81 & 20.38
+	TO=14400s  & Bound $\downarrow$ & 31.53* & 22.73 & {\bf 21.77} & 21.81 & 20.38
     \\
-	 & $\%$ of gap $\downarrow$ & ? & 12 $\%$ & {\bf 10} $\%$& {\bf 10} $\%$& 5$\%$
+	 & $\%$ of gap $\downarrow$ & 39* $\%$ & 12 $\%$ & {\bf 10} $\%$& {\bf 10} $\%$& 5$\%$
 		\\\hline \hline
@@
 {\em Best} uses the best between our {\em Diff} and our {\em 2b+1} for each $i,j$.
-Lower gaps using {\em Best} means that there are cases where {\em Diff} is much better than {\em 2b+1}, and cases where it is the opposite.}
+Lower gaps using {\em Best} means that there are cases where {\em Diff} is much better than {\em 2b+1}, and cases where it is the opposite.
+* for CIFAR-C1, Vhagar failed to compute bounds for some of the cases.
+For such cases, we used numbers from ITNE instead (which is overperforming Vhagar in every test), so these numbers are optimistic evaluation for Vhagar.}
     \label{table.classical}

### 2025-12-11 CAV2026B_cart_pole/CAV2026_a_proof.tex

@@
 \begin{theorem}
-	If a piecewise Lipschitz continuous DT policy $p$ is robustly safe, then
+	If a piecewise Lipschitz continuous DT policy $p$ is robustly safe and $succ$ of the system is Lipschitz continuous, then
 	there exists a DT certificate for safety.
+
+	Here, a set value function $f$ is Lipschitz if there exists a constant $C$ such that for any $x,y$ with $d(x,y)=d$, $f(y)\subseteq B_{Cd}(f(x))$.
 \end{theorem}
@@
 
-The proof is in three steps: \begin{itemize}
-	\item First, we will show, $R(I)$ has an open neighborhood contained in $R_\delta(I)$ and hence disjoint with $U$.
+ Without loss of generality, we assume the Lipschitz constant for $succ$ is 1.
 
-	\item Second, we will show $R(I)$ is attractive in a neighborhood. 
+The proof is in several steps: \begin{itemize}
+	\item First, we will show, $R_{\delta/2}(I)$ has an open neighborhood contained in $R_\delta(I)$ and hence disjoint with $U$.
+
+	\item Second, we will show $R_{\delta/2}(I)$ is attractive in a neighborhood. 
 \end{itemize}
@@
 \begin{proof}
-	Trivial.
+  This is by definition.
 \end{proof}
@@
 \begin{proof}
-	In this proof, we use $R_i$ to denote each $R_{\delta/2}(I)\cap Q_i$. We need to show $R_{\delta/2}(I)$ is attractive in $\bigcup_{i\in I}B_\varepsilon(R_i)\cap Q_i$.
+	We use $R_i$ to denote each $R_{\delta/2}(I)\cap Q_i$.	By assumption, each $Q_i$ is assigned with a Lipschitz continuous function $f_i$ with Lipschitz constant $K_i$.
+Let $K = \max_{i\in I} K_i$ and $\varepsilon = \frac{\delta}{2K+2} < \delta/2$ (for $L_\infty$ distance; for other distance as $L_2$, $L_1$, $\varepsilon$ should be smaller).
 
-	By assumption and definition, each $Q_i$ is assigned with a Lipschitz continuous function $f_i$ with Lipschitz constant $K_i$. Let $K = \max_{i\in I} K_i$ and $\varepsilon = \frac{\delta}{2K+1}$.
-
-	For a point $y$ in $B_\varepsilon(R_i)\cap Q_i$, there exists $x\in R_i$ such that $d(x,y)<\varepsilon$. We consider $succ_p(y)$ and $succ_p(x)$.
+	For a point $y$ in $B_\varepsilon(R_i)\cap Q_i$, there exists $x\in R_i\subseteq Q_i$ such that $d(x,y)<\varepsilon$. We consider $succ_p(y)$ and $succ_p(x)$.
 
 	Since $x,y\in Q_i$, $d(p(x),p(y))\leq K_i d(x,y) < K \varepsilon<\delta/2$.
-Because $x\in R_i\subseteq R_{\delta/2}(I)$, by definition, since $succ_p(y)\in B_{K_i\varepsilon}(succ_p(x))$ and $x\in R_{\delta/2}(I)$, then $succ_p(y)\in R_{\delta/2}(I)$.
+By assumptions, we have $succ_p(y)\subseteq B_{\delta/2}(succ_p(x))$.
+Because $x\in R_i\subseteq R_{\delta/2}(I)$, by definition, we have that $succ_p(y)\subseteq R_{\delta/2}(I)$.
 

### 2025-12-11 CAV2026B_cart_pole/CAV2026_a_proof.tex
proof

@@
 
-	\begin{definition}
-		A system $S$ is a 5-tuple $(X,C,succ, U, I)$ that \begin{itemize}
-			\item $X\subseteq \mathbb{R}^n$ is the full space;
-			\item The control set $C$ is a set and the successor $succ$ is a function from $X\times C$ to $2^X$;
-			\item $U\subseteq X$ is the unsafe region, and nonempty set $I\subseteq X$ disjoint from $U$;
-		\end{itemize}
+\section{Preliminaries}
 
-		The system of $S$ under perturbation of at most $\delta$, $S_\delta$, is a system with the same $(X,U,C,I)$ but a $succ_\delta$ function defined as follows: \begin{align*}
-		succ_\delta(x,c) &= B_\delta(succ(x,c))\\
-		&= \{z:\exists y\in succ(x,c)\ \ d(y,z)<\delta\}.
-		\end{align*} Here $d$ can be an arbitrary kind of distance ($L_2, L_\infty$ and so on).
-	\end{definition}
-
-	Definition of policy:
+We will use $||.||$ as the $L_{\infty}$ distance.
+For $\varepsilon>0$ and a set $Y$ of configuration, we define 
+$B_\epsilon(Y) = \{z \mid \exists y\in Y, \ ||y-z||<\epsilon \}$
+the open ball of distance $\varepsilon$ around $Y$.
+A function $f : A \rightarrow 2^B$
+is Lipschitz continuous if there exists a constant $\ell$ (Lipschitz constant) such that for any $x,x'$:
+ $f(x') \subseteq B_{\ell \cdot ||x'-x||}(f(x))$.
 
 \begin{definition}
-		 \begin{itemize}
-			\item For a system $S = (X,C,succ, U, I)$, a policy $p$ is a function $p: X\rightarrow C$ and the function $succ_p: X\rightarrow 2^X$ is defined by $succ_p(x) = succ(x,p(x))$.
-			\item A policy $p$ is piecewise continuous (piecewise Lipschitz continuous) DT if there exists a decision tree (DT) $\mathcal{T}$ that defines $p$, i.e., each leaf $i$ of $\mathcal{T}$ is assigned a continuous (Lipschitz continuous) function $f_i(x)$ defined on $X$, and $p$ is defined by
-			\[
-			p(x) = f_i(x) \quad \text{if } \mathcal{T}(x)=i.
-			\]
+		A system $S$ is a 5-tuple $(X,C,succ, U, I)$ with: \begin{itemize}
+			\item $X\subseteq \mathbb{R}^n$ is the set of configurations,
+			\item The set $C$ is a set of controlled actions,
+			\item The successor function $succ: X\times C \rightarrow 2^X \setminus \emptyset$ is a Lipschitz continuous and provides the set $succ(x,c)$ of possible successor when chosing action $c$ from configuration $x$,
+			\item The set of unsafe configurations $U\subseteq X$,
+			\item and the set of initial configurations $I\subseteq X$, $>\varepsilon$ away from $U$ for some $\varepsilon$,
 		\end{itemize}
@@
 
-Now we define the reachable set $R$ and $R_\delta$.
+\paragraph{Policy}
+A policy $\sigma$ for system $S = (X,C,succ, U, I)$ is a function 
+$\sigma: X\rightarrow C$. Given $\sigma$, we define 
+$succ_\sigma: X\rightarrow 2^X$ by $succ_\sigma(x) = succ(x,\sigma(x))$.
+A run under $\sigma$ is a sequence $(x_i)_{i \in \mathbb{N}}$ such that
+$x_0 \in I$ and for all $i \geq 0$, $x_{i+1} \in succ_p(x_i)$.
+We define $Reach^S(\sigma) = \{x \mid \exists i, (x_n)_{n \in \mathbb{N}} \text{ a run under } \sigma, x_i=x\}$ the set of state reachable by $\sigma$ in $S$ (in particular from initial states $I$ of $S$).
+
+If $\sigma$ is provided as a decision tree where each leave $i$ is associated with a Lipschitz continuous function $f_i$, then it descirbes a piecewise Lipschitz continuous funciton $f$, and we can $\sigma$ a
+piecewise Lipschitz continuous DT.
+
+\paragraph{Perturbed system}
 
 \begin{definition}
-	For a system $S=(X,C,succ, U, I)$ with policy $p$, the reachable set $R(I)$ is the union of all sequence $\{x_n:n\in\mathbb{N}\}$ that is a run by $S$ and $p$, i.e., $\{x_n:n\in\mathbb{N}\}$ satisfies \begin{align*}
-		x_0&\in I\\
-		x_{n+1} &\in succ_p(x_n), n\in\mathbb{N}
-	\end{align*}
-
-	And the reachable set under perturbation of at most $\delta$ is the union of all sequence $\{x_n:n\in\mathbb{N}\}$ that is a run by $S_\delta$ and $p$, i.e., $\{x_n:n\in\mathbb{N}\}$ satisfies \begin{align*}
-		x_0&\in I\\
-		x_{n+1} &\in B_\delta(succ_p(x_n)), n\in\mathbb{N}
-	\end{align*}
+	For a system $S=(X,C,succ,U,I)$, we define its 
+	$\delta$-perturbation $S_\delta = (X,C, succ_\delta,U,I)$, where: 
+		$succ_\delta(x,c) = (succ(B_\delta(x),c))$.
+	A policy $\sigma$ of $S$ is also a policy for $S_\delta$.
+	We defined $Reach^S_\delta(\sigma) = Reach^{S_\delta}(\sigma)$.
 \end{definition}
 
-Next we define safety.
+A policy $\sigma$ of $S$ is said to be {\em safe} if $Reach^S(\sigma) \cup U = \emptyset$. Policy $\sigma$ is {\em $\delta$-robustly safe} if 
+$Reach_\delta^S(\sigma) \cup U = \emptyset$, and $\sigma$ is {\em robustly safe}
+if it is {\em $\delta$-robustly safe} for some $\delta>0$.
+
+\paragraph{Certificate}
 
 \begin{definition}
-	For a system $S=(X,C,succ, U, I)$, a policy $p$ is safe if $R(I)$ is disjoint from $U$. A policy $p$ is robustly safe if for some $\delta$, $R_\delta(I)$ is disjoint from $U$.
+	A certificate for policy $\sigma$ of system $S=(X,C,succ,U,I)$ is a function 
+	$f : X \rightarrow \{0,1\}$ such that:
+	\begin{itemize}
+		\item $I \subseteq f^{-1}(1)$,
+
+		\item $f^{-1}(1)\cap U = \emptyset$,
+
+		\item For any $x,x' \in X$ such that $f(x)=1$ and $x' \in succ_p(x)$,
+		we have $f(x')=1$.
+\end{itemize}
+If $f$ is providede as a DT, where leaves are associated with $\{0,1\}$,
+then $f$ is called a DT-certificate.
 \end{definition}
 
-Next we define certificate.
+\section{Results}
 
-\begin{definition}
-	For a system $S$ and policy $p$, a certificate is a function $f : A \rightarrow \{0,1\}$ such that:
+\begin{theorem}
+	If a piecewise Lipschitz continuous DT policy $p$ is robustly safe, then
+	there exists a DT-certificate for safety.
+
+	If a piecewise Lipschitz continuous axis aligned DT policy $p$ is robustly safe, then there exists a axis aligned DT-certificate for safety.
+
+	If a ReLU-DNN policy $p$ is robustly safe, then
+	there exists a ReLU-DNN certificate for safety. 
+\end{theorem}
+
+Let $\sigma$ be a piecewise Lipschitz-continuous policy for system $S=(X,C,succ,U,I)$ which is $\delta$-robustly safe for $\delta>0$.
+Let $R_\varepsilon=Reach^S_\varepsilon(\sigma)$ for all $\varepsilon$.
+It means that $R_\delta \cap U = \emptyset$.
+
+Consider $R = B_{\delta/4}(R_{\delta/2})$.
+We show that $R$ satisfies:
+$R_{\delta_2} \subsetneq R \subsetneq R_\delta$ 
+with:
 \begin{itemize}
-		\item $f^{-1}(1)\supseteq I$, $f^{-1}(1)\cap U = \emptyset$.
-
-		\item For any $x$ and $x'$ such that $f(x)=1$, we have $x' \in succ_p(x)$ $f(x')=1$.
+	\item $I \subseteq R$,
+	\item $B_{\delta/4}(R)\cup U = \emptyset$,
+	meaning that $R$ is away from $U$,
+	\item For all polytope $P$ on which 
+    $\sigma$ is Liptscitz continuous (say with function $f$),
+	for all $x \in P \cup R_{\delta/2}$ and 
+	$y$ with $||y-x||<\delta/4$, 
+	$succ(y,f(y)) \in R_{\delta/2}$.
 \end{itemize}
 
-A certificate $f$ is DT if there exists a decision tree (DT) $\mathcal{T}$ that defines $f$, i.e., each leaf $i$ of $\mathcal{T}$ is assigned a number $a_i \in \{0,1\}$, and $f$ is defined by
-\[
-f(x) = a_i \quad \text{if } \mathcal{T}(x)=i.
-\]
-
-\end{definition}
-
-\begin{theorem}
-	If a piecewise Lipschitz continuous DT policy $p$ is robustly safe and $succ$ of the system is Lipschitz continuous, then
-	there exists a DT certificate for safety.
-
-	Here, a set value function $f$ is Lipschitz if there exists a constant $C$ such that for any $x,y$ with $d(x,y)=d$, $f(y)\subseteq B_{Cd}(f(x))$.
-\end{theorem}
-
-From now, we fix a system $S$ and assume $p$ is a piecewise Lipschitz continuous DT policy which is robustly safe for $\delta>0$.
+IT will be sufficient to obtain a DT certificate.
+Only the third item above is non trivial.
 
 Without loss of generality, we assume the Lipschitz constant for $succ$ is 1.
-
-The proof is in several steps: \begin{itemize}
-	\item First, we will show, $R_{\delta/2}(I)$ has an open neighborhood contained in $R_\delta(I)$ and hence disjoint with $U$.
-
-	\item Second, we will show $R_{\delta/2}(I)$ is attractive in a neighborhood. 
-\end{itemize}
-
-\begin{lemma}
-	$B_{\delta/2}(R_{\delta/2}(I))\subseteq R_\delta(I)$.
-\end{lemma}
-
-\begin{proof}
-  This is by definition.
-\end{proof}
 

### 2025-12-12 CAV2026B_cart_pole/CAV2026_a_proof.tex
update

@@
 	$y$ with $||y-x||<\delta/4$, 
-	$succ(y,f(y)) \in R_{\delta/2}$.
+	$succ(y,f(y)) \subseteq R_{\delta/2}$.
 \end{itemize}
@@
 \end{proof}
+
+To prove the third claim, we need to use the definition that $succ$ is also Lipschitz.
 
@@
 
-\begin{lemma}
-	There is a region $A$ satisfying the following:
-	\begin{itemize}
-			\item A is a union of polytopes.
-		\item $A\supseteq R_{\delta/2}(I)$
-		\item $A\subseteq\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$
-	\end{itemize}
-	Hence, from $A$ we can construct a DT certificate.
-\end{lemma}
-
 %\begin{lemma}
-%	Let $S$ be a system with policy $p$ and initial region $I$. For any $x\in R_r(I)$ and any $\varepsilon$, we have
-%	\[
-%	B_\varepsilon(x) \subseteq R_{r+\varepsilon }(I).
-%	\]
-%	Hence $B_\varepsilon(R_r(I)) \subseteq R_{r+\varepsilon}(I)$.
+%	There is a region $A$ satisfying the following:
+%	\begin{itemize}
+%			\item A is a union of polytopes.
+%		\item $A\supseteq R_{\delta/2}(I)$
+%		\item $A\subseteq\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$
+%	\end{itemize}
+%	Hence, from $A$ we can construct a DT certificate.
 %\end{lemma}
-%
-%\begin{proof}
-%	To prove this lemma, fix $x \in R_r(I)$.
-%	
-%	We assume $x = x_{n+1}$ and $x_{n+1} = p(x_n)+d_n$ with $|d_n|<r$ and $x_n\in R_r(I)\cup I\subseteq R_{r+\varepsilon}(I)\cup I$. Then, we have \[
-%	B_{\varepsilon}(x) \subseteq B_{|d_n| + \varepsilon}(p(x_n)) \subseteq B_{r + \varepsilon}(p(x_n)).
-%	\]
-%	
-%	By definition, since $x_n\in R_{r+\varepsilon}(I)\cup I$, $B_{r + \varepsilon}(p(x_n))\subseteq R_{r+\varepsilon}(I)$.
-%	So,
-%	\[
-%B_{\varepsilon}(x) \subseteq
-%	B_{r + \varepsilon}(p(x_n))\subseteq R_{r+\varepsilon}(I).
-%	\]
-%	This completes the proof.
-%\end{proof}
-%
-%\vspace*{2ex}
-%
-%Notice that if $B_\varepsilon(R_r(I)) \subseteq R_{r+\varepsilon}(I)$, then $\operatorname{cl}(R_r(I)) \subseteq \operatorname{int}(R_{r+\varepsilon}(I))$. 
-%
-%\begin{proof}[of Theorem 1]
-%	
-%	We assume that $S$ is $\delta$-robustly safe.
-%	
-%	From Lemma 1, we can see that \begin{itemize}
-%		\item $\operatorname{cl}(R(I)) \subseteq \operatorname{int}(R_\delta(I))$.
-%		
-%		\item Every point in $R(I)$ is at least a distance $\delta$ away from the boundary of $R_\delta(I)$.
-%	\end{itemize}   
-%	
-%	
-%	Therefore, we can partition the space into hypercubes of side length $\frac{\delta}{2\sqrt{n}}$ where $n$ is the dimension, and cover $R(I)$ with these hypercubes.
-Those hypercubes are in $R_\delta(I)$, and even $R_{\delta/2}(I)$.
-%	
-%	Put them together, we can get the following conclusion:
-%	\begin{itemize}
-%		\item There is a union of polytopes $\bigcup_{P \in \mathcal{P}} P$ contained in   $R_{\delta}(I)$ that covers $R(I)$.
-%
-%		\item Any point start from $\bigcup_{P \in \mathcal{P}} P$ following $S$ without perturbation will never enter $U$, and has a minimal distance from $U$.
-%	\end{itemize}
-%\end{proof}
 
